### 2012-05-30 notes/coop.tex
initial commit

\documentclass{article}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{times}

\begin{document}

Of all solution concepts of cooperative games, the core is probably the easiest to underestand. It is the set of all feasible outcomes (payoffs) that no player (participant) or group of participants (coalition) can improve upon by acting for themselves. Put differently, once an agreement in the core has been reached, no individual and no group could gain by regrouping. It stands to reason that in a free market outcomes should be in the core; economic activities should be advantageous to all parties involved. Indeed the concept (though not the term) appeared already in the writings of Edgeworth (1881) (who used the term ``contract curve''), and in the deliberations concerning allocation of the costs involved in the Tennessee Valley Project [Straffin and Heaney (1981)].

Unfortunatly, for many games feasable outcomes which cannot be improved upon may not exist - the cake may not be big enough. In such cases one possibility is to ask that no group could gain much by recontracting. It is as if communications and coalition formations are costly. The minimum size of the set of feasible outcomes required for non-emptiness of the core is given by so-called balancedness condition. The sets containing outcomes upon which nobody could improve by much are called $\epsilon$-cores.

let $N = \{1,2,...,n\}$ be the set of all players. A subset of $N$ is called a \emph{coalition}. The \textit{characteristic function} (of the worth function) is a real-valued function $v$ defined on the coalitions, such that:

\begin{equation}\label{eq:v0}
v(\emptyset) = 0
\end{equation}

Games with tranferable utility (TU Games)
\begin{itemize}
	\item Any two agents can compare their utility
	\item Utility can be transferred between agents
\end{itemize}

Definition: A game v is called $convex$ if for all coalitions S,T,
\begin{equation}\label{eq:con1}
v(S) + v(T) \leq v(S \cup T) + v(S \cap T).
\end{equation}

Consider first the case of a finite set or players $N$. Let \pi be a permutation of $N$.

Theorem (Shapely)

\end{document}

### 2012-06-06 notes/coop.tex
Added a new file

@@
 \documentclass{article}
-\usepackage{array}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{verbatim}
-\usepackage{graphicx}
-\usepackage{times}
 
@@
 
+\hline
+
+A set of tasks needs to be performed,
+\begin{itemize}
+	\item they require different expertises
+	\item they may be decomposed.
+\end{itemize}
+
+Agents do not have enough resource on their own to perform a task.
+
+Find complementary agents to perform the tasks
+\begin{itemize}
+	\item robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
+	\item transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
+\end{itemize}
+
+Issues:
+\begin{itemize}
+	\item What coalition to form?
+	\item How to reward each each member when a task is completed?
+\end{itemize}
+
+\hline
+
 \end{document}

### 2012-06-07 notes/coop.tex
Notes

@@
 \documentclass{article}
+
+\usepackage{amsfonts}
+\usepackage{amssymb}
 
@@
 
-Consider first the case of a finite set or players $N$. Let \pi be a permutation of $N$.
+Consider first the case of a finite set or players $N$. Let $\pi$ be a permutation of $N$.
 
@@
 
-\hline
+\hrule
 
@@
 
-\hline
+\hrule
 
+In this paper we denote by $\mathbb{R}$ the set of all real numbers. The $general coalition game$ (or beifly the game) is a pair ($I$, $V$),
+where $I$ is a non-empty and finite set and $V$ is a mapping associating any subset $K$ of $I$ witha subset of the real space $\mathbb{R}^I$ and preserving the following properties for any $K \subset I$.
+(1..4)
+The elements of the set $I$ are called players, its subsets are $coalitions$ and its partitions into non-empty disjoint coalitions are called $coalition structures$.
+The real-valued vectors from $\mathbb{R}^I$ are called $imputations$ and the sets $V(K), K \subset I,$ represent the sets of all imputations achievable by the coalition $K$.
+The mapping $V$ of $2^I$ into the class of subsets of $\mathbb{R}^I$ is called $generalized characterestic function$.
 \end{document}

### 2012-06-11 notes/coop.tex
Added bib
Report

@@
 The mapping $V$ of $2^I$ into the class of subsets of $\mathbb{R}^I$ is called $generalized characterestic function$.
+
+\hrule
+
+A $coalitional game$ is a pair $G = (N, v)$, where N is a set of players, and v is a function associating with each coalition $S \subset N$ the worth $v(S) \in \mathbb{R}$ that players in $S$ obtain by collaborating with each other.
+A fundamental problem for coalitional games is to characterize the most desirable outcomes in terms of appropriate notions of worth distributions, which are called solution concepts.
+Traditionally, this problem has been formulated over games that are superadditive, i.e., $v(S \cup T ) \geq v(S) + v(T)$ is assumed to hold, for eachpair of disjoint coalitions $S$ and $T$.
+Indeed, on superadditive games, the grand-coalition consisting of all the players in N forms and, accordingly, solution concepts just suggest how the total worth $v(N)$ can be divided among them in a way that is fair and stable [Osborne and Rubinstein, 1994].
+While being rather appealing from a conceptual viewpoint, superadditivity might however not hold in several social environments because of a plethora of different reasons, ranging from normative considerations, to information (observability) imperfections, and to technological constraints (cf.
+[Greenberg, 1994]).
+Under these circumstances, players might want to organize themselves in a coalition structure, i.e., in a partition $\pi$ of $N$ consisting of disjoint and exhaustive coalitions.
+By doing so, the total available worth $\sum_{C \in \pi} v(C)$ might happen to be greater than the worth $v(N)$ associated with the grand-coalition.
+Whenever this is the case, classical solution concepts are not appropriate, and stable outcomes have to be characterized from the "`coalition structure"' perspective, as it was first suggested by Aumann and Dreze [1974].
+As an example, the core of a coalitional game, which is probably the best-known solution concept, finds a counterpart in the coalition structure core—formal definitions are in Section 2 \cite {Greco11}.
+
+\hrule
+
+For any coalition structure $\pi$, let $CS-v(\pi)$ denote the total worth $\sum_{C \in \pi} v(C)$.
+Let $sw(G)$ be the $social welfare$ of $G$, i.e., the maximum worth $CS-v(\pi)$ over all the possible coalition structures $\pi$.
+The set of all coalition structures $\pi$ such that $CS-v(\pi) = sw(G)$ is denoted by $CS-opt(G).$
+Recall that G is cohesive if $v(N) \geq CS-v(\pi)$, for each coalition structure $\pi$ [Osborne and Rubinstein, 1994], and that, though not necessarily superadditive, the grand-coalition anyway always forms in cohesive games.
+Define $G = (N, v)$ as the cohesive game, called the $cohesive cover$ of G, where $v(S) = v(S)$ for each coalition $S \subset N$, and $v(N) = sw(G)$ \cite {Greco11}.
+
+\hrule
+
+\bibliographystyle{plain}
+\bibliography{ehsan}
+
 \end{document}

### 2012-07-31 notes/coop.tex
added new notes
Added repeated games

@@
 \begin{document}
+
+\section{Game Thoery}
+
+\subsection{Repeated Games}
+
+In \cite {ShohamLeytonBrown09} section 6.1 there is discussion of repeated games.
+
+When the infinitely repeated game is transformed into extensive form, the result is an infinite tree.
+So the payoffs cannot be attached to any terminal nodes, nor can they be defined as sum of the payoffs in the stage games )which in general willbe infinite).
+There are two common ways of defining a player's payoff in an infinitly repeated game to get around this problem.
+
+\emph{Average reward: }
+Agent cares more about his well-being in the near term than in the long term.
+\begin{equation}\label{eq:average_reward}
+\lim \limits_{n \to \infty}\frac{\sum_{j=1}^k r_i^{(j)}}{k}
+\end{equation}
+
+\emph{Discount reward: }
+Agent cares about the future just as much as he cares about the present.
+\begin{equation}\label{eq:discount_reward}
+\sum_{j=1}^\infty \beta^j r_i^{(j)} \qquad where \qquad 0 \leq \beta \leq 1
+\end{equation}
+
+\subsection{Learning}
+
+\section{Cooperative Games}
 
@@
 
+\cite {RePEc:eee:gamhes:2} Our social life is conducted almost entirely within the structure of groups of agents: individual consumers are households or families; individual producers are firms which are large coalitions of owners of different factors of production;
+
+\hrule
+
 \bibliographystyle{plain}

### 2012-08-10 notes/statistics/probability.tex
Changes

\documentclass{article}

\usepackage{amsfonts}
\usepackage{amssymb}

\begin{document}

\section{General}

In statistics, "empirical" quantities are those computed from observed values, as opposed to derived from theoretical considerations.

\hrule

\cite{koch2010introduction}If the statements $A_1,A_2,...A_n$ are not only mutually exclusive but also $exhustive$ which means that the background information $C$ stipulates that one and only one statement must be true and if one is true the remaining statements must be false, then we obtain with (2.13) and (2.15) from (2.21)
\begin{equation}\label{eq:exhustive}
P(A_1 + A_2 + ... + A_n | C) = \sum_{i=1}^{n}P(A_i|C) = 1.
\end{equation}

\hrule

\bibliographystyle{plain}
\bibliography{ehsan}

\end{document}

### 2012-08-14 notes/coop.tex
Added
Changes

@@
 
-In \cite {ShohamLeytonBrown09} section 6.1 there is discussion of repeated games.
+In \cite {ShohamLeytonBrown09} section 6.1 and chapter 8 of \cite{RePEc:mtp:titles:0262650401}, there is discussion of repeated games.
 
@@
 
+\cite{Chalkiadakis_simplecoalitional} Theorem 3 provides an efficient algorithm for checking wether the core is non-empty or wether a given demand vector is in the core.
+Indeed, we can first check, for each player $i \in N$, if $i$ is a veto player (by Theorem 2, this can be done in polynomial time).
+The core is non-empty if the answer is "`yes"' for at least one $i \in N$.
+Furthermore, to check if d is in the core, we can check if $d_i > 0$ for any non-veto player $i$; if answer is "`yes"', d is not in the core.
+
 \bibliographystyle{plain}

### 2012-09-01 notes/ideas.tex
changes

\documentclass{article}

\usepackage{amsfonts}
\usepackage{amssymb}

\begin{document}

\section{Game Thoery}

\subsection{Weighted Voting Games (WVGs)}

\cite{Chalkiadakis_simplecoalitional} A WVG is described by its set of players $N$, a vector of players' $weights$ w = (w_1,...,w_n), $w_i \in \mathbb{R}$ for $i \in N$, and a $threshold$ $q \in \mathbb{R}$ we write $G = (N; w; q)$. The utility function $u(S)$ of a game $G = (N; w; q)$ is given by $u(S) = 1$ iff $\sum_{i \in S} w_i \geq q.$

In some cases, the only acceptable outcome of a game is the formation of the $grand coalition$, i.e., the coalition of all players $N$. However, in many multi-agent scenarios it is more natural for agents to split into groups so that each group performs its own task. This is captured by the notion of a $coalition structure$, which is a prtition of the set of agents $N$.

\subsubsection{The Idea}
The idea here can be make the utility function 0 or 1 based on a threshold where that amount of web services or agents can perform a task. Like instead of having real utilities we say agents 1,2,3 can do the task we can make it function of their QoS parameters.

\bibliographystyle{plain}
\bibliography{ehsan}

\end{document}

### 2012-09-01 notes/notes.tex
changes

--- 2012-09-01 notes/ideas.tex
@@
 
-\section{Game Thoery}
-
-\subsection{Weighted Voting Games (WVGs)}
-
-\cite{Chalkiadakis_simplecoalitional} A WVG is described by its set of players $N$, a vector of players' $weights$ w = (w_1,...,w_n), $w_i \in \mathbb{R}$ for $i \in N$, and a $threshold$ $q \in \mathbb{R}$ we write $G = (N; w; q)$.
-The utility function $u(S)$ of a game $G = (N; w; q)$ is given by $u(S) = 1$ iff $\sum_{i \in S} w_i \geq q.$
-
-In some cases, the only acceptable outcome of a game is the formation of the $grand coalition$, i.e., the coalition of all players $N$.
-However, in many multi-agent scenarios it is more natural for agents to split into groups so that each group performs its own task.
-This is captured by the notion of a $coalition structure$, which is a prtition of the set of agents $N$.
-
-\subsubsection{The Idea}
-The idea here can be make the utility function 0 or 1 based on a threshold where that amount of web services or agents can perform a task.
-Like instead of having real utilities we say agents 1,2,3 can do the task we can make it function of their QoS parameters.
-
-\bibliographystyle{plain}
-\bibliography{ehsan}
+hi
 

### 2012-10-09 notes/statistics/probability.tex
Changes
changes

@@
 
+\cite{koch2010introduction} page 31-32:
+
+$p(x|y,C) \propto p(x|C)p(y|x,C)$
+
+The components if the descrete or continuous random vector $x$ are now identified with unkown parameters which were already mentioned in Chapter 2.2.
+The binomial distribution (2.61) possesses, for instance, the parameters $n$ and $p$.
+They may take on different values, but a pair of values determines the binomial distribution.
+In the following example $p$ is an unkown parameter.
+In general, unknown parameters are understood to be quantities which describe unkown phenomena.
+The values of the parameters are unknown.
+To estimate them, measurements, observations or date have to be taken which contain information about unkown parameters.
+This was already indicated in Chapter 2.2.
+
+The vector of values of the random vector $x$ of unkown parameters is also called $x$ becuase of (2.76) to (2.78).
+The set of vectors $x$, that is the set of vectors which contain all possible values for the parameters, is called the $parameter space X$, hence we have $x \in X$ in (2.121) or (2.122).
+The values $y$ of the descrete or continues random vector $y$ represent given data.
+The density function $p(x|C)$ given the background information C contains information about the parameters $x$ before the daya $y$ have been taken.
+One calls $p(x|C)$ tjerefore $prior density function$ or $prior distribution$ for the parameters $x$.
+It contains the prior information about the unknown parameters.
+By taking into account the observations $y$ the density function $p(x|y,C)$ follows.
+It is called $posterior density function$ or $posterior distribution$ for the parameters $x$.
+Via the density function $p(y|x,C)$ the information available in the data $y$ reaches the parameters $x$.
+Since the data $y$ are given, thuis density function is not interpreted as a function of the data $y$ but as as a function of the parameters $x$, and it is called the $likelihood function$, Thus,
+
+posterior density function $\propto$ prior density function $\times$ likelihood function.
+
 \bibliographystyle{plain}
-\bibliography{ehsan}
+\bibliography{prob}
 

### 2012-11-04 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Added paper

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{times}
%\usepackage{cite}
%\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{verbatim}

%\newtheorem{property}{\textbf{Property}}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Analyzing Coopetition Strategies of Services within Communities}

% a short form should be given in case it is too long for the running head
\titlerunning{Lecture Notes in Computer Science}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%

\author{Babak Khosravifar$^1$
\and Mahsa Alishahi$^1$ \and Ehsan Khosrowshahi Asl$^1$ \and Jamal
Bentahar$^1$\and Rabeb Mizouni$^2$\and Hadi Otrok$^2$}

%

% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published

\institute{$^1$Concordia University, Canada, $^2$Khalifa University, UAE\\
$b\_khosr@encs.concordia.ca$, $m\_ali@encs.concordia.ca$, $e\_khosr@encs.concordia.ca$,\\$bentahar@ciise.concordia.ca$,
$rabeb.mizouni@kustar.ac.ae$,$hadi.otrak@kustar.ac.ae$}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Lecture Notes in Computer Science} \tocauthor{Authors'
Instructions} \maketitle

\begin{abstract}
%Web services are business applications having the capability to
%cooperate within groups to increase the efficiency of serving
%customers.
Recently, a number of frameworks have been proposed to
aggregate web services within communities for the purpose of
enhancing their capabilities with respect to providing the
required services. Most of the proposed frameworks suggest that
web services within these communities are competing but also
exhibit cooperative behavior, so web services are said to be
coopetitive. However, deciding which strategy to adopt, which
means competing or cooperating is still an open question. The
purpose of this paper is to answer this question by discussing a
mechanism web services can use to effectively choose interacting
strategies which bring maximum utility. In this direction, we
investigate web services' characteristics and their expected
utilities over different strategies. We enable web services that
are hosted in communities with reasoning capabilities to enhance
their quality of  strategic interacting mechanisms as decision
making procedures. The ultimate objective is to measure the
threshold that web services can use in order to decide about
different interacting strategies. Moreover, we develop a simulated
environment where we analyze different scenarios and verify the
obtained theoretical results using parameters from a real web
services dataset. \keywords{Web services; Reputation; Strategies.}
\end{abstract}

\section{Introduction}\label{Introduction}
Web services are developed to continuously interact with others
that could be different types of web services or service
consumers. Abstracting and associating web services with
knowledge-empowered agents without changing the web services
implementation benefit them from interactions that those agents
are able to manage \cite{Jacyno,Khosravifar1,Yassine}. That means
web services are no more considered as simply passive components
but as intelligent entities that enjoy autonomy and selfishness,
two significant properties in business settings where competition
is a key factor \cite{Jurca2,Khosravifar2}. Those web services
follow two different strategies of cooperating or competing
towards serving service consumers and increasing their utilities
in terms of payoffs. Analyzing web services acting strategies in
such a context in terms of deciding which strategy to choose is an
open and challenging problem. Our main contribution in this paper
is to address this problem and enable web services to cope with
strategic decision making in a particular situation.

There are a number of related proposals that take into account the
correlation between web services and the ways these services
coordinate their actions to accomplish a task. In
\cite{Jurca,Jurca2,Kalepu,Malik,Maximilien1}, the authors propose
to rank web services based on their reputation in the system and
to use this ranking as a means to facilitate cooperation of
services. In those models, services rely on one another using the
reputation ranking system. There are other models that facilitate
cooperation mechanisms using transaction-based web services
\cite{Rosario} and communities that host and gather web services
having similar or complementary functionalities but different QoS
parameters
\cite{Khosravifar1}. %There are also some frameworks
%\cite{Ferguson,Ferguson2} that consider game-theoretic analysis on
%the expected payoffs obtained via different acting strategies.
However, deciding about which strategy to choose when web services
are competing but still need to cooperate to accomplish complex
tasks is still an open issue. We propose analyzing those different
strategies to help web services in their decision making process
when these
web services function within communities. %We summarize most of
%these proposals and concentrate on strategic decision making
%system that ranks web services in the community and analyze their
%effective interacting strategies to accomplish continuous
%requested tasks.
The objective is to enable web services to reasonably evaluate and
decide over their coopetition strategies, which means when to
compete and when to cooperate.

More precisely, we propose a mechanism within which web services
in the community could choose either to compete for an announced
task, or to cooperate with other competing web
services in the same community to accomplish some subtasks of the announced task. %We
%equip intelligent web services to follow a reasoning technique to
%choose best interactive strategy (coopetative attitude, which is
%categorized to compete and cooperate). In the proposed system,
We explore details behind the strategic decision making procedures
and enable web services to apply different techniques to constrain
high efficiency and obtain the maximum utility. We investigate web
services' expected payoffs and the involved probabilities that are
used to choose over the two interacting
strategies. %This mechanism is useful for systems hosting a number
%of intelligent entities that are involved in some cooperative
%work.
As intelligent entities, web services require a reasoning
technique that enhances their abilities over best acting
strategies and the attitude they could exhibit to yield maximum
utility. In this paper, we obtain some theoretical results about
the decision making algorithm that could be used by a typical web
service. We also implement a simulation environment with a number
of communities hosting a number of web services having parameters
extracted from a real dataset \cite{Almasri}\footnote{The
implemented environment includes the QWS dataset by Eyhab Al-Masri
and Qusay H. Mahmoud freely available at:
www.uoguelph.ca/~qmahmoud/qws.}. This dataset represents $2507$
real web services that exist on the web. It includes the QoS
values of $9$ parameters including availability, throughput and
reliability. These QoS values were determined by monitoring the
web services over a $6$ day period. We equip some of those web
services with our proposed strategic decision making procedure and
compare the performance of the equipped services against other
ordinary web services. We provide detailed discussions over the
implemented environment and verify the effectiveness of the
proposed mechanism.

The rest of the paper is organized as follows. Section \ref{The
Proposed Framework} is dedicated to the presentation of some
preliminaries about the system design that are needed to
understand the proposed model. Section \ref{Theoretical Results}
is devoted to the theoretical presentation of our model along with
web services' competitive and cooperative strategies. Section
\ref{Experimental Results} outlines the experimental results and a
detailed comparison of the equipped web services with strategic
reasoning techniques with the ordinary services. Finally, related
work and some conclusions are discussed in Section
\ref{Conclusion}.

\section{The Proposed Framework}\label{The Proposed Framework}
In this Section, we first present the architecture of the proposed
model. We explore the characteristics of intelligent web services
and their network. We link this architecture to the implemented
system where we investigate the services' coopetitive attitudes.
We compute the involved system parameters and explain the web
services' interactive strategy profiles by highlighting their
coopetitive choices.

\begin{figure}[h]
\centering
\includegraphics[scale=1]{architecture++.eps}
\caption{Web services are partitioned into competitive and
cooperative sets. Competitive web services may get tasks directly
from the master web service and they can share it with other
cooperative web services in their collaborative networks.}
\label{architectureFigure}
\end{figure}

\subsection{The Architecture}

The proposed system consists of three types of autonomous entities
with different goals.

1) \textit{Web Services} that reside inside a community which
aggregates a number of functionally similar or complementary web
services as a group (more details about communities of web
services are given in \cite{Khosravifar2010}). Within the same
community, each web service might have a network consisting of
some other web services that might get involved in a cooperative
work (e.g. composition and substitution). As web services are also
competing, particularly when they provide similar functionalities,
each one of them aims to maximize its individual income (i.e. the
payoff) by adopting a given strategy.

2) \textit{Master Web Service} is the manager and representative
of the community of web services. Among other functionalities, the
master web service is responsible for allocating the tasks to web
services within the community. After the task being accomplished,
the master rewards or penalizes the associated web service with
respect to its reputation as a member of the community. The master
is equipped with a task allocation mechanism aiming to increase
service users satisfaction and eventually the community's market
share in the whole system.

3) \textit{Users} generate tasks with specified QoS. In our
proposed system, tasks are continuously being generated and user
satisfaction is abstracted since we focus on web services'
interactive strategies.

Figure \ref{architectureFigure} illustrates the architecture of a
typical community aggregating a number of web services with
different interactive strategies. Some of them compete for the
task where they directly deal with the master. Some others
cooperate in the associated task where they only deal with the
competed web service as the task leader and do not directly
interact with the master (the master deals only with the web
service that has bid for the task, which is responsible of
choosing its collaborative network). In both sets, some web
services are for certain moments out of any collaboration network.
We highlight details of the interactive strategies in the rest of
this section.
%Figure \ref{algorithm1} %exposes the details of task allocation mechanism that is used to select the web services.
In the proposed system, the master sorts the competing web
services based on some parameters (such as reputation) that we
explain in the rest of this section. If the web service is busy or
unwilling to take the task, the master allocates the task to the
second competing web service in the list. There is a chance that
some tasks could not be assigned to any web service. These tasks
are accumulated to the task pool to be allocated in the next task
allocation round. Upon allocation of the task, the web service is
responsible to offer the required QoS that is stated in the task
being generated by a consumer. Afterwards,  the master rewards or
penalizes the competing web service by upgrading or degrading its
reputation according to the offered QoS compared with the required
one. This comparison influences the sorting mechanism used by the
master to allocate the tasks in further task allocation rounds.

%\begin{figure}[h]
%\centering
%\begin{tabular}{l}
% \hline\hline
%\textbf{Algorithm} Task Allocation Mechanism Used by Master Web Service\\  \hline
%  \small\textbf{CompetitiveWebServices}: Make a list of all web services ready to compete flag equal to %true\\
%  SortTaskPool(taskPool)\\
%  \small\textbf{TaskToBeDone}: Select a random number of undone tasks to be allocated\\
%  \small 1: \textbf{foreach} task \textbf{in} CompetitiveWebServices\\
%  \small 2: ~~~~~ \textbf{while} (!task.assigned)\\
%  \small 3: ~~~~~~~~~~~ \textbf{foreach} webservice \textbf{in} CompetitiveWebServices\\
%  \small 4: ~~~~~~~~~~~~~~~~~ \textbf{if}(!webservice.busy)\\
%  \small 5: ~~~~~~~~~~~~~~~~~~~~~~~ \textbf{if}(webservice.acceptTheTask)\\
%  \small 6: ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~webservice.NumberOfOfferedTask+=1\\
%  \small 7: ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~webservice.NumberOfAcceptedTask+=1\\
%  \small 8: ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~webservice.CurrentAssignedTask=task\\
%  \small 9: ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~task.assigned=true\\
%  \small 10: ~~~~~~~~~~~~~~~~~~~~~~~~~~~\textbf{break}\\
%  \small 11: ~~~~~~~~~~~~~~~~~~~~~~ \textbf{else}\\
%  \small 12: ~~~~~~~~~~~~~~~~~~~~~~~~~~~webservice.NumberOfOfferedTask+=1\\
%  \small 13: ~~~~~~~~~~~~~~~~~~~~~~~~~~~webservice.NumberOfRefusedTask+=1\\
%  \end{tabular}
%%
%\caption{Master web service task allocation algorithm that is used to allocate continuous tasks to %appropriate competitive web services.} \label{algorithm1}
%\end{figure}

\subsection{System Parameters}
In this part, we demonstrate the involved parameters and their
corresponding formulations and explanations.

\textbf{Task QoS} ($T_{QoS}^t$) is the required QoS metric for a
specific task at time $t$. Users define tasks with specific QoS
requirements such as response time, availability, and
successability (or accuracy) \cite{Erbin}. We aggregate and
normalize these metrics to a value between $0$
and $1$. %Throughout this paper, we refer to this value as
%$T_{QoS}$.

\textbf{Web service QoS} ($QoS_w^t$) is the QoS provided by the
web service $w$ after performing a task at time $t$. Again the
metrics that contribute in computing this QoS are aggregated and
normalized to a value between $0$ and $1$. The offered quality
might or might not meet the required task quality $T_{QoS}^t$. In
the latter case, the service user would be disappointed and a
negative satisfaction feedback is expected. In our proposed
system, both cases are considered when calculating the web
services' reputation.

%\textbf{NTD} is the number of tasks completed by a web service.

\textbf{Budget} ($B_w^t$) is the amount of money the web service
$w$ has in its disposal at time $t$, which helps pay for the
community membership fees ($\epsilon$) and is one of the
parameters that the web service considers when deciding about
getting involved in a competition or not. This parameter has been
used in other service computing settings such as \cite{Erbin}.

\textbf{Reputation} is a factor in any online community where
trust is important. Without any trust enabling mechanism, users
cannot differentiate between services, specially the ones which
offer the same type of service. Reputation mechanisms usually
aggregate users' experiences and in our case it strongly depends
on QoS that each web service provides. Users define tasks with
specific quality $T_{QoS}^t$, therefore after performing a task
with $QoS_w^t$, the reputation of $w$ gets evaluated by the master
web service. $Rep_{w}^{t}$ refers to the reputation of $w$ at time
$t$.

In Equation \ref{repr}, we compute the reward that the master
computes considering the task QoS compared with the web service
offered quality $QoS_w^t$. In case the offered quality meets user
expectations, the reward value would be positive. In this system,
we consider a small value as default rewards $\eta$ which the
master considers together with the proportional level of
satisfaction as a weighted value (by $\upsilon$). In this case,
the higher the offered quality is, the more weighted reward is. In
case the offered quality did not meet the user expectations, the
reward would be negative. In this case, we also have a default
penalty value $\rho$ (where $\rho>\eta$) together with the
weighted proportional difference. The idea is to harshly penalize
the web services rather than rewarding them. To this end, rational
web services should carefully analyze their capabilities once the
available tasks are announced. In our proposal, web services have
the goal of increasing their budget, which is directly related to
their reputation. Thus, they have to decide strategically how to
maximize this value.

\begin{equation} \label{repr}
reward_w^t= \begin{cases}
\eta + \frac{QoS_w^t}{T_{QoS}^t+QoS_w^t} * \upsilon  & \text{if $T_{QoS}^t\leq QoS_w^t$;}\\
-(\rho + \frac{T_{QoS}^t}{T_{QoS}^t+QoS_w^t} * \upsilon) & \text{otherwise.}\\
\end{cases}
\end{equation}

The assigned reputation value is updated by the computed reward
value. The computed reputation of web services is bounded by the
minimum and maximum reputation values $0$ and $1$. % to constrain
%the balance the cooperative community of web services. The updated
Let $\Gamma = Rep_{w}^{t} + reward_w^t$. The updated reputation
value is then computed as follows:

\begin{equation}\label{repz}
%Rep_{w}^{t+1} = Rep_{w}^{t} + reward
%\end{equation}
%\begin{equation*}
Rep_{w}^{t+1} = \begin{cases}

\Gamma & \text{if $ 0 \leq \Gamma \leq 1$;}\\
0  & \text{if $\Gamma < 0$;}\\
1 & \text{if $\Gamma > 1$.}\\
\end{cases}
\end{equation}

\textbf{Growth Factor} is a parameter which declares web services'
performance based on their recent strategies and activities.
Growth factor is relative to web services' reputation and QoS.
This parameter is the main variable a typical web service uses to
decide which strategy to adopt. The details about the decision
making process is described in Section \ref{Theoretical Results}.
We use Equation \ref{eq:growthfactor} to compute the growth factor
$G^t_w$ of the web service $w$ at time $t$. The growth factor
function should be monotonically increasing in $QoS_w^t$,
$Rep^t_w$ and $B_w^t$, which is satisfied by the equation and this
could be easily proven by calculating the partial derivatives of
this function in 1) $QoS_w^t$; 2) $Rep^t_w$; and then 3) $B_w^t$
and show that they are all positive. The contribution of the
budget $B_w^t$ in the calculation of the growth factor should be
proportional to the ideal budget $\beta_w \times t$ where the web
service receives all the offered tasks during the periods $t$. The
parameter $\beta_w$ denotes the profit obtained considering the
mean received service fee $\mu_w$ and the cost of community
membership $\epsilon$. The mean service fee depends on the
strategy adopted by the web service because a competitive service
receives higher fees $\mu_{w, CM}$ compared to a cooperative one
$\mu_{w, CO}$ ($\mu_{w, CM} > \mu_{w, CO}$). The motivation behind
this is that a competitive web service for a given task is the
leader for that task while other cooperative web services are
performing specific subtasks as asked by the leader.

\begin{equation}\label{eq:growthfactor}
G^t_w = \frac{Rep^t_w + QoS_w^t+\frac{B_w^t}{t\times \beta_w}}{3}
\end{equation}
\begin{equation*}
\beta_w=\mu_{w}-\epsilon, ~~~~~~\mu_{w} \in\{\mu_{w, CM}, \mu_{w,
CO}\}
\end{equation*}

The above explained parameters and other additional parametrs
which we will use in the rest of this paper are listed in Table
\ref{Preliminaries}.

\begin{table}
\centering
\caption{List of proposed system parameters.}
\begin{tabular}{|c|c||c|c|}
\hline
\textbf{Notation} & \textbf{Definition} & \textbf{Notation} & \textbf{Definition}\\
\hline\hline
$T_{QoS}^t$ & Required task QoS at time $t$ & $QoS_w^t$ & Web service $w$ QoS at time $t$ \\
$B_w^t$ & Budget associated to web service $w$ at time $t$ & $Rep^t_w$ & Reputation assigned for $w$ at time $t$\\
$Reward_w^t$ & The reward to update the reputation & $G^t_w$ & The growth factor of $w$ at time $t$\\
$\epsilon$ & The community membership fee & $\pi_{w,CM}^t$ & Competition payoff of $w$ \\
$\pi_{w,CO}^t$ & Cooperation payoff of $w$ & $p_{w,CM}^t$ & Competition probability of $w$ at time $t$\\
$p_{w,CO}^t$ & Cooperation probability of $w$ at time $t$& $COF_w^t$ & Cooperation fee of $w$ at time $t$\\
$\beta_w$ & Profit of $w$& $\mu_{w, CM}$ & Mean service fee for competing $w$ \\
$\mu_{w, CO}$ & Mean service fee for cooperating $w$ & $\tau_w^t$ & Coopetitive threshold of $w$ at time $t$ \\
$P_w^t$ & Probability of competing for $w$ at time $t$& $U_w^t$ & Utility of $w$ at time $t$\\
\hline
\end{tabular}
\label{Preliminaries}
\end{table}

\subsection{Web Service Interactive Strategies}

The main goal of each individual web service is to increase its
income (payoff). This income can be earned from tasks (or
requests) done by this web service. In our model, web services can
decide to compete to get a task from the master web service or to
cooperate with other web services in a given collaborative network
(the way a collaborative network is set by a leader is based on
the cooperative web services reputation and their QoS parameters
that should coincide with the required QoS). Therefore we define
two types of web service strategies; when a web service has higher
level of confidence based on its growth factor, it can compete to
get a task from the master and adopts the competitive strategy. On
the other hand, when it has a lower level of confidence that it
does not feel it can compete with other web services to get a
task, the web service waits for some other web services to
cooperate with for completing a task and thus it adopts the
cooperative strategy. Web services estimate the outcome of all the
strategies and choose one of them accordingly. This decision is
not static but can change over time so web services can switch
from one strategy to the other and this dynamic attitude is
referred to as coopetition. We discuss about this decision making
process in more details in the next section.

\section{Theoretical Results}\label{Theoretical Results}

\subsection{Web Service Decision Making Procedure}
%In the previous section, we introduced web services' interaction
%strategies.
In this section, we explore in details the interaction strategies
and the outcome of each strategy in terms of web services'
utilities. The main part of web services' decision making
procedure falls into their growth factor analysis. In fact, the
growth factor and its comparison to a particular threshold is the
main reason that influences the web service's decision to follow
either competitive or cooperative behavior. Web services initially
compute this value and compare it with their computed threshold.
Generally the main challenge is the threshold computation and we
cope with this issue in the rest of this section. We additionally
use the obtained results in the implemented environment and
analyze their effectiveness on web services' strategic decision
making procedures.

Figure \ref{decisionMakingProcedure} shows the decision making
process that is followed by a typical web service. In case the web
service is ready to compete, there is a chance that it bids for a
task if it has the required capabilities to accomplish that task,
or stays silent and returns to the cooperative status. But in case
the web service is willing to cooperate, it has to wait for a
cooperation opportunity that could be triggered by another web
service that competed and obtained the task, so both web services
will be part of the same collaborative network. In the decision
making process presented in Figure \ref{decisionMakingProcedure},
we assume that the competing web service might get the task
(denoted as $Bid/obtainedTask$) or not get the task in case of
being rejected by the master web service, or do not even bid for
the task (denoted as $Silent/rejectedTask$). For simplicity
reasons and without loss of generality, we group the two cases of
$Bids$ and $obtainedTask$ together as well as $Silent$ and
$rejectedTask$. The rational behind this aggregation is the fact
that our main concentration is web services' status (competitive
or cooperative) over different decision making rounds which could
be caused by internal factors (the web services) or by the
external factor (the master web service).

\begin{figure}[h]
\centering
\includegraphics[scale=0.45]{decision1++.eps}
\caption{Decision making process over competitive and cooperative
strategies.} \label{decisionMakingProcedure}
\end{figure}

Consider a web service $w$ that is willing to compete (that means
the computed growth factor is more than the analyzed threshold).
This web service can estimate the expected payoff associated to
this decision, called competition payoff. Equation \ref{CMPff}
computes this expected payoff for web service $w$ ($\pi_{w,CM}^t$)
considering the $Bid/obtainedTask$ probability of $p_{w,CM}^t$ and
$Silent/rejectedTask$ probability of $1-p_{w,CM}^t$.

\begin{equation}\label{CMPff}
\pi_{w,CM}^t=p_{w,CM}^t(\mu_{w,
CM}-COF_w^t-\epsilon)+(1-p_{w,CM}^t)(-\epsilon)
\end{equation}

In Equation \ref{CMPff}, $\mu_{w, CM}$ is the mean service fee
that is assigned by the master web service to $w$. This means that
a competing web service $w$ directly obtains this fee from the
master web service. Moreover, the competing web service $w$
expects a cooperation fee ($COF_w^t$) that it gives to its
collaborators in case $w$ needs to cooperate with other web
services (cooperative web services in its collaboration network).
In any case, the competing or cooperating web service pays a fixed
amount of membership ($\epsilon$) to the master web service as the
coordinator of the community. This fee would be taken into account
when a web service decides to leave to a cheaper community or act
alone. But to concentrate on the main concerns of this paper, we
skip these small details.

Similar to the competitive web service case, if a web service $w$
declares cooperative status, its expected cooperation payoff
($\pi_{w,CO}^t$) is computed in Equation \ref{CLPff}. In this
equation, $p_{w,CO}^t$ is the probability of getting involved in a
cooperative task with other web services and $1-p_{w,CO}^t$ is the
probability of failure to find such a cooperation opportunity.
These two probabilities are set when $w$ decides to compete. We
recall that $\mu_{w, CO}$ denotes the mean cooperation fee that is
directly obtained from the leader (i.e., the competitive) web
service of the underlying collaborative network. Compared to
$\mu_{w, CM}$, $\mu_{w, CO}$ is relatively smaller since the
competitive web service generally dedicates a portion of its
obtained income to pay other cooperative web services.

\begin{equation}\label{CLPff}
\pi_{w,CO}^t=p_{w,CO}^t (\mu_{w,
CO}-\epsilon)+(1-p_{w,CO}^t)(-\epsilon)
\end{equation}

To analyze the expected payoffs obtained from different
strategies, web services need to compute the estimated
probabilities that distinguish subcases in each behaviorial status
($p_{w,CM}^t$ for competitive and $p_{w,CO}^t$ for cooperative).
To estimate these probabilities, we should notice that they are
functions of web services' reputation values ($Rep_w^t$).
Furthermore, $p_{w,CM}^t$ is also function of the difference
between the offered QoS ($QoS_w^t$) and the requested one
($T_{QoS}^t$); and $p_{w,CO}^t$ is function of the reputation of
other web services in the community because the leader is supposed
to be selective when it comes time to choose the collaborators. To
this end, we first discuss the desirable properties of an
estimation function of each of these probabilities, and show that
the proposed ones satisfy those properties. The desired properties
of $p_{w,CM}^t$ are as follows:

\begin{property}
$p_{w,CM}^t$ is continuous with regard to $Rep^t_w$, $QoS_w^t$,
and $T_{QoS}^t$.
\end{property}
%
\begin{property}
$p_{w,CM}^t$  is monotonically increasing/decreasing in $Rep^t_w$
and $QoS_w^t - T_{QoS}^t$ while $QoS_w^t - T_{QoS}^t$ is positive.
\end{property}
%
\begin{property}
$p_{w,CM}^t$ is null if $QoS_w^t - T_{QoS}^t$ is negative.
\end{property}
%
%\begin{property}
%Assuming that the web service $w$ is known by the master web
%service, $Rep^t_w$ is monotonically increasing or decreasing in
%$QoS_w$.
%\end{property}
%
\begin{property}
The increase slope of $p_{w,CM}^t$ is higher when the reputation
$Rep^t_w$ increases in the interval $[0, 0.5]$ than when it
increases in the interval $]0.5, 1]$.
\end{property}

\noindent Property 1 simply says that the probability of success
competition $p_{w,CM}^t$ can be always estimated as far as
$Rep^t_w$, $QoS_w^t$, and $T_{QoS}^t$ are available. Property 2
says that the reputation and QoS are two key factors that
influence the value of $p_{w,CM}^t$ in the sense of positive
correlation. Property 3 indicates that the probability
$p_{w,CM}^t$ is null if the offered QoS is less than the
expectation. Property 4 promotes the increase of the reputation
for new comers and imposes higher increase rate at the beginning
of the reputation curve because it is always hard to build the
reputation, but once it is built, its maintenance is less
challenging.

\noindent The desired properties of $p_{w,CO}^t$ are as follows:

\begin{property}
$p_{w,CO}^t$ is continuous with regard to $Rep^t_w$ and the
reputation of other web services in the community.
\end{property}
%
\begin{property}
$p_{w,CO}^t$  is monotonically increasing in $Rep^t_w$ and
 monotonically decreasing in the community average reputation.
\end{property}
%
%\begin{property}
%$p_{w,CM}$ is null if $QoS_w^t - T_{QoS}^t$ is negative.
%\end{property}
%
%\begin{property}
%Assuming that the web service $w$ is known by the master web
%service, $Rep^t_w$ is monotonically increasing or decreasing in
%$QoS_w$.
%\end{property}
%
\begin{property}
The increase slope of $p_{w,CO}^t$ is higher when the reputation
$Rep^t_w$ increases in the interval $[0, 0.5]$ than when it
increases in the interval $]0.5, 1]$.
\end{property}

\noindent Property 5 is similar to Property 1. Property 6 says
that $w$ has more chance to get involved in a cooperation if it
has high reputation compared to the other members. This chance
decreases if other web services have higher reputation. Property 7
is similar to Property 4.

Equations  \ref{CMp_w} and \ref{CLp_w} respectively compute the
estimated success probability in cases where the web service $w$
is competing and cooperating. These values are computed
considering web service's reputation value ($Rep^t_w$ computed by
the master), web service's offered QoS ($QoS_w$), the task
required QoS ($T_{QoS}^t$) which is the mean required QoS computed
from previous tasks, the maximum offered QoS ($QoS_k^t$, which is
provided by another competitive web service $k$), and the
cooperative factor $CL_w^t$ of the web service $w$ at time $t$,
which is computed as the portion of web service's current
reputation on the average reputation of the community.

\begin{equation} \label{CMp_w}
p_{w,CM}^t = \begin{cases}
\sin(Rep^t_w\frac{\pi}{2})\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k^t-T_{QoS}^T)} & \text{if $QoS_w^t\geq T_{QoS}^t$;}\\
0 & \text{otherwise.}\\
\end{cases}
\end{equation}

\begin{equation}\label{CLp_w}
p_{w,CO}^t=sin(Rep^t_w\frac{\pi}{2})CL_w^t
\end{equation}
\begin{equation*}
CL_w^t=\frac{Rep^t_w}{\sum_{k\in Community}Rep^t_k/|Community|}
\end{equation*}

It is easy to prove that Equation  \ref{CMp_w} satisfies Property
1. The partial derivative $\frac{\partial p_{w,CM}^t}{\partial
Rep^t_w}$ is positive as the function $\cos$ (the derivative of
$\sin$) is positive on $[0, \frac{\pi}{2}]$ and $Rep^t_w \in [0,
1]$. The partial derivative $\partial p_{w,CM}^t$ with regard to
$QoS_w^t - T_{QoS}^t$ is also positive, which proves the
satisfaction of Property 2. Property 3 is straightforward.
Finally, the increase slope of the function $\sin$ on $[0,
\frac{\pi}{2}]$ proves Property 4.

Similarly, we can easily prove that Equation \ref{CLp_w} satisfies
Property 5. Property 6 can be shown by calculating the partial
derivative $\partial p_{w,CO}^t$ first with regard to $Rep^t_w$
and second with regard to the community average reputation
$\sum_{k\in Community}Rep^t_k/|Community|$. The first partial
derivative is positive and the second is negative, which proves
the satisfaction of Property 6. The proof of satisfaction of
Property 7 is similar to the one of Property 4.

%Considering these involved parameters, we verify that properties
%$1$ to $3$ are satisfied. For property $4$, we use $sinus$
%function to promote the role of reputation influence in this
%system. Using $sinus$ function, we promotoe reputation increase of
%web sevrices specially when it is less than $50\%$. Considering
%the desired properties, the formulas represented in Equations
%\ref{CMp_w} and \ref{CLp_w} are candidates we chose to compute the
%probabilities regarding $Competitive$ and $Cooperative$
%strategies. These formulas are used in implemented system and
%verified with respect to their accuracy and effectiveness in
%adopting different interacting strategies.

%In the proposed heuristic  function, the web service $w$ is not
%aware of current $T_{QoS}$ and $QoS_k$, but could use its previous
%information to estimate their values. To this end, if the web
%service is more informative about the previous data, it could
%obtain more realistic measurement over the estimated
%probabilities.
%
%
%We compute the success probability of cooperation ($p_{w,CO}$)
%similarly in the sense  that we still promote reputation influence
%using $sinus$ function, but multiplied to the cooperative factor
%$CL_w$ of the web service $w$. This value is computed as the
%portion of web service's current reputation on the average
%reputation of the community.

\subsection{Coopetition Threshold}

In this part, we compute the coopetition threshold that a typical
web service could use to adopt reasonable interacting strategies
and we empirically verify the effectiveness of the obtained
results in the next section. In fact, to decide which strategy to
adopt, we let the web service $w$ compare its growth factor
($G_w^t$) with the coopetition threshold it holds at current time
$t$ ($\tau_w^t$) and choose to compete with probability $P_w^t$
that we compute in Equation \ref{P}. Based on this probability, we
calculate the total utility $U_w^t$ in Equation \ref{U}.

\begin{equation} \label{P}
P_w^t= \begin{cases}
\frac{G_w^t}{\tau_w^t}  & \text{if $G_w^t\leq \tau_w^t$;}\\
1 & \text{otherwise.}\\
\end{cases}
\end{equation}

\begin{equation}\label{U}
U_w^t=P_w^t(\pi_{w,CM}^t)+(1-P_w^t)(\pi_{w,CO}^t)
\end{equation}

%Equation  \ref{U} computes the
%expected utility (as accumulated fee) regarding web service $w$.
%This estimated utility is result of aggregation of two different
%interacting strategies of $Competitive$ and $Cooperative$.
%Aggregating these strategic payoffs, web service $w$ follows
%probability distribution of $\{P,1-P\}$. This probability
%distribution is computed in Equation \ref{P}, which is a function
%of the growth factor ($G_w$) and computed threshold ($Tr^t$). So
%if the web service is aware of the reasonable threshold, the value
%$p$ could be computed and used as the core of strategic
%probability distribution. But there is a case where the web
%service does not have a reasonable threshold value and cannot
%rigorously decide for any adopting strategies.

The key factor in the computation of the probability $P_w^t$ and
the associated utility is the threshold value. To compute the
threshold, we use the game theoretic best response technique. A
typical web service $w$ will follow the best response strategy to
maximize its expected aggregated payoff. The idea is to equalize
the expected payoffs of the two acting strategies: compete and
cooperate.
%
%
%by following the following three probability distributions: (1)
%$\{1,0\}$ where the web service always competes; (2) $\{0,1\}$
%where the web service always cooperates; and (3)
%$\{\frac{1}{2},\frac{1}{2}\}$ where the web service equalize the
%probabilities and decides with unbiased distribution. Following
%the third case, the web service equits the expected payoffs as
%outcomes of different interacting strategies.
%
The objective behind equalizing payoffs is to explore conditions
under which the web service $w$ could react with best response to
further decision making procedures. We use the obtained conditions
to compute the threshold $\tau_w^t$ at time $t$. By equalizing
$\pi_{w,CM}^t$ and $\pi_{w,CO}^t$, we obtain:

\begin{equation*}\label{equit}
\pi_{w,CM}^t=\pi_{w,CO}^t      \rightarrow
\end{equation*}
\begin{equation*}
p_{w,CM}^t(\mu_{w,CM}-COF_w^t-\epsilon)+(1-p_{w,CM}^t)(-\epsilon)=p_{w,CO}^t(\mu_{w,
CO}-\epsilon)+(1-p_{w,CO}^t)(-\epsilon)
\end{equation*}
The fixed membership fee $\epsilon$ could be taken out and
canceled from both sides of the equation so we obtain the
following:
\begin{equation*}
p_{w,CM}^t(\mu_{w,CM}-COF_w^t)=p_{w,CO}^t(\mu_{w,CO})\rightarrow
\end{equation*}
\begin{equation*}
sin(Rep^t_w\frac{\pi}{2})\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k-T_{QoS}^t)}(\mu_{w,
CM}-COF_w^t)=sin(Rep^t_w\frac{\pi}{2})CL_w^t(\mu_{w, CO})
\end{equation*}
By simplifying the $sinus$ variable from both sides and
substituting the cooperation factor $CL_w^t$ of the web service
$w$ we obtain the following:
\begin{equation*}
\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k^t-T_{QoS}^t)}(\mu_{w,CM}-COF_w^t)=\frac{Rep^t_w}{\sum_{k\in
Community}Rep^t_k}(\mu_{w, CO})
\end{equation*}
%
We use the obtained equation to obtain the cooperation fee
$COF_w^t$ that is assigned by the web service $w$. This fee
represents the amount that $w$ spends to cooperate with other web
service(s) to accomplish the task. By so doing, we obtain the
maximum amount of cooperation fee that the web service $w$ can use
to constrain the positive payoff out of competing. Otherwise, the
web service stays as cooperative entity. The cooperation fee is
computed in Equation \ref{CLF}.

\begin{equation}\label{CLF}
COF_w^t=\mu_{w,CM}-\frac{Rep^t_w}{\sum_{k\in
Community}Rep^t_k}\frac{\mu_{w,CO}Max_k(Qos_k^t-T_{QoS}^t)}{QoS_w^t-T_{QoS}^t}
\end{equation}

We use the maximum cooperation fee that a web service considers to
constrain the positive expected payoff when the competitive
strategy is adopted to update the threshold for the consequent
time interval ($t+1$). We compare the maximum cooperation fee with
the required fee ($ReqF_w^t$) that the web service indicate to
accomplish the task. The outcome of this comparison is a factor
that uses the current threshold $\tau_w^t$ to compute the
consequent threshold $\tau_w^{t+1}$. As in online learning, the
idea is to compute iteratively the threshold until the fixed point
is achieved, which indicates the threshold's conversion, where the
initial value is randomly chosen (in the simulation different
initial values are used). Equation
\ref{Trt} shows this computation. %We restrict the range of this value to $(0.15,0.85)$ to
%avoid some unreasonable results that could occur due to different
%reasons like system start point or heavy loaded competitive web
%services, \textit{etc}.
To investigate the effectiveness of this threshold on the outcomes
of the web services that follow this reasoning technique, in the
next section, we compare the results of different agents with
diverse strategic reasoning techniques.

\begin{equation}\label{Trt}
\tau_w^{t+1}=\begin{cases}
\Theta & \text{if $0 \leq \Theta \leq 1$}\\
1 & \text{if $\Theta > 1$;}\\
0 & \text{if $\Theta < 0$.}\\
\end{cases}
\end{equation}
\begin{equation*}
\Theta =\tau_w^t \times \frac{COF_w^t}{ReqF_w^t}
\end{equation*}

\section{Experimental Results}\label{Experimental Results}

In this section, we provide an empirical analysis over the
observed results regarding the characteristics of intelligent web
services hosted in different communities of web services. In the
implemented system, we simulate the behaviors of service consumers
as request generators, web services as service providers, and
master web services as community representatives. These entities
are developed with respect to what is explained in Section
\ref{Preliminaries}. The objective is to investigate the
effectiveness of the proposed strategic system on intelligent
web services' overall budget. %Before conducting the simulation, the
%expected behavior of our model is to enhance the budget of web
%services when using our proposed strategic interacting system.
%Although this result is promising, we would like to investigate
%the effectiveness of the proposed strategic system on intelligent
%web services' overall budget compared to the best case. Moreover,
We study the overall performance of the community hosting the
reasoning-empowered web services compared to the ones hosting
stochastic and purely competitive services. The simulation
application is written in \textit{C\#} using \textit{Visual Studio}. Developed web services are initialized with values taken
from a real dataset that includes $2507$ real web services
functioning on the web. The dataset records the QoS values of $9$
parameters including \textit{availability}, \textit{throughput},
and
\textit{reliability} \cite{Almasri}.  %These QoS values
%are determined by monitoring the web services over a $6$-day
%period.

We start our discussions with cumulative budget comparison
regarding different communities within which services follow
different reasoning techniques. Figure \ref{Graph1} part (a)
illustrates three graphs for three different communities. Each
community hosts web services that follow different reasoning
techniques: (1) a community that follows the interactive reasoning
techniques presented in this paper (referred to as coopetitive);
(2) a community that follows a random reasoning technique so
decisions about selecting competitive or cooperative strategies
are totally random (referred to as random coopetitive); and (3) a
competitive community where all services follow the competitive
strategy (referred to as competitive). The proposed model's
reasoning mechanism enables services to effectively select their
interacting strategies and the obtained budget represents the best
outcome over the strategic decision making procedure they run all
the time. This procedure avoids cases where a service selects the
competitive strategy but gets refused to obtain a task from the
master. The procedure allows services to make decisions that
maximize their utilities, so that if the web service cannot
compete, the procedure would suggest to collaborate, which is
better than competing and failing to obtain the task. In this case
(i.e., competing and not getting the task), the service stays idle
but still pays the community membership fee, which means losing
utility. The developed strategic decision making mechanism leads
some web services to follow cooperative strategies that overall
maintain an optimal community budget. In the same figure, we
observe the cumulative budget of a community where services follow
random interacting strategies. The outcome is clearly lower
because services at each run randomly decide over their acting
strategies. This potentially influences the community budget
because a low quality service if randomly selects to follow the
competitive strategy, it will fail to get a task. This kind of
strategy selection is totally stochastic while the task allocation
algorithm follows a logical path. The ideal system is the one that
analyzes the optimal strategic path and consistently follows
strategies that bring maximum outcome. The result regarding the
community that follows the random strategy shows how stochastic
decision making degrades the community budget, but still this
result outperforms the one of the purely competitive community. In
the last case, all the services follow the competitive strategy
and the frequency of getting rejected from a task is relatively
high. In a community with limited number of tasks, the competitive
strategy for all services highly influences the community budget
because a potential group of services are losing at every run.

\begin{figure}%[h]
\centering
\includegraphics[scale=0.6]{graph1Final+.eps}
\caption{Part (a): Cumulative community budget comparison. Part
(b): Average community reputation comparison over different
strategic decisions.} \label{Graph1}
\end{figure}

The results illustrated in Figure \ref{Graph1} part (a)  verify
the importance of the strategic decision making procedure to
logically decide over the possible competitive and cooperative
choices. Figure \ref{Graph1} part (b) illustrates communities
average reputation of involved web services. The graphs represent
the influence of the rewards that the master web service imposes
to encourage highly capable web services to compete for a task. As
for the cumulative budget, we observe that the coopetitive
community outperforms the random coopetitive and competitive
communities in terms of average reputation. The proposed model's
average reputation increases because web services follow optimal
strategies where they can perform better so obtain higher rewards.
For the same reasons as for the cumulative budget, the average
reputation of the random coopetitive community
outperforms the one for the coopetitive community. %The idea is to balance web
%services' strategies to maintain optimal community budget.

 %Figure \ref{Graph2} part (a) illustrates the reputation of the proposed $Coopetitive$ community where
 %we highlight the range of reputation change in the community. The vertical lines denote the range of %reputation that is associated with the master web service. The rewards and penalties applied to %different
% web services show that the master web service over runs extends the reputation range and takes %control of the whole community. In the developed model, web services are encouraged to choose
 %optimal staretgies. This is maintained over growth factor comparison of the $Coopetitive$ web %sevrvices.

In Figure \ref{Graph2} parts (a) and (b), we observe the
competitive and cooperative probability of four different web
services where two of them ($w_1$ and $w_3$) are following optimal
strategies (competitive for $w_1$ and cooperative for $w_3$) and
the two others ($w_2$ and $w_4$) are following non-optimal
strategies. Over elapsing runs, web services that follow optimal
strategies bring best budget. In fact, the master web service
rewards the high quality web service that chooses the competitive
strategy, cooperates with other web services and successfully
accomplishes the task. In this system, the reputation regarding
such a web service is increasing over time and the possibility of
allocating further tasks is increasing as well. By increasing the
growth factor, such a web service (here shown as $w_1$) increases
the probability of selecting the competitive strategy. On the
other hand, the other web service (here shown as $w_2$) that is
incapable of competing is penalized by the master web service
because the offered quality might not meet the required task
quality. Thus, $w_2$ degrades its growth factor by following the
competitive strategy. As intelligent entity, this web service is
encouraged to change its strategy to the cooperative one and thus,
its probability of selecting the competitive strategy is
decreasing over time. We have similar results in Figure
\ref{Graph2} part (b) regarding web services $w_3$ and $w_4$ where
unlike $w_4$, $w_3$ is strategically following the cooperative
strategy. Therefore, $w_4$ is more seeking the competitive
strategy where it can increase its growth factor.

\begin{figure}%[h]
\centering
\includegraphics[scale=0.33]{Graph2.eps}
\caption{Competitive and cooperative probabilities regarding four
different web services.} \label{Graph2}
\end{figure}

We conclude our analysis by discussing the percentage of correct
strategy selection (Figure \ref{Graph3}). By this we mean the
average of web services that can get a task when the coopetitive
strategy is followed. We observe that in different runs, this
percentage is generally increasing. This shows that over runs the
web services get to learn the threshold $\tau_w^t$ that allows
them to select the good strategy. We should notice that in
different runs different initial values of the threshold are used
ranging from $0.3$ for run 1 to $0.6$ for run 4.

\begin{figure}%[h]
\centering
\includegraphics[scale=0.33]{graph3Final+.eps}
\caption{Percentage of correct strategy selection in different
runs using different initial threshold values.} \label{Graph3}
\end{figure}

%We conclude our analysis by discussion over the plots in Figure
%\ref{Graph3}. In this Figure, there are 6 plots that vertically
%refer to a scenario where we change some initialized settings. The
%upper plots represent the percentage of the correct strategy
%selections where is increasing in all scenarios but with different
%slopes. The lower plots illustrate the instant threshold together
%with the instant growth factor of a particular web service that
%follows the coopetitive strategy.

\section{Related Work and Conclusion}\label{Conclusion}

Relevant proposals to the model presented in this paper are the
ones that address service selection and task allocation
mechanisms. In many frameworks proposed in the literature, service
selection and task allocation are regulated based on the
reputation parameter \cite{Maximilien2,Kalepu,Rosario,Ruth}. In
\cite{Huang}, the authors propose a framework to match potential
benefits of web services while cooperating with one another. The
interesting idea is to consider the benefits under four
categories: innovation and learning, internal business process,
customer, and financial benefits. In \cite{Alchieri}, the authors
present a dependable framework for cooperative web services that
is based on the tuple space coordination model. The
intrusion-tolerant perspective is emphasized in this paper where
several security mechanisms are developed to enable a reliable
coordination system. %In \cite{Maximilien2}, authors propose
%ontology for quality of service. Users compute the web services'
%reputation using ratings.
The proposed frameworks mostly aim to facilitate the coordination
mechanism between web services. However, the opposite strategy of
competing is not analyzed where web services might be more
successful when competing within a same group. In fact, web
services are not always willing to cooperate even if they have
some common goals, particularly when they operate within groups
such as communities. In such a context, web services can follow
different interacting strategies and have to decide when to
compete and when to cooperate so that their ultimate goal,
maximizing their incomes, can be better achieved.

The contribution of this paper is the proposition of a coopetitive
strategic model to analyze the interacting behavior of intelligent
web services that are active within communities. We considered two
acting strategies where web services expect different sort of
payoffs: (1) competitive strategy where the web service claims
that it can accomplish a task, and therefore can take the
responsibility over the service consumer satisfaction; and (2)
cooperative strategy where the web service does not take the
responsibility to accomplish the task and only cooperates with
other competitive web services. Our proposed model advances the
state-of-the-art in cooperative systems by enabling intelligent
web services to effectively choose their interacting strategies
that lead to optimal outcomes. The proposed framework provides a
reasoning technique that web services can use to increase their
overall obtained utilities. The theoretical results presented in
this paper are also backed by simulation results using a real web
services dataset. As future work, we plan to emphasize the service
consumer role in the proposed model to obtain more accurate
results when consumers post their service satisfaction feedback.
Moreover, we would like to enhance  the reasoning technique's
features to cope with different unexpected scenarios. We also need
to expand the work to enable services to choose their
collaboration networks.

\begin{comment}

\section{Related Work}

In many frameworks proposed in the literature, service selection
and task allocation are regulated based on the reputation
parameter \cite{Jurca1,Jurca2}. In \cite{Ali}, the proposed
framework regulates the service selection based on the trust
policies expressed by the service users. In \cite{Maximilien2},
authors propose ontology for quality of service. Users compute the
web services' reputation using ratings. The frameworks proposed in
\cite{Kalepu,Maximilien1} address effective reputation mechanism
for web services. All these models address the reputation in
environments where web services function alone. In such models,
web service efficiency is not discussed in details and in general,
balancing the market share with the capacity is not considered as
an issue for web service besides his reputation.

There have been few work addressing the communities of web
service. The objective is to facilitate and improve the process of
web service selection and effectively regulate he process of
request and task allocation \cite{Jacyno}. In \cite{Khosravifar2},
authors propose a reputation-based architecture for communities
and investigate the collusion scenarios that might falsely
increase communities' reputation in the network. In
\cite{Khosravifar1}, the authors mainly address the overall
assessed reputation that is used as a main reason for service
selection. The authors do not consider truth/lie telling analysis
as a factor that impacts service selection in future.

The contribution of this paper is the proposition of a coopetitive
strategic model to analyze the interacting behavior of intelligent
web services that are active in communities of web services. The
proposed framework provides a reasoning technique that web
services can use to increase their overall obtained utilities. The
result of our proposed model is a probability distribution where
an intelligent web service can use over different interacting
strategies.

Our model has the advantage of being simple and  straightforward
in the contribution and the provided results. We considered two
acting strategies where web services expect different sort of
payoffs:  (1) $Competitive$ strategy where the web services claims
that it can accomplish a task and therefore, takes the
responsibility over the service consumer satisfaction; and (2)
$Cooperative$ strategy where the web service does not take the
responsibility to accomplish a task and only cooperates with other
$Competitive$ web services. As future work, we plan to emphasize
the service consumer role in the proposed model to obtain more
accurate results when consumer posts service satisfaction
feedback. Moreover, we would like to enhance  the reasoning
technique's features to cope with different unexpected scenarios.
We also need to expand the simulated environment to study
different scenarios in a number of perspectives.

\section{Conclusion}\label{Conclusion}
The contribution of this paper is the proposition of a
game-theoretic based model to analyze the best efficiency
characteristics for the active services in open networks. The
proposed framework considers the chances of web services in
joining a community in different cases with truthful and lying
information service agents. The proposed game analyzes the
existing Nash equilibrium and situations where the maximum payoff
is obtained.

Our model has the advantage of being simple and taking into
account three important factors: (1) rational services seek better
status in the environment by joining the community; (2) rational
information service agents obtain higher payoff by truth telling;
and (3) the community is obtaining more effective web services
while the information service agents challenge for providing
truthful information. As future work, we plan to consider the user
role in the game to obtain more accurate results when users act
rationally. Moreover, we would like to achieve a collusion
resistant efficiency mechanism, which is still an open problem in
open environments.

\end{comment}

\begin{thebibliography}{1}

\small

\bibitem{Alchieri}
E.A.P. Alchieri, A.N. Bessani, and J. S. Fraga.  A dependable
infrastructure for cooperative web services coordination. Proc. of
the Int. Conf. on Web Services (ICWS), pp. 21-28, 2008.

\bibitem{Almasri}
E. Al-Masri and Q.H. Mahmoud. Discovering the best web service.
Proc. of the 16th int. conf. on World Wide Web (WWW), pp.
1257-1258, 2007.

\bibitem{Maximilien2}
E.M. Maximilien. Multiagent system for dynamic web services
selection. Proc. of the 1st Workshop on Service-Oriented Computing
and Agent-based Eng., pp. 25-29, 2005.

\bibitem{Erbin}
E. Lim, P. Thiran, Z. Maamar, and J. Bentahar. On the analysis of
satisfaction for web services selection. Proc. of the 9th Int.
Conf. on Services Computing (SCC), 2012.

\bibitem{Ferguson}
C. Ferguson and C. Gawargy. U(0,1) Two-person poker models. Game
Theory and Applications, 12:17-37, 2007.

\bibitem{Ferguson2}
T. Ferguson, L. Shapley and R. WeberNotes. Notes on a stochastic
game with information structure. Journal of Game Theory, 31:
223-228, 2003.

\bibitem{Huang}
C.D. Huang, Q. Hu.  Integrating web services with competitive
strategies:The balanced scored approach. Communications of the
Association for Information Systems, 13(1)57-80, 2004.

\bibitem{Jacyno}
M. Jacyno, S. Bullock, M. Luck, and T.R. Payne. Emergent service
provisioning and demand estimation through self-organizing agent
communities. Proc. of the 8'th Int. Conf. on Autonomous Agents and
Multi-Agent Systems (AAMAS), pp. 481-488, 2009.

\bibitem{Jurca}
R. Jurca and B. Faltings. Obtaining reliable feedback for
sanctioning reputation mechanisms. Journal of Artificial
Intelligence Research, 29:391-419, 2007.

\bibitem{Jurca2}
R. Jurca and B. Faltings. Reputation-based service level
agreements for Web services. Proc. of the Int. Conf. on Service
Oriented Computing (ICSOC), Lecture Notes in CS, Volume 3826, pp.
396-409, 2005.

\bibitem{Kalepu}
S. Kalepu, S. Krishnaswamy, S. W. Loke. A QoS metric for selecting
Web services and providers. Proc. of the 4'th Int. Conference on
Web Information Systems Engineering Workshops, pp. 131-139, 2003.

\bibitem{Khosravifar1}
B. Khosravifar, J. Bentahar, A. Moazin, and P. Thiran. On the
reputation of agent-based web services. Proc. of the 24'th Int.
Conf. on Artificial Intelligence (AAAI), pp. 1352-1357, 2010.

\bibitem{Khosravifar2}
B. Khosravifar, J. Bentahar, K. Clacens, C. Goffart, and P.
Thiran. Game-theoretic analysis of a web services Collaborative
mechanism. Proc. of the Int. Conf. on Service Oriented Computing
(ICSOC), pp. 549-556, 2011.

\bibitem{Khosravifar2010}
B. Khosravifar, J. Bentahar, A. Moazin, and P. Thiran. Analyzing
communities of web services using incentives. Journal of Web
Services Research, 7(3):30-51, 2010.

\bibitem{Malik}
Z. Malik and A. Bouguettaya. Evaluating rater credibility for
reputation assessment of web services. Proc. of the 8'th Int.
Conf. on Web Information Systems Engineering (WISE), pp. 38-49,
2007.

\bibitem{Maximilien1}
E.M. Maximilien, and M.P. Singh. Reputation and endorsement for
web services, ACM SIGEcom Exchanges, 3(1):24-31, 2002.

\bibitem{Rahwan}
T. Rahwan, T. Michalak, E. Elkind, P. Faliszewski, J. Sroka, M.
Wooldridge, and N. Jennings. Constrained coalition formation.
Proc. of The 25'th Int. Conf. on Artificial Intelligence (AAAI),
pp. 719-725, 2011.

\bibitem{Rosario}
S. Rosario, A. Benveniste, S. Haar, and C. Jard. Probabilistic QoS
and soft contracts for transaction based Web services. Proc. of
the Int. Conf. on Web Services (ICWS), pp. 126-133, 2007.

\bibitem{Ruth}
M. Ruth and  T. Shengru. Concurrency issues in automating RTS for
web services. Proc. of the Int. Conf. on Web Services (ICWS), pp.
1142-1143, 2007.

\bibitem{Yassine}
A. Yassine, A.A. Shirehjini, S. Shirmohammadi, and T. Tran.
Knowledge-empowered agent information system for privecy payoff in
ecommerce. Knowledge and Information Systems, DOI:
10.1007/s10115-011-0415-3, 2011.

\end{thebibliography}

\end{document}

### 2012-11-22 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Changes

@@
 effectiveness of the proposed strategic system on intelligent
-web services' overall budget. %Before conducting the simulation, the
+web services' overall budge and also the average QoS of tasks performed by 
+community web services which directly affects user satisfaction. 
+%Before conducting the simulation, the
 %expected behavior of our model is to enhance the budget of web
@@
 stochastic and purely competitive services. The simulation
-application is written in \textit{C\#} using \textit{Visual Studio}. Developed web services are initialized with values taken
+application is written in \textit{C\#} using \textit{Visual Studio}. 
+Developed web services are initialized with values taken
 from a real dataset that includes $2507$ real web services

### 2012-11-24 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Added matlab file

@@
 because a low quality service if randomly selects to follow the
-competitive strategy, it will fail to get a task. This kind of
+competitive strategy, it will fail to perform a task with high QoS requirements. This kind of
 strategy selection is totally stochastic while the task allocation
@@
  %optimal staretgies. This is maintained over growth factor comparison of the $Coopetitive$ web %sevrvices.
+
+Figure \ref{membership_fee_graph} depicts how increasing the membership fee which is analogious to getting lower amount of income when doing tasks successfuly affects the overall budget of webservices using different decision making processes.
+In Figure \ref{membership_fee_graph} part(a) we set the membership fee to 2, in \ref{membership_fee_graph} part(b) to reletively high value of 5 and \ref{membership_fee_graph} part(a) shows the result when the membership fee is set to very high fee of 10.
 

### 2012-11-24 papers/coopv2/ICSOC Submission/matlab-charts/avg_bud_medfee.m

@@ -1,0 +1,12 @@
+[v,T,vT]=xlsread('avg_bud_medfee.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+i=1:50;
+t=v(:,1);y=v(:,2);z=v(:,3)
+plot(i,t);
+hold all;
+plot(i,y);
+hold all;
+plot(i,z);

### 2012-11-24 papers/coopv2/ICSOC Submission/matlab-charts/avg_bud_medfee.m
Chart Changes

@@ -9,11 +9,14 @@ set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
 i=0:49;
 t=v(:,9);y=v(:,10);z=v(:,11);
 set(gcf,'Position',[100 100 800 500]);
+
+%subplot(1,3,1);
+
 plot(i,t,i,y,i,z,'linewidth', 2);
 grid on;
 
-set(gca,'Xcolor',[0.5 0.5 0.5]);
-set(gca,'Ycolor',[0.5 0.5 0.5]);
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
 set(gca,'XTick',1:1:50);
 set(gca,'YTick',7000:1500:18000);
 set(gca,'tickdir','in')
@@ -41,5 +44,10 @@ set(hleg1,'FontSize',11);
 xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
 ylabel('Budget', 'FontSize',14);
 
-Caxes = copyobj(gca,gcf);
-set(Caxes, 'color', 'none', 'xcolor', 'k', 'xgrid', 'off', 'ycolor','k', 'ygrid','off');
+%Caxes = copyobj(gca,gcf);
+%set(Caxes, 'color', 'none', 'xcolor', 'k', 'xgrid', 'off', 'ycolor','k', 'ygrid','off');
+
+%subplot(1,3,2);
+%plot(i,t,i,y,i,z,'linewidth', 2);
+%Caxes = copyobj(gca,gcf);
+%set(Caxes, 'color', 'none', 'xcolor', 'k', 'xgrid', 'off', 'ycolor','k', 'ygrid','off');

### 2012-11-25 papers/coopv2/ICSOC Submission/matlab-charts/avg_bud_highfee.m
Changes

@@ -1,4 +1,4 @@
-[v,T,vT]=xlsread('avg_bud_medfee.xlsx') 
+[v,T,vT]=xlsread('avg_bud_highfee.xlsx') 
 % 'xlsx' for exell 2007
 %v: Double
 %T and vT : cell
@@ -7,7 +7,7 @@
 set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
 
 i=0:49;
-t=v(:,9);y=v(:,10);z=v(:,11);
+t=v(:,5);y=v(:,6);z=v(:,7);
 %set(gcf,'Position',[100 100 800 500]);
 set(gcf,'Position',[100 100 550 375]);
 
@@ -21,7 +21,7 @@ grid on;
 %set(gca,'Ycolor',[0.5 0.5 0.5]);
 set(gca,'XTick',1:1:50);
 %set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',7000:2000:18000);
+%set(gca,'YTick',7000:2000:18000);
 set(gca,'tickdir','in')
 set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
     '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
@@ -29,10 +29,10 @@ set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
     '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
     '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
 set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 
 
-%axis([0 50 7000 18000]);
+axis([0 50 0 12000]);
 
 % Add legend
 hleg1 = legend('Coopetitive','Random Coopetitive','Competitive');
@@ -44,8 +44,8 @@ set(hleg1,'FontSize',11);
 %legend boxoff;
 
 % Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
+title('High Membership Fee', 'fontsize', 14);
[…]

### 2012-11-25 papers/coopv2/ICSOC Submission/matlab-charts/avg_bud_medfee3set.m

@@ -21,7 +21,7 @@ grid on;
 %set(gca,'Ycolor',[0.5 0.5 0.5]);
 set(gca,'XTick',1:1:50);
 %set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',7000:2000:18000);
+%set(gca,'YTick',7000:2000:18000);
 set(gca,'tickdir','in')
 set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
     '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
@@ -29,10 +29,10 @@ set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
     '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
     '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
 set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 
 
-%axis([0 50 7000 18000]);
+axis([0 50 0 18000]);
 
 % Add legend
 hleg1 = legend('Coopetitive','Random Coopetitive','Competitive');
@@ -44,7 +44,7 @@ set(hleg1,'FontSize',11);
 %legend boxoff;
 
 % Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
+title('Medium Membership Fee', 'fontsize', 14);
 xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
 ylabel('Budget', 'FontSize',14);
 

### 2012-11-25 papers/coopv2/ICSOC Submission/matlab-charts/avg_bud_veryhighfee.m

@@ -1,4 +1,4 @@
-[v,T,vT]=xlsread('avg_bud_medfee.xlsx') 
+[v,T,vT]=xlsread('avg_bud_veryhighfee.xlsx') 
 % 'xlsx' for exell 2007
 %v: Double
 %T and vT : cell
@@ -7,7 +7,7 @@
 set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
 
 i=0:49;
-t=v(:,9);y=v(:,10);z=v(:,11);
+t=v(:,5);y=v(:,6);z=v(:,7);
 %set(gcf,'Position',[100 100 800 500]);
 set(gcf,'Position',[100 100 550 375]);
 
@@ -21,7 +21,7 @@ grid on;
 %set(gca,'Ycolor',[0.5 0.5 0.5]);
 set(gca,'XTick',1:1:50);
 %set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',7000:2000:18000);
+%set(gca,'YTick',7000:2000:18000);
 set(gca,'tickdir','in')
 set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
     '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
@@ -29,10 +29,10 @@ set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
     '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
     '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
 set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 
 
-%axis([0 50 7000 18000]);
+axis([0 50 0 12000]);
 
 % Add legend
 hleg1 = legend('Coopetitive','Random Coopetitive','Competitive');
@@ -44,9 +44,9 @@ set(hleg1,'FontSize',11);
 %legend boxoff;
 
 % Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
-ylabel('Budget', 'FontSize',14);
+title('Very High Membership Fee', 'fontsize', 14);
[…]

### 2012-11-25 papers/coopv2/ICSOC Submission/matlab-charts/avg_rep.m

@@ -1,4 +1,4 @@
-[v,T,vT]=xlsread('avg_bud_medfee.xlsx') 
+[v,T,vT]=xlsread('avg_rep.xlsx') 
 % 'xlsx' for exell 2007
 %v: Double
 %T and vT : cell
@@ -7,7 +7,7 @@
 set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
 
 i=0:49;
-t=v(:,9);y=v(:,10);z=v(:,11);
+t=v(:,1);y=v(:,2);z=v(:,3);
 %set(gcf,'Position',[100 100 800 500]);
 set(gcf,'Position',[100 100 550 375]);
 
@@ -21,7 +21,7 @@ grid on;
 %set(gca,'Ycolor',[0.5 0.5 0.5]);
 set(gca,'XTick',1:1:50);
 %set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',7000:2000:18000);
+set(gca,'YTick',0:0.1:1);
 set(gca,'tickdir','in')
 set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
     '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
@@ -29,15 +29,15 @@ set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
     '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
     '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
 set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 
-
+axis([0 50 0.2 1]);
 %axis([0 50 7000 18000]);
 
 % Add legend
 hleg1 = legend('Coopetitive','Random Coopetitive','Competitive');
 %set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.27,.7,.1,.2]);
+set(hleg1, 'Position', [.27,.71,.1,.2]);
 set(hleg1,'Interpreter','none');
 %set(hleg1,'color','none');
 set(hleg1,'FontSize',11);
@@ -45,8 +45,8 @@ set(hleg1,'FontSize',11);
 
 % Add title and axis labels
[…]

### 2012-11-25 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Chart Changes
Changes

--- 2012-11-22 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
@@
 \centering
-\includegraphics[scale=0.6]{graph1Final+.eps}
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[scale=0.41]{graphbgtmed.eps}
+\includegraphics[scale=0.41]{graphrep.eps}
 \caption{Part (a): Cumulative community budget comparison. Part
@@
  %optimal staretgies. This is maintained over growth factor comparison of the $Coopetitive$ web %sevrvices.
+
+\begin{figure}%[h]
+\centering
+\includegraphics[scale=0.275]{graphbgtmed3set.eps}
+\includegraphics[scale=0.275]{graphbgthigh.eps}
+\includegraphics[scale=0.275]{graphbgtveryhigh.eps}
+\caption{High membership fees or less task income impacts on different selection strategies, (a) medium membership fee, (b) high membership fee, (c) very high membership fee} \label{membership_fee_graph}
+\end{figure}
+
+\begin{figure}%[h]
+\centering
+\includegraphics[scale=0.275]{graphtaskdone.eps}
+\includegraphics[scale=0.275]{graphtasksatisfaction.eps}
+\includegraphics[scale=0.275]{graphavgqostask.eps}
+\caption{Overall performance from comunity point of view, (a) Total Number of tasks succesfuly done, (b) Ratio of tasks satisfied with required QoS, (c) Average QoS of performed tasks} \label{graph_task}
+\end{figure}
 
@@
 \centering
-\includegraphics[scale=0.33]{Graph2.eps}
+\includegraphics[scale=0.31]{Graph2.eps}
 \caption{Competitive and cooperative probabilities regarding four
@@
 \end{figure}
-
-We conclude our analysis by discussing the percentage of correct
-strategy selection (Figure \ref{Graph3}). By this we mean the
 average of web services that can get a task when the coopetitive
@@
 \centering
-\includegraphics[scale=0.33]{graph3Final+.eps}
-\caption{Percentage of correct strategy selection in different
-runs using different initial threshold values.} \label{Graph3}
+\includegraphics[scale=0.4]{graphdev.eps}
+\includegraphics[scale=0.4]{graphdev2.eps}
+\caption{Utiliy loss while deviating from cooperating decision process, (a) Overall budget when deviating in 0, 10, 20, 30, 40, 50 percent of decision, (b) Ratio of getting earning utility (budget) when deviating from cooperative strategy in 1 to 10 decisions} \label{graph_dev}
 \end{figure}

### 2012-11-25 papers/coopv2/ICSOC Submission/matlab-charts/avg_qos_task.m
Changes

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('avg_qos_task.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);z=v(:,3);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',0:0.1:1);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+axis([0 50 0.4 1]);
+%axis([0 50 7000 18000]);
+
+% Add legend
+hleg1 = legend('Coopetitive','Random Coopetitive','Competitive');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.27,.71,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',11);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Number of Runs';'(c)'}, 'FontSize',14);
+ylabel('Average QoS of Tasks Performed', 'FontSize',14);
+
[…]

### 2012-11-25 papers/coopv2/ICSOC Submission/matlab-charts/decision_dev.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('decision_dev.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|.-|.|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);z=v(:,3);tt=v(:,4);yy=v(:,5);zz=v(:,6);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,i,tt,i,yy,i,zz,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',7000:2000:18000);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 50 7000 18000]);
+
+% Add legend
+hleg1 = legend('0% Deviation','10% Deviation','20% Deviation','30% Deviation','40% Deviation','50% Deviation');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.24,.63,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
[…]

### 2012-11-25 papers/coopv2/ICSOC Submission/matlab-charts/task_done.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('task_done.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);z=v(:,3);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',0:0.1:1);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+%axis([0 50 0.2 1]);
+%axis([0 50 7000 18000]);
+
+% Add legend
+hleg1 = legend('Coopetitive','Random Coopetitive','Competitive');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.27,.71,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',11);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
+ylabel('Number of tasks succesfully done', 'FontSize',14);
+
[…]

### 2012-11-25 papers/coopv2/ICSOC Submission/matlab-charts/task_satisfaction.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('task_satisfaction.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);z=v(:,3);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',0:0.1:1);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+axis([0 50 0 1]);
+%axis([0 50 7000 18000]);
+
+% Add legend
+hleg1 = legend('Coopetitive','Random Coopetitive','Competitive');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.27,.71,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',11);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Number of Runs';'(b)'}, 'FontSize',14);
+ylabel('Task Satisfaction Ratio', 'FontSize',14);
+
[…]

### 2012-11-25 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Changes

@@
 
+In figure \ref{membership_fee_graph} we analyse the scenario where membership fee is high which is analogous to sitations where task income is low.
+For any reason our web services may need to stay in a particular comuunity with economic downtimes.
+We need verify how well the web services can perform in these situations.
+\ref{membership_fee_graph} part (a) depicts the results in normal scenario.
+In part (b) we have inceased the membership fee to the high ammount of 5 per run.
+Web services will need to pay 5 bucks on each iteration of tasks being offered.
+As results the strategic coopetetive decision making process helps web services to still have benefit and random or all compete methods will lose a lot in these scenarios since making mistakes and trying to compete for jobs they cannot afford while having to pay higher membership fees is making them lose budget in a fater pace.
+In part \ref{membership_fee_graph}(c) the membership is higher than average of possible income of what tasks offer.
+It might not berational for selfish self-interet web services to stay in these communities from utility point of view but as mentioned there might be other political reasons they might need to stay in these comuunities.
+As reseults show the random and all compete strategies make webservices bank deplete in no time.
+However our strategic coopetetive decision making process loses budget in a slower pace.
+
 \begin{figure}%[h]

### 2012-11-25 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Changes

@@
 effectiveness of the proposed strategic system on intelligent
-web services' overall budge and also the average QoS of tasks performed by 
+web services' overall budge and also the average quality and quantity of tasks performed by 
 community web services which directly affects user satisfaction. 
@@
 
+hihi
+
 %We conclude our analysis by discussion over the plots in Figure

### 2012-11-25 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Changes

@@
 
-\begin{figure}%[h]
-\centering
-\includegraphics[scale=0.275]{graphtaskdone.eps}
-\includegraphics[scale=0.275]{graphtasksatisfaction.eps}
-\includegraphics[scale=0.275]{graphavgqostask.eps}
-\caption{Overall performance from comunity point of view, (a) Total Number of tasks succesfuly done, (b) Ratio of tasks satisfied with required QoS, (c) Average QoS of performed tasks} \label{graph_task}
-\end{figure}
-
 In Figure \ref{Graph2} parts (a) and (b), we observe the
@@
 \end{figure}
-average of web services that can get a task when the coopetitive
-strategy is followed. We observe that in different runs, this
-percentage is generally increasing. This shows that over runs the
-web services get to learn the threshold $\tau_w^t$ that allows
-them to select the good strategy. We should notice that in
-different runs different initial values of the threshold are used
-ranging from $0.3$ for run 1 to $0.6$ for run 4.
+
+\begin{figure}%[h]
+\centering
+\includegraphics[scale=0.275]{graphtaskdone.eps}
+\includegraphics[scale=0.275]{graphtasksatisfaction.eps}
+\includegraphics[scale=0.275]{graphavgqostask.eps}
+\caption{Overall performance from comunity point of view, (a) Total Number of tasks succesfuly done, (b) Ratio of tasks satisfied with required QoS, (c) Average QoS of performed tasks} \label{graph_task}
+\end{figure}
+
+hihi
 
@@
 
-hihi
+We conclude out analysis by discussing how well our cooperative decision making process is by comparing the final utility of our agents here the end budget our webservices have while deviating from our strategy adopted by an agent which can be either compete or cooperate to the other one.
+In \ref{graph_dev} part (a) we randomly made the web services deviate from the calculated strategy.
+As the results depict, the more web services deviate from cooperative strategy the more they less budget they gain.
+Figure \ref{graph_dev} part (b) we pick one random webservice and once simulate the scenario with its default cooperative strategy and then we redo the simulation with exact same enviroment parameters while adapting the other strategy which is to compete if our cooperative strategy suggested to cooperate or vise versa.
+We run this 50 times and at the end we check their budget and see if they gain more by deviating or not.
+We did this for one single deviation to ten different deviations in lifetime of a web service in community.
+As results indicate with high probability our cooperative strategy yields higher budgets at the end for web services.
 

### 2012-11-25 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Changes

@@
 
-hihi
+The web services are selfish, self interested agents.
+They try to maximise their own utiliy.
+Now we analyse how their strategy effects the social welfare or from user and community point of view how good the tasks are being performed.
+This directly affects user satisfation and community reputation in general.
+The Higher  quality and quantity of tasks perfromed leads to higher user satisfaction for the community which results in better reputaiton for the community.
+The results in figure \ref{graph_task} shows the quality of quantity of tasks being done successfuly in three communities adopting the three different mentioned strategy decision algorithms.
+Part(a)and(b) depicts the number tasks succesfuly done.
+When web services are not capable of performing tasks alone and decide to compete for tasks with high QoS requirements they usually fail to perform the task how ever if they opt for cooperating although they have less income, they have higher chance of performing tasks collabratively with other web serives.
+Figure \ref{graph_task}Part (b) shows the probablilty of successfully performin tasks.
+As results suggest web services using our coopetetive strategy when deciding whether to compete or cooperate have higher chance of tasks to be done than random or all compete strategies.
+The quality of tasks performed are depicted in Figure \ref{graph_task} Part (c).
+It shows the average QoS of tasks perfromed which are finished and done sucessfuly.
+Colabrating increases the performed QoS of tasks, therefore forming collabrative groups improves user satisfaction.
+As results suggest, the coopetetive community outperforms the random and all compete communities in quality of tasks performed.
+
+We conclude out analysis by discussing how effective our cooperative decision making process is by comparing the final utility of our agents here the end budget our webservices have while deviating from our strategy adopted by an agent which can be either compete or cooperate to the other one.
+In \ref{graph_dev} part (a) we randomly made the web services deviate from the calculated strategy.
+As the results depict, the more web services deviate from cooperative strategy the more they less budget they gain.
+Figure \ref{graph_dev} part (b) we pick one random webservice and once simulate the scenario with its default cooperative strategy and then we redo the simulation with exact same enviroment parameters while adapting the other strategy which is to compete if our cooperative strategy suggested to cooperate or vise versa.
+We run this 50 times and at the end we check their budget and see if they gain more by deviating or not.
+We did this for one single deviation to ten different deviations in lifetime of a web service in community.
+As results indicate with high probability our cooperative strategy yields higher budgets at the end for web services.
 
@@
 \end{figure}
-
-We conclude out analysis by discussing how well our cooperative decision making process is by comparing the final utility of our agents here the end budget our webservices have while deviating from our strategy adopted by an agent which can be either compete or cooperate to the other one.
-In \ref{graph_dev} part (a) we randomly made the web services deviate from the calculated strategy.
-As the results depict, the more web services deviate from cooperative strategy the more they less budget they gain.
-Figure \ref{graph_dev} part (b) we pick one random webservice and once simulate the scenario with its default cooperative strategy and then we redo the simulation with exact same enviroment parameters while adapting the other strategy which is to compete if our cooperative strategy suggested to cooperate or vise versa.
-We run this 50 times and at the end we check their budget and see if they gain more by deviating or not.
-We did this for one single deviation to ten different deviations in lifetime of a web service in community.
-As results indicate with high probability our cooperative strategy yields higher budgets at the end for web services.
 

### 2012-11-25 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Changes

--- 2012-11-25 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
@@
 effectiveness of the proposed strategic system on intelligent
-web services' overall budge and also the average quality and quantity of tasks performed by 
+web services' overall budge and also the average QoS of tasks performed by 
 community web services which directly affects user satisfaction. 
@@
 
-In figure \ref{membership_fee_graph} we analyse the scenario where membership fee is high which is analogous to sitations where task income is low.
-For any reason our web services may need to stay in a particular comuunity with economic downtimes.
-We need verify how well the web services can perform in these situations.
-\ref{membership_fee_graph} part (a) depicts the results in normal scenario.
-In part (b) we have inceased the membership fee to the high ammount of 5 per run.
-Web services will need to pay 5 bucks on each iteration of tasks being offered.
-As results the strategic coopetetive decision making process helps web services to still have benefit and random or all compete methods will lose a lot in these scenarios since making mistakes and trying to compete for jobs they cannot afford while having to pay higher membership fees is making them lose budget in a fater pace.
-In part \ref{membership_fee_graph}(c) the membership is higher than average of possible income of what tasks offer.
-It might not berational for selfish self-interet web services to stay in these communities from utility point of view but as mentioned there might be other political reasons they might need to stay in these comuunities.
-As reseults show the random and all compete strategies make webservices bank deplete in no time.
-However our strategic coopetetive decision making process loses budget in a slower pace.
-
 \begin{figure}%[h]
@@
 \end{figure}
-
-hihi
 

### 2012-11-26 papers/coopv2/ICSOC Submission/matlab-charts/avg_bud_highfee.m
Changed 3 in a row graph sizes from 550 to 500

@@ -9,7 +9,7 @@ set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
 i=0:49;
 t=v(:,5);y=v(:,6);z=v(:,7);
 %set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
+set(gcf,'Position',[100 100 500 375]);
 
 %subplot(1,3,1);
 
@@ -37,7 +37,7 @@ axis([0 50 0 12000]);
 % Add legend
 hleg1 = legend('Coopetitive','Random Coopetitive','Competitive');
 %set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.27,.7,.1,.2]);
+set(hleg1, 'Position', [.3,.7,.1,.2]);
 set(hleg1,'Interpreter','none');
 %set(hleg1,'color','none');
 set(hleg1,'FontSize',11);

### 2012-11-26 papers/coopv2/ICSOC Submission/matlab-charts/avg_bud_medfee3set.m

@@ -9,7 +9,7 @@ set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
 i=0:49;
 t=v(:,9);y=v(:,10);z=v(:,11);
 %set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
+set(gcf,'Position',[100 100 500 375]);
 
 %subplot(1,3,1);
 
@@ -37,7 +37,7 @@ axis([0 50 0 18000]);
 % Add legend
 hleg1 = legend('Coopetitive','Random Coopetitive','Competitive');
 %set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.27,.7,.1,.2]);
+set(hleg1, 'Position', [.3,.7,.1,.2]);
 set(hleg1,'Interpreter','none');
 %set(hleg1,'color','none');
 set(hleg1,'FontSize',11);

### 2012-11-26 papers/coopv2/ICSOC Submission/matlab-charts/avg_qos_task.m

@@ -9,7 +9,7 @@ set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
 i=0:49;
 t=v(:,1);y=v(:,2);z=v(:,3);
 %set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
+set(gcf,'Position',[100 100 500 375]);
 
 %subplot(1,3,1);
 
@@ -37,7 +37,7 @@ axis([0 50 0.4 1]);
 % Add legend
 hleg1 = legend('Coopetitive','Random Coopetitive','Competitive');
 %set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.27,.71,.1,.2]);
+set(hleg1, 'Position', [.3,.71,.1,.2]);
 set(hleg1,'Interpreter','none');
 %set(hleg1,'color','none');
 set(hleg1,'FontSize',11);

### 2012-11-26 papers/coopv2/ICSOC Submission/matlab-charts/task_done.m

@@ -9,7 +9,7 @@ set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
 i=0:49;
 t=v(:,1);y=v(:,2);z=v(:,3);
 %set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
+set(gcf,'Position',[100 100 500 375]);
 
 %subplot(1,3,1);
 
@@ -37,7 +37,7 @@ set(gca,'XGrid','off','YGrid','on','ZGrid','off');
 % Add legend
 hleg1 = legend('Coopetitive','Random Coopetitive','Competitive');
 %set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.27,.71,.1,.2]);
+set(hleg1, 'Position', [.3,.71,.1,.2]);
 set(hleg1,'Interpreter','none');
 %set(hleg1,'color','none');
 set(hleg1,'FontSize',11);

### 2012-11-26 papers/coopv2/ICSOC Submission/matlab-charts/task_satisfaction.m

@@ -9,7 +9,7 @@ set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
 i=0:49;
 t=v(:,1);y=v(:,2);z=v(:,3);
 %set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
+set(gcf,'Position',[100 100 500 375]);
 
 %subplot(1,3,1);
 
@@ -37,7 +37,7 @@ axis([0 50 0 1]);
 % Add legend
 hleg1 = legend('Coopetitive','Random Coopetitive','Competitive');
 %set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.27,.71,.1,.2]);
+set(hleg1, 'Position', [.3,.71,.1,.2]);
 set(hleg1,'Interpreter','none');
 %set(hleg1,'color','none');
 set(hleg1,'FontSize',11);

### 2012-11-26 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Changed 3 in a row graph sizes from 550 to 500
Updated Text

--- 2012-11-25 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
@@
 \centering
-\includegraphics[scale=0.275]{graphbgtmed3set.eps}
-\includegraphics[scale=0.275]{graphbgthigh.eps}
-\includegraphics[scale=0.275]{graphbgtveryhigh.eps}
+\includegraphics[scale=0.302]{graphbgtmed3set.eps}
+\includegraphics[scale=0.302]{graphbgthigh.eps}
+\includegraphics[scale=0.302]{graphbgtveryhigh.eps}
 \caption{High membership fees or less task income impacts on different selection strategies, (a) medium membership fee, (b) high membership fee, (c) very high membership fee} \label{membership_fee_graph}
@@
 
-In figure \ref{membership_fee_graph} we analyse the scenario where membership fee is high which is analogous to sitations where task income is low.
-For any reason our web services may need to stay in a particular comuunity with economic downtimes.
+In figure \ref{membership_fee_graph} we analyze the scenario where membership fee is high which is analogous to situations where task income is low.
+For any reason our web services may need to stay in a particular community with economic downtimes.
 We need verify how well the web services can perform in these situations.
 \ref{membership_fee_graph} part (a) depicts the results in normal scenario.
-In part (b) we have inceased the membership fee to the high ammount of 5 per run.
-Web services will need to pay 5 bucks on each iteration of tasks being offered.
-As results the strategic coopetetive decision making process helps web services to still have benefit and random or all compete methods will lose a lot in these scenarios since making mistakes and trying to compete for jobs they cannot afford while having to pay higher membership fees is making them lose budget in a fater pace.
+In part (b) we have increased the membership fee to the high amount of 5 units per run.
+Web services will need to pay 5 units on each iteration of tasks being offered.
+As results the strategic coopetitive decision making process helps web services to still have benefit and random or all compete methods will lose a lot in these scenarios since making mistakes and trying to compete for jobs they cannot afford while having to pay higher membership fees is making them lose budget in a fater pace.
 In part \ref{membership_fee_graph}(c) the membership is higher than average of possible income of what tasks offer.
-It might not berational for selfish self-interet web services to stay in these communities from utility point of view but as mentioned there might be other political reasons they might need to stay in these comuunities.
-As reseults show the random and all compete strategies make webservices bank deplete in no time.
+It might not be rational for selfish self-interest web services to stay in these communities from utility point of view but as mentioned there might be other political reasons they might need to stay in these communities.
+As reseults show the random and all compete strategies make web services bank deplete in no time.
 However our strategic coopetetive decision making process loses budget in a slower pace.
@@
 \centering
-\includegraphics[scale=0.275]{graphtaskdone.eps}
-\includegraphics[scale=0.275]{graphtasksatisfaction.eps}
-\includegraphics[scale=0.275]{graphavgqostask.eps}
+\includegraphics[scale=0.302]{graphtaskdone.eps}
+\includegraphics[scale=0.302]{graphtasksatisfaction.eps}
+\includegraphics[scale=0.302]{graphavgqostask.eps}
 \caption{Overall performance from comunity point of view, (a) Total Number of tasks succesfuly done, (b) Ratio of tasks satisfied with required QoS, (c) Average QoS of performed tasks} \label{graph_task}
@@
 The results in figure \ref{graph_task} shows the quality of quantity of tasks being done successfuly in three communities adopting the three different mentioned strategy decision algorithms.
-Part(a)and(b) depicts the number tasks succesfuly done.
+Figure \ref{graph_task} Part (a) and (b) depicts the number tasks succesfuly done.
 When web services are not capable of performing tasks alone and decide to compete for tasks with high QoS requirements they usually fail to perform the task how ever if they opt for cooperating although they have less income, they have higher chance of performing tasks collabratively with other web serives.
 Figure \ref{graph_task}Part (b) shows the probablilty of successfully performin tasks.
-As results suggest web services using our coopetetive strategy when deciding whether to compete or cooperate have higher chance of tasks to be done than random or all compete strategies.
+As results suggest web services using our coopetitive strategy when deciding whether to compete or cooperate have higher chance of tasks to be done than random or all compete strategies.
 The quality of tasks performed are depicted in Figure \ref{graph_task} Part (c).
@@
 
-We conclude out analysis by discussing how effective our cooperative decision making process is by comparing the final utility of our agents here the end budget our webservices have while deviating from our strategy adopted by an agent which can be either compete or cooperate to the other one.
+We conclude out analysis by discussing how effective our cooperative decision making process is by comparing the final utility of our agents here the end budget our web services have while deviating from our strategy adopted by an agent which can be either compete or cooperate to the other one.
 In \ref{graph_dev} part (a) we randomly made the web services deviate from the calculated strategy.
 As the results depict, the more web services deviate from cooperative strategy the more they less budget they gain.
-Figure \ref{graph_dev} part (b) we pick one random webservice and once simulate the scenario with its default cooperative strategy and then we redo the simulation with exact same enviroment parameters while adapting the other strategy which is to compete if our cooperative strategy suggested to cooperate or vise versa.
-We run this 50 times and at the end we check their budget and see if they gain more by deviating or not.
+Figure \ref{graph_dev} part (b) we pick one random web service and once simulate the scenario with its default cooperative strategy and then we redo the simulation with exact same enviroment parameters while adapting the other strategy which is to compete if our cooperative strategy suggested to cooperate or vice versa.
+We run this scenario 50 times and at the end we check their budget and see if they gain more by deviating or not.
 We did this for one single deviation to ten different deviations in lifetime of a web service in community.

### 2012-11-26 papers/coopv2/ICSOC Submission/matlab-charts/task_done.m

@@ -46,7 +46,7 @@ set(hleg1,'FontSize',11);
 % Add title and axis labels
 % title('Trigonometric Functions', 'fontsize', 10);
 xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
-ylabel('Number of tasks succesfully done', 'FontSize',14);
+ylabel('Number of tasks successfully done', 'FontSize',14);
 
 %Caxes = copyobj(gca,gcf);
 %set(Caxes, 'color', 'none', 'xcolor', 'k', 'xgrid', 'off', 'ycolor','k', 'ygrid','off');

### 2012-11-26 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Updated Text

@@
 Web services will need to pay 5 units on each iteration of tasks being offered.
-As results the strategic coopetitive decision making process helps web services to still have benefit and random or all compete methods will lose a lot in these scenarios since making mistakes and trying to compete for jobs they cannot afford while having to pay higher membership fees is making them lose budget in a fater pace.
+As results the strategic coopetitive decision making process helps web services to still have benefit and random or all compete methods will lose a lot in these scenarios since making mistakes and trying to compete for jobs they cannot afford while having to pay higher membership fees is making them lose budget in a faster pace.
 In part \ref{membership_fee_graph}(c) the membership is higher than average of possible income of what tasks offer.
 It might not be rational for selfish self-interest web services to stay in these communities from utility point of view but as mentioned there might be other political reasons they might need to stay in these communities.
-As reseults show the random and all compete strategies make web services bank deplete in no time.
-However our strategic coopetetive decision making process loses budget in a slower pace.
+As results show the random and all compete strategies make web services bank deplete in no time.
+However our strategic coopetitive decision making process loses budget in a slower pace.
 

### 2012-11-28 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
babak changes

@@
 % first the title is needed
-\title{Analyzing Coopetition Strategies of Services within Communities}
+\title{When to Compete and When to Cooperate: Analysis on Strategies of Services within Communities}
 
@@
 
-\author{Babak Khosravifar$^1$
-\and Mahsa Alishahi$^1$ \and Ehsan Khosrowshahi Asl$^1$ \and Jamal
-Bentahar$^1$\and Rabeb Mizouni$^2$\and Hadi Otrok$^2$}
+\author{Babak Khosravifar$^1$\and Ehsan Khosrowshahi Asl$^2$
+\and Jamal Bentahar$^2$\and Rabeb Mizouni$^3$\and Hadi Otrok$^3$}
 
@@
 
-\institute{$^1$Concordia University, Canada, $^2$Khalifa University, UAE\\
-$b\_khosr@encs.concordia.ca$, $m\_ali@encs.concordia.ca$, $e\_khosr@encs.concordia.ca$,\\$bentahar@ciise.concordia.ca$,
+\institute{$^1$McGill University, Canada, $^2$ Concordia University, Canada, $^3$Khalifa University, UAE\\
+$babak.khosravifar@mcgill.ca$, $e\_khosr@encs.concordia.ca$, $bentahar@ciise.concordia.ca$,
 $rabeb.mizouni@kustar.ac.ae$,$hadi.otrak@kustar.ac.ae$}
@@
 We highlight details of the interactive strategies in the rest of
-this section.
+this Section.
 %Figure \ref{algorithm1} %exposes the details of task allocation mechanism that is used to select the web services.
@@
 \centering
-\includegraphics[scale=0.45]{decision1++.eps}
+\includegraphics[scale=0.55]{decision1++.eps}
 \caption{Decision making process over competitive and cooperative
@@
 are developed with respect to what is explained in Section
-\ref{Preliminaries}. The objective is to investigate the
+\ref{Preliminaries}. In this Section, the objective is to investigate the
 effectiveness of the proposed strategic system on intelligent
-web services' overall budge and also the average quality and quantity of tasks performed by 
+web services' overall budget and also the average quality and quantity of tasks performed by 
 community web services which directly affects user satisfaction. 
@@
 %web services' overall budget compared to the best case. Moreover,
-We study the overall performance of the community hosting the
+To verify these objectives, we study the overall performance of the community hosting the
 reasoning-empowered web services compared to the ones hosting
@@
 some web services to follow cooperative strategies that overall
-maintain an optimal community budget. In the same figure, we
+maintain an optimal community budget. In the same Figure, we
 observe the cumulative budget of a community where services follow
@@
 algorithm follows a logical path. The ideal system is the one that
-analyzes the optimal strategic path and consistently follows
+analyses the optimal strategic path and consistently follows
 strategies that bring maximum outcome. The result regarding the
@@
 
-In figure \ref{membership_fee_graph} we analyze the scenario where membership fee is high which is analogous to situations where task income is low.
+In Figure \ref{membership_fee_graph} we analyze the scenario where membership fee is high which is analogous to situations where task income is low.
 For any reason our web services may need to stay in a particular community with economic downtimes.
@@
 In part (b) we have increased the membership fee to the high amount of 5 units per run.
-Web services will need to pay 5 units on each iteration of tasks being offered.
+Web services will need to pay $5$ units on each iteration of tasks being offered.
 As results the strategic coopetitive decision making process helps web services to still have benefit and random or all compete methods will lose a lot in these scenarios since making mistakes and trying to compete for jobs they cannot afford while having to pay higher membership fees is making them lose budget in a faster pace.
@@
 The Higher  quality and quantity of tasks perfromed leads to higher user satisfaction for the community which results in better reputaiton for the community.
-The results in figure \ref{graph_task} shows the quality of quantity of tasks being done successfuly in three communities adopting the three different mentioned strategy decision algorithms.
+The results in Figure \ref{graph_task} shows the quality of quantity of tasks being done successfuly in three communities adopting the three different mentioned strategy decision algorithms.
 Figure \ref{graph_task} Part (a) and (b) depicts the number tasks succesfuly done.

### 2012-11-29 papers/coopv2/ICSOC Submission/matlab-charts/comp_p.m
Added new coop comp charts

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('comp_p.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|--|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0:0.1:1);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+axis([0 50 0 1]);
+%axis([0 50 7000 18000]);
+
+% Add legend
+hleg1 = legend('Competitive W1','Competitive W2');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.69,.6,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',11);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Number of Runs';'(b)'}, 'FontSize',14);
+ylabel('Reputation', 'FontSize',14);
+
+%Caxes = copyobj(gca,gcf);
[…]

### 2012-12-13 papers/coopv3/IJWGS.tex
Added new paper

--- 2012-11-28 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% This is the LaTeX source for the instructions to authors using
-% the LaTeX document class 'llncs.cls' for contributions to
-% the Lecture Notes in Computer Sciences series.
-% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
-%
-% It may be used as a template for your own input - copy it
-% to a new file with a new name and use it as the basis
-% for your article.
-%
-% NB: the document class 'llncs' has its own and detailed documentation, see
-% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\documentclass[runningheads,a4paper]{llncs}
-
-\usepackage{amssymb}
-\setcounter{tocdepth}{3}
-\usepackage{graphicx}
-\usepackage{times}
-%\usepackage{cite}
-%\usepackage{subfigure}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{verbatim}
-
-%\newtheorem{property}{\textbf{Property}}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[fleqn]{singlecol-new}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\usepackage{amsfonts,amsmath,amscd, amssymb}
+\usepackage{fontspec}
+\setmainfont[Mapping=tex-text]{Times New Roman}
+
+\usepackage{natbib}
+%\usepackage[pdf]{graphicx}%
+\def\newblock{\hskip .11em plus .33em minus .07em}
+
+\makeatletter
+\def\theequation{\arabic{equation}}
+
+\makeatother
+
+%\def\bmD{\mbox{\boldmath $D$}}        %99.10.1
+%\def\bmE{\mbox{\boldmath $E$}}        %99.6.29
+%\def\bmg{\mbox{\boldmath $g$}}
+%\def\bmG{\mbox{\boldmath $G$}}
+%\def\bmM{\mbox{\boldmath $M$}}
+%\def\bmY{\mbox{\boldmath $Y$}}  %99.12.22
+%\def\bmW{\mbox{\boldmath $W$}}  %99.12.22
+%\def\bgamma{\mbox{\boldmath $\gamma$}}
+%\def\tc#1{\textcolor{red}{\bf #1}}
+
+\spaceskip=3.5pt plus1.47pt minus0.77pt \makeatother
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
-
-\mainmatter  % start of an individual contribution
-
-% first the title is needed
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\setcounter{page}{1}
+
+\LRH{}
+\RRH{}
+
+\VOL{x}
+\ISSUE{x}
+\BottomCatch
+\PAGES{xxxx}
+\CLline
+%\PUBYEAR{200x}
+
+\subtitle{}
+
 \title{When to Compete and When to Cooperate: Analysis on Strategies of Services within Communities}
 
-% a short form should be given in case it is too long for the running head
-\titlerunning{Lecture Notes in Computer Science}
-
-% the name(s) of the author(s) follow(s) next
-%
-% NB: Chinese authors should write their first names(s) in front of
-% their surnames. This ensures that the names appear correctly in
-% the running heads and the author index.
-%
-
-\author{Babak Khosravifar$^1$\and Ehsan Khosrowshahi Asl$^2$
-\and Jamal Bentahar$^2$\and Rabeb Mizouni$^3$\and Hadi Otrok$^3$}
-
-%
-
-% (feature abused for this document to repeat the title also on left hand pages)
-
-% the affiliations are given next; don't give your e-mail address
-% unless you accept that it will be published
-
-\institute{$^1$McGill University, Canada, $^2$ Concordia University, Canada, $^3$Khalifa University, UAE\\
-$babak.khosravifar@mcgill.ca$, $e\_khosr@encs.concordia.ca$, $bentahar@ciise.concordia.ca$,
-$rabeb.mizouni@kustar.ac.ae$,$hadi.otrak@kustar.ac.ae$}
-
-%
-% NB: a more complex sample for affiliations and the mapping to the
-% corresponding authors can be found in the file "llncs.dem"
-% (search for the string "\mainmatter" where a contribution starts).
-% "llncs.dem" accompanies the document class "llncs.cls".
-%
-
-\toctitle{Lecture Notes in Computer Science} \tocauthor{Authors'
-Instructions} \maketitle
+\authorA{author}
+
+\affA{Address}
 
 \begin{abstract}
-%Web services are business applications having the capability to
-%cooperate within groups to increase the efficiency of serving
-%customers.
 Recently, a number of frameworks have been proposed to
@@
 obtained theoretical results using parameters from a real web
-services dataset. \keywords{Web services; Reputation; Strategies.}
+services dataset.
 \end{abstract}
+
+\KEYWORD{Web services; Reputation; Strategies.}
+
+\REF{to this paper should be made as follows: Author. (xxxx) `Title', {\it Int. J. }, Vol.~x, No.~x, pp.xxx--xxx.}
+
+\begin{bio}
+
+\end{bio}
+
+\maketitle
 
@@
 of $p_{w,CM}^t$ are as follows:
-
-\begin{property}
+\\
+
+\noindent\textit{Property 1.}
 $p_{w,CM}^t$ is continuous with regard to $Rep^t_w$, $QoS_w^t$,
 and $T_{QoS}^t$.
-\end{property}
-%
-\begin{property}
+\\
+
+%
+\noindent\textit{Property 2.}
 $p_{w,CM}^t$  is monotonically increasing/decreasing in $Rep^t_w$
 and $QoS_w^t - T_{QoS}^t$ while $QoS_w^t - T_{QoS}^t$ is positive.
-\end{property}
-%
-\begin{property}
+\\
+
+%
+\noindent\textit{Property 3.}
 $p_{w,CM}^t$ is null if $QoS_w^t - T_{QoS}^t$ is negative.
-\end{property}
+\\
+
 %
@@
 %
-\begin{property}
+\noindent\textit{Property 4.}
 The increase slope of $p_{w,CM}^t$ is higher when the reputation
@@
 increases in the interval $]0.5, 1]$.
-\end{property}
+\\
 
@@
 \noindent The desired properties of $p_{w,CO}^t$ are as follows:
-
-\begin{property}
+\\
+
+\noindent\textit{Property 5.}
 $p_{w,CO}^t$ is continuous with regard to $Rep^t_w$ and the
 reputation of other web services in the community.
-\end{property}
-%
-\begin{property}
+\\
+
+%
+\noindent\textit{Property 6.}
 $p_{w,CO}^t$  is monotonically increasing in $Rep^t_w$ and
  monotonically decreasing in the community average reputation.
-\end{property}
+\\
+
 %
@@
 %
-\begin{property}
+
+\noindent\textit{Property 7.}
 The increase slope of $p_{w,CO}^t$ is higher when the reputation
@@
 \centering
-\includegraphics[scale=0.31]{Graph2.eps}
+\includegraphics[scale=0.4]{graphcomp.eps}
+\includegraphics[scale=0.4]{graphcomp.eps}
 \caption{Competitive and cooperative probabilities regarding four
@@
 
-\begin{comment}
-
-\section{Related Work}
-
-In many frameworks proposed in the literature, service selection
-and task allocation are regulated based on the reputation
-parameter \cite{Jurca1,Jurca2}. In \cite{Ali}, the proposed
-framework regulates the service selection based on the trust
-policies expressed by the service users. In \cite{Maximilien2},
-authors propose ontology for quality of service. Users compute the
-web services' reputation using ratings. The frameworks proposed in
-\cite{Kalepu,Maximilien1} address effective reputation mechanism
-for web services. All these models address the reputation in
-environments where web services function alone. In such models,
-web service efficiency is not discussed in details and in general,
-balancing the market share with the capacity is not considered as
-an issue for web service besides his reputation.
-
-There have been few work addressing the communities of web
-service. The objective is to facilitate and improve the process of
-web service selection and effectively regulate he process of
-request and task allocation \cite{Jacyno}. In \cite{Khosravifar2},
-authors propose a reputation-based architecture for communities
-and investigate the collusion scenarios that might falsely
-increase communities' reputation in the network. In
-\cite{Khosravifar1}, the authors mainly address the overall
-assessed reputation that is used as a main reason for service
-selection. The authors do not consider truth/lie telling analysis
-as a factor that impacts service selection in future.
-
-The contribution of this paper is the proposition of a coopetitive
-strategic model to analyze the interacting behavior of intelligent
-web services that are active in communities of web services. The
-proposed framework provides a reasoning technique that web
-services can use to increase their overall obtained utilities. The
-result of our proposed model is a probability distribution where
-an intelligent web service can use over different interacting
-strategies.
-
-Our model has the advantage of being simple and  straightforward
-in the contribution and the provided results. We considered two
-acting strategies where web services expect different sort of
-payoffs:  (1) $Competitive$ strategy where the web services claims
-that it can accomplish a task and therefore, takes the
-responsibility over the service consumer satisfaction; and (2)
-$Cooperative$ strategy where the web service does not take the
-responsibility to accomplish a task and only cooperates with other
-$Competitive$ web services. As future work, we plan to emphasize
-the service consumer role in the proposed model to obtain more
-accurate results when consumer posts service satisfaction
-feedback. Moreover, we would like to enhance  the reasoning
-technique's features to cope with different unexpected scenarios.
-We also need to expand the simulated environment to study
-different scenarios in a number of perspectives.
-
-\section{Conclusion}\label{Conclusion}
-The contribution of this paper is the proposition of a
-game-theoretic based model to analyze the best efficiency
-characteristics for the active services in open networks. The
-proposed framework considers the chances of web services in
-joining a community in different cases with truthful and lying
-information service agents. The proposed game analyzes the
-existing Nash equilibrium and situations where the maximum payoff
-is obtained.
-
-Our model has the advantage of being simple and taking into
-account three important factors: (1) rational services seek better
-status in the environment by joining the community; (2) rational
-information service agents obtain higher payoff by truth telling;
-and (3) the community is obtaining more effective web services
-while the information service agents challenge for providing
-truthful information. As future work, we plan to consider the user
-role in the game to obtain more accurate results when users act
-rationally. Moreover, we would like to achieve a collusion
-resistant efficiency mechanism, which is still an open problem in
-open environments.
-
-\end{comment}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%START YOUR SAMPLE TEXT HERE%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2012-12-16 papers/coopv3/IJWGS.tex
Changes

@@
 
-\authorA{author}
-
-\affA{Address}
+\authorA{Babak Khosravifar$^1$, Ehsan KhosrowshahiAsl$^2$,\newline Jamal Bentahar$^2$, Rabeb Mizouni$^3$ and\newline Hadi Otrok$^3$}
+
+\affA{$^1$McGill University, Canada, $^2$Concordia University, Canada,\\ $^3$Khalifa University, UAE\\
+$babak.khosravifar@mcgill.ca$, $e\_khosr@encs.concordia.ca$,\\ $bentahar@ciise.concordia.ca$,
+$rabeb.mizouni@kustar.ac.ae$,\\$hadi.otrak@kustar.ac.ae$}
 
@@
 
-\begin{bio}
-
-\end{bio}
+%\begin{bio}
+%
+%\end{bio}
 
@@
 \centering
-\includegraphics[scale=1]{architecture++.eps}
+\includegraphics[scale=0.9]{architecture++.eps}
 \caption{Web services are partitioned into competitive and
@@
 
+%\begin{table}
+%\centering
+%\caption{List of proposed system parameters.}
+%\begin{tabular}{|c|c||c|c|}
+%\hline
+%\textbf{Notation} & \textbf{Definition} & \textbf{Notation} & \textbf{Definition}\\
+%\hline\hline
+%$T_{QoS}^t$ & Required task QoS at time $t$ & $QoS_w^t$ & Web service $w$ QoS at time $t$ \\
+%$B_w^t$ & Budget associated to web service $w$ at time $t$ & $Rep^t_w$ & Reputation assigned for $w$ at time $t$\\
+%$Reward_w^t$ & The reward to update the reputation & $G^t_w$ & The growth factor of $w$ at time $t$\\
+%$\epsilon$ & The community membership fee & $\pi_{w,CM}^t$ & Competition payoff of $w$ \\
+%$\pi_{w,CO}^t$ & Cooperation payoff of $w$ & $p_{w,CM}^t$ & Competition probability of $w$ at time $t$\\
+%$p_{w,CO}^t$ & Cooperation probability of $w$ at time $t$& $COF_w^t$ & Cooperation fee of $w$ at time $t$\\
+%$\beta_w$ & Profit of $w$& $\mu_{w, CM}$ & Mean service fee for competing $w$ \\
+%$\mu_{w, CO}$ & Mean service fee for cooperating $w$ & $\tau_w^t$ & Coopetitive threshold of $w$ at time $t$ \\
+%$P_w^t$ & Probability of competing for $w$ at time $t$& $U_w^t$ & Utility of $w$ at time $t$\\
+%\hline
+%\end{tabular}
+%\label{Preliminaries}
+%\end{table}
+
 \begin{table}
@@
 \caption{List of proposed system parameters.}
-\begin{tabular}{|c|c||c|c|}
+\begin{tabular}{|c|c|}
 \hline
-\textbf{Notation} & \textbf{Definition} & \textbf{Notation} & \textbf{Definition}\\
+\textbf{Notation} & \textbf{Definition}\\
 \hline\hline
-$T_{QoS}^t$ & Required task QoS at time $t$ & $QoS_w^t$ & Web service $w$ QoS at time $t$ \\
-$B_w^t$ & Budget associated to web service $w$ at time $t$ & $Rep^t_w$ & Reputation assigned for $w$ at time $t$\\
-$Reward_w^t$ & The reward to update the reputation & $G^t_w$ & The growth factor of $w$ at time $t$\\
-$\epsilon$ & The community membership fee & $\pi_{w,CM}^t$ & Competition payoff of $w$ \\
-$\pi_{w,CO}^t$ & Cooperation payoff of $w$ & $p_{w,CM}^t$ & Competition probability of $w$ at time $t$\\
-$p_{w,CO}^t$ & Cooperation probability of $w$ at time $t$& $COF_w^t$ & Cooperation fee of $w$ at time $t$\\
-$\beta_w$ & Profit of $w$& $\mu_{w, CM}$ & Mean service fee for competing $w$ \\
-$\mu_{w, CO}$ & Mean service fee for cooperating $w$ & $\tau_w^t$ & Coopetitive threshold of $w$ at time $t$ \\
-$P_w^t$ & Probability of competing for $w$ at time $t$& $U_w^t$ & Utility of $w$ at time $t$\\
+$T_{QoS}^t$ & Required task QoS at time $t$ \\
+ $QoS_w^t$ & Web service $w$ QoS at time $t$ \\
+$B_w^t$ & Budget associated to web service $w$ at time $t$ \\ 
+$Rep^t_w$ & Reputation assigned for $w$ at time $t$\\
+$Reward_w^t$ & The reward to update the reputation \\ 
+$G^t_w$ & The growth factor of $w$ at time $t$\\
+$\epsilon$ & The community membership fee \\
+$\pi_{w,CM}^t$ & Competition payoff of $w$ \\
+$\pi_{w,CO}^t$ & Cooperation payoff of $w$ \\
+$p_{w,CM}^t$ & Competition probability of $w$ at time $t$\\
+$p_{w,CO}^t$ & Cooperation probability of $w$ at time $t$\\
+$COF_w^t$ & Cooperation fee of $w$ at time $t$\\
+$\beta_w$ & Profit of $w$ \\ 
+$\mu_{w, CM}$ & Mean service fee for competing $w$ \\
+$\mu_{w, CO}$ & Mean service fee for cooperating $w$ \\ 
+$\tau_w^t$ & Coopetitive threshold of $w$ at time $t$ \\
+$P_w^t$ & Probability of competing for $w$ at time $t$ \\ 
+$U_w^t$ & Utility of $w$ at time $t$\\
 \hline
@@
 Web services will need to pay $5$ units on each iteration of tasks being offered.
-As results the strategic coopetitive decision making process helps web services to still have benefit and random or all compete methods will lose a lot in these scenarios since making mistakes and trying to compete for jobs they cannot afford while having to pay higher membership fees is making them lose budget in a faster pace.
+As results clearly illustrate, the strategic coopetitive decision making process helps web services to still have increasing budget whereas random or all compete methods will lose a lot in these scenarios since making mistakes and trying to compete for jobs they cannot afford while having to pay higher membership fees is making them lose budget in a faster pace.
 In part \ref{membership_fee_graph}(c) the membership is higher than average of possible income of what tasks offer.
-It might not be rational for selfish self-interest web services to stay in these communities from utility point of view but as mentioned there might be other political reasons they might need to stay in these communities.
+It might not be rational for selfish self-interest web services to stay in these communities from utility point of view but as mentioned there might be other business reasons they might prefer to stay in these communities.
 As results show the random and all compete strategies make web services bank deplete in no time.
@@
 They try to maximise their own utiliy.
-Now we analyse how their strategy effects the social welfare or from user and community point of view how good the tasks are being performed.
+Now we analyse how their strategy effects the social welfare or how well  the tasks are being performed from user and community point of view.
 This directly affects user satisfation and community reputation in general.
-The Higher  quality and quantity of tasks perfromed leads to higher user satisfaction for the community which results in better reputaiton for the community.
-The results in Figure \ref{graph_task} shows the quality of quantity of tasks being done successfuly in three communities adopting the three different mentioned strategy decision algorithms.
-Figure \ref{graph_task} Part (a) and (b) depicts the number tasks succesfuly done.
+The higher quality and quantity of tasks perfromed leads to higher user satisfaction for the community which results in higher reputaiton for the community.
+The results in Figure \ref{graph_task} show the quality and quantity of tasks being done successfuly in three communities adopting the three different mentioned strategy decision algorithms.
+Figure \ref{graph_task} Part (a) depicts the number tasks succesfuly done.
 When web services are not capable of performing tasks alone and decide to compete for tasks with high QoS requirements they usually fail to perform the task how ever if they opt for cooperating although they have less income, they have higher chance of performing tasks collabratively with other web serives.
@@
 
-We conclude out analysis by discussing how effective our cooperative decision making process is by comparing the final utility of our agents here the end budget our web services have while deviating from our strategy adopted by an agent which can be either compete or cooperate to the other one.
+We conclude out analysis by discussing how effective our coopetitive decision making process is by comparing the final income of our web services when web services are deviating from our coopetitive strategy.
+The adopted strategy is either to compete or to cooperate by deviating we adopt the other strategy.
 In \ref{graph_dev} part (a) we randomly made the web services deviate from the calculated strategy.
-As the results depict, the more web services deviate from cooperative strategy the more they less budget they gain.
-Figure \ref{graph_dev} part (b) we pick one random web service and once simulate the scenario with its default cooperative strategy and then we redo the simulation with exact same enviroment parameters while adapting the other strategy which is to compete if our cooperative strategy suggested to cooperate or vice versa.
+As the results illustrate, the more web services deviate from cooperative strategy the less budget they gain.
+Figure \ref{graph_dev} part (b) we pick one random web service and once simulate the scenario with its default coopetitive strategy and then we redo the simulation with exact same enviroment parameters while adapting the other strategy which is to compete if our coopetitive strategy suggested to cooperate or vice versa.
 We run this scenario 50 times and at the end we check their budget and see if they gain more by deviating or not.
 We did this for one single deviation to ten different deviations in lifetime of a web service in community.
-As results indicate with high probability our cooperative strategy yields higher budgets at the end for web services.
+As results indicate with high probability our coopetitive strategy yields higher budgets at the end for web services.
 

### 2012-12-16 papers/coopv3/matlab-charts/avg_bud_medfee3set.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('avg_bud_medfee.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
+
+i=0:49;
+t=v(:,9);y=v(:,10);z=v(:,11);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 500 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',7000:2000:18000);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 50 0 18000]);
+
+% Add legend
+hleg1 = legend('Coopetitive','Competitive','Random Coopetitive');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.3,.7,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',11);
+%legend boxoff;
+
+% Add title and axis labels
+title('Medium Membership Fee', 'fontsize', 14);
+xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
+ylabel('Budget', 'FontSize',14);
+
+%Caxes = copyobj(gca,gcf);
[…]

### 2012-12-16 papers/coopv3/matlab-charts/avg_rep.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('avg_rep.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);z=v(:,3);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0:0.1:1);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+axis([0 50 0.2 1]);
+%axis([0 50 7000 18000]);
+
+% Add legend
+hleg1 = legend('Coopetitive','Competitive','Random Coopetitive');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.27,.71,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',11);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Number of Runs';'(b)'}, 'FontSize',14);
+ylabel('Reputation', 'FontSize',14);
+
[…]

### 2013-01-01 papers/coopv3/matlab-charts/comp_p.m
Fixed Chart Problem

@@ -45,7 +45,7 @@ set(hleg1,'FontSize',11);
 
 % Add title and axis labels
 % title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Number of Runs';'(b)'}, 'FontSize',14);
+xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
 ylabel('Reputation', 'FontSize',14);
 
 %Caxes = copyobj(gca,gcf);

### 2013-03-01 papers/coalition/coalition.tex
Changes

%% bare_conf.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[10pt, conference, compsocconf]{IEEEtran}
% Add the compsocconf option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

\usepackage{amssymb}
\usepackage{amsthm}

\theoremstyle{plain}
\newtheorem{thm}{Theorem} % reset theorem numbering for each chapter

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition} % definition numbers are dependent on theorem numbers
\newtheorem{exmp}[thm]{Example} % same for example numbers
% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Efficient Coalition Formation for Web Services}

% author names and affiliations
% use a multiple column layout for up to two different
% affiliations

\author{\IEEEauthorblockN{Authors Name/s per 1st Affiliation (Author)}
\IEEEauthorblockA{line 1 (of Affiliation): dept. name of organization\\
line 2: name of organization, acronyms acceptable\\
line 3: City, Country\\
line 4: Email: name@xyz.com}
\and
\IEEEauthorblockN{Authors Name/s per 2nd Affiliation (Author)}
\IEEEauthorblockA{line 1 (of Affiliation): dept. name of organization\\
line 2: name of organization, acronyms acceptable\\
line 3: City, Country\\
line 4: Email: name@xyz.com}
}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

\begin{abstract}
Web services are loosely-coupled business applications and willing to cooperate in distributed settings within different communities for better efficiency, market share and total payoff. There are number of proposed mechanisms and models on aggregating web services, however forming optimal and stable coalitions to maximize individual and community efficiency and income has got less attention. In this paper, we analyze coalition formations using cooperative game-theoretic methods. We propose a mechanism for membership requests and selection of web services in the scenarios in which there are already established communities, Moreover, we analyze the scenarios in which we do not have pre-defined communities and we develop a mechanism for web services to form stable groups allowing them to maximize their efficiency and generate near-optimal (welfare-maximizing) communities. The theoretical and simulation results proves that our algorithms provide web services and community owners with applicable and near optimal decision making mechanisms.

\end{abstract}

\begin{IEEEkeywords}
component; formatting; style; styling;

\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}

Over the past years, web applications have become part of critical buisiness services. The increasing reliance on web-based applications has had significant implications for service providers and its users.

*** talk about functional and non-functional requirements specially for critial applications
*** talk about community of web services

%Some random text:
%A Web service is an interface that describes a collection of operations that are network-accessible through standardized XML messaging. A Web service performs a specific task or a set of tasks.A Web service is described using a standard, formal XML notation, called its service description, that provides all of the details necessary to interact with the service, including message formats (that detail the operations), transport protocols, and location. Web service descriptions are expressed in WSDL.
%
%Web services can become untrustworthy for four reasons: unfulfilled requirements,malicious acts and code changes, erratic Internet behaviors or resource scarcity that result in unacceptable delays, and the poor interoperation of selected services.
%
%A Web service is an independent service component that aims to serve a variety of needs; it is not a single specific application. When the selected Web service component does not thoroughly fulfill its target need, the service becomes untrustworthy. Testing a service to determine that it fulfills all requirements is tricky because testing must verify the satisfaction of both functional and nonfunctional requirements. The nonfunctional requirements (reliability, availability, survivability, interoperability, and a host of other attributes) decide the service quality and require individual testing. Because the user can invoke a Web service only over the Internet, the challenge is how to test for all possible use scenarios.How can testing determine that the service operates effectively and efficiently for a specific application and environment?

\section{Preliminaries}

In this section we discuss the parameters and preliminary concepts that we use in the rest of paper. The way communities of web services are structured and engineered is described thoroughly in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

\subsection{Task Parameters}

\subsection{Web Sercive Parameters}

\subsection{Cooperative Game Concepts}
Cooperative game is a branch of game thoery that studies stretegies of self-interested agents in a setting where agents can increase their payoff by binding agreements and cooperating in groups. We let N to be a set of players. Any subset S of N can form a group that we call it a $coalition$. A $coalitional game$ is a pair $G = (N, v)$ where v is $characteristic function$ which given a coalition is a function $v: 2^N \to \mathbb{R}$ which maps the set of agents of the coalition to a real number v(S), the worth of S. This number usually resembles the output or payoff or performance of these agents working together as a coalition.  If a coalition S forms then it can devide its worth, v(S) in any possible among its members. The payoff vector $x \in \mathbb{R}^S$ is the ammount of payoff being distributed among agents of coalition S. The payoff vector satisfies two conditions:

\begin{itemize}
	\item $x \geq 0$ for all $i \in N$, and
	\item $\sum_{i \in S} x_i \leq v(S)$
\end{itemize}

The second condition is $feasibility$, according to equation below the payoff for each agent cannot be more than coalitions total gain. A payoff vector is also $efficient$ if all the payoff obtained by a coalition is distributed amongst coalition members: $\sum_{i \in S} x_i = v(S)$.

When dealing with cooperative games, two issues need to get addressed: 1. What coalition to form? 2. How to reward each each member when a task is completed?

{\bf Definition 1 (Shapley value)} Given a cooperative game (N, v), the Shapley value of player i is given by: 
\begin{equation}\label{eq:shapley}
\sum_{S \subset N \backslash \left\{i\right\} } \frac{|S|! (n-|S|-1)!}{n!} (v(S \cup \left\{i\right\}) - v(S))
\end{equation}

Shapley value is a unique and fair solution concept for payoff distribution between players or agents.

\subsubsection{Shapley value}
Shapley value is a solution concept for payoff vector, where it tries to achieve fairness
\subsubsection{Core}
123

\section{Problem Formulation and Modeling}

In this section,

\section{Introduction-t}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.7 and later.

All manuscripts must be in English. These guidelines include complete descriptions of the fonts, spacing, and related information for producing your proceedings manuscripts. Please follow them and if you have any questions, direct them to the production editor in charge of your proceedings at Conference Publishing Services (CPS): Phone +1 (714) 821-8380 or Fax +1 (714) 761-1784.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

\section{Type style and Fonts}
Wherever Times is specified, Times Roman or Times New Roman may be used. If neither is available on your system, please use the font closest in appearance to Times. Avoid using bit-mapped fonts if possible. True-Type 1 or Open Type fonts are preferred. Please embed symbol fonts, as well, for math, etc.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals/conferences use top floats
% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
% command of the stfloats package.

\section{Conclusion}
The conclusion goes here. this is more of the conclusion

% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank...
more thanks here

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
\bibliographystyle{IEEEtran}
\bibliography{bibi}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

%\begin{thebibliography}{1}

%\bibitem{IEEEhowto:kopka}
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
%\end{thebibliography}

% that's all folks
\end{document}

### 2013-03-01 papers/coalition/coalition.tex
Changes

@@
 
-{\bf Definition 1 (Shapley value)} Given a cooperative game (N, v), the Shapley value of player i is given by: 
+{\bf Definition 1 (Shapley value)} Given a cooperative game (N, v), the Shapley value of player i is given by\cite{shapley_value}: 
 \begin{equation}\label{eq:shapley}
@@
 
-Shapley value is a unique and fair solution concept for payoff distribution between players or agents.
+Shapley value is a unique and fair solution concept for payoff distribution between agents. It basicly rewards agents with amount of marginal contribution they have to the coalition.
 
-\subsubsection{Shapley value}
-Shapley value is a solution concept for payoff vector, where it tries to achieve fairness
-\subsubsection{Core}
-123
+{\bf Definition 1 (Core)}
 

### 2013-03-01 papers/coalition/coalition.tex
Changes

@@
 A payoff vector is also $efficient$ if all the payoff obtained by a coalition is distributed amongst coalition members: $\sum_{i \in S} x_i = v(S)$.
+This definition of characteristic function works in $transferable utility$ (TU) settings, where utility (payoff) is transfarable from one player to other, in other words players have common currency and a unit of income is worth same for all players \cite{myerson1991game}.
 
-When dealing with cooperative games, two issues need to get addressed: 1. What coalition to form? 2. How to reward each each member when a task is completed?
+When dealing with cooperative games, two issues need to get addressed: 1.
+What coalition to form (Canonical games)?
+2.
+How to reward each each member when a task is completed (Coalition-formation games)?
 
@@
 
-{\bf Definition 1 (Core)}
+{\bf Definition 2 (Core)} A payoff vector x denoted by C(N,v) is in the core of a coalitional game (N, v) if and only if
+\begin{equation}\label{eq:core}
+\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S)
+\end{equation}
+The core if is not empty is basicly a payoff vector (x) where no where no subset of players $S^\prime$ could gain more by deviating and making their own coalition $\sum_{i \in S^\prime} x_i \geq v(S^\prime)$.
 

### 2013-03-02 papers/coalition/coalition.tex
Changes

@@
 %
-%\usepackage[cmex10]{amsmath}
+\usepackage[cmex10]{amsmath}
 % A popular package from the American Mathematical Society that provides
@@
 \begin{IEEEkeywords}
-component; formatting; style; styling;
+Web services; Cooperative game thoery; Community of services;
 
@@
 
-*** talk about functional and non-functional requirements specially for critial applications
-*** talk about community of web services
+*** on functional and non-functional requirements specially for critial applications
+*** on community of web services
 
@@
 
+\subsection{The Architecture and Entities }
+\subsubsection{Web Services}
+\subsubsection{Master Web Service of Communities}
+\subsubsection{Users}
+
 \subsection{Task Parameters}
+\subsubsection{Request rate}
+\subsubsection{Consumption}
+\subsubsection{Requested Reponse Time}
+\subsubsection{Requested Availability}
+\subsubsection{Requested Success Rate}
 
 \subsection{Web Sercive Parameters}
+\subsubsection{Throughput}
+\subsubsection{Capacity}
+\subsubsection{Cost}
+\subsubsection{Reponse Time}
+\subsubsection{Availability}
+\subsubsection{Reliability}
+\subsubsection{Success Rate}
+\subsubsection{Reputation}
 
@@
 \end{equation}
-The core if is not empty is basicly a payoff vector (x) where no where no subset of players $S^\prime$ could gain more by deviating and making their own coalition $\sum_{i \in S^\prime} x_i \geq v(S^\prime)$.
+The core if is not empty is basicly a set of payoff vectors (x) where no subset of players $S^\prime$ could gain more by deviating and making their own coalition $\sum_{i \in S^\prime} x_i \geq v(S^\prime)$.
+The sum of payoffs to the agents in any subcoalition S is at least as large as the amount that these agents could earn by forming a coalition on their own.
+In a sense it is analogue to Nash equilibrium, except that it about deviations by groups of agents.
+The core is the strongest and most popular solution concept in cooperative game thoery, however its computationally very heavy and is not computationally tractable as number of players increase.
+The core of some real-world problem games may be empty, which means having characteristic function $v$ there might be no possible distribution of payoff assuring stability of subgroups.
+
+{\bf Definition 3 (Convex cooperative games)} A game with characteristic function v(S) is convex if:
+\begin{equation}\label{eq:convex}
+V(S) + V(T) \leq v(S \cup T) + v (S \cap T), \forall S,T \subseteq N.
+\end{equation}
+According to a classic result by Shapley \cite{S1971cores} convex games always have a non-empty core.
+In order to come with an algorithm be to able to evaluate if a game with characteristic function v(S) is convex or not, we can use the equation below and will prove its analogous to convexity condition:
+\begin{equation}\label{eq:convex_snow}
+v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T), \forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N; 
+\end{equation}
+
+{\bf Proof:}
+
+\begin{gather*}\label{convexsnowproof}
+v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
+\\
+\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq v (T \cup \left\{i\right\}) + v(S)
+\end{gather*}
+
+We know $T \subseteq N - \left\{i\right\}$, therefor:
+
+\begin{equation*}
+(S \cup \left\{i\right\}) \cap T = T \cup S
+\end{equation*}
+
+and we have $S \subseteq T$, therefor:
+
+\begin{equation*}
+(S \cup \left\{i\right\}) \cap T = S
+\end{equation*}
+
+With a variable chnage of S we have:
+
+\begin{gather*}
+v(S \cup \left\{i\right\}) + v(T) \leq v (T \cup \left\{i\right\}) + v(S)
+\\
+\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq v((S \cup \left\{i\right\}) \cup T) + v((S \cup \left\{i\right\}) \cap T)
+\\
+\rightarrow v(S^\prime) + V(T) \leq v(S^\prime) + v(S^\prime \cap T)
+\end{gather*}
+
+This means inorder to keep the characteristic function convex, new agents should have more marginal contribution as coalition size grows.
 
@@
 
+In this section, we present the architechture of different web service community models and formulate how both web services and community masters as rational agents would maximise their payoff.
+
+\subsection {Web Services and A Grand Community}
+
+In this scenario, there are is a community controller by a community master web sercice. The community master has a secured request rates $(R_{master})$ from users.
+
+\section{Experimental Results}
+
 In this section,
-
-\section{Introduction-t}
-% no \IEEEPARstart
-This demo file is intended to serve as a ``starter file''
-for IEEE conference papers produced under \LaTeX\ using
-IEEEtran.cls version 1.7 and later.
-
-All manuscripts must be in English.
-These guidelines include complete descriptions of the fonts, spacing, and related information for producing your proceedings manuscripts.
-Please follow them and if you have any questions, direct them to the production editor in charge of your proceedings at Conference Publishing Services (CPS): Phone +1 (714) 821-8380 or Fax +1 (714) 761-1784.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-
-\subsection{Subsection Heading Here}
-Subsection text here.
-
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
-
-\section{Type style and Fonts}
-Wherever Times is specified, Times Roman or Times New Roman may be used.
-If neither is available on your system, please use the font closest in appearance to Times.
-Avoid using bit-mapped fonts if possible.
-True-Type 1 or Open Type fonts are preferred.
-Please embed symbol fonts, as well, for math, etc.
 

### 2013-03-02 papers/coalition/coalition.tex
Changes

@@
 
-In this scenario, there are is a community controller by a community master web sercice. The community master has a secured request rates $(R_{master})$ from users.
+In this scenario, there are is a community controller by its master web sercice.
+The community master has some request rate $(R_{master})$ from users.
+Web services need to join a community to be able to get tasks from a master web service.
+Each web service comes with different quality of service patameters and a throughput $(T_ws)$.
+Throughput is the average rate of tasks a web
 

### 2013-03-02 papers/coalition/coalition.tex
Changes

@@
 
-*** on functional and non-functional requirements specially for critial applications
-*** on community of web services
+\\ *** on functional and non-functional requirements specially for critial applications
+
+\\ *** on community of web services
+
+\cite{DBLP:conf/IEEEscc/KhosravifarABT11}
+\cite{DBLP:conf/IEEEscc/LimTMB12}
 
@@
 
+\subsubsection{Shapley value}
+
 {\bf Definition 1 (Shapley value)} Given a cooperative game (N, v), the Shapley value of player i is given by\cite{shapley_value}: 
@@
 Shapley value is a unique and fair solution concept for payoff distribution between agents. It basicly rewards agents with amount of marginal contribution they have to the coalition.
+
+\subsubsection{Core}
 
@@
 This means inorder to keep the characteristic function convex, new agents should have more marginal contribution as coalition size grows.
+
+\subsubsection{Coalition Structure Formation}
+
+Coalition structure formation is the problem of finding best partition of agents into teams, focusing more on optimizing the coalition's ``owner'' payoff.
+In these settings performance of individual agent is less important than the $social welfare$ of the system, which is the sum of the values of all teams.
+Having characterestic function game G, a coalition structure (CS) is $socially optimal$ is CS belongs to set $argmax_{CS \in CS_N}v(CS)$ where v(CS) is sum of the total valuation function of all coalitions inside CS $(v(CS) = \sum_{C \in CS_N}v(CS))$.
 

### 2013-03-03 papers/coalition/coalition.tex
Changes

--- 2013-03-02 papers/coalition/coalition.tex
@@
 \ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
+  \usepackage[pdftex]{graphicx}
   % declare the path(s) where your graphic files are
@@
   % driver is specified.
-  % \usepackage[dvips]{graphicx}
+  \usepackage[dvips]{graphicx}
   % declare the path(s) where your graphic files are
@@
 \fi
+
 % graphicx was written by David Carlisle and Sebastian Rahtz. It is
@@
 
-*** on functional and non-functional requirements specially for critial applications
-*** on community of web services
+TODO on functional and non-functional requirements specially for critial applications \\
+
+TODO on community of web services \\
+
+TODO Problems of \cite{Chun02user-centricperformance, mcknight00a, DBLP:journals/internet/BenatallahSD03, Khosravifar:2009:AIR:1586636.1586906, Rosario:2008:PQS:1512146.1512290} \\
+
+TODO Problems of \cite {DBLP:conf/IEEEscc/LimTMB12} having to cop and optimizing for with all weak web services reduces the optimal result\\
+
+TODO Problems of \cite {DBLP:conf/IEEEscc/KhosravifarABT11} not considering the current web services in coalition and startegies are only based on master web service and new web service gain\\
 
@@
 
+\subsubsection{Coalition Structure Formation}\label{sec:coalition}
+
+Coalition structure formation is the problem of finding best partition of agents into teams, focusing more on optimizing the coalition's ``owner'' payoff.
+In these settings performance of individual agent is less important than the \emph{social welfare} of the system, which is the sum of the values of all teams.
+Having characterestic function game G, a coalition structure (CS) is \emph{socially optimal} is CS belongs to set $argmax_{CS \in CS_N}v(CS)$ where v(CS) is sum of the total valuation function of all coalitions inside CS $(v(CS) = \sum_{C \in CS_N}v(CS))$.
+The outcome of a characterestic function game in coalition structure settings, consists of two parts; first a disjoint partition of players (agents) into coalitions, called a \emph{coalition structure} (CS) and second a \emph{payoff vector} as mentioned in cooperative game solution concepts, which distributes the value of each coalition among its members.
+
 \section{Problem Formulation and Modeling}
@@
 Each web service comes with different quality of service patameters and a throughput $(T_ws)$.
-Throughput is the average rate of tasks a web
+Throughput is the average rate of tasks a web service can perform.
+Therefore, the master web service is providing tasks with rate of $R_{ws}$ and web services perform tasks with some QoS output metrics and a rate or $T_{ws}$.
+In this setting, we define the value of the coalition as follows:
+\begin{equation*}
+output(C) = \sum_{ws}{T_{ws}} \times QoS_{ws}
+\end{equation*}
+
+\begin{equation*}
+v(C) = \left\{ 
+  \begin{array}{l l}
+    output(C) & \quad \text{if $\sum_{ws}{T_{ws}} \leq R_{master}$}\\
+    output(C) \times \frac{R_{master}}{\sum_C{T_{ws}}} & \quad \text{if $\sum_{ws}{T_{ws}} > R_{master}$}
+  \end{array} \right.
+\end{equation*}
+
+The output of a coalition of web services is the rate and quality of task they can perform.
+If the rate is more than master's input task rate, it means the web services inside the community are capable of doing more tasks than exists.
+Considering this the valuation function will balance the output performance and will be the exact ammount and quality of work they can perform within the particular community.
+** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests.
+**
+
+In the first scenario, we only consider one grand coalition and analyse the system from point of view of one master web service and a collection of web services.
+The master web service decides which members can join or should leave the community and distributes the income or tasks among its community members.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{s1.eps}
+\caption{Web Services and A Grand Community}
+\label{fig_sim}
+\end{figure}
+
+The membership decision is made based on throughput and QoS of the requested web service.
+The goal is to have quality web services in community so the community stays stable and no other web services would have incentives to deviate and join ``other'' coalitions.
+Therefore, we it check the core membership of the coalition of all current community members and the new web service.
+Our algorithm uses the shapley value distribution method as described in equation \ref{eq:shapley} to distribute gain of $v(C)$ among all members and then checks if shapley value payoff vector for this community having characteristic function $v(C)$ is Core stable or not.
+In shapley value payoff vector, the payoff for each web service i, is calculated based on their contribution $v(C \cup {i}) - v(C)$ and then averaging over the possible different permutations in which the coalition can be formed.
+It is proven in \cite{DBLP:conf/ijcai/GrecoMPS11} if the Core is non-empty, the shapley payoff vector is a member of Core, so in our algorithm we check the core membership of this payoff vector.
+
+\subsection {Web Services and Many Communities}
+
+In this scenario we consider multiple communities owned by multiple master web services which provide independant request pools.
+Like first scenario master web services form coalitions with web services.
+We use coalition structure formation methods to partition web services into non-empty disjoint coalition structures.
+As mentioned in section \ref{sec:coalition} these algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11} try to solve two fundamental problems of what coalitions to form, and how will the members of these coalitions distribute their total gain to make these coalition structures stable.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{s2.eps}
+\caption{Web Services and Many Communities}
+\label{fig_sim}
+\end{figure}
+
+One of the properties of CS algorithms in our scenario is tha they partition web services with low throughput rate usually join coalitions with less request rate.
+Since the characteristic function $v(C)$ and  the fair payoff vector of shapley value is proportional to their contribution, the web services with small contribution will get payed much less in communities having web services with throughput.
+On the other hand, accoring to valuation function $v(C)$ web services with high throughput will not contribute well to commuinities with low ammount of user requests.
+The strong web services are much more likely to deviate that coalition joining a stronger coalition, making the initial coalition unstable.
+In coalition structure formation study, as mentioned in section \ref{sec:coalition}, maximizing social welfare is more on focus.
+Most algorithms in this area try to maximise overall social welfare.
+For any coalition structure $\pi$, let $v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$ which we call it social welfare.
+The problems in this area deal with finding the maximum value for social welfare over all the possible coalition structures $\pi$.
+These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} ignore the stability of coalitions from individual agent point of view.
+However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}.
+There are even anytime algorithms designed for this end\cite{eps267179}.
+It can be interrupted before it would have normally terminated and yet privade a solution within a bound from the optimal one which makes it very practical to use real world applications.
+The problem is that they try to maximize social benefit while contradicts with interests of selfish self-interest web services.
+However, expirements show web services still reasonably close to optimal payoffs and tasks while we try to optimize the overall social welfare.
+In expirements section, we analyze these scenarios with real world web service data.
+
+\subsection {Web Services collaborating independently}
+
+In this scenario, we do not consider pre-defined communities and master web services.
+Here web services are interested in forming coalitions to perform better and share benefits.
+We do not consider concept of master web services providing requests for others, each web service comes with its own request load which in this scenario we call it \emph{market share}.
+Therefore coalitions will form is web services working together can perform and gain more than working alone individually.
+The worth or value of coalitions of web services is different in this setting, average the QoS metrics of web service, multiply it by a weight where the importance or weigth of each metric is dependant on type of users and requests web services are dealing with.
+For each webservice we multiplay this by web services's market share $(MarketShare_{ws})$ and the summation would be the characterestic or valuation of independent web service coalitions.
+
+\begin{equation*}
+v(C) = \sum_{ws}{\sum_{m=metrics}{\sum_{ws}{QoS^m_{ws} \times C_{coef}} \times w_{metric} } \times ms_{ws}}
+\end{equation*}
+
+$C_{coef}$ is \emph{Collabrative Coefficient} for each QoS metric, it determines how web services providing that QoS metric individually will be effected in a coalition environment.
+If it is more than 1, is means they increase performance by working together and they are \emph{super additive}, otherwise it depicts they would perform better in linear sense if they worked alone.
+Since there are no master web serivces, we assume they eather dynamicly vote for one, or collabrate and agree on decisions and distribute task in round robin or fair fashion.
+Like ``Web Services and Many Communities'' scenario, both core coalition structure analysis and social welfare analysis are applicable in this scenario.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{s3.eps}
+\caption{Web Services collaborating independently}
+\label{fig_sim}
+\end{figure}
 

### 2013-03-03 papers/coalition/coalition.tex
Changes

@@
 \begin{equation*}
-output(C) = \sum_{ws}{T_{ws}} \times QoS_{ws}
+output(C) = \sum_{ws}{(T_{ws} \times QoS_{ws})}
 \end{equation*}
@@
     output(C) & \quad \text{if $\sum_{ws}{T_{ws}} \leq R_{master}$}\\
-    output(C) \times \frac{R_{master}}{\sum_C{T_{ws}}} & \quad \text{if $\sum_{ws}{T_{ws}} > R_{master}$}
+    output(C) \times \frac{R_{master}}{\sum_{ws}{T_{ws}}} & \quad \text{if $\sum_{ws}{T_{ws}} > R_{master}$}
   \end{array} \right.

### 2013-03-03 papers/coalition/coalition.tex
Changes

@@
 Web services need to join a community to be able to get tasks from a master web service.
-Each web service comes with different quality of service patameters and a throughput $(T_ws)$.
+Each web service comes with different quality of service patameters and a throughput $(T_{ws})$.
 Throughput is the average rate of tasks a web service can perform.
@@
 In shapley value payoff vector, the payoff for each web service i, is calculated based on their contribution $v(C \cup {i}) - v(C)$ and then averaging over the possible different permutations in which the coalition can be formed.
-It is proven in \cite{DBLP:conf/ijcai/GrecoMPS11} if the Core is non-empty, the shapley payoff vector is a member of Core, so in our algorithm we check the core membership of this payoff vector.
+It is proven in convex games the Shapley value lies in the core \cite{DBLP:conf/ijcai/GrecoMPS11, myerson1991game}.
+Therefore if the Core is non-empty, the Shapley payoff vector is a member of Core, so in our algorithm we check the core membership of this payoff vector.
 

### 2013-03-04 notes/coop.tex
Changes

@@
 
+\hrule
+
+Any convex game is necessarily superadditive: if a game G = (N, v) is convex, and C and D are two disjoint subsets of N, then we have (here we use our assumption that v(.) = 0).
+However, the converse is not always true, as illustrated
+by the following example. 
+Consider a game G = (N, v), where N = {1, 2, 3}, and v(C) = 1 if |C| .
+2 and v(C) = 0 otherwise; this game is known as the 3-player majority game.
+It is easy to check that this game is superadditive.Onthe other hand, forC = {1, 2} andD = {2, 3},we have v(C) = v(D) = 1
+
 \bibliographystyle{plain}

### 2013-03-04 papers/coalition/coalition.tex
Changes

@@
 
+\subsubsection{$\epsilon-Core$}
+If core set is not empty, it means no coalition of players can gain anything by deviating, it is the strongest stable condition.
+An outcome would be unstable if a coalition can benefit even by a small amount from deviating.
+This is a strong requirement.
+In some situations, deciations can be costly or agents may have some loyatly to their coalitions or even it can be computationaly intractable to find those small benefits.
+It would only make sense for a coalition to deviate if the gain from a deviation exceeded a particular cost for example the costs of deviation.
+$\epsilon-Core$ relaxes the notion of the core, and only require that no coalition can benefit significantly or within a constant ammount($\epsilon$) by deviating.
+
+\begin{equation}\label{eq:core}
+\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
+\end{equation}
+
 \subsubsection{Coalition Structure Formation}\label{sec:coalition}

### 2013-03-06 papers/coalition/coalition.tex
Changes

@@
 
-\author{\IEEEauthorblockN{Authors Name/s per 1st Affiliation (Author)}
-\IEEEauthorblockA{line 1 (of Affiliation): dept. name of organization\\
-line 2: name of organization, acronyms acceptable\\
-line 3: City, Country\\
-line 4: Email: name@xyz.com}
+\author{\IEEEauthorblockN{Ehsan Khosrowshahi Asl, Jamal Bentahar}
+\IEEEauthorblockA{Faculty of Engineeing and Computer Science\\
+Concordia University\\
+Montreal, Canada\\
+e\_khosr@encs.concordia.ca,bentahar@ciise.concordia.ca}
 \and
-\IEEEauthorblockN{Authors Name/s per 2nd Affiliation (Author)}
-\IEEEauthorblockA{line 1 (of Affiliation): dept. name of organization\\
-line 2: name of organization, acronyms acceptable\\
-line 3: City, Country\\
-line 4: Email: name@xyz.com}
+\IEEEauthorblockN{Hadi Otrok, Rabeb Mizouni}
+\IEEEauthorblockA{Department of Electrical and Computer Engineering\\
+Khalifa University\\
+Dubai, UAE\\
+hadi.otrak, rabeb.mizouni@kustar:ac:ae}
 }
@@
 Considering this the valuation function will balance the output performance and will be the exact ammount and quality of work they can perform within the particular community.
-** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests.
+%** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests.
 **
@@
 In the first scenario, we only consider one grand coalition and analyse the system from point of view of one master web service and a collection of web services.
-The master web service decides which members can join or should leave the community and distributes the income or tasks among its community members.
+The master web service decides which members can join %or should leave%
+the community and distributes the income or tasks among its community members.
 
@@
 Therefore if the Core is non-empty, the Shapley payoff vector is a member of Core, so in our algorithm we check the core membership of this payoff vector.
+
+Our algorithm works as follows.
+We have an established community with a master and some (slave) web services already residing in community.
+Now we have a request from a web service to join our community.
+The ideal solution in our method would be analyzing the core or $\epsilon-core$ stability of group having this new member.
+However the normal core membership algorithms are intractable.
+We exploit the equation \ref{eq:convex_snow} to check convexity of our characteristic function game having the new member.
+In that equation we set T to be our community members (C) before having the new web service.
+We set ${i}$ the new web service, and then verify the equation for S, setting $ S = T / W $ where $W$ is all 1-member subset of set C.
+We can relax the equation a bit by adding a constant epsilon to left side of equation.
+We call this method \emph{Depth-1 Convex-Checker} algorithm.
+If the equation is true for all $W$ we let the member join our community, since he will contribute good enough to make our new community stable.
+The run time complexity of this algorithm is O(n) which is huge reduction from $O(2^n)$ checking all possible subsets of N.
+In our second method, we use the same algorithm however this time we set W to be all possible subsets of size two and one of C.
+We call this method \emph{Depth-2 Convex-Checker} and its run time complexity is $O(n^2)$.
+It is possible to develop an anytime algorithm by continuing verifying this condition against all subsets of size 3 to N, and stop whenever we are interrupted.
 
@@
 
-In this section,
+In this section, we discuss the experiments we performed for our scenarios to validate applicability and performance of our proposed methods in realistic environments.
+We created a pool of web services and populated most of their QoS parameters from a real world web service dataset \cite{DBLP:conf/smc/Al-MasriM09a}.
+We programmed the simulations using Java and executed the simulations on a Intel Xeon X3450 machine with 4GBs of memory.
+For other parameters we used normal distribution with parameters that make most sense in real world examples.
+
+We first analyze the most important performance result our communities should perform, quality and quantity of tasks successfully performed by our communities.
+This is the most important criteria for user satisfaction.
+We initiate the community with few web services, then let rejecting and accepting of random webservices go for a while, after that we start task distribution for the cummunities and let them allocate tasks for web services.
+Then we measure the average output performance of tasks in communities following different methods.
+Figure \ref{performanceall} shows the resutlts.
+
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[scale=0.29]{task_done_opt.eps}
+\includegraphics[scale=0.29]{task_qos_opt.eps}
+\caption{Part (a): Cumulative number of tasks succesfully done. Part
+(b): Average QoS of tasks performed.} \label{performanceall}
+\end{figure}
 

### 2013-03-06 papers/coalition/charts/old-charts/task_satisfaction.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('task_satisfaction.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);z=v(:,3);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 500 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',0:0.1:1);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+axis([0 50 0 1]);
+%axis([0 50 7000 18000]);
+
+% Add legend
+hleg1 = legend('Coopetitive','Competitive','Random Coopetitive');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.3,.71,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',11);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Number of Runs';'(b)'}, 'FontSize',14);
+ylabel('Task Satisfaction Ratio', 'FontSize',14);
+
[…]

### 2013-03-06 papers/coalition/charts/task_done.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('task_done.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|+-|.|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);z=v(:,3);tt=v(:,4);yy=v(:,5);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,i,tt,i,yy,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0:200:1600);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 50 0 1600]);
+
+% Add legend
+hleg1 = legend('0% Deviation','10% Deviation','20% Deviation','30% Deviation','40% Deviation');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.24,.63,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
[…]

### 2013-03-06 papers/coalition/charts/task_done_opt.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('task_done_opt.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|.|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);z=v(:,3);tt=v(:,4);yy=v(:,5);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,i,tt,i,yy,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0:200:1600);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 50 0 1600]);
+
+% Add legend
+hleg1 = legend('e-Core','depth-2 Convex','depth-1 Convex','3-Way Sat','2-Player Game');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.24,.63,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Iterations';'(a)'}, 'FontSize',14);
[…]

### 2013-03-06 papers/coalition/charts/task_qos_opt.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('task_qos_opt.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|.|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);z=v(:,3);tt=v(:,4);yy=v(:,5);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,i,tt,i,yy,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',0:200:1600);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+%axis([0 50 0.4 1]);
+%axis([0 50 0 1600]);
+
+% Add legend
+hleg1 = legend('e-Core','depth-2 Convex','depth-1 Convex','3-Way Sat','2-Player Game');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.24,.63,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Iterations';'(a)'}, 'FontSize',14);
[…]

### 2013-03-06 papers/coalition/charts/task_qos_opt.m
Changes

@@ -45,7 +45,7 @@ set(hleg1,'FontSize',10);
 
 % Add title and axis labels
 % title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Iterations';'(a)'}, 'FontSize',14);
+xlabel({'Iterations';'(b)'}, 'FontSize',14);
 ylabel('Average QoS of Tasks Performed', 'FontSize',14);
 
 %Caxes = copyobj(gca,gcf);

### 2013-03-06 papers/coalition/coalition.tex
Changes

@@
 Then we measure the average output performance of tasks in communities following different methods.
-Figure \ref{performanceall} shows the resutlts.
 
@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[scale=0.29]{task_done_opt.eps}
-\includegraphics[scale=0.29]{task_qos_opt.eps}
+\includegraphics[scale=0.61]{task_done_opt.eps}
+\includegraphics[scale=0.61]{task_qos_opt.eps}
 \caption{Part (a): Cumulative number of tasks succesfully done. Part
@@
 \end{figure}
+
+Figure \ref{performanceall} depicts the results of simulation of optimal $\epsilon-Core$, \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods.
+The the \emph{optimal core} method we capped the coalition size to 23 web services, since anything more than that would require analysis with time complexity of O(2^22) which would made that impractical to run in our simulations.
+In other methods there were no cap on size of the community and we had communities of size 60 web services at some points.
+The results show depth-2 and 1 convex checker methods are performing well compared to other methods and all not far from optimal.
 

### 2013-03-06 papers/coalition/coalition.tex
Changes

@@
 Figure \ref{performanceall} depicts the results of simulation of optimal $\epsilon-Core$, \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods.
-The the \emph{optimal core} method we capped the coalition size to 23 web services, since anything more than that would require analysis with time complexity of O(2^22) which would made that impractical to run in our simulations.
+The the \emph{optimal core} method we capped the coalition size to 23 web services, since anything more than that would require analysis with time complexity of $O(2^22)$ which would made that impractical to run in our simulations.
 In other methods there were no cap on size of the community and we had communities of size 60 web services at some points.

### 2013-03-06 papers/coalition/coalition.tex
Changes

@@
 Montreal, Canada\\
-e\_khosr@encs.concordia.ca,bentahar@ciise.concordia.ca}
+e\_khosr@encs.concordia.ca, bentahar@ciise.concordia.ca}
 \and
@@
 
+The valuation function $v(C)$ for this scenario is same as \emph{one grand community} scenario, however in order to prevent master web services joining same community we set $v(C) = 0$, where C has two or more master web services as members.
+
 One of the properties of CS algorithms in our scenario is tha they partition web services with low throughput rate usually join coalitions with less request rate.
-Since the characteristic function $v(C)$ and  the fair payoff vector of shapley value is proportional to their contribution, the web services with small contribution will get payed much less in communities having web services with throughput.
-On the other hand, accoring to valuation function $v(C)$ web services with high throughput will not contribute well to commuinities with low ammount of user requests.
-The strong web services are much more likely to deviate that coalition joining a stronger coalition, making the initial coalition unstable.
-In coalition structure formation study, as mentioned in section \ref{sec:coalition}, maximizing social welfare is more on focus.
-Most algorithms in this area try to maximise overall social welfare.
+Since the characteristic function $v(C)$ and  the fair payoff vector of shapley value is proportional to web services' contribution, the web services with small contribution will get paid much less in communities having web services with high throughput.
+On the other hand, according to valuation function $v(C)$ web services with high throughput will not contribute well to communities with low amount of user requests.
+The strong web services are much more likely to deviate weak coalitions, joining a stronger coalition, making the initial coalition unstable.
+
+In coalition-formation games, formation of the coalitions is the most important aspect of in the game.
+These solutions focus on maximizing social welfare.
 For any coalition structure $\pi$, let $v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$ which we call it social welfare.
 The problems in this area deal with finding the maximum value for social welfare over all the possible coalition structures $\pi$.
-These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} ignore the stability of coalitions from individual agent point of view.
+There are $centralized$ algorithms for this end, however these approaches are generally NP-complete.
+The reason is that number of all possible partitions of a set $N$ grows exponentially with the number of players in $n$, and the centralized algorithms need to iterate through all these partitions.
+%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centrilized algorithms, where all the complexity.
 However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}.
-There are even anytime algorithms designed for this end\cite{eps267179}.
-It can be interrupted before it would have normally terminated and yet privade a solution within a bound from the optimal one which makes it very practical to use real world applications.
-The problem is that they try to maximize social benefit while contradicts with interests of selfish self-interest web services.
-However, expirements show web services still reasonably close to optimal payoffs and tasks while we try to optimize the overall social welfare.
-In expirements section, we analyze these scenarios with real world web service data.
+In our application, we prefer not having a centralized decision maker dictating all web services their decisions.
+Becuase of this plus the complexity issues we would prefer a distributed algorithm where each community master can be a decision maker.
+The aim is to find low complexity and distributed algorithms for forming coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
+The distributed merge-and-split algorithm in \cite{DBLP:journals/igtr/AptW09} suits our application very well.
+It keeps splitting and mergin coalitions where it is preferred by all players inside those coalitions.
 

### 2013-03-07 papers/coalition/charts/least_core.m
Changes

@@ -1,0 +1,58 @@
+[v,T,vT]=xlsread('least_core.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','+|--|--|.|:')
+
+i=0:99;
+t=0:0.01:1;
+y=v(:,1);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,y,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+%set(gca,'XTick',0:10:100);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0:0.1:1);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'0';'0.1';'0.2';'0.3';'0.4';'0.5';'0.6';'0.7';'0.8';'0.9';
+    '1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '0.4';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '0.6';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '0.8';' ';' ';' ';' ';' ';' ';' ';' ';'1';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+axis([0 100 0 1.1]);
+%axis([0 50 0 1600]);
+
+% Add legend
+hleg1 = legend('Least e-Core');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.31,.69,.05,.1]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Epsilon (ratio)'}, 'FontSize',14);
+ylabel('Core Non-Empty', 'FontSize',14);
+
+%Caxes = copyobj(gca,gcf);
[…]

### 2013-03-07 papers/coalition/charts/s2_task_done.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('s2_task_done.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|--|--|.|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0:1000:7000);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 50 0 7000]);
+
+% Add legend
+hleg1 = legend('Dynamic Coalition Formation','Normal Method');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.31,.69,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Iterations';'(a)'}, 'FontSize',14);
+ylabel('Number of tasks successfully done', 'FontSize',14);
+
+%Caxes = copyobj(gca,gcf);
[…]

### 2013-03-07 papers/coalition/charts/s2_task_qos.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('s2_task_qos.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|--|--|.|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0.5:0.04:0.7);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+axis([0 50 0.5 0.7]);
+%axis([0 50 0 1600]);
+
+% Add legend
+hleg1 = legend('Dynamic Coalition Formation','Normal Method');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.31,.69,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Iterations';'(b)'}, 'FontSize',14);
+ylabel('Average QoS of Tasks Performed', 'FontSize',14);
+
[…]

### 2013-03-07 papers/coalition/coalition.tex
Changes

@@
 \subsection{Cooperative Game Concepts}
-Cooperative game is a branch of game thoery that studies stretegies of self-interested agents in a setting where agents can increase their payoff by binding agreements and cooperating in groups.
+Cooperative game is a branch of game theory that studies strategies of self-interested agents in a setting where agents can increase their payoff by binding agreements and cooperating in groups.
 We let N to be a set of players.
@@
 This number usually resembles the output or payoff or performance of these agents working together as a coalition.
-If a coalition S forms then it can devide its worth, v(S) in any possible among its members.
-The payoff vector $x \in \mathbb{R}^S$ is the ammount of payoff being distributed among agents of coalition S.
+If a coalition S forms then it can divide its worth, v(S) in any possible among its members.
+The payoff vector $x \in \mathbb{R}^S$ is the amount of payoff being distributed among agents of coalition S.
 The payoff vector satisfies two conditions:
@@
 A payoff vector is also $efficient$ if all the payoff obtained by a coalition is distributed amongst coalition members: $\sum_{i \in S} x_i = v(S)$.
-This definition of characteristic function works in $transferable utility$ (TU) settings, where utility (payoff) is transfarable from one player to other, in other words players have common currency and a unit of income is worth same for all players \cite{myerson1991game}.
+This definition of characteristic function works in $transferable utility$ (TU) settings, where utility (payoff) is transferable from one player to other, in other words players have common currency and a unit of income is worth same for all players \cite{myerson1991game}.
 
-When dealing with cooperative games, two issues need to get addressed: 1.
-What coalition to form (Canonical games)?
-2.
-How to reward each each member when a task is completed (Coalition-formation games)?
+When dealing with cooperative games, two issues need to get addressed: 1. What coalition to form (Canonical games)? 2. How to reward each member when a task is completed (Coalition-formation games)?
 
@@
 
-Shapley value is a unique and fair solution concept for payoff distribution between agents. It basicly rewards agents with amount of marginal contribution they have to the coalition.
+Shapley value is a unique and fair solution concept for payoff distribution between agents. It basically rewards agents with amount of marginal contribution they have to the coalition.
 
@@
 \end{equation}
-The core if is not empty is basicly a set of payoff vectors (x) where no subset of players $S^\prime$ could gain more by deviating and making their own coalition $\sum_{i \in S^\prime} x_i \geq v(S^\prime)$.
-The sum of payoffs to the agents in any subcoalition S is at least as large as the amount that these agents could earn by forming a coalition on their own.
+The core if is not empty is basically a set of payoff vectors (x) where no subset of players $S^\prime$ could gain more by deviating and making their own coalition $\sum_{i \in S^\prime} x_i \geq v(S^\prime)$.
+The sum of payoffs to the agents in any sub-coalition S is at least as large as the amount that these agents could earn by forming a coalition on their own.
 In a sense it is analogue to Nash equilibrium, except that it about deviations by groups of agents.
-The core is the strongest and most popular solution concept in cooperative game thoery, however its computationally very heavy and is not computationally tractable as number of players increase.
+The core is the strongest and most popular solution concept in cooperative game theory, however its computationally very heavy and is not computationally tractable as number of players increase.
 The core of some real-world problem games may be empty, which means having characteristic function $v$ there might be no possible distribution of payoff assuring stability of subgroups.
@@
 \end{equation}
+
 According to a classic result by Shapley \cite{S1971cores} convex games always have a non-empty core.
-In order to come with an algorithm be to able to evaluate if a game with characteristic function v(S) is convex or not, we can use the equation below and will prove its analogous to convexity condition:
+We will use a variation of convexity condition in our algorithm to check whether our coalitions are stable.
+
+\subsubsection{$\epsilon-Core$}\label{s:epsilon}
+If core set is not empty, it means no coalition of players can gain anything by deviating, it is the strongest stable condition.
+An outcome would be unstable if a coalition can benefit even by a small amount from deviating.
+This is a strong requirement.
+In some situations, deviations can be costly or agents may have some loyalty to their coalitions or even it can be computationally intractable to find those small benefits.
+It would only make sense for a coalition to deviate if the gain from a deviation exceeded a particular cost for example the costs of deviation.
+$\epsilon-Core$ relaxes the notion of the core, and only require that no coalition can benefit significantly or within a constant amount($\epsilon$) by deviating.
+
+\begin{equation}\label{eq:core}
+\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
+\end{equation}
+
+\subsubsection{Coalition Structure Formation}\label{sec:coalition}
+
+Coalition structure formation is the problem of finding best partition of agents into teams, focusing more on optimizing the coalition's ``owner'' payoff.
+In these settings performance of individual agent is less important than the \emph{social welfare} of the system, which is the sum of the values of all teams.
+Having characteristic function game G, a coalition structure (CS) is \emph{socially optimal} is CS belongs to set $argmax_{CS \in CS_N}v(CS)$ where v(CS) is sum of the total valuation function of all coalitions inside CS $(v(CS) = \sum_{C \in CS_N}v(CS))$.
+The outcome of a characteristic function game in coalition structure settings, consists of two parts; first a disjoint partition of players (agents) into coalitions, called a \emph{coalition structure} (CS) and second a \emph{payoff vector} as mentioned in cooperative game solution concepts, which distributes the value of each coalition among its members.
+
+\section{Problem Formulation and Modeling}
+
+In this section, we present the architecture of different web service community models and formulate how both web services and community masters as rational agents would maximise their payoff.
+
+\subsection {Web Services and A Grand Community}
+
+In this scenario, there are is a community controller by its master web service.
+The community master has some request rate $(R_{master})$ from users.
+Web services need to join a community to be able to get tasks from a master web service.
+Each web service comes with different quality of service parameters and a throughput $(T_{ws})$.
+Throughput is the average rate of tasks a web service can perform.
+Therefore, the master web service is providing tasks with rate of $R_{ws}$ and web services perform tasks with some QoS output metrics and a rate or $T_{ws}$.
+In this setting, we define the value of the coalition as follows:
+\begin{equation*}
+output(C) = \sum_{ws}{(T_{ws} \times QoS_{ws})}
+\end{equation*}
+
+\begin{equation*}
+v(C) = \left\{ 
+  \begin{array}{l l}
+    output(C) & \quad \text{if $\sum_{ws}{T_{ws}} \leq R_{master}$}\\
+    output(C) \times \frac{R_{master}}{\sum_{ws}{T_{ws}}} & \quad \text{if $\sum_{ws}{T_{ws}} > R_{master}$}
+  \end{array} \right.
+\end{equation*}
+
+The output of a coalition of web services is the rate and quality of task they can perform.
+If the rate is more than master's input task rate, it means the web services inside the community are capable of doing more tasks than exists.
+Considering this the valuation function will balance the output performance and will be the exact amount and quality of work they can perform within the particular community.
+%** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests.
+**
+
+In the first scenario, we only consider one grand coalition and analyse the system from point of view of one single master web service and a collection of web services.
+The master web service decides which members can join %or should leave%
+the community and distributes the income or tasks among its community members.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{s1.eps}
+\caption{Web Services and A Grand Community}
+\label{fig_sim}
+\end{figure}
+
+The membership decision is made based on throughput and QoS of the requested web service.
+The goal is to have quality web services in community so the community stays stable and no other web services would have incentives to deviate and join ``other'' coalitions.
+Therefore, we it check the core membership of the coalition of all current community members and the new web service.
+Our algorithm uses the Shapley value distribution method as described in equation \ref{eq:shapley} to distribute gain of $v(C)$ among all members and then checks if Shapley value payoff vector for this community having characteristic function $v(C)$ is Core stable or not.
+In Shapley value payoff vector, the payoff for each web service i, is calculated based on their contribution $v(C \cup {i}) - v(C)$ and then averaging over the possible different permutations in which the coalition can be formed, this is why Shapley value distribution is fair.
+It is proven in convex games the Shapley value lies in the core \cite{DBLP:conf/ijcai/GrecoMPS11, myerson1991game}.
+Therefore if the Core is non-empty, the Shapley payoff vector is a member of Core.
+% so in our algorithm we check the core membership of this payoff vector.
+
+\emph{Proposition: } The folowwing statement is equivalent with convex condition of equation \ref{eq:convex}; 
 \begin{equation}\label{eq:convex_snow}
@@
 
-{\bf Proof:}
+\emph{Proof: }
 
@@
 
-This means inorder to keep the characteristic function convex, new agents should have more marginal contribution as coalition size grows.
-
-\subsubsection{$\epsilon-Core$}
-If core set is not empty, it means no coalition of players can gain anything by deviating, it is the strongest stable condition.
-An outcome would be unstable if a coalition can benefit even by a small amount from deviating.
-This is a strong requirement.
-In some situations, deciations can be costly or agents may have some loyatly to their coalitions or even it can be computationaly intractable to find those small benefits.
-It would only make sense for a coalition to deviate if the gain from a deviation exceeded a particular cost for example the costs of deviation.
-$\epsilon-Core$ relaxes the notion of the core, and only require that no coalition can benefit significantly or within a constant ammount($\epsilon$) by deviating.
-
-\begin{equation}\label{eq:core}
-\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
-\end{equation}
-
-\subsubsection{Coalition Structure Formation}\label{sec:coalition}
-
-Coalition structure formation is the problem of finding best partition of agents into teams, focusing more on optimizing the coalition's ``owner'' payoff.
-In these settings performance of individual agent is less important than the \emph{social welfare} of the system, which is the sum of the values of all teams.
-Having characterestic function game G, a coalition structure (CS) is \emph{socially optimal} is CS belongs to set $argmax_{CS \in CS_N}v(CS)$ where v(CS) is sum of the total valuation function of all coalitions inside CS $(v(CS) = \sum_{C \in CS_N}v(CS))$.
-The outcome of a characterestic function game in coalition structure settings, consists of two parts; first a disjoint partition of players (agents) into coalitions, called a \emph{coalition structure} (CS) and second a \emph{payoff vector} as mentioned in cooperative game solution concepts, which distributes the value of each coalition among its members.
-
-\section{Problem Formulation and Modeling}
-
-In this section, we present the architechture of different web service community models and formulate how both web services and community masters as rational agents would maximise their payoff.
-
-\subsection {Web Services and A Grand Community}
-
-In this scenario, there are is a community controller by its master web sercice.
-The community master has some request rate $(R_{master})$ from users.
-Web services need to join a community to be able to get tasks from a master web service.
-Each web service comes with different quality of service patameters and a throughput $(T_{ws})$.
-Throughput is the average rate of tasks a web service can perform.
-Therefore, the master web service is providing tasks with rate of $R_{ws}$ and web services perform tasks with some QoS output metrics and a rate or $T_{ws}$.
-In this setting, we define the value of the coalition as follows:
-\begin{equation*}
-output(C) = \sum_{ws}{(T_{ws} \times QoS_{ws})}
-\end{equation*}
-
-\begin{equation*}
-v(C) = \left\{ 
-  \begin{array}{l l}
-    output(C) & \quad \text{if $\sum_{ws}{T_{ws}} \leq R_{master}$}\\
-    output(C) \times \frac{R_{master}}{\sum_{ws}{T_{ws}}} & \quad \text{if $\sum_{ws}{T_{ws}} > R_{master}$}
-  \end{array} \right.
-\end{equation*}
-
-The output of a coalition of web services is the rate and quality of task they can perform.
-If the rate is more than master's input task rate, it means the web services inside the community are capable of doing more tasks than exists.
-Considering this the valuation function will balance the output performance and will be the exact ammount and quality of work they can perform within the particular community.
-%** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests.
-**
-
-In the first scenario, we only consider one grand coalition and analyse the system from point of view of one master web service and a collection of web services.
-The master web service decides which members can join %or should leave%
-the community and distributes the income or tasks among its community members.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{s1.eps}
-\caption{Web Services and A Grand Community}
-\label{fig_sim}
-\end{figure}
-
-The membership decision is made based on throughput and QoS of the requested web service.
-The goal is to have quality web services in community so the community stays stable and no other web services would have incentives to deviate and join ``other'' coalitions.
-Therefore, we it check the core membership of the coalition of all current community members and the new web service.
-Our algorithm uses the shapley value distribution method as described in equation \ref{eq:shapley} to distribute gain of $v(C)$ among all members and then checks if shapley value payoff vector for this community having characteristic function $v(C)$ is Core stable or not.
-In shapley value payoff vector, the payoff for each web service i, is calculated based on their contribution $v(C \cup {i}) - v(C)$ and then averaging over the possible different permutations in which the coalition can be formed.
-It is proven in convex games the Shapley value lies in the core \cite{DBLP:conf/ijcai/GrecoMPS11, myerson1991game}.
-Therefore if the Core is non-empty, the Shapley payoff vector is a member of Core, so in our algorithm we check the core membership of this payoff vector.
+This means in order to keep the characteristic function convex, new agents should have more marginal contribution as coalition size grows.
 
@@
 
-In this scenario we consider multiple communities owned by multiple master web services which provide independant request pools.
+In this scenario we consider multiple communities owned by multiple master web services which provide independent request pools.
 Like first scenario master web services form coalitions with web services.
@@
 
-One of the properties of CS algorithms in our scenario is tha they partition web services with low throughput rate usually join coalitions with less request rate.
-Since the characteristic function $v(C)$ and  the fair payoff vector of shapley value is proportional to web services' contribution, the web services with small contribution will get paid much less in communities having web services with high throughput.
+One of the properties of coalition structure formation algorithms in our scenario is that they partition web services with low throughput rate usually join coalitions with less request rate.
+Since the characteristic function $v(C)$ and  the fair payoff vector of Shapley value is proportional to web services' contribution, the web services with small contribution will get paid much less in communities having web services with high throughput.
 On the other hand, according to valuation function $v(C)$ web services with high throughput will not contribute well to communities with low amount of user requests.
@@
 The reason is that number of all possible partitions of a set $N$ grows exponentially with the number of players in $n$, and the centralized algorithms need to iterate through all these partitions.
-%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centrilized algorithms, where all the complexity.
+%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity.
 However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}.
@@
 The distributed merge-and-split algorithm in \cite{DBLP:journals/igtr/AptW09} suits our application very well.
-It keeps splitting and mergin coalitions where it is preferred by all players inside those coalitions.
+It keeps splitting and merging coalitions where it is preferred by all players inside those coalitions.
 
@@
 Therefore coalitions will form is web services working together can perform and gain more than working alone individually.
-The worth or value of coalitions of web services is different in this setting, average the QoS metrics of web service, multiply it by a weight where the importance or weigth of each metric is dependant on type of users and requests web services are dealing with.
-For each webservice we multiplay this by web services's market share $(MarketShare_{ws})$ and the summation would be the characterestic or valuation of independent web service coalitions.
+The worth or value of coalitions of web services is different in this setting, average the QoS metrics of web service, multiply it by a weight where the importance or weigth of each metric is dependent on type of users and requests web services are dealing with.
+For each web service we multiply this by web service's market share $(MarketShare_{ws})$ and the summation would be the characteristic or valuation of independent web service coalitions.
 
@@
 If it is more than 1, is means they increase performance by working together and they are \emph{super additive}, otherwise it depicts they would perform better in linear sense if they worked alone.
-Since there are no master web serivces, we assume they eather dynamicly vote for one, or collabrate and agree on decisions and distribute task in round robin or fair fashion.
+Since there are no master web services, we assume they either dynamically vote for one, or collaborate and agree on decisions and distribute task in round robin or fair fashion.
 Like ``Web Services and Many Communities'' scenario, both core coalition structure analysis and social welfare analysis are applicable in this scenario.
@@
 This is the most important criteria for user satisfaction.
-We initiate the community with few web services, then let rejecting and accepting of random webservices go for a while, after that we start task distribution for the cummunities and let them allocate tasks for web services.
+We initiate the community with few web services, then let rejecting and accepting of random web services go for a while, after that we start task distribution for the communities and let them allocate tasks for web services.
 Then we measure the average output performance of tasks in communities following different methods.
@@
 
-Figure \ref{performanceall} depicts the results of simulation of optimal $\epsilon-Core$, \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods.
+Figure \ref{performanceall} depicts the results of simulation of optimal $\epsilon-Core$ with 10\% of total community value deviation allowed (one grand community with many web services), \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods.
 The the \emph{optimal core} method we capped the coalition size to 23 web services, since anything more than that would require analysis with time complexity of $O(2^22)$ which would made that impractical to run in our simulations.
@@
 The results show depth-2 and 1 convex checker methods are performing well compared to other methods and all not far from optimal.
+
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[scale=0.6]{least_core.eps}
+\caption{Smallest value of $\epsilon$ such that the $\epsilon-core$ is non-empty} \label{f_leastcore}
+\end{figure}
+
+As mentioned in section \ref{s:epsilon}, core assumes no coalition of players can gain anything by deviating which is a fairly strong requirement, that is why the notion of $\epsilon-Core$ was introduced.
+Least-Core $e(G)$ of a game $G$, is the minimum amount of $\epsilon$ in which the core is not empty.
+We evaluated the least-core value using our valuation function and our set of web services.
+We pick random number of web services from our data set and form random coalitions consisting of 3 to 25 web services.
+We choose 25 as maximum number of members in our grand coalition since it is computationally very complex for bigger coalitions to compute least-core.
+We set $\epsilon$ to a ratio of total payoff of coalition v(C) from 0 to 1.
+The results in figure \ref{f_leastcore} show, almost in 10\% of random web service coalitions have non-empty core solution and least-core solution is always non-empty letting agents gain only 30\% more by deviating.
+
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[scale=0.61]{s2_task_done.eps}
+\includegraphics[scale=0.61]{s2_task_qos.eps}
+\caption{Part (a): Cumulative number of tasks succesfully done. Part
+(b): Average QoS of tasks performed.} \label{performancemany}
+\end{figure}
+
+In figure \ref{performancemany} we compare our \emph{Web Services and many Communities} scenario with a method which ignores QoS parameters and forms coalitions and allow web services to join only if they have enough requests for them in other words web services can join a community when request rate is less that throughput of all web services inside community ignoring QoS parameters.
+We name this method \emph{Normal method} and use it as our benchmark for our QoS aware coalition formation process.
+As results illustrate clearly, our QoS aware method, forms better coalitions of web services improving performance and satisfaction for both web service and coalitions.
 
@@
 
-% use section* for acknowledgement
-\section*{Acknowledgment}
-
-The authors would like to thank...
-more thanks here
-
 % trigger a \newpage just before the given reference

### 2013-03-07 papers/coalition/charts/least_core.m

@@ -10,7 +10,7 @@ i=0:99;
 t=0:0.01:1;
 y=v(:,1);
 %set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
+set(gcf,'Position',[100 100 600 375]);
 
 %subplot(1,3,1);
 
@@ -25,10 +25,7 @@ grid on;
 set(gca,'YTick',0:0.1:1);
 set(gca,'tickdir','in')
 set(gca,'XTickLabel',{'0';'0.1';'0.2';'0.3';'0.4';'0.5';'0.6';'0.7';'0.8';'0.9';
-    '1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '0.4';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '0.6';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '0.8';' ';' ';' ';' ';' ';' ';' ';' ';'1';});
+    '1';});
 set(gca,'XGrid','off','YGrid','on','ZGrid','off');
 set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 
@@ -46,8 +43,8 @@ set(hleg1,'FontSize',10);
 
 % Add title and axis labels
 % title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Epsilon (ratio)'}, 'FontSize',14);
-ylabel('Core Non-Empty', 'FontSize',14);
+xlabel({'Maximum allowed deviation gain'}, 'FontSize',14);
+ylabel('Least-Core Non-Empty', 'FontSize',14);
 
 %Caxes = copyobj(gca,gcf);
 %set(Caxes, 'color', 'none', 'xcolor', 'k', 'xgrid', 'off', 'ycolor','k', 'ygrid','off');

### 2013-03-07 papers/coalition/coalition.tex
CChanges
CCCChanges
CHanges

@@
 
-We know $T \subseteq N - \left\{i\right\}$, therefor:
+We know $T \subseteq N - \left\{i\right\}$, therefore:
 
@@
 It keeps splitting and merging coalitions where it is preferred by all players inside those coalitions.
+This merge-and-split algorithm is designed to be adoptable for different problems.
+It two functions to be specified, first a preference relation or comparison relation for comparing two collections of different coalition partitions of same players and second function is to assess the stability condition of a partition.
+Having two partition sets of a subset of our players, namely $P = {P_1,...,P_k}$ and $Q = {Q_1,...N_l}$ one example would be to use the social welfare comarison $\sum^k_{i=1}v(P_i) > \sum^k_{i=1}v(N_l)$.
+For our scenario we used $Pareto order$ comparison which is an individual-value order appropriate for our self-interest agents (web services).
+In Pareto order, an allocation or partition $P$ is preferred over another $Q$ if at least one player gets more payoff in new allocation without other players getting hurt, or other players at least same payoff.
+($p_i \geq q_i$ with at least one element $p_i > q_i$).
+As new web services are discovered and get ready to join communities, this algorithm keeps merging and splitting partitions based on the preference or comparison function provides and will stop as the partitions satisfy the stability condition or no further merging and splitting is found satisfying the comparison function.
 

### 2013-03-07 papers/coalition/coalition.tex
CHanges
Changes

@@
 \begin{abstract}
-Web services are loosely-coupled business applications and willing to cooperate in distributed settings within different communities for better efficiency, market share and total payoff.
-There are number of proposed mechanisms and models on aggregating web services, however forming optimal and stable coalitions to maximize individual and community efficiency and income has got less attention.
-In this paper, we analyze coalition formations using cooperative game-theoretic methods.
-We propose a mechanism for membership requests and selection of web services in the scenarios in which there are already established communities, Moreover, we analyze the scenarios in which we do not have pre-defined communities and we develop a mechanism for web services to form stable groups allowing them to maximize their efficiency and generate near-optimal (welfare-maximizing) communities.
-The theoretical and simulation results proves that our algorithms provide web services and community owners with applicable and near optimal decision making mechanisms.
+
+Web services are loosely-coupled business applications and willing to cooperate in distributed settings within different groups called communities.
+Communities aim to provide better efficiency, market share and total payoff.
+There are a number of proposed mechanisms and models on aggregating web services, however forming optimal and stable coalitions to maximize individual and community efficiency and income has got less attention.
+In this paper, we propose an efficient coalition formation mechanism using cooperative game-theoretic methods.
+We propose a mechanism for membership requests and selection of web services in the scenarios in which there are already established communities.
+Moreover, we analyze the scenarios in which we do not have pre-defined communities and we develop a mechanism for web services to form stable groups allowing them to maximize their efficiency and generate near-optimal (welfare-maximizing) communities.
+The theoretical and simulation results show that our algorithms provide web services and community owners with applicable and near-optimal decision making mechanisms.
 
@@
 As new web services are discovered and get ready to join communities, this algorithm keeps merging and splitting partitions based on the preference or comparison function provides and will stop as the partitions satisfy the stability condition or no further merging and splitting is found satisfying the comparison function.
+More details of this algorithm and analyses of generic solutions on these types of games are described in \cite{DBLP:journals/igtr/AptW09}.
 
@@
 \begin{equation*}
-v(C) = \sum_{ws}{\sum_{m=metrics}{\sum_{ws}{QoS^m_{ws} \times C_{coef}} \times w_{metric} } \times ms_{ws}}
+v(C) = \sum_{ws}{\sum_{m=metrics}{\sum_{ws}{QoS^m_{ws} \times CC{m} \times ms_{ws}} \times w_{metric} } }
 \end{equation*}

### 2013-03-08 papers/coalition/coalition.tex
Changes

@@
 As new web services are discovered and get ready to join communities, this algorithm keeps merging and splitting partitions based on the preference or comparison function provides and will stop as the partitions satisfy the stability condition or no further merging and splitting is found satisfying the comparison function.
-More details of this algorithm and analyses of generic solutions on these types of games are described in \cite{DBLP:journals/igtr/AptW09}.
+More details of this algorithm and analyses of generic solutions on coalition formation games are described in \cite{DBLP:journals/igtr/AptW09}.
 
@@
 Figure \ref{performanceall} depicts the results of simulation of optimal $\epsilon-Core$ with 10\% of total community value deviation allowed (one grand community with many web services), \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods.
-The the \emph{optimal core} method we capped the coalition size to 23 web services, since anything more than that would require analysis with time complexity of $O(2^22)$ which would made that impractical to run in our simulations.
+The the \emph{optimal $\epsilon$-core} method we capped the coalition size to 23 web services, since anything more than that would require analysis with time complexity of $O(2^22)$ which would made that impractical to run in our simulations.
 In other methods there were no cap on size of the community and we had communities of size 60 web services at some points.

### 2013-03-08 papers/coalition/charts/task_done_opt.m

@@ -4,7 +4,7 @@
 %T and vT : cell
 %use v containing numbers 
 
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|.|:')
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|+|--|.|:')
 
 i=0:49;
 t=v(:,1);y=v(:,2);z=v(:,3);tt=v(:,4);yy=v(:,5);
@@ -35,9 +35,9 @@ set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 axis([0 50 0 1600]);
 
 % Add legend
-hleg1 = legend('e-Core','depth-2 Convex','depth-1 Convex','3-Way Sat','2-Player Game');
+hleg1 = legend('Optimal epsilon-core','Our depth-2 Convex','Our depth-1 Convex','3-Way Sat','2-Player Game');
 %set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.24,.63,.1,.2]);
+set(hleg1, 'Position', [.26,.66,.1,.2]);
 set(hleg1,'Interpreter','none');
 %set(hleg1,'color','none');
 set(hleg1,'FontSize',10);

### 2013-03-08 papers/coalition/charts/task_qos_opt.m

@@ -4,7 +4,7 @@
 %T and vT : cell
 %use v containing numbers 
 
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|.|:')
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|+|--|.|:')
 
 i=0:49;
 t=v(:,1);y=v(:,2);z=v(:,3);tt=v(:,4);yy=v(:,5);
@@ -35,9 +35,9 @@ set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 %axis([0 50 0 1600]);
 
 % Add legend
-hleg1 = legend('e-Core','depth-2 Convex','depth-1 Convex','3-Way Sat','2-Player Game');
+hleg1 = legend('Optimal epsilon-core','Our depth-2 Convex','Our depth-1 Convex','3-Way Sat','2-Player Game');
 %set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.24,.63,.1,.2]);
+set(hleg1, 'Position', [.252,.67,.1,.2]);
 set(hleg1,'Interpreter','none');
 %set(hleg1,'color','none');
 set(hleg1,'FontSize',10);

### 2013-03-08 papers/coalition/coalition.tex
Changes

@@
 
-\section{Preliminaries}
+\section{Preliminaries}\label{s:preliminaries}
 
@@
 
-\subsubsection{Shapley value}
+%\subsubsection{Shapley value}
 
@@
 \begin{equation}\label{eq:shapley}
-\sum_{S \subset N \backslash \left\{i\right\} } \frac{|S|! (n-|S|-1)!}{n!} (v(S \cup \left\{i\right\}) - v(S))
+\sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (n-|S|-1)!}{n!} (v(S \cup \left\{i\right\}) - v(S))
 \end{equation}
@@
 
-\subsubsection{Core}
+%\subsubsection{Core}
 
@@
 
-\subsubsection{$\epsilon-Core$}\label{s:epsilon}
-If core set is not empty, it means no coalition of players can gain anything by deviating, it is the strongest stable condition.
+\subsubsection*{$\epsilon$-core}\label{s:epsilon}
+%\emph{$\epsilon$-Core:}
+%\\
+When core set is empty, it means no coalition of players can gain anything by deviating, it is the strongest stable condition.
 An outcome would be unstable if a coalition can benefit even by a small amount from deviating.
@@
 
-\subsubsection{Coalition Structure Formation}\label{sec:coalition}
+\subsubsection*{Coalition Structure Formation}\label{sec:coalition}
 
@@
 \centering
-\includegraphics[width=3in]{s1.eps}
+\includegraphics[width=3in]{s1.eps}`
 \caption{Web Services and A Grand Community}
@@
 The worth or value of coalitions of web services is different in this setting, average the QoS metrics of web service, multiply it by a weight where the importance or weigth of each metric is dependent on type of users and requests web services are dealing with.
-For each web service we multiply this by web service's market share $(MarketShare_{ws})$ and the summation would be the characteristic or valuation of independent web service coalitions.
+For each web service we multiply this by web service's market share $(MS_{ws})$ and the summation would be the characteristic or valuation of independent web service coalitions.
 
 \begin{equation*}
-v(C) = \sum_{ws}{\sum_{m=metrics}{\sum_{ws}{QoS^m_{ws} \times CC{m} \times ms_{ws}} \times w_{metric} } }
+v(C) = \sum_{m=metrics}{ \Big( \sum_{ws \in C}{QoS^m_{ws} \times CC^{m} \times MS_{ws} \Big) } \times w_{m} }
 \end{equation*}
 
-$C_{coef}$ is \emph{Collabrative Coefficient} for each QoS metric, it determines how web services providing that QoS metric individually will be effected in a coalition environment.
+$CC^{m}$ is \emph{Collabrative Coefficient} for each QoS metric (non-functional parameter), it determines how web services providing that QoS metric individually will be effected in a coalition environment.
 If it is more than 1, is means they increase performance by working together and they are \emph{super additive}, otherwise it depicts they would perform better in linear sense if they worked alone.
-Since there are no master web services, we assume they either dynamically vote for one, or collaborate and agree on decisions and distribute task in round robin or fair fashion.
-Like ``Web Services and Many Communities'' scenario, both core coalition structure analysis and social welfare analysis are applicable in this scenario.
+$w_m$ is the weight of important for a QoS metric, it gives the community the flexibility to emphasize or neglect a specific QoS parameter.
+Note that $ \sum_{m}{w_m} = 1 $.
+In this scenario we have no master web services, we assume they either dynamically vote for one, or collaborate and agree on decisions and distribute task in round robin or fair fashion.
+We use the same merge-and-split algorithm like ``Web Services and Many Communities'' scenario, to find stable coalitions of web serivces.
 
@@
 
-As mentioned in section \ref{s:epsilon}, core assumes no coalition of players can gain anything by deviating which is a fairly strong requirement, that is why the notion of $\epsilon-Core$ was introduced.
+As mentioned in preliminaries section \ref{s:preliminaries}, core assumes no coalition of players can gain anything by deviating which is a fairly strong requirement, that is why the notion of $\epsilon-Core$ was introduced.
 Least-Core $e(G)$ of a game $G$, is the minimum amount of $\epsilon$ in which the core is not empty.
@@
 \section{Conclusion}
-The conclusion goes here. this is more of the conclusion
+
+In this paper, we proposed a cooperative game theory based model for aggregation of web services within communities.
+The goal of our services is to maximize efficiency of performing tasks by collaborating and forming stable communities.
+Our method considers stability and fairness for all web services within a community and offers an applicable mechanism for membership requests and selection of web services.
+The goal is to increase revenue by improving user satisfaction, which comes from the ability to perform tasks with higher quality and quantity.
+Simulation results show that our, polynomial in complexity, approximation algorithms provide web services and community owners with applicable and near-optimal decision making mechanisms.
+
+As future work, we would like to perform more analytical and theoretical work on the convexity condition for the characteristic function on web service applications.
+A future research direction includes working on compact or succinct representation of our service model to reduce the input complexity of cooperative game stability and fairness and membership checking solutions.
+From web service aspect the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks.
 

### 2013-03-08 papers/coalition/coalition.tex
Changes

@@
 
-\begin{equation*}
-v(C) = \sum_{m=metrics}{ \Big( \sum_{ws \in C}{QoS^m_{ws} \times CC^{m} \times MS_{ws} \Big) } \times w_{m} }
-\end{equation*}
+\begin{equation}
+v(C) = \sum_{m=metrics}{ \Big( \sum_{ws \in C}{QoS^m_{ws} \times MS_{ws} \Big) } \times w_{m} }
+\end{equation}
 
-$CC^{m}$ is \emph{Collabrative Coefficient} for each QoS metric (non-functional parameter), it determines how web services providing that QoS metric individually will be effected in a coalition environment.
+%$CC^{m}$ is \emph{Collabrative Coefficient} for each QoS metric (non-functional parameter), it determines how web services providing that QoS metric individually will be effected in a coalition environment.
 If it is more than 1, is means they increase performance by working together and they are \emph{super additive}, otherwise it depicts they would perform better in linear sense if they worked alone.

### 2013-03-08 papers/coalition/charts/least_core.m
Changes

@@ -33,12 +33,12 @@ axis([0 100 0 1.1]);
 %axis([0 50 0 1600]);
 
 % Add legend
-hleg1 = legend('Least e-Core');
+%%hleg1 = legend('Least epsilon-Core');
 %set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.31,.69,.05,.1]);
-set(hleg1,'Interpreter','none');
+%%set(hleg1, 'Position', [.31,.69,.05,.1]);
+%%set(hleg1,'Interpreter','none');
 %set(hleg1,'color','none');
-set(hleg1,'FontSize',10);
+%%set(hleg1,'FontSize',10);
 %legend boxoff;
 
 % Add title and axis labels

### 2013-03-08 papers/coalition/charts/s2_task_done.m

@@ -35,9 +35,9 @@ set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 axis([0 50 0 7000]);
 
 % Add legend
-hleg1 = legend('Dynamic Coalition Formation','Normal Method');
+hleg1 = legend('Dynamic Coalition Formation','Random Formation');
 %set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.31,.69,.1,.2]);
+set(hleg1, 'Position', [.30,.80,.1,.1]);
 set(hleg1,'Interpreter','none');
 %set(hleg1,'color','none');
 set(hleg1,'FontSize',10);

### 2013-03-08 papers/coalition/charts/s2_task_qos.m

@@ -35,9 +35,9 @@ axis([0 50 0.5 0.7]);
 %axis([0 50 0 1600]);
 
 % Add legend
-hleg1 = legend('Dynamic Coalition Formation','Normal Method');
+hleg1 = legend('Dynamic Coalition Formation','Random Formation');
 %set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.31,.69,.1,.2]);
+set(hleg1, 'Position', [.30,.80,.1,.1]);
 set(hleg1,'Interpreter','none');
 %set(hleg1,'color','none');
 set(hleg1,'FontSize',10);

### 2013-03-09 papers/coalition/coalition.tex
Changes

@@
 In this section we discuss the parameters and preliminary concepts that we use in the rest of paper.
-The way communities of web services are structured and engineered is described thoroughly in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
 
-\subsection{The Architecture and Entities }
-\subsubsection{Web Services}
-\subsubsection{Master Web Service of Communities}
-\subsubsection{Users}
+\subsection{The Architecture}
 
-\subsection{Task Parameters}
-\subsubsection{Request rate}
-\subsubsection{Consumption}
-\subsubsection{Requested Reponse Time}
-\subsubsection{Requested Availability}
-\subsubsection{Requested Success Rate}
+Our system consists of three main type of entities working together:
+
+\emph{1) Web services} are rational entities providing services to end users.
+They aim to maximize their individual income by receiving enough requests from end users.
+In order to increase their revenue, web services seek for more tasks if they have the capacity and throughput.
+Web services can join communities to have better efficiency collabrating with others, have access to higher market share and opportunity to receive a bigger task pool from end users.
+The way the web services reside inside communities and how communities of web services are engineered is described thoroughly in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+
+\emph{2) Master Web Services} are responsible for managing and are representative of the communities of web services.
+Communities receieve tasks from users and they aim to have a healthy set of web services to perform the tasks.
+They seek to maximise user satisfaction by having tasks accomplished with good rate and quality.
+Higher user satisfaction will bring more user tasks and increase the market share of the community.
+
+\emph{3) Users} generate tasks and try to find service providers online to perform the tasks.
+User satisfaction is abstracted as function of quantity and quality of tasks accomplished by our service providers.
 
 \subsection{Web Sercive Parameters}
-\subsubsection{Throughput}
-\subsubsection{Capacity}
-\subsubsection{Cost}
-\subsubsection{Reponse Time}
-\subsubsection{Availability}
-\subsubsection{Reliability}
-\subsubsection{Success Rate}
-\subsubsection{Reputation}
+
+Web services come with different quality parameters. These parameters with a short description are listed in Table \ref{qosws}.
+
+\begin{table}[!t]
+\centering
+\caption{List of web service QoS parameters.}
+\begin{tabular}{|c|c||c|c|}
+\hline
+\textbf{Notation} & \textbf{Definition} \\
+\hline\hline
+$Response Time$ & The average response time of services\\
+$Availability$ & Probability of available during a time frame \\
+$Reliability$ & P of successfully handling tasks during a timeframe\\
+$Successability$ & Probability of handling tasks successfully \\
+$Throughput$ & Average rate of handling tasks \\
+$Latency$ & The average latency of services\\
+$Capacity$ & Amount of resources available\\
+$Cost$ & Mean service fee for cooperating \\
+\hline
+\end{tabular}
+\label{qosws}
+\end{table}
+
+We normalize and aggrigate each of these metrics to a real value between 0 and 1.
+Since tasks are not shared between web services and are distributed among all web serivices inside a community, one can expect tasks within a community to be performed by average quality of web service residing in that community.
+We use this average expected quality output, later in evaluating community $worth$ or $payoff$ function.
 
@@
 In figure \ref{performancemany} we compare our \emph{Web Services and many Communities} scenario with a method which ignores QoS parameters and forms coalitions and allow web services to join only if they have enough requests for them in other words web services can join a community when request rate is less that throughput of all web services inside community ignoring QoS parameters.
-We name this method \emph{Normal method} and use it as our benchmark for our QoS aware coalition formation process.
+We name this method \emph{Random Formation} and use it as our benchmark for our QoS aware coalition formation process.
 As results illustrate clearly, our QoS aware method, forms better coalitions of web services improving performance and satisfaction for both web service and coalitions.

### 2013-03-10 papers/coalition/coalition.tex
Changes

@@
 Over the past years, web applications have become part of critical buisiness services.
-The increasing reliance on web-based applications has had significant implications for service providers and its users.
+The increasing reliance on web-based applications has significant implications for service providers and its users.
+Web services are methods of communication between electronic devices over the internet.
+Web service as a highly available software function acessable at a network address over the web or the cloud usually provides a set of \emph{stateless} functions.
 
@@
 
-TODO on community of web services \\
+The need for highly available and highly responsive services online has called for collaborative communities of these loosely-coupled business services.
+The idea of web service communities and the way they are engineered to collaborate was proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09, DBLP:journals/internet/BenatallahSD03, Rosario:2008:PQS:1512146.1512290} where web services with similar functionality are grouped together and users send their requests to communities assuring higher service availability and performance than individual web services.
+These communities are highly available also more resilience to failure since there is no single point of failure in their architecture.
 
-TODO Problems of \cite{Chun02user-centricperformance, mcknight00a, DBLP:journals/internet/BenatallahSD03, Khosravifar:2009:AIR:1586636.1586906, Rosario:2008:PQS:1512146.1512290} \\
+Most of the recent work on communities of services are either user-centric and focus user satisfaction \cite{Chun02user-centricperformance} or there are many works in distributed, grid, cluster and cloud computing which are system-centric and focus on system throughput and performance and utilization of the system.
+However in real world environments both users and services are selfish and self-interested agents, aiming to maximize their own profit.
+In real world environments, both these parties will participate and collaborate as long as its economically efficient for them.
 
-TODO Problems of \cite {DBLP:conf/IEEEscc/LimTMB12} having to cop and optimizing for with all weak web services reduces the optimal result\\
+Recently, \cite{DBLP:conf/IEEEscc/LimTMB12, DBLP:conf/IEEEscc/KhosravifarABT11} have proposed mechanisms in which try to maximize gain for both parties.
+A two-player non-cooperative game theory method between web services and community manager was proposed in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}.
+The strategies for a web service when facing a new communities, is joining or staying in their community and the set of strategies for communities are allowing to resusing the the web service proposal.
+Both parties based on their capacity, market share and reputation will have different set of utilities over the strategy profiles of the game.
+The problem with this method is the game is between community master and the new web service, and all other web services already residing within the community are ignored.
+Those web services can lose utility and gain having to collabrate with new webserices, they may deviate and join other comuunities if they are unsatisfied.
+In \cite{DBLP:conf/IEEEscc/LimTMB12} a 3-Way satisfaction selection approach has been proposed.
+In thier approach, they proposed a web service selection process for community masters catering for the effciency of 3 parties of users, web services and communities.
+In this work, they show how the gain of these parties are coupled together and they suggest a linear optimization process for optimizing the needs of the 3 parties.
+However, the optimization problem in this solution tends to optimize some parameters considering all web serivces even if they are weak.
+There are no clear thresholds for accepting or rejecting new web services.
+The optimization result for example could suggest web services already residing within the community to increase or decrease their capacity to adjust with weakness of other parties in the system.
+Hoever, a strong performing web service could deviate anytime it finds itself unsatisfied within the community instead of adjusting its service parameters.
 
-TODO Problems of \cite {DBLP:conf/IEEEscc/KhosravifarABT11} not considering the current web services in coalition and startegies are only based on master web service and new web service gain\\
+In this paper, we proposed a cooperative game theory based model for aggregation of web services within communities.
+The solution concepts of cooperative game theory seeks to find most efficient ways of forming coalitions (teams) of agents, maximizing their gain and payoff, and also distributing gain in a fair way to keep coalitions stable by having all agents satisfied.
+We first propose a representation function for communities of web services based on their qualities and capacities.
+Using this function we can evaluate the $worth$ of each coalition of web services.
+Our community managers facing new membership requests, analyses whether the new coalition having the new set of web services will keep the community stable for $all$ web services already residing in the community or not.
+The community manager will reject the membership requests if it finds out new coalition can be unstable since there can be $any$ subset of web services gaining significantly more by deviating, colluding with new web services and joining other communities.
+Also web services facing communities, will try to join communities which maximizes their gain, if they find out they can deviate and agin more, they will form new coalitions with other communities.
+The cooperative game theory solution methods are combinatorial in nature, making them impractical in real world applications; however, using the concepts of group stability we have offered approximation algorithms running in polynomial time providing web services and community owners with applicable and near-optimal decision making mechanisms.
+
+The rest of paper is organized as follows.
+Section \ref{s:preliminaries} describes architecture and parameters and some basic cooperative game theory concepts, section \ref{s:model} presents our solution model in three different scenarios.
+Section \ref{s:resutls} presents our experiments and results and finally section \ref{s:conclusion} concludes the paper and identified future work.
+
+%In prevoius works \cite{Chun02user-centricperformance, mcknight00a, DBLP:journals/internet/BenatallahSD03, Khosravifar:2009:AIR:1586636.1586906, Rosario:2008:PQS:1512146.1512290}
+
+%TODO Problems of \cite {DBLP:conf/IEEEscc/LimTMB12} having to cop and optimizing for with all weak web services reduces the optimal result\\
 
@@
 
-We normalize and aggrigate each of these metrics to a real value between 0 and 1.
+We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a} which has normalized and aggrigated each of these metrics to a real value between 0 and 1.
 Since tasks are not shared between web services and are distributed among all web serivices inside a community, one can expect tasks within a community to be performed by average quality of web service residing in that community.
@@
 
-\section{Problem Formulation and Modeling}
+\section{Problem Formulation and Modeling}\label{s:model}
 
@@
 
-\emph{Proposition: } The folowwing statement is equivalent with convex condition of equation \ref{eq:convex}; 
+\emph{Proposition: } The folowwing statement is equivalent with convex condition of equation \ref{eq:convex}.
 \begin{equation}\label{eq:convex_snow}
-v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T), \forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N; 
+v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T), \\ \forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N; 
 \end{equation}
@@
 This merge-and-split algorithm is designed to be adoptable for different problems.
-It two functions to be specified, first a preference relation or comparison relation for comparing two collections of different coalition partitions of same players and second function is to assess the stability condition of a partition.
+It requires two functions to be specified, first a preference relation or comparison relation for comparing two collections of different coalition partitions of same players and second function is to assess the stability condition of a partition.
 Having two partition sets of a subset of our players, namely $P = {P_1,...,P_k}$ and $Q = {Q_1,...N_l}$ one example would be to use the social welfare comarison $\sum^k_{i=1}v(P_i) > \sum^k_{i=1}v(N_l)$.
@@
 ($p_i \geq q_i$ with at least one element $p_i > q_i$).
-As new web services are discovered and get ready to join communities, this algorithm keeps merging and splitting partitions based on the preference or comparison function provides and will stop as the partitions satisfy the stability condition or no further merging and splitting is found satisfying the comparison function.
+As new web services are discovered and get ready to join communities, this algorithm keeps merging and splitting partitions based on the preference or comparison function provides and will terminate\cite{DBLP:journals/corr/abs-cs-0605132} as the partitions satisfy the stability condition or no further merging and splitting is found satisfying the comparison function.
 More details of this algorithm and analyses of generic solutions on coalition formation games are described in \cite{DBLP:journals/igtr/AptW09}.
@@
 
-\section{Experimental Results}
+\section{Experimental Results}\label{s:resutls}
 
@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[scale=0.61]{task_done_opt.eps}
-\includegraphics[scale=0.61]{task_qos_opt.eps}
+\includegraphics[width=3in]{task_done_opt.eps}
+\includegraphics[width=3in]{task_qos_opt.eps}
 \caption{Part (a): Cumulative number of tasks succesfully done. Part
@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[scale=0.6]{least_core.eps}
+\includegraphics[width=3in]{least_core.eps}
 \caption{Smallest value of $\epsilon$ such that the $\epsilon-core$ is non-empty} \label{f_leastcore}
@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[scale=0.61]{s2_task_done.eps}
-\includegraphics[scale=0.61]{s2_task_qos.eps}
+\includegraphics[width=3in]{s2_task_done.eps}
+\includegraphics[width=3in]{s2_task_qos.eps}
 \caption{Part (a): Cumulative number of tasks succesfully done. Part
@@
 
-\section{Conclusion}
+\section{Conclusion}\label{s:conclusion}
 

### 2013-03-10 papers/coalition/coalition.tex
Changes

@@
 
-TODO on functional and non-functional requirements specially for critial applications \\
-
-The need for highly available and highly responsive services online has called for collaborative communities of these loosely-coupled business services.
+The need for highly available and highly responsive services online has called for collaborative communities of these loosely-coupled business web services.
 The idea of web service communities and the way they are engineered to collaborate was proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09, DBLP:journals/internet/BenatallahSD03, Rosario:2008:PQS:1512146.1512290} where web services with similar functionality are grouped together and users send their requests to communities assuring higher service availability and performance than individual web services.
@@
 Also web services facing communities, will try to join communities which maximizes their gain, if they find out they can deviate and agin more, they will form new coalitions with other communities.
-The cooperative game theory solution methods are combinatorial in nature, making them impractical in real world applications; however, using the concepts of group stability we have offered approximation algorithms running in polynomial time providing web services and community owners with applicable and near-optimal decision making mechanisms.
+The cooperative game theory solution methods are combinatorial in nature and are NP-complete, making them impractical in real world applications; however, using the concepts of group stability we have offered approximation algorithms running in polynomial time providing web services and community owners with applicable and near-optimal decision making mechanisms.
 
@@
 \emph{Proposition: } The folowwing statement is equivalent with convex condition of equation \ref{eq:convex}.
+\\
+\\
+For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
 \begin{equation}\label{eq:convex_snow}
-v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T), \\ \forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N; 
+v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
 \end{equation}

### 2013-03-10 papers/coalition/coalition.tex
Changes

@@
 As future work, we would like to perform more analytical and theoretical work on the convexity condition for the characteristic function on web service applications.
-A future research direction includes working on compact or succinct representation of our service model to reduce the input complexity of cooperative game stability and fairness and membership checking solutions.
-From web service aspect the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks.
+It is possible to work on compact or succinct representation of our service model (i.e.
+a graph representation) to reduce the input complexity and solution concepts of cooperative game and membership checking algorithms.
+From web service aspect, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks.
+Also bargaining theory from cooperating game theory concepts can be used in our scenario.
+The web services would stay and join communities as they wish, however, they would resolve the instability and unfairness issues by side payments.
 

### 2013-03-10 papers/coalition/coalition.tex
Changes

@@
 
-\emph{Proposition: } The folowwing statement is equivalent with convex condition of equation \ref{eq:convex}.
-\\
-\\
-For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
+%\ref{eq:convex}.
+
+\emph{Proposition: } A game with characterestic function v is convex \emph{if and only if for all S, T, and i where} $S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$, 
+%For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
 \begin{equation}\label{eq:convex_snow}
@@
 
-\emph{Proof: }
+\emph{Proof. ``only if''} direction,
 
@@
 
-We know $T \subseteq N - \left\{i\right\}$, therefore:
+Considering $S \subseteq T$:
 
-\begin{equation*}
-(S \cup \left\{i\right\}) \cap T = T \cup S
-\end{equation*}
+\begin{gather*}
+S \cup \left\{i\right\} = (S \cup \left\{i\right\}) \cup T
+\\
+T = (S \cup \left\{i\right\}) \cap T
+\end{gather*}
 
-and we have $S \subseteq T$, therefor:
-
-\begin{equation*}
-(S \cup \left\{i\right\}) \cap T = S
-\end{equation*}
-
-With a variable chnage of S we have:
+By setting $A = S \cup \left\{i\right\}$ and $B = T$ we have:
 
@@
 \\
-\rightarrow v(S^\prime) + V(T) \leq v(S^\prime) + v(S^\prime \cap T)
+\rightarrow v(A) + V(B) \leq v(A \cup B) + v(A \cap B)
+\end{gather*}
+
+For prove of ``if'' direction, for all $A, B \subset N$,
+
+\begin{gather*}
+v(A) - v(A \cap B) \leq v(A \cup B) - v(B)
+\end{gather*}
+
+By setting $S \cup \left\{i\right\} = A$ and $R = B$ where $S \subseteq R$:
+
+\begin{gather*}
+v(S \cup \left\{i\right\}) - v((S \cup \left\{i\right\}) \cap T) \leq v(T \cup (S \cup \left\{i\right\})) - v(T)
+\\
+\rightarrow v(S \cup \left\{i\right\}) - v(S) \leq v(T \cup \left\{i\right\}) - v(T)
 \end{gather*}
@@
 We choose 25 as maximum number of members in our grand coalition since it is computationally very complex for bigger coalitions to compute least-core.
-We set $\epsilon$ to a ratio of total payoff of coalition v(C) from 0 to 1.
+We set $\epsilon$ to a ratio of total payoff of coalition v(C) between 0 and 1.
 The results in figure \ref{f_leastcore} show, almost in 10\% of random web service coalitions have non-empty core solution and least-core solution is always non-empty letting agents gain only 30\% more by deviating.

### 2013-03-11 papers/coalition/coalition.tex
Changes

@@
 
-In this scenario we consider multiple communities owned by multiple master web services which provide independent request pools.
-Like first scenario master web services form coalitions with web services.
+In this scenario we consider multiple communities owned by multiple master web services each providing independent request pools.
+Identical to first scenario master web services form coalitions with web services.
 We use coalition structure formation methods to partition web services into non-empty disjoint coalition structures.
-As mentioned in section \ref{sec:coalition} these algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11} try to solve two fundamental problems of what coalitions to form, and how will the members of these coalitions distribute their total gain to make these coalition structures stable.
+As mentioned in section \ref{sec:coalition} these algorithms \cite{Sandholm1999209, DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11} try to solve key fundamental problems of what coalitions to form, and how to devide the payoffs from collabration.
 
@@
 
-The valuation function $v(C)$ for this scenario is same as \emph{one grand community} scenario, however in order to prevent master web services joining same community we set $v(C) = 0$, where C has two or more master web services as members.
+The valuation function $v(C)$ for this scenario is same as \emph{one grand community} scenario, however in order to prevent master web services joining same community we set $v(C) = 0$, where C has none, or, two or more master web services as members.
 
-One of the properties of coalition structure formation algorithms in our scenario is that they partition web services with low throughput rate usually join coalitions with less request rate.
-Since the characteristic function $v(C)$ and  the fair payoff vector of Shapley value is proportional to web services' contribution, the web services with small contribution will get paid much less in communities having web services with high throughput.
-On the other hand, according to valuation function $v(C)$ web services with high throughput will not contribute well to communities with low amount of user requests.
-The strong web services are much more likely to deviate weak coalitions, joining a stronger coalition, making the initial coalition unstable.
-
-In coalition-formation games, formation of the coalitions is the most important aspect of in the game.
+In coalition-formation games, formation of the coalitions is the most important aspect of the game.
 These solutions focus on maximizing social welfare.
@@
 There are $centralized$ algorithms for this end, however these approaches are generally NP-complete.
-The reason is that number of all possible partitions of a set $N$ grows exponentially with the number of players in $n$, and the centralized algorithms need to iterate through all these partitions.
+The reason is that number of all possible number of partitions of a set $N$ grows exponentially with the number of players in $n$ (Bell number), and the centralized algorithms need to iterate through all these partitions.
 %These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity.
 However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}.
-In our application, we prefer not having a centralized decision maker dictating all web services their decisions.
-Becuase of this plus the complexity issues we would prefer a distributed algorithm where each community master can be a decision maker.
+In our application, we prefer a distributed algorithm where each community master and web service can be a decision maker and decide for its own good.
 The aim is to find low complexity and distributed algorithms for forming coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
 The distributed merge-and-split algorithm in \cite{DBLP:journals/igtr/AptW09} suits our application very well.
-It keeps splitting and merging coalitions where it is preferred by all players inside those coalitions.
-This merge-and-split algorithm is designed to be adoptable for different problems.
-It requires two functions to be specified, first a preference relation or comparison relation for comparing two collections of different coalition partitions of same players and second function is to assess the stability condition of a partition.
-Having two partition sets of a subset of our players, namely $P = {P_1,...,P_k}$ and $Q = {Q_1,...N_l}$ one example would be to use the social welfare comarison $\sum^k_{i=1}v(P_i) > \sum^k_{i=1}v(N_l)$.
+It keeps splitting and merging coalition to partitions which are preferred by all players inside those coalitions.
+
+This merge-and-split algorithm is designed to be adoptable for different applications.
+It requires two functions to be specified, first a preference relation for comparing two collections of different coalition partitions of same set of players and second function is to assess the stability condition of a partition.
+Having two partition sets of players, namely $P = {P_1,...,P_k}$ and $Q = {Q_1,...N_l}$ one example would be to use the social welfare comarison $\sum^k_{i=1}v(P_i) > \sum^k_{i=1}v(N_l)$.
 For our scenario we used $Pareto order$ comparison which is an individual-value order appropriate for our self-interest agents (web services).
-In Pareto order, an allocation or partition $P$ is preferred over another $Q$ if at least one player gets more payoff in new allocation without other players getting hurt, or other players at least same payoff.
+In Pareto order, an allocation or partition $P$ is preferred over another $Q$ if at least one player improves its payoff in new allocation and all other players maintain their payoff.
 ($p_i \geq q_i$ with at least one element $p_i > q_i$).
-As new web services are discovered and get ready to join communities, this algorithm keeps merging and splitting partitions based on the preference or comparison function provides and will terminate\cite{DBLP:journals/corr/abs-cs-0605132} as the partitions satisfy the stability condition or no further merging and splitting is found satisfying the comparison function.
+
+In this scenario, as new web services are discovered and get ready to join communities, our algorithm keeps merging and splitting partitions based on the preference function.
+The decision to merge or split is tied to the fact that all players must benefit, the new web services will merge with communities if $all$ players are able to improve their individual payoff, and some web services may split from old communities, if splitting does not decrease payoff of any web services of the community.
+According to \cite{DBLP:journals/corr/abs-cs-0605132} this sequence of merging and spliting will converge to a final partition, where players (web services) cannot improve their payoff.
 More details of this algorithm and analyses of generic solutions on coalition formation games are described in \cite{DBLP:journals/igtr/AptW09}.
@@
 The results in figure \ref{f_leastcore} show, almost in 10\% of random web service coalitions have non-empty core solution and least-core solution is always non-empty letting agents gain only 30\% more by deviating.
+
+One of the properties of coalition structure formation algorithms in our scenario is that they partition web services with low throughput rate usually join coalitions with less request rate.
+Since the characteristic function $v(C)$ and  the fair payoff vector of Shapley value is proportional to web services' contribution, the web services with small contribution will get paid much less in communities having web services with high throughput.
+On the other hand, according to valuation function $v(C)$ web services with high throughput will not contribute well to communities with low amount of user requests.
+The strong web services are much more likely to deviate weak coalitions, joining a stronger coalition, making the initial coalition unstable.
 

### 2013-03-11 papers/coalition/charts/least_core.m

@@ -8,7 +8,7 @@ set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','+|--|--|.|:')
 
 i=0:99;
 t=0:0.01:1;
-y=v(:,1);
+y=v(:,13);
 %set(gcf,'Position',[100 100 800 500]);
 set(gcf,'Position',[100 100 600 375]);
 

### 2013-03-11 papers/coalition/coalition.tex
Changes

@@
 In this scenario we have no master web services, we assume they either dynamically vote for one, or collaborate and agree on decisions and distribute task in round robin or fair fashion.
-We use the same merge-and-split algorithm like ``Web Services and Many Communities'' scenario, to find stable coalitions of web serivces.
+Here, we utilized the same merge-and-split algorithm which we applied for the \emph{``Web Services and Many Communities''} scenario, to find stable coalitions of web serivces.
 
@@
 Figure \ref{performanceall} depicts the results of simulation of optimal $\epsilon-Core$ with 10\% of total community value deviation allowed (one grand community with many web services), \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods.
-The the \emph{optimal $\epsilon$-core} method we capped the coalition size to 23 web services, since anything more than that would require analysis with time complexity of $O(2^22)$ which would made that impractical to run in our simulations.
+The the \emph{optimal $\epsilon$-core} method we capped the coalition size to 24 web services, since anything more than that would require analysis with time complexity of $O(2^{24-1})$ which would made that impractical to run in our simulations.
 In other methods there were no cap on size of the community and we had communities of size 60 web services at some points.
@@
 We evaluated the least-core value using our valuation function and our set of web services.
-We pick random number of web services from our data set and form random coalitions consisting of 3 to 25 web services.
-We choose 25 as maximum number of members in our grand coalition since it is computationally very complex for bigger coalitions to compute least-core.
+We pick random number of web services from our data set and formed around 10,000 random coalitions consisting of 3 to 25 web services.
+We choose 25 as maximum number of members in our grand coalition since it is computationally very complex for bigger coalitions to compute \emph{$\epsilon$}-core.
 We set $\epsilon$ to a ratio of total payoff of coalition v(C) between 0 and 1.
-The results in figure \ref{f_leastcore} show, almost in 10\% of random web service coalitions have non-empty core solution and least-core solution is always non-empty letting agents gain only 30\% more by deviating.
+The results in figure \ref{f_leastcore} illustrates, almost 10\% of our random web service coalitions have non-empty core solution and \emph{$\epsilon$}-core solution is always non-empty when we let agents gain only 30\% (of $v(C)$) more, by deviating.
 

### 2013-03-12 papers/coalition/coalition.tex
Changes

@@
 \end{equation*}
-
+\setlength{\abovedisplayshortskip}{2pt}
 \begin{equation*}
@@
 \emph{Proof. ``only if''} direction, 
-
+\setlength{\abovedisplayshortskip}{2pt}
 \begin{gather*}\label{convexsnowproof}
@@
 Considering $S \subseteq T$:
-
+\setlength{\abovedisplayshortskip}{2pt}
 \begin{gather*}
@@
 By setting $A = S \cup \left\{i\right\}$ and $B = T$ we have:
-
+\setlength{\abovedisplayshortskip}{2pt}
 \begin{gather*}
@@
 For prove of ``if'' direction, for all $A, B \subset N$,
-
+\setlength{\abovedisplayshortskip}{2pt}
 \begin{gather*}
@@
 By setting $S \cup \left\{i\right\} = A$ and $R = B$ where $S \subseteq R$:
-
+\setlength{\abovedisplayshortskip}{2pt}
 \begin{gather*}
@@
 These solutions focus on maximizing social welfare.
-For any coalition structure $\pi$, let $v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$ which we call it social welfare.
-The problems in this area deal with finding the maximum value for social welfare over all the possible coalition structures $\pi$.
+For any coalition structure $\pi$, let $v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$, which is called \emph{social welfare}.
+The solution concepts in this area deal with finding the maximum value for social welfare over all the possible coalition structures $\pi$.
 There are $centralized$ algorithms for this end, however these approaches are generally NP-complete.
-The reason is that number of all possible number of partitions of a set $N$ grows exponentially with the number of players in $n$ (Bell number), and the centralized algorithms need to iterate through all these partitions.
+The reason is that number of all possible partitions of set $N$ grows exponentially with the number of players in $N$ (Bell number), and the centralized algorithms need to iterate through all these partitions.
 %These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity.
@@
 In our application, we prefer a distributed algorithm where each community master and web service can be a decision maker and decide for its own good.
-The aim is to find low complexity and distributed algorithms for forming coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
+The aim is to find less complex and distributed algorithms for forming coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
 The distributed merge-and-split algorithm in \cite{DBLP:journals/igtr/AptW09} suits our application very well.
@@
 This merge-and-split algorithm is designed to be adoptable for different applications.
-It requires two functions to be specified, first a preference relation for comparing two collections of different coalition partitions of same set of players and second function is to assess the stability condition of a partition.
+One major ingredient to be provider to this algorithm is a preference relation or well-defined orders proper for comparing collections of different coalition partitions of same set of players.
 Having two partition sets of players, namely $P = {P_1,...,P_k}$ and $Q = {Q_1,...N_l}$ one example would be to use the social welfare comarison $\sum^k_{i=1}v(P_i) > \sum^k_{i=1}v(N_l)$.
-For our scenario we used $Pareto order$ comparison which is an individual-value order appropriate for our self-interest agents (web services).
-In Pareto order, an allocation or partition $P$ is preferred over another $Q$ if at least one player improves its payoff in new allocation and all other players maintain their payoff.
+For our scenario we used \emph{Pareto order} comparison which is an individual-value order appropriate for our self-interest agents (web services).
+In Pareto order, an allocation or partition $P$ is preferred over another $Q$ if at least one player improves its payoff in new allocation and all other players still maintain their payoff.
 ($p_i \geq q_i$ with at least one element $p_i > q_i$).
@@
 \includegraphics[width=3in]{least_core.eps}
-\caption{Smallest value of $\epsilon$ such that the $\epsilon-core$ is non-empty} \label{f_leastcore}
+\caption{Analysis of \emph{$\epsilon$-core} set non-emptiness, for different values of $\epsilon$} \label{f_leastcore}
 \end{figure}

### 2013-03-12 papers/coalition/coalition.tex
Changes

@@
 
-The valuation function $v(C)$ for this scenario is same as \emph{one grand community} scenario, however in order to prevent master web services joining same community we set $v(C) = 0$, where C has none, or, two or more master web services as members.
-
 In coalition-formation games, formation of the coalitions is the most important aspect of the game.
@@
 ($p_i \geq q_i$ with at least one element $p_i > q_i$).
+
+The valuation function $v(C)$ for this scenario is same as \emph{``Web Services and A Grand Community''} scenario, however in order to prevent master web services joining same community we set $v(C) = 0$, where C has none, or, two or more master web services as members.
 

### 2013-03-12 papers/coalition/coalition.tex
Changes

@@
 The way the web services reside inside communities and how communities of web services are engineered is described thoroughly in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+Throughout this paper, in our equations, we refer to web services as $ws$.
 
@@
 Since tasks are not shared between web services and are distributed among all web serivices inside a community, one can expect tasks within a community to be performed by average quality of web service residing in that community.
-We use this average expected quality output, later in evaluating community $worth$ or $payoff$ function.
+We use this average expected quality output $(QoS_{ws})$, later in evaluating community $worth$ or $payoff$ function.
 
@@
 Throughput is the average rate of tasks a web service can perform.
-Therefore, the master web service is providing tasks with rate of $R_{ws}$ and web services perform tasks with some QoS output metrics and a rate or $T_{ws}$.
+Therefore, the master web service is providing tasks with rate of $R_{ws}$ and web services perform tasks with average output metrics of $QoS_{ws}$ and a rate or $T_{ws}$.
 In this setting, we define the value of the coalition as follows:
@@
 Therefore coalitions will form is web services working together can perform and gain more than working alone individually.
-The worth or value of coalitions of web services is different in this setting, average the QoS metrics of web service, multiply it by a weight where the importance or weigth of each metric is dependent on type of users and requests web services are dealing with.
+The worth or value of coalitions of web services is different in this setting.
+We average the $quality$ for all metrics of web service $(Q^{m})$, multiply it by a weight where the importance or weigth of each metric is dependent on type of users and requests web services are dealing with.
 For each web service we multiply this by web service's market share $(MS_{ws})$ and the summation would be the characteristic or valuation of independent web service coalitions.
@@
 \begin{equation}
-v(C) = \sum_{m=metrics}{ \Big( \sum_{ws \in C}{QoS^m_{ws} \times MS_{ws} \Big) } \times w_{m} }
+v(C) = \sum_{ws \in C}{ \Big( \frac{\sum_{m=metrics}{Q^m_{ws} \times w_{m}}}{|metrics|} \Big) \times MS_{ws} }
 \end{equation}

### 2013-03-13 papers/coalition/coalition.tex
Changes

@@
 
-Over the past years, web applications have become part of critical buisiness services.
-The increasing reliance on web-based applications has significant implications for service providers and its users.
-Web services are methods of communication between electronic devices over the internet.
-Web service as a highly available software function acessable at a network address over the web or the cloud usually provides a set of \emph{stateless} functions.
+Over the past years, online services have become part of critical business services.
+The increasing reliance on web-based applications has significant implications for service providers which calls for a seamless integration of business process, applications and web services of the Internet.
+Web services as a highly available software function accessible at a network address over the web, usually provid a set of stateless functions.
+Delivering high quality services on the dynamic and unpredictable nature of Internet is a critical and challenging task.
 
@@
 A two-player non-cooperative game theory method between web services and community manager was proposed in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}.
-The strategies for a web service when facing a new communities, is joining or staying in their community and the set of strategies for communities are allowing to resusing the the web service proposal.
+The strategies for a web service when facing a new community, is requesting to join or refusing the invitation to join the community and the set of strategies for communities are inviting the web service or refusing the web service join request.
 Both parties based on their capacity, market share and reputation will have different set of utilities over the strategy profiles of the game.
 The problem with this method is the game is between community master and the new web service, and all other web services already residing within the community are ignored.
-Those web services can lose utility and gain having to collabrate with new webserices, they may deviate and join other comuunities if they are unsatisfied.
+Those web services can lose utility and gain having to collaborate with new web services, they may deviate and join other communities if they are unsatisfied.
 In \cite{DBLP:conf/IEEEscc/LimTMB12} a 3-Way satisfaction selection approach has been proposed.
-In thier approach, they proposed a web service selection process for community masters catering for the effciency of 3 parties of users, web services and communities.
-In this work, they show how the gain of these parties are coupled together and they suggest a linear optimization process for optimizing the needs of the 3 parties.
-However, the optimization problem in this solution tends to optimize some parameters considering all web serivces even if they are weak.
+In their approach, they proposed a web service selection process for community masters catering for the efficiency of 3 parties of users, web services and communities.
+In this work, they show how the gains of these parties are coupled together and they suggest a linear optimization process for optimizing the needs of the 3 parties.
+However, the optimization problem in this solution tends to optimize some parameters considering all web services even if they are weak.
 There are no clear thresholds for accepting or rejecting new web services.
 The optimization result for example could suggest web services already residing within the community to increase or decrease their capacity to adjust with weakness of other parties in the system.
-Hoever, a strong performing web service could deviate anytime it finds itself unsatisfied within the community instead of adjusting its service parameters.
+However, a strong performing web service could deviate anytime it finds itself unsatisfied within the community instead of adjusting its service parameters.
 
@@
 The community manager will reject the membership requests if it finds out new coalition can be unstable since there can be $any$ subset of web services gaining significantly more by deviating, colluding with new web services and joining other communities.
-Also web services facing communities, will try to join communities which maximizes their gain, if they find out they can deviate and agin more, they will form new coalitions with other communities.
+Also web services facing communities, will try to join communities which maximizes their gain, if they find out they can deviate and gain more, they will form new coalitions with other communities.
 The cooperative game theory solution methods are combinatorial in nature and are NP-complete, making them impractical in real world applications; however, using the concepts of group stability we have offered approximation algorithms running in polynomial time providing web services and community owners with applicable and near-optimal decision making mechanisms.
@@
 \hline\hline
-$Response Time$ & The average response time of services\\
 $Availability$ & Probability of available during a time frame \\
@@
 $Cost$ & Mean service fee for cooperating \\
+$Regulatory$ & Compliance with standards, law and rules\\
+$Security$ & Quality of confidentiality and non-repudiation\\
 \hline

### 2013-03-13 papers/coalition/coalition.tex
Changes

@@
 The increasing reliance on web-based applications has significant implications for service providers which calls for a seamless integration of business process, applications and web services of the Internet.
-Web services as a highly available software function accessible at a network address over the web, usually provid a set of stateless functions.
+Web services as a highly available software function accessible at a network address over the web, usually provide a set of stateless functions.
 Delivering high quality services on the dynamic and unpredictable nature of Internet is a critical and challenging task.
@@
 
-Most of the recent work on communities of services are either user-centric and focus user satisfaction \cite{Chun02user-centricperformance} or there are many works in distributed, grid, cluster and cloud computing which are system-centric and focus on system throughput and performance and utilization of the system.
-However in real world environments both users and services are selfish and self-interested agents, aiming to maximize their own profit.
-In real world environments, both these parties will participate and collaborate as long as its economically efficient for them.
+Most of the recent work on communities of services are either user-centric and focus on user satisfaction \cite{Chun02user-centricperformance} or they are system-centric and focus on system throughput and performance and utilization of the system.
+There are many contributions in distributed, grid, cluster and cloud computing services which are system-centric.
+However in real world environments both users and service providers are self-interested agents, aiming to maximize their own profit.
+In real world environments, both these parties will participate and collaborate as long as it's economic and efficient for both of them.
 
-Recently, \cite{DBLP:conf/IEEEscc/LimTMB12, DBLP:conf/IEEEscc/KhosravifarABT11} have proposed mechanisms in which try to maximize gain for both parties.
+Recently, \cite{DBLP:conf/IEEEscc/LimTMB12, DBLP:conf/IEEEscc/KhosravifarABT11} have proposed mechanisms in which they try to maximize gain for both parties.
 A two-player non-cooperative game theory method between web services and community manager was proposed in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}.
@@
 Both parties based on their capacity, market share and reputation will have different set of utilities over the strategy profiles of the game.
-The problem with this method is the game is between community master and the new web service, and all other web services already residing within the community are ignored.
-Those web services can lose utility and gain having to collaborate with new web services, they may deviate and join other communities if they are unsatisfied.
+The problem suffers from ignoring many quality parameters and also ignoring the web services already residing within the community.
+The game is only between the community master and the new web service, and all other web services already residing within the community are ignored.
+Those web services can lose utility or payoff, having to collaborate with new web services.
+They may deviate and join other communities if they are unsatisfied, which is not addressed in their approach.
 In \cite{DBLP:conf/IEEEscc/LimTMB12} a 3-Way satisfaction selection approach has been proposed.
-In their approach, they proposed a web service selection process for community masters catering for the efficiency of 3 parties of users, web services and communities.
+In their approach, they have proposed a web service selection process for community masters catering for the efficiency of all three parties of users, web services and communities.
 In this work, they show how the gains of these parties are coupled together and they suggest a linear optimization process for optimizing the needs of the 3 parties.
@@
 
-In this paper, we proposed a cooperative game theory based model for aggregation of web services within communities.
+In this paper, we propose a cooperative game theory based model for aggregation of web services within communities.
 The solution concepts of cooperative game theory seeks to find most efficient ways of forming coalitions (teams) of agents, maximizing their gain and payoff, and also distributing gain in a fair way to keep coalitions stable by having all agents satisfied.
 We first propose a representation function for communities of web services based on their qualities and capacities.
-Using this function we can evaluate the $worth$ of each coalition of web services.
+Using this function we can evaluate the $worth$ of each community of web services.
 Our community managers facing new membership requests, analyses whether the new coalition having the new set of web services will keep the community stable for $all$ web services already residing in the community or not.
-The community manager will reject the membership requests if it finds out new coalition can be unstable since there can be $any$ subset of web services gaining significantly more by deviating, colluding with new web services and joining other communities.
+The community manager will reject the membership requests if it finds out new coalition would be unstable, preventing $any$ subset of web services from gaining significantly more by deviating and joining other communities.
 Also web services facing communities, will try to join communities which maximizes their gain, if they find out they can deviate and gain more, they will form new coalitions with other communities.
-The cooperative game theory solution methods are combinatorial in nature and are NP-complete, making them impractical in real world applications; however, using the concepts of group stability we have offered approximation algorithms running in polynomial time providing web services and community owners with applicable and near-optimal decision making mechanisms.
+The cooperative game theory solution methods are combinatorial in nature and are NP-complete, making them impractical in real world applications; however, using the concepts of coalition stability we have offered approximation algorithms running in polynomial time providing web services and community managers with applicable and near-optimal decision making mechanisms.
 
@@
 Section \ref{s:preliminaries} describes architecture and parameters and some basic cooperative game theory concepts, section \ref{s:model} presents our solution model in three different scenarios.
-Section \ref{s:resutls} presents our experiments and results and finally section \ref{s:conclusion} concludes the paper and identified future work.
+Section \ref{s:resutls} presents our experiments and results and finally, section \ref{s:conclusion}, concludes the paper and identified future work.
 
@@
 
-This means in order to keep the characteristic function convex, new agents should have more marginal contribution as coalition size grows.
+This implies in order to keep the characteristic function convex, new agents should have more marginal contribution as coalition size grows.
 
@@
 It is possible to work on compact or succinct representation of our service model (i.e.
-a graph representation) to reduce the input complexity and solution concepts of cooperative game and membership checking algorithms.
+a graph representation) to reduce the input complexity and solution concepts of cooperative game and core membership checking algorithms.
 From web service aspect, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks.

### 2013-03-13 papers/coalition/coalition.tex
Changes

@@
 Our community managers facing new membership requests, analyses whether the new coalition having the new set of web services will keep the community stable for $all$ web services already residing in the community or not.
-The community manager will reject the membership requests if it finds out new coalition would be unstable, preventing $any$ subset of web services from gaining significantly more by deviating and joining other communities.
+The community manager will reject the membership requests if it finds out new coalition would be unstable, preventing $any$ subset of web services from gaining significantly more, by deviating and joining other communities.
 Also web services facing communities, will try to join communities which maximizes their gain, if they find out they can deviate and gain more, they will form new coalitions with other communities.
@@
 In order to increase their revenue, web services seek for more tasks if they have the capacity and throughput.
-Web services can join communities to have better efficiency collabrating with others, have access to higher market share and opportunity to receive a bigger task pool from end users.
+Web services can join communities to have better efficiency by collaborating with others, to have access to higher market share and to have opportunity of receiving a bigger task pool from end users.
 The way the web services reside inside communities and how communities of web services are engineered is described thoroughly in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

### 2013-03-14 papers/coalition/coalition.tex
Changes

@@
 They seek to maximise user satisfaction by having tasks accomplished with good rate and quality.
-Higher user satisfaction will bring more user tasks and increase the market share of the community.
+Higher user satisfaction will bring more user tasks and increase the market share and revenue of the community.
 
@@
 
-Web services come with different quality parameters. These parameters with a short description are listed in Table \ref{qosws}.
+Web services come with different quality of service parameters. These parameters with a short description are listed in Table \ref{qosws}.
 
@@
 
-We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a} which has normalized and aggrigated each of these metrics to a real value between 0 and 1.
-Since tasks are not shared between web services and are distributed among all web serivices inside a community, one can expect tasks within a community to be performed by average quality of web service residing in that community.
-We use this average expected quality output $(QoS_{ws})$, later in evaluating community $worth$ or $payoff$ function.
+We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a} which has aggregated and normalized each of these parameters to a real value between 0 and 1.
+Since tasks are not shared between web services and are distributed among all web services inside a community, one can expect tasks within a community to be performed by average quality of web service residing in that community.
+We use this expected quality output $(QoS_{ws})$, later in evaluating community \emph{worth} or \emph{payoff} function.
 
@@
 Cooperative game is a branch of game theory that studies strategies of self-interested agents in a setting where agents can increase their payoff by binding agreements and cooperating in groups.
-We let N to be a set of players.
-Any subset S of N can form a group that we call it a $coalition$.
-A $coalitional game$ is a pair $G = (N, v)$ where v is $characteristic function$ which given a coalition is a function $v: 2^N \to \mathbb{R}$ which maps the set of agents of the coalition to a real number v(S), the worth of S.
+We let $N$ to be a set of players.
+Any subset $S$ of $N$ can form a group that we call it a $coalition$.
+A \emph{coalitional game} is a pair $G = (N, v)$ where $v$ is \emph{characteristic function} which given a coalition is a function $v: 2^N \to \mathbb{R}$ which maps the set of agents of the coalition to a real number v(S), the worth of S.
 This number usually resembles the output or payoff or performance of these agents working together as a coalition.
@@
 A payoff vector is also $efficient$ if all the payoff obtained by a coalition is distributed amongst coalition members: $\sum_{i \in S} x_i = v(S)$.
-This definition of characteristic function works in $transferable utility$ (TU) settings, where utility (payoff) is transferable from one player to other, in other words players have common currency and a unit of income is worth same for all players \cite{myerson1991game}.
+This definition of characteristic function works in \emph{transferable utility} (TU) settings, where utility (payoff) is transferable from one player to other, in other words players have common currency and a unit of income is worth same for all players \cite{myerson1991game}.
 

### 2013-03-14 papers/coalition/coalition.tex
Changes

@@
 Any subset $S$ of $N$ can form a group that we call it a $coalition$.
-A \emph{coalitional game} is a pair $G = (N, v)$ where $v$ is \emph{characteristic function} which given a coalition is a function $v: 2^N \to \mathbb{R}$ which maps the set of agents of the coalition to a real number v(S), the worth of S.
-This number usually resembles the output or payoff or performance of these agents working together as a coalition.
-If a coalition S forms then it can divide its worth, v(S) in any possible among its members.
-The payoff vector $x \in \mathbb{R}^S$ is the amount of payoff being distributed among agents of coalition S.
+A \emph{coalitional game} is a pair $G = (N, v)$ where $v$ is called a \emph{characteristic function}, which given a coalition, is a function $v: 2^N \to \mathbb{R}$ mapping the set of players of the coalition to a real number $v(S)$, the worth of $S$.
+This number usually resembles the output or payoff or performance of these players working together as a coalition.
+If a coalition $S$ forms then it can divide its worth, $v(S)$ in any possible way among its members.
+The payoff vector $x \in \mathbb{R}^S$ is the amount of payoff being distributed among agents of coalition $S$.
 The payoff vector satisfies two conditions:
@@
 
-The second condition is $feasibility$, according to equation below the payoff for each agent cannot be more than coalitions total gain.
-A payoff vector is also $efficient$ if all the payoff obtained by a coalition is distributed amongst coalition members: $\sum_{i \in S} x_i = v(S)$.
+The second criteria is the \emph{feasibility} condition, according to the equation, the payoff for each agent cannot be more than coalitions total gain.
+A payoff vector is also \emph{efficient} if all the payoff obtained by a coalition is distributed amongst coalition members: $\sum_{i \in S} x_i = v(S)$.
 This definition of characteristic function works in \emph{transferable utility} (TU) settings, where utility (payoff) is transferable from one player to other, in other words players have common currency and a unit of income is worth same for all players \cite{myerson1991game}.
@@
 
-{\bf Definition 1 (Shapley value)} Given a cooperative game (N, v), the Shapley value of player i is given by\cite{shapley_value}: 
+{\bf Definition 1 (Shapley value)} Given a cooperative game (N, v), the \emph{Shapley value} of player $i$ is given by\cite{shapley_value}: 
 \begin{equation}\label{eq:shapley}
-\sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (n-|S|-1)!}{n!} (v(S \cup \left\{i\right\}) - v(S))
+\phi_i(v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (n-|S|-1)!}{n!} (v(S \cup \left\{i\right\}) - v(S))
 \end{equation}
 
-Shapley value is a unique and fair solution concept for payoff distribution between agents. It basically rewards agents with amount of marginal contribution they have to the coalition.
+\emph{Shapley value} is a unique and fair solution concept for payoff distribution between agents. It basically rewards agents with the amount of marginal contribution they have to the coalition.
 
@@
 
-{\bf Definition 2 (Core)} A payoff vector x denoted by C(N,v) is in the core of a coalitional game (N, v) if and only if
+{\bf Definition 2 (Core)} A payoff vector $\mathbf{x}$, denoted by $C(N,v)$, is in the $core$ of a coalitional game $(N, v)$ if and only if
 \begin{equation}\label{eq:core}
@@
 \end{equation}
-The core if is not empty is basically a set of payoff vectors (x) where no subset of players $S^\prime$ could gain more by deviating and making their own coalition $\sum_{i \in S^\prime} x_i \geq v(S^\prime)$.
-The sum of payoffs to the agents in any sub-coalition S is at least as large as the amount that these agents could earn by forming a coalition on their own.
+
+The core is basically a set of payoff vectors $(\mathbf{x})$ where no subset of players $S^\prime$ could gain more than their current payoff, by deviating and making their own coalition $\sum_{i \in S^\prime} x_i \geq v(S^\prime)$.
+The sum of payoffs to the players in any sub-coalition $S$ is at least as large as the amount that these players could earn by forming a coalition on their own.
 In a sense it is analogue to Nash equilibrium, except that it about deviations by groups of agents.
-The core is the strongest and most popular solution concept in cooperative game theory, however its computationally very heavy and is not computationally tractable as number of players increase.
-The core of some real-world problem games may be empty, which means having characteristic function $v$ there might be no possible distribution of payoff assuring stability of subgroups.
+The core is the strongest and most popular solution concept in cooperative game theory, however it is a combinatorial problem and is not computationally tractable as number of players increase.
+The core of some real-world problem games may be empty, which means having characteristic function game of $(N,v)$, there might be no possible distribution of payoff assuring stability of subgroups.
 
-{\bf Definition 3 (Convex cooperative games)} A game with characteristic function v(S) is convex if:
+{\bf Definition 3 (Convex cooperative games)} A game with characteristic function $v(S)$ is convex if:
 \begin{equation}\label{eq:convex}
@@
 
-According to a classic result by Shapley \cite{S1971cores} convex games always have a non-empty core.
+According to a classic result by Shapley \cite{S1971cores}, convex games always have a non-empty core.
 We will use a variation of convexity condition in our algorithm to check whether our coalitions are stable.
@@
 %\\
-When core set is empty, it means no coalition of players can gain anything by deviating, it is the strongest stable condition.
+When \emph{core} set of a game is empty, it means no coalition of players can gain anything by deviating.
 An outcome would be unstable if a coalition can benefit even by a small amount from deviating.
 This is a strong requirement.
-In some situations, deviations can be costly or agents may have some loyalty to their coalitions or even it can be computationally intractable to find those small benefits.
-It would only make sense for a coalition to deviate if the gain from a deviation exceeded a particular cost for example the costs of deviation.
-$\epsilon-Core$ relaxes the notion of the core, and only require that no coalition can benefit significantly or within a constant amount($\epsilon$) by deviating.
+In some situations, deviations can be costly or players may have loyalty to their coalitions, or even it can be computationally intractable to find those small benefits.
+It would only make sense for a coalition to deviate if the gain from a deviation exceeded a particular cost for example the cost of deviation.
+\emph{$\epsilon$-core} relaxes the notion of the core, and only requires that, no coalition would benefit significantly, or within a constant amount($\epsilon$) by deviating.
 
@@
 
-Coalition structure formation is the problem of finding best partition of agents into teams, focusing more on optimizing the coalition's ``owner'' payoff.
-In these settings performance of individual agent is less important than the \emph{social welfare} of the system, which is the sum of the values of all teams.
-Having characteristic function game G, a coalition structure (CS) is \emph{socially optimal} is CS belongs to set $argmax_{CS \in CS_N}v(CS)$ where v(CS) is sum of the total valuation function of all coalitions inside CS $(v(CS) = \sum_{C \in CS_N}v(CS))$.
-The outcome of a characteristic function game in coalition structure settings, consists of two parts; first a disjoint partition of players (agents) into coalitions, called a \emph{coalition structure} (CS) and second a \emph{payoff vector} as mentioned in cooperative game solution concepts, which distributes the value of each coalition among its members.
+Coalition structure formation is the problem of finding best partition of agents into teams.
+In these settings, performance of individual agent is less important than the \emph{social welfare} of the system, which is the sum of the values of all teams.
+Having characteristic function game $G(N,v)$, a coalition structure $(CS)$ is \emph{socially optimal} if $CS$ belongs to set $argmax_{CS \in CS_N}v(CS)$ where $v(CS)$ is sum of the values of all coalitions inside $CS$.
+$v(CS) = \sum_{C \in CS_N}v(CS)$.
+%The outcome of a characteristic function game in coalition structure settings, consists of two parts; first a disjoint partition of players (agents) into coalitions, called a \emph{coalition structure} (CS) and second a \emph{payoff vector} as mentioned in cooperative game solution concepts, which distributes the value of each coalition among its members.
 
@@
 
-In this section, we present the architecture of different web service community models and formulate how both web services and community masters as rational agents would maximise their payoff.
+In this section, we present the architecture of different web service community models and formulate how both web services and community masters as rational agents, would adopt strategies to maximize their payoff.
 
@@
 
-In this scenario, there are is a community controller by its master web service.
-The community master has some request rate $(R_{master})$ from users.
+In this scenario, there is a community controller by its master web service.
+The community master has a task request rate $(R_{master})$ from users.
 Web services need to join a community to be able to get tasks from a master web service.
 Each web service comes with different quality of service parameters and a throughput $(T_{ws})$.
-Throughput is the average rate of tasks a web service can perform.
-Therefore, the master web service is providing tasks with rate of $R_{ws}$ and web services perform tasks with average output metrics of $QoS_{ws}$ and a rate or $T_{ws}$.
-In this setting, we define the value of the coalition as follows:
+Throughput is the average rate of tasks a web service can perform per time unit.
+Therefore, the master web service is providing tasks with rate of $R_{ws}$ and web services perform tasks with average output quality of $QoS_{ws}$ and a rate or $T_{ws}$.
+In this setting, we define the value of the coalition of the web services within a community as follows:
 \begin{equation*}
@@
 If the rate is more than master's input task rate, it means the web services inside the community are capable of doing more tasks than exists.
-Considering this the valuation function will balance the output performance and will be the exact amount and quality of work they can perform within the particular community.
+Considering this the valuation function will balance the output performance and will be the exact rate and quality of work they can perform within the particular community.
 %** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests.
@@
 
-The membership decision is made based on throughput and QoS of the requested web service.
-The goal is to have quality web services in community so the community stays stable and no other web services would have incentives to deviate and join ``other'' coalitions.
-Therefore, we it check the core membership of the coalition of all current community members and the new web service.
-Our algorithm uses the Shapley value distribution method as described in equation \ref{eq:shapley} to distribute gain of $v(C)$ among all members and then checks if Shapley value payoff vector for this community having characteristic function $v(C)$ is Core stable or not.
-In Shapley value payoff vector, the payoff for each web service i, is calculated based on their contribution $v(C \cup {i}) - v(C)$ and then averaging over the possible different permutations in which the coalition can be formed, this is why Shapley value distribution is fair.
-It is proven in convex games the Shapley value lies in the core \cite{DBLP:conf/ijcai/GrecoMPS11, myerson1991game}.
-Therefore if the Core is non-empty, the Shapley payoff vector is a member of Core.
+The membership decision is made based on throughput and \emph{QoS} parameters of the requested web service.
+The goal is to have quality web services in community so the community stays stable and no other web services would have incentives to deviate and leave the coalitions.
+Therefore, a basic method would be to check the core membership of the coalition of all current community members (all web services already residing within the community) and the new web service.
+This algorithm would use the \emph{Shapley value} distribution method as described in equation \ref{eq:shapley} to distribute gain of $v(C)$ among all members and then checks if \emph{Shapley value} payoff vector for this community having characteristic function $v(C)$ is \emph{core} stable or not.
+In \emph{Shapley value} payoff vector, the payoff for each web service $ws_i$, is calculated based on their marginal contribution $v(C \cup {i}) - v(C)$ over all the possible different permutations in which the coalition can be formed, this is why \emph{Shapley value} distribution is fair.
+Because of going through all the possible different permutations of subsets of $N$, the nature of the \emph{Shapley value} is combinatorial.
+This makes it impractical to use as size of our coalitions grow.
+
+It is proven, in convex games the \emph{Shapley value} lies in the core \cite{DBLP:conf/ijcai/GrecoMPS11, myerson1991game}.
+Therefore if the \emph{Core} is non-empty, the \emph{Shapley value} payoff vector is a member of \emph{Core}.
 % so in our algorithm we check the core membership of this payoff vector.
@@
 We have an established community with a master and some (slave) web services already residing in community.
-Now we have a request from a web service to join our community.
-The ideal solution in our method would be analyzing the core or $\epsilon-core$ stability of group having this new member.
-However the normal core membership algorithms are intractable.
+A web service would send a join request to the community.
+The ideal solution would be analyzing the \emph{core} or \emph{$\epsilon$-core} stability of group having this new member.
+However the normal core membership algorithms are computationally intractable.
 We exploit the equation \ref{eq:convex_snow} to check convexity of our characteristic function game having the new member.
-In that equation we set T to be our community members (C) before having the new web service.
-We set ${i}$ the new web service, and then verify the equation for S, setting $ S = T / W $ where $W$ is all 1-member subset of set C.
+In the equation, we set $C$ to be our community members $(C)$ before having the new web service.
+We assign ${i}$ to the new web service, and then verify the equation for $S$, setting $ S = T / W $ where $W$ is all possible 1-member subsets of set $N$.
 We can relax the equation a bit by adding a constant epsilon to left side of equation.
 We call this method \emph{Depth-1 Convex-Checker} algorithm.
-If the equation is true for all $W$ we let the member join our community, since he will contribute good enough to make our new community stable.
-The run time complexity of this algorithm is O(n) which is huge reduction from $O(2^n)$ checking all possible subsets of N.
-In our second method, we use the same algorithm however this time we set W to be all possible subsets of size two and one of C.
+If the equation is true for all $W$ we let the new web service join our community, since the web service will contribute good enough to make our new community stable.
+The run time complexity of this algorithm is $O(n)$ which is a great reduction from $O(2^n)$ checking all possible subsets of $N$.
+In our second method, we use the same algorithm however this time we set $W$ to be all possible subsets of size two and one of the community $C$.
 We call this method \emph{Depth-2 Convex-Checker} and its run time complexity is $O(n^2)$.
-It is possible to develop an anytime algorithm by continuing verifying this condition against all subsets of size 3 to N, and stop whenever we are interrupted.
+It is possible to develop an anytime algorithm by continuing verifying this condition against all subsets of size 3 to $|N|$, and stop whenever we the algorithm is interrupted.
 
@@
 If it is more than 1, is means they increase performance by working together and they are \emph{super additive}, otherwise it depicts they would perform better in linear sense if they worked alone.
-$w_m$ is the weight of important for a QoS metric, it gives the community the flexibility to emphasize or neglect a specific QoS parameter.
+$w_m$ is the weight of important for a \emph{QoS} metric, it gives the community the flexibility to emphasize or neglect a specific \emph{QoS} parameter.
 Note that $ \sum_{m}{w_m} = 1 $.
@@
 In this section, we discuss the experiments we performed for our scenarios to validate applicability and performance of our proposed methods in realistic environments.
-We created a pool of web services and populated most of their QoS parameters from a real world web service dataset \cite{DBLP:conf/smc/Al-MasriM09a}.
+We created a pool of web services and populated most of their \emph{QoS} parameters from a real world web service dataset \cite{DBLP:conf/smc/Al-MasriM09a}.
 We programmed the simulations using Java and executed the simulations on a Intel Xeon X3450 machine with 4GBs of memory.
-For other parameters we used normal distribution with parameters that make most sense in real world examples.
+For other parameters missing from the dataset, we used normal random distribution with parameters that make most sense in real world examples.
 
@@
 
-Figure \ref{performanceall} depicts the results of simulation of optimal $\epsilon-Core$ with 10\% of total community value deviation allowed (one grand community with many web services), \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods.
-The the \emph{optimal $\epsilon$-core} method we capped the coalition size to 24 web services, since anything more than that would require analysis with time complexity of $O(2^{24-1})$ which would made that impractical to run in our simulations.
+Figure \ref{performanceall} depicts the results of simulation of optimal \emph{$\epsilon$-core} with 10\% of total community value deviation allowed (one grand community with many web services), \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods.
+The the \emph{optimal $\epsilon$-core} method we capped the coalition size to 24 web services, since anything more than that would require analysis with time complexity of $O(2^{24-1})$, making it impractical to run in our simulations.
 In other methods there were no cap on size of the community and we had communities of size 60 web services at some points.
-The results show depth-2 and 1 convex checker methods are performing well compared to other methods and all not far from optimal.
+The results show \depth{depth-2 and 1 convex checker} methods are performing well compared to other methods and all not far from optimal.
 
@@
 
-As mentioned in preliminaries section \ref{s:preliminaries}, core assumes no coalition of players can gain anything by deviating which is a fairly strong requirement, that is why the notion of $\epsilon-Core$ was introduced.
+As mentioned in section \ref{s:preliminaries}, core assumes no coalition of players can gain anything by deviating which is a fairly strong requirement, that is why the notion of \emph{$\epsilon$-core} was introduced.
 Least-Core $e(G)$ of a game $G$, is the minimum amount of $\epsilon$ in which the core is not empty.
@@
 We pick random number of web services from our data set and formed around 10,000 random coalitions consisting of 3 to 25 web services.
-We choose 25 as maximum number of members in our grand coalition since it is computationally very complex for bigger coalitions to compute \emph{$\epsilon$}-core.
-We set $\epsilon$ to a ratio of total payoff of coalition v(C) between 0 and 1.
-The results in figure \ref{f_leastcore} illustrates, almost 10\% of our random web service coalitions have non-empty core solution and \emph{$\epsilon$}-core solution is always non-empty when we let agents gain only 30\% (of $v(C)$) more, by deviating.
+We choose 25 as maximum number of members in our grand coalition since it is computationally very complex for bigger coalitions to compute \emph{$\epsilon$-core}.
+We set $\epsilon$ to a ratio of total payoff of coalition $v(C)$ between 0 and 1.
+The results in figure \ref{f_leastcore} illustrates, almost 10\% of our random web service coalitions have non-empty core solution and \emph{$\epsilon$-core} solution is always non-empty when we let agents gain only 30\% (of $v(C)$) more, by deviating.
 

### 2013-03-15 papers/coalition/coalition.tex
Changes

@@
 
-We first analyze the most important performance result our communities should perform, quality and quantity of tasks successfully performed by our communities.
+We analyze the most important performance result the communities should perform, quality and quantity of tasks successfully performed by the communities.
 This is the most important criteria for user satisfaction.
-We initiate the community with few web services, then let rejecting and accepting of random web services go for a while, after that we start task distribution for the communities and let them allocate tasks for web services.
+We initiate the community with few web services, then let rejecting and accepting of random web services go for a short number of iterations, after that we start task distribution for the communities and let them allocate tasks for web services.
 Then we measure the average output performance of tasks in communities following different methods.
@@
 
-Figure \ref{performanceall} depicts the results of simulation of optimal \emph{$\epsilon$-core} with 10\% of total community value deviation allowed (one grand community with many web services), \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods.
-The the \emph{optimal $\epsilon$-core} method we capped the coalition size to 24 web services, since anything more than that would require analysis with time complexity of $O(2^{24-1})$, making it impractical to run in our simulations.
+Figure \ref{performanceall} depicts the results of optimal \emph{$\epsilon$-core}, by assigning $\epsilon$ to 15\% of total community worth, $\epsilon = 0.15 \times v(C)$, allowing subsets of coalition to gain maximum 15\% of $v(C)$, \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, \emph{3-Way Satisfactory}\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative}\cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods in \emph{one grand community with many web services} scenario.
+In the \emph{optimal $\epsilon$-core} method we capped the coalition size to 25 web services, since anything more than that would require analysis with time complexity of $O(2^{n-1})$, making it impractical to run in our simulations.
 In other methods there were no cap on size of the community and we had communities of size 60 web services at some points.
-The results show \depth{depth-2 and 1 convex checker} methods are performing well compared to other methods and all not far from optimal.
+The results show \emph{depth-2 and 1 convex checker} methods are performing better compared to other methods and their performance is close to optimal \emph{$\epsilon$-core} method.
 
@@
 
-As mentioned in section \ref{s:preliminaries}, core assumes no coalition of players can gain anything by deviating which is a fairly strong requirement, that is why the notion of \emph{$\epsilon$-core} was introduced.
+As mentioned in section \ref{s:preliminaries}, the concept of \emph{core}, assumes no coalition of players can gain anything by deviating which is a fairly strong requirement, that is why the notion of \emph{$\epsilon$-core} was introduced.
 Least-Core $e(G)$ of a game $G$, is the minimum amount of $\epsilon$ in which the core is not empty.
 We evaluated the least-core value using our valuation function and our set of web services.
-We pick random number of web services from our data set and formed around 10,000 random coalitions consisting of 3 to 25 web services.
-We choose 25 as maximum number of members in our grand coalition since it is computationally very complex for bigger coalitions to compute \emph{$\epsilon$-core}.
+We pick random number of web services from our dataset and formed around 10,000 random coalitions consisting of 3 to 26 web services.
+We choose 26 as maximum number of members in our grand coalition since it is computationally very complex for bigger coalitions to compute \emph{$\epsilon$-core}.
 We set $\epsilon$ to a ratio of total payoff of coalition $v(C)$ between 0 and 1.
-The results in figure \ref{f_leastcore} illustrates, almost 10\% of our random web service coalitions have non-empty core solution and \emph{$\epsilon$-core} solution is always non-empty when we let agents gain only 30\% (of $v(C)$) more, by deviating.
+The results in figure \ref{f_leastcore} illustrates, almost 10\% of our random web service coalitions have non-empty \emph{core} solution and \emph{$\epsilon$-core} solution is \emph{always} non-empty when we let agents gain 30\% (of $v(C)$) more, by deviating.
 

### 2013-03-16 papers/coalition/coalition.tex
Changes

@@
 \usepackage{amsthm}
-
+\pagestyle{plain}
 \theoremstyle{plain}
-\newtheorem{thm}{Theorem} % reset theorem numbering for each chapter
-
+\newtheorem{thm}{Theorem}% reset theorem numbering for each chapter
+\newtheorem{Proposition}{Proposition}
 \theoremstyle{definition}
@@
 \IEEEauthorblockA{Department of Electrical and Computer Engineering\\
-Khalifa University\\
-Dubai, UAE\\
+Khalifa University of Science, Technology and Research\\
+Abu Dhabi, UAE\\
 hadi.otrak, rabeb.mizouni@kustar:ac:ae}
@@
 
-Web services are loosely-coupled business applications and willing to cooperate in distributed settings within different groups called communities.
-Communities aim to provide better efficiency, market share and total payoff.
-There are a number of proposed mechanisms and models on aggregating web services, however forming optimal and stable coalitions to maximize individual and community efficiency and income has got less attention.
-In this paper, we propose an efficient coalition formation mechanism using cooperative game-theoretic methods.
-We propose a mechanism for membership requests and selection of web services in the scenarios in which there are already established communities.
-Moreover, we analyze the scenarios in which we do not have pre-defined communities and we develop a mechanism for web services to form stable groups allowing them to maximize their efficiency and generate near-optimal (welfare-maximizing) communities.
-The theoretical and simulation results show that our algorithms provide web services and community owners with applicable and near-optimal decision making mechanisms.
+Web services are loosely-coupled business applications willing to
+cooperate in distributed settings within different groups called
+communities. Communities aim to provide better visibility,
+efficiency, market share and total payoff. There are a number of
+proposed mechanisms and models on aggregating web services and
+making them cooperate within their communities. However, forming
+optimal and stable communities as coalitions to maximize
+individual and group efficiency and income has not been addressed
+yet. In this paper, we propose an efficient coalition formation
+mechanism using cooperative game-theoretic techniques. We propose
+a mechanism for community membership requests and selections of
+web services in the scenarios where established communities
+already exist. Moreover, we analyze the scenarios where
+communities are not established yet. The ultimate objective is to
+develop a mechanism for web services to form stable groups
+allowing them to maximize their efficiency and generate
+near-optimal (welfare-maximizing) communities. The theoretical and
+simulation results show that our algorithms provide web services
+and community owners with applicable and near-optimal decision
+making mechanisms.
 
@@
 
-\section{Introduction}
-
-Over the past years, online services have become part of critical business services.
-The increasing reliance on web-based applications has significant implications for service providers which calls for a seamless integration of business process, applications and web services of the Internet.
-Web services as a highly available software function accessible at a network address over the web, usually provide a set of stateless functions.
-Delivering high quality services on the dynamic and unpredictable nature of Internet is a critical and challenging task.
-
-The need for highly available and highly responsive services online has called for collaborative communities of these loosely-coupled business web services.
-The idea of web service communities and the way they are engineered to collaborate was proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09, DBLP:journals/internet/BenatallahSD03, Rosario:2008:PQS:1512146.1512290} where web services with similar functionality are grouped together and users send their requests to communities assuring higher service availability and performance than individual web services.
-These communities are highly available also more resilience to failure since there is no single point of failure in their architecture.
-
-Most of the recent work on communities of services are either user-centric and focus on user satisfaction \cite{Chun02user-centricperformance} or they are system-centric and focus on system throughput and performance and utilization of the system.
-There are many contributions in distributed, grid, cluster and cloud computing services which are system-centric.
-However in real world environments both users and service providers are self-interested agents, aiming to maximize their own profit.
-In real world environments, both these parties will participate and collaborate as long as it's economic and efficient for both of them.
-
-Recently, \cite{DBLP:conf/IEEEscc/LimTMB12, DBLP:conf/IEEEscc/KhosravifarABT11} have proposed mechanisms in which they try to maximize gain for both parties.
-A two-player non-cooperative game theory method between web services and community manager was proposed in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}.
-The strategies for a web service when facing a new community, is requesting to join or refusing the invitation to join the community and the set of strategies for communities are inviting the web service or refusing the web service join request.
-Both parties based on their capacity, market share and reputation will have different set of utilities over the strategy profiles of the game.
-The problem suffers from ignoring many quality parameters and also ignoring the web services already residing within the community.
-The game is only between the community master and the new web service, and all other web services already residing within the community are ignored.
-Those web services can lose utility or payoff, having to collaborate with new web services.
-They may deviate and join other communities if they are unsatisfied, which is not addressed in their approach.
-In \cite{DBLP:conf/IEEEscc/LimTMB12} a 3-Way satisfaction selection approach has been proposed.
-In their approach, they have proposed a web service selection process for community masters catering for the efficiency of all three parties of users, web services and communities.
-In this work, they show how the gains of these parties are coupled together and they suggest a linear optimization process for optimizing the needs of the 3 parties.
-However, the optimization problem in this solution tends to optimize some parameters considering all web services even if they are weak.
-There are no clear thresholds for accepting or rejecting new web services.
-The optimization result for example could suggest web services already residing within the community to increase or decrease their capacity to adjust with weakness of other parties in the system.
-However, a strong performing web service could deviate anytime it finds itself unsatisfied within the community instead of adjusting its service parameters.
-
-In this paper, we propose a cooperative game theory based model for aggregation of web services within communities.
-The solution concepts of cooperative game theory seeks to find most efficient ways of forming coalitions (teams) of agents, maximizing their gain and payoff, and also distributing gain in a fair way to keep coalitions stable by having all agents satisfied.
-We first propose a representation function for communities of web services based on their qualities and capacities.
-Using this function we can evaluate the $worth$ of each community of web services.
-Our community managers facing new membership requests, analyses whether the new coalition having the new set of web services will keep the community stable for $all$ web services already residing in the community or not.
-The community manager will reject the membership requests if it finds out new coalition would be unstable, preventing $any$ subset of web services from gaining significantly more, by deviating and joining other communities.
-Also web services facing communities, will try to join communities which maximizes their gain, if they find out they can deviate and gain more, they will form new coalitions with other communities.
-The cooperative game theory solution methods are combinatorial in nature and are NP-complete, making them impractical in real world applications; however, using the concepts of coalition stability we have offered approximation algorithms running in polynomial time providing web services and community managers with applicable and near-optimal decision making mechanisms.
-
-The rest of paper is organized as follows.
-Section \ref{s:preliminaries} describes architecture and parameters and some basic cooperative game theory concepts, section \ref{s:model} presents our solution model in three different scenarios.
-Section \ref{s:resutls} presents our experiments and results and finally, section \ref{s:conclusion}, concludes the paper and identified future work.
+\section{Introduction and Related Work}
+
+Over the past years, online services have become part of many
+scalable business applications. The increasing reliance on
+web-based applications has significantly influenced the way web
+services are engineered. Web services provide a set of stateless
+software functions accessible at a network address over the web.
+The recent developments are shifting web services from passive and
+individual components to autonomous and group-based components
+where interaction, composition, and cooperation are the key
+challenges \cite{ICWS2011-1,SCC2011-1}. The main objective is to
+achieve a seamless integration of business processes, applications
+and web services. Delivering high quality services considering the
+dynamic and unpredictable nature of the Internet is still a very
+critical and challenging issue.
+
+The need for highly available and responsive services has called
+for grouping and collaborative mechanisms of loosely-coupled web
+services, particularly in business settings. The idea of grouping
+web services within communities and the way those communities are
+engineered so that web services can better collaborate have been
+proposed and investigated in
+\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
+Communities are virtual groups of web services having similar
+functionalities, but probably different non-functional quality
+attributes, which form the QoS parameters. When communities are
+used, users send their requests to the masters of those
+communities, which are responsible of managing the communities,
+forwarding the requests to the suitable member web services and
+checking the credentials of those members. Communities aim to
+provide higher service availability and performance than what
+individual web services can provide. The high availability of
+services and the community resilience to failure are guaranteed
+since web services can cooperate and replace each other within the
+same community and since there is no single point of failure in
+the communities architecture.
+
+Most of the recent work on communities of services are either
+user-centric and focus on user satisfaction
+\cite{Chun02user-centricperformance} or system-centric and focus
+on the whole system throughput, performance and utilization. There
+are many contributions in distributed, grid, cluster and cloud
+services which are system-centric. However, in real world
+environments and applications, both users and service providers
+are self-interested agents, aiming to maximize their own profit.
+In those environments, both parties (users and services) will
+collaborate as long as they are getting more benefits and payoff.
+
+In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
+DBLP:conf/IEEEscc/KhosravifarABT11} proposed mechanisms to help
+users and services maximize their gain. A two-player
+non-cooperative game between web services and community master was
+introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this
+game-theoretic model, the strategies available to a web service
+when facing a new community are requesting to join the community,
+accepting the master's invitation to join the community, or
+refusing the invitation to join. The set of strategies for
+communities are inviting the web service or refusing the web
+service's join request. Based on their capacity, market share and
+reputation, the two players have different set of utilities over
+the strategy profiles of the game. The main limits of this game
+model are: 1) its consideration of only three quality parameters,
+while the other factors are simply ignored; and 2) the
+non-consideration of the web services already residing within the
+community. The game is only between the community master and the
+new web service, and the inputs from all the other members are
+simply ignored. The consideration of those inputs is a significant
+issue as existing web services can lose utility or payoff because
+of the new member, which can results in an unhealthy and unstable
+group. The problem comes from the fact that the existing members
+should collaborate with the new web services, so probably their
+performance as a group can suffer. Existing members may even
+deviate and try to join other communities if they are unsatisfied.
+Those considerations of forming stable and efficient coalitions
+are the main contributions of our paper.
+
+In \cite{DBLP:conf/IEEEscc/LimTMB12} a 3-way satisfaction approach
+for selecting web services has been proposed. In this approach,
+the authors proposed a web service selection process that the
+community masters can use. The approach considerers the efficiency
+of all the three involved parties, namely users, web services and
+communities. In this work, it is shown how the gains of these
+parties are coupled together using a linear optimization process.
+However, the optimization problem in this solution tends to
+optimize some parameters considering all web services regardless
+of their efficiency and contribution to the community's welfare.
+Moreover, there are no clear thresholds for accepting or rejecting
+new web services. The solution of the optimization problem could,
+for instance, suggest web services already residing within the
+community to increase or decrease their capacity to cover up the
+weakness of other parties in the system. However, a high
+performing web service could deviate anytime it finds itself
+unsatisfied within the community instead of adjusting its service
+parameters.
+
+\textbf{Contributions.} In this paper, we use game theory to
+propose a cooperative game model for the aggregation of web
+services within communities. The solution concepts of our
+cooperative game seeks to find efficient ways of forming
+coalitions (teams) of web services so that they can maximize their
+gain and payoff, and distribute the gain in a fair way among all
+the web services. Achieving Fairness when the gain is distributed
+among the community members is the main factor to keep the
+coalition stable as no web service will expect to gain better by
+deviating for the community. In other words, the coalition is made
+efficient if all the members are satisfied. We first propose a
+representation function for communities of web services based on
+their QoS attributes. By using this function, we can evaluate the
+$worth$ of each community of web services. When facing new
+membership requests, a typical community master checks whether the
+new coalition having the old and new set of web services will keep
+the community stable or not. The community master will reject the
+membership requests if it finds out that the new coalition would
+be unstable, preventing $any$ subset of web services from gaining
+significantly more by deviating from the community and joining
+other communities or forming new ones. The computation of
+solutions for cooperative game theory problems is combinatorial in
+nature and proven to be NP-complete \cite{Algorithmic}, making
+this computation impractical in real world applications. However,
+using the concepts of coalition stability, we propose
+approximation algorithms running in polynomial time providing web
+services and community masters with applicable and near-optimal
+decision making mechanisms.
+
+The rest of paper is organized as follows. Section
+\ref{s:preliminaries} describes the architecture, considered
+parameters and some basic cooperative game theory concepts.
+Section \ref{s:model} presents our solution model in three
+different scenarios. Section \ref{s:resutls} describes our
+experiments and results. Finally, Section \ref{s:conclusion},
+concludes the paper and identifies future work.
 
@@
 
-In this section we discuss the parameters and preliminary concepts that we use in the rest of paper.
+In this section, we discuss the parameters and preliminary
+concepts that we use in the rest of the paper.
 
@@
 
-Our system consists of three main type of entities working together:
-
-\emph{1) Web services} are rational entities providing services to end users.
-They aim to maximize their individual income by receiving enough requests from end users.
-In order to increase their revenue, web services seek for more tasks if they have the capacity and throughput.
-Web services can join communities to have better efficiency by collaborating with others, to have access to higher market share and to have opportunity of receiving a bigger task pool from end users.
-The way the web services reside inside communities and how communities of web services are engineered is described thoroughly in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
-Throughout this paper, in our equations, we refer to web services as $ws$.
-
-\emph{2) Master Web Services} are responsible for managing and are representative of the communities of web services.
-Communities receieve tasks from users and they aim to have a healthy set of web services to perform the tasks.
-They seek to maximise user satisfaction by having tasks accomplished with good rate and quality.
-Higher user satisfaction will bring more user tasks and increase the market share and revenue of the community.
-
-\emph{3) Users} generate tasks and try to find service providers online to perform the tasks.
-User satisfaction is abstracted as function of quantity and quality of tasks accomplished by our service providers.
-
-\subsection{Web Sercive Parameters}
-
-Web services come with different quality of service parameters. These parameters with a short description are listed in Table \ref{qosws}.
+Our system consists of three main types of entities working
+together:
+
+\emph{1) Web services} are rational entities\footnote{The term
+rational is used here in the sense that web services are utility
+maximizers} providing services to end users. They aim to maximize
+their individual income by receiving enough requests from end
+users. In order to increase their revenue, web services seek for
+more tasks if they have the capacity and throughput to do so. Web
+services can join communities to have better efficiency by
+collaborating with others, to have access to higher market share,
+and to have opportunity of receiving a bigger task pool from end
+users. The way the web services reside inside communities and how
+communities of web services are engineered is described in
+\cite{DBLP:journals/ijebr/MaamarSTBB09}. Throughout this paper, in
+our equations, we refer to web services as $ws$ and to the set of
+web services hosted by a given community as $C$. To simply the
+notation, sometimes we simply write $ws$ instead of $ws \in C$ to
+go through the elements $ws$ of the set $C$.
+
+\emph{2) Master Web Services} are representatives of the
+communities of web services and responsible for their management.
+Communities receive requests from users and aim to host a healthy
+set of web services to perform the required tasks. They seek to
+maximize user satisfaction by having tasks accomplished according
+to the desired QoS. In fact, higher user satisfaction will bring
+more user requests and increase the market share and revenue of
+the community.
+
+\emph{3) Users} generate requests and try to find the best
+available services. User satisfaction is abstracted as function of
+quantity and quality of tasks accomplished by a given service.
+
+\subsection{Web Service Parameters}
+
+Web services come with different quality of service parameters.
+These parameters with a short description are listed in Table
+\ref{qosws}.
 
@@
 \hline
-\textbf{Notation} & \textbf{Definition} \\
+\textbf{Parameter} & \textbf{Definition} \\
 \hline\hline
-$Availability$ & Probability of available during a time frame \\
-$Reliability$ & P of successfully handling tasks during a timeframe\\
-$Successability$ & Probability of handling tasks successfully \\
-$Throughput$ & Average rate of handling tasks \\
+$Availability$ & Probability of being available during a time frame \\
+$Reliability$ & Probability of successfully handling requests \\
+&during a timeframe\\
+$Successability$ & Rate of successfully handled requests \\
+$Throughput$ & Average rate of handling requests \\
 $Latency$ & The average latency of services\\
 $Capacity$ & Amount of resources available\\
-$Cost$ & Mean service fee for cooperating \\
+$Cost$ & Mean service fee \\
 $Regulatory$ & Compliance with standards, law and rules\\
@@
 
-We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a} which has aggregated and normalized each of these parameters to a real value between 0 and 1.
-Since tasks are not shared between web services and are distributed among all web services inside a community, one can expect tasks within a community to be performed by average quality of web service residing in that community.
-We use this expected quality output $(QoS_{ws})$, later in evaluating community \emph{worth} or \emph{payoff} function.
+We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
+which has aggregated and normalized each of these parameters to a
+real value between 0 and 1. Since requests are not shared among
+web services and are distributed among all of them inside a
+community, each one of them comes with a given QoS denoted by
+$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain
+aggregation function of the parameters considered in Table
+\ref{qosws}. We use this quality output later in evaluating the
+community \emph{worth} or \emph{payoff} function.
 
 \subsection{Cooperative Game Concepts}
-Cooperative game is a branch of game theory that studies strategies of self-interested agents in a setting where agents can increase their payoff by binding agreements and cooperating in groups.
-We let $N$ to be a set of players.
-Any subset $S$ of $N$ can form a group that we call it a $coalition$.
-A \emph{coalitional game} is a pair $G = (N, v)$ where $v$ is called a \emph{characteristic function}, which given a coalition, is a function $v: 2^N \to \mathbb{R}$ mapping the set of players of the coalition to a real number $v(S)$, the worth of $S$.
-This number usually resembles the output or payoff or performance of these players working together as a coalition.
-If a coalition $S$ forms then it can divide its worth, $v(S)$ in any possible way among its members.
-The payoff vector $x \in \mathbb{R}^S$ is the amount of payoff being distributed among agents of coalition $S$.
-The payoff vector satisfies two conditions:
+Cooperative game is a branch of game theory that studies
+strategies of self-interested entities or agents in a setting
+where those agents can increase their payoff by binding agreements
+and cooperating in groups. We let $N$ be a set of players. Any
+subset $S$ of $N$ can form a group called $coalition$. A
+\emph{coalitional game} is a pair $G = (N, v)$ where $v$ is called
+a \emph{characteristic function}, which given a coalition, is a
+function $v: 2^N \to \mathbb{R}$ mapping the set of players of the
+coalition to a real number $v(S)$, the worth of $S$. This number
+usually represents the output or payoff or again the performance
+of these players working together as coalition.  If a coalition
+$S$ is formed, then it can divide its worth, $v(S)$ in any
+possible way among its members. The payoff vector $x \in
+\mathbb{R}^S$ is the amount of payoff being distributed among the
+members of the coalition $S$. The payoff vector satisfies two
+conditions:
 
 \begin{itemize}
-	\item $x \geq 0$ for all $i \in N$, and
+    \item $x_i \geq 0$ for all $i \in N$, and
     \item $\sum_{i \in S} x_i \leq v(S)$
@@
 
-The second criteria is the \emph{feasibility} condition, according to the equation, the payoff for each agent cannot be more than coalitions total gain.
-A payoff vector is also \emph{efficient} if all the payoff obtained by a coalition is distributed amongst coalition members: $\sum_{i \in S} x_i = v(S)$.
-This definition of characteristic function works in \emph{transferable utility} (TU) settings, where utility (payoff) is transferable from one player to other, in other words players have common currency and a unit of income is worth same for all players \cite{myerson1991game}.
-
-When dealing with cooperative games, two issues need to get addressed: 1. What coalition to form (Canonical games)? 2. How to reward each member when a task is completed (Coalition-formation games)?
+The second criteria is called the \emph{feasibility} condition,
+according to which, the payoff for each agent cannot be more than
+the coalition total gain. A payoff vector is also \emph{efficient}
+if the payoff obtained by a coalition is distributed amongst the
+coalition members: $\sum_{i \in S} x_i = v(S)$. This definition of
+the characteristic function works in \emph{transferable utility}
+(TU) settings, where utility (i.e., payoff) is transferable from
+one player to another, or in other words, players have common
+currency and a unit of income is worth same for all players
+\cite{myerson1991game}.
+
+When dealing with cooperative games, two issues need to be
+addressed:\\ 1. What coalition to form (Canonical games)? \\
+2. How to reward each member when a task is completed
+(Coalition-formation games)?\\
+%
+The following definitions help address these two issues.
 
@@
 
-{\bf Definition 1 (Shapley value)} Given a cooperative game (N, v), the \emph{Shapley value} of player $i$ is given by\cite{shapley_value}: 
+{\bf Definition 1 (Shapley value)} Given a cooperative game $(N,
+v)$, the \emph{Shapley value} of player $i$ is given
+by\cite{shapley_value}:
 \begin{equation}\label{eq:shapley}
-\phi_i(v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (n-|S|-1)!}{n!} (v(S \cup \left\{i\right\}) - v(S))
+\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} }
+\frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))
 \end{equation}
 
-\emph{Shapley value} is a unique and fair solution concept for payoff distribution between agents. It basically rewards agents with the amount of marginal contribution they have to the coalition.
+\emph{Shapley value} is a unique and fair solution concept for
+payoff distribution among the members of the coalition. It
+basically rewards members with the amount of marginal contribution
+they have to the coalition.
 
@@
 
-{\bf Definition 2 (Core)} A payoff vector $\mathbf{x}$, denoted by $C(N,v)$, is in the $core$ of a coalitional game $(N, v)$ if and only if
+{\bf Definition 2 (Core)} A payoff vector $x$ is in the $core$ of
+a coalitional game $(N, v)$ if and only if:
 \begin{equation}\label{eq:core}
@@
 
-The core is basically a set of payoff vectors $(\mathbf{x})$ where no subset of players $S^\prime$ could gain more than their current payoff, by deviating and making their own coalition $\sum_{i \in S^\prime} x_i \geq v(S^\prime)$.
-The sum of payoffs to the players in any sub-coalition $S$ is at least as large as the amount that these players could earn by forming a coalition on their own.
-In a sense it is analogue to Nash equilibrium, except that it about deviations by groups of agents.
-The core is the strongest and most popular solution concept in cooperative game theory, however it is a combinatorial problem and is not computationally tractable as number of players increase.
-The core of some real-world problem games may be empty, which means having characteristic function game of $(N,v)$, there might be no possible distribution of payoff assuring stability of subgroups.
-
-{\bf Definition 3 (Convex cooperative games)} A game with characteristic function $v(S)$ is convex if:
+The core is basically a set of payoff vectors where no subset of
+players $S^\prime$ could gain more than their current payoff by
+deviating and making their own coalition $\sum_{i \in S^\prime}
+x_i \geq v(S^\prime)$. The sum of payoffs of the players in any
+sub-coalition $S$ is at least as large as the amount that these
+players could earn by forming a coalition by their own. In a
+sense, it is analogue to Nash equilibrium, except that core is
+about deviations from groups of entities. The core is the
+strongest and most popular solution concept in cooperative game
+theory. However, its computation is a combinatorial problem and
+becomes intractable as the number of players increases. The core
+of some real-world problem games may be empty, which means having
+the characteristic function of the game $(N,v)$, there might be no
+possible distribution of payoff assuring stability of subgroups.
+
+{\bf Definition 3 (Convex cooperative games)} A game $(N,v)$ with
+characteristic function $v(S)$ is convex if:
 \begin{equation}\label{eq:convex}
-V(S) + V(T) \leq v(S \cup T) + v (S \cap T), \forall S,T \subseteq N.
+v(S) + v(T) \leq v(S \cup T) + v (S \cap T), \forall S,T \subseteq
+N.
 \end{equation}
 
-According to a classic result by Shapley \cite{S1971cores}, convex games always have a non-empty core.
-We will use a variation of convexity condition in our algorithm to check whether our coalitions are stable.
+According to a classic result by Shapley \cite{S1971cores}, convex
+games always have a non-empty core. We will use a variation of
+convexity condition in our algorithm to check whether our
+coalitions are stable.
 
@@
 %\\
-When \emph{core} set of a game is empty, it means no coalition of players can gain anything by deviating.
-An outcome would be unstable if a coalition can benefit even by a small amount from deviating.
-This is a strong requirement.
-In some situations, deviations can be costly or players may have loyalty to their coalitions, or even it can be computationally intractable to find those small benefits.
-It would only make sense for a coalition to deviate if the gain from a deviation exceeded a particular cost for example the cost of deviation.
-\emph{$\epsilon$-core} relaxes the notion of the core, and only requires that, no coalition would benefit significantly, or within a constant amount($\epsilon$) by deviating.
+When the \emph{core} set of a game is empty, it means no coalition
+of players can gain anything by deviating. An outcome would be
+unstable if a coalition can benefit even by a small amount from
+deviating, which is a strong requirement. In fact, in some
+situations, deviations can be costly, or players may have loyalty
+to their coalitions, or even it can be computationally intractable
+to find those small benefits. It would only make sense for a
+coalition to deviate if the gain from a deviation exceeds the cost
+of performing the deviation. \emph{$\epsilon$-core} relaxes the
+notion of the core, and only requires that no coalition would
+benefit significantly, or within a constant amount($\epsilon$) by
+deviating (see Equation \ref{eq:core}).
 
@@
 
-Coalition structure formation is the problem of finding best partition of agents into teams.
-In these settings, performance of individual agent is less important than the \emph{social welfare} of the system, which is the sum of the values of all teams.
-Having characteristic function game $G(N,v)$, a coalition structure $(CS)$ is \emph{socially optimal} if $CS$ belongs to set $argmax_{CS \in CS_N}v(CS)$ where $v(CS)$ is sum of the values of all coalitions inside $CS$.
-$v(CS) = \sum_{C \in CS_N}v(CS)$.
+Coalition structure formation is the problem of finding the best
+partition of web services into teams. In these settings, the
+performance of an individual service is less important than the
+\emph{social welfare} of the whole system, which is the sum of the
+values of all teams. Having the game $(N,v)$, a coalition
+structure $(CS)$ is \emph{socially optimal} if $CS$ belongs to set
+$\operatorname*{arg\,max}_{CS} v(CS)$ where $v(CS)$ is the sum of
+the values of all coalitions inside $CS$. $v(CS) = \sum_{C \in
+CS}v(C)$.
 %The outcome of a characteristic function game in coalition structure settings, consists of two parts; first a disjoint partition of players (agents) into coalitions, called a \emph{coalition structure} (CS) and second a \emph{payoff vector} as mentioned in cooperative game solution concepts, which distributes the value of each coalition among its members.
@@
 
-In this section, we present the architecture of different web service community models and formulate how both web services and community masters as rational agents, would adopt strategies to maximize their payoff.
-
-\subsection {Web Services and A Grand Community}
-
-In this scenario, there is a community controller by its master web service.
-The community master has a task request rate $(R_{master})$ from users.
-Web services need to join a community to be able to get tasks from a master web service.
-Each web service comes with different quality of service parameters and a throughput $(T_{ws})$.
-Throughput is the average rate of tasks a web service can perform per time unit.
-Therefore, the master web service is providing tasks with rate of $R_{ws}$ and web services perform tasks with average output quality of $QoS_{ws}$ and a rate or $T_{ws}$.
-In this setting, we define the value of the coalition of the web services within a community as follows:
+In this section, we present different web service community models
+and focus on the problem of how both web services and community
+masters as rational entities would adopt strategies to maximize
+their payoff.
+
+\subsection {Web Services and One Community}
+
+In this scenario, we assume the existence of a typical community
+managed by its master web service and web services need to join it
+to be able to get requests from the master. The community master
+is characterized by a requests rate $(R_{M})$ from users. Each web
+service comes with a given QoS ($QoS_{ws}$) from which the
+throughput $T_{ws}$ is excluded. This exclusion allows us to build
+our analysis on the particular value of $T_{ws}$. Throughput is
+the average rate of tasks a web service can perform per time unit.
+Therefore, the master web service is providing tasks with the rate
+of $R_{ws}$ and web services perform tasks with average output
+quality of $QoS_{ws}$ and a throughput rate of $T_{ws}$. In this
+setting, we define the value of the coalition of the web services
+within a community as a function increasing in both $T_{ws}$ and
+$QoS_{ws}$ as follows:
 \begin{equation*}
-output(C) = \sum_{ws}{(T_{ws} \times QoS_{ws})}
+output(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
 \end{equation*}
 \setlength{\abovedisplayshortskip}{2pt}
-\begin{equation*}
+\begin{equation}
 v(C) = \left\{
   \begin{array}{l l}
-    output(C) & \quad \text{if $\sum_{ws}{T_{ws}} \leq R_{master}$}\\
-    output(C) \times \frac{R_{master}}{\sum_{ws}{T_{ws}}} & \quad \text{if $\sum_{ws}{T_{ws}} > R_{master}$}
+    output(C) & \quad \text{if $\sum_{ws}{T_{ws}} \leq R_{M}$}\\
+    output(C) \times \frac{R_{M}}{\sum_{ws}{T_{ws}}} & \quad \text{if $\sum_{ws}{T_{ws}} > R_{M}$}
   \end{array} \right.
-\end{equation*}
-
-The output of a coalition of web services is the rate and quality of task they can perform.
-If the rate is more than master's input task rate, it means the web services inside the community are capable of doing more tasks than exists.
-Considering this the valuation function will balance the output performance and will be the exact rate and quality of work they can perform within the particular community.
+\end{equation}
+
+The output of a coalition of web services is a function of the
+throughput and provided QoS. If the throughput rate is more than
+the master's input request rate, it means the web services inside
+the community are capable of serving more requests than the
+demand. Considering this factor, the valuation function is
+designed to balance the output performance so that it matches the
+exact throughput rate and QoS the web service can provide within
+the particular community.
 %** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests.
@@
 
-In the first scenario, we only consider one grand coalition and analyse the system from point of view of one single master web service and a collection of web services.
-The master web service decides which members can join %or should leave%
-the community and distributes the income or tasks among its community members.
+In this first scenario, we only consider one grand coalition and
+analyze the system from the point of view of one single master web
+service and a collection of web services. The master web service
+decides which members can join
+%or should leave%
+the community and distributes the requests and income among its
+community members (see Figure \ref{fig_sim1}).
 
@@
 \caption{Web Services and A Grand Community}
-\label{fig_sim}
+\label{fig_sim1}
 \end{figure}
 
-The membership decision is made based on throughput and \emph{QoS} parameters of the requested web service.
-The goal is to have quality web services in community so the community stays stable and no other web services would have incentives to deviate and leave the coalitions.
-Therefore, a basic method would be to check the core membership of the coalition of all current community members (all web services already residing within the community) and the new web service.
-This algorithm would use the \emph{Shapley value} distribution method as described in equation \ref{eq:shapley} to distribute gain of $v(C)$ among all members and then checks if \emph{Shapley value} payoff vector for this community having characteristic function $v(C)$ is \emph{core} stable or not.
-In \emph{Shapley value} payoff vector, the payoff for each web service $ws_i$, is calculated based on their marginal contribution $v(C \cup {i}) - v(C)$ over all the possible different permutations in which the coalition can be formed, this is why \emph{Shapley value} distribution is fair.
-Because of going through all the possible different permutations of subsets of $N$, the nature of the \emph{Shapley value} is combinatorial.
-This makes it impractical to use as size of our coalitions grow.
-
-It is proven, in convex games the \emph{Shapley value} lies in the core \cite{DBLP:conf/ijcai/GrecoMPS11, myerson1991game}.
-Therefore if the \emph{Core} is non-empty, the \emph{Shapley value} payoff vector is a member of \emph{Core}.
+The membership decision is made based on throughput and \emph{QoS}
+of the considered web service. The goal is to have quality web
+services in the community so it stays stable and no other web
+services would have incentives to deviate and leave the coalition
+$C$. Therefore, a basic method would be to check the core of the
+coalition $C$ considering all the current community members (all
+web services already residing within the community) and the new
+web service. This algorithm uses the \emph{Shapley value}
+distribution method as described in Equation \ref{eq:shapley} to
+distribute the gain of $v(C)$ among all the members and then
+checks if the \emph{Shapley value} payoff vector for this
+community having the characteristic function $v(C)$ is in the
+\emph{core}. In the \emph{Shapley value} payoff vector, the payoff
+for each web service $ws_i$ is calculated based on its marginal
+contribution $v(C \cup {i}) - v(C)$ over all the possible
+different permutations in which the coalition can be formed, which
+makes the payoff distribution fair. Because of going through all
+the possible permutations of subsets of $N$, the nature of the
+\emph{Shapley value} is combinatorial. This makes it impractical
+to use as the size of our coalitions grows. However, it is proven
+that in convex games, the \emph{Shapley value} lies in the core
+\cite{DBLP:conf/ijcai/GrecoMPS11, myerson1991game}. Thus, if the
+\emph{Core} is non-empty, the payoff vector is a member of the
+\emph{Core}. The following proposition is important to make our
+algorithm tractable.
 % so in our algorithm we check the core membership of this payoff vector.
@@
 
-\emph{Proposition: } A game with characterestic function v is convex \emph{if and only if for all S, T, and i where} $S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$, 
+\begin{Proposition}\label{proposition} A game with a characteristic function $v$
+is convex if and only if for all $S$, $T$, and $i$ where $S
+\subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in
+N$,
 %For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
@@
 \end{equation}
-
-\emph{Proof. ``only if''} direction, 
-\setlength{\abovedisplayshortskip}{2pt}
+\end{Proposition}
+\emph{Proof.}\\$~~~~$\textbf{1}. ``only if'' direction:\\
+%\setlength{\abovedisplayshortskip}{2pt}
+Assume:\\
+\vspace{-1cm}
 \begin{gather*}\label{convexsnowproof}
-v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
+v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\})
+- v(T)
 \\
@@
 \end{gather*}
-
-For prove of ``if'' direction, for all $A, B \subset N$,
-\setlength{\abovedisplayshortskip}{2pt}
+Consequently, the game is convex.
+
+$~~~~$\textbf{2}. ``if'' direction:\\
+Assume the game is convex. Thus, for all $A, B \subset N$, we
+have: \setlength{\abovedisplayshortskip}{2pt}
 \begin{gather*}
@@
 
-This implies in order to keep the characteristic function convex, new agents should have more marginal contribution as coalition size grows.
-
-Our algorithm works as follows.
-We have an established community with a master and some (slave) web services already residing in community.
-A web service would send a join request to the community.
-The ideal solution would be analyzing the \emph{core} or \emph{$\epsilon$-core} stability of group having this new member.
-However the normal core membership algorithms are computationally intractable.
-We exploit the equation \ref{eq:convex_snow} to check convexity of our characteristic function game having the new member.
-In the equation, we set $C$ to be our community members $(C)$ before having the new web service.
-We assign ${i}$ to the new web service, and then verify the equation for $S$, setting $ S = T / W $ where $W$ is all possible 1-member subsets of set $N$.
-We can relax the equation a bit by adding a constant epsilon to left side of equation.
-We call this method \emph{Depth-1 Convex-Checker} algorithm.
-If the equation is true for all $W$ we let the new web service join our community, since the web service will contribute good enough to make our new community stable.
-The run time complexity of this algorithm is $O(n)$ which is a great reduction from $O(2^n)$ checking all possible subsets of $N$.
-In our second method, we use the same algorithm however this time we set $W$ to be all possible subsets of size two and one of the community $C$.
-We call this method \emph{Depth-2 Convex-Checker} and its run time complexity is $O(n^2)$.
-It is possible to develop an anytime algorithm by continuing verifying this condition against all subsets of size 3 to $|N|$, and stop whenever we the algorithm is interrupted.
+As a direct consequence of this proposition, in order to keep the
+characteristic function convex, new web services should have more
+marginal contribution as the coalition size grows.
+
+Our algorithm works as follows. We have an established community
+with a master and some member web services already residing in the
+community. A web service would send a join request to the
+community. The ideal solution would be analyzing the \emph{core}
+or \emph{$\epsilon$-core} stability of the group having this new
+member. As the normal core membership algorithm is computationally
+intractable, we exploit Proposition \ref{proposition} and Equation
+\ref{eq:convex_snow} to check the convexity of our game having
+characteristic function where the new member is added. In the
+equation, we set $C$ to be our community members $(C)$ before
+having the new web service. We assign ${i}$ to the new web
+service, and then verify the equation for $S$, setting $ S = T /
+W1 $ where $W1$ is the set of all possible subsets of the set $N$
+having the size $1$. We can relax the equation a bit by adding a
+constant $\epsilon$ to the left side of the equation. We call this
+method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
+satisfied for all $W1$, we let the new web service join our
+community, since the web service will contribute positively enough
+to make our new community stable. Since only subsets of size $1$
+are checked, the following Proposition holds.
+
+\begin{Proposition}\label{complexity1}
+The run time complexity of Depth-1 Convex-Checker algorithm is
+$O(n)$.
+\end{Proposition}
+
+By this result, we obtain a significant reduction from $O(2^n)$,
+which is the complexity of checking all possible subsets of $N$.
+In our second method, we use the same algorithm, but this time we
+set $W2$ to be the set of all possible subsets of size two and one
+of the community $C$. We call this method \emph{Depth-2
+Convex-Checker} and its run time complexity is still
+linear:
+
+\begin{Proposition}\label{complexity1}
+The run time complexity of Depth-2 Convex-Checker algorithm is
+$O(n^2)$.
+\end{Proposition}
+
+It is possible to develop an anytime algorithm by continuing the
+verification of this condition against all subsets of size $3$,
+$4$, etc. until the algorithm gets interrupted.
 
@@
 
-In this scenario we consider multiple communities owned by multiple master web services each providing independent request pools.
-Identical to first scenario master web services form coalitions with web services.
-We use coalition structure formation methods to partition web services into non-empty disjoint coalition structures.
-As mentioned in section \ref{sec:coalition} these algorithms \cite{Sandholm1999209, DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11} try to solve key fundamental problems of what coalitions to form, and how to devide the payoffs from collabration.
+In this scenario, we consider multiple communities managed by
+multiple master web services, each of which is providing
+independent request pools (see Figure \ref{fig_sim2}). Identical
+to the first scenario, master web services form coalitions with
+web services. We use coalition structure formation methods to
+partition web services into non-empty disjoint coalition
+structures. As mentioned in Section \ref{sec:coalition}, the used
+algorithms \cite{Sandholm1999209,
+DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
+solve key fundamental problems of what coalitions to form, and how
+to divide the payoffs among the collaborators.
 
@@
 \caption{Web Services and Many Communities}
-\label{fig_sim}
+\label{fig_sim2}
 \end{figure}
 
-In coalition-formation games, formation of the coalitions is the most important aspect of the game.
-These solutions focus on maximizing social welfare.
-For any coalition structure $\pi$, let $v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$, which is called \emph{social welfare}.
-The solution concepts in this area deal with finding the maximum value for social welfare over all the possible coalition structures $\pi$.
-There are $centralized$ algorithms for this end, however these approaches are generally NP-complete.
-The reason is that number of all possible partitions of set $N$ grows exponentially with the number of players in $N$ (Bell number), and the centralized algorithms need to iterate through all these partitions.
+In coalition-formation games, formation of the coalitions is the
+most important aspect. The solutions focus on maximizing the
+social welfare. For any coalition structure $\pi$, let
+$v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$,
+which represents the \emph{social welfare}. The solution concepts
+in this area deal with finding the maximum value for the social
+welfare over all the possible coalition structures $\pi$. There
+are $centralized$ algorithms for this end, but these approaches
+are generally NP-complete. The reason is that the number of all
+possible partitions of the set $N$ grows exponentially with the
+number of players in $N$, and the centralized algorithms need to
+iterate through all these partitions.
 %These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity.
 However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}.
-In our application, we prefer a distributed algorithm where each community master and web service can be a decision maker and decide for its own good.
-The aim is to find less complex and distributed algorithms for forming coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
-The distributed merge-and-split algorithm in \cite{DBLP:journals/igtr/AptW09} suits our application very well.
-It keeps splitting and merging coalition to partitions which are preferred by all players inside those coalitions.
-
-This merge-and-split algorithm is designed to be adoptable for different applications.
-One major ingredient to be provider to this algorithm is a preference relation or well-defined orders proper for comparing collections of different coalition partitions of same set of players.
-Having two partition sets of players, namely $P = {P_1,...,P_k}$ and $Q = {Q_1,...N_l}$ one example would be to use the social welfare comarison $\sum^k_{i=1}v(P_i) > \sum^k_{i=1}v(N_l)$.
-For our scenario we used \emph{Pareto order} comparison which is an individual-value order appropriate for our self-interest agents (web services).
-In Pareto order, an allocation or partition $P$ is preferred over another $Q$ if at least one player improves its payoff in new allocation and all other players still maintain their payoff.
-($p_i \geq q_i$ with at least one element $p_i > q_i$).
-
-The valuation function $v(C)$ for this scenario is same as \emph{``Web Services and A Grand Community''} scenario, however in order to prevent master web services joining same community we set $v(C) = 0$, where C has none, or, two or more master web services as members.
-
-In this scenario, as new web services are discovered and get ready to join communities, our algorithm keeps merging and splitting partitions based on the preference function.
-The decision to merge or split is tied to the fact that all players must benefit, the new web services will merge with communities if $all$ players are able to improve their individual payoff, and some web services may split from old communities, if splitting does not decrease payoff of any web services of the community.
-According to \cite{DBLP:journals/corr/abs-cs-0605132} this sequence of merging and spliting will converge to a final partition, where players (web services) cannot improve their payoff.
-More details of this algorithm and analyses of generic solutions on coalition formation games are described in \cite{DBLP:journals/igtr/AptW09}.
-
-\subsection {Web Services collaborating independently}
+In our model, we propose using a distributed algorithm where each
+community master and web service can be a decision maker and
+decide for its own good. The aim is to find less complex and
+distributed algorithms for forming web services
+coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
+The distributed merge-and-split algorithm in
+\cite{DBLP:journals/igtr/AptW09} suits our application very well.
+It keeps splitting and merging coalitions to partitions which are
+preferred by all the players inside those coalitions.
+
+This merge-and-split algorithm is designed to be adaptable to
+different applications. One major ingredient to use such an
+algorithm is a preference relation or well-defined orders proper
+for comparing collections of different coalition partitions of the
+same set of players. Having two partition sets of players, namely
+$P = {P_1,...,P_k}$ and $Q = {Q_1,...Q_l}$, one example would be
+to use the social welfare comparison $\sum^k_{i=1}v(P_i) >
+\sum^l_{j=1}v(Q_j)$. For our scenario, we use \emph{Pareto order}
+comparison, which is an individual-value order appropriate for our
+self-interest web services. In the Pareto order, an allocation or
+partition $P$ is preferred over another $Q$ if at least one player
+improves its payoff in the new allocation and all the other
+players still maintain their payoff ($p_i \geq q_i$ with at least
+one element $p_i > q_i$).
+
+The valuation function $v(C)$ for this scenario is the same as
+\emph{``Web Services and One Community''} scenario. However, in
+order to prevent master web services joining the same community,
+we set $v(C) = 0$ when $C$ has either none, or more than one
+master web service as member.
+
+In this scenario, as new web services are discovered and get ready
+to join communities, our algorithm keeps merging and splitting
+partitions based on the preference function. The decision to merge
+or split is tied to the fact that all players must benefit. The
+new web services will merge with communities if $all$ the players
+are able to improve their individual payoff, and some web services
+may split from old communities, if splitting does not decrease the
+payoff of any web service of the community. According to
+\cite{DBLP:journals/corr/abs-cs-0605132}, this sequence of merging
+and splitting will converge to a final partition, where web
+services cannot improve their payoff. More details of this
+algorithm and analysis of generic solutions on coalition formation
+games are described in \cite{DBLP:journals/igtr/AptW09}.
+
+\textbf{Jamal: I stopped Here}
+
+\subsection {Web Services Collaborating Independently}
 
@@
 \caption{Web Services collaborating independently}
-\label{fig_sim}
+\label{fig_sim3}
 \end{figure}
@@
 As results illustrate clearly, our QoS aware method, forms better coalitions of web services improving performance and satisfaction for both web service and coalitions.
-
 % An example of a floating figure using the graphicx package.
@@
 \bibliographystyle{IEEEtran}
-\bibliography{bibi}
+\bibliography{Ehsan}
 % argument is your BibTeX string definitions and bibliography database(s)

### 2013-03-17 papers/coalition/coalition++.tex
Changes

--- 2013-03-16 papers/coalition/coalition.tex
@@
 In this scenario, we assume the existence of a typical community
-managed by its master web service and web services need to join it
-to be able to get requests from the master. The community master
-is characterized by a requests rate $(R_{M})$ from users. Each web
+managed by its master, and web services need to join it to be able
+to get requests from the master. The community master is
+characterized by a requests rate $(R_{M})$ from users. Each web
 service comes with a given QoS ($QoS_{ws}$) from which the
@@
 the average rate of tasks a web service can perform per time unit.
-Therefore, the master web service is providing tasks with the rate
-of $R_{ws}$ and web services perform tasks with average output
-quality of $QoS_{ws}$ and a throughput rate of $T_{ws}$. In this
-setting, we define the value of the coalition of the web services
-within a community as a function increasing in both $T_{ws}$ and
-$QoS_{ws}$ as follows:
+Thus, web services perform tasks with an average output quality of
+$QoS_{ws}$ and a throughput rate of $T_{ws}$. In this setting, we
+define the value of the coalition of the web services within a
+community as a function increasing in both $T_{ws}$ and $QoS_{ws}$
+as follows:
 \begin{equation*}
@@
 the possible permutations of subsets of $N$, the nature of the
-\emph{Shapley value} is combinatorial. This makes it impractical
+\emph{Shapley value} is combinatorial, which makes it impractical
 to use as the size of our coalitions grows. However, it is proven
@@
 
-As a direct consequence of this proposition, in order to keep the
-characteristic function convex, new web services should have more
-marginal contribution as the coalition size grows.
+Thus, in order to keep the characteristic function convex, new web
+services should have more marginal contribution as the coalition
+size grows.
 
@@
 
-\textbf{Jamal: I stopped Here}
-
 \subsection {Web Services Collaborating Independently}
 
-In this scenario, we do not consider pre-defined communities and master web services.
-Here web services are interested in forming coalitions to perform better and share benefits.
-We do not consider concept of master web services providing requests for others, each web service comes with its own request load which in this scenario we call it \emph{market share}.
-Therefore coalitions will form is web services working together can perform and gain more than working alone individually.
-The worth or value of coalitions of web services is different in this setting.
-We average the $quality$ for all metrics of web service $(Q^{m})$, multiply it by a weight where the importance or weigth of each metric is dependent on type of users and requests web services are dealing with.
-For each web service we multiply this by web service's market share $(MS_{ws})$ and the summation would be the characteristic or valuation of independent web service coalitions.
+In this scenario, there is no pre-defined community and web
+services are interested in forming new ones to perform better and
+share benefits (see Figure \ref{fig_sim3}). Consequently, there is
+no master web service providing requests for others, but each web
+service comes with its own request load called \emph{market
+share}. Communities can be formed because by working together web
+services can expect to gain more than working individually. The
+worth or value of a coalition of web services is different in this
+setting. Let $metrics$ be the set of quality metrics, we average
+the values $Q^m_{ws}$ for all quality metrics ($m \in metrics$)
+for each web service $ws$, multiply it by a weight reflecting the
+importance of each metric for each web service ($w^m_{ws}$) (Note
+that $ \sum_{m}{w^m_{ws}} = 1 $). For each web service, we
+multiply this weighted average by web service's market share
+$(\mu_{ws})$ and the summation over all the web services of the
+community to be established would be the characteristic or
+valuation function. This function has the property to be
+increasing in the market share and QoS.
 
 \begin{equation}
-v(C) = \sum_{ws \in C}{ \Big( \frac{\sum_{m=metrics}{Q^m_{ws} \times w_{m}}}{|metrics|} \Big) \times MS_{ws} }
+v(C) = \sum_{ws \in C}{ \Big( \frac{\sum_{m \in metrics}{Q^m_{ws}
+\times w^m_{ws}}}{|metrics|} \Big) \times \mu_{ws} }
 \end{equation}
@@
 If it is more than 1, is means they increase performance by working together and they are \emph{super additive}, otherwise it depicts they would perform better in linear sense if they worked alone.
-$w_m$ is the weight of important for a \emph{QoS} metric, it gives the community the flexibility to emphasize or neglect a specific \emph{QoS} parameter.
-Note that $ \sum_{m}{w_m} = 1 $.
-In this scenario we have no master web services, we assume they either dynamically vote for one, or collaborate and agree on decisions and distribute task in round robin or fair fashion.
-Here, we utilized the same merge-and-split algorithm which we applied for the \emph{``Web Services and Many Communities''} scenario, to find stable coalitions of web serivces.
+As there is no pre-defined master web services in this scenario,
+we assume that the members of each coalition either dynamically
+vote for one, or collaborate and distribute tasks in round robin
+or fair fashion. To form stable coalitions, we use the same
+merge-and-split algorithm we applied for the \emph{``Web Services
+and Many Communities''} scenario.
 
@@
 
-\section{Experimental Results}\label{s:resutls}
-
-In this section, we discuss the experiments we performed for our scenarios to validate applicability and performance of our proposed methods in realistic environments.
-We created a pool of web services and populated most of their \emph{QoS} parameters from a real world web service dataset \cite{DBLP:conf/smc/Al-MasriM09a}.
-We programmed the simulations using Java and executed the simulations on a Intel Xeon X3450 machine with 4GBs of memory.
-For other parameters missing from the dataset, we used normal random distribution with parameters that make most sense in real world examples.
-
-We analyze the most important performance result the communities should perform, quality and quantity of tasks successfully performed by the communities.
-This is the most important criteria for user satisfaction.
-We initiate the community with few web services, then let rejecting and accepting of random web services go for a short number of iterations, after that we start task distribution for the communities and let them allocate tasks for web services.
-Then we measure the average output performance of tasks in communities following different methods.
+\section{Experimental Results and Analysis}\label{s:resutls}
+
+In this section, we discuss the experiments we performed for our
+scenarios to validate the applicability and performance of our
+proposed methods in realistic environments. We created a pool of
+web services and populated most of their \emph{QoS} parameters
+from a real world web service dataset
+\cite{DBLP:conf/smc/Al-MasriM09a}. We implemented the simulations
+using Java and executed the simulations on an Intel Xeon X3450
+machine with 4GBs of memory. For other parameters missing from the
+dataset, we used normal random distribution with parameters
+estimated using the method of maximum likelihood.
+
+One of the key criteria reflecting the performance of web service
+coalitions is the user satisfaction. User satisfaction can be
+measured in terms of quality and quantity of requests (or tasks)
+successfully answered by the communities. We initiate the
+communities with few web services, then let rejecting and
+accepting random web services go for a short number of iterations.
+After that, we start the request distribution for the communities
+and let them allocate requests among member web services.
+Thereafter, we measure the average output performance of tasks in
+communities following different methods.
 
@@
 \includegraphics[width=3in]{task_qos_opt.eps}
-\caption{Part (a): Cumulative number of tasks succesfully done. Part
-(b): Average QoS of tasks performed.} \label{performanceall}
+\caption{Part (a): Cumulative number of requests successfully
+done. Part (b): Average QoS of requests performed.}
+\label{performanceall}
 \end{figure}
 
-Figure \ref{performanceall} depicts the results of optimal \emph{$\epsilon$-core}, by assigning $\epsilon$ to 15\% of total community worth, $\epsilon = 0.15 \times v(C)$, allowing subsets of coalition to gain maximum 15\% of $v(C)$, \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, \emph{3-Way Satisfactory}\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative}\cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods in \emph{one grand community with many web services} scenario.
-In the \emph{optimal $\epsilon$-core} method we capped the coalition size to 25 web services, since anything more than that would require analysis with time complexity of $O(2^{n-1})$, making it impractical to run in our simulations.
-In other methods there were no cap on size of the community and we had communities of size 60 web services at some points.
-The results show \emph{depth-2 and 1 convex checker} methods are performing better compared to other methods and their performance is close to optimal \emph{$\epsilon$-core} method.
+Figure \ref{performanceall} depicts the results of optimal
+\emph{$\epsilon$-core}, \emph{Depth-1 Convex-Checker},
+\emph{Depth-2 Convex-Checker}, \emph{3-Way Satisfaction}
+\cite{DBLP:conf/IEEEscc/LimTMB12}, and \emph{2 Player
+Non-Cooperative} \cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods
+in \emph{one grand community with many web services} scenario. For
+\emph{$\epsilon$-core}, we assign $\epsilon$ to 15\% of total
+community worth, $\epsilon = 0.15 \times v(C)$, which allows
+subsets of the coalition to gain maximum 15\% of $v(C)$. In the
+\emph{optimal $\epsilon$-core} method, we capped the coalition
+size to 25 web services, since anything more than that would
+require analysis with time complexity of $O(2^{n-1})$, making it
+impractical to run in our simulations. In the other methods, there
+were no cap on size of the community and we had communities of
+size 60 web services at some points. The results show that our
+\emph{depth-2 convex checker} method is performing better compared
+to the other methods and its performance is close to optimal
+\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
+and \emph{3-Way Satisfaction} are also performing well.
 
@@
 
-As mentioned in section \ref{s:preliminaries}, the concept of \emph{core}, assumes no coalition of players can gain anything by deviating which is a fairly strong requirement, that is why the notion of \emph{$\epsilon$-core} was introduced.
-Least-Core $e(G)$ of a game $G$, is the minimum amount of $\epsilon$ in which the core is not empty.
-We evaluated the least-core value using our valuation function and our set of web services.
-We pick random number of web services from our dataset and formed around 10,000 random coalitions consisting of 3 to 26 web services.
-We choose 26 as maximum number of members in our grand coalition since it is computationally very complex for bigger coalitions to compute \emph{$\epsilon$-core}.
-We set $\epsilon$ to a ratio of total payoff of coalition $v(C)$ between 0 and 1.
-The results in figure \ref{f_leastcore} illustrates, almost 10\% of our random web service coalitions have non-empty \emph{core} solution and \emph{$\epsilon$-core} solution is \emph{always} non-empty when we let agents gain 30\% (of $v(C)$) more, by deviating.
-
-One of the properties of coalition structure formation algorithms in our scenario is that they partition web services with low throughput rate usually join coalitions with less request rate.
-Since the characteristic function $v(C)$ and  the fair payoff vector of Shapley value is proportional to web services' contribution, the web services with small contribution will get paid much less in communities having web services with high throughput.
-On the other hand, according to valuation function $v(C)$ web services with high throughput will not contribute well to communities with low amount of user requests.
-The strong web services are much more likely to deviate weak coalitions, joining a stronger coalition, making the initial coalition unstable.
+As mentioned in Section \ref{s:preliminaries}, the concept of
+\emph{core}, assumes no coalition of players can gain anything by
+deviating, which is a fairly strong requirement, and that is why
+the notion of \emph{$\epsilon$-core} was introduced. Least-Core
+$e(G)$ of a game $G$, is the minimum amount of $\epsilon$ so that
+the core is not empty. We evaluated the least-core value using our
+valuation function and our set of web services. We picked random
+number of web services from the dataset and formed around 10,000
+random coalitions consisting of 3 to 26 web services. We choose 26
+as the maximum number of members in our grand coalition since it
+is computationally very complex for bigger coalitions to compute
+\emph{$\epsilon$-core}. We set $\epsilon$ to a ratio of total
+payoff of coalition $v(C)$ between 0 and 1. The results in Figure
+\ref{f_leastcore} illustrates that almost 10\% of our random web
+service coalitions have non-empty \emph{core} solution and
+\emph{$\epsilon$-core} solution is \emph{always} non-empty when we
+let agents gain 30\% more of $v(C)$ by deviating.
+
+One of the properties of coalition structure formation algorithms
+in our third scenario is that they partition web services with low
+throughput rate so that they usually join coalitions with less
+request rate. Since the characteristic function $v(C)$ and the
+fair Shapely payoff vector is proportional to web services'
+contribution, the web services with small contribution will get
+paid much less in communities having web services with high
+throughput. On the other hand, according to the valuation function
+$v(C)$, web services with high throughput will not contribute well
+to communities with low amount of user requests (low market
+share). The strong web services are likely to deviate from weak
+coalitions, joining a stronger one, which makes the initial
+coalition unstable.
 
@@
 
-In figure \ref{performancemany} we compare our \emph{Web Services and many Communities} scenario with a method which ignores QoS parameters and forms coalitions and allow web services to join only if they have enough requests for them in other words web services can join a community when request rate is less that throughput of all web services inside community ignoring QoS parameters.
-We name this method \emph{Random Formation} and use it as our benchmark for our QoS aware coalition formation process.
-As results illustrate clearly, our QoS aware method, forms better coalitions of web services improving performance and satisfaction for both web service and coalitions.
+In Figure \ref{performancemany}, we compare our \emph{Web Services
+and many Communities} scenario with a method which ignores QoS
+parameters and forms coalitions by allowing web services to join
+only if they have enough requests for themselves. In other words,
+web services can join a community when the request rate is less
+than the throughput of all the member web services. We name this
+method \emph{Random Formation} and use it as a benchmark for our
+QoS-aware coalition formation process. As the results illustrate,
+our method forms better coalitions of web services improving
+performance and satisfaction for both web services and coalitions.
 % An example of a floating figure using the graphicx package.
@@
 
-In this paper, we proposed a cooperative game theory based model for aggregation of web services within communities.
-The goal of our services is to maximize efficiency of performing tasks by collaborating and forming stable communities.
-Our method considers stability and fairness for all web services within a community and offers an applicable mechanism for membership requests and selection of web services.
-The goal is to increase revenue by improving user satisfaction, which comes from the ability to perform tasks with higher quality and quantity.
-Simulation results show that our, polynomial in complexity, approximation algorithms provide web services and community owners with applicable and near-optimal decision making mechanisms.
-
-As future work, we would like to perform more analytical and theoretical work on the convexity condition for the characteristic function on web service applications.
-It is possible to work on compact or succinct representation of our service model (i.e.
-a graph representation) to reduce the input complexity and solution concepts of cooperative game and core membership checking algorithms.
-From web service aspect, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks.
-Also bargaining theory from cooperating game theory concepts can be used in our scenario.
-The web services would stay and join communities as they wish, however, they would resolve the instability and unfairness issues by side payments.
+In this paper, we proposed a cooperative game theory-based model
+for the aggregation of web services within communities. The goal
+of our services is to maximize efficiency by collaborating and
+forming stable coalitions. Our method considers stability and
+fairness for all web services within a community and offers an
+applicable mechanism for membership requests and selection of web
+services. The ultimate goal is to increase revenue by improving
+user satisfaction, which comes from the ability to perform more
+tasks with high quality. Simulation results show that our,
+polynomial in complexity, approximation algorithms provide web
+services and community owners with applicable and near-optimal
+decision making mechanisms.
+
+As future work, we would like to perform more analytical and
+theoretical analysis on the convexity condition for the
+characteristic function on web service applications. It is
+possible to work on compact or succinct representation of our
+service model (i.e. a graph representation) to reduce the input
+complexity and solution concepts of cooperative game and core
+membership checking algorithms. From web service perspective, the
+work can be extended to consider web service compositions where a
+group of web services having different set of skills cooperate to
+perform composite tasks. Also bargaining theory from cooperating
+game theory concepts can be used to help web services resolve the
+instability and unfairness issues by side payments.
 

### 2013-03-22 papers/coalition/fixes-extension-ideas.tex
Changes

\documentclass{article}

\usepackage{amsfonts}
\usepackage{amssymb}

\begin{document}

\section{Coalition}

\subsection{Fixes}

This domain can be modeled as a cooperative game.

Add that weights equal in expirement section.

However, unlike [1] we study...

The convexity prove has mistakes.

%\bibliographystyle{plain}
%\bibliography{ehsan}

\end{document}

### 2013-04-07 papers/coalition2-journal-extension/coalition_ext.tex
Changes

--- 2013-03-17 papers/coalition/coalition++.tex
@@
 \\
-\rightarrow v(A) + V(B) \leq v(A \cup B) + v(A \cap B)
+\rightarrow v(A) + v(B) \leq v(A \cup B) + v(A \cap B)
 \end{gather*}
@@
 
-By setting $S \cup \left\{i\right\} = A$ and $R = B$ where $S \subseteq R$:
+By setting $S \cup \left\{i\right\} = A$ and $T = B$ where $S \subseteq T$:
 \setlength{\abovedisplayshortskip}{2pt}
@@
 \emph{optimal $\epsilon$-core} method, we capped the coalition
-size to 25 web services, since anything more than that would
-require analysis with time complexity of $O(2^{n-1})$, making it
+size to 25 web services, since the method is computationally 
+intractable and anything more than that would make it
 impractical to run in our simulations. In the other methods, there

### 2013-04-22 papers/coalition/SCC2013_WSCoalition.tex
Changes

--- 2013-03-17 papers/coalition/coalition++.tex
@@
 theoretical analysis on the convexity condition for the
-characteristic function on web service applications. It is
-possible to work on compact or succinct representation of our
-service model (i.e. a graph representation) to reduce the input
-complexity and solution concepts of cooperative game and core
-membership checking algorithms. From web service perspective, the
+characteristic function on web service applications. From web service perspective, the
 work can be extended to consider web service compositions where a

### 2013-04-22 papers/coalition/SCC2013_WSCoalition.tex
Changes

@@
 partitions based on the preference function. The decision to merge
-or split is tied to the fact that all players must benefit. The
+or split is based on the fact that all players must benefit. The
 new web services will merge with communities if $all$ the players
@@
 $e(G)$ of a game $G$, is the minimum amount of $\epsilon$ so that
-the core is not empty. We evaluated the least-core value using our
-valuation function and our set of web services. We picked random
+the core is not empty. We evaluated the non-emptiness of \emph{$\epsilon$-core} set using the
+valuation function and a set of web services. We picked random
 number of web services from the dataset and formed around 10,000
 random coalitions consisting of 3 to 26 web services. We choose 26
-as the maximum number of members in our grand coalition since it
-is computationally very complex for bigger coalitions to compute
-\emph{$\epsilon$-core}. We set $\epsilon$ to a ratio of total
-payoff of coalition $v(C)$ between 0 and 1. The results in Figure
+as the maximum number of members in our coalition since it
+is computationally very complex for larger coalitions to verify whether 
+\emph{$\epsilon$-core} set is empty or not.
+Also instead of considering $\epsilon$ amount of constant deviation in \emph{$\epsilon$-core} definition (Equation \ref{eq:core}), we similarly defined \emph{relative $\epsilon$-core} concept where no coalition would benefit more than \emph{$\epsilon$.v(C)} by deviating.
+We set $\epsilon$ between 0 and 1 and verify the \emph{relative $\epsilon$-core} set non emptiness.
+The results in Figure
 \ref{f_leastcore} illustrates that almost 10\% of our random web
@@
 \emph{$\epsilon$-core} solution is \emph{always} non-empty when we
-let agents gain 30\% more of $v(C)$ by deviating.
+let agents gain only 30\% more of $v(C)$ by deviating.
 
@@
 As future work, we would like to perform more analytical and
-theoretical analysis on the convexity condition for the
-characteristic function on web service applications. From web service perspective, the
+theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the
+characteristic function in web service applications. From web service perspective, the
 work can be extended to consider web service compositions where a

### 2013-04-22 papers/coalition/SCC2013_WSCoalition.tex
Changes

@@
 When dealing with cooperative games, two issues need to be
-addressed:\\ 1. What coalition to form (Canonical games)? \\
-2. How to reward each member when a task is completed
-(Coalition-formation games)?\\
+addressed:\\ 1. What coalitions to form? \\
+2. How to reward each member when a task is completed?\\
 %
@@
 \emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
-and \emph{3-Way Satisfaction} are also performing well.
+and the \emph{3-Way Satisfaction} method, are also performing well.
 
@@
 \emph{$\epsilon$-core} set is empty or not.
-Also instead of considering $\epsilon$ amount of constant deviation in \emph{$\epsilon$-core} definition (Equation \ref{eq:core}), we similarly defined \emph{relative $\epsilon$-core} concept where no coalition would benefit more than \emph{$\epsilon$.v(C)} by deviating.
-We set $\epsilon$ between 0 and 1 and verify the \emph{relative $\epsilon$-core} set non emptiness.
+Also instead of considering $\epsilon$ amount of constant deviation in \emph{$\epsilon$-core} definition (Equation \ref{eq:core}), we similarly defined \emph{relative $\epsilon$-core} concept where no coalition would benefit more than \emph{$\epsilon$ $\times$ v(C)} by deviating.
+We set $\epsilon$ between 0 and 1 and verify the \emph{relative $\epsilon$-core} set non-emptiness.
 The results in Figure

### 2013-04-26 papers/coalition/SCC2013_WSCoalition.tex
Changes

@@
 already exist. Moreover, we analyze the scenarios where
-communities are not established yet. The ultimate objective is to
+communities are not established yet and web services can form multiple communities. The ultimate objective is to
 develop a mechanism for web services to form stable groups
@@
 \begin{IEEEkeywords}
-Web services; Cooperative game thoery; Community of services;
+Web services; Cooperative game theory; Community of services;
 

### 2013-05-11 papers/coalition-journal-extension/coalition_journal.tex
Added new journal template

--- 2013-04-26 papers/coalition/SCC2013_WSCoalition.tex
@@
-%% bare_conf.tex
+%% bare_jrnl_compsoc.tex
 %% V1.3
@@
 %% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
+%% (requires IEEEtran.cls version 1.7 or later) with an IEEE Computer
+%% Society journal paper.
 %%
@@
 %
-\documentclass[10pt, conference, compsocconf]{IEEEtran}
-% Add the compsocconf option for Computer Society conferences.
+% The Computer Society usually requires 10pt for submissions.
+%
+\documentclass[10pt,journal,cspaper,compsoc]{IEEEtran}
 %
@@
 % manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
+% \documentclass[12pt,journal,compsoc]{../sty/IEEEtran}
 
@@
 %
-%\usepackage{cite}
+\ifCLASSOPTIONcompsoc
+  % IEEE Computer Society needs nocompress option
+  % requires cite.sty v4.0 or later (November 2003)
+  % \usepackage[nocompress]{cite}
+\else
+  % normal IEEE
+  % \usepackage{cite}
+\fi
 % cite.sty was written by Donald Arseneau
@@
 % The documentation is contained in the cite.sty file itself.
+%
+% Note that some packages require special options to format as the Computer
+% Society requires. In particular, Computer Society  papers do not use
+% compressed citation ranges as is done in typical IEEE papers
+% (e.g., [1]-[4]). Instead, they list every citation separately in order
+% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
+% package with the nocompress option which is supported by cite.sty v4.0
+% and later. Note also the use of a CLASSOPTION conditional provided by
+% IEEEtran.cls V1.7 and later.
 
@@
 \fi
-
 % graphicx was written by David Carlisle and Sebastian Rahtz. It is
@@
 
+\usepackage{amsfonts}
+\usepackage{amssymb,amsmath}
+
 % *** MATH PACKAGES ***
 %
-\usepackage[cmex10]{amsmath}
+%\usepackage[cmex10]{amsmath}
 % A popular package from the American Mathematical Society that provides
@@
 % *** SUBFIGURE PACKAGES ***
+%\ifCLASSOPTIONcompsoc
+%\usepackage[tight,normalsize,sf,SF]{subfigure}
+%\else
 %\usepackage[tight,footnotesize]{subfigure}
+%\fi
 % subfigure.sty was written by Steven Douglas Cochran. This package makes it
@@
 % work, it is a good idea to load it with the tight package option to reduce
-% the amount of white space around the subfigures. subfigure.sty is already
+% the amount of white space around the subfigures. Computer Society papers
+% use a larger font and \sffamily font for their captions, hence the
+% additional options needed under compsoc mode. subfigure.sty is already
 % installed on most LaTeX systems. The latest version and documentation can
@@
 
-%\usepackage[caption=false]{caption}
-%\usepackage[font=footnotesize]{subfig}
+%\ifCLASSOPTIONcompsoc
+%  \usepackage[caption=false]{caption}
+%  \usepackage[font=normalsize,labelfont=sf,textfont=sf]{subfig}
+%\else
+%  \usepackage[caption=false]{caption}
+%  \usepackage[font=footnotesize]{subfig}
+%\fi
 % subfig.sty, also written by Steven Douglas Cochran, is the modern
@@
 % the caption=false option directly:
-%\usepackage[caption=false,font=footnotesize]{subfig}
+%\ifCLASSOPTIONcompsoc
+%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+%\else
+%  \usepackage[caption=false,font=footnotesize]{subfig}
+%\fi
 %
@@
 
+%\ifCLASSOPTIONcaptionsoff
+%  \usepackage[nomarkers]{endfloat}
+% \let\MYoriglatexcaption\caption
+% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
+%\fi
+% endfloat.sty was written by James Darrell McCauley and Jeff Goldberg.
+% This package may be useful when used in conjunction with IEEEtran.cls'
+% captionsoff option. Some IEEE journals/societies require that submissions
+% have lists of figures/tables at the end of the paper and that
+% figures/tables without any captions are placed on a page by themselves at
+% the end of the document. If needed, the draftcls IEEEtran class option or
+% \CLASSINPUTbaselinestretch interface can be used to increase the line
+% spacing as well. Be sure and use the nomarkers option of endfloat to
+% prevent endfloat from "marking" where the figures would have been placed
+% in the text. The two hack lines of code above are a slight modification of
+% that suggested by in the endfloat docs (section 8.3.1) to ensure that
+% the full captions always appear in the list of figures/tables - even if
+% the user used the short optional argument of \caption[]{}.
+% IEEE papers do not typically make use of \caption[]'s optional argument,
+% so this should not be an issue. A similar trick can be used to disable
+% captions of packages such as subfig.sty that lack options to turn off
+% the subcaptions:
+% For subfig.sty:
+% \let\MYorigsubfloat\subfloat
+% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
+% For subfigure.sty:
+% \let\MYorigsubfigure\subfigure
+% \renewcommand{\subfigure}[2][\relax]{\MYorigsubfigure[]{#2}}
+% However, the above trick will not work if both optional arguments of
+% the \subfloat/subfig command are used. Furthermore, there needs to be a
+% description of each subfigure *somewhere* and endfloat does not add
+% subfigure captions to its list of figures. Thus, the best approach is to
+% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
+% and instead reference/explain all the subfigures within the main caption.
+% The latest version of endfloat.sty and its documentation can obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
+%
+% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
+% later in the document, say, to conditionally put the References on a 
+% page by themselves.
+
 % *** PDF, URL AND HYPERLINK PACKAGES ***
@@
 
-\usepackage{amssymb}
-\usepackage{amsthm}
-\pagestyle{plain}
-\theoremstyle{plain}
-\newtheorem{thm}{Theorem}% reset theorem numbering for each chapter
-\newtheorem{Proposition}{Proposition}
-\theoremstyle{definition}
-\newtheorem{defn}[thm]{Definition} % definition numbers are dependent on theorem numbers
-\newtheorem{exmp}[thm]{Example} % same for example numbers
 % *** Do not adjust lengths that control margins, column widths, etc. ***
@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Efficient Coalition Formation for Web Services}
-
-% author names and affiliations
-% use a multiple column layout for up to two different
-% affiliations
-
-\author{\IEEEauthorblockN{Ehsan Khosrowshahi Asl, Jamal Bentahar}
-\IEEEauthorblockA{Faculty of Engineeing and Computer Science\\
-Concordia University\\
-Montreal, Canada\\
-e\_khosr@encs.concordia.ca, bentahar@ciise.concordia.ca}
-\and
-\IEEEauthorblockN{Hadi Otrok, Rabeb Mizouni}
-\IEEEauthorblockA{Department of Electrical and Computer Engineering\\
-Khalifa University of Science, Technology and Research\\
-Abu Dhabi, UAE\\
-hadi.otrak, rabeb.mizouni@kustar:ac:ae}
-}
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-%
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3},
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
-\maketitle
-
+\title{Efficient Coalition Formation \\ for Web Services}
+%
+%
+% author names and IEEE memberships
+% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
+% a structure at a ~ so this keeps an author's name from being broken across
+% two lines.
+% use \thanks{} to gain access to the first footnote area
+% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
+% was not built to handle multiple paragraphs
+%
+%
+%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
+% lists the Computer Society journals use for "first footnote" author
+% affiliations. Use \IEEEcompsocthanksitem which works much like \item
+% for each affiliation group. When not in compsoc mode,
+% \IEEEcompsocitemizethanks becomes like \thanks and
+% \IEEEcompsocthanksitem becomes a line break with idention. This
+% facilitates dual compilation, although admittedly the differences in the
+% desired content of \author between the different types of papers makes a
+% one-size-fits-all approach a daunting prospect. For instance, compsoc 
+% journal papers have the author affiliations above the "Manuscript
+% received ..."  text while in non-compsoc journals this is reversed. Sigh.
+
+\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
+        John~Doe,~\IEEEmembership{Fellow,~OSA,}
+        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
+\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell is with the Department
+of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
+GA, 30332.\protect\\
+% note need leading \protect in front of \\ to get a newline within \thanks as
+% \\ is fragile and will error, could use \hfil\break instead.
+E-mail: see http://www.michaelshell.org/contact.html
+\IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
+\thanks{}}
+
+% note the % following the last \IEEEmembership and also \thanks - 
+% these prevent an unwanted space from occurring between the last author name
+% and the end of the author line. i.e., if you had this:
+% 
+% \author{....lastname \thanks{...} \thanks{...} }
+%                     ^------------^------------^----Do not want these spaces!
+%
+% a space would be appended to the last name and could cause every name on that
+% line to be shifted left slightly. This is one of those "LaTeX things". For
+% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
+% "AB" then you have to do: "\textbf{A}\textbf{B}"
+% \thanks is no different in this regard, so shield the last } of each \thanks
+% that ends a line with a % and do not let a space in before the next \thanks.
+% Spaces after \IEEEmembership other than the last one are OK (and needed) as
+% you are supposed to have spaces between the names. For what it is worth,
+% this is a minor point as most people would not even notice if the said evil
+% space somehow managed to creep in.
+
+% The paper headers
+\markboth{Journal of \LaTeX\ Class Files,~Vol.~6, No.~1, January~2007}%
+{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
+% The only time the second header will appear is for the odd numbered pages
+% after the title page when using the twoside option.
+% 
+% *** Note that you probably will NOT want to include the author's ***
+% *** name in the headers of peer review papers.                   ***
+% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
+% you desire.
+
+% The publisher's ID mark at the bottom of the page is less important with
+% Computer Society journal papers as those publications place the marks
+% outside of the main text columns and, therefore, unlike regular IEEE
+% journals, the available text space is not reduced by their presence.
+% If you want to put a publisher's ID mark on the page you can do it like
+% this:
+%\IEEEpubid{0000--0000/00\$00.00~\copyright~2007 IEEE}
+% or like this to get the Computer Society new two part style.
+%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2007 IEEE}%
+%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
+% Remember, if you use this you must call \IEEEpubidadjcol in the second
+% column for its text to clear the IEEEpubid mark (Computer Society jorunal
+% papers don't need this extra clearance.)
+
+% for Computer Society papers, we must declare the abstract and index terms
+% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
+% command as these need to go into the title area created by \maketitle.
+\IEEEcompsoctitleabstractindextext{%
 \begin{abstract}
-
+%\boldmath
 Web services are loosely-coupled business applications willing to
@@
 making mechanisms.
-
 \end{abstract}
-
-\begin{IEEEkeywords}
+% IEEEtran.cls defaults to using nonbold math in the Abstract.
+% This preserves the distinction between vectors and scalars. However,
+% if the journal you are submitting to favors bold math in the abstract,
+% then you can use LaTeX's standard command \boldmath at the very start
+% of the abstract to achieve this. Many IEEE journals frown on math
+% in the abstract anyway. In particular, the Computer Society does
+% not want either math or citations to appear in the abstract.
+
+% Note that keywords are not normally used for peer review papers.
+\begin{keywords}
 Web services; Cooperative game theory; Community of services;
-
-\end{IEEEkeywords}
+\end{keywords}}
+
+% make the title area
+\maketitle
+
+% To allow for easy dual compilation without having to reenter the
+% abstract/keywords data, the \IEEEcompsoctitleabstractindextext text will
+% not be used in maketitle, but will appear (i.e., to be "transported")
+% here as \IEEEdisplaynotcompsoctitleabstractindextext when compsoc mode
+% is not selected <OR> if conference mode is selected - because compsoc
+% conference papers position the abstract like regular (non-compsoc)
+% papers do!
+\IEEEdisplaynotcompsoctitleabstractindextext
+% \IEEEdisplaynotcompsoctitleabstractindextext has no effect when using
+% compsoc under a non-conference mode.
 
@@
 
-\section{Introduction and Related Work}
-
-Over the past years, online services have become part of many
+\section{Introduction}
+
+\IEEEPARstart{O}{ver} the past years, online services have become part of many
 scalable business applications. The increasing reliance on
@@
 
-%In prevoius works \cite{Chun02user-centricperformance, mcknight00a, DBLP:journals/internet/BenatallahSD03, Khosravifar:2009:AIR:1586636.1586906, Rosario:2008:PQS:1512146.1512290}
-
-%TODO Problems of \cite {DBLP:conf/IEEEscc/LimTMB12} having to cop and optimizing for with all weak web services reduces the optimal result\\
-
-%Some random text:
-%A Web service is an interface that describes a collection of operations that are network-accessible through standardized XML messaging.
-A Web service performs a specific task or a set of tasks.A Web service is described using a standard, formal XML notation, called its service description, that provides all of the details necessary to interact with the service, including message formats (that detail the operations), transport protocols, and location.
-Web service descriptions are expressed in WSDL.
-%
-%Web services can become untrustworthy for four reasons: unfulfilled requirements,malicious acts and code changes, erratic Internet behaviors or resource scarcity that result in unacceptable delays, and the poor interoperation of selected services.
-%
-%A Web service is an independent service component that aims to serve a variety of needs; it is not a single specific application.
-When the selected Web service component does not thoroughly fulfill its target need, the service becomes untrustworthy.
-Testing a service to determine that it fulfills all requirements is tricky because testing must verify the satisfaction of both functional and nonfunctional requirements.
-The nonfunctional requirements (reliability, availability, survivability, interoperability, and a host of other attributes) decide the service quality and require individual testing.
-Because the user can invoke a Web service only over the Internet, the challenge is how to test for all possible use scenarios.How can testing determine that the service operates effectively and efficiently for a specific application and environment?
+% Computer Society journal papers do something a tad strange with the very
+% first section heading (almost always called "Introduction"). They place it
+% ABOVE the main text! IEEEtran.cls currently does not do this for you.
+% However, You can achieve this effect by making LaTeX jump through some
+% hoops via something like:
+%
+%\ifCLASSOPTIONcompsoc
+%  \noindent\raisebox{2\baselineskip}[0pt][0pt]%
+%  {\parbox{\columnwidth}{\section{Introduction}\label{sec:introduction}%
+%  \global\everypar=\everypar}}%
+%  \vspace{-1\baselineskip}\vspace{-\parskip}\par
+%\else
+%  \section{Introduction}\label{sec:introduction}\par
+%\fi
+%
+% Admittedly, this is a hack and may well be fragile, but seems to do the
+% trick for me. Note the need to keep any \label that may be used right
+% after \section in the above as the hack puts \section within a raised box.
+
+% The very first letter is a 2 line initial drop letter followed
+% by the rest of the first word in caps (small caps for compsoc).
+% 
+% form to use if the first word consists of a single letter:
+% \IEEEPARstart{A}{demo} file is ....
+% 
+% form to use if you need the single drop letter followed by
+% normal text (unknown if ever used by IEEE):
+% \IEEEPARstart{A}{}demo file is ....
+% 
+% Some journals put the first two words in caps:
+% \IEEEPARstart{T}{his demo} file is ....
+% 
+% Here we have the typical use of a "T" for an initial drop letter
+% and "HIS" in caps to complete the first word.
+%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
+%for IEEE Computer Society journal papers produced under \LaTeX\ using
+%IEEEtran.cls version 1.7 and later.
+% You must have at least 2 lines in the paragraph with the drop letter
+% (should never be an issue)
+%I wish you the best of success.
+
+%\hfill mds
+
+%\hfill January 11, 2007
 
@@
 \hline\hline
-$Availability$ & Probability of being available during a time frame \\
-$Reliability$ & Probability of successfully handling requests \\
-&during a timeframe\\
+$Availability$ & Probability of being available during \\
+&a time frame \\
+$Reliability$ & Probability of successfully handling \\
+&requests during a timeframe\\
 $Successability$ & Rate of successfully handled requests \\
@@
 $Regulatory$ & Compliance with standards, law and rules\\
-$Security$ & Quality of confidentiality and non-repudiation\\
+$Security$ & Quality of confidentiality \\ 
+&and non-repudiation\\
 \hline
@@
 a coalitional game $(N, v)$ if and only if:
-\begin{equation}\label{eq:core}
+\begin{equation}\label{eq:core3}
 \forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S)
@@
 
-\begin{equation}\label{eq:core}
+\begin{equation}\label{eq:core2}
 \forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
@@
 
-\begin{Proposition}\label{proposition} A game with a characteristic function $v$
+\newtheorem{theorem}{Proposition}
+%\begin{theorem}[Einstein-Podolsky-Rosenberg]
+\begin{theorem}
+A game with a characteristic function $v$
 is convex if and only if for all $S$, $T$, and $i$ where $S
@@
 \end{equation}
-\end{Proposition}
-\emph{Proof.}\\$~~~~$\textbf{1}. ``only if'' direction:\\
+\end{theorem}
+
+%\begin{Proposition}\label{proposition} A game with a characteristic function $v$
+%is convex if and only if for all $S$, $T$, and $i$ where $S
+%\subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in
+%N$,
+%For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
+%\begin{equation}\label{eq:convex_snow}
+%v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
+%\end{equation}
+%\end{Proposition}
+
+\begin{proof} 
+We first prove the ``only if'' direction:
+%\\$~~~~$\textbf{1}. ``only if'' direction:\\
+\\$~~~~$\ \textbf{1}. ``only if'' direction:\\
 %\setlength{\abovedisplayshortskip}{2pt}
 Assume:\\
-\vspace{-1cm}
+\vspace{-0.5cm}
 \begin{gather*}\label{convexsnowproof}
@@
 \\
-\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq v((S \cup \left\{i\right\}) \cup T) + v((S \cup \left\{i\right\}) \cap T)
+\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq 
+\\
+v((S \cup \left\{i\right\}) \cup T) + v((S \cup \left\{i\right\}) \cap T)
 \\
@@
 
-$~~~~$\textbf{2}. ``if'' direction:\\
+\textbf{2}. ``if'' direction:\\
 Assume the game is convex. Thus, for all $A, B \subset N$, we
@@
 \end{gather*}
+
+\end{proof}
 
@@
 
-\begin{Proposition}\label{complexity1}
+\begin{Proposition}\label{complexity2}
 The run time complexity of Depth-2 Convex-Checker algorithm is
@@
 \emph{$\epsilon$-core} set is empty or not.
-Also instead of considering $\epsilon$ amount of constant deviation in \emph{$\epsilon$-core} definition (Equation \ref{eq:core}), we similarly defined \emph{relative $\epsilon$-core} concept where no coalition would benefit more than \emph{$\epsilon$ $\times$ v(C)} by deviating.
+Also instead of considering $\epsilon$ amount of constant deviation in \emph{$\epsilon$-core} definition (Equation \ref{eq:core2}), we similarly defined \emph{relative $\epsilon$-core} concept where no coalition would benefit more than \emph{$\epsilon$ $\times$ v(C)} by deviating.
 We set $\epsilon$ between 0 and 1 and verify the \emph{relative $\epsilon$-core} set non-emptiness.
@@
 performance and satisfaction for both web services and coalitions.
+
+%\subsection{Subsection Heading Here}
+%Subsection text here.
+
+% needed in second column of first page if using \IEEEpubid
+%\IEEEpubidadjcol
+
+%\subsubsection{Subsubsection Heading Here}
+%Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection %text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.
+%Subsubsection text here.Subsubsection text here.Subsubsection text here.
+
+%Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection %text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.
+
 % An example of a floating figure using the graphicx package.
@@
 
-% Note that IEEE typically puts floats only at the top, even when this
+% Note that IEEE CS typically puts floats only at the top, even when this
 % results in a large percentage of a column being occupied by floats.
+% However, the Computer Society has been known to put floats at the bottom.
 
@@
 %
-% Note that often IEEE papers with subfigures do not employ subfigure
+% Note that often IEEE CS papers with subfigures do not employ subfigure
 % captions (using the optional argument to \subfloat), but instead will
@@
 % anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals/conferences use top floats
-% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
-% command of the stfloats package.
+% positioning is not used. Most IEEE journals use top floats exclusively.
+% However, Computer Society journals sometimes do use bottom floats - bear
+% this in mind when choosing appropriate optional arguments for the
+% figure/table environments.
+% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
+% floats. This can be corrected via the \fnbelowfloat command of the
+% stfloats package.
 
@@
 
-% conference papers do not normally have an appendix
+% if have a single appendix:
+%\appendix[Proof of the Zonklar Equations]
+% or
+%\appendix  % for no appendix heading
+% do not use \section anymore after \appendix, only \section*
+% is possibly needed
+
+% use appendices with more than one appendix
+% then use \section to start each appendix
+% you must declare a \section before using any
+% \subsection or using \label (\appendices by itself
+% starts a section numbered zero.)
+%
+
+%\appendices
+%\section{Proof of the First Zonklar Equation}
+%Appendix one text goes here.
+
+% you can choose not to have a title for an appendix
+% if you want by leaving the argument blank
+%\section{}
+%Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.
+
+% use section* for acknowledgement
+\ifCLASSOPTIONcompsoc
+  % The Computer Society usually uses the plural form
+  \section*{Acknowledgments}
+\else
+  % regular IEEE prefers the singular form
+  \section*{Acknowledgment}
+\fi
+
+The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...
+
+% Can use something like this to put references on a page
+% by themselves when using endfloat and the captionsoff option.
+\ifCLASSOPTIONcaptionsoff
+  \newpage
+\fi
 
@@
 
+\bibliographystyle{IEEEtran}
+\bibliography{Ehsan}
+
 % can use a bibliography generated by BibTeX as a .bbl file
@@
 % http://www.michaelshell.org/tex/ieeetran/bibtex/
-\bibliographystyle{IEEEtran}
-\bibliography{Ehsan}
+%\bibliographystyle{IEEEtran}
 % argument is your BibTeX string definitions and bibliography database(s)
@@
 % (used to reserve space for the reference number labels box)
-
 %\begin{thebibliography}{1}
@@
 %\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+%This is an example of a book reference
+%H. Kopka and P.W. Daly, \emph{A Guide to {\LaTeX}}, third ed. Harlow, U.K.: Addison-Wesley, 1999.
+
+%This is an example of a Transactions article reference
+%D.S.
+Coming and O.G.
+Staadt, "Velocity-Aligned Discrete Oriented Polytopes for Dynamic Collision Detection," IEEE Trans.
+Visualization and Computer Graphics, vol. 14,  no. 1,  pp.
+1-12,  Jan/Feb  2008, doi:10.1109/TVCG.2007.70405.
+
+%This is an example of a article from a conference proceeding
+%H.
+Goto, Y.
+Hasegawa, and M.
+Tanaka, "Efficient Scheduling Focusing on the Duality of MPL Representation," Proc.
+IEEE Symp.
+Computational Intelligence in Scheduling (SCIS '07), pp.
+57-64, Apr.
+2007, doi:10.1109/SCIS.2007.367670.
+
+%This is an example of a PrePrint reference
+%J.M.P.
+Martinez, R.B.
+Llavori, M.J.A.
+Cabo, and T.B.
+Pedersen, "Integrating Data Warehouses with Web Data: A Survey," IEEE Trans.
+Knowledge and Data Eng., preprint, 21 Dec.
+2007, doi:10.1109/TKDE.2007.190746.
+
+%Again, see the IEEEtrans_HOWTO.pdf for several more bibliographical examples. Also, more style examples
+%can be seen at http://www.computer.org/author/style/transref.htm
 %\end{thebibliography}
+
+% biography section
+% 
+% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+% needed around the contents of the optional argument to biography to prevent
+% the LaTeX parser from getting confused when it sees the complicated
+% \includegraphics command within an optional argument. (You could create
+% your own custom macro containing the \includegraphics command to make things
+% simpler here.)
+%\begin{biography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
+% or if you just want to reserve a space for a photo:
+
+\begin{IEEEbiography}{Michael Shell}
+Biography text here.
+\end{IEEEbiography}
+
+% if you will not have a photo at all:
+\begin{IEEEbiographynophoto}{John Doe}
+Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.
+\end{IEEEbiographynophoto}
+
+% insert where needed to balance the two columns on the last page with
+% biographies
+%\newpage
+
+\begin{IEEEbiographynophoto}{Jane Doe}
+Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.
+\end{IEEEbiographynophoto}
+
+% You can push biographies down or up by placing
+% a \vfill before or after them. The appropriate
+% use of \vfill depends on what kind of text is
+% on the last page and whether or not the columns
+% are being equalized.
+
+%\vfill
+
+% Can be used to pull up biographies so that the bottom of the last one
+% is flush with the other column.
+%\enlargethispage{-5in}
 

### 2013-05-11 papers/coalition2-journal-extension/charts/least_core.m

@@ -1,55 +1,0 @@
-[v,T,vT]=xlsread('least_core.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','+|--|--|.|:')
-
-i=0:99;
-t=0:0.01:1;
-y=v(:,13);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 600 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,y,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-%set(gca,'XTick',0:10:100);
-%set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',0:0.1:1);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'0';'0.1';'0.2';'0.3';'0.4';'0.5';'0.6';'0.7';'0.8';'0.9';
-    '1';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-axis([0 100 0 1.1]);
-%axis([0 50 0 1600]);
-
-% Add legend
-%%hleg1 = legend('Least epsilon-Core');
-%set(hleg1,'Location','NorthWest');
-%%set(hleg1, 'Position', [.31,.69,.05,.1]);
-%%set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-%%set(hleg1,'FontSize',10);
-%legend boxoff;
-
-% Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Maximum allowed deviation gain'}, 'FontSize',14);
-ylabel('Least-Core Non-Empty', 'FontSize',14);
-
-%Caxes = copyobj(gca,gcf);
-%set(Caxes, 'color', 'none', 'xcolor', 'k', 'xgrid', 'off', 'ycolor','k', 'ygrid','off');
-
-%subplot(1,3,2);
-%plot(i,t,i,y,i,z,'linewidth', 2);
-%Caxes = copyobj(gca,gcf);
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/old-charts/avg_bud_highfee.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('avg_bud_highfee.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
-
-i=0:49;
-t=v(:,5);y=v(:,6);z=v(:,7);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 500 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,i,z,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-%set(gca,'YTick',7000:2000:18000);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-
-axis([0 50 0 12000]);
-
-% Add legend
-hleg1 = legend('Coopetitive','Competitive','Random Coopetitive');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.3,.7,.1,.2]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',11);
-%legend boxoff;
-
-% Add title and axis labels
-title('High Membership Fee', 'fontsize', 14);
-xlabel({'Number of Runs';'(b)'}, 'FontSize',14);
-ylabel('Budget', 'FontSize',14);
-
-%Caxes = copyobj(gca,gcf);
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/old-charts/avg_bud_medfee.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('avg_bud_medfee.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
-
-i=0:49;
-t=v(:,9);y=v(:,10);z=v(:,11);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,i,z,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',7000:2000:18000);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-
-%axis([0 50 7000 18000]);
-
-% Add legend
-hleg1 = legend('Coopetitive','Competitive','Random Coopetitive');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.27,.7,.1,.2]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',11);
-%legend boxoff;
-
-% Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
-ylabel('Budget', 'FontSize',14);
-
-%Caxes = copyobj(gca,gcf);
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/old-charts/avg_bud_medfee3set.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('avg_bud_medfee.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
-
-i=0:49;
-t=v(:,9);y=v(:,10);z=v(:,11);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 500 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,i,z,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-%set(gca,'YTick',7000:2000:18000);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-
-axis([0 50 0 18000]);
-
-% Add legend
-hleg1 = legend('Coopetitive','Competitive','Random Coopetitive');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.3,.7,.1,.2]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',11);
-%legend boxoff;
-
-% Add title and axis labels
-title('Medium Membership Fee', 'fontsize', 14);
-xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
-ylabel('Budget', 'FontSize',14);
-
-%Caxes = copyobj(gca,gcf);
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/old-charts/avg_bud_veryhighfee.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('avg_bud_veryhighfee.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
-
-i=0:49;
-t=v(:,5);y=v(:,6);z=v(:,7);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 500 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,i,z,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-%set(gca,'YTick',7000:2000:18000);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-
-axis([0 50 0 12000]);
-
-% Add legend
-hleg1 = legend('Coopetitive','Competitive','Random Coopetitive');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.3,.7,.1,.2]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',11);
-%legend boxoff;
-
-% Add title and axis labels
-title('Very High Membership Fee', 'fontsize', 14);
-xlabel({'Number of Runs';'(c)'}, 'FontSize',14);
-ylabel('Budget', 'FontSize', 14, 'FontWeight','bold');
-
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/old-charts/avg_qos_task.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('avg_qos_task.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
-
-i=0:49;
-t=v(:,1);y=v(:,2);z=v(:,3);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 500 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,i,z,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-%set(gca,'YTick',0:0.1:1);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-axis([0 50 0.4 1]);
-%axis([0 50 7000 18000]);
-
-% Add legend
-hleg1 = legend('Coopetitive','Competitive','Random Coopetitive');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.3,.71,.1,.2]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',11);
-%legend boxoff;
-
-% Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Number of Runs';'(c)'}, 'FontSize',14);
-ylabel('Average QoS of Tasks Performed', 'FontSize',14);
-
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/old-charts/avg_rep.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('avg_rep.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
-
-i=0:49;
-t=v(:,1);y=v(:,2);z=v(:,3);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,i,z,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',0:0.1:1);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-axis([0 50 0.2 1]);
-%axis([0 50 7000 18000]);
-
-% Add legend
-hleg1 = legend('Coopetitive','Competitive','Random Coopetitive');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.27,.71,.1,.2]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',11);
-%legend boxoff;
-
-% Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Number of Runs';'(b)'}, 'FontSize',14);
-ylabel('Reputation', 'FontSize',14);
-
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/old-charts/comp_p.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('comp_p.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|--|:')
-
-i=0:49;
-t=v(:,1);y=v(:,2);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',0:0.1:1);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-axis([0 50 0 1]);
-%axis([0 50 7000 18000]);
-
-% Add legend
-hleg1 = legend('Competitive W1','Competitive W2');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.69,.6,.1,.2]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',11);
-%legend boxoff;
-
-% Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
-ylabel('Reputation', 'FontSize',14);
-
-%Caxes = copyobj(gca,gcf);
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/old-charts/coop_p.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('coop_p.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|--|:')
-
-i=0:49;
-t=v(:,1);y=v(:,2);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',0:0.1:1);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-axis([0 50 0 1]);
-%axis([0 50 7000 18000]);
-
-% Add legend
-hleg1 = legend('Cooperative W3','Cooperative W4');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.69,.65,.1,.2]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',11);
-%legend boxoff;
-
-% Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Number of Runs';'(b)'}, 'FontSize',14);
-ylabel('Reputation', 'FontSize',14);
-
-%Caxes = copyobj(gca,gcf);
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/old-charts/decision_dev.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('decision_dev.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|+-|.|:')
-
-i=0:49;
-t=v(:,1);y=v(:,2);z=v(:,3);tt=v(:,4);yy=v(:,5);zz=v(:,6);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,i,z,i,tt,i,yy,i,zz,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',7000:2000:18000);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-
-axis([0 50 7000 18000]);
-
-% Add legend
-hleg1 = legend('0% Deviation','10% Deviation','20% Deviation','30% Deviation','40% Deviation','50% Deviation');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.24,.63,.1,.2]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',10);
-%legend boxoff;
-
-% Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/old-charts/decision_dev2.m

@@ -1,61 +1,0 @@
-[v,T,vT]=xlsread('decision_dev2.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-%set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-*|-.|--|.-|.|:')
-
-i=1:10;
-t=v(:,1);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
-
-%subplot(1,3,1);
-
-%plot(i,t,'--rs','LineWidth',2, 'MarkerEdgeColor','k', 'MarkerFaceColor','g', 'MarkerSize',10);
-plot(i,t,'--blacks','LineWidth',2,...
-                'MarkerEdgeColor','black',...
-                'MarkerFaceColor','black',...
-                'MarkerSize',10);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:10);
-%set(gca,'YTick',7000:1500:18000);
-%set(gca,'YTick',7000:2000:18000);
-set(gca,'tickdir','in');
-%set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-%    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-%    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-%    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-%    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-
-axis([0 11 0.82 1]);
-
-% Add legend
-%hleg1 = legend('0% Deviation','10% Deviation','20% Deviation','30% Deviation','40% Deviation','50% Deviation');
-%set(hleg1,'Location','NorthWest');
-%set(hleg1, 'Position', [.24,.63,.1,.2]);
-%set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-%set(hleg1,'FontSize',10);
-%legend boxoff;
-
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/old-charts/task_done.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('task_done.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
-
-i=0:49;
-t=v(:,1);y=v(:,2);z=v(:,3);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 500 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,i,z,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-%set(gca,'YTick',0:0.1:1);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-%axis([0 50 0.2 1]);
-%axis([0 50 7000 18000]);
-
-% Add legend
-hleg1 = legend('Coopetitive','Competitive','Random Coopetitive');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.3,.71,.1,.2]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',11);
-%legend boxoff;
-
-% Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
-ylabel('Number of tasks successfully done', 'FontSize',14);
-
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/old-charts/task_satisfaction.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('task_satisfaction.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
-
-i=0:49;
-t=v(:,1);y=v(:,2);z=v(:,3);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 500 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,i,z,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-%set(gca,'YTick',0:0.1:1);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-axis([0 50 0 1]);
-%axis([0 50 7000 18000]);
-
-% Add legend
-hleg1 = legend('Coopetitive','Competitive','Random Coopetitive');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.3,.71,.1,.2]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',11);
-%legend boxoff;
-
-% Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Number of Runs';'(b)'}, 'FontSize',14);
-ylabel('Task Satisfaction Ratio', 'FontSize',14);
-
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/s2_task_done.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('s2_task_done.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|--|--|.|:')
-
-i=0:49;
-t=v(:,1);y=v(:,2);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',0:1000:7000);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-
-axis([0 50 0 7000]);
-
-% Add legend
-hleg1 = legend('Dynamic Coalition Formation','Random Formation');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.30,.80,.1,.1]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',10);
-%legend boxoff;
-
-% Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Iterations';'(a)'}, 'FontSize',14);
-ylabel('Number of tasks successfully done', 'FontSize',14);
-
-%Caxes = copyobj(gca,gcf);
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/s2_task_qos.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('s2_task_qos.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|--|--|.|:')
-
-i=0:49;
-t=v(:,1);y=v(:,2);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',0.5:0.04:0.7);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-axis([0 50 0.5 0.7]);
-%axis([0 50 0 1600]);
-
-% Add legend
-hleg1 = legend('Dynamic Coalition Formation','Random Formation');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.30,.80,.1,.1]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',10);
-%legend boxoff;
-
-% Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Iterations';'(b)'}, 'FontSize',14);
-ylabel('Average QoS of Tasks Performed', 'FontSize',14);
-
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/task_done.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('task_done.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|+-|.|:')
-
-i=0:49;
-t=v(:,1);y=v(:,2);z=v(:,3);tt=v(:,4);yy=v(:,5);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,i,z,i,tt,i,yy,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',0:200:1600);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-
-axis([0 50 0 1600]);
-
-% Add legend
-hleg1 = legend('0% Deviation','10% Deviation','20% Deviation','30% Deviation','40% Deviation');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.24,.63,.1,.2]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',10);
-%legend boxoff;
-
-% Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/task_done_opt.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('task_done_opt.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|+|--|.|:')
-
-i=0:49;
-t=v(:,1);y=v(:,2);z=v(:,3);tt=v(:,4);yy=v(:,5);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,i,z,i,tt,i,yy,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',0:200:1600);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-
-axis([0 50 0 1600]);
-
-% Add legend
-hleg1 = legend('Optimal epsilon-core','Our depth-2 Convex','Our depth-1 Convex','3-Way Sat','2-Player Game');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.26,.66,.1,.2]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',10);
-%legend boxoff;
-
-% Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Iterations';'(a)'}, 'FontSize',14);
[…]

### 2013-05-11 papers/coalition2-journal-extension/charts/task_qos_opt.m

@@ -1,57 +1,0 @@
-[v,T,vT]=xlsread('task_qos_opt.xlsx') 
-% 'xlsx' for exell 2007
-%v: Double
-%T and vT : cell
-%use v containing numbers 
-
-set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|+|--|.|:')
-
-i=0:49;
-t=v(:,1);y=v(:,2);z=v(:,3);tt=v(:,4);yy=v(:,5);
-%set(gcf,'Position',[100 100 800 500]);
-set(gcf,'Position',[100 100 550 375]);
-
-%subplot(1,3,1);
-
-h = plot(i,t,i,y,i,z,i,tt,i,yy,'linewidth', 2);
-%set(h(1),'linewidth',3);
-grid on;
-
-%set(gca,'Xcolor',[0.5 0.5 0.5]);
-%set(gca,'Ycolor',[0.5 0.5 0.5]);
-set(gca,'XTick',1:1:50);
-%set(gca,'YTick',7000:1500:18000);
-%set(gca,'YTick',0:200:1600);
-set(gca,'tickdir','in')
-set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
-    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
-set(gca,'XGrid','off','YGrid','on','ZGrid','off');
-set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
-
-%axis([0 50 0.4 1]);
-%axis([0 50 0 1600]);
-
-% Add legend
-hleg1 = legend('Optimal epsilon-core','Our depth-2 Convex','Our depth-1 Convex','3-Way Sat','2-Player Game');
-%set(hleg1,'Location','NorthWest');
-set(hleg1, 'Position', [.252,.67,.1,.2]);
-set(hleg1,'Interpreter','none');
-%set(hleg1,'color','none');
-set(hleg1,'FontSize',10);
-%legend boxoff;
-
-% Add title and axis labels
-% title('Trigonometric Functions', 'fontsize', 10);
[…]

### 2013-05-11 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 a coalitional game $(N, v)$ if and only if:
-\begin{equation}\label{eq:core3}
+\begin{equation}\label{eq:core}
 \forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S)
@@
 %\begin{theorem}[Einstein-Podolsky-Rosenberg]
-\begin{theorem}
+\begin{theorem}\label{proposition1}
 A game with a characteristic function $v$
@@
 member. As the normal core membership algorithm is computationally
-intractable, we exploit Proposition \ref{proposition} and Equation
+intractable, we exploit Proposition \ref{proposition1} and Equation
 \ref{eq:convex_snow} to check the convexity of our game having
@@
 
-\begin{Proposition}\label{complexity1}
-The run time complexity of Depth-1 Convex-Checker algorithm is
-$O(n)$.
-\end{Proposition}
+\begin{theorem}\label{complexity1}
+\emph{The run time complexity of Depth-1 Convex-Checker algorithm is
+$O(n)$.}
+\end{theorem}
 
@@
 
-\begin{Proposition}\label{complexity2}
-The run time complexity of Depth-2 Convex-Checker algorithm is
-$O(n^2)$.
-\end{Proposition}
+\begin{theorem}\label{complexity2}
+\emph{The run time complexity of Depth-2 Convex-Checker algorithm is
+$O(n^2)$.}
+\end{theorem}
 

### 2013-05-26 papers/coalition-journal-extension/coalition_journal.tex
Changes
changes

@@
 %% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
+%% andbgf
 %% http://www.ieee.org/
@@
 and to have opportunity of receiving a bigger task pool from end
-users. The way the web services reside inside communities and how
-communities of web services are engineered is described in
-\cite{DBLP:journals/ijebr/MaamarSTBB09}. Throughout this paper, in
+users. Throughout this paper, in
 our equations, we refer to web services as $ws$ and to the set of
@@
 
-\emph{2) Master Web Services} are representatives of the
+\emph{2) Master Web Services} or the community coordinators, are representatives of the
 communities of web services and responsible for their management.
@@
 community \emph{worth} or \emph{payoff} function.
+
+\subsection{Web Service Communities}\label{webservice-communities}
+
+Figure \ref{fig_community} represents the architecture of web service communities.
+The communities are basicly as an abstraction model of web services, they aggrigate web services and communicate with UDDI registeries and users using same protocols as web services.
+Community cordinators or master web services are responsible for community development, managing membership requests from web services and distributing user tasks among the community members.
+Communitiy coordinators try to attract quality web services and keep the community as stable as possible.
+The way the web services reside inside communities and how communities of web services are engineered is described comprehensivly in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+
+\begin{figure*}[!t]
+\centerline{\includegraphics[width=6.25in]{community.eps}}
+\caption{Architecture of Web Service communities}
+\label{fig_community}
+\end{figure*}
 
@@
 
+\section{Related Work}\label{s:relatedwork}
+
+Game theory provides a rich set of frameworks and mathematical tools for rational agents seeking to maximise their profit and efficiency through choosing best available streteghies in multi-agent enviroments.
+
 %\subsection{Subsection Heading Here}

### 2013-05-26 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 Figure \ref{fig_community} represents the architecture of web service communities.
-The communities are basicly as an abstraction model of web services, they aggrigate web services and communicate with UDDI registeries and users using same protocols as web services.
+The communities are basicly an abstract model of web services, they aggrigate web services and communicate with other entities such as UDDI registeries and users, using identical protocols as web services.
+Web services join communities to increase their utility by having a larger market share and task pool.
 Community cordinators or master web services are responsible for community development, managing membership requests from web services and distributing user tasks among the community members.
-Communitiy coordinators try to attract quality web services and keep the community as stable as possible.
+Communitiy coordinators try to attract quality web services and keep the community as stable and productive as possible to gain better reputation and user satisfaction which results in having a higher market share for the community.
 The way the web services reside inside communities and how communities of web services are engineered is described comprehensivly in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

### 2013-05-28 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 
+In this section, we present the web service and community coordinator's intractions, the task distribution process and revenue models in web service communities.
+
+\subsection{Task destribution}
+
+As mentioned in section \ref{webservice-communities}, communities are robust service providers with well stablished market share and reputation.
+By maintaining their reputation and performance, they attract  end users which choose them as service providers to perform their tasks.
+The community master is characterizd by a request rate $(R_M)$ from users.
+Each web service comes with a given QoS ($QoS_{ws}$) from which the throughput $T_{ws}$ is excluded.
+This exclusion allows us to build our analysis on the particular value of $T_{ws}$.
+Throughput is the average rate of tasks a web service can perform per time unit.
+Thus, web services perform tasks with an average output quality of $QoS_{ws}$ and a throughput rate of $T_{ws}$.
+The community master uses a weighted fair queuing scheduling technique to distribute task ammoung its members.
+
+\section{Web Service Cooperative Games}\label{s:model}
+
 In this section, we present different web service community models

### 2013-05-29 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 By maintaining their reputation and performance, they attract  end users which choose them as service providers to perform their tasks.
-The community master is characterizd by a request rate $(R_M)$ from users.
-Each web service comes with a given QoS ($QoS_{ws}$) from which the throughput $T_{ws}$ is excluded.
-This exclusion allows us to build our analysis on the particular value of $T_{ws}$.
+The community master is characterizd by a request rate $(R_C)$ from users.
+Each web service comes with a given QoS ($QoS_{ws}$) from which the throughput $Tr_{ws}$ is excluded.
+This exclusion allows us to build our analysis on the particular value of $Tr_{ws}$.
 Throughput is the average rate of tasks a web service can perform per time unit.
-Thus, web services perform tasks with an average output quality of $QoS_{ws}$ and a throughput rate of $T_{ws}$.
-The community master uses a weighted fair queuing scheduling technique to distribute task ammoung its members.
+Thus, web services perform tasks with an average output quality of $QoS_{ws}$ and a throughput rate of $Tr_{ws}$.
+
+The community master uses a slightly modified \emph{weighted fair queuing} method to distribute task among its members.
+The goal is to allocate incoming tasks to web services with a rate matching throughput value of $Tr_{ws}$.
+In \emph{weighted fair queuing} method \emph{all} the input flow is multiplexed along different paths, however in our case if the input rate $(R_C)$ of the community is more than summation of throughput values of web services, some of the input tasks will be queued and served with delay.
+Thus, the amount of tasks performed by community is $\sum_{ws \in C}{(Tr_{ws})}$ when $\sum_{ws}{Tr_{ws}} \leq R_{C}$.
+However, when the community has more web services having more total throughput value than community's request rate $(R_C)$ the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $R_C \times \frac{Tr_{ws}}{\sum_{ws}{Tr_{ws}}}$ for each web service ($ws$) and the total rate of tasks being performed is $R_C$, the community's receiving request rate.
+The best situation for communities would be to have around the same number
 

### 2013-05-31 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 
-\subsection{Web Service Parameters}
+\subsection{Web Service Parameters}\label{ws_parameters}
 
@@
 However, when the community has more web services having more total throughput value than community's request rate $(R_C)$ the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $R_C \times \frac{Tr_{ws}}{\sum_{ws}{Tr_{ws}}}$ for each web service ($ws$) and the total rate of tasks being performed is $R_C$, the community's receiving request rate.
-The best situation for communities would be to have around the same number
-
-\section{Web Service Cooperative Games}\label{s:model}
+
+\subsection{Community Revenue}
+
+The communities and web services earn revenue by performing tasks.
+The total gain is function of quality ($QoS_{ws}$) and quantity($Tr_{ws}$) of tasks being performed.
+As mentioned in section \ref{ws_parameters} $QoS_{ws}$ is obtained by a certain aggregation function of the parameters considered in Table \ref{qosws}.
+We have adopted a linear equal weigth average over all QoS parameteres listed in table \ref{qosws} excluding the $Throuput$ and $Cost$ parameters.
+A community has the option to weigh specific QoS patameters more or less depending on the expectations of their clients.
+
+The maximum potential output $(PO(C))$ of a community is aggregation of number of tasks, times their quality, for each web service participating as a member of the community:
+
+\begin{equation}
+PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
+\end{equation}
+
+If the summation of throughput ($Tr_{ws}$) values of community members exceeds the input task rate of the community ($R_C$) the community cannot perform at its maximum potential.
+It means community has more web services than it needs for performing input task load.
+Therefore, in these cases, the actual output has to be normalized to the ammount of tasks being performed.
+
+\begin{equation}
+Out(C) = \left\{
+  \begin{array}{l l}
+    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{M}$}\\
+    PO(C) \times \frac{R_{M}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{M}$}
+  \end{array} \right.
+\end{equation}
+
+The revenue function of the web service community, is a linear function of $Out(C)$ with a positive constant multiplier.
+
+\subsection{Case Study}
+
+In this section, we analyse a few numerical examples and discuss the motivation of web services and community intractions and the strategies they can adopt and the revenue they can earn adopting different strategies.
+
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+\caption{Three web services of example 1}
+\label{example_1}
+\centering
+\begin{tabular}{c c c c}
+\hline
+$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
+\hline
+1 & 0.8 & 4 & 3.2\\
+1 & 0.8 & 5 & 4.0\\
+1 & 0.8 & 3 & 2.4\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+% \caption{Three web services}
+\label{example_1_1}
+\centering
+\begin{tabular}{c c || c c}
+\hline
+Community & Value & Community & Value\\
+\hline
+$\left\{1\right\}$ & 3.2 & $\left\{1,2\right\}$ & 7.2\\
+$\left\{2\right\}$ & 4.0 & $\left\{1,3\right\}$ & 6.8\\
+$\left\{3\right\}$ & 2.4 & $\left\{2,3\right\}$ & 6.4\\
+$\left\{1,2,3\right\}$ & 8.0\\
+\hline
+Community $R_C$: 12\\
+\hline
+\end{tabular}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+\caption{Three web services of example 2}
+\label{example_2}
+\centering
+\begin{tabular}{c c c c}
+\hline
+$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
+\hline
+1 & 0.8 & 5 & 4.0\\
+1 & 0.7 & 6 & 4.2\\
+1 & 0.7 & 4 & 2.8\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+% \caption{Three web services}
+\label{example_2_2}
+\centering
+\begin{tabular}{c c || c c}
+\hline
+Community & Value & Community & Value\\
+\hline
+$\left\{1\right\}$ & 4.0 & $\left\{1,2\right\}$ & 7.4\\
+$\left\{2\right\}$ & 4.2 & $\left\{1,3\right\}$ & 6.8\\
+$\left\{3\right\}$ & 2.8 & $\left\{2,3\right\}$ & 7.0\\
+$\left\{1,2,3\right\}$ & 7.3\\
+\hline
+Community $R_C$: 10\\
+\hline
+\end{tabular}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In the first example, we present a community with $R_C$ of 10, and three web services each having different $QoS$ and $Th_{ws}$ values as listed in table \ref{example_1}.
+
+\section{Web Service Cooperative Games}\label{s:game_solution}
 

### 2013-05-31 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 \hline
-Community & Value & Community & Value\\
+Community & Worth & Community & Worth\\
 \hline
@@
 
-In the first example, we present a community with $R_C$ of 10, and three web services each having different $QoS$ and $Th_{ws}$ values as listed in table \ref{example_1}.
+In the first example, we present a community with $R_C$ value of 10, and three web services each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}.
 

### 2013-06-02 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 
-In the first example, we present a community with $R_C$ value of 10, and three web services each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}.
+We present an example with a community with $R_C$ value of 10, and three web services each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}.
 

### 2013-06-06 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 We present an example with a community with $R_C$ value of 10, and three web services each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}.
+The worth of a community is calculated based on $Out(C)$ equation (\ref{xxxxxx}) which is amount of output being generated by the community.
+Web services working individually, without joining a community, have small market shares.
+The first table shows in figure \ref{xxxxxx} lists the web services with their aggregated $QoS_{ws}$ parameters, their task input rate while working alone, and also their $Th_{ws}$ throughput value.
+The second table shows all the possible communities and their worth.
+The values suggest, communities having more web services have better gain and output.
+However community tries to distribute the gain between web services.
+Sometimes it is impossible to share the gain between all web services in a way no subset of them would individually gain more if they had their own group.
+In our example, as listed at table \ref{xxxxxx}, web services {ws_1} and {ws_2} working together can gain
 

### 2013-06-11 papers/coalition-journal-extension/coalition_journal.tex
Changes

--- 2013-06-02 papers/coalition-journal-extension/coalition_journal.tex
@@
 
-\begin{equation}
+\begin{equation}\label{out_c}
 Out(C) = \left\{
   \begin{array}{l l}
-    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{M}$}\\
-    PO(C) \times \frac{R_{M}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{M}$}
+    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{C}$}\\
+    PO(C) \times \frac{R_{C}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{C}$}
   \end{array} \right.
@@
 1 & 0.8 & 4 & 3.2\\
-1 & 0.8 & 5 & 4.0\\
-1 & 0.8 & 3 & 2.4\\
+2 & 0.8 & 5 & 4.0\\
+3 & 0.8 & 3 & 2.4\\
 \hline
@@
 % \caption{Three web services}
-\label{example_1_1}
+\label{example_1_2}
 \centering
@@
 1 & 0.8 & 5 & 4.0\\
-1 & 0.7 & 6 & 4.2\\
-1 & 0.7 & 4 & 2.8\\
+2 & 0.7 & 6 & 4.2\\
+3 & 0.7 & 4 & 2.8\\
 \hline
@@
 We present an example with a community with $R_C$ value of 10, and three web services each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}.
+The worth of a community is calculated based on $Out(C)$ equation (\ref{out_c}) which is the amount of output being generated by the community.
+The first table in figure \ref{example_1} lists the web services with their aggregated $QoS_{ws}$ parameters, their task input rate while working alone, and also their $Th_{ws}$ throughput value.
+The second table shows all the possible communities and their worth.
+The values suggest, communities having more web services have better gain and output.
+However community tries to distribute the gain between web services.
+Sometimes it is impossible to share the gain between all web services in a way no subset of them would individually gain more if they had their own group.
+In this example, the value community of ${ws_1}$ and ${ws_2}$ is 7.2, with ${ws_3}$ joining the community the value of community increases to 8.0, however there is no way to distribute the value among web services, where ${ws_1}$ and ${ws_2}$ can earn 7.2, and ${ws_3}$ earn at least 2.4, which they could earn before joining the community.
+This makes the group unstable.
+In the example of table \ref{example_2}, we even have situations where a web service (${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$) decreases the the value of cumminity.
+The reason is, the community is already full and all tasks are almost being distributed and new community with bad quality can degrade the average quality of tasks being done by the community.
+In both examples, the request of joining of web service ${ws_3}$ should be rejected by the community.
+
+Now we consider another example, in which we have different comunitites with different market share and ${R_C}$ values, and also web services having a small share of market share independantly, providing them with a small task pull.
+In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the $social welfare$.
+In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1, ws_3\right\}$, which yeilds a total value of $32 + 16 = 48$.
+In these type of scenarios,
+
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+\caption{Three web services of example 3}
+\label{example_3}
+\centering
+\begin{tabular}{c c c c}
+\hline
+$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
+\hline
+1 & 0.8 & 10 & 5\\
+2 & 0.8 & 20 & 5\\
+3 & 0.8 & 30 & 5\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+% \caption{Three web services}
+\label{example_3_2}
+\centering
+\begin{tabular}{c c || c c}
+\hline
+Community & Worth & Community & Worth\\
+\hline
+$\left\{C_1\right\}$ & 0 & $\left\{C_2\right\}$ & 0\\
+$\left\{C_1, ws_1\right\}$ & 8 & $\left\{C_2, ws_1\right\}$ & 8\\
+$\left\{C_1, ws_2\right\}$ & 16 & $\left\{C_2, ws_2\right\}$ & 16\\
+$\left\{C_1, ws_3\right\}$ & 16 & $\left\{C_2, ws_3\right\}$ & 24\\
+$\left\{C_1, ws_1, ws_2\right\}$ & 16 & $\left\{C_2, ws_1, ws_2\right\}$ & 24\\
+$\left\{C_1, ws_1, ws_3\right\}$ & 16 & $\left\{C_2, ws_1, ws_3\right\}$ & 32\\
+$\left\{C_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_2, ws_2, ws_3\right\}$ & 32\\
+$\left\{C_1, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_2, ws_1, ws_2, ws_3\right\}$ & 32\\
+$\left\{C_1, C_2, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
+$\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
+\hline
+Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
+\hline
+\end{tabular}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2013-06-11 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 The total gain is function of quality ($QoS_{ws}$) and quantity($Tr_{ws}$) of tasks being performed.
-As mentioned in section \ref{ws_parameters} $QoS_{ws}$ is obtained by a certain aggregation function of the parameters considered in Table \ref{qosws}.
+As mentioned in section \ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain aggregation function of the parameters considered in Table \ref{qosws}.
 We have adopted a linear equal weigth average over all QoS parameteres listed in table \ref{qosws} excluding the $Throuput$ and $Cost$ parameters.
@@
 
-Now we consider another example, in which we have different comunitites with different market share and ${R_C}$ values, and also web services having a small share of market share independantly, providing them with a small task pull.
+Now we consider another example, in which we have different comunitites with different market share, ${R_C}$ values.
+Web services also have a small share of market independantly, providing them with a small task pull.
 In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the $social welfare$.
 In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1, ws_3\right\}$, which yeilds a total value of $32 + 16 = 48$.
-In these type of scenarios,
+In these type of scenarios, the goal is to reach stability, adopting a distributed approach where all players have the power of choice on the decision of whether or not they join a coalition.
+The communities usually start the game having some stablished members, encountring new web services, the communities may exchange web services and new web services would join them having at least one player gaining utility, without hurting any other participant.
+In this example if we initially having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1\right\}$ and a ${ws_3}$ as new webservice, ${ws_3}$ joining ${C_1}$ would hurt at least itself or $ws_2$, however ${ws_3}$ joining ${C_2}$ would not hurt any participants and ${ws_3}$ would earn more within the community and the community will have enough web services performing the incoming tasks from users.
 

### 2013-06-12 papers/coalition-journal-extension/coalition_journal.tex
Changes

--- 2013-06-11 papers/coalition-journal-extension/coalition_journal.tex
@@
 
+While distributing tasks, the community master can verify the performance, throughput and quality of tasks being performed by web services.
+It can recognize if web services are capable of doing the amount of tasks they advertised.
+If for any reason there is a decline in quality metrics or throughput, the master community will announce the new parameters and community masters and members can consider those values as benchmark for future performance calculations and also penalize them.
+Therefor its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities.
+Also it's important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.
+
 \subsection{Community Revenue}
@@
 This makes the group unstable.
-In the example of table \ref{example_2}, we even have situations where a web service (${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$) decreases the the value of cumminity.
+In the example of table \ref{example_2}, we even have situations where a web service (${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$) decreases the value of community.
 The reason is, the community is already full and all tasks are almost being distributed and new community with bad quality can degrade the average quality of tasks being done by the community.
 In both examples, the request of joining of web service ${ws_3}$ should be rejected by the community.
-
-Now we consider another example, in which we have different comunitites with different market share and ${R_C}$ values, and also web services having a small share of market share independantly, providing them with a small task pull.
-In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the $social welfare$.
-In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1, ws_3\right\}$, which yeilds a total value of $32 + 16 = 48$.
-In these type of scenarios,
 
@@
 
+Now we consider another example, in which we have different communities with different market share, ${R_C}$ values.
+Web services also have a small share of market independently, providing them with a small task pull.
+In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the $social welfare$.
+In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1, ws_3\right\}$, which yields a total value of $32 + 16 = 48$.
+In these types of scenarios, the goal is to reach stability, adopting a distributed approach where all players have the power of choice on the decision of whether or not they join a coalition.
+The communities usually start the game having some established members, encountering new web services, the communities may exchange web services and new web services would join them having at least one player gaining utility, without hurting any other participant.
+In this example if we initially having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1\right\}$ and a ${ws_3}$ as new web service, ${ws_3}$ joining ${C_1}$ would hurt at least itself or $ws_2$, however ${ws_3}$ joining ${C_2}$ would not hurt any participants and ${ws_3}$ would earn more within the community and the community will have enough web services performing the incoming tasks from users.
+
 \section{Web Service Cooperative Games}\label{s:game_solution}
@@
 to get requests from the master. The community master is
-characterized by a requests rate $(R_{M})$ from users. Each web
+characterized by a requests rate $(R_{C})$ from users. Each web
 service comes with a given QoS ($QoS_{ws}$) from which the
@@
 \setlength{\abovedisplayshortskip}{2pt}
-\begin{equation}
+\begin{equation}\label{eq:valuation}
 v(C) = \left\{
   \begin{array}{l l}
-    output(C) & \quad \text{if $\sum_{ws}{T_{ws}} \leq R_{M}$}\\
-    output(C) \times \frac{R_{M}}{\sum_{ws}{T_{ws}}} & \quad \text{if $\sum_{ws}{T_{ws}} > R_{M}$}
+    output(C) & \quad \text{if $\sum_{ws}{T_{ws}} \leq R_{C}$}\\
+    output(C) \times \frac{R_{C}}{\sum_{ws}{T_{ws}}} & \quad \text{if $\sum_{ws}{T_{ws}} > R_{C}$}
   \end{array} \right.
@@
 
-\subsection {Web Services Collaborating Independently}
-
-In this scenario, there is no pre-defined community and web
-services are interested in forming new ones to perform better and
-share benefits (see Figure \ref{fig_sim3}). Consequently, there is
-no master web service providing requests for others, but each web
-service comes with its own request load called \emph{market
-share}. Communities can be formed because by working together web
-services can expect to gain more than working individually. The
-worth or value of a coalition of web services is different in this
-setting. Let $metrics$ be the set of quality metrics, we average
-the values $Q^m_{ws}$ for all quality metrics ($m \in metrics$)
-for each web service $ws$, multiply it by a weight reflecting the
-importance of each metric for each web service ($w^m_{ws}$) (Note
-that $ \sum_{m}{w^m_{ws}} = 1 $). For each web service, we
-multiply this weighted average by web service's market share
-$(\mu_{ws})$ and the summation over all the web services of the
-community to be established would be the characteristic or
-valuation function. This function has the property to be
-increasing in the market share and QoS.
-
-\begin{equation}
-v(C) = \sum_{ws \in C}{ \Big( \frac{\sum_{m \in metrics}{Q^m_{ws}
-\times w^m_{ws}}}{|metrics|} \Big) \times \mu_{ws} }
-\end{equation}
-
-%$CC^{m}$ is \emph{Collabrative Coefficient} for each QoS metric (non-functional parameter), it determines how web services providing that QoS metric individually will be effected in a coalition environment.
-If it is more than 1, is means they increase performance by working together and they are \emph{super additive}, otherwise it depicts they would perform better in linear sense if they worked alone.
-As there is no pre-defined master web services in this scenario,
-we assume that the members of each coalition either dynamically
-vote for one, or collaborate and distribute tasks in round robin
-or fair fashion. To form stable coalitions, we use the same
-merge-and-split algorithm we applied for the \emph{``Web Services
-and Many Communities''} scenario.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{s3.eps}
-\caption{Web Services collaborating independently}
-\label{fig_sim3}
-\end{figure}
+\subsection{Taxtation and Community Stability}\label{s:tax}
+
+We discuessed $core$ as one the preeminent solution concepts in cooperative games.
+Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group.
+However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept opening room for agents to cooperate and stay in the community and increasing the community stability.
+The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent point of view.
+It claims agents for any reason will be not willing to deviate to gain less that $\epsilon$ amount of profit.
+However, in our case, the community master is willing to keep web services in communities too.
+There are several reasons for this, one is there is always possibility that agents may leave the community or they may under perform from the values they initially performing with.
+According to the web service community's valuation function \ref{eq:valuation} and as mentioned in examples 1, 2 and 3,
 

### 2013-06-15 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 
-We discuessed $core$ as one the preeminent solution concepts in cooperative games.
+We discuessed $core$ as one the preminent solution concepts in cooperative games.
 Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group.
-However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept opening room for agents to cooperate and stay in the community and increasing the community stability.
-The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent point of view.
-It claims agents for any reason will be not willing to deviate to gain less that $\epsilon$ amount of profit.
+However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal ammount of $\epsilon$ by deviating.
+The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent's point of view.
+It claims agents for any reason will be not willing to deviate to gain less than $\epsilon$ amount of profit.
 However, in our case, the community master is willing to keep web services in communities too.
-There are several reasons for this, one is there is always possibility that agents may leave the community or they may under perform from the values they initially performing with.
-According to the web service community's valuation function \ref{eq:valuation} and as mentioned in examples 1, 2 and 3,
+There are several reasons for this, one reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with.
+To this end, our communities will reward and valuate web services in the community
 

### 2013-06-16 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal ammount of $\epsilon$ by deviating.
+One way for communities to ensure community stability could be applying a $\epsilon$ ammount of cost for web services changing communities.
+However this would need all community masters to agree on and this will not work for webservices gaining more when working alone.
+Comuunity stability is an attractice property for communities, also communities would benefit by having slightly more web services then having the exact number of web services satisfying task rate cap.
+There are several reasons for this, one reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with.
+Thus, another way to garantee \emph{$\epsilon$-core} stability can be achieved by some surplus payments from community masters.
+These concepts of applying changes in coalition values in order to reduce their bargaining power are called $taxtation$ methods\cite{eps346856}.
+
 The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent's point of view.
 It claims agents for any reason will be not willing to deviate to gain less than $\epsilon$ amount of profit.
-However, in our case, the community master is willing to keep web services in communities too.
+Communities can agree on However, in our case, the community master is willing to keep web services in communities too.
 There are several reasons for this, one reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with.

### 2013-06-17 papers/coalition-journal-extension/coalition_journal.tex
A small info added to log
Changes

--- 2013-06-15 papers/coalition-journal-extension/coalition_journal.tex
@@
 However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal ammount of $\epsilon$ by deviating.
+Comuunity stability is an attractice property for communities, also communities would benefit by having slightly more web services then having the exact number of web services satisfying task rate cap.
+One reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with.
+
+One way for communities to ensure community stability could be applying a tax, $\epsilon$ ammount of cost for web services changing communities which would make deviation a costly act.
+However this would require all community coordinators to agree on same ammount of taxtation, being governed by some external entities or web services would join communities with lesser ammount of tax.
+Another viable solution in our scenario is to stabilize the game using external subsidies.
+The reason a game is not stable is that the community is not making enough revenue to allocate the players with enough gain.
+A community can subside the community with a contant coefficient value of $\lambda$.
+Rewarding a community with high number of quality participants with $\lambdav(C)$, where $\lambda \leq 1$.
+This can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable.
+Subsiding or taxting in order to reduce the bargaining power of sub coalitions are called $taxtation$\cite{eps346856} methods and have been .
+
+Thus, another way to garantee \emph{$\epsilon$-core} stability can be achieved by some surplus payments from community coordinators.
+These concepts of applying cost in coallition values in order to reduce their bargaining power are called $taxtation$ methods\cite{eps346856}.
+
 The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent's point of view.
 It claims agents for any reason will be not willing to deviate to gain less than $\epsilon$ amount of profit.
-However, in our case, the community master is willing to keep web services in communities too.
+Communities can agree on However, in our case, the community master is willing to keep web services in communities too.
 There are several reasons for this, one reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with.

### 2013-06-21 papers/coalition-journal-extension/coalition_journal.tex
Added charts

@@
 The reason a game is not stable is that the community is not making enough revenue to allocate the players with enough gain.
-A community can subside the community with a contant coefficient value of $\lambda$.
-Rewarding a community with high number of quality participants with $\lambdav(C)$, where $\lambda \leq 1$.
-This can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable.
-Subsiding or taxting in order to reduce the bargaining power of sub coalitions are called $taxtation$\cite{eps346856} methods and have been .
-
-Thus, another way to garantee \emph{$\epsilon$-core} stability can be achieved by some surplus payments from community coordinators.
+A community master can subside its community with a constant coefficient value of $\lambda$.
+Rewarding a community with high number of quality participants with $\lambda v(C)$, where $\lambda \leq 1$.
+Obviously with a big number of $\lambda$ it is always possible to stabilize the community.
+However, this can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable.
+Subsiding or taxting in order to reduce the bargaining power of sub coalitions are called $taxtation$\cite{eps346856} methods.
+
+%Thus, another way to garantee \emph{$\epsilon$-core} stability can be achieved by some surplus payments from community coordinators.
 These concepts of applying cost in coallition values in order to reduce their bargaining power are called $taxtation$ methods\cite{eps346856}.
 
-The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent's point of view.
+%The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent's point of view.
 It claims agents for any reason will be not willing to deviate to gain less than $\epsilon$ amount of profit.
@@
 using Java and executed the simulations on an Intel Xeon X3450
-machine with 4GBs of memory. For other parameters missing from the
+machine with 6GBs of memory. For other parameters missing from the
 dataset, we used normal random distribution with parameters

### 2013-06-21 papers/coalition-journal-extension/charts/s2_task_qos.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('s2_task_qos.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|--|--|.|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0.5:0.04:0.7);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+axis([0 50 0.5 0.7]);
+%axis([0 50 0 1600]);
+
+% Add legend
+hleg1 = legend('Dynamic Coalition Formation','Random Formation');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.30,.80,.1,.1]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Iterations';'(b)'}, 'FontSize',14);
+ylabel('Average QoS of Tasks Performed', 'FontSize',14);
+
[…]

### 2013-06-21 papers/coalition-journal-extension/charts/taxtation.m

@@ -1,0 +1,61 @@
+% Create the data to be plotted
+TBdata = [1.0 10 0 87 0.77;
+          1.1 12 0.8 93 0.78; 
+          1.2 14 1.96 96 0.8; 
+          1.3 15 3.6 98 0.8;
+          1.4 15 4.8 98 0.79; 
+          1.5 16 6.4 97 0.81; 
+          1.6 16 7.68 98 0.81; 
+          1.7 16 8.96 98 0.82;
+          1.8 16 10.24 98 0.82; 
+          1.9 16 11.52 98 0.83; 
+          2.0 17 13.6 98 0.83];
+
+%measles = [38556 24472 14556 18060 19549 8122 28541 7880 3283 4135 7953 1884]';
+%mumps = [20178 23536 34561 37395 36072 32237 18597 9408 6005 6268 8963 13882]';
+%chickenPox = [37140 32169 37533 39103 33244 23269 16737 5411 3435 6052 12825 23332]';
+taxt = TBdata(:, 1);
+size = TBdata(:, 2);
+cost = TBdata(:, 3);
+tasknum  = TBdata(:, 4);
+quality  = TBdata(:, 5);
+
+
+
+% Create the pie chart in position 1 of a 2x2 grid
+figure;
+subplot(2, 2, 1);
+plot(taxt, size, '.-');
+xlabel('Years');
+ylabel('Infection Rate');
+title('Tuberculosis Cases');
+axis([1 2 0 20]);
+set(gca,'XTick',[1 1.2 1.4 1.6 1.8 2]);
+
+
+% Create the bar chart in position 2 of a 2x2 grid
+subplot(2, 2, 2);
+plot(taxt, cost, '.-');
+xlabel('Years');
+ylabel('Infection Rate');
+title('Tuberculosis Cases');
+axis([1 2 0 20]);
+set(gca,'XTick',[1 1.2 1.4 1.6 1.8 2]);
+
+% Create the stem chart in position 3 of a 2x2 grid
+subplot(2, 2, 3);
+plot(taxt, tasknum, '.-');
+xlabel('Years');
+ylabel('Infection Rate');
+title('Tuberculosis Cases');
+axis([1 2 0 100]);
+set(gca,'XTick',[1 1.2 1.4 1.6 1.8 2]);
+
+% Create the line plot in position 4 of a 2x2 grid
+subplot(2, 2, 4);
+plot(taxt, quality, '.-');
[…]

### 2013-06-21 papers/coalition-journal-extension/charts/test.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('task_qos_opt.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-.|-+|--|.|:')
+
+i=1:10;
+%t=v(:,1);y=v(:,2);z=v(:,3);tt=v(:,4);yy=v(:,5);
+t = [0.01,0.20,0.15,0.05,0.22,0.02,0.11,0.21,0.10,0.05];
+y = [0.01,0.99,0.15,0.95,0.22,0.80,0.11,0.75,0.07,1];
+z = [0.99,0.98,0.95,0.99,0.90,0.90,0.80,0.95,0.90,1];
+%set(gcf,'Position',[100 100 800 500]);
+set(gca,'Position',[0.1 0.1 0.6 0.8]);
+set(gcf,'Position',[100 100 800 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:10);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',0:200:1600);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'M0';'M1';'M2';'M3';'M4';'M5';'M6';'M7';'M8';'M9';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+axis([0.5 10.5 0 1.2]);
+%axis([0 50 0 1600]);
+
+% Add legend
+hleg1 = legend('Optimal epsilon-core','Our depth-2 Convex','Our depth-1 Convex');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [0.8,.4,.1,.1]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
[…]

### 2013-06-22 papers/coalition-journal-extension/coalition_journal.tex
Added new charts

@@
 
-\subsection{Taxtation and Community Stability}\label{s:tax}
+\subsection{Taxtation, Subsiding and Community Stability}\label{s:tax}
 
@@
 
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=3in]{taxtation.eps}
+\caption{Analysis of community subsiding coefficient $\lambda$ on average community size (a), cost (b), number of tasks performed (c), and average quality of service of tasks performed (d).} \label{f_taxtation}
+\end{figure}
+
+texttext texttexttexttext texttexttexttext texttexttexttext texttext texttext texttext texttext texttext texttext
+
+\begin{figure*}[!t]
+\centerline{\includegraphics[width=6.75in]{tax_dyn.eps}}
+\caption{Analysis of community subsiding coefficient $\lambda$ having web service different stability levels of $\tau$ on average community size, number of tasks performed, and average quality of service, and average cost/income of communities.}
+\label{fig_dynamic_taxtation}
+\end{figure*}
+
+texttext texttexttexttext texttexttexttext texttexttexttext texttext texttext texttext texttext texttext texttext
+
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=3in]{avg_task_ws_done.eps}
+\includegraphics[width=3in]{avg_qos_ws_done.eps}
+\includegraphics[width=3in]{avg_avail_ws_done.eps}
+\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
+(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
+\end{figure}
+
+texttext texttexttexttext texttexttexttext texttexttexttext texttext texttext texttext texttext texttext texttext
+
 \section{Related Work}\label{s:relatedwork}

### 2013-06-22 papers/coalition-journal-extension/charts/avg_avail_ws_done.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('avg_avail_ws_task.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|--|--|.|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0.5:0.05:1);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+axis([0 50 0.5 1.05]);
+%axis([0 50 0 1600]);
+
+% Add legend
+hleg1 = legend('Our Method','High Availability Coalition Method');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.61,.22,.1,.1]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Iterations';'(c)'}, 'FontSize',14);
+ylabel('Average Availability', 'FontSize',14);
+
+%Caxes = copyobj(gca,gcf);
[…]

### 2013-06-22 papers/coalition-journal-extension/charts/avg_qos_ws_done.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('avg_qos_ws_task.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|--|--|.|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0.5:0.05:0.9);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+axis([0 50 0.5 0.9]);
+%axis([0 50 0 1600]);
+
+% Add legend
+hleg1 = legend('Our Method','High Availability Coalition Method');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.32,.80,.1,.1]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Iterations';'(b)'}, 'FontSize',14);
+ylabel('Average QoS of Tasks Performed', 'FontSize',14);
+
[…]

### 2013-06-22 papers/coalition-journal-extension/charts/avg_task_ws_done.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('avg_task_ws_done.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|--|--|.|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0:1000:7000);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 50 0 7000]);
+
+% Add legend
+hleg1 = legend('Our Task Destribution','Availability Based Task Distribution');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.33,.80,.1,.1]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Iterations';'(a)'}, 'FontSize',14);
+ylabel('Number of tasks successfully done', 'FontSize',14);
+
+%Caxes = copyobj(gca,gcf);
[…]

### 2013-06-22 papers/coalition-journal-extension/charts/s2_task_qos.m

@@ -21,7 +21,7 @@ grid on;
 %set(gca,'Ycolor',[0.5 0.5 0.5]);
 set(gca,'XTick',1:1:50);
 %set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',0.5:0.04:0.7);
+set(gca,'YTick',0.5:0.1:0.9);
 set(gca,'tickdir','in')
 set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
     '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
@@ -31,7 +31,7 @@ set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
 set(gca,'XGrid','off','YGrid','on','ZGrid','off');
 set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 
-axis([0 50 0.5 0.7]);
+axis([0 50 0.5 0.9]);
 %axis([0 50 0 1600]);
 
 % Add legend

### 2013-06-22 papers/coalition-journal-extension/charts/task_qos_opt.m

@@ -21,7 +21,7 @@ grid on;
 %set(gca,'Ycolor',[0.5 0.5 0.5]);
 set(gca,'XTick',1:1:50);
 %set(gca,'YTick',7000:1500:18000);
-%set(gca,'YTick',0:200:1600);
+set(gca,'YTick',0.72:0.02:0.85);
 set(gca,'tickdir','in')
 set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
     '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
@@ -31,7 +31,7 @@ set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
 set(gca,'XGrid','off','YGrid','on','ZGrid','off');
 set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 
-%axis([0 50 0.4 1]);
+axis([0 50 0.72 0.85]);
 %axis([0 50 0 1600]);
 
 % Add legend

### 2013-06-22 papers/coalition-journal-extension/charts/tax_dyn.m

@@ -1,0 +1,199 @@
+% Create the data to be plotted
+TBdata = [0.0 10 0 87 0.77;
+          0.1 10 0.88 93 0.78; 
+          0.2 9 1.76 96 0.8; 
+          0.3 8 2.88 98 0.8;
+          0.4 8 4.16 98 0.79; 
+          0.5 7 5.6 97 0.81];
+
+%measles = [38556 24472 14556 18060 19549 8122 28541 7880 3283 4135 7953 1884]';
+%mumps = [20178 23536 34561 37395 36072 32237 18597 9408 6005 6268 8963 13882]';
+%chickenPox = [37140 32169 37533 39103 33244 23269 16737 5411 3435 6052 12825 23332]';
+taxt = TBdata(:, 1);
+%size = TBdata(:, 2);
+size1 = [10,10,9,8,8,7];
+cost1 = [0,0,0,0,0,0];
+income1 = [63,60,55,47,41,29];
+tasknum1 = [83,78,73,63,54,40];
+quality1  = [0.77,0.77,0.76,0.75,0.75,0.74];
+
+size2 = [12,12,11,11,10,10];
+income2 = [77,76,73,72,69,64];
+tasknum2 = [96,95,93,92,89,84];
+quality2  = [0.8,0.8,0.79,0.78,0.78,0.77];
+cost2 = 0.3 .* quality2 .* size2;
+
+size3 = [14,13,13,13,12,11];
+income3 = [76,75,73,72,70,67];
+tasknum3 = [98,97,96,96,93,90];
+quality3  = [0.78,0.78,0.77,0.76,0.76,0.75];
+cost3 = 0.6 .* quality3 .* size3;
+
+size4 = [17,16,16,16,16,15];
+income4 = [76,76,75,74,73,72];
+tasknum4 = [98,98,98,98,97,97];
+quality4  = [0.78,0.78,0.77,0.76,0.76,0.75];
+cost4 = 1 .* quality4 .* size4;
+
+
+
+% Create the pie chart in position 1 of a 2x2 grid
+figure;
+subplot(4, 4, 1);
+plot(taxt, size1, '.-');
+xlabel('\tau');
+ylabel('Size');
+title('\lambda = 1');
+axis([0 0.5 0 20]);
+set(gca,'XTick',[0.0 0.1 0.2 0.3 0.4 0.5]);
+grid on
+
+% Create the bar chart in position 2 of a 2x2 grid
[…]

### 2013-06-22 papers/coalition-journal-extension/charts/taxtation.m

@@ -1,13 +1,13 @@
 % Create the data to be plotted
 TBdata = [1.0 10 0 87 0.77;
-          1.1 12 0.8 93 0.78; 
-          1.2 14 1.96 96 0.8; 
-          1.3 15 3.6 98 0.8;
-          1.4 15 4.8 98 0.79; 
-          1.5 16 6.4 97 0.81; 
-          1.6 16 7.68 98 0.81; 
-          1.7 16 8.96 98 0.82;
-          1.8 16 10.24 98 0.82; 
+          1.1 11 0.88 93 0.78; 
+          1.2 11 1.76 96 0.8; 
+          1.3 12 2.88 98 0.8;
+          1.4 13 4.16 98 0.79; 
+          1.5 14 5.6 97 0.81; 
+          1.6 14 6.72 98 0.81; 
+          1.7 15 8.4 98 0.82;
+          1.8 15 9.6 98 0.82; 
           1.9 16 11.52 98 0.83; 
           2.0 17 13.6 98 0.83];
 
@@ -26,36 +26,40 @@ quality  = TBdata(:, 5);
 figure;
 subplot(2, 2, 1);
 plot(taxt, size, '.-');
-xlabel('Years');
-ylabel('Infection Rate');
-title('Tuberculosis Cases');
+xlabel('\lambda');
+ylabel('Size');
+title('(a)');
 axis([1 2 0 20]);
 set(gca,'XTick',[1 1.2 1.4 1.6 1.8 2]);
+grid on;
 
 
 % Create the bar chart in position 2 of a 2x2 grid
 subplot(2, 2, 2);
 plot(taxt, cost, '.-');
-xlabel('Years');
-ylabel('Infection Rate');
-title('Tuberculosis Cases');
+xlabel('\lambda');
+ylabel('Subside Cost');
+title('(b)');
 axis([1 2 0 20]);
 set(gca,'XTick',[1 1.2 1.4 1.6 1.8 2]);
+grid on;
 
 % Create the stem chart in position 3 of a 2x2 grid
 subplot(2, 2, 3);
 plot(taxt, tasknum, '.-');
-xlabel('Years');
-ylabel('Infection Rate');
-title('Tuberculosis Cases');
+xlabel('\lambda');
+ylabel('|tasks performed|');
+title('(c)');
 axis([1 2 0 100]);
 set(gca,'XTick',[1 1.2 1.4 1.6 1.8 2]);
+grid on;
 
[…]

### 2013-07-01 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 Non-Cooperative} \cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods
-in \emph{one grand community with many web services} scenario. For
-\emph{$\epsilon$-core}, we assign $\epsilon$ to 15\% of total
+in \emph{one grand community with many web services} scenario.
+
+For \emph{$\epsilon$-core}, we assign $\epsilon$ to 15\% of total
 community worth, $\epsilon = 0.15 \times v(C)$, which allows

### 2013-07-03 papers/coalition-journal-extension/coalition_journal.tex
Changes

--- 2013-06-22 papers/coalition-journal-extension/coalition_journal.tex
@@
 Non-Cooperative} \cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods
-in \emph{one grand community with many web services} scenario. For
-\emph{$\epsilon$-core}, we assign $\epsilon$ to 15\% of total
-community worth, $\epsilon = 0.15 \times v(C)$, which allows
+in \emph{one grand community with many web services} scenario.
+
+For the \emph{optimal core} method we have used the well known \emph{$\epsilon$-core} method as the 
+taxtation method to relax the core condition for more communities to form. 
+We have assigned $\epsilon$ to 15\% of total community worth, $\epsilon = 0.15 \times v(C)$, which allows
 subsets of the coalition to gain maximum 15\% of $v(C)$. In the
@@
 size to 25 web services, since the method is computationally 
-intractable and anything more than that would make it
+intractable as number of web services increase and anything more than that would make it
 impractical to run in our simulations. In the other methods, there
@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=3in]{taxtation.eps}
+\caption{Analysis of community subsiding coefficient $\lambda$ on average community size (a), cost (b), number of tasks performed (c), and average quality of service of tasks performed (d).} \label{f_taxtation}
+\end{figure}
+
+As mentioned in section \ref{s:tax}
+
+texttext texttexttexttext texttexttexttext texttexttexttext texttext texttext texttext texttext texttext texttext
+
+\begin{figure*}[!t]
+\centerline{\includegraphics[width=6.75in]{tax_dyn.eps}}
+\caption{Analysis of community subsiding coefficient $\lambda$ having web service different stability levels of $\tau$ on average community size, number of tasks performed, and average quality of service, and average cost/income of communities.}
+\label{fig_dynamic_taxtation}
+\end{figure*}
+
+texttext texttexttexttext texttexttexttext texttexttexttext texttext texttext texttext texttext texttext texttext
+
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=3in]{avg_task_ws_done.eps}
+\includegraphics[width=3in]{avg_qos_ws_done.eps}
+\includegraphics[width=3in]{avg_avail_ws_done.eps}
+\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
+(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
+\end{figure}
+
+texttext texttexttexttext texttexttexttext texttexttexttext texttext texttext texttext texttext texttext texttext
+
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
 \includegraphics[width=3in]{s2_task_done.eps}
@@
 performance and satisfaction for both web services and coalitions.
-
-\begin{figure}[!t]
-\centering
-%\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{taxtation.eps}
-\caption{Analysis of community subsiding coefficient $\lambda$ on average community size (a), cost (b), number of tasks performed (c), and average quality of service of tasks performed (d).} \label{f_taxtation}
-\end{figure}
-
-texttext texttexttexttext texttexttexttext texttexttexttext texttext texttext texttext texttext texttext texttext
-
-\begin{figure*}[!t]
-\centerline{\includegraphics[width=6.75in]{tax_dyn.eps}}
-\caption{Analysis of community subsiding coefficient $\lambda$ having web service different stability levels of $\tau$ on average community size, number of tasks performed, and average quality of service, and average cost/income of communities.}
-\label{fig_dynamic_taxtation}
-\end{figure*}
-
-texttext texttexttexttext texttexttexttext texttexttexttext texttext texttext texttext texttext texttext texttext
-
-\begin{figure}[!t]
-\centering
-%\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{avg_task_ws_done.eps}
-\includegraphics[width=3in]{avg_qos_ws_done.eps}
-\includegraphics[width=3in]{avg_avail_ws_done.eps}
-\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
-(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
-\end{figure}
-
-texttext texttexttexttext texttexttexttext texttexttexttext texttext texttext texttext texttext texttext texttext
 

### 2013-07-04 papers/coalition-journal-extension/coalition_journal.tex
changes

@@
 For the \emph{optimal core} method we have used the well known \emph{$\epsilon$-core} method as the 
-taxtation method to relax the core condition for more communities to form. 
+taxtation method to relax the core condition to help communities, attract web services. 
 We have assigned $\epsilon$ to 15\% of total community worth, $\epsilon = 0.15 \times v(C)$, which allows
@@
 One of the properties of coalition structure formation algorithms
-in our third scenario is that they partition web services with low
+in our second scenario is that they partition web services with low
 throughput rate so that they usually join coalitions with less

### 2013-07-05 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 
-\section{Introduction}
+\section{Introduction and Related Work}
 
@@
 
-As mentioned in section \ref{s:tax}
-
-texttext texttexttexttext texttexttexttext texttexttexttext texttext texttext texttext texttext texttext texttext
+As mentioned in section \ref{s:tax} in order to help community stability, is to subside the community by a relative coefficient ($\lambda$) so the value of $\lambda V(C)$ is devided among the community members.
+We have analysed the effect of subsiding and the cost it incurs to our web service communities.
+Figure \ref{f_taxtation} shows the results.
+In this expirement we have set a community with input task rate $R_C$ of 100 and having abstract web services throuput rate $T_r$ value of a random distribution with average 10 tasks per iteration.
+Part (a) shows the community size increases in a linear fashion as ($\lambda$) increases.
+However the cost is having a slight exponential growth rate since, not only ($\lambda$) increases also the size of the community is also increasing slowly.
+Therefore subsiding can be costly for larger number of $\lambda$ value.
+Part (c) of figure \ref{f_taxtation} depicts the number of tasks done by the community per iteration.
+It is obvoius with $\lambda$ value of 1.3 which is 30\% of community valuation, the number of tasks done almost reaches the input task rate cap of 100 tasks per iteration.
+The average quality of tasks also has a slight increase since the community will be able to afford better and more web services to join the community.
+These results proves with quality metrics our agents as web services have and their collabrative worth, the increase rate of subsiding more 1.3 is not very effective and is costly to perform.
 
@@
 
-texttext texttexttexttext texttexttexttext texttexttexttext texttext texttext texttext texttext texttext texttext
-
-\begin{figure}[!t]
-\centering
-%\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{avg_task_ws_done.eps}
-\includegraphics[width=3in]{avg_qos_ws_done.eps}
-\includegraphics[width=3in]{avg_avail_ws_done.eps}
-\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
-(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
-\end{figure}
-
-texttext texttexttexttext texttexttexttext texttexttexttext texttext texttext texttext texttext texttext texttext
+In previous experiment, we consider the scenario where all web services are stable will not leave the group and will fulfill their promised quality metrics for a good period of time.
+However, in real world scenarios of web services, this is not always the case.
+This is the reason why community would be interested in subsiding a community of larger group web services, paying a few more web services in order to keep the group reliable from end user point of view.
+In our next scenario, we have introduced the new instability variable $\tau$ from 0 to 1, 0 meaning web services having no instability issues and will perform as they claimed until the end of experiment and 1 meaning very unstable web services which will stop functioning on the first iteration of community distributing tasks.
+Figure \ref{fig_dynamic_taxtation} illustrates the results of our experiment having web services with average instability values of 0 to 0.5 and having relative subside value $\lambda$ if 1,1.3,1.6 and 2.
+The \emph{Cost / Income} charts on right column, shows having subside value of 1.3 incurs the least cost and increases the community income significantly.
+Subsiding values of 1.6 and 2 , incur a lot of cost to community and only slightly increase the community revenue.
+Also the role of subsiding is much more obvious when we have unstable web services.
+In scenarios where web services are 100\% stable, subsiding cost will hardly be compensated by community revenue.
 
@@
 
-\section{Related Work}\label{s:relatedwork}
-
-Game theory provides a rich set of frameworks and mathematical tools for rational agents seeking to maximise their profit and efficiency through choosing best available streteghies in multi-agent enviroments.
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=3in]{avg_task_ws_done.eps}
+\includegraphics[width=3in]{avg_qos_ws_done.eps}
+\includegraphics[width=3in]{avg_avail_ws_done.eps}
+\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
+(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
+\end{figure}
+
+Finally, in our last experiment, we compare our work with the work in \cite{10.1109/TSC.2012.12} which we call it \emph{High Availability Coalition Method} because of nature of their community valuation function, which considers community availability as main consideration.
+Their community formation model is very different than ours, however we have been very careful to make the experiment environment as fair and similar as possible.
+We limited our maximum community size by 5 in order to have communities with almost the same size.
+In their method, they have used web services as backups rather than active collaborative players, and they only get task when the first web service in an ordered chain fails to perform the task.
+However with recent advancement in cloud and hardware infrastructures availability is less of an issue for web services, and web services are highly available.
+Part(a) of figure \ref{fig_avail_method} shows our method performs almost performs tasks successfully with rate of three times more than \emph{High Availability Method} because of real cooperative nature and task distribution of our algorithm.
+The average quality of service of tasks performed is also better since our method considers all quality of service metrics mentioned in table \ref{qosws}.
+Part(c) shows the availability of community from end user point of view.
+The \emph {High Availability Method} almost has 100\% uptime since they use web services as backups, so the chance of job failing reduces significantly as community members increase.
+In our method we have more chance of fail for each web service, however with some subsiding, and hiring a few more web service they can compensate the low chance of failure of web services in our community.
+
+%\section{Related Work}\label{s:relatedwork}
+
+%Game theory provides a rich set of frameworks and mathematical tools for rational agents seeking to maximise their profit and efficiency through choosing best available streteghies in multi-agent enviroments.
 

### 2013-07-05 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 
-As mentioned in section \ref{s:tax} in order to help community stability, is to subside the community by a relative coefficient ($\lambda$) so the value of $\lambda V(C)$ is devided among the community members.
+As mentioned in section \ref{s:tax} in order to help community stability, is to subside the community by a relative coefficient ($\lambda$) so the value of $\lambda v(C)$ is devided among the community members.
 We have analysed the effect of subsiding and the cost it incurs to our web service communities.

### 2013-07-05 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 a mechanism for community membership requests and selections of
-web services in the scenarios where established communities
-already exist. Moreover, we analyze the scenarios where
-communities are not established yet and web services can form multiple communities. The ultimate objective is to
+web services in the scenarios where there is interaction between one community and many web services 
+and scenarios where web services can join multiple established communities. The ultimate objective is to
 develop a mechanism for web services to form stable groups
@@
 near-optimal (welfare-maximizing) communities. The theoretical and
-simulation results show that our algorithms provide web services
-and community owners with applicable and near-optimal decision
+extensive simulation results show that our algorithms provide web services
+and community owners, in real-world like environments, with applicable and near-optimal decision
 making mechanisms.
@@
 In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
-DBLP:conf/IEEEscc/KhosravifarABT11} proposed mechanisms to help
+DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
 users and services maximize their gain. A two-player
@@
 parameters.
+
+In \cite{10.1109/TSC.2012.12} a cooperative scheme among autonomous 
+web services based on coalitional game theory has been introduced. They have proposed an algorithm to 
+reach individually stable coalition partition for web services in order to
+maximize their efficiency. The communities choose new web services on the promise 
+that no it would benefit the community without decreasing any other web service's
+income. In their model, the worth of community is evaluated with a lot of emphasis on 
+availability metric and also considering price and cost values only. The community structure is based on a coordination chain,
+where a web service is assigned as a \emph{primary} web service and the community task destribution
+method, will initially invoke primary web service and only if the primary web service is unavailable
+will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to 
+have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays 
+with recent advancement in cloud and hardware infrastructures availability is less of an issue. So the backup web services 
+in their model have a very low chance of getting jobs, especially the ones further in chain which is huge waste of web service
+capability.
 
@@
 Part(a) of figure \ref{fig_avail_method} shows our method performs almost performs tasks successfully with rate of three times more than \emph{High Availability Method} because of real cooperative nature and task distribution of our algorithm.
+This result shows using web services as backups, and not as real collabrative players is a huge waste of web service capability since they have very low chance of getting jobs and its the primary web service (the first in their coordination chain) which does most of the work.
 The average quality of service of tasks performed is also better since our method considers all quality of service metrics mentioned in table \ref{qosws}.

### 2013-07-06 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 characterized by a requests rate $(R_{C})$ from users. Each web
-service comes with a given QoS ($QoS_{ws}$) from which the
-throughput $T_{ws}$ is excluded. This exclusion allows us to build
-our analysis on the particular value of $T_{ws}$. Throughput is
-the average rate of tasks a web service can perform per time unit.
-Thus, web services perform tasks with an average output quality of
-$QoS_{ws}$ and a throughput rate of $T_{ws}$. In this setting, we
-define the value of the coalition of the web services within a
-community as a function increasing in both $T_{ws}$ and $QoS_{ws}$
-as follows:
-\begin{equation*}
-output(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
-\end{equation*}
-\setlength{\abovedisplayshortskip}{2pt}
-\begin{equation}\label{eq:valuation}
-v(C) = \left\{
-  \begin{array}{l l}
-    output(C) & \quad \text{if $\sum_{ws}{T_{ws}} \leq R_{C}$}\\
-    output(C) \times \frac{R_{C}}{\sum_{ws}{T_{ws}}} & \quad \text{if $\sum_{ws}{T_{ws}} > R_{C}$}
-  \end{array} \right.
-\end{equation}
-
-The output of a coalition of web services is a function of the
+service comes with a given QoS ($QoS_{ws}$). The worth of a community 
+$v(C)$ is set to Out(C) based on equation \ref{out_c}.
+
+As mentioned in previous section, the worth and output of a 
+community of web services is a function of the
 throughput and provided QoS. If the throughput rate is more than

### 2013-07-11 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 Communities are virtual groups of web services having similar
-functionalities, but probably different non-functional quality
+functionalities \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,Liris-3375}, but probably different non-functional quality
 attributes, which form the QoS parameters. When communities are
@@
 maximize their efficiency. The communities choose new web services on the promise 
-that no it would benefit the community without decreasing any other web service's
-income. In their model, the worth of community is evaluated with a lot of emphasis on 
-availability metric and also considering price and cost values only. The community structure is based on a coordination chain,
+that it would benefit the community without decreasing any other web service's
+income. In their model, the worth of community is evaluated with high emphasis on 
+availability metric and considering price and cost values only. The community structure is based on a coordination chain,
 where a web service is assigned as a \emph{primary} web service and the community task destribution
-method, will initially invoke primary web service and only if the primary web service is unavailable
+method, will initially invoke the primary web service and only if the primary web service is unavailable
 will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to 
 have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays 
-with recent advancement in cloud and hardware infrastructures availability is less of an issue. So the backup web services 
-in their model have a very low chance of getting jobs, especially the ones further in chain which is huge waste of web service
-capability.
+with recent advancement in cloud and hardware infrastructures availability is becoming less of an issue. So the backup web services 
+in their model have a very low chance of getting jobs, especially the ones further in chain, which is huge waste of web services
+capabilities.
 
@@
 parameters and some basic cooperative game theory concepts. 
-Section \ref{s:model} presents our solution model in three
+Section \ref{s:model} provides the problem statement and some numerical examples.
+Section \ref{s:game_solution} presents our solution model in two
 different scenarios. Section \ref{s:resutls} describes our
@@
 
-Finally, in our last experiment, we compare our work with the work in \cite{10.1109/TSC.2012.12} which we call it \emph{High Availability Coalition Method} because of nature of their community valuation function, which considers community availability as main consideration.
+Finally, in our last experiment, we compare our work with the work in \cite{10.1109/TSC.2012.12} which we call it \emph{High Availability Coalition} method, because of nature of their community valuation function, which focuses on community availability as main consideration.
 Their community formation model is very different than ours, however we have been very careful to make the experiment environment as fair and similar as possible.
@@
 However with recent advancement in cloud and hardware infrastructures availability is less of an issue for web services, and web services are highly available.
-Part(a) of figure \ref{fig_avail_method} shows our method performs almost performs tasks successfully with rate of three times more than \emph{High Availability Method} because of real cooperative nature and task distribution of our algorithm.
+Part(a) of figure \ref{fig_avail_method} shows our method performs almost performs tasks successfully with rate of three times more than \emph{High Availability Coalition} method because of real cooperative nature and task distribution of our algorithm.
 This result shows using web services as backups, and not as real collabrative players is a huge waste of web service capability since they have very low chance of getting jobs and its the primary web service (the first in their coordination chain) which does most of the work.
@@
 Part(c) shows the availability of community from end user point of view.
-The \emph {High Availability Method} almost has 100\% uptime since they use web services as backups, so the chance of job failing reduces significantly as community members increase.
+The \emph {High Availability Coalition} method almost has 100\% uptime since they use web services as backups, so the chance of job failing reduces significantly as community members increase.
 In our method we have more chance of fail for each web service, however with some subsiding, and hiring a few more web service they can compensate the low chance of failure of web services in our community.

### 2013-07-11 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 Communities are virtual groups of web services having similar
-functionalities \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,Liris-3375}, but probably different non-functional quality
+functionalities \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7}, but probably different non-functional quality
 attributes, which form the QoS parameters. When communities are

### 2013-07-16 proposal/proposal/Proposal File/chapter5.tex
Proposal

\setcounter{chapter}{5}
\chapter{Milestones}
In this chapter, we describe the phases of our plan for exploring the research challenges and investigating the research issues identified in Chapter 4. This chapter also includes research methodology and future publication plan.

\section {Research Methodology and Time Line}

    \par The goal of the research project of my Ph.D program is to propose a technically and economically feasible architecture for path stability in MANETs environment.

    \begin{figure}
                \begin{center}
                \includegraphics[width=16cm, height=22cm]{Figures/timetable.eps}\label{Timetable}
                \caption{Research milestones and time line}
                \end{center}
\end{figure}

   % To investigate the architecture of MANETs, we will experiment on backup path, protection, transmission range, interference, and multi Path modeling and analysis on 3D MANETs technologies. We will apply an efficient clustering algorithm for the hierarchical placement of equipment in the above mentioned access network architecture. We will develop mathematical models for different architectures. We will also investigate the protection schemes for these architectures.

The time duration of each task includes the modeling of the proposed solution,  its implementation, validation, performance evaluation  and  publication of its outcome.

\section {Publication Plan}

### 2013-07-24 proposal/proposal/Abstract.tex
Added new proposal files

--- 2013-07-06 papers/coalition-journal-extension/coalition_journal.tex
@@
-%% bare_jrnl_compsoc.tex
-%% V1.3
-%% 2007/01/11
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE Computer
-%% Society journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% andbgf
-%% http://www.ieee.org/
+\begin{center}
+{\LARGE\textbf{Abstract}}
+\end{center}
 
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-% Note that the a4paper option is mainly intended so that authors in
-% countries using A4 can easily print to A4 and see how their papers will
-% look in print - the typesetting of the document will not typically be
-% affected with changes in paper size (but the bottom and side margins will).
-% Use the testflow package mentioned above to verify correct handling of
-% both paper sizes by the user's LaTeX system.
-%
-% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
-% draft mode.
-%
-% The Computer Society usually requires 10pt for submissions.
-%
-\documentclass[10pt,journal,cspaper,compsoc]{IEEEtran}
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[12pt,journal,compsoc]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-\ifCLASSOPTIONcompsoc
-  % IEEE Computer Society needs nocompress option
-  % requires cite.sty v4.0 or later (November 2003)
-  % \usepackage[nocompress]{cite}
-\else
-  % normal IEEE
-  % \usepackage{cite}
-\fi
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
-% not currently provide for hyperlinked citations.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
-%
-% Note that some packages require special options to format as the Computer
-% Society requires. In particular, Computer Society  papers do not use
-% compressed citation ranges as is done in typical IEEE papers
-% (e.g., [1]-[4]). Instead, they list every citation separately in order
-% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
-% package with the nocompress option which is supported by cite.sty v4.0
-% and later. Note also the use of a CLASSOPTION conditional provided by
-% IEEEtran.cls V1.7 and later.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
-% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-\usepackage{amsfonts}
-\usepackage{amssymb,amsmath}
-
-% *** MATH PACKAGES ***
-%
-%\usepackage[cmex10]{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-%\usepackage{mdwmath}
-%\usepackage{mdwtab}
-% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
-% especially mdwmath.sty and mdwtab.sty which are used to format equations
-% and tables, respectively. The MDWtools set is already installed on most
-% LaTeX systems. The lastest version and documentation is available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-%\usepackage{eqparbox}
-% Also of notable interest is Scott Pakin's eqparbox package for creating
-% (automatically sized) equal width boxes - aka "natural width parboxes".
-% Available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%\usepackage[tight,normalsize,sf,SF]{subfigure}
-%\else
-%\usepackage[tight,footnotesize]{subfigure}
-%\fi
-% subfigure.sty was written by Steven Douglas Cochran. This package makes it
-% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
-% work, it is a good idea to load it with the tight package option to reduce
-% the amount of white space around the subfigures. Computer Society papers
-% use a larger font and \sffamily font for their captions, hence the
-% additional options needed under compsoc mode. subfigure.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at:
-% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
-% subfigure.sty has been superceeded by subfig.sty.
-
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false]{caption}
-%  \usepackage[font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false]{caption}
-%  \usepackage[font=footnotesize]{subfig}
-%\fi
-% subfig.sty, also written by Steven Douglas Cochran, is the modern
-% replacement for subfigure.sty. However, subfig.sty requires and
-% automatically loads Axel Sommerfeldt's caption.sty which will override
-% IEEEtran.cls handling of captions and this will result in nonIEEE style
-% figure/table captions. To prevent this problem, be sure and preload
-% caption.sty with its "caption=false" package option. This is will preserve
-% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
-% (recommended due to many improvements over 1.2) of subfig.sty supports
-% the caption=false option directly:
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-%
-% The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-% The latest version and documentation of caption.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Documentation is contained in the stfloats.sty comments as well as in the
-% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
-% does not allow \baselineskip to stretch. Authors submitting work to the
-% IEEE should note that IEEE rarely uses double column equations and
-% that authors should try to avoid such use. Do not be tempted to use the
-% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
-% not format its papers in such ways.
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley and Jeff Goldberg.
-% This package may be useful when used in conjunction with IEEEtran.cls'
-% captionsoff option. Some IEEE journals/societies require that submissions
-% have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.3.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% For subfigure.sty:
-% \let\MYorigsubfigure\subfigure
-% \renewcommand{\subfigure}[2][\relax]{\MYorigsubfigure[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat/subfig command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
-% Read the url.sty source comments for usage information. Basically,
-% \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
-\title{Efficient Coalition Formation \\ for Web Services}
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
-%
-%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
-% lists the Computer Society journals use for "first footnote" author
-% affiliations. Use \IEEEcompsocthanksitem which works much like \item
-% for each affiliation group. When not in compsoc mode,
-% \IEEEcompsocitemizethanks becomes like \thanks and
-% \IEEEcompsocthanksitem becomes a line break with idention. This
-% facilitates dual compilation, although admittedly the differences in the
-% desired content of \author between the different types of papers makes a
-% one-size-fits-all approach a daunting prospect. For instance, compsoc 
-% journal papers have the author affiliations above the "Manuscript
-% received ..."  text while in non-compsoc journals this is reversed. Sigh.
-
-\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
-        John~Doe,~\IEEEmembership{Fellow,~OSA,}
-        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
-\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell is with the Department
-of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
-GA, 30332.\protect\\
-% note need leading \protect in front of \\ to get a newline within \thanks as
-% \\ is fragile and will error, could use \hfil\break instead.
-E-mail: see http://www.michaelshell.org/contact.html
-\IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
-\thanks{}}
-
-% note the % following the last \IEEEmembership and also \thanks - 
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-% 
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
-
-% The paper headers
-\markboth{Journal of \LaTeX\ Class Files,~Vol.~6, No.~1, January~2007}%
-{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% The publisher's ID mark at the bottom of the page is less important with
-% Computer Society journal papers as those publications place the marks
-% outside of the main text columns and, therefore, unlike regular IEEE
-% journals, the available text space is not reduced by their presence.
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2007 IEEE}
-% or like this to get the Computer Society new two part style.
-%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2007 IEEE}%
-%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark (Computer Society jorunal
-% papers don't need this extra clearance.)
-
-% for Computer Society papers, we must declare the abstract and index terms
-% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
-% command as these need to go into the title area created by \maketitle.
-\IEEEcompsoctitleabstractindextext{%
-\begin{abstract}
-%\boldmath
 Web services are loosely-coupled business applications willing to
@@
 making mechanisms.
-\end{abstract}
-% IEEEtran.cls defaults to using nonbold math in the Abstract.
-% This preserves the distinction between vectors and scalars. However,
-% if the journal you are submitting to favors bold math in the abstract,
-% then you can use LaTeX's standard command \boldmath at the very start
-% of the abstract to achieve this. Many IEEE journals frown on math
-% in the abstract anyway. In particular, the Computer Society does
-% not want either math or citations to appear in the abstract.
-
-% Note that keywords are not normally used for peer review papers.
-\begin{keywords}
-Web services; Cooperative game theory; Community of services;
-\end{keywords}}
-
-% make the title area
-\maketitle
-
-% To allow for easy dual compilation without having to reenter the
-% abstract/keywords data, the \IEEEcompsoctitleabstractindextext text will
-% not be used in maketitle, but will appear (i.e., to be "transported")
-% here as \IEEEdisplaynotcompsoctitleabstractindextext when compsoc mode
-% is not selected <OR> if conference mode is selected - because compsoc
-% conference papers position the abstract like regular (non-compsoc)
-% papers do!
-\IEEEdisplaynotcompsoctitleabstractindextext
-% \IEEEdisplaynotcompsoctitleabstractindextext has no effect when using
-% compsoc under a non-conference mode.
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\section{Introduction and Related Work}
-
-\IEEEPARstart{O}{ver} the past years, online services have become part of many
-scalable business applications. The increasing reliance on
-web-based applications has significantly influenced the way web
-services are engineered. Web services provide a set of stateless
-software functions accessible at a network address over the web.
-The recent developments are shifting web services from passive and
-individual components to autonomous and group-based components
-where interaction, composition, and cooperation are the key
-challenges \cite{ICWS2011-1,SCC2011-1}. The main objective is to
-achieve a seamless integration of business processes, applications
-and web services. Delivering high quality services considering the
-dynamic and unpredictable nature of the Internet is still a very
-critical and challenging issue.
-
-The need for highly available and responsive services has called
-for grouping and collaborative mechanisms of loosely-coupled web
-services, particularly in business settings. The idea of grouping
-web services within communities and the way those communities are
-engineered so that web services can better collaborate have been
-proposed and investigated in
-\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
-Communities are virtual groups of web services having similar
-functionalities, but probably different non-functional quality
-attributes, which form the QoS parameters. When communities are
-used, users send their requests to the masters of those
-communities, which are responsible of managing the communities,
-forwarding the requests to the suitable member web services and
-checking the credentials of those members. Communities aim to
-provide higher service availability and performance than what
-individual web services can provide. The high availability of
-services and the community resilience to failure are guaranteed
-since web services can cooperate and replace each other within the
-same community and since there is no single point of failure in
-the communities architecture.
-
-Most of the recent work on communities of services are either
-user-centric and focus on user satisfaction
-\cite{Chun02user-centricperformance} or system-centric and focus
-on the whole system throughput, performance and utilization. There
-are many contributions in distributed, grid, cluster and cloud
-services which are system-centric. However, in real world
-environments and applications, both users and service providers
-are self-interested agents, aiming to maximize their own profit.
-In those environments, both parties (users and services) will
-collaborate as long as they are getting more benefits and payoff.
-
-In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
-DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
-users and services maximize their gain. A two-player
-non-cooperative game between web services and community master was
-introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this
-game-theoretic model, the strategies available to a web service
-when facing a new community are requesting to join the community,
-accepting the master's invitation to join the community, or
-refusing the invitation to join. The set of strategies for
-communities are inviting the web service or refusing the web
-service's join request. Based on their capacity, market share and
-reputation, the two players have different set of utilities over
-the strategy profiles of the game. The main limits of this game
-model are: 1) its consideration of only three quality parameters,
-while the other factors are simply ignored; and 2) the
-non-consideration of the web services already residing within the
-community. The game is only between the community master and the
-new web service, and the inputs from all the other members are
-simply ignored. The consideration of those inputs is a significant
-issue as existing web services can lose utility or payoff because
-of the new member, which can results in an unhealthy and unstable
-group. The problem comes from the fact that the existing members
-should collaborate with the new web services, so probably their
-performance as a group can suffer. Existing members may even
-deviate and try to join other communities if they are unsatisfied.
-Those considerations of forming stable and efficient coalitions
-are the main contributions of our paper.
-
-In \cite{DBLP:conf/IEEEscc/LimTMB12} a 3-way satisfaction approach
-for selecting web services has been proposed. In this approach,
-the authors proposed a web service selection process that the
-community masters can use. The approach considerers the efficiency
-of all the three involved parties, namely users, web services and
-communities. In this work, it is shown how the gains of these
-parties are coupled together using a linear optimization process.
-However, the optimization problem in this solution tends to
-optimize some parameters considering all web services regardless
-of their efficiency and contribution to the community's welfare.
-Moreover, there are no clear thresholds for accepting or rejecting
-new web services. The solution of the optimization problem could,
-for instance, suggest web services already residing within the
-community to increase or decrease their capacity to cover up the
-weakness of other parties in the system. However, a high
-performing web service could deviate anytime it finds itself
-unsatisfied within the community instead of adjusting its service
-parameters.
-
-In \cite{10.1109/TSC.2012.12} a cooperative scheme among autonomous 
-web services based on coalitional game theory has been introduced. They have proposed an algorithm to 
-reach individually stable coalition partition for web services in order to
-maximize their efficiency. The communities choose new web services on the promise 
-that no it would benefit the community without decreasing any other web service's
-income. In their model, the worth of community is evaluated with a lot of emphasis on 
-availability metric and also considering price and cost values only. The community structure is based on a coordination chain,
-where a web service is assigned as a \emph{primary} web service and the community task destribution
-method, will initially invoke primary web service and only if the primary web service is unavailable
-will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to 
-have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays 
-with recent advancement in cloud and hardware infrastructures availability is less of an issue. So the backup web services 
-in their model have a very low chance of getting jobs, especially the ones further in chain which is huge waste of web service
-capability.
-
-\textbf{Contributions.} In this paper, we use game theory to
-propose a cooperative game model for the aggregation of web
-services within communities. The solution concepts of our
-cooperative game seeks to find efficient ways of forming
-coalitions (teams) of web services so that they can maximize their
-gain and payoff, and distribute the gain in a fair way among all
-the web services. Achieving Fairness when the gain is distributed
-among the community members is the main factor to keep the
-coalition stable as no web service will expect to gain better by
-deviating for the community. In other words, the coalition is made
-efficient if all the members are satisfied. We first propose a
-representation function for communities of web services based on
-their QoS attributes. By using this function, we can evaluate the
-$worth$ of each community of web services. When facing new
-membership requests, a typical community master checks whether the
-new coalition having the old and new set of web services will keep
-the community stable or not. The community master will reject the
-membership requests if it finds out that the new coalition would
-be unstable, preventing $any$ subset of web services from gaining
-significantly more by deviating from the community and joining
-other communities or forming new ones. The computation of
-solutions for cooperative game theory problems is combinatorial in
-nature and proven to be NP-complete \cite{Algorithmic}, making
-this computation impractical in real world applications. However,
-using the concepts of coalition stability, we propose
-approximation algorithms running in polynomial time providing web
-services and community masters with applicable and near-optimal
-decision making mechanisms.
-
-The rest of paper is organized as follows. Section
-\ref{s:preliminaries} describes the architecture, considered
-parameters and some basic cooperative game theory concepts.
-Section \ref{s:model} presents our solution model in three
-different scenarios. Section \ref{s:resutls} describes our
-experiments and results. Finally, Section \ref{s:conclusion},
-concludes the paper and identifies future work.
-
-% Computer Society journal papers do something a tad strange with the very
-% first section heading (almost always called "Introduction"). They place it
-% ABOVE the main text! IEEEtran.cls currently does not do this for you.
-% However, You can achieve this effect by making LaTeX jump through some
-% hoops via something like:
-%
-%\ifCLASSOPTIONcompsoc
-%  \noindent\raisebox{2\baselineskip}[0pt][0pt]%
-%  {\parbox{\columnwidth}{\section{Introduction}\label{sec:introduction}%
-%  \global\everypar=\everypar}}%
-%  \vspace{-1\baselineskip}\vspace{-\parskip}\par
-%\else
-%  \section{Introduction}\label{sec:introduction}\par
-%\fi
-%
-% Admittedly, this is a hack and may well be fragile, but seems to do the
-% trick for me. Note the need to keep any \label that may be used right
-% after \section in the above as the hack puts \section within a raised box.
-
-% The very first letter is a 2 line initial drop letter followed
-% by the rest of the first word in caps (small caps for compsoc).
-% 
-% form to use if the first word consists of a single letter:
-% \IEEEPARstart{A}{demo} file is ....
-% 
-% form to use if you need the single drop letter followed by
-% normal text (unknown if ever used by IEEE):
-% \IEEEPARstart{A}{}demo file is ....
-% 
-% Some journals put the first two words in caps:
-% \IEEEPARstart{T}{his demo} file is ....
-% 
-% Here we have the typical use of a "T" for an initial drop letter
-% and "HIS" in caps to complete the first word.
-%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
-%for IEEE Computer Society journal papers produced under \LaTeX\ using
-%IEEEtran.cls version 1.7 and later.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-%I wish you the best of success.
-
-%\hfill mds
-
-%\hfill January 11, 2007
-
-\section{Preliminaries}\label{s:preliminaries}
-
-In this section, we discuss the parameters and preliminary
-concepts that we use in the rest of the paper.
-
-\subsection{The Architecture}
-
-Our system consists of three main types of entities working
-together:
-
-\emph{1) Web services} are rational entities\footnote{The term
-rational is used here in the sense that web services are utility
-maximizers} providing services to end users. They aim to maximize
-their individual income by receiving enough requests from end
-users. In order to increase their revenue, web services seek for
-more tasks if they have the capacity and throughput to do so. Web
-services can join communities to have better efficiency by
-collaborating with others, to have access to higher market share,
-and to have opportunity of receiving a bigger task pool from end
-users. Throughout this paper, in
-our equations, we refer to web services as $ws$ and to the set of
-web services hosted by a given community as $C$. To simply the
-notation, sometimes we simply write $ws$ instead of $ws \in C$ to
-go through the elements $ws$ of the set $C$.
-
-\emph{2) Master Web Services} or the community coordinators, are representatives of the
-communities of web services and responsible for their management.
-Communities receive requests from users and aim to host a healthy
-set of web services to perform the required tasks. They seek to
-maximize user satisfaction by having tasks accomplished according
-to the desired QoS. In fact, higher user satisfaction will bring
-more user requests and increase the market share and revenue of
-the community.
-
-\emph{3) Users} generate requests and try to find the best
-available services. User satisfaction is abstracted as function of
-quantity and quality of tasks accomplished by a given service.
-
-\subsection{Web Service Parameters}\label{ws_parameters}
-
-Web services come with different quality of service parameters.
-These parameters with a short description are listed in Table
-\ref{qosws}.
-
-\begin{table}[!t]
-\centering
-\caption{List of web service QoS parameters.}
-\begin{tabular}{|c|c||c|c|}
-\hline
-\textbf{Parameter} & \textbf{Definition} \\
-\hline\hline
-$Availability$ & Probability of being available during \\
-&a time frame \\
-$Reliability$ & Probability of successfully handling \\
-&requests during a timeframe\\
-$Successability$ & Rate of successfully handled requests \\
-$Throughput$ & Average rate of handling requests \\
-$Latency$ & The average latency of services\\
-$Capacity$ & Amount of resources available\\
-$Cost$ & Mean service fee \\
-$Regulatory$ & Compliance with standards, law and rules\\
-$Security$ & Quality of confidentiality \\ 
-&and non-repudiation\\
-\hline
-\end{tabular}
-\label{qosws}
-\end{table}
-
-We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
-which has aggregated and normalized each of these parameters to a
-real value between 0 and 1. Since requests are not shared among
-web services and are distributed among all of them inside a
-community, each one of them comes with a given QoS denoted by
-$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain
-aggregation function of the parameters considered in Table
-\ref{qosws}. We use this quality output later in evaluating the
-community \emph{worth} or \emph{payoff} function.
-
-\subsection{Web Service Communities}\label{webservice-communities}
-
-Figure \ref{fig_community} represents the architecture of web service communities.
-The communities are basicly an abstract model of web services, they aggrigate web services and communicate with other entities such as UDDI registeries and users, using identical protocols as web services.
-Web services join communities to increase their utility by having a larger market share and task pool.
-Community cordinators or master web services are responsible for community development, managing membership requests from web services and distributing user tasks among the community members.
-Communitiy coordinators try to attract quality web services and keep the community as stable and productive as possible to gain better reputation and user satisfaction which results in having a higher market share for the community.
-The way the web services reside inside communities and how communities of web services are engineered is described comprehensivly in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
-
-\begin{figure*}[!t]
-\centerline{\includegraphics[width=6.25in]{community.eps}}
-\caption{Architecture of Web Service communities}
-\label{fig_community}
-\end{figure*}
-
-\subsection{Cooperative Game Concepts}
-Cooperative game is a branch of game theory that studies
-strategies of self-interested entities or agents in a setting
-where those agents can increase their payoff by binding agreements
-and cooperating in groups. We let $N$ be a set of players. Any
-subset $S$ of $N$ can form a group called $coalition$. A
-\emph{coalitional game} is a pair $G = (N, v)$ where $v$ is called
-a \emph{characteristic function}, which given a coalition, is a
-function $v: 2^N \to \mathbb{R}$ mapping the set of players of the
-coalition to a real number $v(S)$, the worth of $S$. This number
-usually represents the output or payoff or again the performance
-of these players working together as coalition.  If a coalition
-$S$ is formed, then it can divide its worth, $v(S)$ in any
-possible way among its members. The payoff vector $x \in
-\mathbb{R}^S$ is the amount of payoff being distributed among the
-members of the coalition $S$. The payoff vector satisfies two
-conditions:
-
-\begin{itemize}
-    \item $x_i \geq 0$ for all $i \in N$, and
-    \item $\sum_{i \in S} x_i \leq v(S)$
-\end{itemize}
-
-The second criteria is called the \emph{feasibility} condition,
-according to which, the payoff for each agent cannot be more than
-the coalition total gain. A payoff vector is also \emph{efficient}
-if the payoff obtained by a coalition is distributed amongst the
-coalition members: $\sum_{i \in S} x_i = v(S)$. This definition of
-the characteristic function works in \emph{transferable utility}
-(TU) settings, where utility (i.e., payoff) is transferable from
-one player to another, or in other words, players have common
-currency and a unit of income is worth same for all players
-\cite{myerson1991game}.
-
-When dealing with cooperative games, two issues need to be
-addressed:\\ 1. What coalitions to form? \\
-2. How to reward each member when a task is completed?\\
-%
-The following definitions help address these two issues.
-
-%\subsubsection{Shapley value}
-
-{\bf Definition 1 (Shapley value)} Given a cooperative game $(N,
-v)$, the \emph{Shapley value} of player $i$ is given
-by\cite{shapley_value}:
-\begin{equation}\label{eq:shapley}
-\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} }
-\frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))
-\end{equation}
-
-\emph{Shapley value} is a unique and fair solution concept for
-payoff distribution among the members of the coalition. It
-basically rewards members with the amount of marginal contribution
-they have to the coalition.
-
-%\subsubsection{Core}
-
-{\bf Definition 2 (Core)} A payoff vector $x$ is in the $core$ of
-a coalitional game $(N, v)$ if and only if:
-\begin{equation}\label{eq:core}
-\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S)
-\end{equation}
-
-The core is basically a set of payoff vectors where no subset of
-players $S^\prime$ could gain more than their current payoff by
-deviating and making their own coalition $\sum_{i \in S^\prime}
-x_i \geq v(S^\prime)$. The sum of payoffs of the players in any
-sub-coalition $S$ is at least as large as the amount that these
-players could earn by forming a coalition by their own. In a
-sense, it is analogue to Nash equilibrium, except that core is
-about deviations from groups of entities. The core is the
-strongest and most popular solution concept in cooperative game
-theory. However, its computation is a combinatorial problem and
-becomes intractable as the number of players increases. The core
-of some real-world problem games may be empty, which means having
-the characteristic function of the game $(N,v)$, there might be no
-possible distribution of payoff assuring stability of subgroups.
-
-{\bf Definition 3 (Convex cooperative games)} A game $(N,v)$ with
-characteristic function $v(S)$ is convex if:
-\begin{equation}\label{eq:convex}
-v(S) + v(T) \leq v(S \cup T) + v (S \cap T), \forall S,T \subseteq
-N.
-\end{equation}
-
-According to a classic result by Shapley \cite{S1971cores}, convex
-games always have a non-empty core. We will use a variation of
-convexity condition in our algorithm to check whether our
-coalitions are stable.
-
-\subsubsection*{$\epsilon$-core}\label{s:epsilon}
-%\emph{$\epsilon$-Core:}
-%\\
-When the \emph{core} set of a game is empty, it means no coalition
-of players can gain anything by deviating. An outcome would be
-unstable if a coalition can benefit even by a small amount from
-deviating, which is a strong requirement. In fact, in some
-situations, deviations can be costly, or players may have loyalty
-to their coalitions, or even it can be computationally intractable
-to find those small benefits. It would only make sense for a
-coalition to deviate if the gain from a deviation exceeds the cost
-of performing the deviation. \emph{$\epsilon$-core} relaxes the
-notion of the core, and only requires that no coalition would
-benefit significantly, or within a constant amount($\epsilon$) by
-deviating (see Equation \ref{eq:core}).
-
-\begin{equation}\label{eq:core2}
-\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
-\end{equation}
-
-\subsubsection*{Coalition Structure Formation}\label{sec:coalition}
-
-Coalition structure formation is the problem of finding the best
-partition of web services into teams. In these settings, the
-performance of an individual service is less important than the
-\emph{social welfare} of the whole system, which is the sum of the
-values of all teams. Having the game $(N,v)$, a coalition
-structure $(CS)$ is \emph{socially optimal} if $CS$ belongs to set
-$\operatorname*{arg\,max}_{CS} v(CS)$ where $v(CS)$ is the sum of
-the values of all coalitions inside $CS$. $v(CS) = \sum_{C \in
-CS}v(C)$.
-%The outcome of a characteristic function game in coalition structure settings, consists of two parts; first a disjoint partition of players (agents) into coalitions, called a \emph{coalition structure} (CS) and second a \emph{payoff vector} as mentioned in cooperative game solution concepts, which distributes the value of each coalition among its members.
-
-\section{Problem Formulation and Modeling}\label{s:model}
-
-In this section, we present the web service and community coordinator's intractions, the task distribution process and revenue models in web service communities.
-
-\subsection{Task destribution}
-
-As mentioned in section \ref{webservice-communities}, communities are robust service providers with well stablished market share and reputation.
-By maintaining their reputation and performance, they attract  end users which choose them as service providers to perform their tasks.
-The community master is characterizd by a request rate $(R_C)$ from users.
-Each web service comes with a given QoS ($QoS_{ws}$) from which the throughput $Tr_{ws}$ is excluded.
-This exclusion allows us to build our analysis on the particular value of $Tr_{ws}$.
-Throughput is the average rate of tasks a web service can perform per time unit.
-Thus, web services perform tasks with an average output quality of $QoS_{ws}$ and a throughput rate of $Tr_{ws}$.
-
-The community master uses a slightly modified \emph{weighted fair queuing} method to distribute task among its members.
-The goal is to allocate incoming tasks to web services with a rate matching throughput value of $Tr_{ws}$.
-In \emph{weighted fair queuing} method \emph{all} the input flow is multiplexed along different paths, however in our case if the input rate $(R_C)$ of the community is more than summation of throughput values of web services, some of the input tasks will be queued and served with delay.
-Thus, the amount of tasks performed by community is $\sum_{ws \in C}{(Tr_{ws})}$ when $\sum_{ws}{Tr_{ws}} \leq R_{C}$.
-However, when the community has more web services having more total throughput value than community's request rate $(R_C)$ the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $R_C \times \frac{Tr_{ws}}{\sum_{ws}{Tr_{ws}}}$ for each web service ($ws$) and the total rate of tasks being performed is $R_C$, the community's receiving request rate.
-
-While distributing tasks, the community master can verify the performance, throughput and quality of tasks being performed by web services.
-It can recognize if web services are capable of doing the amount of tasks they advertised.
-If for any reason there is a decline in quality metrics or throughput, the master community will announce the new parameters and community masters and members can consider those values as benchmark for future performance calculations and also penalize them.
-Therefor its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities.
-Also it's important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.
-
-\subsection{Community Revenue}
-
-The communities and web services earn revenue by performing tasks.
-The total gain is function of quality ($QoS_{ws}$) and quantity($Tr_{ws}$) of tasks being performed.
-As mentioned in section \ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain aggregation function of the parameters considered in Table \ref{qosws}.
-We have adopted a linear equal weigth average over all QoS parameteres listed in table \ref{qosws} excluding the $Throuput$ and $Cost$ parameters.
-A community has the option to weigh specific QoS patameters more or less depending on the expectations of their clients.
-
-The maximum potential output $(PO(C))$ of a community is aggregation of number of tasks, times their quality, for each web service participating as a member of the community:
-
-\begin{equation}
-PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
-\end{equation}
-
-If the summation of throughput ($Tr_{ws}$) values of community members exceeds the input task rate of the community ($R_C$) the community cannot perform at its maximum potential.
-It means community has more web services than it needs for performing input task load.
-Therefore, in these cases, the actual output has to be normalized to the ammount of tasks being performed.
-
-\begin{equation}\label{out_c}
-Out(C) = \left\{
-  \begin{array}{l l}
-    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{C}$}\\
-    PO(C) \times \frac{R_{C}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{C}$}
-  \end{array} \right.
-\end{equation}
-
-The revenue function of the web service community, is a linear function of $Out(C)$ with a positive constant multiplier.
-
-\subsection{Case Study}
-
-In this section, we analyse a few numerical examples and discuss the motivation of web services and community intractions and the strategies they can adopt and the revenue they can earn adopting different strategies.
-
-%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[!t]
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-\caption{Three web services of example 1}
-\label{example_1}
-\centering
-\begin{tabular}{c c c c}
-\hline
-$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
-\hline
-1 & 0.8 & 4 & 3.2\\
-2 & 0.8 & 5 & 4.0\\
-3 & 0.8 & 3 & 2.4\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}[!t]
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-% \caption{Three web services}
-\label{example_1_2}
-\centering
-\begin{tabular}{c c || c c}
-\hline
-Community & Worth & Community & Worth\\
-\hline
-$\left\{1\right\}$ & 3.2 & $\left\{1,2\right\}$ & 7.2\\
-$\left\{2\right\}$ & 4.0 & $\left\{1,3\right\}$ & 6.8\\
-$\left\{3\right\}$ & 2.4 & $\left\{2,3\right\}$ & 6.4\\
-$\left\{1,2,3\right\}$ & 8.0\\
-\hline
-Community $R_C$: 12\\
-\hline
-\end{tabular}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[!t]
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-\caption{Three web services of example 2}
-\label{example_2}
-\centering
-\begin{tabular}{c c c c}
-\hline
-$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
-\hline
-1 & 0.8 & 5 & 4.0\\
-2 & 0.7 & 6 & 4.2\\
-3 & 0.7 & 4 & 2.8\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}[!t]
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-% \caption{Three web services}
-\label{example_2_2}
-\centering
-\begin{tabular}{c c || c c}
-\hline
-Community & Worth & Community & Worth\\
-\hline
-$\left\{1\right\}$ & 4.0 & $\left\{1,2\right\}$ & 7.4\\
-$\left\{2\right\}$ & 4.2 & $\left\{1,3\right\}$ & 6.8\\
-$\left\{3\right\}$ & 2.8 & $\left\{2,3\right\}$ & 7.0\\
-$\left\{1,2,3\right\}$ & 7.3\\
-\hline
-Community $R_C$: 10\\
-\hline
-\end{tabular}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We present an example with a community with $R_C$ value of 10, and three web services each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}.
-The worth of a community is calculated based on $Out(C)$ equation (\ref{out_c}) which is the amount of output being generated by the community.
-The first table in figure \ref{example_1} lists the web services with their aggregated $QoS_{ws}$ parameters, their task input rate while working alone, and also their $Th_{ws}$ throughput value.
-The second table shows all the possible communities and their worth.
-The values suggest, communities having more web services have better gain and output.
-However community tries to distribute the gain between web services.
-Sometimes it is impossible to share the gain between all web services in a way no subset of them would individually gain more if they had their own group.
-In this example, the value community of ${ws_1}$ and ${ws_2}$ is 7.2, with ${ws_3}$ joining the community the value of community increases to 8.0, however there is no way to distribute the value among web services, where ${ws_1}$ and ${ws_2}$ can earn 7.2, and ${ws_3}$ earn at least 2.4, which they could earn before joining the community.
-This makes the group unstable.
-In the example of table \ref{example_2}, we even have situations where a web service (${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$) decreases the value of community.
-The reason is, the community is already full and all tasks are almost being distributed and new community with bad quality can degrade the average quality of tasks being done by the community.
-In both examples, the request of joining of web service ${ws_3}$ should be rejected by the community.
-
-%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[!t]
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-\caption{Three web services of example 3}
-\label{example_3}
-\centering
-\begin{tabular}{c c c c}
-\hline
-$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
-\hline
-1 & 0.8 & 10 & 5\\
-2 & 0.8 & 20 & 5\\
-3 & 0.8 & 30 & 5\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}[!t]
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-% \caption{Three web services}
-\label{example_3_2}
-\centering
-\begin{tabular}{c c || c c}
-\hline
-Community & Worth & Community & Worth\\
-\hline
-$\left\{C_1\right\}$ & 0 & $\left\{C_2\right\}$ & 0\\
-$\left\{C_1, ws_1\right\}$ & 8 & $\left\{C_2, ws_1\right\}$ & 8\\
-$\left\{C_1, ws_2\right\}$ & 16 & $\left\{C_2, ws_2\right\}$ & 16\\
-$\left\{C_1, ws_3\right\}$ & 16 & $\left\{C_2, ws_3\right\}$ & 24\\
-$\left\{C_1, ws_1, ws_2\right\}$ & 16 & $\left\{C_2, ws_1, ws_2\right\}$ & 24\\
-$\left\{C_1, ws_1, ws_3\right\}$ & 16 & $\left\{C_2, ws_1, ws_3\right\}$ & 32\\
-$\left\{C_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_2, ws_2, ws_3\right\}$ & 32\\
-$\left\{C_1, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_2, ws_1, ws_2, ws_3\right\}$ & 32\\
-$\left\{C_1, C_2, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
-$\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
-\hline
-Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
-\hline
-\end{tabular}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Now we consider another example, in which we have different communities with different market share, ${R_C}$ values.
-Web services also have a small share of market independently, providing them with a small task pull.
-In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the $social welfare$.
-In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1, ws_3\right\}$, which yields a total value of $32 + 16 = 48$.
-In these types of scenarios, the goal is to reach stability, adopting a distributed approach where all players have the power of choice on the decision of whether or not they join a coalition.
-The communities usually start the game having some established members, encountering new web services, the communities may exchange web services and new web services would join them having at least one player gaining utility, without hurting any other participant.
-In this example if we initially having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1\right\}$ and a ${ws_3}$ as new web service, ${ws_3}$ joining ${C_1}$ would hurt at least itself or $ws_2$, however ${ws_3}$ joining ${C_2}$ would not hurt any participants and ${ws_3}$ would earn more within the community and the community will have enough web services performing the incoming tasks from users.
-
-\section{Web Service Cooperative Games}\label{s:game_solution}
-
-In this section, we present different web service community models
-and focus on the problem of how both web services and community
-masters as rational entities would adopt strategies to maximize
-their payoff.
-
-\subsection {Web Services and One Community}
-
-In this scenario, we assume the existence of a typical community
-managed by its master, and web services need to join it to be able
-to get requests from the master. The community master is
-characterized by a requests rate $(R_{C})$ from users. Each web
-service comes with a given QoS ($QoS_{ws}$). The worth of a community 
-$v(C)$ is set to Out(C) based on equation \ref{out_c}.
-
-As mentioned in previous section, the worth and output of a 
-community of web services is a function of the
-throughput and provided QoS. If the throughput rate is more than
-the master's input request rate, it means the web services inside
-the community are capable of serving more requests than the
-demand. Considering this factor, the valuation function is
-designed to balance the output performance so that it matches the
-exact throughput rate and QoS the web service can provide within
-the particular community.
-%** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests.
-**
-
-In this first scenario, we only consider one grand coalition and
-analyze the system from the point of view of one single master web
-service and a collection of web services. The master web service
-decides which members can join
-%or should leave%
-the community and distributes the requests and income among its
-community members (see Figure \ref{fig_sim1}).
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{s1.eps}`
-\caption{Web Services and A Grand Community}
-\label{fig_sim1}
-\end{figure}
-
-The membership decision is made based on throughput and \emph{QoS}
-of the considered web service. The goal is to have quality web
-services in the community so it stays stable and no other web
-services would have incentives to deviate and leave the coalition
-$C$. Therefore, a basic method would be to check the core of the
-coalition $C$ considering all the current community members (all
-web services already residing within the community) and the new
-web service. This algorithm uses the \emph{Shapley value}
-distribution method as described in Equation \ref{eq:shapley} to
-distribute the gain of $v(C)$ among all the members and then
-checks if the \emph{Shapley value} payoff vector for this
-community having the characteristic function $v(C)$ is in the
-\emph{core}. In the \emph{Shapley value} payoff vector, the payoff
-for each web service $ws_i$ is calculated based on its marginal
-contribution $v(C \cup {i}) - v(C)$ over all the possible
-different permutations in which the coalition can be formed, which
-makes the payoff distribution fair. Because of going through all
-the possible permutations of subsets of $N$, the nature of the
-\emph{Shapley value} is combinatorial, which makes it impractical
-to use as the size of our coalitions grows. However, it is proven
-that in convex games, the \emph{Shapley value} lies in the core
-\cite{DBLP:conf/ijcai/GrecoMPS11, myerson1991game}. Thus, if the
-\emph{Core} is non-empty, the payoff vector is a member of the
-\emph{Core}. The following proposition is important to make our
-algorithm tractable.
-% so in our algorithm we check the core membership of this payoff vector.
-
-%\ref{eq:convex}.
-
-\newtheorem{theorem}{Proposition}
-%\begin{theorem}[Einstein-Podolsky-Rosenberg]
-\begin{theorem}\label{proposition1}
-A game with a characteristic function $v$
-is convex if and only if for all $S$, $T$, and $i$ where $S
-\subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in
-N$,
-%For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
-\begin{equation}\label{eq:convex_snow}
-v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
-\end{equation}
-\end{theorem}
-
-%\begin{Proposition}\label{proposition} A game with a characteristic function $v$
-%is convex if and only if for all $S$, $T$, and $i$ where $S
-%\subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in
-%N$,
-%For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
-%\begin{equation}\label{eq:convex_snow}
-%v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
-%\end{equation}
-%\end{Proposition}
-
-\begin{proof} 
-We first prove the ``only if'' direction:
-%\\$~~~~$\textbf{1}. ``only if'' direction:\\
-\\$~~~~$\ \textbf{1}. ``only if'' direction:\\
-%\setlength{\abovedisplayshortskip}{2pt}
-Assume:\\
-\vspace{-0.5cm}
-\begin{gather*}\label{convexsnowproof}
-v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\})
-- v(T)
-\\
-\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq v (T \cup \left\{i\right\}) + v(S)
-\end{gather*}
-
-Considering $S \subseteq T$:
-\setlength{\abovedisplayshortskip}{2pt}
-\begin{gather*}
-S \cup \left\{i\right\} = (S \cup \left\{i\right\}) \cup T
-\\
-T = (S \cup \left\{i\right\}) \cap T
-\end{gather*}
-
-By setting $A = S \cup \left\{i\right\}$ and $B = T$ we have:
-\setlength{\abovedisplayshortskip}{2pt}
-\begin{gather*}
-v(S \cup \left\{i\right\}) + v(T) \leq v (T \cup \left\{i\right\}) + v(S)
-\\
-\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq 
-\\
-v((S \cup \left\{i\right\}) \cup T) + v((S \cup \left\{i\right\}) \cap T)
-\\
-\rightarrow v(A) + v(B) \leq v(A \cup B) + v(A \cap B)
-\end{gather*}
-Consequently, the game is convex.
-
-\textbf{2}. ``if'' direction:\\
-Assume the game is convex. Thus, for all $A, B \subset N$, we
-have: \setlength{\abovedisplayshortskip}{2pt}
-\begin{gather*}
-v(A) - v(A \cap B) \leq v(A \cup B) - v(B)
-\end{gather*}
-
-By setting $S \cup \left\{i\right\} = A$ and $T = B$ where $S \subseteq T$:
-\setlength{\abovedisplayshortskip}{2pt}
-\begin{gather*}
-v(S \cup \left\{i\right\}) - v((S \cup \left\{i\right\}) \cap T) \leq v(T \cup (S \cup \left\{i\right\})) - v(T)
-\\
-\rightarrow v(S \cup \left\{i\right\}) - v(S) \leq v(T \cup \left\{i\right\}) - v(T)
-\end{gather*}
-
-\end{proof}
-
-Thus, in order to keep the characteristic function convex, new web
-services should have more marginal contribution as the coalition
-size grows.
-
-Our algorithm works as follows. We have an established community
-with a master and some member web services already residing in the
-community. A web service would send a join request to the
-community. The ideal solution would be analyzing the \emph{core}
-or \emph{$\epsilon$-core} stability of the group having this new
-member. As the normal core membership algorithm is computationally
-intractable, we exploit Proposition \ref{proposition1} and Equation
-\ref{eq:convex_snow} to check the convexity of our game having
-characteristic function where the new member is added. In the
-equation, we set $C$ to be our community members $(C)$ before
-having the new web service. We assign ${i}$ to the new web
-service, and then verify the equation for $S$, setting $ S = T /
-W1 $ where $W1$ is the set of all possible subsets of the set $N$
-having the size $1$. We can relax the equation a bit by adding a
-constant $\epsilon$ to the left side of the equation. We call this
-method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
-satisfied for all $W1$, we let the new web service join our
-community, since the web service will contribute positively enough
-to make our new community stable. Since only subsets of size $1$
-are checked, the following Proposition holds.
-
-\begin{theorem}\label{complexity1}
-\emph{The run time complexity of Depth-1 Convex-Checker algorithm is
-$O(n)$.}
-\end{theorem}
-
-By this result, we obtain a significant reduction from $O(2^n)$,
-which is the complexity of checking all possible subsets of $N$.
-In our second method, we use the same algorithm, but this time we
-set $W2$ to be the set of all possible subsets of size two and one
-of the community $C$. We call this method \emph{Depth-2
-Convex-Checker} and its run time complexity is still
-linear:
-
-\begin{theorem}\label{complexity2}
-\emph{The run time complexity of Depth-2 Convex-Checker algorithm is
-$O(n^2)$.}
-\end{theorem}
-
-It is possible to develop an anytime algorithm by continuing the
-verification of this condition against all subsets of size $3$,
-$4$, etc. until the algorithm gets interrupted.
-
-\subsection {Web Services and Many Communities}
-
-In this scenario, we consider multiple communities managed by
-multiple master web services, each of which is providing
-independent request pools (see Figure \ref{fig_sim2}). Identical
-to the first scenario, master web services form coalitions with
-web services. We use coalition structure formation methods to
-partition web services into non-empty disjoint coalition
-structures. As mentioned in Section \ref{sec:coalition}, the used
-algorithms \cite{Sandholm1999209,
-DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
-solve key fundamental problems of what coalitions to form, and how
-to divide the payoffs among the collaborators.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{s2.eps}
-\caption{Web Services and Many Communities}
-\label{fig_sim2}
-\end{figure}
-
-In coalition-formation games, formation of the coalitions is the
-most important aspect. The solutions focus on maximizing the
-social welfare. For any coalition structure $\pi$, let
-$v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$,
-which represents the \emph{social welfare}. The solution concepts
-in this area deal with finding the maximum value for the social
-welfare over all the possible coalition structures $\pi$. There
-are $centralized$ algorithms for this end, but these approaches
-are generally NP-complete. The reason is that the number of all
-possible partitions of the set $N$ grows exponentially with the
-number of players in $N$, and the centralized algorithms need to
-iterate through all these partitions.
-%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity.
-However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}.
-In our model, we propose using a distributed algorithm where each
-community master and web service can be a decision maker and
-decide for its own good. The aim is to find less complex and
-distributed algorithms for forming web services
-coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
-The distributed merge-and-split algorithm in
-\cite{DBLP:journals/igtr/AptW09} suits our application very well.
-It keeps splitting and merging coalitions to partitions which are
-preferred by all the players inside those coalitions.
-
-This merge-and-split algorithm is designed to be adaptable to
-different applications. One major ingredient to use such an
-algorithm is a preference relation or well-defined orders proper
-for comparing collections of different coalition partitions of the
-same set of players. Having two partition sets of players, namely
-$P = {P_1,...,P_k}$ and $Q = {Q_1,...Q_l}$, one example would be
-to use the social welfare comparison $\sum^k_{i=1}v(P_i) >
-\sum^l_{j=1}v(Q_j)$. For our scenario, we use \emph{Pareto order}
-comparison, which is an individual-value order appropriate for our
-self-interest web services. In the Pareto order, an allocation or
-partition $P$ is preferred over another $Q$ if at least one player
-improves its payoff in the new allocation and all the other
-players still maintain their payoff ($p_i \geq q_i$ with at least
-one element $p_i > q_i$).
-
-The valuation function $v(C)$ for this scenario is the same as
-\emph{``Web Services and One Community''} scenario. However, in
-order to prevent master web services joining the same community,
-we set $v(C) = 0$ when $C$ has either none, or more than one
-master web service as member.
-
-In this scenario, as new web services are discovered and get ready
-to join communities, our algorithm keeps merging and splitting
-partitions based on the preference function. The decision to merge
-or split is based on the fact that all players must benefit. The
-new web services will merge with communities if $all$ the players
-are able to improve their individual payoff, and some web services
-may split from old communities, if splitting does not decrease the
-payoff of any web service of the community. According to
-\cite{DBLP:journals/corr/abs-cs-0605132}, this sequence of merging
-and splitting will converge to a final partition, where web
-services cannot improve their payoff. More details of this
-algorithm and analysis of generic solutions on coalition formation
-games are described in \cite{DBLP:journals/igtr/AptW09}.
-
-\subsection{Taxtation, Subsiding and Community Stability}\label{s:tax}
-
-We discuessed $core$ as one the preminent solution concepts in cooperative games.
-Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group.
-However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal ammount of $\epsilon$ by deviating.
-Comuunity stability is an attractice property for communities, also communities would benefit by having slightly more web services then having the exact number of web services satisfying task rate cap.
-One reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with.
-
-One way for communities to ensure community stability could be applying a tax, $\epsilon$ ammount of cost for web services changing communities which would make deviation a costly act.
-However this would require all community coordinators to agree on same ammount of taxtation, being governed by some external entities or web services would join communities with lesser ammount of tax.
-Another viable solution in our scenario is to stabilize the game using external subsidies.
-The reason a game is not stable is that the community is not making enough revenue to allocate the players with enough gain.
-A community master can subside its community with a constant coefficient value of $\lambda$.
-Rewarding a community with high number of quality participants with $\lambda v(C)$, where $\lambda \leq 1$.
-Obviously with a big number of $\lambda$ it is always possible to stabilize the community.
-However, this can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable.
-Subsiding or taxting in order to reduce the bargaining power of sub coalitions are called $taxtation$\cite{eps346856} methods.
-
-%Thus, another way to garantee \emph{$\epsilon$-core} stability can be achieved by some surplus payments from community coordinators.
-These concepts of applying cost in coallition values in order to reduce their bargaining power are called $taxtation$ methods\cite{eps346856}.
-
-%The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent's point of view.
-It claims agents for any reason will be not willing to deviate to gain less than $\epsilon$ amount of profit.
-Communities can agree on However, in our case, the community master is willing to keep web services in communities too.
-There are several reasons for this, one reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with.
-To this end, our communities will reward and valuate web services in the community
-
-\section{Experimental Results and Analysis}\label{s:resutls}
-
-In this section, we discuss the experiments we performed for our
-scenarios to validate the applicability and performance of our
-proposed methods in realistic environments. We created a pool of
-web services and populated most of their \emph{QoS} parameters
-from a real world web service dataset
-\cite{DBLP:conf/smc/Al-MasriM09a}. We implemented the simulations
-using Java and executed the simulations on an Intel Xeon X3450
-machine with 6GBs of memory. For other parameters missing from the
-dataset, we used normal random distribution with parameters
-estimated using the method of maximum likelihood.
-
-One of the key criteria reflecting the performance of web service
-coalitions is the user satisfaction. User satisfaction can be
-measured in terms of quality and quantity of requests (or tasks)
-successfully answered by the communities. We initiate the
-communities with few web services, then let rejecting and
-accepting random web services go for a short number of iterations.
-After that, we start the request distribution for the communities
-and let them allocate requests among member web services.
-Thereafter, we measure the average output performance of tasks in
-communities following different methods.
-
-\begin{figure}[!t]
-\centering
-%\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{task_done_opt.eps}
-\includegraphics[width=3in]{task_qos_opt.eps}
-\caption{Part (a): Cumulative number of requests successfully
-done. Part (b): Average QoS of requests performed.}
-\label{performanceall}
-\end{figure}
-
-Figure \ref{performanceall} depicts the results of optimal
-\emph{$\epsilon$-core}, \emph{Depth-1 Convex-Checker},
-\emph{Depth-2 Convex-Checker}, \emph{3-Way Satisfaction}
-\cite{DBLP:conf/IEEEscc/LimTMB12}, and \emph{2 Player
-Non-Cooperative} \cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods
-in \emph{one grand community with many web services} scenario.
-
-For the \emph{optimal core} method we have used the well known \emph{$\epsilon$-core} method as the 
-taxtation method to relax the core condition to help communities, attract web services. 
-We have assigned $\epsilon$ to 15\% of total community worth, $\epsilon = 0.15 \times v(C)$, which allows
-subsets of the coalition to gain maximum 15\% of $v(C)$. In the
-\emph{optimal $\epsilon$-core} method, we capped the coalition
-size to 25 web services, since the method is computationally 
-intractable as number of web services increase and anything more than that would make it
-impractical to run in our simulations. In the other methods, there
-were no cap on size of the community and we had communities of
-size 60 web services at some points. The results show that our
-\emph{depth-2 convex checker} method is performing better compared
-to the other methods and its performance is close to optimal
-\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
-and the \emph{3-Way Satisfaction} method, are also performing well.
-
-\begin{figure}[!t]
-\centering
-%\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{least_core.eps}
-\caption{Analysis of \emph{$\epsilon$-core} set non-emptiness, for different values of $\epsilon$} \label{f_leastcore}
-\end{figure}
-
-As mentioned in Section \ref{s:preliminaries}, the concept of
-\emph{core}, assumes no coalition of players can gain anything by
-deviating, which is a fairly strong requirement, and that is why
-the notion of \emph{$\epsilon$-core} was introduced. Least-Core
-$e(G)$ of a game $G$, is the minimum amount of $\epsilon$ so that
-the core is not empty. We evaluated the non-emptiness of \emph{$\epsilon$-core} set using the
-valuation function and a set of web services. We picked random
-number of web services from the dataset and formed around 10,000
-random coalitions consisting of 3 to 26 web services. We choose 26
-as the maximum number of members in our coalition since it
-is computationally very complex for larger coalitions to verify whether 
-\emph{$\epsilon$-core} set is empty or not.
-Also instead of considering $\epsilon$ amount of constant deviation in \emph{$\epsilon$-core} definition (Equation \ref{eq:core2}), we similarly defined \emph{relative $\epsilon$-core} concept where no coalition would benefit more than \emph{$\epsilon$ $\times$ v(C)} by deviating.
-We set $\epsilon$ between 0 and 1 and verify the \emph{relative $\epsilon$-core} set non-emptiness.
-The results in Figure
-\ref{f_leastcore} illustrates that almost 10\% of our random web
-service coalitions have non-empty \emph{core} solution and
-\emph{$\epsilon$-core} solution is \emph{always} non-empty when we
-let agents gain only 30\% more of $v(C)$ by deviating.
-
-One of the properties of coalition structure formation algorithms
-in our second scenario is that they partition web services with low
-throughput rate so that they usually join coalitions with less
-request rate. Since the characteristic function $v(C)$ and the
-fair Shapely payoff vector is proportional to web services'
-contribution, the web services with small contribution will get
-paid much less in communities having web services with high
-throughput. On the other hand, according to the valuation function
-$v(C)$, web services with high throughput will not contribute well
-to communities with low amount of user requests (low market
-share). The strong web services are likely to deviate from weak
-coalitions, joining a stronger one, which makes the initial
-coalition unstable.
-
-\begin{figure}[!t]
-\centering
-%\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{taxtation.eps}
-\caption{Analysis of community subsiding coefficient $\lambda$ on average community size (a), cost (b), number of tasks performed (c), and average quality of service of tasks performed (d).} \label{f_taxtation}
-\end{figure}
-
-As mentioned in section \ref{s:tax} in order to help community stability, is to subside the community by a relative coefficient ($\lambda$) so the value of $\lambda v(C)$ is devided among the community members.
-We have analysed the effect of subsiding and the cost it incurs to our web service communities.
-Figure \ref{f_taxtation} shows the results.
-In this expirement we have set a community with input task rate $R_C$ of 100 and having abstract web services throuput rate $T_r$ value of a random distribution with average 10 tasks per iteration.
-Part (a) shows the community size increases in a linear fashion as ($\lambda$) increases.
-However the cost is having a slight exponential growth rate since, not only ($\lambda$) increases also the size of the community is also increasing slowly.
-Therefore subsiding can be costly for larger number of $\lambda$ value.
-Part (c) of figure \ref{f_taxtation} depicts the number of tasks done by the community per iteration.
-It is obvoius with $\lambda$ value of 1.3 which is 30\% of community valuation, the number of tasks done almost reaches the input task rate cap of 100 tasks per iteration.
-The average quality of tasks also has a slight increase since the community will be able to afford better and more web services to join the community.
-These results proves with quality metrics our agents as web services have and their collabrative worth, the increase rate of subsiding more 1.3 is not very effective and is costly to perform.
-
-\begin{figure*}[!t]
-\centerline{\includegraphics[width=6.75in]{tax_dyn.eps}}
-\caption{Analysis of community subsiding coefficient $\lambda$ having web service different stability levels of $\tau$ on average community size, number of tasks performed, and average quality of service, and average cost/income of communities.}
-\label{fig_dynamic_taxtation}
-\end{figure*}
-
-In previous experiment, we consider the scenario where all web services are stable will not leave the group and will fulfill their promised quality metrics for a good period of time.
-However, in real world scenarios of web services, this is not always the case.
-This is the reason why community would be interested in subsiding a community of larger group web services, paying a few more web services in order to keep the group reliable from end user point of view.
-In our next scenario, we have introduced the new instability variable $\tau$ from 0 to 1, 0 meaning web services having no instability issues and will perform as they claimed until the end of experiment and 1 meaning very unstable web services which will stop functioning on the first iteration of community distributing tasks.
-Figure \ref{fig_dynamic_taxtation} illustrates the results of our experiment having web services with average instability values of 0 to 0.5 and having relative subside value $\lambda$ if 1,1.3,1.6 and 2.
-The \emph{Cost / Income} charts on right column, shows having subside value of 1.3 incurs the least cost and increases the community income significantly.
-Subsiding values of 1.6 and 2 , incur a lot of cost to community and only slightly increase the community revenue.
-Also the role of subsiding is much more obvious when we have unstable web services.
-In scenarios where web services are 100\% stable, subsiding cost will hardly be compensated by community revenue.
-
-\begin{figure}[!t]
-\centering
-%\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{s2_task_done.eps}
-\includegraphics[width=3in]{s2_task_qos.eps}
-\caption{Part (a): Cumulative number of tasks succesfully done. Part
-(b): Average QoS of tasks performed.} \label{performancemany}
-\end{figure}
-
-In Figure \ref{performancemany}, we compare our \emph{Web Services
-and many Communities} scenario with a method which ignores QoS
-parameters and forms coalitions by allowing web services to join
-only if they have enough requests for themselves. In other words,
-web services can join a community when the request rate is less
-than the throughput of all the member web services. We name this
-method \emph{Random Formation} and use it as a benchmark for our
-QoS-aware coalition formation process. As the results illustrate,
-our method forms better coalitions of web services improving
-performance and satisfaction for both web services and coalitions.
-
-\begin{figure}[!t]
-\centering
-%\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{avg_task_ws_done.eps}
-\includegraphics[width=3in]{avg_qos_ws_done.eps}
-\includegraphics[width=3in]{avg_avail_ws_done.eps}
-\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
-(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
-\end{figure}
-
-Finally, in our last experiment, we compare our work with the work in \cite{10.1109/TSC.2012.12} which we call it \emph{High Availability Coalition Method} because of nature of their community valuation function, which considers community availability as main consideration.
-Their community formation model is very different than ours, however we have been very careful to make the experiment environment as fair and similar as possible.
-We limited our maximum community size by 5 in order to have communities with almost the same size.
-In their method, they have used web services as backups rather than active collaborative players, and they only get task when the first web service in an ordered chain fails to perform the task.
-However with recent advancement in cloud and hardware infrastructures availability is less of an issue for web services, and web services are highly available.
-Part(a) of figure \ref{fig_avail_method} shows our method performs almost performs tasks successfully with rate of three times more than \emph{High Availability Method} because of real cooperative nature and task distribution of our algorithm.
-This result shows using web services as backups, and not as real collabrative players is a huge waste of web service capability since they have very low chance of getting jobs and its the primary web service (the first in their coordination chain) which does most of the work.
-The average quality of service of tasks performed is also better since our method considers all quality of service metrics mentioned in table \ref{qosws}.
-Part(c) shows the availability of community from end user point of view.
-The \emph {High Availability Method} almost has 100\% uptime since they use web services as backups, so the chance of job failing reduces significantly as community members increase.
-In our method we have more chance of fail for each web service, however with some subsiding, and hiring a few more web service they can compensate the low chance of failure of web services in our community.
-
-%\section{Related Work}\label{s:relatedwork}
-
-%Game theory provides a rich set of frameworks and mathematical tools for rational agents seeking to maximise their profit and efficiency through choosing best available streteghies in multi-agent enviroments.
-
-%\subsection{Subsection Heading Here}
-%Subsection text here.
-
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
-
-%\subsubsection{Subsubsection Heading Here}
-%Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection %text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.
-%Subsubsection text here.Subsubsection text here.Subsubsection text here.
-
-%Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection %text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.
-
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that IEEE CS typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-% However, the Computer Society has been known to put floats at the bottom.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command, the
-% \label for the overall figure must come after \caption.
-% \hfil must be used as a separator to get equal spacing.
-% The subfigure.sty package works much the same way, except \subfigure is
-% used instead of \subfloat.
-%
-%\begin{figure*}[!t]
-%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
-%\label{fig_second_case}}}
-%\caption{Simulation results}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE CS papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-
-% An example of a floating table. Note that, for IEEE style tables, the 
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals use top floats exclusively.
-% However, Computer Society journals sometimes do use bottom floats - bear
-% this in mind when choosing appropriate optional arguments for the
-% figure/table environments.
-% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
-% floats. This can be corrected via the \fnbelowfloat command of the
-% stfloats package.
-
-\section{Conclusion}\label{s:conclusion}
-
-In this paper, we proposed a cooperative game theory-based model
-for the aggregation of web services within communities. The goal
-of our services is to maximize efficiency by collaborating and
-forming stable coalitions. Our method considers stability and
-fairness for all web services within a community and offers an
-applicable mechanism for membership requests and selection of web
-services. The ultimate goal is to increase revenue by improving
-user satisfaction, which comes from the ability to perform more
-tasks with high quality. Simulation results show that our,
-polynomial in complexity, approximation algorithms provide web
-services and community owners with applicable and near-optimal
-decision making mechanisms.
-
-As future work, we would like to perform more analytical and
-theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the
-characteristic function in web service applications. From web service perspective, the
-work can be extended to consider web service compositions where a
-group of web services having different set of skills cooperate to
-perform composite tasks. Also bargaining theory from cooperating
-game theory concepts can be used to help web services resolve the
-instability and unfairness issues by side payments.
-
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-%\appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
-
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%
-
-%\appendices
-%\section{Proof of the First Zonklar Equation}
-%Appendix one text goes here.
-
-% you can choose not to have a title for an appendix
-% if you want by leaving the argument blank
-%\section{}
-%Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.Appendix two text goes here.
-
-% use section* for acknowledgement
-\ifCLASSOPTIONcompsoc
-  % The Computer Society usually uses the plural form
-  \section*{Acknowledgments}
-\else
-  % regular IEEE prefers the singular form
-  \section*{Acknowledgment}
-\fi
-
-The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...The authors would like to thank...
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-\bibliographystyle{IEEEtran}
-\bibliography{Ehsan}
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-%\begin{thebibliography}{1}
-
-%\bibitem{IEEEhowto:kopka}
-%This is an example of a book reference
-%H. Kopka and P.W. Daly, \emph{A Guide to {\LaTeX}}, third ed. Harlow, U.K.: Addison-Wesley, 1999.
-
-%This is an example of a Transactions article reference
-%D.S.
-Coming and O.G.
-Staadt, "Velocity-Aligned Discrete Oriented Polytopes for Dynamic Collision Detection," IEEE Trans.
-Visualization and Computer Graphics, vol. 14,  no. 1,  pp.
-1-12,  Jan/Feb  2008, doi:10.1109/TVCG.2007.70405.
-
-%This is an example of a article from a conference proceeding
-%H.
-Goto, Y.
-Hasegawa, and M.
-Tanaka, "Efficient Scheduling Focusing on the Duality of MPL Representation," Proc.
-IEEE Symp.
-Computational Intelligence in Scheduling (SCIS '07), pp.
-57-64, Apr.
-2007, doi:10.1109/SCIS.2007.367670.
-
-%This is an example of a PrePrint reference
-%J.M.P.
-Martinez, R.B.
-Llavori, M.J.A.
-Cabo, and T.B.
-Pedersen, "Integrating Data Warehouses with Web Data: A Survey," IEEE Trans.
-Knowledge and Data Eng., preprint, 21 Dec.
-2007, doi:10.1109/TKDE.2007.190746.
-
-%Again, see the IEEEtrans_HOWTO.pdf for several more bibliographical examples. Also, more style examples
-%can be seen at http://www.computer.org/author/style/transref.htm
-%\end{thebibliography}
-
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{biography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
-\begin{IEEEbiography}{Michael Shell}
-Biography text here.
-\end{IEEEbiography}
-
-% if you will not have a photo at all:
-\begin{IEEEbiographynophoto}{John Doe}
-Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.
-\end{IEEEbiographynophoto}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-\begin{IEEEbiographynophoto}{Jane Doe}
-Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.Biography text here.
-\end{IEEEbiographynophoto}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-% that's all folks
-\end{document}

### 2013-07-24 proposal/proposal/chapter1.tex
Added new proposal files

\setcounter{chapter}{1}
%*******************************START INTRODUCTION **********************************
\section{Introduction}\label{sec:intro}
In this chapter we introduce the context of this research, which is about argumentation-based negotiation dialogue games. We also present the motivations behind this work and the research questions. Also, we discuss the objective of this research and our preliminary contributions. Proposal organization is presented in the last section.

\subsection{Context of the research}\label{sec:context}

Autonomous agents and multiagent systems (MAS) provide a technology offering an alternative for the design of intelligent and cooperative
systems. Recently, efforts have been made to develop novel tools, methods, and frameworks to establish the necessary standards for wider
use of MAS as an emerging paradigm ~\cite{Mehdi03}. An increasing interest within this paradigm is on modeling interactions and dialogue systems.
In fact, several dialogue systems have been proposed in the literature for modeling \emph{information seeking} dialogues (e.g.,~\cite{MWParsons03}),
\emph{inquiry} dialogues (e.g.,~\cite{BlackH07,Black09}), \emph{deliberation} dialogues (e.g.,~\cite{Tolchinsky2012}), \emph{persuasion}
dialogues (e.g., ~\cite{Amgoud00}), and \emph{negotiation} dialogues (e.g., ~\cite{KSycara90}), which are our concern in this paper.
Negotiation is a form of interaction in which a group of agents, with conflicting interests, but a desire to cooperate, try to come to a mutually
acceptable agreement on the division of scarce resources~\cite{Rahwan03,Bentahar07}. It is worth noting that in all types of dialogue systems
mentioned above, a dialogue game is a normative model of dialogue, which mainly consists of: i) a set of moves (e.g., challenge, assertion, question, etc.);
ii) one commitment store for each conversant where the advanced moves are stored; iii) a communication language specifying the locution that will be
used by agents during a dialogue for exchanging moves; iv) a protocol specifying the set of rules governing the dialogues; and v) agents' strategies,
which are the different tactics used by agents for selecting their moves at each step in the dialogue~\cite{AmgoudS08}. A dialogue correctly proceeds
as long as the participants conform to the dialogue rules and eventually ends when some termination rules are achieved~\cite{AmgoudS08,Nicolas03,Prakken01}.

In the recent years, argumentation theory has been widely investigated and used to model and analyze dialogue games~\cite{BentaharAIR,BentaharKBS10,Reed06,Mahalakshmi09}.
Argumentation provides a powerful tool to represent, model, and reason about dialogue moves, strategies, and dialogue outcomes. The core idea is the ability
to support moves with justifications and explanations, which play a key role in persuasion and negotiation settings~\cite{GarciaCRS13}. In this paper, we
will focus on the exchanged moves in a dialogue game (i.e., the dialogue itself) and the agents playing these moves when supporting arguments are used.
The main issue we are investigating is the uncertainty index of selecting the right moves during the dialogue, the certainty index that the selected move
will be accepted by the addressee, and the uncertainty index of the whole dialogue. Uncertainty can be thought of as being the inverse of information. Information
about a particular engineering or scientific problem may be incomplete, imprecise, fragmentary, unreliable, vague, contradictory, or even deficient~\cite{RossJA13}.
Uncertainty about values of given variables (e.g., the disease affecting a patient in medical applications) can result from some errors and hence from unreliability
(in the case of sensors) or from different background knowledge (in the case of agents). As a result, it is possible to obtain different uncertain pieces of
information about a given value from different sources~\cite{Jenhani07}. Our aim is to investigate the uncertainty issues that the agent faces when choosing an
argument to play in argumentation-based negotiations. In the literature, many efforts have been deployed to model negotiation. A brief description of those efforts
is given in the following subsection.

A multiagent system is a system where agents (software autonomous entities) are allowed to freely enter and leave the
system, thus making the environment continuously changing. These agents need to communicate with each other, with individual or
collective tasks, with different resources, and different skills. As a result, these agent societies are becoming more and more
similar to the human ones~\cite{Falcone99}.\\
An attractive characteristic of MAS is that agents can act more effectively in groups. Agents are designed to
autonomously collaborate with each other in order to satisfy both their internal goals and the shared external demands
generated by virtue of their participation in agent societies. \\
The languages used by agents to communicate are called Agent Communication Languages (ACLs). The main objective of an
ACL is to model a suitable framework that allows heterogeneous agents to interact and to communicate with meaningful
statements that convey information about their environment or knowledge~\cite{Kone00}. Two main ACLs have been proposed:
the Knowledge Query and Manipulation Language (KQML)~\cite{Finin95}, and the Foundation for Intelligent Physical Agents'
Agent Communication Language (FIPA-ACL)~\cite{Fipa01}.\\
Furthermore, there is an increasing interest on modeling interactions and dialogue systems. Indeed, several
dialogue systems have been proposed in the literature for modeling information seeking dialogues (e.g.~\cite{MWParsons03}),
inquiry dialogues (e.g.,~\cite{BlackH07}), persuasion dialogues (e.g.,~\cite{Amgoud00}) and finally negotiation dialogues
(e.g.,~\cite{KSycara90}).\\
Evaluating multiagent systems and the dialogues taking place between the participants is a very important issue in the recent
developments of multiagent systems. The existing approaches on evaluating these systems are focusing on one aspect at a time, such as
evaluating persuasion dialogues (~\cite{Amgoud00}), and measuring the impact of argumentation (~\cite{Hunter04}). They are more concerned
with proposing dialogue strategies and analyzing dialogues. However, nothing is said about the agents' certainty about their dialogues and
the goodness degree of the agents in the dialogues. In this thesis, we are interested particularly in negotiation dialogue games. In fact,
negotiation is a form of interaction in which a group of agents, with conflicting interests, but a desire to cooperate, try to come to a
mutually acceptable agreement on the division of scarce resources ~\cite{Rahwan03,Bentahar07}. Dialogue games are a set of rules governing the
dialogue. such rules specify the allowed communicative acts agents can perform when participating in  a dialogue. Precisely, we focus in this
work on quantitative negotiation dialogue games such as bargaining. We will focus first on the exchanged moves (i.e. the dialogue itself) in
terms of the certainty index of selecting the right moves during the dialogue, and the certainty index of the whole dialogue. Uncertainty about
values of given variables (e.g. the disease affecting a patient in medical applications) can result from some errors and hence from non-reliability
(in the case of sensors) or from different background knowledge (in the case of agents). As a result, it is possible to obtain different uncertain
pieces of information about a given value from different sources ~\cite{Jenhani07}. The second focus of this thesis is on the agents' strategies in
terms of goodness degree of the agents in the real dialogue (i.e. the dialogue that effectively happened between the participants) and the farness
degree of the agents from the right dialogue (i.e. the best dialogue that can be produced by two agents if they know the knowledge bases of each other).
For example in negotiation setting, the best dialogue is the one in which with a minimum number of moves, two agents can achieve the best agreement for
both of them, if such an agreement exists considering the knowledge bases of these two agents.
%

\subsection{Motivations and research questions}\label{sec:motivation}

Multiagent systems are widely used in everyday life, and to add more value to these systems in the field of software engineering,
they supposed to be measurable. Our motivation is to find a way to measure these systems from different aspects such as measuring
the dialogues, the performance of the participants in the dialogues, and the protocols governing the dialogues, etc. In order to evaluate
dialogues in multiagent systems, we define a new set of measurements from an external agent's point of view. Defining measures for the
participants in the dialogues is another motivation in this thesis. The aim behind developing such measurements is to help engineers and
developers of agent-based systems in evaluating these systems and their performances.\\

\indent When monitoring a dialogue between two or more agents, there are many question that should be answered. In this thesis, we are interested in answering the following questions:

\begin{itemize}
\item How much are agents certain about selecting a move at each dialogue step?
\item How much are agents certain about their dialogues?
\item How good are agents in the real dialogue (i.e. the effective dialogue)?
\item How far are agents from the right dialogue (i.e. the best dialogue given the knowledge bases of the participants)?
\end{itemize}
Answering these questions is undoubtedly complex. Therefore, we do not expect a comprehensive answer to all these questions.

\subsection{Research objectives and contributions}\label{sec:contribution}

The main objective of this thesis is to develop a new set of measurements for negotiation dialogue games to help in evaluating and
comparing different negotiation dialogues with different participants for the same topic. The importance of introducing measures for
negotiation dialogue games at each step of the dialogue such as measuring how much the agent is certain about its move is to help in developing intelligent multiagent systems (MAS) and to help evaluating different agents provided by different developers.\\
\indent Our research aims to ensure that the agents' certainty about their dialogue is fairly represented at each step during
the dialogue by making sure that the agent's certainty about selecting the right move is kept in mind and considered as a property
of multiagent systems.\\
\indent The main contribution of this thesis is the proposition of a new set of measures for dialogue games from an external agent's point of view.
In particular, we introduce two sets of measurements. In the first set  we use Shannon entropy to measure the certainty index of the dialogue.
This involves i) using Shannon entropy to measure the agent's certainty about each move during the dialogue; and ii) using
Shannon entropy to measure the certainty of the agents about the whole dialogue with two different ways. The first way is
by taking the average of the certainty index of all moves, and the second way is by determining all possible dialogues and
applying the general formula of Shannon entropy. In the second set, we are measuring how good are agents in the real dialogue
\emph{(Goodness Degree )}, and measuring how far are agents from the right dialogue \emph{(Farness Degree)}~\cite{Marey09}.

As mentioned earlier, there exist several proposals on the argumentation-based negotiation. Most of them are concerned with proposing protocols to show how agents can
interact with each other, and how arguments and offers can be generated, evaluated and exchanged during the negotiation process. However, none of them has investigated
the agents' uncertainty about the exchanged arguments and how such an uncertainty could be measured at each dialogue step to assist the agents make a better decision. The
uncertainty is generally defined as ``that which is not precisely known''. This definition permits the identification of different kinds of uncertainty arising from different
sources and activities, most of which go unnoticed in analysis. To the best of our knowledge, this work is the first of it's kind in dealing with the agent's uncertainty
while making a decision at each dialogue step in order to achieve an agreement. In this paper, we define a new set of uncertainty measures for dialogue games from an
external agent's point of view. In particular, we distinguish two types of uncertainty: \textbf{Type I} and \textbf{Type II}.

Type I is about the uncertainty of playing the right move (i.e., advancing the right argument) at each dialogue step. For this type, we use Shannon entropy to measure: i) the
uncertainty index of the agent that he is selecting the right move at each step during the dialogue; and ii) the uncertainty index of both agents participating in the dialogue
about the whole dialogue. The latter measurement will be conducted in two different ways. The first way is by taking the average of the uncertainty index of all moves,
and the second is by determining all possible dialogues based on the union of the agents' knowledge bases and applying the general formula of Shannon entropy.

Type II is about the uncertainty of the agent that the selected move (argument) will be accepted by the addressee (from now on we will call this second type of uncertainty
by \emph{uncertainty degree}). In this context, we introduce a new classification of arguments based on their certainty index. These measures are of great importance since
they can be used as guidelines for a protocol in order to generate the best dialogue between autonomous intelligent agents.

Figure \ref{fig1.0} summarizes the whole proposed approach where the certainty index ($CI$) and weighted certainty index ($W\_CI$) of the moves and the whole dialogue are
measured for Type I. For Type II, different cases are considered depending on how many arguments are in use.

\begin{figure}[t]
                \begin{center}
                \includegraphics[width=15cm, height=11cm]{Figures/Approach1.eps}
                \end{center}
                \caption{General overview of the approach}\label{fig1.0}
                \label{Stack}
                \end{figure}

\subsection{Research outline}\label{sec:outline}
The rest of the paper is organized as follows: In Section~\ref{sec:Argumentation}, we present a  brief theoretical background on the argumentation system
and agent's theory, strategic reasoning, tactic reasoning and risk of failure notions are also discussed in this section. In Section~\ref{sec:uncertainty},
we present the agent's uncertainty measures using Shannon entropy, which include type I (measuring the uncertainty of the agent about selecting the right move)
and type II (measuring the uncertainty degree that the selected move will be accepted). Argument classification is also presented in this section. Related work
is discussed in Section~\ref{sec:related}. Finally, conclusion and future work are presented in Section~\ref{sec:conclusion}.

%****************************************** END INTRODUCTION****************************************

### 2013-07-24 proposal/proposal/chapter2.tex
Added new proposal files

\setcounter{chapter}{2}
%*******************************START Background **********************************

\section{Introduction to Multiagent Systems}\label{sec:MAS}

\section{Types of Dialogue Games}\label{sec:DialogueGames}

\section{Negotiation Dialogue Games}\label{sec:Negotiation}
Negotiation is a form of interaction in which a group of self-interested agents with conflicting interests and a desire to cooperate attempt to 
reach  a mutual acceptable agreement on the division of scarce resources.

   \subsection{Negotiation Component}\label{sec:NComp}

   \subsection{Approaches to Automated Negotiation}\label{sec:Nappro}

Three types of approaches have been discussed in MAS literature as the authors argued in~\cite{JenningsPASC01}. These approaches are:
the \textit{game-theoretic} approach, the \textit{heuristic-based} approach, and the \textit{argumentation-based} negotiation (ABN)
approach.

The Game-theoretic approach is based on studying and developing strategic negotiation models based on game-theoretic precedents~\cite{Neumann44,JeffreyG94}.
The basic idea of this approach is to see the negotiation process as a game in which each participant tries to maximize his own utility. While this approach
is very promising in terms of results analysis, it suffers from some drawbacks as the authors argued in ~\cite{AmgoudV11}, due to the assumptions upon which
it is built. The most important ones are (i) the approach allows agents to exchange offers only, but not reasons or justifications, and (ii) the preference relation
$\succeq$ on offers is fixed during a negotiation for an agent. These assumptions are not realistic since in everyday life, other information than offers may be exchanged.
Moreover, it is very common that preferences on offers may change~\cite{AmgoudV11}.

The second approach is heuristic-based. This approach came to overcome some limitations of the game-theoretic approach (e.g., ~\cite{FatimaWJ04,JenningsPASC01}).
Heuristics are ad hoc rules that aim to achieve a good solution, but not necessarily an optimal one. That is why some strong assumptions made in the game-theoretic
approach such as the notion of rationality of agents as well as their resources are relaxed. Even though this approach came to cope with the game-theoretic approach
limitations, it does not solve the problem of the preference relation, i.e., the relation $\succeq$ remains the same during the negotiation~\cite{AmgoudV11}.

The third approach, which is our focus in this paper, is the argumentation-based negotiation approach (ABN). Plenty of research has been done on this approach as
witnessed by many publications, such as ~\cite{AmgoudPM00,Hunter04,Mbarki06,AmgoudDM07,AmgoudV11,EliseYP12}. The basic idea behind this approach is to allow the
participants of the negotiation dialogue not only to exchange offers, but also reasons and justifications that support these offers in order to mutually influence
their preference relation on the set of offers, and consequently to the out come of the dialogue. In~\cite{RahwanSD03}, the authors have introduced a particular
style of argument-based negotiation, namely interest-based negotiation (IBN), which is  a form of ABN in which agents explore and discuss their underlying interests.
%*******************************End Background **********************************

### 2013-07-24 proposal/proposal/chapter3.tex
Added new proposal files

\setcounter{chapter}{3}
\chapter{Contribution and Research Activities}

%******************** START Contribution and Research Activities. ***************
In this chapter we will introduce the important notions in argumentation-based negotiation,  
\section{Argumentation System and Agent Theory}\label{sec:Argumentation}
Let us recall some basic definitions in the argumentation-based negotiation.

\begin{definition}{\emph{[Move].}} \label{Move}
Let $Ag = \{Ag_1,Ag_2, \ldots\}$ be a set of symbols representing agent names that may be involved in a negotiation dialogue $D$. A
move $M_i\in D$ consists of the agent that utters the move: $Speaker(M_i)\in Ag$; the set of agents to which the move is
addressed: $Hearer(M_i)\subseteq Ag$; and the content of the move: $Content(M_i)$.
\end{definition}

For simplification reasons, we will consider bilateral negotiation (i.e., only two agents involved in the dialogue $Ag_1$ and $Ag_2$).
Multi-party dialogues is an important issue that we plan to investigate in future work. During a dialogue, several moves may be uttered.
Those moves constitute a dialogue $D$, which is a sequence of moves denoted by $[M_0$,$M_1$,\ldots,$M_n]$, where $M_0$ is the initial move,
$M_n$ is the final one, and $|D|$ is the length of the dialogue (i.e., $|D| = |[M_0$,$M_1$,\ldots,$M_n]| = n+1$).

In what follows, we assume that the agents exchange the content of the moves during the dialogue as arguments because our approach is
argumentation-based. In argumentation systems the logical language $\pounds$ is essential, we will recall the definition of the
argument concept, a definition of the attack relation between arguments, and the definition of acceptability
from~\cite{Amgoud00}, then we will use these definitions in our approach. Here $\Gamma$ indicates a possibly inconsistent
knowledge base with no deductive closure, and $\vdash$ stands for classical inference.

\begin{definition}{\emph{[Argument].}} \label{Argument}
An argument $Arg$ is a pair $(H, h)$ where $h$ is a formula of $\pounds$ and $H$ a subset of  $\Gamma$ such that: i) $H$ is
consistent, ii) $H \vdash h$ and iii) $H$ is minimal, so that no subset of $H$ satisfying both i and ii exists. $H$ is called the
support of the argument and $h$ its conclusion.
\end{definition}

\begin{definition}{\emph{[Attack].}} \label{Attack}
Let $(H, h)$, $(H^{\prime}, h^{\prime})$ be two arguments. $(H^{\prime}, h^{\prime})$ attacks $(H, h)$ iff $H^{\prime} \vdash
\neg h$. In other words, an argument is attacked iff there is an argument for the negation of its conclusion.
\end{definition}

Our dialogue architecture also involves general knowledge, such as knowledge about the dialogue subject. Agents can also reason about
their preferences in relation to beliefs. The idea is to capture the fact that some facts are believed more than others. For this
reason, we assume, like in~\cite{Mbarki06}, that any set of facts has a preference order over it. We suppose that this ordering
derives from the fact that the agent's knowledge base ($\Gamma$) is stratified into non-overlapping sets $\Gamma_1,\cdots ,
\Gamma_n$ such that facts in $\Gamma_i$ are all equally preferred and are more preferred than those in $\Gamma_j$ where $i < j$. The
preference level of a subset of $\Gamma$ whose elements belong to different non-overlapping sets is defined as follows.

\begin{definition}{\emph{[Preference Level].}} \label{preferenceLevel}
The preference level of a nonempty subset $\gamma$ of $\Gamma$ denoted by level $(\gamma)$ is the number of the highest numbered
layer which has a member in $\gamma$.
\end{definition}
\begin{example}
Let $\Gamma = \Gamma_1 \bigcup \Gamma_2 $ with $\Gamma_1$ = $\{ a, b\}$ and $\Gamma_2$ = $\{ c,d \}$ and $\gamma = \{a\}$ and
$\gamma\prime = \{a,d\}$. We have: level$(\gamma) = 1$ and level$(\gamma\prime) = 2$.
\end{example}

\subsection{Strategic and Tactic Reasoning}\label{sec:reasoning}
A preliminary framework for strategic and tactic reasoning for agent communication was proposed in~\cite{Mbarki06}. This
reasoning framework is specified using argumentation theory combined to a relevance theory. Strategic reasoning enables agents
to decide about the global communication plan in terms of the macro-actions to perform in order to achieve the main dialogue
goal. Tactic reasoning, on the other hand, allows agents to locally select, at each dialogue step the most appropriate
argument according to the adopted strategy.

In this paper, we refine, and use the notion of strategic and tactic reasoning. The agent uses his tactic reasoning at each dialogue
step to measure his uncertainty about selecting the right move to achieve some sub goals of the global goal (i.e., the agreement in our case).
In other words, how agent can select the right argument from a set of possible choices at certain dialogue step depends on his tactic by assigning
different probability values to the different arguments and select the one with higher probability to be accepted by his opponent. On the other hand,
this tactic is based on the adapted strategy that the agent built before starting the negotiation to achieve the agreement. Moreover, we study the
relationship between these two types of uncertainty not only when a unique move is considered, but also when the whole dialogue is being analyzed.

%\subsubsection{Strategic Reasoning}\label{sec:Strategic}
\textbf{Strategic Reasoning}\\
Before engaging in a negotiation, agents must build a global strategy on the sub-goals to achieve. Sub-goals determine the general steps to follow so
that the global goal can be realized. Strategy is subject to the agent's current beliefs and constraints, such as the agent's budget and negotiation
time limit. To achieve the same negotiation goal, an agent can have several alternative strategies reflected by different sets of subgoals. The dialogue
goal, sub-goals, and constraints can be expressed using propositional logic. The set of constraints can be inconsistent, but the sub-set of those constraints
and the sub-set of beliefs the agent decides to consider should be consistent. We define the strategy as a function that associates to a goal and a sub-set
of consistent beliefs and constraints a sub-set of alternatives, each of which is a set of sub goals, which means an element of the set $2^{2^{\mathbb{B}}}$,
where $\mathbb{B}$ is the set of goals.

\begin{definition}{\emph{[Strategy]\footnote{This definition is different than the one proposed in~\cite{Mbarki06}, in the sense that this function
associates a set of sub-goals to a sub-set of agent's knowledge base and constraints instead of associating a set of goals to a set of operational constraint
and a set of conversational criterions.}. }} \label{strategy}
Let $\mathbb{B}$ be a set of goals, $\mathbb{C}$ a set of constraints and $\Gamma$ the agent's knowledge base. A strategy is a function:
\begin{equation}\label{equation2-}
\mathcal{S}: \mathbb{B} \times 2^{\mathbb{C}} \times 2^{\Gamma}
\rightarrow 2^{2^{\mathbb{B}}}
\end{equation}
\end{definition}

%\subsubsection{Tactic Reasoning}\label{sec:tactic}
\textbf{Tactic Reasoning} \\
Tactics allow agents to select one action (i.e., the content of the move or the argument) from a set of possible actions (i.e., set of
arguments) in order to achieve a sub-goal as computed by the adapted strategy. The purpose of this theory is to ensure that the selected argument
is the most appropriate one according to the current context i.e., the less risk of failure, the more favorable and the more preferable one,
which means the move with the higher probability. Our aim is to investigate the uncertainty issues associated with the agent while taking decision
and selecting the arguments. By refining some definition in the work presented in~\cite{Mbarki06} such as the definition of strategy, context,
tactic, and risk of failure. We will advocate some criteria that help to compute and analyze the agents' uncertainty at each negotiation step i.e., at
the tactic level. and based on these criteria we classify the set of possible arguments into three different classes ``\textit{Arguments Classification}",
which will be introduced later on in section~\ref{sec:classification}. This also will help the agents to assign the probability to each possible argument
and use it in measuring the uncertainty using Shannon Entropy as it will be explained in section~\ref{moveuncertainty}. Arguments classification is based
on the relevance of arguments, risk of failure, favorite and preference relations. In the following we will discuss the definitions of these notions.

\textbf{Relevance of Argument.} \\
We define the relevance of argument as in~\cite{Mbarki06} according to the conversation context. This will allow the participants in the dialogue to
select the most relevant argument from the set of possible arguments at certain dialogue step by taking into account the last communicative act as well as the
previous ones. This will give the agents the ability of backtracking in case the choice is shown to be incorrect because the selected argument is not accepted
by the addressee. The arguments are ordered based on their relevance, and the process of selecting arguments is called \emph{Arguments Selection Mechanism}.

%The authors in~\cite{Mbarki06}, have defined the relevance of an argument according to the conversation context. The objective is
%to allow agents to select the most relevant argument from the set of possible arguments at a given dialogue step by taking into
%account the last communicative act as well as the previous ones. This will give the participants the ability of backtracking in
%case the choice is shown to be incorrect because the selected argument is not accepted by the addressee. The arguments are
%ordered based on their relevance, and the process of selecting arguments is called \emph{Arguments Selection Mechanism}.

\textbf{Arguments Selection Mechanism.} \\
Let $\pounds$ be a logical language. We define the conversation context for an agent $Ag_1$ committed in a conversation with
another agent $Ag_2$ as follows:

\begin{definition}{\emph{[Context].}} \label{context}
The conversation context for an agent $Ag_1$ (the speaker) committed in a conversation with an agent $Ag_2$ (the addressee)
is a 7-tuple $C_{Ag_1,Ag_2} = \big<\mathcal{S},\mathcal{T},T,s,P_{Ag_1,Ag_2},CK\big>$ where:
\begin{itemize}
  \item $\mathcal{S}$ is the speaker's strategy;

  \item $\mathcal{T}$ is the current speaker's tactic, which we will define after introducing all the context elements;

  \item $T$ is a formula of $\pounds$ representing the negotiation topic that corresponds to the global goal;

  \item $s$ is a formula of $\pounds$ representing the argument on which the speaker should act;

  \item $P_{Ag_1,Ag_2}$ is the set of $Ag_{1}^{\prime}s$ beliefs about $Ag_{2}^{\prime}s$ beliefs $P^{bel}_{Ag_1,Ag_2}$ and
   about $Ag_{2}^{\prime}s$ preferences $P^{pref}_{Ag_1,Ag_2}$.   Thus $P_{Ag_1,Ag_2}$ = $P^{bel}_{Ag_1,Ag_2} \cup P^{pref}_{Ag_1,Ag_2}$;

  \item $CK$ is the common knowledge that the two agents share about the conversation.
\end{itemize}
In this definition we refine the context definition proposed in~\cite{Mbarki06} by adding the speaker strategy, the current
speaker tactic and the negotiation topic that corresponds to the global goal.
\end{definition}
During negotiation, $CK$ is constantly updated by adding all the information on which the two agents agree, including the accepted
arguments. We also assume that $CK \cap P_{Ag_1,Ag_2} = \emptyset$. In the context $C_{Ag_1,Ag_2}$, the influence of the
strategy on the tactic is reflected through the link between the topic $T$, the current argument $s$ and the strategy
$\mathcal{S}$. Let $\mathbb{T}$ be the set of topics ($T \in \mathbb{T}$), $g$ the current goal ($g \in \mathbb{B}$), $C$ the
sub-set of current constraints ($C \in \mathbb{C}$), $\gamma$ the sub-set of beliefs the agent is currently considering ($\gamma \in
\Gamma$), and $\mathbb{A}$ the set of arguments ($s \in \mathbb{A}$), we define the tactic as follows:

\begin{definition}{\emph{[Tactic]. }} \label{tactic}
A tactic is a function:
\begin{equation}\label{equation2}
\mathcal{T}: \mathbb{T} \times \mathcal{S}(g,C,\gamma) \times
\mathbb{A} \rightarrow \mathbb{B}
\end{equation}
\end{definition}

The key idea is that the current action (at the tactic level) is related to a sub-goal, which is determined by the strategy. From
the operational perspective, the current argument $s$ can attack or support the formula representing the sub-goal $T$. In order to
define the logical relation between $T$ and $s$, the authors in \cite{Mbarki06} introduced the notion of argumentation tree and
the notion of path that are defined as follow.

\begin{definition}{\emph{[Argumentation Tree].}} \label{tree}
Let $Ag$ be the set of participating agents and $Arg \subseteq \mathbb{A}$ be the set of arguments used by the agents in the
dialogue. An argumentation tree $Tr$ is a 2-tuple $Tr =\big<N,\rightarrow\big>$ where:

\begin{itemize}
  \item $N = \{(Ag_i, (H, h)) \mid Ag_i \in Ag, (H, h) \in Arg \}$ is the set of nodes. Each node is described as a pair $(Ag_i, (H, h))$,
  which indicates that the argument $(H, h)$ is used by the agent $Ag_i$.
  \item $ \rightarrow \subseteq  N \times N $ is a relation between nodes. We write $n_0 \rightarrow n_1$ instead of $(n_0, n_1) \in \rightarrow $
  where $\{n_0, n_1\} \subseteq N$. The relation $ \rightarrow $ is defined as follows:
       $(Ag_1, (H, h)) \rightarrow (Ag_2, (H^{\prime}, h^{\prime}))$ iff $Ag_1 \neq Ag_2$ and $(H^{\prime}, h^{\prime})$ attacks $(H, h)$.
\end{itemize}
\end{definition}

\begin{definition}{\emph{[Path]. }} \label{path}
Let $Tr = \big<N, \rightarrow \big>$ be an argumentation tree. A path in $Tr$ is a finite sequence of nodes $n_0, n_1,\cdots , n_m$
such that $\forall i$ ,$   0 \leq i < m $ : $n_i \rightarrow n_{i+1}$.
\end{definition}

In order to distinguish between relevant and irrelevant arguments in a given context  let us recall the definition of irrelevant
arguments:

\begin{definition}{\emph{[Irrelevant Argument]. }} \label{irrelevant}
Let $C_{Ag_1,Ag_2}$ = $\big<\mathcal{S}, \mathcal{T},T, s,P_{Ag_1,Ag_2},CK \big>$ be a conversation context, $Ag$ be the
set of participating agents, $Tr = \big<N, \rightarrow \big>$ be the argumentation tree associated to the conversation, and $(Ag_i,
(H, h))$ be a node in $Tr$ where $i \in \{1, 2\}$. $(H, h)$ is irrelevant in the context $C_{Ag_1,Ag_2}$ iff:

\begin{enumerate}
  \item  There is no path between the node $(Ag_i, (H, h))$ and the root of $Tr$ or;
  \item  $\exists x \in  CK : H \vdash \neg x$.

\end{enumerate}
\end{definition}

The distinction between relevant and irrelevant arguments allows agents to eliminate irrelevant arguments at each dialogue step before
ordering the relevant arguments in order to select the most relevant one.
Agents also have private preferences about different knowledge. Therefore, they may have private preferences about arguments.
This preference relation denoted by $(H, h)  \ll^{Ag_i}_{pref}  (H^{\prime}, h^{\prime})$ means that agent $Ag_i$ prefers the
argument $(H^{\prime}, h^{\prime})$ to the argument $(H, h)$.

\begin{definition}{\emph{[Preference]. }} \label{preference}
Let $(H, h)$ and $(H^{\prime}, h^{\prime})$ be two arguments. $(H, h)  \ll^{Ag_i}_{pref}  (H^{\prime}, h^{\prime})$ iff level $(H^{\prime}) \leq$ level $(H)$.
\end{definition}

Because $\leq$ is an ordering relation, the preference relation $\ll^{Ag_i}_{pref}$ is reflexive, antisymmetric, and transitive.
Agents may also have favorites among their arguments. How an agent favors an argument over others depends on the dialogue type. For
example, in a persuasive dialogue, an agent can favor arguments having more chances to be accepted by the addressee. In order to
characterize this notion, we introduce the notion of weight of an argument. The weight of an argument $(H,h)$ compared to another
argument $(H^{\prime},h^{\prime})$ in the context $C_{Ag_1,Ag_2}$ = $\big<\mathcal{S},\mathcal{T},T, s,P_{Ag_1,Ag_2},CK\big>$ is
denoted by $W_{(H,h)/(H^{\prime},h^{\prime})}^{P_{Ag_1,Ag_2}}$ and is evaluated according to the following algorithm:

\begin{algorithm}{\emph{\textbf{Algorithm} 1.}} \label{algorithm1}\\
\\ Step 1:  $ W_{(H,h)/(H^{\prime},h^{\prime})}^{P_{Ag_1,Ag_2}} = 0 . $ \\
\\Step 2:  $(\forall x \in H),(\forall x^{\prime}  \in H^{\prime} ):
 ( pref(x,x^{\prime}) \in P_{Ag_1,Ag_2}^{pref})\Rightarrow W_{(H,h)/(H^{\prime},h^{\prime})}^{P_{Ag_1,Ag_2}} = W_{(H,h)/(H^{\prime},h^{\prime})}^{P_{Ag_1,Ag_2}}  +  1 $
\end{algorithm}

$pref(x,x^{\prime}) \in P_{Ag_1,Ag_2}^{pref} $ means that $Ag_1$ believes that $Ag_2$ prefers $x$ to $x^{\prime}$. According to
this algorithm, the weight of an argument $(H, h)$ compared to another argument $(H^{\prime}, h^{\prime})$ is incremented by 1
each time $Ag_1$ believes that $Ag_2$ prefers a knowledge in $H$ to a knowledge in $H^{\prime}$. Indeed, each element of $H$ is
compered once to each element of $H^{\prime}$ according to the preference relation. Consequently, the computation algorithm of
the weight of an argument is finite because $H$ and $H^{\prime}$ are finite sets. The favorite relation is denoted by
$\preceq_{fav}^{P_{Ag_1,Ag_2}}$ and the strict favorite relation is denoted by $\prec_{fav}^{P_{Ag_1,Ag_2}}$.  $(H, h)
\preceq_{fav}^{P_{Ag_1,Ag_2}}  (H^{\prime},h^{\prime})$ means that agent $Ag_1$ favors the argument $(H^{\prime},h^{\prime})$ over
the argument $(H, h)$ according to $P_{Ag_1,Ag_2}$. This relation is defined as follows.

\begin{definition}{\emph{[Favorite Argument]. }} \label{favorite}
Let $C_{Ag_1,Ag_2}$ = $\big<\mathcal{S},\mathcal{T},T, s,P_{Ag_1,Ag_2},CK\big>$ be a conversation context and $(H, h)$
and $(H^{\prime},h^{\prime})$ be two arguments in the context $C_{Ag_1,Ag_2}$. We have:
\begin{itemize}
\item $(H, h)\preceq _{fav}^{P_{Ag_1,Ag_2}} (H^{\prime},h^{\prime})$ iff   $ W_{(H,h)/(H^{\prime},h^{\prime})}^{P_{Ag_1,Ag_2}} \leq W_{(H^{\prime},h^{\prime})/(H,h)}^{P_{Ag_1,Ag_2}}$ , \\
\item $(H, h)\preceq _{fav}^{P_{Ag_1,Ag_2}} (H^{\prime},h^{\prime})$ iff   $ W_{(H,h)/(H^{\prime},h^{\prime})}^{P_{Ag_1,Ag_2}} < W_{(H^{\prime},h^{\prime})/(H,h)}^{P_{Ag_1,Ag_2}}$.
\end{itemize}
\end{definition}

In order to allow agents to select the most relevant argument in a conversation context, an ordering relation between relevant
arguments is used. This ordering relation depends on the adopted strategy and is based on the notion of the risk of failure of an
argument. This notion of risk is subjective and there are several heuristics to evaluate it. In this paper, we use a heuristic based
on the fact that $CK$ contains certain knowledge and $P_{Ag_1,Ag_2}$ contains uncertain beliefs. To define this notion
formally, let $|H|_{\emptyset}$ be the number of formulas in $H$ that are not in $CK \cup P_{Ag_1,Ag_2}$, $|H|_{CK}$ be the number
of formulas in $H$ that are in $CK$, and $|H|_{P_{Ag_1,Ag_2}}$ be the number of formulas in $H$ that are in $P_{Ag_1,Ag_2}$.

\begin{definition}{\emph{[Risk of Failure of an Argument]. }} \label{risk}
Let $C_{Ag_1,Ag_2}$ = $\big<\mathcal{S},\mathcal{T},T, s,P_{Ag_1,Ag_2},CK\big>$ be a conversation context and $(H, h)$
and $(H', h')$ be two relevant arguments in the context $C_{Ag_1,Ag_2}$. The risk of failure $risk(H, h)$ of an argument
$(H, h)$ is a function mapping an argument to a natural number that satisfies the following property: $risk(H, h)\geq risk(H',
h')$ iff:
\begin{itemize}
\item   $|H|_{\emptyset} \geq |H'|_{\emptyset}$; or

\item   $|H|_{\emptyset} = |H'|_{\emptyset}$ and $|H|_{CK} \leq
|H'|_{CK}$; or

\item $|H|_{\emptyset} = |H'|_{\emptyset}$, $|H|_{CK} =
|H'|_{CK}$, and $|H|_{P_{Ag_1,Ag_2}} \leq |H'|_{P_{Ag_1,Ag_2}}$.
\end{itemize}
\end{definition}

Other approaches like those used in fuzzy systems to reason with uncertainty (using for example probabilities and possibilities)
can also be used to evaluate the risk of an argument. The advantages of our approach are its straightforward implementation
and additivity over uncertain hypotheses, which means adding uncertain hypotheses increases the risk of failure of an argument.
The relevance ordering relation denoted by $\preceq_r$ is defined as follows.

\begin{definition}{\emph{[Relevance Ordering Relation].}} \label{relevance}
Let $C_{Ag_1,Ag_2} = \big<\mathcal{S},\mathcal{T},T, s,P_{Ag_1,Ag_2},CK\big>$ be a conversation context and $(H, h)$
and $(H^{\prime},h^{\prime})$ be two relevant arguments in the context $C_{Ag_1,Ag_2}$. $(H^{\prime},h^{\prime})$ is more
relevant than $(H, h)$ denoted by $(H, h) \preceq_r (H^{\prime},h^{\prime})$ iff:
\begin{itemize}
\item $risk(H^{\prime},h^{\prime}) < risk(H, h)$; or

\item $risk(H^{\prime},h^{\prime}) = risk(H, h)$ and $(H, h) \prec_{fav}^{P_{Ag_1,Ag_2}} (H^{\prime},h^{\prime})$; or

\item $risk(H^{\prime},h^{\prime}) = risk(H, h)$ and $(H, h) \preceq_{fav}^{P_{Ag_1,Ag_2}} (H^{\prime},h^{\prime})$ and
$(H^{\prime},h^{\prime}) \preceq_{fav}^{P_{Ag_1,Ag_2}} (H,h)$ and $(H,h) \ll_{pref}^{Ag_1} (H^{\prime},h^{\prime}) $.
\end{itemize}
\end{definition}

According to this definition, $(H^{\prime},h^{\prime})$ is more relevant than $(H, h)$ if the risk of $(H, h)$ is greater than the
risk of $(H^{\prime},h^{\prime})$. If the two arguments have the same risk, the more relevant argument is the more favorable one
according to the favorite relation. If the two arguments have the same risk and they are equal according to the favorite relation,
the more relevant argument is the more preferable one according to the preference relation. The two arguments have the same relevance
if in addition they are equal according to the reference relation.

\subsubsection{Computational complexity of the Selection Mechanism}

Computationally speaking, the arguments selection mechanism is based on :
\begin{enumerate}
 \item The elimination of irrelevant arguments;
 \item The construction of new relevant arguments;
 \item The ordering of the relevant arguments using the relevance ordering relation; and
 \item The selection of one of the most relevant arguments.

\end{enumerate}

This process is executed by each participating agent at each dialogue step at the tactical level. The relevant arguments that
are not selected at a step $t_i$, are recorded and added to the set of potential arguments $PA$ because they can be used at a
subsequent step. The set of potential arguments can be viewed as a stack in which the higher level argument is the most relevant one.
A relevant argument constructed at a step $t_i$ and used latter at a step $t_j$ simulates the backtracking towards a previous node in
the argumentation tree and the construction of a new path.

Here we prove that our selection mechanism is tractable if arguments are represented using propositional Horn clauses.
propositional Horn clauses is a restricted language that has been proved to be sufficient to represent and reason about
knowledge in many concrete applications \cite{BentaharIEEEIS2007}. A propositional Horn clause is a disjunction of literals, which are
atomic propositions (called positive literals) or their negations (called negative literals), with at most one positive literal.
Formally, a propositional Horn clause has the form $\neg p_1 \vee \neg p_2 \vee \dots \vee \neg p_n \vee c$ or also $p_1 \wedge p_2
\wedge \dots \wedge p_n \rightarrow c$, which is simply an implication. A propositional Horn formula is a conjunction of
propositional Horn clauses. We focus on a further restriction called propositional definite Horn clauses, where each clause has
exactly one positive literal. A propositional definite Horn formula is a conjunction of propositional definite Horn clauses.
This restriction is of particular interest in modeling argumentation reasoning for negotiation, because formulas of the
type $p_1 \wedge p_2 \wedge \dots p_n \rightarrow c$ are adequate to describe interrelationships between premises (i.e., reasons or
justifications) and conclusions (i.e., offers). Thus, agents could support their offers (the part $c$) as positive literals using the
support $p_1 \wedge p_2 \wedge \dots p_n$.

\begin{theorem}\label{Complexity1}
If arguments are represented in proportional definite Horn clauses, the arguments selection mechanism runs in polynomial time.
\end{theorem}

\noindent\emph{\textbf{Proof.}} \emph{It is known from Bentahar et al. \cite{BentaharIEEEIS2007}, that given a Horn knowledge base
$\Gamma$, a subset $H \subseteq \Gamma$, and a formula $h$; checking whether $(H, h)$ is an argument is polynomial. To decide
if an argument is irrelevant, we have to check if 1) $H \vdash \neg x$ for an $x \in CK$, which can be done in polynomial time
since $H$ is a definite Horn formula; or 2) there is a path from the root to $(H, h)$, which is a graph reachability problem, and
it is known by Jones \cite{Jones} that the problem is in NLOGSPACE. Since NLOGSPACE $\subseteq$ P, the problem can be
solved in polynomial time. To decide about the preference, we only need to compute the level of an argument from the level of a
subset of $\Gamma$, which is  a simple procedure that is obviously polynomial. Computing the favorite argument given two arguments
needs the computation of the arguments' weight, which is again a polynomial procedure as shown by Algorithm 1. To compere two given
arguments using the risk, we only need to compute the number of formulas in $H$ and check if they are part of different sets,
which is a polynomial procedure. Finally, the relevance ordering relation is simply based on comparing risks and favorites, which
are both polynomial, so we are done.}~~$\blacksquare$
 \section{Agent's Uncertainty}\label{sec:uncertainty}

\subsection{Generalities and Overview}

The process of selecting arguments is always associated with a degree of uncertainty. Despite the agent will select the most relevant argument
at each dialogue step using his theory and tactic reasoning, however, there still be a doubt that the selected argument is the right one
and it will be accepted by the addressee.  To measure this uncertainty, we use Shannon entropy as we did in our pervious work ~\cite{MareyBE09}, a
well-known technique that defines and quantifies the information. The idea behind Shannon entropy in information theory is based on the amount of
randomness that exists in a random event. In dialogue games, we assume that at each dialogue step, the agent has different choices of arguments
(i.e., the set of potential arguments $PA$ at that step) and he will select one of them. The selection is based on the speaker's knowledge base and
characterized by an amount of uncertainty over this base and an amount of randomness over the addressee's knowledge, beliefs, and preferences. Indeed,
Shannon entropy is a measure of the uncertainty associated with a random variable (i.e., in our case, the selected argument). The more uncertain we are
about the content of the message, the more informative it is~\cite{CoverT91}.

\begin{definition}{\emph{[Shannon entropy]. }} \label{entropy}
Shannon entropy for a discrete random variable \emph{$X$} taking its values from a set of values \emph{$S$} (sample space),
with probability mass function \emph{$P(x)$} is given by Equation~\ref{equation1}:

\begin{equation}\label{equation1}
H(X) = - \sum_{x\in S} P(x)Log P(x)
\end{equation}

\end{definition}

Shannon entropy $H(X)$ depends on the probability distribution of $X$ rather than the actual values of $X$. The logarithm in
Equation~\ref{equation1} is considered to be of base 2 in the computations. The value of $H(X)$ varies from zero to $Log(|S|)$,
where zero means that there is no uncertainty, while $Log(|S|)$ is the maximum value of uncertainty. In this paper, we aim to
investigate to what extent we can use Shannon entropy in the evaluation of the agent's uncertainty in the dialogue. We place
ourselves in the role of an external observer trying to evaluate the uncertainty of the participants to the dialogue i.e., how
certain/uncertain each agent is about the selected move, how certain/uncertain he is that the selected move will be accepted by
the addressee and the distinction between these tow types of uncertainty. The basic idea is to measure how much the agent is
uncertain about selecting the right move $M_i$ at each step $t_i$ in dialogue $D$ by assuming that there is a set $S_i$ of choices
facing the agent at each dialogue step. Throughout the paper, we will measure the agent's uncertainty using Shannon entropy, then
we normalize it to have a value between zero and one and subtracting it from one to get the agent's certainty for selecting the right
move at that step. We call this measure the \emph{certainty index} ``$CI(M_i)$" of that move, and then we calculate how much the agents
are certain about the whole dialogue using what we call the \emph{certainty index of the dialogue} ``$CI(D)$" by taking the average of
the certainty index of all moves in this dialogue (taking the minimum is another choice that we also discuss).
Furthermore, we measure the certainty index of the whole dialogue by computing all possible dialogues, using the Cartesian product
of all possible moves, and determining the probability of each dialogue, and then applying the general formula of Shannon entropy
for the whole dialogue (exactly as what we do in the case of calculating the certainty of the moves). Moreover, we differentiate
between to types of uncertainty; namely Type 1, and Type 2, and for the first time we classify the arguments into three classes based on
three criteria that we will introduce later on.

To allow agents to refer to their dialogue history, a data structure called commitment store $``CS"$ is used to restore
utterances that agents utter during the dialogue~\cite{Hamblin70}.
Let $Ag_1$ and $Ag_2$ be two agents $Ag_1 \neq Ag_2$. Also, let $\Gamma_{Ag_x}$ be $Ag_x's$ knowledge base ($x \in \{1,2\}$).
$CS_{Ag_x}^{t_i}$ is the commitment store of agent $Ag_x$ at step $t_i$ of the dialogue. Suppose that at step $t_{i-1}$, agent
$Ag_2$ uttered a move. To utter a move at the next step $t_i$, agent $Ag_1$ should consider his knowledge base and the content of
$Ag_2's$ commitment store. Let $m_{i}^j$ be the $j^{th}$ move among the possible moves an agent has at the step $t_i$ and
$P(m_{i}^j)$ the associated probability such that the relationship between the move $M_i$ and $m_{i}^j$ is as follows:

\begin{equation}\label{equation3}
\forall i ~ \exists j : M_{i} = m_{i}^j
\end{equation}

where $M_{i}$ is the selected move the agent utters at the step $t_{i}$, and the production of moves for $Ag_1$ along with their
probabilities is a function of $\Gamma_{Ag_1}$ and $CS_{Ag_2}^{t_i}$:

\begin{equation}\label{equation4}
\zeta(\Gamma_ {Ag_1} \cup  CS_{Ag_2}^{t_i}) = \{(m_{i}^j , P(m_{i}^j)) | m_{i}^j\in S_{i}\}
\end{equation}
where $S_i$ is the set of choices facing the agent at the dialogue step $t_i$.

We belief that such measures can help the participants to the dialogue make a better decisions for playing the most appropriate argument at
each moment (i.e., at the tactical level) to achieve their agreements based on the adapted strategy, and it will help evaluate dialogues and strategies
of the participants to these dialogues. In what follows we introduce the two types of agent's uncertainty.

%In~\cite{MareyBE09}, we proposed a set of metrics using Shannon entropy. We placed ourselves in the role of an external observer
%to evaluate the dialogue. The basic idea is to measure how much the agents are uncertain/certian about selecting the right move
%$M_i$ at each step $t_i$ in dialogue $D$ by assuming that there is a set of potential moves (i.e., arguments) facing the agent at
%each dialogue step. Based on that, we can calculate the certainty index of the dialogue $CI(D)$, which reflects the certainty degree
%of the agents about the whole dialogue. Such measures will help evaluate dialogues and strategies of the
%participants to these dialogues.
%
%In this paper, we extend our previous work to evaluate the uncertainty/certainty index that the selected move will be
%accepted by the addressee and analyze the relationship between these two types of uncertainty (i.e., the agent's uncertainty about
%selecting the right move and the agent's uncertainty that the selected move will be accepted by the addressee). Moreover, we
%analyze special cases in which we cannot consider the certainty index as an indicator of the agent's certainty that the selected
%move will be accepted by the addressee, but as a representation of the agent's certainty about selecting the right move at that step.
%For instance, when there is only one argument, or all the available arguments have the same probability. We belief that such
%measures can help the participants to the dialogue make decisions for playing the most appropriate argument at each moment (at the
%tactical level) to achieve their goals based on the adapted strategy.

%For simplification reasons, we will consider only two agents involved in the dialogue $Ag_1$ and $Ag_2$. Multi-party dialogue
%is an important issue that we plan to investigate in future work. During a dialogue, several moves may be uttered. Those moves
%constitute a dialogue $D$, which is a sequence of moves denoted by $[M_0,M_1,\cdots ,M_n]$, where $M_0$ is the initial move, $M_n$ is
%the final one, and $|D|$ is the length of the dialogue (i.e., $|D|
%= n$).

\subsection{Agent's Uncertainty: Type I}\label{sec:type1}

In this section, we will discuss to what extent we can use Shannon entropy in dialogue games to measure the uncertainty/certainty
index of the agents about their dialogue. To do so, we measure the uncertainty index of the agents about their moves and then we
compute the uncertainty index about the whole dialogue. The following two subsections illustrate these measures.

\subsubsection{Measuring How Certain the Agent is about his Move}\label{moveuncertainty}
To measure the uncertainty index of the agent about his move, we calculate Shannon entropy of that move, which means the agent's
uncertainty about selecting the right move at a given dialogue step. Here we consider only possible moves, which are moves whose
the associated probability is in $[0,1]$. Then we normalize this value by dividing it by the logarithm of the number of all
possible moves at that step. By subtracting the normalized value from one; we get the agent's certainty index about selecting the
right move at this step.

\begin{definition}{\emph{[Move's entropy]. }} \label{Move'sentropy}
Let $D = [M_0, M_1, \ldots, M_n]$ be a negotiation dialogue, and suppose that at each dialogue step $t_i$ a set $S_i$ of moves
$\{m_i^1,m_i^2,\ldots,m_i^k\}$ are possible, and each one of them is associated with a given probability $P(m_i^j) = 1-risk(m_i^j)$,
such that $\sum_{m_i^j\in S_i} P(m_i^j)=1$. Shannon entropy for a random move $M_i$ taking its values from the set of moves $S_i$ is
defined by:
\begin{equation}\label{equation5}
H(M_i) = - \sum_{m_i^j\in S_i}P(m_i^j)Log P(m_i^j)
\end{equation}
\end{definition}

The value of $H(M_i)$ varies from zero to $Log(|S_i|)$, where zero means that there is no uncertainty (i.e., there is only one
choice), while $Log(|S_i|)$ means that the uncertainty is at its maximum value (i.e., all moves have the same probability). We
further normalize $H(M_i)$ to have a metric that ranges from 0 to 1. This can be achieved by dividing $H(M_i)$ by $Log(|S_i|)$. So,
the uncertainty about selecting the right move is given by:

\begin{equation}\label{equation6}
\mu(M_i)=
\begin{cases} 0 & \text{\emph{iff}}~~~Log(|S_i|)=0
\\
H(M_i)/Log(|S_i|) &otherwise
\end{cases}
\end{equation}

\begin{proposition} \label{proposition1}
The uncertainty of a move $M_i$ at a certain step $t_i$ during the dialogue is equal to zero (i.e., $\mu(M_i)=0$) iff at that step the
agent has only one choice.
\end{proposition}

\noindent\emph{\textbf{Proof.}}\\
\emph{$\mu(M_i)= 0 \Leftrightarrow Log(|S_i|)=0$\\
\\ $\Leftrightarrow  |S_i|=1$.~~$\blacksquare$}

So, there is only one move in $S_i$ available to the agent at step $t_i$. Intuitively, at the beginning steps of a dialogue, the
uncertainty is expected to be high as all possible moves have close probabilities, then gradually the uncertainty decreases,
because agents are rational and they learn from each other when advancing in the dialogue.

\begin{proposition}\label{proposition2}
The uncertainty of a move $M_i$ at a certain step $t_i$ during the dialogue is equal to one $($i.e., $\mu(M_i)=1)$ iff at that step,
all the moves in $S_i$ have the same probability.
\end{proposition}

\noindent\emph{\textbf{Proof.}}

\emph{Let us first prove the direct implication $\Rightarrow$. We assume that all the moves at a certain step \emph{$t_i$} have the
same probability, and prove that the uncertainty is equal to one. Without loss of generality, we assume that \emph{$|S_i|=k_i$}. So
we have:
\\ $\mu(M_i) = H(M_i)/Log(k_i)$\\
\\ $= - \sum_{m_i^j\in S_i, j=1}^{k_i}~P(m_i^j)Log P(m_i^j)/Log(k_i)$\\
\\ $= -{k_i}[(1/{k_i})Log(1/{k_i})]/Log(k_i)$\\
\\ $= -[Log(1/{k_i})]/Log(k_i)$\\
\\ $= Log(k_i)/Log(k_i)$\\
\\ $= 1$ \\\\
Let us now prove the inverse implication $\Leftarrow$. We assume that the uncertainty is
equal to one, and prove that all moves have the same probability. So we have:\\
\\ $\mu(M_i) = 1 $   \\
\\ $\Rightarrow 1= H(M_i)/Log(k_i)$\\
\\ $\Rightarrow 1= - \sum_{m_i^j\in S_i, j=1}^{k_i}~P(m_i^j)Log P(m_i^j)/Log(k_i)$\\
\\ $\Rightarrow - Log(k_i)= \sum_{m_i^j\in S_i, j=1}^{k_i}~P(m_i^j)Log P(m_i^j)$\\
\\ $\Rightarrow Log(1/k_i)= \sum_{m_i^j\in S_i, j=1}^{k_i}~P(m_i^j)Log P(m_i^j)$\\
\\ $\Rightarrow Log(1/{k_i})= P(m_i^1)Log P(m_i^1) + P(m_i^2)Log P(m_i^2)+ \ldots + P(m_i^{k_i})Log P(m_i^{k_i})$\\
\\By taking the exponential of both sides of the equation, we obtain:\\
\\ $\exp^{Log(1/{k_i})}=\exp^{P(m_i^1)Log P(m_i^1) + P(m_i^2)Log P(m_i^2)+ \ldots + P(m_i^{k_i})Log P(m_i^{k_i})}$\\
\\ $\Rightarrow 1/{k_i} = \exp^{P(m_i^1)Log P(m_i^1)} * \exp^{P(m_i^2)Log P(m_i^2)}* \ldots * \exp^{P(m_i^{k_i})Log P(m_i^{k_i})}$\\
\\ $\Rightarrow 1/{k_i} = \exp^{Log{P(m_i^1)^{P(m_i^1)}}}* \exp^{Log P(m_i^2)^{P(m_i^2)}}* \ldots * \exp^{Log P(m_i^{k_i})^{P(m_i^{k_i})}}$\\
\\ $\Rightarrow 1/{k_i} = {P(m_i^1)^{P(m_i^1)}}*{P(m_i^2)^{P(m_i^2)}}* \ldots * {P(m_i^{k_i})^{P(m_i^{k_i})}}$\\
\\ $\Rightarrow 1/{k_i} = \Pi_{m_i^j\in S_i, j=1}^{k_i}~{P(m_i^j)^{P(m_i^j)}}$ \\
\\Because $1$ is the maximum uncertainty, the solution of this equation can be obtained by resolving the following optimization problem:
%
\begin{equation*}
Max[\Pi_{m_i^j\in S_i, j=1}^{k_i}~{P(m_i^j)^{P(m_i^j)}}] \\
\end{equation*}
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$subject~ to:$
%
\begin{equation*}
\begin{cases} \sum_{m_i^j\in S_i, j=1}^{k_i}~P(m_i^j)=1\\
0<P(m_i^j)\leq 1 ~~~~~ \forall ~1 \leq j \leq {k_i}
\end{cases}
\end{equation*}
%
Using the nonlinear programming techniques, we can easily find the solution of this  problem, which is:  $\forall ~1 \leq j \leq k ~
P(m_i^j)= 1/{k_i}$}.~~$\blacksquare$

\begin{definition}{\emph{[Move's Certainty Index]}} \label{Move'sCertainty}
Let $D=[M_0, M_1, \ldots, M_n]$ be a negotiation dialogue, and suppose that at each dialogue step $t_i$ a set $S_i$ of moves
$m_i^j$ are possible, and each one of them is associated with a given probability $P(m_i^j)$ such that $\sum_{m_i^j\in
S_i}P(m_i^j)=1$. If Shannon entropy of the move $M_i$ at step $t_i$ is $H(M_i)$, we define the certainty index of the move as
follows:

\begin{equation}\label{equation7}
CI(M_i)=
\begin{cases} 1 & \text{iff}~~~Log(|S_i|)=0
\\
1- H(M_i)/Log(|S_i|) &otherwise
\end{cases}
\end{equation}

\end{definition}

Using the certainty index, we can determine at each dialogue step how much the agent is certain about the move
he can play at that time. The following lemmas are straightforward from Propositions
\ref{proposition1} and ~\ref{proposition2}.

\begin{lemma}\label{lemma1}
The certainty index of a move $M_i$ at a given step $t_i$ in the dialogue is at its maximum value ``1" iff the agent
has only one choice at that step.
\end{lemma}

\begin{lemma}\label{lemma2}
The certainty index of a move $M_i$ at a given step $t_i$ in the dialogue is at its minimum value ``0" iff the agent
has more than one move at the same step with equal probabilities.
\end{lemma}

By considering the uncertainty and certainty index of dialogue moves, agents should resolve at each dialogue step
$t_i$ one of the following equivalent optimization problems.
\begin{enumerate}
  \item  At each dialogue step the agent should minimize the uncertainty index.

    \begin{equation}\label{equation8}
    M_i^* = \underset{\small{M_i}}{\operatorname{argmin}} \, \mu(M_i)
    \end{equation}
  \item  At each dialogue step the agent should maximize the certainty index.
   \begin{equation}\label{equation9}
   M_i^* = \underset{\small{M_i}}{\operatorname{argmax}} \, CI(M_i)
 \end{equation}

\end{enumerate}

\begin{theorem}
There is an algorithm for solving these optimization problems in a polynomial time.
\end{theorem}

\noindent\emph{\textbf{Proof.}} \emph{
Because these problems are equivalent, we consider only one of them, for example the maximization one.
Without loss of generality, we assume that agent $Ag_1$ should solve this problem. The algorithm is as follows:\\
1) $Ag_1$ should calculate the probability of each possible move $m_i^j$ $(1 \leq j \leq k)$ using the \emph{moves probability function}:
 $\zeta(\Gamma_{Ag_1} \cup CS_{Ag_2}^{t_i})$ considering his knowledge base $\Gamma_{Ag_1}$ and $Ag_2's$ commitment store $CS_{Ag_2}^{t_i}$; \\
2) take the move with the highest probability. Because $\Gamma_{Ag_1}$ and $CS_{Ag_2}^{t_i}$ are bounded at each step
$t_i$, this calculation is clearly polynomial and searching the maximum probability is polynomial, so we are done.}
~~$\blacksquare$

This theorem is compatible with the intuition that by adding new information in $CS_{Ag_2}^{t_i}$, the number of possible choices
decreases. However, this is only true when we consider just the next move. When we consider the whole dialogue, the complexity is
much higher.

\begin{example}\label{example1}
Let us consider a negotiation dialogue $D$ between two agents $Ag_1$ and $Ag_2$ such that $D=[M_0, M_1, M_2]$, and the number of
possible moves at each dialogue step is $|S_i|=3$. In the following we explain how to measure the certainty index of the
move $M_0$. Using Equation~\ref{equation7}, we obtain:\\
\\$CI(M_0)= 1- H(M_0)/Log(|S_0|)$\\
\\$CI(M_0)= 1- [(-\sum_{j=1}^{3} P(m_0^j)Log P(m_0^j))/Log(3)]$\\
\\$CI(M_0)= 1+ [(P(m_0^1)Log P(m_0^1)+P(m_0^2)Log P(m_0^2)+P(m_0^3)Log P(m_0^3))/Log(3)]$\\
\\From Table~\ref{Table1}, we have: \\
\\$CI(M_0)= 1+ [((0.33* -1.599) + (0.33 *-1.599)+(0.34 * -1.556))/Log(3)]$\\
\\$CI(M_0)= 1- 1 = 0$\\\\
%
Table~\ref{Table1} shows the possible choices of the moves that facing agent $Ag_1$ at step $t_0$ to play his first move $M_0$ in
the first column, and their associated probabilities in the second column. From the above calculations, we notice that the certainty
index of agent $Ag_1$ about selecting the right move at this step is at its minimum value ``0" because agent $Ag_1$ had different
choices of moves with equal probabilities of acceptance from the addressee agent $Ag_2$. This means that agent $Ag_1$ was uncertain
$100 \%$ about which move he should play.

\begin{table}[tbp]
\centering \caption{Measuring the certainty index of the move
$M_0$ in Example~\ref{example1}.} \label{Table1}
\begin{tabular}{cccc}\hline
\textbf{Possible Moves}&{P($m_0^j$)}&\textbf{Log P($m_0^j$)}&\textbf{P($m_0^j$)Log P($m_0^j$)}\\
\hline
{$m_0^1$}&{0.33}&{-1.599}&{-0.528}\\
{$m_0^2$}&{0.33}&{-1.599}&{-0.528}\\
{$m_0^3$}&{0.34}&{-1.556}&{-0.529}\\
\hline
   & {H($M_0$)=1.58}&{$\mu(M_0)=1$} & {$CI(M_0)=0$} \\
   \hline
\end{tabular}
\end{table}
%
The above calculations and Table~\ref{Table1} are just for the first move $M_0$, and to obtain the certainty index of the other
two moves $M_1$ and $M_2$, we use the same procedure as for $M_0$.

At step $t_1$, agent $Ag_2$ to play his move $M_1$ as a reply to agent $Ag_1$, he had three different choices of moves  with
different values of probabilities $(0.05, 0.12, 0.83)$, such that the sum is equal to one. From the calculation we find that agent
$Ag_2$ was certain about $0.50 \%$, $(i.e., CI(M_1)= 0.50 \%)$ that he will select the move with higher probability $(0.83)$ of
acceptance from agent $Ag_1$. The other two choices that agent $Ag_2$ had were with lower probabilities and he was uncertain
about them.

At step $t_2$, agent $Ag_1$ to reply to agent $Ag_2$ with his move $M_2$, he had different choices of moves with different values of
probabilities $(0.9999,1E-8,1E-8)$, such that the sum is equal to one. Agent $Ag_1$ was then certain almost $100 \%$, and the
certainty index is at its maximum value ``1". This is because all choices that he had are with very low probabilities except one of
them was with very high probability.
\end{example}

In order to highlight the quality of information involved in the selected move in terms of its certainty index, we assign a weight
to this move. We suppose that the selected moves have different weights reflecting the importance degree of the moves. For
example, in some negotiation dialogues, the last moves could be more important than the first moves as they lead to an agreement.
Let $\mathcal{M}$ be the set of all moves. The weight of the move is calculated based on algorithm 1 and assigned to the move using
the following function:

\begin{equation}\label{equation10}
W: \mathcal{M} \rightarrow \mathbb{N}^*
\end{equation}

\begin{definition}{\emph{[Weighted Certainty Index of the Move].}} \label{WeightedCI}
Let $D=[M_0, M_1, \ldots, M_n]$ be a negotiation dialogue, and $CI(M_i)$ the certainty index of the move $M_i$ at a step $t_i$
and $W(M_i)$ the weight of that move at that step. We define the weighted certainty index as follows:

\begin{equation}\label{equation11}
W\_CI(M_i) = W(M_i)*CI(M_i)
\end{equation}

\end{definition}

\subsubsection{Measuring how Certain the Agents are about the Dialogue}\label{dialogueuncertainty}
In section \ref{moveuncertainty}, we discussed how to measure the agent's uncertainty/certainty about his move at each dialogue
step. In this section, we will discuss how to measure the uncertainty/certainty index of the agents about the whole dialogue.
We will present this in two different methods. The first method is by using the average of the calculated uncertainty/certainty index
of all moves in the dialogue. The second one is by calculating the possible number of dialogues and the probability of each one, and
then we apply Shannon entropy in the same way as for the moves. Measuring the certainty of the dialogue by considering the minimum
certainty over all the moves is another way if the agent is very conservative. In this paper, we only focus on the first two methods.

\textbf{Method 1: Using the Average of CI for all Moves}.\\
The basic idea is to measure how much each agent is uncertain/certain about his move at each dialogue step. Then we
calculate how much the two agents are uncertain/certain about the ``whole dialogue" by taking the average of the
uncertainty/certainty index of all the moves in the dialogue.

\begin{definition}{\emph{[Agents' Certainty about the Dialogue]. }} \label{agentsCIDialogue}
Let $D =[M_0, M_1, \ldots, M_n]$ be a negotiation dialogue with length $|D| = n+1$. $Ag_1$ and $Ag_2$ are the two agents
participating to the dialogue, where $Ag_1$ utters the even moves and $Ag_2$ utters the odd ones. $CI(M_i)$ is the certainty index
of the move $M_i$ at the step $t_i$. The certainty index of the dialogue ``$CI(D)$" is given by:

\begin{equation}\label{equation12}
CI(D) = \sum_{M_i\in D} CI(M_i)/(|D|)
\end{equation}

\end{definition}

\begin{example}\label{example2}
Let us consider that we have three negotiation dialogues $D_1$, $D_2$ and $D_3$, such that $D_k={[M_0, M_1,\ldots, M_9]}$, $(1
\leq k \leq 3)$. Table~\ref{Table2} shows the dialogue moves and the certainty index of each move in the dialogue. We suppose that
it is given that at each dialogue step each agent has different choices with their associated probabilities (i.e., complement of
risk), and we calculate the certainty index of each possible move based on Equation~\ref{equation7} as we did in
Example~\ref{example1}. Then we compute the certainty index of each dialogue by applying Equation~\ref{equation12}. We will
calculate the certainty index of $D_1$, and in the same way we calculate it for $D_2$ and $D_3$.
%
\\\\Using Equation~\ref{equation7}, we have:\\
\\$CI(D_1)$ = $\sum_{M_{i}\in D_{1}} CI(M_i)/(|D_1|)$\\
\\From Table~\ref{Table2}, we obtain:\\
\\$CI(D_1) = [0.01+0.20+0.15+0.05+0.22+0.02+0.11+0.21+0.10+0.05]/10$\\
\\$CI(D_1) = 0.112 $\\
\\In the same way we can find that:\\
 \\$CI(D_2) = 0.503, $  and \\
 \\$CI(D_3) = 0.936 $\\\\
%
\begin{table}[tbp]
\centering \caption{The certainty index of the dialogues of Example~\ref{example2}} \label{Table2}
\begin{tabular}{cccc}\hline
\textbf{Dialogue Moves}&\textbf{CI($M_i$) of $D_1$}&\textbf{CI($M_i$) of $D_2$}&\textbf{CI($M_i$) of $D_3$}\\
\hline
   {$M_0$} & {0.01} & {0.01} & {0.99} \\
   {$M_1$} & {0.20} & {0.99} & {0.98} \\
   {$M_2$} & {0.15} & {0.15} & {0.95} \\
   {$M_3$} & {0.05} & {0.95} & {0.99} \\
   {$M_4$} & {0.22} & {0.22} & {0.90} \\
   {$M_5$} & {0.02} & {0.80} & {0.90} \\
   {$M_6$} & {0.11} & {0.11} & {0.80} \\
   {$M_7$} & {0.21} & {0.75} & {0.95} \\
   {$M_8$} & {0.10} & {0.05} & {0.90} \\
   {$M_9$} & {0.05} & {1}    & {1} \\
\hline
   & {CI($D_1$)=0.112} & {CI($D_2$)=0.503}    & {CI($D_3$)=0.936} \\
\hline
\end{tabular}
\end{table}
%
We notice that for the dialogue $D_1$, the certainty index is low. This is because the certainty indexes of all the moves in this
dialogue are low as they range between $0.01$ and $0.22$. This means that the participants were not certain about the dialogue,
and even if they achieve an agreement, they do not know whether it is a good agreement or not.

%Figure~\ref{fig1} shows the certainty indexes of the moves in these three dialogues.

%\begin{figure}[t]
%                \begin{center}
%                \includegraphics[width=12cm, height=6cm]{Figures/CImoves.eps}
%                \end{center}
%                \caption{The certainty indexes of the moves in the dialogues of Example ~\ref{example2}}\label{fig1}
%                \label{Stack}
%                \end{figure}

The certainty index of the dialogue $D_2$ is medium, and that is because of the low certainty of the agent \emph{$Ag_1$} about his
moves during the dialogue, and the high certainty of the agent $Ag_2$ about his moves in the same dialogue. So, when we take the
average of the certainty indexes of all the moves, we get a medium certainty index for the whole dialogue.

%Figure~\ref{fig1} shows the difference between $Ag_1$ and $Ag_2$ in the performance during
%the dialogue, where $Ag_2$ is doing better compared to $Ag_1$.

In the third dialogue $D_3$, the certainty index is very high. This means the participants were very certain about their moves at
each step during the dialogue. %We can notice from
%Figure~\ref{fig1}, that the performance of both agents is very good.
\end{example}

Taking the average of the certainty indexes of all moves gives us an indicator about how certain the agents are about their
dialogue. However, it does not allow us to compare different dialogues with the same certainty index. To do so, we define
another metric called the \emph{weighted certainty index} of the dialogue by giving weights to the moves and taking the average of
the weighted certainty indexes of all the moves.

\begin{definition}{\emph{[Weighted Certainty Index of the Dialogue]. }}\label{WeightedCIDialogue}
Let $D =[M_0, M_1,\ldots,M_n]$ be a negotiation dialogue. $Ag_1$ and $Ag_2$ are the two agents participating
to the dialogue, where $Ag_1$ utters the even moves and $Ag_2$ utters the odd moves. $CI(M_i)$ is the certainty index
of the move $M_i$ at the step $t_i$, and $W(M_i)$ the weight of $M_i$. The weighted certainty index of the dialogue is given by:
\begin{equation}\label{equation13}
 W\_CI(D)=\sum_{M_i\in D}{W(M_i)*CI(M_i)}/\sum_{M_i\in D}W(M_i)
\end{equation}
\end{definition}
%
This will help us compare dialogues with the same certainty index. This is because the average of weighted certainty index of all
moves can be different than the average of certainty index of the moves without weights ``$CI(D)$".
%
\begin{example}\label{example3}
let us consider the following three negotiation dialogues $D_1$, $D_2$ and $D_3$ (that are different from the dialogues considered
in example~\ref{example2}), such that $D_k=[M_0,M_1,\ldots,M_5]$, $(1 \leq k \leq 3)$. Table~\ref{Table3} shows the certainty index
and weight of each move. The certainty index of each move is calculated as in example~\ref{example1}, and the certainty index of each
dialogue is calculated based on Equation~\ref{equation12}, as in Example~\ref{example2}. By applying Equation~\ref{equation13}, we obtain
the weighted certainty index of each dialogue. In the following we explain how we calculate the weighted certainty index for $D_1$, and
in the same way we calculate it for $D_2$ and $D_3$.
%
\\\\ Using Equation~\ref{equation13}: \\
\\ $W\_CI(D_1)=\sum_{M_i\in D_1}{W(M_i)*CI(M_i)}/\sum_{M_i\in D_1}W(M_i)$\\
\\From Table~\ref{Table3}, we have:\\
\\ $W\_CI(D_1)= [(0.5*1)+(0.5*2)+(0.5*3)+(0.5*4)+(0.5*5)+(0.5*6)]/21 $\\
\\ $W\_CI(D_1)= 0.50 $\\
and in the same way we can find that:
\\ $W\_CI(D_2)= 0.64 $\\
\\ $W\_CI(D_3)= 0.36 $\\\\
%
\begin{table}[tbp]
\centering \caption{Weighted certainty index of the dialogues of Example~\ref{example3}} \label{Table3}
\begin{tabular}{ccccc}\hline
\textbf{Dialogue Moves}&\textbf{CI($M_i$) of $D_1$}&\textbf{CI($M_i$) of $D_2$}&\textbf{CI($M_i$) of $D_3$}&\textbf{W($M_i$)}\\
\hline
{$M_0$} & {0.50} & {0.10} & {0.90} &  {1} \\
{$M_1$} & {0.50} & {0.25} & {0.75} &  {2} \\
{$M_2$} & {0.50} & {0.40} & {0.60} &  {3} \\
{$M_3$} & {0.50} & {0.60} & {0.40} &  {4} \\
{$M_4$} & {0.50} & {0.75} & {0.25} &  {5} \\
{$M_5$} & {0.50} & {0.90} & {0.10} &  {6} \\
\hline
 & {CI($D_1$)=0.50} & {CI($D_2$)=0.50} & {CI($D_3$)=0.50} \\
 & {W\_CI($D_1$)=0.50} & {W\_CI($D_2$)=0.64} & {W\_CI($D_3$)=0.36} \\
\hline
\end{tabular}
\end{table}

From the calculations and Table ~\ref{Table3}, we see that in $D_1$ the agents have the same $CI$ from the first move
till the last one, and it is medium so the certainty index of the whole dialogue is medium too. In $D_2$, the agents were
uncertain about their moves (i.e. $CI$ very low) in the very early stages of the dialogue, and then the $CI$ of their moves started
increasing to reach 0.90, which is a very good certainty index to guarantee a good agreement. While in $D_3$, we notice the opposite
situation of $D_2$, where the agents have started very certain about their moves then their certainty started decreasing, which might
result in not achieving an agreement. In this example, if we look at $W\_CI$ of each dialogue, we see that $D_2$ is the best dialogue,
because its weighted certainty index is greater than that of $D_1$ and $D_3$, followed by $D_1$ and then $D_3$. We notice in the case
of $D_2$ that both agents have started with low certainty about their moves, then they have started learning from each other till they
become more certain, especially in the last two moves. Also, we notice that the three different dialogues have the same certainty index,
so by calculating just the certainty index of the dialogue we cannot compare such dialogues except if we look at the performance of the
participants during the dialogue. However, we can do so by calculating the weighted certainty index of each dialogue, which gives us a
good indicator about the goodness of dialogues.

%\begin{figure}[t]
%                \begin{center}
%                \includegraphics[width=12cm, height=6cm]{Figures/CIexam3.eps}
%                \end{center}
%                \caption{The certainty indexes of the three dialogues of example \ref{example3}}\label{fig2}
%                \label{Stack}
%                \end{figure}

%Figure~\ref{fig2} shows the diagrams of certainty indexes of the moves in the three dialogues.

Figure~\ref{fig3} shows the weighted certainty indexes of the moves for the three dialogues, and here we can see the
difference between the three dialogues after giving weights to the moves as we discussed before.
\begin{figure}[t]
                \begin{center}
                \includegraphics[width=12cm, height=6cm]{Figures/WCIexam3.eps}
                \end{center}
                \caption{The weighted certainty indexes of the three dialogues of example \ref{example3}} \label{fig3}
                \label{Stack}
                \end{figure}
\end{example}

\textbf{Method 2: Using the Probability of all Possible Dialogues}\\
In this method, we measure the certainty index of the dialogue by calculating the number of all possible dialogues using the Cartesian
product of all possible moves $m_i^j$ at each step $t_i$ in the dialogue. Thus, by knowing the probability of each possible move, we
can calculate the probability of each possible dialogue, and then we apply the general formula of Shannon entropy.

\begin{definition}{\emph{[Number of Possible Dialogues]. }} \label{NofPDialogues}
Let $D = [M_0, M_1,\ldots, M_n]$ be a negotiation dialogue and $Ag_1$ and $Ag_1$ are the two agents participating to it. Suppose
that at each dialogue step $t_i$, the move $M_i$ has a set $S_i$ of possible moves $S_i=\{m_i^1,m_i^2,\ldots, m_i^{k_i}\}$, each
one with probability $P(m_i^j)$. The number of all possible moves is equal to $\sum_{i=0}^{n} k_i$. The union of all sets of the
moves is $\Omega= S_1 \cup S_2 \cup \ldots \cup S_n$, such that there is no intersection between the sets of moves: $S_1 \cap S_2
\cap \ldots \cap S_n = \emptyset$. So, the number of possible dialogues is $N_D = |S_0 \times S_1 \times \ldots \times S_n|$.
\end{definition}

As explained in Equation \ref{equation3}, each move $M_i$ in a possible dialogue $D_l$ is equal to a possible move $m_i^j$ for a
given $j$. Thus, $P(M_i) = P(m_i^j)$. Knowing this probability, we can calculate the probability of a dialogue $D_l$ as follows:

\begin{equation}\label{equation14}
P(D_l)=P(M_0) \times P(M_1) \times \ldots \times P(M_n)
\end{equation}
%
Because $\forall i \sum_{j=1}^{k_i} P(m_i^j)=1$, the sum of the probabilities of all possible dialogues is equal to one (i.e., $\sum_{l=1}^{N_D} P(D_l)=1$).
Now we can define the certainty index of the dialogue as we did for the move in Section~\ref{moveuncertainty}.

First, we measure the uncertainty of the dialogue by the general formula of Shannon entropy:
%
\begin{equation}\label{equation15}
H(D) = -\sum_{l=1}^{N_D}P(D_l) Log(D_l)
\end{equation}
%
Then, we normalize it by dividing it by $Log(N_D)$ to have a metric between 0 and 1, and finally, we measure the certainty
index of the dialogue by subtracting the normalized value from one. So, the certainty index of the dialogue is given by:
\begin{equation}\label{equation16}
CI(D) =1 - H(D)/ Log(N_D)
\end{equation}

\begin{example}\label{example4}
Let us consider the negotiation dialogue in example~\ref{example1}, where $n=k_i=3$, $1 \leq i \leq 3$. The number of all possible dialogues is
($N_D = 27$ dialogues) and the probability of each possible dialogue is computed by the product of probability of its moves. For example for $D_1$,
we take the first possible choice of the moves ($m_0^1, m_1^1, m_2^1$) with their respective probabilities ($0.33,0.05,1$). So, the probability of
$D_1$ is equal to $0.02$, and in the same way we compute the probability of all possible dialogues. By applying Equation~\ref{equation15}, we get
the entropy of the dialogue $H(D)=2.39$, and by applying Equation~\ref{equation16}, we get the certainty index of the dialogue $CI(D)=0.497$. Here we
notice that the certainty index of the dialogue is medium, and if we compare the result in this method with the result in the previous one, which uses
the average of certainty index of all moves, and applying it on the same example (Example~\ref{example1}), we notice that the result is almost the same.
\end{example}

\subsection{Agent's Uncertainty: Type II}\label{sec:type2}
In Section~\ref{sec:type1}, we assumed that the probability of each possible argument is given through the risk value of the
move, but we did not elaborate in details on how it can be assigned. Furthermore, the addressee is not considered in Type I
uncertainty.
In this section, these two issues will be addressed. We will explain in more details how probabilities can be assigned based on
three main criteria involving the addressee as discussed in  Section~\ref{sec:reasoning}, which are as follows:
\begin{enumerate}
  \item $Cr1$: Risk of failure;
  \item $Cr2$: Favorite relation; and
  \item $Cr3$: Preference relation.
\end{enumerate}

These criteria have precedence relation over each other. This means the order of examining these criteria is important in order
to assign probabilities to the different arguments available at certain step. First, we check $(Cr1)$ to examine the risk of
failure of each possible argument in the move and assign the probability so that the less move's risk of failure, the more
likely to be accepted by the addressee. Second, if there is more than one argument with the same risk of failure, then we check the
second criterion $(Cr2)$, which examines the favorite relation and we assign higher probability to the more favorable argument.
Third, if arguments have the same risk and are equally favorable, then we check the third criterion $(Cr3)$, which examines the
preference relation. This process follows the argument selection mechanism and it depends on the agent's tactic and
the adapted strategy presented in Section~\ref{sec:reasoning},
The notion of argument's probability is subjective and different heuristic approaches to evaluate it can be proposed. In this
paper, we use a heuristic similar to the one used to evaluate the risk of failure. Probabilities are based on the fact that the
knowledge base $CK$ contains certain knowledge and the set of agent's beliefs and preferences $P_{Ag_1,Ag_2}$ contains uncertain
beliefs. Therefore, the probability of an argument that belongs to $CK$ to be accepted by the addressee is higher than the
probability of another argument that belongs to the set $P_{Ag_1,Ag_2}$. Consequently, the risk of failure of an argument
belonging to $CK$ is less than another argument belonging to $P_{Ag_1,Ag_2}$. In fact, in negotiation dialogues, the
probability of a move at a given step $t_i$ depends on the knowledge the agent has at that step (i.e., the content of the
agent's knowledge base at that step), the favorite relation, and the preference relation.

%Based on these facts, we found that the best way to assign
%probability to the set of possible arguments at each dialogue step
%(i.e., at the tactical level) is the subjective method, which can
%be used when the assumptions used in the classical method are not
%applicable and the past statistics that can be used for the
%relative frequency method are unavailable. In such a situation,
%the basis for assigning probability to experimental outcomes is
%previous business experience, belief, and even feeling. So, this
%method relies on individual judgmental, and it is highly
%subjective.

\begin{definition}{\emph{[Move's Probability Function].}} \label{probabilityfunction}
Let $CK$ be the set of common agents' knowledge, $P_{Ag_1,Ag_2}$ the set of $Ag_{1}^{\prime}s$ beliefs about $Ag_{2}^{\prime}s$
beliefs, $f_r$ the set of favorable arguments, $p_r$ the set of preferred arguments, and $\mathcal{M}$ the set of all possible
moves, we define $\Delta$ as a function associating a set of knowledge and preferences and favorites to a set of possible moves
and their probabilities. We call this function the \textit{move's probability function}.
\begin{equation}\label{equation17}
 \Delta : 2^{k_n \times f_{r} \times p_{r} } \rightarrow 2^{\mathcal{M} \times [0,1]}
\end{equation}
where:\\
$k_n = CK \times P_{Ag_1,Ag_2}$;\\
$f_r=\{(Arg_i, Arg_j) \in \mathbb{A} \times \mathbb{A} | Arg_i
\preceq_{fav}^{P_{Ag_1, Ag_2}} Arg_j\}$; and \\
$p_r=\{(Arg_i, Arg_j) \in \mathbb{A} \times \mathbb{A} | Arg_i
\ll_{pref}^{Ag_1} Arg_j\}$.
\end{definition}

%To explain more this function, we assume that $CK$ is contains a
%set of propositions $P_1,P_2,\cdots P_n $, this means $CK=
%\{P_1,P_2,\cdots ,P_n\}$.
%$f_r$ : is the set of favorable arguments and we represent them as
%pairs $(Arg_1,Arg_2)$ which means $Arg_1$ is more favorable than
%$Arg_2$. So, $f_r =\{(Arg_1,Arg_2),(Arg_2,Arg_4),\cdots\}$.

%$p_r$ : is the set of preferred arguments and we represent them
%also as pairs $(Arg_1,Arg_2$) which means $Arg_1$ is more
%preferable than $Arg_2$. So, $p_r = \{(Arg_1,Arg_2),(Arg_2,Arg_4),
%\cdots\}$.

%Now the product of   $CK \times f_{r} \times p_{r}$ =
%$\{(M_1,P(M_1)), (M_2,P(M_2)), \cdots \}$, and it should satisfy
%the following conditions:

The function $\Delta$ should satisfy the following properties:

\begin{itemize}
\item   Minimality: $\forall I, I' \in 2^{k_n \times f_{r} \times
p_{r} }$ if $I \subseteq I'$ and no relevant argument can be
generated from $I'-I$, then $\Delta (I) = \Delta(I')$.

\item Uniqueness: $\forall I \in 2^{k_n \times f_{r} \times p_{r}
}$ and $\forall i, j$ s.t. $\{(M_i,P(M_i )),(M_j,P(M_j))\}
\subseteq \Delta(I)$, if $i \neq j$, then $M_i \neq M_j$.

\item Universality: $\forall I \in 2^{k_n \times f_{r} \times
p_{r} }$ if $I = \{(M_1,P(M_1)), \cdots ,(M_n,P(M_n ))\}$, then
$\sum_{i=1}^n P(M_i)=1 $.

\end{itemize}

The procedure is as follows. First, we calculate the risk of failure of each possible move based on the argument supporting it,
then we order them ascending based on the risk of failure. Second, if there is more than one move with the same risk of failure, then
we check the favorite relation for the equivalent arguments in terms of risk of failure and reorder them descending based on the
favorite relation. Third, if there is more than one argument equally favorable then we check the preference relation and
reorder them descending based on the preference relation. We assume that each of the three resulting classes $c$ $(1 \leq c
\leq 3)$ is associated with a given probability $P_c$ ($P_1 < P_2 < P_3$) (this aspect will be addressed in the next section). The
agents have to perform this procedure at each dialogue step in order to be able to assign the probability based on the order of
arguments. After that, the uncertainty can be measured based on these probabilities following the method we advocated in Section
\ref{sec:type1}. The only difference is that unlike the procedure of Section \ref{sec:type1}, here the probability that the
addressee accepts the move is being considered since probability computation is based on the agent's common knowledge and the
beliefs of the speaker agent about the beliefs of the addressee and his preferences using the following probability ordering
relation.
\begin{definition}{\emph{[Probability Ordering Relation]. }} \label{probabilityorderingrelation}
Let $C_{Ag_1,Ag_2} = \big<\mathcal{S},\mathcal{T},T, s,P_{Ag_1,Ag_2},CK\big>$ be a conversation context and $Arg_i$ and
$Arg_j$ be two relevant arguments in the context $C_{Ag_1,Ag_2}$. The probability of argument $Arg_i$ is greater than the
probability of argument $Arg_j$: $P(Arg_j) \leq P(Arg_i)$ iff $(Arg_j) \preceq_r (Arg_i)$.
\end{definition}

\begin{theorem}\label{Complexity2}
If arguments are represented in proportional definite Horn clauses, the probability assignment procedure runs in polynomial
time.
\end{theorem}

\noindent\emph{\textbf{Proof.}} \emph{the result is straightforward from Definition \ref{probabilityorderingrelation}
and Theorem \ref{Complexity1}}.~~$\blacksquare$

%The following algorithm explains how to assign probabilities to
%the potential arguments $PA$ at each dialogue step.
%
%\begin{algorithm}{\emph{\textbf{Algorithm 2: How to assign probabilities to the PA}.}} \label{algorithm2}\\
%\\ Step 1:
%\\ 1.1-- Let n= number of possible arguments.
%\\1.2-- for i=1,n calculate $risk(Arg_i)$
%\\1.3-- order the arguments ascending based on $Cr1$.\\
%\\Step 2:
%\\2.1-- if $\exists$ i,j $\in$ n, i $\neq$ j : $risk(Arg_i)$ = $risk(Arg_j)$ then check $Cr2$ (i.e., which $Arg_? \prec_{fav}^{P_{Ag_1,Ag_2}}  Arg_?$)
%\\2.2-- reorder them descending based on $Cr2$.
%\\Step 3:
%\\3.1-- if $\exists$ i,j $\in$ n, i $\neq$ j : $risk(Arg_i)$ = $risk(Arg_j)$ and $Arg_i \preceq_{fav}^{P_{Ag_1,Ag_2}}  Arg_j$   and $Arg_j \preceq_{fav}^{P_{Ag_1,Ag_2}}  Arg_i$,  Then check $Cr3$  (i.e., which $Arg_? \ll_{pref}^{Ag_i} Arg_?$)
%\\3.2-- reorder them descending based on $Cr3$.
%\\Step 4:
%\\ Assign a value to each possible argument, such that this value satisfies the definition~\ref{probabilityorderingrelation}, and the probability of all possible arguments satisfies the probability condition $\sum_{i=1}^n P(M_i)=1$.
%%\\apply the function~\ref{equation17}, to assign probability to each possible argument.\\
%\end{algorithm}

Based on uncertainty Type II, we introduce a new classification of arguments for negotiation based on their risk of failure,
which means on their probabilities.

\subsubsection{Arguments Classification}\label{sec:classification}
There are three main classes of arguments in our framework: Class $A$ of arguments (and consequently of moves supported by those
arguments) having low risk of failure (certain arguments); Class $B$ of arguments having medium risk of failure (medium certain arguments);
and Class $C$ of arguments having high risk of failure (uncertain arguments). The three classes $A$, $B$, and $C$ are disjoint, i.e.,
$A \cap B = A \cap C = B \cap C = \emptyset$. Each class is divided into three subclasses. In what follows, we explain these classes in details.\\

\begin{figure}
                \begin{center}
                \includegraphics[width=10cm,
                height=8cm]{Figures/argumentclass.eps}\label{ClassificationFigure}
                \caption{Argument classification}
                \end{center}
\end{figure}

\textbf{Class $A$: Low risk (Highly certain arguments)}\\
Arguments of this class have equal risk, which is less than the risk of any other argument not part of that class. Formally:
\begin{equation}
Arg_i \in  A~ \text{iff}:
\begin{cases}
risk(Arg_i) = risk (Arg_j) & \forall Arg_j \in A
\\
risk(Arg_i) < risk(Arg_j)  & \forall Arg_j \notin A
\end{cases}
\end{equation}

This class is composed of three disjoint subclasses: $A_a$, $A_b$, and $A_c$, i.e., $A_a \cap A_b = A_a \cap A_c = A_b \cap A_c
=\emptyset$. Let $=_{fav}^{P_{Ag_1, Ag_2}}$ be the favorite equality relation defined as follows: for two arguments $Arg_i$ and
$Arg_j$, $Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j$ iff $Arg_i \preceq_{fav}^{P_{Ag_1, Ag_2}} Arg_j$ and $Arg_j \preceq_{fav}^{P_{Ag_1, Ag_2}} Arg_i$.
The preference equality relation $=_{pref}^{Ag_1}$ is defined from $\ll_{pref}^{Ag_1}$ in the same way. $A_a$ is defined as follows:
\begin{equation}
Arg_i \in A_a~ \text{iff}:
\begin{cases}
Arg_i \in A
\\
Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j & \forall Arg_j \in A_a
\\
Arg_j \preceq_{fav}^{P_{Ag_1, Ag_2}} Arg_i & \forall Arg_j \in
A-A_a
\\
Arg_i =_{pref}^{Ag_1} Arg_j & \forall Arg_j \in A_a
\\
Arg_j \prec_{pref}^{Ag_1} Arg_i & \forall Arg_j \in A-A_a
\text{~s.t.~} Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j
\end{cases}
\end{equation}

This means, arguments in $A_a$ are equality favorable and preferable, more favorable than any other argument which is not
part of $A_a$, and more preferable than any other favorably equally argument.

In the sam way, the second class $A_b$ is defined as follows:
\begin{equation}
Arg_i \in A_b~ \text{iff}:
\begin{cases}
Arg_i \in A-A_a
\\
Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j & \forall Arg_j \in A_b
\\
Arg_j \preceq_{fav}^{P_{Ag_1, Ag_2}} Arg_i & \forall Arg_j \in
(A-A_a)-A_b
\\
Arg_i =_{pref}^{Ag_1} Arg_j & \forall Arg_j \in A_b
\\
Arg_j \prec_{pref}^{Ag_1} Arg_i & \forall Arg_j \in (A-A_a)-A_b
\text{~s.t.~} Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j
\end{cases}
\end{equation}

Finally, the third class $A_c$ is defined as follows:
\begin{equation}
A_c = (A-A_a)-A_b = A-(A_a \cup A_b)
\end{equation}

\textbf{Class $B$: Medium risk (Medium certain arguments)}\\
Arguments of this class have equal risk, which is less than the risk of any other argument not part of the union of that class and
Class $A$. Formally:
\begin{equation}
Arg_i \in B~ \text{iff}:
\begin{cases}
risk(Arg_i) = risk (Arg_j) & \forall Arg_j \in B
\\
risk(Arg_i) < risk(Arg_j) & \forall Arg_j \notin A \cup B
\end{cases}
\end{equation}

As for Class $A$, this class is composed of three disjoint subclasses: $B_a$, $B_b$, and $B_c$. $B_a$ is defined as follows:
\begin{equation}
Arg_i \in B_a~ \text{iff}:
\begin{cases}
Arg_i \in B
\\
Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j & \forall Arg_j \in B_a
\\
Arg_j \preceq_{fav}^{P_{Ag_1, Ag_2}} Arg_i & \forall Arg_j \in
B-B_a
\\
Arg_i =_{pref}^{Ag_1} Arg_j & \forall Arg_j \in B_a
\\
Arg_j \prec_{pref}^{Ag_1} Arg_i & \forall Arg_j \in B-B_a
\text{~s.t.~} Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j
\end{cases}
\end{equation}

%This means, arguments in $A_a$ are equally favorable and
%preferable, more favorable than any other argument which is not
%part of $A_a$, and more preferable than any other favorably
%equally argument.

In the sam way, the second class $B_b$ is defined as follows:
\begin{equation}
Arg_i \in B_b~ \text{iff}:
\begin{cases}
Arg_i \in B-B_a
\\
Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j & \forall Arg_j \in B_b
\\
Arg_j \preceq_{fav}^{P_{Ag_1, Ag_2}} Arg_i & \forall Arg_j \in
(B-B_a)-B_b
\\
Arg_i =_{pref}^{Ag_1} Arg_j & \forall Arg_j \in B_b
\\
Arg_j \prec_{pref}^{Ag_1} Arg_i & \forall Arg_j \in (B-B_a)-B_b
\text{~s.t.~} Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j
\end{cases}
\end{equation}

Finally, the third class $B_c$ is defined as follows:
\begin{equation}
B_c = (B-B_a)-B_b = B-(B_a \cup B_b)
\end{equation}

\textbf{Class $C$: High risk (Uncertain arguments)}\\
This class is simply defined from the two other classes where $\mathbb{A}_{C_{Ag_1, Ag_2}}$ is the set of arguments in the
context $C_{Ag_1, Ag_2}$ as follows:
\begin{equation}
C = \mathbb{A}_{C_{Ag_1, Ag_2}}-(A \cup B)
\end{equation}

The subclasses $C_a$, $C_b$, and $C_c$ are defined in the same way as the subclasses of $A$ and $B$.

The following theorem is straightforward from the above equations and Definition \ref{probabilityorderingrelation}.
\begin{theorem}
Arguments in Class $A$ have higher probability to be accepted than arguments in Class $B$ and arguments in class $B$ have higher
probability to be accepted than arguments in Class $C$.
\end{theorem}

\begin{comment}

If the argument contains formulas $\in CK$, then the $risk(Arg_i)= v1$ and in this case the argument has less risk of failure because the $CK$ has certain information (i.e., $v1$ can be equal to 0) and therefore, it has a higher chance to be accepted by the addressee. Furthermore, we distinguish three other sub-classes in case of there is more than one argument with risk of failure = $v1$, and they differ in terms of favorite and preference relations, these subclasses are as follows:\\
\textit{Class a1:} the argument is class $a1$ if it is more favorable compared to the other arguments that have the same risk of failure $v1$.\\
\textit{Class a2:} if there is more than one argument equally favorable in addition to the equality of risk failure $v1$, then we assign class $a2$ to the more preferred one, and \\
\textit{Class a3}: to the less preferred one.\\

\textbf{Class B: Arguments contain only formulas in $P_{Ag_1,Ag_2}$.}\\
If the arguments contain formulas $\in P_{Ag_1,Ag_2}$, then the $risk(Arg_i)= v2$ and in this case the risk of failure of the argument is greater than that in \textit{class A} (i.e., $v1 < v2$) because the information in $P_{Ag_1,Ag_2}$ is not certain, and therefore, the chance to be accepted by the addressee is less. As in \textit{class A}, we distinguish three other sub-classes in case of there is more than one argument with risk of failure = $v2$ and they differ in terms of favorite and preference relations, these sub-classes are as follows:\\

\textit{Class b1:} the argument is class $b1$ if it is more favorable compared to the other arguments that have the same risk of failure $v2$.\\
\textit{Class b2:} if there is more than one argument equally favorable in addition to the equality of risk failure $v2$, then we assign class $b2$ to the more preferred one, and \\
\textit{Class b3}: to the less preferred arguments.\\

\textbf{Class C: Otherwise: ``Argument contains formulas not in $CK$ and not in $P_{Ag_1,Ag_2}$".}\\

If the arguments contain formulas $\notin CK$ and $\notin
P_{Ag_1,Ag_2}$, then the $risk(Arg_i)= v3$ and in this case the
risk of failure of the argument is greater than that in
\textit{class A} and \textit{class B}
(i.e., $v1  < v2  < v3$) and consequently, the chance to be accepted by the addressee is more less than the above two classes. As in \textit{class A} and in class \textit{class B}, we distinguish three other sub-classes in case of there is more than one argument with risk of failure = $v3$ and they differ in terms of favorite and preference relations, these subclasses are as follows:\\
\textit{Class c1:} the argument is class $c1$ if it is more favorable compared to the other arguments that have the same risk of failure $v3$ .\\
\textit{Class c2:} if there is more than one argument equally favorable in addition to the equality of risk failure $v3$, then we assign class $c2$ to the more preferred one, and \\
 \textit{Class c3}: to the less preferred arguments.\\
Where $v1 < v2 < v3$ and $v1, v2, v3 \in R$.

To measure the agent's uncertainty/certainty that the selected argument will be accepted by the addressee (here we will call it the \textit{uncertainty/ceratinty degree} to distinguish it from the \textit{uncertainty index}), will use the same formulas that we used in section (~\ref{sec:type1}). Now let us present the different situations to distinguish between these two types of uncertainty.

\subsubsection{Different Cases}\label{sec:cases}
We can distinguish three different cases that make the difference between two types of the agent's uncertainty clear.\\

\textbf{Case 1: If there is only one possible argument}.\\
If the agent has just one possible argument, then the probability of that argument will be at its maximum value (i.e., equal to one to satisfy the probability condition $\Sigma_{m_{j}^{i} \in PA_{i}} P(m_{j}^{i}=1))$ and the uncertainty degree will be at its minimum value (i.e., equal to zero, based on proposition~\ref{proposition1}). In this case the \textit{uncertainty degree} is equal to the \textit{uncertainty index} and it does not represent the agent's uncertainty that the selected move will be accepted by the addressee, it rather represents the agent's uncertainty about selecting the right argument at that step, regardless it will be accepted by the addressee agent or not, because the available argument can be any of the above classes, and therefore, if the class of the argument is $C$ for instance, then the chance for this argument to be accepted is very weak and this contradicts the high probability assigned to this argument (equal to one). However, this is not applicable for all classes, for example if the argument is class $A$, then there is a high chance to be accepted, so the high probability assigned matches the low uncertainty we achieved and this a special case of \textit{case 1}.

\begin{proposition} \label{proposition3}
In negotiation dialogue games, at each dialogue step the uncertainty degree is equal to the uncertainty index, and it represents the agent's uncertainty about selecting the right argument as well as the agent's uncertainty about the selected argument to be accepted by the addressee and it will be at it's minimum value iff at that step there is only one possible argument and it has class A.
\end{proposition}

\textbf{proof}\\
From proposition~\ref{proposition1}, it's clear that the uncertainty of selecting the right move will be at its minimum
value ``0" iff there is only one possible argument, and if the class of this argument is A, then the risk of failure is at its
minimum value too, which means the uncertainty about the argument to be accepted is at its minimum value ``0". So the uncertainty of
selecting the right argument ``certainty index" and the uncertainty about the argument to be accepted by the addressee
``certainty degree" is the same.  ~~~~~~~~~$\blacksquare$

\begin{proposition} \label{proposition4}
In negotiation dialogue games, at each dialogue step if there is only one possible argument, the uncertainty degree is equal to the uncertainty index and it just represents the agent's uncertainty about selecting the right argument iff that argument is not class A.
\end{proposition}

\textbf{proof}\\
If there is only one possible argument, the uncertainty will be at its minimum value ``0" ~\ref{proposition1}. Now, if the available
argument is not class A, then the risk of failure will be greeter than V1. In this case we can not consider the uncertainty value
``0" as an indicator for the move to be accepted by the addressee, rather, we consider it as an index of selecting the right argument
since there is no other choice. ~~~~~~~~~$\blacksquare$

\textbf{Case 2: If there is more than one possible argument with the same class}.\\
If all possible arguments have the same class then they will be equally probably to be selected and the uncertainty will be at its maximum value (i.e., equal to one, following proposition 2), and again as in case 1, it does not always represent the uncertainty about the selected argument to be accepted or refused by the addressee, because the possible arguments might have a high risk of failure (e.g. in class c), in this case it represents the agent's uncertainty about the argument to be accepted. In the other hand, if all arguments have class A, for example, which means a very low risk of failure, then the uncertainty does not represent the uncertainty that the argument will be accepted, it rather represents the uncertainty about selecting the right move.

\begin{proposition} \label{proposition5}
In negotiation dialogue games, if all possible arguments at certain dialogue step have the same class, then the uncertainty of the selected argument is at its maximum value, and it represents only the agent's uncertainty about selecting the right argument, except if the arguments are class C.
\end{proposition}

\textbf{proof}\\
If all possible arguments have the same class, then they will have same probability value which leads to maximum value of uncertainty
``1" see~\ref{proposition2}. If the arguments have class A, then the risk of failure will be at its minimum value ``0", and in this
case the low risk of failure contradict the high uncertainty for the argument to be accepted. So we can not consider this high
uncertainty as an indicator of accepting. ~~~~~~~~~$\blacksquare$

\textbf{Case 3: If there is more than one argument with different classes}.\\
In this case, the assignment of the probability will be based on the class of the argument, and following the argument selection mechanism, the agent will select the higher argument class, so the uncertainty in this case represents the agent's uncertainty that the selected argument will accepted by the addressee. This will enhance the performance of the agent towards achieving the dialogue goal.\\
The different cases that show the argument class and the associated type of uncertainty are summarized in    Table~\ref{Table4}.

\begin{table}[tbp]
\centering \caption{Argument classes vs. Uncertainty types} \label{Table4}
\begin{tabular}{||c|c|c|c||}\hline\hline
\multicolumn{4}{||c||}{\textbf{Number of possible arguments}} \\
\hline\hline
One possible argument & Uncertainty Type  & More than one possible argument & Uncertainty Type \\
\hline
Class A               & Type  I / Type II & Same class =  Class A   & Type  I \\ \hline
Class B               & Type  I           & Same class =  Class B   & Type  I \\ \hline
Class C               & Type  I           & Same class =  Class C   & Type  I \\ \hline
                      &                   & Different classes       &Type  I / Type  II\\
\hline
\end{tabular}
\end{table}

\end{comment}

### 2013-07-24 proposal/proposal/chapter4.tex
Added new proposal files

\setcounter{chapter}{4}

\chapter{Conclusion and Future Work}

\section{Conclusion}\label{sec:conclusion}
In this paper, we proposed a new set of uncertainty measures for the agents in argumentation-based negotiation dialogues from an
external agent's point of view. Specifically, we introduced two types of uncertainty measures: 1) Type I, the uncertainty index of
playing the right move at each dialogue step; and 2) Type II, the uncertainty degree of the agent that the move will be accepted by
the addressee.
For uncertainty Type I, we used Shannon entropy to assess the agents' uncertainty/certainty about their moves in the negotiation
dialogues. We supposed that an external agent is monitoring the dialogue, and he wants to evaluate this dialogue in terms of the
agent's uncertainty/certainty about selecting the right move at each step. In fact, at each step, the agent is supposed to have
different choices, each choice is associated with a probability of being the right one, %which represents the risk of failure for this move to be accepted by the addressee.
this probability reflects the importance of information included in that move, where the higher the probability is, the
more certain the agent becomes (lower uncertainty). So we analyzed the fact that negotiating agents are rational, and they always
try to perform the actions that will result in the optimal outcome for themselves. We used Shannon entropy to measure: i) the
uncertainty/certainty index and the weighted uncertainty/certainty index of the agent that he is playing the right move at each
step during the dialogue; and ii) the uncertainty/certainty index and the weighted uncertainty/certainty index of both agents
participating in the dialogue about the whole dialogue. This was done in two different ways. The first is by taking the average of
the uncertainty index of all moves, and the second is by determining all possible dialogues and applying the general formula of Shannon entropy.

For uncertainty Type II, we formalized the probability association to the arguments and the uncertainty that the move will be
accepted by the addressee. In this context, we introduced a new classification of arguments based on the notion of risk of failure
and showed that this classification is compatible with the probability that the moves supported by those arguments will be
accepted by the address. An important result of this paper is that the selection and probability ordering mechanisms of arguments
are tractable as they can be performed in polynomial time if arguments are represented in propositional definite Horn logic.

In our proposed measures, the move with the higher certainty (lower uncertainty) index is considered as the best move. We analyzed
the fact that negotiating agents are rational, and they always try to perform the actions that will result in the optimal outcome
for themselves. We started our work with measuring the uncertainty/certainty index of each move at each dialogue step, and in order
to distinguish between two moves with the same certainty index, we assigned weight to each move, which reflects the importance of the
move. Then, we proceeded to the whole dialogue and we measured the uncertainty/certainty index for the dialogue in two different ways,
and we proved that the two ways give the same result. Also, assigning weight to the moves allowed us to compare two different dialogues.
We believe that such measures are very significant and helpful in evaluating the dialogue and the agent's strategies, especially when
they are making a decision and selecting the best moves to achieve an agreement (if one exists) in a timely manner.

\section{Future Work}\label{sec:future}
In this paper, we mainly focused on the classical (i.e., precise) probability theory, particularly the classical Shannonian
information theory to measure the uncertainty. As pointed out in \cite{Harmanec1999}, there are other approaches of measuring
uncertainty in the theories of imprecise probabilities, particularly the Dempster-Shafer theory (also known as the theory
of belief functions) \cite{Shafer76} and the possibility theory \cite{Dubois2001}. As future work, we will study key measurements
in these two theories such as \emph{nonspecificity}, \emph{confusion}, \emph{dissonance}, \emph{discord}, and \emph{strife}, and
we will adapt, define and integrate them in our framework. Combining and aggregating those measurements to finally measure the
total uncertainty will be investigated as well. The requirements of those new metrics as reported in \cite{Harmanec1999} will be
analyzed. Those requirements are: 1) generalization, meaning that the new uncertainty measures should generalize the uncertainty
measures already established in the classical probability theory; 2) subadditivity, meaning that when the problem is broken into
two orthogonal subproblems, the uncertainty of the original problem should be less than or equal to the sum of uncertainties of the
subproblems; and 3) additivity, meaning that under the assumption of no interaction and no dependency between the subproblems, the
uncertainty of the original problem is equal to the sum of uncertainties of the subproblems.

Another plan for future work is to extend the proposed metrics for other dialogue game types such as persuasion, deliberation,
inquiry and information seeking. We also plan to analyze argumentation-based dialogues to evaluate agent strategies and
analyze them from the optimization perspective. Analyzing the computational complexity of such optimization problems is another
direction for future work. Finally, we plan to analyze multi-party dialogues to which many agents can participate. Extending the
proposed metrics to this type of dialogues is not straightforward. For example, defining the rules of a multi-party negotiation is
much more complicated than two-party dialogues. In fact, multi-party dialogues cannot be simply reduced to many two-party dialogues.

### 2013-07-25 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 a mechanism for community membership requests and selections of
-web services in the scenarios where there is interaction between one community and many web services 
-and scenarios where web services can join multiple established communities. The ultimate objective is to
+web services under two scenarios where: (1) there is interaction between one community and many web services
+and (2) web services can join multiple established communities. The ultimate objective is to
 develop a mechanism for web services to form stable groups

### 2013-07-26 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 quantity and quality of tasks accomplished by a given service. 
+Higher user satisfaction leads to higher trust of the community by users hence directing more requests towards that service provider.
 
@@
 Figure \ref{fig_community} represents the architecture of web service communities.
-The communities are basicly an abstract model of web services, they aggrigate web services and communicate with other entities such as UDDI registeries and users, using identical protocols as web services.
+The communities are essentially an abstract model of web services.
+They aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols as web services.
 Web services join communities to increase their utility by having a larger market share and task pool.
-Community cordinators or master web services are responsible for community development, managing membership requests from web services and distributing user tasks among the community members.
-Communitiy coordinators try to attract quality web services and keep the community as stable and productive as possible to gain better reputation and user satisfaction which results in having a higher market share for the community.
-The way the web services reside inside communities and how communities of web services are engineered is described comprehensivly in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+Community coordinators or master web services are responsible for community development, managing membership requests from web services and distributing user tasks among the community members.
+Community coordinators try to attract quality web services and keep the community as stable and productive as possible to gain better reputation and user satisfaction which results in having a higher market share for the community.
+The way the web services reside inside communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
 

### 2013-07-26 papers/old-coalition-journal-extension/charts/old-charts/avg_bud_highfee.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('avg_bud_highfee.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
+
+i=0:49;
+t=v(:,5);y=v(:,6);z=v(:,7);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 500 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',7000:2000:18000);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 50 0 12000]);
+
+% Add legend
+hleg1 = legend('Coopetitive','Competitive','Random Coopetitive');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.3,.7,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',11);
+%legend boxoff;
+
+% Add title and axis labels
+title('High Membership Fee', 'fontsize', 14);
+xlabel({'Number of Runs';'(b)'}, 'FontSize',14);
+ylabel('Budget', 'FontSize',14);
+
+%Caxes = copyobj(gca,gcf);
[…]

### 2013-07-26 papers/old-coalition-journal-extension/charts/old-charts/avg_qos_task.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('avg_qos_task.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);z=v(:,3);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 500 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',0:0.1:1);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+axis([0 50 0.4 1]);
+%axis([0 50 7000 18000]);
+
+% Add legend
+hleg1 = legend('Coopetitive','Competitive','Random Coopetitive');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.3,.71,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',11);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Number of Runs';'(c)'}, 'FontSize',14);
+ylabel('Average QoS of Tasks Performed', 'FontSize',14);
+
[…]

### 2013-07-26 papers/old-coalition-journal-extension/charts/old-charts/comp_p.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('comp_p.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|--|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0:0.1:1);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+axis([0 50 0 1]);
+%axis([0 50 7000 18000]);
+
+% Add legend
+hleg1 = legend('Competitive W1','Competitive W2');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.69,.6,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',11);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
+ylabel('Reputation', 'FontSize',14);
+
+%Caxes = copyobj(gca,gcf);
[…]

### 2013-07-26 papers/old-coalition-journal-extension/charts/old-charts/coop_p.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('coop_p.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|--|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0:0.1:1);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+axis([0 50 0 1]);
+%axis([0 50 7000 18000]);
+
+% Add legend
+hleg1 = legend('Cooperative W3','Cooperative W4');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.69,.65,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',11);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Number of Runs';'(b)'}, 'FontSize',14);
+ylabel('Reputation', 'FontSize',14);
+
+%Caxes = copyobj(gca,gcf);
[…]

### 2013-07-26 papers/old-coalition-journal-extension/charts/old-charts/decision_dev2.m

@@ -1,0 +1,61 @@
+[v,T,vT]=xlsread('decision_dev2.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+%set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-*|-.|--|.-|.|:')
+
+i=1:10;
+t=v(:,1);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+%plot(i,t,'--rs','LineWidth',2, 'MarkerEdgeColor','k', 'MarkerFaceColor','g', 'MarkerSize',10);
+plot(i,t,'--blacks','LineWidth',2,...
+                'MarkerEdgeColor','black',...
+                'MarkerFaceColor','black',...
+                'MarkerSize',10);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:10);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',7000:2000:18000);
+set(gca,'tickdir','in');
+%set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 11 0.82 1]);
+
+% Add legend
+%hleg1 = legend('0% Deviation','10% Deviation','20% Deviation','30% Deviation','40% Deviation','50% Deviation');
+%set(hleg1,'Location','NorthWest');
+%set(hleg1, 'Position', [.24,.63,.1,.2]);
+%set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+%set(hleg1,'FontSize',10);
+%legend boxoff;
+
[…]

### 2013-07-26 papers/old-coalition-journal-extension/charts/old-charts/task_done.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('task_done.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);z=v(:,3);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 500 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',0:0.1:1);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+%axis([0 50 0.2 1]);
+%axis([0 50 7000 18000]);
+
+% Add legend
+hleg1 = legend('Coopetitive','Competitive','Random Coopetitive');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.3,.71,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',11);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
+ylabel('Number of tasks successfully done', 'FontSize',14);
+
[…]

### 2013-07-26 papers/old-coalition-journal-extension/charts/s2_task_done.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('s2_task_done.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|--|--|.|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0:1000:7000);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 50 0 7000]);
+
+% Add legend
+hleg1 = legend('Dynamic Coalition Formation','Random Formation');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.30,.80,.1,.1]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Iterations';'(a)'}, 'FontSize',14);
+ylabel('Number of tasks successfully done', 'FontSize',14);
+
+%Caxes = copyobj(gca,gcf);
[…]

### 2013-07-26 papers/old-coalition-journal-extension/charts/task_done_opt.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('task_done_opt.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|+|--|.|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);z=v(:,3);tt=v(:,4);yy=v(:,5);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,i,tt,i,yy,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0:200:1600);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 50 0 1600]);
+
+% Add legend
+hleg1 = legend('Optimal epsilon-core','Our depth-2 Convex','Our depth-1 Convex','3-Way Sat','2-Player Game');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.26,.66,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Iterations';'(a)'}, 'FontSize',14);
[…]

### 2013-07-27 papers/coalition-journal-extension/coalition_journal.tex
Changes

@@
 DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
-users and services maximize their gain. A two-player
+users and services to maximize their gain. A two-player
 non-cooperative game between web services and community master was
@@
 
-In \cite{DBLP:conf/IEEEscc/LimTMB12} a 3-way satisfaction approach
+In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
 for selecting web services has been proposed. In this approach,
 the authors proposed a web service selection process that the
-community masters can use. The approach considerers the efficiency
+community masters can use. The approach considers the efficiency
 of all the three involved parties, namely users, web services and
@@
 
-In \cite{10.1109/TSC.2012.12} a cooperative scheme among autonomous
+In \cite{10.1109/TSC.2012.12}, a cooperative scheme among autonomous
 web services based on coalitional game theory has been introduced. They have proposed an algorithm to
@@
 our equations, we refer to web services as $ws$ and to the set of
-web services hosted by a given community as $C$. To simply the
+web services hosted by a given community as $C$. To simplify the
 notation, sometimes we simply write $ws$ instead of $ws \in C$ to
@@
 subset $S$ of $N$ can form a group called $coalition$. A
-\emph{coalitional game} is a pair $G = (N, v)$ where $v$ is called
-a \emph{characteristic function}, which given a coalition, is a
-function $v: 2^N \to \mathbb{R}$ mapping the set of players of the
+\emph{coalitional game} is a pair $G = (N, v)$, where $v$ is called
+a \emph{characteristic function} $v: 2^N \to \mathbb{R}$, mapping the set of players of the
 coalition to a real number $v(S)$, the worth of $S$. This number
@@
 one player to another, or in other words, players have common
-currency and a unit of income is worth same for all players
+currency and a unit of income that is worth the same for all players
 \cite{myerson1991game}.
@@
 When dealing with cooperative games, two issues need to be
-addressed:\\ 1. What coalitions to form? \\
+addressed:\\ 1. Which coalitions among all possible coalitions to form? \\
 2. How to reward each member when a task is completed?\\
@@
 The communities and web services earn revenue by performing tasks.
-The total gain is function of quality ($QoS_{ws}$) and quantity($Tr_{ws}$) of tasks being performed.
+The total gain is function of quality ($QoS_{ws}$) and quantity ($Tr_{ws}$) of tasks being performed.
 As mentioned in section \ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain aggregation function of the parameters considered in Table \ref{qosws}.
 We have adopted a linear equal weigth average over all QoS parameteres listed in table \ref{qosws} excluding the $Throuput$ and $Cost$ parameters.
-A community has the option to weigh specific QoS patameters more or less depending on the expectations of their clients.
+A community has the option to weight specific QoS patameters more or less depending on the expectations of their clients.
 
@@
 Sometimes it is impossible to share the gain between all web services in a way no subset of them would individually gain more if they had their own group.
-In this example, the value community of ${ws_1}$ and ${ws_2}$ is 7.2, with ${ws_3}$ joining the community the value of community increases to 8.0, however there is no way to distribute the value among web services, where ${ws_1}$ and ${ws_2}$ can earn 7.2, and ${ws_3}$ earn at least 2.4, which they could earn before joining the community.
+In this example, the value community of ${ws_1}$ and ${ws_2}$ is 7.2, with ${ws_3}$ joining the community the value of community increases to 8.0.
+However there is no way to distribute the value among web services, where ${ws_1}$ and ${ws_2}$ can earn 7.2, and ${ws_3}$ earn at least 2.4, which they could earn before joining the community.
 This makes the group unstable.
@@
 Web services also have a small share of market independently, providing them with a small task pull.
-In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the $social welfare$.
+In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the \emph{social welfare}.
 In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1, ws_3\right\}$, which yields a total value of $32 + 16 = 48$.
@@
 In this example if we initially having two coalitions of $\left\{C_1, ws_2\right\}$ and $\left\{C_2, ws_1\right\}$ and a ${ws_3}$ as new web service, ${ws_3}$ joining ${C_1}$ would hurt at least itself or $ws_2$, however ${ws_3}$ joining ${C_2}$ would not hurt any participants and ${ws_3}$ would earn more within the community and the community will have enough web services performing the incoming tasks from users.
+
+The first two examples illustrate the fact that a community cannot simply increase its revenue by adding more web services.
+The web services and even community owners are autonomous agents and would deviate and be displeased about the community if new members cause a drop in their profit.
+The job of the community master is to attract as many quality web services it can and keep them satisfied; hence the group stability is guaranteed.
+The third example highlights another type of problem we would like to address, which is how to form best possible groups of communities, and allocate web services among communities in a way which would maximize payoff for of our agents and members already residing in the communities.
+In next section, we provide collaborative game theory based algorithms for our autonomous agents, to tackle these problems and find applicable and efficient strategies for communities and web services to maximize their profit.
 
@@
 
-We discuessed $core$ as one the preminent solution concepts in cooperative games.
+We discuessed $core$ as one of the preminent solution concepts in cooperative games.
 Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group.
@@
 Comuunity stability is an attractice property for communities, also communities would benefit by having slightly more web services then having the exact number of web services satisfying task rate cap.
-One reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with.
+One reason is that there is always the possibility that the agents may leave the community or they may under perform from the quality values they were initially performing with.
 
@@
 However, this can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable.
-Subsiding or taxting in order to reduce the bargaining power of sub coalitions are called $taxtation$\cite{eps346856} methods.
+Subsiding or taxting in order to reduce the bargaining power of sub coalitions are called $taxtation$ \cite{eps346856} methods.
 

### 2013-08-15 proposal/proposal/chapter1.tex
Changes

@@
-\setcounter{chapter}{1}
+\setcounter{chapter}{0}
 %*******************************START INTRODUCTION **********************************
-\section{Introduction}\label{sec:intro}
+\chapter{Introduction}\label{sec:intro}
 In this chapter we introduce the context of this research, which is about argumentation-based negotiation dialogue games.
@@
 
-\subsection{Context of the research}\label{sec:context}
+\section{Context of the research}\label{sec:context}
 
@@
 
-\subsection{Motivations and research questions}\label{sec:motivation}
+\section{Motivations and research questions}\label{sec:motivation}
 
@@
 
-\subsection{Research objectives and contributions}\label{sec:contribution}
+\section{Research objectives and contributions}\label{sec:contribution}
 
@@
 
-\subsection{Research outline}\label{sec:outline}
+\section{Research outline}\label{sec:outline}
 The rest of the paper is organized as follows: In Section~\ref{sec:Argumentation}, we present a  brief theoretical background on the argumentation system

### 2013-08-21 notes/notes.tex
changes
Changes

@@
 
-hi
+\section{Computation Complexity and Intractability}
+
+\subsection{NP-Completeness}
+
+To prove that $\prod$ is NP-complete, we merely show that \cite{Garey:1990:CIG:574848}
+
+\begin{enumerate}
+\item $\prod \in$ NP and,
+\item some known NP-complete problem $\prod^\prime$ transforms to $\prod$.
+\end{enumerate}
+
+\section{Game Theory}
+
+\subsection{Learning in Games}
+Stochastic games generalize both Markov decision processes and repeated games.
+
+\section{Paper Reviewers}
+I strongly believe that research in this direction is very important as service computing get matured and move towards seamless integration of web services dynamically.
+
+This paper proposes an efficient coalition formation mechanism using cooperative game-theoretic techniques.
+The mechanism could be useful for web services to form stable groups allowing them to maximize their efficiency and generate near-optimal communities.
+
+The related work and introduction are in Section 1.
+The authors only give a review and analyze of references [6]~[9],which is not adequate.
+I also found some other references in the Performance Formulation and Modeling Section, but it is required to summary them is the related work section to give a clear comparison.
+
+\bibliographystyle{plain}
+\bibliography{ehsan}
 

### 2013-08-21 proposal/proposal/chapter2.tex
Changes

@@
-\setcounter{chapter}{2}
+\setcounter{chapter}{1}
 %*******************************START Background **********************************
 
-\section{Introduction to Multiagent Systems}\label{sec:MAS}
+\chapter{Background and Relevant Literature}\label{sec:MAS}
 
@@
 
-Three types of approaches have been discussed in MAS literature as the authors argued in~\cite{JenningsPASC01}. These approaches are:
-the \textit{game-theoretic} approach, the \textit{heuristic-based} approach, and the \textit{argumentation-based} negotiation (ABN)
-approach.
-
-The Game-theoretic approach is based on studying and developing strategic negotiation models based on game-theoretic precedents~\cite{Neumann44,JeffreyG94}.
-The basic idea of this approach is to see the negotiation process as a game in which each participant tries to maximize his own utility. While this approach
-is very promising in terms of results analysis, it suffers from some drawbacks as the authors argued in ~\cite{AmgoudV11}, due to the assumptions upon which
-it is built. The most important ones are (i) the approach allows agents to exchange offers only, but not reasons or justifications, and (ii) the preference relation
-$\succeq$ on offers is fixed during a negotiation for an agent. These assumptions are not realistic since in everyday life, other information than offers may be exchanged.
-Moreover, it is very common that preferences on offers may change~\cite{AmgoudV11}.
-
-The second approach is heuristic-based. This approach came to overcome some limitations of the game-theoretic approach (e.g., ~\cite{FatimaWJ04,JenningsPASC01}).
-Heuristics are ad hoc rules that aim to achieve a good solution, but not necessarily an optimal one. That is why some strong assumptions made in the game-theoretic
-approach such as the notion of rationality of agents as well as their resources are relaxed. Even though this approach came to cope with the game-theoretic approach
-limitations, it does not solve the problem of the preference relation, i.e., the relation $\succeq$ remains the same during the negotiation~\cite{AmgoudV11}.
-
-The third approach, which is our focus in this paper, is the argumentation-based negotiation approach (ABN). Plenty of research has been done on this approach as
-witnessed by many publications, such as ~\cite{AmgoudPM00,Hunter04,Mbarki06,AmgoudDM07,AmgoudV11,EliseYP12}. The basic idea behind this approach is to allow the
-participants of the negotiation dialogue not only to exchange offers, but also reasons and justifications that support these offers in order to mutually influence
-their preference relation on the set of offers, and consequently to the out come of the dialogue. In~\cite{RahwanSD03}, the authors have introduced a particular
-style of argument-based negotiation, namely interest-based negotiation (IBN), which is  a form of ABN in which agents explore and discuss their underlying interests.
 %*******************************End Background **********************************

### 2013-08-21 proposal/proposal/chapter3.tex
Changes

@@
-\setcounter{chapter}{3}
+\setcounter{chapter}{2}
 \chapter{Contribution and Research Activities}
@@
 \section{Argumentation System and Agent Theory}\label{sec:Argumentation}
-Let us recall some basic definitions in the argumentation-based negotiation.
-
-\begin{definition}{\emph{[Move].}} \label{Move}
-Let $Ag = \{Ag_1,Ag_2, \ldots\}$ be a set of symbols representing agent names that may be involved in a negotiation dialogue $D$. A
-move $M_i\in D$ consists of the agent that utters the move: $Speaker(M_i)\in Ag$; the set of agents to which the move is
-addressed: $Hearer(M_i)\subseteq Ag$; and the content of the move: $Content(M_i)$.
-\end{definition}
-
-For simplification reasons, we will consider bilateral negotiation (i.e., only two agents involved in the dialogue $Ag_1$ and $Ag_2$).
-Multi-party dialogues is an important issue that we plan to investigate in future work. During a dialogue, several moves may be uttered.
-Those moves constitute a dialogue $D$, which is a sequence of moves denoted by $[M_0$,$M_1$,\ldots,$M_n]$, where $M_0$ is the initial move,
-$M_n$ is the final one, and $|D|$ is the length of the dialogue (i.e., $|D| = |[M_0$,$M_1$,\ldots,$M_n]| = n+1$).
-
-In what follows, we assume that the agents exchange the content of the moves during the dialogue as arguments because our approach is
-argumentation-based. In argumentation systems the logical language $\pounds$ is essential, we will recall the definition of the
-argument concept, a definition of the attack relation between arguments, and the definition of acceptability
-from~\cite{Amgoud00}, then we will use these definitions in our approach. Here $\Gamma$ indicates a possibly inconsistent
-knowledge base with no deductive closure, and $\vdash$ stands for classical inference.
-
-\begin{definition}{\emph{[Argument].}} \label{Argument}
-An argument $Arg$ is a pair $(H, h)$ where $h$ is a formula of $\pounds$ and $H$ a subset of  $\Gamma$ such that: i) $H$ is
-consistent, ii) $H \vdash h$ and iii) $H$ is minimal, so that no subset of $H$ satisfying both i and ii exists. $H$ is called the
-support of the argument and $h$ its conclusion.
-\end{definition}
-
-\begin{definition}{\emph{[Attack].}} \label{Attack}
-Let $(H, h)$, $(H^{\prime}, h^{\prime})$ be two arguments. $(H^{\prime}, h^{\prime})$ attacks $(H, h)$ iff $H^{\prime} \vdash
-\neg h$. In other words, an argument is attacked iff there is an argument for the negation of its conclusion.
-\end{definition}
-
-Our dialogue architecture also involves general knowledge, such as knowledge about the dialogue subject. Agents can also reason about
-their preferences in relation to beliefs. The idea is to capture the fact that some facts are believed more than others. For this
-reason, we assume, like in~\cite{Mbarki06}, that any set of facts has a preference order over it. We suppose that this ordering
-derives from the fact that the agent's knowledge base ($\Gamma$) is stratified into non-overlapping sets $\Gamma_1,\cdots ,
-\Gamma_n$ such that facts in $\Gamma_i$ are all equally preferred and are more preferred than those in $\Gamma_j$ where $i < j$. The
-preference level of a subset of $\Gamma$ whose elements belong to different non-overlapping sets is defined as follows.
-
-\begin{definition}{\emph{[Preference Level].}} \label{preferenceLevel}
-The preference level of a nonempty subset $\gamma$ of $\Gamma$ denoted by level $(\gamma)$ is the number of the highest numbered
-layer which has a member in $\gamma$.
-\end{definition}
-\begin{example}
-Let $\Gamma = \Gamma_1 \bigcup \Gamma_2 $ with $\Gamma_1$ = $\{ a, b\}$ and $\Gamma_2$ = $\{ c,d \}$ and $\gamma = \{a\}$ and
-$\gamma\prime = \{a,d\}$. We have: level$(\gamma) = 1$ and level$(\gamma\prime) = 2$.
-\end{example}
-
-\subsection{Strategic and Tactic Reasoning}\label{sec:reasoning}
-A preliminary framework for strategic and tactic reasoning for agent communication was proposed in~\cite{Mbarki06}. This
-reasoning framework is specified using argumentation theory combined to a relevance theory. Strategic reasoning enables agents
-to decide about the global communication plan in terms of the macro-actions to perform in order to achieve the main dialogue
-goal. Tactic reasoning, on the other hand, allows agents to locally select, at each dialogue step the most appropriate
-argument according to the adopted strategy.
-
-In this paper, we refine, and use the notion of strategic and tactic reasoning. The agent uses his tactic reasoning at each dialogue
-step to measure his uncertainty about selecting the right move to achieve some sub goals of the global goal (i.e., the agreement in our case).
-In other words, how agent can select the right argument from a set of possible choices at certain dialogue step depends on his tactic by assigning
-different probability values to the different arguments and select the one with higher probability to be accepted by his opponent. On the other hand,
-this tactic is based on the adapted strategy that the agent built before starting the negotiation to achieve the agreement. Moreover, we study the
-relationship between these two types of uncertainty not only when a unique move is considered, but also when the whole dialogue is being analyzed.
-
-%\subsubsection{Strategic Reasoning}\label{sec:Strategic}
-\textbf{Strategic Reasoning}\\
-Before engaging in a negotiation, agents must build a global strategy on the sub-goals to achieve. Sub-goals determine the general steps to follow so
-that the global goal can be realized. Strategy is subject to the agent's current beliefs and constraints, such as the agent's budget and negotiation
-time limit. To achieve the same negotiation goal, an agent can have several alternative strategies reflected by different sets of subgoals. The dialogue
-goal, sub-goals, and constraints can be expressed using propositional logic. The set of constraints can be inconsistent, but the sub-set of those constraints
-and the sub-set of beliefs the agent decides to consider should be consistent. We define the strategy as a function that associates to a goal and a sub-set
-of consistent beliefs and constraints a sub-set of alternatives, each of which is a set of sub goals, which means an element of the set $2^{2^{\mathbb{B}}}$,
-where $\mathbb{B}$ is the set of goals.
-
-\begin{definition}{\emph{[Strategy]\footnote{This definition is different than the one proposed in~\cite{Mbarki06}, in the sense that this function
-associates a set of sub-goals to a sub-set of agent's knowledge base and constraints instead of associating a set of goals to a set of operational constraint
-and a set of conversational criterions.}. }} \label{strategy}
-Let $\mathbb{B}$ be a set of goals, $\mathbb{C}$ a set of constraints and $\Gamma$ the agent's knowledge base. A strategy is a function:
-\begin{equation}\label{equation2-}
-\mathcal{S}: \mathbb{B} \times 2^{\mathbb{C}} \times 2^{\Gamma}
-\rightarrow 2^{2^{\mathbb{B}}}
-\end{equation}
-\end{definition}
-
-%\subsubsection{Tactic Reasoning}\label{sec:tactic}
-\textbf{Tactic Reasoning} \\
-Tactics allow agents to select one action (i.e., the content of the move or the argument) from a set of possible actions (i.e., set of
-arguments) in order to achieve a sub-goal as computed by the adapted strategy. The purpose of this theory is to ensure that the selected argument
-is the most appropriate one according to the current context i.e., the less risk of failure, the more favorable and the more preferable one,
-which means the move with the higher probability. Our aim is to investigate the uncertainty issues associated with the agent while taking decision
-and selecting the arguments. By refining some definition in the work presented in~\cite{Mbarki06} such as the definition of strategy, context,
-tactic, and risk of failure. We will advocate some criteria that help to compute and analyze the agents' uncertainty at each negotiation step i.e., at
-the tactic level. and based on these criteria we classify the set of possible arguments into three different classes ``\textit{Arguments Classification}",
-which will be introduced later on in section~\ref{sec:classification}. This also will help the agents to assign the probability to each possible argument
-and use it in measuring the uncertainty using Shannon Entropy as it will be explained in section~\ref{moveuncertainty}. Arguments classification is based
-on the relevance of arguments, risk of failure, favorite and preference relations. In the following we will discuss the definitions of these notions.
-
-\textbf{Relevance of Argument.} \\
-We define the relevance of argument as in~\cite{Mbarki06} according to the conversation context. This will allow the participants in the dialogue to
-select the most relevant argument from the set of possible arguments at certain dialogue step by taking into account the last communicative act as well as the
-previous ones. This will give the agents the ability of backtracking in case the choice is shown to be incorrect because the selected argument is not accepted
-by the addressee. The arguments are ordered based on their relevance, and the process of selecting arguments is called \emph{Arguments Selection Mechanism}.
-
-%The authors in~\cite{Mbarki06}, have defined the relevance of an argument according to the conversation context. The objective is
-%to allow agents to select the most relevant argument from the set of possible arguments at a given dialogue step by taking into
-%account the last communicative act as well as the previous ones. This will give the participants the ability of backtracking in
-%case the choice is shown to be incorrect because the selected argument is not accepted by the addressee. The arguments are
-%ordered based on their relevance, and the process of selecting arguments is called \emph{Arguments Selection Mechanism}.
-
-\textbf{Arguments Selection Mechanism.} \\
-Let $\pounds$ be a logical language. We define the conversation context for an agent $Ag_1$ committed in a conversation with
-another agent $Ag_2$ as follows:
-
-\begin{definition}{\emph{[Context].}} \label{context}
-The conversation context for an agent $Ag_1$ (the speaker) committed in a conversation with an agent $Ag_2$ (the addressee)
-is a 7-tuple $C_{Ag_1,Ag_2} = \big<\mathcal{S},\mathcal{T},T,s,P_{Ag_1,Ag_2},CK\big>$ where:
-\begin{itemize}
-  \item $\mathcal{S}$ is the speaker's strategy;
-
-  \item $\mathcal{T}$ is the current speaker's tactic, which we will define after introducing all the context elements;
-
-  \item $T$ is a formula of $\pounds$ representing the negotiation topic that corresponds to the global goal;
-
-  \item $s$ is a formula of $\pounds$ representing the argument on which the speaker should act;
-
-  \item $P_{Ag_1,Ag_2}$ is the set of $Ag_{1}^{\prime}s$ beliefs about $Ag_{2}^{\prime}s$ beliefs $P^{bel}_{Ag_1,Ag_2}$ and
-   about $Ag_{2}^{\prime}s$ preferences $P^{pref}_{Ag_1,Ag_2}$.   Thus $P_{Ag_1,Ag_2}$ = $P^{bel}_{Ag_1,Ag_2} \cup P^{pref}_{Ag_1,Ag_2}$;
-
-  \item $CK$ is the common knowledge that the two agents share about the conversation.
-\end{itemize}
-In this definition we refine the context definition proposed in~\cite{Mbarki06} by adding the speaker strategy, the current
-speaker tactic and the negotiation topic that corresponds to the global goal.
-\end{definition}
-During negotiation, $CK$ is constantly updated by adding all the information on which the two agents agree, including the accepted
-arguments. We also assume that $CK \cap P_{Ag_1,Ag_2} = \emptyset$. In the context $C_{Ag_1,Ag_2}$, the influence of the
-strategy on the tactic is reflected through the link between the topic $T$, the current argument $s$ and the strategy
-$\mathcal{S}$. Let $\mathbb{T}$ be the set of topics ($T \in \mathbb{T}$), $g$ the current goal ($g \in \mathbb{B}$), $C$ the
-sub-set of current constraints ($C \in \mathbb{C}$), $\gamma$ the sub-set of beliefs the agent is currently considering ($\gamma \in
-\Gamma$), and $\mathbb{A}$ the set of arguments ($s \in \mathbb{A}$), we define the tactic as follows:
-
-\begin{definition}{\emph{[Tactic]. }} \label{tactic}
-A tactic is a function:
-\begin{equation}\label{equation2}
-\mathcal{T}: \mathbb{T} \times \mathcal{S}(g,C,\gamma) \times
-\mathbb{A} \rightarrow \mathbb{B}
-\end{equation}
-\end{definition}
-
-The key idea is that the current action (at the tactic level) is related to a sub-goal, which is determined by the strategy. From
-the operational perspective, the current argument $s$ can attack or support the formula representing the sub-goal $T$. In order to
-define the logical relation between $T$ and $s$, the authors in \cite{Mbarki06} introduced the notion of argumentation tree and
-the notion of path that are defined as follow.
-
-\begin{definition}{\emph{[Argumentation Tree].}} \label{tree}
-Let $Ag$ be the set of participating agents and $Arg \subseteq \mathbb{A}$ be the set of arguments used by the agents in the
-dialogue. An argumentation tree $Tr$ is a 2-tuple $Tr =\big<N,\rightarrow\big>$ where:
-
-\begin{itemize}
-  \item $N = \{(Ag_i, (H, h)) \mid Ag_i \in Ag, (H, h) \in Arg \}$ is the set of nodes. Each node is described as a pair $(Ag_i, (H, h))$,
-  which indicates that the argument $(H, h)$ is used by the agent $Ag_i$.
-  \item $ \rightarrow \subseteq  N \times N $ is a relation between nodes. We write $n_0 \rightarrow n_1$ instead of $(n_0, n_1) \in \rightarrow $
-  where $\{n_0, n_1\} \subseteq N$. The relation $ \rightarrow $ is defined as follows:
-       $(Ag_1, (H, h)) \rightarrow (Ag_2, (H^{\prime}, h^{\prime}))$ iff $Ag_1 \neq Ag_2$ and $(H^{\prime}, h^{\prime})$ attacks $(H, h)$.
-\end{itemize}
-\end{definition}
-
-\begin{definition}{\emph{[Path]. }} \label{path}
-Let $Tr = \big<N, \rightarrow \big>$ be an argumentation tree. A path in $Tr$ is a finite sequence of nodes $n_0, n_1,\cdots , n_m$
-such that $\forall i$ ,$   0 \leq i < m $ : $n_i \rightarrow n_{i+1}$.
-\end{definition}
-
-In order to distinguish between relevant and irrelevant arguments in a given context  let us recall the definition of irrelevant
-arguments:
-
-\begin{definition}{\emph{[Irrelevant Argument]. }} \label{irrelevant}
-Let $C_{Ag_1,Ag_2}$ = $\big<\mathcal{S}, \mathcal{T},T, s,P_{Ag_1,Ag_2},CK \big>$ be a conversation context, $Ag$ be the
-set of participating agents, $Tr = \big<N, \rightarrow \big>$ be the argumentation tree associated to the conversation, and $(Ag_i,
-(H, h))$ be a node in $Tr$ where $i \in \{1, 2\}$. $(H, h)$ is irrelevant in the context $C_{Ag_1,Ag_2}$ iff:
-
-\begin{enumerate}
-  \item  There is no path between the node $(Ag_i, (H, h))$ and the root of $Tr$ or;
-  \item  $\exists x \in  CK : H \vdash \neg x$.
-
-\end{enumerate}
-\end{definition}
-
-The distinction between relevant and irrelevant arguments allows agents to eliminate irrelevant arguments at each dialogue step before
-ordering the relevant arguments in order to select the most relevant one.
-Agents also have private preferences about different knowledge. Therefore, they may have private preferences about arguments.
-This preference relation denoted by $(H, h)  \ll^{Ag_i}_{pref}  (H^{\prime}, h^{\prime})$ means that agent $Ag_i$ prefers the
-argument $(H^{\prime}, h^{\prime})$ to the argument $(H, h)$.
-
-\begin{definition}{\emph{[Preference]. }} \label{preference}
-Let $(H, h)$ and $(H^{\prime}, h^{\prime})$ be two arguments. $(H, h)  \ll^{Ag_i}_{pref}  (H^{\prime}, h^{\prime})$ iff level $(H^{\prime}) \leq$ level $(H)$.
-\end{definition}
-
-Because $\leq$ is an ordering relation, the preference relation $\ll^{Ag_i}_{pref}$ is reflexive, antisymmetric, and transitive.
-Agents may also have favorites among their arguments. How an agent favors an argument over others depends on the dialogue type. For
-example, in a persuasive dialogue, an agent can favor arguments having more chances to be accepted by the addressee. In order to
-characterize this notion, we introduce the notion of weight of an argument. The weight of an argument $(H,h)$ compared to another
-argument $(H^{\prime},h^{\prime})$ in the context $C_{Ag_1,Ag_2}$ = $\big<\mathcal{S},\mathcal{T},T, s,P_{Ag_1,Ag_2},CK\big>$ is
-denoted by $W_{(H,h)/(H^{\prime},h^{\prime})}^{P_{Ag_1,Ag_2}}$ and is evaluated according to the following algorithm:
-
-\begin{algorithm}{\emph{\textbf{Algorithm} 1.}} \label{algorithm1}\\
-\\ Step 1:  $ W_{(H,h)/(H^{\prime},h^{\prime})}^{P_{Ag_1,Ag_2}} = 0 . $ \\
-\\Step 2:  $(\forall x \in H),(\forall x^{\prime}  \in H^{\prime} ):
- ( pref(x,x^{\prime}) \in P_{Ag_1,Ag_2}^{pref})\Rightarrow W_{(H,h)/(H^{\prime},h^{\prime})}^{P_{Ag_1,Ag_2}} = W_{(H,h)/(H^{\prime},h^{\prime})}^{P_{Ag_1,Ag_2}}  +  1 $
-\end{algorithm}
-
-$pref(x,x^{\prime}) \in P_{Ag_1,Ag_2}^{pref} $ means that $Ag_1$ believes that $Ag_2$ prefers $x$ to $x^{\prime}$. According to
-this algorithm, the weight of an argument $(H, h)$ compared to another argument $(H^{\prime}, h^{\prime})$ is incremented by 1
-each time $Ag_1$ believes that $Ag_2$ prefers a knowledge in $H$ to a knowledge in $H^{\prime}$. Indeed, each element of $H$ is
-compered once to each element of $H^{\prime}$ according to the preference relation. Consequently, the computation algorithm of
-the weight of an argument is finite because $H$ and $H^{\prime}$ are finite sets. The favorite relation is denoted by
-$\preceq_{fav}^{P_{Ag_1,Ag_2}}$ and the strict favorite relation is denoted by $\prec_{fav}^{P_{Ag_1,Ag_2}}$.  $(H, h)
-\preceq_{fav}^{P_{Ag_1,Ag_2}}  (H^{\prime},h^{\prime})$ means that agent $Ag_1$ favors the argument $(H^{\prime},h^{\prime})$ over
-the argument $(H, h)$ according to $P_{Ag_1,Ag_2}$. This relation is defined as follows.
-
-\begin{definition}{\emph{[Favorite Argument]. }} \label{favorite}
-Let $C_{Ag_1,Ag_2}$ = $\big<\mathcal{S},\mathcal{T},T, s,P_{Ag_1,Ag_2},CK\big>$ be a conversation context and $(H, h)$
-and $(H^{\prime},h^{\prime})$ be two arguments in the context $C_{Ag_1,Ag_2}$. We have:
-\begin{itemize}
-\item $(H, h)\preceq _{fav}^{P_{Ag_1,Ag_2}} (H^{\prime},h^{\prime})$ iff   $ W_{(H,h)/(H^{\prime},h^{\prime})}^{P_{Ag_1,Ag_2}} \leq W_{(H^{\prime},h^{\prime})/(H,h)}^{P_{Ag_1,Ag_2}}$ , \\
-\item $(H, h)\preceq _{fav}^{P_{Ag_1,Ag_2}} (H^{\prime},h^{\prime})$ iff   $ W_{(H,h)/(H^{\prime},h^{\prime})}^{P_{Ag_1,Ag_2}} < W_{(H^{\prime},h^{\prime})/(H,h)}^{P_{Ag_1,Ag_2}}$.
-\end{itemize}
-\end{definition}
-
-In order to allow agents to select the most relevant argument in a conversation context, an ordering relation between relevant
-arguments is used. This ordering relation depends on the adopted strategy and is based on the notion of the risk of failure of an
-argument. This notion of risk is subjective and there are several heuristics to evaluate it. In this paper, we use a heuristic based
-on the fact that $CK$ contains certain knowledge and $P_{Ag_1,Ag_2}$ contains uncertain beliefs. To define this notion
-formally, let $|H|_{\emptyset}$ be the number of formulas in $H$ that are not in $CK \cup P_{Ag_1,Ag_2}$, $|H|_{CK}$ be the number
-of formulas in $H$ that are in $CK$, and $|H|_{P_{Ag_1,Ag_2}}$ be the number of formulas in $H$ that are in $P_{Ag_1,Ag_2}$.
-
-\begin{definition}{\emph{[Risk of Failure of an Argument]. }} \label{risk}
-Let $C_{Ag_1,Ag_2}$ = $\big<\mathcal{S},\mathcal{T},T, s,P_{Ag_1,Ag_2},CK\big>$ be a conversation context and $(H, h)$
-and $(H', h')$ be two relevant arguments in the context $C_{Ag_1,Ag_2}$. The risk of failure $risk(H, h)$ of an argument
-$(H, h)$ is a function mapping an argument to a natural number that satisfies the following property: $risk(H, h)\geq risk(H',
-h')$ iff:
-\begin{itemize}
-\item   $|H|_{\emptyset} \geq |H'|_{\emptyset}$; or
-
-\item   $|H|_{\emptyset} = |H'|_{\emptyset}$ and $|H|_{CK} \leq
-|H'|_{CK}$; or
-
-\item $|H|_{\emptyset} = |H'|_{\emptyset}$, $|H|_{CK} =
-|H'|_{CK}$, and $|H|_{P_{Ag_1,Ag_2}} \leq |H'|_{P_{Ag_1,Ag_2}}$.
-\end{itemize}
-\end{definition}
-
-Other approaches like those used in fuzzy systems to reason with uncertainty (using for example probabilities and possibilities)
-can also be used to evaluate the risk of an argument. The advantages of our approach are its straightforward implementation
-and additivity over uncertain hypotheses, which means adding uncertain hypotheses increases the risk of failure of an argument.
-The relevance ordering relation denoted by $\preceq_r$ is defined as follows.
-
-\begin{definition}{\emph{[Relevance Ordering Relation].}} \label{relevance}
-Let $C_{Ag_1,Ag_2} = \big<\mathcal{S},\mathcal{T},T, s,P_{Ag_1,Ag_2},CK\big>$ be a conversation context and $(H, h)$
-and $(H^{\prime},h^{\prime})$ be two relevant arguments in the context $C_{Ag_1,Ag_2}$. $(H^{\prime},h^{\prime})$ is more
-relevant than $(H, h)$ denoted by $(H, h) \preceq_r (H^{\prime},h^{\prime})$ iff:
-\begin{itemize}
-\item $risk(H^{\prime},h^{\prime}) < risk(H, h)$; or
-
-\item $risk(H^{\prime},h^{\prime}) = risk(H, h)$ and $(H, h) \prec_{fav}^{P_{Ag_1,Ag_2}} (H^{\prime},h^{\prime})$; or
-
-\item $risk(H^{\prime},h^{\prime}) = risk(H, h)$ and $(H, h) \preceq_{fav}^{P_{Ag_1,Ag_2}} (H^{\prime},h^{\prime})$ and
-$(H^{\prime},h^{\prime}) \preceq_{fav}^{P_{Ag_1,Ag_2}} (H,h)$ and $(H,h) \ll_{pref}^{Ag_1} (H^{\prime},h^{\prime}) $.
-\end{itemize}
-\end{definition}
-
-According to this definition, $(H^{\prime},h^{\prime})$ is more relevant than $(H, h)$ if the risk of $(H, h)$ is greater than the
-risk of $(H^{\prime},h^{\prime})$. If the two arguments have the same risk, the more relevant argument is the more favorable one
-according to the favorite relation. If the two arguments have the same risk and they are equal according to the favorite relation,
-the more relevant argument is the more preferable one according to the preference relation. The two arguments have the same relevance
-if in addition they are equal according to the reference relation.
-
-\subsubsection{Computational complexity of the Selection Mechanism}
-
-Computationally speaking, the arguments selection mechanism is based on :
-\begin{enumerate}
- \item The elimination of irrelevant arguments;
- \item The construction of new relevant arguments;
- \item The ordering of the relevant arguments using the relevance ordering relation; and
- \item The selection of one of the most relevant arguments.
-
-\end{enumerate}
-
-This process is executed by each participating agent at each dialogue step at the tactical level. The relevant arguments that
-are not selected at a step $t_i$, are recorded and added to the set of potential arguments $PA$ because they can be used at a
-subsequent step. The set of potential arguments can be viewed as a stack in which the higher level argument is the most relevant one.
-A relevant argument constructed at a step $t_i$ and used latter at a step $t_j$ simulates the backtracking towards a previous node in
-the argumentation tree and the construction of a new path.
-
-Here we prove that our selection mechanism is tractable if arguments are represented using propositional Horn clauses.
-propositional Horn clauses is a restricted language that has been proved to be sufficient to represent and reason about
-knowledge in many concrete applications \cite{BentaharIEEEIS2007}. A propositional Horn clause is a disjunction of literals, which are
-atomic propositions (called positive literals) or their negations (called negative literals), with at most one positive literal.
-Formally, a propositional Horn clause has the form $\neg p_1 \vee \neg p_2 \vee \dots \vee \neg p_n \vee c$ or also $p_1 \wedge p_2
-\wedge \dots \wedge p_n \rightarrow c$, which is simply an implication. A propositional Horn formula is a conjunction of
-propositional Horn clauses. We focus on a further restriction called propositional definite Horn clauses, where each clause has
-exactly one positive literal. A propositional definite Horn formula is a conjunction of propositional definite Horn clauses.
-This restriction is of particular interest in modeling argumentation reasoning for negotiation, because formulas of the
-type $p_1 \wedge p_2 \wedge \dots p_n \rightarrow c$ are adequate to describe interrelationships between premises (i.e., reasons or
-justifications) and conclusions (i.e., offers). Thus, agents could support their offers (the part $c$) as positive literals using the
-support $p_1 \wedge p_2 \wedge \dots p_n$.
-
-\begin{theorem}\label{Complexity1}
-If arguments are represented in proportional definite Horn clauses, the arguments selection mechanism runs in polynomial time.
-\end{theorem}
-
-\noindent\emph{\textbf{Proof.}} \emph{It is known from Bentahar et al. \cite{BentaharIEEEIS2007}, that given a Horn knowledge base
-$\Gamma$, a subset $H \subseteq \Gamma$, and a formula $h$; checking whether $(H, h)$ is an argument is polynomial. To decide
-if an argument is irrelevant, we have to check if 1) $H \vdash \neg x$ for an $x \in CK$, which can be done in polynomial time
-since $H$ is a definite Horn formula; or 2) there is a path from the root to $(H, h)$, which is a graph reachability problem, and
-it is known by Jones \cite{Jones} that the problem is in NLOGSPACE. Since NLOGSPACE $\subseteq$ P, the problem can be
-solved in polynomial time. To decide about the preference, we only need to compute the level of an argument from the level of a
-subset of $\Gamma$, which is  a simple procedure that is obviously polynomial. Computing the favorite argument given two arguments
-needs the computation of the arguments' weight, which is again a polynomial procedure as shown by Algorithm 1. To compere two given
-arguments using the risk, we only need to compute the number of formulas in $H$ and check if they are part of different sets,
-which is a polynomial procedure. Finally, the relevance ordering relation is simply based on comparing risks and favorites, which
-are both polynomial, so we are done.}~~$\blacksquare$
- \section{Agent's Uncertainty}\label{sec:uncertainty}
-
-\subsection{Generalities and Overview}
-
-The process of selecting arguments is always associated with a degree of uncertainty. Despite the agent will select the most relevant argument
-at each dialogue step using his theory and tactic reasoning, however, there still be a doubt that the selected argument is the right one
-and it will be accepted by the addressee.  To measure this uncertainty, we use Shannon entropy as we did in our pervious work ~\cite{MareyBE09}, a
-well-known technique that defines and quantifies the information. The idea behind Shannon entropy in information theory is based on the amount of
-randomness that exists in a random event. In dialogue games, we assume that at each dialogue step, the agent has different choices of arguments
-(i.e., the set of potential arguments $PA$ at that step) and he will select one of them. The selection is based on the speaker's knowledge base and
-characterized by an amount of uncertainty over this base and an amount of randomness over the addressee's knowledge, beliefs, and preferences. Indeed,
-Shannon entropy is a measure of the uncertainty associated with a random variable (i.e., in our case, the selected argument). The more uncertain we are
-about the content of the message, the more informative it is~\cite{CoverT91}.
-
-\begin{definition}{\emph{[Shannon entropy]. }} \label{entropy}
-Shannon entropy for a discrete random variable \emph{$X$} taking its values from a set of values \emph{$S$} (sample space),
-with probability mass function \emph{$P(x)$} is given by Equation~\ref{equation1}:
-
-\begin{equation}\label{equation1}
-H(X) = - \sum_{x\in S} P(x)Log P(x)
-\end{equation}
-
-\end{definition}
-
-Shannon entropy $H(X)$ depends on the probability distribution of $X$ rather than the actual values of $X$. The logarithm in
-Equation~\ref{equation1} is considered to be of base 2 in the computations. The value of $H(X)$ varies from zero to $Log(|S|)$,
-where zero means that there is no uncertainty, while $Log(|S|)$ is the maximum value of uncertainty. In this paper, we aim to
-investigate to what extent we can use Shannon entropy in the evaluation of the agent's uncertainty in the dialogue. We place
-ourselves in the role of an external observer trying to evaluate the uncertainty of the participants to the dialogue i.e., how
-certain/uncertain each agent is about the selected move, how certain/uncertain he is that the selected move will be accepted by
-the addressee and the distinction between these tow types of uncertainty. The basic idea is to measure how much the agent is
-uncertain about selecting the right move $M_i$ at each step $t_i$ in dialogue $D$ by assuming that there is a set $S_i$ of choices
-facing the agent at each dialogue step. Throughout the paper, we will measure the agent's uncertainty using Shannon entropy, then
-we normalize it to have a value between zero and one and subtracting it from one to get the agent's certainty for selecting the right
-move at that step. We call this measure the \emph{certainty index} ``$CI(M_i)$" of that move, and then we calculate how much the agents
-are certain about the whole dialogue using what we call the \emph{certainty index of the dialogue} ``$CI(D)$" by taking the average of
-the certainty index of all moves in this dialogue (taking the minimum is another choice that we also discuss).
-Furthermore, we measure the certainty index of the whole dialogue by computing all possible dialogues, using the Cartesian product
-of all possible moves, and determining the probability of each dialogue, and then applying the general formula of Shannon entropy
-for the whole dialogue (exactly as what we do in the case of calculating the certainty of the moves). Moreover, we differentiate
-between to types of uncertainty; namely Type 1, and Type 2, and for the first time we classify the arguments into three classes based on
-three criteria that we will introduce later on.
-
-To allow agents to refer to their dialogue history, a data structure called commitment store $``CS"$ is used to restore
-utterances that agents utter during the dialogue~\cite{Hamblin70}.
-Let $Ag_1$ and $Ag_2$ be two agents $Ag_1 \neq Ag_2$. Also, let $\Gamma_{Ag_x}$ be $Ag_x's$ knowledge base ($x \in \{1,2\}$).
-$CS_{Ag_x}^{t_i}$ is the commitment store of agent $Ag_x$ at step $t_i$ of the dialogue. Suppose that at step $t_{i-1}$, agent
-$Ag_2$ uttered a move. To utter a move at the next step $t_i$, agent $Ag_1$ should consider his knowledge base and the content of
-$Ag_2's$ commitment store. Let $m_{i}^j$ be the $j^{th}$ move among the possible moves an agent has at the step $t_i$ and
-$P(m_{i}^j)$ the associated probability such that the relationship between the move $M_i$ and $m_{i}^j$ is as follows:
-
-\begin{equation}\label{equation3}
-\forall i ~ \exists j : M_{i} = m_{i}^j
-\end{equation}
-
-where $M_{i}$ is the selected move the agent utters at the step $t_{i}$, and the production of moves for $Ag_1$ along with their
-probabilities is a function of $\Gamma_{Ag_1}$ and $CS_{Ag_2}^{t_i}$:
-
-\begin{equation}\label{equation4}
-\zeta(\Gamma_ {Ag_1} \cup  CS_{Ag_2}^{t_i}) = \{(m_{i}^j , P(m_{i}^j)) | m_{i}^j\in S_{i}\}
-\end{equation}
-where $S_i$ is the set of choices facing the agent at the dialogue step $t_i$.
-
-We belief that such measures can help the participants to the dialogue make a better decisions for playing the most appropriate argument at
-each moment (i.e., at the tactical level) to achieve their agreements based on the adapted strategy, and it will help evaluate dialogues and strategies
-of the participants to these dialogues. In what follows we introduce the two types of agent's uncertainty.
-
-%In~\cite{MareyBE09}, we proposed a set of metrics using Shannon entropy. We placed ourselves in the role of an external observer
-%to evaluate the dialogue. The basic idea is to measure how much the agents are uncertain/certian about selecting the right move
-%$M_i$ at each step $t_i$ in dialogue $D$ by assuming that there is a set of potential moves (i.e., arguments) facing the agent at
-%each dialogue step. Based on that, we can calculate the certainty index of the dialogue $CI(D)$, which reflects the certainty degree
-%of the agents about the whole dialogue. Such measures will help evaluate dialogues and strategies of the
-%participants to these dialogues.
-%
-%In this paper, we extend our previous work to evaluate the uncertainty/certainty index that the selected move will be
-%accepted by the addressee and analyze the relationship between these two types of uncertainty (i.e., the agent's uncertainty about
-%selecting the right move and the agent's uncertainty that the selected move will be accepted by the addressee). Moreover, we
-%analyze special cases in which we cannot consider the certainty index as an indicator of the agent's certainty that the selected
-%move will be accepted by the addressee, but as a representation of the agent's certainty about selecting the right move at that step.
-%For instance, when there is only one argument, or all the available arguments have the same probability. We belief that such
-%measures can help the participants to the dialogue make decisions for playing the most appropriate argument at each moment (at the
-%tactical level) to achieve their goals based on the adapted strategy.
-
-%For simplification reasons, we will consider only two agents involved in the dialogue $Ag_1$ and $Ag_2$. Multi-party dialogue
-%is an important issue that we plan to investigate in future work. During a dialogue, several moves may be uttered. Those moves
-%constitute a dialogue $D$, which is a sequence of moves denoted by $[M_0,M_1,\cdots ,M_n]$, where $M_0$ is the initial move, $M_n$ is
-%the final one, and $|D|$ is the length of the dialogue (i.e., $|D|
-%= n$).
-
-\subsection{Agent's Uncertainty: Type I}\label{sec:type1}
-
-In this section, we will discuss to what extent we can use Shannon entropy in dialogue games to measure the uncertainty/certainty
-index of the agents about their dialogue. To do so, we measure the uncertainty index of the agents about their moves and then we
-compute the uncertainty index about the whole dialogue. The following two subsections illustrate these measures.
-
-\subsubsection{Measuring How Certain the Agent is about his Move}\label{moveuncertainty}
-To measure the uncertainty index of the agent about his move, we calculate Shannon entropy of that move, which means the agent's
-uncertainty about selecting the right move at a given dialogue step. Here we consider only possible moves, which are moves whose
-the associated probability is in $[0,1]$. Then we normalize this value by dividing it by the logarithm of the number of all
-possible moves at that step. By subtracting the normalized value from one; we get the agent's certainty index about selecting the
-right move at this step.
-
-\begin{definition}{\emph{[Move's entropy]. }} \label{Move'sentropy}
-Let $D = [M_0, M_1, \ldots, M_n]$ be a negotiation dialogue, and suppose that at each dialogue step $t_i$ a set $S_i$ of moves
-$\{m_i^1,m_i^2,\ldots,m_i^k\}$ are possible, and each one of them is associated with a given probability $P(m_i^j) = 1-risk(m_i^j)$,
-such that $\sum_{m_i^j\in S_i} P(m_i^j)=1$. Shannon entropy for a random move $M_i$ taking its values from the set of moves $S_i$ is
-defined by:
-\begin{equation}\label{equation5}
-H(M_i) = - \sum_{m_i^j\in S_i}P(m_i^j)Log P(m_i^j)
-\end{equation}
-\end{definition}
-
-The value of $H(M_i)$ varies from zero to $Log(|S_i|)$, where zero means that there is no uncertainty (i.e., there is only one
-choice), while $Log(|S_i|)$ means that the uncertainty is at its maximum value (i.e., all moves have the same probability). We
-further normalize $H(M_i)$ to have a metric that ranges from 0 to 1. This can be achieved by dividing $H(M_i)$ by $Log(|S_i|)$. So,
-the uncertainty about selecting the right move is given by:
-
-\begin{equation}\label{equation6}
-\mu(M_i)=
-\begin{cases} 0 & \text{\emph{iff}}~~~Log(|S_i|)=0
-\\
-H(M_i)/Log(|S_i|) &otherwise
-\end{cases}
-\end{equation}
-
-\begin{proposition} \label{proposition1}
-The uncertainty of a move $M_i$ at a certain step $t_i$ during the dialogue is equal to zero (i.e., $\mu(M_i)=0$) iff at that step the
-agent has only one choice.
-\end{proposition}
-
-\noindent\emph{\textbf{Proof.}}\\
-\emph{$\mu(M_i)= 0 \Leftrightarrow Log(|S_i|)=0$\\
-\\ $\Leftrightarrow  |S_i|=1$.~~$\blacksquare$}
-
-So, there is only one move in $S_i$ available to the agent at step $t_i$. Intuitively, at the beginning steps of a dialogue, the
-uncertainty is expected to be high as all possible moves have close probabilities, then gradually the uncertainty decreases,
-because agents are rational and they learn from each other when advancing in the dialogue.
-
-\begin{proposition}\label{proposition2}
-The uncertainty of a move $M_i$ at a certain step $t_i$ during the dialogue is equal to one $($i.e., $\mu(M_i)=1)$ iff at that step,
-all the moves in $S_i$ have the same probability.
-\end{proposition}
-
-\noindent\emph{\textbf{Proof.}}
-
-\emph{Let us first prove the direct implication $\Rightarrow$. We assume that all the moves at a certain step \emph{$t_i$} have the
-same probability, and prove that the uncertainty is equal to one. Without loss of generality, we assume that \emph{$|S_i|=k_i$}. So
-we have:
-\\ $\mu(M_i) = H(M_i)/Log(k_i)$\\
-\\ $= - \sum_{m_i^j\in S_i, j=1}^{k_i}~P(m_i^j)Log P(m_i^j)/Log(k_i)$\\
-\\ $= -{k_i}[(1/{k_i})Log(1/{k_i})]/Log(k_i)$\\
-\\ $= -[Log(1/{k_i})]/Log(k_i)$\\
-\\ $= Log(k_i)/Log(k_i)$\\
-\\ $= 1$ \\\\
-Let us now prove the inverse implication $\Leftarrow$. We assume that the uncertainty is
-equal to one, and prove that all moves have the same probability. So we have:\\
-\\ $\mu(M_i) = 1 $   \\
-\\ $\Rightarrow 1= H(M_i)/Log(k_i)$\\
-\\ $\Rightarrow 1= - \sum_{m_i^j\in S_i, j=1}^{k_i}~P(m_i^j)Log P(m_i^j)/Log(k_i)$\\
-\\ $\Rightarrow - Log(k_i)= \sum_{m_i^j\in S_i, j=1}^{k_i}~P(m_i^j)Log P(m_i^j)$\\
-\\ $\Rightarrow Log(1/k_i)= \sum_{m_i^j\in S_i, j=1}^{k_i}~P(m_i^j)Log P(m_i^j)$\\
-\\ $\Rightarrow Log(1/{k_i})= P(m_i^1)Log P(m_i^1) + P(m_i^2)Log P(m_i^2)+ \ldots + P(m_i^{k_i})Log P(m_i^{k_i})$\\
-\\By taking the exponential of both sides of the equation, we obtain:\\
-\\ $\exp^{Log(1/{k_i})}=\exp^{P(m_i^1)Log P(m_i^1) + P(m_i^2)Log P(m_i^2)+ \ldots + P(m_i^{k_i})Log P(m_i^{k_i})}$\\
-\\ $\Rightarrow 1/{k_i} = \exp^{P(m_i^1)Log P(m_i^1)} * \exp^{P(m_i^2)Log P(m_i^2)}* \ldots * \exp^{P(m_i^{k_i})Log P(m_i^{k_i})}$\\
-\\ $\Rightarrow 1/{k_i} = \exp^{Log{P(m_i^1)^{P(m_i^1)}}}* \exp^{Log P(m_i^2)^{P(m_i^2)}}* \ldots * \exp^{Log P(m_i^{k_i})^{P(m_i^{k_i})}}$\\
-\\ $\Rightarrow 1/{k_i} = {P(m_i^1)^{P(m_i^1)}}*{P(m_i^2)^{P(m_i^2)}}* \ldots * {P(m_i^{k_i})^{P(m_i^{k_i})}}$\\
-\\ $\Rightarrow 1/{k_i} = \Pi_{m_i^j\in S_i, j=1}^{k_i}~{P(m_i^j)^{P(m_i^j)}}$ \\
-\\Because $1$ is the maximum uncertainty, the solution of this equation can be obtained by resolving the following optimization problem:
-%
-\begin{equation*}
-Max[\Pi_{m_i^j\in S_i, j=1}^{k_i}~{P(m_i^j)^{P(m_i^j)}}] \\
-\end{equation*}
-~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$subject~ to:$
-%
-\begin{equation*}
-\begin{cases} \sum_{m_i^j\in S_i, j=1}^{k_i}~P(m_i^j)=1\\
-0<P(m_i^j)\leq 1 ~~~~~ \forall ~1 \leq j \leq {k_i}
-\end{cases}
-\end{equation*}
-%
-Using the nonlinear programming techniques, we can easily find the solution of this  problem, which is:  $\forall ~1 \leq j \leq k ~
-P(m_i^j)= 1/{k_i}$}.~~$\blacksquare$
-
-\begin{definition}{\emph{[Move's Certainty Index]}} \label{Move'sCertainty}
-Let $D=[M_0, M_1, \ldots, M_n]$ be a negotiation dialogue, and suppose that at each dialogue step $t_i$ a set $S_i$ of moves
-$m_i^j$ are possible, and each one of them is associated with a given probability $P(m_i^j)$ such that $\sum_{m_i^j\in
-S_i}P(m_i^j)=1$. If Shannon entropy of the move $M_i$ at step $t_i$ is $H(M_i)$, we define the certainty index of the move as
-follows:
-
-\begin{equation}\label{equation7}
-CI(M_i)=
-\begin{cases} 1 & \text{iff}~~~Log(|S_i|)=0
-\\
-1- H(M_i)/Log(|S_i|) &otherwise
-\end{cases}
-\end{equation}
-
-\end{definition}
-
-Using the certainty index, we can determine at each dialogue step how much the agent is certain about the move
-he can play at that time. The following lemmas are straightforward from Propositions
-\ref{proposition1} and ~\ref{proposition2}.
-
-\begin{lemma}\label{lemma1}
-The certainty index of a move $M_i$ at a given step $t_i$ in the dialogue is at its maximum value ``1" iff the agent
-has only one choice at that step.
-\end{lemma}
-
-\begin{lemma}\label{lemma2}
-The certainty index of a move $M_i$ at a given step $t_i$ in the dialogue is at its minimum value ``0" iff the agent
-has more than one move at the same step with equal probabilities.
-\end{lemma}
-
-By considering the uncertainty and certainty index of dialogue moves, agents should resolve at each dialogue step
-$t_i$ one of the following equivalent optimization problems.
-\begin{enumerate}
-  \item  At each dialogue step the agent should minimize the uncertainty index.
-
-    \begin{equation}\label{equation8}
-    M_i^* = \underset{\small{M_i}}{\operatorname{argmin}} \, \mu(M_i)
-    \end{equation}
-  \item  At each dialogue step the agent should maximize the certainty index.
-   \begin{equation}\label{equation9}
-   M_i^* = \underset{\small{M_i}}{\operatorname{argmax}} \, CI(M_i)
- \end{equation}
-
-\end{enumerate}
-
-\begin{theorem}
-There is an algorithm for solving these optimization problems in a polynomial time.
-\end{theorem}
-
-\noindent\emph{\textbf{Proof.}} \emph{
-Because these problems are equivalent, we consider only one of them, for example the maximization one.
-Without loss of generality, we assume that agent $Ag_1$ should solve this problem. The algorithm is as follows:\\
-1) $Ag_1$ should calculate the probability of each possible move $m_i^j$ $(1 \leq j \leq k)$ using the \emph{moves probability function}:
- $\zeta(\Gamma_{Ag_1} \cup CS_{Ag_2}^{t_i})$ considering his knowledge base $\Gamma_{Ag_1}$ and $Ag_2's$ commitment store $CS_{Ag_2}^{t_i}$; \\
-2) take the move with the highest probability. Because $\Gamma_{Ag_1}$ and $CS_{Ag_2}^{t_i}$ are bounded at each step
-$t_i$, this calculation is clearly polynomial and searching the maximum probability is polynomial, so we are done.}
-~~$\blacksquare$
-
-This theorem is compatible with the intuition that by adding new information in $CS_{Ag_2}^{t_i}$, the number of possible choices
-decreases. However, this is only true when we consider just the next move. When we consider the whole dialogue, the complexity is
-much higher.
-
-\begin{example}\label{example1}
-Let us consider a negotiation dialogue $D$ between two agents $Ag_1$ and $Ag_2$ such that $D=[M_0, M_1, M_2]$, and the number of
-possible moves at each dialogue step is $|S_i|=3$. In the following we explain how to measure the certainty index of the
-move $M_0$. Using Equation~\ref{equation7}, we obtain:\\
-\\$CI(M_0)= 1- H(M_0)/Log(|S_0|)$\\
-\\$CI(M_0)= 1- [(-\sum_{j=1}^{3} P(m_0^j)Log P(m_0^j))/Log(3)]$\\
-\\$CI(M_0)= 1+ [(P(m_0^1)Log P(m_0^1)+P(m_0^2)Log P(m_0^2)+P(m_0^3)Log P(m_0^3))/Log(3)]$\\
-\\From Table~\ref{Table1}, we have: \\
-\\$CI(M_0)= 1+ [((0.33* -1.599) + (0.33 *-1.599)+(0.34 * -1.556))/Log(3)]$\\
-\\$CI(M_0)= 1- 1 = 0$\\\\
-%
-Table~\ref{Table1} shows the possible choices of the moves that facing agent $Ag_1$ at step $t_0$ to play his first move $M_0$ in
-the first column, and their associated probabilities in the second column. From the above calculations, we notice that the certainty
-index of agent $Ag_1$ about selecting the right move at this step is at its minimum value ``0" because agent $Ag_1$ had different
-choices of moves with equal probabilities of acceptance from the addressee agent $Ag_2$. This means that agent $Ag_1$ was uncertain
-$100 \%$ about which move he should play.
-
-\begin{table}[tbp]
-\centering \caption{Measuring the certainty index of the move
-$M_0$ in Example~\ref{example1}.} \label{Table1}
-\begin{tabular}{cccc}\hline
-\textbf{Possible Moves}&{P($m_0^j$)}&\textbf{Log P($m_0^j$)}&\textbf{P($m_0^j$)Log P($m_0^j$)}\\
-\hline
-{$m_0^1$}&{0.33}&{-1.599}&{-0.528}\\
-{$m_0^2$}&{0.33}&{-1.599}&{-0.528}\\
-{$m_0^3$}&{0.34}&{-1.556}&{-0.529}\\
-\hline
-   & {H($M_0$)=1.58}&{$\mu(M_0)=1$} & {$CI(M_0)=0$} \\
-   \hline
-\end{tabular}
-\end{table}
-%
-The above calculations and Table~\ref{Table1} are just for the first move $M_0$, and to obtain the certainty index of the other
-two moves $M_1$ and $M_2$, we use the same procedure as for $M_0$.
-
-At step $t_1$, agent $Ag_2$ to play his move $M_1$ as a reply to agent $Ag_1$, he had three different choices of moves  with
-different values of probabilities $(0.05, 0.12, 0.83)$, such that the sum is equal to one. From the calculation we find that agent
-$Ag_2$ was certain about $0.50 \%$, $(i.e., CI(M_1)= 0.50 \%)$ that he will select the move with higher probability $(0.83)$ of
-acceptance from agent $Ag_1$. The other two choices that agent $Ag_2$ had were with lower probabilities and he was uncertain
-about them.
-
-At step $t_2$, agent $Ag_1$ to reply to agent $Ag_2$ with his move $M_2$, he had different choices of moves with different values of
-probabilities $(0.9999,1E-8,1E-8)$, such that the sum is equal to one. Agent $Ag_1$ was then certain almost $100 \%$, and the
-certainty index is at its maximum value ``1". This is because all choices that he had are with very low probabilities except one of
-them was with very high probability.
-\end{example}
-
-In order to highlight the quality of information involved in the selected move in terms of its certainty index, we assign a weight
-to this move. We suppose that the selected moves have different weights reflecting the importance degree of the moves. For
-example, in some negotiation dialogues, the last moves could be more important than the first moves as they lead to an agreement.
-Let $\mathcal{M}$ be the set of all moves. The weight of the move is calculated based on algorithm 1 and assigned to the move using
-the following function:
-
-\begin{equation}\label{equation10}
-W: \mathcal{M} \rightarrow \mathbb{N}^*
-\end{equation}
-
-\begin{definition}{\emph{[Weighted Certainty Index of the Move].}} \label{WeightedCI}
-Let $D=[M_0, M_1, \ldots, M_n]$ be a negotiation dialogue, and $CI(M_i)$ the certainty index of the move $M_i$ at a step $t_i$
-and $W(M_i)$ the weight of that move at that step. We define the weighted certainty index as follows:
-
-\begin{equation}\label{equation11}
-W\_CI(M_i) = W(M_i)*CI(M_i)
-\end{equation}
-
-\end{definition}
-
-\subsubsection{Measuring how Certain the Agents are about the Dialogue}\label{dialogueuncertainty}
-In section \ref{moveuncertainty}, we discussed how to measure the agent's uncertainty/certainty about his move at each dialogue
-step. In this section, we will discuss how to measure the uncertainty/certainty index of the agents about the whole dialogue.
-We will present this in two different methods. The first method is by using the average of the calculated uncertainty/certainty index
-of all moves in the dialogue. The second one is by calculating the possible number of dialogues and the probability of each one, and
-then we apply Shannon entropy in the same way as for the moves. Measuring the certainty of the dialogue by considering the minimum
-certainty over all the moves is another way if the agent is very conservative. In this paper, we only focus on the first two methods.
-
-\textbf{Method 1: Using the Average of CI for all Moves}.\\
-The basic idea is to measure how much each agent is uncertain/certain about his move at each dialogue step. Then we
-calculate how much the two agents are uncertain/certain about the ``whole dialogue" by taking the average of the
-uncertainty/certainty index of all the moves in the dialogue.
-
-\begin{definition}{\emph{[Agents' Certainty about the Dialogue]. }} \label{agentsCIDialogue}
-Let $D =[M_0, M_1, \ldots, M_n]$ be a negotiation dialogue with length $|D| = n+1$. $Ag_1$ and $Ag_2$ are the two agents
-participating to the dialogue, where $Ag_1$ utters the even moves and $Ag_2$ utters the odd ones. $CI(M_i)$ is the certainty index
-of the move $M_i$ at the step $t_i$. The certainty index of the dialogue ``$CI(D)$" is given by:
-
-\begin{equation}\label{equation12}
-CI(D) = \sum_{M_i\in D} CI(M_i)/(|D|)
-\end{equation}
-
-\end{definition}
-
-\begin{example}\label{example2}
-Let us consider that we have three negotiation dialogues $D_1$, $D_2$ and $D_3$, such that $D_k={[M_0, M_1,\ldots, M_9]}$, $(1
-\leq k \leq 3)$. Table~\ref{Table2} shows the dialogue moves and the certainty index of each move in the dialogue. We suppose that
-it is given that at each dialogue step each agent has different choices with their associated probabilities (i.e., complement of
-risk), and we calculate the certainty index of each possible move based on Equation~\ref{equation7} as we did in
-Example~\ref{example1}. Then we compute the certainty index of each dialogue by applying Equation~\ref{equation12}. We will
-calculate the certainty index of $D_1$, and in the same way we calculate it for $D_2$ and $D_3$.
-%
-\\\\Using Equation~\ref{equation7}, we have:\\
-\\$CI(D_1)$ = $\sum_{M_{i}\in D_{1}} CI(M_i)/(|D_1|)$\\
-\\From Table~\ref{Table2}, we obtain:\\
-\\$CI(D_1) = [0.01+0.20+0.15+0.05+0.22+0.02+0.11+0.21+0.10+0.05]/10$\\
-\\$CI(D_1) = 0.112 $\\
-\\In the same way we can find that:\\
- \\$CI(D_2) = 0.503, $  and \\
- \\$CI(D_3) = 0.936 $\\\\
-%
-\begin{table}[tbp]
-\centering \caption{The certainty index of the dialogues of Example~\ref{example2}} \label{Table2}
-\begin{tabular}{cccc}\hline
-\textbf{Dialogue Moves}&\textbf{CI($M_i$) of $D_1$}&\textbf{CI($M_i$) of $D_2$}&\textbf{CI($M_i$) of $D_3$}\\
-\hline
-   {$M_0$} & {0.01} & {0.01} & {0.99} \\
-   {$M_1$} & {0.20} & {0.99} & {0.98} \\
-   {$M_2$} & {0.15} & {0.15} & {0.95} \\
-   {$M_3$} & {0.05} & {0.95} & {0.99} \\
-   {$M_4$} & {0.22} & {0.22} & {0.90} \\
-   {$M_5$} & {0.02} & {0.80} & {0.90} \\
-   {$M_6$} & {0.11} & {0.11} & {0.80} \\
-   {$M_7$} & {0.21} & {0.75} & {0.95} \\
-   {$M_8$} & {0.10} & {0.05} & {0.90} \\
-   {$M_9$} & {0.05} & {1}    & {1} \\
-\hline
-   & {CI($D_1$)=0.112} & {CI($D_2$)=0.503}    & {CI($D_3$)=0.936} \\
-\hline
-\end{tabular}
-\end{table}
-%
-We notice that for the dialogue $D_1$, the certainty index is low. This is because the certainty indexes of all the moves in this
-dialogue are low as they range between $0.01$ and $0.22$. This means that the participants were not certain about the dialogue,
-and even if they achieve an agreement, they do not know whether it is a good agreement or not.
-
-%Figure~\ref{fig1} shows the certainty indexes of the moves in these three dialogues.
-
-%\begin{figure}[t]
-%                \begin{center}
-%                \includegraphics[width=12cm, height=6cm]{Figures/CImoves.eps}
-%                \end{center}
-%                \caption{The certainty indexes of the moves in the dialogues of Example ~\ref{example2}}\label{fig1}
-%                \label{Stack}
-%                \end{figure}
-
-The certainty index of the dialogue $D_2$ is medium, and that is because of the low certainty of the agent \emph{$Ag_1$} about his
-moves during the dialogue, and the high certainty of the agent $Ag_2$ about his moves in the same dialogue. So, when we take the
-average of the certainty indexes of all the moves, we get a medium certainty index for the whole dialogue.
-
-%Figure~\ref{fig1} shows the difference between $Ag_1$ and $Ag_2$ in the performance during
-%the dialogue, where $Ag_2$ is doing better compared to $Ag_1$.
-
-In the third dialogue $D_3$, the certainty index is very high. This means the participants were very certain about their moves at
-each step during the dialogue. %We can notice from
-%Figure~\ref{fig1}, that the performance of both agents is very good.
-\end{example}
-
-Taking the average of the certainty indexes of all moves gives us an indicator about how certain the agents are about their
-dialogue. However, it does not allow us to compare different dialogues with the same certainty index. To do so, we define
-another metric called the \emph{weighted certainty index} of the dialogue by giving weights to the moves and taking the average of
-the weighted certainty indexes of all the moves.
-
-\begin{definition}{\emph{[Weighted Certainty Index of the Dialogue]. }}\label{WeightedCIDialogue}
-Let $D =[M_0, M_1,\ldots,M_n]$ be a negotiation dialogue. $Ag_1$ and $Ag_2$ are the two agents participating
-to the dialogue, where $Ag_1$ utters the even moves and $Ag_2$ utters the odd moves. $CI(M_i)$ is the certainty index
-of the move $M_i$ at the step $t_i$, and $W(M_i)$ the weight of $M_i$. The weighted certainty index of the dialogue is given by:
-\begin{equation}\label{equation13}
- W\_CI(D)=\sum_{M_i\in D}{W(M_i)*CI(M_i)}/\sum_{M_i\in D}W(M_i)
-\end{equation}
-\end{definition}
-%
-This will help us compare dialogues with the same certainty index. This is because the average of weighted certainty index of all
-moves can be different than the average of certainty index of the moves without weights ``$CI(D)$".
-%
-\begin{example}\label{example3}
-let us consider the following three negotiation dialogues $D_1$, $D_2$ and $D_3$ (that are different from the dialogues considered
-in example~\ref{example2}), such that $D_k=[M_0,M_1,\ldots,M_5]$, $(1 \leq k \leq 3)$. Table~\ref{Table3} shows the certainty index
-and weight of each move. The certainty index of each move is calculated as in example~\ref{example1}, and the certainty index of each
-dialogue is calculated based on Equation~\ref{equation12}, as in Example~\ref{example2}. By applying Equation~\ref{equation13}, we obtain
-the weighted certainty index of each dialogue. In the following we explain how we calculate the weighted certainty index for $D_1$, and
-in the same way we calculate it for $D_2$ and $D_3$.
-%
-\\\\ Using Equation~\ref{equation13}: \\
-\\ $W\_CI(D_1)=\sum_{M_i\in D_1}{W(M_i)*CI(M_i)}/\sum_{M_i\in D_1}W(M_i)$\\
-\\From Table~\ref{Table3}, we have:\\
-\\ $W\_CI(D_1)= [(0.5*1)+(0.5*2)+(0.5*3)+(0.5*4)+(0.5*5)+(0.5*6)]/21 $\\
-\\ $W\_CI(D_1)= 0.50 $\\
-and in the same way we can find that:
-\\ $W\_CI(D_2)= 0.64 $\\
-\\ $W\_CI(D_3)= 0.36 $\\\\
-%
-\begin{table}[tbp]
-\centering \caption{Weighted certainty index of the dialogues of Example~\ref{example3}} \label{Table3}
-\begin{tabular}{ccccc}\hline
-\textbf{Dialogue Moves}&\textbf{CI($M_i$) of $D_1$}&\textbf{CI($M_i$) of $D_2$}&\textbf{CI($M_i$) of $D_3$}&\textbf{W($M_i$)}\\
-\hline
-{$M_0$} & {0.50} & {0.10} & {0.90} &  {1} \\
-{$M_1$} & {0.50} & {0.25} & {0.75} &  {2} \\
-{$M_2$} & {0.50} & {0.40} & {0.60} &  {3} \\
-{$M_3$} & {0.50} & {0.60} & {0.40} &  {4} \\
-{$M_4$} & {0.50} & {0.75} & {0.25} &  {5} \\
-{$M_5$} & {0.50} & {0.90} & {0.10} &  {6} \\
-\hline
- & {CI($D_1$)=0.50} & {CI($D_2$)=0.50} & {CI($D_3$)=0.50} \\
- & {W\_CI($D_1$)=0.50} & {W\_CI($D_2$)=0.64} & {W\_CI($D_3$)=0.36} \\
-\hline
-\end{tabular}
-\end{table}
-
-From the calculations and Table ~\ref{Table3}, we see that in $D_1$ the agents have the same $CI$ from the first move
-till the last one, and it is medium so the certainty index of the whole dialogue is medium too. In $D_2$, the agents were
-uncertain about their moves (i.e. $CI$ very low) in the very early stages of the dialogue, and then the $CI$ of their moves started
-increasing to reach 0.90, which is a very good certainty index to guarantee a good agreement. While in $D_3$, we notice the opposite
-situation of $D_2$, where the agents have started very certain about their moves then their certainty started decreasing, which might
-result in not achieving an agreement. In this example, if we look at $W\_CI$ of each dialogue, we see that $D_2$ is the best dialogue,
-because its weighted certainty index is greater than that of $D_1$ and $D_3$, followed by $D_1$ and then $D_3$. We notice in the case
-of $D_2$ that both agents have started with low certainty about their moves, then they have started learning from each other till they
-become more certain, especially in the last two moves. Also, we notice that the three different dialogues have the same certainty index,
-so by calculating just the certainty index of the dialogue we cannot compare such dialogues except if we look at the performance of the
-participants during the dialogue. However, we can do so by calculating the weighted certainty index of each dialogue, which gives us a
-good indicator about the goodness of dialogues.
-
-%\begin{figure}[t]
-%                \begin{center}
-%                \includegraphics[width=12cm, height=6cm]{Figures/CIexam3.eps}
-%                \end{center}
-%                \caption{The certainty indexes of the three dialogues of example \ref{example3}}\label{fig2}
-%                \label{Stack}
-%                \end{figure}
-
-%Figure~\ref{fig2} shows the diagrams of certainty indexes of the moves in the three dialogues.
-
-Figure~\ref{fig3} shows the weighted certainty indexes of the moves for the three dialogues, and here we can see the
-difference between the three dialogues after giving weights to the moves as we discussed before.
-\begin{figure}[t]
-                \begin{center}
-                \includegraphics[width=12cm, height=6cm]{Figures/WCIexam3.eps}
-                \end{center}
-                \caption{The weighted certainty indexes of the three dialogues of example \ref{example3}} \label{fig3}
-                \label{Stack}
-                \end{figure}
-\end{example}
-
-\textbf{Method 2: Using the Probability of all Possible Dialogues}\\
-In this method, we measure the certainty index of the dialogue by calculating the number of all possible dialogues using the Cartesian
-product of all possible moves $m_i^j$ at each step $t_i$ in the dialogue. Thus, by knowing the probability of each possible move, we
-can calculate the probability of each possible dialogue, and then we apply the general formula of Shannon entropy.
-
-\begin{definition}{\emph{[Number of Possible Dialogues]. }} \label{NofPDialogues}
-Let $D = [M_0, M_1,\ldots, M_n]$ be a negotiation dialogue and $Ag_1$ and $Ag_1$ are the two agents participating to it. Suppose
-that at each dialogue step $t_i$, the move $M_i$ has a set $S_i$ of possible moves $S_i=\{m_i^1,m_i^2,\ldots, m_i^{k_i}\}$, each
-one with probability $P(m_i^j)$. The number of all possible moves is equal to $\sum_{i=0}^{n} k_i$. The union of all sets of the
-moves is $\Omega= S_1 \cup S_2 \cup \ldots \cup S_n$, such that there is no intersection between the sets of moves: $S_1 \cap S_2
-\cap \ldots \cap S_n = \emptyset$. So, the number of possible dialogues is $N_D = |S_0 \times S_1 \times \ldots \times S_n|$.
-\end{definition}
-
-As explained in Equation \ref{equation3}, each move $M_i$ in a possible dialogue $D_l$ is equal to a possible move $m_i^j$ for a
-given $j$. Thus, $P(M_i) = P(m_i^j)$. Knowing this probability, we can calculate the probability of a dialogue $D_l$ as follows:
-
-\begin{equation}\label{equation14}
-P(D_l)=P(M_0) \times P(M_1) \times \ldots \times P(M_n)
-\end{equation}
-%
-Because $\forall i \sum_{j=1}^{k_i} P(m_i^j)=1$, the sum of the probabilities of all possible dialogues is equal to one (i.e., $\sum_{l=1}^{N_D} P(D_l)=1$).
-Now we can define the certainty index of the dialogue as we did for the move in Section~\ref{moveuncertainty}.
-
-First, we measure the uncertainty of the dialogue by the general formula of Shannon entropy:
-%
-\begin{equation}\label{equation15}
-H(D) = -\sum_{l=1}^{N_D}P(D_l) Log(D_l)
-\end{equation}
-%
-Then, we normalize it by dividing it by $Log(N_D)$ to have a metric between 0 and 1, and finally, we measure the certainty
-index of the dialogue by subtracting the normalized value from one. So, the certainty index of the dialogue is given by:
-\begin{equation}\label{equation16}
-CI(D) =1 - H(D)/ Log(N_D)
-\end{equation}
-
-\begin{example}\label{example4}
-Let us consider the negotiation dialogue in example~\ref{example1}, where $n=k_i=3$, $1 \leq i \leq 3$. The number of all possible dialogues is
-($N_D = 27$ dialogues) and the probability of each possible dialogue is computed by the product of probability of its moves. For example for $D_1$,
-we take the first possible choice of the moves ($m_0^1, m_1^1, m_2^1$) with their respective probabilities ($0.33,0.05,1$). So, the probability of
-$D_1$ is equal to $0.02$, and in the same way we compute the probability of all possible dialogues. By applying Equation~\ref{equation15}, we get
-the entropy of the dialogue $H(D)=2.39$, and by applying Equation~\ref{equation16}, we get the certainty index of the dialogue $CI(D)=0.497$. Here we
-notice that the certainty index of the dialogue is medium, and if we compare the result in this method with the result in the previous one, which uses
-the average of certainty index of all moves, and applying it on the same example (Example~\ref{example1}), we notice that the result is almost the same.
-\end{example}
-
-\subsection{Agent's Uncertainty: Type II}\label{sec:type2}
-In Section~\ref{sec:type1}, we assumed that the probability of each possible argument is given through the risk value of the
-move, but we did not elaborate in details on how it can be assigned. Furthermore, the addressee is not considered in Type I
-uncertainty.
-In this section, these two issues will be addressed. We will explain in more details how probabilities can be assigned based on
-three main criteria involving the addressee as discussed in  Section~\ref{sec:reasoning}, which are as follows:
-\begin{enumerate}
-  \item $Cr1$: Risk of failure;
-  \item $Cr2$: Favorite relation; and
-  \item $Cr3$: Preference relation.
-\end{enumerate}
-
-These criteria have precedence relation over each other. This means the order of examining these criteria is important in order
-to assign probabilities to the different arguments available at certain step. First, we check $(Cr1)$ to examine the risk of
-failure of each possible argument in the move and assign the probability so that the less move's risk of failure, the more
-likely to be accepted by the addressee. Second, if there is more than one argument with the same risk of failure, then we check the
-second criterion $(Cr2)$, which examines the favorite relation and we assign higher probability to the more favorable argument.
-Third, if arguments have the same risk and are equally favorable, then we check the third criterion $(Cr3)$, which examines the
-preference relation. This process follows the argument selection mechanism and it depends on the agent's tactic and
-the adapted strategy presented in Section~\ref{sec:reasoning},
-The notion of argument's probability is subjective and different heuristic approaches to evaluate it can be proposed. In this
-paper, we use a heuristic similar to the one used to evaluate the risk of failure. Probabilities are based on the fact that the
-knowledge base $CK$ contains certain knowledge and the set of agent's beliefs and preferences $P_{Ag_1,Ag_2}$ contains uncertain
-beliefs. Therefore, the probability of an argument that belongs to $CK$ to be accepted by the addressee is higher than the
-probability of another argument that belongs to the set $P_{Ag_1,Ag_2}$. Consequently, the risk of failure of an argument
-belonging to $CK$ is less than another argument belonging to $P_{Ag_1,Ag_2}$. In fact, in negotiation dialogues, the
-probability of a move at a given step $t_i$ depends on the knowledge the agent has at that step (i.e., the content of the
-agent's knowledge base at that step), the favorite relation, and the preference relation.
-
-%Based on these facts, we found that the best way to assign
-%probability to the set of possible arguments at each dialogue step
-%(i.e., at the tactical level) is the subjective method, which can
-%be used when the assumptions used in the classical method are not
-%applicable and the past statistics that can be used for the
-%relative frequency method are unavailable. In such a situation,
-%the basis for assigning probability to experimental outcomes is
-%previous business experience, belief, and even feeling. So, this
-%method relies on individual judgmental, and it is highly
-%subjective.
-
-\begin{definition}{\emph{[Move's Probability Function].}} \label{probabilityfunction}
-Let $CK$ be the set of common agents' knowledge, $P_{Ag_1,Ag_2}$ the set of $Ag_{1}^{\prime}s$ beliefs about $Ag_{2}^{\prime}s$
-beliefs, $f_r$ the set of favorable arguments, $p_r$ the set of preferred arguments, and $\mathcal{M}$ the set of all possible
-moves, we define $\Delta$ as a function associating a set of knowledge and preferences and favorites to a set of possible moves
-and their probabilities. We call this function the \textit{move's probability function}.
-\begin{equation}\label{equation17}
- \Delta : 2^{k_n \times f_{r} \times p_{r} } \rightarrow 2^{\mathcal{M} \times [0,1]}
-\end{equation}
-where:\\
-$k_n = CK \times P_{Ag_1,Ag_2}$;\\
-$f_r=\{(Arg_i, Arg_j) \in \mathbb{A} \times \mathbb{A} | Arg_i
-\preceq_{fav}^{P_{Ag_1, Ag_2}} Arg_j\}$; and \\
-$p_r=\{(Arg_i, Arg_j) \in \mathbb{A} \times \mathbb{A} | Arg_i
-\ll_{pref}^{Ag_1} Arg_j\}$.
-\end{definition}
-
-%To explain more this function, we assume that $CK$ is contains a
-%set of propositions $P_1,P_2,\cdots P_n $, this means $CK=
-%\{P_1,P_2,\cdots ,P_n\}$.
-%$f_r$ : is the set of favorable arguments and we represent them as
-%pairs $(Arg_1,Arg_2)$ which means $Arg_1$ is more favorable than
-%$Arg_2$. So, $f_r =\{(Arg_1,Arg_2),(Arg_2,Arg_4),\cdots\}$.
-
-%$p_r$ : is the set of preferred arguments and we represent them
-%also as pairs $(Arg_1,Arg_2$) which means $Arg_1$ is more
-%preferable than $Arg_2$. So, $p_r = \{(Arg_1,Arg_2),(Arg_2,Arg_4),
-%\cdots\}$.
-
-%Now the product of   $CK \times f_{r} \times p_{r}$ =
-%$\{(M_1,P(M_1)), (M_2,P(M_2)), \cdots \}$, and it should satisfy
-%the following conditions:
-
-The function $\Delta$ should satisfy the following properties:
-
-\begin{itemize}
-\item   Minimality: $\forall I, I' \in 2^{k_n \times f_{r} \times
-p_{r} }$ if $I \subseteq I'$ and no relevant argument can be
-generated from $I'-I$, then $\Delta (I) = \Delta(I')$.
-
-\item Uniqueness: $\forall I \in 2^{k_n \times f_{r} \times p_{r}
-}$ and $\forall i, j$ s.t. $\{(M_i,P(M_i )),(M_j,P(M_j))\}
-\subseteq \Delta(I)$, if $i \neq j$, then $M_i \neq M_j$.
-
-\item Universality: $\forall I \in 2^{k_n \times f_{r} \times
-p_{r} }$ if $I = \{(M_1,P(M_1)), \cdots ,(M_n,P(M_n ))\}$, then
-$\sum_{i=1}^n P(M_i)=1 $.
-
-\end{itemize}
-
-The procedure is as follows. First, we calculate the risk of failure of each possible move based on the argument supporting it,
-then we order them ascending based on the risk of failure. Second, if there is more than one move with the same risk of failure, then
-we check the favorite relation for the equivalent arguments in terms of risk of failure and reorder them descending based on the
-favorite relation. Third, if there is more than one argument equally favorable then we check the preference relation and
-reorder them descending based on the preference relation. We assume that each of the three resulting classes $c$ $(1 \leq c
-\leq 3)$ is associated with a given probability $P_c$ ($P_1 < P_2 < P_3$) (this aspect will be addressed in the next section). The
-agents have to perform this procedure at each dialogue step in order to be able to assign the probability based on the order of
-arguments. After that, the uncertainty can be measured based on these probabilities following the method we advocated in Section
-\ref{sec:type1}. The only difference is that unlike the procedure of Section \ref{sec:type1}, here the probability that the
-addressee accepts the move is being considered since probability computation is based on the agent's common knowledge and the
-beliefs of the speaker agent about the beliefs of the addressee and his preferences using the following probability ordering
-relation.
-\begin{definition}{\emph{[Probability Ordering Relation]. }} \label{probabilityorderingrelation}
-Let $C_{Ag_1,Ag_2} = \big<\mathcal{S},\mathcal{T},T, s,P_{Ag_1,Ag_2},CK\big>$ be a conversation context and $Arg_i$ and
-$Arg_j$ be two relevant arguments in the context $C_{Ag_1,Ag_2}$. The probability of argument $Arg_i$ is greater than the
-probability of argument $Arg_j$: $P(Arg_j) \leq P(Arg_i)$ iff $(Arg_j) \preceq_r (Arg_i)$.
-\end{definition}
-
-\begin{theorem}\label{Complexity2}
-If arguments are represented in proportional definite Horn clauses, the probability assignment procedure runs in polynomial
-time.
-\end{theorem}
-
-\noindent\emph{\textbf{Proof.}} \emph{the result is straightforward from Definition \ref{probabilityorderingrelation}
-and Theorem \ref{Complexity1}}.~~$\blacksquare$
-
-%The following algorithm explains how to assign probabilities to
-%the potential arguments $PA$ at each dialogue step.
-%
-%\begin{algorithm}{\emph{\textbf{Algorithm 2: How to assign probabilities to the PA}.}} \label{algorithm2}\\
-%\\ Step 1:
-%\\ 1.1-- Let n= number of possible arguments.
-%\\1.2-- for i=1,n calculate $risk(Arg_i)$
-%\\1.3-- order the arguments ascending based on $Cr1$.\\
-%\\Step 2:
-%\\2.1-- if $\exists$ i,j $\in$ n, i $\neq$ j : $risk(Arg_i)$ = $risk(Arg_j)$ then check $Cr2$ (i.e., which $Arg_? \prec_{fav}^{P_{Ag_1,Ag_2}}  Arg_?$)
-%\\2.2-- reorder them descending based on $Cr2$.
-%\\Step 3:
-%\\3.1-- if $\exists$ i,j $\in$ n, i $\neq$ j : $risk(Arg_i)$ = $risk(Arg_j)$ and $Arg_i \preceq_{fav}^{P_{Ag_1,Ag_2}}  Arg_j$   and $Arg_j \preceq_{fav}^{P_{Ag_1,Ag_2}}  Arg_i$,  Then check $Cr3$  (i.e., which $Arg_?
-\ll_{pref}^{Ag_i} Arg_?$)
-%\\3.2-- reorder them descending based on $Cr3$.
-%\\Step 4:
-%\\ Assign a value to each possible argument, such that this value satisfies the definition~\ref{probabilityorderingrelation}, and the probability of all possible arguments satisfies the probability condition $\sum_{i=1}^n P(M_i)=1$.
-%%\\apply the function~\ref{equation17}, to assign probability to each possible argument.\\
-%\end{algorithm}
-
-Based on uncertainty Type II, we introduce a new classification of arguments for negotiation based on their risk of failure,
-which means on their probabilities.
-
-\subsubsection{Arguments Classification}\label{sec:classification}
-There are three main classes of arguments in our framework: Class $A$ of arguments (and consequently of moves supported by those
-arguments) having low risk of failure (certain arguments); Class $B$ of arguments having medium risk of failure (medium certain arguments);
-and Class $C$ of arguments having high risk of failure (uncertain arguments). The three classes $A$, $B$, and $C$ are disjoint, i.e.,
-$A \cap B = A \cap C = B \cap C = \emptyset$. Each class is divided into three subclasses. In what follows, we explain these classes in details.\\
-
-\begin{figure}
-                \begin{center}
-                \includegraphics[width=10cm,
-                height=8cm]{Figures/argumentclass.eps}\label{ClassificationFigure}
-                \caption{Argument classification}
-                \end{center}
-\end{figure}
-
-\textbf{Class $A$: Low risk (Highly certain arguments)}\\
-Arguments of this class have equal risk, which is less than the risk of any other argument not part of that class. Formally:
-\begin{equation}
-Arg_i \in  A~ \text{iff}:
-\begin{cases}
-risk(Arg_i) = risk (Arg_j) & \forall Arg_j \in A
-\\
-risk(Arg_i) < risk(Arg_j)  & \forall Arg_j \notin A
-\end{cases}
-\end{equation}
-
-This class is composed of three disjoint subclasses: $A_a$, $A_b$, and $A_c$, i.e., $A_a \cap A_b = A_a \cap A_c = A_b \cap A_c
-=\emptyset$. Let $=_{fav}^{P_{Ag_1, Ag_2}}$ be the favorite equality relation defined as follows: for two arguments $Arg_i$ and
-$Arg_j$, $Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j$ iff $Arg_i \preceq_{fav}^{P_{Ag_1, Ag_2}} Arg_j$ and $Arg_j \preceq_{fav}^{P_{Ag_1, Ag_2}} Arg_i$.
-The preference equality relation $=_{pref}^{Ag_1}$ is defined from $\ll_{pref}^{Ag_1}$ in the same way. $A_a$ is defined as follows:
-\begin{equation}
-Arg_i \in A_a~ \text{iff}:
-\begin{cases}
-Arg_i \in A
-\\
-Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j & \forall Arg_j \in A_a
-\\
-Arg_j \preceq_{fav}^{P_{Ag_1, Ag_2}} Arg_i & \forall Arg_j \in
-A-A_a
-\\
-Arg_i =_{pref}^{Ag_1} Arg_j & \forall Arg_j \in A_a
-\\
-Arg_j \prec_{pref}^{Ag_1} Arg_i & \forall Arg_j \in A-A_a
-\text{~s.t.~} Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j
-\end{cases}
-\end{equation}
-
-This means, arguments in $A_a$ are equality favorable and preferable, more favorable than any other argument which is not
-part of $A_a$, and more preferable than any other favorably equally argument.
-
-In the sam way, the second class $A_b$ is defined as follows:
-\begin{equation}
-Arg_i \in A_b~ \text{iff}:
-\begin{cases}
-Arg_i \in A-A_a
-\\
-Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j & \forall Arg_j \in A_b
-\\
-Arg_j \preceq_{fav}^{P_{Ag_1, Ag_2}} Arg_i & \forall Arg_j \in
-(A-A_a)-A_b
-\\
-Arg_i =_{pref}^{Ag_1} Arg_j & \forall Arg_j \in A_b
-\\
-Arg_j \prec_{pref}^{Ag_1} Arg_i & \forall Arg_j \in (A-A_a)-A_b
-\text{~s.t.~} Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j
-\end{cases}
-\end{equation}
-
-Finally, the third class $A_c$ is defined as follows:
-\begin{equation}
-A_c = (A-A_a)-A_b = A-(A_a \cup A_b)
-\end{equation}
-
-\textbf{Class $B$: Medium risk (Medium certain arguments)}\\
-Arguments of this class have equal risk, which is less than the risk of any other argument not part of the union of that class and
-Class $A$. Formally:
-\begin{equation}
-Arg_i \in B~ \text{iff}:
-\begin{cases}
-risk(Arg_i) = risk (Arg_j) & \forall Arg_j \in B
-\\
-risk(Arg_i) < risk(Arg_j) & \forall Arg_j \notin A \cup B
-\end{cases}
-\end{equation}
-
-As for Class $A$, this class is composed of three disjoint subclasses: $B_a$, $B_b$, and $B_c$. $B_a$ is defined as follows:
-\begin{equation}
-Arg_i \in B_a~ \text{iff}:
-\begin{cases}
-Arg_i \in B
-\\
-Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j & \forall Arg_j \in B_a
-\\
-Arg_j \preceq_{fav}^{P_{Ag_1, Ag_2}} Arg_i & \forall Arg_j \in
-B-B_a
-\\
-Arg_i =_{pref}^{Ag_1} Arg_j & \forall Arg_j \in B_a
-\\
-Arg_j \prec_{pref}^{Ag_1} Arg_i & \forall Arg_j \in B-B_a
-\text{~s.t.~} Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j
-\end{cases}
-\end{equation}
-
-%This means, arguments in $A_a$ are equally favorable and
-%preferable, more favorable than any other argument which is not
-%part of $A_a$, and more preferable than any other favorably
-%equally argument.
-
-In the sam way, the second class $B_b$ is defined as follows:
-\begin{equation}
-Arg_i \in B_b~ \text{iff}:
-\begin{cases}
-Arg_i \in B-B_a
-\\
-Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j & \forall Arg_j \in B_b
-\\
-Arg_j \preceq_{fav}^{P_{Ag_1, Ag_2}} Arg_i & \forall Arg_j \in
-(B-B_a)-B_b
-\\
-Arg_i =_{pref}^{Ag_1} Arg_j & \forall Arg_j \in B_b
-\\
-Arg_j \prec_{pref}^{Ag_1} Arg_i & \forall Arg_j \in (B-B_a)-B_b
-\text{~s.t.~} Arg_i =_{fav}^{P_{Ag_1, Ag_2}} Arg_j
-\end{cases}
-\end{equation}
-
-Finally, the third class $B_c$ is defined as follows:
-\begin{equation}
-B_c = (B-B_a)-B_b = B-(B_a \cup B_b)
-\end{equation}
-
-\textbf{Class $C$: High risk (Uncertain arguments)}\\
-This class is simply defined from the two other classes where $\mathbb{A}_{C_{Ag_1, Ag_2}}$ is the set of arguments in the
-context $C_{Ag_1, Ag_2}$ as follows:
-\begin{equation}
-C = \mathbb{A}_{C_{Ag_1, Ag_2}}-(A \cup B)
-\end{equation}
-
-The subclasses $C_a$, $C_b$, and $C_c$ are defined in the same way as the subclasses of $A$ and $B$.
-
-The following theorem is straightforward from the above equations and Definition \ref{probabilityorderingrelation}.
-\begin{theorem}
-Arguments in Class $A$ have higher probability to be accepted than arguments in Class $B$ and arguments in class $B$ have higher
-probability to be accepted than arguments in Class $C$.
-\end{theorem}
-
-\begin{comment}
-
-If the argument contains formulas $\in CK$, then the $risk(Arg_i)= v1$ and in this case the argument has less risk of failure because the $CK$ has certain information (i.e., $v1$ can be equal to 0) and therefore, it has a higher chance to be accepted by the addressee.
-Furthermore, we distinguish three other sub-classes in case of there is more than one argument with risk of failure = $v1$, and they differ in terms of favorite and preference relations, these subclasses are as follows:\\
-\textit{Class a1:} the argument is class $a1$ if it is more favorable compared to the other arguments that have the same risk of failure $v1$.\\
-\textit{Class a2:} if there is more than one argument equally favorable in addition to the equality of risk failure $v1$, then we assign class $a2$ to the more preferred one, and \\
-\textit{Class a3}: to the less preferred one.\\
-
-\textbf{Class B: Arguments contain only formulas in $P_{Ag_1,Ag_2}$.}\\
-If the arguments contain formulas $\in P_{Ag_1,Ag_2}$, then the $risk(Arg_i)= v2$ and in this case the risk of failure of the argument is greater than that in \textit{class A} (i.e., $v1 < v2$) because the information in $P_{Ag_1,Ag_2}$ is not certain, and therefore, the chance to be accepted by the addressee is less.
-As in \textit{class A}, we distinguish three other sub-classes in case of there is more than one argument with risk of failure = $v2$ and they differ in terms of favorite and preference relations, these sub-classes are as follows:\\
-
-\textit{Class b1:} the argument is class $b1$ if it is more favorable compared to the other arguments that have the same risk of failure $v2$.\\
-\textit{Class b2:} if there is more than one argument equally favorable in addition to the equality of risk failure $v2$, then we assign class $b2$ to the more preferred one, and \\
-\textit{Class b3}: to the less preferred arguments.\\
-
-\textbf{Class C: Otherwise: ``Argument contains formulas not in $CK$ and not in $P_{Ag_1,Ag_2}$".}\\
-
-If the arguments contain formulas $\notin CK$ and $\notin
-P_{Ag_1,Ag_2}$, then the $risk(Arg_i)= v3$ and in this case the
-risk of failure of the argument is greater than that in
-\textit{class A} and \textit{class B}
-(i.e., $v1  < v2  < v3$) and consequently, the chance to be accepted by the addressee is more less than the above two classes.
-As in \textit{class A} and in class \textit{class B}, we distinguish three other sub-classes in case of there is more than one argument with risk of failure = $v3$ and they differ in terms of favorite and preference relations, these subclasses are as follows:\\
-\textit{Class c1:} the argument is class $c1$ if it is more favorable compared to the other arguments that have the same risk of failure $v3$ .\\
-\textit{Class c2:} if there is more than one argument equally favorable in addition to the equality of risk failure $v3$, then we assign class $c2$ to the more preferred one, and \\
- \textit{Class c3}: to the less preferred arguments.\\
-Where $v1 < v2 < v3$ and $v1, v2, v3 \in R$.
-
-To measure the agent's uncertainty/certainty that the selected argument will be accepted by the addressee (here we will call it the \textit{uncertainty/ceratinty degree} to distinguish it from the \textit{uncertainty index}), will use the same formulas that we used in section (~\ref{sec:type1}).
-Now let us present the different situations to distinguish between these two types of uncertainty.
-
-\subsubsection{Different Cases}\label{sec:cases}
-We can distinguish three different cases that make the difference between two types of the agent's uncertainty clear.\\
-
-\textbf{Case 1: If there is only one possible argument}.\\
-If the agent has just one possible argument, then the probability of that argument will be at its maximum value (i.e., equal to one to satisfy the probability condition $\Sigma_{m_{j}^{i} \in PA_{i}} P(m_{j}^{i}=1))$ and the uncertainty degree will be at its minimum value (i.e., equal to zero, based on proposition~\ref{proposition1}).
-In this case the \textit{uncertainty degree} is equal to the \textit{uncertainty index} and it does not represent the agent's uncertainty that the selected move will be accepted by the addressee, it rather represents the agent's uncertainty about selecting the right argument at that step, regardless it will be accepted by the addressee agent or not, because the available argument can be any of the above classes, and therefore, if the class of the argument is $C$ for instance, then the chance for this argument to be accepted is very weak and this contradicts the high probability assigned to this argument (equal to one).
-However, this is not applicable for all classes, for example if the argument is class $A$, then there is a high chance to be accepted, so the high probability assigned matches the low uncertainty we achieved and this a special case of \textit{case 1}.
-
-\begin{proposition} \label{proposition3}
-In negotiation dialogue games, at each dialogue step the uncertainty degree is equal to the uncertainty index, and it represents the agent's uncertainty about selecting the right argument as well as the agent's uncertainty about the selected argument to be accepted by the addressee and it will be at it's minimum value iff at that step there is only one possible argument and it has class A.
-\end{proposition}
-
-\textbf{proof}\\
-From proposition~\ref{proposition1}, it's clear that the uncertainty of selecting the right move will be at its minimum
-value ``0" iff there is only one possible argument, and if the class of this argument is A, then the risk of failure is at its
-minimum value too, which means the uncertainty about the argument to be accepted is at its minimum value ``0". So the uncertainty of
-selecting the right argument ``certainty index" and the uncertainty about the argument to be accepted by the addressee
-``certainty degree" is the same.  ~~~~~~~~~$\blacksquare$
-
-\begin{proposition} \label{proposition4}
-In negotiation dialogue games, at each dialogue step if there is only one possible argument, the uncertainty degree is equal to the uncertainty index and it just represents the agent's uncertainty about selecting the right argument iff that argument is not class A.
-\end{proposition}
-
-\textbf{proof}\\
-If there is only one possible argument, the uncertainty will be at its minimum value ``0" ~\ref{proposition1}. Now, if the available
-argument is not class A, then the risk of failure will be greeter than V1. In this case we can not consider the uncertainty value
-``0" as an indicator for the move to be accepted by the addressee, rather, we consider it as an index of selecting the right argument
-since there is no other choice. ~~~~~~~~~$\blacksquare$
-
-\textbf{Case 2: If there is more than one possible argument with the same class}.\\
-If all possible arguments have the same class then they will be equally probably to be selected and the uncertainty will be at its maximum value (i.e., equal to one, following proposition 2), and again as in case 1, it does not always represent the uncertainty about the selected argument to be accepted or refused by the addressee, because the possible arguments might have a high risk of failure (e.g.
-in class c), in this case it represents the agent's uncertainty about the argument to be accepted.
-In the other hand, if all arguments have class A, for example, which means a very low risk of failure, then the uncertainty does not represent the uncertainty that the argument will be accepted, it rather represents the uncertainty about selecting the right move.
-
-\begin{proposition} \label{proposition5}
-In negotiation dialogue games, if all possible arguments at certain dialogue step have the same class, then the uncertainty of the selected argument is at its maximum value, and it represents only the agent's uncertainty about selecting the right argument, except if the arguments are class C.
-\end{proposition}
-
-\textbf{proof}\\
-If all possible arguments have the same class, then they will have same probability value which leads to maximum value of uncertainty
-``1" see~\ref{proposition2}. If the arguments have class A, then the risk of failure will be at its minimum value ``0", and in this
-case the low risk of failure contradict the high uncertainty for the argument to be accepted. So we can not consider this high
-uncertainty as an indicator of accepting. ~~~~~~~~~$\blacksquare$
-
-\textbf{Case 3: If there is more than one argument with different classes}.\\
-In this case, the assignment of the probability will be based on the class of the argument, and following the argument selection mechanism, the agent will select the higher argument class, so the uncertainty in this case represents the agent's uncertainty that the selected argument will accepted by the addressee.
-This will enhance the performance of the agent towards achieving the dialogue goal.\\
-The different cases that show the argument class and the associated type of uncertainty are summarized in    Table~\ref{Table4}.
-
-\begin{table}[tbp]
-\centering \caption{Argument classes vs. Uncertainty types} \label{Table4}
-\begin{tabular}{||c|c|c|c||}\hline\hline
-\multicolumn{4}{||c||}{\textbf{Number of possible arguments}} \\
-\hline\hline
-One possible argument & Uncertainty Type  & More than one possible argument & Uncertainty Type \\
-\hline
-Class A               & Type  I / Type II & Same class =  Class A   & Type  I \\ \hline
-Class B               & Type  I           & Same class =  Class B   & Type  I \\ \hline
-Class C               & Type  I           & Same class =  Class C   & Type  I \\ \hline
-                      &                   & Different classes       &Type  I / Type  II\\
-\hline
-\end{tabular}
-\end{table}
-
-\end{comment}

### 2013-08-21 proposal/proposal/chapter4.tex
Changes

@@
-\setcounter{chapter}{4}
+\setcounter{chapter}{3}
 
-\chapter{Conclusion and Future Work}
+\chapter{Efficient Coalition Formation for Autonomous Web Services}
 
-\section{Conclusion}\label{sec:conclusion}
-In this paper, we proposed a new set of uncertainty measures for the agents in argumentation-based negotiation dialogues from an
-external agent's point of view. Specifically, we introduced two types of uncertainty measures: 1) Type I, the uncertainty index of
-playing the right move at each dialogue step; and 2) Type II, the uncertainty degree of the agent that the move will be accepted by
-the addressee.
-For uncertainty Type I, we used Shannon entropy to assess the agents' uncertainty/certainty about their moves in the negotiation
-dialogues. We supposed that an external agent is monitoring the dialogue, and he wants to evaluate this dialogue in terms of the
-agent's uncertainty/certainty about selecting the right move at each step. In fact, at each step, the agent is supposed to have
-different choices, each choice is associated with a probability of being the right one, %which represents the risk of failure for this move to be accepted by the addressee.
-this probability reflects the importance of information included in that move, where the higher the probability is, the
-more certain the agent becomes (lower uncertainty). So we analyzed the fact that negotiating agents are rational, and they always
-try to perform the actions that will result in the optimal outcome for themselves. We used Shannon entropy to measure: i) the
-uncertainty/certainty index and the weighted uncertainty/certainty index of the agent that he is playing the right move at each
-step during the dialogue; and ii) the uncertainty/certainty index and the weighted uncertainty/certainty index of both agents
-participating in the dialogue about the whole dialogue. This was done in two different ways. The first is by taking the average of
-the uncertainty index of all moves, and the second is by determining all possible dialogues and applying the general formula of Shannon entropy.
+\section{Preliminaries}\label{s:preliminaries}
 
-For uncertainty Type II, we formalized the probability association to the arguments and the uncertainty that the move will be
-accepted by the addressee. In this context, we introduced a new classification of arguments based on the notion of risk of failure
-and showed that this classification is compatible with the probability that the moves supported by those arguments will be
-accepted by the address. An important result of this paper is that the selection and probability ordering mechanisms of arguments
-are tractable as they can be performed in polynomial time if arguments are represented in propositional definite Horn logic.
+In this section, we discuss the parameters and preliminary
+concepts that we use in the rest of the paper.
 
-In our proposed measures, the move with the higher certainty (lower uncertainty) index is considered as the best move. We analyzed
-the fact that negotiating agents are rational, and they always try to perform the actions that will result in the optimal outcome
-for themselves. We started our work with measuring the uncertainty/certainty index of each move at each dialogue step, and in order
-to distinguish between two moves with the same certainty index, we assigned weight to each move, which reflects the importance of the
-move. Then, we proceeded to the whole dialogue and we measured the uncertainty/certainty index for the dialogue in two different ways,
-and we proved that the two ways give the same result. Also, assigning weight to the moves allowed us to compare two different dialogues.
-We believe that such measures are very significant and helpful in evaluating the dialogue and the agent's strategies, especially when
-they are making a decision and selecting the best moves to achieve an agreement (if one exists) in a timely manner.
+\subsection{The Architecture}
 
-\section{Future Work}\label{sec:future}
-In this paper, we mainly focused on the classical (i.e., precise) probability theory, particularly the classical Shannonian
-information theory to measure the uncertainty. As pointed out in \cite{Harmanec1999}, there are other approaches of measuring
-uncertainty in the theories of imprecise probabilities, particularly the Dempster-Shafer theory (also known as the theory
-of belief functions) \cite{Shafer76} and the possibility theory \cite{Dubois2001}. As future work, we will study key measurements
-in these two theories such as \emph{nonspecificity}, \emph{confusion}, \emph{dissonance}, \emph{discord}, and \emph{strife}, and
-we will adapt, define and integrate them in our framework. Combining and aggregating those measurements to finally measure the
-total uncertainty will be investigated as well. The requirements of those new metrics as reported in \cite{Harmanec1999} will be
-analyzed. Those requirements are: 1) generalization, meaning that the new uncertainty measures should generalize the uncertainty
-measures already established in the classical probability theory; 2) subadditivity, meaning that when the problem is broken into
-two orthogonal subproblems, the uncertainty of the original problem should be less than or equal to the sum of uncertainties of the
-subproblems; and 3) additivity, meaning that under the assumption of no interaction and no dependency between the subproblems, the
-uncertainty of the original problem is equal to the sum of uncertainties of the subproblems.
+Our system consists of three main types of entities working
+together:
 
-Another plan for future work is to extend the proposed metrics for other dialogue game types such as persuasion, deliberation,
-inquiry and information seeking. We also plan to analyze argumentation-based dialogues to evaluate agent strategies and
-analyze them from the optimization perspective. Analyzing the computational complexity of such optimization problems is another
-direction for future work. Finally, we plan to analyze multi-party dialogues to which many agents can participate. Extending the
-proposed metrics to this type of dialogues is not straightforward. For example, defining the rules of a multi-party negotiation is
-much more complicated than two-party dialogues. In fact, multi-party dialogues cannot be simply reduced to many two-party dialogues.
+\emph{1) Web services} are rational entities\footnote{The term
+rational is used here in the sense that web services are utility
+maximizers} providing services to end users. They aim to maximize
+their individual income by receiving enough requests from end
+users. In order to increase their revenue, web services seek for
+more tasks if they have the capacity and throughput to do so. Web
+services can join communities to have better efficiency by
+collaborating with others, to have access to higher market share,
+and to have opportunity of receiving a bigger task pool from end
+users. Throughout this paper, in
+our equations, we refer to web services as $ws$ and to the set of
+web services hosted by a given community as $C$. To simplify the
+notation, sometimes we simply write $ws$ instead of $ws \in C$ to
+go through the elements $ws$ of the set $C$.
+
+\emph{2) Master Web Services} or the community coordinators, are representatives of the
+communities of web services and responsible for their management.
+Communities receive requests from users and aim to host a healthy
+set of web services to perform the required tasks. They seek to
+maximize user satisfaction by having tasks accomplished according
+to the desired QoS. In fact, higher user satisfaction will bring
+more user requests and increase the market share and revenue of
+the community.
+
+\emph{3) Users} generate requests and try to find the best
+available services. User satisfaction is abstracted as function of
+quantity and quality of tasks accomplished by a given service.
+Higher user satisfaction leads to higher trust of the community by users hence directing more requests towards that service provider.
+
+\subsection{Web Service Parameters}\label{ws_parameters}
+
+Web services come with different quality of service parameters.
+These parameters with a short description are listed in Table
+\ref{qosws}.
+
+\begin{table}[!t]
+\centering
+\caption{List of web service QoS parameters.}
+\begin{tabular}{|c|c||c|c|}
+\hline
+\textbf{Parameter} & \textbf{Definition} \\
+\hline\hline
+$Availability$ & Probability of being available during \\
+&a time frame \\
+$Reliability$ & Probability of successfully handling \\
+&requests during a timeframe\\
+$Successability$ & Rate of successfully handled requests \\
+$Throughput$ & Average rate of handling requests \\
+$Latency$ & The average latency of services\\
+$Capacity$ & Amount of resources available\\
+$Cost$ & Mean service fee \\
+$Regulatory$ & Compliance with standards, law and rules\\
+$Security$ & Quality of confidentiality \\
+&and non-repudiation\\
+\hline
+\end{tabular}
+\label{qosws}
+\end{table}
+
+We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
+which has aggregated and normalized each of these parameters to a
+real value between 0 and 1. Since requests are not shared among
+web services and are distributed among all of them inside a
+community, each one of them comes with a given QoS denoted by
+$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain
+aggregation function of the parameters considered in Table
+\ref{qosws}. We use this quality output later in evaluating the
+community \emph{worth} or \emph{payoff} function.
+
+\subsection{Web Service Communities}\label{webservice-communities}
+
+Figure \ref{fig_community} represents the architecture of web service communities.
+The communities are essentially an abstract model of web services.
+They aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols as web services.
+Web services join communities to increase their utility by having a larger market share and task pool.
+Community coordinators or master web services are responsible for community development, managing membership requests from web services and distributing user tasks among the community members.
+Community coordinators try to attract quality web services and keep the community as stable and productive as possible to gain better reputation and user satisfaction which results in having a higher market share for the community.
+The way the web services reside inside communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+
+\begin{figure*}[!t]
+\centerline{\includegraphics[width=6.25in]{Figures/community.eps}}
+\caption{Architecture of Web Service communities}
+\label{fig_community}
+\end{figure*}

### 2013-08-21 proposal/proposal/chapter5.tex
Changes

--- 2013-07-16 proposal/proposal/Proposal File/chapter5.tex
@@
-\setcounter{chapter}{5}
-\chapter{Milestones}
+\setcounter{chapter}{4}
+\chapter{Conclusion and Future Work}
 In this chapter, we describe the phases of our plan for exploring the research challenges and investigating the research issues identified in Chapter 4.
@@
 
-\section {Research Methodology and Time Line}
+\section {Conclusion}
 
-    \par The goal of the research project of my Ph.D program is to propose a technically and economically feasible architecture for path stability in MANETs environment.
+In this report, we proposed a cooperative game theory-based model
+for the aggregation of web services within communities. The goal
+of our services is to maximize efficiency by collaborating and
+forming stable coalitions. Our method considers stability and
+fairness for all web services within a community and offers an
+applicable mechanism for membership requests and selection of web
+services. The ultimate goal is to increase revenue by improving
+user satisfaction, which comes from the ability to perform more
+tasks with high quality. Simulation results show that our,
+polynomial in complexity, approximation algorithms provide web
+services and community owners with applicable and near-optimal
+decision making mechanisms.
+
+As future work, we would like to perform more analytical and
+theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the
+characteristic function in web service applications. From web service perspective, the
+work can be extended to consider web service compositions where a
+group of web services having different set of skills cooperate to
+perform composite tasks. Also bargaining theory from cooperating
+game theory concepts can be used to help web services resolve the
+instability and unfairness issues by side payments.
+
+\section {Future Plan and Timeline}
+
+\par text text
 
@@
     \end{figure}
-
-   % To investigate the architecture of MANETs, we will experiment on backup path, protection, transmission range, interference, and multi Path modeling and analysis on 3D MANETs technologies.
-We will apply an efficient clustering algorithm for the hierarchical placement of equipment in the above mentioned access network architecture.
-We will develop mathematical models for different architectures.
-We will also investigate the protection schemes for these architectures.
-
-The time duration of each task includes the modeling of the proposed solution,  its implementation, validation, performance evaluation  and  publication of its outcome.
-
-\section {Publication Plan}

### 2013-08-22 proposal/proposal/chapter3.tex
Changes

@@
 \setcounter{chapter}{2}
-\chapter{Contribution and Research Activities}
 
-%******************** START Contribution and Research Activities. ***************
-In this chapter we will introduce the important notions in argumentation-based negotiation,
-\section{Argumentation System and Agent Theory}\label{sec:Argumentation}
+\chapter{Efficient Coalition Formation for Autonomous Web Services}
+
+\section{Preliminaries}\label{s:preliminaries}
+
+In this section, we discuss the parameters and preliminary
+concepts that we use in the rest of the paper.
+
+\subsection{The Architecture}
+
+Our system consists of three main types of entities working
+together:
+
+\emph{1) Web services} are rational entities\footnote{The term
+rational is used here in the sense that web services are utility
+maximizers} providing services to end users. They aim to maximize
+their individual income by receiving enough requests from end
+users. In order to increase their revenue, web services seek for
+more tasks if they have the capacity and throughput to do so. Web
+services can join communities to have better efficiency by
+collaborating with others, to have access to higher market share,
+and to have opportunity of receiving a bigger task pool from end
+users. Throughout this paper, in
+our equations, we refer to web services as $ws$ and to the set of
+web services hosted by a given community as $C$. To simplify the
+notation, sometimes we simply write $ws$ instead of $ws \in C$ to
+go through the elements $ws$ of the set $C$.
+
+\emph{2) Master Web Services} or the community coordinators, are representatives of the
+communities of web services and responsible for their management.
+Communities receive requests from users and aim to host a healthy
+set of web services to perform the required tasks. They seek to
+maximize user satisfaction by having tasks accomplished according
+to the desired QoS. In fact, higher user satisfaction will bring
+more user requests and increase the market share and revenue of
+the community.
+
+\emph{3) Users} generate requests and try to find the best
+available services. User satisfaction is abstracted as function of
+quantity and quality of tasks accomplished by a given service.
+Higher user satisfaction leads to higher trust of the community by users hence directing more requests towards that service provider.
+
+\subsection{Web Service Parameters}\label{ws_parameters}
+
+Web services come with different quality of service parameters.
+These parameters with a short description are listed in Table
+\ref{qosws}.
+
+\begin{table}[!t]
+\centering
+\caption{List of web service QoS parameters.}
+\begin{tabular}{|c|c||c|c|}
+\hline
+\textbf{Parameter} & \textbf{Definition} \\
+\hline\hline
+$Availability$ & Probability of being available during \\
+&a time frame \\
+$Reliability$ & Probability of successfully handling \\
+&requests during a timeframe\\
+$Successability$ & Rate of successfully handled requests \\
+$Throughput$ & Average rate of handling requests \\
+$Latency$ & The average latency of services\\
+$Capacity$ & Amount of resources available\\
+$Cost$ & Mean service fee \\
+$Regulatory$ & Compliance with standards, law and rules\\
+$Security$ & Quality of confidentiality \\
+&and non-repudiation\\
+\hline
+\end{tabular}
+\label{qosws}
+\end{table}
+
+We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
+which has aggregated and normalized each of these parameters to a
+real value between 0 and 1. Since requests are not shared among
+web services and are distributed among all of them inside a
+community, each one of them comes with a given QoS denoted by
+$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain
+aggregation function of the parameters considered in Table
+\ref{qosws}. We use this quality output later in evaluating the
+community \emph{worth} or \emph{payoff} function.
+
+\subsection{Web Service Communities}\label{webservice-communities}
+
+Figure \ref{fig_community} represents the architecture of web service communities.
+The communities are essentially an abstract model of web services.
+They aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols as web services.
+Web services join communities to increase their utility by having a larger market share and task pool.
+Community coordinators or master web services are responsible for community development, managing membership requests from web services and distributing user tasks among the community members.
+Community coordinators try to attract quality web services and keep the community as stable and productive as possible to gain better reputation and user satisfaction which results in having a higher market share for the community.
+The way the web services reside inside communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+
+\begin{figure*}[!t]
+\centerline{\includegraphics[width=6.25in]{Figures/community.eps}}
+\caption{Architecture of Web Service communities}
+\label{fig_community}
+\end{figure*}

### 2013-08-22 proposal/proposal/chapter4.tex
Changes

@@
 
-\chapter{Efficient Coalition Formation for Autonomous Web Services}
+\chapter{Cooperative Game Solution Concepts}
 
-\section{Preliminaries}\label{s:preliminaries}
-
-In this section, we discuss the parameters and preliminary
-concepts that we use in the rest of the paper.
-
-\subsection{The Architecture}
-
-Our system consists of three main types of entities working
-together:
-
-\emph{1) Web services} are rational entities\footnote{The term
-rational is used here in the sense that web services are utility
-maximizers} providing services to end users. They aim to maximize
-their individual income by receiving enough requests from end
-users. In order to increase their revenue, web services seek for
-more tasks if they have the capacity and throughput to do so. Web
-services can join communities to have better efficiency by
-collaborating with others, to have access to higher market share,
-and to have opportunity of receiving a bigger task pool from end
-users. Throughout this paper, in
-our equations, we refer to web services as $ws$ and to the set of
-web services hosted by a given community as $C$. To simplify the
-notation, sometimes we simply write $ws$ instead of $ws \in C$ to
-go through the elements $ws$ of the set $C$.
-
-\emph{2) Master Web Services} or the community coordinators, are representatives of the
-communities of web services and responsible for their management.
-Communities receive requests from users and aim to host a healthy
-set of web services to perform the required tasks. They seek to
-maximize user satisfaction by having tasks accomplished according
-to the desired QoS. In fact, higher user satisfaction will bring
-more user requests and increase the market share and revenue of
-the community.
-
-\emph{3) Users} generate requests and try to find the best
-available services. User satisfaction is abstracted as function of
-quantity and quality of tasks accomplished by a given service.
-Higher user satisfaction leads to higher trust of the community by users hence directing more requests towards that service provider.
-
-\subsection{Web Service Parameters}\label{ws_parameters}
-
-Web services come with different quality of service parameters.
-These parameters with a short description are listed in Table
-\ref{qosws}.
-
-\begin{table}[!t]
-\centering
-\caption{List of web service QoS parameters.}
-\begin{tabular}{|c|c||c|c|}
-\hline
-\textbf{Parameter} & \textbf{Definition} \\
-\hline\hline
-$Availability$ & Probability of being available during \\
-&a time frame \\
-$Reliability$ & Probability of successfully handling \\
-&requests during a timeframe\\
-$Successability$ & Rate of successfully handled requests \\
-$Throughput$ & Average rate of handling requests \\
-$Latency$ & The average latency of services\\
-$Capacity$ & Amount of resources available\\
-$Cost$ & Mean service fee \\
-$Regulatory$ & Compliance with standards, law and rules\\
-$Security$ & Quality of confidentiality \\
-&and non-repudiation\\
-\hline
-\end{tabular}
-\label{qosws}
-\end{table}
-
-We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
-which has aggregated and normalized each of these parameters to a
-real value between 0 and 1. Since requests are not shared among
-web services and are distributed among all of them inside a
-community, each one of them comes with a given QoS denoted by
-$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain
-aggregation function of the parameters considered in Table
-\ref{qosws}. We use this quality output later in evaluating the
-community \emph{worth} or \emph{payoff} function.
-
-\subsection{Web Service Communities}\label{webservice-communities}
-
-Figure \ref{fig_community} represents the architecture of web service communities.
-The communities are essentially an abstract model of web services.
-They aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols as web services.
-Web services join communities to increase their utility by having a larger market share and task pool.
-Community coordinators or master web services are responsible for community development, managing membership requests from web services and distributing user tasks among the community members.
-Community coordinators try to attract quality web services and keep the community as stable and productive as possible to gain better reputation and user satisfaction which results in having a higher market share for the community.
-The way the web services reside inside communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
-
-\begin{figure*}[!t]
-\centerline{\includegraphics[width=6.25in]{Figures/community.eps}}
-\caption{Architecture of Web Service communities}
-\label{fig_community}
-\end{figure*}
+%******************** START Contribution and Research Activities. ***************
+In this chapter we will introduce the important notions in argumentation-based negotiation,
+\section{Argumentation System and Agent Theory}\label{sec:Argumentation}

### 2013-08-30 proposal/proposal/chapter3.tex
Changes

@@
 
-\chapter{Efficient Coalition Formation for Autonomous Web Services}
+\chapter{Coalition Formation for Autonomous Web Services}
 
@@
 \begin{figure*}[!t]
-\centerline{\includegraphics[width=6.25in]{Figures/community.eps}}
+\centerline{\includegraphics[width=15cm]{Figures/community.eps}}
 \caption{Architecture of Web Service communities}
@@
 \end{figure*}
+
+\subsection{Cooperative Game Concepts}
+Cooperative game is a branch of game theory that studies
+strategies of self-interested entities or agents in a setting
+where those agents can increase their payoff by binding agreements
+and cooperating in groups. We let $N$ be a set of players. Any
+subset $S$ of $N$ can form a group called $coalition$. A
+\emph{coalitional game} is a pair $G = (N, v)$, where $v$ is called
+a \emph{characteristic function} $v: 2^N \to \mathbb{R}$, mapping the set of players of the
+coalition to a real number $v(S)$, the worth of $S$. This number
+usually represents the output or payoff or again the performance
+of these players working together as coalition.  If a coalition
+$S$ is formed, then it can divide its worth, $v(S)$ in any
+possible way among its members. The payoff vector $x \in
+\mathbb{R}^S$ is the amount of payoff being distributed among the
+members of the coalition $S$. The payoff vector satisfies two
+conditions:
+
+\begin{itemize}
+    \item $x_i \geq 0$ for all $i \in N$, and
+    \item $\sum_{i \in S} x_i \leq v(S)$
+\end{itemize}
+
+The second criteria is called the \emph{feasibility} condition,
+according to which, the payoff for each agent cannot be more than
+the coalition total gain. A payoff vector is also \emph{efficient}
+if the payoff obtained by a coalition is distributed amongst the
+coalition members: $\sum_{i \in S} x_i = v(S)$. This definition of
+the characteristic function works in \emph{transferable utility}
+(TU) settings, where utility (i.e., payoff) is transferable from
+one player to another, or in other words, players have common
+currency and a unit of income that is worth the same for all players
+\cite{myerson1991game}.
+
+When dealing with cooperative games, two issues need to be
+addressed:\\ 1. Which coalitions among all possible coalitions to form? \\
+2. How to reward each member when a task is completed?\\
+%
+The following definitions help address these two issues.
+
+{\bf Definition 1 (Shapley value)} Given a cooperative game $(N,
+v)$, the \emph{Shapley value} of player $i$ is given
+by\cite{shapley_value}:
+\begin{equation}\label{eq:shapley}
+\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} }
+\frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))
+\end{equation}
+
+\emph{Shapley value} is a unique and fair solution concept for
+payoff distribution among the members of the coalition. It
+basically rewards members with the amount of marginal contribution
+they have to the coalition.
+
+%\subsubsection{Core}
+
+{\bf Definition 2 (Core)} A payoff vector $x$ is in the $core$ of
+a coalitional game $(N, v)$ if and only if:
+\begin{equation}\label{eq:core}
+\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S)
+\end{equation}
+
+The core is basically a set of payoff vectors where no subset of
+players $S^\prime$ could gain more than their current payoff by
+deviating and making their own coalition $\sum_{i \in S^\prime}
+x_i \geq v(S^\prime)$. The sum of payoffs of the players in any
+sub-coalition $S$ is at least as large as the amount that these
+players could earn by forming a coalition by their own. In a
+sense, it is analogue to Nash equilibrium, except that core is
+about deviations from groups of entities. The core is the
+strongest and most popular solution concept in cooperative game
+theory. However, its computation is a combinatorial problem and
+becomes intractable as the number of players increases. The core
+of some real-world problem games may be empty, which means having
+the characteristic function of the game $(N,v)$, there might be no
+possible distribution of payoff assuring stability of subgroups.
+
+{\bf Definition 3 (Convex cooperative games)} A game $(N,v)$ with
+characteristic function $v(S)$ is convex if:
+\begin{equation}\label{eq:convex}
+v(S) + v(T) \leq v(S \cup T) + v (S \cap T), \forall S,T \subseteq
+N.
+\end{equation}
+
+According to a classic result by Shapley \cite{S1971cores}, convex
+games always have a non-empty core. We will use a variation of
+convexity condition in our algorithm to check whether our
+coalitions are stable.
+
+\subsubsection*{$\epsilon$-core}\label{s:epsilon}
+%\emph{$\epsilon$-Core:}
+%\\
+When the \emph{core} set of a game is empty, it means no coalition
+of players can gain anything by deviating. An outcome would be
+unstable if a coalition can benefit even by a small amount from
+deviating, which is a strong requirement. In fact, in some
+situations, deviations can be costly, or players may have loyalty
+to their coalitions, or even it can be computationally intractable
+to find those small benefits. It would only make sense for a
+coalition to deviate if the gain from a deviation exceeds the cost
+of performing the deviation. \emph{$\epsilon$-core} relaxes the
+notion of the core, and only requires that no coalition would
+benefit significantly, or within a constant amount($\epsilon$) by
+deviating (see Equation \ref{eq:core}).
+
+\begin{equation}\label{eq:core2}
+\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
+\end{equation}
+
+\subsubsection*{Coalition Structure Formation}\label{sec:coalition}
+
+Coalition structure formation is the problem of finding the best
+partition of web services into teams. In these settings, the
+performance of an individual service is less important than the
+\emph{social welfare} of the whole system, which is the sum of the
+values of all teams. Having the game $(N,v)$, a coalition
+structure $(CS)$ is \emph{socially optimal} if $CS$ belongs to set
+$\operatorname*{arg\,max}_{CS} v(CS)$ where $v(CS)$ is the sum of
+the values of all coalitions inside $CS$. $v(CS) = \sum_{C \in
+CS}v(C)$.
+%The outcome of a characteristic function game in coalition structure settings, consists of two parts; first a disjoint partition of players (agents) into coalitions, called a \emph{coalition structure} (CS) and second a \emph{payoff vector} as mentioned in cooperative game solution concepts, which distributes the value of each coalition among its members.
+
+\section{Problem Formulation and Modeling}\label{s:model}
+
+In this section, we present  web services and community coordinator's interactions, the task distribution process and revenue models in web service communities.
+
+\subsection{Task distribution}
+
+As mentioned in section \ref{webservice-communities}, communities are robust service providers with well established market share and reputation.
+By maintaining their reputation and performance, they attract  end users which choose them as service providers to perform their tasks.
+The community master is characterized by a request rate $(R_C)$ from users.
+Each web service comes with a given QoS ($QoS_{ws}$) from which the throughput $Th_{ws}$ is excluded.
+Throughput is the average rate of tasks a web service can perform per time unit.
+Its exclusion from $QoS_{ws}$ allows us to build our analysis on the particular value of $Th_{ws}$.
+Thus, web services perform tasks with an average output quality of $QoS_{ws}$ and a throughput rate of $Th_{ws}$.
+
+The community master uses a slightly modified \emph{weighted fair queuing} method to distribute tasks among its members.
+The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{ws}$.
+In \emph{weighted fair queuing} method \emph{all} the input flow is multiplexed along different paths, however in our case if the input rate $(R_C)$ of the community is more than the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with delay.
+Thus, the amount of tasks performed by community is $\sum_{ws \in C}{(Th_{ws})}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$.
+However, when the input rate $(R_C)$ of the community is less than the summation of throughput values of the web services in the community,
+%the community has more web services having more total throughput value than community's request rate
+$(R_C)$ the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $R_C \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) and the total rate of tasks being performed is $R_C$, the community's receiving request rate.
+
+While distributing tasks, the community master can verify the performance, throughput and quality of service of   tasks being performed by web services.
+It can recognize if web services are capable of doing the amount of tasks they advertised.
+If for any reason there is a decline in quality metrics or throughput, the  community master will announce the new parameters and community masters and members can consider those values as benchmark for future performance calculations but also to penalize them.
+In this way, players have incentive to reveal their real capabilities to profit best from the community and to avoid being penalized.
+In addition, the system should be dynamic enough to detect and react to web services quality metrics variation as over time web service metrics may  degrade or improve, a change that the community should adjust to.
+% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities.
+Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.
+
+\subsection{Community Revenue}
+
+The communities and web services earn revenue by performing tasks.
+The total gain is function of quality ($QoS_{ws}$) and throughput ($Th_{ws}$) of tasks being performed.
+As mentioned in section \ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain aggregation function of the parameters considered in Table \ref{qosws}.
+We have adopted a linear equal weight average over all QoS parameters listed in table \ref{qosws} excluding the $Throughput$ and $Cost$ parameters.
+A community has the option to weigh specific QoS parameters depending on the expectations of their clients.
+
+The maximum potential output of a community $(PO(C))$  is an aggregation of number of tasks, times their quality, for each web service member of the community:
+
+\begin{equation}
+PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
+\end{equation}
+
+If the summation of throughput values ($Th_{ws}$) of community members exceeds the input task rate of the community ($R_C$) the community cannot perform at its maximum potential.
+It denotes the case when the community has more web services than it needs to perform the input task load.
+The actual output has to be normalized to the amount of tasks being performed.
+
+\begin{equation}\label{out_c}
+Out(C) = \left\{
+  \begin{array}{l l}
+    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{C}$}\\
+    PO(C) \times \frac{R_{C}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{C}$}
+  \end{array} \right.
+\end{equation}
+
+The revenue function of the web service community is a linear function of $Out(C)$ with a positive constant multiplier.
+
+\subsection{Case Study}
+
+In this section, we analyze three numerical examples and discuss the motivation of web services and community interactions and the strategies they can adopt and the revenue they can earn adopting these different strategies.
+
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+\caption{Example 1}
+\label{example_1}
+\centering
+\begin{tabular}{c c c c}
+\hline
+$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
+\hline
+1 & 0.8 & 4 & 3.2\\
+2 & 0.8 & 5 & 4.0\\
+3 & 0.8 & 3 & 2.4\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+% \caption{Three web services}
+\label{example_1_2}
+\centering
+\begin{tabular}{c c || c c}
+\hline
+Community & Worth & Community & Worth\\
+\hline
+$\left\{1\right\}$ & 3.2 & $\left\{1,2\right\}$ & 7.2\\
+$\left\{2\right\}$ & 4.0 & $\left\{1,3\right\}$ & 5.6\\
+$\left\{3\right\}$ & 2.4 & $\left\{2,3\right\}$ & 6.4\\
+$\left\{1,2,3\right\}$ & 8.0\\
+\hline
+Community $R_C$: 10\\
+\hline
+\end{tabular}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+\caption{Example 2}
+\label{example_2}
+\centering
+\begin{tabular}{c c c c}
+\hline
+$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
+\hline
+1 & 0.8 & 5 & 4.0\\
+2 & 0.7 & 6 & 4.2\\
+3 & 0.7 & 4 & 2.8\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+% \caption{Three web services}
+\label{example_2_2}
+\centering
+\begin{tabular}{c c || c c}
+\hline
+Community & Worth & Community & Worth\\
+\hline
+$\left\{1\right\}$ & 4.0 & $\left\{1,2\right\}$ & 7.4\\
+$\left\{2\right\}$ & 4.2 & $\left\{1,3\right\}$ & 6.8\\
+$\left\{3\right\}$ & 2.8 & $\left\{2,3\right\}$ & 7.0\\
+$\left\{1,2,3\right\}$ & 7.3\\
+\hline
+Community $R_C$: 10\\
+\hline
+\end{tabular}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%, %%%%%%%%%%%%%%%%%%%%%%
+
+In the first example,  we present the case of a community with $R_C =10 $, and three web services, each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}.
+The worth of a community is calculated based on $Out(C)$ equation (\ref{out_c}) which is the amount of output being generated by the community.
+The first table  lists the web services with their aggregated $QoS_{ws}$ parameters, their task input rate while working alone, and also their  throughput value $Th_{ws}$.
+The second table shows all the possible communities and their respective worth.
+The obtained values suggest that  communities having more web services have better gain and output.
+However each community needs to  distribute the gain between web services.
+Sometimes it is impossible to share the gain between all web services in a way that no subset of them would individually gain more if they form their own group.
+In this example, the value community of ${ws_1}$ and ${ws_2}$ is 7.2, With ${ws_3}$ joining the community the worth increases to 8.0.
+However there is no way to distribute the value among web services to have  ${ws_1}$ and ${ws_2}$  earning 7.2, and ${ws_3}$ earning at least 2.4, the gain they could earn before joining the community.
+This fact makes the group unstable.
+In the second  example, shown in table \ref{example_2}, we even have situations where a web service (${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$) decreases the value of community.
+The reason is, the community is already full and all tasks are almost being distributed and new community with bad quality can degrade the average quality of tasks being done by the community.
+In both examples, the request of joining of web service ${ws_3}$ should be rejected by the community.
+
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+\caption{Example 3}
+\label{example_3}
+\centering
+\begin{tabular}{c c c c}
+\hline
+$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
+\hline
+1 & 0.8 & 10 & 5\\
+2 & 0.8 & 20 & 5\\
+3 & 0.8 & 30 & 5\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+% \caption{Three web services}
+\label{example_3_2}
+\centering
+\begin{tabular}{c c || c c}
+\hline
+Community & Worth & Community & Worth\\
+\hline
+$\left\{C_{ms_1}\right\}$ & 0 & $\left\{C_{ms_2}\right\}$ & 0\\
+$\left\{C_{ms_1}, ws_1\right\}$ & 8 & $\left\{C_{ms_2}, ws_1\right\}$ & 8\\
+$\left\{C_{ms_1}, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_2\right\}$ & 16\\
+$\left\{C_{ms_1}, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_3\right\}$ & 24\\
+$\left\{C_{ms_1}, ws_1, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2\right\}$ & 24\\
+$\left\{C_{ms_1}, ws_1, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_3\right\}$ & 32\\
+$\left\{C_{ms_1}, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_2, ws_3\right\}$ & 32\\
+$\left\{C_{ms_1}, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2, ws_3\right\}$ & 32\\
+$\left\{C_{ms_1}, C_{ms_2}, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
+$\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
+\hline
+Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
+\hline
+\end{tabular}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In Example 3, we consider the case of having different communities with different market share, ${R_C}$ values.
+Web services also have a small share of market independently, providing them with a small task pull.
+In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the \emph{social welfare}.
+In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_{master_1}, ws_2\right\}$ and $\left\{C_{master_2}, ws_1, ws_3\right\}$, which yields a total value of $32 + 16 = 48$.
+In these types of scenarios, the goal is to reach stability, adopting a distributed approach where all players have the power of choice on the decision of whether or not they join a coalition.
+The communities usually start the game having some established members, encountering new web services, the communities may exchange web services and new web services would join them having at least one player gaining utility, without hurting any other participant.
+In this example if we initially having two coalitions of $\left\{C_{master_1}, ws_2\right\}$ and $\left\{C_{master_2}, ws_1\right\}$ and a ${ws_3}$ as new web service, ${ws_3}$ joining ${C_{master_1}}$ would hurt at least itself or $ws_2$, however ${ws_3}$ joining ${C_{master_2}}$ would not hurt any participants and ${ws_3}$ would earn more within the community and the community will have enough web services performing the incoming tasks from users.
+
+The first two examples illustrate the fact that a community cannot simply increase its revenue by adding more web services.
+The web services and even community owners are autonomous agents and would deviate and be displeased about the community if new members cause a drop in their profit.
+The job of the community master is to attract as many quality web services it can and keep them satisfied; hence the group stability is guaranteed.
+The third example highlights another type of problem we would like to address, which is how to form best possible groups of communities, and allocate web services among communities in a way which would maximize payoff for of our agents and members already residing in the communities.
+In next section, we provide collaborative game theory based algorithms for our autonomous agents, to tackle these problems and find applicable and efficient strategies for communities and web services to maximize their profit.
+
+ \section{Web Service Cooperative Games}\label{s:game_solution}
+
+In this section, we present different web service community models
+and focus on the problem of how both web services and community
+masters as rational entities would adopt strategies to maximize
+their payoff.
+
+\subsection {Web Services and One Community}
+
+In this scenario, we assume the existence of a typical community
+managed by its master, and web services need to join it to be able
+to get requests from the master. The community master is
+characterized by a requests rate $(R_{C})$ from users. Each web
+service comes with a given QoS ($QoS_{ws}$). The worth of a community
+$v(C)$ is set to Out(C) based on equation \ref{out_c}.
+
+As mentioned in previous section, the worth and output of a
+community of web services is a function of the
+throughput and provided QoS. If the throughput rate is more than
+the master's input request rate, it means the web services inside
+the community are capable of serving more requests than the
+demand. Considering this factor, the valuation function is
+designed to balance the output performance so that it matches the
+exact throughput rate and QoS the web service can provide within
+the particular community.
+%** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests.
+**
+
+In this first scenario, we only consider one grand coalition and
+analyze the system from the point of view of one single master web
+service and a collection of web services. The master web service
+decides which members can join
+%or should leave%
+the community and distributes the requests and income among its
+community members (see Figure \ref{fig_sim1}).
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{Figures/s1.eps}`
+\caption{Web Services and A Grand Community}
+\label{fig_sim1}
+\end{figure}
+
+The membership decision is made based on throughput and \emph{QoS}
+of the considered web service. The goal is to have quality web
+services in the community so it stays stable and no other web
+services would have incentives to deviate and leave the coalition
+$C$. Therefore, a basic method would be to check the core of the
+coalition $C$ considering all the current community members (all
+web services already residing within the community) and the new
+web service. This algorithm uses the \emph{Shapley value}
+distribution method as described in Equation \ref{eq:shapley} to
+distribute the gain of $v(C)$ among all the members and then
+checks if the \emph{Shapley value} payoff vector for this
+community having the characteristic function $v(C)$ is in the
+\emph{core}. In the \emph{Shapley value} payoff vector, the payoff
+for each web service $ws_i$ is calculated based on its marginal
+contribution $v(C \cup {i}) - v(C)$ over all the possible
+different permutations in which the coalition can be formed, which
+makes the payoff distribution fair. Because of going through all
+the possible permutations of subsets of $N$, the nature of the
+\emph{Shapley value} is combinatorial, which makes it impractical
+to use as the size of our coalitions grows. However, it is proven
+that in convex games, the \emph{Shapley value} lies in the core
+\cite{DBLP:conf/ijcai/GrecoMPS11, myerson1991game}. Thus, if the
+\emph{Core} is non-empty, the payoff vector is a member of the
+\emph{Core}. The following proposition is important to make our
+algorithm tractable.
+% so in our algorithm we check the core membership of this payoff vector.
+
+%\ref{eq:convex}.
+
+%\newtheorem{theorem}{Proposition}
+%\begin{theorem}[Einstein-Podolsky-Rosenberg]
+\begin{theorem}\label{proposition1}
+A game with a characteristic function $v$
+is convex if and only if for all $S$, $T$, and $i$ where $S
+\subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in
+N$,
+%For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
+\begin{equation}\label{eq:convex_snow}
+v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
+\end{equation}
+\end{theorem}
+
+%\begin{Proposition}\label{proposition} A game with a characteristic function $v$
+%is convex if and only if for all $S$, $T$, and $i$ where $S
+%\subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in
+%N$,
+%For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
+%\begin{equation}\label{eq:convex_snow}
+%v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
+%\end{equation}
+%\end{Proposition}
+
+\begin{proof}
+We first prove the ``only if'' direction:
+%\\$~~~~$\textbf{1}. ``only if'' direction:\\
+\\$~~~~$\ \textbf{1}. ``only if'' direction:\\
+%\setlength{\abovedisplayshortskip}{2pt}
+Assume:\\
+\vspace{-0.5cm}
+\begin{gather*}\label{convexsnowproof}
+v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\})
+- v(T)
+\\
+\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq v (T \cup \left\{i\right\}) + v(S)
+\end{gather*}
+
+Considering $S \subseteq T$:
+\setlength{\abovedisplayshortskip}{2pt}
+\begin{gather*}
+S \cup \left\{i\right\} = (S \cup \left\{i\right\}) \cup T
+\\
+T = (S \cup \left\{i\right\}) \cap T
+\end{gather*}
+
+By setting $A = S \cup \left\{i\right\}$ and $B = T$ we have:
+\setlength{\abovedisplayshortskip}{2pt}
+\begin{gather*}
+v(S \cup \left\{i\right\}) + v(T) \leq v (T \cup \left\{i\right\}) + v(S)
+\\
+\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq
+\\
+v((S \cup \left\{i\right\}) \cup T) + v((S \cup \left\{i\right\}) \cap T)
+\\
+\rightarrow v(A) + v(B) \leq v(A \cup B) + v(A \cap B)
+\end{gather*}
+Consequently, the game is convex.
+
+\textbf{2}. ``if'' direction:\\
+Assume the game is convex. Thus, for all $A, B \subset N$, we
+have: \setlength{\abovedisplayshortskip}{2pt}
+\begin{gather*}
+v(A) - v(A \cap B) \leq v(A \cup B) - v(B)
+\end{gather*}
+
+By setting $S \cup \left\{i\right\} = A$ and $T = B$ where $S \subseteq T$:
+\setlength{\abovedisplayshortskip}{2pt}
+\begin{gather*}
+v(S \cup \left\{i\right\}) - v((S \cup \left\{i\right\}) \cap T) \leq v(T \cup (S \cup \left\{i\right\})) - v(T)
+\\
+\rightarrow v(S \cup \left\{i\right\}) - v(S) \leq v(T \cup \left\{i\right\}) - v(T)
+\end{gather*}
+
+\end{proof}
+
+Thus, in order to keep the characteristic function convex, new web
+services should have more marginal contribution as the coalition
+size grows.
+
+Our algorithm works as follows. We have an established community
+with a master and some member web services already residing in the
+community. A web service would send a join request to the
+community. The ideal solution would be analyzing the \emph{core}
+or \emph{$\epsilon$-core} stability of the group having this new
+member. As the normal core membership algorithm is computationally
+intractable, we exploit Proposition \ref{proposition1} and Equation
+\ref{eq:convex_snow} to check the convexity of our game having
+characteristic function where the new member is added. In the
+equation, we set $C$ to be our community members $(C)$ before
+having the new web service. We assign ${i}$ to the new web
+service, and then verify the equation for $S$, setting $ S = T /
+W1 $ where $W1$ is the set of all possible subsets of the set $N$
+having the size $1$. We can relax the equation a bit by adding a
+constant $\epsilon$ to the left side of the equation. We call this
+method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
+satisfied for all $W1$, we let the new web service join our
+community, since the web service will contribute positively enough
+to make our new community stable. Since only subsets of size $1$
+are checked, the following Proposition holds.
+
+\begin{theorem}\label{complexity1}
+\emph{The run time complexity of Depth-1 Convex-Checker algorithm is
+$O(n)$.}
+\end{theorem}
+
+By this result, we obtain a significant reduction from $O(2^n)$,
+which is the complexity of checking all possible subsets of $N$.
+In our second method, we use the same algorithm, but this time we
+set $W2$ to be the set of all possible subsets of size two and one
+of the community $C$. We call this method \emph{Depth-2
+Convex-Checker} and its run time complexity is still
+linear:
+
+\begin{theorem}\label{complexity2}
+\emph{The run time complexity of Depth-2 Convex-Checker algorithm is
+$O(n^2)$.}
+\end{theorem}
+
+It is possible to develop an anytime algorithm by continuing the
+verification of this condition against all subsets of size $3$,
+$4$, etc. until the algorithm gets interrupted.
+
+\subsection {Web Services and Many Communities}
+
+In this scenario, we consider multiple communities managed by
+multiple master web services, each of which is providing
+independent request pools (see Figure \ref{fig_sim2}). Identical
+to the first scenario, master web services form coalitions with
+web services. We use coalition structure formation methods to
+partition web services into non-empty disjoint coalition
+structures. As mentioned in Section \ref{sec:coalition}, the used
+algorithms \cite{Sandholm1999209,DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
+solve key fundamental problems of what coalitions to form, and how
+to divide the payoffs among the collaborators.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{Figures/s2.eps}
+\caption{Web Services and Many Communities}
+\label{fig_sim2}
+\end{figure}

### 2013-09-04 proposal/proposal/chapter3.tex
Changes

@@
 structures. As mentioned in Section \ref{sec:coalition}, the used
-algorithms \cite{Sandholm1999209,DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
+algorithms \cite{Sandholm:1999:CSG:317145.317152,DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
 solve key fundamental problems of what coalitions to form, and how
@@
 \end{figure}
+
+In coalition-formation games, formation of the coalitions is the
+most important aspect. The solutions focus on maximizing the
+social welfare. For any coalition structure $\pi$, let
+$v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$,
+which represents the \emph{social welfare}. The solution concepts
+in this area deal with finding the maximum value for the social
+welfare over all the possible coalition structures $\pi$. There
+are $centralized$ algorithms for this end, but these approaches
+are generally NP-complete. The reason is that the number of all
+possible partitions of the set $N$ grows exponentially with the
+number of players in $N$, and the centralized algorithms need to
+iterate through all these partitions.
+%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity.
+However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}.
+In our model, we propose using a distributed algorithm where each
+community master and web service can be a decision maker and
+decide for its own good. The aim is to find less complex and
+distributed algorithms for forming web services
+coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
+The distributed merge-and-split algorithm in
+\cite{DBLP:journals/igtr/AptW09} suits our application very well.
+It keeps splitting and merging coalitions to partitions which are
+preferred by all the players inside those coalitions.
+
+This merge-and-split algorithm is designed to be adaptable to
+different applications. One major ingredient to use such an
+algorithm is a preference relation or well-defined orders proper
+for comparing collections of different coalition partitions of the
+same set of players. Having two partition sets of players, namely
+$P = {P_1,...,P_k}$ and $Q = {Q_1,...Q_l}$, one example would be
+to use the social welfare comparison $\sum^k_{i=1}v(P_i) >
+\sum^l_{j=1}v(Q_j)$. For our scenario, we use \emph{Pareto order}
+comparison, which is an individual-value order appropriate for our
+self-interest web services. In the Pareto order, an allocation or
+partition $P$ is preferred over another $Q$ if at least one player
+improves its payoff in the new allocation and all the other
+players still maintain their payoff ($p_i \geq q_i$ with at least
+one element $p_i > q_i$).
+
+The valuation function $v(C)$ for this scenario is the same as
+\emph{``Web Services and One Community''} scenario. However, in
+order to prevent master web services joining the same community,
+we set $v(C) = 0$ when $C$ has either none, or more than one
+master web service as member.
+
+In this scenario, as new web services are discovered and get ready
+to join communities, our algorithm keeps merging and splitting
+partitions based on the preference function. The decision to merge
+or split is based on the fact that all players must benefit. The
+new web services will merge with communities if $all$ the players
+are able to improve their individual payoff, and some web services
+may split from old communities, if splitting does not decrease the
+payoff of any web service of the community. According to
+\cite{DBLP:journals/corr/abs-cs-0605132}, this sequence of merging
+and splitting will converge to a final partition, where web
+services cannot improve their payoff. More details of this
+algorithm and analysis of generic solutions on coalition formation
+games are described in \cite{DBLP:journals/igtr/AptW09}.
+
+\subsection{Taxtation, Subsiding and Community Stability}\label{s:tax}
+
+We discuessed $core$ as one of the preminent solution concepts in cooperative games.
+Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group.
+However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal ammount of $\epsilon$ by deviating.
+Comuunity stability is an attractice property for communities, also communities would benefit by having slightly more web services then having the exact number of web services satisfying task rate cap.
+One reason is that there is always the possibility that the agents may leave the community or they may under perform from the quality values they were initially performing with.
+
+One way for communities to ensure community stability could be applying a tax, $\epsilon$ ammount of cost for web services changing communities which would make deviation a costly act.
+However this would require all community coordinators to agree on same ammount of taxtation, being governed by some external entities or web services would join communities with lesser ammount of tax.
+Another viable solution in our scenario is to stabilize the game using external subsidies.
+The reason a game is not stable is that the community is not making enough revenue to allocate the players with enough gain.
+A community master can subside its community with a constant coefficient value of $\lambda$.
+Rewarding a community with high number of quality participants with $\lambda v(C)$, where $\lambda \leq 1$.
+Obviously with a big number of $\lambda$ it is always possible to stabilize the community.
+However, this can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable.
+Subsiding or taxting in order to reduce the bargaining power of sub coalitions are called $taxtation$ \cite{eps346856} methods.
+
+%Thus, another way to garantee \emph{$\epsilon$-core} stability can be achieved by some surplus payments from community coordinators.
+These concepts of applying cost in coallition values in order to reduce their bargaining power are called $taxtation$ methods\cite{eps346856}.
+
+%The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent's point of view.
+It claims agents for any reason will be not willing to deviate to gain less than $\epsilon$ amount of profit.
+Communities can agree on However, in our case, the community master is willing to keep web services in communities too.
+There are several reasons for this, one reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with.
+To this end, our communities will reward and valuate web services in the community
+
+\section{Experimental Results and Analysis}\label{s:resutls}
+
+In this section, we discuss the experiments we performed for our
+scenarios to validate the applicability and performance of our
+proposed methods in realistic environments. We created a pool of
+web services and populated most of their \emph{QoS} parameters
+from a real world web service dataset
+\cite{DBLP:conf/smc/Al-MasriM09a}. We implemented the simulations
+using Java and executed the simulations on an Intel Xeon X3450
+machine with 6GBs of memory. For other parameters missing from the
+dataset, we used normal random distribution with parameters
+estimated using the method of maximum likelihood.
+
+One of the key criteria reflecting the performance of web service
+coalitions is the user satisfaction. User satisfaction can be
+measured in terms of quality and quantity of requests (or tasks)
+successfully answered by the communities. We initiate the
+communities with few web services, then let rejecting and
+accepting random web services go for a short number of iterations.
+After that, we start the request distribution for the communities
+and let them allocate requests among member web services.
+Thereafter, we measure the average output performance of tasks in
+communities following different methods.
+
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=3in]{Figures/task_done_opt.eps}
+\includegraphics[width=3in]{Figures/task_qos_opt.eps}
+\caption{Part (a): Cumulative number of requests successfully
+done. Part (b): Average QoS of requests performed.}
+\label{performanceall}
+\end{figure}
+
+Figure \ref{performanceall} depicts the results of optimal
+\emph{$\epsilon$-core}, \emph{Depth-1 Convex-Checker},
+\emph{Depth-2 Convex-Checker}, \emph{3-Way Satisfaction}
+\cite{DBLP:conf/IEEEscc/LimTMB12}, and \emph{2 Player
+Non-Cooperative} \cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods
+in \emph{one grand community with many web services} scenario.
+
+For the \emph{optimal core} method we have used the well known \emph{$\epsilon$-core} method as the
+taxtation method to relax the core condition to help communities, attract web services.
+We have assigned $\epsilon$ to 15\% of total community worth, $\epsilon = 0.15 \times v(C)$, which allows
+subsets of the coalition to gain maximum 15\% of $v(C)$. In the
+\emph{optimal $\epsilon$-core} method, we capped the coalition
+size to 25 web services, since the method is computationally
+intractable as number of web services increase and anything more than that would make it
+impractical to run in our simulations. In the other methods, there
+were no cap on size of the community and we had communities of
+size 60 web services at some points. The results show that our
+\emph{depth-2 convex checker} method is performing better compared
+to the other methods and its performance is close to optimal
+\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
+and the \emph{3-Way Satisfaction} method, are also performing well.
+
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=3in]{Figures/least_core.eps}
+\caption{Analysis of \emph{$\epsilon$-core} set non-emptiness, for different values of $\epsilon$} \label{f_leastcore}
+\end{figure}
+
+As mentioned in Section \ref{s:preliminaries}, the concept of
+\emph{core}, assumes no coalition of players can gain anything by
+deviating, which is a fairly strong requirement, and that is why
+the notion of \emph{$\epsilon$-core} was introduced. Least-Core
+$e(G)$ of a game $G$, is the minimum amount of $\epsilon$ so that
+the core is not empty. We evaluated the non-emptiness of \emph{$\epsilon$-core} set using the
+valuation function and a set of web services. We picked random
+number of web services from the dataset and formed around 10,000
+random coalitions consisting of 3 to 26 web services. We choose 26
+as the maximum number of members in our coalition since it
+is computationally very complex for larger coalitions to verify whether
+\emph{$\epsilon$-core} set is empty or not.
+Also instead of considering $\epsilon$ amount of constant deviation in \emph{$\epsilon$-core} definition (Equation \ref{eq:core2}), we similarly defined \emph{relative $\epsilon$-core} concept where no coalition would benefit more than \emph{$\epsilon$ $\times$ v(C)} by deviating.
+We set $\epsilon$ between 0 and 1 and verify the \emph{relative $\epsilon$-core} set non-emptiness.
+The results in Figure
+\ref{f_leastcore} illustrates that almost 10\% of our random web
+service coalitions have non-empty \emph{core} solution and
+\emph{$\epsilon$-core} solution is \emph{always} non-empty when we
+let agents gain only 30\% more of $v(C)$ by deviating.
+
+One of the properties of coalition structure formation algorithms
+in our second scenario is that they partition web services with low
+throughput rate so that they usually join coalitions with less
+request rate. Since the characteristic function $v(C)$ and the
+fair Shapely payoff vector is proportional to web services'
+contribution, the web services with small contribution will get
+paid much less in communities having web services with high
+throughput. On the other hand, according to the valuation function
+$v(C)$, web services with high throughput will not contribute well
+to communities with low amount of user requests (low market
+share). The strong web services are likely to deviate from weak
+coalitions, joining a stronger one, which makes the initial
+coalition unstable.
+
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=3in]{Figures/taxtation.eps}
+\caption{Analysis of community subsiding coefficient $\lambda$ on average community size (a), cost (b), number of tasks performed (c), and average quality of service of tasks performed (d).} \label{f_taxtation}
+\end{figure}
+
+As mentioned in section \ref{s:tax} in order to help community stability, is to subside the community by a relative coefficient ($\lambda$) so the value of $\lambda v(C)$ is devided among the community members.
+We have analysed the effect of subsiding and the cost it incurs to our web service communities.
+Figure \ref{f_taxtation} shows the results.
+In this expirement we have set a community with input task rate $R_C$ of 100 and having abstract web services throuput rate $T_r$ value of a random distribution with average 10 tasks per iteration.
+Part (a) shows the community size increases in a linear fashion as ($\lambda$) increases.
+However the cost is having a slight exponential growth rate since, not only ($\lambda$) increases also the size of the community is also increasing slowly.
+Therefore subsiding can be costly for larger number of $\lambda$ value.
+Part (c) of figure \ref{f_taxtation} depicts the number of tasks done by the community per iteration.
+It is obvoius with $\lambda$ value of 1.3 which is 30\% of community valuation, the number of tasks done almost reaches the input task rate cap of 100 tasks per iteration.
+The average quality of tasks also has a slight increase since the community will be able to afford better and more web services to join the community.
+These results proves with quality metrics our agents as web services have and their collabrative worth, the increase rate of subsiding more 1.3 is not very effective and is costly to perform.
+
+\begin{figure*}[!t]
+\centerline{\includegraphics[width=6.75in]{Figures/tax_dyn.eps}}
+\caption{Analysis of community subsiding coefficient $\lambda$ having web service different stability levels of $\tau$ on average community size, number of tasks performed, and average quality of service, and average cost/income of communities.}
+\label{fig_dynamic_taxtation}
+\end{figure*}
+
+In previous experiment, we consider the scenario where all web services are stable will not leave the group and will fulfill their promised quality metrics for a good period of time.
+However, in real world scenarios of web services, this is not always the case.
+This is the reason why community would be interested in subsiding a community of larger group web services, paying a few more web services in order to keep the group reliable from end user point of view.
+In our next scenario, we have introduced the new instability variable $\tau$ from 0 to 1, 0 meaning web services having no instability issues and will perform as they claimed until the end of experiment and 1 meaning very unstable web services which will stop functioning on the first iteration of community distributing tasks.
+Figure \ref{fig_dynamic_taxtation} illustrates the results of our experiment having web services with average instability values of 0 to 0.5 and having relative subside value $\lambda$ if 1,1.3,1.6 and 2.
+The \emph{Cost / Income} charts on right column, shows having subside value of 1.3 incurs the least cost and increases the community income significantly.
+Subsiding values of 1.6 and 2 , incur a lot of cost to community and only slightly increase the community revenue.
+Also the role of subsiding is much more obvious when we have unstable web services.
+In scenarios where web services are 100\% stable, subsiding cost will hardly be compensated by community revenue.
+
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=3in]{Figures/s2_task_done.eps}
+\includegraphics[width=3in]{Figures/s2_task_qos.eps}
+\caption{Part (a): Cumulative number of tasks succesfully done. Part
+(b): Average QoS of tasks performed.} \label{performancemany}
+\end{figure}
+
+In Figure \ref{performancemany}, we compare our \emph{Web Services
+and many Communities} scenario with a method which ignores QoS
+parameters and forms coalitions by allowing web services to join
+only if they have enough requests for themselves. In other words,
+web services can join a community when the request rate is less
+than the throughput of all the member web services. We name this
+method \emph{Random Formation} and use it as a benchmark for our
+QoS-aware coalition formation process. As the results illustrate,
+our method forms better coalitions of web services improving
+performance and satisfaction for both web services and coalitions.
+
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=3in]{Figures/avg_task_ws_done.eps}
+\includegraphics[width=3in]{Figures/avg_qos_ws_done.eps}
+\includegraphics[width=3in]{Figures/avg_avail_ws_done.eps}
+\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
+(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
+\end{figure}
+
+Finally, in our last experiment, we compare our work with the work in \cite{10.1109/TSC.2012.12} which we call it \emph{High Availability Coalition} method, because of nature of their community valuation function, which focuses on community availability as main consideration.
+Their community formation model is very different than ours, however we have been very careful to make the experiment environment as fair and similar as possible.
+We limited our maximum community size by 5 in order to have communities with almost the same size.
+In their method, they have used web services as backups rather than active collaborative players, and they only get task when the first web service in an ordered chain fails to perform the task.
+However with recent advancement in cloud and hardware infrastructures availability is less of an issue for web services, and web services are highly available.
+Part(a) of figure \ref{fig_avail_method} shows our method performs almost performs tasks successfully with rate of three times more than \emph{High Availability Coalition} method because of real cooperative nature and task distribution of our algorithm.
+This result shows using web services as backups, and not as real collabrative players is a huge waste of web service capability since they have very low chance of getting jobs and its the primary web service (the first in their coordination chain) which does most of the work.
+The average quality of service of tasks performed is also better since our method considers all quality of service metrics mentioned in table \ref{qosws}.
+Part(c) shows the availability of community from end user point of view.
+The \emph {High Availability Coalition} method almost has 100\% uptime since they use web services as backups, so the chance of job failing reduces significantly as community members increase.
+In our method we have more chance of fail for each web service, however with some subsiding, and hiring a few more web service they can compensate the low chance of failure of web services in our community.
+
+\section{Conclusion}\label{s:conclusion}
+
+In this paper, we proposed a cooperative game theory-based model
+for the aggregation of web services within communities. The goal
+of our services is to maximize efficiency by collaborating and
+forming stable coalitions. Our method considers stability and
+fairness for all web services within a community and offers an
+applicable mechanism for membership requests and selection of web
+services. The ultimate goal is to increase revenue by improving
+user satisfaction, which comes from the ability to perform more
+tasks with high quality. Simulation results show that our,
+polynomial in complexity, approximation algorithms provide web
+services and community owners with applicable and near-optimal
+decision making mechanisms.
+
+As future work, we would like to perform more analytical and
+theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the
+characteristic function in web service applications. From web service perspective, the
+work can be extended to consider web service compositions where a
+group of web services having different set of skills cooperate to
+perform composite tasks. Also bargaining theory from cooperating
+game theory concepts can be used to help web services resolve the
+instability and unfairness issues by side payments.

### 2013-10-20 notes/coop.tex
Changes

@@
 
+\hrule
+
+Coalition-game thoery provides suitable analytical tools that have been widely explored in different diciplines such as economics and political sceince.
+With the recent emergence of cooperation as a new networking paradigm, coalition-game  theory started to become a central framework for modeling cooperation in wireless and communication networks.
+For instance, coalition games prove to be a very powerful tool for designing fair, robust, practical and efficient cooperation strategies in communication networks.
+
 \bibliographystyle{plain}

### 2013-10-26 notes/latex.tex
changes

--- 2013-08-15 proposal/proposal/chapter1.tex
@@
-\setcounter{chapter}{0}
-%*******************************START INTRODUCTION **********************************
-\chapter{Introduction}\label{sec:intro}
-In this chapter we introduce the context of this research, which is about argumentation-based negotiation dialogue games.
-We also present the motivations behind this work and the research questions.
-Also, we discuss the objective of this research and our preliminary contributions.
-Proposal organization is presented in the last section.
+\documentclass{article}
 
-\section{Context of the research}\label{sec:context}
+\usepackage{amsfonts}
+\usepackage{amssymb}
 
-Autonomous agents and multiagent systems (MAS) provide a technology offering an alternative for the design of intelligent and cooperative
-systems. Recently, efforts have been made to develop novel tools, methods, and frameworks to establish the necessary standards for wider
-use of MAS as an emerging paradigm ~\cite{Mehdi03}. An increasing interest within this paradigm is on modeling interactions and dialogue systems.
-In fact, several dialogue systems have been proposed in the literature for modeling \emph{information seeking} dialogues (e.g.,~\cite{MWParsons03}),
-\emph{inquiry} dialogues (e.g.,~\cite{BlackH07,Black09}), \emph{deliberation} dialogues (e.g.,~\cite{Tolchinsky2012}), \emph{persuasion}
-dialogues (e.g., ~\cite{Amgoud00}), and \emph{negotiation} dialogues (e.g., ~\cite{KSycara90}), which are our concern in this paper.
-Negotiation is a form of interaction in which a group of agents, with conflicting interests, but a desire to cooperate, try to come to a mutually
-acceptable agreement on the division of scarce resources~\cite{Rahwan03,Bentahar07}. It is worth noting that in all types of dialogue systems
-mentioned above, a dialogue game is a normative model of dialogue, which mainly consists of: i) a set of moves (e.g., challenge, assertion, question, etc.);
-ii) one commitment store for each conversant where the advanced moves are stored; iii) a communication language specifying the locution that will be
-used by agents during a dialogue for exchanging moves; iv) a protocol specifying the set of rules governing the dialogues; and v) agents' strategies,
-which are the different tactics used by agents for selecting their moves at each step in the dialogue~\cite{AmgoudS08}. A dialogue correctly proceeds
-as long as the participants conform to the dialogue rules and eventually ends when some termination rules are achieved~\cite{AmgoudS08,Nicolas03,Prakken01}.
+\begin{document}
 
-In the recent years, argumentation theory has been widely investigated and used to model and analyze dialogue games~\cite{BentaharAIR,BentaharKBS10,Reed06,Mahalakshmi09}.
-Argumentation provides a powerful tool to represent, model, and reason about dialogue moves, strategies, and dialogue outcomes. The core idea is the ability
-to support moves with justifications and explanations, which play a key role in persuasion and negotiation settings~\cite{GarciaCRS13}. In this paper, we
-will focus on the exchanged moves in a dialogue game (i.e., the dialogue itself) and the agents playing these moves when supporting arguments are used.
-The main issue we are investigating is the uncertainty index of selecting the right moves during the dialogue, the certainty index that the selected move
-will be accepted by the addressee, and the uncertainty index of the whole dialogue. Uncertainty can be thought of as being the inverse of information. Information
-about a particular engineering or scientific problem may be incomplete, imprecise, fragmentary, unreliable, vague, contradictory, or even deficient~\cite{RossJA13}.
-Uncertainty about values of given variables (e.g., the disease affecting a patient in medical applications) can result from some errors and hence from unreliability
-(in the case of sensors) or from different background knowledge (in the case of agents). As a result, it is possible to obtain different uncertain pieces of
-information about a given value from different sources~\cite{Jenhani07}. Our aim is to investigate the uncertainty issues that the agent faces when choosing an
-argument to play in argumentation-based negotiations. In the literature, many efforts have been deployed to model negotiation. A brief description of those efforts
-is given in the following subsection.
-
-A multiagent system is a system where agents (software autonomous entities) are allowed to freely enter and leave the
-system, thus making the environment continuously changing. These agents need to communicate with each other, with individual or
-collective tasks, with different resources, and different skills. As a result, these agent societies are becoming more and more
-similar to the human ones~\cite{Falcone99}.\\
-An attractive characteristic of MAS is that agents can act more effectively in groups. Agents are designed to
-autonomously collaborate with each other in order to satisfy both their internal goals and the shared external demands
-generated by virtue of their participation in agent societies. \\
-The languages used by agents to communicate are called Agent Communication Languages (ACLs). The main objective of an
-ACL is to model a suitable framework that allows heterogeneous agents to interact and to communicate with meaningful
-statements that convey information about their environment or knowledge~\cite{Kone00}. Two main ACLs have been proposed:
-the Knowledge Query and Manipulation Language (KQML)~\cite{Finin95}, and the Foundation for Intelligent Physical Agents'
-Agent Communication Language (FIPA-ACL)~\cite{Fipa01}.\\
-Furthermore, there is an increasing interest on modeling interactions and dialogue systems. Indeed, several
-dialogue systems have been proposed in the literature for modeling information seeking dialogues (e.g.~\cite{MWParsons03}),
-inquiry dialogues (e.g.,~\cite{BlackH07}), persuasion dialogues (e.g.,~\cite{Amgoud00}) and finally negotiation dialogues
-(e.g.,~\cite{KSycara90}).\\
-Evaluating multiagent systems and the dialogues taking place between the participants is a very important issue in the recent
-developments of multiagent systems. The existing approaches on evaluating these systems are focusing on one aspect at a time, such as
-evaluating persuasion dialogues (~\cite{Amgoud00}), and measuring the impact of argumentation (~\cite{Hunter04}). They are more concerned
-with proposing dialogue strategies and analyzing dialogues. However, nothing is said about the agents' certainty about their dialogues and
-the goodness degree of the agents in the dialogues. In this thesis, we are interested particularly in negotiation dialogue games. In fact,
-negotiation is a form of interaction in which a group of agents, with conflicting interests, but a desire to cooperate, try to come to a
-mutually acceptable agreement on the division of scarce resources ~\cite{Rahwan03,Bentahar07}. Dialogue games are a set of rules governing the
-dialogue. such rules specify the allowed communicative acts agents can perform when participating in  a dialogue. Precisely, we focus in this
-work on quantitative negotiation dialogue games such as bargaining. We will focus first on the exchanged moves (i.e. the dialogue itself) in
-terms of the certainty index of selecting the right moves during the dialogue, and the certainty index of the whole dialogue. Uncertainty about
-values of given variables (e.g. the disease affecting a patient in medical applications) can result from some errors and hence from non-reliability
-(in the case of sensors) or from different background knowledge (in the case of agents). As a result, it is possible to obtain different uncertain
-pieces of information about a given value from different sources ~\cite{Jenhani07}. The second focus of this thesis is on the agents' strategies in
-terms of goodness degree of the agents in the real dialogue (i.e. the dialogue that effectively happened between the participants) and the farness
-degree of the agents from the right dialogue (i.e. the best dialogue that can be produced by two agents if they know the knowledge bases of each other).
-For example in negotiation setting, the best dialogue is the one in which with a minimum number of moves, two agents can achieve the best agreement for
-both of them, if such an agreement exists considering the knowledge bases of these two agents.
-%
-
-\section{Motivations and research questions}\label{sec:motivation}
-
-Multiagent systems are widely used in everyday life, and to add more value to these systems in the field of software engineering,
-they supposed to be measurable. Our motivation is to find a way to measure these systems from different aspects such as measuring
-the dialogues, the performance of the participants in the dialogues, and the protocols governing the dialogues, etc. In order to evaluate
-dialogues in multiagent systems, we define a new set of measurements from an external agent's point of view. Defining measures for the
-participants in the dialogues is another motivation in this thesis. The aim behind developing such measurements is to help engineers and
-developers of agent-based systems in evaluating these systems and their performances.\\
-
-\indent When monitoring a dialogue between two or more agents, there are many question that should be answered. In this thesis, we are interested in answering the following questions:
-
-\begin{itemize}
-\item How much are agents certain about selecting a move at each dialogue step?
-\item How much are agents certain about their dialogues?
-\item How good are agents in the real dialogue (i.e. the effective dialogue)?
-\item How far are agents from the right dialogue (i.e. the best dialogue given the knowledge bases of the participants)?
-\end{itemize}
-Answering these questions is undoubtedly complex. Therefore, we do not expect a comprehensive answer to all these questions.
-
-\section{Research objectives and contributions}\label{sec:contribution}
-
-The main objective of this thesis is to develop a new set of measurements for negotiation dialogue games to help in evaluating and
-comparing different negotiation dialogues with different participants for the same topic. The importance of introducing measures for
-negotiation dialogue games at each step of the dialogue such as measuring how much the agent is certain about its move is to help in developing intelligent multiagent systems (MAS) and to help evaluating different agents provided by different developers.\\
-\indent Our research aims to ensure that the agents' certainty about their dialogue is fairly represented at each step during
-the dialogue by making sure that the agent's certainty about selecting the right move is kept in mind and considered as a property
-of multiagent systems.\\
-\indent The main contribution of this thesis is the proposition of a new set of measures for dialogue games from an external agent's point of view.
-In particular, we introduce two sets of measurements. In the first set  we use Shannon entropy to measure the certainty index of the dialogue.
-This involves i) using Shannon entropy to measure the agent's certainty about each move during the dialogue; and ii) using
-Shannon entropy to measure the certainty of the agents about the whole dialogue with two different ways. The first way is
-by taking the average of the certainty index of all moves, and the second way is by determining all possible dialogues and
-applying the general formula of Shannon entropy. In the second set, we are measuring how good are agents in the real dialogue
-\emph{(Goodness Degree )}, and measuring how far are agents from the right dialogue \emph{(Farness Degree)}~\cite{Marey09}.
-
-As mentioned earlier, there exist several proposals on the argumentation-based negotiation. Most of them are concerned with proposing protocols to show how agents can
-interact with each other, and how arguments and offers can be generated, evaluated and exchanged during the negotiation process. However, none of them has investigated
-the agents' uncertainty about the exchanged arguments and how such an uncertainty could be measured at each dialogue step to assist the agents make a better decision. The
-uncertainty is generally defined as ``that which is not precisely known''. This definition permits the identification of different kinds of uncertainty arising from different
-sources and activities, most of which go unnoticed in analysis. To the best of our knowledge, this work is the first of it's kind in dealing with the agent's uncertainty
-while making a decision at each dialogue step in order to achieve an agreement. In this paper, we define a new set of uncertainty measures for dialogue games from an
-external agent's point of view. In particular, we distinguish two types of uncertainty: \textbf{Type I} and \textbf{Type II}.
-
-Type I is about the uncertainty of playing the right move (i.e., advancing the right argument) at each dialogue step. For this type, we use Shannon entropy to measure: i) the
-uncertainty index of the agent that he is selecting the right move at each step during the dialogue; and ii) the uncertainty index of both agents participating in the dialogue
-about the whole dialogue. The latter measurement will be conducted in two different ways. The first way is by taking the average of the uncertainty index of all moves,
-and the second is by determining all possible dialogues based on the union of the agents' knowledge bases and applying the general formula of Shannon entropy.
-
-Type II is about the uncertainty of the agent that the selected move (argument) will be accepted by the addressee (from now on we will call this second type of uncertainty
-by \emph{uncertainty degree}). In this context, we introduce a new classification of arguments based on their certainty index. These measures are of great importance since
-they can be used as guidelines for a protocol in order to generate the best dialogue between autonomous intelligent agents.
+\section{Latex}
 
@@
 
-\section{Research outline}\label{sec:outline}
-The rest of the paper is organized as follows: In Section~\ref{sec:Argumentation}, we present a  brief theoretical background on the argumentation system
-and agent's theory, strategic reasoning, tactic reasoning and risk of failure notions are also discussed in this section. In Section~\ref{sec:uncertainty},
-we present the agent's uncertainty measures using Shannon entropy, which include type I (measuring the uncertainty of the agent about selecting the right move)
-and type II (measuring the uncertainty degree that the selected move will be accepted). Argument classification is also presented in this section. Related work
-is discussed in Section~\ref{sec:related}. Finally, conclusion and future work are presented in Section~\ref{sec:conclusion}.
+ \emph{(Farness Degree)}~\cite{Marey09}.
 
-%****************************************** END INTRODUCTION****************************************
+\bibliographystyle{plain}
+\bibliography{ehsan}
+
+\end{document}

### 2013-10-26 notes/shapley.tex
changes

\documentclass{article}

\usepackage{amsfonts}
\usepackage{amssymb}

\begin{document}

\section{Shapley Value}

Shapley value basically tries to distribute the earn of the group to all the participating agents in a fair way, so the result is a vector for all agants: lets say \emph{Pay(i)} is the payment that should be made to agent \emph{i}.
\\
\\
The way it calculates \emph{Pay(i)} for each agent is basically, for all subsets of agents, let's see how much they make with and without agent \emph{i} and average that, so in a group of 3 agents {1,2,3}, payment for player 1 is going to be like:
\\
\\
\begin{gather*}
P(1) = 
\\
 (
\\
v(\left\{1\right\} + \left\{\right\}) - v(\left\{\right\}) +
\\
v(\left\{1\right\} + \left\{2\right\}) - v(\left\{2\right\}) + 
\\
v(\left\{1\right\} + \left\{3\right\}) - v(\left\{3\right\}) +
\\
v(\left\{1\right\} + \left\{2,3\right\}) - v(\left\{2,3\right\})  
\\
) / 4
\\
\end{gather*}
\\
So in the example of gloves after the calculations we have: \\
P(left hand glove 1) = 1/6, \\
P(left hand glove 2) = 1/6, \\
P(right hand glove 3)  = 2/3 \\
\\
Right hand will recieve more payment since the right hand glove contributes more to different subsets and is more important while left hand glove is redundant in most cases and doesn't add much value to group.
\\
\\
Now since this is computationally heavy (we need to average each agents contribution to \emph{\textbf{all possible subsets}}). What they did in that paper did and claimed to be egalitarian is: 
They say we pay each agent the amount they made alone (in glove example working alone earns 0) and distribute rest equally between agents. So in that example:
\\
\\
P(left hand glove 1) = 1/3, \\
P(left hand glove 2) = 1/3, \\
P(right hand glove 3)  = 1/3 \\

This is not a general method and I didn't find this in any other paper as egaliterian method for shapley value, (I checked that refrence before), but it's very fast to calculate however it does not have 4 important properties of shapely value (Efficiency, Symmetry, Linearity, Zero Player - non dictatorship) and is not fair at all and can cause agents to leave because of this distribution

%\bibliographystyle{plain}
%\bibliography{ehsan}

\end{document}

### 2013-10-30 proposal/proposal/chapter2.tex
changes

@@
 
-\section{Types of Dialogue Games}\label{sec:DialogueGames}
+    \section{Community of Web Services}\label{sec:CommunityWS}
 
-\section{Negotiation Dialogue Games}\label{sec:Negotiation}
-Negotiation is a form of interaction in which a group of self-interested agents with conflicting interests and a desire to cooperate attempt to
-reach  a mutual acceptable agreement on the division of scarce resources.
+        \subsection{Web Services}\label{sec:WS}
 
-   \subsection{Negotiation Component}\label{sec:NComp}
+        \subsection{Definition}\label{sec:CWSDefinition}
 
-   \subsection{Approaches to Automated Negotiation}\label{sec:Nappro}
+        \subsection{Architecture}\label{sec:CWSArchitecture}
+
+        \subsection{Operations}\label{sec:CWSOperations}
+
+            \subsubsection{Community Development}\label{sec:CWSCommunityDev}
+
+            \subsubsection{Web Service Attraction and Retention}\label{sec:CWSAttraction}
+
+            \subsubsection{Web Service Selection}\label{sec:CWSSelection}
+
+    \subsection{Related Work}\label{sec:CWSRelatedWork}
 

### 2013-11-03 proposal/proposal/chapter1.tex
changes

@@
 \chapter{Introduction}\label{sec:intro}
-In this chapter we introduce the context of this research, which is about argumentation-based negotiation dialogue games.
-We also present the motivations behind this work and the research questions.
-Also, we discuss the objective of this research and our preliminary contributions.
-Proposal organization is presented in the last section.
+In this chapter we introduce the context of this research, which is about community of web services as autonomous agents and cooperative game theoretic solution concepts.
+We discuss literature review and their shortcomings then present the motivations behind this work.
+Also, we discuss our preliminary contributions.
 
@@
 
-Autonomous agents and multiagent systems (MAS) provide a technology offering an alternative for the design of intelligent and cooperative
-systems. Recently, efforts have been made to develop novel tools, methods, and frameworks to establish the necessary standards for wider
-use of MAS as an emerging paradigm ~\cite{Mehdi03}. An increasing interest within this paradigm is on modeling interactions and dialogue systems.
-In fact, several dialogue systems have been proposed in the literature for modeling \emph{information seeking} dialogues (e.g.,~\cite{MWParsons03}),
-\emph{inquiry} dialogues (e.g.,~\cite{BlackH07,Black09}), \emph{deliberation} dialogues (e.g.,~\cite{Tolchinsky2012}), \emph{persuasion}
-dialogues (e.g., ~\cite{Amgoud00}), and \emph{negotiation} dialogues (e.g., ~\cite{KSycara90}), which are our concern in this paper.
-Negotiation is a form of interaction in which a group of agents, with conflicting interests, but a desire to cooperate, try to come to a mutually
-acceptable agreement on the division of scarce resources~\cite{Rahwan03,Bentahar07}. It is worth noting that in all types of dialogue systems
-mentioned above, a dialogue game is a normative model of dialogue, which mainly consists of: i) a set of moves (e.g., challenge, assertion, question, etc.);
-ii) one commitment store for each conversant where the advanced moves are stored; iii) a communication language specifying the locution that will be
-used by agents during a dialogue for exchanging moves; iv) a protocol specifying the set of rules governing the dialogues; and v) agents' strategies,
-which are the different tactics used by agents for selecting their moves at each step in the dialogue~\cite{AmgoudS08}. A dialogue correctly proceeds
-as long as the participants conform to the dialogue rules and eventually ends when some termination rules are achieved~\cite{AmgoudS08,Nicolas03,Prakken01}.
-
-In the recent years, argumentation theory has been widely investigated and used to model and analyze dialogue games~\cite{BentaharAIR,BentaharKBS10,Reed06,Mahalakshmi09}.
-Argumentation provides a powerful tool to represent, model, and reason about dialogue moves, strategies, and dialogue outcomes. The core idea is the ability
-to support moves with justifications and explanations, which play a key role in persuasion and negotiation settings~\cite{GarciaCRS13}. In this paper, we
-will focus on the exchanged moves in a dialogue game (i.e., the dialogue itself) and the agents playing these moves when supporting arguments are used.
-The main issue we are investigating is the uncertainty index of selecting the right moves during the dialogue, the certainty index that the selected move
-will be accepted by the addressee, and the uncertainty index of the whole dialogue. Uncertainty can be thought of as being the inverse of information. Information
-about a particular engineering or scientific problem may be incomplete, imprecise, fragmentary, unreliable, vague, contradictory, or even deficient~\cite{RossJA13}.
-Uncertainty about values of given variables (e.g., the disease affecting a patient in medical applications) can result from some errors and hence from unreliability
-(in the case of sensors) or from different background knowledge (in the case of agents). As a result, it is possible to obtain different uncertain pieces of
-information about a given value from different sources~\cite{Jenhani07}. Our aim is to investigate the uncertainty issues that the agent faces when choosing an
-argument to play in argumentation-based negotiations. In the literature, many efforts have been deployed to model negotiation. A brief description of those efforts
-is given in the following subsection.
-
-A multiagent system is a system where agents (software autonomous entities) are allowed to freely enter and leave the
-system, thus making the environment continuously changing. These agents need to communicate with each other, with individual or
-collective tasks, with different resources, and different skills. As a result, these agent societies are becoming more and more
-similar to the human ones~\cite{Falcone99}.\\
-An attractive characteristic of MAS is that agents can act more effectively in groups. Agents are designed to
-autonomously collaborate with each other in order to satisfy both their internal goals and the shared external demands
-generated by virtue of their participation in agent societies. \\
-The languages used by agents to communicate are called Agent Communication Languages (ACLs). The main objective of an
-ACL is to model a suitable framework that allows heterogeneous agents to interact and to communicate with meaningful
-statements that convey information about their environment or knowledge~\cite{Kone00}. Two main ACLs have been proposed:
-the Knowledge Query and Manipulation Language (KQML)~\cite{Finin95}, and the Foundation for Intelligent Physical Agents'
-Agent Communication Language (FIPA-ACL)~\cite{Fipa01}.\\
-Furthermore, there is an increasing interest on modeling interactions and dialogue systems. Indeed, several
-dialogue systems have been proposed in the literature for modeling information seeking dialogues (e.g.~\cite{MWParsons03}),
-inquiry dialogues (e.g.,~\cite{BlackH07}), persuasion dialogues (e.g.,~\cite{Amgoud00}) and finally negotiation dialogues
-(e.g.,~\cite{KSycara90}).\\
-Evaluating multiagent systems and the dialogues taking place between the participants is a very important issue in the recent
-developments of multiagent systems. The existing approaches on evaluating these systems are focusing on one aspect at a time, such as
-evaluating persuasion dialogues (~\cite{Amgoud00}), and measuring the impact of argumentation (~\cite{Hunter04}). They are more concerned
-with proposing dialogue strategies and analyzing dialogues. However, nothing is said about the agents' certainty about their dialogues and
-the goodness degree of the agents in the dialogues. In this thesis, we are interested particularly in negotiation dialogue games. In fact,
-negotiation is a form of interaction in which a group of agents, with conflicting interests, but a desire to cooperate, try to come to a
-mutually acceptable agreement on the division of scarce resources ~\cite{Rahwan03,Bentahar07}. Dialogue games are a set of rules governing the
-dialogue. such rules specify the allowed communicative acts agents can perform when participating in  a dialogue. Precisely, we focus in this
-work on quantitative negotiation dialogue games such as bargaining. We will focus first on the exchanged moves (i.e. the dialogue itself) in
-terms of the certainty index of selecting the right moves during the dialogue, and the certainty index of the whole dialogue. Uncertainty about
-values of given variables (e.g. the disease affecting a patient in medical applications) can result from some errors and hence from non-reliability
-(in the case of sensors) or from different background knowledge (in the case of agents). As a result, it is possible to obtain different uncertain
-pieces of information about a given value from different sources ~\cite{Jenhani07}. The second focus of this thesis is on the agents' strategies in
-terms of goodness degree of the agents in the real dialogue (i.e. the dialogue that effectively happened between the participants) and the farness
-degree of the agents from the right dialogue (i.e. the best dialogue that can be produced by two agents if they know the knowledge bases of each other).
-For example in negotiation setting, the best dialogue is the one in which with a minimum number of moves, two agents can achieve the best agreement for
-both of them, if such an agreement exists considering the knowledge bases of these two agents.
-%
-
 \section{Motivations and research questions}\label{sec:motivation}
 
-Multiagent systems are widely used in everyday life, and to add more value to these systems in the field of software engineering,
-they supposed to be measurable. Our motivation is to find a way to measure these systems from different aspects such as measuring
-the dialogues, the performance of the participants in the dialogues, and the protocols governing the dialogues, etc. In order to evaluate
-dialogues in multiagent systems, we define a new set of measurements from an external agent's point of view. Defining measures for the
-participants in the dialogues is another motivation in this thesis. The aim behind developing such measurements is to help engineers and
-developers of agent-based systems in evaluating these systems and their performances.\\
+Over the past years, online services have become part of many
+scalable business applications. The increasing reliance on
+web-based applications has significantly influenced the way web
+services are engineered. Web services provide a set of stateless
+software functions accessible at a network address over the web.
+The recent developments are shifting web services from passive and
+individual components to autonomous and group-based components
+where interaction, composition, and cooperation are the key
+challenges \cite{ICWS2011-1,SCC2011-1}. The main objective is to
+achieve a seamless integration of business processes, applications
+and web services. Delivering high quality services considering the
+dynamic and unpredictable nature of the Internet is still a very
+critical and challenging issue.
 
-\indent When monitoring a dialogue between two or more agents, there are many question that should be answered. In this thesis, we are interested in answering the following questions:
+The need for highly available and responsive services has called
+for grouping and collaborative mechanisms of loosely-coupled web
+services, particularly in business settings. The idea of grouping
+web services within communities and the way those communities are
+engineered so that web services can better collaborate have been
+proposed and investigated in
+\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
+Communities are virtual groups of web services having similar
+functionalities \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7}, but probably different non-functional quality
+attributes, which form the QoS parameters. When communities are
+used, users send their requests to the masters of those
+communities, which are responsible of managing the communities,
+forwarding the requests to the suitable member web services and
+checking the credentials of those members. Communities aim to
+provide higher service availability and performance than what
+individual web services can provide. The high availability of
+services and the community resilience to failure are guaranteed
+since web services can cooperate and replace each other within the
+same community and since there is no single point of failure in
+the communities architecture.
 
-\begin{itemize}
-\item How much are agents certain about selecting a move at each dialogue step?
-\item How much are agents certain about their dialogues?
-\item How good are agents in the real dialogue (i.e. the effective dialogue)?
-\item How far are agents from the right dialogue (i.e. the best dialogue given the knowledge bases of the participants)?
-\end{itemize}
-Answering these questions is undoubtedly complex. Therefore, we do not expect a comprehensive answer to all these questions.
+Most of the recent work on communities of services are either
+user-centric and focus on user satisfaction
+\cite{Chun02user-centricperformance} or system-centric and focus
+on the whole system throughput, performance and utilization. There
+are many contributions in distributed, grid, cluster and cloud
+services which are system-centric. However, in real world
+environments and applications, both users and service providers
+are self-interested agents, aiming to maximize their own profit.
+In those environments, both parties (users and services) will
+collaborate as long as they are getting more benefits and payoff.
+
+In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
+DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
+users and services to maximize their gain. A two-player
+non-cooperative game between web services and community master was
+introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this
+game-theoretic model, the strategies available to a web service
+when facing a new community are requesting to join the community,
+accepting the master's invitation to join the community, or
+refusing the invitation to join. The set of strategies for
+communities are inviting the web service or refusing the web
+service's join request. Based on their capacity, market share and
+reputation, the two players have different set of utilities over
+the strategy profiles of the game. The main limits of this game
+model are: 1) its consideration of only three quality parameters,
+while the other factors are simply ignored; and 2) the
+non-consideration of the web services already residing within the
+community. The game is only between the community master and the
+new web service, and the inputs from all the other members are
+simply ignored. The consideration of those inputs is a significant
+issue as existing web services can lose utility or payoff because
+of the new member, which can results in an unhealthy and unstable
+group. The problem comes from the fact that the existing members
+should collaborate with the new web services, so probably their
+performance as a group can suffer. Existing members may even
+deviate and try to join other communities if they are unsatisfied.
+Those considerations of forming stable and efficient coalitions
+are the main contributions of our paper.
+
+In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
+for selecting web services has been proposed. In this approach,
+the authors proposed a web service selection process that the
+community masters can use. The approach considers the efficiency
+of all the three involved parties, namely users, web services and
+communities. In this work, it is shown how the gains of these
+parties are coupled together using a linear optimization process.
+However, the optimization problem in this solution tends to
+optimize some parameters considering all web services regardless
+of their efficiency and contribution to the community's welfare.
+Moreover, there are no clear thresholds for accepting or rejecting
+new web services. The solution of the optimization problem could,
+for instance, suggest web services already residing within the
+community to increase or decrease their capacity to cover up the
+weakness of other parties in the system. However, a high
+performing web service could deviate anytime it finds itself
+unsatisfied within the community instead of adjusting its service
+parameters.
+
+In \cite{10.1109/TSC.2012.12}, a cooperative scheme among autonomous
+web services based on coalitional game theory has been introduced. They have proposed an algorithm to
+reach individually stable coalition partition for web services in order to
+maximize their efficiency. The communities choose new web services on the promise
+that it would benefit the community without decreasing any other web service's
+income. In their model, the worth of community is evaluated with high emphasis on
+availability metric and considering price and cost values only. The community structure is based on a coordination chain,
+where a web service is assigned as a \emph{primary} web service and the community task destribution
+method, will initially invoke the primary web service and only if the primary web service is unavailable
+will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to
+have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays
+with recent advancement in cloud and hardware infrastructures availability is becoming less of an issue. So the backup web services
+in their model have a very low chance of getting jobs, especially the ones further in chain, which is huge waste of web services
+capabilities.
+
+% ooooooold
+%\indent When monitoring a dialogue between two or more agents, there are many question that should be answered. In this thesis, we are interested in answering the following questions:
+%\begin{itemize}
+%\item How much are agents certain about selecting a move at each dialogue step?
+%\item How much are agents certain about their dialogues?
+%\item How good are agents in the real dialogue (i.e. the effective dialogue)?
+%\item How far are agents from the right dialogue (i.e. the best dialogue given the knowledge bases of the participants)?
+%\end{itemize}
+%Answering these questions is undoubtedly complex. Therefore, we do not expect a comprehensive answer to all these questions.
 
@@
 
-The main objective of this thesis is to develop a new set of measurements for negotiation dialogue games to help in evaluating and
-comparing different negotiation dialogues with different participants for the same topic. The importance of introducing measures for
-negotiation dialogue games at each step of the dialogue such as measuring how much the agent is certain about its move is to help in developing intelligent multiagent systems (MAS) and to help evaluating different agents provided by different developers.\\
-\indent Our research aims to ensure that the agents' certainty about their dialogue is fairly represented at each step during
-the dialogue by making sure that the agent's certainty about selecting the right move is kept in mind and considered as a property
-of multiagent systems.\\
-\indent The main contribution of this thesis is the proposition of a new set of measures for dialogue games from an external agent's point of view.
-In particular, we introduce two sets of measurements. In the first set  we use Shannon entropy to measure the certainty index of the dialogue.
-This involves i) using Shannon entropy to measure the agent's certainty about each move during the dialogue; and ii) using
-Shannon entropy to measure the certainty of the agents about the whole dialogue with two different ways. The first way is
-by taking the average of the certainty index of all moves, and the second way is by determining all possible dialogues and
-applying the general formula of Shannon entropy. In the second set, we are measuring how good are agents in the real dialogue
-\emph{(Goodness Degree )}, and measuring how far are agents from the right dialogue \emph{(Farness Degree)}~\cite{Marey09}.
-
-As mentioned earlier, there exist several proposals on the argumentation-based negotiation. Most of them are concerned with proposing protocols to show how agents can
-interact with each other, and how arguments and offers can be generated, evaluated and exchanged during the negotiation process. However, none of them has investigated
-the agents' uncertainty about the exchanged arguments and how such an uncertainty could be measured at each dialogue step to assist the agents make a better decision. The
-uncertainty is generally defined as ``that which is not precisely known''. This definition permits the identification of different kinds of uncertainty arising from different
-sources and activities, most of which go unnoticed in analysis. To the best of our knowledge, this work is the first of it's kind in dealing with the agent's uncertainty
-while making a decision at each dialogue step in order to achieve an agreement. In this paper, we define a new set of uncertainty measures for dialogue games from an
-external agent's point of view. In particular, we distinguish two types of uncertainty: \textbf{Type I} and \textbf{Type II}.
-
-Type I is about the uncertainty of playing the right move (i.e., advancing the right argument) at each dialogue step. For this type, we use Shannon entropy to measure: i) the
-uncertainty index of the agent that he is selecting the right move at each step during the dialogue; and ii) the uncertainty index of both agents participating in the dialogue
-about the whole dialogue. The latter measurement will be conducted in two different ways. The first way is by taking the average of the uncertainty index of all moves,
-and the second is by determining all possible dialogues based on the union of the agents' knowledge bases and applying the general formula of Shannon entropy.
-
-Type II is about the uncertainty of the agent that the selected move (argument) will be accepted by the addressee (from now on we will call this second type of uncertainty
-by \emph{uncertainty degree}). In this context, we introduce a new classification of arguments based on their certainty index. These measures are of great importance since
-they can be used as guidelines for a protocol in order to generate the best dialogue between autonomous intelligent agents.
-
-Figure \ref{fig1.0} summarizes the whole proposed approach where the certainty index ($CI$) and weighted certainty index ($W\_CI$) of the moves and the whole dialogue are
-measured for Type I. For Type II, different cases are considered depending on how many arguments are in use.
-
-\begin{figure}[t]
-                \begin{center}
-                \includegraphics[width=15cm, height=11cm]{Figures/Approach1.eps}
-                \end{center}
-                \caption{General overview of the approach}\label{fig1.0}
-                \label{Stack}
-                \end{figure}
+In this research work, we use game theory to
+propose a cooperative game model for the aggregation of web
+services within communities. The solution concepts of our
+cooperative game seeks to find efficient ways of forming
+coalitions (teams) of web services so that they can maximize their
+gain and payoff, and distribute the gain in a fair way among all
+the web services. Achieving Fairness when the gain is distributed
+among the community members is the main factor to keep the
+coalition stable as no web service will expect to gain better by
+deviating for the community. In other words, the coalition is made
+efficient if all the members are satisfied. We first propose a
+representation function for communities of web services based on
+their QoS attributes. By using this function, we can evaluate the
+$worth$ of each community of web services. When facing new
+membership requests, a typical community master checks whether the
+new coalition having the old and new set of web services will keep
+the community stable or not. The community master will reject the
+membership requests if it finds out that the new coalition would
+be unstable, preventing $any$ subset of web services from gaining
+significantly more by deviating from the community and joining
+other communities or forming new ones. The computation of
+solutions for cooperative game theory problems is combinatorial in
+nature and proven to be NP-complete \cite{Algorithmic}, making
+this computation impractical in real world applications. However,
+using the concepts of coalition stability, we propose
+approximation algorithms running in polynomial time providing web
+services and community masters with applicable and near-optimal
+decision making mechanisms.
 
 \section{Research outline}\label{sec:outline}
-The rest of the paper is organized as follows: In Section~\ref{sec:Argumentation}, we present a  brief theoretical background on the argumentation system
-and agent's theory, strategic reasoning, tactic reasoning and risk of failure notions are also discussed in this section. In Section~\ref{sec:uncertainty},
-we present the agent's uncertainty measures using Shannon entropy, which include type I (measuring the uncertainty of the agent about selecting the right move)
-and type II (measuring the uncertainty degree that the selected move will be accepted). Argument classification is also presented in this section. Related work
-is discussed in Section~\ref{sec:related}. Finally, conclusion and future work are presented in Section~\ref{sec:conclusion}.
+The rest of the paper is organized as follows: In Section~\ref{sec:Argumentation}
 

### 2013-11-05 proposal/proposal/Abstract.tex
Changes

@@
 individual and group efficiency and income has not been addressed
-yet. In this paper, we propose an efficient coalition formation
+yet.
+
+In this proposal, we propose an efficient coalition formation
 mechanism using cooperative game-theoretic techniques. We propose
@@
 making mechanisms.
+
+In future work, we need to apply different cooperative game techniques such as nucleus, 
+kernel and bargaining solution concepts and theoretically analyse solution concepts, 
+based on functions representing payoff and quality metrics the web service communities. 
+We also aim to apply reinforcement learning techniques for individual web service 
+strategic decision making process.

### 2013-11-05 proposal/proposal/chapter2.tex
changes
Changes

@@
 
-        \subsection{Web Services}\label{sec:WS}
+        \subsection{Web Services}\label{sec:BRWS}
 
@@
 
-    \subsection{Related Work}\label{sec:CWSRelatedWork}
+        \subsection{Related Work}\label{sec:BRRelatedWork}
+
+One of the first contributions in which web service community was introduced was in \cite{Zeng:2003:QDW:775152.775211}.
+They defined web service community as collection of web services providing same functionality however with different quality metrics.
+
+Most of the recent work on communities of services are either
+user-centric and focus on user satisfaction
+\cite{Chun02user-centricperformance} or system-centric and focus
+on the whole system throughput, performance and utilization. There
+are many contributions in distributed, grid, cluster and cloud
+services which are system-centric. However, in real world
+environments and applications, both users and service providers
+are self-interested agents, aiming to maximize their own profit.
+In those environments, both parties (users and services) will
+collaborate as long as they are getting more benefits and payoff.
+
+In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
+DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
+users and services to maximize their gain. A two-player
+non-cooperative game between web services and community master was
+introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this
+game-theoretic model, the strategies available to a web service
+when facing a new community are requesting to join the community,
+accepting the master's invitation to join the community, or
+refusing the invitation to join. The set of strategies for
+communities are inviting the web service or refusing the web
+service's join request. Based on their capacity, market share and
+reputation, the two players have different set of utilities over
+the strategy profiles of the game. The main limits of this game
+model are: 1) its consideration of only three quality parameters,
+while the other factors are simply ignored; and 2) the
+non-consideration of the web services already residing within the
+community. The game is only between the community master and the
+new web service, and the inputs from all the other members are
+simply ignored. The consideration of those inputs is a significant
+issue as existing web services can lose utility or payoff because
+of the new member, which can results in an unhealthy and unstable
+group. The problem comes from the fact that the existing members
+should collaborate with the new web services, so probably their
+performance as a group can suffer. Existing members may even
+deviate and try to join other communities if they are unsatisfied.
+Those considerations of forming stable and efficient coalitions
+are the main contributions of our paper.
+
+In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
+for selecting web services has been proposed. In this approach,
+the authors proposed a web service selection process that the
+community masters can use. The approach considers the efficiency
+of all the three involved parties, namely users, web services and
+communities. In this work, it is shown how the gains of these
+parties are coupled together using a linear optimization process.
+However, the optimization problem in this solution tends to
+optimize some parameters considering all web services regardless
+of their efficiency and contribution to the community's welfare.
+Moreover, there are no clear thresholds for accepting or rejecting
+new web services. The solution of the optimization problem could,
+for instance, suggest web services already residing within the
+community to increase or decrease their capacity to cover up the
+weakness of other parties in the system. However, a high
+performing web service could deviate anytime it finds itself
+unsatisfied within the community instead of adjusting its service
+parameters.
+
+In \cite{10.1109/TSC.2012.12}, a cooperative scheme among autonomous
+web services based on coalitional game theory has been introduced. They have proposed an algorithm to
+reach individually stable coalition partition for web services in order to
+maximize their efficiency. The communities choose new web services on the promise
+that it would benefit the community without decreasing any other web service's
+income. In their model, the worth of community is evaluated with high emphasis on
+availability metric and considering price and cost values only. The community structure is based on a coordination chain,
+where a web service is assigned as a \emph{primary} web service and the community task destribution
+method, will initially invoke the primary web service and only if the primary web service is unavailable
+will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to
+have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays
+with recent advancement in cloud and hardware infrastructures availability is becoming less of an issue. So the backup web services
+in their model have a very low chance of getting jobs, especially the ones further in chain, which is huge waste of web services
+capabilities.
+
+    \section{Cooperative Game Theory in Multiagent Systems}\label{sec:CGTMS}
+
+        \subsection{Cooperative Game Thoery}\label{sec:BRWS}
+
+        \subsection{Motivating Example}\label{sec:CWSDefinition}
+
+        One the closest examples of cooperative situations, for our service model is \emph{Single landowner and landless workers} example. 
+        This example was introduced in \cite{GVK369342747} and represents the \emph{landowner} entity which is providing jobs and \emph{landless workers} who cannot do anything by themselves and need to work with a landowner to gain some income.
+
+        Suppose that the land is owned by a single person, the \emph{landowner}. We refer to the other people as \emph{workers}. In this case we have the following game model:
+
+        \begin{itemize}
+        \item \emph{Players} The landowner and the $m$ workers.
+        \item \emph{Actions} A coalition consisting solely of workers has a single action in which no member receibes any output.
+The set of actions of a coalition $S$ consisting of the landowner and $k$ workers is the set of all $S$-allocations of the output $f(k+1)$ among the members of $S$.
+        \item \emph{Preferences} Each player's preferences are represented by the amount of output he obtains.
+        \end{itemize}
+
+        \subsection{Cooperative Games in Service Oriented Computing}\label{sec:CWSArchitecture}
+
+        \subsection{Representation and Complexity issues}\label{sec:CWSArchitecture}
+
+        \subsection{Related Work}\label{sec:CGTMSRelatedWork}
+
+Cooperative game theory provides a set of mathematical and optimization tools for multi-agent environments.
+These tools have been utilized in communication networks and service oriented computing literature, where nodes as rational agents try to reason strategically and maximise their benefit.
 

### 2013-11-05 proposal/proposal/chapter5.tex
Changes

@@
 
-As future work, we would like to perform more analytical and
-theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the
-characteristic function in web service applications. From web service perspective, the
-work can be extended to consider web service compositions where a
-group of web services having different set of skills cooperate to
-perform composite tasks. Also bargaining theory from cooperating
-game theory concepts can be used to help web services resolve the
-instability and unfairness issues by side payments.
+%As future work, we would like to perform more analytical and
+%theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the
+%characteristic function in web service applications. From web service perspective, the
+%work can be extended to consider web service compositions where a
+%group of web services having different set of skills cooperate to
+%perform composite tasks. Also bargaining theory from cooperating
+%game theory concepts can be used to help web services resolve the
+%instability and unfairness issues by side payments.
 
@@
 
-\par text text
+\indent The future goals in this PhD research work mainly consists of:
+
+\begin{itemize}
+\item Analysing other cooperative solution concepts such as Kernel and Nucleolus where payoff division is guaranteed to exist but may have optimal results.
+\item Applying Weighted Voting Games (WCG) type of valuation function in our scenarios, Developing a multiple weighted algorithm to find best coalition structures satisfying different weights on each community.
+\item Implementing Q-learning and reinforcement learning technique and also a tic-tac-toe based repeated game technique for individual Web Service decision making process, in long term and repeated game scenarios.
+\item Developing a community membership algorithm technique for our agents in "incomplete information" settings.
+\end{itemize}
+Answering these questions is undoubtedly complex. Therefore, we do not expect a comprehensive answer to all these questions.
 
@@
                 \begin{center}
-                \includegraphics[width=16cm, height=22cm]{Figures/timetable.eps}\label{Timetable}
+                \includegraphics[width=16cm, height=22cm]{timeline/timetable.pdf}\label{Timetable}
                 \caption{Research milestones and time line}

### 2013-11-06 proposal/proposal/chapter5.tex
Changes

@@
 \item Implementing Q-learning and reinforcement learning technique and also a tic-tac-toe based repeated game technique for individual Web Service decision making process, in long term and repeated game scenarios.
+\item Developing an approximation algorithm for shapely value payoff distribution vector in community of service setting.    
 \item Developing a community membership algorithm technique for our agents in "incomplete information" settings.
+\item Developing an open source, Java based Tool, with UI for solving Core and Shapely solution concepts based on different input valuation functions.
 \end{itemize}
-Answering these questions is undoubtedly complex. Therefore, we do not expect a comprehensive answer to all these questions.
 

### 2013-11-06 proposal/proposal/chapter2.tex
Changes

@@
 
+In this chapter, we briefly review web services, then we introduce the concept of communities of web services, their architecture and applications and the benefits of forming communities.
+Then we discuss the cooperative game theory concepts used throughout our research work.
+Finally, we discuss the relevant related work on web service communities and games in service oriented computing literature.
+
     \section{Community of Web Services}\label{sec:CommunityWS}
+    In this section, we discuss the concept of communities of web services, and we discuss the architecture and operations of community members.
 
-        \subsection{Web Services}\label{sec:BRWS}
+        \subsection{Web Services}\label{sec:CWSWebServices}
+        Over the past years, online services have become part of standard daily life of people around the globe. Many applications these days rely on 
+        web services from different providers to function. Most modern computer applications, specially 
+        mobile and tablet applications which have limited storage and processing power
+        are merely just an interface aggregating different information from online service providers.
+        Examples are vast, weather forecasting, ticket selling, local maps and places search, shopping apps, almost all rely on
+        robust web service providers.
+
+        The World Wide Web Consortium (W3C) defines web services as follows: "software
+        system designed to support interpretable machine-to-machine interaction over a network.
+        It has an interface described in a machine-processable format (specifically WSDL). Other
+        systems interact with the web service in a manner prescribed by its description using
+        SOAP messages, typically conveyed using HTTP with XML serialization in conjunction
+        with other Web-related standards". When developers declare a new web service, it will
+        be discovered based on its description that fully describes the service. Developers also
+        have to declare a public interface and a readable documentation to help other developers
+        when integrating different services \cite{w3cwsdl}. Nowadays Web API standards which do not 
+        require XML-based web service protocols like SOAP and WSDL are also emerging. They are also called 
+        REST (representational state transfer) services which are moving towards simpler communication protocols.
+        They are not restricted to XML formats, recently JSON, a human readable and simpler format is becoming popular among online service providers.
+
+        We are not going to delve into engineering details of online web service implementation and its protocols in this proposal. 
+        We consider the service, web services provide as a request-response operation, where they receive a message specifying a question, 
+        based on this message they generate a response, satisfying end users' need. Service providers usually charge end users for services they provide,
+        gaining profit in the process. For example Google has listed their pricing and plans for wide range of services they provide
+        on their web service console page\footnote{https://code.google.com/apis/console}.
+
+        In our research work, we abstract web services as rational entities\footnote{The term 
+        rational is used here in the sense that web services are utility
+        maximizers} providing services to end users. They aim to maximize
+        their individual income by receiving enough requests from end
+        users. In order to increase their revenue, web services seek for
+        more tasks if they have the capacity and throughput to do so. Web
+        services can join communities to have better efficiency by
+        collaborating with others, to have access to higher market share,
+        and to have opportunity of receiving a bigger task pool from end
+        users. Also the high reliance on web services, has increased quality expectations from end users.
+        Communities of web services can provide higher performance, reliability, fail recovery for end users.
 
         \subsection{Definition}\label{sec:CWSDefinition}
+        Community in dictionary definition refers to "the condition of sharing or having certain attitudes and interests in common" or "a group of people living in the same place or having a particular characteristic in common".
+In \cite{DBLP:journals/internet/BenatallahSD03, Zeng:2003:QDW:775152.775211} introduce community of web services as collection of cooperative web services with a common service and functionality but different QoS metrics.
+Therefore $communities$ are differentiated from $composition$ type of web service cooperation in which web services with different functionalities work together to generate a new service provider with composite functionality.
 
@@
 
-        Suppose that the land is owned by a single person, the \emph{landowner}. We refer to the other people as \emph{workers}. In this case we have the following game model:
-
-        \begin{itemize}
-        \item \emph{Players} The landowner and the $m$ workers.
-        \item \emph{Actions} A coalition consisting solely of workers has a single action in which no member receibes any output.
-The set of actions of a coalition $S$ consisting of the landowner and $k$ workers is the set of all $S$-allocations of the output $f(k+1)$ among the members of $S$.
-        \item \emph{Preferences} Each player's preferences are represented by the amount of output he obtains.
-        \end{itemize}
+        In this game, land is owned by a single person, the \emph{landowner}.
+We refer to the other people as \emph{workers}.
+In this case we have a game there the set of players are the landowner and the $m$ workers, possible actions for coalitions with only workers would be distributing the zero output for all where no member receives any output.
+The set of actions of a coalition $S$ consisting of the landowner and $k$ workers would be the set of all $S$-allocations of the output $f(k+1)$ among the members of $S$.
+The preference of each player would be the amount of out she obtains.
 

### 2013-11-07 proposal/proposal/chapter2.tex
changes

@@
 
-        \subsection{Definition}\label{sec:CWSDefinition}
+        \subsection{Web Service Communities}\label{sec:CWSDefinition}
         Community in dictionary definition refers to "the condition of sharing or having certain attitudes and interests in common" or "a group of people living in the same place or having a particular characteristic in common".
@@
 
-        \subsection{Architecture}\label{sec:CWSArchitecture}
+        Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09} proposed the an architecture
+        utilizing \emph{Contract-Net} protocol for engineering community of web services.
+        This architecture has been further developed in \cite{conf/IEEEscc/BenharrefSBB11, conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11, CSTintercommunity}.
+        Community of web services have two major roles for members of a community, the master and slave web service.
+        Master web services lead communities and are responsible for community and membership management of the community, they try to invite and and convince web services to join the
+        community. They can attract new web services to their communities by awarding them more payoff. They also can eject some web services from the community improving the
+        community and individual member satisfaction, and overall community reputation.
 
-        \subsection{Operations}\label{sec:CWSOperations}
+        \begin{figure}
+            \begin{center}
+            \includegraphics[width=16cm]{Figures/wsarch.eps}\label{wsarch}
+            \caption{Communities of Web Services Architecture as Proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}}
+            \end{center}
+        \end{figure}
 
-            \subsubsection{Community Development}\label{sec:CWSCommunityDev}
+        Figure \ref{wsarch} depicts the basic architecture of communities of web services. The main components of the architecture are: 1) the providers of web services,
+        2) UDDI registries and 3) communities of web services.
+Communities abstract the same model of defining, announcing and invoking of web services.
+They also adopt the same protocols that standard web services use with UDDI registries.
+UDDI is a platform-independent XML based registry list which facilitates worldwide web service discovery.
 
-            \subsubsection{Web Service Attraction and Retention}\label{sec:CWSAttraction}
+        The master web service is responsible with communication with web service providers and discovery registries. It it responsible for task distribution, web service selection,
+        community management, maintaining a healthy set of web services satisfying end users requests with high QoS. In communities, the masters web services can be
+        dedicated web services playing the master role during the entire time of being in the community. This master web service is independently developed and never
+        participates in any composition. The master web services can also be chosen out of normal web services already inside the community \cite{DBLP:journals/ijebr/MaamarSTBB09}.
 
-            \subsubsection{Web Service Selection}\label{sec:CWSSelection}
+    \section{Cooperative Game Theory in Multi-agent Systems}\label{sec:CGTMS}
 
-        \subsection{Related Work}\label{sec:BRRelatedWork}
+        \subsection{Cooperative Game Thoery}\label{sec:BRWS}
+
+        \subsection{Motivating Example}\label{sec:CWSDefinition}
+
+        An example which has closely resembles our community service model is the \emph{Single landowner and landless workers} example.
+        This example was introduced in \cite{GVK369342747} and represents the \emph{landowner} entity which is providing jobs and \emph{landless workers} who cannot do anything by themselves and need to work with a landowner to gain some income.
+
+        In this game, land is owned by a single person, the \emph{landowner}.
+We refer to the other people as \emph{workers}.
+In this case we have a game there the set of players are the landowner and the $m$ workers, possible actions for coalitions with only workers would be distributing the zero output for all where no member receives any output.
+The set of actions of a coalition $S$ consisting of the landowner and $k$ workers would be the set of all $S$-allocations of the output $f(k+1)$ among the members of $S$.
+The preference of each player would be the amount of out she obtains.
+
+        \subsection{Cooperative Games in Service Oriented Computing}\label{sec:CWSArchitecture}
+
+        \subsection{Representation and Complexity issues}\label{sec:CWSArchitecture}
+
+    \section{Related Work}\label{sec:BRRelatedWork}
 
@@
 They defined web service community as collection of web services providing same functionality however with different quality metrics.
+
+        Medjahed and Boubuettaya \cite{journals/dpd/MedjahedB05} have proposed a framework and a community builder mechanism which uses semantic analysis, providing an ontological organization of web services having same domain of interest.
+The community builder would suggest web services having similar operations with any community to join the community, or form their own communities in case the semantic analysis cannot find any community with close enough operations and service types.
 
@@
 
-    \section{Cooperative Game Theory in Multiagent Systems}\label{sec:CGTMS}
-
-        \subsection{Cooperative Game Thoery}\label{sec:BRWS}
-
-        \subsection{Motivating Example}\label{sec:CWSDefinition}
-
-        One the closest examples of cooperative situations, for our service model is \emph{Single landowner and landless workers} example. 
-        This example was introduced in \cite{GVK369342747} and represents the \emph{landowner} entity which is providing jobs and \emph{landless workers} who cannot do anything by themselves and need to work with a landowner to gain some income.
-
-        In this game, land is owned by a single person, the \emph{landowner}.
-We refer to the other people as \emph{workers}.
-In this case we have a game there the set of players are the landowner and the $m$ workers, possible actions for coalitions with only workers would be distributing the zero output for all where no member receives any output.
-The set of actions of a coalition $S$ consisting of the landowner and $k$ workers would be the set of all $S$-allocations of the output $f(k+1)$ among the members of $S$.
-The preference of each player would be the amount of out she obtains.
-
-        \subsection{Cooperative Games in Service Oriented Computing}\label{sec:CWSArchitecture}
-
-        \subsection{Representation and Complexity issues}\label{sec:CWSArchitecture}
-
-        \subsection{Related Work}\label{sec:CGTMSRelatedWork}
-
 Cooperative game theory provides a set of mathematical and optimization tools for multi-agent environments.

### 2013-11-07 proposal/proposal/chapter1.tex
Changes
changes

@@
 \section{Research outline}\label{sec:outline}
-The rest of the paper is organized as follows: In Section~\ref{sec:Argumentation}
-
-%****************************************** END INTRODUCTION****************************************
+The rest of the paper is organized as follows: We present in Chapter~\ref{sec:MAS} the background 
+needed for our research along with the relevant related work. Chapter 3 provides the problem statement and presents our solution model in two 
+different scenarios with some primitive results. Finally in Chapter 4, we present our conclusion, future plan, and the timetable of our research.

### 2013-11-07 proposal/proposal/chapter2.tex
changes

@@
             \begin{center}
-            \includegraphics[width=16cm]{Figures/wsarch.eps}\label{wsarch}
+%            \includegraphics[width=16cm]{Figures/wsarch.eps}\label{wsarch}
+            \includegraphics[width=16cm]{Figures/community.eps}\label{wsarch}
             \caption{Communities of Web Services Architecture as Proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}}
@@
 
-    \section{Cooperative Game Theory in Multi-agent Systems}\label{sec:CGTMS}
+    \section{Cooperative Game Theory and Multi-agent Systems}\label{sec:CGTMS}
 
-        \subsection{Cooperative Game Thoery}\label{sec:BRWS}
+%        Cooperative game theory provides a set of mathematical and optimization tools for multi-agent environments.
+These tools have been utilized in communication networks and service oriented computing literature, where nodes as rational agents try to reason strategically and maximise their benefit.
 
-        \subsection{Motivating Example}\label{sec:CWSDefinition}
+        Cooperative game is a branch of game theory that studies
+        strategies of self-interested entities or agents in a setting
+        where those agents can increase their payoff by binding agreements
+        and cooperating in groups. We let $N$ be a set of players. Any
+        subset $S$ of $N$ can form a group called $coalition$. A
+        \emph{coalitional game} is a pair $G = (N, v)$, where $v$ is called
+        a \emph{characteristic function} $v: 2^N \to \mathbb{R}$, mapping the set of players of the
+        coalition to a real number $v(S)$, the worth of $S$. This number
+        usually represents the output or payoff or again the performance
+        of these players working together as coalition.  If a coalition
+        $S$ is formed, then it can divide its worth, $v(S)$ in any
+        possible way among its members. The payoff vector $x \in
+        \mathbb{R}^S$ is the amount of payoff being distributed among the
+        members of the coalition $S$. The payoff vector satisfies two
+        conditions:
+
+        \begin{itemize}
+            \item $x_i \geq 0$ for all $i \in N$, and
+            \item $\sum_{i \in S} x_i \leq v(S)$
+        \end{itemize}
+
+        The second criteria is called the \emph{feasibility} condition,
+        according to which, the payoff for each agent cannot be more than
+        the coalition total gain. A payoff vector is also \emph{efficient}
+        if the payoff obtained by a coalition is distributed amongst the
+        coalition members: $\sum_{i \in S} x_i = v(S)$. This definition of
+        the characteristic function works in \emph{transferable utility}
+        (TU) settings, where utility (i.e., payoff) is transferable from
+        one player to another, or in other words, players have common
+        currency and a unit of income that is worth the same for all players
+        \cite{myerson1991game}.
+
+        When dealing with cooperative games, two issues need to be
+        addressed:\\ 1. Which coalitions among all possible coalitions to form? \\
+        2. How to reward each member when a task is completed?\\
+        %
+        The following sections help address these two issues.
+
+        \subsection{Cooperative Game Concepts}
+
+            {\bf Definition 1 (Shapley value)} Given a cooperative game $(N,
+            v)$, the \emph{Shapley value} of player $i$ is given
+            by\cite{shapley_value}:
+            \begin{equation}\label{eq:shapley}
+            \phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} }
+            \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))
+            \end{equation}
+
+            \emph{Shapley value} is a unique and fair solution concept for
+            payoff distribution among the members of the coalition. It
+            basically rewards members with the amount of marginal contribution
+            they have to the coalition.
+
+            %\subsubsection{Core}
+
+            {\bf Definition 2 (Core)} A payoff vector $x$ is in the $core$ of
+            a coalitional game $(N, v)$ if and only if:
+            \begin{equation}\label{eq:core}
+            \forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S)
+            \end{equation}
+
+            The core is basically a set of payoff vectors where no subset of
+            players $S^\prime$ could gain more than their current payoff by
+            deviating and making their own coalition $\sum_{i \in S^\prime}
+            x_i \geq v(S^\prime)$. The sum of payoffs of the players in any
+            sub-coalition $S$ is at least as large as the amount that these
+            players could earn by forming a coalition by their own. In a
+            sense, it is analogue to Nash equilibrium, except that core is
+            about deviations from groups of entities. The core is the
+            strongest and most popular solution concept in cooperative game
+            theory. However, its computation is a combinatorial problem and
+            becomes intractable as the number of players increases. The core
+            of some real-world problem games may be empty, which means having
+            the characteristic function of the game $(N,v)$, there might be no
+            possible distribution of payoff assuring stability of subgroups.
+
+            {\bf Definition 3 (Convex cooperative games)} A game $(N,v)$ with
+            characteristic function $v(S)$ is convex if:
+            \begin{equation}\label{eq:convex}
+            v(S) + v(T) \leq v(S \cup T) + v (S \cap T), \forall S,T \subseteq
+            N.
+            \end{equation}
+
+            According to a classic result by Shapley \cite{S1971cores}, convex
+            games always have a non-empty core. We will use a variation of
+            convexity condition in our algorithm to check whether our
+            coalitions are stable.
+
+            \subsubsection*{$\epsilon$-core}\label{s:epsilon}
+            %\emph{$\epsilon$-Core:}
+            %\\
+            When the \emph{core} set of a game is empty, it means no coalition
+            of players can gain anything by deviating. An outcome would be
+            unstable if a coalition can benefit even by a small amount from
+            deviating, which is a strong requirement. In fact, in some
+            situations, deviations can be costly, or players may have loyalty
+            to their coalitions, or even it can be computationally intractable
+            to find those small benefits. It would only make sense for a
+            coalition to deviate if the gain from a deviation exceeds the cost
+            of performing the deviation. \emph{$\epsilon$-core} relaxes the
+            notion of the core, and only requires that no coalition would
+            benefit significantly, or within a constant amount($\epsilon$) by
+            deviating (see Equation \ref{eq:core}).
+
+            \begin{equation}\label{eq:core2}
+            \forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
+            \end{equation}
+
+            \subsubsection*{Coalition Structure Formation}\label{sec:coalition}
+
+            Coalition structure formation is the problem of finding the best
+            partition of web services into teams. In these settings, the
+            performance of an individual service is less important than the
+            \emph{social welfare} of the whole system, which is the sum of the
+            values of all teams. Having the game $(N,v)$, a coalition
+            structure $(CS)$ is \emph{socially optimal} if $CS$ belongs to set
+            $\operatorname*{arg\,max}_{CS} v(CS)$ where $v(CS)$ is the sum of
+            the values of all coalitions inside $CS$. $v(CS) = \sum_{C \in
+            CS}v(C)$.
+            %The outcome of a characteristic function game in coalition structure settings, consists of two parts; first a disjoint partition of players (agents) into coalitions, called a \emph{coalition structure} (CS) and second a \emph{payoff vector} as mentioned in cooperative game solution concepts, which distributes the value of each coalition among its members.
+
+        \subsection{Examples on Cooperative Games}\label{sec:CWSDefinition}
 
@@
 
-        \subsection{Cooperative Games in Service Oriented Computing}\label{sec:CWSArchitecture}
+        In this game the action $a_{N}$ of the grand coalition in which the landowner obtains all the output $f$(n)
+        is in the core: all coalitions that can produce any output include the landowner, and none of these
+        coalitions has any actions that makes her better off than she is in $a_{N}$.
+
+        For any value of n The core contains actions in which the workers receive some output. 
+        The workers need the landowner to produce any output, but the landowner
+        also needs the workers to produce more than $f$(1), so stable actions of the grand coalition exist in which the
+        workers receive some output. Take the landowner to be player 1, and consider the action $a_{N}$ of the grand
+        coalition in which each player $i$ obtains the output $x_{i}$, where $x_{1}+...+x_{n}=f(n)$. Under what conditions
+        on  $(x_{1},..,x_{n})$ is $a_{N}$ in the core? Because of my assumption about the shape of the function $f$, the
+        coalitions most capable of profitably deviating from $a_{N}$ consist of the landowner and every worker but one.
+         Such a coalition can, by itself, produce $f(n-1)$, and it may distribute this output in any way among its members.
+         Thus for a deviation by such a coalition not to be profitable, the sum of $x_{i}$ and any collection of $(n-2)$ other
+          $x'_{i}$s must be at least $f(n-1)$. That is, $(x_{1}+...+x_{n})-x_{i}\geq f(n-1)$ for every $j=2,..,n$. Because
+          $x_{1}+...+x_{n}=f(n)$, we conclude that $x_{i}\leq f(n)-f(n-1)$ for every player $j$ with $J\geq 2$ (i.e. every worker).
+          That is, if $a_{N}$ is in the core then $0\leq x_{j}\leq f(n)-f(n-1)$ for every player $J\geq 2$. In fact, every such action
+          is in the core, as you are asked to verify in the following exercise.
+
+%          Core of landowner-worker game: Check that no coalition can improve upon any action of the grand
+%          coalition in which the output received by every worker is nonnegative and at most $f(n)-f(n-1)$. (Use the fact that
+%          the form of $f$ implies that $f(n)-f(k)\geq (n-k)(f(n)-f(n-1))$ for every $k\leq n$.)
+
+%          We conclude that the core of the game is the set of all actions of the grand coalition in which the output $x_{i}$
+%          obtained by each worker $i$ satisfies $0\leq x-{1}\leq f(n)-f(n-1)$ and the output obtained by the landowner is the
+%          difference between $f(n)$ and the sum of the worker's shares. In economics jargon, $f(n)-f(n-1)$ is a worker's
+%          ``marginal product". Thus in any action in the core, each worker obtains at most her marginal product.
+
+%          The worker's shares of output are driven down to at most $f(n)-f(n-1)$ by competition between coalitions consisting
+%          of the landowner and workers, in cahoots with the landowner, can deviate and increase their share of output. That is,
+%          each worker's share of output is limited by her comrade's attempts to obtain more output.
+
+%          The fact that each worker's share of output is held down by interworker competition suggests that the workers might
+%          be better off if they were to agree not to join deviating coalitions \emph{except as a group}. You are  asked to check
+%          this idea in the following exercise.
+
+        %\subsection{Cooperative Games in Service Oriented Computing}\label{sec:CWSArchitecture}
 
         \subsection{Representation and Complexity issues}\label{sec:CWSArchitecture}
+
+        Shapely value is the unique "fair" way to distribute the total surplus generated by the coalition, among all the players.
+        The nature of the Shapley value is combinatorial, as all possible orderings to form a
+        coalition needs to be considered. This computational complexity can sometimes be
+        an advantage as agents cannot benefit from manipulation. For example, it is NP-complete
+        to determine whether for a bunch of agents to collude and make their own coalition and guarantee
+        an increase in payoff of all participants\cite{conf/aaai/YokooCSOI05}. 
+        There are some representations that allow to compute the Shapley value efficiently by reducing the input size of the problem.
+        One example is \emph{Induced subgraph games}
+        which was introduced by Deng and Papadimitriou \cite{Deng94}. In this representation, players are represented by graph nodes, and
+        their valuation function should be sum of weights all edges between the node and all its neighbors. It is a succinct representation, using
+        an adjacency matrix, which need only $O(n^2)$ space to store all the input, which is a big reduction from $O(2^n)$.
+        if weights of all the edges in graph are all positive, the Shapley value can be computed in $O(n^2)$ time. 
+        However, this representation is not complete, some games cannot be represented by a induced subgraph game\cite{conf/aaai/YokooCSOI05}.
+
+        Ketchpel introduces the Bilateral Shapley Value (BSV)\cite{conf/aaai/Ketchpel94a} for coalition games with general valaution functions.
+        It reduces the combinatorial complexity of the computation of the Shapley value, breaking the community to multiple disjoint set. 
+        With backtracking and dynamic programming like methods, they merge and store the marginal contribution of disjoint coalitions,
+        reducing the overall complexity of the algorithm.
+
+        In order to make cooperative game concepts practical in real world application, we have proposed an approximation multi-layer 
+        algorithm useful for service orinted computing settings. Our excrements illustrate, these algorithms can provide 
+        applicable and near optimal solutions for real world applications.
 
@@
 
-Cooperative game theory provides a set of mathematical and optimization tools for multi-agent environments.
-These tools have been utilized in communication networks and service oriented computing literature, where nodes as rational agents try to reason strategically and maximise their benefit.
+        % THIS IS REPEATED
+        In this research work, we use game theory to
+        propose a cooperative game model for the aggregation of web
+        services within communities. The solution concepts of our
+        cooperative game seeks to find efficient ways of forming
+        coalitions (teams) of web services so that they can maximize their
+        gain and payoff, and distribute the gain in a fair way among all
+        the web services. Achieving Fairness when the gain is distributed
+        among the community members is the main factor to keep the
+        coalition stable as no web service will expect to gain better by
+        deviating for the community. In other words, the coalition is made
+        efficient if all the members are satisfied. We first propose a
+        representation function for communities of web services based on
+        their QoS attributes. By using this function, we can evaluate the
+        $worth$ of each community of web services. When facing new
+        membership requests, a typical community master checks whether the
+        new coalition having the old and new set of web services will keep
+        the community stable or not. The community master will reject the
+        membership requests if it finds out that the new coalition would
+        be unstable, preventing $any$ subset of web services from gaining
+        significantly more by deviating from the community and joining
+        other communities or forming new ones. The computation of
+        solutions for cooperative game theory problems is combinatorial in
+        nature and proven to be NP-complete \cite{Algorithmic}, making
+        this computation impractical in real world applications. However,
+        using the concepts of coalition stability, we propose
+        approximation algorithms running in polynomial time providing web
+        services and community masters with applicable and near-optimal
+        decision making mechanisms.
 

### 2013-11-07 proposal/proposal/chapter3.tex
changes

@@
 \end{figure*}
-
-\subsection{Cooperative Game Concepts}
-Cooperative game is a branch of game theory that studies
-strategies of self-interested entities or agents in a setting
-where those agents can increase their payoff by binding agreements
-and cooperating in groups. We let $N$ be a set of players. Any
-subset $S$ of $N$ can form a group called $coalition$. A
-\emph{coalitional game} is a pair $G = (N, v)$, where $v$ is called
-a \emph{characteristic function} $v: 2^N \to \mathbb{R}$, mapping the set of players of the
-coalition to a real number $v(S)$, the worth of $S$. This number
-usually represents the output or payoff or again the performance
-of these players working together as coalition.  If a coalition
-$S$ is formed, then it can divide its worth, $v(S)$ in any
-possible way among its members. The payoff vector $x \in
-\mathbb{R}^S$ is the amount of payoff being distributed among the
-members of the coalition $S$. The payoff vector satisfies two
-conditions:
-
-\begin{itemize}
-    \item $x_i \geq 0$ for all $i \in N$, and
-    \item $\sum_{i \in S} x_i \leq v(S)$
-\end{itemize}
-
-The second criteria is called the \emph{feasibility} condition,
-according to which, the payoff for each agent cannot be more than
-the coalition total gain. A payoff vector is also \emph{efficient}
-if the payoff obtained by a coalition is distributed amongst the
-coalition members: $\sum_{i \in S} x_i = v(S)$. This definition of
-the characteristic function works in \emph{transferable utility}
-(TU) settings, where utility (i.e., payoff) is transferable from
-one player to another, or in other words, players have common
-currency and a unit of income that is worth the same for all players
-\cite{myerson1991game}.
-
-When dealing with cooperative games, two issues need to be
-addressed:\\ 1. Which coalitions among all possible coalitions to form? \\
-2. How to reward each member when a task is completed?\\
-%
-The following definitions help address these two issues.
-
-{\bf Definition 1 (Shapley value)} Given a cooperative game $(N,
-v)$, the \emph{Shapley value} of player $i$ is given
-by\cite{shapley_value}:
-\begin{equation}\label{eq:shapley}
-\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} }
-\frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))
-\end{equation}
-
-\emph{Shapley value} is a unique and fair solution concept for
-payoff distribution among the members of the coalition. It
-basically rewards members with the amount of marginal contribution
-they have to the coalition.
-
-%\subsubsection{Core}
-
-{\bf Definition 2 (Core)} A payoff vector $x$ is in the $core$ of
-a coalitional game $(N, v)$ if and only if:
-\begin{equation}\label{eq:core}
-\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S)
-\end{equation}
-
-The core is basically a set of payoff vectors where no subset of
-players $S^\prime$ could gain more than their current payoff by
-deviating and making their own coalition $\sum_{i \in S^\prime}
-x_i \geq v(S^\prime)$. The sum of payoffs of the players in any
-sub-coalition $S$ is at least as large as the amount that these
-players could earn by forming a coalition by their own. In a
-sense, it is analogue to Nash equilibrium, except that core is
-about deviations from groups of entities. The core is the
-strongest and most popular solution concept in cooperative game
-theory. However, its computation is a combinatorial problem and
-becomes intractable as the number of players increases. The core
-of some real-world problem games may be empty, which means having
-the characteristic function of the game $(N,v)$, there might be no
-possible distribution of payoff assuring stability of subgroups.
-
-{\bf Definition 3 (Convex cooperative games)} A game $(N,v)$ with
-characteristic function $v(S)$ is convex if:
-\begin{equation}\label{eq:convex}
-v(S) + v(T) \leq v(S \cup T) + v (S \cap T), \forall S,T \subseteq
-N.
-\end{equation}
-
-According to a classic result by Shapley \cite{S1971cores}, convex
-games always have a non-empty core. We will use a variation of
-convexity condition in our algorithm to check whether our
-coalitions are stable.
-
-\subsubsection*{$\epsilon$-core}\label{s:epsilon}
-%\emph{$\epsilon$-Core:}
-%\\
-When the \emph{core} set of a game is empty, it means no coalition
-of players can gain anything by deviating. An outcome would be
-unstable if a coalition can benefit even by a small amount from
-deviating, which is a strong requirement. In fact, in some
-situations, deviations can be costly, or players may have loyalty
-to their coalitions, or even it can be computationally intractable
-to find those small benefits. It would only make sense for a
-coalition to deviate if the gain from a deviation exceeds the cost
-of performing the deviation. \emph{$\epsilon$-core} relaxes the
-notion of the core, and only requires that no coalition would
-benefit significantly, or within a constant amount($\epsilon$) by
-deviating (see Equation \ref{eq:core}).
-
-\begin{equation}\label{eq:core2}
-\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
-\end{equation}
-
-\subsubsection*{Coalition Structure Formation}\label{sec:coalition}
-
-Coalition structure formation is the problem of finding the best
-partition of web services into teams. In these settings, the
-performance of an individual service is less important than the
-\emph{social welfare} of the whole system, which is the sum of the
-values of all teams. Having the game $(N,v)$, a coalition
-structure $(CS)$ is \emph{socially optimal} if $CS$ belongs to set
-$\operatorname*{arg\,max}_{CS} v(CS)$ where $v(CS)$ is the sum of
-the values of all coalitions inside $CS$. $v(CS) = \sum_{C \in
-CS}v(C)$.
-%The outcome of a characteristic function game in coalition structure settings, consists of two parts; first a disjoint partition of players (agents) into coalitions, called a \emph{coalition structure} (CS) and second a \emph{payoff vector} as mentioned in cooperative game solution concepts, which distributes the value of each coalition among its members.
 
@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{Figures/taxtation.eps}
-\caption{Analysis of community subsiding coefficient $\lambda$ on average community size (a), cost (b), number of tasks performed (c), and average quality of service of tasks performed (d).} \label{f_taxtation}
-\end{figure}
-
-As mentioned in section \ref{s:tax} in order to help community stability, is to subside the community by a relative coefficient ($\lambda$) so the value of $\lambda v(C)$ is devided among the community members.
-We have analysed the effect of subsiding and the cost it incurs to our web service communities.
-Figure \ref{f_taxtation} shows the results.
-In this expirement we have set a community with input task rate $R_C$ of 100 and having abstract web services throuput rate $T_r$ value of a random distribution with average 10 tasks per iteration.
-Part (a) shows the community size increases in a linear fashion as ($\lambda$) increases.
-However the cost is having a slight exponential growth rate since, not only ($\lambda$) increases also the size of the community is also increasing slowly.
-Therefore subsiding can be costly for larger number of $\lambda$ value.
-Part (c) of figure \ref{f_taxtation} depicts the number of tasks done by the community per iteration.
-It is obvoius with $\lambda$ value of 1.3 which is 30\% of community valuation, the number of tasks done almost reaches the input task rate cap of 100 tasks per iteration.
-The average quality of tasks also has a slight increase since the community will be able to afford better and more web services to join the community.
-These results proves with quality metrics our agents as web services have and their collabrative worth, the increase rate of subsiding more 1.3 is not very effective and is costly to perform.
-
-\begin{figure*}[!t]
-\centerline{\includegraphics[width=6.75in]{Figures/tax_dyn.eps}}
-\caption{Analysis of community subsiding coefficient $\lambda$ having web service different stability levels of $\tau$ on average community size, number of tasks performed, and average quality of service, and average cost/income of communities.}
-\label{fig_dynamic_taxtation}
-\end{figure*}
-
-In previous experiment, we consider the scenario where all web services are stable will not leave the group and will fulfill their promised quality metrics for a good period of time.
-However, in real world scenarios of web services, this is not always the case.
-This is the reason why community would be interested in subsiding a community of larger group web services, paying a few more web services in order to keep the group reliable from end user point of view.
-In our next scenario, we have introduced the new instability variable $\tau$ from 0 to 1, 0 meaning web services having no instability issues and will perform as they claimed until the end of experiment and 1 meaning very unstable web services which will stop functioning on the first iteration of community distributing tasks.
-Figure \ref{fig_dynamic_taxtation} illustrates the results of our experiment having web services with average instability values of 0 to 0.5 and having relative subside value $\lambda$ if 1,1.3,1.6 and 2.
-The \emph{Cost / Income} charts on right column, shows having subside value of 1.3 incurs the least cost and increases the community income significantly.
-Subsiding values of 1.6 and 2 , incur a lot of cost to community and only slightly increase the community revenue.
-Also the role of subsiding is much more obvious when we have unstable web services.
-In scenarios where web services are 100\% stable, subsiding cost will hardly be compensated by community revenue.
-
-\begin{figure}[!t]
-\centering
-%\includegraphics[scale=0.6]{graph1Final+.eps}
 \includegraphics[width=3in]{Figures/s2_task_done.eps}
@@
 In our method we have more chance of fail for each web service, however with some subsiding, and hiring a few more web service they can compensate the low chance of failure of web services in our community.
-
-\section{Conclusion}\label{s:conclusion}
-
-In this paper, we proposed a cooperative game theory-based model
-for the aggregation of web services within communities. The goal
-of our services is to maximize efficiency by collaborating and
-forming stable coalitions. Our method considers stability and
-fairness for all web services within a community and offers an
-applicable mechanism for membership requests and selection of web
-services. The ultimate goal is to increase revenue by improving
-user satisfaction, which comes from the ability to perform more
-tasks with high quality. Simulation results show that our,
-polynomial in complexity, approximation algorithms provide web
-services and community owners with applicable and near-optimal
-decision making mechanisms.
-
-As future work, we would like to perform more analytical and
-theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the
-characteristic function in web service applications. From web service perspective, the
-work can be extended to consider web service compositions where a
-group of web services having different set of skills cooperate to
-perform composite tasks. Also bargaining theory from cooperating
-game theory concepts can be used to help web services resolve the
-instability and unfairness issues by side payments.

### 2013-11-08 proposal/proposal/chapter1.tex
changes

@@
 Also, we discuss our preliminary contributions.
-
-\section{Context of the research}\label{sec:context}
 
@@
 availability metric and considering price and cost values only. The community structure is based on a coordination chain,
-where a web service is assigned as a \emph{primary} web service and the community task destribution
+where a web service is assigned as a \emph{primary} web service and the community task distribution
 method, will initially invoke the primary web service and only if the primary web service is unavailable
@@
 %Answering these questions is undoubtedly complex. Therefore, we do not expect a comprehensive answer to all these questions.
+
+\section{Motivating Scenario}\label{sec:motexample}
+
+In this section, we present a scenario and demonstrate why there is a need for community of services and why it should satisfy all business models involved. 
+We first propose an example of real world scenario, focusing on user experience. Nowadays most of the computer applications, are dependant on multiple online 
+service provides, examples are vast in daily life of people nowadays, weather forecasting, ticketing services, map services, local places guides and so on. Most mobile or web applications 
+cannot independently provide these information and they rely on different online services providing these information. 
+The high competition on services, requires applications to use reliable and high quality services. 
+Because if user checks a web site or runs an application on his/her mobile, upon having downtime, or having high response delay or encountering any non satisfying quality metric, the user
+will instantly remove the application, which is a huge business concert for application providers.
+For example, if someone installs a ticketing application on mobile and the application is not using quality service providers, the user would instantly uninstall the application, which has a high negative affect on application visibility.
+Or lets say you search "Montreal Weather" on a search engine and you click on a web site which is slow (because its using a bad weather web service as source of its raw data), the user will press "back", leave the web site and try another link which has a bad Search Engine Optimization (SEO) effect for the web site, and search engines would not show that web site on search results anymore, which is a business and revenue loss for the application.
+Thus end user satisfaction is the main goal of all online providers otherwise they will lose the market to competitions very fast.
+This is the main goal of community of services, to provide higher quality, higher uptime and reliability for end users.
+To this end, community formation, should consider important QoS parameters while forming the community and during membership management.
+
+High demand on online services has created a big competition on this area.
+For example an application developer, right now needs to choose between hundreds of web services online providing local places information such as coffees, venues, shops and bars nearby a geographic position.
+It is hard for new web services to find their customers and be visible for end users amongs hundereds or thousands of other service providers, even if they provide high quality of service.
+Hence, our community of web services, provides them with the chance of joining the communities which already have established market share, and providing them with a great source of revenue, proportional to their QoS and throughput.
+However, its important for community manager to consider all parties involved, for example if market share is not big enough, bringing
+new web services, can cause revenue drop for the already residing members in community, since basically there would be not enough tasks and revenue to be shared among web services.
+This will not effect user satisfaction, but other quality web services may collude leave the community, and join another community, hurting the community stability.
+This is an important issue which has not been addressed previously in similar related works.
+On the other hand, if communities bound the number of web services exactly to the numbers satisfying their market share, in the case of failure of a web service, the reliability and availability metrics of the community could get hurt.
+This also has not been efficiently addressed in any other related work.
+In this research work, we try to propose community formation algorithms, satisfying all parties involved.
+This is a complete business model, considering end users, community managers and service providers.
 

### 2013-11-08 proposal/proposal/chapter2.tex
changes

@@
 %            \includegraphics[width=16cm]{Figures/wsarch.eps}\label{wsarch}
-            \includegraphics[width=16cm]{Figures/community.eps}\label{wsarch}
+            \includegraphics[width=16cm]{Figures/wsarch.eps}\label{wsarch}
             \caption{Communities of Web Services Architecture as Proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}}
@@
 
-        \subsection{Examples on Cooperative Games}\label{sec:CWSDefinition}
+        \subsection{Cooperative Game Examples}\label{sec:CWSDefinition}
+
+        \emph {THIS EXAMPLE IT NOT COMPLETE YET}
 
         An example which has closely resembles our community service model is the \emph{Single landowner and landless workers} example.
-        This example was introduced in \cite{GVK369342747} and represents the \emph{landowner} entity which is providing jobs and \emph{landless workers} who cannot do anything by themselves and need to work with a landowner to gain some income.
+        This example was introduced in \cite{GVK369342747} and represents the \emph{landowner} entity which is providing jobs and \emph{landless workers} who cannot do anything by themselves and need to work with a landowner to gain revenue (payoff).
 
@@
         With backtracking and dynamic programming like methods, they merge and store the marginal contribution of disjoint coalitions,
-        reducing the overall complexity of the algorithm.
+        reducing the overall complexity of the algorithm. However, the solution is still NP-Complete and BSV time and space complexity grows exponentially.
 
@@
         % THIS IS REPEATED
+        \emph {-- this is repeated --} 
         In this research work, we use game theory to

### 2013-11-12 notes/notes.tex
changes

@@
 
+\section{To add on proposal}
+
+\subsection{a good intro}
+Coalition-game thoery provides suitable analytical tools that have been widely explored in different diciplines such as economics and political sceince.
+With the recent emergence of cooperation as a new networking paradigm, coalition-game  theory started to become a central framework for modeling cooperation in wireless and communication networks.
+For instance, coalition games prove to be a very powerful tool for designing fair, robust, practical and efficient cooperation strategies in communication networks.
+
+\subsection{contractnet}
+
+Using round robin instead of contractnet, to reduce the simulation complexity. Both have identical behavoiurs.
+we dont want WS not bid if they are not working at that moment.
+
+\subsection{other}
+
+adding "`towards defingin and assessing the non-functional properties of communities of web services"' as good refrence for QoS metrics.
+
+adding a tree chart of what we cover in proposed method section.
+
+adding shapely value properties.
+
 \bibliographystyle{plain}

### 2013-11-18 proposal/proposal/chapter1.tex
chnages

@@
 
-\section{Motivations and research questions}\label{sec:motivation}
+\section{Context}\label{sec:motivation}
 
@@
 
-Most of the recent work on communities of services are either
-user-centric and focus on user satisfaction
-\cite{Chun02user-centricperformance} or system-centric and focus
-on the whole system throughput, performance and utilization. There
-are many contributions in distributed, grid, cluster and cloud
-services which are system-centric. However, in real world
-environments and applications, both users and service providers
-are self-interested agents, aiming to maximize their own profit.
-In those environments, both parties (users and services) will
-collaborate as long as they are getting more benefits and payoff.
-
-In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
-DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
-users and services to maximize their gain. A two-player
-non-cooperative game between web services and community master was
-introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this
-game-theoretic model, the strategies available to a web service
-when facing a new community are requesting to join the community,
-accepting the master's invitation to join the community, or
-refusing the invitation to join. The set of strategies for
-communities are inviting the web service or refusing the web
-service's join request. Based on their capacity, market share and
-reputation, the two players have different set of utilities over
-the strategy profiles of the game. The main limits of this game
-model are: 1) its consideration of only three quality parameters,
-while the other factors are simply ignored; and 2) the
-non-consideration of the web services already residing within the
-community. The game is only between the community master and the
-new web service, and the inputs from all the other members are
-simply ignored. The consideration of those inputs is a significant
-issue as existing web services can lose utility or payoff because
-of the new member, which can results in an unhealthy and unstable
-group. The problem comes from the fact that the existing members
-should collaborate with the new web services, so probably their
-performance as a group can suffer. Existing members may even
-deviate and try to join other communities if they are unsatisfied.
-Those considerations of forming stable and efficient coalitions
-are the main contributions of our paper.
-
-In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
-for selecting web services has been proposed. In this approach,
-the authors proposed a web service selection process that the
-community masters can use. The approach considers the efficiency
-of all the three involved parties, namely users, web services and
-communities. In this work, it is shown how the gains of these
-parties are coupled together using a linear optimization process.
-However, the optimization problem in this solution tends to
-optimize some parameters considering all web services regardless
-of their efficiency and contribution to the community's welfare.
-Moreover, there are no clear thresholds for accepting or rejecting
-new web services. The solution of the optimization problem could,
-for instance, suggest web services already residing within the
-community to increase or decrease their capacity to cover up the
-weakness of other parties in the system. However, a high
-performing web service could deviate anytime it finds itself
-unsatisfied within the community instead of adjusting its service
-parameters.
-
-In \cite{10.1109/TSC.2012.12}, a cooperative scheme among autonomous
-web services based on coalitional game theory has been introduced. They have proposed an algorithm to
-reach individually stable coalition partition for web services in order to
-maximize their efficiency. The communities choose new web services on the promise
-that it would benefit the community without decreasing any other web service's
-income. In their model, the worth of community is evaluated with high emphasis on
-availability metric and considering price and cost values only. The community structure is based on a coordination chain,
-where a web service is assigned as a \emph{primary} web service and the community task distribution
-method, will initially invoke the primary web service and only if the primary web service is unavailable
-will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to
-have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays
-with recent advancement in cloud and hardware infrastructures availability is becoming less of an issue. So the backup web services
-in their model have a very low chance of getting jobs, especially the ones further in chain, which is huge waste of web services
-capabilities.
-
-% ooooooold
-%\indent When monitoring a dialogue between two or more agents, there are many question that should be answered. In this thesis, we are interested in answering the following questions:
-%\begin{itemize}
-%\item How much are agents certain about selecting a move at each dialogue step?
-%\item How much are agents certain about their dialogues?
-%\item How good are agents in the real dialogue (i.e. the effective dialogue)?
-%\item How far are agents from the right dialogue (i.e. the best dialogue given the knowledge bases of the participants)?
-%\end{itemize}
-%Answering these questions is undoubtedly complex. Therefore, we do not expect a comprehensive answer to all these questions.
-
 \section{Motivating Scenario}\label{sec:motexample}
@@
 
-\section{Research objectives and contributions}\label{sec:contribution}
+\section{Motivation and research Questions}\label{sec:researchquestions}
 
-In this research work, we use game theory to
+Web service communities are dynamic by design \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+Web services are modeled as intelligent autonomous agents, where they can adopt a strategy maximizing their payoff at any time.
+In web service communities, a web service has its own right to determine when to join a community and when to leave a community.
+Community managers can invite or ask a web service to leave in order to maximise their profit.
+Users can simply stop sending requests to a web service which is not providing satisfactory services.
+
+Most of the recent work on communities of services are either
+user-centric and focus on user satisfaction
+\cite{Chun02user-centricperformance} or system-centric and focus
+on the whole system throughput, performance and utilization. There
+are many contributions in distributed, grid, cluster and cloud
+services which are system-centric. However, in real world
+environments and applications, both users and service providers
+are self-interested agents, aiming to maximize their own profit.
+In those environments, both parties (users and services) will
+collaborate as long as they are getting more benefits and payoff. 
+Our initial research question is:
+\emph{How can we model the community of services for the autonomous agents, in order to maximize the throughput for users, web services and community organizers involved?}
+
+In order to address this shortcoming, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
+DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
+users and services to maximize their gain. A two-player
+non-cooperative game between web services and community master was
+introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. 
+In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
+for selecting web services has been proposed. In this approach,
+the authors proposed a web service selection process that the
+community masters can use. The approach considers the efficiency
+of all the three involved parties, namely users, web services and
+communities.
+
+%The consideration of those inputs is a significant
+%issue as existing web services can lose utility or payoff because
+%of the new member, which can results in an unhealthy and unstable
+%group. The problem comes from the fact that the existing members
+%should collaborate with the new web services, so probably their
+%performance as a group can suffer. Existing members may even
+%deviate and try to join other communities if they are unsatisfied.
+%Those considerations of forming stable and efficient coalitions
+%are the main contributions of our paper.
+
+%However, a high
+%performing web service could deviate anytime it finds itself
+%unsatisfied within the community instead of adjusting its service
+%parameters.
+
+Our question we would like to explore is:
+\emph{How can we model the the fairness efficiently in communities of web services and form stable communities?}
+
+In \cite{10.1109/TSC.2012.12}, a cooperative scheme among autonomous
+web services based on coalitional game theory has been introduced. They have proposed an algorithm to
+reach individually stable coalition partition for web services in order to
+maximize their efficiency. The communities choose new web services on the promise
+that it would benefit the community without decreasing any other web service's
+income. In their model, the worth of community is evaluated with high emphasis on
+availability metric and considering price and cost values only. The community structure is based on a coordination chain,
+where a web service is assigned as a \emph{primary} web service and the community task distribution
+method, will initially invoke the primary web service and only if the primary web service is unavailable
+will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to
+have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays
+with recent advancement in cloud and hardware infrastructures availability is becoming less of an issue. So the backup web services
+in their model have a very low chance of getting jobs, especially the ones further in chain, which is huge waste of web services
+capabilities.
+
+Another research question we would like to work on is:
+\emph{How can we model the community of web services based on cooperative game theory models in a realistic and applicable way?}
+
+% ooooooold
+%\indent When monitoring a dialogue between two or more agents, there are many question that should be answered. In this thesis, we are interested in answering the following questions:
+%\begin{itemize}
+%\item How much are agents certain about selecting a move at each dialogue step?
+%\item How much are agents certain about their dialogues?
+%\item How good are agents in the real dialogue (i.e. the effective dialogue)?
+%\item How far are agents from the right dialogue (i.e. the best dialogue given the knowledge bases of the participants)?
+%\end{itemize}
+%Answering these questions is undoubtedly complex. Therefore, we do not expect a comprehensive answer to all these questions.
+
+\section{Research Objectives and contributions}\label{sec:motexample}
+
+In this research work, I will use game theory to
 propose a cooperative game model for the aggregation of web
@@
 
-\section{Research outline}\label{sec:outline}
+\indent In this proposal, I will address the problem of forming stable and efficient coalitions for maximising web services and community revenue.
+The main objectives in this proposal work are:
+\begin{itemize}
+\item To apply cooperative game theory solution concepts in order to address the problem of optimizing coalition formation for a stable community that can maximise the total payoff.
+\item To reduce the complexity of cooperative game theory solution concepts tailored to the problem model of communities of web services in order to make these solutions applicable in real world scenarios.
+\item To increase community stability by subsiding and taxation methods.
+\item To validate the proposed methods by simulation and comparing our results with other similar works.
+\end{itemize}
+
+\section{Proposal Organization}\label{sec:outline}
 The rest of the paper is organized as follows: We present in Chapter~\ref{sec:MAS} the background
-needed for our research along with the relevant related work. Chapter 3 provides the problem statement and presents our solution model in two
+needed for our research along with the relevant related work. Chapter~\ref{sec:coalitionformationws} provides the problem statement and presents our solution model in two
 different scenarios with some primitive results. Finally in Chapter 4, we present our conclusion, future plan, and the timetable of our research.

### 2013-11-20 proposal/proposal/chapter1.tex
changes

@@
 
-In this section, we present a scenario and demonstrate why there is a need for community of services and why it should satisfy all business models involved.
-We first propose an example of real world scenario, focusing on user experience. Nowadays most of the computer applications, are dependant on multiple online
-service provides, examples are vast in daily life of people nowadays, weather forecasting, ticketing services, map services, local places guides and so on. Most mobile or web applications
-cannot independently provide these information and they rely on different online services providing these information.
-The high competition on services, requires applications to use reliable and high quality services.
-Because if user checks a web site or runs an application on his/her mobile, upon having downtime, or having high response delay or encountering any non satisfying quality metric, the user
-will instantly remove the application, which is a huge business concert for application providers.
-For example, if someone installs a ticketing application on mobile and the application is not using quality service providers, the user would instantly uninstall the application, which has a high negative affect on application visibility.
-Or lets say you search "Montreal Weather" on a search engine and you click on a web site which is slow (because its using a bad weather web service as source of its raw data), the user will press "back", leave the web site and try another link which has a bad Search Engine Optimization (SEO) effect for the web site, and search engines would not show that web site on search results anymore, which is a business and revenue loss for the application.
-Thus end user satisfaction is the main goal of all online providers otherwise they will lose the market to competitions very fast.
-This is the main goal of community of services, to provide higher quality, higher uptime and reliability for end users.
-To this end, community formation, should consider important QoS parameters while forming the community and during membership management.
+In this section, we present a scenario and demonstrate why there is a need for a community of services and why it should satisfy all business models involved.
+We first propose an example of a real world scenario, focusing on user experience.
+Nowadays most of the computer applications are dependent on multiple online service provides, there are a plethora of options available to people in today's society, weather forecasting, ticketing services, map services, local places guides and so on.
+Most mobile or web applications cannot independently provide this information and they rely on different online services to provide this information.
+The high competition within the services industry requires applications to use reliable and high quality online service providers.
+
+If the user were to check a web site or run an application on his/her mobile upon having downtime, or having high response delay or encountering any non-satisfying quality metric, the user will instantly remove the application, which is a huge business concern for application providers.
+For example, if someone installs a ticketing application on mobile and the application is not using high quality service providers, the user would instantly uninstall the application, which has an extremely negative impact on the visibility of the application.
+Or let's say you search "Montreal Weather" on a search engine and you click on a web site which is slow because it is using a bad weather web service as source of its raw data, the user will leave the web site and try another link from search results, which has a bad Search Engine Optimization (SEO) effect for the web site, and search engines would not show that web site on search results anymore, which is a business and revenue loss for the application.
+Thus end user satisfaction is the main goal for online providers otherwise they will lose the market to competitors very quickly.
+Communities of web service, by providing services with higher quality, higher uptime and reliability for end users, aim to reach this goal.
+To this end, community management decisions should factor in important QoS parameters while forming the community and during membership management.
 
 High demand on online services has created a big competition on this area.
-For example an application developer, right now needs to choose between hundreds of web services online providing local places information such as coffees, venues, shops and bars nearby a geographic position.
-It is hard for new web services to find their customers and be visible for end users amongs hundereds or thousands of other service providers, even if they provide high quality of service.
-Hence, our community of web services, provides them with the chance of joining the communities which already have established market share, and providing them with a great source of revenue, proportional to their QoS and throughput.
-However, its important for community manager to consider all parties involved, for example if market share is not big enough, bringing
-new web services, can cause revenue drop for the already residing members in community, since basically there would be not enough tasks and revenue to be shared among web services.
-This will not effect user satisfaction, but other quality web services may collude leave the community, and join another community, hurting the community stability.
+For example an application developer right now needs to choose between hundreds of web services online, providing local places information such as coffees, venues, shops and bars nearby a geographic position.
+It is hard for new web services to find their customers and be visible for end users amongst hundreds or thousands of other service providers, even if they provide a high quality of service.
+Hence, community of web services provides them with the chance of joining the communities which already have established market share, and providing them with a great source of revenue, proportional to their QoS and throughput.
+However, it is important for a community manager to consider all parties involved, for example if market share is not big enough, bringing new web services, can cause revenue drop for the already residing members in community,   since basically there would be not enough tasks and revenue to be shared among web services.
+This will not affect user satisfaction, but other quality web services may collude, leave, and join another community, hurting the community stability.
 This is an important issue which has not been addressed previously in similar related works.
 On the other hand, if communities bound the number of web services exactly to the numbers satisfying their market share, in the case of failure of a web service, the reliability and availability metrics of the community could get hurt.
-This also has not been efficiently addressed in any other related work.
+This has also not been efficiently addressed in any other related work.
 In this research work, we try to propose community formation algorithms, satisfying all parties involved.
@@
 Web service communities are dynamic by design \cite{DBLP:journals/ijebr/MaamarSTBB09}.
-Web services are modeled as intelligent autonomous agents, where they can adopt a strategy maximizing their payoff at any time.
-In web service communities, a web service has its own right to determine when to join a community and when to leave a community.
+In these communities, web services are modeled as intelligent autonomous agents, where they can adopt a strategy maximizing their payoff at any time.
+A web service has its own right to determine when to join a community and when to leave a community.
 Community managers can invite or ask a web service to leave in order to maximise their profit.
 Users can simply stop sending requests to a web service which is not providing satisfactory services.
-
+Thus its important to consider all parties involved in community management decision making process.
 Most of the recent work on communities of services are either
@@
 communities.
+The issue with these solution concepts is that they consider community as whole and model it as one entity in their formulations.
+A community master decides on behalf of an aggregated function of parameters of all the web services in the community.
+This can hurt the overall revenue for some individual web services, or even a subset of web services.
+They can collude and form their own community and gain more, instead of having to adjust and share their resources to other members.
+Another important issue which needs to be considered is community stability.
+In community of web services, the web services and community organizers collaborate to perform tasks.
+Having jointly completed a task and generated revenue, they need to agree on some reasonable method of dividing profits (or tasks) among themselves.
+This is an key issue for stability of communities which has not had enough attention in related work.
+If the revenue sharing mechanism is not fair enough for any subset of web services working in the community, as profit maximizing agents, they would just deviate and make their own group inorder to gain more and fair share of profit.
+So an important research question that we would like to address is:
+\emph{How can we model the the fairness, efficiently in communities of web services and form stable communities?}
 
@@
 %parameters.
-
-Our question we would like to explore is:
-\emph{How can we model the the fairness efficiently in communities of web services and form stable communities?}
 
@@
 Another research question we would like to work on is:
-\emph{How can we model the community of web services based on cooperative game theory models in a realistic and applicable way?}
+\emph{How can we model the community of web services based on cooperative game theory models in a realistic, applicable and practical way?}
 
@@
 \section{Proposal Organization}\label{sec:outline}
-The rest of the paper is organized as follows: We present in Chapter~\ref{sec:MAS} the background
+The rest of the proposal is organized as follows: We present in Chapter~\ref{sec:MAS} the background
 needed for our research along with the relevant related work. Chapter~\ref{sec:coalitionformationws} provides the problem statement and presents our solution model in two
-different scenarios with some primitive results. Finally in Chapter 4, we present our conclusion, future plan, and the timetable of our research.
+different scenarios with some primitive results. Finally in Chapter~\ref{sec:conclusionfuturework}, we present our conclusion, future plan, and the timetable of our research.

### 2013-11-20 proposal/proposal/chapter3.tex
changes

@@
 
-\chapter{Coalition Formation for Autonomous Web Services}
+\chapter{Coalition Formation for Autonomous Web Services}\label{sec:coalitionformationws}
 
@@
 In this section, we discuss the parameters and preliminary
-concepts that we use in the rest of the paper.
+concepts that we use in the rest of the proposal.
 
@@
 and to have opportunity of receiving a bigger task pool from end
-users. Throughout this paper, in
+users. Throughout this proposal, in
 our equations, we refer to web services as $ws$ and to the set of

### 2013-11-20 proposal/proposal/chapter5.tex
changes

@@
-\setcounter{chapter}{4}
-\chapter{Conclusion and Future Work}
+\setcounter{chapter}{3}
+\chapter{Conclusion and Future Work}\label{sec:conclusionfuturework}
 In this chapter, we describe the phases of our plan for exploring the research challenges and investigating the research issues identified in Chapter 4.
@@
                 \begin{center}
-                \includegraphics[width=16cm, height=22cm]{timeline/timetable.pdf}\label{Timetable}
-                \caption{Research milestones and time line}
+%                \includegraphics[width=16cm, height=22cm]{timeline/timetable.pdf}\label{Timetable}
+                \includegraphics[width=16cm]{timeline/timetable.pdf}\label{Timetable}
+                \caption{Research milestones and timeline}
                 \end{center}

### 2013-11-22 proposal/proposal/chapter4.tex
changes

@@
 
-%******************** START Contribution and Research Activities. ***************
-In this chapter we will introduce the important notions in argumentation-based negotiation,
-\section{Argumentation System and Agent Theory}\label{sec:Argumentation}
+This chapter was merged with chapter 2
+
+\begin{definition}{\emph{[Preference Level].}} \label{preferenceLevel}
+The preference level of a nonempty subset $\gamma$ of $\Gamma$ denoted by level $(\gamma)$ is the number of the highest numbered
+layer which has a member in $\gamma$.
+\end{definition}
+\begin{example}
+Let $\Gamma = \Gamma_1 \bigcup \Gamma_2 $ with $\Gamma_1$ = $\{ a, b\}$ and $\Gamma_2$ = $\{ c,d \}$ and $\gamma = \{a\}$ and
+$\gamma\prime = \{a,d\}$. We have: level$(\gamma) = 1$ and level$(\gamma\prime) = 2$.
+\end{example}
+
+\begin{algorithm}{\emph{\textbf{Algorithm} 1.}} \label{algorithm1}\\
+\\ Step 1:  $ W_{(H,h)/(H^{\prime},h^{\prime})}^{P_{Ag_1,Ag_2}} = 0 . $ \\
+\\Step 2:  $(\forall x \in H),(\forall x^{\prime}  \in H^{\prime} ):
+ ( pref(x,x^{\prime}) \in P_{Ag_1,Ag_2}^{pref})\Rightarrow W_{(H,h)/(H^{\prime},h^{\prime})}^{P_{Ag_1,Ag_2}} = W_{(H,h)/(H^{\prime},h^{\prime})}^{P_{Ag_1,Ag_2}}  +  1 $
+\end{algorithm}
+
+\begin{theorem}\label{Complexity1}
+If arguments are represented in proportional definite Horn clauses, the arguments selection mechanism runs in polynomial time.
+\end{theorem}
+
+\noindent\emph{\textbf{Proof.}} \emph{It is known from Bentahar et al. \cite{BentaharIEEEIS2007}, that given a Horn knowledge base
+$\Gamma$, a subset $H \subseteq \Gamma$, and a formula $h$; checking whether $(H, h)$ is an argument is polynomial. To decide
+if an argument is irrelevant, we have to check if 1) $H \vdash \neg x$ for an $x \in CK$, which can be done in polynomial time
+since $H$ is a definite Horn formula; or 2) there is a path from the root to $(H, h)$, which is a graph reachability problem, and
+it is known by Jones \cite{Jones} that the problem is in NLOGSPACE. Since NLOGSPACE $\subseteq$ P, the problem can be
+solved in polynomial time. To decide about the preference, we only need to compute the level of an argument from the level of a
+subset of $\Gamma$, which is  a simple procedure that is obviously polynomial. Computing the favorite argument given two arguments
+needs the computation of the arguments' weight, which is again a polynomial procedure as shown by Algorithm 1. To compere two given
+arguments using the risk, we only need to compute the number of formulas in $H$ and check if they are part of different sets,
+which is a polynomial procedure. Finally, the relevance ordering relation is simply based on comparing risks and favorites, which
+are both polynomial, so we are done.}~~$\blacksquare$

### 2013-11-23 proposal/proposal/chapter2.tex
changes

@@
 
-        \subsection{Cooperative Game Examples}\label{sec:CWSDefinition}
+        \subsection{Examples on Cooperative Game Solution Concepts}\label{sec:CWSDefinition}
 
@@
         Those considerations of forming stable and efficient coalitions
-        are the main contributions of our paper.
+        are the main contributions of this research work.
 

### 2013-12-01 proposal/proposal/chapter2.tex
changes

@@
 
-        \subsection{Examples on Cooperative Game Solution Concepts}\label{sec:CWSDefinition}
+        %\subsection{Examples on Cooperative Game Solution Concepts}\label{sec:CWSDefinition}
 
             \emph {THIS EXAMPLE IT NOT COMPLETE YET}
+
+            \begin{example}\label{ex:simplecore1}
+                Consider a game $G = (N, v)$, with two players where $N = {1,2}$.
+Each of these players can produce 5 units of output working alone and by collaborating they can produce 20 units worth of output.
+Therefore we have: $v({1}) = 5, v({2}) = 5, v({1,2}) = 20$.
+The $core$ of the game, which is the set of all possible distribution of gain among players guaranteeing stability is: $core(N,v) = \{(x_1,x_2) \in R^2 | x_1 >= 5, x_2 >= 5, x_1 + x_2 = 20\}$, as illustrated in figure \ref{fig:coreex1}.
+Distributing the 20 units of income, among these two players, for all the points in the line will make outcome stable, since non of these players can gain more than 5 by working alone.
+However although they have same qualities, the core can suggest a stable outcode where one agent can earn three times more than the other agent: $\{5,15\}$.
+As mentioned in previous section, $core$ result may not be fair, the $core$ only considers stability.
+However, \emph{Shapley value} considers fairness.
+According to equation \ref{eq:shapley}, the two  workers should each share 10 units of income, since they have the same marginal contribution to all subsets of the coalition.
+As you can see the distribution vector of $\{10,10\}$ is also a member in $core$ set.
+Later we are going to show if $core$ of a coalition game is not empty, and game is convex, the shapely value lies within $core$ set.
+            \end{example}
+
+            \begin{figure}
+                \begin{center}
+                \includegraphics[width=3in]{Figures/excore.eps}\label{fig:coreex1}
+                \caption{Core of the 2-player game of example \ref{ex:simplecore1}}
+                \end{center}
+            \end{figure}
+
+            \begin{example}\label{ex:simplecorealpha}
+                Consider a game $G = (N, v)$,  where $N = {1,2,3}$ and $v(\{i\}) = 0$, $v(\{Ci\}) = \alpha for |C| = 2$ and $v(\{N\}) = 1$. The $core$ of the game, 
+            \end{example}
+
+            \begin{example}\label{ex:simplecore2}
 
@@
                 is in the core, as you are asked to verify in the following exercise.
+
+            \end{example}
 

### 2013-12-02 proposal/proposal/chapter2.tex
fixes

@@
         where those agents can increase their payoff by binding agreements
-        and cooperating in groups. We let $N$ be a set of players. Any
-        subset $S$ of $N$ can form a group called $coalition$. A
+        and cooperating in groups. We let $N$ be a set of players which can form a group called a $coalition$. A
         \emph{coalitional game} is a pair $G = (N, v)$, where $v$ is called
         a \emph{characteristic function} $v: 2^N \to \mathbb{R}$, mapping the set of players of the
-        coalition to a real number $v(S)$, the worth of $S$. This number
+        coalition to a real number $v(N)$, the worth of $N$. This number
         usually represents the output or payoff or again the performance
         of these players working together as coalition.  If a coalition
-        $S$ is formed, then it can divide its worth, $v(S)$ in any
+        $S$ is formed, then it can divide its worth, $v(N)$ in any
         possible way among its members. The payoff vector $x \in
-        \mathbb{R}^S$ is the amount of payoff being distributed among the
-        members of the coalition $S$. The payoff vector satisfies two
+        \mathbb{R}^N$ is the amount of payoff being distributed among the
+        members of the coalition $N$. The payoff vector satisfies two
         conditions:
@@
             \item $x_i \geq 0$ for all $i \in N$, and
-            \item $\sum_{i \in S} x_i \leq v(S)$
+            \item $\sum_{i \in N} x_i \leq v(N)$
         \end{itemize}
@@
             basically rewards members with the amount of marginal contribution
-            they have to the coalition.
+            they have to the coalition.  It checks the contribution of member $i$ by adding the agent, to all possible subsets
+            of coalitions $S$, where $S \subseteq N\backslash\left\{i\right\}$. If he is added to the set $S$, his
+            contribution to the coalition is $v(S \cup \left\{i\right\}) - v(S)$. Average marginal contribution of agent $i$'s
+            is calculated by averaging this value over all possible subsets of $N$, in $Shapley value$ equation (\ref{eq:shapley}).
 
@@
             \begin{example}\label{ex:simplecorealpha}
-                Consider a game $G = (N, v)$,  where $N = {1,2,3}$ and $v(\{i\}) = 0$, $v(\{Ci\}) = \alpha for |C| = 2$ and $v(\{N\}) = 1$. The $core$ of the game, 
+                In this example, we want to analyse games under conditions which core can be empty.
+Consider a game $G = (N, v)$,  where $N = {1,2,3}$ and $v(\{i\}) = 0$, $v(\{Ci\}) = \alpha for |C| = 2$ and $v(\{N\}) = 1$.
+The $(x_1,x_2,x_3)$ distribution vector is in $core$ if $x \geq 0$, $\forall i, \forall j, x_i + x_j \geq \alpha $
             \end{example}

### 2013-12-02 proposal/proposal/chapter3.tex
fixes

@@
 As mentioned in previous section, the worth and output of a
-community of web services is a function of the
-throughput and provided QoS. If the throughput rate is more than
+community  is a function of the
+throughput and provided QoS of its web service members. If the throughput rate is more than
 the master's input request rate, it means the web services inside
@@
 \begin{gather*}
-S \cup \left\{i\right\} = (S \cup \left\{i\right\}) \cup T
+T \cup \left\{i\right\} = (S \cup \left\{i\right\}) \cup T
 \\
-T = (S \cup \left\{i\right\}) \cap T
+S = (S \cup \left\{i\right\}) \cap T
 \end{gather*}
@@
 
-Our algorithm works as follows. We have an established community
-with a master and some member web services already residing in the
-community. A web service would send a join request to the
-community. The ideal solution would be analyzing the \emph{core}
+Our algorithm works as follows. Given an  established community
+with a master and some member web services, a web service would send a \emph{join request} to join  the
+community. Ideally, the \emph{core}
 or \emph{$\epsilon$-core} stability of the group having this new
-member. As the normal core membership algorithm is computationally
+member should be analyzed. As the normal core membership algorithm is computationally
 intractable, we exploit Proposition \ref{proposition1} and Equation
@@
 characteristic function where the new member is added. In the
-equation, we set $C$ to be our community members $(C)$ before
-having the new web service. We assign ${i}$ to the new web
+equation, let $C$  be our community members before
+having the new web service join the community. Let  ${i}$ be the new web
 service, and then verify the equation for $S$, setting $ S = T /
@@
 
-It is possible to develop an anytime algorithm by continuing the
-verification of this condition against all subsets of size $3$,
+It is possible to develop an algorithm that continues the
+verification of this condition against subsets of size $3$,
 $4$, etc. until the algorithm gets interrupted.
@@
 structures. As mentioned in Section \ref{sec:coalition}, the used
-algorithms \cite{Sandholm:1999:CSG:317145.317152,DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
+algorithms in \cite{Sandholm:1999:CSG:317145.317152,DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
 solve key fundamental problems of what coalitions to form, and how
@@
 may split from old communities, if splitting does not decrease the
-payoff of any web service of the community. According to
+payoff of \emph{any} web service of the community. According to
 \cite{DBLP:journals/corr/abs-cs-0605132}, this sequence of merging
@@
 
-\subsection{Taxtation, Subsiding and Community Stability}\label{s:tax}
+\subsection{Taxation, Subsiding and Community Stability}\label{s:tax}
 
-We discuessed $core$ as one of the preminent solution concepts in cooperative games.
+ssed $core$ as one of the prominent solution concepts in cooperative games.
 Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group.
-However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal ammount of $\epsilon$ by deviating.
-Comuunity stability is an attractice property for communities, also communities would benefit by having slightly more web services then having the exact number of web services satisfying task rate cap.
-One reason is that there is always the possibility that the agents may leave the community or they may under perform from the quality values they were initially performing with.
+However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal amount of $\epsilon$ by deviating.
+Stability is an attractive property for communities.
+In addition, communities would benefit by having slightly more web services then the exact number of web services satisfying task rate cap.
+This is because  there is always a possibility that the agents may leave the community or they may under perform and degrade the quality values they were initially performing with.
 
-One way for communities to ensure community stability could be applying a tax, $\epsilon$ ammount of cost for web services changing communities which would make deviation a costly act.
-However this would require all community coordinators to agree on same ammount of taxtation, being governed by some external entities or web services would join communities with lesser ammount of tax.
-Another viable solution in our scenario is to stabilize the game using external subsidies.
-The reason a game is not stable is that the community is not making enough revenue to allocate the players with enough gain.
+One way for communities to ensure  stability could be  by applying a tax, $\epsilon$ amount of cost for web services changing communities which would make deviation a costly act.
+However this would require all community coordinators to agree on a same amount of taxation, being governed by some external entities or web services would join communities with lesser amount of tax.
+Another viable solution to our scenario is to stabilize the game using external subsidies.
+The reason a gamWe discue is not stable is that the community is not making enough revenue to allocate  enough gain to the players.
 A community master can subside its community with a constant coefficient value of $\lambda$.
+
 Rewarding a community with high number of quality participants with $\lambda v(C)$, where $\lambda \leq 1$.
-Obviously with a big number of $\lambda$ it is always possible to stabilize the community.
+
+Obviously with a big number of $\lambda$, it is always possible to stabilize the community.
 However, this can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable.
-Subsiding or taxting in order to reduce the bargaining power of sub coalitions are called $taxtation$ \cite{eps346856} methods.
+Subsiding or taxing in order to reduce the bargaining power of sub coalitions are called $taxation$ \cite{eps346856} methods.
 
@@
 measured in terms of quality and quantity of requests (or tasks)
-successfully answered by the communities. We initiate the
+successfully answered by the communities. We initiated the
 communities with few web services, then let rejecting and
 accepting random web services go for a short number of iterations.
-After that, we start the request distribution for the communities
+After that, we started the request distribution for the communities
 and let them allocate requests among member web services.
-Thereafter, we measure the average output performance of tasks in
+Thereafter, we measured the average output performance of tasks in
 communities following different methods.
@@
 were no cap on size of the community and we had communities of
-size 60 web services at some points. The results show that our
+size 60 web services at some points.
+In this scenario our community receives 30 tasks on average per iteration, from users.
+The community, after the task distribution process on each iteration, will reevaluate QoS metrics of its members and can check for new membership requests.
+Web services may join or leave the community between iterations.
+The results show that our
 \emph{depth-2 convex checker} method is performing better compared
@@
 method \emph{Random Formation} and use it as a benchmark for our
-QoS-aware coalition formation process. As the results illustrate,
+QoS-aware coalition formation process. In this scenario, each user individually generates randomly
+between 0 to 10 number of tasks per iteration, then the users target a community and direct their requests to the chosen community. As the results illustrate,
 our method forms better coalitions of web services improving

### 2013-12-02 proposal/proposal/chapter2.tex
changes

@@
         if the payoff obtained by a coalition is distributed amongst the
-        coalition members: $\sum_{i \in S} x_i = v(S)$. This definition of
+        coalition members: $\sum_{i \in N} x_i = v(N)$. This definition of
         the characteristic function works in \emph{transferable utility}
@@
 
-            \emph {THIS EXAMPLE IT NOT COMPLETE YET}
-
             \begin{example}\label{ex:simplecore1}
@@
 Consider a game $G = (N, v)$,  where $N = {1,2,3}$ and $v(\{i\}) = 0$, $v(\{Ci\}) = \alpha for |C| = 2$ and $v(\{N\}) = 1$.
-The $(x_1,x_2,x_3)$ distribution vector is in $core$ if $x \geq 0$, $\forall i, \forall j, x_i + x_j \geq \alpha $
+The $(x_1,x_2,x_3)$ distribution vector according to equation \ref{eq:core}, is in $core$ if $x_i \geq 0$ which implies each player will get more than 0 which they would when working alone and $\forall i, \forall j, x_i + x_j \geq \alpha $ which implied any pair of players will get more than $\alpha$ which they would earn if they worked in pair without the third player and finally $\sum_{i \in N} x_i = 1$ which implied all the gain is distributed among the three players.
+Based on these three equations we have, $\forall i \in N 0 \leqslant 1 - \alpha$ and $\sum_{i \in N} x_i = 1$.
+By summing first equation for all three platers, we conclude $Core (N,v)$ is nonempty iff $\alpha \leqslant \frac{2}{3}$.
+When alpha is more than $\frac{2}{3}$, the contribution of third player is not good enough to justify the group of three players working together.
+The third player will increase the revenue with less then $\frac{1}{3}$, and the other two players, both can get better share of revenue if they work together.
+This is why the group of three players working together when $\alpha > \frac{2}{3}$ is not stable.
             \end{example}
 
-            \begin{example}\label{ex:simplecore2}
-
-                An example which has closely resembles our community service model is the \emph{Single landowner and landless workers} example.
-                This example was introduced in \cite{GVK369342747} and represents the \emph{landowner} entity which is providing jobs and \emph{landless workers} who cannot do anything by themselves and need to work with a landowner to gain revenue (payoff).
-
-                In this game, land is owned by a single person, the \emph{landowner}.
+            %\begin{example}\label{ex:simplecore2}
+%
+%                An example which has closely resembles our community service model is the \emph{Single landowner and landless workers} example.
+%                This example was introduced in \cite{GVK369342747} and represents the \emph{landowner} entity which is providing jobs and \emph{landless workers} who cannot do anything by themselves and need to work with a landowner to gain revenue (payoff).
+%
+%                In this game, land is owned by a single person, the \emph{landowner}.
 We refer to the other people as \emph{workers}.
@@
 The preference of each player would be the amount of out she obtains.
-
-                In this game the action $a_{N}$ of the grand coalition in which the landowner obtains all the output $f$(n)
-                is in the core: all coalitions that can produce any output include the landowner, and none of these
-                coalitions has any actions that makes her better off than she is in $a_{N}$.
-
-                For any value of n The core contains actions in which the workers receive some output.
-                The workers need the landowner to produce any output, but the landowner
-                also needs the workers to produce more than $f$(1), so stable actions of the grand coalition exist in which the
-                workers receive some output. Take the landowner to be player 1, and consider the action $a_{N}$ of the grand
-                coalition in which each player $i$ obtains the output $x_{i}$, where $x_{1}+...+x_{n}=f(n)$. Under what conditions
-                on  $(x_{1},..,x_{n})$ is $a_{N}$ in the core? Because of my assumption about the shape of the function $f$, the
-                coalitions most capable of profitably deviating from $a_{N}$ consist of the landowner and every worker but one.
-                Such a coalition can, by itself, produce $f(n-1)$, and it may distribute this output in any way among its members.
-                Thus for a deviation by such a coalition not to be profitable, the sum of $x_{i}$ and any collection of $(n-2)$ other
-                $x'_{i}$s must be at least $f(n-1)$. That is, $(x_{1}+...+x_{n})-x_{i}\geq f(n-1)$ for every $j=2,..,n$. Because
-                $x_{1}+...+x_{n}=f(n)$, we conclude that $x_{i}\leq f(n)-f(n-1)$ for every player $j$ with $J\geq 2$ (i.e. every worker).
-                That is, if $a_{N}$ is in the core then $0\leq x_{j}\leq f(n)-f(n-1)$ for every player $J\geq 2$. In fact, every such action
-                is in the core, as you are asked to verify in the following exercise.
-
-            \end{example}
+%
+%                In this game the action $a_{N}$ of the grand coalition in which the landowner obtains all the output $f$(n)
+%                is in the core: all coalitions that can produce any output include the landowner, and none of these
+%                coalitions has any actions that makes her better off than she is in $a_{N}$.
+%
+%                For any value of n The core contains actions in which the workers receive some output.
+%                The workers need the landowner to produce any output, but the landowner
+%                also needs the workers to produce more than $f$(1), so stable actions of the grand coalition exist in which the
+%                workers receive some output. Take the landowner to be player 1, and consider the action $a_{N}$ of the grand
+%                coalition in which each player $i$ obtains the output $x_{i}$, where $x_{1}+...+x_{n}=f(n)$. Under what conditions
+%                on  $(x_{1},..,x_{n})$ is $a_{N}$ in the core? Because of my assumption about the shape of the function $f$, the
+%                coalitions most capable of profitably deviating from $a_{N}$ consist of the landowner and every worker but one.
+%                Such a coalition can, by itself, produce $f(n-1)$, and it may distribute this output in any way among its members.
+%                Thus for a deviation by such a coalition not to be profitable, the sum of $x_{i}$ and any collection of $(n-2)$ other
+%                $x'_{i}$s must be at least $f(n-1)$. That is, $(x_{1}+...+x_{n})-x_{i}\geq f(n-1)$ for every $j=2,..,n$. Because
+%                $x_{1}+...+x_{n}=f(n)$, we conclude that $x_{i}\leq f(n)-f(n-1)$ for every player $j$ with $J\geq 2$ (i.e. every worker).
+%                That is, if $a_{N}$ is in the core then $0\leq x_{j}\leq f(n)-f(n-1)$ for every player $J\geq 2$. In fact, every such action
+%                is in the core, as you are asked to verify in the following exercise.
+%
+%            \end{example}
 
@@
 
-        % THIS IS REPEATED
-        \emph {-- this is repeated --}
-        In this research work, we use game theory to
+        In this research work, I will use game theory to
         propose a cooperative game model for the aggregation of web

### 2013-12-02 proposal/proposal/Abstract.tex
changes

--- 2013-07-24 proposal/proposal/Abstract.tex
@@
 optimal and stable communities as coalitions to maximize
-individual and group efficiency and income has not been addressed
-yet. In this paper, we propose an efficient coalition formation
-mechanism using cooperative game-theoretic techniques. We propose
-a mechanism for community membership requests and selections of
-web services in the scenarios where there is interaction between one community and many web services
-and scenarios where web services can join multiple established communities. The ultimate objective is to
-develop a mechanism for web services to form stable groups
-allowing them to maximize their efficiency and generate
-near-optimal (welfare-maximizing) communities. The theoretical and
-extensive simulation results show that our algorithms provide web services
-and community owners, in real-world like environments, with applicable and near-optimal decision
-making mechanisms.
+individual and group efficiency and income for all the involved
+parties has not been addressed yet.
+
+In this proposal, we identify the problem of defining efficient
+algorithms for coalition formation mechanisms within communities
+and propose preliminary results using cooperative game-theoretic
+techniques. We propose a mechanism for community membership
+requests and selections of web services in the scenarios where
+there is interaction between one community and many web services
+and scenarios where web services can join multiple established
+communities. The ultimate objective is to develop a mechanism for
+web services to form stable groups allowing them to maximize their
+efficiency and generate near-optimal (welfare-maximizing)
+communities. The theoretical and extensive simulation results show
+that our algorithms provide web services and community owners, in
+real-world like environments, with applicable and near-optimal
+decision making mechanisms.
+
+As remaining work in this thesis, we propose to apply different
+cooperative game techniques such as nucleus, kernel and bargaining
+solution concepts and theoretically analyze those solution
+concepts based on functions representing payoff and quality
+metrics of the communities. We also aim to apply reinforcement
+learning techniques for individual web service strategic decision
+making process.

### 2013-12-02 proposal/proposal/chapter1.tex
changes

@@
 \chapter{Introduction}\label{sec:intro}
-In this chapter we introduce the context of this research, which is about community of web services as autonomous agents and cooperative game theoretic solution concepts.
-We discuss literature review and their shortcomings then present the motivations behind this work.
-Also, we discuss our preliminary contributions.
+In this chapter, we introduce the context of this research, which
+is about communities of web services abstracted as autonomous
+agents. Those agent-based web services use cooperative game
+theoretic solution concepts for decision making. We discuss the
+motivations of this work and briefly review the literature to
+identify the problems we aim to solve in this thesis. Moreover, we
+discuss our objectives and preliminary contributions.
 
-\section{Context}\label{sec:motivation}
+\section{Context of Research}\label{sec:motivation}
 
@@
 
+Typically, web services are business applications deployed as
+autonomous and interoperable agents \cite{Alescio}. In fact, the
+W3C consortium defines a web service as ``an abstract notion that
+must be implemented by a concrete agent''. However, the web is
+stocked with agent-based services that offer similar business
+functionalities, which leads to service consumers having
+difficulties in choosing the most appropriate agents to interact
+with.
+
 The need for highly available and responsive services has called
@@
 Communities are virtual groups of web services having similar
-functionalities \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7}, but probably different non-functional quality
-attributes, which form the QoS parameters. When communities are
-used, users send their requests to the masters of those
-communities, which are responsible of managing the communities,
-forwarding the requests to the suitable member web services and
-checking the credentials of those members. Communities aim to
-provide higher service availability and performance than what
-individual web services can provide. The high availability of
-services and the community resilience to failure are guaranteed
-since web services can cooperate and replace each other within the
-same community and since there is no single point of failure in
-the communities architecture.
+functionalities \cite{Zeng:2003:QDW:775152.775211,
+Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7},
+but probably different non-functional quality attributes, which
+form the QoS parameters. When communities are used, users send
+their requests to the masters of those communities, which are
+responsible of managing the communities, forwarding the requests
+to the suitable member web services and checking the credentials
+of those members. Communities aim to provide higher service
+availability and performance than what individual web services can
+provide. The high availability of services and the community
+resilience to failure are guaranteed since web services can
+cooperate and replace each other within the same community and
+since there is no single point of failure in the communities
+architecture.
 
@@
 
-In this section, we present a scenario and demonstrate why there is a need for a community of services and why it should satisfy all business models involved.
-We first propose an example of a real world scenario, focusing on user experience.
-Nowadays most of the computer applications are dependent on multiple online service provides, there are a plethora of options available to people in today's society, weather forecasting, ticketing services, map services, local places guides and so on.
-Most mobile or web applications cannot independently provide this information and they rely on different online services to provide this information.
-The high competition within the services industry requires applications to use reliable and high quality online service providers.
+In this section, we present a scenario and demonstrate why there
+is need for communities of services. We first propose an example
+of a real world scenario, focusing on user experience. There are a
+plethora of options available to people in today's society,
+including weather forecasting, ticketing services, map services,
+local places guides and so on. Most mobile or web applications
+cannot independently satisfy users requests and should rely on
+different online services. The high competition within the
+services industry requires applications to use reliable and high
+quality online service providers.
 
-If the user were to check a web site or run an application on his/her mobile upon having downtime, or having high response delay or encountering any non-satisfying quality metric, the user will instantly remove the application, which is a huge business concern for application providers.
-For example, if someone installs a ticketing application on mobile and the application is not using high quality service providers, the user would instantly uninstall the application, which has an extremely negative impact on the visibility of the application.
-Or let's say you search "Montreal Weather" on a search engine and you click on a web site which is slow because it is using a bad weather web service as source of its raw data, the user will leave the web site and try another link from search results, which has a bad Search Engine Optimization (SEO) effect for the web site, and search engines would not show that web site on search results anymore, which is a business and revenue loss for the application.
-Thus end user satisfaction is the main goal for online providers otherwise they will lose the market to competitors very quickly.
-Communities of web service, by providing services with higher quality, higher uptime and reliability for end users, aim to reach this goal.
-To this end, community management decisions should factor in important QoS parameters while forming the community and during membership management.
+If the user were to check a web site or run an application on her
+mobile device upon having downtime, or having high response delay
+or encountering any non-satisfying quality metric, she will
+instantly remove the application, which is a huge business concern
+for application providers. For example, if a user installs a
+ticketing application on her mobile device and the application is
+not using high quality service providers, the user would instantly
+uninstall the application, which has an extremely negative impact
+on the
+visibility of the application. %Let us say you search "Montreal
+%Weather" on a search engine and you click on a web site which is
+%slow because it is using a bad weather web service as source of
+%its raw data, the user will leave the web site and try another
+%link from search results, which has a bad Search Engine
+%Optimization (SEO) effect for the web site, and search engines
+%would not show that web site on search results anymore, which is a
+%business and revenue loss for the application.
+Thus, end user satisfaction is the main goal for competitive
+online providers. Communities of web service, by providing
+services with higher quality, higher uptime and reliability for
+end users, aim to reach this goal. To this end, community
+management decisions should capitalize on important QoS parameters
+while forming the community and during membership management.
 
-High demand on online services has created a big competition on this area.
-For example an application developer right now needs to choose between hundreds of web services online, providing local places information such as coffees, venues, shops and bars nearby a geographic position.
-It is hard for new web services to find their customers and be visible for end users amongst hundreds or thousands of other service providers, even if they provide a high quality of service.
-Hence, community of web services provides them with the chance of joining the communities which already have established market share, and providing them with a great source of revenue, proportional to their QoS and throughput.
-However, it is important for a community manager to consider all parties involved, for example if market share is not big enough, bringing new web services, can cause revenue drop for the already residing members in community,   since basically there would be not enough tasks and revenue to be shared among web services.
-This will not affect user satisfaction, but other quality web services may collude, leave, and join another community, hurting the community stability.
-This is an important issue which has not been addressed previously in similar related works.
-On the other hand, if communities bound the number of web services exactly to the numbers satisfying their market share, in the case of failure of a web service, the reliability and availability metrics of the community could get hurt.
-This has also not been efficiently addressed in any other related work.
-In this research work, we try to propose community formation algorithms, satisfying all parties involved.
-This is a complete business model, considering end users, community managers and service providers.
+High demand on online services has created a massive business
+competition. For example, nowadays users are provided with
+multiple choices of web services offering local places information
+such as coffees, venues, and shops nearby a geographic position.
+It is hard for new web services to find their customers and be
+visible for end users amongst hundreds or thousands of other
+available services, even if they provide a high quality of
+service. Hence, the concept of communities of web services
+provides them with the chance of joining a platform with an
+established market share and reputation. However, it is crucial
+for a community manager to consider many factors when inviting or
+accepting new members. For example, if the market share is not big
+enough, bringing new web services can cause revenue drop for the
+already residing members. This may encourage other web services to
+collude, leave, or join other communities, hurting the community
+stability. This is an important issue which has not been addressed
+previously in the relevant literature. On the other hand, if
+communities bound the number of web services to ensure higher
+revenue, availability and response time could be negatively
+affected if some members encounter problems. This is because
+alternative web services for substitution will be limited.  This
+has also not been efficiently addressed in the related work.
+Consequently, community formation algorithms satisfying some
+desirable properties such as community stability and overall
+revenue are yet to be defined considering end users, community
+managers and service providers.
 
-\section{Motivation and research Questions}\label{sec:researchquestions}
+\section{Motivation and Research Questions}\label{sec:researchquestions}
 
-Web service communities are dynamic by design \cite{DBLP:journals/ijebr/MaamarSTBB09}.
-In these communities, web services are modeled as intelligent autonomous agents, where they can adopt a strategy maximizing their payoff at any time.
-A web service has its own right to determine when to join a community and when to leave a community.
-Community managers can invite or ask a web service to leave in order to maximise their profit.
-Users can simply stop sending requests to a web service which is not providing satisfactory services.
-Thus its important to consider all parties involved in community management decision making process.
-Most of the recent work on communities of services are either
-user-centric and focus on user satisfaction
+Web service communities are dynamic by design
+\cite{DBLP:journals/ijebr/MaamarSTBB09}. In these communities, web
+services are modeled as intelligent autonomous agents, where they
+can adopt a strategy maximizing their payoff at any time. A web
+service can ask joining a community and has the right to leave it.
+Community managers can invite or ask a web service to leave in
+order to maximize the community profit. Users can simply stop
+sending requests to a web service which is not providing
+satisfactory services. Thus its important to consider all the
+parties involved in the decision making process about the
+community management. Most of the recent work on communities of
+services are either user-centric and focus on user satisfaction
 \cite{Chun02user-centricperformance} or system-centric and focus
@@
 collaborate as long as they are getting more benefits and payoff.
-Our initial research question is:
-\emph{How can we model the community of services for the autonomous agents, in order to maximize the throughput for users, web services and community organizers involved?}
+Our initial research question is: \emph{How can we model the
+community of agent-based services in order to maximize the utility
+of involved users, web services and community organizers?}
 
-In order to address this shortcoming, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
-DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
-users and services to maximize their gain. A two-player
-non-cooperative game between web services and community master was
-introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}.
-In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
+In order to address this problem, recently
+\cite{DBLP:conf/IEEEscc/LimTMB12,
+DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
+mechanisms to help users and services maximize their gain. A
+two-player non-cooperative game between web services and community
+master was introduced in
+\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In
+\cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
 for selecting web services has been proposed. In this approach,
@@
 of all the three involved parties, namely users, web services and
-communities.
-The issue with these solution concepts is that they consider community as whole and model it as one entity in their formulations.
-A community master decides on behalf of an aggregated function of parameters of all the web services in the community.
-This can hurt the overall revenue for some individual web services, or even a subset of web services.
-They can collude and form their own community and gain more, instead of having to adjust and share their resources to other members.
-Another important issue which needs to be considered is community stability.
-In community of web services, the web services and community organizers collaborate to perform tasks.
-Having jointly completed a task and generated revenue, they need to agree on some reasonable method of dividing profits (or tasks) among themselves.
-This is an key issue for stability of communities which has not had enough attention in related work.
-If the revenue sharing mechanism is not fair enough for any subset of web services working in the community, as profit maximizing agents, they would just deviate and make their own group inorder to gain more and fair share of profit.
-So an important research question that we would like to address is:
-\emph{How can we model the the fairness, efficiently in communities of web services and form stable communities?}
+communities. The issue with these solution concepts is that they
+consider community as a whole and model it as one entity in their
+formulations. A community master decides on behalf of all the
+members using an aggregated function of parameters. This can hurt
+the overall revenue for some individual web services, or even a
+subset of web services. Those services can collude and form their
+own community and gain more, instead of having to adjust and share
+their resources with other members. Another important issue which
+needs to be considered is the community stability. In community of
+web services, the members and community organizers collaborate to
+perform tasks. Having jointly completed a task and generated
+revenue, they need to agree on some reasonable method of dividing
+profits (or tasks) among themselves. This is a key issue for the
+group stability still to be investigated. If the revenue sharing
+mechanism is not fair enough for any subset of web services
+working in the community, these agents, as profit maximizing
+entities, would just deviate and make their own group. So an
+important research question that we would like to address is:
+\emph{How can we model fair and stable communities as coalitions
+of agent-based web services?}
 
@@
 
-In \cite{10.1109/TSC.2012.12}, a cooperative scheme among autonomous
-web services based on coalitional game theory has been introduced. They have proposed an algorithm to
-reach individually stable coalition partition for web services in order to
-maximize their efficiency. The communities choose new web services on the promise
-that it would benefit the community without decreasing any other web service's
-income. In their model, the worth of community is evaluated with high emphasis on
-availability metric and considering price and cost values only. The community structure is based on a coordination chain,
-where a web service is assigned as a \emph{primary} web service and the community task distribution
-method, will initially invoke the primary web service and only if the primary web service is unavailable
-will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to
-have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays
-with recent advancement in cloud and hardware infrastructures availability is becoming less of an issue. So the backup web services
-in their model have a very low chance of getting jobs, especially the ones further in chain, which is huge waste of web services
-capabilities.
-
-Another research question we would like to work on is:
-\emph{How can we model the community of web services based on cooperative game theory models in a realistic, applicable and practical way?}
+In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
+autonomous web services based on coalitional game theory has been
+introduced. The authors have proposed an algorithm to reach
+individually stable coalition partition for web services in order
+to maximize their efficiency. The communities choose new web
+services on the promise that it would benefit the community
+without decreasing any other web service's income. In their model,
+the worth of community is evaluated with high emphasis on the
+availability metric and considering price and cost values only.
+The community structure is based on a coordination chain, where a
+web service is assigned as a \emph{primary} web service and the
+community task distribution method will initially invoke the
+primary web service. Only if the primary web service is
+unavailable, the next backup web services in the ordered
+coordination chain will be invoked. However, in cooperative
+models, it is preferred to have a real and active cooperative
+activity engaging all agents to perform the tasks more
+efficiently. Thus, the final research question we would like to
+work on is: \emph{How can we model and analyze the cooperation
+among the community members in realistic, applicable and practical
+settings?}
 
@@
 
-\section{Research Objectives and contributions}\label{sec:motexample}
+\section{Research Objectives and Contributions}\label{sec:motexample}
 
-In this research work, I will use game theory to
-propose a cooperative game model for the aggregation of web
-services within communities. The solution concepts of our
-cooperative game seeks to find efficient ways of forming
-coalitions (teams) of web services so that they can maximize their
-gain and payoff, and distribute the gain in a fair way among all
-the web services. Achieving Fairness when the gain is distributed
-among the community members is the main factor to keep the
-coalition stable as no web service will expect to gain better by
-deviating for the community. In other words, the coalition is made
-efficient if all the members are satisfied. We first propose a
-representation function for communities of web services based on
-their QoS attributes. By using this function, we can evaluate the
-$worth$ of each community of web services. When facing new
-membership requests, a typical community master checks whether the
-new coalition having the old and new set of web services will keep
-the community stable or not. The community master will reject the
+In this research work, our first objective is to propose a
+cooperative model as game for the aggregation of web services
+within communities. The solution concepts of our cooperative game
+seeks to find efficient ways of forming coalitions (teams) of web
+services so that they can maximize their gain and payoff, and
+distribute the gain in a fair way among all the member services.
+Achieving Fairness when the gain is distributed among the
+community members is the main factor to keep the coalition stable
+as no web service will expect to gain better by deviating from the
+community. In other words, the coalition is made efficient if all
+the members are satisfied. We first propose a representation
+function for communities of web services based on their QoS
+attributes. By using this function, we can evaluate the $worth$ of
+each community of web services. When facing new membership
+requests, a typical community master checks whether the new
+coalition having the old and new set of web services will keep the
+community stable or not. The community master will reject the
 membership requests if it finds out that the new coalition would
@@
 other communities or forming new ones. The computation of
-solutions for cooperative game theory problems is combinatorial in
-nature and proven to be NP-complete \cite{Algorithmic}, making
-this computation impractical in real world applications. However,
-using the concepts of coalition stability, we propose
-approximation algorithms running in polynomial time providing web
-services and community masters with applicable and near-optimal
-decision making mechanisms.
+solutions for cooperative games is combinatorial in nature and
+proven to be NP-complete \cite{Algorithmic}, making this
+computation impractical in real world applications. However, using
+the concepts of coalition stability, the second objective is to
+investigate approximation algorithms running in polynomial time
+providing web services and community masters with applicable and
+near-optimal decision making mechanisms.
 
-\indent In this proposal, I will address the problem of forming stable and efficient coalitions for maximising web services and community revenue.
-The main objectives in this proposal work are:
+\indent To summarize, the main problem we aim to tackle in this
+thesis is the formation of stable and efficient coalitions
+maximizing web services and community revenue. The main objectives
+are:
 \begin{itemize}
-\item To apply cooperative game theory solution concepts in order to address the problem of optimizing coalition formation for a stable community that can maximise the total payoff.
-\item To reduce the complexity of cooperative game theory solution concepts tailored to the problem model of communities of web services in order to make these solutions applicable in real world scenarios.
-\item To increase community stability by subsiding and taxation methods.
-\item To validate the proposed methods by simulation and comparing our results with other similar works.
+\item To propose a cooperative model and analyze its solution
+concepts in order to address the problem of optimizing coalition
+formation for a stable community.
+
+\item To reduce the complexity of computing the solution concepts
+of the cooperative model tailored to the problem of communities of
+agent-based web services in order to make these solutions
+applicable in real world scenarios.
+
+\item To analyze the effect of different membership and taxation
+models that the master can apply to the members on the stability
+of the community.
+
+\item To investigate the impact of learning on individual and
+group decision making within the cooperative model of the
+community.
+
+\item To validate the proposed methods by extensive simulations
+and comparison with other similar proposals.
 \end{itemize}
@@
 \section{Proposal Organization}\label{sec:outline}
-The rest of the proposal is organized as follows: We present in Chapter~\ref{sec:MAS} the background
-needed for our research along with the relevant related work. Chapter~\ref{sec:coalitionformationws} provides the problem statement and presents our solution model in two
-different scenarios with some primitive results. Finally in Chapter~\ref{sec:conclusionfuturework}, we present our conclusion, future plan, and the timetable of our research.
+The rest of the proposal is organized as follows: We present in
+Chapter~\ref{sec:MAS} the background needed for our research along
+with relevant related work. Chapter~\ref{sec:coalitionformationws}
+provides the problem statement and presents our solution model in
+two different scenarios with some preliminary results. Finally, in
+Chapter~\ref{sec:conclusionfuturework}, we present our conclusion,
+future plan, and the timetable of our research.

### 2013-12-02 proposal/proposal/chapter2.tex
changes

@@
 
-In this chapter, we briefly review web services, then we introduce the concept of communities of web services, their architecture and applications and the benefits of forming communities.
-Then we discuss the cooperative game theory concepts used throughout our research work.
-Finally, we discuss the relevant related work on web service communities and games in service oriented computing literature.
+In this chapter, we briefly review web services, then we introduce
+the concept of communities of web services, their architecture and
+applications and the benefits of forming communities. Thereafter,
+we discuss the cooperative game theory concepts used throughout
+the proposal. Finally, we discuss relevant related work on web
+service communities and games in the literature of service
+oriented computing.
 
     \section{Community of Web Services}\label{sec:CommunityWS}
-        In this section, we discuss the concept of communities of web services, and we discuss the architecture and operations of community members.
+    In this section, we present web services and discuss the concept
+    of their communities from architectural and operations
+    perspectives.
 

### 2013-12-03 proposal/proposal/chapter5.tex
changes

@@
 \chapter{Conclusion and Future Work}\label{sec:conclusionfuturework}
-In this chapter, we describe the phases of our plan for exploring the research challenges and investigating the research issues identified in Chapter 4.
-This chapter also includes research methodology and future publication plan.
+In this chapter, we describe the phases of our plan for exploring
+the research challenges and investigating the research issues
+identified in Chapter 3. This chapter also includes research
+methodology and future publication plan.
 
@@
 
-In this report, we proposed a cooperative game theory-based model
-for the aggregation of web services within communities. The goal
-of our services is to maximize efficiency by collaborating and
-forming stable coalitions. Our method considers stability and
-fairness for all web services within a community and offers an
-applicable mechanism for membership requests and selection of web
-services. The ultimate goal is to increase revenue by improving
-user satisfaction, which comes from the ability to perform more
-tasks with high quality. Simulation results show that our,
-polynomial in complexity, approximation algorithms provide web
-services and community owners with applicable and near-optimal
-decision making mechanisms.
+In this report, we presented research problems and questions we
+aim to address in the thesis and proposed some preliminary results
+about a cooperative game theory-based model for the aggregation of
+web services within communities. The goal of our services is to
+maximize efficiency by collaborating and forming stable
+coalitions. Our method considers stability and fairness for all
+web services within a community and offers an applicable mechanism
+for membership requests and selection of web services. The
+ultimate goal is to increase revenue by improving user
+satisfaction, which comes from the ability to perform more tasks
+with high quality. Simulation results show that our approximation
+algorithms are polynomial in complexity and provide web services
+and community owners with applicable and near-optimal decision
+making mechanisms.
 
@@
 
-\indent The future goals in this PhD research work mainly consists of:
+\indent The future goals in this Ph.D. research work are:
 
 \begin{itemize}
-\item Analysing other cooperative solution concepts such as Kernel and Nucleolus where payoff division is guaranteed to exist but may have optimal results.
-\item Applying Weighted Voting Games (WCG) type of valuation function in our scenarios, Developing a multiple weighted algorithm to find best coalition structures satisfying different weights on each community.
-\item Implementing Q-learning and reinforcement learning technique and also a tic-tac-toe based repeated game technique for individual Web Service decision making process, in long term and repeated game scenarios.
-\item Developing an approximation algorithm for shapely value payoff distribution vector in community of service setting.
-\item Developing a community membership algorithm technique for our agents in "incomplete information" settings.
-\item Developing an open source, Java based Tool, with UI for solving Core and Shapely solution concepts based on different input valuation functions.
+\item Analyzing other cooperative solution concepts such as Kernel
+and Nucleolus where payoff division is guaranteed to exist and may
+have optimal results.
+
+\item Applying other valuation function in our scenarios using for
+instance Weighted Voting Games (WCG) in order to develop a
+multiple weighted algorithm to find best coalition structures
+satisfying different weights on each community.
+
+\item Analyzing the impact of Q-learning and reinforcement
+learning on the performance of our model.
+
+\item Developing an approximation algorithm for shapely value
+payoff distribution vector in community setting.
+
+\item Developing a community membership algorithm technique for
+our agents in "incomplete information" settings.
+
+%\item Developing an open source, Java based Tool, with UI for
+%solving Core and Shapely solution concepts based on different
+%input valuation functions.
 \end{itemize}
@@
 %                \includegraphics[width=16cm, height=22cm]{timeline/timetable.pdf}\label{Timetable}
-                \includegraphics[width=16cm]{timeline/timetable.pdf}\label{Timetable}
+                \includegraphics[width=16cm]{timeline/timetable1.eps}\label{Timetable}
                 \caption{Research milestones and timeline}

### 2013-12-03 proposal/proposal/chapter3.tex
changes

@@
 \chapter{Coalition Formation for Autonomous Web Services}\label{sec:coalitionformationws}
+
+In this chapter, we present our coalition model of agent-based web
+services within communities\cite{SCC2013efficient}. We start by describing the general
+architecture and considered parameters for web services.
+Thereafter, problem modeling and formulation will be introduced in
+terms of task distribution and community revenue. Web service
+cooperative games in different settings will follow along with
+some simulation results.
 
@@
 
-\subsection{The Architecture}
+\subsection{Architecture}
 
@@
 
-\emph{1) Web services} are rational entities\footnote{The term
-rational is used here in the sense that web services are utility
-maximizers} providing services to end users. They aim to maximize
-their individual income by receiving enough requests from end
-users. In order to increase their revenue, web services seek for
-more tasks if they have the capacity and throughput to do so. Web
-services can join communities to have better efficiency by
-collaborating with others, to have access to higher market share,
-and to have opportunity of receiving a bigger task pool from end
-users. Throughout this proposal, in
-our equations, we refer to web services as $ws$ and to the set of
-web services hosted by a given community as $C$. To simplify the
+\emph{1) Web services} are rational entities that aim to maximize
+their utilities by providing high quality services to end users.
+They aim to maximize their individual income by receiving enough
+requests from end users. In order to increase their revenue, web
+services seek for more tasks if they have the capacity and
+throughput to do so. Web services can join communities to have
+better efficiency by collaborating with others, to have access to
+higher market share, and to have opportunity of receiving a bigger
+task pool from end users. Throughout this proposal, in our
+equations, we refer to web services as $ws$ and to the set of web
+services hosted by a given community as $C$. To simplify the
 notation, sometimes we simply write $ws$ instead of $ws \in C$ to
@@
 
-Figure \ref{fig_community} represents the architecture of web service communities.
-The communities are essentially an abstract model of web services.
-They aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols as web services.
-Web services join communities to increase their utility by having a larger market share and task pool.
-Community coordinators or master web services are responsible for community development, managing membership requests from web services and distributing user tasks among the community members.
-Community coordinators try to attract quality web services and keep the community as stable and productive as possible to gain better reputation and user satisfaction which results in having a higher market share for the community.
-The way the web services reside inside communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+Figure 3 represents our revised architecture of web service
+communities where tasks are to be distributed among the members
+that are interested in forming stable coalitions. As discussed in
+Chapter 2, communities are essentially virtual platforms
+aggregating web services having similar and complementary
+functionalities and communicate with other entities such as UDDI
+registries and users using particular protocols. Web services join
+communities to increase their utility by having larger market
+share and task pool. Community coordinators or master web services
+are responsible for community development, managing membership
+requests from web services and distributing user tasks among the
+community members. Community coordinators try to attract quality
+web services and keep the community as stable and productive as
+possible to gain better reputation and user satisfaction, which
+results in having higher revenue.
 
 \begin{figure*}[!t]
-\centerline{\includegraphics[width=15cm]{Figures/community.eps}}
+\centerline{\includegraphics[width=15cm]{Figures/archss.eps}}
 \caption{Architecture of Web Service communities}
@@
 
-\subsection{Task distribution}
+\subsection{Task Distribution}
 
-As mentioned in section \ref{webservice-communities}, communities are robust service providers with well established market share and reputation.
-By maintaining their reputation and performance, they attract  end users which choose them as service providers to perform their tasks.
-The community master is characterized by a request rate $(R_C)$ from users.
-Each web service comes with a given QoS ($QoS_{ws}$) from which the throughput $Th_{ws}$ is excluded.
-Throughput is the average rate of tasks a web service can perform per time unit.
-Its exclusion from $QoS_{ws}$ allows us to build our analysis on the particular value of $Th_{ws}$.
-Thus, web services perform tasks with an average output quality of $QoS_{ws}$ and a throughput rate of $Th_{ws}$.
+As mentioned in Section \ref{webservice-communities}, communities
+are robust service providers with well established market share
+and reputation. By maintaining their reputation and performance,
+they attract  end users which choose them as service providers to
+perform their tasks. The community master is characterized by a
+request rate $(R_C)$ from users. Each web service comes with a
+given QoS ($QoS_{ws}$) from which the throughput $Th_{ws}$ is
+excluded. Throughput is the average rate of tasks a web service
+can perform per time unit. Its exclusion from $QoS_{ws}$ allows us
+to build our analysis on the particular value of $Th_{ws}$. Thus,
+web services perform tasks with an average output quality of
+$QoS_{ws}$ and a throughput rate of $Th_{ws}$.
 
@@
 The communities and web services earn revenue by performing tasks.
-The total gain is function of quality ($QoS_{ws}$) and throughput ($Th_{ws}$) of tasks being performed.
-As mentioned in section \ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain aggregation function of the parameters considered in Table \ref{qosws}.
-We have adopted a linear equal weight average over all QoS parameters listed in table \ref{qosws} excluding the $Throughput$ and $Cost$ parameters.
-A community has the option to weigh specific QoS parameters depending on the expectations of their clients.
+The total gain is function of quality ($QoS_{ws}$) and throughput
+($Th_{ws}$) of tasks being performed. As mentioned in section
+\ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain
+aggregation function of the parameters considered in Table
+\ref{qosws}. We have adopted a linear equal weight average over
+all QoS parameters listed in Table \ref{qosws} excluding the
+$Throughput$ and $Cost$ parameters. A community has the option to
+weigh specific QoS parameters depending on the expectations of
+their clients.
 
@@
 % \extrarowheight as needed to properly center the text within the cells
-\caption{Example 1}
+\caption{Case Study: Example 1}
 \label{example_1}
@@
 % \extrarowheight as needed to properly center the text within the cells
-\caption{Example 2}
+\caption{Case Study: Example 2}
 \label{example_2}
@@
 
-In the first example,  we present the case of a community with $R_C =10 $, and three web services, each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}.
-The worth of a community is calculated based on $Out(C)$ equation (\ref{out_c}) which is the amount of output being generated by the community.
-The first table  lists the web services with their aggregated $QoS_{ws}$ parameters, their task input rate while working alone, and also their  throughput value $Th_{ws}$.
-The second table shows all the possible communities and their respective worth.
-The obtained values suggest that  communities having more web services have better gain and output.
-However each community needs to  distribute the gain between web services.
-Sometimes it is impossible to share the gain between all web services in a way that no subset of them would individually gain more if they form their own group.
-In this example, the value community of ${ws_1}$ and ${ws_2}$ is 7.2, With ${ws_3}$ joining the community the worth increases to 8.0.
-However there is no way to distribute the value among web services to have  ${ws_1}$ and ${ws_2}$  earning 7.2, and ${ws_3}$ earning at least 2.4, the gain they could earn before joining the community.
-This fact makes the group unstable.
-In the second  example, shown in table \ref{example_2}, we even have situations where a web service (${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$) decreases the value of community.
-The reason is, the community is already full and all tasks are almost being distributed and new community with bad quality can degrade the average quality of tasks being done by the community.
-In both examples, the request of joining of web service ${ws_3}$ should be rejected by the community.
+In the first example,  we present the case of a community with
+$R_C =10 $, and three web services, each having different
+$QoS_{ws}$ and $Th_{ws}$ values as listed in Table
+\ref{example_1}. The worth of a community is calculated based on
+$Out(C)$ equation (\ref{out_c}) which is the amount of output
+being generated by the community. The first table  lists the web
+services with their aggregated $QoS_{ws}$ parameters, their task
+input rate while working alone, and also their  throughput value
+$Th_{ws}$. The second table shows all the possible communities and
+their respective worth. The obtained values suggest that
+communities having more web services have better gain and output.
+However each community needs to  distribute the gain between web
+services. Sometimes it is impossible to share the gain between all
+web services in a way that no subset of them would individually
+gain more if they form their own group. In this example, the value
+community of ${ws_1}$ and ${ws_2}$ is 7.2, With ${ws_3}$ joining
+the community the worth increases to 8.0. However there is no way
+to distribute the value among web services to have  ${ws_1}$ and
+${ws_2}$  earning 7.2, and ${ws_3}$ earning at least 2.4, the gain
+they could earn before joining the community. This fact makes the
+group unstable. In the second  example, shown in Table
+\ref{example_2}, we even have situations where a web service
+(${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$)
+decreases the value of community. The reason is, the community is
+already full and all tasks are almost being distributed and new
+community with bad quality can degrade the average quality of
+tasks being done by the community. In both examples, the request
+of joining of web service ${ws_3}$ should be rejected by the
+community.
 
@@
 % \extrarowheight as needed to properly center the text within the cells
-\caption{Example 3}
+\caption{Case Study: Example 3}
 \label{example_3}
@@
 decide for its own good. The aim is to find less complex and
-distributed algorithms for forming web services
-coalitions\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
+distributed algorithms for forming web services coalitions
+\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
 The distributed merge-and-split algorithm in
@@
 
-Finally, in our last experiment, we compare our work with the work in \cite{10.1109/TSC.2012.12} which we call it \emph{High Availability Coalition} method, because of nature of their community valuation function, which focuses on community availability as main consideration.
-Their community formation model is very different than ours, however we have been very careful to make the experiment environment as fair and similar as possible.
-We limited our maximum community size by 5 in order to have communities with almost the same size.
-In their method, they have used web services as backups rather than active collaborative players, and they only get task when the first web service in an ordered chain fails to perform the task.
-However with recent advancement in cloud and hardware infrastructures availability is less of an issue for web services, and web services are highly available.
-Part(a) of figure \ref{fig_avail_method} shows our method performs almost performs tasks successfully with rate of three times more than \emph{High Availability Coalition} method because of real cooperative nature and task distribution of our algorithm.
-This result shows using web services as backups, and not as real collabrative players is a huge waste of web service capability since they have very low chance of getting jobs and its the primary web service (the first in their coordination chain) which does most of the work.
-The average quality of service of tasks performed is also better since our method considers all quality of service metrics mentioned in table \ref{qosws}.
-Part(c) shows the availability of community from end user point of view.
-The \emph {High Availability Coalition} method almost has 100\% uptime since they use web services as backups, so the chance of job failing reduces significantly as community members increase.
-In our method we have more chance of fail for each web service, however with some subsiding, and hiring a few more web service they can compensate the low chance of failure of web services in our community.
+Finally, in our last experiment, we compare our work with the work
+in \cite{10.1109/TSC.2012.12} which we call it \emph{High
+Availability Coalition} method, because of nature of their
+community valuation function, which focuses on community
+availability as main consideration. Their community formation
+model is very different than ours, however we have been very
+careful to make the experiment environment as fair and similar as
+possible. We limited our maximum community size by 5 in order to
+have communities with almost the same size. In their method, they
+have used web services as backups rather than active collaborative
+players, and they only get task when the first web service in an
+ordered chain fails to perform the task. However with recent
+advancement in cloud and hardware infrastructures availability is
+less of an issue for web services, and web services are highly
+available. Part(a) of figure \ref{fig_avail_method} shows our
+method performs almost performs tasks successfully with rate of
+three times more than \emph{High Availability Coalition} method
+because of real cooperative nature and task distribution of our
+algorithm. This result shows using web services as backups, and
+not as real collabrative players is a huge waste of web service
+capability since they have very low chance of getting jobs and its
+the primary web service (the first in their coordination chain)
+which does most of the work. The average quality of service of
+tasks performed is also better since our method considers all
+quality of service metrics mentioned in Table \ref{qosws}. Part(c)
+shows the availability of community from end user point of view.
+The \emph {High Availability Coalition} method almost has 100\%
+uptime since they use web services as backups, so the chance of
+job failing reduces significantly as community members increase.
+In our method we have more chance of fail for each web service,
+however with some subsiding, and hiring a few more web service
+they can compensate the low chance of failure of web services in
+our community.

### 2013-12-05 proposal/presentation/Faisal Proposal Presentation/faisal_presentation.tex
changes

\documentclass{beamer}
\usepackage[latin1]{inputenc,colortbl}
\usepackage{epsfig}
\usetheme{Frankfurt}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[page number]
%\newtheorem{definition}{Definition}
\title[Analyzing the Interaction between Knowledge and Social Commitment in Multi-Agent Systems]{Analyzing the Interaction between Knowledge and Social Commitments in Multi-Agent Systems}
\author{Faisal Al-Saqqar\\ \vspace{0.2cm} Supervised by: Dr. Jamal Bentahar}
\institute{Department of Computer Science and Software Engineering\\Concordia University}
\date{August 08, 2013}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame1 title page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\titlepage
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame2 outline page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item {\bf Introduction}
    	\item Background and Literature Review
    	\item Proposed Research
        \item Contributions and Research Activities
    	\item Time Line
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame3 introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%\section{Motivation}
\subsection{Multi-Agent Systems MASs}
    \begin{frame}{Motivation}
    \begin{itemize}
    \item In concrete applications such as business settings, agents should reason on their knowledge and their social commitments at the same time, particularly when they are engaged in conversations.
    \item Examples:
     \begin{itemize}
      \item \textbf{NetBill payment protocol}.
      \item \textbf{The travel agent}.
      \item \textbf{The car rental company}.
     \end{itemize}
\end{itemize}
\begin{figure}[htbp]
\centering
%\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
\includegraphics[width=1.0 \columnwidth]{figures/figure7.png}
%%\includegraphics[scale=0.5]{figure1}
%\caption{The NetBill payment protocol} \label{figure7}
\end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Problems and Research Questions}

\begin{itemize}
\item \textbf{How to analyze the interaction between knowledge and social commitments in MASs?}.
\item There is \textbf{no formal framework and semantics} available in the
literature that allow us to reason about knowledge and social commitments in MASs at the same time.

\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Continue: Problems and Research Questions}
 \begin{itemize}
   \item \textbf{How can we define a formal computational logic that can capture both knowledge and social commitments, so that properties involving both of them simultaneously can be expressed?}
        \begin{itemize}
         \item Combining logics of knowledge and commitments into one logic called Computation Tree Logic of Knowledge and Commitments (CTLKC).
        \end{itemize}
    \item \textbf{Is it enough to simply combine the current versions of knowledge and commitment logics?}
        \begin{itemize}
         \item Analyze the consistency of the CTLKC logic.
        \end{itemize}
    \item \textbf{What are the characteristics of the new logic that will combine knowledge and commitments?}
        \begin{itemize}
         \item The new logic should solve any inconsistency that might result from the combination of the two logics.
        \end{itemize}
\end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    \begin{frame}{Multi-Agent Systems MASs}
%        \begin{itemize}
%            \itemsep=.35cm
%        	\item Multi-Agent System (MAS).
%            %\item Autonomous agents.
%        	\item Knowledge in MASs.
%            \item Social commitments in MASs.
%        \end{itemize}
%\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}
\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item {\bf Background and Literature Review}
    	\item Proposed Research
        \item Contributions and Research Activities
    	\item Time Line
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame9 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Knowledge in MASs}
    \begin{frame}{Knowledge in MASs}

        \begin{itemize}
            \itemsep=.35cm
        	\item \textbf{Knowledge in MASs}.

             \begin{itemize}
              \item Hintikka and Lenzen.
              \item Kripke Models $M = (S, \{R_i\}_{i \in A}, V)$.
              \item Interpreted Systems.\\
              The formalism of interpreted systems is used to model the temporal evolution of a system of agents in order to reason about knowledge and temporal properties.\\
\textbf{Example:} ``Bob knows that it is sunny in Montreal".\\
This knowledge is denoted by $K_{Bob} \varphi$, where $\varphi$ means it is sunny in Montreal.
            \end{itemize}

        \end{itemize}

    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame10 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Social commitments in MASs}
    \begin{frame}{Commitments in MASs}
        Agent Communication Languages (ACLs).
        \begin{itemize}
            \itemsep=.35cm
        	\item \textbf{Commitments in MASs}
            \begin{itemize}
              \item \textbf{Mental Approaches}. \\Agents can read each other minds.
              \item \textbf{Social Approaches}. \\
              Formally, $C_{i\rightarrow j}\varphi$ means that agent $i$, the debtor (that makes the commitment), commits to agent $j$, the creditor (towards which the commitment is made), that $\varphi$ (the content of the commitment) holds. \\
              \textbf{Example:}  A customer $Cus$ commits to send payment to a merchant $Mer$. This commitment is denoted by $C_{Cus \rightarrow Mer} \varphi$, where $\varphi$ means send payment.

            \end{itemize}

        \end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame11 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Interpreted Systems}

    \begin{frame}{Interpreted Systems}
      \begin{itemize}
         \item A system is composed of a set of agents $ \mathcal{A}  =  \{  1, \dots, n  \} $.
         \item Each agent $i$ is described by:
                \begin{itemize}
                  \item A set of local states $L_i$.
                  \item A set of local actions $Act_i$.
                  \item A local protocol function $ P_i : L_i \rightarrow 2^{Act_i} $.
                  \item $ \tau_i $ is a local evolution function $ \tau_i : L_i \times Act_i \rightarrow L_i$.
                \end{itemize}
         \item ACT is the set of joint actions \\
          $ ACT = Act_1 \times \dots \times Act_n $
            \end{itemize}

    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame14 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Interpreted Systems}
    \begin{itemize}
    \item G is the set of all global states in the system \\
             $ G = L_1 \times \dots \times L_n$ is the Cartesian product of all local states of $n$ agents.
       \begin{itemize}
       \item A global state $ \mathfrak{g} = ( l_1, \dots,l_n) \in G$ represents a ``snapshot" of the system.
       \item The local state of agent $i$ in the global state $\mathfrak{g}$ is represented by the notation $ l_i(\mathfrak{g}) $.
       \end{itemize}
    \item The global evolution (transition) function can be defined as follows: $ \tau : G \times ACT \rightarrow G $.
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Extended Interpreted Systems}

\begin{itemize}
\item El-Menshawy et al. and Bentahar et al. extended the formalism of interpreted systems.
    \begin{itemize}
    \item Each agent $i \in \mathcal{A}$ is associated with a set of local
variables $Var_i$.
    \item A shared variable exists between two agents $i$ and $j$ iff $ Var_i \cap Var_j \neq \emptyset$, which means the existence of communication channel between the two agents.
        \end{itemize}
\end{itemize}
\begin{figure}[htbp]
\centering
%\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
\includegraphics[width=.70 \columnwidth]{figures/figure8.png}
%%\includegraphics[scale=0.5]{figure1}
\caption{The NetBill payment protocol} \label{figure8}
\end{figure}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame15 outline page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Computation Tree Logic of Knowledge (CTLK)}
\begin{definition} [Model of CTLK]\label{Model of CTLK}
A model $ \mathcal{M_K}$ $=(S,I,R_t,\{\approx_i|i\in \mathcal{ A}\}, \mathcal{V})$ that belongs to the set of all models $\mathbb{M}$ is a tuple, where:
\begin {itemize}
\item $ S \subseteq L_1 \times \dots \times L_n $ is the set of
reachable global states for the system.
\item $ I \subseteq S $ is a set of initial global states for the system.
\item $ R_t \subseteq S \times S $ is the transition relation defined by $( s,s') \in R_t $ iff there exists a joint action $( a_1, \dots , a_n) \in ACT $ such that $ \tau (s, a_1, \dots, a_n) = s'$.
\item For each agent $i \in \mathcal{A}$, $ \approx _i  \subseteq S \times S
$ is the epistemic accessibility relation defined by $ s \approx_i
s' $ iff $ l_i(s) = l_i(s') $.
\item $ \mathcal{V} : S \rightarrow 2 ^{\Phi_p} $ is a valuation function where $\Phi_p $ is a set of atomic propositions.
\end {itemize}
\label {dfn: Model of CTLK}
\end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Syntax of CTLK}
\begin{definition} [Syntax of CTLK]\label{Syntax of CTLK}~\\
$~~~~~~~~~~~~~ \varphi ::= p \mid \neg \varphi \mid \varphi \vee
\varphi \mid EX \varphi  \mid E ( \varphi U \varphi) \mid EG
\varphi \mid K_i \varphi$\\
Where:
\begin{itemize}
\item $ p \in \Phi_p$ is an atomic proposition; \item The boolean
connectives $\neg$, and $\vee$ are defined in the usual way; \item
$E$ is the existential quantifier on paths; \item $X$, $U$, and
$G$ are CTL path modal connectives standing for ``next", ``until",
and ``globally" respectively; and \item The modal connective $K_i$
stands for ``knowledge for agent $i$".
\end{itemize}
\label {dfn: Syntax of CTLK}
\end{definition}
In this logic, \textbf{$K_i \varphi$ is read as ``agent $i$ knows
$\varphi"$.}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Satisfaction of CTLK}
\begin{definition} [Satisfaction of CTLK]~\\
Given the model $ \mathcal M$, the satisfaction of a CTLK formula
$ \varphi$ in a global state $ s$, denoted by $ (\mathcal M, s )
\models \varphi$, is recursively defined as follows:

\begin{itemize}
\item $ (\mathcal{M}, s ) \models p$ iff $ p \in \mathcal{V}(s)$;
\item $ (\mathcal{M}, s ) \models \neg \varphi$ iff $ (\mathcal{M}, s ) \nvDash \varphi$;
\item $ (\mathcal{M}, s ) \models \varphi \vee \psi$ iff $(\mathcal{M}, s ) \models \varphi$ or $(\mathcal{M}, s ) \models \psi$;
\item $ (\mathcal{M}, s ) \models EX \varphi $ iff there exists a path $\pi$ starting at $s$ such that $ (\mathcal{M}, \pi(1) ) \models \varphi$;
\item $ (\mathcal{M}, s ) \models E ( \varphi U \psi)$ iff there exists a path $\pi$ starting at $s$ such that for some $ k \geq 0$,
$ (\mathcal{M}, \pi(k) ) \models \psi$ and $ (\mathcal{M}, \pi(j) ) \models \varphi$ for all $ 0 \leq j < k$;

\end{itemize}
\label {dfn: Satisfaction of CTLK}
\end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Satisfaction of CTLK}
\begin{definition} [Satisfaction of CTLK]~\\
\begin{itemize}
\item $ (\mathcal{M}, s ) \models EG \varphi$ iff there exists a path $\pi$  starting at $s$ such that $ (\mathcal{M}, \pi(k) ) \models \varphi$ for all $ k \geq 0$;
\item $ (\mathcal{M}, s ) \models K_i \varphi $ iff for all global states $s' \in S$ such that $s \approx_i s'$, we have $(\mathcal{M}, s' ) \models \varphi $.
\end{itemize}
\label {dfn: Satisfaction of CTLK}
\end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Computation Tree Logic of Commitment (CTLC)}
CTLC logic is an extension of CTL logic with modalities for reasoning about \textbf{commitments and their fulfillment}.
\begin{definition} [Model of CTLC]\label{Model of CTLC}
A model $\mathcal{M_C}=(S,I,R_t, \{\sim _{i \rightarrow j}|{(i,j)\in \mathcal{A}^2}\},\mathcal{V})$ that belongs to the set of all models $\mathbb{M}$ is a tuple, where:
\begin {itemize}
\item $S, I, R_t$ and $\mathcal{V}$ are the same as in Definition (Model of CTLK).
\item For each pair $(i, j) \in \mathcal{A}^2 $, $\sim _{i \rightarrow j} \subseteq S \times S $ is the social accessibility relation defined by $ s \sim _{i \rightarrow j} s' $ iff
     1) $ l_i(s) = l_i(s') $ and 2) $ Var_i \cap Var_j \neq \emptyset $ such that  $ \forall x \in Var_i \cap Var_j $ we have $ l_i^x(s) = l_j^x(s') $ and $ \forall y \in Var_j - Var_i $ we have $ l_j^y(s) = l_j^y(s')$.

\end {itemize}
\label {dfn: Model of CTLC}
\end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame} {Syntax of CTLC}
\begin{definition}[Syntax of CTLC]~\\
$ ~~~~~~~~~~~~~\varphi ::= p \mid \neg \varphi \mid \varphi \vee
\varphi \mid EX \varphi  \mid E ( \varphi U \varphi) \mid EG
\varphi \mid C_{i\rightarrow j} \varphi \mid Fu (C_{i\rightarrow
j}\varphi)$.
\label {dfn: Syntax of CTLC}\\
Where:
\begin{itemize}
  \item $ p, E, X, G, U, \neg $ and $\vee$ are defined as in Definition (Syntax of CTLK);
  \item The modal connective $C_{i \rightarrow j}$ stands for ``commitment from $i$ to $j$"; and
  \item The modal connective $Fu$ stands for ``fulfillment".
\end{itemize}
\end{definition}
\textbf{In this logic, $C_{i\rightarrow j}\varphi$ is read as ``agent $i$ commits towards agent $j$ to bring about $\varphi$". $Fu (C_{i\rightarrow j}\varphi)$ is read as ``the commitment $C_{i\rightarrow j}\varphi$ is fulfilled".}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame} {Satisfaction of CTLC}
As the main fragment of CTLC logic is the CTL logic, hereafter, we only recall the semantics of the commitment and fulfillment modalities.
\begin{itemize}
\item $ (\mathcal{M_C}, s ) \models C_{i\rightarrow j} \varphi $ iff for all global states $ s' \in S $ such that $ s \sim_{i \rightarrow j} s' $, we have $ (\mathcal{M_C}, s' ) \models \varphi $;
\item $ (\mathcal{M_C}, s ) \models Fu (C_{i\rightarrow j} \varphi)$ iff there exists $ s' \in S $ such that $ s' \sim_{i \rightarrow j} s $ and $ (\mathcal{M_C}, s' ) \models C_{i\rightarrow j} \varphi$.
\end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Research}
\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item {\bf Proposed Research}
        \item Contribution and Research Activities
    	\item Time Line
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame16 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Combining Logics}

\begin{frame}{A schematic view of our approach}

\begin{figure}[htbp]
\centering
%\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
\includegraphics[width=1.05 \columnwidth]{figures/figure9.png}
%%\includegraphics[scale=0.5]{figure1}
%\caption{Our approach} %\label{figure9}
\end{figure}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{frame}{Combining Logics}
Given \textbf{two logics} $L_1$ and $L_2$, their \textbf{languages} $\mathcal{L}_1$ and $\mathcal{L}_2$, and their
\textbf{axiomatic systems} $\mathcal{X}_1$ and $\mathcal{X}_2$, the logic
$L_1 \otimes L_2$ is the smallest logic with the following
characteristics:
\begin{itemize}
  \item The language $\mathcal{L}_{L_1\otimes L_2}$ is the union of $\mathcal{L}_{L_1}$ and $\mathcal{L}_{L_2}$.
  \item The logic $L_1 \otimes L_2$ is axiomatised by the set of axioms $\mathcal{X}_1 \cup \mathcal{X}_2$.
\end{itemize}
If the logics $L_1$ and $L_2$ are interpreted using Kripke frames
$F_1 = (S, R_1^1, \dots, R_n^1)$ and $F_2 = (S, R_1^2, \dots
,R_m^2 )$ where $R^1_{x/x\in[1,n]}$ and $R^2_{y/y\in[1,m]}$ are
\textbf{accessibility relations}, then the semantics for $L_1 \otimes L_2$
can be defined in the Kripke frame $F =(S, R_1^1, \dots , R_n^1,
R_1^2, \dots ,R_m^2 )$ obtained by the \textit{independent join} of the two
frames $F_1$ and $F_2$.
    \end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame17 Proposed Research
\begin{frame} {Model of CTLKC}
\begin{definition} [Model of CTLKC]\label{Model of CTLKC}
A model $\mathcal{M}=(S,I,R_t,\{\approx_i|i\in \mathcal{ A}\},\{\sim _{i \rightarrow j}|{(i,j)\in \mathcal{A}^2}\},\mathcal{V})$ that belongs to the set of all models $\mathbb{M}$ is a tuple, where:
\begin {itemize}
\item $S, I, R_t$ and $\mathcal{V}$ are the same as in Definition (Model of CTLK);
\item For each agent $i \in \mathcal{A}$, $ \approx _i  \subseteq S \times S
$ is the epistemic accessibility relation defined by $ s \approx_i
s' $ iff $ l_i(s) = l_i(s') $;
\item For each pair $(i, j) \in \mathcal{A}^2 $, $\sim _{i \rightarrow j} \subseteq S \times S $ is the social accessibility relation defined by $ s \sim _{i \rightarrow j} s' $ iff
     1) $ l_i(s) = l_i(s') $ and
     2) $ Var_i \cap Var_j \neq \emptyset $ such that  $ \forall x \in Var_i \cap Var_j $ we have $ l_i^x(s) = l_j^x(s') $ and $ \forall y \in Var_j - Var_i $ we have $ l_j^y(s) = l_j^y(s')$;
\item $ \mathcal{V} : S \rightarrow 2 ^{\Phi_p} $ is a valuation function where $\Phi_p $ is a set of atomic propositions.
\end {itemize}
\label {dfn: Model of CTLKC}
\end{definition}
 \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame} {Syntax of CTLKC}

\begin{definition}[Syntax of CTLKC]~\\
$ ~~~~~~~~~~~~~\varphi ::= p \mid \neg \varphi \mid \varphi \vee
\varphi \mid EX \varphi  \mid E ( \varphi U \varphi) \mid EG
\varphi\mid K_i \varphi \mid C_{i\rightarrow j} \varphi \mid Fu
(C_{i\rightarrow j}\varphi)$. \label {dfn: Syntax of CTLKC}
\end{definition}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame18 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Selection Criteria}
We propose the following criteria based on \textbf{common intuitions}:
\begin{itemize}
%\begin{enumerate}
  \item It should not be the case that an agent commits about everything he knows to others.
  \item It should not be the case that an agent commits about everything known by others.
  \item An agent should know about his own commitment.
  \item An agent should be aware of any commitment directed towards him.
  \item An agent should know the content of his fulfilled commitment.
  \item An agent should know the content of any fulfilled commitment directed towards him.

\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Continue: Selection Criteria}
\begin{itemize}
 \item An agent should know about the fulfillment of his commitment.
 \item An agent should know about the fulfillment of any commitment directed towards him.
  \item A sincere agent should know (i.e., believe) the content of his own commitment.
  \item A sincere agent should fulfill his commitment.
  \item A liar agent could not know (i.e., believe) the content of his commitment.
  \item If an agent knows about his own commitment, then this commitment should exist, which means an agent should not know about a non-existing commitment.
\end{itemize}
%\end{enumerate}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Running Example: NetBill Payment Protocol}
%
\begin{figure}[htbp]
\centering
%\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
\includegraphics[width=.75 \columnwidth]{figures/figure1.png}
%%\includegraphics[scale=0.5]{figure1}
%\caption{The NetBill payment protocol} \label{figure1}
\end{figure}
\begin{itemize}
\item $C_{Cus \rightarrow Mer}$ $sendPayment$.
 \item $C_{Mer \rightarrow Cus}$ $deliverGoods$.
 \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame19 Proposed Research
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Desiderata of Paradoxes}

\begin{frame}{Desiderata of Paradoxes}
Paradoxes are represented as reasoning rules that are: 1) not reasonable in
open MAS, but they are valid in CTLKC; or 2) desirable for the
interaction between knowledge and commitments, but they can get
violated in CTLKC because they are not valid.
 \begin{enumerate}

\vspace{0.2cm} \item [P1.]\textbf{[Committing everything known to
others]}

$K_i \varphi \Rightarrow C_{i \rightarrow j}\varphi, $ for all $j
\in A$ where $i \neq j$.

\textbf{ Meaning:} An agent (the debtor) commits towards all other
agents (the creditors) about what he knows.\\
\textbf{Example 1:}
$K_{Mer}$ $deliverGoods \Rightarrow$ $C_{Mer \rightarrow
Cus}$ $deliverGoods$.

\vspace{0.2cm} \item [P2.]\textbf{[Committing everything known by
others]}

 $ K_i K_j \varphi \Rightarrow C_{i \rightarrow j} \varphi$ such that $ i \neq j$.

\textbf{Meaning:} An agent (the debtor) commits toward another
agent (the creditor) to bring about what he (i.e., the debtor)
knows about the creditor's knowledge.\\
\textbf{Example 2:}
$K_{Cus} K_{Mer}$ $deliverGoods \Rightarrow$ $C_{Cus \rightarrow Mer}$
$deliverGoods$.

\end{enumerate}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame20 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Continue: Desiderata of Paradoxes}
 \begin{enumerate}
\vspace{0.2cm} \item [P3.][\textbf{Committing everything known
from others}]
$ K_i K_j \varphi \Rightarrow C_{j \rightarrow i} \varphi$ such that $ i \neq j$.

\textbf{Meaning:} An agent (the debtor) commits toward another
agent (the creditor) to bring about what the creditor knows about
the debtor's knowledge.\\
\textbf{Example 3:}\\
$K_{Cus} K_{Mer}$ $deliverGoods \Rightarrow$ $C_{Mer \rightarrow Cus}$
$deliverGoods$.

\vspace{0.2cm} \item [P4.][\textbf{Knowing about his own
commitment}]

$C_{i\rightarrow j} \varphi \Rightarrow K_i (C_{i\rightarrow j}
\varphi) $ where $i \neq j$.

\textbf{Meaning:} An agent knows about his commitment.

\textbf{Example 4:}\\
$C_{Cus \rightarrow Mer}$ $sendPayment $ $\Rightarrow K_{Cus}$ $(C_{Cus \rightarrow Mer}$ $sendPayment)$.
\end{enumerate}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Continue: Desiderata of Paradoxes}

\begin{figure}[htbp]
    \begin{center}
%\includegraphics[width=10cm, height=5cm]{figures/figure2.eps}
    \includegraphics[width=.75 \columnwidth]{figures/figure2.png}
   % \caption{Model 1} \label{figure2}
    \end{center}
    \end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Continue: Desiderata of Paradoxes}
\begin{enumerate}
\vspace{0.2cm} \item [P5.][\textbf{Knowing the content of his own
fulfilled commitment}]

$Fu (C _{i\rightarrow j} \varphi) \Rightarrow K _i \varphi$ where
$i \neq j$.

\textbf{Meaning:} An agent knows the content of his fulfilled
commitment.\\
\textbf{Example 5:}\\
$Fu (C _{Cus\rightarrow Mer} sendPayment) \Rightarrow K_{Cus}$ $sendPayment$.
\begin{figure}[htbp]
    \begin{center}
%\includegraphics[width=10cm, height=5cm]{figures/figure2.eps}
    \includegraphics[width=.75 \columnwidth]{figures/figure3.png}
   % \caption{Model 2} \label{figure3}
    \end{center}
    \end{figure}

\end{enumerate}     	
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame23 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 \begin{frame}{Continue: Desiderata of Paradoxes}
 \begin{enumerate}

\vspace{0.2cm} \item [P6.][\textbf{Knowing the content of the
other's fulfilled commitment}]

$Fu (C _{i\rightarrow j} \varphi) \Rightarrow K_j \varphi$ where
$i \neq j$.

\textbf{Meaning:} The creditor knows the content of the debtor's
fulfilled commitment.\\
\textbf{Example 6:}\\
$ Fu (C_{cust \rightarrow Mer}$ $sendPayment)$ $\Rightarrow $ $k_{Mer} sendPayment$.
	\begin{figure}[htbp]
\begin{center}
%\includegraphics[width=12cm, height=5cm]{figures/figure4.eps}
\includegraphics[width=.70 \columnwidth]{figures/figure4.png}
%\caption{Model 3} \label{figure4}
\end{center}
\end{figure}
\end{enumerate}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame24 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Continue: Desiderata of Paradoxes}
\begin{enumerate}
    \vspace{0.2cm} \item [P7.][\textbf{Knowing the commitment of the
other}]

$C_{i\rightarrow j} \varphi \Rightarrow AF K_j (C_{i\rightarrow j}
\varphi) $ where $i \neq j$.

\textbf{Meaning:} An agent should be aware of any commitments
directed towards him.\\
\textbf{Example 7:}\\
$C_{Mer \rightarrow Cus}$ $deliverGoods$ $\Rightarrow $ $AF K_{Cus}(C_{Mer \rightarrow Cus}$
$deliverGoods$).
\begin{figure}[htbp]
\centering
\includegraphics[width=.50 \columnwidth]{figures/figure5.png}
%\includegraphics[width=12cm, height=7cm]{figures/figure5.eps}
%\includegraphics[scale=0.5]{figure4.eps}
%\caption{Model 4} \label{figure5}
\end{figure}

\end{enumerate}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Continue: Desiderata of Paradoxes}
\begin{enumerate}
    \vspace{0.2cm} \item [P8.][\textbf{Knowing the fulfillment of his
own commitment}]

$Fu(C _{i\rightarrow j} \varphi) \Rightarrow K_i Fu(C
_{i\rightarrow j} \varphi)$ where $i \neq j$.

\textbf{Meaning:} The agent knows that he fulfills his commitment.\\
\textbf{Example 8:}\\
$Fu(C_{Cus\rightarrow Mer} sendPayment)\Rightarrow K_{Cus}Fu(C_{Cus \rightarrow Mer} sendPayment)$.

\vspace{0.2cm} \item [P9.][\textbf{Knowing the fulfillment of the
debtor's commitment}]

$Fu(C _{i\rightarrow j} \varphi) \Rightarrow K_j Fu(C_{i\rightarrow j} \varphi)$ where $i \neq j$.

\textbf{Meaning:} The creditor knows that the debtor fulfills his
commitment.\\
\textbf{Example 9:}\\
$Fu(C_{Cus \rightarrow Mer} sendPayment)\Rightarrow K_{Mer} Fu(C_{Cus \rightarrow Mer} sendPayment)$.
\end{enumerate}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame25 outline page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{CTLKC properties}
\begin{frame}{CTLKC properties}
In addition to the properties of knowledge (in CTLK) and commitments (in CTLC), those properties hold in CTLKC:
\begin{enumerate}

\vspace{0.2cm} \item [Prop 1.] $C_{i \rightarrow j}\varphi
\Rightarrow \varphi$ is satisfiable but not valid.
\vspace{0.2cm} \item [Prop 2.] $C_{i \rightarrow j}\varphi
\Rightarrow K_i \varphi$ is satisfiable but not valid.
\vspace{0.2cm} \item [Prop 3.] $(C_{i \rightarrow j}\varphi \wedge
K_i (\varphi \Rightarrow \psi)) \Rightarrow C_{i \rightarrow j}
\psi$ is valid.
\vspace{0.2cm} \item [Prop 4.] $(C_{i \rightarrow j}(\varphi
\Rightarrow \psi) \wedge K_i \varphi) \Rightarrow C_{i \rightarrow
j} \psi$ is valid.
\vspace{0.2cm} \item [Prop 5.] $(C_{i \rightarrow j}\varphi \wedge
K_j (\varphi \Rightarrow \psi)) \Rightarrow C_{i \rightarrow j}
\psi$ is satisfiable but not valid.
\vspace{0.2cm} \item [Prop 6.] $(C_{i \rightarrow j}(\varphi
\Rightarrow \psi) \wedge K_j \varphi) \Rightarrow C_{i \rightarrow
j} \psi$ is satisfiable but not valid

\end{enumerate}
\end{frame}

\section{Research Activities}
\begin{frame}{Contribution and Research Activities}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item Proposed Research
        \item {\bf Contribution and Research Activities}
    	\item Time Line
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame26 Contribution and Research Activities %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contributions}
    \begin{frame}{Contributions}

    \begin{itemize}
     \itemsep=.35cm
     \item A new combined temporal logic, called CTLKC, that combines both CTLK and CTLC logics is introduced.
     \item This logic served as a language to express a set of rules that are used to reason about the interaction between knowledge and social commitments.
     \item Selection criteria are proposed to capture such reasoning rules.
     \item Nine paradoxes are recognized in CTLKC logic that should be addressed in any consistent logic combining knowledge and commitments.
     \item Six properties are identified and should be met in any logic combining knowledge and commitments.
        \end{itemize}

    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame27 Contribution and Research Activities

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame30 outline page
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Milestones}
\begin{frame}{Milestones}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item Proposed Research
        \item Contribution and Research Activities
    	\item {\bf Time Line}
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Research Activities Goal}
    \begin{frame}{Research Activities Goal}
    We aim to cover all possible relations between knowledge and commitments as single and group interactions by:

        \begin{itemize}
              \item Defining a new consistent logic that combines knowledge and commitments and solves the nine paradoxes while satisfying the six properties.
              \item Addressing the model checking problem of the new logic from both algorithmic and complexity perspectives.
              \item Implementing the new model checking algorithms on top of MCMAS+.
              \item Identifying a new semantics for group committing.
              \item Adding the group knowledge to the framework.
        \end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time Line}
    \begin{frame}{Time Line}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=.65 \columnwidth]{figures/figure6.png}
%\includegraphics[width=16cm, height=21cm]{figures/figure6.eps}
%\caption{Schedule time of research} \label{figure6}
\end{center}
\end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame27 Milestones %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Publications}

1- Submitted a journal paper entitled ``\textbf{Interaction between knowledge and Social Commitments in MASs}", Applied Intelligence Journal, Springer.\\

%\centering
%\begin{itemize}
%\item \textbf{Questions Please !}
%\end{itemize}

\end{frame}

\end{document}

### 2013-12-09 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

--- 2013-12-05 proposal/presentation/Faisal Proposal Presentation/faisal_presentation.tex
@@
 %\newtheorem{definition}{Definition}
-\title[Analyzing the Interaction between Knowledge and Social Commitment in Multi-Agent Systems]{Analyzing the Interaction between Knowledge and Social Commitments in Multi-Agent Systems}
-\author{Faisal Al-Saqqar\\ \vspace{0.2cm} Supervised by: Dr. Jamal Bentahar}
+\title[Cooperative Decision Making for Communities of Autonomous Web Services]{Cooperative Decision Making for Communities of Autonomous Web Services}
+\author{Ehsan Khosrowshahi Asl\\ \vspace{0.2cm} Supervised by: \\Dr. Jamal Bentahar \\Dr. Hadi Otrok}
 \institute{Department of Computer Science and Software Engineering\\Concordia University}
-\date{August 08, 2013}
+\date{December 17, 2013}
 \begin{document}
@@
 %\section{Motivation}
-\subsection{Multi-Agent Systems MASs}
+\subsection{Motivation}
     \begin{frame}{Motivation}
     \begin{itemize}
-    \item In concrete applications such as business settings, agents should reason on their knowledge and their social commitments at the same time, particularly when they are engaged in conversations.
-    \item Examples:
+        \item High reliance on web services, created high competition and great business opportunities for online service developers 
+        \item Community goals:
         \begin{itemize}
-      \item \textbf{NetBill payment protocol}.
-      \item \textbf{The travel agent}.
-      \item \textbf{The car rental company}.
+            \item \textbf{User satisfaction, Service quality, high availability and responsiveness}.
+            \item \textbf{Web Service Discovery over Internet}.
         \end{itemize}
@@
 \begin{itemize}
-\item \textbf{How to analyze the interaction between knowledge and social commitments in MASs?}.
-\item There is \textbf{no formal framework and semantics} available in the
-literature that allow us to reason about knowledge and social commitments in MASs at the same time.
+    \item \textbf{How can we model the
+        community of agent-based services in order to maximize the utility
+        of involved users, web services and community organizers?}.
+        \begin{itemize}
+            \item Most of the recent work on communities of
+            services are either user-centric and focus on user satisfaction
+            or system-centric and focus on the whole system throughput, performance and utilization.
+        \end{itemize}
+
+    \item \textbf{How can we model fair and stable communities as coalitions
+        of agent-based web services?}.
+        \begin{itemize}
+            \item All parties involved are self-interest agents and have the authority to deviate leave the community if they can improve their income in some other ways.
+        \end{itemize}
 
@@
  \begin{itemize}
-   \item \textbf{How can we define a formal computational logic that can capture both knowledge and social commitments, so that properties involving both of them simultaneously can be expressed?}
+   \item \textbf{How can we model and analyze the cooperation
+        among the community members in realistic, applicable and practical
+        settings?}
         \begin{itemize}
-         \item Combining logics of knowledge and commitments into one logic called Computation Tree Logic of Knowledge and Commitments (CTLKC).
+            \item Modeling the preference and valuation functions considering the worth of all subsets of players in realistic cooperative scenarios
+            \item Solution concepts complexity issues
         \end{itemize}
-    \item \textbf{Is it enough to simply combine the current versions of knowledge and commitment logics?}
-        \begin{itemize}
-         \item Analyze the consistency of the CTLKC logic.
-        \end{itemize}
-    \item \textbf{What are the characteristics of the new logic that will combine knowledge and commitments?}
-        \begin{itemize}
-         \item The new logic should solve any inconsistency that might result from the combination of the two logics.
-        \end{itemize}
+
 \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Knowledge in MASs}
-    \begin{frame}{Knowledge in MASs}
-
+\subsection{Communities of Web Services}
+    \begin{frame}{Community of Web Services}
+        Communities of Web Services
         \begin{itemize}
-            \itemsep=.35cm
-        	\item \textbf{Knowledge in MASs}.
-
-             \begin{itemize}
-              \item Hintikka and Lenzen.
-              \item Kripke Models $M = (S, \{R_i\}_{i \in A}, V)$.
-              \item Interpreted Systems.\\
-              The formalism of interpreted systems is used to model the temporal evolution of a system of agents in order to reason about knowledge and temporal properties.\\
-\textbf{Example:} ``Bob knows that it is sunny in Montreal".\\
-This knowledge is denoted by $K_{Bob} \varphi$, where $\varphi$ means it is sunny in Montreal.
+            \item Ease and improve the process of Web services discovery in an open environment like the Internet
+        	\item Improve service quality, availability and responsiveness
         \end{itemize}
 
-        \end{itemize}
+        \begin{figure}[htbp]
+            \centering
+            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
+            \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
+            %%\includegraphics[scale=0.5]{figure1}
+            %\caption{The NetBill payment protocol} \label{figure7}
+        \end{figure}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Social commitments in MASs}
-    \begin{frame}{Commitments in MASs}
-        Agent Communication Languages (ACLs).
+%\subsection{Social commitments in MASs}
+    \begin{frame}{Communities of Web Services}
+        Communities of Web Services
         \begin{itemize}
             \itemsep=.35cm
-        	\item \textbf{Commitments in MASs}
+        	\item \textbf{Communities of web services operations}
             \begin{itemize}
-              \item \textbf{Mental Approaches}. \\Agents can read each other minds.
-              \item \textbf{Social Approaches}. \\
-              Formally, $C_{i\rightarrow j}\varphi$ means that agent $i$, the debtor (that makes the commitment), commits to agent $j$, the creditor (towards which the commitment is made), that $\varphi$ (the content of the commitment) holds.
-\\
-              \textbf{Example:}  A customer $Cus$ commits to send payment to a merchant $Mer$. This commitment is denoted by $C_{Cus \rightarrow Mer} \varphi$, where $\varphi$ means send payment.
-
+              \item Community Development
+              \item Web Services Attraction and Retention
+              \item Web Service Selection
+            \end{itemize}                      	      	
         \end{itemize}
 
-        \end{itemize}
-
+        \begin{figure}[htbp]
+            \centering
+            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
+            \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
+            %%\includegraphics[scale=0.5]{figure1}
+            %\caption{The NetBill payment protocol} \label{figure7}
+        \end{figure}
     \end{frame}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Interpreted Systems}
+\subsection{Cooperative Game Theory}
 
-    \begin{frame}{Interpreted Systems}
+    \begin{frame}{Cooperative Game Theory}
       \begin{itemize}
-         \item A system is composed of a set of agents $ \mathcal{A}  =  \{  1, \dots, n  \} $.
-         \item Each agent $i$ is described by:
+         \item Cooperative games are a branch of game theory that models cooperation or collaboration between agents.   
          \begin{itemize}
-                  \item A set of local states $L_i$.
-                  \item A set of local actions $Act_i$.
-                  \item A local protocol function $ P_i : L_i \rightarrow 2^{Act_i} $.
-                  \item $ \tau_i $ is a local evolution function $ \tau_i : L_i \times Act_i \rightarrow L_i$.
+            \item A set of tasks needs to be performed, they require different expertise.
+            \item Agents do not have enough resource on their own to perform a task.
+            \item Find complementary agents to perform the tasks.
+            \begin{itemize}
+                \item robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
+                \item transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
             \end{itemize}
-         \item ACT is the set of joint actions \\
-          $ ACT = Act_1 \times \dots \times Act_n $
+        \end{itemize}      
+        \item \textbf{issues:}
+            \begin{itemize}
+                \item What coalition to form?
+                \item How to reward each each member when a task is completed?
+            \end{itemize}
+      \end{itemize}
+    \end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame14 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{The classic problem}
+    We have a population $N$ of $n$ agents.    
+    \begin{definition} [Coalition]~\\
+       A coalition $C$ is a set of agents: $C \in 2^N$.
+        \begin{itemize}
+            \item $N$ is the set of all agents (or players)
+            \item $v:2^N \rightarrow R$ is the \emph{valuation function}. For $C \subseteq N$, $v(C)$ is the value obtained by the coalition $C$
+        \end{itemize}
+        \label {dfn:Coalition}
+    \end{definition}
+
+    \begin{itemize}        
+        \item \textbf{problem:} a game $(N,v)$, and we assume all agents in $N$ want to cooperate.
+        \item \textbf{solution:} a payoff distribution $x \in R^n$ that provides a value to individual agents.
+
+        \begin{itemize}
+            \item What are the interesting properties that $x$ should satisfy?
+            \item How to determine the payoff vector $x$?
         \end{itemize}
 
-    \end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame14 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Interpreted Systems}
-    \begin{itemize}
-    \item G is the set of all global states in the system \\
-             $ G = L_1 \times \dots \times L_n$ is the Cartesian product of all local states of $n$ agents.
-       \begin{itemize}
-       \item A global state $ \mathfrak{g} = ( l_1, \dots,l_n) \in G$ represents a ``snapshot" of the system.
-       \item The local state of agent $i$ in the global state $\mathfrak{g}$ is represented by the notation $ l_i(\mathfrak{g}) $.
-       \end{itemize}
-    \item The global evolution (transition) function can be defined as follows: $ \tau : G \times ACT \rightarrow G $.
     \end{itemize}
@@
 
-\begin{frame}{Extended Interpreted Systems}
+\begin{frame}{An Example}
 
-\begin{itemize}
-\item El-Menshawy et al. and Bentahar et al. extended the formalism of interpreted systems.
-    \begin{itemize}
-    \item Each agent $i \in \mathcal{A}$ is associated with a set of local
-variables $Var_i$.
-    \item A shared variable exists between two agents $i$ and $j$ iff $ Var_i \cap Var_j \neq \emptyset$, which means the existence of communication channel between the two agents.
-        \end{itemize}
-\end{itemize}
-\begin{figure}[htbp]
-\centering
-%\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
-\includegraphics[width=.70 \columnwidth]{figures/figure8.png}
-%%\includegraphics[scale=0.5]{figure1}
-\caption{The NetBill payment protocol} \label{figure8}
-\end{figure}
+    \begin{center}
+        $N = \{1,2,3\}$ \\
+        $v(\{1\}) = 0, v(\{2\}) = 0, v(\{3\}) = 0$ \\
+        $v(\{1,2\}) = 90, v(\{1,3\}) = 80, v(\{2,3\}) = 70$ \\
+        $v(\{1,2,3\}) = 105$ \\
+    \end{center}
 

### 2013-12-09 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{The classic problem}
+\begin{frame}{The Classic Problem}
     We have a population $N$ of $n$ agents.
@@
         $v(\{1\}) = 0, v(\{2\}) = 0, v(\{3\}) = 0$ \\
-        $v(\{1,2\}) = 90, v(\{1,3\}) = 80, v(\{2,3\}) = 70$ \\
+        $v(\{1,2\}) = 90$ \\ 
+        $v(\{1,3\}) = 80$ \\ 
+        $v(\{2,3\}) = 70$ \\
         $v(\{1,2,3\}) = 105$ \\
     \end{center}
+
+    What should we do?
+    \begin{itemize}
+        \item form $\{1,2,3\}$ and share equally $(35,35,35)$?
+        \item 3 can say to 1 ``let's form $\{1,3\}$ and share (40,0,40)''
+        \item 2 can say to 1 ``let's form $\{1,2\}$ and share (45,45,0)''
+        \item 3 can say to 2 ``OK, let's form $\{2,3\}$ and share (0,46,24)''
+        \item 1 can say to 2 and 3, ``fine! $\{1,2,3\}$ and (33,47,25)''
+        \item ...what is a good solution?
+    \end{itemize}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Computation Tree Logic of Knowledge (CTLK)}
-\begin{definition} [Model of CTLK]\label{Model of CTLK}
-A model $ \mathcal{M_K}$ $=(S,I,R_t,\{\approx_i|i\in \mathcal{ A}\}, \mathcal{V})$ that belongs to the set of all models $\mathbb{M}$ is a tuple, where:
-\begin {itemize}
-\item $ S \subseteq L_1 \times \dots \times L_n $ is the set of
-reachable global states for the system.
-\item $ I \subseteq S $ is a set of initial global states for the system.
-\item $ R_t \subseteq S \times S $ is the transition relation defined by $( s,s') \in R_t $ iff there exists a joint action $( a_1, \dots , a_n) \in ACT $ such that $ \tau (s, a_1, \dots, a_n) = s'$.
-\item For each agent $i \in \mathcal{A}$, $ \approx _i  \subseteq S \times S
-$ is the epistemic accessibility relation defined by $ s \approx_i
-s' $ iff $ l_i(s) = l_i(s') $.
-\item $ \mathcal{V} : S \rightarrow 2 ^{\Phi_p} $ is a valuation function where $\Phi_p $ is a set of atomic propositions.
-\end {itemize}
-\label {dfn: Model of CTLK}
+\begin{frame}{Transferable and Non Transferable Utility Games}
+    \begin{itemize}
+        \item \textbf{Games with Transferable Utility (TU games)}
+        \begin{itemize}
+            \item Utility is worth the same for all agents
+            \item Utility can be {\color{red} compared} or {\color{red} transfered} between agents.
+            \item Irrespective of the division of the coalitional payoff, members of the coalition enjoy the same total utility.
+        \end{itemize}
+
+        \begin{definition} [Valuation or Characteristic function]\label{dfn:valuationfunction}
+            A \emph{valuation function v} associates a real number $v(C)$ to any subset $C \subseteq N$, i.e., $v:2^N \rightarrow R$ \\
+            A {\color{blue}\emph{TU game}} is a pair $(N,v)$ where $N$ is a set of agents and where $v$ is a valuation function.
+            \label {dfn:valuationfunction}
         \end{definition}
+
+        \item \textbf{Games with Non Transferable Utility (NTU games)} \\
+            Agents have different preferences over coalitions and rewards. Non-monetary rewards, i.e. item allocation type of problems where items have different values for different players.
+    \end{itemize}
+
 \end{frame}

### 2013-12-10 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Syntax of CTLK}
-\begin{definition} [Syntax of CTLK]\label{Syntax of CTLK}~\\
-$~~~~~~~~~~~~~ \varphi ::= p \mid \neg \varphi \mid \varphi \vee
-\varphi \mid EX \varphi  \mid E ( \varphi U \varphi) \mid EG
-\varphi \mid K_i \varphi$\\
-Where:
+\begin{frame}{Some properties of valuation functions}
+    $\forall C_1,C_2 \subseteq N | C_1 \bigcap C_2 = \emptyset, i \in N, i \notin C_1$
     \begin{itemize}
-\item $ p \in \Phi_p$ is an atomic proposition; \item The boolean
-connectives $\neg$, and $\vee$ are defined in the usual way; \item
-$E$ is the existential quantifier on paths; \item $X$, $U$, and
-$G$ are CTL path modal connectives standing for ``next", ``until",
-and ``globally" respectively; and \item The modal connective $K_i$
-stands for ``knowledge for agent $i$".
+        \item {\color{red} additive:} $v(C_1 \bigcup C_2) = v(C_1) + v(C_2)$
+        \item {\color{red} super additive:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2)$ This is satisfied is many applications, or bigger coalitions will not form.
+        \item {\color{red} weekly super additive:} $v(C_1 \bigcup \{i\}) \geq v(C_1) + v(\{i\})$
+        \item {\color{red} subadditive:} $v(C_1 \bigcup C_2) \leq v(C_1) + v(C_2)$
     \end{itemize}
-\label {dfn: Syntax of CTLK}
-\end{definition}
-In this logic, \textbf{$K_i \varphi$ is read as ``agent $i$ knows
-$\varphi"$.}
+
+    $\forall C_1,C_2 \subseteq N$
+    \begin{itemize}
+        \item {\color{red} convex:} $v(C_1) + v(C_2) \leq v(C_1 \bigcup C_2) + v(C_1 \bigcap C_2)$ Convexity has important properties in cooperative game theory solution concepts.
+    \end{itemize}
 \end{frame}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Satisfaction of CTLK}
-\begin{definition} [Satisfaction of CTLK]~\\
-Given the model $ \mathcal M$, the satisfaction of a CTLK formula
-$ \varphi$ in a global state $ s$, denoted by $ (\mathcal M, s )
-\models \varphi$, is recursively defined as follows:
+\begin{frame}{Solution properties}
+    Let $x \in R^n$ be a solution of the TU game $(N,v)$
+    \begin{itemize}
+        \item {\color{red} Feasible solution:} $\sum_{i \in N} x(i) \leq v(N)$
+        \item {\color{red} Efficiency:} $x(N) = v(N)$
+        \begin{itemize}
+            \item the payoff distribution is an allocation of the entire worth of the grand coalition to all agents
+        \end{itemize}
+        \item {\color{red} Individual rationality:} $\forall i \in N, x(i) \geq v(\{i\})$
+        \begin{itemize}
+            \item player obtains at least its self-value of payoff
+        \end{itemize}
+        \item {\color{red} Group rationality:} $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
+    \end{itemize}
 
-\begin{itemize}
-\item $ (\mathcal{M}, s ) \models p$ iff $ p \in \mathcal{V}(s)$;
-\item $ (\mathcal{M}, s ) \models \neg \varphi$ iff $ (\mathcal{M}, s ) \nvDash \varphi$;
-\item $ (\mathcal{M}, s ) \models \varphi \vee \psi$ iff $(\mathcal{M}, s ) \models \varphi$ or $(\mathcal{M}, s ) \models \psi$;
-\item $ (\mathcal{M}, s ) \models EX \varphi $ iff there exists a path $\pi$ starting at $s$ such that $ (\mathcal{M}, \pi(1) ) \models \varphi$;
-\item $ (\mathcal{M}, s ) \models E ( \varphi U \psi)$ iff there exists a path $\pi$ starting at $s$ such that for some $ k \geq 0$,
-$ (\mathcal{M}, \pi(k) ) \models \psi$ and $ (\mathcal{M}, \pi(j) ) \models \varphi$ for all $ 0 \leq j < k$;
+    \vspace{0.2cm}
 
-\end{itemize}
-\label {dfn: Satisfaction of CTLK}
-\end{definition}
+    An {\color{red} imputation} is a payoff distribution $x$ that is efficient and individual rational.
+
 \end{frame}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Satisfaction of CTLK}
-\begin{definition} [Satisfaction of CTLK]~\\
+\begin{frame}{Stability}
     \begin{itemize}
-\item $ (\mathcal{M}, s ) \models EG \varphi$ iff there exists a path $\pi$  starting at $s$ such that $ (\mathcal{M}, \pi(k) ) \models \varphi$ for all $ k \geq 0$;
-\item $ (\mathcal{M}, s ) \models K_i \varphi $ iff for all global states $s' \in S$ such that $s \approx_i s'$, we have $(\mathcal{M}, s' ) \models \varphi $.
+        \item We all want to work together and get $v(N)$, but we all have different views about how to share the fruits of our work.
+We can use the values of other coalitions as arguments in favor of a distribution.
+        \item 3 can say to 1 ``let's form $\{1,3\}$ and share (40,0,40)''
+        \item 2 can say to 1 ``let's form $\{1,2\}$ and share (45,45,0)''
+        \item 3 can say to 2 ``OK, let's form $\{2,3\}$ and share (0,46,24)''
+        \item 1 can say to 2 and 3, ``fine! $\{1,2,3\}$ and (33,47,25)''
+        \item ...what is a good solution?
     \end{itemize}
-\label {dfn: Satisfaction of CTLK}
-\end{definition}
 \end{frame}

### 2013-12-11 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

@@
         \end{itemize}
-        \label {dfn:Coalition}
     \end{definition}
@@
             A {\color{blue}\emph{TU game}} is a pair $(N,v)$ where $N$ is a set of agents and where $v$ is a valuation function.
-            \label {dfn:valuationfunction}
         \end{definition}
@@
 We can use the values of other coalitions as arguments in favor of a distribution.
-        \item 3 can say to 1 ``let's form $\{1,3\}$ and share (40,0,40)''
-        \item 2 can say to 1 ``let's form $\{1,2\}$ and share (45,45,0)''
-        \item 3 can say to 2 ``OK, let's form $\{2,3\}$ and share (0,46,24)''
-        \item 1 can say to 2 and 3, ``fine! $\{1,2,3\}$ and (33,47,25)''
-        \item ...what is a good solution?
+        \item A condition for a coalition to form: 
+            {\color{red}all} agents prefer to be in it. i.e., none of the participants wishes she were in a different coalition or by herself {\color{red} $\Rightarrow Stability$ }
+        \item The {\color{red} core} is a stability concepts for which no agents prefer to deviate to form a different coalition.
+        \item Is the coalition stable $\Leftrightarrow$ Is the core non-empty
     \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Computation Tree Logic of Commitment (CTLC)}
+\begin{frame}{Solution Concepts: Core}
     CTLC logic is an extension of CTL logic with modalities for reasoning about \textbf{commitments and their fulfillment}.
-\begin{definition} [Model of CTLC]\label{Model of CTLC}
-A model $\mathcal{M_C}=(S,I,R_t, \{\sim _{i \rightarrow j}|{(i,j)\in \mathcal{A}^2}\},\mathcal{V})$ that belongs to the set of all models $\mathbb{M}$ is a tuple, where:
-\begin {itemize}
-\item $S, I, R_t$ and $\mathcal{V}$ are the same as in Definition (Model of CTLK).
-\item For each pair $(i, j) \in \mathcal{A}^2 $, $\sim _{i \rightarrow j} \subseteq S \times S $ is the social accessibility relation defined by $ s \sim _{i \rightarrow j} s' $ iff
-     1) $ l_i(s) = l_i(s') $ and 2) $ Var_i \cap Var_j \neq \emptyset $ such that  $ \forall x \in Var_i \cap Var_j $ we have $ l_i^x(s) = l_j^x(s') $ and $ \forall y \in Var_j - Var_i $ we have $ l_j^y(s) = l_j^y(s')$.
+    \begin{definition} [Imputation]\label{dfn:imputationbig}
+        An {\color{red}imputation} is a payoff distribution $x$ that is efficient and individually rational.
+        \begin{itemize}
+            \item $\sum_{i \in N} x(i) = v(N)$ (efficiency)
+            \item for all $i \in N, x_i \geq v(\{i\})$ (individual rationality)
+        \end{itemize}        
+    \end{definition}
 
-\end {itemize}
-\label {dfn: Model of CTLC}
+    \begin{definition} [Group rationality]\label{dfn:grouprationality}
+        $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
     \end{definition}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame} {Syntax of CTLC}
-\begin{definition}[Syntax of CTLC]~\\
-$ ~~~~~~~~~~~~~\varphi ::= p \mid \neg \varphi \mid \varphi \vee
-\varphi \mid EX \varphi  \mid E ( \varphi U \varphi) \mid EG
-\varphi \mid C_{i\rightarrow j} \varphi \mid Fu (C_{i\rightarrow
-j}\varphi)$.
-\label {dfn: Syntax of CTLC}\\
-Where:
-\begin{itemize}
-  \item $ p, E, X, G, U, \neg $ and $\vee$ are defined as in Definition (Syntax of CTLK);
-  \item The modal connective $C_{i \rightarrow j}$ stands for ``commitment from $i$ to $j$"; and
-  \item The modal connective $Fu$ stands for ``fulfillment".
-\end{itemize}
+\begin{frame} {Solution Concepts: Core}
+    The core relates to the stability of the grand coalition: \\ No group of agents has any incentive to change coalition.
+    \begin{definition}[$Core$ of a game $(N,v)$]\label{dfn:core}
+        Let $(N,v)$ be a cooperative game, and assume they form the coalition $N$. The core of $(N,v)$ is the set:
+        \vspace{0.1cm}
+        \begin{center}
+            $Core(N,v) = \{x \in R^n | x$ is a group rational imputation$\}$        
+        \end{center}
+        Equivalently,
+        \vspace{0.1cm}
+        \begin{center}
+            $Core(N,v) = \{x \in R^n | x(N) \leq v(N) \wedge x(C) \geq v(C) \forall C \subseteq N\}$
+        \end{center}
     \end{definition}
-\textbf{In this logic, $C_{i\rightarrow j}\varphi$ is read as ``agent $i$ commits towards agent $j$ to bring about $\varphi$".
-$Fu (C_{i\rightarrow j}\varphi)$ is read as ``the commitment $C_{i\rightarrow j}\varphi$ is fulfilled".}
+
 \end{frame}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame} {Satisfaction of CTLC}
-As the main fragment of CTLC logic is the CTL logic, hereafter, we only recall the semantics of the commitment and fulfillment modalities.
-\begin{itemize}
-\item $ (\mathcal{M_C}, s ) \models C_{i\rightarrow j} \varphi $ iff for all global states $ s' \in S $ such that $ s \sim_{i \rightarrow j} s' $, we have $ (\mathcal{M_C}, s' ) \models \varphi $;
-\item $ (\mathcal{M_C}, s ) \models Fu (C_{i\rightarrow j} \varphi)$ iff there exists $ s' \in S $ such that $ s' \sim_{i \rightarrow j} s $ and $ (\mathcal{M_C}, s' ) \models C_{i\rightarrow j} \varphi$.
-\end{itemize}
+\begin{frame} {Example: Core}
+
+    \begin{center}
+      $N = \{1,2\}$ \\
+      $v(\{1\}) = 5, v(\{2\}) = 5$ \\
+      $v(\{1,2\}) = 20$ \\      
+    \end{center}
+
+    $Core(N,n) = \{(x_1,x_2) \in R^2 | x_1 \geq 5, x_2 \geq 5, x_1 + x_2 = 20\}$
+
+    \begin{figure}[htbp]
+        \centering
+        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
+        \includegraphics[width=0.3 \columnwidth]{figures/coreex1.png}
+        %%\includegraphics[scale=0.5]{figure1}
+        %\caption{The NetBill payment protocol} \label{figure7}
+    \end{figure}
+
+    The core may not be fair: the core only considers stability.
+
 \end{frame}

### 2013-12-11 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

@@
 \end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Solution Concepts: Shapley Value}
+    \begin{definition} [Marginal contribution]\label{dfn:marginalcontribution}
+        The {\color{red}marginal contribution} of agent $i$ for a coalition $C \subseteq N \backslash \{i\}$ is $mc_i(C) = v(C \cup \{i\}) - v(C)$
+    \end{definition}
+
+    \begin{itemize}
+        \item By considering average marginal contribution over all possible subset of coalitions, we can achieve a fair distribution.\\
+        \item Let $\prod(N)$ denote the set of all permutations of the sequence $(1,...n)$. Therefore: $\phi_i(N,v) = \frac{\sum_{\sigma \in \phi_i(N)}}{mc(\sigma)}$
+    \end{itemize}
+
+    \begin{definition} [Shapley Value]\label{dfn:shapleyvalue}
+        Given a coalitional game $(N,v)$, the Shapley value of player $i$ is given by: \\
+        $\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))$
+    \end{definition}
+\end{frame}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Some properties}
+    \begin{itemize}
+        \item The core may not always be non-empty
+        \item Shapley value always exists and is unique.
+        \item When the valuation function is {\color{red}superadditive}, the Shapley value is {\color{red}individually rational}, i.e., it is an imputation.
+        \item When the valuation function is {\color{red}convex}, the Shapley value is also group rational, hence, it is in the {\color{red}core}.        
+        \item A convex game has a non-empty core
+        \item There are other well-known solution concepts: The bargaining set, The nucleolus and The nucleolus.
+    \end{itemize}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-12-12 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

@@
 \end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{$\epsilon$-Core}
+    \begin{itemize}
+        \item The core may not always be non-empty       
+        \item (To add some items)
+    \end{itemize}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Coalition Structures}
+    \begin{itemize}
+        \item To reach a stable partition having many coalitions. 
+        \item (To add some items)       
+    \end{itemize}
+\end{frame}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Combining Logics}
+\subsection{Problem Formulation and Modeling}
 
-\begin{frame}{A schematic view of our approach}
+\begin{frame}{Problem Formulation and Modeling}
+    \begin{itemize}
+        \item Communities are robust service providers with well established market share and reputation
+        \item The community is characterized by a request rate $R_C$
+        \item Web services can perform tasks with some throughput rate ($Th_{ws}$)
+        \item Web services come with different values of $QoS_{ws}$ for different metrics.
+        \item 123
+    \end{itemize}    
+\end{frame}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Task distribution}
+    \begin{itemize}
+        \item Our model uses a slightly modified $weighted fair queuing$ method for task distribution rather than Contract-Net.
+        \item All the input flow is multiplexed amount different web services with weights proportional to their throughput value ($Th_{ws}$).
+        \item Queues will happen if $R_C$ is more than summation web services throughput.
+        \item Weighted task rate of: $R_C \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ or $Th_{ws}$
+    \end{itemize}
     \begin{figure}[htbp]
@@
         %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
-\includegraphics[width=1.05 \columnwidth]{figures/figure9.png}
+        \includegraphics[width=0.8 \columnwidth]{figures/community.png}
         %%\includegraphics[scale=0.5]{figure1}
-%\caption{Our approach} %\label{figure9}
+        %\caption{The NetBill payment protocol} \label{figure7}
     \end{figure}    
-
 \end{frame}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Combining Logics}
-Given \textbf{two logics} $L_1$ and $L_2$, their \textbf{languages} $\mathcal{L}_1$ and $\mathcal{L}_2$, and their
-\textbf{axiomatic systems} $\mathcal{X}_1$ and $\mathcal{X}_2$, the logic
-$L_1 \otimes L_2$ is the smallest logic with the following
-characteristics:
+\begin{frame}{Community Revenue}
     \begin{itemize}
-  \item The language $\mathcal{L}_{L_1\otimes L_2}$ is the union of $\mathcal{L}_{L_1}$ and $\mathcal{L}_{L_2}$.
-  \item The logic $L_1 \otimes L_2$ is axiomatised by the set of axioms $\mathcal{X}_1 \cup \mathcal{X}_2$.
+        \item Maximum potential output of a community:
+            \begin{equation*}
+                PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
+            \end{equation*}
+        \item if $Th_{ws} > R_C$, the community cannot perform at its maximum potential.
+        \item Actual output:
+            \begin{equation}\label{out_c}
+                Out(C) = \left\{
+                  \begin{array}{l l}
+                    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{C}$}\\
+                    PO(C) \times \frac{R_{C}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{C}$}
+                  \end{array} \right.
+            \end{equation}
     \end{itemize}
-If the logics $L_1$ and $L_2$ are interpreted using Kripke frames
-$F_1 = (S, R_1^1, \dots, R_n^1)$ and $F_2 = (S, R_1^2, \dots
-,R_m^2 )$ where $R^1_{x/x\in[1,n]}$ and $R^2_{y/y\in[1,m]}$ are
-\textbf{accessibility relations}, then the semantics for $L_1 \otimes L_2$
-can be defined in the Kripke frame $F =(S, R_1^1, \dots , R_n^1,
-R_1^2, \dots ,R_m^2 )$ obtained by the \textit{independent join} of the two
-frames $F_1$ and $F_2$.
 \end{frame}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame17 Proposed Research
-\begin{frame} {Model of CTLKC}
-\begin{definition} [Model of CTLKC]\label{Model of CTLKC}
-A model $\mathcal{M}=(S,I,R_t,\{\approx_i|i\in \mathcal{ A}\},\{\sim _{i \rightarrow j}|{(i,j)\in \mathcal{A}^2}\},\mathcal{V})$ that belongs to the set of all models $\mathbb{M}$ is a tuple, where:
-\begin {itemize}
-\item $S, I, R_t$ and $\mathcal{V}$ are the same as in Definition (Model of CTLK);
-\item For each agent $i \in \mathcal{A}$, $ \approx _i  \subseteq S \times S
-$ is the epistemic accessibility relation defined by $ s \approx_i
-s' $ iff $ l_i(s) = l_i(s') $;
-\item For each pair $(i, j) \in \mathcal{A}^2 $, $\sim _{i \rightarrow j} \subseteq S \times S $ is the social accessibility relation defined by $ s \sim _{i \rightarrow j} s' $ iff
-     1) $ l_i(s) = l_i(s') $ and
-     2) $ Var_i \cap Var_j \neq \emptyset $ such that  $ \forall x \in Var_i \cap Var_j $ we have $ l_i^x(s) = l_j^x(s') $ and $ \forall y \in Var_j - Var_i $ we have $ l_j^y(s) = l_j^y(s')$;
-\item $ \mathcal{V} : S \rightarrow 2 ^{\Phi_p} $ is a valuation function where $\Phi_p $ is a set of atomic propositions.
-\end {itemize}
-\label {dfn: Model of CTLKC}
-\end{definition}
- \end{frame}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame} {Syntax of CTLKC}
+\begin{frame}{Example 1}
+    \begin{table}[!t]
+    \renewcommand{\arraystretch}{1.3}
+    % if using array.sty, it might be a good idea to tweak the value of
+    % \extrarowheight as needed to properly center the text within the cells
+    \label{example_1}
+    \centering
+    \begin{tabular}{c c c c}
+    \hline
+    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
+    \hline
+    1 & 0.8 & 4 & 3.2\\
+    2 & 0.8 & 5 & 4.0\\
+    3 & 0.8 & 3 & 2.4\\
+    \hline
+    \end{tabular}
+    \end{table}
 
-\begin{definition}[Syntax of CTLKC]~\\
-$ ~~~~~~~~~~~~~\varphi ::= p \mid \neg \varphi \mid \varphi \vee
-\varphi \mid EX \varphi  \mid E ( \varphi U \varphi) \mid EG
-\varphi\mid K_i \varphi \mid C_{i\rightarrow j} \varphi \mid Fu
-(C_{i\rightarrow j}\varphi)$. \label {dfn: Syntax of CTLKC}
-\end{definition}
-
+    \begin{table}[!t]
+    \renewcommand{\arraystretch}{1.3}
+    % if using array.sty, it might be a good idea to tweak the value of
+    % \extrarowheight as needed to properly center the text within the cells
+    % \caption{Three web services}
+    \label{example_1_2}
+    \centering
+    \begin{tabular}{c c || c c}
+    \hline
+    Community & Worth & Community & Worth\\
+    \hline
+    $\left\{1\right\}$ & 3.2 & $\left\{1,2\right\}$ & 7.2\\
+    $\left\{2\right\}$ & 4.0 & $\left\{1,3\right\}$ & 5.6\\
+    $\left\{3\right\}$ & 2.4 & $\left\{2,3\right\}$ & 6.4\\
+    $\left\{1,2,3\right\}$ & 8.0\\
+    \hline
+    Community $R_C$: 10\\
+    \hline
+    \end{tabular}
+    \end{table}
 \end{frame}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame18 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Selection Criteria}
-We propose the following criteria based on \textbf{common intuitions}:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Example 2}
+    \begin{table}[!t]
+    \renewcommand{\arraystretch}{1.3}
+    % if using array.sty, it might be a good idea to tweak the value of
+    % \extrarowheight as needed to properly center the text within the cells
+    \label{example_2}
+    \centering
+    \begin{tabular}{c c c c}
+    \hline
+    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
+    \hline
+    1 & 0.8 & 5 & 4.0\\
+    2 & 0.7 & 6 & 4.2\\
+    3 & 0.7 & 4 & 2.8\\
+    \hline
+    \end{tabular}
+    \end{table}
+
+    \begin{table}[!t]
+    \renewcommand{\arraystretch}{1.3}
+    % if using array.sty, it might be a good idea to tweak the value of
+    % \extrarowheight as needed to properly center the text within the cells
+    % \caption{Three web services}
+    \label{example_2_2}
+    \centering
+    \begin{tabular}{c c || c c}
+    \hline
+    Community & Worth & Community & Worth\\
+    \hline
+    $\left\{1\right\}$ & 4.0 & $\left\{1,2\right\}$ & 7.4\\
+    $\left\{2\right\}$ & 4.2 & $\left\{1,3\right\}$ & 6.8\\
+    $\left\{3\right\}$ & 2.8 & $\left\{2,3\right\}$ & 7.0\\
+    $\left\{1,2,3\right\}$ & 7.3\\
+    \hline
+    Community $R_C$: 10\\
+    \hline
+    \end{tabular}
+    \end{table}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Example 3}
+    \begin{table}[!t]
+    \renewcommand{\arraystretch}{0.8}
+    % if using array.sty, it might be a good idea to tweak the value of
+    % \extrarowheight as needed to properly center the text within the cells
+    \label{example_3}
+    \centering
+    \begin{tabular}{c c c c}
+    \hline
+    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
+    \hline
+    1 & 0.8 & 10 & 5\\
+    2 & 0.8 & 20 & 5\\
+    3 & 0.8 & 30 & 5\\
+    \hline
+    \end{tabular}
+    \end{table}
+
+    \begin{table}[!t]
+    \renewcommand{\arraystretch}{0.8}
+    % if using array.sty, it might be a good idea to tweak the value of
+    % \extrarowheight as needed to properly center the text within the cells
+    % \caption{Three web services}
+    \label{example_3_2}
+    \centering
+    \begin{tabular}{c c || c c}
+    \hline
+    Community & Worth & Community & Worth\\
+    \hline
+    $\left\{C_{ms_1}\right\}$ & 0 & $\left\{C_{ms_2}\right\}$ & 0\\
+    $\left\{C_{ms_1}, ws_1\right\}$ & 8 & $\left\{C_{ms_2}, ws_1\right\}$ & 8\\
+    $\left\{C_{ms_1}, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_2\right\}$ & 16\\
+    $\left\{C_{ms_1}, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_3\right\}$ & 24\\
+    $\left\{C_{ms_1}, ws_1, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2\right\}$ & 24\\
+    $\left\{C_{ms_1}, ws_1, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_3\right\}$ & 32\\
+    $\left\{C_{ms_1}, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_2, ws_3\right\}$ & 32\\
+    $\left\{C_{ms_1}, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2, ws_3\right\}$ & 32\\
+    $\left\{C_{ms_1}, C_{ms_2}, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
+    $\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
+    \hline
+    Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
+    \hline
+    \end{tabular}
+    \end{table}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame19 Proposed Research
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Web Service Cooperative Games}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Scenario One: Web Services and One Community}
+    \begin{figure}[htbp]
+        \centering
+        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
+        \includegraphics[width=0.8 \columnwidth]{figures/scenario1.png}
+        %%\includegraphics[scale=0.5]{figure1}
+        %\caption{The NetBill payment protocol} \label{figure7}
+    \end{figure}
+
     \begin{itemize}
-%\begin{enumerate}
-  \item It should not be the case that an agent commits about everything he knows to others.
-  \item It should not be the case that an agent commits about everything known by others.
-  \item An agent should know about his own commitment.
-  \item An agent should be aware of any commitment directed towards him.
-  \item An agent should know the content of his fulfilled commitment.
-  \item An agent should know the content of any fulfilled commitment directed towards him.
+        \item A typical WS community, where web services can join or leave
+        \item $v(C) = out(C)$
+        \item Membership decision in made based on throughput and QoS of the web services.
+        \item Community master needs to get quality web services to keep community stable, so other web services have no incentive to leave.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Continue: Selection Criteria}
+
+\begin{frame}{Scenario One: Web Services and One Community}
     \begin{itemize}
- \item An agent should know about the fulfillment of his commitment.
- \item An agent should know about the fulfillment of any commitment directed towards him.
-  \item A sincere agent should know (i.e., believe) the content of his own commitment.
-  \item A sincere agent should fulfill his commitment.
-  \item A liar agent could not know (i.e., believe) the content of his commitment.
-  \item If an agent knows about his own commitment, then this commitment should exist, which means an agent should not know about a non-existing commitment.
+        \item 123123
+        \item 123123
+        \item 123123
     \end{itemize}
-%\end{enumerate}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}{Running Example: NetBill Payment Protocol}
-%
     \begin{figure}[htbp]
@@
         %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
-\includegraphics[width=.75 \columnwidth]{figures/figure1.png}
+        \includegraphics[width=0.8 \columnwidth]{figures/scenario2.png}
         %%\includegraphics[scale=0.5]{figure1}
-%\caption{The NetBill payment protocol} \label{figure1}
+        %\caption{The NetBill payment protocol} \label{figure7}
     \end{figure}
-\begin{itemize}
-\item $C_{Cus \rightarrow Mer}$ $sendPayment$.
- \item $C_{Mer \rightarrow Cus}$ $deliverGoods$.
- \end{itemize}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame19 Proposed Research
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Desiderata of Paradoxes}
-
-\begin{frame}{Desiderata of Paradoxes}
-Paradoxes are represented as reasoning rules that are: 1) not reasonable in
-open MAS, but they are valid in CTLKC; or 2) desirable for the
-interaction between knowledge and commitments, but they can get
-violated in CTLKC because they are not valid.
- \begin{enumerate}
-
-\vspace{0.2cm} \item [P1.]\textbf{[Committing everything known to
-others]}
-
-$K_i \varphi \Rightarrow C_{i \rightarrow j}\varphi, $ for all $j
-\in A$ where $i \neq j$.
-
-\textbf{ Meaning:} An agent (the debtor) commits towards all other
-agents (the creditors) about what he knows.\\
-\textbf{Example 1:}
-$K_{Mer}$ $deliverGoods \Rightarrow$ $C_{Mer \rightarrow
-Cus}$ $deliverGoods$.
-
-\vspace{0.2cm} \item [P2.]\textbf{[Committing everything known by
-others]}
-
- $ K_i K_j \varphi \Rightarrow C_{i \rightarrow j} \varphi$ such that $ i \neq j$.
-
-\textbf{Meaning:} An agent (the debtor) commits toward another
-agent (the creditor) to bring about what he (i.e., the debtor)
-knows about the creditor's knowledge.\\
-\textbf{Example 2:}
-$K_{Cus} K_{Mer}$ $deliverGoods \Rightarrow$ $C_{Cus \rightarrow Mer}$
-$deliverGoods$.
-
-\end{enumerate}
 
 \end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame20 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{frame}{Research Activities Goal}
-    We aim to cover all possible relations between knowledge and commitments as single and group interactions by:
+    \begin{itemize}
+        \item Analyzing other cooperative solution concepts such as Kernel
+        and Nucleolus where payoff division is guaranteed to exist and may
+        have optimal results.
 
-        \begin{itemize}
-              \item Defining a new consistent logic that combines knowledge and commitments and solves the nine paradoxes while satisfying the six properties.
-              \item Addressing the model checking problem of the new logic from both algorithmic and complexity perspectives.
-              \item Implementing the new model checking algorithms on top of MCMAS+.
-              \item Identifying a new semantics for group committing.
-              \item Adding the group knowledge to the framework.
+        \item Applying other valuation function in our scenarios using for
+        instance Weighted Voting Games (WCG) in order to develop a
+        multiple weighted algorithm to find best coalition structures
+        satisfying different weights on each community.
+
+        \item Analyzing the impact of Q-learning and reinforcement
+        learning on the performance of our model.
+
+        \item Developing an approximation algorithm for shapely value
+        payoff distribution vector in community setting.
+
+        \item Developing a community membership algorithm technique for
+        our agents in "incomplete information" settings.
+
+        %\item Developing an open source, Java based Tool, with UI for
+        %solving Core and Shapely solution concepts based on different
+        %input valuation functions.
     \end{itemize}
-
 \end{frame}
@@
 \begin{center}
-\includegraphics[width=.65 \columnwidth]{figures/figure6.png}
+\includegraphics[width=1 \columnwidth]{figures/timetable.png}
 %\includegraphics[width=16cm, height=21cm]{figures/figure6.eps}
@@
 
-1- Submitted a journal paper entitled ``\textbf{Interaction between knowledge and Social Commitments in MASs}", Applied Intelligence Journal, Springer.\\
+    \begin{enumerate}
+        \item Published a paper in 10th International Conference on Services Computing; \emph{"Efficient Coalition Formation for Web Services"} {\color{blue} (Accepted)}
+        \item Submitted a Journal Paper to the International Journal of Web and Grid Services; IEEE Transactions on Services Computing {\color{blue} (Second round of review)}
+        \item Submitted a Paper to the 10th International Conference on Service Oriented Computing (ICSOC 2012); \emph{"Analyzing Coopetition Strategies of Services within Communities"} {\color{blue} (Accepted)}
+        \item Submitted a Journal Paper to the International Journal of Web and Grid Services; IEEE Transactions on Services Computing; \emph{"To Compete or to Cooperate?
+This is the Question in Communities of Autonomous Services"}
+    \end{enumerate}
 

### 2013-12-12 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

@@
     	\item Proposed Research
-        \item Contributions and Research Activities
     	\item Time Line
@@
         %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
-        \includegraphics[width=1.0 \columnwidth]{figures/figure7.png}
+        %\includegraphics[width=1.0 \columnwidth]{figures/figure7.png}
         %%\includegraphics[scale=0.5]{figure1}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Coalition Structures}
-    \begin{itemize}
-        \item To reach a stable partition having many coalitions. 
-        \item (To add some items)       
-    \end{itemize}
-\end{frame}
 
@@
     	\item {\bf Proposed Research}
-        \item Contribution and Research Activities
     	\item Time Line
@@
         \item Web services come with different values of $QoS_{ws}$ for different metrics.
-        \item 123
     \end{itemize}
@@
         \item A typical WS community, where web services can join or leave
-        \item $v(C) = out(C)$
+        \item $v(C) = Out(C)$
         \item Membership decision in made based on throughput and QoS of the web services.
         \item Community master needs to get quality web services to keep community stable, so other web services have no incentive to leave.
+    \end{itemize}
 
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Scenario One: Web Services and One Community}
+
+    \begin{itemize}
+        \item Upon receiving membership request the master web service checks if the coalition will be stable having the new member.
+        \item If the game is convex, core exists.
+        \item If the game is convex, Shapley value is in core.
+        \item Convexity Condition:
+        \begin{center}          
+          $\forall S,T | S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N,$ \\
+          $v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)$ \\
+          $\Leftrightarrow$  \\
+          $v(S' \cup T') \geq v(S') + v(T') - v(S' \cap T')$            
+        \end{center}
+    \end{itemize}
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Scenario One: Web Services and One Community}
+
+    \begin{figure}[htbp]
+        \centering
+        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
+        \includegraphics[width=0.92 \columnwidth]{figures/dp.png}
+        %%\includegraphics[scale=0.5]{figure1}
+        %\caption{The NetBill payment protocol} \label{figure7}
+    \end{figure}
+
+    \begin{itemize}
+        \item Approximation of the optimum result for each level, is it possible?
     \end{itemize}
@@
 
-\begin{frame}{Scenario One: Web Services and One Community}
+\begin{frame}{Scenario Two: Web Services and Many Community}
     \begin{itemize}        
-        \item 123123
-        \item 123123
-        \item 123123
+        \item Based on Coalition Structure theory
+        \begin{itemize}    
+            \item What coalitions to form? 
+            \item Stability in coalition structure, is a partition of players, where no other partition can provide all agents with better utility.
+        \end{itemize}
+        \item Has to be distributed not centralized
+        \item Merge and Split Algorithm
+        \begin{itemize}
+            \item Iterative
+            \item Converges to a final partition
+        \end{itemize}
     \end{itemize}
@@
         %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
-        \includegraphics[width=0.8 \columnwidth]{figures/scenario2.png}
+        \includegraphics[width=0.5 \columnwidth]{figures/scenario2.png}
         %%\includegraphics[scale=0.5]{figure1}
@@
     \end{figure}       	
+\end{frame}
 
+\begin{frame}{Representation and Complexity issues}
+    \begin{itemize}
+        \item Core and Shapley value are combinatorial problems.
+        \item Input size is exponential.
+        \item Compact or succinct representation of coalition games. A representation so that the input size is a polynomial in the number of agents.
+    \end{itemize}
 \end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}{Continue: Desiderata of Paradoxes}
- \begin{enumerate}
-\vspace{0.2cm} \item [P3.][\textbf{Committing everything known
-from others}]
-$ K_i K_j \varphi \Rightarrow C_{j \rightarrow i} \varphi$ such that $ i \neq j$.
-
-\textbf{Meaning:} An agent (the debtor) commits toward another
-agent (the creditor) to bring about what the creditor knows about
-the debtor's knowledge.\\
-\textbf{Example 3:}\\
-$K_{Cus} K_{Mer}$ $deliverGoods \Rightarrow$ $C_{Mer \rightarrow Cus}$
-$deliverGoods$.
-
-\vspace{0.2cm} \item [P4.][\textbf{Knowing about his own
-commitment}]
-
-$C_{i\rightarrow j} \varphi \Rightarrow K_i (C_{i\rightarrow j}
-\varphi) $ where $i \neq j$.
-
-\textbf{Meaning:} An agent knows about his commitment.
-
-\textbf{Example 4:}\\
-$C_{Cus \rightarrow Mer}$ $sendPayment $ $\Rightarrow K_{Cus}$ $(C_{Cus \rightarrow Mer}$ $sendPayment)$.
-\end{enumerate}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Induced subgraph games}
+    \begin{itemize}
+        \item An induced subgraph game is a coalitional game defined by an undirected weighted graph $G = (V,W)$ where $V$ is the set of vertices and $W : V \rightarrow V$ is the set of edges weights.
+For $(i,j) \in V^2$, $w_{ij}$ is the weight of the edge between $i$ and $j$.
+        \item $N = V$
+        \item for all $C \subseteq N, v(C) = \sum_{(i,j) \in C} w_{ij}$
+        \item {\color{red}Space Complexity:} Using an adjacency matrix, we need to provide $n^2$ entries.
+        \item {\color{red}Convexity:} If all the weights are nonnegative then the game is convex.
+        \item {\color{red}Shapley Value:} $\phi_i(N,v) = \frac{1}{2} \sum_{(i,j) \in N^2 | i \neq j}w_{ij}$
+        \item This is {\color{red}not complete}. Many TU games cannot be represented by a induced subgraph game
 
-\begin{frame}{Continue: Desiderata of Paradoxes}
-
-\begin{figure}[htbp]
-    \begin{center}
-%\includegraphics[width=10cm, height=5cm]{figures/figure2.eps}
-    \includegraphics[width=.75 \columnwidth]{figures/figure2.png}
-   % \caption{Model 1} \label{figure2}
-    \end{center}
-    \end{figure}
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}{Continue: Desiderata of Paradoxes}
-\begin{enumerate}
-\vspace{0.2cm} \item [P5.][\textbf{Knowing the content of his own
-fulfilled commitment}]
-
-$Fu (C _{i\rightarrow j} \varphi) \Rightarrow K _i \varphi$ where
-$i \neq j$.
-
-\textbf{Meaning:} An agent knows the content of his fulfilled
-commitment.\\
-\textbf{Example 5:}\\
-$Fu (C _{Cus\rightarrow Mer} sendPayment) \Rightarrow K_{Cus}$ $sendPayment$.
-\begin{figure}[htbp]
-    \begin{center}
-%\includegraphics[width=10cm, height=5cm]{figures/figure2.eps}
-    \includegraphics[width=.75 \columnwidth]{figures/figure3.png}
-   % \caption{Model 2} \label{figure3}
-    \end{center}
-    \end{figure}
-
-\end{enumerate}     	
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame23 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
- \begin{frame}{Continue: Desiderata of Paradoxes}
- \begin{enumerate}
-
-\vspace{0.2cm} \item [P6.][\textbf{Knowing the content of the
-other's fulfilled commitment}]
-
-$Fu (C _{i\rightarrow j} \varphi) \Rightarrow K_j \varphi$ where
-$i \neq j$.
-
-\textbf{Meaning:} The creditor knows the content of the debtor's
-fulfilled commitment.\\
-\textbf{Example 6:}\\
-$ Fu (C_{cust \rightarrow Mer}$ $sendPayment)$ $\Rightarrow $ $k_{Mer} sendPayment$.
-	\begin{figure}[htbp]
-\begin{center}
-%\includegraphics[width=12cm, height=5cm]{figures/figure4.eps}
-\includegraphics[width=.70 \columnwidth]{figures/figure4.png}
-%\caption{Model 3} \label{figure4}
-\end{center}
-\end{figure}
-\end{enumerate}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame24 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Continue: Desiderata of Paradoxes}
-\begin{enumerate}
-    \vspace{0.2cm} \item [P7.][\textbf{Knowing the commitment of the
-other}]
-
-$C_{i\rightarrow j} \varphi \Rightarrow AF K_j (C_{i\rightarrow j}
-\varphi) $ where $i \neq j$.
-
-\textbf{Meaning:} An agent should be aware of any commitments
-directed towards him.\\
-\textbf{Example 7:}\\
-$C_{Mer \rightarrow Cus}$ $deliverGoods$ $\Rightarrow $ $AF K_{Cus}(C_{Mer \rightarrow Cus}$
-$deliverGoods$).
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=.50 \columnwidth]{figures/figure5.png}
-%\includegraphics[width=12cm, height=7cm]{figures/figure5.eps}
-%\includegraphics[scale=0.5]{figure4.eps}
-%\caption{Model 4} \label{figure5}
-\end{figure}
-
-\end{enumerate}
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Continue: Desiderata of Paradoxes}
-\begin{enumerate}
-    \vspace{0.2cm} \item [P8.][\textbf{Knowing the fulfillment of his
-own commitment}]
-
-$Fu(C _{i\rightarrow j} \varphi) \Rightarrow K_i Fu(C
-_{i\rightarrow j} \varphi)$ where $i \neq j$.
-
-\textbf{Meaning:} The agent knows that he fulfills his commitment.\\
-\textbf{Example 8:}\\
-$Fu(C_{Cus\rightarrow Mer} sendPayment)\Rightarrow K_{Cus}Fu(C_{Cus \rightarrow Mer} sendPayment)$.
-
-\vspace{0.2cm} \item [P9.][\textbf{Knowing the fulfillment of the
-debtor's commitment}]
-
-$Fu(C _{i\rightarrow j} \varphi) \Rightarrow K_j Fu(C_{i\rightarrow j} \varphi)$ where $i \neq j$.
-
-\textbf{Meaning:} The creditor knows that the debtor fulfills his
-commitment.\\
-\textbf{Example 9:}\\
-$Fu(C_{Cus \rightarrow Mer} sendPayment)\Rightarrow K_{Mer} Fu(C_{Cus \rightarrow Mer} sendPayment)$.
-\end{enumerate}
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame25 outline page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{CTLKC properties}
-\begin{frame}{CTLKC properties}
-In addition to the properties of knowledge (in CTLK) and commitments (in CTLC), those properties hold in CTLKC:
-\begin{enumerate}
-
-\vspace{0.2cm} \item [Prop 1.] $C_{i \rightarrow j}\varphi
-\Rightarrow \varphi$ is satisfiable but not valid.
-\vspace{0.2cm} \item [Prop 2.] $C_{i \rightarrow j}\varphi
-\Rightarrow K_i \varphi$ is satisfiable but not valid.
-\vspace{0.2cm} \item [Prop 3.] $(C_{i \rightarrow j}\varphi \wedge
-K_i (\varphi \Rightarrow \psi)) \Rightarrow C_{i \rightarrow j}
-\psi$ is valid.
-\vspace{0.2cm} \item [Prop 4.] $(C_{i \rightarrow j}(\varphi
-\Rightarrow \psi) \wedge K_i \varphi) \Rightarrow C_{i \rightarrow
-j} \psi$ is valid.
-\vspace{0.2cm} \item [Prop 5.] $(C_{i \rightarrow j}\varphi \wedge
-K_j (\varphi \Rightarrow \psi)) \Rightarrow C_{i \rightarrow j}
-\psi$ is satisfiable but not valid.
-\vspace{0.2cm} \item [Prop 6.] $(C_{i \rightarrow j}(\varphi
-\Rightarrow \psi) \wedge K_j \varphi) \Rightarrow C_{i \rightarrow
-j} \psi$ is satisfiable but not valid
-
-\end{enumerate}
-\end{frame}
-
-\section{Research Activities}
-\begin{frame}{Contribution and Research Activities}
-    \begin{itemize}
-     	\itemsep=.5cm
-    	\item Introduction
-    	\item Background and Literature Review
-    	\item Proposed Research
-        \item {\bf Contribution and Research Activities}
-    	\item Time Line
     \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Contributions}
-    \begin{frame}{Contributions}
+\subsection{Preliminary Results}
+\begin{frame}{Preliminary Results}
 
-    \begin{itemize}
-     \itemsep=.35cm
-     \item A new combined temporal logic, called CTLKC, that combines both CTLK and CTLC logics is introduced.
-     \item This logic served as a language to express a set of rules that are used to reason about the interaction between knowledge and social commitments.
-     \item Selection criteria are proposed to capture such reasoning rules.
-     \item Nine paradoxes are recognized in CTLKC logic that should be addressed in any consistent logic combining knowledge and commitments.
-     \item Six properties are identified and should be met in any logic combining knowledge and commitments.
-        \end{itemize}
+    \begin{figure}[!t]
+    \centering
+    %\includegraphics[scale=0.6]{graph1Final+.eps}
+    \includegraphics[width=2.1in]{figures/task_done_opt.pdf}
+    \includegraphics[width=2.1in]{figures/task_qos_opt.pdf}
+    \caption{Part (a): Cumulative number of requests successfully
+    done. Part (b): Average QoS of requests performed.}
+    \label{performanceall}
+    \end{figure}
 
 \end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame27 Contribution and Research Activities
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Preliminary Results}
+    \begin{figure}[!t]
+        \centering
+        %\includegraphics[scale=0.6]{graph1Final+.eps}
+        \includegraphics[width=3in]{figures/least_core.pdf}
+        \caption{Analysis of \emph{$\epsilon$-core} set non-emptiness, for different values of $\epsilon$} \label{f_leastcore}
+    \end{figure}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Preliminary Results}
+    \begin{figure}[!t]
+        \centering
+        %\includegraphics[scale=0.6]{graph1Final+.eps}
+        \includegraphics[width=2.1in]{figures/s2_task_done.pdf}
+        \includegraphics[width=2.1in]{figures/s2_task_qos.pdf}
+        \caption{Part (a): Cumulative number of tasks succesfully done. Part
+        (b): Average QoS of tasks performed.} \label{performancemany}
+    \end{figure}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Preliminary Results}
+    \begin{figure}[!t]
+        \centering
+        %\includegraphics[scale=0.6]{graph1Final+.eps}
+        \includegraphics[width=1.45in]{figures/avg_task_ws_done.pdf}
+        \includegraphics[width=1.45in]{figures/avg_qos_ws_done.pdf}
+        \includegraphics[width=1.45in]{figures/avg_avail_ws_done.pdf}
+        \caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
+        (b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
+    \end{figure}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
     	\item Proposed Research
-        \item Contribution and Research Activities
     	\item {\bf Time Line}

### 2013-12-14 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

@@
 
-\begin{frame}{Scenario Two: Web Services and Many Community}
+\begin{frame}{Scenario Two: Web Services and Many Communities}
     \begin{itemize}
@@
     \end{itemize}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Induced subgraph games}
+
+    \begin{table}
+        \small
+        \begin{tabular}{l|c|c|c|c}
+        Representations                  & Space    & Shapley                  & Core Existence  & Complete     \\ \hline
+        Graph (w+)                       & P        & P                        & P               & Not          \\
+        Graph                            & P        & NP-Complete              & NP-Complete     & Not          \\
+        Synergy                          & NA       & P (l input)              & P               & Not          \\
+        Multi-issue                      & NA       & P (l input)              & NP-Complete     & Complete     \\
+        MC-net                           & NA       & P (l input)              & NP-hard         & Complete     \\
+        \end{tabular}
+    \end{table}
+
+    \begin{itemize}
+        \item Our web service community valuation function representation ($v(C) = out(C)$) space requirement, grows linearly to input size.        
+    \end{itemize}
+
 \end{frame}

### 2013-12-14 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

@@
     \begin{itemize}
-        \item {\color{red} convex:} $v(C_1) + v(C_2) \leq v(C_1 \bigcup C_2) + v(C_1 \bigcap C_2)$ Convexity has important properties in cooperative game theory solution concepts.
+        \item {\color{red} convex:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2) - v(C_1 \bigcap C_2)$. Convexity has important properties in cooperative game theory solution concepts.
     \end{itemize}
@@
 \end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{$\epsilon$-Core}
-    \begin{itemize}
-        \item The core may not always be non-empty
-        \item (To add some items)
-    \end{itemize}
-\end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
         \begin{center}
+          $v(A \cup B) \geq v(A) + v(B) - v(A \cap B)$ \\
+          $\Leftrightarrow$  \\
           $\forall S,T | S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N,$ \\
-          $v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)$ \\
-          $\Leftrightarrow$  \\
-          $v(S' \cup T') \geq v(S') + v(T') - v(S' \cap T')$
+          {\color{blue} $v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)$ }
         \end{center}
+        \item Depth-1 Convexity Check: $O(n)$
+        \item Depth-2 Convexity Check: $O(n^2)$
     \end{itemize}
@@
             \item Stability in coalition structure, is a partition of players, where no other partition can provide all agents with better utility.
+            \item Social welfare: $\operatorname*{arg\,max}_{CS} v(CS)$ where $v(CS) = \sum_{C \in CS}v(C)$.
         \end{itemize}
         \item Has to be distributed not centralized
-        \item Merge and Split Algorithm
+        \item Merge and Split Algorithm {\footnotesize{\color{blue}{(Krzysztof R. Apt and Andreas Witzel)}}}
         \begin{itemize}
@@
     \end{figure}       	
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{$\epsilon$-Core}
+    \begin{itemize}
+        \item The core may not always be non-empty, core is a strong condition
+        \item $\epsilon$-core relaxes the core condition
+        \item $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon$
+        \item relative e-core: $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq (1-\epsilon).v(S)$
+    \end{itemize}
 \end{frame}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Induced subgraph games}
+\begin{frame}{Different Compact Representations of Coalition Games}
 

### 2013-12-15 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

@@
         \item High reliance on web services, created high competition and great business opportunities for online service developers
-        \item Community goals:
+        \item Community of web services
+        \item Goals:
         \begin{itemize}
@@
         community of agent-based services in order to maximize the utility
-        of involved users, web services and community organizers?}.
+        of involved users, web services and community organizers?}
         \begin{itemize}
@@
     \item \textbf{How can we model fair and stable communities as coalitions
-        of agent-based web services?}.
+        of agent-based web services?}
         \begin{itemize}

### 2013-12-15 proposal/proposal/chapter3.tex
changes

@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{Figures/avg_task_ws_done.eps}
-\includegraphics[width=3in]{Figures/avg_qos_ws_done.eps}
-\includegraphics[width=3in]{Figures/avg_avail_ws_done.eps}
+\includegraphics[width=2.5in]{Figures/avg_task_ws_done.eps}
+\includegraphics[width=2.5in]{Figures/avg_qos_ws_done.eps}
+\includegraphics[width=2.5in]{Figures/avg_avail_ws_done.eps}
 \caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part

### 2013-12-15 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes
ehsan

@@
             \item \textbf{User satisfaction, Service quality, high availability and responsiveness}.
-            \item \textbf{Web Service Discovery over Internet}.
+            \item \textbf{Facilitate Web Service Discovery over Internet}.
         \end{itemize}
@@
         %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
-        %\includegraphics[width=1.0 \columnwidth]{figures/figure7.png}
+        \includegraphics[width=1.0 \columnwidth]{figures/wsinternet.png}
         %%\includegraphics[scale=0.5]{figure1}
@@
 \end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Solution Concepts: Core}
-    CTLC logic is an extension of CTL logic with modalities for reasoning about \textbf{commitments and their fulfillment}.
-    \begin{definition} [Imputation]\label{dfn:imputationbig}
-        An {\color{red}imputation} is a payoff distribution $x$ that is efficient and individually rational.
-        \begin{itemize}
-            \item $\sum_{i \in N} x(i) = v(N)$ (efficiency)
-            \item for all $i \in N, x_i \geq v(\{i\})$ (individual rationality)
-        \end{itemize}
-    \end{definition}
 
-    \begin{definition} [Group rationality]\label{dfn:grouprationality}
-        $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
-    \end{definition}
-\end{frame}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-12-16 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

@@
         \end{itemize}
-        \item \textbf{issues:}
+        \item \textbf{Issues:}
             \begin{itemize}
@@
     \begin{itemize}
-        \item \textbf{problem:} a game $(N,v)$, and we assume all agents in $N$ want to cooperate.
-        \item \textbf{solution:} a payoff distribution $x \in R^n$ that provides a value to individual agents.
+        \item \textbf{Problem:} a game $(N,v)$, and we assume all agents in $N$ want to cooperate.
+        \item \textbf{Solution:} a payoff distribution $x \in R^n$ that provides a value to individual agents.
 
@@
         \begin{center}
-            $Core(N,v) = \{x \in R^n | x(N) \leq v(N) \wedge x(C) \geq v(C) \forall C \subseteq N\}$
+            $Core(N,v) = \{x \in R^n | x(N) \leq v(N) \wedge x(C) \geq v(C), \forall C \subseteq N\}$
         \end{center}
@@
         \item A convex game has a non-empty core
+        \item Core and Shapley value are combinatorial problems.
         \item There are other well-known solution concepts: The bargaining set, The nucleolus and The nucleolus.
@@
     \begin{itemize}
-        \item Our model uses a slightly modified $weighted fair queuing$ method for task distribution rather than Contract-Net.
+        \item Our model uses a slightly modified \emph{weighted fair queuing} method for task distribution rather than Contract-Net.
         \item All the input flow is multiplexed amount different web services with weights proportional to their throughput value ($Th_{ws}$).
@@
             \end{equation*}
-        \item if $Th_{ws} > R_C$, the community cannot perform at its maximum potential.
+        \item if $\sum_{ws}{Th_{ws}} > R_C$, the community cannot perform at its maximum potential.
         \item Actual output:
@@
 
-    \begin{itemize}
-        \item Approximation of the optimum result for each level, is it possible?
-    \end{itemize}
+    %\begin{itemize}
+    %    \item Approximation of the optimum result for each level, is it possible?
+    %\end{itemize}
 
@@
     \end{itemize}
-\end{frame}
-
-\begin{frame}{Representation and Complexity issues}
-    \begin{itemize}
-        \item Core and Shapley value are combinatorial problems.
-        \item Input size is exponential.
-        \item Compact or succinct representation of coalition games. A representation so that the input size is a polynomial in the number of agents.
-    \end{itemize}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Induced subgraph games}
-    \begin{itemize}
-        \item An induced subgraph game is a coalitional game defined by an undirected weighted graph $G = (V,W)$ where $V$ is the set of vertices and $W : V \rightarrow V$ is the set of edges weights.
-For $(i,j) \in V^2$, $w_{ij}$ is the weight of the edge between $i$ and $j$.
-        \item $N = V$
-        \item for all $C \subseteq N, v(C) = \sum_{(i,j) \in C} w_{ij}$
-        \item {\color{red}Space Complexity:} Using an adjacency matrix, we need to provide $n^2$ entries.
-        \item {\color{red}Convexity:} If all the weights are nonnegative then the game is convex.
-        \item {\color{red}Shapley Value:} $\phi_i(N,v) = \frac{1}{2} \sum_{(i,j) \in N^2 | i \neq j}w_{ij}$
-        \item This is {\color{red}not complete}. Many TU games cannot be represented by a induced subgraph game
-
-    \end{itemize}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Different Compact Representations of Coalition Games}
-
-    \begin{table}
-        \small
-        \begin{tabular}{l|c|c|c|c}
-        Representations                  & Space    & Shapley                  & Core Existence  & Complete     \\ \hline
-        Graph (w+)                       & P        & P                        & P               & Not          \\
-        Graph                            & P        & NP-Complete              & NP-Complete     & Not          \\
-        Synergy                          & NA       & P (l input)              & P               & Not          \\
-        Multi-issue                      & NA       & P (l input)              & NP-Complete     & Complete     \\
-        MC-net                           & NA       & P (l input)              & NP-hard         & Complete     \\
-        \end{tabular}
-    \end{table}
-
-    \begin{itemize}
-        \item Our web service community valuation function representation ($v(C) = out(C)$) space requirement, grows linearly to input size.
-    \end{itemize}
-
 \end{frame}
@@
 \begin{frame}{Research Activities Goal}
-    \begin{itemize}
+    \begin{enumerate}
         \item Analyzing other cooperative solution concepts such as Kernel
@@
 
-        \item Developing an approximation algorithm for shapely value
-        payoff distribution vector in community setting.
-
         \item Developing a community membership algorithm technique for
@@
         %input valuation functions.
+    \end{enumerate}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Representation and Complexity issues}
+    \begin{itemize}
+        \item Core and Shapley value are combinatorial problems.
+        \item Input size is exponential.
+        \item Compact or succinct representation of coalition games. A representation so that the input size is a polynomial in the number of agents.
     \end{itemize}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Induced subgraph games}
+    \begin{itemize}
+        \item An induced subgraph game is a coalitional game defined by an undirected weighted graph $G = (V,W)$ where $V$ is the set of vertices and $W : V \rightarrow V$ is the set of edges weights.
+For $(i,j) \in V^2$, $w_{ij}$ is the weight of the edge between $i$ and $j$.
+        \item $N = V$
+        \item for all $C \subseteq N, v(C) = \sum_{(i,j) \in C} w_{ij}$
+        \item {\color{red}Space Complexity:} Using an adjacency matrix, we need to provide $n^2$ entries.
+        \item {\color{red}Convexity:} If all the weights are nonnegative then the game is convex.
+        \item {\color{red}Shapley Value:} $\phi_i(N,v) = \frac{1}{2} \sum_{(i,j) \in N^2 | i \neq j}w_{ij}$
+        \item This is {\color{red}not complete}. Many TU games cannot be represented by a induced subgraph game
+
+    \end{itemize}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Different Compact Representations of Coalition Games}
+
+    \begin{table}
+        \small
+        \begin{tabular}{l|c|c|c|c}
+        Representations                  & Space    & Shapley                  & Core Existence  & Complete     \\ \hline
+        Graph (w+)                       & P        & P                        & P               & Not          \\
+        Graph                            & P        & NP-Complete              & NP-Complete     & Not          \\
+        Synergy                          & NA       & P (l input)              & P               & Not          \\
+        Multi-issue                      & NA       & P (l input)              & NP-Complete     & Complete     \\
+        MC-net                           & NA       & P (l input)              & NP-hard         & Complete     \\
+        \end{tabular}
+    \end{table}
+
+    \begin{itemize}
+        \item Our web service community valuation function representation ($v(C) = out(C)$) space requirement, grows linearly to input size.
+        \item Developing an approximation algorithm for shapely value payoff distribution vector in community setting.
+    \end{itemize}
+
 \end{frame}

### 2013-12-16 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

@@
     	\item Proposed Research
-    	\item Time Line
+    	\item Timeline and Feature Work
     \end{itemize}
@@
         \item High reliance on web services, created high competition and great business opportunities for online service developers
-        \item Community of web services
-        \item Goals:
+        \item Community of web services, Goals:        
         \begin{itemize}
@@
             \item \textbf{Facilitate Web Service Discovery over Internet}.
+            \item \textbf{Maintaining high reputation and market share}.
         \end{itemize}
@@
         	\item Improve service quality, availability and responsiveness
+            \item Maintaining high reputation and market share
         \end{itemize}
@@
     	\item {\bf Proposed Research}
-    	\item Time Line
+    	\item Timeline and Feature Work
     \end{itemize}
@@
     	\item Proposed Research
-    	\item {\bf Time Line}
+    	\item {\bf Timeline and Feature Work}
     \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Time Line}
-    \begin{frame}{Time Line}
+\subsection{Timeline}
+    \begin{frame}{Timeline}
 
@@
         \item Submitted a Paper to the 10th International Conference on Service Oriented Computing (ICSOC 2012); \emph{"Analyzing Coopetition Strategies of Services within Communities"} {\color{blue} (Accepted)}
-        \item Submitted a Journal Paper to the International Journal of Web and Grid Services; IEEE Transactions on Services Computing; \emph{"To Compete or to Cooperate?
+        \item Submitted a Journal Paper to the International Journal of Expert Systems With Applications; IEEE Transactions on Services Computing; \emph{"To Compete or to Cooperate?
 This is the Question in Communities of Autonomous Services"}

### 2013-12-16 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

@@
     \begin{itemize}
-        \item High reliance on web services, created high competition and great business opportunities for online service developers
-        \item Community of web services, Goals:        
+        \item High reliance on web services created high competition and great business opportunities for online service developers
+        \item Community of web services: Clustering similar web services in order to:
         \begin{itemize}
-            \item \textbf{User satisfaction, Service quality, high availability and responsiveness}.
+            \item \textbf{Provide better user satisfaction through high availability and responsiveness}.
             \item \textbf{Facilitate Web Service Discovery over Internet}.
-            \item \textbf{Maintaining high reputation and market share}.
+            \item \textbf{Maintain high reputation and market share}.
         \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\subsection{Communities of Web Services}
+%    \begin{frame}{Community of Web Services}
+%       Communities of Web Services
+%       \begin{itemize}
+%           \item Ease and improve the process of Web services discovery in an open environment like the Internet
+%       	\item Improve service quality, availability and responsiveness
+%           \item Maintaining high reputation and market share
+%       \end{itemize}
+
+%       \begin{figure}[htbp]
+%           \centering
+            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
+%           \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
+            %%\includegraphics[scale=0.5]{figure1}
+            %\caption{The NetBill payment protocol} \label{figure7}
+%       \end{figure}
+
+%   \end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame10 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\subsection{Social commitments in MASs}
+    \begin{frame}{Communities of Web Services}
+        Communities of Web Services
+        \begin{itemize}
+            \itemsep=.35cm
+        	\item \textbf{Communities of web services operations}
+            \begin{itemize}
+              \item Community development
+              \item Web services attraction and retention
+              \item Web service selection
+            \end{itemize}                      	      	
+        \end{itemize}
+
+        \begin{figure}[htbp]
+            \centering
+            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
+            \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
+            %%\includegraphics[scale=0.5]{figure1}
+            %\caption{The NetBill payment protocol} \label{figure7}
+        \end{figure}
+    \end{frame}
+
 \begin{frame}{Problems and Research Questions}
@@
         \begin{itemize}
-            \item Most of the recent work on communities of
+            \item Most of the work on communities of
             services are either user-centric and focus on user satisfaction
@@
         \begin{itemize}
-            \item All parties involved are self-interest agents and have the authority to deviate leave the community if they can improve their income in some other ways.
+            \item All parties involved are self-interest agents and have the right to leave the community if they can improve their income in some other ways.
         \end{itemize}
@@
         \begin{itemize}
-            \item Modeling the preference and valuation functions considering the worth of all subsets of players in realistic cooperative scenarios
-            \item Solution concepts complexity issues            
+            \item The first issue is about the evaluation of web services that are working together inside communities.
+            \item The second issue is about the complexity of cooperative game theory solution concepts.
         \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Communities of Web Services}
-    \begin{frame}{Community of Web Services}
-        Communities of Web Services
-        \begin{itemize}
-            \item Ease and improve the process of Web services discovery in an open environment like the Internet
-        	\item Improve service quality, availability and responsiveness
-            \item Maintaining high reputation and market share
-        \end{itemize}
 
-        \begin{figure}[htbp]
-            \centering
-            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
-            \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
-            %%\includegraphics[scale=0.5]{figure1}
-            %\caption{The NetBill payment protocol} \label{figure7}
-        \end{figure}
-
-    \end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame10 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Social commitments in MASs}
-    \begin{frame}{Communities of Web Services}
-        Communities of Web Services
-        \begin{itemize}
-            \itemsep=.35cm
-        	\item \textbf{Communities of web services operations}
-            \begin{itemize}
-              \item Community Development
-              \item Web Services Attraction and Retention
-              \item Web Service Selection
-            \end{itemize}                      	      	
-        \end{itemize}
-
-        \begin{figure}[htbp]
-            \centering
-            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
-            \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
-            %%\includegraphics[scale=0.5]{figure1}
-            %\caption{The NetBill payment protocol} \label{figure7}
-        \end{figure}
-    \end{frame}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame11 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
          \begin{itemize}
-            \item A set of tasks needs to be performed, they require different expertise.
-            \item Agents do not have enough resource on their own to perform a task.
-            \item Find complementary agents to perform the tasks.
+            \item Cooperation to perform a set of tasks that requires different expertise.
+            \item Agents do not have enough resource on their own to perform the tasks.
+            \item Examples:
             \begin{itemize}
-                \item robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
-                \item transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
+                \item Robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
+                \item Transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
             \end{itemize}
@@
             \begin{itemize}
-                \item What coalition to form?
-                \item How to reward each each member when a task is completed?
+                \item Coalition formation.
+                \item Rewarding members when a task is completed.
             \end{itemize}
@@
     \begin{itemize}
-        \item \textbf{Problem:} a game $(N,v)$, and we assume all agents in $N$ want to cooperate.
+        \item \textbf{Problem:} Given a game $(N,v)$, and assuming all agents in $N$ want to cooperate, how to distribute the gain among the agents?
         \item \textbf{Solution:} a payoff distribution $x \in R^n$ that provides a value to individual agents.
@@
             \item Utility is worth the same for all agents
-            \item Utility can be {\color{red} compared} or {\color{red} transfered} between agents.
-            \item Irrespective of the division of the coalitional payoff, members of the coalition enjoy the same total utility.
+            \item Utility can be {\color{red} compared} or {\color{red} transferred} between agents.
+            \item Irrespective of the division of the coalitional payoff.
+            \begin{itemize}
+                \item In that case members of the coalition enjoy the same total utility.
+            \end{itemize}
         \end{itemize}
 
-        \begin{definition} [Valuation or Characteristic function]\label{dfn:valuationfunction}
+        \begin{definition} [Valuation or Characteristic Function]\label{dfn:valuationfunction}
             A \emph{valuation function v} associates a real number $v(C)$ to any subset $C \subseteq N$, i.e., $v:2^N \rightarrow R$ \\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Some properties of valuation functions}
+\begin{frame}{Some Properties of Valuation Functions}
     $\forall C_1,C_2 \subseteq N | C_1 \bigcap C_2 = \emptyset, i \in N, i \notin C_1$
     \begin{itemize}
-        \item {\color{red} additive:} $v(C_1 \bigcup C_2) = v(C_1) + v(C_2)$
-        \item {\color{red} super additive:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2)$ This is satisfied is many applications, or bigger coalitions will not form.
-        \item {\color{red} weekly super additive:} $v(C_1 \bigcup \{i\}) \geq v(C_1) + v(\{i\})$
-        \item {\color{red} subadditive:} $v(C_1 \bigcup C_2) \leq v(C_1) + v(C_2)$
+        \item {\color{blue} Additive:} $v(C_1 \bigcup C_2) = v(C_1) + v(C_2)$
+        \item {\color{blue} Super additive:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2)$ This is satisfied is many applications, or bigger coalitions will not form.
+        \item {\color{blue} Weekly super additive:} $v(C_1 \bigcup \{i\}) \geq v(C_1) + v(\{i\})$        
     \end{itemize}
@@
     \begin{itemize}
-        \item {\color{red} convex:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2) - v(C_1 \bigcap C_2)$. Convexity has important properties in cooperative game theory solution concepts.
+        \item {\color{blue} Convex:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2) - v(C_1 \bigcap C_2)$. Convexity has important properties in cooperative game theory solution concepts.
+    \end{itemize}
+    \begin{itemize}
+        \item {\color{red} Subadditive:} $v(C_1 \bigcup C_2) \leq v(C_1) + v(C_2)$
     \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Solution properties}
+\begin{frame}{Solution Properties}
     Let $x \in R^n$ be a solution of the TU game $(N,v)$
     \begin{itemize}
-        \item {\color{red} Feasible solution:} $\sum_{i \in N} x(i) \leq v(N)$
-        \item {\color{red} Efficiency:} $x(N) = v(N)$
+        \item {\color{blue} Feasible solution:} $\sum_{i \in N} x(i) \leq v(N)$
+        \item {\color{blue} Efficiency:} $x(N) = v(N)$
         \begin{itemize}
@@
         \end{itemize}
-        \item {\color{red} Individual rationality:} $\forall i \in N, x(i) \geq v(\{i\})$
+        \item {\color{blue} Individual rationality:} $\forall i \in N, x(i) \geq v(\{i\})$
         \begin{itemize}
@@
         \end{itemize}
-        \item {\color{red} Group rationality:} $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
+        \item {\color{blue} Group rationality:} $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
     \end{itemize}
@@
         \item A condition for a coalition to form:
-            {\color{red}all} agents prefer to be in it. i.e., none of the participants wishes she were in a different coalition or by herself {\color{red} $\Rightarrow Stability$ }
-        \item The {\color{red} core} is a stability concepts for which no agents prefer to deviate to form a different coalition.
-        \item Is the coalition stable $\Leftrightarrow$ Is the core non-empty
+            {\color{blue}all} agents prefer to be in it. i.e., none of the participants wishes she were in a different coalition or by herself {\color{red} $\Rightarrow Stability$ }
+        \item The {\color{blue} core} is a stability concept for which no agents prefer to deviate to form a different coalition.        
     \end{itemize}
@@
     \end{definition}
+
+    \begin{itemize}
+       \item The coalition is stable $\Leftrightarrow$ The core is not empty
+    \end{itemize}
 
@@
 \begin{frame}{Solution Concepts: Shapley Value}
-    \begin{definition} [Marginal contribution]\label{dfn:marginalcontribution}
+    \begin{definition} [Marginal Contribution]\label{dfn:marginalcontribution}
         The {\color{red}marginal contribution} of agent $i$ for a coalition $C \subseteq N \backslash \{i\}$ is $mc_i(C) = v(C \cup \{i\}) - v(C)$
@@
     \begin{itemize}
-        \item By considering average marginal contribution over all possible subset of coalitions, we can achieve a fair distribution.\\
+        \item By considering average marginal contribution over all possible subsets of coalitions, we can achieve a fair distribution.\\
         \item Let $\prod(N)$ denote the set of all permutations of the sequence $(1,...n)$. Therefore: $\phi_i(N,v) = \frac{\sum_{\sigma \in \phi_i(N)}}{mc(\sigma)}$

### 2013-12-17 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Transferable and Non Transferable Utility Games}
-    \begin{itemize}
-        \item \textbf{Games with Transferable Utility (TU games)}
-        \begin{itemize}
-            \item Utility is worth the same for all agents
-            \item Utility can be {\color{red} compared} or {\color{red} transferred} between agents.
-            \item Irrespective of the division of the coalitional payoff.
-            \begin{itemize}
-                \item In that case members of the coalition enjoy the same total utility.
-            \end{itemize}
-        \end{itemize}
+%\begin{frame}{Transferable and Non Transferable Utility Games}
+%    \begin{itemize}
+%        \item \textbf{Games with Transferable Utility (TU games)}
+%        \begin{itemize}
+%            \item Utility is worth the same for all agents.
+%            \item Utility can be {\color{red} compared} or {\color{red} transferred} between agents.
+%            \item Irrespective of the division of the coalitional payoff.
+%            \begin{itemize}
+%                \item In that case members of the coalition enjoy the same total utility.
+%            \end{itemize}
+%        \end{itemize}
+%
+%
+%        \begin{definition} [Valuation or Characteristic Function]\label{dfn:valuationfunction}
+%            A \emph{valuation function v} associates a real number $v(C)$ to any subset $C \subseteq N$, i.e., $v:2^N \rightarrow R$ \\
+%            A {\color{blue}\emph{TU game}} is a pair $(N,v)$ where $N$ is a set of agents and where $v$ is a valuation function.
+%        \end{definition}
+%
+%
+%
+%        \item \textbf{Games with Non Transferable Utility (NTU games)} \\
+%            Agents have different preferences over coalitions and rewards. Non-monetary rewards, i.e. item allocation type of problems where items have %different values for different players.
+%    \end{itemize}
 
-        \begin{definition} [Valuation or Characteristic Function]\label{dfn:valuationfunction}
-            A \emph{valuation function v} associates a real number $v(C)$ to any subset $C \subseteq N$, i.e., $v:2^N \rightarrow R$ \\
-            A {\color{blue}\emph{TU game}} is a pair $(N,v)$ where $N$ is a set of agents and where $v$ is a valuation function.
-        \end{definition}
-
-        \item \textbf{Games with Non Transferable Utility (NTU games)} \\
-            Agents have different preferences over coalitions and rewards. Non-monetary rewards, i.e. item allocation type of problems where items have different values for different players.
-    \end{itemize}
-
-\end{frame}
+%\end{frame}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{frame}{Solution Properties}
-    Let $x \in R^n$ be a solution of the TU game $(N,v)$
+    Let $x \in R^n$ be a solution of the coalition game $(N,v)$
     \begin{itemize}
@@
         \begin{itemize}
-            \item the payoff distribution is an allocation of the entire worth of the grand coalition to all agents
+            \item the payoff distribution is an allocation of the entire worth of the grand coalition to all agents.
         \end{itemize}
@@
         \begin{itemize}
-            \item player obtains at least its self-value of payoff
+            \item player obtains at least its self-value of payoff.
         \end{itemize}
@@
 
-    An {\color{red} imputation} is a payoff distribution $x$ that is efficient and individual rational.
+    An {\color{blue} imputation} is a payoff distribution $x$ that is efficient and individual rational.
 
@@
         \item A condition for a coalition to form:
-            {\color{blue}all} agents prefer to be in it. i.e., none of the participants wishes she were in a different coalition or by herself {\color{red} $\Rightarrow Stability$ }
+            {\color{blue}all} agents prefer to be in it. i.e., none of the participants wishes she were in a different coalition or by herself {\color{blue} $\Rightarrow Stability$ }
         \item The {\color{blue} core} is a stability concept for which no agents prefer to deviate to form a different coalition.
@@
     The core relates to the stability of the grand coalition: \\ No group of agents has any incentive to change coalition.
-    \begin{definition}[$Core$ of a game $(N,v)$]\label{dfn:core}
+    \begin{definition}[$Core$ of a Game $(N,v)$]\label{dfn:core}
         Let $(N,v)$ be a cooperative game, and assume they form the coalition $N$. The core of $(N,v)$ is the set:
@@
     \begin{definition} [Marginal Contribution]\label{dfn:marginalcontribution}
-        The {\color{red}marginal contribution} of agent $i$ for a coalition $C \subseteq N \backslash \{i\}$ is $mc_i(C) = v(C \cup \{i\}) - v(C)$
+        The {\color{blue}marginal contribution} of agent $i$ for a coalition $C \subseteq N \backslash \{i\}$ is $mc_i(C) = v(C \cup \{i\}) - v(C)$
     \end{definition}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Some properties}
+\begin{frame}{Some Properties}
     \begin{itemize}
-        \item The core may not always be non-empty
+        \item The core may not always be non-empty.
         \item Shapley value always exists and is unique.
-        \item When the valuation function is {\color{red}superadditive}, the Shapley value is {\color{red}individually rational}, i.e., it is an imputation.
-        \item When the valuation function is {\color{red}convex}, the Shapley value is also group rational, hence, it is in the {\color{red}core}.
-        \item A convex game has a non-empty core
+        \item When the valuation function is {\color{blue}superadditive}, the Shapley value is {\color{blue}individually rational}, i.e., it is an imputation.
+        \item When the valuation function is {\color{blue}convex}, the Shapley value is also group rational, hence, it is in the {\color{blue}core}.
+        \item A convex game has a non-empty core.
         \item Core and Shapley value are combinatorial problems.
@@
     \begin{itemize}
-        \item Communities are robust service providers with well established market share and reputation
-        \item The community is characterized by a request rate $R_C$
-        \item Web services can perform tasks with some throughput rate ($Th_{ws}$)
+        \item Communities are robust service providers with well established market share and reputation.
+        \item The community is characterized by a request rate $R_C$.
+        \item Web services can perform tasks with some throughput rate ($Th_{ws}$).
         \item Web services come with different values of $QoS_{ws}$ for different metrics.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Task distribution}
+\begin{frame}{Task Distribution}
     \begin{itemize}
@@
     \begin{itemize}
-        \item A typical WS community, where web services can join or leave
-        \item $v(C) = Out(C)$
+        \item A typical WS community, where web services can join or leave.
+        \item $v(C) = Out(C)$.
         \item Membership decision in made based on throughput and QoS of the web services.
@@
         \end{itemize}
-        \item Has to be distributed not centralized
+        \item Has to be distributed not centralized.
         \item Merge and Split Algorithm {\footnotesize{\color{blue}{(Krzysztof R. Apt and Andreas Witzel)}}}
         \begin{itemize}
-            \item Iterative
+            \item Is iterative
             \item Converges to a final partition
@@
     \begin{itemize}
-        \item The core may not always be non-empty, core is a strong condition
-        \item $\epsilon$-core relaxes the core condition
+        \item The core may not always be non-empty, core is a strong condition.
+        \item $\epsilon$-core relaxes the core condition.
         \item $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon$
@@
         \includegraphics[width=3in]{figures/least_core.pdf}
-        \caption{Analysis of \emph{$\epsilon$-core} set non-emptiness, for different values of $\epsilon$} \label{f_leastcore}
+        \caption{Analysis of \emph{$\epsilon$-core} set non-emptiness, for different values of $\epsilon$}. \label{f_leastcore}
     \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Representation and Complexity issues}
+\begin{frame}{Representation and Complexity Issues}
     \begin{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Induced subgraph games}
+\begin{frame}{Induced Subgraph Games}
     \begin{itemize}
@@
         \item for all $C \subseteq N, v(C) = \sum_{(i,j) \in C} w_{ij}$
-        \item {\color{red}Space Complexity:} Using an adjacency matrix, we need to provide $n^2$ entries.
-        \item {\color{red}Convexity:} If all the weights are nonnegative then the game is convex.
-        \item {\color{red}Shapley Value:} $\phi_i(N,v) = \frac{1}{2} \sum_{(i,j) \in N^2 | i \neq j}w_{ij}$
-        \item This is {\color{red}not complete}. Many TU games cannot be represented by a induced subgraph game
+        \item {\color{blue}Space Complexity:} Using an adjacency matrix, we need to provide $n^2$ entries.
+        \item {\color{blue}Convexity:} If all the weights are nonnegative then the game is convex.
+        \item {\color{blue}Shapley Value:} $\phi_i(N,v) = \frac{1}{2} \sum_{(i,j) \in N^2 | i \neq j}w_{ij}$
+        \item This is {\color{blue}not complete}. Many coalition games cannot be represented by a induced subgraph game.
 
@@
         \item Submitted a Paper to the 10th International Conference on Service Oriented Computing (ICSOC 2012); \emph{"Analyzing Coopetition Strategies of Services within Communities"} {\color{blue} (Accepted)}
-        \item Submitted a Journal Paper to the International Journal of Expert Systems With Applications; IEEE Transactions on Services Computing; \emph{"To Compete or to Cooperate?
+        \item Submitted a Journal Paper to the International Journal of Expert Systems With Applications; \emph{"To Compete or to Cooperate?
 This is the Question in Communities of Autonomous Services"}

### 2013-12-17 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

@@
 
-    \begin{frame}{Cooperative Game Theory}
-      \begin{itemize}
-         \item Cooperative games are a branch of game theory that models cooperation or collaboration between agents.
-         \begin{itemize}
-            \item Cooperation to perform a set of tasks that requires different expertise.
-            \item Agents do not have enough resource on their own to perform the tasks.
-            \item Examples:
-            \begin{itemize}
-                \item Robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
-                \item Transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
-            \end{itemize}
-        \end{itemize}
-        \item \textbf{Issues:}
-            \begin{itemize}
-                \item Coalition formation.
-                \item Rewarding members when a task is completed.
-            \end{itemize}
-      \end{itemize}
-    \end{frame}
+%    \begin{frame}{Cooperative Game Theory}
+%      \begin{itemize}
+%         \item Cooperative games are a branch of game theory that models cooperation or collaboration between agents.
+%         \begin{itemize}
+%            \item Cooperation to perform a set of tasks that requires different expertise.
+%            \item Agents do not have enough resource on their own to perform the tasks.
+%            \item Examples:
+%            \begin{itemize}
+%                \item Robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
+%                \item Transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
+%            \end{itemize}
+%        \end{itemize}
+%        \item \textbf{Issues:}
+%            \begin{itemize}
+%                \item Coalition formation.
+%                \item Rewarding members when a task is completed.
+%            \end{itemize}
+%      \end{itemize}
+%    \end{frame}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{The Classic Problem}
-    We have a population $N$ of $n$ agents.
+\begin{frame}{Cooperative Game Theory}
+    \begin{itemize}
+         \item Cooperative games are a branch of game theory that models cooperation or collaboration between agents within coalitions.
+    \end{itemize}
     \begin{definition} [Coalition]~\\
-       A coalition $C$ is a set of agents: $C \in 2^N$.
+       We have a population $N$ of $n$ agents, A coalition $C$ is a set of agents: $C \in 2^N$.
         \begin{itemize}
@@
         \item {\color{blue} Weekly super additive:} $v(C_1 \bigcup \{i\}) \geq v(C_1) + v(\{i\})$
+        \item {\color{red} Subadditive:} $v(C_1 \bigcup C_2) \leq v(C_1) + v(C_2)$
     \end{itemize}
@@
         \item {\color{blue} Convex:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2) - v(C_1 \bigcap C_2)$. Convexity has important properties in cooperative game theory solution concepts.
-    \end{itemize}
-    \begin{itemize}
-        \item {\color{red} Subadditive:} $v(C_1 \bigcup C_2) \leq v(C_1) + v(C_2)$
     \end{itemize}
@@
         \item {\color{blue} Feasible solution:} $\sum_{i \in N} x(i) \leq v(N)$
-        \item {\color{blue} Efficiency:} $x(N) = v(N)$
+        \item {\color{blue} Efficiency:} $\sum_{i \in N} x(i) = v(N)$
         \begin{itemize}
@@
     \begin{itemize}
-        \item Communities are robust service providers with well established market share and reputation.
+        \item Communities of web services are robust service providers with well established market share and reputation.
         \item The community is characterized by a request rate $R_C$.
@@
         \item $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon$
-        \item relative e-core: $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq (1-\epsilon).v(S)$
+        \item relative $\epsilon$-Core: $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq (1-\epsilon).v(S)$
     \end{itemize}

### 2013-12-31 papers/coalition-journal-R1/response_letterr.tex
changes

%\documentclass[preprint,authoryear,12pt]{elsarticle}
\documentclass[times, 12pt,a4paper]{article}
\usepackage{graphicx,amssymb,amsthm,stmaryrd}%,booktabs}
\usepackage{times}
\usepackage{amsmath,url,algorithm,algorithmic,mathrsfs,makeidx}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{epsfig}
\usepackage{latex8}

%journal{Journal of Knowledge-Based Systems}

\begin{document}
%\begin{frontmatter}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{example}{Example}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary} {Corollary}
\title{\underline{Response Letter}\\\vspace{0.5cm}Efficient Community Formation for Web Services}
\author{Ehsan Khosrowshahi Asl\\
e\_khosr@encs.concordia.ca\\
\and
Hadi Otrok\\
hadi.otrok@kustar.ac.ae \\
\and
Jamal Bentahar\\
bentahar@ciise.concordia.ca \\
\and
Rabeb Mizouni\\
rabeb.mizouni@kustar.ac.ae \\
}

\maketitle

First, we would like to thank and express our appreciation to the
reviewers for taking the time to carefully review our manuscript,
and for their insightful, valuable, and very useful comments. We
would like to thank the editor as well for his valuable comments
and suggestions for improvements. We carefully considered the
comments and implemented all of them in the revised version. In
this letter, we will explain, point by point, how the issues
raised in the reviews are addressed and answered. We start by
reporting a summary of changes.

\begin{center}
\textbf{\textit{ Summary of changes:}}
\end{center}

\begin{itemize}
\item  We fixed the paradoxes highlighted in the previous version
of the manuscript by proposing CTLKC$^+$, a new logic that can be
used to reason simultaneously about knowledge and social
commitments in multi-agent systems.

\item  We added the model, syntax and semantics of CTLKC$^+$.

\item  We explained the new social accessibility relation of
CTLKC$^+$, its intuition and its properties.

             %\item  We fixed eight paradoxes using the semantics of CTLKC$^+$ logic by providing formal proofs for the valid properties and models (counterexamples) for the non-valid properties.
             %\item  We removed paradox P7 (the reasons for that will be explained later).
             %\item  We added some references recommended by the reviewers.

\item We outlined a model checking technique for CTLKC$^+$ based
on the reduction from the model checking problem of GCTL$^*$, a
generalized logic of CTL*.

\item We analyzed the computational complexity of the model
checking problem of CTLKC$^+$ and proved that this complexity is
the same as the one of model checking CTLK and CTLC separately.

\item We implemented the proposed model checking technique and
reported verification results.

\item We highlighted the motivations and contributions of the
paper.

\end{itemize}

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%% REVIEWER 1 %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
  \textbf{Reviewer 1}
\end{center}

\vspace{0.4cm}\textbf{\underline{1. Reviewer}:} 
You should relate V(S) to PO(C) in equations 5 and 6.

\vspace{0.2cm}\textbf{\underline{Answer 1}: 
We modified the section and added the connection at the end of paragraph, 
however we had already connected them when we were describing the algorithm 
of our scenario in section 4.1}

\vspace{0.4cm}\textbf{\underline{2. Reviewer}:} 
please add some definitions such as the one for Grand coalition
to make the paper self-contained.

\vspace{0.2cm}\textbf{\underline{Answer 2}: 
Great suggestion, we did add more definitions for second scneraio too.}

\vspace{0.4cm}\textbf{\underline{3. Reviewer}:} 
Why you didn't leverage the foundations of repeated games instead of
coalitional games? Is there any strong reason?.

\vspace{0.2cm}\textbf{\underline{Answer 3}: 
The communities are models as cooperative groups and that is why cooperative game thoery methods provide us with great decision mechanisims for forming groups and coalitions which would benefit all the agents involved altogether. In repeated games, there should be a repeatable game between agents one to one, where decision cannot be optimal for all the agents involved. We belieave repeated game is appropriate in cases where there is a lot of competing one-to-one interaction between agents are happening, and actually we are working on repeated games and specificly repeated game with learning techniques such as q-learning to help distribute the ``task distribution job'' among all the web services. Where web services are having different confidence states, and based on their action history and state they are in, web services can directly opt for getting and performing tasks alone or cooperating which other agents. 
}

\vspace{0.4cm}\textbf{\underline{4. Reviewer}:} 
What do you mean by "the algorithm gets interrupted": is it based on
a logical condition? if yes, what is it?

\vspace{0.2cm}\textbf{\underline{Answer 4}: 
It means if there is time constraint, the algorithm can get interrupted any time, and yet have depth(n-1) results. Each depth will have $O(n^2)$ cases to check, so for example if in 5 second it reaches depth 10, and we interrupt the algorithm since we cannot wait any loner,  we at least have checked for all subsets of depth 9}

\vspace{0.4cm}\textbf{\underline{5. Reviewer}:} 
Please provide equations using lambda and epsilon and relate them
to your model that uses Rc.

\vspace{0.2cm}\textbf{\underline{Answer 5}: 
We added the new stability($Core$ condition} in case of having taxtation.}

\vspace{0.4cm}\textbf{\underline{5. Reviewer}:} 
For the epslion core method: the value of epsilon should be
varied to verify its impact in the experiments section.

\vspace{0.2cm}\textbf{\underline{Answer 5}: 
That is exactly what we are doing, we changes the explanation to make what we did more clear.}

\vspace{0.4cm}\textbf{\underline{6. Reviewer}:} 
The experiments are missing a comparison with [18] is missing.

\vspace{0.2cm}\textbf{\underline{Answer 6}: 
The expirement which was illustrated in figure[9] was comparision of our work with [18], for all the scenarios which we could make it comparable and fair with.}

\vspace{0.4cm}\textbf{\underline{7. Reviewer}:} 
Scalability evaluation is missing: what is the impact of increasing the number of services/communities on the system efficiency?.

\vspace{0.2cm}\textbf{\underline{Answer 7}: 
As mentioned in the paper, our algorithms run in $O(n)$ and $O(n^2)$ time as number of web services with a community (n) grows. Also with the real web service data provided in http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/ the largest communities in our expirements, did not grow larger than 60 web services. However in cases where $R_C$ is very large, communities can grow
large. However there will be no problem community management, and task distrobution algorithms as the number of web services grows, I could set $R_C$ very large in simulation but since we do not evaluate run time of comunity formation and membership strategies decisions, it will not affect our results.
}

All other comments are directly addressed in paper.

%%%%%%%%%%%%%%%%%%%%%%%%% REVIEWER 2 %%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2cm}

\begin{center}
  \textbf{Reviewer 2}
\end{center}

\vspace{0.4cm}\textbf{\underline{1. Reviewer}:}  Though there’s a referral to [8] it’d be helpful to explain more the concept of “Community coordinators” web services, somewhere in the early parts of the paper. How’s it different from other (common) web services in a given community.

``community master'' and ``community coordinator'' – are these different?

\vspace{0.2cm}\textbf{\underline{Answer 1}: We changed the way how we described our architecture, we dropped the concept of community master web service and we defined a separate entity as community coordinator.}

\vspace{0.4cm} \textbf{\underline{2. Reviewer}}: p.10 ``our community receives 130 tasks from users'' what are the types of tasks. Are these simulated or real functions that need to performed by web services?

\vspace{0.2cm}\textbf{\underline{Answer 2}: The tasks are randomly generated, and since communities are composed of web services performing same type of operations, they have same functional requirement and are of same type. In our implementation, we let communities perform tasks, and based on community task queue delay and also the assigned web service quality metric such as reliability, throughput, latency, successability and other metrics, the tasks will be performed with different qualities which we have evaluated and illustrated the results as average QoS of tasks performed}

All other comments are directly addressed in paper.

%%%%%%%%%%%%%%%%%%%%%%%%% REVIEWER 3 %%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2cm}

\newpage

\begin{center}
  \textbf{Reviewer 3}
\end{center}

\vspace{0.4cm}\textbf{\underline{1. Reviewer}:}  It is not convincing that the formation of service community can be modeled as a cooperative gaming problem. First, the concept of service community used in this paper is different from the ones used in the existing work, such as in the referred papers. The general idea of service community is a homogeneous service group that conceptually include services providing similar functionality. Services in the same community are independent and autonomous. There is no central control mechanism for the community. On the other hand, the concept of service community of this paper is a group of services which are monitored and managed by a community manager. It is not clear how realistic or practical such a community is and what the real world examples are.

\vspace{0.2cm}\textbf{\underline{Answer 1}: We changed the way how we described our architecture, we dropped the concept of community master web service and we defined a separate entity as community coordinator.}

\vspace{0.4cm}\textbf{\underline{2. Reviewer}:}  The problem is modeled in a way so that the cooperative game theory can be applied, but not in a way that is consistent with the real world scenarios. The service parameters, such as its request rate and throughout rate are not in line with the general characteristics of web services, such as input and output parameters. It is not clear how the proposed service parameters are obtained and why they are important to determine a service's membership to a community, considering that they depend on not only the service's capacity, but also the amount and frequency of user requests, which can be random.

\vspace{0.2cm}\textbf{\underline{Answer 2}: We changed the way how we described our architecture, we dropped the concept of community master web service and we defined a separate entity as community coordinator.}

\vspace{0.4cm}\textbf{\underline{3. Reviewer}:}  The paper conducted a simulation instead of an experimental study using real world web services. This also suggests the difficulties of finding real world examples and application for the proposed idea.

\vspace{0.2cm}\textbf{\underline{Answer 3}: We changed the way how we described our architecture, we dropped the concept of community master web service and we defined a separate entity as community coordinator.}

\vspace{0.4cm}

\vspace{1cm}

Finally, we hope that we have answered all the questions raised by
the reviewers, which will make the paper accepted for publication
in Applied Intelligence Journal.

{
%\bibliographystyle{plain}
%\bibliography{omar}
}
\end{document}

### 2014-01-01 papers/coalition-journal-R1/response_letterr.tex
changes

@@
 this letter, we will explain, point by point, how the issues
-raised in the reviews are addressed and answered. We start by
-reporting a summary of changes.
+raised in the reviews are addressed and answered.
 
-\begin{center}
-\textbf{\textit{ Summary of changes:}}
-\end{center}
-
-\begin{itemize}
-\item  We fixed the paradoxes highlighted in the previous version
-of the manuscript by proposing CTLKC$^+$, a new logic that can be
-used to reason simultaneously about knowledge and social
-commitments in multi-agent systems.
-
-\item  We added the model, syntax and semantics of CTLKC$^+$.
-
-\item  We explained the new social accessibility relation of
-CTLKC$^+$, its intuition and its properties.
-
-             %\item  We fixed eight paradoxes using the semantics of CTLKC$^+$ logic by providing formal proofs for the valid properties and models (counterexamples) for the non-valid properties.
-             %\item  We removed paradox P7 (the reasons for that will be explained later).
-             %\item  We added some references recommended by the reviewers.
-
-\item We outlined a model checking technique for CTLKC$^+$ based
-on the reduction from the model checking problem of GCTL$^*$, a
-generalized logic of CTL*.
-
-\item We analyzed the computational complexity of the model
-checking problem of CTLKC$^+$ and proved that this complexity is
-the same as the one of model checking CTLK and CTLC separately.
-
-\item We implemented the proposed model checking technique and
-reported verification results.
-
-\item We highlighted the motivations and contributions of the
-paper.
-
-\end{itemize}
-
-\newpage
+%\newpage
 
@@
 \vspace{0.2cm}\textbf{\underline{Answer 5}:
-We added the new stability($Core$ condition} in case of having taxtation.}
+We added the new stability($Core$ condition) in case of having taxtation.}
 
@@
 \vspace{0.2cm}\textbf{\underline{Answer 6}:
-The expirement which was illustrated in figure[9] was comparision of our work with [18], for all the scenarios which we could make it comparable and fair with.}
+The expirement which was illustrated in figure[9] was comparision of our work with [18], for all the scenarios which we could make it comparable and fair with.
+We have called their method ``High Availability Coalition Method''}
 
@@
 
-All other comments are directly addressed in paper.
-
 %%%%%%%%%%%%%%%%%%%%%%%%% REVIEWER 2 %%%%%%%%%%%%%%%%%%%%%%%%%
 \vspace{2cm}
+
+\newpage
 
@@
 
-All other comments are directly addressed in paper.
-
 %%%%%%%%%%%%%%%%%%%%%%%%% REVIEWER 3 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 1}: We changed the way how we described our architecture, we dropped the concept of community master web service and we defined a separate entity as community coordinator.}
+\vspace{0.2cm}\textbf{\underline{Answer 1}: Most of the existing work such as [Liu 2012][18] (Coordinators), [Lim 2012][16] (Master Web Services], [Benatallah 2003][9] (Service Containers), [Maamar 2008][14], [Maamar 2009][8] (Master Web service), [Zeng 2003][11] (Service selection and task delegation), [Medjahed 2005][13] (Community Providers), [Limam 2010]\footnote{Managing Web Services Communities: A Cache for Queries Optimisation, International Journal on Web Service Computing, Vol.1, No.1, pp 2230-7702, 2010} (Centralized access in their community definition), have clearly stated that communities of web services need a centralized manager for the purposes of developing, coordinating and managing the community and in some of the works, being the access point of the community and having the task of delegating tasks.
+We have added a web service community related work section to highlight this point.}
 
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 2}: We changed the way how we described our architecture, we dropped the concept of community master web service and we defined a separate entity as community coordinator.}
+\vspace{0.2cm}\textbf{\underline{Answer 2}: For web services quality metrics, we have used a real world data set provided at: http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/.
+Having a request rate for communities cannot be unrealistic, here is a real world example: Kooshiar Azimian.
+CEO of concertboom.com has provided me with their access and request rates of the web services they use\ref{cblog}.
+Their website provides ticketing information for events happening close to user's location.
+They use Ticketnetwork.com web services\footnote{Affiliate program link: http://www.ticketnetwork.com/affiliates/agreement.aspx} \footnote{Web Service API documentation: http://www.getacoder.com/data/projects/77613/TicketNetwork\%20Web\%20Services\%20(W2)-.doc}, \footnote{We were asked not to enclose these data publicly, thats why we could not add them to paper} and have implemented their back-end code in Java.
+They currently almost have 340,000 daily page views, so they call the ticketnetwork web service almost 4 times per second to get the seating chart and tickets available for the events.
+During a day, the pick time happens at around 20:00 UTC time, which has almost 10\% more request rates than around the lower pick which is around 7:00 AM UTC time.
+Therefore basically ticketnetwork, knows concertboom.com as a user has a request rate of 340,000 requests per day or almost 3.95 requests per second and they can adjust and change these thresholds, and adjust the internal service providers and resources they have to provide these rate of services.
+}
+
+\begin{figure}
+\begin{center}
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=10cm]{cb.eps}\label{cblog}
+\caption{Number of ticket pageviews of concertboom.com during May 5th, until Sep 9th, 2013}
+\end{center}
+\end{figure}
 
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 3}: We changed the way how we described our architecture, we dropped the concept of community master web service and we defined a separate entity as community coordinator.}
+\vspace{0.2cm}\textbf{\underline{Answer 3}: Our focus is on non-functional properties of web services and is extendable to any type of web service communities providing any type of service, which there is high demand, request load and competition for that service type such as mapping, weather, ticketing, and local places information.
+As mentioned in previous answer we used a real data set of web services (http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/) for our implementations.
+We also added a functional SOAP (xml) based request, response to our implementation, however this as expected did not affect our simulation results, since our concern, as most of the related work, in on non-functional properties of web services.
+We added a modification to paper and highlighted this.
+In many related work such as
+[Yu 2013]\footnote{Q.
+Yu and A.
+Bouguettaya, Efficient Service Skyline Computation for Composite Service Selection, IEEE Transactions on Knowledge and Data Engineering (TKDE), vo.
+25, no.
+4, pp.
+776-789, 2013},
+[Limam 2010]\footnote{Managing Web Services Communities: A Cache for Queries Optimisation, International Journal on Web Service Computing, Vol.1, No.1, pp 2230-7702, 2010}, and
+[Liu 2012]\footnote{A.
+Liu, Q.
+Li, L.
+Huang, S.
+Ying, and M.
+Xiao,Coalitional game for community-based autonomous web services cooperation, IEEE Transactions on Services Computing, vol.
+99, no.
+PrePrints, 2012.}
+the results have been evaluated using simulations}
 
@@
 the reviewers, which will make the paper accepted for publication
-in Applied Intelligence Journal.
+in IEEE Transactions on Services Computing (TSC).
 

### 2014-01-04 papers/coalition-journal-R1/response_letterr.tex
changes
Rabeb changes

@@
 however we had already connected them when we were describing the algorithm
-of our scenario in section 4.1}
+of our scenario in section 4.1  
+% RABEB: I do not get what you mean by however we had ....
+I beleive taht you need to reformulate your answer by saying that : The connection between V(S) to PO(C) has been already defined when describing the algorithm of our scenario in section 4.1.
+To clarify it more, we modified the section and we added the connection at the end of the paragraph.
+}
 
@@
 \vspace{0.2cm}\textbf{\underline{Answer 2}:
-Great suggestion, we did add more definitions for second scneraio too.}
+Great suggestion, we did add more definitions for second scenario too.
+% RABEB : Cite the definitions you added (we did add the definitions of Grand coalition, .....
+
+}
 
@@
 \vspace{0.2cm}\textbf{\underline{Answer 3}:
-The communities are models as cooperative groups and that is why cooperative game thoery methods provide us with great decision mechanisims for forming groups and coalitions which would benefit all the agents involved altogether.
-In repeated games, there should be a repeatable game between agents one to one, where decision cannot be optimal for all the agents involved.
-We belieave repeated game is appropriate in cases where there is a lot of competing one-to-one interaction between agents are happening, and actually we are working on repeated games and specificly repeated game with learning techniques such as q-learning to help distribute the ``task distribution job'' among all the web services.
-Where web services are having different confidence states, and based on their action history and state they are in, web services can directly opt for getting and performing tasks alone or cooperating which other agents.
+Communities can be seen as cooperative groups where members of the same community cooperate  to achieve a better outcome.
+In this context, cooperative game theory methods provide us with great decision mechanisms for forming groups and coalitions which would benefit the agents involved altogether.
+In repeated games, there should be a repeatable game between agents one to one.
+The  decision cannot be optimal for all the agents involved.
+We believe repeated game is appropriate in cases where there is a lot of competing one-to-one interactions between agents  happening and not in coalitions.
+ and actually we are working on repeated games and specifically repeated game with learning techniques such as q-learning to help distribute the ``task distribution job'' among all the web services where web services are having different confidence states, and based on their action history and state they are in, web services can directly opt for getting and performing tasks alone or cooperating which other agents.
+% RABEB: I do not see the need for the last sentence starting from and actually we are as you are opening the door for questioning our decision  ...
+
 }
@@
 \vspace{0.2cm}\textbf{\underline{Answer 4}:
-It means if there is time constraint, the algorithm can get interrupted any time, and yet have depth(n-1) results.
-Each depth will have $O(n^2)$ cases to check, so for example if in 5 second it reaches depth 10, and we interrupt the algorithm since we cannot wait any loner,  we at least have checked for all subsets of depth 9}
+It means if there is time constraint, the algorithm can get interrupted any time, and yet has depth(n-1) results.
+Each depth will have $O(n^2)$ cases to check, so for example if in 5 second it reaches depth 10, and we interrupt the algorithm since we cannot wait any longer,  we at least have checked for all subsets of depth 9}
 
@@
 \vspace{0.2cm}\textbf{\underline{Answer 5}:
-We added the new stability($Core$ condition) in case of having taxtation.}
+We added the new stability($Core$ condition) in case of having taxtation.
+%RABEB: can you please specify where you have added this
+}
 
 \vspace{0.4cm}\textbf{\underline{5. Reviewer}:}
-For the epslion core method: the value of epsilon should be
+For the epsilon core method: the value of epsilon should be
 varied to verify its impact in the experiments section.
@@
 \vspace{0.2cm}\textbf{\underline{Answer 5}:
-That is exactly what we are doing, we changes the explanation to make what we did more clear.}
+Yes, the value of epsilon should vary to verify its impact and that is exactly what we are doing. We changed  the explanation to make this fact  more clear.}
 
@@
 \vspace{0.2cm}\textbf{\underline{Answer 6}:
-The expirement which was illustrated in figure[9] was comparision of our work with [18], for all the scenarios which we could make it comparable and fair with.
-We have called their method ``High Availability Coalition Method''}
+The experiment which was illustrated in figure[9] presents a comparison of our work with [18].
+We have called their method ``High Availability Coalition Method'' and we did a comparison for all the scenarios which we could make it comparable and fair with.
+%rabeb: can you please change the alst sentence. What are the scenarios we have compared to and those that we cannot compare and why  
+ }
 
@@
 \vspace{0.2cm}\textbf{\underline{Answer 7}:
-As mentioned in the paper, our algorithms run in $O(n)$ and $O(n^2)$ time as number of web services with a community (n) grows.
-Also with the real web service data provided in http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/ the largest communities in our expirements, did not grow larger than 60 web services.
+As mentioned in the paper, our algorithms run in $O(n)$ and $O(n^2)$ time as number of web services within a community (n) grows.
+Also with the real web service data provided in http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/, the largest communities used in our experiments did not grow larger than 60 web services.
 However in cases where $R_C$ is very large, communities can grow
 large.
-However there will be no problem community management, and task distrobution algorithms as the number of web services grows, I could set $R_C$ very large in simulation but since we do not evaluate run time of comunity formation and membership strategies decisions, it will not affect our results.
+This fact has no impact on the community management, and task distribution algorithms as the number of web services grows, during the simulation  $R_C$ could be set to a very large number  but since we do not evaluate run time of community formation and membership strategies decisions, this will not affect our results.
+%RABEB: it is not clear what you would like to say in the last sentence.
+
 }
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 1}: We changed the way how we described our architecture, we dropped the concept of community master web service and we defined a separate entity as community coordinator.}
+\vspace{0.2cm}\textbf{\underline{Answer 1}: We changed the way  we described our architecture. We dropped the concept of community master web service and we defined  community coordinator.}
 
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 2}: The tasks are randomly generated, and since communities are composed of web services performing same type of operations, they have same functional requirement and are of same type.
-In our implementation, we let communities perform tasks, and based on community task queue delay and also the assigned web service quality metric such as reliability, throughput, latency, successability and other metrics, the tasks will be performed with different qualities which we have evaluated and illustrated the results as average QoS of tasks performed}
+\vspace{0.2cm}\textbf{\underline{Answer 2}: The tasks are randomly generated, and since communities are composed of web services performing the same type of operations, the tasks have the same functional requirement and are of the same type.
+In our implementation, we let communities perform tasks, and based on community task queue delay and also the assigned web service quality metric such as reliability, throughput, latency and other metrics, these tasks will be performed with different qualities which we have evaluated and illustrated the results as average QoS of tasks performed
+%Rabeb: can you please add where we have presented these results 
+}
 
@@
 \vspace{0.2cm}\textbf{\underline{Answer 1}: Most of the existing work such as [Liu 2012][18] (Coordinators), [Lim 2012][16] (Master Web Services], [Benatallah 2003][9] (Service Containers), [Maamar 2008][14], [Maamar 2009][8] (Master Web service), [Zeng 2003][11] (Service selection and task delegation), [Medjahed 2005][13] (Community Providers), [Limam 2010]\footnote{Managing Web Services Communities: A Cache for Queries Optimisation, International Journal on Web Service Computing, Vol.1, No.1, pp 2230-7702, 2010} (Centralized access in their community definition), have clearly stated that communities of web services need a centralized manager for the purposes of developing, coordinating and managing the community and in some of the works, being the access point of the community and having the task of delegating tasks.
-We have added a web service community related work section to highlight this point.}
+We have added a web service community related work section in section I to highlight this point.
+
+}
 
@@
 Their website provides ticketing information for events happening close to user's location.
-They use Ticketnetwork.com web services\footnote{Affiliate program link: http://www.ticketnetwork.com/affiliates/agreement.aspx} \footnote{Web Service API documentation: http://www.getacoder.com/data/projects/77613/TicketNetwork\%20Web\%20Services\%20(W2)-.doc}, \footnote{We were asked not to enclose these data publicly, thats why we could not add them to paper} and have implemented their back-end code in Java.
+They use Ticketnetwork.com web services\footnote{Affiliate program link: http://www.ticketnetwork.com/affiliates/agreement.aspx} \footnote{Web Service API documentation: http://www.getacoder.com/data/projects/77613/TicketNetwork\%20Web\%20Services\%20(W2)-.doc}, \footnote{We were asked not to enclose these data publicly, that's why we could not add them to the paper} and have implemented their back-end code in Java.
 They currently almost have 340,000 daily page views, so they call the ticketnetwork web service almost 4 times per second to get the seating chart and tickets available for the events.
@@
 \vspace{0.2cm}\textbf{\underline{Answer 3}: Our focus is on non-functional properties of web services and is extendable to any type of web service communities providing any type of service, which there is high demand, request load and competition for that service type such as mapping, weather, ticketing, and local places information.
+%rabeb: did not understand this sentence
+
  As mentioned in previous answer we used a real data set of web services (http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/) for our implementations.
-We also added a functional SOAP (xml) based request, response to our implementation, however this as expected did not affect our simulation results, since our concern, as most of the related work, in on non-functional properties of web services.
-We added a modification to paper and highlighted this.
-In many related work such as
-[Yu 2013]\footnote{Q.
+We also added a functional SOAP (xml) based request, response to our implementation, however this as expected did not affect our simulation results, since our concern, as most of the related work, is on non-functional properties of web services.
+We modified the implementation section of the  paper to highlight this.
+ Simulation is a commonly used approach in web service community for validation.
+For instance, [Yu 2013]\footnote{Q.
 Yu and A.
@@
 99, no.
-PrePrints, 2012.}
-the results have been evaluated using simulations}
+PrePrints, 2012.} the contribution which we have extended their work,
+have evaluated their results using simulations.
+
+}
 

### 2014-01-07 papers/coalition-journal-R1/response_letterr.tex
changes

@@
 \vspace{0.2cm}\textbf{\underline{Answer 1}:
-We modified the section and added the connection at the end of paragraph,
-however we had already connected them when we were describing the algorithm
-of our scenario in section 4.1  
+The connection between V(S) to PO(C) has been already defined when describing the algorithm of our scenario in section 4.1.
+To clarify it more, we modified the section and we added the connection at the end of the paragraph.
+}
 % RABEB: I do not get what you mean by however we had ....
@@
 To clarify it more, we modified the section and we added the connection at the end of the paragraph.
-}
 
-\vspace{0.4cm}\textbf{\underline{2. Reviewer}:}
-please add some definitions such as the one for Grand coalition
-to make the paper self-contained.
+%\vspace{0.4cm}\textbf{\underline{2. Reviewer}:}
+%please add some definitions such as the one for Grand coalition
+%to make the paper self-contained.
 
-\vspace{0.2cm}\textbf{\underline{Answer 2}:
-Great suggestion, we did add more definitions for second scenario too.
-% RABEB : Cite the definitions you added (we did add the definitions of Grand coalition, .....
-
-}
+%\vspace{0.2cm}\textbf{\underline{Answer 2}:
+%Great suggestion, we did add more definitions for second scenario too.
+% RABEB : Cite the definitions you added we did add the definitions of Grand coalition, .....
+%}
 
@@
 The  decision cannot be optimal for all the agents involved.
-We believe repeated game is appropriate in cases where there is a lot of competing one-to-one interactions between agents  happening and not in coalitions.
- and actually we are working on repeated games and specifically repeated game with learning techniques such as q-learning to help distribute the ``task distribution job'' among all the web services where web services are having different confidence states, and based on their action history and state they are in, web services can directly opt for getting and performing tasks alone or cooperating which other agents.
+We believe repeated game is more appropriate in cases where there is a lot of competing one-to-one interactions between agents  happening and not in coalitions.
+ %and actually we are working on repeated games and specifically repeated game with learning techniques such as q-learning to help distribute the ``task distribution job'' among all the web services where web services are having different confidence states, and based on their action history and state they are in, web services can directly opt for getting and performing tasks alone or cooperating which other agents.
+}
 % RABEB: I do not see the need for the last sentence starting from and actually we are as you are opening the door for questioning our decision  ...
-
-}
 
@@
 It means if there is time constraint, the algorithm can get interrupted any time, and yet has depth(n-1) results.
-Each depth will have $O(n^2)$ cases to check, so for example if in 5 second it reaches depth 10, and we interrupt the algorithm since we cannot wait any longer,  we at least have checked for all subsets of depth 9}
+Each depth will have $O(n^2)$ cases to check, so for example if in 5 second it reaches depth 10, and we interrupt the algorithm since we cannot wait any longer,  we at least have checked for all subsets of depth 9}.
+Clarification has been added in the paper to explain the algorithm interruption.
 
@@
 \vspace{0.2cm}\textbf{\underline{Answer 5}:
-We added the new stability($Core$ condition) in case of having taxtation.
-%RABEB: can you please specify where you have added this
+We added the new stability($Core$ condition) in case of having taxation (Page 10, Equation 8).
 }
@@
 \vspace{0.2cm}\textbf{\underline{Answer 6}:
-The experiment which was illustrated in figure[9] presents a comparison of our work with [18].
-We have called their method ``High Availability Coalition Method'' and we did a comparison for all the scenarios which we could make it comparable and fair with.
-%rabeb: can you please change the alst sentence. What are the scenarios we have compared to and those that we cannot compare and why  
+The experiment which was illustrated in figure[9] presents a comparison of our work with [18]. We have called their method ``High Availability Coalition Method''.
  }
@@
 \vspace{0.2cm}\textbf{\underline{Answer 7}:
-As mentioned in the paper, our algorithms run in $O(n)$ and $O(n^2)$ time as number of web services within a community (n) grows.
-Also with the real web service data provided in http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/, the largest communities used in our experiments did not grow larger than 60 web services.
-However in cases where $R_C$ is very large, communities can grow
-large.
-This fact has no impact on the community management, and task distribution algorithms as the number of web services grows, during the simulation  $R_C$ could be set to a very large number  but since we do not evaluate run time of community formation and membership strategies decisions, this will not affect our results.
-%RABEB: it is not clear what you would like to say in the last sentence.
-
+Actually we tried scalability tests, however they did not provide us any special results, since
+as mentioned in the paper, our algorithms run in $O(n)$ and $O(n^2)$ time as number of web services within a community (n) grows.  So basically our algorithms run in polynomial time.
+% rabeb: what do you mean our algorithms run in instant time ? do you mean polynomial time 
+ When conducting our experiments using the real web service data provided in http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/, the largest communities used  did not grow larger than 60 web services.
+On the other hand, increasing number of tasks  will not effect our results, since communities would only accept tasks at rate $R_C$.
+In case $R_C$ is set very large, communities can grow larger, and may suffer from  bottleneck due to huge number of task processing on a single server, a fact that is out of scope of this paper.
 }
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 2}: The tasks are randomly generated, and since communities are composed of web services performing the same type of operations, the tasks have the same functional requirement and are of the same type.
-In our implementation, we let communities perform tasks, and based on community task queue delay and also the assigned web service quality metric such as reliability, throughput, latency and other metrics, these tasks will be performed with different qualities which we have evaluated and illustrated the results as average QoS of tasks performed
-%Rabeb: can you please add where we have presented these results 
+\vspace{0.2cm}\textbf{\underline{Answer 2}: During our experiments,  the tasks are randomly generated.
+Since communities are composed of web services performing the same type of operations, these tasks have the same functional requirement and are of the same type.
+In our implementation, we let communities perform tasks.
+Based on community task queue delay and  the assigned web service quality metrics (such as reliability, throughput, latency and other metrics) these tasks will be performed with different qualities.
+In experimental results and analysis section, we have illustrated and evaluated  the average QoS of tasks performed.
 }
@@
 We have added a web service community related work section in section I to highlight this point.
-
 }
@@
 Having a request rate for communities cannot be unrealistic, here is a real world example: Kooshiar Azimian.
-CEO of concertboom.com has provided me with their access and request rates of the web services they use\ref{cblog}.
+CEO of concertboom.com has provided us with their access and request rates of the web services they use\ref{cblog}.
 Their website provides ticketing information for events happening close to user's location.
 They use Ticketnetwork.com web services\footnote{Affiliate program link: http://www.ticketnetwork.com/affiliates/agreement.aspx} \footnote{Web Service API documentation: http://www.getacoder.com/data/projects/77613/TicketNetwork\%20Web\%20Services\%20(W2)-.doc}, \footnote{We were asked not to enclose these data publicly, that's why we could not add them to the paper} and have implemented their back-end code in Java.
-They currently almost have 340,000 daily page views, so they call the ticketnetwork web service almost 4 times per second to get the seating chart and tickets available for the events.
-During a day, the pick time happens at around 20:00 UTC time, which has almost 10\% more request rates than around the lower pick which is around 7:00 AM UTC time.
-Therefore basically ticketnetwork, knows concertboom.com as a user has a request rate of 340,000 requests per day or almost 3.95 requests per second and they can adjust and change these thresholds, and adjust the internal service providers and resources they have to provide these rate of services.
+As shown in figure \ref{fig1}, they currently have an average of 340,000 daily page views.
+They call the ticketnetwork web service almost 4 times per second to get the seating chart and tickets available for the events.
+During a day, the pick time happens at around 20:00 UTC time, which has almost 10\% more requests than during the lower pick time, which happens around 7:00 AM UTC time.
+Therefore basically ticketnetwork, knows concertboom.com as a user has a request rate of 340,000 requests per day or almost 3.95 requests per second and can adjust the internal service providers and resources so they can  provide these rate of services.
 }
@@
 \caption{Number of ticket pageviews of concertboom.com during May 5th, until Sep 9th, 2013}
+\label{fig1}
 \end{center}
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 3}: Our focus is on non-functional properties of web services and is extendable to any type of web service communities providing any type of service, which there is high demand, request load and competition for that service type such as mapping, weather, ticketing, and local places information.
-%rabeb: did not understand this sentence
-
- As mentioned in previous answer we used a real data set of web services (http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/) for our implementations.
-We also added a functional SOAP (xml) based request, response to our implementation, however this as expected did not affect our simulation results, since our concern, as most of the related work, is on non-functional properties of web services.
-We modified the implementation section of the  paper to highlight this.
- Simulation is a commonly used approach in web service community for validation.
-For instance, [Yu 2013]\footnote{Q.
+\vspace{0.2cm}\textbf{\underline{Answer 3}:
+%Our focus is on non-functional properties of web services and is extendable to any type of web service communities providing any type of service, which there is high demand, request load and competition for that service type such as mapping, weather, ticketing, and local places information.
+ As mentioned in our previous answer, we have used a real data set of web services (http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/) during our experiments.
+We also added a functional SOAP (XML) messaging system to our implementation, however this as expected did not affect our simulation results, since our concern, as most of the related work, is on non-functional properties of web services.
+We could deploy web services using JAX-WS in Java and deploy on different servers, however those web services would not reflect the quality of service parameters of real web services under load in real world, however those data set provides of with QoS values of real functioning web services online.
+ Similar works on web service community or composition such as
+[Yu 2013]\footnote{Q.
 Yu and A.
@@
 PrePrints, 2012.} the contribution which we have extended their work,
-have evaluated their results using simulations.
-
+have also evaluated their results using simulations.
 }

### 2014-01-07 papers/coalition-journal-R1/_old_response_letterr.tex
changes

--- 2014-01-07 papers/coalition-journal-R1/response_letterr.tex
@@
 It means if there is time constraint, the algorithm can get interrupted any time, and yet has depth(n-1) results.
-Each depth will have $O(n^2)$ cases to check, so for example if in 5 second it reaches depth 10, and we interrupt the algorithm since we cannot wait any longer,  we at least have checked for all subsets of depth 9}.
-Clarification has been added in the paper to explain the algorithm interruption.
+Each depth will have $O(n^2)$ cases to check, so for example if in 5 second it reaches depth 10, and we interrupt the algorithm since we cannot wait any longer,  we at least have checked for all subsets of depth 9}
 
@@
 }
+%RABEB: can you please specify where you have added this
 
@@
 Actually we tried scalability tests, however they did not provide us any special results, since
-as mentioned in the paper, our algorithms run in $O(n)$ and $O(n^2)$ time as number of web services within a community (n) grows.  So basically our algorithms run in polynomial time.
-% rabeb: what do you mean our algorithms run in instant time ? do you mean polynomial time 
- When conducting our experiments using the real web service data provided in http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/, the largest communities used  did not grow larger than 60 web services.
-On the other hand, increasing number of tasks  will not effect our results, since communities would only accept tasks at rate $R_C$.
-In case $R_C$ is set very large, communities can grow larger, and may suffer from  bottleneck due to huge number of task processing on a single server, a fact that is out of scope of this paper.
+as mentioned in the paper, our algorithms run in $O(n)$ and $O(n^2)$ time as number of web services within a community (n) grows, so basically our algorithms run in instant time.
+Also with the real web service data provided in http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/, the largest communities used in our experiments did not grow larger than 60 web services.
+Increasing number of tasks also will not effect us, since communities would only accept tasks at rate $R_C$.
+However in cases where $R_C$ is set very large, communities can grow larger, and bottleneck of huge number of task processing on a single server, is out of scope of this paper.
+large. 
 }
+%RABEB: it is not clear what you would like to say in the last sentence.
 
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 2}: During our experiments,  the tasks are randomly generated.
-Since communities are composed of web services performing the same type of operations, these tasks have the same functional requirement and are of the same type.
-In our implementation, we let communities perform tasks.
-Based on community task queue delay and  the assigned web service quality metrics (such as reliability, throughput, latency and other metrics) these tasks will be performed with different qualities.
-In experimental results and analysis section, we have illustrated and evaluated  the average QoS of tasks performed.
+\vspace{0.2cm}\textbf{\underline{Answer 2}: The tasks are randomly generated, and since communities are composed of web services performing the same type of operations, the tasks have the same functional requirement and are of the same type.
+In our implementation, we let communities perform tasks, and based on community task queue delay and also the assigned web service quality metric such as reliability, throughput, latency and other metrics, these tasks will be performed with different qualities which in excremental results and analysis section we have evaluated and illustrated the results as average QoS of tasks performed
+%Rabeb: can you please add where we have presented these results
 }
@@
 Having a request rate for communities cannot be unrealistic, here is a real world example: Kooshiar Azimian.
-CEO of concertboom.com has provided us with their access and request rates of the web services they use\ref{cblog}.
+CEO of concertboom.com has provided me with their access and request rates of the web services they use\ref{cblog}.
 Their website provides ticketing information for events happening close to user's location.
 They use Ticketnetwork.com web services\footnote{Affiliate program link: http://www.ticketnetwork.com/affiliates/agreement.aspx} \footnote{Web Service API documentation: http://www.getacoder.com/data/projects/77613/TicketNetwork\%20Web\%20Services\%20(W2)-.doc}, \footnote{We were asked not to enclose these data publicly, that's why we could not add them to the paper} and have implemented their back-end code in Java.
-As shown in figure \ref{fig1}, they currently have an average of 340,000 daily page views.
-They call the ticketnetwork web service almost 4 times per second to get the seating chart and tickets available for the events.
-During a day, the pick time happens at around 20:00 UTC time, which has almost 10\% more requests than during the lower pick time, which happens around 7:00 AM UTC time.
-Therefore basically ticketnetwork, knows concertboom.com as a user has a request rate of 340,000 requests per day or almost 3.95 requests per second and can adjust the internal service providers and resources so they can  provide these rate of services.
+They currently almost have 340,000 daily page views, so they call the ticketnetwork web service almost 4 times per second to get the seating chart and tickets available for the events.
+During a day, the pick time happens at around 20:00 UTC time, which has almost 10\% more request rates than around the lower pick which is around 7:00 AM UTC time.
+Therefore basically ticketnetwork, knows concertboom.com as a user has a request rate of 340,000 requests per day or almost 3.95 requests per second and they can adjust and change these thresholds, and adjust the internal service providers and resources they have to provide these rate of services.
 }
@@
 \caption{Number of ticket pageviews of concertboom.com during May 5th, until Sep 9th, 2013}
-\label{fig1}
 \end{center}
@@
 %Our focus is on non-functional properties of web services and is extendable to any type of web service communities providing any type of service, which there is high demand, request load and competition for that service type such as mapping, weather, ticketing, and local places information.
- As mentioned in our previous answer, we have used a real data set of web services (http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/) during our experiments.
+ As mentioned in previous answer we used a real data set of web services (http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/) for our implementations.
 We also added a functional SOAP (XML) messaging system to our implementation, however this as expected did not affect our simulation results, since our concern, as most of the related work, is on non-functional properties of web services.
@@
 PrePrints, 2012.} the contribution which we have extended their work,
-have also evaluated their results using simulations.
+have evaluated their results using simulations.
 }

### 2014-01-20 papers/coalition-journal-R1/response_letter-final.tex
changes

%\documentclass[preprint,authoryear,12pt]{elsarticle}
\documentclass[times, 12pt,a4paper]{article}
\usepackage{graphicx,amssymb,amsthm,stmaryrd}%,booktabs}
\usepackage{times}
\usepackage{amsmath,url,algorithm,algorithmic,mathrsfs,makeidx}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{epsfig}
\usepackage{latex8}

%journal{Journal of Knowledge-Based Systems}

\begin{document}
%\begin{frontmatter}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{example}{Example}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary} {Corollary}
\title{\underline{Response Letter}\\\vspace{0.5cm}Efficient Community Formation for Web Services}
\author{Ehsan Khosrowshahi Asl\\
e\_khosr@encs.concordia.ca\\
\and
Jamal Bentahar\\
bentahar@ciise.concordia.ca \\
\and
Hadi Otrok\\
hadi.otrok@kustar.ac.ae \\
\and
Rabeb Mizouni\\
rabeb.mizouni@kustar.ac.ae \\
}

\maketitle

First, we would like to thank and express our appreciation to the
reviewers for taking the time to carefully review our manuscript,
and for their insightful, valuable, and very useful comments. We
would like to thank the associate and chief editors as well for
their valuable comments and suggestions for improvements. We
carefully considered the comments and implemented all of them in
the revised version. In this letter, we will explain, point by
point, how the issues raised in the reviews are addressed and
answered. We hope our answers and revisions will satisfy the
reviewers and editors, which will make the paper accepted for
publication in IEEE Transactions on Services Computing (TSC).\\

%\newpage

%%%%%%%%%%%%%%%%%%%%%%%%% REVIEWER 1 %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
  \textbf{Reviewer 1}
\end{center}

\vspace{0.6cm} \textbf{\underline{Reviewer's appreciation}:} The
paper presents a nice modelling of community formation based on
coalition games. The authors defended well their approach and
provided good illustrative examples.

\vspace{0.2cm}\textbf{\underline{Answer}: Thank you for the
positive feedback.}

\vspace{0.5cm} \textbf{\underline{1. Reviewer}:} Page 4: Last
paragraph: should be $x_i$ instead of $i$ at the condition level.

\vspace{0.2cm}\textbf{\underline{Answer 1}: Thanks for the
comment. Actually, the confusion comes from Equation 2, which
should be $\forall S \subseteq N, \sum_{i \in S} x_i \geq v(S)$
instead of $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S)$
as $x_i$ is the payoff vector of the player $i$ and $S$ is the set
of all players. This has been fixed in Equation 2 and Equation 4
as well (Section 2.4).}

\vspace{0.5cm}\textbf{\underline{2. Reviewer}:}  Page 6: You
should relate $v(S)$ to $PO(C)$ in equations 5 and 6.

\vspace{0.2cm}\textbf{\underline{Answer 2}: The connection between
$v(S)$ and $PO(C)$ has been mentioned in Section 3.3, second
paragraph and when we described the algorithm of our scenario in
Section 4.1. To be more specific, the connection is between $v(C)$
and $Out(C)$ that is computed in Equation 6 based on $PO(C)$
computed in Equation 5. The connection is that the worth of a
community is set to the output the community can generate, i.e.,
$v(C) = Out(C)$. However, we agree that this should be reported
earlier. In the revised version it is clearly stated just after
Equation 6 (Section 3.2). }
% RABEB: I do not get what you mean by however we had .... I beleive taht you need to reformulate your answer by saying that : The connection between V(S) to PO(C) has been already defined when describing the algorithm of our scenario in section 4.1. To clarify it more, we modified the section and we added the connection at the end of the paragraph.

\vspace{0.5cm}\textbf{\underline{3. Reviewer}:} Page 7: Please add
some definitions such as the one for Grand coalition to make the
paper self-contained.

\vspace{0.2cm}\textbf{\underline{Answer 3}: In the revised
version, all the needed concepts are defined. Grand coalition is
defined as follows: In cooperative game theory, grand coalition is
a coalition that contains a maximum number of players as long as
they can maintain a stable (in terms of membership) and beneficial
(in terms of utility) group for all the players (Section 4.1,
paragraph 3).}

\vspace{0.5cm}\textbf{\underline{4. Reviewer}:} Why you didn't
leverage the foundations of repeated games instead of coalitional
games? Is there any strong reason?.

\vspace{0.2cm}\textbf{\underline{Answer 4}: The main objective of
this work is to optimize the gain of web service communities as a
whole and to ensure the creation of stable communities in terms of
joining and leaving activities. Such a problem is formulated by
the means of coalition games, a part of cooperative game theory
where the gain can be fairly distributed based on the contribution
of each member using the theory of \emph{shapley value}. In this
context, communities can be formed and have their stability
condition formulated based on the \emph{Core} solution concepts.
Repeated games fit better in situations where web services are
competing with each other so they can learn the best response by
playing the game repeatedly. In our case, web services are rather
cooperating where the objective of web services communities is to
motivate intra-community cooperation and to motivate quality web
services to join such communities. Because each community is seen
as a cooperative group where members cooperate to achieve a better
outcome, cooperative game theory methods provide us with great
decision mechanisms for forming groups and coalitions which would
benefit the agents involved altogether.}

\textbf{In fact, because members of the same community are
providing similar functionalities, one can argue that they are
competing with each other, rather than cooperating. However, the
main idea, and also the main innovation and contribution of the
paper is to show that those member web services can form strong
and stable communities as coalitions so that they can better
compete as a whole with other web services and other communities,
which will allow them to be better off. In other words, we are
promoting the idea of intra-community cooperation and
inter-community competition. This justifies the use of coalition
games instead of repeated games.}

\textbf{Because we found it important as motivation of our choice
of coalition games, this discussion is reflected in the revised
version in the introduction section (Section 1, Motivations part).
In this new part, we added examples from the business world to
highlight the cooperation strategy. This has been raised by
Reviewer 3 as well (see additional details in our Answer 1 to
Reviewer 3).}

%In repeated games, there should be a repeatable game between agents one to one. The  decision cannot be optimal for all the agents involved. We believe repeated game is more appropriate in cases where there is a lot of competing one-to-one interactions between agents  happening and not in coalitions.
 %and actually we are working on repeated games and specifically repeated game with learning techniques such as q-learning to help distribute the ``task distribution job'' among all the web services where web services are having different confidence states, and based on their action history and state they are in, web services can directly opt for getting and performing tasks alone or cooperating which other agents.
% RABEB: I do not see the need for the last sentence starting from and actually we are as you are opening the door for questioning our decision  ...

\vspace{0.5cm}\textbf{\underline{5. Reviewer}:} Page 8: What do
you mean by "the algorithm gets interrupted": is it based on a
logical condition? if yes, what is it?

\vspace{0.2cm}\textbf{\underline{Answer 5}: The interruption we
are mentioning can be either caused by time/memory constraints
when the number of subsets is big enough (timeout) or forced
manually by the system designer if for example the already
obtained results are satisfactory. In fact, if the algorithm gets
interrupted while verifying $depth(n)$, it will have $depth(n-1)$
already verified. Each depth will have $O(n^2)$ cases to check, so
for example if it reaches depth 10, and the algorithm gets
interrupted (manually or because of system resources), we at least
have checked for all the subsets of depth 9. Clarification has
been added in the revised manuscript at Section 4.1, last
paragraph.}

\vspace{0.5cm}\textbf{\underline{6. Reviewer}:} Page 9: Please
provide equations using $\lambda$ and $\epsilon$ and relate them
to your model that uses $R_C$.

\vspace{0.2cm}\textbf{\underline{Answer 6}: Thanks for this
suggestion. We added in the revised version the following equation
Equation 8 (Section 4.3, paragraph 2) linking the Shapley value of
a web service $i$ when moving from one community $C$ to another
one $C'$ to $\epsilon$.
%
\begin{equation*}\label{eq:gainsh}
g_i(C \rightarrow C') = \phi_i(C',v) - \phi_i(C,v) - \epsilon
\end{equation*}
%
It relates our model that uses $R_C$ and $\epsilon$ as the Shapley
value is computed using $v(C)$, which in turn is computed using
$Out(C)$ based on $R_C$. The idea is that before deciding to
change the community (from $C$ to $C'$), each web service $i$ has
to be sure that the gain $g_i(C \rightarrow C')$ calculated based
on the Shapley values of $i$ in the previous and new communities
and the tax $\epsilon$ is positive, which means, what the web
service would gain in $C'$ is greater than what it gains in $C$
and the tax it would pay if moving all together. Furthermore, we
added in paragraph 3 of the same section (Section 4.3) the
following linear program that determines the minimum value of
$\lambda$ that makes the community stable ($Core$ condition):
%
 \begin{alignat*}{3}
    \min~   & \lambda  \\
    \text{s.t. } & \lambda v(C) > v(C') & ~& \text{ for all } C' \subset C
  \end{alignat*}
%
}

\vspace{0.5cm}\textbf{\underline{7. Reviewer}:} Page 10: For the
$\epsilon$ core method: the value of $\epsilon$ should be varied
to verify its impact in the experiments section.

\vspace{0.2cm}\textbf{\underline{Answer 7}: Yes, the value of
$\epsilon$ should vary to verify its impact and that is exactly
what we are doing in our experiments. In the revised manuscript,
we changed the explanation to make this fact more clear: Section
5, paragraph 5. See also Fig. 5}

\vspace{0.5cm}\textbf{\underline{8. Reviewer}:} The experiments
are missing a comparison with [18].

\vspace{0.2cm}\textbf{\underline{Answer 8}: The experiment
illustrated in Figure 9 (Last paragraph of Section 5) presents a
comparison of our work with [18]. We have called their method
``High Availability Coalition model''. We highlight this in the
new caption of this figure.}

\vspace{0.5cm}\textbf{\underline{9. Reviewer}:} Scalability
evaluation is missing: what is the impact of increasing the number
of services/communities on the system efficiency?.

\vspace{0.2cm}\textbf{\underline{Answer 9}: We conducted
scalability tests. We used 10,000 communities consisting of 3 to
160 web services. This number is large enough since in the
concrete examples of coalitions in the airlines domain we are
implementing, the largest coalition, Star
Alliance\footnote{\url{www.staralliance.com}}, has 28 airline
members. When conducting our experiments using the real web
service data provided in
\url{http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/}, in
average, the communities were populated by 60 web services. Thus,
in total, the number of used web services is 600,000. This makes
our system scalable enough. We also conducted experiments with a
large number of tasks from users up to 130 per iteration per
community, which means 6500 (130*50) tasks per community. We
observed that increasing the number of communities and web
services did not affect the overall efficiency of the system in
terms of coalition formation. In fact, as mentioned in the paper,
our algorithms run in $O(n)$ and $O(n^2)$ time as the number of
web services $(n)$ within a community grows. Thus, our algorithms
run in polynomial time. On the other hand, increasing the number
of tasks did not affect our results, since communities only accept
tasks at rate $R_C$. In the revised manuscript we highlighted the
runtime of our \emph{Depth-1 Convex-Checker} and \emph{Depth-2
Convex-Checker} methods in our experiments in Section 5, paragraph
4.}
%In case $R_C$ is set very large, communities can grow larger, and may suffer from  bottleneck due to huge number of task processing on a single server, a fact that is out of scope of this paper.

%%%%%%%%%%%%%%%%%%%%%%%%% REVIEWER 2 %%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2cm}

\newpage

\begin{center}
  \textbf{Reviewer 2}
\end{center}

\vspace{0.6cm} \textbf{\underline{Reviewer's appreciation}:} This
paper investigates into web services communities and the quality
of service in aggregating the web services in communities. The aim
is to maximize the efficiency through collaboration and through
forming coalitions of web services and improving the overall QoS
and revenue. The problem of web services community is interesting
as there exist a large number of web services with varying level
of QoS. The paper provides a good rationale behind the use and
establishment of communities of web services – esp. community web
services should be highly available and responsive; maintain
collaboration with others as well as maintain their own autonomy,
when used in business or any other settings.

The paper reviews the current work on web service communities and
QoS and identifies their strengths and weaknesses. It then
exploits the game theory approach and proposes a cooperative game
model for the aggregation of web services within communities. The
proposed model is well designed and developed. It’s also logically
mapped to the characteristics of web services they exhibit in
communities.

The proposed model is implemented as a prototype system and
various simulation experiments are conducted. The experimental
results show the benefits of the proposed model in terms of
stability, fairness, increase in revenue and in improvement of
user satisfaction.

Overall, the paper is well written and well structured.

\vspace{0.2cm}\textbf{\underline{Answer}: Thank you for the
positive feedback.}

\vspace{0.5cm}\textbf{\underline{1. Reviewer}:}  Though there's a
referral to [8] it'd be helpful to explain more the concept of
``Community coordinators'' web services, somewhere in the early
parts of the paper. How's it different from other (common) web
services in a given community?

``community master'' and ``community coordinator'' are these
different?

\vspace{0.2cm}\textbf{\underline{Answer 1}: First, there is no
difference between community master and community coordinator. To
avoid the confusion, we only use in the revised version the term
``community coordinator'' as community manager for our
architecture; ``community master'' has been kept only when it is
used as such in the literature. Second, we agree on your
suggestion and added the following explanation in Section 1,
paragraph 2: When communities are used, users send their requests
to the coordinators of those communities, which play the role of
their representatives or access points. Community coordinator is a
particular service that takes in charge the verification of
credentials of new web services before accepting them to join the
community, inviting good web services to join the community,
firing bad web services if they don't perform as expected, etc.
The coordinator is responsible for all the operations related to
the management of the community infrastructure in terms of
regulating the membership and insuring that the overall
performance is satisfactory. Unlike web services that are members
of the community, the coordinator does not offer services directly
to the users, it only forwards the requests to the suitable
members. The coordinator is created by the community owner when
the community is initiated.}

\vspace{0.5cm} \textbf{\underline{2. Reviewer}}: p.4 ``If he is
added to the set $S$,…'', ``his contribution…'' not sure `he' and
`his' are the right terminologies.

\vspace{0.2cm}\textbf{\underline{Answer 2}: We agree, we rephrased
the sentence as follows:  If the member $i$ is added to the set
$S$, the contribution of this set to the coalition is $v(S \cup
\left\{i\right\}) - v(S)$.}

\vspace{0.5cm} \textbf{\underline{3. Reviewer}}: p.10 ``our
community receives 130 tasks from users'' what are the types of
tasks. Are these simulated or real functions that need to
performed by web services?

\vspace{0.2cm}\textbf{\underline{Answer 3}: In the previous
version, the tasks were abstract. In the revised version, the
tasks are real tasks about flight booking that need to be
performed by web services. The users provide the flight dates, the
origin and destination, type of tickets, and number of guests. Web
services will find different flights with different companies,
prices, timing, etc. During our experiments, the tasks are
randomly generated and are coded as XML requests (String) and
responses are also coded in XML. Based on community task queue
delay and the assigned web service quality metrics (such as
reliability, throughput, latency and other metrics) these tasks
will be performed with different qualities. In the experimental
results and analysis section (Section 5), we have illustrated and
evaluated the average QoS of tasks performed. In the revised
manuscript, we added more explanations and details about the tasks
in Section 5. Other details are also mentioned in our Answer 5 to
Reviewer 3.}

\vspace{0.5cm} \textbf{\underline{4. Reviewer}}: p.9 “agents would
only earn a minimal amount of e by deviating….” …by deviating from
what?

\vspace{0.2cm}\textbf{\underline{Answer 4}: We mean deviating from
the coalition. This has been fixed in the revised version.}

%%%%%%%%%%%%%%%%%%%%%%%%% REVIEWER 3 %%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2cm}

\newpage

\begin{center}
  \textbf{Reviewer 3}
\end{center}

\vspace{0.6cm}\textbf{\underline{1. Reviewer}:}  It is not
convincing that the formation of service community can be modeled
as a cooperative gaming problem.

\vspace{0.2cm}\textbf{\underline{Answer 1}: As argued in our
Answer 2 to Reviewer 1, we are advocating the idea of community as
a way to group web services in order to increase the total gain of
all the members where each web service gain is more than or equal
to what this web service would obtain being outside the community.
This is because the community can provide wider visibility, better
market share, higher reputation, and better way of sharing
resources. Community for us is an infrastructure and being part of
it should benefit the web service, but also the community as a
whole. As argued in [Maamar et al., 2011]\footnote{Z. Maamar, P.
Thiran, and J. Bentahar (2011). Web services communities: from
intra-community Coopetition to inter-community Competition. In
E-Business Application for Product Development and Competitive
Growth: Emerging Technologies, In Lee editor, pp. 333-343, IGI
Global.}, inside a community, web services can either compete or
cooperate. In this paper, we stress the intra-community
cooperation between web services for a better inter-community
competition. The main idea is that to form a stable web service
community and to have fair distribution of the total gain based on
the contribution of each individual, cooperative game theory,
particularly coalition game theory, is very suitable to formalize
such a problem. Cooperation between competitors is a well
established practice in economical theories (see for instance
[Chetty and Wilson 2003]\footnote{S. K. Chetty and H. I. M. Wilson
(2003). Collaborating with competitors to acquire resources.
International Business Review, vol. 12. pp. 61-81.} and [Bucklin
and Sengupta 1993]\footnote{L. P. Bucklin and S. Sengupta (1993).
Organizing successful co-marketing alliances. Journal of
Marketing. vol. 57, pp. 32-46.}). This happens in real business
world scenarios. As an example, let us consider major carrier
airlines providing ticket selling services. Those airlines can be
seen as competing agents, each one tries to maximize its utility
by gaining more market share. However, nowadays those companies
are usually part of different coalitions (alliances) such as Star
Alliance\footnote{\url{www.staralliance.com}} (28 airline members
including Scandinavian Airlines, Thai Airways International, Air
Canada, Lufthansa, and United Airlines),
SkyTeam\footnote{\url{www.skyteam.com}} (19 members, among them
Aerom\'{e}xico, Air France, Delta Air Lines, Continental Airlines,
KLM, and Northwest Airlines), and Oneworld\footnote{\url{
www.oneworld.com}} (13 members including Air Berlin, American
Airlines, British Airways, Cathay Pacific, Iberia, Japan Airlines,
Malaysia Airlines, and Qatar Airways). By sharing resources and
market share and having the option of service multi-hop air
tickets combined from different airlines, each airline member of a
coalition can increase its gain by collaborating. The question is
when this collaboration would be beneficial for all the agents
involved? For example the three alliances would not gain anything
by collaborating and sharing resources with airlines of low
reputation and quality. They will lose their market and would
rather stay away from this collaboration. Therefore, no stable
community can be formed between well established and poor
airlines. Another example of cooperation among competitors is the
arrangement between PSA Peugeot Citro\"{e}n and Toyota to create
Toyota Peugeot Citro\"{e}n Automobile
(TPCA)\footnote{\url{www.tpca.cz/en/}} in order to share
components for a new city car where the different companies save
money on shared costs while remaining competitive in other areas.
Our solution of cooperation between competitor web services within
coalitions follows these models. We updated the paper to reflect
this important discussion by adding a new part, called
motivations, to the introduction (Section 1).}

\vspace{0.5cm}\textbf{\underline{2. Reviewer}:}  First, the
concept of service community used in this paper is different from
the ones used in the existing work, such as in the referred
papers. The general idea of service community is a homogeneous
service group that conceptually include services providing similar
functionality. Services in the same community are independent and
autonomous. There is no central control mechanism for the
community. On the other hand, the concept of service community of
this paper is a group of services which are monitored and managed
by a community manager. It is not clear how realistic or practical
such a community is and what the real world examples are.

\vspace{0.2cm}\textbf{\underline{Answer 2}: Most of the existing
work have clearly stated that communities of web services need a
centralized manager for the purposes of developing, coordinating
and managing the community infrastructure and in some of the
works, being the access point of the community and having the role
of delegating tasks:
%
\begin{itemize}
%
\item {[Liu et al. 2012][28]} (published in the same journal IEEE
Transactions on Services Computing, 2012): The authors used a very
similar architecture to the one we are using in our paper. Each
web service community has a \emph{coordinator} which is
responsible for receiving and satisfying customers' requests and
``\underline{managing the cooperation among the members}''. The
coordinator plays then the role of the community manager.
%
\item {[Lim et al. 2012][26]}: The paper uses exactly the
architecture we are using here. Each community is managed by a
\emph{Master Web Service}.
%
\item {[Benatallah et al. 2003][9]}: The paper introduces the
concept of \emph{service container}, which plays the role of
community and its manager at the same time.  A container is a
service that aggregates several functionally similar services.
Containers exist independently of the services they aggregate. The
service container is the one to invoke instead of an elementary or
composite service aggregated by that container.
%
\item {[Maamar et al. 2008][14], [Maamar et al. 2009][8]}: Here
again the architecture proposed in these papers is the one we are
using in our work.
%
\item {[Zeng et al. 2003][11]}: The paper describes a global
planning selection algorithm and a delegation algorithm to be run
when a request to execute an operation is received by the
community. This needs a central entity to run those algorithms.
Such entity plays the role of the community coordinator or
manager.
%
\item {[Medjahed and Bouguettaya 2005][13]}: The paper describes
the concept of \emph{community agents} associated to
\emph{community providers}. A community agent is responsible,
among other things, of the registration of services with the
community. The paper uses the example of a community that provides
health care services to senior citizens. In this example, a
governmental entity is needed to check the health care standards
used by the members before authorizing them to be part of the
community. Such a central entity is represented by the community
agent. Thus, community agents are playing the role of community
managers.
%
\item {[Limam and Akaichi 2010]}\footnote{H. Limam and J. Akaich.
Managing web services communities: A cache for queries
optimisation, International Journal on Web Service Computing,
Vol.1, No.1, pp 2230-7702, 2010}: The paper describes explicitly
the concept of \emph{centralized access} in the community
definition.
%
\end{itemize}
%
It is worth mentioning that in our work, service community is also
a homogeneous service group that hosts services providing similar
functionalities. Moreover, services in the same community are also
independent and autonomous in our work. They are self-interest and
utility maximizer agents, and behave autonomously towards
maximizing their own profits using our game theory approach. They
have the freedom to leave the community anytime if they are not
satisfied about the profit they are making. Having a community
manager, only means that the management of the community
infrastructure in terms of accepting new web services and
verifying the credentials of the members is centralized. In other
words, the coordinator does not manage web services, but does
manage the community. The manager does not dictate what the web
services should do and how they should behave. In fact, all the
existing proposals agree that because the community is an
infrastructure that hosts different web services, membership
cannot be leaved open so that any web service can join even those
having poor quality and bad reputation. A community is a system
that should accept only particular web services, and there should
be a mechanism to control the credentials of the members.}

\textbf{Going back to the real world example of airlines
alliances:
%
\begin{itemize}
%
\item Star Alliance is managed by a centralized company \emph{Star
Alliance Services GmbH}, which was created on behalf of its
members and led by the current CEO, Mark Schwab. Star Alliance
Services GmbH is responsible of coordinating the development and
strategies of the airline alliance from its base in Frankfurt am
Main,
Germany\footnote{\url{www.staralliance.com/en/about/organisation/}}.
%
\item SkyTeam has centralized core management team, \emph{SkyTeam
Central}, based at the World Trade Center Schiphol Airport and led
by the current Chairman of the SkyTeam Governing Board, Leo van
Wijk. The core management team ``is responsible for overseeing
day-to-day operations of the alliance, including: marketing,
sales, airport synergies and transfer product, cargo, advertising
and brand, alliance operations, finance, corporate communications
and alliance
administration''\footnote{\url{http://www.skyteam.com/en/About-us/Organization/Management/}}.
%
\item Oneworld is managed by its central alliance office, the
\emph{Oneworld Management Company} (\emph{oMC}) based in New York
City and led by Tom Horton (Chairman) and Bruce Ashby (CEO). The
oMC acts as the alliance's central secretariat, with
responsibility for driving future growth and the launch of new
customer services and
benefits\footnote{\url{www.oneworld.com/news-information/oneworld-fact-sheets}}.
%
\end{itemize}
%
In all these alliances, accepting a new member or pending a member
is decided centrally. Regarding the second example, TPCA coalition
is also managed by a central management company based in the
industrial zone of Kolin - Ov\v{c}\'{a}ry, Czech republic and led
by Kenta Koide,
president\footnote{\url{www.tpca.cz/en/about-us/management-tpca-en-us/}}.}
%

\textbf{In the revised manuscript, we reported these discussions
in the motivation part of the introduction (Section 1) and in the
related work section (Section 2).}

\vspace{0.5cm}\textbf{\underline{3. Reviewer}:}  The problem is
modeled in a way so that the cooperative game theory can be
applied, but not in a way that is consistent with the real world
scenarios.

\vspace{0.2cm}\textbf{\underline{Answer 3}: Answers 1 and 2 are
answers for this comment as well.}

\vspace{0.5cm}\textbf{\underline{4. Reviewer}:}  The service
parameters, such as its request rate and  throughput rate are not
in line with the general characteristics of web services, such as
input and output parameters. It is not clear how the proposed
service parameters are obtained and why they are important to
determine a service's membership to a community, considering that
they depend on not only the service's capacity, but also the
amount and frequency of user requests, which can be random.

\vspace{0.2cm}\textbf{\underline{Answer 4}: First, we have to
mention that we are focusing on \underline{quality metrics}, which
are non-functional. Our proposal is general and independent from
the functional input-output parameters. The parameters we are
using are the typical parameters of web services,  which are
obtained from a real world data set provided at:
\url{http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/}. The
request rate was inspired by market share and reputation models of
communities of web services, which have been used in other
proposals such as [17],[23]. Those parameters are important as
community coordinators tend to accept only good web services which
provide good QoS and have the potential to increase the utility of
the community. It has been showed in [23] that the request rate is
positively correlated with the trust and performance of web
services, which means it is not random when the service is running
for a large enough period of time. In fact, having a
\emph{casi-static} request rate for communities is not
unrealistic. To support our claim, we provide data from a real
world example. The CEO of \url{concertboom.com}, Kooshiar Azimian,
has provided us with their access and request rates of the web
services they use\ref{cblog}. Their service provides ticketing
information for events happening close to user's location. They
use Ticketnetwork.com web services\footnote{Affiliate program
link: http://www.ticketnetwork.com/affiliates/agreement.aspx}
\footnote{Web Service API documentation:
\url{www.getacoder.com/data/projects/77613/TicketNetwork\%20Web\%20Services\%20(W2)-.doc}},
and have implemented their back-end code in Java. As shown in
Figure \ref{fig1}, they currently have an average of 340,000 daily
page views or almost 3.95 requests per second. They invoke the
\url{ticketnetwork} web service almost 4 times per second to get
the seating chart and tickets available for the events. During a
day, the pick time happens at around 20:00 UTC time, which has
almost 10\% more requests than during the lower pick time, which
happens around 7:00 AM UTC time. As shown in the figure, the
pattern of request rate is casi-stable during the period between
May and September.
%Therefore, \url{ticketnetwork} knows that
%\url{concertboom.com} has a request rate of 340,000 requests per
%day or almost 3.95 requests per second and can adjust the internal
%service providers and resources so they can  provide these rate of
%services.
}

\textbf{Because the data of \url{concertboom.com} are private, we
were asked not to disclose them publicly. We only get from the
company the consensus to use them for the response letter. This is
the reason why we could not add them to the paper.}

\begin{figure}
\begin{center}
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[width=10cm]{cb.eps}\label{cblog}
\caption{Number of ticket pageviews of concertboom.com during May 5th, until Sep 9th, 2013}
\label{fig1}
\end{center}
\end{figure}

\vspace{0.5cm}\textbf{\underline{5. Reviewer}:}  The paper
conducted a simulation instead of an experimental study using real
world web services. This also suggests the difficulties of finding
real world examples and application for the proposed idea.

\vspace{0.2cm}\textbf{\underline{Answer 5}:
%Our focus is on non-functional properties of web services and is extendable to any type of web service communities providing any type of service, which there is high demand, request load and competition for that service type such as mapping, weather, ticketing, and local places information.
As mentioned previously, for our experiments, we have implemented
our web services using real data extracted from a data set of web
services
(\url{http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/}).
This makes our web services behave like real ones. In the previous
version, web services were implemented as abstract enteties as the
main purpose was to focus on the quality metrics. In the revised
version, we use flight booking services and airlines coalitions as
concrete application domain. An XML SOAP based messaging system is
also implemented. The request contains the flight dates, the
origin and destination, type of tickets, and number of guests. The
response contains different flights with different companies,
prices, timing, etc. We have gathered around 200,000 flights and
stored them in our MongoDB database. As expected, this did not
affect our experimental results, since our concern, as most of the
related work, is on non-functional properties of web services. We
could deploy web services using JAX-WS in Java and deploy on
different servers. However, those web services would not reflect
the quality of service parameters of real web services under load
in real world. For example, we cannot evaluate the exact
bottlenecks different type of services may have, some qualities
may drop because of heavy load of DB queries, some because of
network congestions and delays while trying to generate the
results for end users. Therefore, the real world data can provide
us with QoS values of real functioning web services online. We
have carefully examined many published proposals in services
computing including work on web service community and composition
such as [Yu 2013]\footnote{Q. Yu and A. Bouguettaya, Efficient
Service Skyline Computation for Composite Service Selection, IEEE
Transactions on Knowledge and Data Engineering (TKDE), vo. 25, no.
4, pp. 776-789, 2013}, [Limam 2010]\footnote{H. Limam and J.
Akaich. Managing web services communities: A cache for queries
optimisation, International Journal on Web Service Computing,
Vol.1, No.1, pp 2230-7702, 2010}, [Liu 2012]\footnote{A. Liu, Q.
Li, L. Huang, S. Ying, and M. Xiao,Coalitional game for
community-based autonomous web services cooperation, IEEE
Transactions on Services Computing, vol. 99, no. PrePrints, 2012.}
and many others; we found that they evaluated their results using
a similar methodology. For the real world applications part of the
comment, see the previous answers.}

\vspace{0.5cm}

\vspace{1cm}

{
%\bibliographystyle{plain}
%\bibliography{omar}
}
\end{document}

### 2014-01-31 papers/Exp Sys App/coop_response_letter.tex
added coop paper

--- 2014-01-20 papers/coalition-journal-R1/response_letter-final.tex
@@
 \newtheorem{corollary} {Corollary}
-\title{\underline{Response Letter}\\\vspace{0.5cm}Efficient Community Formation for Web Services}
+\title{\underline{Response Letter}\\\vspace{0.5cm}To Compete or Cooperate? This is the Question in Communities of Autonomous Services}
 \author{Ehsan Khosrowshahi Asl\\
@@
 \and
+Rabeb Mizouni\\
+rabeb.mizouni@kustar.ac.ae \\
+\and
+Babak Khosravifar\\
+babak.khosravifar@mcgill.ca \\
+\and
 Hadi Otrok\\
 hadi.otrok@kustar.ac.ae \\
-\and
-Rabeb Mizouni\\
-rabeb.mizouni@kustar.ac.ae \\
 }
@@
 reviewers and editors, which will make the paper accepted for
-publication in IEEE Transactions on Services Computing (TSC).\\
+publication in Expert Systems With Applications Journal.\\
 
@@
 
-\vspace{0.6cm} \textbf{\underline{Reviewer's appreciation}:} The
-paper presents a nice modelling of community formation based on
-coalition games. The authors defended well their approach and
-provided good illustrative examples.
+\textbf{\underline{Reviewer}:} The presented paper is very good and up to date in the state of the art.
+The paper addresses a framework in which the agents use decision mechanisms in order to compete or cooperate.
 
-\vspace{0.2cm}\textbf{\underline{Answer}: Thank you for the
-positive feedback.}
-
-\vspace{0.5cm} \textbf{\underline{1. Reviewer}:} Page 4: Last
-paragraph: should be $x_i$ instead of $i$ at the condition level.
+\vspace{0.5cm} \textbf{\underline{1.
+Reviewer}:} The abstract should be shorter and it lacks information on the proposed framework and the decision mechanism based on game theory which are not mentioned.
+The suggested modifications aim make the abstract and the conclusion more similar.
 
 \vspace{0.2cm}\textbf{\underline{Answer 1}: Thanks for the
-comment. Actually, the confusion comes from Equation 2, which
-should be $\forall S \subseteq N, \sum_{i \in S} x_i \geq v(S)$
-instead of $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S)$
-as $x_i$ is the payoff vector of the player $i$ and $S$ is the set
-of all players. This has been fixed in Equation 2 and Equation 4
-as well (Section 2.4).}
+comment. We made the abstract shorter and added the information about our decision making process which based on game-theoretic best response technique in the abstract.}
 
-\vspace{0.5cm}\textbf{\underline{2. Reviewer}:}  Page 6: You
-should relate $v(S)$ to $PO(C)$ in equations 5 and 6.
+\vspace{0.5cm}\textbf{\underline{2.
+Reviewer}:}  In section 2.2 (system parameters), the authors should specify how many parameters are used before explaining them and using such parameters in the proposed mathematics.
+This should aid the reader in better understanding.
 
-\vspace{0.2cm}\textbf{\underline{Answer 2}: The connection between
-$v(S)$ and $PO(C)$ has been mentioned in Section 3.3, second
-paragraph and when we described the algorithm of our scenario in
-Section 4.1. To be more specific, the connection is between $v(C)$
-and $Out(C)$ that is computed in Equation 6 based on $PO(C)$
-computed in Equation 5. The connection is that the worth of a
-community is set to the output the community can generate, i.e.,
-$v(C) = Out(C)$. However, we agree that this should be reported
-earlier. In the revised version it is clearly stated just after
-Equation 6 (Section 3.2). }
-% RABEB: I do not get what you mean by however we had ....
-I beleive taht you need to reformulate your answer by saying that : The connection between V(S) to PO(C) has been already defined when describing the algorithm of our scenario in section 4.1.
-To clarify it more, we modified the section and we added the connection at the end of the paragraph.
+\vspace{0.2cm}\textbf{\underline{Answer 2}: We added a short summary about the system parameters in section 2.2.
+We have five system parameters and the other variables are derived or calculated based on these five parameters which are listed in Table 1.
+The title for Table 1.
+which was ``List of proposed system parameters'' was not very appropriate and we apologize for the confusion that it has caused.
+We changed its title to ``List of abbreviations''}
 
-\vspace{0.5cm}\textbf{\underline{3. Reviewer}:} Page 7: Please add
-some definitions such as the one for Grand coalition to make the
-paper self-contained.
+\vspace{0.5cm}\textbf{\underline{3. Reviewer}:} The text consists on very long paragraphs, mainly section 4 (experimental results), which makes the reading difficult.
 
@@
 
-\vspace{0.5cm}\textbf{\underline{4. Reviewer}:} Why you didn't
-leverage the foundations of repeated games instead of coalitional
-games? Is there any strong reason?.
+\vspace{0.5cm}\textbf{\underline{4.
+Reviewer}:} Still in section 4, the simulation application should be better specified, adding information on used machine, architecture, most important used services, etc.
 
@@
 whole and to ensure the creation of stable communities in terms of
-joining and leaving activities. Such a problem is formulated by
-the means of coalition games, a part of cooperative game theory
-where the gain can be fairly distributed based on the contribution
-of each member using the theory of \emph{shapley value}. In this
-context, communities can be formed and have their stability
-condition formulated based on the \emph{Core} solution concepts.
-Repeated games fit better in situations where web services are
-competing with each other so they can learn the best response by
-playing the game repeatedly. In our case, web services are rather
-cooperating where the objective of web services communities is to
-motivate intra-community cooperation and to motivate quality web
-services to join such communities. Because each community is seen
-as a cooperative group where members cooperate to achieve a better
-outcome, cooperative game theory methods provide us with great
-decision mechanisms for forming groups and coalitions which would
-benefit the agents involved altogether.}
+joining and leaving activities.}
 
-\textbf{In fact, because members of the same community are
-providing similar functionalities, one can argue that they are
-competing with each other, rather than cooperating. However, the
-main idea, and also the main innovation and contribution of the
-paper is to show that those member web services can form strong
-and stable communities as coalitions so that they can better
-compete as a whole with other web services and other communities,
-which will allow them to be better off. In other words, we are
-promoting the idea of intra-community cooperation and
-inter-community competition. This justifies the use of coalition
-games instead of repeated games.}
-
-\textbf{Because we found it important as motivation of our choice
-of coalition games, this discussion is reflected in the revised
-version in the introduction section (Section 1, Motivations part).
-In this new part, we added examples from the business world to
-highlight the cooperation strategy. This has been raised by
-Reviewer 3 as well (see additional details in our Answer 1 to
-Reviewer 3).}
-
-%In repeated games, there should be a repeatable game between agents one to one.
-The  decision cannot be optimal for all the agents involved.
-We believe repeated game is more appropriate in cases where there is a lot of competing one-to-one interactions between agents  happening and not in coalitions.
- %and actually we are working on repeated games and specifically repeated game with learning techniques such as q-learning to help distribute the ``task distribution job'' among all the web services where web services are having different confidence states, and based on their action history and state they are in, web services can directly opt for getting and performing tasks alone or cooperating which other agents.
-% RABEB: I do not see the need for the last sentence starting from and actually we are as you are opening the door for questioning our decision  ...
-
-\vspace{0.5cm}\textbf{\underline{5. Reviewer}:} Page 8: What do
-you mean by "the algorithm gets interrupted": is it based on a
-logical condition? if yes, what is it?
+\vspace{0.5cm}\textbf{\underline{5. Reviewer}:} Figure 3 is misplaced.
 
@@
 
-\vspace{0.5cm}\textbf{\underline{6. Reviewer}:} Page 9: Please
-provide equations using $\lambda$ and $\epsilon$ and relate them
-to your model that uses $R_C$.
+\vspace{0.5cm}\textbf{\underline{6. Reviewer}:} 6) There are some minor format errors that should be addressed.
 
-\vspace{0.2cm}\textbf{\underline{Answer 6}: Thanks for this
-suggestion. We added in the revised version the following equation
-Equation 8 (Section 4.3, paragraph 2) linking the Shapley value of
-a web service $i$ when moving from one community $C$ to another
-one $C'$ to $\epsilon$.
-%
-\begin{equation*}\label{eq:gainsh}
-g_i(C \rightarrow C') = \phi_i(C',v) - \phi_i(C,v) - \epsilon
-\end{equation*}
-%
-It relates our model that uses $R_C$ and $\epsilon$ as the Shapley
-value is computed using $v(C)$, which in turn is computed using
-$Out(C)$ based on $R_C$. The idea is that before deciding to
-change the community (from $C$ to $C'$), each web service $i$ has
-to be sure that the gain $g_i(C \rightarrow C')$ calculated based
-on the Shapley values of $i$ in the previous and new communities
-and the tax $\epsilon$ is positive, which means, what the web
-service would gain in $C'$ is greater than what it gains in $C$
-and the tax it would pay if moving all together. Furthermore, we
-added in paragraph 3 of the same section (Section 4.3) the
-following linear program that determines the minimum value of
-$\lambda$ that makes the community stable ($Core$ condition):
-%
- \begin{alignat*}{3}
-    \min~   & \lambda  \\
-    \text{s.t. } & \lambda v(C) > v(C') & ~& \text{ for all } C' \subset C
-  \end{alignat*}
-%
+\vspace{0.2cm}\textbf{\underline{Answer 6}: Tha
 }
 
-\vspace{0.5cm}\textbf{\underline{7. Reviewer}:} Page 10: For the
-$\epsilon$ core method: the value of $\epsilon$ should be varied
-to verify its impact in the experiments section.
-
-\vspace{0.2cm}\textbf{\underline{Answer 7}: Yes, the value of
-$\epsilon$ should vary to verify its impact and that is exactly
-what we are doing in our experiments. In the revised manuscript,
-we changed the explanation to make this fact more clear: Section
-5, paragraph 5. See also Fig. 5}
-
-\vspace{0.5cm}\textbf{\underline{8. Reviewer}:} The experiments
-are missing a comparison with [18].
-
-\vspace{0.2cm}\textbf{\underline{Answer 8}: The experiment
-illustrated in Figure 9 (Last paragraph of Section 5) presents a
-comparison of our work with [18]. We have called their method
-``High Availability Coalition model''. We highlight this in the
-new caption of this figure.}
-
-\vspace{0.5cm}\textbf{\underline{9. Reviewer}:} Scalability
-evaluation is missing: what is the impact of increasing the number
-of services/communities on the system efficiency?.
-
-\vspace{0.2cm}\textbf{\underline{Answer 9}: We conducted
-scalability tests. We used 10,000 communities consisting of 3 to
-160 web services. This number is large enough since in the
-concrete examples of coalitions in the airlines domain we are
-implementing, the largest coalition, Star
-Alliance\footnote{\url{www.staralliance.com}}, has 28 airline
-members. When conducting our experiments using the real web
-service data provided in
-\url{http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/}, in
-average, the communities were populated by 60 web services. Thus,
-in total, the number of used web services is 600,000. This makes
-our system scalable enough. We also conducted experiments with a
-large number of tasks from users up to 130 per iteration per
-community, which means 6500 (130*50) tasks per community. We
-observed that increasing the number of communities and web
-services did not affect the overall efficiency of the system in
-terms of coalition formation. In fact, as mentioned in the paper,
-our algorithms run in $O(n)$ and $O(n^2)$ time as the number of
-web services $(n)$ within a community grows. Thus, our algorithms
-run in polynomial time. On the other hand, increasing the number
-of tasks did not affect our results, since communities only accept
-tasks at rate $R_C$. In the revised manuscript we highlighted the
-runtime of our \emph{Depth-1 Convex-Checker} and \emph{Depth-2
-Convex-Checker} methods in our experiments in Section 5, paragraph
-4.}
-%In case $R_C$ is set very large, communities can grow larger, and may suffer from  bottleneck due to huge number of task processing on a single server, a fact that is out of scope of this paper.
+%\vspace{0.2cm}\textbf{\underline{Answer 9}: We 
+%\url{http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/}, in}
 
@@
 
-\vspace{0.6cm} \textbf{\underline{Reviewer's appreciation}:} This
-paper investigates into web services communities and the quality
-of service in aggregating the web services in communities. The aim
-is to maximize the efficiency through collaboration and through
-forming coalitions of web services and improving the overall QoS
-and revenue. The problem of web services community is interesting
-as there exist a large number of web services with varying level
-of QoS. The paper provides a good rationale behind the use and
-establishment of communities of web services – esp. community web
-services should be highly available and responsive; maintain
-collaboration with others as well as maintain their own autonomy,
-when used in business or any other settings.
+\textbf{\underline{Reviewer}:} The paper perfectly fits within the scope of Expert Systems.
+This manuscript investigates the development of communities of autonomous services, formalizing the question "To compete or to cooperate?" between them.
+The authors do so by theorising and conducting a study through a dataset of 2,507 real services functioning on the web.
 
-The paper reviews the current work on web service communities and
-QoS and identifies their strengths and weaknesses. It then
-exploits the game theory approach and proposes a cooperative game
-model for the aggregation of web services within communities. The
-proposed model is well designed and developed. It’s also logically
-mapped to the characteristics of web services they exhibit in
-communities.
+\vspace{0.5cm}\textbf{\underline{1. Reviewer}:}  Abstract: In my opinion, it is not necessary to talk about the sample used.
 
-The proposed model is implemented as a prototype system and
-various simulation experiments are conducted. The experimental
-results show the benefits of the proposed model in terms of
-stability, fairness, increase in revenue and in improvement of
-user satisfaction.
+\vspace{0.2cm}\textbf{\underline{Answer 1}: First}
 
-Overall, the paper is well written and well structured.
-
-\vspace{0.2cm}\textbf{\underline{Answer}: Thank you for the
-positive feedback.}
-
-\vspace{0.5cm}\textbf{\underline{1. Reviewer}:}  Though there's a
-referral to [8] it'd be helpful to explain more the concept of
-``Community coordinators'' web services, somewhere in the early
-parts of the paper. How's it different from other (common) web
-services in a given community?
-
-``community master'' and ``community coordinator'' are these
-different?
-
-\vspace{0.2cm}\textbf{\underline{Answer 1}: First, there is no
-difference between community master and community coordinator. To
-avoid the confusion, we only use in the revised version the term
-``community coordinator'' as community manager for our
-architecture; ``community master'' has been kept only when it is
-used as such in the literature. Second, we agree on your
-suggestion and added the following explanation in Section 1,
-paragraph 2: When communities are used, users send their requests
-to the coordinators of those communities, which play the role of
-their representatives or access points. Community coordinator is a
-particular service that takes in charge the verification of
-credentials of new web services before accepting them to join the
-community, inviting good web services to join the community,
-firing bad web services if they don't perform as expected, etc.
-The coordinator is responsible for all the operations related to
-the management of the community infrastructure in terms of
-regulating the membership and insuring that the overall
-performance is satisfactory. Unlike web services that are members
-of the community, the coordinator does not offer services directly
-to the users, it only forwards the requests to the suitable
-members. The coordinator is created by the community owner when
-the community is initiated.}
-
-\vspace{0.5cm} \textbf{\underline{2. Reviewer}}: p.4 ``If he is
-added to the set $S$,…'', ``his contribution…'' not sure `he' and
-`his' are the right terminologies.
+\vspace{0.5cm} \textbf{\underline{2.
+Reviewer}}:  Introduction: The first phrase ``Services are software systems...'' should include which kind of services are being analysed: intelligent, autonomous,...
+The definition used does not correspond to ``Services'' as a whole.
 
@@
 \left\{i\right\}) - v(S)$.}
-
-\vspace{0.5cm} \textbf{\underline{3. Reviewer}}: p.10 ``our
-community receives 130 tasks from users'' what are the types of
-tasks. Are these simulated or real functions that need to
-performed by web services?
+\vspace{0.5cm} \textbf{\underline{3.
+Reviewer}}: Related work: The authors state in page 21: ``The interesting idea is to consider the benefits under four categories: innovation and learning,...''.
+If this is an interesting idea, it should be further explained.
+I agree with the authors, these benefits are very interesting, please provide further details.
 
@@
 version, the tasks were abstract. In the revised version, the
-tasks are real tasks about flight booking that need to be
-performed by web services. The users provide the flight dates, the
-origin and destination, type of tickets, and number of guests. Web
-services will find different flights with different companies,
-prices, timing, etc. During our experiments, the tasks are
-randomly generated and are coded as XML requests (String) and
-responses are also coded in XML. Based on community task queue
-delay and the assigned web service quality metrics (such as
-reliability, throughput, latency and other metrics) these tasks
-will be performed with different qualities. In the experimental
-results and analysis section (Section 5), we have illustrated and
-evaluated the average QoS of tasks performed. In the revised
-manuscript, we added more explanations and details about the tasks
-in Section 5. Other details are also mentioned in our Answer 5 to
-Reviewer 3.}
+tasks are real tasks about flight booking that need to be.}
 
-\vspace{0.5cm} \textbf{\underline{4. Reviewer}}: p.9 “agents would
-only earn a minimal amount of e by deviating….” …by deviating from
-what?
+\vspace{0.5cm} \textbf{\underline{4.
+Reviewer}}:  Conclusion: The paper identifies clearly the implications for practice and further research.
+I consider the service consumer role very interesting for future research.
 
@@
 the coalition. This has been fixed in the revised version.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%% REVIEWER 3 %%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{2cm}
-
-\newpage
-
-\begin{center}
-  \textbf{Reviewer 3}
-\end{center}
-
-\vspace{0.6cm}\textbf{\underline{1. Reviewer}:}  It is not
-convincing that the formation of service community can be modeled
-as a cooperative gaming problem.
 
@@
 
-\vspace{0.5cm}\textbf{\underline{2. Reviewer}:}  First, the
-concept of service community used in this paper is different from
-the ones used in the existing work, such as in the referred
-papers. The general idea of service community is a homogeneous
-service group that conceptually include services providing similar
-functionality. Services in the same community are independent and
-autonomous. There is no central control mechanism for the
-community. On the other hand, the concept of service community of
-this paper is a group of services which are monitored and managed
-by a community manager. It is not clear how realistic or practical
-such a community is and what the real world examples are.
-
-\vspace{0.2cm}\textbf{\underline{Answer 2}: Most of the existing
-work have clearly stated that communities of web services need a
-centralized manager for the purposes of developing, coordinating
-and managing the community infrastructure and in some of the
-works, being the access point of the community and having the role
-of delegating tasks:
-%
-\begin{itemize}
-%
-\item {[Liu et al. 2012][28]} (published in the same journal IEEE
-Transactions on Services Computing, 2012): The authors used a very
-similar architecture to the one we are using in our paper. Each
-web service community has a \emph{coordinator} which is
-responsible for receiving and satisfying customers' requests and
-``\underline{managing the cooperation among the members}''. The
-coordinator plays then the role of the community manager.
-%
-\item {[Lim et al. 2012][26]}: The paper uses exactly the
-architecture we are using here. Each community is managed by a
-\emph{Master Web Service}.
-%
-\item {[Benatallah et al. 2003][9]}: The paper introduces the
-concept of \emph{service container}, which plays the role of
-community and its manager at the same time.  A container is a
-service that aggregates several functionally similar services.
-Containers exist independently of the services they aggregate. The
-service container is the one to invoke instead of an elementary or
-composite service aggregated by that container.
-%
-\item {[Maamar et al. 2008][14], [Maamar et al. 2009][8]}: Here
-again the architecture proposed in these papers is the one we are
-using in our work.
-%
-\item {[Zeng et al. 2003][11]}: The paper describes a global
-planning selection algorithm and a delegation algorithm to be run
-when a request to execute an operation is received by the
-community. This needs a central entity to run those algorithms.
-Such entity plays the role of the community coordinator or
-manager.
-%
-\item {[Medjahed and Bouguettaya 2005][13]}: The paper describes
-the concept of \emph{community agents} associated to
-\emph{community providers}. A community agent is responsible,
-among other things, of the registration of services with the
-community. The paper uses the example of a community that provides
-health care services to senior citizens. In this example, a
-governmental entity is needed to check the health care standards
-used by the members before authorizing them to be part of the
-community. Such a central entity is represented by the community
-agent. Thus, community agents are playing the role of community
-managers.
-%
-\item {[Limam and Akaichi 2010]}\footnote{H. Limam and J. Akaich.
-Managing web services communities: A cache for queries
-optimisation, International Journal on Web Service Computing,
-Vol.1, No.1, pp 2230-7702, 2010}: The paper describes explicitly
-the concept of \emph{centralized access} in the community
-definition.
-%
-\end{itemize}
-%
-It is worth mentioning that in our work, service community is also
-a homogeneous service group that hosts services providing similar
-functionalities. Moreover, services in the same community are also
-independent and autonomous in our work. They are self-interest and
-utility maximizer agents, and behave autonomously towards
-maximizing their own profits using our game theory approach. They
-have the freedom to leave the community anytime if they are not
-satisfied about the profit they are making. Having a community
-manager, only means that the management of the community
-infrastructure in terms of accepting new web services and
-verifying the credentials of the members is centralized. In other
-words, the coordinator does not manage web services, but does
-manage the community. The manager does not dictate what the web
-services should do and how they should behave. In fact, all the
-existing proposals agree that because the community is an
-infrastructure that hosts different web services, membership
-cannot be leaved open so that any web service can join even those
-having poor quality and bad reputation. A community is a system
-that should accept only particular web services, and there should
-be a mechanism to control the credentials of the members.}
-
-\textbf{Going back to the real world example of airlines
-alliances:
-%
-\begin{itemize}
-%
-\item Star Alliance is managed by a centralized company \emph{Star
-Alliance Services GmbH}, which was created on behalf of its
-members and led by the current CEO, Mark Schwab. Star Alliance
-Services GmbH is responsible of coordinating the development and
-strategies of the airline alliance from its base in Frankfurt am
-Main,
-Germany\footnote{\url{www.staralliance.com/en/about/organisation/}}.
-%
-\item SkyTeam has centralized core management team, \emph{SkyTeam
-Central}, based at the World Trade Center Schiphol Airport and led
-by the current Chairman of the SkyTeam Governing Board, Leo van
-Wijk. The core management team ``is responsible for overseeing
-day-to-day operations of the alliance, including: marketing,
-sales, airport synergies and transfer product, cargo, advertising
-and brand, alliance operations, finance, corporate communications
-and alliance
-administration''\footnote{\url{http://www.skyteam.com/en/About-us/Organization/Management/}}.
-%
-\item Oneworld is managed by its central alliance office, the
-\emph{Oneworld Management Company} (\emph{oMC}) based in New York
-City and led by Tom Horton (Chairman) and Bruce Ashby (CEO). The
-oMC acts as the alliance's central secretariat, with
-responsibility for driving future growth and the launch of new
-customer services and
-benefits\footnote{\url{www.oneworld.com/news-information/oneworld-fact-sheets}}.
-%
-\end{itemize}
-%
-In all these alliances, accepting a new member or pending a member
-is decided centrally. Regarding the second example, TPCA coalition
-is also managed by a central management company based in the
-industrial zone of Kolin - Ov\v{c}\'{a}ry, Czech republic and led
-by Kenta Koide,
-president\footnote{\url{www.tpca.cz/en/about-us/management-tpca-en-us/}}.}
-%
-
-\textbf{In the revised manuscript, we reported these discussions
-in the motivation part of the introduction (Section 1) and in the
-related work section (Section 2).}
-
-\vspace{0.5cm}\textbf{\underline{3. Reviewer}:}  The problem is
-modeled in a way so that the cooperative game theory can be
-applied, but not in a way that is consistent with the real world
-scenarios.
-
-\vspace{0.2cm}\textbf{\underline{Answer 3}: Answers 1 and 2 are
-answers for this comment as well.}
-
-\vspace{0.5cm}\textbf{\underline{4. Reviewer}:}  The service
-parameters, such as its request rate and  throughput rate are not
-in line with the general characteristics of web services, such as
-input and output parameters. It is not clear how the proposed
-service parameters are obtained and why they are important to
-determine a service's membership to a community, considering that
-they depend on not only the service's capacity, but also the
-amount and frequency of user requests, which can be random.
-
-\vspace{0.2cm}\textbf{\underline{Answer 4}: First, we have to
-mention that we are focusing on \underline{quality metrics}, which
-are non-functional. Our proposal is general and independent from
-the functional input-output parameters. The parameters we are
-using are the typical parameters of web services,  which are
-obtained from a real world data set provided at:
-\url{http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/}. The
-request rate was inspired by market share and reputation models of
-communities of web services, which have been used in other
-proposals such as [17],[23]. Those parameters are important as
-community coordinators tend to accept only good web services which
-provide good QoS and have the potential to increase the utility of
-the community. It has been showed in [23] that the request rate is
-positively correlated with the trust and performance of web
-services, which means it is not random when the service is running
-for a large enough period of time. In fact, having a
-\emph{casi-static} request rate for communities is not
-unrealistic. To support our claim, we provide data from a real
-world example. The CEO of \url{concertboom.com}, Kooshiar Azimian,
-has provided us with their access and request rates of the web
-services they use\ref{cblog}. Their service provides ticketing
-information for events happening close to user's location. They
-use Ticketnetwork.com web services\footnote{Affiliate program
-link: http://www.ticketnetwork.com/affiliates/agreement.aspx}
-\footnote{Web Service API documentation:
-\url{www.getacoder.com/data/projects/77613/TicketNetwork\%20Web\%20Services\%20(W2)-.doc}},
-and have implemented their back-end code in Java. As shown in
-Figure \ref{fig1}, they currently have an average of 340,000 daily
-page views or almost 3.95 requests per second. They invoke the
-\url{ticketnetwork} web service almost 4 times per second to get
-the seating chart and tickets available for the events. During a
-day, the pick time happens at around 20:00 UTC time, which has
-almost 10\% more requests than during the lower pick time, which
-happens around 7:00 AM UTC time. As shown in the figure, the
-pattern of request rate is casi-stable during the period between
-May and September.
-%Therefore, \url{ticketnetwork} knows that
-%\url{concertboom.com} has a request rate of 340,000 requests per
-%day or almost 3.95 requests per second and can adjust the internal
-%service providers and resources so they can  provide these rate of
-%services.
-}
-
-\textbf{Because the data of \url{concertboom.com} are private, we
-were asked not to disclose them publicly. We only get from the
-company the consensus to use them for the response letter. This is
-the reason why we could not add them to the paper.}
-
-\begin{figure}
-\begin{center}
-%\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=10cm]{cb.eps}\label{cblog}
-\caption{Number of ticket pageviews of concertboom.com during May 5th, until Sep 9th, 2013}
-\label{fig1}
-\end{center}
-\end{figure}
-
-\vspace{0.5cm}\textbf{\underline{5. Reviewer}:}  The paper
-conducted a simulation instead of an experimental study using real
-world web services. This also suggests the difficulties of finding
-real world examples and application for the proposed idea.
-
-\vspace{0.2cm}\textbf{\underline{Answer 5}:
-%Our focus is on non-functional properties of web services and is extendable to any type of web service communities providing any type of service, which there is high demand, request load and competition for that service type such as mapping, weather, ticketing, and local places information.
-As mentioned previously, for our experiments, we have implemented
-our web services using real data extracted from a data set of web
-services
-(\url{http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/}).
-This makes our web services behave like real ones. In the previous
-version, web services were implemented as abstract enteties as the
-main purpose was to focus on the quality metrics. In the revised
-version, we use flight booking services and airlines coalitions as
-concrete application domain. An XML SOAP based messaging system is
-also implemented. The request contains the flight dates, the
-origin and destination, type of tickets, and number of guests. The
-response contains different flights with different companies,
-prices, timing, etc. We have gathered around 200,000 flights and
-stored them in our MongoDB database. As expected, this did not
-affect our experimental results, since our concern, as most of the
-related work, is on non-functional properties of web services. We
-could deploy web services using JAX-WS in Java and deploy on
-different servers. However, those web services would not reflect
-the quality of service parameters of real web services under load
-in real world. For example, we cannot evaluate the exact
-bottlenecks different type of services may have, some qualities
-may drop because of heavy load of DB queries, some because of
-network congestions and delays while trying to generate the
-results for end users. Therefore, the real world data can provide
-us with QoS values of real functioning web services online. We
-have carefully examined many published proposals in services
-computing including work on web service community and composition
-such as [Yu 2013]\footnote{Q. Yu and A. Bouguettaya, Efficient
-Service Skyline Computation for Composite Service Selection, IEEE
-Transactions on Knowledge and Data Engineering (TKDE), vo. 25, no.
-4, pp. 776-789, 2013}, [Limam 2010]\footnote{H. Limam and J.
-Akaich. Managing web services communities: A cache for queries
-optimisation, International Journal on Web Service Computing,
-Vol.1, No.1, pp 2230-7702, 2010}, [Liu 2012]\footnote{A. Liu, Q.
-Li, L. Huang, S. Ying, and M. Xiao,Coalitional game for
-community-based autonomous web services cooperation, IEEE
-Transactions on Services Computing, vol. 99, no. PrePrints, 2012.}
-and many others; we found that they evaluated their results using
-a similar methodology. For the real world applications part of the
-comment, see the previous answers.}
-
-\vspace{0.5cm}
-
-\vspace{1cm}
-
-{
-%\bibliographystyle{plain}
-%\bibliography{omar}
-}
 \end{document}

### 2014-01-31 papers/Exp Sys App/BNJ Exp Sys App.tex
added coop paper

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{times}
%\usepackage{cite}
%\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{verbatim}

%\newtheorem{property}{\textbf{Property}}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{To Compete or Cooperate? This is the Question in
Communities of Autonomous Services}

% a short form should be given in case it is too long for the running head
\titlerunning{Expert Systems with Applications}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%

\author{}

\author{Ehsan Khosrowshahi Asl$^1$\and Jamal Bentahar$^1$\and  Rabeb Mizouni$^3$\and Babak Khosravifar$^2$\and Hadi Otrok$^3$}

%

% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published

\institute{$^1$Concordia University, Montreal, Canada\\
$^2$McGill University, Montreal, Canada\\
$^3$Khalifa University of Science, Technology, and Research, Abu Dhabi, UAE\\
$e\_khosr@encs.concordia.ca$, $bentahar@ciise.concordia.ca$,
$rabeb.mizouni@kustar.ac.ae$, $babak.khosravifar@mcgill.ca$,
$hadi.otrak@kustar.ac.ae$}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

%\toctitle{}
\tocauthor{Authors' Instructions} \maketitle

\begin{abstract}
%Web services are business applications having the capability to
%cooperate within groups to increase the efficiency of serving
%customers.
In the last few years, communities of services have been studied
in a certain numbers of proposals as virtual pockets of similar
expertise. The motivation is to provide these services with high
chance of discovery through better visibility, and to enhance
their capabilities when it comes to provide requested
functionalities. In the proposed frameworks of these communities,
a common assumption is that residing services, which are supposed
to be autonomous and intelligent, are competing over received
requests, but also exhibit cooperative behaviors, for instance in
terms of substituting each other. When competitive and cooperative
behaviors and strategies are combined, autonomous services are
said to be ``coopetitive''. In this coopetition context, deciding
to compete or cooperate at different moments in time is an open
question yet to be addressed. The contribution of this paper is
the answer to this challenging question by proposing a decision
mechanism that services can use to effectively choose competition
or cooperation strategies that maximize their payoffs. To achieve
this objective, we investigate autonomous services'
characteristics and their expected utilities over different
strategies. We enable services that are hosted in communities with
interaction and decision making capabilities. The ultimate
objective is to measure the threshold that services can use in
order to decide about the two strategies. We show that services
are sometimes better off competing and sometimes better off
cooperating based on their capabilities and the capabilities of
their peers. We prove that the proposed decision mechanism is
efficient and can be implemented in time linear in the length of
the time period considered for the analysis and the number of
services in the community. Moreover, we conduct extensive
simulations, analyze various scenarios, and confirm the obtained
theoretical results using parameters from a real services dataset
on the web. \keywords{Agent-based services; Decision making;
Strategies.}
\end{abstract}

\section{Introduction}\label{Introduction}
Services are software systems providing a standard way of
interoperability among different applications. They are developed
to continuously and autonomously interact with each other to
fulfill users' requests. Organizing services within virtual
structures called \emph{communities} has been proposed for the
purpose of making their discovery easier and increasing the
likelihood of their cooperation
\cite{Benatallah2003,Maamar2009,Medjahed2007,Medjahed2005}. The
idea behind communities is to gather services having similar
functionalities but distinct non-functional properties. In that
context, communities are providing pockets of expertise and
networks of services able to cooperate by substituting each other
in case of execution problems
\cite{Bentahar2008,Maamar2009,Mhamdi2012}.

\textbf{\underline{Motivations}}. Abstracting and associating
services\footnote{In this paper, the terms service, agent-based
service, and service agent have the same meaning and are used
interchangeably.} with knowledge-empowered agents without changing
these services implementation has already been proposed and widely
analyzed
\cite{Garcia2009,Lomusio2012,Maamar2005,Paschke2011,Pradhan}. Such
an agent-based abstraction benefits services from advanced
interaction and decision-making techniques that those agents are
able to manage \cite{Jacyno,Bentahar,Sanchez2011}. That means
services are no more considered as simply passive components but
as intelligent entities that enjoy autonomy and selfishness, two
significant properties in business settings where competition is a
key factor \cite{Jurca2,Khosravifar2}. Within communities, those
services, selfish and utility maximizers by nature, can follow two
different strategies, namely cooperation and competition in order
to increase their payoffs when they provide services to consumers
\cite{Maamar2011}. In typical business settings, services are used
to compete within communities as they provide the same
functionalities and the number of users requests is finite.
However, the same reason of providing similar functionalities can
lead services to cooperate because they can replace each other in
case of failure or unavailability, and services can do better in a
coalition structure. Analyzing services competition and
cooperation strategies within communities is still an open problem
that motivates the research described in this paper.

\textbf{\underline{Contributions}}. Analyzing services acting
behaviors in such a context in terms of deciding which strategy to
choose is an open and challenging problem. Our main contribution
in this paper is to address this problem using the game-theoretic
\emph{best response} technique \cite{Fudenberg1991}. Best response
is the strategy that produces the most favorable outcome for a
player, taking other players' strategies as given. The framework
we propose in this paper enables services to cope with strategic
decision making in different scenarios. More precisely, in this
paper we define and analyze the properties of different key
factors and parameters, such as a new metric called \emph{growth
factor} aiming to measure the performance of services taking into
account their reputation and QoS. These factors are then used to
compute a threshold, called \emph{coopetition threshold}, which
helps service agents decide either to compete or cooperate based
on the expected payoff. A preliminary short version of this paper
is presented in \cite{Khosravifar-ICSOC2012} where the need of
analyzing coopetition strategies of communities of autonomous
services has been identified and the general architecture has been
introduced. However, this paper extends
\cite{Khosravifar-ICSOC2012} by 1) considering more parameters (20
instead of only 5) including cooperation and competition fees and
probabilities, which makes the system comprehensive; 2) using game
theory to analyze the strategies and characterize the payoffs,
which makes the mathematical and theoretical apparatus richer; 3)
introducing and formalizing the concept of coopetition threshold,
which allows services to decide about their strategies; 4)
analyzing the computational complexity of the decision procedure,
which shows the feasibility and efficiency of the approach; and 5)
extending the simulation results and analysis by considering more
scenarios.

In a nutshell, we propose a mechanism within which service agents
in the community could choose either to compete for an announced
task\footnote{Requests and tasks are used in this paper
interchangeably.}, or to cooperate with other competing
services in the same community to accomplish some subtasks of the announced task. %We
%equip intelligent web services to follow a reasoning technique to
%choose best interactive strategy (Coopetitive attitude, which is
%categorized to compete and cooperate). In the proposed system,
We explore details behind the strategic decision making procedures
and enable service agents to apply different techniques to
constrain high efficiency and obtain the maximum utility. We
investigate services' expected payoffs and the involved
probabilities that are used to choose over the two interacting
strategies. %This mechanism is useful for systems hosting a number
%of intelligent entities that are involved in some cooperative
%work.
As intelligent entities, service agents require a reasoning
technique that enhances their abilities over best acting
strategies and the attitude they could exhibit to yield maximum
utility. In this paper, we present theoretical results about the
decision making algorithm that could be used by a typical service
agent. We also discuss implementation of a simulation environment
with a number of communities hosting a number of services having
parameters extracted from a real dataset
\cite{Almasri}\footnote{The implemented environment includes the
QWS dataset by Eyhab Al-Masri and Qusay H. Mahmoud freely
available at: www.uoguelph.ca/~qmahmoud/qws.}. This dataset
represents $2507$ real services that exist on the web. It includes
the QoS values of $9$ parameters including availability,
throughput and reliability. These QoS values were determined by
monitoring the services over a $6$ day period. We equip some of
those services with our proposed strategic decision making
procedure and compare the performance of the equipped services
against other ordinary services. We provide detailed discussions
over the implemented environment and verify the effectiveness of
the proposed mechanism.

\textbf{\underline{Paper Organization}}. The rest of the paper is
organized as follows. Section \ref{The Proposed Framework}
presents some preliminaries about the system design needed to
understand the proposed model. Section \ref{Theoretical Results}
introduces the theoretical model along with services' competitive
and cooperative strategies. Section \ref{Experimental Results}
outlines the experimental results and a detailed comparison of the
equipped services with our strategic reasoning techniques with the
ordinary services. Discussion of relevant related work is
presented in Section \ref{Related Work}. Finally, Section
\ref{Conclusion} concludes the paper.

\section{The Proposed Framework}\label{The Proposed Framework}
In this section, we first present the architecture of the proposed
model. We explore the characteristics of intelligent service
agents and their network. We link this architecture to the
implemented system where we investigate the services' coopetitive
attitudes. We compute the involved system parameters and explain
the services' interactive strategy profiles by highlighting their
coopetitive choices.

\begin{figure}[h]
\centering
\includegraphics[scale=1]{architecture++.eps}
\caption{Services are partitioned into competitive and cooperative
sets. Competitive services may get tasks directly from the master
agent and they can share it with other cooperative services in
their collaborative networks within the same community.}
\label{architectureFigure}
\end{figure}

\subsection{The Architecture}

The proposed system consists of three types of autonomous entities
with different goals \cite{Khosravifar-ICSOC2012}:

1) \textit{Services} that reside inside a community which
aggregates a number of functionally similar or complementary
services as a group (more details about communities of services
are given in \cite{Khosravifar2010,Maamar2009}). Within the same
community, each service might have a network consisting of some
other services that might get involved in a cooperative work (e.g.
composition and substitution). As services are also competing,
particularly when they provide similar functionalities, each one
of them aims to maximize its individual income (i.e., the payoff)
by adopting a given strategy.

2) \textit{Master Service} is the manager and representative of
the community of services. Among other functionalities, the master
agent is responsible for allocating the tasks to services within
the community. After the task being accomplished, and based on the
delivered quality of service, the master rewards or penalizes the
associated service agent by updating its reputation. The master is
equipped with a task allocation mechanism aiming to increase
service users satisfaction and eventually the community's market
share in the whole system.

3) \textit{Users} generate tasks with specified QoS. In our
proposed system, tasks are continuously being generated and user
satisfaction is abstracted since we focus on services' interactive
strategies.

Figure \ref{architectureFigure} illustrates the architecture of a
typical community aggregating a number of services with different
interactive strategies. Some of them compete for the task where
they directly deal with the master. Some others cooperate in the
associated task where they only deal with the competed service as
the task leader and do not directly interact with the master (the
master deals only with the service that has bid for the task,
which is responsible of choosing its collaborative network). In
both sets, some service agents are for certain moments out of any
collaboration network. We highlight details of the interactive
strategies in the rest of this section.
%Figure \ref{algorithm1} %exposes the details of task allocation mechanism that is used to select the web services.
In the proposed system, the master sorts the competing services
(i.e., the bidders) based on some parameters (such as reputation)
that we explain in the rest of this section. The winner to which
the master allocates the task is the bidder
service agent that is ranked first. %If the web
%service is busy or unwilling to take the task, the master
%allocates the task to the second competing web service in the
%list.
There is a chance that some tasks could not be assigned to any
service. These tasks are accumulated in the task pool to be
allocated in the next task allocation round. Upon allocation of
the task, the service is responsible for offering the required QoS
that is stated in the task being generated by a consumer.
Afterwards,  the master rewards or penalizes the competing
service by upgrading or degrading its reputation according to the
offered QoS compared with the required one. This comparison
influences the sorting mechanism used by the master to allocate
the tasks in further task allocation rounds.

%\begin{figure}[h]
%\centering
%\begin{tabular}{l}
% \hline\hline
%\textbf{Algorithm} Task Allocation Mechanism Used by Master Web Service\\  \hline
%  \small\textbf{CompetitiveWebServices}: Make a list of all web services ready to compete flag equal to %true\\
%  SortTaskPool(taskPool)\\
%  \small\textbf{TaskToBeDone}: Select a random number of undone tasks to be allocated\\
%  \small 1: \textbf{foreach} task \textbf{in} CompetitiveWebServices\\
%  \small 2: ~~~~~ \textbf{while} (!task.assigned)\\
%  \small 3: ~~~~~~~~~~~ \textbf{foreach} webservice \textbf{in} CompetitiveWebServices\\
%  \small 4: ~~~~~~~~~~~~~~~~~ \textbf{if}(!webservice.busy)\\
%  \small 5: ~~~~~~~~~~~~~~~~~~~~~~~ \textbf{if}(webservice.acceptTheTask)\\
%  \small 6: ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~webservice.NumberOfOfferedTask+=1\\
%  \small 7: ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~webservice.NumberOfAcceptedTask+=1\\
%  \small 8: ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~webservice.CurrentAssignedTask=task\\
%  \small 9: ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~task.assigned=true\\
%  \small 10: ~~~~~~~~~~~~~~~~~~~~~~~~~~~\textbf{break}\\
%  \small 11: ~~~~~~~~~~~~~~~~~~~~~~ \textbf{else}\\
%  \small 12: ~~~~~~~~~~~~~~~~~~~~~~~~~~~webservice.NumberOfOfferedTask+=1\\
%  \small 13: ~~~~~~~~~~~~~~~~~~~~~~~~~~~webservice.NumberOfRefusedTask+=1\\
%  \end{tabular}
%%
%\caption{Master web service task allocation algorithm that is used to
%allocate continuous tasks to %appropriate competitive web services.}
%\label{algorithm1}
%\end{figure}

\subsection{System Parameters}
In this part, we demonstrate the involved parameters and their
corresponding formulations and explanations. \textbf{}

\textbf{Task QoS} ($T_{QoS}^r$) is the required QoS metric for a
specific task $r$. Users define tasks with specific QoS
requirements such as response time, availability, and
successability (or accuracy) \cite{Lim}. We aggregate and
normalize these metrics to a value between $0$
and $1$. %Throughout this paper, we refer to this value as
%$T_{QoS}$.

\textbf{Service QoS} ($QoS_w^r$) is the QoS provided by the
service $w$ after performing the task $r$. Again, the metrics that
contribute in computing this QoS are aggregated and normalized to
a value between $0$ and $1$. The offered quality might or might
not meet the required task quality $T_{QoS}^r$. In the latter
case, the service user would be disappointed and a negative
satisfaction feedback is expected. In our proposed system, both
cases are considered when calculating the services' reputation.

%\textbf{NTD} is the number of tasks completed by a web service.

\textbf{Budget} ($B_w^t$) is the amount of money the service agent
$w$ has in its disposal during the window time $t$ (i.e.,
$[0,t]$), which helps pay for the community membership fees
($\epsilon$) and is one of the parameters that the service agent
considers when deciding about getting involved in a competition or
not. This parameter has been used in other service computing
settings such as \cite{Khosravifar-ICSOC2012,Lim}.

\textbf{Reputation} ($Rep_w^t$) is a significant factor in any
online community \cite{Fouss2010}. Without a reputation enabling
mechanism, users cannot differentiate among services, specially
the ones which offer the same type of service. Reputation
mechanisms usually aggregate users' experiences and in our case it
strongly depends on QoS that each service provides. Users define
tasks, each one with specific quality $T_{QoS}^r$, so that after
performing a certain number of tasks, each one with $QoS_w^r$,
during a window time $t$, the reputation of $w$ gets evaluated by
the master agent. $Rep_{w}^{t}$ refers to the reputation of $w$
during that window time $t$.

In Equation \ref{repr}, we compute the reward that the master
computes considering the task $r$'s QoS $T_{QoS}^r$ compared with
the service offered quality $QoS_w^r$. In case the offered quality
meets user expectations, the reward value would be positive. In
this system, we consider a small value as default rewards $\eta$
which the master considers together with the proportional level of
satisfaction as a weighted value (by $\upsilon$). In this case,
the higher the offered quality, the more weighted reward. In case
the offered quality did not meet the user expectations, the reward
would be negative. A default penalty value $\rho$ (where
$\rho>\eta$) together with the weighted proportional difference
are therefore considered. The idea is to harshly penalize the
services rather than rewarding them. To this end, rational service
agents should carefully analyze their capabilities once the
available tasks are announced. Equation \ref{reward} computes the
obtained reward by $w$ during the window time $t$ considering the
set $task_w^t$ of tasks performed by $w$ during the window time
$t$. In our proposal, service agents have the goal of increasing
their budget, which is directly related to their reputation. Thus,
they have to decide strategically how to maximize this value.

\begin{equation} \label{repr}
reward_w^r = \begin{cases}
\eta + \upsilon \frac{QoS_w^r}{T_{QoS}^r+QoS_w^r}   & \text{if $T_{QoS}^r\leq QoS_w^r$;}\\
-(\rho +  \upsilon \frac{T_{QoS}^r}{T_{QoS}^r+QoS_w^r} ) & \text{otherwise.}\\
\end{cases}
\end{equation}

\begin{equation} \label{reward}
reward_w^t =
\begin{cases}
\frac{\sum_{r \in
task_w^t}reward_w^r}{|task_w^t|}& \text{if $task_w^t \neq \emptyset$;}\\
0 & \text{otherwise.}\\
\end{cases}
\end{equation}

The assigned reputation value is updated by the computed reward
value. The computed reputation of services is bounded by the
minimum and maximum reputation values $0$ and $1$. % to constrain
%the balance the cooperative community of web services. The updated
Let $\Gamma = Rep_{w}^{t} + reward_w^t$. The updated reputation
value is then computed as follows:

\begin{equation}\label{repz}
%Rep_{w}^{t+1} = Rep_{w}^{t} + reward
%\end{equation}
%\begin{equation*}
Rep_{w}^{t+1} = \begin{cases}

\Gamma & \text{if $ 0 \leq \Gamma \leq 1$;}\\
0  & \text{if $\Gamma < 0$;}\\
1 & \text{if $\Gamma > 1$.}\\
\end{cases}
\end{equation}
%
For new services with no previous reputation value, we use the
bootstrapping trust technique proposed in \cite{Yahyaoui2}. This
technique consists in giving the new services a chance and observe
their behaviors for a period of testing time. The observation
sequence is modeled as a hidden Markov model that is used to
detect the behavior of the service by comparing the observation
behavior against pre-defined trust patterns. Based on the matching
result, an initial value is assigned to the service. Using this
initial reputation value, services quickly converge to their
actual and stable values using the update function.

\begin{proposition}\label{Complexity-Rep}
$Rep_{w}^{t}$ can be computed in time $O(|t|)$, i.e., in time
linear in the size of the window $t$.
\end{proposition}

\begin{proof}\footnote{In this paper, we
assume that the common arithmetic and elementary functions, such
as multiplication, division and trigonometric functions can be
computed in time $O(1)$ as they operate on inputs of fixed sizes.}
The function $Rep_{w}^{t}$ is recursive on $t$, but the algorithm
works by storing the last calculated reputation value in a
variable, so it will not be recalculated again at each iteration.
However, the calculation of $reward_w^t$ is needed. Since the
function $reward_w^t$ can be computed in time linear in the number
of tasks (see Equations \ref{repr} and \ref{reward}), which in
turn is linear in the size of the window time, the result follows.
$\Box$
\end{proof}

\textbf{Growth Factor} ($G_w^t$) is a parameter which declares
services' performance based on their recent strategies and
activities. Growth factor is relative to services' reputation
$Rep_w^t$, QoS during the window time $t$ $QoS_w^t$, and budget
$B_w^t$. This factor is the main variable a typical service uses
to decide about which strategy to adopt. The details about the
decision making process are described in Section \ref{Theoretical
Results}. We use Equation \ref{eq:growthfactor} to compute the
growth factor $G^t_w$ of the service $w$ during the window time
$t$ as the average of the three aforementioned parameters, where
$n_t$ is the total number of offered tasks to the whole community
during the
window time $t$, %(we consider the time window $t$ large enough so
%that $n_t \neq 0$),
$\mu_w$ is the mean received service fee, and $\epsilon$ is the
cost of community membership.

\begin{equation}\label{eq:growthfactor}
G^t_w = \frac{Rep^t_w + QoS_w^t+\frac{B_w^t}{n_t  \mu_w -
\epsilon}}{3}
\end{equation}
\begin{equation*}
\mu_{w} \in\{\mu_{w, CM}, \mu_{w, CO}\},~~~QoS_w^t =
\begin{cases} \frac{\sum_{r \in
task_w^t}QoS_w^r}{|task_w^t|}& \text{if $task_w^t \neq \emptyset$;}\\
0 & \text{otherwise.}\\
\end{cases}
\end{equation*}

This equation is designed so that it satisfies the following
desirable properties:

\begin{enumerate}

\item The growth factor function should be monotonically
increasing in the offered quality of service $QoS_w^t$.

\item The growth factor function should be monotonically
increasing in the service's reputation $Rep^t_w$.

\item The growth factor function should be monotonically
increasing in the budget $B_w^t$ if the maximum possible profit is
positive and monotonically decreasing in $B_w^t$ if the maximum
possible profit is negative. This property reflects the idea that
the budget contributes in the increase of the growth factor as far
as there is a chance to make profit. In fact, the contribution of
the budget $B_w^t$ in the calculation of the growth factor should
be proportional to the maximum possible profit $n_t \mu_w -
\epsilon$ where the service $w$ receives all the offered tasks
during the window time $t$.

\end{enumerate}

  % if the profit $\beta_w$ made by the web service $w$
%considering the mean received service fee $\mu_w$ and the cost of
%community membership $\epsilon$ is positive.
It is easy to show that Equation \ref{eq:growthfactor} satisfies
the three aforementioned properties by calculating the partial
derivatives $\partial G^t_w$ of this function in 1) $QoS_w^t$
($\frac{\partial G^t_w}{\partial QoS_w^t} = \frac{1}{3} $); 2)
$Rep^t_w$ ($\frac{\partial G^t_w}{\partial Rep^t_w} = \frac{1}{3}
$); and 3) $B_w^t$ ($\frac{\partial G^t_w}{\partial B_w^t} =
\frac{1}{3 (n_t \mu_w - \epsilon)} $). Thus, the sign of the two
first partial derivatives is positive and the sign of
$\frac{\partial G^t_w}{\partial B_w^t}$ depends on the sign of the
maximum profit $n_t \mu_w - \epsilon$, so we are done. The mean
service fee depends on the strategy adopted by the service because
a competitive service receives higher fees $\mu_{w, CM}$ compared
to a cooperative one $\mu_{w, CO}$ ($\mu_{w, CM} > \mu_{w, CO}$).
The motivation behind this is that a competitive service for a
given task is the leader for that task while other cooperative
services are performing specific subtasks as asked by the leader.

\begin{proposition}\label{Complexity-Growth_Factor}
$G_w^t$ can be computed in time linear in the size of the window
$t$.
\end{proposition}

\begin{proof}
As shown in the second part of Equation \ref{eq:growthfactor}, the
function $QoS_w^t$ can be computed in time linear in the number of
tasks, which in turn is linear in the size of the window time.
Since $B_w^t$ is constant, the result follows from Proposition
\ref{Complexity-Rep}. $\Box$
\end{proof}

The above explained parameters and other additional parameters
which will be used in the rest of this paper are listed and self
explained in Table \ref{Preliminaries}.

\begin{table}
\centering
\caption{List of abbreviations.}
\begin{tabular}{|c|c||c|c|}
\hline
\textbf{Notation} & \textbf{Definition} & \textbf{Notation} & \textbf{Definition}\\
\hline\hline
$T_{QoS}^r$    & Required task QoS for the task $r$   & $T_{QoS}^t$      & Mean required task QoS during $t$\\
$QoS_w^r$      & Service $w$ QoS for the task $r$ & $QoS_w^t$        & $w$ QoS during the window time $t$\\
$Reward_w^r$   & Reward obtained by $w$ w.r.t. $r$    & $Reward_w^t$ & Reward to update the reputation\\
$Rep^t_w$      & Reputation assigned for $w$          & $B_w^t$          & Budget associated to service $w$ \\
$G^t_w$        & Growth factor of $w$ during $t$      & $\epsilon$       & Community membership fee\\
$\pi_{w,CM}^t$ & Competition payoff of $w$            & $\pi_{w,CO}^t$   & Cooperation payoff of $w$\\
$p_{w,CM}^t$   & Competition probability of $w$       & $p_{w,CO}^t$     & Cooperation probability of $w$\\
$COF_w^t$      & Cooperation fee of $w$               & $\beta_{w}$      & Profit of $w$\\
$\mu_{w, CM}$  & Mean service fee for competing $w$   & $\mu_{w, CO}$    & Mean service fee for cooperating $w$\\
$\tau_w^t$     & Coopetitive threshold of $w$         & $P_w^t$          & Probability of competing for $w$\\
$U_w^t$        & Utility of $w$                       & $E^t_w$          & Expected number of tasks\\

\hline
\end{tabular}
\label{Preliminaries}
\end{table}

\subsection{Service Interactive Strategies}

The main goal of each individual service agent is to increase its
income (payoff). This income can be earned from tasks (or
requests) done by this service. In our model, services can decide
to compete to get a task from the master agent or to cooperate
with other services within a given collaborative network (the way
a collaborative network is set by a leader is based on the
cooperative services reputation and their QoS parameters that
should coincide with the required QoS). Therefore we define two
types of service strategies. First, when a service has higher
level of confidence based on its growth factor, it can compete to
get a task from the master and adopts the competitive strategy.
Second, when the service agent has a lower level of confidence
that it does not feel capable to compete, it waits for some other
services to cooperate with to perform some tasks \footnote{Through
the paper, requests or tasks are supposed to be decomposable.},
and thus it adopts the cooperative strategy. Services estimate the
outcome of all the strategies and choose one of them accordingly.
This decision is not static but can change over time so service
agents can switch from one strategy to the other, and this dynamic
attitude is referred to as coopetition. The underlying decision
making process is presented in the next section.

\section{Theoretical Results}\label{Theoretical Results}

\subsection{Service Decision Making Procedure}
%In the previous section, we introduced web services' interaction
%strategies.
In this section, we explore in details the interaction strategies
and the outcome of each strategy in terms of services' utilities.
The main part of services' decision making procedure falls into
their growth factor analysis. In fact, the comparison of the
growth factor to a particular threshold is the main reason that
influences the service's decision to follow either competitive or
cooperative behavior. service agents initially compute this value
and compare it with their computed threshold. Generally the main
challenge is the threshold computation and we cope with this issue
in the rest of this section. We additionally use the obtained
results in the implemented environment and analyze their
effectiveness on services' strategic decision making procedures.

Figure \ref{decisionMakingProcedure} shows the decision making
process that is followed by a typical service. In case the service
agent is ready to compete, there is a chance that it bids for a
task if it has the required capabilities to accomplish that task,
or stays silent and returns to the cooperative status. But in case
the service agent is willing to cooperate, it has to wait for a
cooperation opportunity that could be triggered by another service
agent that competed and obtained the task, so both services will
be part of the same collaborative network. In the decision making
process presented in Figure \ref{decisionMakingProcedure}, we
assume that the competing service might get the task (denoted as
$Bid/obtainedTask$) or not in case of being rejected by the master
agent, or do not even bid for the task (denoted as
$Silent/rejectedTask$). For simplicity reasons and without loss of
generality, we group the two cases of $Bids$ and $obtainedTask$
together as well as $Silent$ and $rejectedTask$. The rational
behind this aggregation is the fact that our main concentration is
services' status (competitive or cooperative) over different
decision making rounds, which could be caused by internal factors
(the services) or by the external factor (the master agent).

\begin{figure}[h]
\centering
\includegraphics[scale=0.55]{decision1++.eps}
\caption{Decision making process over competitive and cooperative
strategies.} \label{decisionMakingProcedure}
\end{figure}

Consider a service $w$ that is willing to compete for the period
of time $t$ (that means the computed growth factor is more than
the analyzed threshold). This service can estimate the expected
payoff associated to this decision, called \emph{competition
payoff}. Equation \ref{CMPff} computes this expected payoff for
the competing service $w$ ($\pi_{w,CM}^t$) considering the
$Bid/obtainedTask$ probability of $p_{w,CM}^t$ and
$Silent/rejectedTask$ probability of $1-p_{w,CM}^t$.

\begin{equation}\label{CMPff}
\pi_{w,CM}^t=p_{w,CM}^t(\mu_{w, CM}E^t_w-COF_w^t
E^t_w-\epsilon)+(1-p_{w,CM}^t)(-\epsilon)
\end{equation}

In Equation \ref{CMPff}, $E^t_w$ is the number of tasks that $w$
expects during the window time $t$, and $\mu_{w, CM}$ is the mean
service fee that is assigned by the master agent to $w$. This
means that a competing service directly obtains this fee from the
master agent. Moreover, the competing service $w$ expects a
cooperation fee ($COF_w^t$) that it gives to its collaborators in
case $w$ needs to cooperate with other services (cooperative
service agents in its collaboration network). In any case, the
competing or cooperating service agent pays a fixed amount of
membership ($\epsilon$) to the master agent, which plays the role
of the community's coordinator. This fee would be taken into
account when a service decides to leave to a cheaper community or
act alone. But to concentrate on the main concerns of this paper,
we skip these small details.\\\\
%
From Equation \ref{CMPff}, the following proposition is
straightforward.

\begin{proposition}\label{Complexity-Competition_Payoff}
The complexity of computing the competition payoff $\pi_{w,CM}^t$
is linear in the competition probability $p_{w,CM}^t$, the
expected number of tasks $E^t_w$, and the cooperation fee
$COF_w^t$.
\end{proposition}

The arrival of requests for service $w$ during the time unit $t$
(denoted here by $m_w(t)$) can be modeled as a nonhomogeneous
Poisson process \cite{Khosravifar-ICWS2010,Ruggeri2005}, which
means as a Poisson process with dynamic arrival rate
$\lambda_w(x)$ where $x$ belongs to the time unit $t$. The arrival
rate is thus a function of time and typically varies significantly
from moment to moment. In nonhomogeneous Poisson process, $m_w(t)$
is expressed as follows:

$$ m_w(t)= \int_0^t \! \lambda_w(x) \ \mathrm{d}x$$
%
And the probability of having exactly $n$ requests during the
window $t$ is computed as follows:

$$ p(m_w(t) = n) = \frac{(m_w(t))^n}{n! \ e^{m_w(t)}}  $$
%
Let $Max_w^t$ be the maximum number of requests that $w$ can
receive during $t$. The number of expected requests $E^t_w$ is
given by the parameter $\lambda_w(t)$ as follows:

\begin{equation}\label{Expectation}
E^t_w = \lambda_w(t) = \sum_{n=1}^{Max_w^t} n \ p(m_w(t) = n)
\end{equation}
%
The parameter $\lambda_w(t)$ is usually estimated from data
samples using the least squares, iterative least squares, or
maximum likelihood \cite{Massey1996}.

\begin{proposition}\label{Complexity-Expectation}
The complexity of computing the expected number of requests
$E^t_w$ is linear in the size of the window time $t$.
\end{proposition}

\begin{proof}
For a fixed function $\lambda_w(x)$, $m_w(t)$ can be computed in
$O(1)$. Thus, from Equation \ref{Expectation}, it follows that
$E^t_w$ can be computed in time linear in $Max_w^t$. As $Max_w^t$
is linear in $t$, the result follows. $\Box$
\end{proof}

Similar to the competitive service case, if a service $w$ declares
cooperative status, its expected \emph{cooperation payoff}
($\pi_{w,CO}^t$) is computed in Equation \ref{CLPff}. In this
equation, $p_{w,CO}^t$ is the probability of getting involved in a
cooperative task with other services and $1-p_{w,CO}^t$ is the
probability of failure to find such a cooperation opportunity.
These two probabilities are set when $w$ decides to compete. We
recall that $\mu_{w, CO}$ denotes the mean cooperation fee that is
directly obtained from the leader (i.e., the competitive) service
of the underlying collaborative network. Compared to $\mu_{w,
CM}$, $\mu_{w, CO}$ is relatively smaller since the competitive
service generally dedicates a portion of its obtained income to
pay other cooperative services.

\begin{equation}\label{CLPff}
\pi_{w,CO}^t=p_{w,CO}^t (\mu_{w,
CO}E^t_w-\epsilon)+(1-p_{w,CO}^t)(-\epsilon)
\end{equation}
%
From Equation \ref{CLPff}, the following proposition holds.

\begin{proposition}\label{Complexity-Cooperation_Payoff}
The complexity of computing the cooperation payoff $\pi_{w,CO}^t$
is linear in the cooperation probability $p_{w,CO}^t$ and the
expected number of tasks $E^t_w$.
\end{proposition}

To analyze the expected payoffs obtained from different
strategies, services need to compute the estimated probabilities
that distinguish subcases in each behaviorial status ($p_{w,CM}^t$
for competitive and $p_{w,CO}^t$ for cooperative). To estimate
these probabilities, we should notice that they are functions of
services' reputation values ($Rep_w^t$). Furthermore, $p_{w,CM}^t$
is also function of the difference between the offered QoS
($QoS_w^t$) and the mean requested one considering the set of all
tasks $task^t$ ($T_{QoS}^t$ (see Equation \ref{Mean-Quality}));
and $p_{w,CO}^t$ is function of the reputation of other services
in the community because the leader is supposed to be selective
when it comes to choose the collaborators. To this end, we first
discuss the desirable properties of an estimation function of each
of these probabilities, and show that the proposed ones satisfy
those properties.

\begin{equation}\label{Mean-Quality}
T_{QoS}^t =
\begin{cases} \frac{\sum_{r \in
task^t}T_{QoS}^r}{|task^t|}& \text{if $task^t \neq \emptyset$;}\\
0 & \text{otherwise.}\\
\end{cases}
\end{equation}
%

\begin{proposition}\label{Complexity-Mean_Quality}
$T_{QoS}^t$ can be computed in time linear in the size of the
window $t$.
\end{proposition}

\begin{proof}
From Equation \ref{Mean-Quality},  $T_{QoS}^t$ can be computed in
time linear in $|task^t|$, which in turn is linear in the window
size $|t|$. $\Box$

\end{proof}

The desired properties of $p_{w,CM}^t$ are as follows:

\begin{property}
$p_{w,CM}^t$ is continuous with regard to $Rep^t_w$, $QoS_w^t$,
and $T_{QoS}^t$.
\end{property}
%
\begin{property}
$p_{w,CM}^t$  is monotonically increasing in $Rep^t_w$ and
$QoS_w^t - T_{QoS}^t$ while $QoS_w^t - T_{QoS}^t$ is positive.
\end{property}
%
\begin{property}
$p_{w,CM}^t$ is null if $QoS_w^t - T_{QoS}^t$ is negative.
\end{property}
%
%\begin{property}
%Assuming that the web service $w$ is known by the master web
%service, $Rep^t_w$ is monotonically increasing or decreasing in
%$QoS_w$.
%\end{property}
%
\begin{property}
The increase slope of $p_{w,CM}^t$ is higher when the reputation
$Rep^t_w$ increases in the interval $[0, 0.5]$ than when it
increases in the interval $]0.5, 1]$.
\end{property}

\noindent Property 1 simply says that the probability of success
competition $p_{w,CM}^t$ can be always estimated as far as
$Rep^t_w$, $QoS_w^t$, and $T_{QoS}^t$ are available. Property 2
says that the reputation and QoS are two key factors that
influence the value of $p_{w,CM}^t$ in the sense of positive
correlation. Property 3 indicates that the probability
$p_{w,CM}^t$ is null if the offered QoS is less than the
expectation. Property 4 promotes the increase of the reputation
for new comers and imposes higher increase rate at the beginning
of the reputation curve because it is always hard to build the
reputation, but once it is built, its maintenance is less
challenging.

\noindent The desired properties of $p_{w,CO}^t$ are as follows:

\begin{property}
$p_{w,CO}^t$ is continuous with regard to $Rep^t_w$ and the
reputation of other services in the community.
\end{property}
%
\begin{property}
$p_{w,CO}^t$  is monotonically increasing in $Rep^t_w$ and
 monotonically decreasing in the community average reputation.
\end{property}
%
%\begin{property}
%$p_{w,CM}$ is null if $QoS_w^t - T_{QoS}^t$ is negative.
%\end{property}
%
%\begin{property}
%Assuming that the web service $w$ is known by the master web
%service, $Rep^t_w$ is monotonically increasing or decreasing in
%$QoS_w$.
%\end{property}
%
\begin{property}
The increase slope of $p_{w,CO}^t$ is higher when the reputation
$Rep^t_w$ increases in the interval $[0, 0.5]$ than when it
increases in the interval $]0.5, 1]$.
\end{property}

\noindent Property 5 is similar to Property 1. Property 6 says
that $w$ has more chance to get involved in a cooperation if it
has high reputation compared to the other members. This chance
decreases if other services have higher reputation. Property 7 is
similar to Property 4.

Equations  \ref{CMp_w} and \ref{CLp_w} respectively compute the
estimated success probability in cases where service $w$ is
competing and cooperating. These values are computed considering
service's reputation value ($Rep^t_w$ computed by the master),
service's offered QoS ($QoS^t_w$), the task required QoS
($T_{QoS}^t$), which is the mean required QoS computed from
previous tasks, the maximum offered QoS ($QoS_k^t$, which is
provided by another competitive service $k$), and the cooperative
factor $CL_w^t$ of service $w$ during the window time $t$, which
is computed as the portion of service's current reputation on the
average reputation of the community $\mathcal{C}$.

\begin{equation} \label{CMp_w}
p_{w,CM}^t = \begin{cases}
\sin(Rep^t_w\frac{\pi}{2})\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k^t-T_{QoS}^t)} & \text{if $QoS_w^t\geq T_{QoS}^t$;}\\
0 & \text{otherwise.}\\
\end{cases}
\end{equation}

\begin{equation}\label{CLp_w}
p_{w,CO}^t=\sin(Rep^t_w\frac{\pi}{2})CL_w^t
\end{equation}
\begin{equation*}
CL_w^t=\frac{Rep^t_w}{\sum_{k\in
\mathcal{C}}Rep^t_k/|\mathcal{C}|}
\end{equation*}

\begin{theorem}
Equation  \ref{CMp_w} satisfies Properties 1 to 4.
\end{theorem}

\begin{proof}
It is easy to show the continuity of Equation \ref{CMp_w}, which
satisfies Property 1. The partial derivative $\frac{\partial
p_{w,CM}^t}{\partial Rep^t_w} = \frac{\pi}{2}
\cos(Rep^t_w\frac{\pi}{2})\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k^t-T_{QoS}^t)}$
is positive as the function $\cos$ (the derivative of $\sin$) is
positive on $[0, \frac{\pi}{2}]$, $Rep^t_w \in [0, 1]$, and
$QoS_w^t\geq T_{QoS}^t$. The partial derivative $\partial
p_{w,CM}^t$ with regard to $QoS_w^t - T_{QoS}^t$ ($\frac{\partial
p_{w,CM}^t}{\partial(QoS_w^t - T_{QoS}^t)} =
\frac{\sin(Rep^t_w\frac{\pi}{2})}{Max_k(Qos_k^t-T_{QoS}^t)}$) is
also positive since $Qos_k^t-T_{QoS}^t > 0$ and
$Rep^t_w\frac{\pi}{2} \in [0, \frac{\pi}{2}]$ and $\sin$ is
positive on $[0, \frac{\pi}{2}]$, which proves the satisfaction of
Property 2. Property 3 is straightforward. Finally, the increase
slope of the function $\sin$ on $[0, \frac{\pi}{2}]$ proves
Property 4. $\Box$
\end{proof}

\begin{theorem}
Equation  \ref{CLp_w} satisfies Properties 5 to 7.
\end{theorem}
%
\begin{proof}
We can easily show the continuity  of Equation \ref{CLp_w} from
which Property 5 follows. Property 6 can be shown by calculating
the partial derivative $\partial p_{w,CO}^t$ first with regard to
$Rep^t_w$ and second with regard to the community $\mathcal{C}$
average reputation $\sum_{k\in \mathcal{C}}Rep^t_k/|\mathcal{C}|$,
where $|\mathcal{C}|$ is the cardinality of the considered
community $\mathcal{C}$. The first partial derivative
($\frac{\pi}{2}\cos(Rep^t_w\frac{\pi}{2})CL_w^t$) is positive and
the second ($\frac{-\sin(Rep^t_w\frac{\pi}{2})Rep^t_w}{(\sum_{k\in
\mathcal{C}}Rep^t_k/|\mathcal{C}|)^2}$) is negative, which proves
the satisfaction of Property 6. The proof of satisfaction of
Property 7 is similar to the one of Property 4. $\Box$
\end{proof}
%Considering these involved parameters, we verify that properties
%$1$ to $3$ are satisfied. For property $4$, we use $sinus$
%function to promote the role of reputation influence in this
%system. Using $sinus$ function, we promote reputation increase of
%web services specially when it is less than $50\%$. Considering
%the desired properties, the formulas represented in Equations
%\ref{CMp_w} and \ref{CLp_w} are candidates we chose to compute the
%probabilities regarding $Competitive$ and $Cooperative$
%strategies. These formulas are used in implemented system and
%verified with respect to their accuracy and effectiveness in
%adopting different interacting strategies.

%In the proposed heuristic  function, the web service $w$ is not
%aware of current $T_{QoS}$ and $QoS_k$, but could use its previous
%information to estimate their values. To this end, if the web
%service is more informative about the previous data, it could
%obtain more realistic measurement over the estimated
%probabilities.
%
%
%We compute the success probability of cooperation ($p_{w,CO}$)
%similarly in the sense  that we still promote reputation influence
%using $sinus$ function, but multiplied to the cooperative factor
%$CL_w$ of the web service $w$. This value is computed as the
%portion of web service's current reputation on the average
%reputation of the community.

\begin{proposition}\label{Complexity-Probability_Competition}
$p_{w,CM}^t$ can be computed in time linear in the window size
$|t|$.
\end{proposition}

\begin{proof}
The result follows directly from 1) Equation \ref{CMp_w}; 2)
Proposition \ref{Complexity-Rep} (Complexity of $Rep^t_w$ is
linear in the window size $|t|$); 3) second part of Equation
\ref{eq:growthfactor} (the function $QoS_w^t$ can be computed in
time linear in the number of tasks, which in turn is linear in the
size of the window time); 4) Proposition
\ref{Complexity-Mean_Quality} (Complexity of $T_{QoS}^t$ is linear
in the size of the window $t$); and 5) the fact that those
functions are computed independently one from the other. $\Box$
\end{proof}

\begin{proposition}\label{Complexity-Probability_Cooperation}
$p_{w,CO}^t$ can be computed in time $O(|t|.|\mathcal{C}|)$, which
means linear in both the size of the window $t$ and the size of
the community $\mathcal{C}$.
\end{proposition}

\begin{proof}
From Proposition \ref{Complexity-Rep}, $Rep^t_w$ can be computed
in $O(|t|)$. Consequently, the function $\sum_{k\in
\mathcal{C}}Rep^t_k$ can be computed in $O(|t|.|\mathcal{C}|)$, so
it does the computation of the function $CL_w^t$ as $Rep^t_w$ will
be computed just once and stored in a variable. The same variable
will be used to compute $\sin(Rep^t_w\frac{\pi}{2})$. Thus, from
Equation \ref{CLp_w}, the result follows. $\Box$
\end{proof}

\subsection{Coopetition Threshold}

In this part, we compute the coopetition threshold that a typical
service agent could use to adopt reasonable interacting strategies
and we empirically verify the effectiveness of the obtained
results in the next section. In fact, to decide which strategy to
adopt, we let the service agent $w$ compare its growth factor
$G_w^t$ with the coopetition threshold $\tau_w^t$ it holds at
current window time $t$ and choose to compete with probability
$P_w^t$ that we compute in Equation \ref{P}. Based on this
probability, we calculate the total utility $U_w^t$ in Equation
\ref{U}.

\begin{equation} \label{P}
P_w^t= \begin{cases}
\frac{G_w^t}{\tau_w^t}  & \text{if $G_w^t\leq \tau_w^t$;}\\
1 & \text{otherwise.}\\
\end{cases}
\end{equation}

\begin{equation}\label{U}
U_w^t=P_w^t(\pi_{w,CM}^t)+(1-P_w^t)(\pi_{w,CO}^t)
\end{equation}

%Equation  \ref{U} computes the
%expected utility (as accumulated fee) regarding web service $w$.
%This estimated utility is result of aggregation of two different
%interacting strategies of $Competitive$ and $Cooperative$.
%Aggregating these strategic payoffs, web service $w$ follows
%probability distribution of $\{P,1-P\}$. This probability
%distribution is computed in Equation \ref{P}, which is a function
%of the growth factor ($G_w$) and computed threshold ($Tr^t$). So
%if the web service is aware of the reasonable threshold, the value
%$p$ could be computed and used as the core of strategic
%probability distribution. But there is a case where the web
%service does not have a reasonable threshold value and cannot
%rigorously decide for any adopting strategies.

The key factor in the computation of the probability $P_w^t$ and
the associated utility is the threshold value. To compute the
threshold, we use the game-theoretic best response technique. A
typical service agent $w$ will follow the best response strategy
to maximize its expected aggregated payoff. The idea is to
equalize the expected payoffs of the two acting strategies:
compete and cooperate.
%
%
%by following the following three probability distributions: (1)
%$\{1,0\}$ where the web service always competes; (2) $\{0,1\}$
%where the web service always cooperates; and (3)
%$\{\frac{1}{2},\frac{1}{2}\}$ where the web service equalize the
%probabilities and decides with unbiased distribution. Following
%the third case, the web service equites the expected payoffs as
%outcomes of different interacting strategies.
%
The objective behind equalizing payoffs is to explore conditions
under which service agent $w$ could react with best response to
further decision making procedures. We use the obtained conditions
to compute the threshold $\tau_w^t$ during the window time $t$. By
equalizing $\pi_{w,CM}^t$ and $\pi_{w,CO}^t$, we obtain:

\begin{equation*}\label{equit}
\pi_{w,CM}^t=\pi_{w,CO}^t      \rightarrow
\end{equation*}
\begin{equation*}
p_{w,CM}^t(\mu_{w,CM}-COF_w^t-\epsilon)+(1-p_{w,CM}^t)(-\epsilon)=p_{w,CO}^t(\mu_{w,
CO}-\epsilon)+(1-p_{w,CO}^t)(-\epsilon)
\end{equation*}
Which means:
\begin{equation*}
p_{w,CM}^t(\mu_{w,CM}-COF_w^t - \epsilon) =
p_{w,CO}^t(\mu_{w,CO}-\epsilon)+(-\epsilon)(p_{w,CM}^t -
p_{w,CO}^t)
\end{equation*}
So, we obtain:
\begin{equation*}
\mu_{w,CM}-COF_w^t - \epsilon =
\frac{p_{w,CO}^t~~\mu_{w,CO}}{p_{w,CM}^t}-\epsilon
\end{equation*}
Therefore:
\begin{equation*}
\mu_{w,CM}-COF_w^t = \frac{p_{w,CO}^t~~\mu_{w,CO}}{p_{w,CM}^t}
\end{equation*}
From which, we derive:
\begin{equation*}
COF_w^t = \mu_{w,CM} - \frac{p_{w,CO}^t~~\mu_{w,CO}}{p_{w,CM}^t}
\end{equation*}
Replacing $p_{w,CM}^t$ and $p_{w,CO}^t$ using Equations
\ref{CMp_w} and \ref{CLp_w}, we derive the following:
\begin{equation*}
COF_w^t = \mu_{w,CM} -
\frac{sin(Rep^t_w\frac{\pi}{2})CL_w^t~~\mu_{w,CO}}{sin(Rep^t_w\frac{\pi}{2})\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k-T_{QoS}^t)}}
\end{equation*}
%The fixed membership fee $\epsilon$ could be taken out and
%canceled from both sides of the equation so we obtain the
%following:
%\begin{equation*}
%p_{w,CM}^t(\mu_{w,CM}-COF_w^t)=p_{w,CO}^t(\mu_{w,CO})\rightarrow
%\end{equation*}
%
%\begin{equation*}
%sin(Rep^t_w\frac{\pi}{2})\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k-T_{QoS}^t)}(\mu_{w,
%CM}-COF_w^t)=sin(Rep^t_w\frac{\pi}{2})CL_w^t(\mu_{w, CO})
%\end{equation*}
By simplifying the $sinus$ function from both the numerator and
denominator sides and substituting the cooperation factor $CL_w^t$
of service $w$ we obtain Equation \ref{CLF}:

\begin{equation}\label{CLF}
COF_w^t=\mu_{w,CM}-\frac{Rep^t_w~|\mathcal{C}|}{\sum_{k\in
\mathcal{C}}Rep^t_k}\frac{\mu_{w,CO}Max_k(Qos_k^t-T_{QoS}^t)}{QoS_w^t-T_{QoS}^t}
\end{equation}

Equation \ref{CLF} computes the cooperation fee $COF_w^t$ that is
assigned by service $w$. This fee represents the amount that $w$
spends to cooperate with other service(s) to accomplish the task.
By so doing, we obtain the maximum amount of cooperation fee that
service $w$ can use to constrain the positive payoff out of
competing. Otherwise, the service stays as cooperative entity.

\begin{proposition}\label{Complexity-COF}
$COF_w^t$ can be computed in time $O(|t|.|\mathcal{C}|)$, which
means linear in both the size of the window $t$ and the size of
the community $\mathcal{C}$.
\end{proposition}

\begin{proof}
From Proposition \ref{Complexity-Rep}, $Rep^t_w$ can be computed
in $O(|t|)$. Consequently, the function $\sum_{k\in
\mathcal{C}}Rep^t_k$ can be computed in $O(|t|.|\mathcal{C}|)$.
Since $QoS_w^t$ and $T_{QoS}^t$ can be computed in time $O(t)$
(from the second part of Equation \ref{eq:growthfactor} and
Proposition \ref{Complexity-Mean_Quality} respectively), we are
done. $\Box$
\end{proof}

\begin{lemma} \label{Complexity-Competition_Payoff-Final}
The competition payoff $\pi_{w,CM}^t$ can be computed in time
$O(|t|.|\mathcal{C}|)$.
\end{lemma}

\begin{proof}
The result follows directly from Propositions
\ref{Complexity-Competition_Payoff}, \ref{Complexity-Expectation},
\ref{Complexity-Probability_Competition}, and
\ref{Complexity-COF}. $\Box$
\end{proof}

\begin{lemma} \label{Complexity-Cooperation_Payoff-Final}
The cooperation payoff $\pi_{w,CO}^t$ can be computed in time
$O(|t|.|\mathcal{C}|)$.
\end{lemma}

\begin{proof}
The result follows directly from Propositions
\ref{Complexity-Expectation}, \ref{Complexity-Cooperation_Payoff},
and \ref{Complexity-Probability_Cooperation}. $\Box$
\end{proof}

%\begin{equation*}
%\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k^t-T_{QoS}^t)}(\mu_{w,CM}-COF_w^t)=\frac{Rep^t_w}{\sum_{k\in
%Community}Rep^t_k}(\mu_{w, CO})
%\end{equation*}
%

We use the maximum cooperation fee that a service agent considers
to constrain the positive expected payoff when the competitive
strategy is adopted to update the threshold for the consequent
time window ($t+1$). We compare the maximum cooperation fee with
the required fee ($ReqF_w^t$) that the service indicates to
accomplish the task. The outcome of this comparison is a factor
that uses the current threshold $\tau_w^t$ to compute the
consequent threshold $\tau_w^{t+1}$. As in online learning, the
idea is to compute iteratively the threshold until the fixed point
is achieved, which indicates the threshold's conversion, where the
initial value is randomly chosen (in the simulation different
initial values are used). Equation
\ref{Trt} shows this computation. %We restrict the range of this value to $(0.15,0.85)$ to
%avoid some unreasonable results that could occur due to different
%reasons like system start point or heavy loaded competitive web
%services, \textit{etc}.
To investigate the effectiveness of this threshold on the outcomes
of the services that follow this reasoning technique, in the next
section, we compare the results of different agents with diverse
strategic reasoning techniques.

\begin{equation}\label{Trt}
\tau_w^{t+1}=\begin{cases}
\Theta & \text{if $0 \leq \Theta \leq 1$}\\
1 & \text{if $\Theta > 1$;}\\
0 & \text{if $\Theta < 0$.}\\
\end{cases}
\end{equation}
\begin{equation*}
\Theta =\tau_w^t \ \frac{COF_w^t}{ReqF_w^t}
\end{equation*}

\begin{proposition}\label{Complexity-Threshold}
The threshold $\tau_w^{t}$ can be computed in time
$O(|t|.|\mathcal{C}|)$, which means linear in both the size of the
window $t$ and the size of the community $\mathcal{C}$.
\end{proposition}

\begin{proof}
From Equation \ref{Trt}, the computation of $\tau_w^{t}$ is
recursive on $t$, and the algorithm works by keeping the last
computed value in a variable, which saves the time of
re-calculation. Thus, the complexity of calculating $\tau_w^{t}$
is determined by the complexity of calculating $COF_w^t$ since
$ReqF_w^t$ is constant during the period $t$. Consequently, the
result follows from Proposition \ref{Complexity-COF}. $\Box$
\end{proof}

\begin{theorem}\label{Complexity-Procedure}
The time complexity of the proposed decision mechanism is
$O(|t|.|\mathcal{C}|)$, which means linear in both the size of the
window $t$ and the size of the community $\mathcal{C}$.
\end{theorem}

\begin{proof}
The procedure mechanism is based on comparing the growth factor
$G_w^t$ with the coopetition threshold $\tau_w^t$ as shown in
Equations \ref{P} and \ref{U}. Thus, the result follows from
Propositions \ref{Complexity-Growth_Factor} and
\ref{Complexity-Threshold}. $\Box$
\end{proof}

\section{Experimental Results}\label{Experimental Results}

In this section, we provide an empirical analysis over the
theoretical results regarding the characteristics of intelligent
service agents hosted in different communities of services. In the
implemented system, we simulate the behaviors of service consumers
as request generators, service agents as service providers, and
master agents as community representatives. These entities are
developed with respect to what is explained in Section
\ref{Preliminaries}. In this section, the objective is to
investigate the effectiveness of the proposed strategic system on
intelligent services' overall budget and also the average quality
and quantity of tasks performed by the community of services,
which directly affects user satisfaction.
%Before conducting the simulation, the
%expected behavior of our model is to enhance the budget of web
%services when using our proposed strategic interacting system.
%Although this result is promising, we would like to investigate
%the effectiveness of the proposed strategic system on intelligent
%web services' overall budget compared to the best case. Moreover,
To verify these objectives, we study the overall performance of
the community hosting the reasoning-empowered services compared to
the ones hosting stochastic and purely competitive services. By
stochastic services, we mean services that adopt at each moment
competitive or cooperative strategies in an equally but random
way. By equally, we mean the choices are fairly divided between
the two strategies. The simulation application is written in
\textit{C\#} using \textit{Visual Studio}. Developed services are
initialized with values taken from a real dataset that includes
$2507$ real services functioning on the web. The dataset records
the QoS values of $9$ parameters including \textit{availability},
\textit{throughput}, and
\textit{reliability} \cite{Almasri}.  %These QoS values
%are determined by monitoring the web services over a $6$-day
%period.

We start our discussions with cumulative budget comparison
regarding different communities within which services follow
different reasoning techniques. Figure \ref{Graph1} part (a)
illustrates three graphs for three different communities. Each
community hosts services that follow different reasoning
techniques: (1) a community that follows the interactive reasoning
techniques presented in this paper (referred to as coopetitive);
(2) a community that follows a stochastic reasoning technique so
decisions about selecting competitive or cooperative strategies
are totally random (referred to as random coopetitive); and (3) a
competitive community where all services follow the competitive
strategy (referred to as competitive). The proposed model's
reasoning mechanism enables services to effectively select their
interacting strategies and the obtained budget represents the best
outcome over the strategic decision making procedure they run all
the time. This procedure avoids cases where a service selects the
competitive strategy but gets refused to obtain a task from the
master. The procedure allows services to make decisions that
maximize their utilities, so that if the service cannot compete,
the procedure would suggest to collaborate, which is better than
competing and failing to obtain the task. In this case (i.e.,
competing and not getting the task), the service stays idle but
still pays the community membership fee, which means losing
utility. The developed strategic decision making mechanism leads
some service agents to follow cooperative strategies that overall
maintain an optimal community budget. In the same figure, we
observe the cumulative budget of a community where services follow
random interacting strategies. The outcome is clearly lower
because services at each run randomly decide over their acting
strategies. This potentially influences the community budget
because a low quality service if randomly selects to follow the
competitive strategy, it will fail to perform a task with high QoS
requirements. This kind of strategy selection is totally
stochastic while the task allocation algorithm follows a logical
path. The ideal system is the one that analyzes the optimal
strategic path and consistently follows strategies that bring
maximum outcome. The result regarding the community that follows
the random strategy shows how stochastic decision making degrades
the community budget, but still this result outperforms the one of
the purely competitive community. In this purely competitive case,
all the services follow the competitive strategy and the frequency
of getting rejected from a task is relatively high. In a community
with limited number of tasks, the competitive strategy for all
services highly influences the community budget because a
potential group of services are losing at every run.

The results illustrated in Figure \ref{Graph1} part (a)  verify
the importance of the strategic decision making procedure to
logically decide over the possible competitive and cooperative
choices. Figure \ref{Graph1} part (b) illustrates communities
average reputation of involved services. The graphs represent the
influence of the rewards that the master agent uses to encourage
highly capable services to compete for a task. As for the
cumulative budget, we observe that the coopetitive community
outperforms the random coopetitive and competitive communities in
terms of average reputation. The proposed model's average
reputation increases because services follow optimal strategies
where they can perform better so obtain higher rewards. For the
same reasons as for the cumulative budget, the average reputation
of the random coopetitive community
outperforms the one of the competitive community. %The idea is to balance web
%services' strategies to maintain optimal community budget.

\begin{figure}%[h]
%\centering
%\includegraphics[scale=0.6]{graph1Final+.eps}
\includegraphics[scale=0.47]{graphbgtmed.eps}
\includegraphics[scale=0.47]{graphrep.eps}
\caption{Part (a): Cumulative community budget comparison. Part
(b): Average community reputation comparison over different
strategic decisions.} \label{Graph1}
\end{figure}

 %Figure \ref{Graph2} part (a) illustrates the reputation of the proposed $Coopetitive$ community where
 %we highlight the range of reputation change in the community. The vertical lines denote the range of %reputation that is associated with the master web service. The rewards and penalties applied to %different
% web services show that the master web service over runs extends the reputation range and takes %control of the whole community. In the developed model, web services are encouraged to choose
 %optimal strategies. This is maintained over growth factor comparison of the $Coopetitive$ web %services.

\begin{figure}[h]
\centering
\includegraphics[scale=0.458]{graphbgtmed3set.eps}
\includegraphics[scale=0.458]{graphbgthigh.eps}
\includegraphics[scale=0.5]{graphbgtveryhigh.eps}
\caption{High membership fees or less task income impacts on
different selection strategies. Part (a) Medium membership fee.
Part (b) High membership fee. Part (c) Very high membership fee.}
\label{membership_fee_graph}
\end{figure}

In Figure \ref{membership_fee_graph}, we analyze the scenario
where the membership fee is high, which is analogous to situations
where the task income is low. We need to verify how well services
can perform in these situations. Figure \ref{membership_fee_graph}
part (a) depicts the results in a normal scenario. In part (b), we
have increased the membership fee to the high amount of 5 units
per run. Services will need to pay $5$ units on each iteration of
tasks being offered. As results, the strategic coopetitive
decision making process helps services make benefits, but
stochastic and compete methods lead to lose income since making
mistakes and trying to compete for jobs the services cannot afford
while having to pay higher membership fees is making them lose
budget in a faster pace. In part (c), the membership fee is higher
than an average income that
a task can generate. %It might not be rational for selfish
%self-interest web services to stay in these communities from the
%utility perspective, but as mentioned there might be other
%political reasons they might need to stay in these communities. As
The simulation shows that the stochastic and compete strategies
make services budget decreases drastically. However, our strategic
coopetitive decision making process loses budget in a slower pace.

In Figure \ref{Graph2} parts (a) and (b), we observe the
competitive and cooperative probability of four different services
where two of them ($w_1$ and $w_3$) are following optimal
strategies as suggested by our model (competitive for $w_1$ and
cooperative for $w_3$) and the two others ($w_2$ and $w_4$) are
following non-optimal strategies, which are the opposite of what
our model suggests. Over elapsing runs, services that follow
optimal strategies bring best reputation. In fact, the master
agent rewards the high quality service that chooses the
competitive strategy, cooperates with other peers and successfully
accomplishes the task. In this system, the reputation regarding
such a service is increasing over time and the possibility of
allocating further tasks is increasing as well. By increasing the
growth factor, such a service (here shown as $w_1$) increases the
probability of selecting the competitive strategy. On the other
hand, the other service (here shown as $w_2$) that is incapable of
competing is penalized by the master agent because the offered
quality might not meet the required task quality. Thus, $w_2$
degrades its growth factor by following the competitive strategy.
As intelligent entity, this service is encouraged to change its
strategy to the cooperative one and thus, its probability of
selecting the competitive strategy is decreasing over time. We
have similar results in Figure \ref{Graph2} part (b) regarding
services $w_3$ and $w_4$ where unlike $w_4$, $w_3$ is
strategically following the cooperative strategy allowing for an
increase in the
overall reputation. %Therefore, $w_4$ is more seeking the
%competitive strategy where it can increase its growth factor.

\begin{figure}[h]
%\centering
\includegraphics[scale=0.47]{graphcomp.eps}
\includegraphics[scale=0.47]{graphcoop.eps}
\caption{Reputation progress of four different services: W$_1$ and
W$_3$ are following our strategic decision model; W$_2$ and W$_4$
are following the opposite.} \label{Graph2}
\end{figure}

In our model, services are managed by selfish agents in the sense
they try to maximize their own utilities. We analyze how their
strategies affect the social welfare, and from user's and
community's point of view how good the tasks are being performed.
This directly impacts user's satisfaction and community's
reputation in general. The Higher quality and quantity of tasks
performed leads to higher user's satisfaction for the community
which results in better reputation for the community. The results
in Figure \ref{graph_task} show the quality and quantity of tasks
being done successfully in three communities adopting the three
different aforementioned strategy decision algorithms. Part (a)
depicts the number of tasks successfully done. When services are
not capable of performing tasks alone and decide to compete for
tasks with high QoS requirements, they usually fail to perform the
task. However, if they opt for cooperating although they have less
income, they have higher chance of performing tasks
collaboratively with other services. Figure \ref{graph_task}, Part
(b) shows the probability of successfully performing tasks, which
influences users' satisfaction. The results show that services
using our coopetitive strategy when deciding whether to compete or
cooperate have higher chance to get high satisfaction ratio
compared to stochastic and compete strategies. The quality of
tasks performed are depicted in Figure \ref{graph_task} Part (c).
The figure shows the average QoS of tasks successfully
performed. %Collaborating increases the performed QoS of tasks,
%therefore forming collaborative groups improves user satisfaction.
As clearly confirmed by the simulation, the coopetitive community
outperforms the stochastic and compete communities.

\begin{figure}[h]
\centering
\includegraphics[scale=0.458]{graphtaskdone.eps}
\includegraphics[scale=0.458]{graphtasksatisfaction.eps}
\includegraphics[scale=0.5]{graphavgqostask.eps}
\caption{Overall performance from community's point of view. Part
(a) Total number of tasks successfully done. Part (b) Ratio of
tasks satisfied with required QoS. Part (c) Average QoS of
performed tasks.} \label{graph_task}
\end{figure}

We conclude our analysis by discussing how effective our
coopetitive decision making model is by comparing the final
utility (in terms of income) of services following our model with
other services deviating from that coopetitive model. In Figure
\ref{graph_dev} Part (a), we made the services deviate from the
suggested strategy. As the simulation shows, the more services
deviate from our coopetitive strategy the more they make less
benefits. In Part (b), we pick one random service and simulate the
scenario with its default coopetitive strategy and then we redo
the simulation with exactly the same environment parameters while
gradually alternating the decisions. By alternating we mean
adapting the opposite of what our model does suggest. Thus, if the
coopetitive model suggests to compete, the service agent will
cooperate and vice versa. We run this scenario 50 times and at the
end we check the service's budget and see if it gains more by
deviating or not. We did this for one single deviation (i.e.,
alternating only one decision) to 10 different deviations
(alternating 10 different decisions) during the 50 times run. As
the results show, deviating from the coopetitive strategy yields
less income for the service.

\begin{figure}%[h]
%\centering
\includegraphics[scale=0.47]{graphdev.eps}
\includegraphics[scale=0.47]{graphdev2.eps}
\caption{Utility loss while deviating from our coopetitive
decision process. Part (a) Overall budget when deviating from our
model in 0, 10, 20, 30, 40, and 50 percent of decisions. Part (b)
Ratio of getting earning utility (budget) when deviating from our
coopetitive strategy in 1 to 10 decisions.} \label{graph_dev}
\end{figure}

%We conclude our analysis by discussion over the plots in Figure
%\ref{Graph3}. In this Figure, there are 6 plots that vertically
%refer to a scenario where we change some initialized settings. The
%upper plots represent the percentage of the correct strategy
%selections where is increasing in all scenarios but with different
%slopes. The lower plots illustrate the instant threshold together
%with the instant growth factor of a particular web service that
%follows the coopetitive strategy.

\section{Related Work}\label{Related Work}

At the best of our knowledge, there is no work in the literature
of service and agent computing addressing the issue of coopetition
strategies and when to cooperate or to compete. However, some
relevant proposals to the model presented in this paper are the
ones that address service selection and task allocation
mechanisms. In many frameworks proposed in the literature, service
selection and task allocation are regulated based on the
reputation parameter \cite{Bentahar,Rosario,Ruth,Yahyaoui}. In
\cite{Huang}, the authors propose a framework to match potential
benefits of services while cooperating with one another. The
interesting idea is to consider the benefits under four
categories: innovation and learning, internal business process,
customer, and financial benefits. In \cite{Alchieri}, the authors
present a dependable framework for cooperative service agents that
is based on the tuple space coordination model. The
intrusion-tolerant perspective is emphasized in this paper where
several security mechanisms are developed to enable a reliable
coordination system. %In \cite{Maximilien2}, authors propose
%ontology for quality of service. Users compute the web services'
%reputation using ratings.
The proposed frameworks mostly aim to facilitate the coordination
mechanism between services. However, the opposite strategy of
competing is not analyzed where services might be more successful
when competing within the same group. In fact, services are not
always willing to cooperate even if they have some common goals,
particularly when they operate within groups such as communities.
In such a context, service agents can follow different interacting
strategies and have to decide when to compete and when to
cooperate so that their ultimate goal, maximizing their incomes,
can be better achieved. In our framework, we analyze those
different strategies to help services in their decision making
process when these
agents function within communities. %We summarize most of
%these proposals and concentrate on strategic decision making
%system that ranks web services in the community and analyze their
%effective interacting strategies to accomplish continuous
%requested tasks.
We enable service agents to reasonably evaluate and decide over
their coopetition strategies, which means deciding when to compete
and when to cooperate.

Furthermore, there are a number of related proposals that take
into account the correlation between (web) services and the ways
these services coordinate their actions to accomplish the required
tasks. In \cite{Jurca,Jurca2,Malik,Maximilien1,Yahyaoui}, the
authors propose to rank services based on their reputation in the
system and to use this ranking as a means to facilitate
cooperation of services. In those models, services rely on one
another on the basis of the reputation ranking system, using,
among other parameters, the QoS \cite{Qian-Tao-2012}. There are
other models that facilitate cooperation mechanisms among services
using various techniques. Examples of those techniques include 1)
coordination between two types of behaviors associated with
component services: operational and control behaviors
\cite{Yahyaoui3}; 2) Services-based workflows \cite{Wu-2011}; 3)
transaction-based approaches \cite{Gao,Rosario}; 4) agent
coordination mechanisms \cite{Charif,Gutierrez-Garcia-2013}; 5)
logical techniques \cite{Okutan,Tang}; and 6) community models,
which are virtual structures that aim at increasing the visibility
of services and facilitating their discovery and composition by
hosting and gathering services having similar or complementary
functionalities but different QoS parameters
\cite{Khosravifar2010}. %There are also some frameworks
%\cite{Ferguson,Ferguson2} that consider game-theoretic analysis on
%the expected payoffs obtained via different acting strategies.
However, deciding about which strategy to choose when services are
competing but still need to cooperate to accomplish complex tasks
has not been addressed and kept as open issue in all these
proposals as faithfully argued in
\cite{Maamar2011,Khosravifar-ICSOC2012}.

\section{Conclusion}\label{Conclusion}

The contribution of this paper is the proposition of a coopetitive
strategic model to analyze the interacting behavior of intelligent
services that are active within communities. We considered two
acting strategies where service agents expect different sort of
payoffs: (1) competitive strategy where the service claims that it
can accomplish a task, and therefore can take the responsibility
over the service consumer satisfaction; and (2) cooperative
strategy where the service does not take the responsibility to
accomplish the task and only cooperates with competitive peers.
Our proposed model advances the state-of-the-art in cooperative
systems by enabling intelligent agent-based services to
effectively choose their interacting strategies that lead to
optimal outcomes. The proposed framework provides a reasoning
technique that service agents can use to increase their overall
obtained utilities. The theoretical results presented in this
paper are also backed by simulation results using a real services
dataset. Those results showed that our model outperforms existing
competitive and random coopetitive strategies and the more
services deviate from the coopetitive strategy suggested by our
decision-making mechanism the more they make less benefits. Thus,
deviating from our coopetitive strategy yields less income for the
service.

As future work, we plan to emphasize the service consumer role in
the proposed model to obtain more accurate results when consumers
post their service satisfaction feedback. Moreover, we would like
to enhance  the reasoning technique's features to cope with
different unexpected scenarios. We also need to expand the work to
enable services to choose their collaboration networks.

\begin{comment}

\section{Related Work}

In many frameworks proposed in the literature, service selection
and task allocation are regulated based on the reputation
parameter \cite{Jurca1,Jurca2}. In \cite{Ali}, the proposed
framework regulates the service selection based on the trust
policies expressed by the service users. The frameworks proposed
in \cite{Maximilien1,Yahyaoui} address effective reputation
mechanisms for web services using ontology and game theory. All
these models address the reputation in environments where web
services function alone. In such models, web service efficiency is
not addressed and in general, balancing the market share with the
capacity is not considered as an issue for web service besides his
reputation.

There have been few proposals addressing the communities of web
service. The objective is to facilitate and improve the process of
web service selection and effectively regulate he process of
request and task allocation \cite{Jacyno}. In \cite{Khosravifar2},
authors propose a reputation-based architecture for communities
and investigate the collusion scenarios that might falsely
increase communities' reputation in the network. In
\cite{Bentahar,Khosravifar1}, the authors mainly address the
overall assessed reputation that is used as a main reason for
service selection. The authors do not consider truth/lie telling
analysis as a factor that impacts service selection in future.

The contribution of this paper is the proposition of a coopetitive
strategic model to analyze the interacting behavior of intelligent
web services that are active in communities of web services. The
proposed framework provides a reasoning technique that web
services can use to increase their overall obtained utilities. The
result of our proposed model is a probability distribution where
an intelligent web service can use over different interacting
strategies.

Our model has the advantage of being simple and  straightforward
in the contribution and the provided results. We considered two
acting strategies where web services expect different sort of
payoffs:  (1) $Competitive$ strategy where the web services claims
that it can accomplish a task and therefore, takes the
responsibility over the service consumer satisfaction; and (2)
$Cooperative$ strategy where the web service does not take the
responsibility to accomplish a task and only cooperates with other
$Competitive$ web services. As future work, we plan to emphasize
the service consumer role in the proposed model to obtain more
accurate results when consumer posts service satisfaction
feedback. Moreover, we would like to enhance  the reasoning
technique's features to cope with different unexpected scenarios.
We also need to expand the simulated environment to study
different scenarios in a number of perspectives.

\section{Conclusion}\label{Conclusion}
The contribution of this paper is the proposition of a
game-theoretic based model to analyze the best efficiency
characteristics for the active services in open networks. The
proposed framework considers the chances of web services in
joining a community in different cases with truthful and lying
information service agents. The proposed game analyzes the
existing Nash equilibrium and situations where the maximum payoff
is obtained.

Our model has the advantage of being simple and taking into
account three important factors: (1) rational services seek better
status in the environment by joining the community; (2) rational
information service agents obtain higher payoff by truth telling;
and (3) the community is obtaining more effective web services
while the information service agents challenge for providing
truthful information. As future work, we plan to consider the user
role in the game to obtain more accurate results when users act
rationally. Moreover, we would like to achieve a collusion
resistant efficiency mechanism, which is still an open problem in
open environments.

\end{comment}

\begin{thebibliography}{1}

%\small

\bibitem{Alchieri} E.A.P. Alchieri, A.N. Bessani, and J.S. Fraga.
A dependable infrastructure for cooperative web services
coordination. Proc. of the Int. Conf. on Web Services (ICWS), pp.
21--28, 2008.

\bibitem{Almasri} E. Al-Masri and Q.H. Mahmoud. Discovering the
best web service. Proc. of the 16th int. conf. on World Wide Web
(WWW), pp. 1257--1258, 2007.

\bibitem{Benatallah2003} B. Benatallah, Q.Z. Sheng, and M. Dumas.
The self-serv environment for web services composition. IEEE
Internet Computing, 7(1):40--48, 2003.

\bibitem{Bentahar} J. Bentahar, B. Khosravifar, M.A. Serhani, and M.
Alishahi. On the analysis of reputation for agent-based web
services. Expert Systems with Applications, 39(16):12438--12450,
2012.

\bibitem{Bentahar2008} J. Bentahar, Z. Maamar, W. Wan, D.
Benslimane, P. Thiran, and S. Subramanian. Agent-based communities
of web services: an argumentation-driven approach. Service
Oriented Computing and Applications 2(4):219--238, 2008.

%\bibitem{Blanco} E. Blanco, Y. Cardinale, and M.E. Vidal. Experiences
%of sampling-based approaches for estimating QoS parameters in the
%web service composition problem. International Journal of Web and
%Grid Services, 8(1):1--30, 2012.

\bibitem{Charif} Y. Charif and N. Sabouret. Dynamic service
composition enabled by introspective agent coordination.
Autonomous Agents and Multi-Agent Systems,  26(1):54--85, 2013.

\bibitem{Fouss2010} F. Fouss, Y. Achbany, and M. Saerens.
A probabilistic reputation model based on transaction ratings.
Information Sciences, 180(11):2095--2123, 2010.

%\bibitem{Derbas2005} G. Derbas, A. Kayssi, A. Chehab, H. Artail, and A.
%Tajeddine. A trust model for distributed systems based on
%reputation. International Journal of Web and Grid Services,
%1(3/4):.416--447, 2005.

\bibitem{Fudenberg1991} D. Fudenberg and J. Tirole. \emph{Game Theory}, Cambridge
MA: MIT Press, 1991.

\bibitem{Gao} L. Gao, S.D. Urban, and J. Ramachandran. A survey
of transactional issues for web service composition and recovery.
International Journal of Web and Grid Services, 7(4):331--356,
2011.

%\bibitem{Ferguson}
%C. Ferguson and C. Gawargy. U(0,1) Two-person poker models. Game
%Theory and Applications, 12:17-37, 2007.

%\bibitem{Ferguson2}
%T. Ferguson, L. Shapley, and R. WeberNotes. Notes on a stochastic
%game with information structure. Journal of Game Theory, 31:
%223-228, 2003.

\bibitem{Garcia2009} F. Garcia-Sancheza, R. Valencia-Gariaa, R.
Martinez-Bejarb, and J.T. Fernandez-Breis. An ontology,
intelligent agent-based framework for the provision of semantic
web services. Expert Systems with Applications, 36(2):3167--3187,
2009.

\bibitem{Huang} C.D. Huang and Q. Hu.  Integrating web services
with competitive strategies: The balanced scored approach.
Communications of the Association for Information Systems,
13(1):57--80, 2004.

%\bibitem{Hwang2007} S-Y. Hwang, H. Wang, J. Tang, and J.
%Srivastava. A probabilistic approach to modeling and estimating
%the QoS of web-services-based workflows. Information Sciences,
%177(23):5484--5503, 2007.

\bibitem{Jacyno} M. Jacyno, S. Bullock, M. Luck, and T.R. Payne.
Emergent service provisioning and demand estimation through
self-organizing agent communities. Proc. of the 8'th Int. Conf. on
Autonomous Agents and Multi-Agent Systems (AAMAS), pp. 481--488,
2009.

\bibitem{Jurca} R. Jurca and B. Faltings. Obtaining reliable
feedback for sanctioning reputation mechanisms. Journal of
Artificial Intelligence Research, 29:391--419, 2007.

\bibitem{Jurca2} R. Jurca and B. Faltings. Reputation-based
service level agreements for web services. Proc. of the Int. Conf.
on Service Oriented Computing (ICSOC), Lecture Notes in CS, Volume
3826, pp. 396--409, 2005.

\bibitem{Khosravifar2} B. Khosravifar, J. Bentahar, K. Clacens,
C. Goffart, and P. Thiran. Game-theoretic analysis of a web
services Collaborative mechanism. Proc. of the Int. Conf. on
Service Oriented Computing (ICSOC), pp. 549--556, 2011.

\bibitem{Khosravifar-ICWS2010} B. Khosravifar, J. Bentahar, and A. Moazin.
Analyzing the relationships between some parameters of web
services reputation. Proc. of the 8th IEEE Int. Conf. on Web
Services (ICWS), pp. 329--336, 2010.

\bibitem{Khosravifar2010} B. Khosravifar, J. Bentahar, A. Moazin,
and P. Thiran. Analyzing communities of web services using
incentives. Journal of Web Services Research, 7(3):30--51, 2010.

\bibitem{Khosravifar1} B. Khosravifar, J. Bentahar, A. Moazin,
and P. Thiran. On the reputation of agent-based web services.
Proc. of the 24'th Int. Conf. on Artificial Intelligence (AAAI),
pp. 1352--1357, 2010.

\bibitem{Khosravifar-ICSOC2012} B. Khosravifar, M. Alishahi, E. Khosrowshahi Asl, J. Bentahar, R.
Mizouni, and H. Otrok. Analyzing Coopetition Strategies of
Services within Communities. Proc. of the Int. Conf. on Service
Oriented Computing (ICSOC), pp. 656--663, 2012.

%\bibitem{Li2010} J. Li, J. Huai, C. Hu, and Y. Zhu. A secure collaboration service for
%dynamic virtual organizations. Information Sciences,
%180(17):3086-–3107, 2010.

\bibitem{Lim} E. Lim, P. Thiran, Z. Maamar, and J. Bentahar. On
the analysis of satisfaction for web services selection. Proc. of
the 9th Int. Conf. on Services Computing (SCC), 2012.

\bibitem{Lomusio2012} A. Lomuscio, H. Qu, and M. Solanki. Towards
verifying contract regulated service composition. Autonomous
Agents and Multi-Agent Systems, 24(3):345--373, 2012.

\bibitem{Maamar2011} Z. Maamar, P. Thiran, and J. Bentahar. Web
services communities: from intra-community coopetition to
inter-community competition. In E-Business Application for Product
Development and Competitive Growth: Emerging Technologies, pp.
333--343, IGI Global, 2011.

\bibitem{Maamar2005} Z. Maamar, S. Moustefaoui, and H. Yahyaoui.
Towards an agent-based and context-oriented approach for web
services composition. IEEE Transactions on Knowledge and Data
Engineering, 17(5):686--697, 2005.

\bibitem{Maamar2009} Z. Maamar, S. Subramanian, P. Thiran, D. Benslimane,
and J. Bentahar. An approach to engineer communities of web
services: concepts, architecture, operation, and deployment.
International Journal of E-Business Research, 5(4):1--21, 2009.

\bibitem{Malik} Z. Malik and A. Bouguettaya. Evaluating rater
credibility for reputation assessment of web services. Proc. of
the 8'th Int. Conf. on Web Information Systems Engineering (WISE),
pp. 38--49, 2007.

\bibitem{Massey1996}  W.A. Massey, G.A. Parker, W. Whitt.
Estimating the parameters of a nonhomogeneous Poisson process with
linear rate. Telecommunication Systems, 5(2):361--388, 1996.

\bibitem{Maximilien1} E.M. Maximilien, and M.P. Singh. Reputation
and endorsement for web services, ACM SIGEcom Exchanges,
3(1):24--31, 2002.

\bibitem{Medjahed2007} B. Medjahed and Y. Atif. Context-based matching for web
service composition. Distributed and Parallel Databases,
21(1):5--37, 2007.

\bibitem{Medjahed2005} B. Medjahed and A. Bouguettaya. A dynamic foundational
architecture for semantic web services. Distributed and Parallel
Databases, 17(2):179--206, 2005.

\bibitem{Mhamdi2012} M.A. M'hamdi and J. Bentahar. Scheduling
reputation maintenance in agent-based communities using game
theory. Journal of Software 7(7):1514--1523, 2012.

\bibitem{Gutierrez-Garcia-2013} J. O. Gutierrez-Garcia, and K. M. Sim.
Agent-based cloud service composition. Applied Intelligence,
38(3):436--464, 2013.

\bibitem{Okutan}
C. Okutan and N.K. Cicekli. A monolithic approach to automated
composition of semantic web services with the Event Calculus.
Knowledge-Based Systems, 23(5):440--454, 2010.

%\bibitem{Kirci2010} E.K. Ozorhan, E.K. Kuban, and N.K. Cicekli.
%Automated composition of web services with the abductive event
%calculus. Information Sciences, 180(19):3589--3613, 2010.

%\bibitem{Park} S.Y. Park, S. Han, and H.Y Youn. Efficient message
%transport interface between agent framework and event service.
%International Journal of Web and Grid Services, 2(3):331--352,
%2006.

\bibitem{Paschke2011} A. Paschke and H. Boley. Rule responder:
Rule-based agents for the semantic-pragmatic web. J. Artif.
Intell. Tools, 20(6):1043--1081, 2011.

\bibitem{Pradhan} S. Pradhan and H. Lu. Business transaction
coordination in multi-agent financial web services. International
Journal of Web and Grid Services, 3(1):38--57, 2007.

%\bibitem{Rahwan}
%T. Rahwan, T. Michalak, E. Elkind, P. Faliszewski, J. Sroka, M.
%Wooldridge, and N. Jennings. Constrained coalition formation.
%Proc. of The 25'th Int. Conf. on Artificial Intelligence (AAAI),
%pp. 719-725, 2011.

\bibitem{Rosario} S. Rosario, A. Benveniste, S. Haar, and C.
Jard. Probabilistic QoS and soft contracts for transaction based
web services. Proc. of the Int. Conf. on Web Services (ICWS), pp.
126--133, 2007.

\bibitem{Ruggeri2005} F. Ruggeri and S. Sivaganesan. On modeling change points in
non-homogeneous Poisson processes. Statistical Inference for
Stochastic Processes 8(3):311--329, 2005.

\bibitem{Ruth} M. Ruth and  T. Shengru. Concurrency issues in
automating RTS for web services. Proc. of the Int. Conf. on Web
Services (ICWS), pp. 1142--1143, 2007.

\bibitem{Sanchez2011} V. Sanchez-Anguix, S. Valero, and A. Garcia-Fornes,
A genetic Approach for long term virtual organization distribut.
Int. J. Artif. Intell. Tools, 20(2):271--295, 2011.

\bibitem{Tang} X. Tang, C. Jiang, and M. Zhou. Automatic web
service composition based on Horn clauses and Petri nets. Expert
Systems with Applications, 38(10):13024--13031, 2011.

\bibitem{Qian-Tao-2012} Q. Tao, H. Chang, C. Gu, and Y. Yi.
A novel prediction approach for trustworthy QoS of web services.
Expert Systems with Applications, 39(3):3676--3681, 2012.

\bibitem{Wu-2011} Shiow-yang Wu, Kuo-Chang Lin.
Structured design, consistency analysis and failure reasoning of
business workflows with activity-control templates and causal
ordering. Expert Systems with Applications, 38(7):8000--8013,
2011.

\bibitem{Yahyaoui} H. Yahyaoui. A trust-based game theoretical
model for web services collaboration. Knowledge-Based Systems,
27:162--169, 2012.

\bibitem{Yahyaoui2} H. Yahyaoui and S. Zhioua. Bootstrapping trust of web services
through behavior observation. Proc. of the Int. Conf. on Web
Engineering (ICWE), pp. 319--330, 2011.

\bibitem{Yahyaoui3} H. Yahyaoui, Z. Maamar, and K. Boukadi. A framework to coordinate
web services in composition scenarios. International Journal of
Web and Grid Services, 6(2):95--123, 2010.

%\bibitem{Yassine} A. Yassine, A.A. Shirehjini, S. Shirmohammadi,
%and T. Tran. Knowledge-empowered agent information system for
%privecy payoff in ecommerce. Knowledge and Information Systems,
%DOI: 10.1007/s10115-011-0415-3, 2011.

\end{thebibliography}

\end{document}

### 2014-01-31 papers/Exp Sys App/matlab-charts/avg_bud_medfee.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('avg_bud_medfee.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|:')
+
+i=0:49;
+t=v(:,9);y=v(:,10);z=v(:,11);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',7000:2000:18000);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+%axis([0 50 7000 18000]);
+
+% Add legend
+hleg1 = legend('Coopetitive','Competitive','Random Coopetitive');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.27,.7,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',11);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
+xlabel({'Number of Runs';'(a)'}, 'FontSize',14);
+ylabel('Budget', 'FontSize',14);
+
+%Caxes = copyobj(gca,gcf);
[…]

### 2014-01-31 papers/Exp Sys App/matlab-charts/decision_dev.m

@@ -1,0 +1,57 @@
+[v,T,vT]=xlsread('decision_dev.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|+-|.|:')
+
+i=0:49;
+t=v(:,1);y=v(:,2);z=v(:,3);tt=v(:,4);yy=v(:,5);zz=v(:,6);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,i,tt,i,yy,i,zz,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',7000:2000:18000);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 50 7000 18000]);
+
+% Add legend
+hleg1 = legend('0% Deviation','10% Deviation','20% Deviation','30% Deviation','40% Deviation','50% Deviation');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.24,.63,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
[…]

### 2014-01-31 papers/coop-journal-R1/coop_response_letter.tex
changes

--- 2014-01-31 papers/Exp Sys App/coop_response_letter.tex
@@
 \vspace{0.2cm}\textbf{\underline{Answer 1}: Thanks for the
-comment. We made the abstract shorter and added the information about our decision making process which based on game-theoretic best response technique in the abstract.}
+comment. We made the abstract shorter and added the information about our decision making process which is based on ``game-theoretic best response technique'' to the abstract.}
 
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 2}: We added a short summary about the system parameters in section 2.2.
-We have five system parameters and the other variables are derived or calculated based on these five parameters which are listed in Table 1.
+\vspace{0.2cm}\textbf{\underline{Answer 2}: In the revised version, we added a short summary about the system parameters in section 2.2.
+We have five system parameters \emph{Task QoS}, \emph{Service QoS}, \emph{Budget}, \emph{Reputation} and \emph{Growth Factor}) and the other variables are derived or calculated based on these five parameters which are listed in Table 1.
 The title for Table 1.
-which was ``List of proposed system parameters'' was not very appropriate and we apologize for the confusion that it has caused.
+which was ``List of proposed system parameters'' was not very appropriate.
 We changed its title to ``List of abbreviations''}
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 3}: In the revised
-version, all the needed concepts are defined. Grand coalition is
-defined as follows: In cooperative game theory, grand coalition is
-a coalition that contains a maximum number of players as long as
-they can maintain a stable (in terms of membership) and beneficial
-(in terms of utility) group for all the players (Section 4.1,
-paragraph 3).}
+\vspace{0.2cm}\textbf{\underline{Answer 3}: We edited the text in the revised version.}
 
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 4}: The main objective of
-this work is to optimize the gain of web service communities as a
-whole and to ensure the creation of stable communities in terms of
-joining and leaving activities.}
+\vspace{0.2cm}\textbf{\underline{Answer 4}: We agree.
+In the revised manuscript, we added more explanations and details about the architecture and service types.
+Each web service was modeled based on a class and we initiated many threads on a single process for the web services.
+They used abstract XML based messaging system with request parameters and a list of abstract XML based responses.
+Based on community task queue delay and the assigned web service quality metrics (such as reliability, throughput, latency and other metrics) these tasks will be performed with different qualities.
+In the experimental results and analysis section (Section 4), we have illustrated and
+evaluated the average QoS of tasks performed. In the revised manuscript, we added more explanations and details about the architecture and service types.
+}
 
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 5}: The interruption we
-are mentioning can be either caused by time/memory constraints
-when the number of subsets is big enough (timeout) or forced
-manually by the system designer if for example the already
-obtained results are satisfactory. In fact, if the algorithm gets
-interrupted while verifying $depth(n)$, it will have $depth(n-1)$
-already verified. Each depth will have $O(n^2)$ cases to check, so
-for example if it reaches depth 10, and the algorithm gets
-interrupted (manually or because of system resources), we at least
-have checked for all the subsets of depth 9. Clarification has
-been added in the revised manuscript at Section 4.1, last
-paragraph.}
+\vspace{0.2cm}\textbf{\underline{Answer 5}: Thanks for noticing the mistake, we replaced the Figure at the correct position (we put it after the paragraph it was first mentioned on) and double checked all other figures and tables placements.}
 
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 6}: Tha
+\vspace{0.2cm}\textbf{\underline{Answer 6}: As mentioned in our Answer 4, we checked the formatting issues of paper as much as we could and we believe other formatting details will be covered the journal editors.
 }
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 1}: First}
+\vspace{0.2cm}\textbf{\underline{Answer 1}: True, as argued in our Answer 1 to Reviewer 1, We made the abstract more compact and removed some unnecessary details. }
 
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 2}: We agree, we rephrased
-the sentence as follows:  If the member $i$ is added to the set
-$S$, the contribution of this set to the coalition is $v(S \cup
-\left\{i\right\}) - v(S)$.}
+\vspace{0.2cm}\textbf{\underline{Answer 2}: We agree, the definition was too broad we rephrased
+the sentence as follows: Online Services are software systems providing a standard way of
+interoperability among different applications. These services are developed
+ in an autonomous and intelligent manner to continuously and autonomously interact with each other to
+fulfill users' requests.}
+
 \vspace{0.5cm} \textbf{\underline{3.
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 1}: As argued in our
-Answer 2 to Reviewer 1, we are advocating the idea of community as
-a way to group web services in order to increase the total gain of
-all the members where each web service gain is more than or equal
-to what this web service would obtain being outside the community.
-This is because the community can provide wider visibility, better
-market share, higher reputation, and better way of sharing
-resources. Community for us is an infrastructure and being part of
-it should benefit the web service, but also the community as a
-whole. As argued in [Maamar et al., 2011]\footnote{Z. Maamar, P.
-Thiran, and J. Bentahar (2011). Web services communities: from
-intra-community Coopetition to inter-community Competition. In
-E-Business Application for Product Development and Competitive
-Growth: Emerging Technologies, In Lee editor, pp. 333-343, IGI
-Global.}, inside a community, web services can either compete or
-cooperate. In this paper, we stress the intra-community
-cooperation between web services for a better inter-community
-competition. The main idea is that to form a stable web service
-community and to have fair distribution of the total gain based on
-the contribution of each individual, cooperative game theory,
-particularly coalition game theory, is very suitable to formalize
-such a problem. Cooperation between competitors is a well
-established practice in economical theories (see for instance
-[Chetty and Wilson 2003]\footnote{S. K. Chetty and H. I. M. Wilson
-(2003). Collaborating with competitors to acquire resources.
-International Business Review, vol. 12. pp. 61-81.} and [Bucklin
-and Sengupta 1993]\footnote{L. P. Bucklin and S. Sengupta (1993).
-Organizing successful co-marketing alliances. Journal of
-Marketing. vol. 57, pp. 32-46.}). This happens in real business
-world scenarios. As an example, let us consider major carrier
-airlines providing ticket selling services. Those airlines can be
-seen as competing agents, each one tries to maximize its utility
-by gaining more market share. However, nowadays those companies
-are usually part of different coalitions (alliances) such as Star
-Alliance\footnote{\url{www.staralliance.com}} (28 airline members
-including Scandinavian Airlines, Thai Airways International, Air
-Canada, Lufthansa, and United Airlines),
-SkyTeam\footnote{\url{www.skyteam.com}} (19 members, among them
-Aerom\'{e}xico, Air France, Delta Air Lines, Continental Airlines,
-KLM, and Northwest Airlines), and Oneworld\footnote{\url{
-www.oneworld.com}} (13 members including Air Berlin, American
-Airlines, British Airways, Cathay Pacific, Iberia, Japan Airlines,
-Malaysia Airlines, and Qatar Airways). By sharing resources and
-market share and having the option of service multi-hop air
-tickets combined from different airlines, each airline member of a
-coalition can increase its gain by collaborating. The question is
-when this collaboration would be beneficial for all the agents
-involved? For example the three alliances would not gain anything
-by collaborating and sharing resources with airlines of low
-reputation and quality. They will lose their market and would
-rather stay away from this collaboration. Therefore, no stable
-community can be formed between well established and poor
-airlines. Another example of cooperation among competitors is the
-arrangement between PSA Peugeot Citro\"{e}n and Toyota to create
-Toyota Peugeot Citro\"{e}n Automobile
-(TPCA)\footnote{\url{www.tpca.cz/en/}} in order to share
-components for a new city car where the different companies save
-money on shared costs while remaining competitive in other areas.
-Our solution of cooperation between competitor web services within
-coalitions follows these models. We updated the paper to reflect
-this important discussion by adding a new part, called
-motivations, to the introduction (Section 1).}
-
 \end{document}

### 2014-01-31 papers/coop-journal-R1/BNJ Exp Sys App.tex
changes

--- 2014-01-31 papers/Exp Sys App/BNJ Exp Sys App.tex
@@
 \section{Introduction}\label{Introduction}
-Services are software systems providing a standard way of
-interoperability among different applications. They are developed
-to continuously and autonomously interact with each other to
-fulfill users' requests. Organizing services within virtual
+\textbf {Online Services are software systems providing a standard way of
+interoperability among different applications. These services are developed
+ in an autonomous and intelligent manner to continuously and autonomously interact with each other to
+fulfill users' requests.} Organizing services within virtual
 structures called \emph{communities} has been proposed for the
@@
 In this part, we demonstrate the involved parameters and their
-corresponding formulations and explanations. \textbf{}
+corresponding formulations and explanations.
+\textbf{Our proposed decision making process, utilizes five system parameters namely \emph{Task QoS}, \emph{Service QoS}, \emph{Budget}, \emph{Reputation} and \emph{Growth Factor}.
+In the following, we describe these parameters in more detail.
+}
 
@@
 way. By equally, we mean the choices are fairly divided between
-the two strategies. The simulation application is written in
-\textit{C\#} using \textit{Visual Studio}. Developed services are
+the two strategies. 
+\textbf{The simulation application is written in
+\textit{C\#} using \textit{Visual Studio} and executed the implementation on an Intel Xeon X3450 machine with 6GBs of memory.}
+ Developed services are
 initialized with values taken from a real dataset that includes

### 2014-02-01 papers/coop-journal-R1/coop_response_letter.tex
changes

@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 3}: In the previous
-version, the tasks were abstract. In the revised version, the
-tasks are real tasks about flight booking that need to be.}
+\vspace{0.2cm}\textbf{\underline{Answer 3}: In the revised manuscript, page 21 we added more description about their framework.
+Here is the quick summary of their definitions as we added to paper: \emph{Innovation and learning perspective} focuses on the knowledge, skills, and systems needed to improve the business continually.
+Necessary factors to build strategic capabilities and efficiency in addressed in internal business process.
+Values that customers seek are considered in \emph{customer perspective} and financial performance to maximize the shareholder value are analyzed in \emph{financial perspective}.
+Their goal is to design the framework for cooperating web services, inline with business strategy of firms in IT industry.}
 
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 4}: We mean deviating from
-the coalition. This has been fixed in the revised version.}
+\vspace{0.2cm}\textbf{\underline{Answer 4}: Thanks for your comment.
+As mentioned in the manuscript, this is something we are considering as our furutre work.
+A case study in which we can collect user feedback, and adding it as a system parameter in our algorithm can improve our decision making process from users perspective which will lead to more efficiency, payoff and income for our web services}
 

### 2014-02-01 papers/coop-journal-R1/BNJ Exp Sys App.tex
changes

@@
 selection and task allocation are regulated based on the
-reputation parameter \cite{Bentahar,Rosario,Ruth,Yahyaoui}. In
-\cite{Huang}, the authors propose a framework to match potential
+reputation parameter \cite{Bentahar,Rosario,Ruth,Yahyaoui}. 
+\textbf{In \cite{Huang}, the authors propose a framework to match potential
 benefits of services while cooperating with one another. The
@@
 categories: innovation and learning, internal business process,
-customer, and financial benefits. In \cite{Alchieri}, the authors
+customer, and financial benefits. 
+\emph{Innovation and learning perspective} focuses on the knowledge, skills, and systems needed to improve the business continually.
+Necessary factors to build strategic capabilities and efficiency in addressed in internal business process.
+Values that customers seek are considered in \emph{customer perspective} and financial performance to maximize the shareholder value are analyzed in \emph{financial perspective}.
+Their goal is to design the framework for cooperating web services, inline with business strategy of firms in IT industry.}
+In \cite{Alchieri}, the authors
 present a dependable framework for cooperative service agents that

### 2014-02-23 papers/coop-journal-R1/coop_response_letter.tex
changes

@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 3}: We edited the text in the revised version.}
+\vspace{0.2cm}\textbf{\underline{Answer 3}: We edited the text in the revised version and made some paragraphs shorter to improve readability of paper.}
 
@@
 In the revised manuscript, we added more explanations and details about the architecture and service types.
-Each web service was modeled based on a class and we initiated many threads on a single process for the web services.
-They used abstract XML based messaging system with request parameters and a list of abstract XML based responses.
-Based on community task queue delay and the assigned web service quality metrics (such as reliability, throughput, latency and other metrics) these tasks will be performed with different qualities.
-In the experimental results and analysis section (Section 4), we have illustrated and
-evaluated the average QoS of tasks performed. In the revised manuscript, we added more explanations and details about the architecture and service types.
+Web services were modeled as a \emph{class} and using \emph{Await} and \emph{Async} models we initiated many web services, each running as a thread.
+We implemented XML based messaging system (like SOAP) with request parameters and a list of XML based responses.
+The request
+contains the flight dates, the origin and destination, type of tickets, and number of guests.
+The response contains different flights with different companies, prices, timing, etc.
+We have gathered around 200,000 flights and stored them in our MongoDB database.
+A pool of web services was initiated and had their \emph{QoS} parameters populated based on the dataset of 2,507 real services functioning on the web.
 }
@@
 
-\vspace{0.2cm}\textbf{\underline{Answer 5}: Thanks for noticing the mistake, we replaced the Figure at the correct position (we put it after the paragraph it was first mentioned on) and double checked all other figures and tables placements.}
+\vspace{0.2cm}\textbf{\underline{Answer 5}: True.
+In the revised manuscript, we replaced the Figure at the correct position (we put it after the paragraph it was first mentioned on) and double checked all other figures and tables placements.}
 
@@
 interoperability among different applications. These services are developed
- in an autonomous and intelligent manner to continuously and autonomously interact with each other to
+ as autonomous and intelligent agents and they continuously and autonomously interact with each other to
 fulfill users' requests.}

### 2014-02-23 papers/coop-journal-R1/BNJ Exp Sys App.tex
changes

@@
 interoperability among different applications. These services are developed
- in an autonomous and intelligent manner to continuously and autonomously interact with each other to
+ as autonomous and intelligent agents and they continuously and autonomously interact with each other to
 fulfill users' requests.} Organizing services within virtual
@@
 the two strategies.
+
 \textbf{The simulation application is written in
-\textit{C\#} using \textit{Visual Studio} and executed the implementation on an Intel Xeon X3450 machine with 6GBs of memory.}
- Developed services are
-initialized with values taken from a real dataset that includes
-$2507$ real services functioning on the web. The dataset records
-the QoS values of $9$ parameters including \textit{availability},
-\textit{throughput}, and
-\textit{reliability} \cite{Almasri}.  %These QoS values
+\textit{C\#} using \textit{Visual Studio}.
+We performed the implementation on a single Intel Xeon X3450 machine with 6GBs of memory.
+Web services were modeled as a \emph{class} and using \emph{Await} and \emph{Async} models we initiated many web services, each running as a thread.
+We implemented XML based messaging system (like SOAP) with request parameters and a list of XML based responses.
+The request
+contains the flight dates, the origin and destination, type of tickets, and number of guests.
+The response contains different flights with different companies, prices, timing, etc.
+We have gathered around 200,000 flights and stored them in our MongoDB database.
+A pool of services are initialized with values taken from a real dataset that includes $2507$ real services functioning on the web.}
+The dataset records the QoS values of $9$ parameters including \textit{availability},
+\textit{throughput}, and \textit{reliability} \cite{Almasri}.  %These QoS values
 %are determined by monitoring the web services over a $6$-day

### 2014-03-02 seminar/seminar_report/chapter2.tex
changes

--- 2013-12-02 proposal/proposal/chapter2.tex
@@
 \subsection{Web Services}\label{sec:CWSWebServices}
-        Over the past years, online services have become part of standard daily life of people around the globe. Many applications these days rely on
-        web services from different providers to function. Most modern computer applications, specially
-        mobile and tablet applications which have limited storage and processing power
-        are merely just an interface aggregating different information from online service providers.
-        Examples are vast, weather forecasting, ticket selling, local maps and places search, shopping apps, almost all rely on
-        robust web service providers.
+Over the past years, online services have become part of standard
+daily life of people around the globe. Many modern applications
+rely on web services from different providers. For instance, many
+mobile and tablet applications which have limited storage and
+processing power are merely interfaces aggregating different
+information from online services. Examples are vast, weather
+forecasting, ticket selling, shopping apps, local maps and places
+searching.
 
-        The World Wide Web Consortium (W3C) defines web services as follows: "software
-        system designed to support interpretable machine-to-machine interaction over a network.
-        It has an interface described in a machine-processable format (specifically WSDL). Other
-        systems interact with the web service in a manner prescribed by its description using
-        SOAP messages, typically conveyed using HTTP with XML serialization in conjunction
-        with other Web-related standards". When developers declare a new web service, it will
-        be discovered based on its description that fully describes the service. Developers also
-        have to declare a public interface and a readable documentation to help other developers
-        when integrating different services \cite{w3cwsdl}. Nowadays Web API standards which do not
-        require XML-based web service protocols like SOAP and WSDL are also emerging. They are also called
-        REST (representational state transfer) services which are moving towards simpler communication protocols.
-        They are not restricted to XML formats, recently JSON, a human readable and simpler format is becoming popular among online service providers.
+The World Wide Web Consortium (W3C) defines web services as
+follows: ``software system designed to support interpretable
+machine-to-machine interaction over a network. It has an interface
+described in a machine-processable format (specifically WSDL).
+Other systems interact with the web service in a manner prescribed
+by its description using SOAP messages, typically conveyed using
+HTTP with XML serialization in conjunction with other Web-related
+standards''. When developers declare a new web service, it will be
+discovered based on its description that fully discloses its
+functionalities. Developers also have to declare a public
+interface and a readable documentation to help other developers
+when integrating different services \cite{w3cwsdl}. Nowadays, web
+API standards which do not require XML-based web service protocols
+like SOAP and WSDL are also emerging. They are also called REST
+(representational state transfer) services which are moving
+towards simpler communication protocols. %They are not restricted
+%to XML formats, recently JSON, a human readable and simpler format
+%is becoming popular among online service providers.
 
-        We are not going to delve into engineering details of online web service implementation and its protocols in this proposal.
-        We consider the service, web services provide as a request-response operation, where they receive a message specifying a question,
-        based on this message they generate a response, satisfying end users' need. Service providers usually charge end users for services they provide,
-        gaining profit in the process. For example Google has listed their pricing and plans for wide range of services they provide
-        on their web service console page\footnote{https://code.google.com/apis/console}.
+We are not going to delve into engineering details of online web
+service implementation and its protocols in this proposal. We are
+interested in web services from their business model perspective.
+Service providers usually charge end users for services they
+provide. For example, Google has listed their pricing and plans
+for wide range of services they provide on their web service
+console page\footnote{https://code.google.com/apis/console}.
 
-        In our research work, we abstract web services as rational entities\footnote{The term
+In our research work, we abstract web services as rational
+agents\footnote{The term
         rational is used here in the sense that web services are utility
@@
         services can join communities to have better efficiency by
-        collaborating with others, to have access to higher market share,
+        collaborating with others, to have access to broad market share,
         and to have opportunity of receiving a bigger task pool from end
-        users. Also the high reliance on web services, has increased quality expectations from end users.
-        Communities of web services can provide higher performance, reliability, fail recovery for end users.
+        users. Furthermore, the high reliance on web services has increased quality expectations from end users.
+        Communities of web services can provide higher availability, performance, reliability, and recovery for end users.
 
 \subsection{Web Service Communities}\label{sec:CWSDefinition}
-        Community in dictionary definition refers to "the condition of sharing or having certain attitudes and interests in common" or "a group of people living in the same place or having a particular characteristic in common".
-In \cite{DBLP:journals/internet/BenatallahSD03, Zeng:2003:QDW:775152.775211} introduce community of web services as collection of cooperative web services with a common service and functionality but different QoS metrics.
-Therefore $communities$ are differentiated from $composition$ type of web service cooperation in which web services with different functionalities work together to generate a new service provider with composite functionality.
+Community refers to ``the condition of sharing or having certain
+attitudes and interests in common'' or ``a group of people living
+in the same place or having a particular characteristic in
+common''\footnote{Oxford Dictionaries}. In
+\cite{DBLP:journals/internet/BenatallahSD03,
+Zeng:2003:QDW:775152.775211}, the authors introduce community of
+web services as collection of cooperative web services with common
+functionalitiers but different QoS metrics. Therefore
+$communities$ are differentiated from $composition$ types of web
+service cooperation in which web services with different
+functionalities work together to generate a new service with
+composite functionality.
 
-        Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09} proposed the an architecture
-        utilizing \emph{Contract-Net} protocol for engineering community of web services.
-        This architecture has been further developed in \cite{conf/IEEEscc/BenharrefSBB11, conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11, CSTintercommunity}.
-        Community of web services have two major roles for members of a community, the master and slave web service.
-        Master web services lead communities and are responsible for community and membership management of the community, they try to invite and and convince web services to join the
-        community. They can attract new web services to their communities by awarding them more payoff. They also can eject some web services from the community improving the
-        community and individual member satisfaction, and overall community reputation.
+Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
+then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
+proposed an architecture utilizing \emph{Contract-Net} protocol
+for engineering task distribution within communities. This
+architecture has been further developed in
+\cite{conf/IEEEscc/BenharrefSBB11, conf/IEEEscc/KhosravifarBMMT10,
+conf/aina/LimTM11, CSTintercommunity}. Two types of roles have
+been distinguished for community members: masters and slaves.
+Master web services lead communities and are responsible for
+membership management. They can invite and convince slave web
+services to join the community, and attract new slave web services
+to their communities by awarding them better payoff. Moreover,
+they can eject some slave members from the community to improve
+its overall reputation if these members are misbehaving or cannot
+provide the promised QoS \cite{DBLP:journals/ijebr/MaamarSTBB09}.
 
@@
 
-        Figure \ref{wsarch} depicts the basic architecture of communities of web services. The main components of the architecture are: 1) the providers of web services,
-        2) UDDI registries and 3) communities of web services.
-Communities abstract the same model of defining, announcing and invoking of web services.
-They also adopt the same protocols that standard web services use with UDDI registries.
-UDDI is a platform-independent XML based registry list which facilitates worldwide web service discovery.
+Figure 1 %\ref{wsarch}
+depicts the basic architecture of
+communities of web services. The main components of the
+architecture are: 1) the providers of web services; 2) UDDI
+registries; and 3) communities platform. Communities abstract the
+same model of defining, announcing and invoking web services. They
+also adopt the same protocols that standard web services use with
+UDDI registries. UDDI is a platform-independent XML based registry
+list which facilitates worldwide web service discovery.
 
-        The master web service is responsible with communication with web service providers and discovery registries. It it responsible for task distribution, web service selection,
-        community management, maintaining a healthy set of web services satisfying end users requests with high QoS. In communities, the masters web services can be
-        dedicated web services playing the master role during the entire time of being in the community. This master web service is independently developed and never
-        participates in any composition. The master web services can also be chosen out of normal web services already inside the community \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+%The master web service is responsible with communication with web
+%service providers and discovery registries. It it responsible for
+%task distribution, web service selection, community management,
+%maintaining a healthy set of web services satisfying end users
+%requests with high QoS. In communities, the masters web services
+%can be dedicated web services playing the master role during the
+%entire time of being in the community. This master web service is
+%independently developed and never participates in any
+%composition. The master web services can also be chosen out of
+%normal web services already inside the community
+%\cite{DBLP:journals/ijebr/MaamarSTBB09}.
 
-    \section{Cooperative Game Theory and Multi-agent Systems}\label{sec:CGTMS}
+\section{Cooperative Game Theory and Multi-Agent Systems}\label{sec:CGTMS}
 
@@
 where those agents can increase their payoff by binding agreements
-        and cooperating in groups. We let $N$ be a set of players which can form a group called a $coalition$. A
-        \emph{coalitional game} is a pair $G = (N, v)$, where $v$ is called
-        a \emph{characteristic function} $v: 2^N \to \mathbb{R}$, mapping the set of players of the
-        coalition to a real number $v(N)$, the worth of $N$. This number
-        usually represents the output or payoff or again the performance
-        of these players working together as coalition.  If a coalition
-        $S$ is formed, then it can divide its worth, $v(N)$ in any
-        possible way among its members. The payoff vector $x \in
+and cooperating in groups. We let $N$ be a set of players which
+can form a group called a $coalition$. A \emph{coalitional game}
+is a pair $G = (N, v)$, where $v$ is called a \emph{characteristic
+function} $v: 2^N \to \mathbb{R}$, mapping the set of players of
+the coalition to a real number $v(N)$, the worth of $N$. This
+number usually represents the output or payoff or again the
+performance of these players working together as coalition. If a
+coalition $S$ is formed, then it can divide its worth, $v(N)$ in
+any possible way among its members. The payoff vector $x \in
 \mathbb{R}^N$ is the amount of payoff being distributed among the
@@
             {\bf Definition 1 (Shapley value)} Given a cooperative game $(N,
-            v)$, the \emph{Shapley value} of player $i$ is given
-            by\cite{shapley_value}:
+            v)$, the \emph{Shapley value} of player $i$ is given by \cite{shapley_value}:
             \begin{equation}\label{eq:shapley}
@@
 
-        %\subsection{Examples on Cooperative Game Solution Concepts}\label{sec:CWSDefinition}
+        \subsection{Representation and Complexity Issues}\label{sec:CWSArchitecture}
 
-            \begin{example}\label{ex:simplecore1}
-                Consider a game $G = (N, v)$, with two players where $N = {1,2}$.
-Each of these players can produce 5 units of output working alone and by collaborating they can produce 20 units worth of output.
-Therefore we have: $v({1}) = 5, v({2}) = 5, v({1,2}) = 20$.
-The $core$ of the game, which is the set of all possible distribution of gain among players guaranteeing stability is: $core(N,v) = \{(x_1,x_2) \in R^2 | x_1 >= 5, x_2 >= 5, x_1 + x_2 = 20\}$, as illustrated in figure \ref{fig:coreex1}.
-Distributing the 20 units of income, among these two players, for all the points in the line will make outcome stable, since non of these players can gain more than 5 by working alone.
-However although they have same qualities, the core can suggest a stable outcode where one agent can earn three times more than the other agent: $\{5,15\}$.
-As mentioned in previous section, $core$ result may not be fair, the $core$ only considers stability.
-However, \emph{Shapley value} considers fairness.
-According to equation \ref{eq:shapley}, the two  workers should each share 10 units of income, since they have the same marginal contribution to all subsets of the coalition.
-As you can see the distribution vector of $\{10,10\}$ is also a member in $core$ set.
-Later we are going to show if $core$ of a coalition game is not empty, and game is convex, the shapely value lies within $core$ set.
-            \end{example}
-
-            \begin{figure}
-                \begin{center}
-                \includegraphics[width=3in]{Figures/excore.eps}\label{fig:coreex1}
-                \caption{Core of the 2-player game of example \ref{ex:simplecore1}}
-                \end{center}
-            \end{figure}
-
-            \begin{example}\label{ex:simplecorealpha}
-                In this example, we want to analyse games under conditions which core can be empty.
-Consider a game $G = (N, v)$,  where $N = {1,2,3}$ and $v(\{i\}) = 0$, $v(\{Ci\}) = \alpha for |C| = 2$ and $v(\{N\}) = 1$.
-The $(x_1,x_2,x_3)$ distribution vector according to equation \ref{eq:core}, is in $core$ if $x_i \geq 0$ which implies each player will get more than 0 which they would when working alone and $\forall i, \forall j, x_i + x_j \geq \alpha $ which implied any pair of players will get more than $\alpha$ which they would earn if they worked in pair without the third player and finally $\sum_{i \in N} x_i = 1$ which implied all the gain is distributed among the three players.
-Based on these three equations we have, $\forall i \in N 0 \leqslant 1 - \alpha$ and $\sum_{i \in N} x_i = 1$.
-By summing first equation for all three platers, we conclude $Core (N,v)$ is nonempty iff $\alpha \leqslant \frac{2}{3}$.
-When alpha is more than $\frac{2}{3}$, the contribution of third player is not good enough to justify the group of three players working together.
-The third player will increase the revenue with less then $\frac{1}{3}$, and the other two players, both can get better share of revenue if they work together.
-This is why the group of three players working together when $\alpha > \frac{2}{3}$ is not stable.
-            \end{example}
-
-            %\begin{example}\label{ex:simplecore2}
-%
-%                An example which has closely resembles our community service model is the \emph{Single landowner and landless workers} example.
-%                This example was introduced in \cite{GVK369342747} and represents the \emph{landowner} entity which is providing jobs and \emph{landless workers} who cannot do anything by themselves and need to work with a landowner to gain revenue (payoff).
-%
-%                In this game, land is owned by a single person, the \emph{landowner}.
-We refer to the other people as \emph{workers}.
-In this case we have a game there the set of players are the landowner and the $m$ workers, possible actions for coalitions with only workers would be distributing the zero output for all where no member receives any output.
-The set of actions of a coalition $S$ consisting of the landowner and $k$ workers would be the set of all $S$-allocations of the output $f(k+1)$ among the members of $S$.
-The preference of each player would be the amount of out she obtains.
-%
-%                In this game the action $a_{N}$ of the grand coalition in which the landowner obtains all the output $f$(n)
-%                is in the core: all coalitions that can produce any output include the landowner, and none of these
-%                coalitions has any actions that makes her better off than she is in $a_{N}$.
-%
-%                For any value of n The core contains actions in which the workers receive some output.
-%                The workers need the landowner to produce any output, but the landowner
-%                also needs the workers to produce more than $f$(1), so stable actions of the grand coalition exist in which the
-%                workers receive some output. Take the landowner to be player 1, and consider the action $a_{N}$ of the grand
-%                coalition in which each player $i$ obtains the output $x_{i}$, where $x_{1}+...+x_{n}=f(n)$. Under what conditions
-%                on  $(x_{1},..,x_{n})$ is $a_{N}$ in the core? Because of my assumption about the shape of the function $f$, the
-%                coalitions most capable of profitably deviating from $a_{N}$ consist of the landowner and every worker but one.
-%                Such a coalition can, by itself, produce $f(n-1)$, and it may distribute this output in any way among its members.
-%                Thus for a deviation by such a coalition not to be profitable, the sum of $x_{i}$ and any collection of $(n-2)$ other
-%                $x'_{i}$s must be at least $f(n-1)$. That is, $(x_{1}+...+x_{n})-x_{i}\geq f(n-1)$ for every $j=2,..,n$. Because
-%                $x_{1}+...+x_{n}=f(n)$, we conclude that $x_{i}\leq f(n)-f(n-1)$ for every player $j$ with $J\geq 2$ (i.e. every worker).
-%                That is, if $a_{N}$ is in the core then $0\leq x_{j}\leq f(n)-f(n-1)$ for every player $J\geq 2$. In fact, every such action
-%                is in the core, as you are asked to verify in the following exercise.
-%
-%            \end{example}
-
-%          Core of landowner-worker game: Check that no coalition can improve upon any action of the grand
-%          coalition in which the output received by every worker is nonnegative and at most $f(n)-f(n-1)$. (Use the fact that
-%          the form of $f$ implies that $f(n)-f(k)\geq (n-k)(f(n)-f(n-1))$ for every $k\leq n$.)
-
-%          We conclude that the core of the game is the set of all actions of the grand coalition in which the output $x_{i}$
-%          obtained by each worker $i$ satisfies $0\leq x-{1}\leq f(n)-f(n-1)$ and the output obtained by the landowner is the
-%          difference between $f(n)$ and the sum of the worker's shares. In economics jargon, $f(n)-f(n-1)$ is a worker's
-%          ``marginal product". Thus in any action in the core, each worker obtains at most her marginal product.
-
-%          The worker's shares of output are driven down to at most $f(n)-f(n-1)$ by competition between coalitions consisting
-%          of the landowner and workers, in cahoots with the landowner, can deviate and increase their share of output. That is,
-%          each worker's share of output is limited by her comrade's attempts to obtain more output.
-
-%          The fact that each worker's share of output is held down by interworker competition suggests that the workers might
-%          be better off if they were to agree not to join deviating coalitions \emph{except as a group}. You are  asked to check
-%          this idea in the following exercise.
-
-        %\subsection{Cooperative Games in Service Oriented Computing}\label{sec:CWSArchitecture}
-
-        \subsection{Representation and Complexity issues}\label{sec:CWSArchitecture}
-
-        Shapely value is the unique "fair" way to distribute the total surplus generated by the coalition, among all the players.
+        Shapely value is the unique ``fair'' way to distribute the total surplus generated by the coalition, among all the players.
         The nature of the Shapley value is combinatorial, as all possible orderings to form a
@@
         to determine whether for a bunch of agents to collude and make their own coalition and guarantee
-        an increase in payoff of all participants\cite{conf/aaai/YokooCSOI05}.
-        There are some representations that allow to compute the Shapley value efficiently by reducing the input size of the problem.
+        an increase in payoff of all participants \cite{conf/aaai/YokooCSOI05}.
+        There are some representations that allow us to compute the Shapley value efficiently by reducing the input size of the problem.
         One example is \emph{Induced subgraph games}
         which was introduced by Deng and Papadimitriou \cite{Deng94}. In this representation, players are represented by graph nodes, and
-        their valuation function should be sum of weights all edges between the node and all its neighbors. It is a succinct representation, using
-        an adjacency matrix, which need only $O(n^2)$ space to store all the input, which is a big reduction from $O(2^n)$.
-        if weights of all the edges in graph are all positive, the Shapley value can be computed in $O(n^2)$ time.
-        However, this representation is not complete, some games cannot be represented by a induced subgraph game\cite{conf/aaai/YokooCSOI05}.
+        their valuation function should be the sum of weights of all edges between the node and all its neighbors. It is a succinct representation, using
+        an adjacency matrix, which needs only $O(n^2)$ space to store all the input, which is a major improvement from $O(2^n)$ because
+        if weights of all the edges in graph are all positive, the Shapley value can be computed in time $O(n^2)$.
+        However, this representation is not complete, some games cannot be represented by a induced subgraph game \cite{conf/aaai/YokooCSOI05}.
 
-        Ketchpel introduces the Bilateral Shapley Value (BSV)\cite{conf/aaai/Ketchpel94a} for coalition games with general valaution functions.
+        Ketchpel introduces the Bilateral Shapley Value (BSV) \cite{conf/aaai/Ketchpel94a} for coalition games with general valaution functions.
         It reduces the combinatorial complexity of the computation of the Shapley value, breaking the community to multiple disjoint set.
@@
 
-        One of the first contributions in which web service community was introduced was in \cite{Zeng:2003:QDW:775152.775211}.
-They defined web service community as collection of web services providing same functionality however with different quality metrics.
-
-        Medjahed and Boubuettaya \cite{journals/dpd/MedjahedB05} have proposed a framework and a community builder mechanism which uses semantic analysis, providing an ontological organization of web services having same domain of interest.
-The community builder would suggest web services having similar operations with any community to join the community, or form their own communities in case the semantic analysis cannot find any community with close enough operations and service types.
+The idea of grouping web services within virtual structures was
+fist proposed by Zeng et al. \cite{Zeng:2003:QDW:775152.775211}.
+The authors defined web service community as collection of web
+services providing the same functionality, but with different
+quality metrics. Medjahed and Boubuettaya
+\cite{journals/dpd/MedjahedB05} have proposed a framework and a
+community builder mechanism which uses semantic analysis,
+providing an ontological organization of web services having the
+same domain of interest. The community builder would suggest web
+services having similar operations to join the same community, or
+form their own community in case the semantic analysis cannot find
+any community that matches the service types.
 
@@
         DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
-        users and services to maximize their gain. A two-player
+        users and services maximize their gain. A two-player
         non-cooperative game between web services and community master was
@@
         In \cite{10.1109/TSC.2012.12}, a cooperative scheme among autonomous
-        web services based on coalitional game theory has been introduced. They have proposed an algorithm to
+        web services based on coalitional game theory has been introduced. The authors have proposed an algorithm to
         reach individually stable coalition partition for web services in order to
@@
 
-        In this research work, I will use game theory to
+\section{Conclusive Remarks}
+
+        In this research work, we will use game theory to
         propose a cooperative game model for the aggregation of web
@@
         coalition stable as no web service will expect to gain better by
-        deviating for the community. In other words, the coalition is made
+        deviating from the community. In other words, the coalition is made
         efficient if all the members are satisfied. We first propose a

### 2014-03-02 seminar/seminar_report/chapter5.tex
changes

--- 2013-12-03 proposal/proposal/chapter5.tex
@@
 
-    \begin{figure}
-                \begin{center}
-%                \includegraphics[width=16cm, height=22cm]{timeline/timetable.pdf}\label{Timetable}
-                \includegraphics[width=16cm]{timeline/timetable1.eps}\label{Timetable}
-                \caption{Research milestones and timeline}
-                \end{center}
-    \end{figure}
+\subsection {Publications }
+
+    \begin{enumerate}        
+        \item Published a Journal Paper to the International Journal of Expert Systems With Applications; \emph{"To Compete or to Cooperate?
+This is the Question in Communities of Autonomous Services"}, 2014
+        \item Published a Journal Paper to the IEEE Transactions on Services Computing; \emph{"Efficient Community Formation for Web Services"}, 2014        
+        \item Published a paper in 10th IEEE International Conference on Services Computing; \emph{"Efficient Coalition Formation for Web Services"}, 2013
+        \item Published a Paper to the 10th International Conference on Service Oriented Computing; \emph{"Analyzing Coopetition Strategies of Services within Communities"}, 2012        
+    \end{enumerate}

### 2014-03-03 seminar/seminar_report/chapter2.tex
changes

@@
 \subsection{Web Services}\label{sec:CWSWebServices}
-Over the past years, online services have become part of standard
-daily life of people around the globe. Many modern applications
-rely on web services from different providers. For instance, many
-mobile and tablet applications which have limited storage and
-processing power are merely interfaces aggregating different
-information from online services. Examples are vast, weather
-forecasting, ticket selling, shopping apps, local maps and places
-searching.
-
-The World Wide Web Consortium (W3C) defines web services as
-follows: ``software system designed to support interpretable
-machine-to-machine interaction over a network. It has an interface
-described in a machine-processable format (specifically WSDL).
-Other systems interact with the web service in a manner prescribed
-by its description using SOAP messages, typically conveyed using
-HTTP with XML serialization in conjunction with other Web-related
-standards''. When developers declare a new web service, it will be
-discovered based on its description that fully discloses its
-functionalities. Developers also have to declare a public
-interface and a readable documentation to help other developers
-when integrating different services \cite{w3cwsdl}. Nowadays, web
-API standards which do not require XML-based web service protocols
-like SOAP and WSDL are also emerging. They are also called REST
-(representational state transfer) services which are moving
-towards simpler communication protocols. %They are not restricted
-%to XML formats, recently JSON, a human readable and simpler format
-%is becoming popular among online service providers.
-
-We are not going to delve into engineering details of online web
-service implementation and its protocols in this proposal. We are
-interested in web services from their business model perspective.
-Service providers usually charge end users for services they
-provide. For example, Google has listed their pricing and plans
-for wide range of services they provide on their web service
-console page\footnote{https://code.google.com/apis/console}.
 
@@
 
-        When dealing with cooperative games, two issues need to be
-        addressed:\\ 1. Which coalitions among all possible coalitions to form? \\
-        2. How to reward each member when a task is completed?\\
-        %
-        The following sections help address these two issues.
-
         \subsection{Cooperative Game Concepts}
@@
 
-            \subsubsection*{$\epsilon$-core}\label{s:epsilon}
-            %\emph{$\epsilon$-Core:}
-            %\\
-            When the \emph{core} set of a game is empty, it means no coalition
-            of players can gain anything by deviating. An outcome would be
-            unstable if a coalition can benefit even by a small amount from
-            deviating, which is a strong requirement. In fact, in some
-            situations, deviations can be costly, or players may have loyalty
-            to their coalitions, or even it can be computationally intractable
-            to find those small benefits. It would only make sense for a
-            coalition to deviate if the gain from a deviation exceeds the cost
-            of performing the deviation. \emph{$\epsilon$-core} relaxes the
-            notion of the core, and only requires that no coalition would
-            benefit significantly, or within a constant amount($\epsilon$) by
-            deviating (see Equation \ref{eq:core}).
-
-            \begin{equation}\label{eq:core2}
-            \forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
-            \end{equation}
+            %\subsubsection*{$\epsilon$-core}\label{s:epsilon}
+%            %\emph{$\epsilon$-Core:}
+%            %\\
+%            When the \emph{core} set of a game is empty, it means no coalition
+%            of players can gain anything by deviating. An outcome would be
+%            unstable if a coalition can benefit even by a small amount from
+%            deviating, which is a strong requirement. In fact, in some
+%            situations, deviations can be costly, or players may have loyalty
+%            to their coalitions, or even it can be computationally intractable
+%            to find those small benefits. It would only make sense for a
+%            coalition to deviate if the gain from a deviation exceeds the cost
+%            of performing the deviation. \emph{$\epsilon$-core} relaxes the
+%            notion of the core, and only requires that no coalition would
+%            benefit significantly, or within a constant amount($\epsilon$) by
+%            deviating (see Equation \ref{eq:core}).
+%
+%            \begin{equation}\label{eq:core2}
+%            \forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
+%            \end{equation}
 
@@
         In order to make cooperative game concepts practical in real world application, we have proposed an approximation multi-layer
-        algorithm useful for service orinted computing settings. Our excrements illustrate, these algorithms can provide
+        algorithm useful for service oriented computing settings. Our excrements illustrate, these algorithms can provide
         applicable and near optimal solutions for real world applications.
+
+\subsection{Stability of Coalitions}
+
+Core stability is a highly desirable property however in many problems it is not achievable.
+It would be more ideal to maintain a set of somewhat stable payoffs when the core is empty.
+There are several approaches to achieve this goal.
+One may drop the stability requirement and focus on other types of solutions for which a payoff division is guaranteed to exist.
+Two well known solution concepts in this category are \emph{nucleolus}\cite{schmeidler_nucleolus_1969} and the \emph{bargaining set}\cite{Davis67existenceof}.
+They try to minimize some measure of unhappiness in the game for the agents.
+
+Another approach to stabilize the game can be achieved via external subsides.
+When \emph{Core} is empty it means the game is not stable since the coalition is unable to generate enough revenue to satisfy the demands of each subset of agents.
+An external party that is interested in stabilizing the game provides a subsidy to the agents if they form the grand coalition, and thus a value of $\lambda v(C)$ is divided among them, where $\lambda \geq 1$.
+Clearly any game can be stabilized using a large enough $\lambda$, however the external party would be interested in the minimal subsidy required in order to stabilize the game.
+
+A community can also be stabilized by relaxing the core constraints.
+According to \emph{Core}, an outcome is unstable if a coalition can benefit even by a small amount from deviating, which is a strong requirement.
+In fact, in some situations, deviations can be costly, or players may have loyalty to their coalitions, or even it can be computationally intractable to find those small benefits.
+It would only make sense for a coalition to deviate if the gain from a deviation exceeds the cost of performing the deviation.
+\emph{$\epsilon$-core} relaxes the notion of the core, and only requires that no coalition would benefit significantly, or within a constant amount($\epsilon$) by deviating (see Equation \ref{eq:core}).
+
+   \begin{equation}\label{eq:core2}
+       \forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
+   \end{equation}
+
+Alternatively, the $\epsilon$ can be thought of as a \emph{tax} imposed on a coalition should it choose to deviate.
+This can again be seen as an external party, trying to stabilize the coalition by imposing some \emph{tax} on deviation.
+Taxation and subsiding as methods of stabilizing cooperative games have been studied in \cite{RePEc:spr:jogath:v:38:y:2009:i:1:p:3-16, RePEc:mse:cesdoc:12022r, Bachrach:2009:CSC:1692490.1692502, conf/ijcai/MeirRM11}.
 

### 2014-03-03 seminar/seminar_report/chapter3.tex
changes

--- 2013-12-03 proposal/proposal/chapter3.tex
@@
 The revenue function of the web service community is a linear function of $Out(C)$ with a positive constant multiplier.
-
-\subsection{Case Study}
-
-In this section, we analyze three numerical examples and discuss the motivation of web services and community interactions and the strategies they can adopt and the revenue they can earn adopting these different strategies.
-
-%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[!t]
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-\caption{Case Study: Example 1}
-\label{example_1}
-\centering
-\begin{tabular}{c c c c}
-\hline
-$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
-\hline
-1 & 0.8 & 4 & 3.2\\
-2 & 0.8 & 5 & 4.0\\
-3 & 0.8 & 3 & 2.4\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}[!t]
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-% \caption{Three web services}
-\label{example_1_2}
-\centering
-\begin{tabular}{c c || c c}
-\hline
-Community & Worth & Community & Worth\\
-\hline
-$\left\{1\right\}$ & 3.2 & $\left\{1,2\right\}$ & 7.2\\
-$\left\{2\right\}$ & 4.0 & $\left\{1,3\right\}$ & 5.6\\
-$\left\{3\right\}$ & 2.4 & $\left\{2,3\right\}$ & 6.4\\
-$\left\{1,2,3\right\}$ & 8.0\\
-\hline
-Community $R_C$: 10\\
-\hline
-\end{tabular}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[!t]
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-\caption{Case Study: Example 2}
-\label{example_2}
-\centering
-\begin{tabular}{c c c c}
-\hline
-$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
-\hline
-1 & 0.8 & 5 & 4.0\\
-2 & 0.7 & 6 & 4.2\\
-3 & 0.7 & 4 & 2.8\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}[!t]
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-% \caption{Three web services}
-\label{example_2_2}
-\centering
-\begin{tabular}{c c || c c}
-\hline
-Community & Worth & Community & Worth\\
-\hline
-$\left\{1\right\}$ & 4.0 & $\left\{1,2\right\}$ & 7.4\\
-$\left\{2\right\}$ & 4.2 & $\left\{1,3\right\}$ & 6.8\\
-$\left\{3\right\}$ & 2.8 & $\left\{2,3\right\}$ & 7.0\\
-$\left\{1,2,3\right\}$ & 7.3\\
-\hline
-Community $R_C$: 10\\
-\hline
-\end{tabular}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%, %%%%%%%%%%%%%%%%%%%%%%
-
-In the first example,  we present the case of a community with
-$R_C =10 $, and three web services, each having different
-$QoS_{ws}$ and $Th_{ws}$ values as listed in Table
-\ref{example_1}. The worth of a community is calculated based on
-$Out(C)$ equation (\ref{out_c}) which is the amount of output
-being generated by the community. The first table  lists the web
-services with their aggregated $QoS_{ws}$ parameters, their task
-input rate while working alone, and also their  throughput value
-$Th_{ws}$. The second table shows all the possible communities and
-their respective worth. The obtained values suggest that
-communities having more web services have better gain and output.
-However each community needs to  distribute the gain between web
-services. Sometimes it is impossible to share the gain between all
-web services in a way that no subset of them would individually
-gain more if they form their own group. In this example, the value
-community of ${ws_1}$ and ${ws_2}$ is 7.2, With ${ws_3}$ joining
-the community the worth increases to 8.0. However there is no way
-to distribute the value among web services to have  ${ws_1}$ and
-${ws_2}$  earning 7.2, and ${ws_3}$ earning at least 2.4, the gain
-they could earn before joining the community. This fact makes the
-group unstable. In the second  example, shown in Table
-\ref{example_2}, we even have situations where a web service
-(${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$)
-decreases the value of community. The reason is, the community is
-already full and all tasks are almost being distributed and new
-community with bad quality can degrade the average quality of
-tasks being done by the community. In both examples, the request
-of joining of web service ${ws_3}$ should be rejected by the
-community.
-
-%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[!t]
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-\caption{Case Study: Example 3}
-\label{example_3}
-\centering
-\begin{tabular}{c c c c}
-\hline
-$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
-\hline
-1 & 0.8 & 10 & 5\\
-2 & 0.8 & 20 & 5\\
-3 & 0.8 & 30 & 5\\
-\hline
-\end{tabular}
-\end{table}
-
-\begin{table}[!t]
-\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-% \caption{Three web services}
-\label{example_3_2}
-\centering
-\begin{tabular}{c c || c c}
-\hline
-Community & Worth & Community & Worth\\
-\hline
-$\left\{C_{ms_1}\right\}$ & 0 & $\left\{C_{ms_2}\right\}$ & 0\\
-$\left\{C_{ms_1}, ws_1\right\}$ & 8 & $\left\{C_{ms_2}, ws_1\right\}$ & 8\\
-$\left\{C_{ms_1}, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_2\right\}$ & 16\\
-$\left\{C_{ms_1}, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_3\right\}$ & 24\\
-$\left\{C_{ms_1}, ws_1, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2\right\}$ & 24\\
-$\left\{C_{ms_1}, ws_1, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_3\right\}$ & 32\\
-$\left\{C_{ms_1}, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_2, ws_3\right\}$ & 32\\
-$\left\{C_{ms_1}, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2, ws_3\right\}$ & 32\\
-$\left\{C_{ms_1}, C_{ms_2}, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
-$\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
-\hline
-Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
-\hline
-\end{tabular}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In Example 3, we consider the case of having different communities with different market share, ${R_C}$ values.
-Web services also have a small share of market independently, providing them with a small task pull.
-In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the \emph{social welfare}.
-In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_{master_1}, ws_2\right\}$ and $\left\{C_{master_2}, ws_1, ws_3\right\}$, which yields a total value of $32 + 16 = 48$.
-In these types of scenarios, the goal is to reach stability, adopting a distributed approach where all players have the power of choice on the decision of whether or not they join a coalition.
-The communities usually start the game having some established members, encountering new web services, the communities may exchange web services and new web services would join them having at least one player gaining utility, without hurting any other participant.
-In this example if we initially having two coalitions of $\left\{C_{master_1}, ws_2\right\}$ and $\left\{C_{master_2}, ws_1\right\}$ and a ${ws_3}$ as new web service, ${ws_3}$ joining ${C_{master_1}}$ would hurt at least itself or $ws_2$, however ${ws_3}$ joining ${C_{master_2}}$ would not hurt any participants and ${ws_3}$ would earn more within the community and the community will have enough web services performing the incoming tasks from users.
-
-The first two examples illustrate the fact that a community cannot simply increase its revenue by adding more web services.
-The web services and even community owners are autonomous agents and would deviate and be displeased about the community if new members cause a drop in their profit.
-The job of the community master is to attract as many quality web services it can and keep them satisfied; hence the group stability is guaranteed.
-The third example highlights another type of problem we would like to address, which is how to form best possible groups of communities, and allocate web services among communities in a way which would maximize payoff for of our agents and members already residing in the communities.
-In next section, we provide collaborative game theory based algorithms for our autonomous agents, to tackle these problems and find applicable and efficient strategies for communities and web services to maximize their profit.
 
@@
 
-\subsection{Taxation, Subsiding and Community Stability}\label{s:tax}
+\section{Taxation, Subsiding and Community Stability}\label{s:tax}
 
-ssed $core$ as one of the prominent solution concepts in cooperative games.
-Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group.
-However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal amount of $\epsilon$ by deviating.
-Stability is an attractive property for communities.
-In addition, communities would benefit by having slightly more web services then the exact number of web services satisfying task rate cap.
-This is because  there is always a possibility that the agents may leave the community or they may under perform and degrade the quality values they were initially performing with.
+We discussed $core$ as one of the prominent solution concepts in
+cooperative games. Working together, completing tasks and
+generating revenue, agents need to distribute the gain in a way no
+agents would gain more by forming their own group. However, in
+most cases, the core of a game is empty, so we introduced the
+\emph{$\epsilon$-core} concept, where agents would only earn a
+minimal amount of $\epsilon$ by deviating from the coalition.
+Stability is an attractive property for communities. In addition,
+communities would benefit by having slightly more web services
+than the exact number of web services needed to satisfy the task
+rate cap. This is because there is always a possibility that the
+web services may leave the community or they may under perform and
+degrade the quality values they were initially performing with.
 
-One way for communities to ensure  stability could be  by applying a tax, $\epsilon$ amount of cost for web services changing communities which would make deviation a costly act.
-However this would require all community coordinators to agree on a same amount of taxation, being governed by some external entities or web services would join communities with lesser amount of tax.
-Another viable solution to our scenario is to stabilize the game using external subsidies.
-The reason a gamWe discue is not stable is that the community is not making enough revenue to allocate  enough gain to the players.
-A community master can subside its community with a constant coefficient value of $\lambda$.
+The solution we propose for communities to ensure stability is
+applying a tax $\epsilon$, which is an amount of cost for those
+web services that decide to change communities (let us say from
+$C$ to $C'$), which would make deviation a costly act. However,
+this would require all the community coordinators to agree on a
+same amount of taxation, being governed by some external entities;
+otherwise, web services would join communities charging the lowest
+amount of tax. Before deciding to change the community, each web
+service $i$ has to be sure that the gain $g_i(C \rightarrow C')$
+calculated in Equation \ref{eq:gainsh} based on the Shapley values
+of $i$ in the previous and new communities and the tax $\epsilon$
+is positive, which means, what the web service would gain in $C'$
+is greater than what it gains in $C$ and the tax it would pay if
+moving all together:
 
-Rewarding a community with high number of quality participants with $\lambda v(C)$, where $\lambda \leq 1$.
+\begin{equation}\label{eq:gainsh}
+g_i(C \rightarrow C') = \phi_i(C',v) - \phi_i(C,v) - \epsilon
+\end{equation}
 
-Obviously with a big number of $\lambda$, it is always possible to stabilize the community.
-However, this can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable.
-Subsiding or taxing in order to reduce the bargaining power of sub coalitions are called $taxation$ \cite{eps346856} methods.
+Another viable solution we introduce to our scenario is to
+stabilize the game using external subsidies. The reason a game is
+not stable is that the community is not making enough revenue to
+allocate enough gain to the players. A community coordinator can
+subside its community with a constant coefficient value of
+$\lambda$.
+%
+%Rewarding a community with high number of quality participants
+%with $\lambda v(C)$, where $\lambda \leq 1$.
+%
+Obviously, with a big value for $\lambda$, it is always possible
+to stabilize the community. However, this can be a costly act for
+the community coordinators, so they are interested in the minimum
+subside value of $\lambda$ making the community stable. This can
+be achieved by solving the following linear program:
+%
+  \begin{alignat*}{3}
+    \min~   & \lambda  \\
+    \text{s.t. } & \lambda v(C) > v(C') & ~& \text{ for all } C' \subset C
+  \end{alignat*}
+
+%When a new web service $i$, wants to join the community, the
+%valuation function of the community members and the new web
+%service is subsided by the community coordinator in order to
+%incentivize formation of this community and is set to:
+%\begin{equation}\label{eq:taxv}
+%v'(C \cup \{i\}) = \lambda \times v(C \cup \{i\})
+%\end{equation}
+%In equation \ref{eq:taxv} the value of $v'$ is
+%replaced with the valuation function for the new forming coalition
+%$C \cup \{i\}$.
+Subsiding or taxing in order to reduce the
+bargaining power of sub coalitions are called $taxation$
+\cite{eps346856} methods. We evaluate the effectiveness of these
+two methods experimentally through extensive implementations in
+the next section.
 
@@
 scenarios to validate the applicability and performance of our
-proposed methods in realistic environments. We created a pool of
-web services and populated most of their \emph{QoS} parameters
-from a real world web service dataset
-\cite{DBLP:conf/smc/Al-MasriM09a}. We implemented the simulations
-using Java and executed the simulations on an Intel Xeon X3450
-machine with 6GBs of memory. For other parameters missing from the
-dataset, we used normal random distribution with parameters
-estimated using the method of maximum likelihood.
+proposed methods in realistic environments.
+An XML SOAP based messaging system was implemented. The request
+contains the flight dates, the origin and destination, type of
+tickets, and number of guests. The response contains different
+flights with different companies, prices, timing, etc. We have
+gathered around 200,000 flights and stored them in our MongoDB
+database. We created a pool of web services and populated most of
+their \emph{QoS} parameters from a real world web service dataset
+\cite{DBLP:conf/smc/Al-MasriM09a}\footnote[1]{The implemented
+environment includes the QWS dataset by Eyhab Al-Masri and Qusay
+H. Mahmoud freely available at:
+http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/.}. To test
+our methods, we formed around 10,000 random coalitions consisting
+of 3 to 160 web services. In average, the communities were populated by 60 web
+services. Thus, in total, the number of used web services is
+600,000. This makes our system scalable enough. We implemented the
+scenarios using Java and executed the experiments on an Intel Xeon
+X3450 machine with 6GBs of memory. For other parameters missing
+from the dataset, we used normal random distribution with
+parameters estimated using the method of maximum likelihood.
 
@@
 measured in terms of quality and quantity of requests (or tasks)
-successfully answered by the communities. We initiated the
+successfully answered by the communities. We initiate the
 communities with few web services, then let rejecting and
 accepting random web services go for a short number of iterations.
-After that, we started the request distribution for the communities
+After that, we start the request distribution for the communities
 and let them allocate requests among member web services.
-Thereafter, we measured the average output performance of tasks in
+Thereafter, we measure the average output performance of tasks in
 communities following different methods.
 
-\begin{figure}[!t]
+\begin{figure*}%[!t]
 \centering
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{Figures/task_done_opt.eps}
-\includegraphics[width=3in]{Figures/task_qos_opt.eps}
+\includegraphics[width=2.8in]{task_done_opt.eps}
+\includegraphics[width=2.8in]{task_qos_opt.eps}
 \caption{Part (a): Cumulative number of requests successfully
@@
 \label{performanceall}
-\end{figure}
+\end{figure*}
 
-Figure \ref{performanceall} depicts the results of optimal
-\emph{$\epsilon$-core}, \emph{Depth-1 Convex-Checker},
-\emph{Depth-2 Convex-Checker}, \emph{3-Way Satisfaction}
-\cite{DBLP:conf/IEEEscc/LimTMB12}, and \emph{2 Player
-Non-Cooperative} \cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods
-in \emph{one grand community with many web services} scenario.
+Figure \ref{performanceall} depicts the results of our methods:
+\emph{Depth-1 Convex-Checker} and \emph{Depth-2 Convex-Checker},
+and compares them with \emph{3-Way Satisfaction} (from
+\cite{DBLP:conf/IEEEscc/LimTMB12}), and \emph{2 Player
+Non-Cooperative} (from \cite{DBLP:conf/IEEEscc/KhosravifarABT11})
+methods in \emph{one grand community with many web services}
+scenario. The figure also depicts the results of the theoretical
+\emph{optimal $\epsilon$-core} as benchmark.
 
-For the \emph{optimal core} method we have used the well known \emph{$\epsilon$-core} method as the
-taxtation method to relax the core condition to help communities, attract web services.
-We have assigned $\epsilon$ to 15\% of total community worth, $\epsilon = 0.15 \times v(C)$, which allows
-subsets of the coalition to gain maximum 15\% of $v(C)$. In the
-\emph{optimal $\epsilon$-core} method, we capped the coalition
-size to 25 web services, since the method is computationally
-intractable as number of web services increase and anything more than that would make it
-impractical to run in our simulations. In the other methods, there
-were no cap on size of the community and we had communities of
-size 60 web services at some points.
-In this scenario our community receives 30 tasks on average per iteration, from users.
-The community, after the task distribution process on each iteration, will reevaluate QoS metrics of its members and can check for new membership requests.
-Web services may join or leave the community between iterations.
-The results show that our
+For the \emph{optimal core} method, we have used the well known
+\emph{$\epsilon$-core} method as the taxation method to relax the
+core condition to help communities attract web services. We have
+assigned $\epsilon$ to 15\% of total community worth, which means
+$\epsilon = 0.15 \times v(C)$. This allows subsets of the
+coalition to gain maximum 15\% of $v(C)$. In the \emph{optimal
+$\epsilon$-core} method, we capped the coalition size to 25 web
+services, since the method is computationally intractable as the
+number of web services increases. In fact, given the machine
+configuration we used in our experiments, the maximum number we
+could run for this method is 25, which is very realistic if we
+consider the real airlines coalitions (the three well known
+coalitions have respectively 28, 19, and 13 members). In the other
+methods, there were no cap on size of the community and we had
+communities of size 160 web services at some points, as discussed
+above. In the experiments, our \emph{Depth-1 Convex-Checker} and
+\emph{Depth-2 Convex-Checker} methods generate results instantly
+(0.01ms in Java millisecond time unit granularity) in our machines
+since their runtime with respect to the size of input (number of
+web services) is $O(n)$ and $O(n^2)$ respectively. This shows that
+the algorithms are efficient and the system is easily scalable. In
+this scenario, our community receives 130 tasks from users on
+average per iteration. These tasks are about flight booking and
+are expected to be performed by the community. They are randomly
+generated using a poisson distribution (having 130 as parameter).
+Depending on community task queue and the assigned web services'
+quality metrics the task will be performed with some qualities.
+The community, after the task distribution process on each
+iteration, will reevaluate QoS metrics of its members and can
+check for new membership requests. Web services may join or leave
+the community between iterations. The results show that our
 \emph{depth-2 convex checker} method is performing better compared
-to the other methods and its performance is close to optimal
+to the other methods and its performance is close to the optimal
 \emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
-and the \emph{3-Way Satisfaction} method, are also performing well.
+and the \emph{3-Way Satisfaction} method, are also performing
+well.
 
-\begin{figure}[!t]
+\begin{figure*}%[!t]
 \centering
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{Figures/least_core.eps}
-\caption{Analysis of \emph{$\epsilon$-core} set non-emptiness, for different values of $\epsilon$} \label{f_leastcore}
-\end{figure}
+\includegraphics[width=3in]{least_core.eps}
+\caption{Analysis of \emph{$\epsilon$-core} set non-emptiness for
+different values of $\epsilon$} \label{f_leastcore}
+\end{figure*}
 
@@
 the notion of \emph{$\epsilon$-core} was introduced. Least-Core
-$e(G)$ of a game $G$, is the minimum amount of $\epsilon$ so that
-the core is not empty. We evaluated the non-emptiness of \emph{$\epsilon$-core} set using the
-valuation function and a set of web services. We picked random
-number of web services from the dataset and formed around 10,000
-random coalitions consisting of 3 to 26 web services. We choose 26
-as the maximum number of members in our coalition since it
-is computationally very complex for larger coalitions to verify whether
-\emph{$\epsilon$-core} set is empty or not.
-Also instead of considering $\epsilon$ amount of constant deviation in \emph{$\epsilon$-core} definition (Equation \ref{eq:core2}), we similarly defined \emph{relative $\epsilon$-core} concept where no coalition would benefit more than \emph{$\epsilon$ $\times$ v(C)} by deviating.
-We set $\epsilon$ between 0 and 1 and verify the \emph{relative $\epsilon$-core} set non-emptiness.
-The results in Figure
-\ref{f_leastcore} illustrates that almost 10\% of our random web
-service coalitions have non-empty \emph{core} solution and
+$e(G)$ of a game $G$ is the minimum amount of $\epsilon$ so that
+the core is not empty. We evaluated the non-emptiness of
+\emph{$\epsilon$-core} set using our valuation function and a set
+of web services from our coalitions.  The restriction on the
+number of web services per coalition for this particular method is
+justified because it is
+%We picked random number of web services from the
+%dataset and formed around 10,000 random coalitions consisting of 3
+%to 28 web services. We choose 28 as the maximum number of members
+%in our coalitions since in the concrete examples of coalitions in
+%the airline domain we are implementing, the largest coalition,
+%Star Alliance\footnote{\url{www.staralliance.com}}, has 28 airline
+%members. This makes the total number of web services achieves
+%280,000, which is scalable enough. Moreover, it is computationally
+very complex for larger coalitions to verify whether
+\emph{$\epsilon$-core} set is empty or not. Also instead of
+considering $\epsilon$ amount of constant deviation in
+\emph{$\epsilon$-core} definition (Equation \ref{eq:core2}), we    %TODO FIX THIS
+similarly defined \emph{relative $\epsilon$-core} concept where no
+coalition would benefit more than \emph{$\epsilon \times v(C)$} by
+deviating. We vary $\epsilon$ so that it takes different values
+from $0$ to $1$ and observe the impact in terms of verifying the
+\emph{relative $\epsilon$-core} set non-emptiness. The results in
+Figure \ref{f_leastcore} illustrate that almost 10\% of our random
+web service coalitions have non-empty \emph{core} solution and
 \emph{$\epsilon$-core} solution is \emph{always} non-empty when we
@@
 One of the properties of coalition structure formation algorithms
-in our second scenario is that they partition web services with low
-throughput rate so that they usually join coalitions with less
+in our second scenario is that they partition web services with
+low throughput rate so that they usually join coalitions with less
 request rate. Since the characteristic function $v(C)$ and the
-fair Shapely payoff vector is proportional to web services'
+fair Shapley payoff vector is proportional to web services'
 contribution, the web services with small contribution will get
@@
 
-\begin{figure}[!t]
+\begin{figure*}%[!t]
 \centering
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{Figures/s2_task_done.eps}
-\includegraphics[width=3in]{Figures/s2_task_qos.eps}
-\caption{Part (a): Cumulative number of tasks succesfully done. Part
-(b): Average QoS of tasks performed.} \label{performancemany}
-\end{figure}
+\includegraphics[width=3in]{taxtation.eps}
+\caption{Analysis of community subsiding coefficient $\lambda$ on
+average community size (a), cost (b), number of tasks performed
+(c), and average quality of service of tasks performed (d).}
+\label{f_taxtation}
+\end{figure*}
 
-In Figure \ref{performancemany}, we compare our \emph{Web Services
-and many Communities} scenario with a method which ignores QoS
-parameters and forms coalitions by allowing web services to join
+As mentioned in Section \ref{s:tax}, a solution to help the
+community stabilize is to subside the community by a relative
+coefficient ($\lambda$) so the value of $\lambda v(C)$ is divided
+among the community members. We have analyzed the effect of
+subsiding and the cost it incurs to our web service communities.
+Figure \ref{f_taxtation} shows the results. In this experiment, we
+have set a community with input task rate $R_C$ of 100 and having
+web services throughput rate $Th_{ws}$ values from a normal
+distribution with average 10 tasks per iteration and standard
+deviation 2. Part (a) shows the community size increases in a
+linear fashion as ($\lambda$) increases. However, the cost (Part
+(b)) is having a slight exponential growth rate since, not only
+($\lambda$) increases, but also the size of the community is
+increasing slowly. Therefore, subsiding can be costly for larger
+number of $\lambda$ values. Part (c) depicts the number of tasks
+done by the community per iteration. It is obvious that with
+$\lambda$ value of 1.3, which is 30\% of the community valuation,
+the number of tasks done almost reaches the input task rate cap of
+100 tasks per iteration. The average quality of tasks also has a
+slight increase since the community will be able to afford better
+and more web services to join the community (Part (d)). These
+results show the effectiveness of our subsiding method and its
+impact on the QoS. In fact, using more than 30\% of the community
+valuation as subsidy is not very effective and is costly to
+perform.
+
+\begin{figure*}%[!t]
+\centerline{\includegraphics[width=6.8in]{tax_dyn.eps}}
+\caption{Analysis of community subsiding coefficient $\lambda$
+having web service different stability levels of $\tau$ on average
+community size, number of tasks performed, average quality of
+service, and average cost/income of communities.}
+\label{fig_dynamic_taxtation}
+\end{figure*}
+
+In the previous experiment, we considered the scenario where all
+web services are stable, will not leave the group, and will
+fulfill their promised QoS for a good period of time. However, in
+real world scenarios of web services, this is not always the case.
+This is the reason why the community coordinator would be interested in paying
+web services in order to keep the group reliable from the end
+user's point of view. In our next scenario, we have introduced the
+new instability variable $\tau$ ranging from 0 to 1, 0 meaning web
+services having no instability issues and will perform as they
+claimed until the end of the experiment, and 1 meaning very
+unstable web services, which will stop functioning on the first
+iteration of the community distributing tasks. Figure
+\ref{fig_dynamic_taxtation} illustrates the results of our
+experiment having web services with average instability values of
+0 to 0.5 and having relative subside value $\lambda$ of 1, 1.3,
+1.6, and 2. The \emph{Cost/Income} charts on the right column show
+that having subside value of 1.3 incurs the least cost and
+increases the community income significantly. Subsiding values of
+1.6 and 2 yield high cost to the community and only slightly
+increase the community revenue. Moreover, the role of subsiding is
+much more obvious when we have unstable web services. In scenarios
+where web services are 100\% stable, the subsiding cost will
+hardly be compensated by the community revenue.
+
+\begin{figure*}%[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=2.8in]{s2_task_done.eps}
+\includegraphics[width=2.8in]{s2_task_qos.eps}
+\caption{Part (a): Cumulative number of tasks successfully done.
+Part (b): Average QoS of tasks performed.} \label{performancemany}
+\end{figure*}
+
+In Figure \ref{performancemany}, we consider \emph{Web Services
+and many Communities} scenario and we compare our dynamic
+coalition formation solution with a method which ignores QoS
+parameters and forms communities by allowing web services to join
 only if they have enough requests for themselves. In other words,
@@
 method \emph{Random Formation} and use it as a benchmark for our
-QoS-aware coalition formation process. In this scenario, each user individually generates randomly
-between 0 to 10 number of tasks per iteration, then the users target a community and direct their requests to the chosen community. As the results illustrate,
-our method forms better coalitions of web services improving
-performance and satisfaction for both web services and coalitions.
+QoS-aware community formation process. In this scenario, each user
+individually generates randomly between 0 to 10 number of tasks
+per iteration, then the users target a community and direct their
+requests to the chosen community. As the results illustrate, our
+method forms better communities of web services improving
+performance and satisfaction for both web services and
+communities.
 
-\begin{figure}[!t]
+\begin{figure*}%[!t]
 \centering
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{Figures/avg_task_ws_done.eps}
-\includegraphics[width=3in]{Figures/avg_qos_ws_done.eps}
-\includegraphics[width=3in]{Figures/avg_avail_ws_done.eps}
-\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
-(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
-\end{figure}
+\includegraphics[width=1.9in]{avg_task_ws_done.eps}
+\includegraphics[width=1.9in]{avg_qos_ws_done.eps}
+\includegraphics[width=1.9in]{avg_avail_ws_done.eps}
+\caption{A comparison between our community model and the High
+Availability Coalition model from \cite{10.1109/TSC.2012.12}. Part
+(a): Cumulative number of tasks successfully done. Part (b):
+Average QoS of tasks performed. Part (c): Average community
+service availability} \label{fig_avail_method}
+\end{figure*}
 
-Finally, in our last experiment, we compare our work with the work
-in \cite{10.1109/TSC.2012.12} which we call it \emph{High
-Availability Coalition} method, because of nature of their
-community valuation function, which focuses on community
-availability as main consideration. Their community formation
-model is very different than ours, however we have been very
-careful to make the experiment environment as fair and similar as
-possible. We limited our maximum community size by 5 in order to
-have communities with almost the same size. In their method, they
-have used web services as backups rather than active collaborative
-players, and they only get task when the first web service in an
-ordered chain fails to perform the task. However with recent
-advancement in cloud and hardware infrastructures availability is
-less of an issue for web services, and web services are highly
-available. Part(a) of figure \ref{fig_avail_method} shows our
-method performs almost performs tasks successfully with rate of
-three times more than \emph{High Availability Coalition} method
-because of real cooperative nature and task distribution of our
-algorithm. This result shows using web services as backups, and
-not as real collabrative players is a huge waste of web service
-capability since they have very low chance of getting jobs and its
-the primary web service (the first in their coordination chain)
-which does most of the work. The average quality of service of
-tasks performed is also better since our method considers all
-quality of service metrics mentioned in Table \ref{qosws}. Part(c)
-shows the availability of community from end user point of view.
-The \emph {High Availability Coalition} method almost has 100\%
-uptime since they use web services as backups, so the chance of
-job failing reduces significantly as community members increase.
-In our method we have more chance of fail for each web service,
-however with some subsiding, and hiring a few more web service
-they can compensate the low chance of failure of web services in
-our community.
+Finally, in our last experiment, we compare our model with the
+solution proposed in \cite{10.1109/TSC.2012.12}, which we call
+\emph{High Availability Coalition} model. In this method, the
+community valuation function focuses on the community availability
+as main consideration. The community formation model used in this
+method is very different from ours, but we have been very careful
+to make the experiment environment as fair and similar to ours as
+possible. We limited our maximum community size to 5 in order to
+have communities with almost the same size as in
+\cite{10.1109/TSC.2012.12}. In the High Availability Coalition
+model, the authors have used web services as backups rather than
+active collaborative players, and those web services only get a
+task when the first web service in an ordered chain fails to
+perform that task. %However, with recent advancement in cloud and
+%hardware infrastructures, availability is less of an issue for web
+%services, and web services are highly available.
+Part(a) of Figure \ref{fig_avail_method} shows that with our
+method, the number of tasks successfully done is higher with a
+rate of three times more than the High Availability Coalition
+model thanks to the cooperative behavior of web services and the
+task distribution process of our algorithm. This result shows that
+using web services as backups, and not as real collaborative
+players results in a considerable waste of web services capability
+since services have very low chance of getting jobs and its the
+primary web service (the first in the coordination chain) which
+does most of the work. As shown in Part (b), the average quality
+of service of tasks performed using our solution is also higher
+since our method considers all quality of service metrics
+mentioned in Table \ref{qosws}. Part(c) shows the availability of
+communities from the end user's point of view. The High
+Availability Coalition model has almost 100\% uptime since web
+services are used as backups, so the chance of job failing is
+getting reduced significantly as community members increase. In
+our method, we have more chance of failure for each web service.
+However, with some subsidies and by hiring a few more web
+services, the chance of failure of web services in our communities
+can be lowered.

### 2014-03-03 seminar/seminar_report/chapter5.tex
changes

@@
 
-In this report, we presented research problems and questions we
-aim to address in the thesis and proposed some preliminary results
-about a cooperative game theory-based model for the aggregation of
-web services within communities. The goal of our services is to
-maximize efficiency by collaborating and forming stable
+In this report, we proposed a cooperative game theory based model for the aggregation of web services within communities.
+The goal of our services is to maximize efficiency by collaborating and forming stable
 coalitions. Our method considers stability and fairness for all
@@
 
+\begin{center}
+    \begin{tabular}{ | l | l | p{5cm} |}
+    \hline
+    Term & Activity & Publication \\ \hline
+    Winter 2014 & 1 & 1 \\ \hline
+    Summer 2014 & 1 & 1 \\ \hline
+    Fall 2014 & 1 & 1 \\ \hline
+    Winter 2015 & 1 & 1 \\
+    \hline
+    \end{tabular}
+\end{center}
+
 \subsection {Publications }

### 2014-03-03 seminar/seminar_report/chapter1.tex
change

--- 2013-12-02 proposal/proposal/chapter1.tex
@@
 
-\section{Motivating Scenario}\label{sec:motexample}
-
-In this section, we present a scenario and demonstrate why there
-is need for communities of services. We first propose an example
-of a real world scenario, focusing on user experience. There are a
-plethora of options available to people in today's society,
-including weather forecasting, ticketing services, map services,
-local places guides and so on. Most mobile or web applications
-cannot independently satisfy users requests and should rely on
-different online services. The high competition within the
-services industry requires applications to use reliable and high
-quality online service providers.
-
-If the user were to check a web site or run an application on her
-mobile device upon having downtime, or having high response delay
-or encountering any non-satisfying quality metric, she will
-instantly remove the application, which is a huge business concern
-for application providers. For example, if a user installs a
-ticketing application on her mobile device and the application is
-not using high quality service providers, the user would instantly
-uninstall the application, which has an extremely negative impact
-on the
-visibility of the application. %Let us say you search "Montreal
-%Weather" on a search engine and you click on a web site which is
-%slow because it is using a bad weather web service as source of
-%its raw data, the user will leave the web site and try another
-%link from search results, which has a bad Search Engine
-%Optimization (SEO) effect for the web site, and search engines
-%would not show that web site on search results anymore, which is a
-%business and revenue loss for the application.
-Thus, end user satisfaction is the main goal for competitive
-online providers. Communities of web service, by providing
-services with higher quality, higher uptime and reliability for
-end users, aim to reach this goal. To this end, community
-management decisions should capitalize on important QoS parameters
-while forming the community and during membership management.
-
-High demand on online services has created a massive business
-competition. For example, nowadays users are provided with
-multiple choices of web services offering local places information
-such as coffees, venues, and shops nearby a geographic position.
-It is hard for new web services to find their customers and be
-visible for end users amongst hundreds or thousands of other
-available services, even if they provide a high quality of
-service. Hence, the concept of communities of web services
-provides them with the chance of joining a platform with an
-established market share and reputation. However, it is crucial
-for a community manager to consider many factors when inviting or
-accepting new members. For example, if the market share is not big
-enough, bringing new web services can cause revenue drop for the
-already residing members. This may encourage other web services to
-collude, leave, or join other communities, hurting the community
-stability. This is an important issue which has not been addressed
-previously in the relevant literature. On the other hand, if
-communities bound the number of web services to ensure higher
-revenue, availability and response time could be negatively
-affected if some members encounter problems. This is because
-alternative web services for substitution will be limited.  This
-has also not been efficiently addressed in the related work.
-Consequently, community formation algorithms satisfying some
-desirable properties such as community stability and overall
-revenue are yet to be defined considering end users, community
-managers and service providers.
-
 \section{Motivation and Research Questions}\label{sec:researchquestions}
@@
 collaborate as long as they are getting more benefits and payoff.
-Our initial research question is: \emph{How can we model the
-community of agent-based services in order to maximize the utility
-of involved users, web services and community organizers?}
 
-In order to address this problem, recently
+Recently
 \cite{DBLP:conf/IEEEscc/LimTMB12,
@@
 working in the community, these agents, as profit maximizing
-entities, would just deviate and make their own group. So an
-important research question that we would like to address is:
-\emph{How can we model fair and stable communities as coalitions
-of agent-based web services?}
-
-%The consideration of those inputs is a significant
-%issue as existing web services can lose utility or payoff because
-%of the new member, which can results in an unhealthy and unstable
-%group. The problem comes from the fact that the existing members
-%should collaborate with the new web services, so probably their
-%performance as a group can suffer. Existing members may even
-%deviate and try to join other communities if they are unsatisfied.
-%Those considerations of forming stable and efficient coalitions
-%are the main contributions of our paper.
-
-%However, a high
-%performing web service could deviate anytime it finds itself
-%unsatisfied within the community instead of adjusting its service
-%parameters.
+entities, would just deviate and make their own group.
 
@@
 settings?}
-
-% ooooooold
-%\indent When monitoring a dialogue between two or more agents, there are many question that should be answered. In this thesis, we are interested in answering the following questions:
-%\begin{itemize}
-%\item How much are agents certain about selecting a move at each dialogue step?
-%\item How much are agents certain about their dialogues?
-%\item How good are agents in the real dialogue (i.e. the effective dialogue)?
-%\item How far are agents from the right dialogue (i.e. the best dialogue given the knowledge bases of the participants)?
-%\end{itemize}
-%Answering these questions is undoubtedly complex. Therefore, we do not expect a comprehensive answer to all these questions.
 
@@
 
-\section{Proposal Organization}\label{sec:outline}
+\section{Report Organization}\label{sec:outline}
 The rest of the proposal is organized as follows: We present in

### 2014-03-03 seminar/seminar_report/chapter3.tex
change

@@
 To this end, our communities will reward and valuate web services in the community
+
+\section{Competitive behaviour of services within communities}\label{s:coop}
+
+In previous sections, our focus was on community formation and we the focus was on cooperative behaviour of the web services as agents.
+However competition within cooperative environments, for business agents having different set of capabilities.
+Within communities, those services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}.
+In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite.
+However, the same reason of providing similar functionalities can lead services to cooperate because they can replace each other in case of failure or unavailability, and services can do better in a coalition structure.
+Analyzing services competition and cooperation strategies within communities is still an open problem that motivates the research described in this section.
+we propose a mechanism within which service agents
+in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this paper interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task.
+We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate).
+In the proposed system, We explore details behind the strategic decision making procedures and enable service agents to apply different techniques to constrain high efficiency and obtain the maximum utility.
+We investigate services' expected payoffs and the involved probabilities that are used to choose over the two interacting strategies.
+
+\subsection{The Proposed Framework}\label{The Proposed Framework}
+In this section, we first present the architecture of the proposed
+model. We explore the characteristics of intelligent service
+agents and their network. We link this architecture to the
+implemented system where we investigate the services' coopetitive
+attitudes. We compute the involved system parameters and explain
+the services' interactive strategy profiles by highlighting their
+coopetitive choices.
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=1]{architecture++.eps}
+\caption{Services are partitioned into competitive and cooperative
+sets. Competitive services may get tasks directly from the master
+agent and they can share it with other cooperative services in
+their collaborative networks within the same community.}
+\label{architectureFigure}
+\end{figure}
+
+\subsubsection{The Architecture}
+
+Figure \ref{architectureFigure} illustrates the architecture of a
+typical community aggregating a number of services with different
+interactive strategies. Some of them compete for the task where
+they directly deal with the master. Some others cooperate in the
+associated task where they only deal with the competed service as
+the task leader and do not directly interact with the master (the
+master deals only with the service that has bid for the task,
+which is responsible of choosing its collaborative network). In
+both sets, some service agents are for certain moments out of any
+collaboration network. We highlight details of the interactive
+strategies in the rest of this section.
+%Figure \ref{algorithm1} %exposes the details of task allocation mechanism that is used to select the web services.
+In the proposed system, the master sorts the competing services
+(i.e., the bidders) based on some parameters (such as reputation)
+that we explain in the rest of this section. The winner to which
+the master allocates the task is the bidder
+service agent that is ranked first. %If the web
+%service is busy or unwilling to take the task, the master
+%allocates the task to the second competing web service in the
+%list.
+There is a chance that some tasks could not be assigned to any
+service. These tasks are accumulated in the task pool to be
+allocated in the next task allocation round. Upon allocation of
+the task, the service is responsible for offering the required QoS
+that is stated in the task being generated by a consumer.
+Afterwards,  the master rewards or penalizes the competing
+service by upgrading or degrading its reputation according to the
+offered QoS compared with the required one. This comparison
+influences the sorting mechanism used by the master to allocate
+the tasks in further task allocation rounds.
+
+%ok til here
+
+\subsubsection{System Parameters}
+In this section, we demonstrate the involved parameters and their
+corresponding formulations and explanations.
+
+\textbf{Task QoS} ($T_{QoS}^r$) is the required QoS metric for a
+specific task $r$. Users define tasks with specific QoS
+requirements such as response time, availability, and
+successability (or accuracy). We aggregate and
+normalize these metrics to a value between $0$
+and $1$. %Throughout this paper, we refer to this value as
+%$T_{QoS}$.
+
+\textbf{Service QoS} ($QoS_w^r$) is the QoS provided by the
+service $w$ after performing the task $r$. Again, the metrics that
+contribute in computing this QoS are aggregated and normalized to
+a value between $0$ and $1$. The offered quality might or might
+not meet the required task quality $T_{QoS}^r$. In the latter
+case, the service user would be disappointed and a negative
+satisfaction feedback is expected. In our proposed system, both
+cases are considered when calculating the services' reputation.
+
+%\textbf{NTD} is the number of tasks completed by a web service.
+
+\textbf{Budget} ($B_w^t$) is the amount of money the service agent
+$w$ has in its disposal during the window time $t$ (i.e.,
+$[0,t]$), which helps pay for the community membership fees
+($\epsilon$) and is one of the parameters that the service agent
+considers when deciding about getting involved in a competition or
+not.
+
+\textbf{Reputation} ($Rep_w^t$) is a significant factor in any
+online community \cite{Fouss:2010:PRM:1751668.1751727}. Without a reputation enabling
+mechanism, users cannot differentiate among services, specially
+the ones which offer the same type of service. Reputation
+mechanisms usually aggregate users' experiences and in our case it
+strongly depends on QoS that each service provides. Users define
+tasks, each one with specific quality $T_{QoS}^r$, so that after
+performing a certain number of tasks, each one with $QoS_w^r$,
+during a window time $t$, the reputation of $w$ gets evaluated by
+the master agent. $Rep_{w}^{t}$ refers to the reputation of $w$
+during that window time $t$.
+
+In Equation \ref{repr}, we compute the reward that the master
+computes considering the task $r$'s QoS $T_{QoS}^r$ compared with
+the service offered quality $QoS_w^r$. In case the offered quality
+meets user expectations, the reward value would be positive. In
+this system, we consider a small value as default rewards $\eta$
+which the master considers together with the proportional level of
+satisfaction as a weighted value (by $\upsilon$). In this case,
+the higher the offered quality, the more weighted reward. In case
+the offered quality did not meet the user expectations, the reward
+would be negative. A default penalty value $\rho$ (where
+$\rho>\eta$) together with the weighted proportional difference
+are therefore considered. The idea is to harshly penalize the
+services rather than rewarding them. To this end, rational service
+agents should carefully analyze their capabilities once the
+available tasks are announced. Equation \ref{reward} computes the
+obtained reward by $w$ during the window time $t$ considering the
+set $task_w^t$ of tasks performed by $w$ during the window time
+$t$. In our proposal, service agents have the goal of increasing
+their budget, which is directly related to their reputation. Thus,
+they have to decide strategically how to maximize this value.
+
+\begin{equation} \label{repr}
+reward_w^r = \begin{cases}
+\eta + \upsilon \frac{QoS_w^r}{T_{QoS}^r+QoS_w^r}   & \text{if $T_{QoS}^r\leq QoS_w^r$;}\\
+-(\rho +  \upsilon \frac{T_{QoS}^r}{T_{QoS}^r+QoS_w^r} ) & \text{otherwise.}\\
+\end{cases}
+\end{equation}
+
+\begin{equation} \label{reward}
+reward_w^t =
+\begin{cases}
+\frac{\sum_{r \in
+task_w^t}reward_w^r}{|task_w^t|}& \text{if $task_w^t \neq \emptyset$;}\\
+0 & \text{otherwise.}\\
+\end{cases}
+\end{equation}
+
+The assigned reputation value is updated by the computed reward
+value. The computed reputation of services is bounded by the
+minimum and maximum reputation values $0$ and $1$. % to constrain
+%the balance the cooperative community of web services. The updated
+Let $\Gamma = Rep_{w}^{t} + reward_w^t$. The updated reputation
+value is then computed as follows:
+
+\begin{equation}\label{repz}
+%Rep_{w}^{t+1} = Rep_{w}^{t} + reward
+%\end{equation}
+%\begin{equation*}
+Rep_{w}^{t+1} = \begin{cases}
+
+\Gamma & \text{if $ 0 \leq \Gamma \leq 1$;}\\
+0  & \text{if $\Gamma < 0$;}\\
+1 & \text{if $\Gamma > 1$.}\\
+\end{cases}
+\end{equation}
+%
+For new services with no previous reputation value, we use the
+bootstrapping trust technique proposed in \cite{conf/icwe/YahyaouiZ11}. This
+technique consists in giving the new services a chance and observe
+their behaviors for a period of testing time. The observation
+sequence is modeled as a hidden Markov model that is used to
+detect the behavior of the service by comparing the observation
+behavior against pre-defined trust patterns. Based on the matching
+result, an initial value is assigned to the service. Using this
+initial reputation value, services quickly converge to their
+actual and stable values using the update function.
+
+\begin{proposition}\label{Complexity-Rep}
+$Rep_{w}^{t}$ can be computed in time $O(|t|)$, i.e., in time
+linear in the size of the window $t$.
+\end{proposition}
+
+\begin{proof}\footnote{In this paper, we
+assume that the common arithmetic and elementary functions, such
+as multiplication, division and trigonometric functions can be
+computed in time $O(1)$ as they operate on inputs of fixed sizes.}
+The function $Rep_{w}^{t}$ is recursive on $t$, but the algorithm
+works by storing the last calculated reputation value in a
+variable, so it will not be recalculated again at each iteration.
+However, the calculation of $reward_w^t$ is needed. Since the
+function $reward_w^t$ can be computed in time linear in the number
+of tasks (see Equations \ref{repr} and \ref{reward}), which in
+turn is linear in the size of the window time, the result follows.
+$\Box$
+\end{proof}
+
+\textbf{Growth Factor} ($G_w^t$) is a parameter which declares
+services' performance based on their recent strategies and
+activities. Growth factor is relative to services' reputation
+$Rep_w^t$, QoS during the window time $t$ $QoS_w^t$, and budget
+$B_w^t$. This factor is the main variable a typical service uses
+to decide about which strategy to adopt. The details about the
+decision making process are described in Section \ref{Theoretical
+Results}. We use Equation \ref{eq:growthfactor} to compute the
+growth factor $G^t_w$ of the service $w$ during the window time
+$t$ as the average of the three aforementioned parameters, where
+$n_t$ is the total number of offered tasks to the whole community
+during the
+window time $t$, %(we consider the time window $t$ large enough so
+%that $n_t \neq 0$),
+$\mu_w$ is the mean received service fee, and $\epsilon$ is the
+cost of community membership.
+
+\begin{equation}\label{eq:growthfactor}
+G^t_w = \frac{Rep^t_w + QoS_w^t+\frac{B_w^t}{n_t  \mu_w -
+\epsilon}}{3}
+\end{equation}
+\begin{equation*}
+\mu_{w} \in\{\mu_{w, CM}, \mu_{w, CO}\},~~~QoS_w^t =
+\begin{cases} \frac{\sum_{r \in
+task_w^t}QoS_w^r}{|task_w^t|}& \text{if $task_w^t \neq \emptyset$;}\\
+0 & \text{otherwise.}\\
+\end{cases}
+\end{equation*}
+
+This equation is designed so that it satisfies the following
+desirable properties:
+
+\begin{enumerate}
+
+\item The growth factor function should be monotonically
+increasing in the offered quality of service $QoS_w^t$.
+
+\item The growth factor function should be monotonically
+increasing in the service's reputation $Rep^t_w$.
+
+\item The growth factor function should be monotonically
+increasing in the budget $B_w^t$ if the maximum possible profit is
+positive and monotonically decreasing in $B_w^t$ if the maximum
+possible profit is negative. This property reflects the idea that
+the budget contributes in the increase of the growth factor as far
+as there is a chance to make profit. In fact, the contribution of
+the budget $B_w^t$ in the calculation of the growth factor should
+be proportional to the maximum possible profit $n_t \mu_w -
+\epsilon$ where the service $w$ receives all the offered tasks
+during the window time $t$.
+
+\end{enumerate}
+
+  % if the profit $\beta_w$ made by the web service $w$
+%considering the mean received service fee $\mu_w$ and the cost of
+%community membership $\epsilon$ is positive.
+It is easy to show that Equation \ref{eq:growthfactor} satisfies
+the three aforementioned properties by calculating the partial
+derivatives $\partial G^t_w$ of this function in 1) $QoS_w^t$
+($\frac{\partial G^t_w}{\partial QoS_w^t} = \frac{1}{3} $); 2)
+$Rep^t_w$ ($\frac{\partial G^t_w}{\partial Rep^t_w} = \frac{1}{3}
+$); and 3) $B_w^t$ ($\frac{\partial G^t_w}{\partial B_w^t} =
+\frac{1}{3 (n_t \mu_w - \epsilon)} $). Thus, the sign of the two
+first partial derivatives is positive and the sign of
+$\frac{\partial G^t_w}{\partial B_w^t}$ depends on the sign of the
+maximum profit $n_t \mu_w - \epsilon$, so we are done. The mean
+service fee depends on the strategy adopted by the service because
+a competitive service receives higher fees $\mu_{w, CM}$ compared
+to a cooperative one $\mu_{w, CO}$ ($\mu_{w, CM} > \mu_{w, CO}$).
+The motivation behind this is that a competitive service for a
+given task is the leader for that task while other cooperative
+services are performing specific subtasks as asked by the leader.
+
+\begin{proposition}\label{Complexity-Growth_Factor}
+$G_w^t$ can be computed in time linear in the size of the window
+$t$.
+\end{proposition}
+
+\begin{proof}
+As shown in the second part of Equation \ref{eq:growthfactor}, the
+function $QoS_w^t$ can be computed in time linear in the number of
+tasks, which in turn is linear in the size of the window time.
+Since $B_w^t$ is constant, the result follows from Proposition
+\ref{Complexity-Rep}. $\Box$
+\end{proof}
+
+\subsubsection{Service Interactive Strategies}
+
+The main goal of each individual service agent is to increase its
+income (payoff). This income can be earned from tasks (or
+requests) done by this service. In our model, services can decide
+to compete to get a task from the master agent or to cooperate
+with other services within a given collaborative network (the way
+a collaborative network is set by a leader is based on the
+cooperative services reputation and their QoS parameters that
+should coincide with the required QoS). Therefore we define two
+types of service strategies. First, when a service has higher
+level of confidence based on its growth factor, it can compete to
+get a task from the master and adopts the competitive strategy.
+Second, when the service agent has a lower level of confidence
+that it does not feel capable to compete, it waits for some other
+services to cooperate with to perform some tasks \footnote{Through
+the paper, requests or tasks are supposed to be decomposable.},
+and thus it adopts the cooperative strategy. Services estimate the
+outcome of all the strategies and choose one of them accordingly.
+This decision is not static but can change over time so service
+agents can switch from one strategy to the other, and this dynamic
+attitude is referred to as coopetition.
 
@@
 can be lowered.
+
+\subsection*{Coopetitive behaviour of services within communities}\label{sb:resutlscoop}
+
+In this section, the objective is to investigate the effectiveness of the proposed strategic system in section \ref{s:coop}.
+
+We start our discussions with cumulative budget comparison
+regarding different communities within which services follow
+different reasoning techniques. Figure \ref{Graph1} part (a)
+illustrates three graphs for three different communities. Each
+community hosts services that follow different reasoning
+techniques: (1) a community that follows the interactive reasoning
+techniques presented in this paper (referred to as coopetitive);
+(2) a community that follows a stochastic reasoning technique so
+decisions about selecting competitive or cooperative strategies
+are totally random (referred to as random coopetitive); and (3) a
+competitive community where all services follow the competitive
+strategy (referred to as competitive). The proposed model's
+reasoning mechanism enables services to effectively select their
+interacting strategies and the obtained budget represents the best
+outcome over the strategic decision making procedure they run all
+the time. This procedure avoids cases where a service selects the
+competitive strategy but gets refused to obtain a task from the
+master. The procedure allows services to make decisions that
+maximize their utilities, so that if the service cannot compete,
+the procedure would suggest to collaborate, which is better than
+competing and failing to obtain the task. In this case (i.e.,
+competing and not getting the task), the service stays idle but
+still pays the community membership fee, which means losing
+utility. The developed strategic decision making mechanism leads
+some service agents to follow cooperative strategies that overall
+maintain an optimal community budget. In the same figure, we
+observe the cumulative budget of a community where services follow
+random interacting strategies. The outcome is clearly lower
+because services at each run randomly decide over their acting
+strategies. This potentially influences the community budget
+because a low quality service if randomly selects to follow the
+competitive strategy, it will fail to perform a task with high QoS
+requirements. This kind of strategy selection is totally
+stochastic while the task allocation algorithm follows a logical
+path. The ideal system is the one that analyzes the optimal
+strategic path and consistently follows strategies that bring
+maximum outcome. The result regarding the community that follows
+the random strategy shows how stochastic decision making degrades
+the community budget, but still this result outperforms the one of
+the purely competitive community. In this purely competitive case,
+all the services follow the competitive strategy and the frequency
+of getting rejected from a task is relatively high. In a community
+with limited number of tasks, the competitive strategy for all
+services highly influences the community budget because a
+potential group of services are losing at every run.
+
+The results illustrated in Figure \ref{Graph1} part (a)  verify
+the importance of the strategic decision making procedure to
+logically decide over the possible competitive and cooperative
+choices. Figure \ref{Graph1} part (b) illustrates communities
+average reputation of involved services. The graphs represent the
+influence of the rewards that the master agent uses to encourage
+highly capable services to compete for a task. As for the
+cumulative budget, we observe that the coopetitive community
+outperforms the random coopetitive and competitive communities in
+terms of average reputation. The proposed model's average
+reputation increases because services follow optimal strategies
+where they can perform better so obtain higher rewards. For the
+same reasons as for the cumulative budget, the average reputation
+of the random coopetitive community
+outperforms the one of the competitive community. %The idea is to balance web
+%services' strategies to maintain optimal community budget.
+
+\begin{figure}%[h]
+%\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[scale=0.47]{graphbgtmed.eps}
+\includegraphics[scale=0.47]{graphrep.eps}
+\caption{Part (a): Cumulative community budget comparison. Part
+(b): Average community reputation comparison over different
+strategic decisions.} \label{Graph1}
+\end{figure}
+
+ %Figure \ref{Graph2} part (a) illustrates the reputation of the proposed $Coopetitive$ community where
+ %we highlight the range of reputation change in the community.
+The vertical lines denote the range of %reputation that is associated with the master web service.
+The rewards and penalties applied to %different
+% web services show that the master web service over runs extends the reputation range and takes %control of the whole community. In the developed model, web services are encouraged to choose
+ %optimal strategies. This is maintained over growth factor comparison of the $Coopetitive$ web %services.
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=0.35]{graphbgtmed3set.eps}
+\includegraphics[scale=0.35]{graphbgthigh.eps}
+\includegraphics[scale=0.35]{graphbgtveryhigh.eps}
+\caption{High membership fees or less task income impacts on
+different selection strategies. Part (a) Medium membership fee.
+Part (b) High membership fee. Part (c) Very high membership fee.}
+\label{membership_fee_graph}
+\end{figure}
+
+In Figure \ref{membership_fee_graph}, we analyze the scenario
+where the membership fee is high, which is analogous to situations
+where the task income is low. We need to verify how well services
+can perform in these situations. Figure \ref{membership_fee_graph}
+part (a) depicts the results in a normal scenario. In part (b), we
+have increased the membership fee to the high amount of 5 units
+per run. Services will need to pay $5$ units on each iteration of
+tasks being offered. As results, the strategic coopetitive
+decision making process helps services make benefits, but
+stochastic and compete methods lead to lose income since making
+mistakes and trying to compete for jobs the services cannot afford
+while having to pay higher membership fees is making them lose
+budget in a faster pace. In part (c), the membership fee is higher
+than an average income that
+a task can generate. %It might not be rational for selfish
+%self-interest web services to stay in these communities from the
+%utility perspective, but as mentioned there might be other
+%political reasons they might need to stay in these communities. As
+The simulation shows that the stochastic and compete strategies
+make services budget decreases drastically. However, our strategic
+coopetitive decision making process loses budget in a slower pace.
+
+In Figure \ref{Graph2} parts (a) and (b), we observe the
+competitive and cooperative probability of four different services
+where two of them ($w_1$ and $w_3$) are following optimal
+strategies as suggested by our model (competitive for $w_1$ and
+cooperative for $w_3$) and the two others ($w_2$ and $w_4$) are
+following non-optimal strategies, which are the opposite of what
+our model suggests. Over elapsing runs, services that follow
+optimal strategies bring best reputation. In fact, the master
+agent rewards the high quality service that chooses the
+competitive strategy, cooperates with other peers and successfully
+accomplishes the task. In this system, the reputation regarding
+such a service is increasing over time and the possibility of
+allocating further tasks is increasing as well. By increasing the
+growth factor, such a service (here shown as $w_1$) increases the
+probability of selecting the competitive strategy. On the other
+hand, the other service (here shown as $w_2$) that is incapable of
+competing is penalized by the master agent because the offered
+quality might not meet the required task quality. Thus, $w_2$
+degrades its growth factor by following the competitive strategy.
+As intelligent entity, this service is encouraged to change its
+strategy to the cooperative one and thus, its probability of
+selecting the competitive strategy is decreasing over time. We
+have similar results in Figure \ref{Graph2} part (b) regarding
+services $w_3$ and $w_4$ where unlike $w_4$, $w_3$ is
+strategically following the cooperative strategy allowing for an
+increase in the
+overall reputation. %Therefore, $w_4$ is more seeking the
+%competitive strategy where it can increase its growth factor.
+
+\begin{figure}[h]
+%\centering
+\includegraphics[scale=0.47]{graphcomp.eps}
+\includegraphics[scale=0.47]{graphcoop.eps}
+\caption{Reputation progress of four different services: W$_1$ and
+W$_3$ are following our strategic decision model; W$_2$ and W$_4$
+are following the opposite.} \label{Graph2}
+\end{figure}
+
+In our model, services are managed by selfish agents in the sense
+they try to maximize their own utilities. We analyze how their
+strategies affect the social welfare, and from user's and
+community's point of view how good the tasks are being performed.
+This directly impacts user's satisfaction and community's
+reputation in general. The Higher quality and quantity of tasks
+performed leads to higher user's satisfaction for the community
+which results in better reputation for the community. The results
+in Figure \ref{graph_task} show the quality and quantity of tasks
+being done successfully in three communities adopting the three
+different aforementioned strategy decision algorithms. Part (a)
+depicts the number of tasks successfully done. When services are
+not capable of performing tasks alone and decide to compete for
+tasks with high QoS requirements, they usually fail to perform the
+task. However, if they opt for cooperating although they have less
+income, they have higher chance of performing tasks
+collaboratively with other services. Figure \ref{graph_task}, Part
+(b) shows the probability of successfully performing tasks, which
+influences users' satisfaction. The results show that services
+using our coopetitive strategy when deciding whether to compete or
+cooperate have higher chance to get high satisfaction ratio
+compared to stochastic and compete strategies. The quality of
+tasks performed are depicted in Figure \ref{graph_task} Part (c).
+The figure shows the average QoS of tasks successfully
+performed. %Collaborating increases the performed QoS of tasks,
+%therefore forming collaborative groups improves user satisfaction.
+As clearly confirmed by the simulation, the coopetitive community
+outperforms the stochastic and compete communities.
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=0.35]{graphtaskdone.eps}
+\includegraphics[scale=0.35]{graphtasksatisfaction.eps}
+\includegraphics[scale=0.35]{graphavgqostask.eps}
+\caption{Overall performance from community's point of view. Part
+(a) Total number of tasks successfully done. Part (b) Ratio of
+tasks satisfied with required QoS. Part (c) Average QoS of
+performed tasks.} \label{graph_task}
+\end{figure}

### 2014-03-03 seminar/seminar_report/chapter1.tex
changes

@@
 web-based applications has significantly influenced the way web
-services are engineered. Web services provide a set of stateless
-software functions accessible at a network address over the web.
-The recent developments are shifting web services from passive and
-individual components to autonomous and group-based components
-where interaction, composition, and cooperation are the key
-challenges \cite{ICWS2011-1,SCC2011-1}. The main objective is to
-achieve a seamless integration of business processes, applications
-and web services. Delivering high quality services considering the
-dynamic and unpredictable nature of the Internet is still a very
-critical and challenging issue.
-
-Typically, web services are business applications deployed as
-autonomous and interoperable agents \cite{Alescio}. In fact, the
-W3C consortium defines a web service as ``an abstract notion that
-must be implemented by a concrete agent''. However, the web is
-stocked with agent-based services that offer similar business
-functionalities, which leads to service consumers having
-difficulties in choosing the most appropriate agents to interact
-with.
-
+services are engineered. 
+%Web services provide a set of stateless
+%software functions accessible at a network address over the web.
+%The recent developments are shifting web services from passive and
+%individual components to autonomous and group-based components
+%where interaction, composition, and cooperation are the key
+%challenges \cite{ICWS2011-1,SCC2011-1}. The main objective is to
+%achieve a seamless integration of business processes, applications
+%and web services. Delivering high quality services considering the
+%dynamic and unpredictable nature of the Internet is still a very
+%critical and challenging issue.
+%Typically, web services are business applications deployed as
+%autonomous and interoperable agents \cite{Alescio}. In fact, the
+%W3C consortium defines a web service as ``an abstract notion that
+%must be implemented by a concrete agent''. However, the web is
+%stocked with agent-based services that offer similar business
+%functionalities, which leads to service consumers having
+%difficulties in choosing the most appropriate agents to interact
+%with.
 The need for highly available and responsive services has called
@@
 but probably different non-functional quality attributes, which
-form the QoS parameters. When communities are used, users send
-their requests to the masters of those communities, which are
-responsible of managing the communities, forwarding the requests
-to the suitable member web services and checking the credentials
-of those members. Communities aim to provide higher service
+form the QoS parameters. 
+%When communities are used, users send
+%their requests to the masters of those communities, which are
+%responsible of managing the communities, forwarding the requests
+%to the suitable member web services and checking the credentials
+%of those members.
+Communities aim to provide higher service
 availability and performance than what individual web services can
-provide. The high availability of services and the community
-resilience to failure are guaranteed since web services can
-cooperate and replace each other within the same community and
-since there is no single point of failure in the communities
-architecture.
+provide. 
+%The high availability of services and the community
+%resilience to failure are guaranteed since web services can
+%cooperate and replace each other within the same community and
+%since there is no single point of failure in the communities
+%architecture.
 
-\section{Motivation and Research Questions}\label{sec:researchquestions}
+\section{Motivation and Research Objectives}\label{sec:motexample}
 
@@
 parties involved in the decision making process about the
-community management. Most of the recent work on communities of
-services are either user-centric and focus on user satisfaction
-\cite{Chun02user-centricperformance} or system-centric and focus
-on the whole system throughput, performance and utilization. There
-are many contributions in distributed, grid, cluster and cloud
-services which are system-centric. However, in real world
-environments and applications, both users and service providers
-are self-interested agents, aiming to maximize their own profit.
-In those environments, both parties (users and services) will
-collaborate as long as they are getting more benefits and payoff.
-
-Recently
-\cite{DBLP:conf/IEEEscc/LimTMB12,
-DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
-mechanisms to help users and services maximize their gain. A
-two-player non-cooperative game between web services and community
-master was introduced in
-\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In
-\cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
-for selecting web services has been proposed. In this approach,
-the authors proposed a web service selection process that the
-community masters can use. The approach considers the efficiency
-of all the three involved parties, namely users, web services and
-communities. The issue with these solution concepts is that they
-consider community as a whole and model it as one entity in their
-formulations. A community master decides on behalf of all the
-members using an aggregated function of parameters. This can hurt
-the overall revenue for some individual web services, or even a
-subset of web services. Those services can collude and form their
-own community and gain more, instead of having to adjust and share
-their resources with other members. Another important issue which
-needs to be considered is the community stability. In community of
-web services, the members and community organizers collaborate to
-perform tasks. Having jointly completed a task and generated
-revenue, they need to agree on some reasonable method of dividing
-profits (or tasks) among themselves. This is a key issue for the
-group stability still to be investigated. If the revenue sharing
-mechanism is not fair enough for any subset of web services
-working in the community, these agents, as profit maximizing
-entities, would just deviate and make their own group.
-
-In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
-autonomous web services based on coalitional game theory has been
-introduced. The authors have proposed an algorithm to reach
-individually stable coalition partition for web services in order
-to maximize their efficiency. The communities choose new web
-services on the promise that it would benefit the community
-without decreasing any other web service's income. In their model,
-the worth of community is evaluated with high emphasis on the
-availability metric and considering price and cost values only.
-The community structure is based on a coordination chain, where a
-web service is assigned as a \emph{primary} web service and the
-community task distribution method will initially invoke the
-primary web service. Only if the primary web service is
-unavailable, the next backup web services in the ordered
-coordination chain will be invoked. However, in cooperative
-models, it is preferred to have a real and active cooperative
-activity engaging all agents to perform the tasks more
-efficiently. Thus, the final research question we would like to
-work on is: \emph{How can we model and analyze the cooperation
-among the community members in realistic, applicable and practical
-settings?}
-
-\section{Research Objectives and Contributions}\label{sec:motexample}
+community management.
 
@@
 \section{Report Organization}\label{sec:outline}
-The rest of the proposal is organized as follows: We present in
+The rest of the report is organized as follows: We present in
 Chapter~\ref{sec:MAS} the background needed for our research along

### 2014-03-03 seminar/seminar_report/chapter2.tex
changes
change

@@
 
-In this chapter, we briefly review web services, then we introduce
+In this chapter then we introduce
 the concept of communities of web services, their architecture and
@@
 \subsection{Web Service Communities}\label{sec:CWSDefinition}
-Community refers to ``the condition of sharing or having certain
-attitudes and interests in common'' or ``a group of people living
-in the same place or having a particular characteristic in
-common''\footnote{Oxford Dictionaries}. In
-\cite{DBLP:journals/internet/BenatallahSD03,
+ In \cite{DBLP:journals/internet/BenatallahSD03,
 Zeng:2003:QDW:775152.775211}, the authors introduce community of
 web services as collection of cooperative web services with common
-functionalitiers but different QoS metrics. Therefore
+functionalities but different QoS metrics. Therefore
 $communities$ are differentiated from $composition$ types of web
@@
 
-Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
-then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
+Maamar et al. in \cite{DBLP:journals/ijebr/MaamarSTBB09}
 proposed an architecture utilizing \emph{Contract-Net} protocol
@@
 
-        \begin{figure}
-            \begin{center}
+%        \begin{figure}
+%            \begin{center}
 %            \includegraphics[width=16cm]{Figures/wsarch.eps}\label{wsarch}
-            \includegraphics[width=16cm]{Figures/wsarch.eps}\label{wsarch}
-            \caption{Communities of Web Services Architecture as Proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}}
-            \end{center}
-        \end{figure}
-
-Figure 1 %\ref{wsarch}
-depicts the basic architecture of
-communities of web services. The main components of the
-architecture are: 1) the providers of web services; 2) UDDI
-registries; and 3) communities platform. Communities abstract the
-same model of defining, announcing and invoking web services. They
-also adopt the same protocols that standard web services use with
-UDDI registries. UDDI is a platform-independent XML based registry
-list which facilitates worldwide web service discovery.
+%            \caption{Communities of Web Services Architecture as Proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}}
+%            \end{center}
+%        \end{figure}
+%
+%Figure 1 %\ref{wsarch}
+%depicts the basic architecture of
+%communities of web services. The main components of the
+%architecture are: 1) the providers of web services; 2) UDDI
+%registries; and 3) communities platform. Communities abstract the
+%same model of defining, announcing and invoking web services. They
+%also adopt the same protocols that standard web services use with
+%UDDI registries. UDDI is a platform-independent XML based registry
+%list which facilitates worldwide web service discovery.
 
@@
 \mathbb{R}^N$ is the amount of payoff being distributed among the
-members of the coalition $N$. The payoff vector satisfies two
-conditions:
-
-        \begin{itemize}
-            \item $x_i \geq 0$ for all $i \in N$, and
-            \item $\sum_{i \in N} x_i \leq v(N)$
-        \end{itemize}
-
-        The second criteria is called the \emph{feasibility} condition,
-        according to which, the payoff for each agent cannot be more than
-        the coalition total gain. A payoff vector is also \emph{efficient}
+members of the coalition $N$.  A payoff vector is also \emph{efficient}
 if the payoff obtained by a coalition is distributed amongst the
-        coalition members: $\sum_{i \in N} x_i = v(N)$. This definition of
-        the characteristic function works in \emph{transferable utility}
-        (TU) settings, where utility (i.e., payoff) is transferable from
-        one player to another, or in other words, players have common
-        currency and a unit of income that is worth the same for all players
-        \cite{myerson1991game}.
+coalition members: $\sum_{i \in N} x_i = v(N)$.
 
@@
             \emph{Shapley value} is a unique and fair solution concept for
-            payoff distribution among the members of the coalition. It
-            basically rewards members with the amount of marginal contribution
-            they have to the coalition.  It checks the contribution of member $i$ by adding the agent, to all possible subsets
-            of coalitions $S$, where $S \subseteq N\backslash\left\{i\right\}$. If he is added to the set $S$, his
-            contribution to the coalition is $v(S \cup \left\{i\right\}) - v(S)$. Average marginal contribution of agent $i$'s
-            is calculated by averaging this value over all possible subsets of $N$, in $Shapley value$ equation (\ref{eq:shapley}).
+            payoff distribution among the members of the coalition.
 
@@
             deviating and making their own coalition $\sum_{i \in S^\prime}
-            x_i \geq v(S^\prime)$. The sum of payoffs of the players in any
-            sub-coalition $S$ is at least as large as the amount that these
-            players could earn by forming a coalition by their own. In a
-            sense, it is analogue to Nash equilibrium, except that core is
-            about deviations from groups of entities. The core is the
-            strongest and most popular solution concept in cooperative game
-            theory. However, its computation is a combinatorial problem and
-            becomes intractable as the number of players increases. The core
-            of some real-world problem games may be empty, which means having
-            the characteristic function of the game $(N,v)$, there might be no
-            possible distribution of payoff assuring stability of subgroups.
+            x_i \geq v(S^\prime)$.
 
@@
         if weights of all the edges in graph are all positive, the Shapley value can be computed in time $O(n^2)$.
-        However, this representation is not complete, some games cannot be represented by a induced subgraph game \cite{conf/aaai/YokooCSOI05}.
-
-        Ketchpel introduces the Bilateral Shapley Value (BSV) \cite{conf/aaai/Ketchpel94a} for coalition games with general valaution functions.
-        It reduces the combinatorial complexity of the computation of the Shapley value, breaking the community to multiple disjoint set.
-        With backtracking and dynamic programming like methods, they merge and store the marginal contribution of disjoint coalitions,
-        reducing the overall complexity of the algorithm. However, the solution is still NP-Complete and BSV time and space complexity grows exponentially.
 
@@
 This can again be seen as an external party, trying to stabilize the coalition by imposing some \emph{tax} on deviation.
-Taxation and subsiding as methods of stabilizing cooperative games have been studied in \cite{RePEc:spr:jogath:v:38:y:2009:i:1:p:3-16, RePEc:mse:cesdoc:12022r, Bachrach:2009:CSC:1692490.1692502, conf/ijcai/MeirRM11}.
-
-\section{Related Work}\label{sec:BRRelatedWork}
-
-The idea of grouping web services within virtual structures was
-fist proposed by Zeng et al. \cite{Zeng:2003:QDW:775152.775211}.
-The authors defined web service community as collection of web
-services providing the same functionality, but with different
-quality metrics. Medjahed and Boubuettaya
-\cite{journals/dpd/MedjahedB05} have proposed a framework and a
-community builder mechanism which uses semantic analysis,
-providing an ontological organization of web services having the
-same domain of interest. The community builder would suggest web
-services having similar operations to join the same community, or
-form their own community in case the semantic analysis cannot find
-any community that matches the service types.
-
-        Most of the recent work on communities of services are either
-        user-centric and focus on user satisfaction
-        \cite{Chun02user-centricperformance} or system-centric and focus
-        on the whole system throughput, performance and utilization. There
-        are many contributions in distributed, grid, cluster and cloud
-        services which are system-centric. However, in real world
-        environments and applications, both users and service providers
-        are self-interested agents, aiming to maximize their own profit.
-        In those environments, both parties (users and services) will
-        collaborate as long as they are getting more benefits and payoff.
-
-        In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
-        DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
-        users and services maximize their gain. A two-player
-        non-cooperative game between web services and community master was
-        introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this
-        game-theoretic model, the strategies available to a web service
-        when facing a new community are requesting to join the community,
-        accepting the master's invitation to join the community, or
-        refusing the invitation to join. The set of strategies for
-        communities are inviting the web service or refusing the web
-        service's join request. Based on their capacity, market share and
-        reputation, the two players have different set of utilities over
-        the strategy profiles of the game. The main limits of this game
-        model are: 1) its consideration of only three quality parameters,
-        while the other factors are simply ignored; and 2) the
-        non-consideration of the web services already residing within the
-        community. The game is only between the community master and the
-        new web service, and the inputs from all the other members are
-        simply ignored. The consideration of those inputs is a significant
-        issue as existing web services can lose utility or payoff because
-        of the new member, which can results in an unhealthy and unstable
-        group. The problem comes from the fact that the existing members
-        should collaborate with the new web services, so probably their
-        performance as a group can suffer. Existing members may even
-        deviate and try to join other communities if they are unsatisfied.
-        Those considerations of forming stable and efficient coalitions
-        are the main contributions of this research work.
-
-        In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
-        for selecting web services has been proposed. In this approach,
-        the authors proposed a web service selection process that the
-        community masters can use. The approach considers the efficiency
-        of all the three involved parties, namely users, web services and
-        communities. In this work, it is shown how the gains of these
-        parties are coupled together using a linear optimization process.
-        However, the optimization problem in this solution tends to
-        optimize some parameters considering all web services regardless
-        of their efficiency and contribution to the community's welfare.
-        Moreover, there are no clear thresholds for accepting or rejecting
-        new web services. The solution of the optimization problem could,
-        for instance, suggest web services already residing within the
-        community to increase or decrease their capacity to cover up the
-        weakness of other parties in the system. However, a high
-        performing web service could deviate anytime it finds itself
-        unsatisfied within the community instead of adjusting its service
-        parameters.
-
-        In \cite{10.1109/TSC.2012.12}, a cooperative scheme among autonomous
-        web services based on coalitional game theory has been introduced. The authors have proposed an algorithm to
-        reach individually stable coalition partition for web services in order to
-        maximize their efficiency. The communities choose new web services on the promise
-        that it would benefit the community without decreasing any other web service's
-        income. In their model, the worth of community is evaluated with high emphasis on
-        availability metric and considering price and cost values only. The community structure is based on a coordination chain,
-        where a web service is assigned as a \emph{primary} web service and the community task destribution
-        method, will initially invoke the primary web service and only if the primary web service is unavailable
-        will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to
-        have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays
-        with recent advancement in cloud and hardware infrastructures availability is becoming less of an issue. So the backup web services
-        in their model have a very low chance of getting jobs, especially the ones further in chain, which is huge waste of web services
-        capabilities.
-
-\section{Conclusive Remarks}
-
-        In this research work, we will use game theory to
-        propose a cooperative game model for the aggregation of web
-        services within communities. The solution concepts of our
-        cooperative game seeks to find efficient ways of forming
-        coalitions (teams) of web services so that they can maximize their
-        gain and payoff, and distribute the gain in a fair way among all
-        the web services. Achieving Fairness when the gain is distributed
-        among the community members is the main factor to keep the
-        coalition stable as no web service will expect to gain better by
-        deviating from the community. In other words, the coalition is made
-        efficient if all the members are satisfied. We first propose a
-        representation function for communities of web services based on
-        their QoS attributes. By using this function, we can evaluate the
-        $worth$ of each community of web services. When facing new
-        membership requests, a typical community master checks whether the
-        new coalition having the old and new set of web services will keep
-        the community stable or not. The community master will reject the
-        membership requests if it finds out that the new coalition would
-        be unstable, preventing $any$ subset of web services from gaining
-        significantly more by deviating from the community and joining
-        other communities or forming new ones. The computation of
-        solutions for cooperative game theory problems is combinatorial in
-        nature and proven to be NP-complete \cite{Algorithmic}, making
-        this computation impractical in real world applications. However,
-        using the concepts of coalition stability, we propose
-        approximation algorithms running in polynomial time providing web
-        services and community masters with applicable and near-optimal
-        decision making mechanisms.
+Taxation and subsiding as methods of stabilizing cooperative games have been studied in \cite{RePEc:spr:jogath:v:38:y:2009:i:1:p:3-16, Bachrach:2009:CSC:1692490.1692502, conf/ijcai/MeirRM11}.
 

### 2014-03-03 seminar/seminar_report/chapter3.tex
changes

@@
 Web services come with different quality of service parameters.
-These parameters with a short description are listed in Table
-\ref{qosws}.
-
-\begin{table}[!t]
-\centering
-\caption{List of web service QoS parameters.}
-\begin{tabular}{|c|c||c|c|}
-\hline
-\textbf{Parameter} & \textbf{Definition} \\
-\hline\hline
-$Availability$ & Probability of being available during \\
-&a time frame \\
-$Reliability$ & Probability of successfully handling \\
-&requests during a timeframe\\
-$Successability$ & Rate of successfully handled requests \\
-$Throughput$ & Average rate of handling requests \\
-$Latency$ & The average latency of services\\
-$Capacity$ & Amount of resources available\\
-$Cost$ & Mean service fee \\
-$Regulatory$ & Compliance with standards, law and rules\\
-$Security$ & Quality of confidentiality \\
-&and non-repudiation\\
-\hline
-\end{tabular}
-\label{qosws}
-\end{table}
-
+These parameters include availability, reliability, successability, throughput, latency, capacity, cost, regulatory and security\cite{DBLP:conf/smc/Al-MasriM09a}.
 We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
@@
 community, each one of them comes with a given QoS denoted by
-$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain
-aggregation function of the parameters considered in Table
-\ref{qosws}. We use this quality output later in evaluating the
+$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain linear weight function of the parameters. We use this quality output later in evaluating the
 community \emph{worth} or \emph{payoff} function.
@@
 \begin{figure*}[!t]
-\centerline{\includegraphics[width=15cm]{Figures/archss.eps}}
+\centerline{\includegraphics[width=15cm]{community.eps}}
 \caption{Architecture of Web Service communities}
@@
 The total gain is function of quality ($QoS_{ws}$) and throughput
-($Th_{ws}$) of tasks being performed. As mentioned in section
-\ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain
-aggregation function of the parameters considered in Table
-\ref{qosws}. We have adopted a linear equal weight average over
-all QoS parameters listed in Table \ref{qosws} excluding the
+($Th_{ws}$) of tasks being performed. We have adopted a linear equal weight average over
+the QoS parameters excluding the
 $Throughput$ and $Cost$ parameters. A community has the option to
@@
 the community and distributes the requests and income among its
-community members (see Figure \ref{fig_sim1}).
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{Figures/s1.eps}`
-\caption{Web Services and A Grand Community}
-\label{fig_sim1}
-\end{figure}
+community members.
+
+%\begin{figure}[!t]
+%\centering
+%\includegraphics[width=3in]{Figures/s1.eps}`
+%\caption{Web Services and A Grand Community}
+%\label{fig_sim1}
+%\end{figure}
 
@@
 algorithm tractable.
-% so in our algorithm we check the core membership of this payoff vector.
-
-%\ref{eq:convex}.
-
-%\newtheorem{theorem}{Proposition}
-%\begin{theorem}[Einstein-Podolsky-Rosenberg]
-\begin{theorem}\label{proposition1}
-A game with a characteristic function $v$
-is convex if and only if for all $S$, $T$, and $i$ where $S
-\subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in
-N$,
-%For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
-\begin{equation}\label{eq:convex_snow}
-v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
-\end{equation}
-\end{theorem}
-
-%\begin{Proposition}\label{proposition} A game with a characteristic function $v$
-%is convex if and only if for all $S$, $T$, and $i$ where $S
-%\subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in
-%N$,
-%For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
-%\begin{equation}\label{eq:convex_snow}
-%v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
-%\end{equation}
-%\end{Proposition}
-
-\begin{proof}
-We first prove the ``only if'' direction:
-%\\$~~~~$\textbf{1}. ``only if'' direction:\\
-\\$~~~~$\ \textbf{1}. ``only if'' direction:\\
-%\setlength{\abovedisplayshortskip}{2pt}
-Assume:\\
-\vspace{-0.5cm}
-\begin{gather*}\label{convexsnowproof}
-v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\})
-- v(T)
-\\
-\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq v (T \cup \left\{i\right\}) + v(S)
-\end{gather*}
-
-Considering $S \subseteq T$:
-\setlength{\abovedisplayshortskip}{2pt}
-\begin{gather*}
-T \cup \left\{i\right\} = (S \cup \left\{i\right\}) \cup T
-\\
-S = (S \cup \left\{i\right\}) \cap T
-\end{gather*}
-
-By setting $A = S \cup \left\{i\right\}$ and $B = T$ we have:
-\setlength{\abovedisplayshortskip}{2pt}
-\begin{gather*}
-v(S \cup \left\{i\right\}) + v(T) \leq v (T \cup \left\{i\right\}) + v(S)
-\\
-\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq
-\\
-v((S \cup \left\{i\right\}) \cup T) + v((S \cup \left\{i\right\}) \cap T)
-\\
-\rightarrow v(A) + v(B) \leq v(A \cup B) + v(A \cap B)
-\end{gather*}
-Consequently, the game is convex.
-
-\textbf{2}. ``if'' direction:\\
-Assume the game is convex. Thus, for all $A, B \subset N$, we
-have: \setlength{\abovedisplayshortskip}{2pt}
-\begin{gather*}
-v(A) - v(A \cap B) \leq v(A \cup B) - v(B)
-\end{gather*}
-
-By setting $S \cup \left\{i\right\} = A$ and $T = B$ where $S \subseteq T$:
-\setlength{\abovedisplayshortskip}{2pt}
-\begin{gather*}
-v(S \cup \left\{i\right\}) - v((S \cup \left\{i\right\}) \cap T) \leq v(T \cup (S \cup \left\{i\right\})) - v(T)
-\\
-\rightarrow v(S \cup \left\{i\right\}) - v(S) \leq v(T \cup \left\{i\right\}) - v(T)
-\end{gather*}
-
-\end{proof}
-
-Thus, in order to keep the characteristic function convex, new web
-services should have more marginal contribution as the coalition
-size grows.
-
-Our algorithm works as follows. Given an  established community
-with a master and some member web services, a web service would send a \emph{join request} to join  the
-community. Ideally, the \emph{core}
-or \emph{$\epsilon$-core} stability of the group having this new
-member should be analyzed. As the normal core membership algorithm is computationally
-intractable, we exploit Proposition \ref{proposition1} and Equation
-\ref{eq:convex_snow} to check the convexity of our game having
-characteristic function where the new member is added. In the
-equation, let $C$  be our community members before
-having the new web service join the community. Let  ${i}$ be the new web
-service, and then verify the equation for $S$, setting $ S = T /
-W1 $ where $W1$ is the set of all possible subsets of the set $N$
-having the size $1$. We can relax the equation a bit by adding a
-constant $\epsilon$ to the left side of the equation. We call this
-method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
-satisfied for all $W1$, we let the new web service join our
-community, since the web service will contribute positively enough
-to make our new community stable. Since only subsets of size $1$
-are checked, the following Proposition holds.
-
-\begin{theorem}\label{complexity1}
-\emph{The run time complexity of Depth-1 Convex-Checker algorithm is
-$O(n)$.}
-\end{theorem}
-
-By this result, we obtain a significant reduction from $O(2^n)$,
-which is the complexity of checking all possible subsets of $N$.
-In our second method, we use the same algorithm, but this time we
-set $W2$ to be the set of all possible subsets of size two and one
-of the community $C$. We call this method \emph{Depth-2
-Convex-Checker} and its run time complexity is still
-linear:
-
-\begin{theorem}\label{complexity2}
-\emph{The run time complexity of Depth-2 Convex-Checker algorithm is
-$O(n^2)$.}
-\end{theorem}
-
-It is possible to develop an algorithm that continues the
-verification of this condition against subsets of size $3$,
-$4$, etc. until the algorithm gets interrupted.
 
@@
 multiple master web services, each of which is providing
-independent request pools (see Figure \ref{fig_sim2}). Identical
+independent request pools. Identical
 to the first scenario, master web services form coalitions with
@@
 
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3in]{Figures/s2.eps}
-\caption{Web Services and Many Communities}
-\label{fig_sim2}
-\end{figure}
+%\begin{figure}[!t]
+%\centering
+%\includegraphics[width=3in]{Figures/s2.eps}
+%\caption{Web Services and Many Communities}
+%\label{fig_sim2}
+%\end{figure}
 
@@
 
-This merge-and-split algorithm is designed to be adaptable to
-different applications. One major ingredient to use such an
-algorithm is a preference relation or well-defined orders proper
-for comparing collections of different coalition partitions of the
-same set of players. Having two partition sets of players, namely
-$P = {P_1,...,P_k}$ and $Q = {Q_1,...Q_l}$, one example would be
-to use the social welfare comparison $\sum^k_{i=1}v(P_i) >
-\sum^l_{j=1}v(Q_j)$. For our scenario, we use \emph{Pareto order}
-comparison, which is an individual-value order appropriate for our
-self-interest web services. In the Pareto order, an allocation or
-partition $P$ is preferred over another $Q$ if at least one player
-improves its payoff in the new allocation and all the other
-players still maintain their payoff ($p_i \geq q_i$ with at least
-one element $p_i > q_i$).
-
-The valuation function $v(C)$ for this scenario is the same as
-\emph{``Web Services and One Community''} scenario. However, in
-order to prevent master web services joining the same community,
-we set $v(C) = 0$ when $C$ has either none, or more than one
-master web service as member.
-
-In this scenario, as new web services are discovered and get ready
-to join communities, our algorithm keeps merging and splitting
-partitions based on the preference function. The decision to merge
-or split is based on the fact that all players must benefit. The
-new web services will merge with communities if $all$ the players
-are able to improve their individual payoff, and some web services
-may split from old communities, if splitting does not decrease the
-payoff of \emph{any} web service of the community. According to
-\cite{DBLP:journals/corr/abs-cs-0605132}, this sequence of merging
-and splitting will converge to a final partition, where web
-services cannot improve their payoff. More details of this
-algorithm and analysis of generic solutions on coalition formation
-games are described in \cite{DBLP:journals/igtr/AptW09}.
-
 \section{Taxation, Subsiding and Community Stability}\label{s:tax}
@@
 both sets, some service agents are for certain moments out of any
-collaboration network. We highlight details of the interactive
-strategies in the rest of this section.
-%Figure \ref{algorithm1} %exposes the details of task allocation mechanism that is used to select the web services.
-In the proposed system, the master sorts the competing services
-(i.e., the bidders) based on some parameters (such as reputation)
-that we explain in the rest of this section. The winner to which
-the master allocates the task is the bidder
-service agent that is ranked first. %If the web
-%service is busy or unwilling to take the task, the master
-%allocates the task to the second competing web service in the
-%list.
-There is a chance that some tasks could not be assigned to any
-service. These tasks are accumulated in the task pool to be
-allocated in the next task allocation round. Upon allocation of
+collaboration network. Upon allocation of
 the task, the service is responsible for offering the required QoS
@@
 %the balance the cooperative community of web services. The updated
-Let $\Gamma = Rep_{w}^{t} + reward_w^t$. The updated reputation
-value is then computed as follows:
-
-\begin{equation}\label{repz}
-%Rep_{w}^{t+1} = Rep_{w}^{t} + reward
+%Let $\Gamma = Rep_{w}^{t} + reward_w^t$. 
+%The updated reputation
+%value is then computed as follows:
+%
+%\begin{equation}\label{repz}
+%%Rep_{w}^{t+1} = Rep_{w}^{t} + reward
+%%\end{equation}
+%%\begin{equation*}
+%Rep_{w}^{t+1} = \begin{cases}
+%
+%\Gamma & \text{if $ 0 \leq \Gamma \leq 1$;}\\
+%0  & \text{if $\Gamma < 0$;}\\
+%1 & \text{if $\Gamma > 1$.}\\
+%\end{cases}
 %\end{equation}
-%\begin{equation*}
-Rep_{w}^{t+1} = \begin{cases}
-
-\Gamma & \text{if $ 0 \leq \Gamma \leq 1$;}\\
-0  & \text{if $\Gamma < 0$;}\\
-1 & \text{if $\Gamma > 1$.}\\
-\end{cases}
-\end{equation}
 %
-For new services with no previous reputation value, we use the
-bootstrapping trust technique proposed in \cite{conf/icwe/YahyaouiZ11}. This
-technique consists in giving the new services a chance and observe
-their behaviors for a period of testing time. The observation
-sequence is modeled as a hidden Markov model that is used to
-detect the behavior of the service by comparing the observation
-behavior against pre-defined trust patterns. Based on the matching
-result, an initial value is assigned to the service. Using this
-initial reputation value, services quickly converge to their
-actual and stable values using the update function.
-
-\begin{proposition}\label{Complexity-Rep}
-$Rep_{w}^{t}$ can be computed in time $O(|t|)$, i.e., in time
-linear in the size of the window $t$.
-\end{proposition}
-
-\begin{proof}\footnote{In this paper, we
-assume that the common arithmetic and elementary functions, such
-as multiplication, division and trigonometric functions can be
-computed in time $O(1)$ as they operate on inputs of fixed sizes.}
-The function $Rep_{w}^{t}$ is recursive on $t$, but the algorithm
-works by storing the last calculated reputation value in a
-variable, so it will not be recalculated again at each iteration.
-However, the calculation of $reward_w^t$ is needed. Since the
-function $reward_w^t$ can be computed in time linear in the number
-of tasks (see Equations \ref{repr} and \ref{reward}), which in
-turn is linear in the size of the window time, the result follows.
-$\Box$
-\end{proof}
+%For new services with no previous reputation value, we use the
+%bootstrapping trust technique proposed in \cite{conf/icwe/YahyaouiZ11}. This
+%technique consists in giving the new services a chance and observe
+%their behaviors for a period of testing time. The observation
+%sequence is modeled as a hidden Markov model that is used to
+%detect the behavior of the service by comparing the observation
+%behavior against pre-defined trust patterns. Based on the matching
+%result, an initial value is assigned to the service. Using this
+%initial reputation value, services quickly converge to their
+%actual and stable values using the update function.
+
+%\begin{proposition}\label{Complexity-Rep}
+%$Rep_{w}^{t}$ can be computed in time $O(|t|)$, i.e., in time
+%linear in the size of the window $t$.
+%\end{proposition}
+
+%\begin{proof}\footnote{In this paper, we
+%assume that the common arithmetic and elementary functions, such
+%as multiplication, division and trigonometric functions can be
+%computed in time $O(1)$ as they operate on inputs of fixed sizes.}
+%The function $Rep_{w}^{t}$ is recursive on $t$, but the algorithm
+%works by storing the last calculated reputation value in a
+%variable, so it will not be recalculated again at each iteration.
+%However, the calculation of $reward_w^t$ is needed. Since the
+%function $reward_w^t$ can be computed in time linear in the number
+%of tasks (see Equations \ref{repr} and \ref{reward}), which in
+%turn is linear in the size of the window time, the result follows.
+%$\Box$
+%\end{proof}
 
@@
 $B_w^t$. This factor is the main variable a typical service uses
-to decide about which strategy to adopt. The details about the
-decision making process are described in Section \ref{Theoretical
-Results}. We use Equation \ref{eq:growthfactor} to compute the
+to decide about which strategy to adopt. We use Equation \ref{eq:growthfactor} to compute the
 growth factor $G^t_w$ of the service $w$ during the window time
@@
 
-This equation is designed so that it satisfies the following
-desirable properties:
-
-\begin{enumerate}
-
-\item The growth factor function should be monotonically
-increasing in the offered quality of service $QoS_w^t$.
-
-\item The growth factor function should be monotonically
-increasing in the service's reputation $Rep^t_w$.
-
-\item The growth factor function should be monotonically
-increasing in the budget $B_w^t$ if the maximum possible profit is
-positive and monotonically decreasing in $B_w^t$ if the maximum
-possible profit is negative. This property reflects the idea that
-the budget contributes in the increase of the growth factor as far
-as there is a chance to make profit. In fact, the contribution of
-the budget $B_w^t$ in the calculation of the growth factor should
-be proportional to the maximum possible profit $n_t \mu_w -
-\epsilon$ where the service $w$ receives all the offered tasks
-during the window time $t$.
-
-\end{enumerate}
-
   % if the profit $\beta_w$ made by the web service $w$
@@
 %community membership $\epsilon$ is positive.
-It is easy to show that Equation \ref{eq:growthfactor} satisfies
-the three aforementioned properties by calculating the partial
-derivatives $\partial G^t_w$ of this function in 1) $QoS_w^t$
-($\frac{\partial G^t_w}{\partial QoS_w^t} = \frac{1}{3} $); 2)
-$Rep^t_w$ ($\frac{\partial G^t_w}{\partial Rep^t_w} = \frac{1}{3}
-$); and 3) $B_w^t$ ($\frac{\partial G^t_w}{\partial B_w^t} =
-\frac{1}{3 (n_t \mu_w - \epsilon)} $). Thus, the sign of the two
-first partial derivatives is positive and the sign of
-$\frac{\partial G^t_w}{\partial B_w^t}$ depends on the sign of the
-maximum profit $n_t \mu_w - \epsilon$, so we are done. The mean
+%It is easy to show that Equation \ref{eq:growthfactor} satisfies
+%the three aforementioned properties by calculating the partial
+%derivatives $\partial G^t_w$ of this function in 1) $QoS_w^t$
+%($\frac{\partial G^t_w}{\partial QoS_w^t} = \frac{1}{3} $); 2)
+%$Rep^t_w$ ($\frac{\partial G^t_w}{\partial Rep^t_w} = \frac{1}{3}
+%$); and 3) $B_w^t$ ($\frac{\partial G^t_w}{\partial B_w^t} =
+%\frac{1}{3 (n_t \mu_w - \epsilon)} $). Thus, the sign of the two
+%first partial derivatives is positive and the sign of
+%$\frac{\partial G^t_w}{\partial B_w^t}$ depends on the sign of the
+%maximum profit $n_t \mu_w - \epsilon$, so we are done.
+The mean
 service fee depends on the strategy adopted by the service because
@@
 
-\begin{proposition}\label{Complexity-Growth_Factor}
-$G_w^t$ can be computed in time linear in the size of the window
-$t$.
-\end{proposition}
-
-\begin{proof}
-As shown in the second part of Equation \ref{eq:growthfactor}, the
-function $QoS_w^t$ can be computed in time linear in the number of
-tasks, which in turn is linear in the size of the window time.
-Since $B_w^t$ is constant, the result follows from Proposition
-\ref{Complexity-Rep}. $\Box$
-\end{proof}
+%\begin{proposition}\label{Complexity-Growth_Factor}
+%$G_w^t$ can be computed in time linear in the size of the window
+%$t$.
+%\end{proposition}
+%
+%\begin{proof}
+%As shown in the second part of Equation \ref{eq:growthfactor}, the
+%function $QoS_w^t$ can be computed in time linear in the number of
+%tasks, which in turn is linear in the size of the window time.
+%Since $B_w^t$ is constant, the result follows from Proposition
+%\ref{Complexity-Rep}. $\Box$
+%\end{proof}
 
@@
 of 3 to 160 web services. In average, the communities were populated by 60 web
-services. Thus, in total, the number of used web services is
-600,000. This makes our system scalable enough. We implemented the
+services. We implemented the
 scenarios using Java and executed the experiments on an Intel Xeon
-X3450 machine with 6GBs of memory. For other parameters missing
-from the dataset, we used normal random distribution with
-parameters estimated using the method of maximum likelihood.
+X3450 machine with 6GBs of memory.
 
@@
 $\epsilon = 0.15 \times v(C)$. This allows subsets of the
-coalition to gain maximum 15\% of $v(C)$. In the \emph{optimal
-$\epsilon$-core} method, we capped the coalition size to 25 web
-services, since the method is computationally intractable as the
-number of web services increases. In fact, given the machine
-configuration we used in our experiments, the maximum number we
-could run for this method is 25, which is very realistic if we
-consider the real airlines coalitions (the three well known
-coalitions have respectively 28, 19, and 13 members). In the other
-methods, there were no cap on size of the community and we had
-communities of size 160 web services at some points, as discussed
-above. In the experiments, our \emph{Depth-1 Convex-Checker} and
+coalition to gain maximum 15\% of $v(C)$. 
+%In the \emph{optimal
+%$\epsilon$-core} method, we capped the coalition size to 25 web
+%services, since the method is computationally intractable as the
+%number of web services increases. In fact, given the machine
+%configuration we used in our experiments, the maximum number we
+%could run for this method is 25, which is very realistic if we
+%consider the real airlines coalitions (the three well known
+%coalitions have respectively 28, 19, and 13 members). In the other
+%methods, there were no cap on size of the community and we had
+%communities of size 160 web services at some points, as discussed
+%above.
+In the experiments, our \emph{Depth-1 Convex-Checker} and
 \emph{Depth-2 Convex-Checker} methods generate results instantly
@@
 
-\begin{figure*}%[!t]
-\centering
-%\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{least_core.eps}
-\caption{Analysis of \emph{$\epsilon$-core} set non-emptiness for
-different values of $\epsilon$} \label{f_leastcore}
-\end{figure*}
-
-As mentioned in Section \ref{s:preliminaries}, the concept of
-\emph{core}, assumes no coalition of players can gain anything by
-deviating, which is a fairly strong requirement, and that is why
-the notion of \emph{$\epsilon$-core} was introduced. Least-Core
-$e(G)$ of a game $G$ is the minimum amount of $\epsilon$ so that
-the core is not empty. We evaluated the non-emptiness of
-\emph{$\epsilon$-core} set using our valuation function and a set
-of web services from our coalitions.  The restriction on the
-number of web services per coalition for this particular method is
-justified because it is
-%We picked random number of web services from the
-%dataset and formed around 10,000 random coalitions consisting of 3
-%to 28 web services. We choose 28 as the maximum number of members
-%in our coalitions since in the concrete examples of coalitions in
-%the airline domain we are implementing, the largest coalition,
-%Star Alliance\footnote{\url{www.staralliance.com}}, has 28 airline
-%members. This makes the total number of web services achieves
-%280,000, which is scalable enough. Moreover, it is computationally
-very complex for larger coalitions to verify whether
-\emph{$\epsilon$-core} set is empty or not. Also instead of
-considering $\epsilon$ amount of constant deviation in
-\emph{$\epsilon$-core} definition (Equation \ref{eq:core2}), we    %TODO FIX THIS
-similarly defined \emph{relative $\epsilon$-core} concept where no
-coalition would benefit more than \emph{$\epsilon \times v(C)$} by
-deviating. We vary $\epsilon$ so that it takes different values
-from $0$ to $1$ and observe the impact in terms of verifying the
-\emph{relative $\epsilon$-core} set non-emptiness. The results in
-Figure \ref{f_leastcore} illustrate that almost 10\% of our random
-web service coalitions have non-empty \emph{core} solution and
-\emph{$\epsilon$-core} solution is \emph{always} non-empty when we
-let agents gain only 30\% more of $v(C)$ by deviating.
-
-One of the properties of coalition structure formation algorithms
-in our second scenario is that they partition web services with
-low throughput rate so that they usually join coalitions with less
-request rate. Since the characteristic function $v(C)$ and the
-fair Shapley payoff vector is proportional to web services'
-contribution, the web services with small contribution will get
-paid much less in communities having web services with high
-throughput. On the other hand, according to the valuation function
-$v(C)$, web services with high throughput will not contribute well
-to communities with low amount of user requests (low market
-share). The strong web services are likely to deviate from weak
-coalitions, joining a stronger one, which makes the initial
-coalition unstable.
+%
+%\begin{figure*}%[!t]
+%\centering
+%%\includegraphics[scale=0.6]{graph1Final+.eps}
+%\includegraphics[width=3in]{least_core.eps}
+%\caption{Analysis of \emph{$\epsilon$-core} set non-emptiness for
+%different values of $\epsilon$} \label{f_leastcore}
+%\end{figure*}
+%
+%As mentioned in Section \ref{s:preliminaries}, the concept of
+%\emph{core}, assumes no coalition of players can gain anything by
+%deviating, which is a fairly strong requirement, and that is why
+%the notion of \emph{$\epsilon$-core} was introduced. Least-Core
+%$e(G)$ of a game $G$ is the minimum amount of $\epsilon$ so that
+%the core is not empty. We evaluated the non-emptiness of
+%\emph{$\epsilon$-core} set using our valuation function and a set
+%of web services from our coalitions.  The restriction on the
+%number of web services per coalition for this particular method is
+%justified because it is
+%very complex for larger coalitions to verify whether
+%\emph{$\epsilon$-core} set is empty or not. Also instead of
+%considering $\epsilon$ amount of constant deviation in
+%\emph{$\epsilon$-core} definition (Equation \ref{eq:core2}), we    %TODO FIX THIS
+%similarly defined \emph{relative $\epsilon$-core} concept where no
+%coalition would benefit more than \emph{$\epsilon \times v(C)$} by
+%deviating. We vary $\epsilon$ so that it takes different values
+%from $0$ to $1$ and observe the impact in terms of verifying the
+%\emph{relative $\epsilon$-core} set non-emptiness. The results in
+%Figure \ref{f_leastcore} illustrate that almost 10\% of our random
+%web service coalitions have non-empty \emph{core} solution and
+%\emph{$\epsilon$-core} solution is \emph{always} non-empty when we
+%let agents gain only 30\% more of $v(C)$ by deviating.
 
@@
 of service of tasks performed using our solution is also higher
-since our method considers all quality of service metrics
-mentioned in Table \ref{qosws}. Part(c) shows the availability of
+since our method considers all quality of service metrics used. Part(c) shows the availability of
 communities from the end user's point of view. The High
@@
 techniques: (1) a community that follows the interactive reasoning
-techniques presented in this paper (referred to as coopetitive);
+techniques presented in this report (referred to as coopetitive);
 (2) a community that follows a stochastic reasoning technique so
@@
 competitive community where all services follow the competitive
-strategy (referred to as competitive). The proposed model's
-reasoning mechanism enables services to effectively select their
-interacting strategies and the obtained budget represents the best
-outcome over the strategic decision making procedure they run all
-the time. This procedure avoids cases where a service selects the
-competitive strategy but gets refused to obtain a task from the
-master. The procedure allows services to make decisions that
-maximize their utilities, so that if the service cannot compete,
-the procedure would suggest to collaborate, which is better than
-competing and failing to obtain the task. In this case (i.e.,
-competing and not getting the task), the service stays idle but
-still pays the community membership fee, which means losing
-utility. The developed strategic decision making mechanism leads
-some service agents to follow cooperative strategies that overall
-maintain an optimal community budget. In the same figure, we
-observe the cumulative budget of a community where services follow
-random interacting strategies. The outcome is clearly lower
-because services at each run randomly decide over their acting
-strategies. This potentially influences the community budget
-because a low quality service if randomly selects to follow the
-competitive strategy, it will fail to perform a task with high QoS
-requirements. This kind of strategy selection is totally
-stochastic while the task allocation algorithm follows a logical
-path. The ideal system is the one that analyzes the optimal
-strategic path and consistently follows strategies that bring
-maximum outcome. The result regarding the community that follows
-the random strategy shows how stochastic decision making degrades
-the community budget, but still this result outperforms the one of
-the purely competitive community. In this purely competitive case,
-all the services follow the competitive strategy and the frequency
-of getting rejected from a task is relatively high. In a community
-with limited number of tasks, the competitive strategy for all
-services highly influences the community budget because a
-potential group of services are losing at every run.
+strategy (referred to as competitive). 
+%The proposed model's
+%reasoning mechanism allows services to make decisions that
+%maximize their utilities, so that if the service cannot compete,
+%the procedure would suggest to collaborate, which is better than
+%competing and failing to obtain the task. In this case, the service stays idle but
+%still pays the community membership fee, which means losing
+%utility. The developed strategic decision making mechanism leads
+%some service agents to follow cooperative strategies that overall
+%maintain an optimal community budget. In the same figure, we
+%observe the cumulative budget of a community where services follow
+%random interacting strategies. The outcome is clearly lower
+%because services at each run randomly decide over their acting
+%strategies. This potentially influences the community budget
+%because a low quality service if randomly selects to follow the
+%competitive strategy, it will fail to perform a task with high QoS
+%requirements.
 
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[scale=0.35]{graphbgtmed3set.eps}
-\includegraphics[scale=0.35]{graphbgthigh.eps}
-\includegraphics[scale=0.35]{graphbgtveryhigh.eps}
-\caption{High membership fees or less task income impacts on
-different selection strategies. Part (a) Medium membership fee.
-Part (b) High membership fee. Part (c) Very high membership fee.}
-\label{membership_fee_graph}
-\end{figure}
-
-In Figure \ref{membership_fee_graph}, we analyze the scenario
-where the membership fee is high, which is analogous to situations
-where the task income is low. We need to verify how well services
-can perform in these situations. Figure \ref{membership_fee_graph}
-part (a) depicts the results in a normal scenario. In part (b), we
-have increased the membership fee to the high amount of 5 units
-per run. Services will need to pay $5$ units on each iteration of
-tasks being offered. As results, the strategic coopetitive
-decision making process helps services make benefits, but
-stochastic and compete methods lead to lose income since making
-mistakes and trying to compete for jobs the services cannot afford
-while having to pay higher membership fees is making them lose
-budget in a faster pace. In part (c), the membership fee is higher
-than an average income that
-a task can generate. %It might not be rational for selfish
-%self-interest web services to stay in these communities from the
-%utility perspective, but as mentioned there might be other
-%political reasons they might need to stay in these communities. As
-The simulation shows that the stochastic and compete strategies
-make services budget decreases drastically. However, our strategic
-coopetitive decision making process loses budget in a slower pace.
-
-In Figure \ref{Graph2} parts (a) and (b), we observe the
-competitive and cooperative probability of four different services
-where two of them ($w_1$ and $w_3$) are following optimal
-strategies as suggested by our model (competitive for $w_1$ and
-cooperative for $w_3$) and the two others ($w_2$ and $w_4$) are
-following non-optimal strategies, which are the opposite of what
-our model suggests. Over elapsing runs, services that follow
-optimal strategies bring best reputation. In fact, the master
-agent rewards the high quality service that chooses the
-competitive strategy, cooperates with other peers and successfully
-accomplishes the task. In this system, the reputation regarding
-such a service is increasing over time and the possibility of
-allocating further tasks is increasing as well. By increasing the
-growth factor, such a service (here shown as $w_1$) increases the
-probability of selecting the competitive strategy. On the other
-hand, the other service (here shown as $w_2$) that is incapable of
-competing is penalized by the master agent because the offered
-quality might not meet the required task quality. Thus, $w_2$
-degrades its growth factor by following the competitive strategy.
-As intelligent entity, this service is encouraged to change its
-strategy to the cooperative one and thus, its probability of
-selecting the competitive strategy is decreasing over time. We
-have similar results in Figure \ref{Graph2} part (b) regarding
-services $w_3$ and $w_4$ where unlike $w_4$, $w_3$ is
-strategically following the cooperative strategy allowing for an
-increase in the
-overall reputation. %Therefore, $w_4$ is more seeking the
-%competitive strategy where it can increase its growth factor.
-
-\begin{figure}[h]
-%\centering
-\includegraphics[scale=0.47]{graphcomp.eps}
-\includegraphics[scale=0.47]{graphcoop.eps}
-\caption{Reputation progress of four different services: W$_1$ and
-W$_3$ are following our strategic decision model; W$_2$ and W$_4$
-are following the opposite.} \label{Graph2}
-\end{figure}
-
 In our model, services are managed by selfish agents in the sense
@@
 being done successfully in three communities adopting the three
-different aforementioned strategy decision algorithms. Part (a)
-depicts the number of tasks successfully done. When services are
-not capable of performing tasks alone and decide to compete for
-tasks with high QoS requirements, they usually fail to perform the
-task. However, if they opt for cooperating although they have less
-income, they have higher chance of performing tasks
-collaboratively with other services. Figure \ref{graph_task}, Part
-(b) shows the probability of successfully performing tasks, which
-influences users' satisfaction. The results show that services
-using our coopetitive strategy when deciding whether to compete or
-cooperate have higher chance to get high satisfaction ratio
-compared to stochastic and compete strategies. The quality of
-tasks performed are depicted in Figure \ref{graph_task} Part (c).
-The figure shows the average QoS of tasks successfully
-performed. %Collaborating increases the performed QoS of tasks,
-%therefore forming collaborative groups improves user satisfaction.
-As clearly confirmed by the simulation, the coopetitive community
+different aforementioned strategy decision algorithms. As clearly confirmed by the simulation, the coopetitive community
 outperforms the stochastic and compete communities.

### 2014-03-04 seminar/seminar_report/Abstract.tex
changes

--- 2013-07-24 proposal/proposal/Abstract.tex
@@
 
-Web services are loosely-coupled business applications willing to
-cooperate in distributed settings within different groups called
-communities. Communities aim to provide better visibility,
-efficiency, market share and total payoff. There are a number of
-proposed mechanisms and models on aggregating web services and
-making them cooperate within their communities. However, forming
-optimal and stable communities as coalitions to maximize
-individual and group efficiency and income has not been addressed
-yet. In this paper, we propose an efficient coalition formation
-mechanism using cooperative game-theoretic techniques. We propose
-a mechanism for community membership requests and selections of
-web services in the scenarios where there is interaction between one community and many web services
-and scenarios where web services can join multiple established communities. The ultimate objective is to
-develop a mechanism for web services to form stable groups
-allowing them to maximize their efficiency and generate
-near-optimal (welfare-maximizing) communities. The theoretical and
-extensive simulation results show that our algorithms provide web services
-and community owners, in real-world like environments, with applicable and near-optimal decision
-making mechanisms.
+In the last few years, communities of services have been studied in a certain numbers of proposals as virtual pockets of similar expertise.
+The motivation is to provide these services with high chance of discovery through better visibility, and to enhance their capabilities when it comes to provide requested functionalities.
+There are a number of proposed mechanisms and models on aggregating web services and making them cooperate within their communities.
+However, forming optimal and stable communities as coalitions to maximize individual and group efficiency and income for all the involved parties has not been addressed yet.
+Also, in the proposed frameworks of these communities, a common assumption is that residing services, which are supposed to be autonomous and intelligent, are competing over received requests, but also exhibit cooperative behaviors, for instance in terms of substituting each other.
+
+In this report, we identify the problem of defining efficient algorithms for coalition formation mechanisms within communities and propose preliminary results using cooperative game-theoretic techniques.
+We propose a mechanism for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities.
+The ultimate objective is to develop a mechanism for web services to form stable groups allowing them to maximize their efficiency and generate near-optimal (welfare-maximizing) communities.
+The theoretical and extensive simulation results show that our algorithms provide web services and community owners, in real-world like environments, with applicable and near-optimal decision making mechanisms.
+We also propose a decision mechanism based on learning methods for services within communities to effectively choose the tasks to perform based on their capabilities and the competition between other community members.

### 2014-03-04 seminar/seminar_report/chapter1.tex
changes

@@
 \chapter{Introduction}\label{sec:intro}
-In this chapter, we introduce the context of this research, which
-is about communities of web services abstracted as autonomous
-agents. Those agent-based web services use cooperative game
-theoretic solution concepts for decision making. We discuss the
-motivations of this work and briefly review the literature to
-identify the problems we aim to solve in this thesis. Moreover, we
-discuss our objectives and preliminary contributions.
+%In this chapter, we introduce the context of this research, which
+%is about communities of web services abstracted as autonomous
+%agents. Those agent-based web services use cooperative game
+%theoretic solution concepts for decision making. We discuss the
+%motivations of this work and briefly review the literature to
+%identify the problems we aim to solve in this thesis. Moreover, we
+%discuss our objectives and preliminary contributions.
 
@@
 
+Within communities, service providers can 
+can have competitive behaviour as they provide the same functionalities and the number of users requests is finite.
+So as an extension to our work, we have implemented a framework in which service providers can opt for performing tasks if they feel they are capable enough.
+We have implemented an online learning mechanism for service providers with different captaincies to learn over time which strategy to choose based on their own and other service providers status and capabilities.
+After establishing states of our model and observing convincing results from our learning method, we plan to extend the learning process using reinforcement learning (q-learning) techniques.
+
 \indent To summarize, the main problem we aim to tackle in this

### 2014-03-04 seminar/seminar_report/chapter2.tex
changes

@@
 
-\section{Community of Web Services}\label{sec:CommunityWS}
-In this section, we present web services and discuss the concept
-of their communities from architectural and operations
-perspectives.
-
-\subsection{Web Services}\label{sec:CWSWebServices}
-
-In our research work, we abstract web services as rational
-agents\footnote{The term
-        rational is used here in the sense that web services are utility
-        maximizers} providing services to end users. They aim to maximize
-        their individual income by receiving enough requests from end
-        users. In order to increase their revenue, web services seek for
-        more tasks if they have the capacity and throughput to do so. Web
-        services can join communities to have better efficiency by
-        collaborating with others, to have access to broad market share,
-        and to have opportunity of receiving a bigger task pool from end
-        users. Furthermore, the high reliance on web services has increased quality expectations from end users.
-        Communities of web services can provide higher availability, performance, reliability, and recovery for end users.
-
-\subsection{Web Service Communities}\label{sec:CWSDefinition}
- In \cite{DBLP:journals/internet/BenatallahSD03,
-Zeng:2003:QDW:775152.775211}, the authors introduce community of
-web services as collection of cooperative web services with common
-functionalities but different QoS metrics. Therefore
-$communities$ are differentiated from $composition$ types of web
-service cooperation in which web services with different
-functionalities work together to generate a new service with
-composite functionality.
-
-Maamar et al. in \cite{DBLP:journals/ijebr/MaamarSTBB09}
-proposed an architecture utilizing \emph{Contract-Net} protocol
-for engineering task distribution within communities. This
-architecture has been further developed in
-\cite{conf/IEEEscc/BenharrefSBB11, conf/IEEEscc/KhosravifarBMMT10,
-conf/aina/LimTM11, CSTintercommunity}. Two types of roles have
-been distinguished for community members: masters and slaves.
-Master web services lead communities and are responsible for
-membership management. They can invite and convince slave web
-services to join the community, and attract new slave web services
-to their communities by awarding them better payoff. Moreover,
-they can eject some slave members from the community to improve
-its overall reputation if these members are misbehaving or cannot
-provide the promised QoS \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+%\section{Community of Web Services}\label{sec:CommunityWS}
+%In this section, we present web services and discuss the concept
+%of their communities from architectural and operations
+%perspectives.
+%
+%\subsection{Web Services}\label{sec:CWSWebServices}
+%
+%In our research work, we abstract web services as rational
+%agents\footnote{The term
+%        rational is used here in the sense that web services are utility
+%        maximizers} providing services to end users. They aim to maximize
+%        their individual income by receiving enough requests from end
+%        users. In order to increase their revenue, web services seek for
+%        more tasks if they have the capacity and throughput to do so. Web
+%        services can join communities to have better efficiency by
+%        collaborating with others, to have access to broad market share,
+%        and to have opportunity of receiving a bigger task pool from end
+%        users. Furthermore, the high reliance on web services has increased quality expectations from end users.
+%        Communities of web services can provide higher availability, performance, reliability, and recovery for end users.
+%
+%\subsection{Web Service Communities}\label{sec:CWSDefinition}
+% In \cite{DBLP:journals/internet/BenatallahSD03,
+%Zeng:2003:QDW:775152.775211}, the authors introduce community of
+%web services as collection of cooperative web services with common
+%functionalities but different QoS metrics. Therefore
+%$communities$ are differentiated from $composition$ types of web
+%service cooperation in which web services with different
+%functionalities work together to generate a new service with
+%composite functionality.
+%
+%
+%Maamar et al. in \cite{DBLP:journals/ijebr/MaamarSTBB09}
+%proposed an architecture utilizing \emph{Contract-Net} protocol
+%for engineering task distribution within communities. This
+%architecture has been further developed in
+%\cite{conf/IEEEscc/BenharrefSBB11, conf/IEEEscc/KhosravifarBMMT10,
+%conf/aina/LimTM11, CSTintercommunity}. Two types of roles have
+%been distinguished for community members: masters and slaves.
+%Master web services lead communities and are responsible for
+%membership management. They can invite and convince slave web
+%services to join the community, and attract new slave web services
+%to their communities by awarding them better payoff. Moreover,
+%they can eject some slave members from the community to improve
+%its overall reputation if these members are misbehaving or cannot
+%provide the promised QoS \cite{DBLP:journals/ijebr/MaamarSTBB09}.
 
@@
 
-            \subsubsection*{Coalition Structure Formation}\label{sec:coalition}
+%            \subsubsection*{Coalition Structure Formation}\label{sec:coalition}
 
-            Coalition structure formation is the problem of finding the best
+            \emph{Coalition structure formation} is the problem of finding the best
             partition of web services into teams. In these settings, the
@@
 
-        \subsection{Representation and Complexity Issues}\label{sec:CWSArchitecture}
-
-        Shapely value is the unique ``fair'' way to distribute the total surplus generated by the coalition, among all the players.
-        The nature of the Shapley value is combinatorial, as all possible orderings to form a
-        coalition needs to be considered. This computational complexity can sometimes be
-        an advantage as agents cannot benefit from manipulation. For example, it is NP-complete
-        to determine whether for a bunch of agents to collude and make their own coalition and guarantee
-        an increase in payoff of all participants \cite{conf/aaai/YokooCSOI05}.
-        There are some representations that allow us to compute the Shapley value efficiently by reducing the input size of the problem.
-        One example is \emph{Induced subgraph games}
-        which was introduced by Deng and Papadimitriou \cite{Deng94}. In this representation, players are represented by graph nodes, and
-        their valuation function should be the sum of weights of all edges between the node and all its neighbors. It is a succinct representation, using
-        an adjacency matrix, which needs only $O(n^2)$ space to store all the input, which is a major improvement from $O(2^n)$ because
-        if weights of all the edges in graph are all positive, the Shapley value can be computed in time $O(n^2)$.
-
-        In order to make cooperative game concepts practical in real world application, we have proposed an approximation multi-layer
-        algorithm useful for service oriented computing settings. Our excrements illustrate, these algorithms can provide
-        applicable and near optimal solutions for real world applications.
+%        \subsection{Representation and Complexity Issues}\label{sec:CWSArchitecture}
+%
+%        Shapely value is the unique ``fair'' way to distribute the total surplus generated by the coalition, among all the players.
+%        The nature of the Shapley value is combinatorial, as all possible orderings to form a
+%        coalition needs to be considered. This computational complexity can sometimes be
+%        an advantage as agents cannot benefit from manipulation. For example, it is NP-complete
+%        to determine whether for a bunch of agents to collude and make their own coalition and guarantee
+%        an increase in payoff of all participants \cite{conf/aaai/YokooCSOI05}.
+%        There are some representations that allow us to compute the Shapley value efficiently by reducing the input size of the problem.
+%        One example is \emph{Induced subgraph games}
+%        which was introduced by Deng and Papadimitriou \cite{Deng94}. In this representation, players are represented by graph nodes, and
+%        their valuation function should be the sum of weights of all edges between the node and all its neighbors. It is a succinct representation, using
+%        an adjacency matrix, which needs only $O(n^2)$ space to store all the input, which is a major improvement from $O(2^n)$ because
+%        if weights of all the edges in graph are all positive, the Shapley value can be computed in time $O(n^2)$.
+%
+%        In order to make cooperative game concepts practical in real world application, we have proposed an approximation multi-layer
+%        algorithm useful for service oriented computing settings. Our excrements illustrate, these algorithms can provide
+%        applicable and near optimal solutions for real world applications.
 

### 2014-03-04 seminar/seminar_report/chapter3.tex
changes

@@
 
-In this section, we discuss the parameters and preliminary
-concepts that we use in the rest of the proposal.
-
-\subsection{Architecture}
-
 Our system consists of three main types of entities working
-together:
-
-\emph{1) Web services} are rational entities that aim to maximize
+together: \emph{1) Web services} are rational entities that aim to maximize
 their utilities by providing high quality services to end users.
@@
 equations, we refer to web services as $ws$ and to the set of web
-services hosted by a given community as $C$. To simplify the
-notation, sometimes we simply write $ws$ instead of $ws \in C$ to
-go through the elements $ws$ of the set $C$.
-
+services hosted by a given community as $C$. 
+%To simplify the
+%notation, sometimes we simply write $ws$ instead of $ws \in C$ to
+%go through the elements $ws$ of the set $C$.
 \emph{2) Master Web Services} or the community coordinators, are representatives of the
@@
 maximize user satisfaction by having tasks accomplished according
-to the desired QoS. In fact, higher user satisfaction will bring
-more user requests and increase the market share and revenue of
-the community.
-
+to the desired QoS. 
+%In fact, higher user satisfaction will bring
+%more user requests and increase the market share and revenue of
+%the community. 
 \emph{3) Users} generate requests and try to find the best
@@
 Higher user satisfaction leads to higher trust of the community by users hence directing more requests towards that service provider.
-
-\subsection{Web Service Parameters}\label{ws_parameters}
 
@@
 
-\subsection{Web Service Communities}\label{webservice-communities}
-
 Figure 3 represents our revised architecture of web service
@@
 communities to increase their utility by having larger market
-share and task pool. Community coordinators or master web services
-are responsible for community development, managing membership
-requests from web services and distributing user tasks among the
-community members. Community coordinators try to attract quality
-web services and keep the community as stable and productive as
-possible to gain better reputation and user satisfaction, which
-results in having higher revenue.
+share and task pool. 
+%Community coordinators or master web services
+%are responsible for community development, managing membership
+%requests from web services and distributing user tasks among the
+%community members. Community coordinators try to attract quality
+%web services and keep the community as stable and productive as
+%possible to gain better reputation and user satisfaction, which
+%results in having higher revenue.
 
@@
 
-As mentioned in Section \ref{webservice-communities}, communities
+As mentioned in Section \ref{s:preliminaries}, communities
 are robust service providers with well established market share
@@
 
-In previous sections, our focus was on community formation and we the focus was on cooperative behaviour of the web services as agents.
-However competition within cooperative environments, for business agents having different set of capabilities.
+In previous sections, our focus was on community formation and we emphasised on cooperative behaviour of the web services as agents.
 Within communities, those services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}.
@@
 
-\begin{figure*}%[!t]
+\begin{figure*}%[!t]In the previous experiment, we considered the scenario where all
+web services are stable, will not leave the group, and will
+fulfill their promised QoS for a good period of time. However, in
+real world scenarios of web services, this is not always the case.
+This is the reason why the community coordinator would be interested in paying
+web services in order to keep the group reliable from the end
+user's point of view.
 \centerline{\includegraphics[width=6.8in]{tax_dyn.eps}}
@@
 
-In the previous experiment, we considered the scenario where all
-web services are stable, will not leave the group, and will
-fulfill their promised QoS for a good period of time. However, in
-real world scenarios of web services, this is not always the case.
-This is the reason why the community coordinator would be interested in paying
-web services in order to keep the group reliable from the end
-user's point of view. In our next scenario, we have introduced the
+In our next scenario, we have introduced the
 new instability variable $\tau$ ranging from 0 to 1, 0 meaning web
@@
 In this section, the objective is to investigate the effectiveness of the proposed strategic system in section \ref{s:coop}.
-
 We start our discussions with cumulative budget comparison

### 2014-03-04 seminar/seminar_report/chapter5.tex
changes

@@
 \chapter{Conclusion and Future Work}\label{sec:conclusionfuturework}
-In this chapter, we describe the phases of our plan for exploring
-the research challenges and investigating the research issues
-identified in Chapter 3. This chapter also includes research
-methodology and future publication plan.
-
-\section {Conclusion}
 
@@
 
-\item Applying other valuation function in our scenarios using for
-instance Weighted Voting Games (WCG) in order to develop a
-multiple weighted algorithm to find best coalition structures
-satisfying different weights on each community.
-
 \item Analyzing the impact of Q-learning and reinforcement
@@
 
-\item Developing an approximation algorithm for shapely value
-payoff distribution vector in community setting.
-
 \item Developing a community membership algorithm technique for
-our agents in "incomplete information" settings.
+our agents in more distributed and "incomplete information" settings.
 

### 2014-03-04 seminar/seminar_report/chapter5.tex
changes

@@
     \begin{enumerate}
-        \item Published a Journal Paper to the International Journal of Expert Systems With Applications; \emph{"To Compete or to Cooperate?
-This is the Question in Communities of Autonomous Services"}, 2014
-        \item Published a Journal Paper to the IEEE Transactions on Services Computing; \emph{"Efficient Community Formation for Web Services"}, 2014
-        \item Published a paper in 10th IEEE International Conference on Services Computing; \emph{"Efficient Coalition Formation for Web Services"}, 2013
-        \item Published a Paper to the 10th International Conference on Service Oriented Computing; \emph{"Analyzing Coopetition Strategies of Services within Communities"}, 2012
+        \item E.
+Khosrowshahi Asl, J.
+Bentahar, H.
+Otrok, R.
+Mizouni, \emph{``Efficient Community Formation for Web Services.''} Accepted at IEEE Transactions on Services Computing, Feb.
+2014, IEEE.
+(Impact factor: 2.46)
+        \item E.
+Khosrowshahi Asl, J.
+Bentahar, R.
+Mizouni, B.
+Khosravifar, H.
+Otrok, \emph{``To Compete or to Cooperate?
+This is the Question in Communities of Autonomous Services.''} In the Journal of Expert Systems and Applications, Feb.
+2014, Elsevier.
+(Impact factor: 1.854, 5-year:  2.339)
+        \item Published a conference paper in 10th IEEE International Conference on Services Computing; \emph{``Efficient Coalition Formation for Web Services''}, 2013
+        \item Published a conference paper to the 10th International Conference on Service Oriented Computing; \emph{``Analyzing Coopetition Strategies of Services within Communities''}, 2012
     \end{enumerate}

### 2014-03-04 seminar/seminar_report/chapter3.tex
changes

@@
 Web services come with different quality of service parameters.
-These parameters include availability, reliability, successability, throughput, latency, capacity, cost, regulatory and security\cite{DBLP:conf/smc/Al-MasriM09a}.
+These parameters include availability, reliability, successability, throughput, latency, capacity, cost, regulatory and security\cite{DBLP:conf/smc/Al-MasriM09a}\footnote[1]{The implemented environment includes the QWS dataset by Eyhab Al-Masri and Qusay H.
+Mahmoud freely available at: http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/.}.
 We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}

### 2014-03-04 seminar/seminar_report/chapter5.tex
changes

@@
 \begin{itemize}
-\item Analyzing other cooperative solution concepts such as Kernel
+\item \textbf{Winter 2014: }Analyzing other cooperative solution concepts such as Kernel
 and Nucleolus where payoff division is guaranteed to exist and may
@@
 
-\item Analyzing the impact of Q-learning and reinforcement
+\item \textbf{Summer 2014: }Analyzing the impact of Q-learning and reinforcement
 learning on the performance of our model.
 
-\item Developing a community membership algorithm technique for
-our agents in more distributed and "incomplete information" settings.
+\item \textbf{Fall 2014: }Developing a community membership algorithm technique for
+our agents in more distributed and ``incomplete information'' settings.
 
+\item \textbf{Winter 2015: }Thesis work and PhD Defense.
 %\item Developing an open source, Java based Tool, with UI for
@@
 
-\begin{center}
-    \begin{tabular}{ | l | l | p{5cm} |}
-    \hline
-    Term & Activity & Publication \\ \hline
-    Winter 2014 & 1 & 1 \\ \hline
-    Summer 2014 & 1 & 1 \\ \hline
-    Fall 2014 & 1 & 1 \\ \hline
-    Winter 2015 & 1 & 1 \\
-    \hline
-    \end{tabular}
-\end{center}
+%\begin{center}
+%    \begin{tabular}{ | l | l | p{5cm} |}
+%    \hline
+%    Term & Activity & Publication \\ \hline
+%    Winter 2014 & 1 & 1 \\ \hline
+%    Summer 2014 & 1 & 1 \\ \hline
+%    Fall 2014 & 1 & 1 \\ \hline
+%    Winter 2015 & 1 & 1 \\
+%    \hline
+%    \end{tabular}
+%\end{center}
 
@@
     \begin{enumerate}
+        \small{
         \item E.
@@
 (Impact factor: 1.854, 5-year:  2.339)
-        \item Published a conference paper in 10th IEEE International Conference on Services Computing; \emph{``Efficient Coalition Formation for Web Services''}, 2013
-        \item Published a conference paper to the 10th International Conference on Service Oriented Computing; \emph{``Analyzing Coopetition Strategies of Services within Communities''}, 2012
+        \item E.
+Khosrowshahi Asl, J.
+Bentahar, H.
+Otrok, R.
+Mizouni, \emph{``Efficient Coalition Formation for Web Services.
+In the 10th''} IEEE  International Conference on Services Computing (SCC 2013), Santa Clara Marriott, CA, USA, June 27-July 2, 2013
+        \item B.
+Khosravifar, M.
+Alishahi, E.
+Khosrowshahi Asl, J.
+Bentahar, R.
+Mizouni, H.
+Otrok, \emph{``Analyzing Coopetition Strategies of Services within Communities''}.
+In the 10th International Conference on Service Oriented Computing, (ICSOC 2012), Shanghai, China, Nov.
+2012
+        }
     \end{enumerate}

### 2014-03-05 seminar/seminar_report/Abstract.tex
changes

@@
 However, forming optimal and stable communities as coalitions to maximize individual and group efficiency and income for all the involved parties has not been addressed yet.
-Also, in the proposed frameworks of these communities, a common assumption is that residing services, which are supposed to be autonomous and intelligent, are competing over received requests, but also exhibit cooperative behaviors, for instance in terms of substituting each other.
+Also, in the proposed frameworks of these communities, a common assumption is that residing services, which are supposed to be autonomous and intelligent, are competing over received requests.
+However, those services can also exhibit cooperative behaviors, for instance in terms of substituting each other.
+Deciding to compete or cooperate inside communities is a problem yet to be investigated.
 
-In this report, we identify the problem of defining efficient algorithms for coalition formation mechanisms within communities and propose preliminary results using cooperative game-theoretic techniques.
+In this report, we identify the problem of defining efficient algorithms for coalition formation mechanisms within communities and propose some results using cooperative game-theoretic techniques.
 We propose a mechanism for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities.

### 2014-03-05 seminar/seminar_report/chapter1.tex
changes

@@
 sending requests to a web service which is not providing
-satisfactory services. Thus its important to consider all the
+satisfactory services. Thus it is important to consider all the
 parties involved in the decision making process about the
@@
 
-Within communities, service providers can 
-can have competitive behaviour as they provide the same functionalities and the number of users requests is finite.
-So as an extension to our work, we have implemented a framework in which service providers can opt for performing tasks if they feel they are capable enough.
-We have implemented an online learning mechanism for service providers with different captaincies to learn over time which strategy to choose based on their own and other service providers status and capabilities.
-After establishing states of our model and observing convincing results from our learning method, we plan to extend the learning process using reinforcement learning (q-learning) techniques.
+Within communities, services can exhibit competitive behavior as they provide the same functionalities and the number of users requests is finite.
+However, for the same reason of being functionally similar, services can cooperate with each other, for example to substitute each other in order to perform some sub-tasks.
+So as an extension of our work, we have proposed a framework in which services can opt for performing tasks if they feel they are capable enough
+or decide to cooperate by showing the availability to perform some sub-tasks.
+We have implemented an online learning mechanism for services with different capabilities to learn over time which strategy to choose based on their own and other services status and capabilities.
+After establishing states of our model and observing convincing results from our learning method, we plan to extend the learning process using reinforcement learning (Q-learning) techniques.
 
-\indent To summarize, the main problem we aim to tackle in this
-thesis is the formation of stable and efficient coalitions
-maximizing web services and community revenue. The main objectives
-are:
+\indent To summarize, the main problems we aim to tackle in this
+thesis are the formation of stable and efficient coalitions
+maximizing web services and community revenue and the decision over the strategy to play about competing or cooperating.
+The main objectives are:
 \begin{itemize}
@@
 \section{Report Organization}\label{sec:outline}
-The rest of the report is organized as follows: We present in
+The rest of the report is organized as follows. We present in
 Chapter~\ref{sec:MAS} the background needed for our research along

### 2014-03-05 seminar/seminar_report/chapter2.tex
changes

@@
 
-In this chapter then we introduce
+In this chapter we introduce
 the concept of communities of web services, their architecture and
-applications and the benefits of forming communities. Thereafter,
+applications and the benefits of forming such communities. Thereafter,
 we discuss the cooperative game theory concepts used throughout
@@
 
-Alternatively, the $\epsilon$ can be thought of as a \emph{tax} imposed on a coalition should it choose to deviate.
+Alternatively, $\epsilon$ can be thought of as a \emph{tax} imposed on a coalition should it choose to deviate.
 This can again be seen as an external party, trying to stabilize the coalition by imposing some \emph{tax} on deviation.

### 2014-03-05 seminar/seminar_report/chapter3.tex
changes

--- 2014-03-04 seminar/seminar_report/chapter3.tex
@@
 
-\chapter{Coalition Formation for Autonomous Web Services}\label{sec:coalitionformationws}
+\chapter{Coalition Formation and Coopetitive Behavior of Autonomous Web Services}\label{sec:coalitionformationws}
 
 In this chapter, we present our coalition model of agent-based web
-services within communities\cite{SCC2013efficient}. We start by describing the general
+services within communities \cite{SCC2013efficient}. We start by describing the general
 architecture and considered parameters for web services.
@@
 Web services come with different quality of service parameters.
-These parameters include availability, reliability, successability, throughput, latency, capacity, cost, regulatory and security\cite{DBLP:conf/smc/Al-MasriM09a}.
+These parameters include availability, reliability, successability, throughput, latency, capacity, cost, regulatory and security \cite{DBLP:conf/smc/Al-MasriM09a}\footnote[1]{The implemented environment includes the QWS dataset by Eyhab Al-Masri and Qusay H.
+Mahmoud freely available at: http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/.}.
 We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
@@
 It can recognize if web services are capable of doing the amount of tasks they advertised.
-If for any reason there is a decline in quality metrics or throughput, the  community master will announce the new parameters and community masters and members can consider those values as benchmark for future performance calculations but also to penalize them.
-In this way, players have incentive to reveal their real capabilities to profit best from the community and to avoid being penalized.
+If for any reason there is a decline in quality metrics or throughput, the  community master will announce the new parameters and community masters and members can consider those values as benchmark for future performance calculations.
+Web services that got their quality declined are penalized, and in this way, players have incentive to reveal their real capabilities to profit best from the community and to avoid being penalized.
 In addition, the system should be dynamic enough to detect and react to web services quality metrics variation as over time web service metrics may  degrade or improve, a change that the community should adjust to.
@@
 partition web services into non-empty disjoint coalition
-structures. As mentioned in Section \ref{sec:coalition}, the used
+structures. The used
 algorithms in \cite{Sandholm:1999:CSG:317145.317152,DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
@@
 
-\section{Competitive behaviour of services within communities}\label{s:coop}
+\section{Coopetitive Behavior of Services within Communities}\label{s:coop}
 
-In previous sections, our focus was on community formation and we emphasised on cooperative behaviour of the web services as agents.
+In previous sections, our focus was on community formation and we emphasised on cooperative behavior of the web services as agents.
 Within communities, those services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}.
@@
 we propose a mechanism within which service agents
-in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this paper interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task.
+in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this report interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task.
 We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate).
@@
 
-\subsection{The Proposed Framework}\label{The Proposed Framework}
-In this section, we first present the architecture of the proposed
+%\subsection{The Proposed Framework}\label{The Proposed Framework}
+Here, we first present the architecture of the proposed
 model. We explore the characteristics of intelligent service
@@
 
-\subsubsection{The Architecture}
+\subsection{Architecture}
 
@@
 
-\subsubsection{System Parameters}
+\subsection{System Parameters}
 In this section, we demonstrate the involved parameters and their
@@
 
-\subsubsection{Service Interactive Strategies}
+\subsection{Service Interactive Strategies}
 
@@
 services to cooperate with to perform some tasks \footnote{Through
-the paper, requests or tasks are supposed to be decomposable.},
+the report, requests or tasks are supposed to be decomposable.},
 and thus it adopts the cooperative strategy. Services estimate the
@@
 \section{Experimental Results and Analysis}\label{s:resutls}
+
+\subsection{Coalition Formation and Stability}
 
@@
 this scenario, our community receives 130 tasks from users on
-average per iteration. These tasks are about flight booking and
-are expected to be performed by the community. They are randomly
-generated using a poisson distribution (having 130 as parameter).
+average per iteration. These tasks are randomly generated.
+%These tasks are about flight booking and
+%are expected to be performed by the community. They are randomly
+%generated using a poisson distribution (having 130 as parameter).
 Depending on community task queue and the assigned web services'
@@
 
-\subsection*{Coopetitive behaviour of services within communities}\label{sb:resutlscoop}
+\subsection{Coopetitive Behavior}\label{sb:resutlscoop}
 
-In this section, the objective is to investigate the effectiveness of the proposed strategic system in section \ref{s:coop}.
+In this section, the objective is to investigate the effectiveness of the proposed strategic system in Section \ref{s:coop}.
 We start our discussions with cumulative budget comparison

### 2014-03-05 seminar/seminar_report/chapter5.tex
changes

@@
 \chapter{Conclusion and Future Work}\label{sec:conclusionfuturework}
+
+\section {Conclusion}
 
@@
 making mechanisms.
+
+We also proposed a coopetitive strategic model to analyze
+the interacting behavior of intelligent services that are active within communities.
+We considered two acting strategies where service agents expect different sort of payoffs:
+(1) competitive strategy where the service claims that it can accomplish a task,
+and therefore can take the responsibility over the service consumer satisfaction; and (2)
+cooperative strategy where the service does not take the responsibility to accomplish
+the task and only cooperates with competitive peers. Our proposed model advances the
+state-of-the-art in cooperative systems by enabling intelligent agent-based services to
+effectively choose their interacting strategies that lead to optimal outcomes. The proposed
+framework provides a reasoning technique that service agents can use to increase
+their overall obtained utilities. The theoretical results presented in this research work are also
+backed by simulation results using a real services dataset. Those results showed that
+our model outperforms existing competitive and random coopetitive strategies.
 
@@
 
-\item \textbf{Winter 2015: }Thesis work and PhD Defense.
+\item \textbf{Winter 2015: }Thesis work and Ph.D. Defense.
 %\item Developing an open source, Java based Tool, with UI for
@@
 
-\subsection {Publications }
+\section {Publications }
 
@@
 Khosravifar, H.
-Otrok, \emph{``To Compete or to Cooperate?
+Otrok, \emph{``To Compete or Cooperate?
 This is the Question in Communities of Autonomous Services.''} In the Journal of Expert Systems and Applications, Feb.

### 2014-09-25 papers/webservice-coalition-learning/figures/matlab/coloredbar.m
changes

@@ -1,0 +1,25 @@
+function h = coloredbar( x, labels, colors, varargin )
+%Coloredbar - create a bar chart with passed in colours
+%   x - vector of values for bar heights
+%   labels - vector of strings for bar labels
+%   colors - vector of color specs for bar colours
+%   ... - additional value argument paris for bar chart
+%  
+% Returns: handle to bar object
+%
+    if(~isvector(x))
+        error('coloredbar currently only accepts single series\n');
+    end
+    for ii = length(x):-1:1
+        h = bar(x(1:ii), 'FaceColor', colors{ii});
+        hold on;
+    end
+    
+    set(gca, 'xticklabel', labels);
+    
+    for ii = 1:2:size(varargin, 2)
+        set(h, varargin{ii}, varargin{ii+1});
+    end
+
+end
+

### 2014-09-25 papers/webservice-coalition-learning/figures/matlab/mlisa_chart_utility.m

@@ -1,0 +1,116 @@
+% Create the data to be plotted
+
+color1 = [0.0,0.0,0.5];
+color2 = [0.7,0.7,0.95];
+fontsize = 12;
+
+[v,T,vT]=xlsread('mlisa_chart_utility.xlsx') 
+gainR020 = v((1:1:20),1);
+gainR010 = v((1:1:20),2);
+gainR007 = v((1:1:20),3);
+gainR005 = v((1:1:20),4);
+
+ratioR020 = v((25:1:44),1);
+ratioR010 = v((25:1:44),2);
+ratioR007 = v((25:1:44),3);
+ratioR005 = v((25:1:44),4);
+
+xvalue = (1:1:20)';
+wsname = vT((4:1:23),1);
+
+% Create the pie chart in position 1 of a 2x2 grid
+hFig = figure(1);
+set(hFig, 'Position', [100 100 800 800])
+%set(0,'DefaultAxesColorOrder',[1 0 0],'DefaultAxesLineStyleOrder','-|+|--|.|:')
+set(0,'DefaultAxesColorOrder',[0 0 0;0.5 0.5 0.5])
+
+
+% Create the bar chart in position 1 of a 3x2 grid
+subplot(2, 2, 1);
+%plot(xvalue, normal1, 's-', xvalue, attack1, '*-', 'linewidth', 2, 'markers',4);
+bar(xvalue(1:1:10), gainR020(1:1:10), 0.4, 'FaceColor',color1);
+hold on
+bar(xvalue(11:1:20), gainR020(11:1:20), 0.4, 'FaceColor',color2);
+xlabel('Trained WS           Rational WS','FontSize',fontsize);
+ylabel('Utility Gain','FontSize',fontsize);
+title ('R=0.2 (a)','FontSize',fontsize);
+%title('TITLE');
+axis([0 21 0 400]);
+set(gca,'XTick',[1 5 10 15 20]);
+hleg1 = legend('Trained', 'Rational');
+set(hleg1,'Orientation','horizontal');
+grid on
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'XTickLabel',wsname);
+%axes('xlim',[0 19],'xtick',xvalue,'xticklabel',wsname)
+
+%hleg1 = legend('Normal data', 'Attacks');
+%set(hleg1, 'Position', [.248,.842,.1,.2]);
+%set(hleg1,'Interpreter','none');
[…]

### 2014-09-25 papers/webservice-coalition-learning/figures/matlab/mlisa_chart_utility_ratio.m

@@ -1,0 +1,110 @@
+% Create the data to be plotted
+
+color1 = [0.0,0.0,0.5];
+color2 = [0.7,0.7,0.95];
+
+[v,T,vT]=xlsread('mlisa_chart_utility.xlsx') 
+gainR020 = v((1:1:20),1);
+gainR010 = v((1:1:20),2);
+gainR007 = v((1:1:20),3);
+gainR005 = v((1:1:20),4);
+
+ratioR020 = v((25:1:44),1);
+ratioR010 = v((25:1:44),2);
+ratioR007 = v((25:1:44),3);
+ratioR005 = v((25:1:44),4);
+
+xvalue = (1:1:20)';
+wsname = vT((4:1:23),1);
+
+% Create the pie chart in position 1 of a 2x2 grid
+hFig = figure(1);
+set(hFig, 'Position', [100 100 800 800])
+%set(0,'DefaultAxesColorOrder',[1 0 0],'DefaultAxesLineStyleOrder','-|+|--|.|:')
+set(0,'DefaultAxesColorOrder',[0 0 0;0.5 0.5 0.5])
+
+
+% Create the bar chart in position 1 of a 3x2 grid
+subplot(2, 2, 1);
+%plot(xvalue, normal1, 's-', xvalue, attack1, '*-', 'linewidth', 2, 'markers',4);
+bar(xvalue(1:1:10), ratioR020(1:1:10), 0.4, 'FaceColor',color1);
+hold on
+bar(xvalue(11:1:20), ratioR020(11:1:20), 0.4, 'FaceColor',color2);
+xlabel('Trained WS           Rational WS','FontSize',fontsize);
+ylabel('Utility Gain','FontSize',fontsize);
+title ('R=0.2 (a)','FontSize',fontsize);
+%title('TITLE');
+axis([0 21 0 22]);
+set(gca,'XTick',[1 5 10 15 20]);
+hleg1 = legend('Trained', 'Rational');
+grid on
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'XTickLabel',wsname);
+%axes('xlim',[0 19],'xtick',xvalue,'xticklabel',wsname)
+
+%hleg1 = legend('Normal data', 'Attacks');
+%set(hleg1, 'Position', [.248,.842,.1,.2]);
+%set(hleg1,'Interpreter','none');
+%set(hleg1,'Orientation','horizontal');
[…]

### 2014-09-25 papers/webservice-coalition-learning/figures/matlab/mlisa_roc.m

@@ -1,0 +1,59 @@
+[v,T,vT]=xlsread('mlisa_chart_roc.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+%set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|:|--|-.')
+%set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-.r*|:|--|-.')
+
+i=0:49;
+it=v(:,24);iy=v(:,24);iz=v(:,24);itt=v(:,24);
+t=v(:,25);y=v(:,29);z=v(:,34);tt=v(:,36);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(it,t,'--go',iy,y,'--mo',iz,z,':bs',itt,tt,'-.r*', 'MarkerSize',2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+%set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',0:200:1600);
+set(gca,'tickdir','in')
+%set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+%axis([0 50 0 1600]);
+
+% Add legend
[…]

### 2014-09-25 papers/webservice-coalition-learning/figures/matlab/mlisa_stats1.m

@@ -1,0 +1,59 @@
+[v,T,vT]=xlsread('mlisa_chart_stats.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|+-|.|:')
+
+i=0:62;
+t=v(:,1);y=v(:,2);z=v(:,3);tt=v(:,4);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,i,tt,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:63);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0:5000:30000);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '51';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    ' ';' ';'63';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 63 0 30000]);
+
+% Add legend
+hleg1 = legend('R=0.2','R=0.1','R=0.07','R=0.05');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.24,.63,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
[…]

### 2014-09-25 papers/webservice-coalition-learning/figures/matlab/mlisa_stats2.m

@@ -1,0 +1,59 @@
+[v,T,vT]=xlsread('mlisa_chart_stats.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|+-|.|:')
+
+i=0:62;
+t=v(:,21);y=v(:,22);z=v(:,23);tt=v(:,24);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,i,tt,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:63);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',0:5000:30000);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '51';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    ' ';' ';'63';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 63 0 1400]);
+
+% Add legend
+hleg1 = legend('R=0.2','R=0.1','R=0.07','R=0.05');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.74,.69,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
[…]

### 2014-09-25 papers/webservice-coalition-learning/figures/matlab/mlisa_stats3.m

@@ -1,0 +1,59 @@
+[v,T,vT]=xlsread('mlisa_chart_stats.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|+-|.|:')
+
+i=0:62;
+t=v(:,7);y=v(:,8);z=v(:,9);tt=v(:,10);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(i,t,i,y,i,z,i,tt,'linewidth', 2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:63);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0:0.5:3.5);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '51';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    ' ';' ';'63';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 63 0 3.5]);
+
+% Add legend
+hleg1 = legend('R=0.2','R=0.1','R=0.07','R=0.05');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.74,.69,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
+% Add title and axis labels
+% title('Trigonometric Functions', 'fontsize', 10);
[…]

### 2014-09-27 papers/webservice-coalition-learning/figures/matlab/mlisa_stats2.m
changes

@@ -7,7 +7,8 @@
 set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|+-|.|:')
 
 i=0:62;
-t=v(:,21);y=v(:,22);z=v(:,23);tt=v(:,24);
+%t=v(:,21);y=v(:,22);z=v(:,23);tt=v(:,24);
+t=v(:,31);y=v(:,32);z=v(:,33);tt=v(:,34);
 %set(gcf,'Position',[100 100 800 500]);
 set(gcf,'Position',[100 100 550 375]);
 

### 2014-09-29 papers/webservice-coalition-learning/figures/matlab/mlisa_stats1.m
changes

@@ -38,7 +38,7 @@ set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 axis([0 63 0 30000]);
 
 % Add legend
-hleg1 = legend('R=0.2','R=0.1','R=0.07','R=0.05');
+hleg1 = legend('R=0.20','R=0.10','R=0.07','R=0.05');
 %set(hleg1,'Location','NorthWest');
 set(hleg1, 'Position', [.24,.63,.1,.2]);
 set(hleg1,'Interpreter','none');

### 2014-09-29 papers/webservice-coalition-learning/figures/matlab/mlisa_stats2.m

@@ -36,10 +36,10 @@ set(gca,'XGrid','off','YGrid','on','ZGrid','off');
 set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 
 
-axis([0 63 0 1400]);
+axis([0 63 0 900]);
 
 % Add legend
-hleg1 = legend('R=0.2','R=0.1','R=0.07','R=0.05');
+hleg1 = legend('R=0.20','R=0.10','R=0.07','R=0.05');
 %set(hleg1,'Location','NorthWest');
 set(hleg1, 'Position', [.74,.69,.1,.2]);
 set(hleg1,'Interpreter','none');

### 2014-09-29 papers/webservice-coalition-learning/figures/matlab/mlisa_stats3.m

@@ -38,7 +38,7 @@ set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 axis([0 63 0 3.5]);
 
 % Add legend
-hleg1 = legend('R=0.2','R=0.1','R=0.07','R=0.05');
+hleg1 = legend('R=0.20','R=0.10','R=0.07','R=0.05');
 %set(hleg1,'Location','NorthWest');
 set(hleg1, 'Position', [.74,.69,.1,.2]);
 set(hleg1,'Interpreter','none');

### 2014-10-08 course-game/session1/ehsan_session1.tex
changes

--- 2013-12-17 proposal/presentation/ekpresentation/ehsan_presentation.tex
@@
 %\newtheorem{definition}{Definition}
-\title[Cooperative Decision Making for Communities of Autonomous Web Services]{Cooperative Decision Making for Communities of Autonomous Web Services}
-\author{Ehsan Khosrowshahi Asl\\ \vspace{0.2cm} Supervised by: \\Dr. Jamal Bentahar \\Dr. Hadi Otrok}
+\title[Lecture 8: Extensive Form Games with Perfect Information]{Lecture 8: Extensive Form Games with Perfect Information}
+\author{INSE 6441/2 DD\\ \vspace{0.2cm} Applied Game Theory and Mechanism Design \\ Fall 2014}
 \institute{Department of Computer Science and Software Engineering\\Concordia University}
-\date{December 17, 2013}
+\date{Novermber 17, 2014}
 \begin{document}
@@
 
-\begin{frame}{Presentation Outline}
+\begin{frame}{Overview}
     \begin{itemize}
@@
     	\item {\bf Introduction}
-    	\item Background and Literature Review
-    	\item Proposed Research
-    	\item Timeline and Feature Work
+    	\item S2
+    	\item S3
+    	\item S4
     \end{itemize}
 \end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame3 introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-%\section{Motivation}
-\subsection{Motivation}
-    \begin{frame}{Motivation}
-    \begin{itemize}
-        \item High reliance on web services created high competition and great business opportunities for online service developers
-        \item Community of web services: Clustering similar web services in order to:
-        \begin{itemize}
-            \item \textbf{Provide better user satisfaction through high availability and responsiveness}.
-            \item \textbf{Facilitate Web Service Discovery over Internet}.
-            \item \textbf{Maintain high reputation and market share}.
-        \end{itemize}
-    \end{itemize}
-    \begin{figure}[htbp]
-        \centering
-        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
-        \includegraphics[width=1.0 \columnwidth]{figures/wsinternet.png}
-        %%\includegraphics[scale=0.5]{figure1}
-        %\caption{The NetBill payment protocol} \label{figure7}
-    \end{figure}
-    \end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\subsection{Communities of Web Services}
-%    \begin{frame}{Community of Web Services}
-%       Communities of Web Services
-%       \begin{itemize}
-%           \item Ease and improve the process of Web services discovery in an open environment like the Internet
-%       	\item Improve service quality, availability and responsiveness
-%           \item Maintaining high reputation and market share
-%       \end{itemize}
-
-%       \begin{figure}[htbp]
-%           \centering
-            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
-%           \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
-            %%\includegraphics[scale=0.5]{figure1}
-            %\caption{The NetBill payment protocol} \label{figure7}
-%       \end{figure}
-
-%   \end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame10 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\subsection{Social commitments in MASs}
-    \begin{frame}{Communities of Web Services}
-        Communities of Web Services
-        \begin{itemize}
-            \itemsep=.35cm
-        	\item \textbf{Communities of web services operations}
-            \begin{itemize}
-              \item Community development
-              \item Web services attraction and retention
-              \item Web service selection
-            \end{itemize}                      	      	
-        \end{itemize}
-
-        \begin{figure}[htbp]
-            \centering
-            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
-            \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
-            %%\includegraphics[scale=0.5]{figure1}
-            %\caption{The NetBill payment protocol} \label{figure7}
-        \end{figure}
-    \end{frame}
-
-\begin{frame}{Problems and Research Questions}
-
-\begin{itemize}
-    \item \textbf{How can we model the
-        community of agent-based services in order to maximize the utility
-        of involved users, web services and community organizers?}
-        \begin{itemize}
-            \item Most of the work on communities of
-            services are either user-centric and focus on user satisfaction
-            or system-centric and focus on the whole system throughput, performance and utilization.
-        \end{itemize}
-
-    \item \textbf{How can we model fair and stable communities as coalitions
-        of agent-based web services?}
-        \begin{itemize}
-            \item All parties involved are self-interest agents and have the right to leave the community if they can improve their income in some other ways.
-        \end{itemize}
-
-\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}{Continue: Problems and Research Questions}
- \begin{itemize}
-   \item \textbf{How can we model and analyze the cooperation
-        among the community members in realistic, applicable and practical
-        settings?}
-        \begin{itemize}
-            \item The first issue is about the evaluation of web services that are working together inside communities.
-            \item The second issue is about the complexity of cooperative game theory solution concepts.
-        \end{itemize}
-
-\end{itemize}
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%    \begin{frame}{Multi-Agent Systems MASs}
-%        \begin{itemize}
-%            \itemsep=.35cm
-%        	\item Multi-Agent System (MAS).
-%            %\item Autonomous agents.
-%        	\item Knowledge in MASs.
-%            \item Social commitments in MASs.
-%        \end{itemize}
-%\end{frame}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{frame}{Transferable and Non Transferable Utility Games}
-%    \begin{itemize}
-%        \item \textbf{Games with Transferable Utility (TU games)}
-%        \begin{itemize}
-%            \item Utility is worth the same for all agents.
-%            \item Utility can be {\color{red} compared} or {\color{red} transferred} between agents.
-%            \item Irrespective of the division of the coalitional payoff.
-%            \begin{itemize}
-%                \item In that case members of the coalition enjoy the same total utility.
-%            \end{itemize}
-%        \end{itemize}
-%
-%
-%        \begin{definition} [Valuation or Characteristic Function]\label{dfn:valuationfunction}
-%            A \emph{valuation function v} associates a real number $v(C)$ to any subset $C \subseteq N$, i.e., $v:2^N \rightarrow R$ \\
-%            A {\color{blue}\emph{TU game}} is a pair $(N,v)$ where $N$ is a set of agents and where $v$ is a valuation function.
-%        \end{definition}
-%
-%
-%
-%        \item \textbf{Games with Non Transferable Utility (NTU games)} \\
-%            Agents have different preferences over coalitions and rewards. Non-monetary rewards, i.e. item allocation type of problems where items have %different values for different players.
-%    \end{itemize}
+\begin{frame}{Transferable and Non Transferable Utility Games}
+    \begin{itemize}
+        \item \textbf{Games with Transferable Utility (TU games)}
+        \begin{itemize}
+            \item Utility is worth the same for all agents.
+            \item Utility can be {\color{red} compared} or {\color{red} transferred} between agents.
+            \item Irrespective of the division of the coalitional payoff.
+            \begin{itemize}
+                \item In that case members of the coalition enjoy the same total utility.
+            \end{itemize}
+        \end{itemize}
 
-%\end{frame}
+        \begin{definition} [Valuation or Characteristic Function]\label{dfn:valuationfunction}
+            A \emph{valuation function v} associates a real number $v(C)$ to any subset $C \subseteq N$, i.e., $v:2^N \rightarrow R$ \\
+            A {\color{blue}\emph{TU game}} is a pair $(N,v)$ where $N$ is a set of agents and where $v$ is a valuation function.
+        \end{definition}
+
+        \item \textbf{Games with Non Transferable Utility (NTU games)} \\
+            Agents have different preferences over coalitions and rewards. Non-monetary rewards, i.e. item allocation type of problems where items have different values for different players.
+    \end{itemize}
+\end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
         \begin{center}
-            $Core(N,v) = \{x \in R^n | x(N) \leq v(N) \wedge x(C) \geq v(C), \forall C \subseteq N\}$
+            $Core(N,v) = \{x \in R^n | x(N) \leq v(N) \wedge x(C) \geq v(C), \forall C \subseteq N\}$ \\
         \end{center}
+        \small{$x(N) = \sum_{i \in N} x(i)$}
     \end{definition}
@@
         \item Core and Shapley value are combinatorial problems.
-        \item There are other well-known solution concepts: The bargaining set, The nucleolus and The nucleolus.
+        \item There are other well-known solution concepts: Bargaining set, nucleolus and kernel.
     \end{itemize}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Proposed Research}
-\begin{frame}{Presentation Outline}
-    \begin{itemize}
-     	\itemsep=.5cm
-    	\item Introduction
-    	\item Background and Literature Review
-    	\item {\bf Proposed Research}
-    	\item Timeline and Feature Work
-    \end{itemize}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame16 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Problem Formulation and Modeling}
-
-\begin{frame}{Problem Formulation and Modeling}
-    \begin{itemize}
-        \item Communities are robust service providers with well established market share and reputation.
-        \item The community is characterized by a request rate $R_C$.
-        \item Web services can perform tasks with some throughput rate ($Th_{ws}$).
-        \item Web services come with different values of $QoS_{ws}$ for different metrics.
-    \end{itemize}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Task Distribution}
-    \begin{itemize}
-        \item Our model uses a slightly modified \emph{weighted fair queuing} method for task distribution rather than Contract-Net.
-        \item All the input flow is multiplexed amount different web services with weights proportional to their throughput value ($Th_{ws}$).
-        \item Queues will happen if $R_C$ is more than summation web services throughput.
-        \item Weighted task rate of: $R_C \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ or $Th_{ws}$
-    \end{itemize}
-    \begin{figure}[htbp]
-        \centering
-        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
-        \includegraphics[width=0.8 \columnwidth]{figures/community.png}
-        %%\includegraphics[scale=0.5]{figure1}
-        %\caption{The NetBill payment protocol} \label{figure7}
-    \end{figure}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Community Revenue}
-    \begin{itemize}
-        \item Maximum potential output of a community:
-            \begin{equation*}
-                PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
-            \end{equation*}
-        \item if $\sum_{ws}{Th_{ws}} > R_C$, the community cannot perform at its maximum potential.
-        \item Actual output:
-            \begin{equation}\label{out_c}
-                Out(C) = \left\{
-                  \begin{array}{l l}
-                    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{C}$}\\
-                    PO(C) \times \frac{R_{C}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{C}$}
-                  \end{array} \right.
-            \end{equation}
-    \end{itemize}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Example 1}
-    \begin{table}[!t]
-    \renewcommand{\arraystretch}{1.3}
-    % if using array.sty, it might be a good idea to tweak the value of
-    % \extrarowheight as needed to properly center the text within the cells
-    \label{example_1}
-    \centering
-    \begin{tabular}{c c c c}
-    \hline
-    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
-    \hline
-    1 & 0.8 & 4 & 3.2\\
-    2 & 0.8 & 5 & 4.0\\
-    3 & 0.8 & 3 & 2.4\\
-    \hline
-    \end{tabular}
-    \end{table}
-
-    \begin{table}[!t]
-    \renewcommand{\arraystretch}{1.3}
-    % if using array.sty, it might be a good idea to tweak the value of
-    % \extrarowheight as needed to properly center the text within the cells
-    % \caption{Three web services}
-    \label{example_1_2}
-    \centering
-    \begin{tabular}{c c || c c}
-    \hline
-    Community & Worth & Community & Worth\\
-    \hline
-    $\left\{1\right\}$ & 3.2 & $\left\{1,2\right\}$ & 7.2\\
-    $\left\{2\right\}$ & 4.0 & $\left\{1,3\right\}$ & 5.6\\
-    $\left\{3\right\}$ & 2.4 & $\left\{2,3\right\}$ & 6.4\\
-    $\left\{1,2,3\right\}$ & 8.0\\
-    \hline
-    Community $R_C$: 10\\
-    \hline
-    \end{tabular}
-    \end{table}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Example 2}
-    \begin{table}[!t]
-    \renewcommand{\arraystretch}{1.3}
-    % if using array.sty, it might be a good idea to tweak the value of
-    % \extrarowheight as needed to properly center the text within the cells
-    \label{example_2}
-    \centering
-    \begin{tabular}{c c c c}
-    \hline
-    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
-    \hline
-    1 & 0.8 & 5 & 4.0\\
-    2 & 0.7 & 6 & 4.2\\
-    3 & 0.7 & 4 & 2.8\\
-    \hline
-    \end{tabular}
-    \end{table}
-
-    \begin{table}[!t]
-    \renewcommand{\arraystretch}{1.3}
-    % if using array.sty, it might be a good idea to tweak the value of
-    % \extrarowheight as needed to properly center the text within the cells
-    % \caption{Three web services}
-    \label{example_2_2}
-    \centering
-    \begin{tabular}{c c || c c}
-    \hline
-    Community & Worth & Community & Worth\\
-    \hline
-    $\left\{1\right\}$ & 4.0 & $\left\{1,2\right\}$ & 7.4\\
-    $\left\{2\right\}$ & 4.2 & $\left\{1,3\right\}$ & 6.8\\
-    $\left\{3\right\}$ & 2.8 & $\left\{2,3\right\}$ & 7.0\\
-    $\left\{1,2,3\right\}$ & 7.3\\
-    \hline
-    Community $R_C$: 10\\
-    \hline
-    \end{tabular}
-    \end{table}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Example 3}
-    \begin{table}[!t]
-    \renewcommand{\arraystretch}{0.8}
-    % if using array.sty, it might be a good idea to tweak the value of
-    % \extrarowheight as needed to properly center the text within the cells
-    \label{example_3}
-    \centering
-    \begin{tabular}{c c c c}
-    \hline
-    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
-    \hline
-    1 & 0.8 & 10 & 5\\
-    2 & 0.8 & 20 & 5\\
-    3 & 0.8 & 30 & 5\\
-    \hline
-    \end{tabular}
-    \end{table}
-
-    \begin{table}[!t]
-    \renewcommand{\arraystretch}{0.8}
-    % if using array.sty, it might be a good idea to tweak the value of
-    % \extrarowheight as needed to properly center the text within the cells
-    % \caption{Three web services}
-    \label{example_3_2}
-    \centering
-    \begin{tabular}{c c || c c}
-    \hline
-    Community & Worth & Community & Worth\\
-    \hline
-    $\left\{C_{ms_1}\right\}$ & 0 & $\left\{C_{ms_2}\right\}$ & 0\\
-    $\left\{C_{ms_1}, ws_1\right\}$ & 8 & $\left\{C_{ms_2}, ws_1\right\}$ & 8\\
-    $\left\{C_{ms_1}, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_2\right\}$ & 16\\
-    $\left\{C_{ms_1}, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_3\right\}$ & 24\\
-    $\left\{C_{ms_1}, ws_1, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2\right\}$ & 24\\
-    $\left\{C_{ms_1}, ws_1, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_3\right\}$ & 32\\
-    $\left\{C_{ms_1}, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_2, ws_3\right\}$ & 32\\
-    $\left\{C_{ms_1}, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2, ws_3\right\}$ & 32\\
-    $\left\{C_{ms_1}, C_{ms_2}, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
-    $\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
-    \hline
-    Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
-    \hline
-    \end{tabular}
-    \end{table}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame19 Proposed Research
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Web Service Cooperative Games}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Scenario One: Web Services and One Community}
-    \begin{figure}[htbp]
-        \centering
-        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
-        \includegraphics[width=0.8 \columnwidth]{figures/scenario1.png}
-        %%\includegraphics[scale=0.5]{figure1}
-        %\caption{The NetBill payment protocol} \label{figure7}
-    \end{figure}
-
-    \begin{itemize}
-        \item A typical WS community, where web services can join or leave.
-        \item $v(C) = Out(C)$.
-        \item Membership decision in made based on throughput and QoS of the web services.
-        \item Community master needs to get quality web services to keep community stable, so other web services have no incentive to leave.
-    \end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Scenario One: Web Services and One Community}
-
-    \begin{itemize}
-        \item Upon receiving membership request the master web service checks if the coalition will be stable having the new member.
-        \item If the game is convex, core exists.
-        \item If the game is convex, Shapley value is in core.
-        \item Convexity Condition:
-        \begin{center}
-          $v(A \cup B) \geq v(A) + v(B) - v(A \cap B)$ \\
-          $\Leftrightarrow$  \\
-          $\forall S,T | S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N,$ \\
-          {\color{blue} $v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)$ }
-        \end{center}
-        \item Depth-1 Convexity Check: $O(n)$
-        \item Depth-2 Convexity Check: $O(n^2)$
-    \end{itemize}
-
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Scenario One: Web Services and One Community}
-
-    \begin{figure}[htbp]
-        \centering
-        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
-        \includegraphics[width=0.92 \columnwidth]{figures/dp.png}
-        %%\includegraphics[scale=0.5]{figure1}
-        %\caption{The NetBill payment protocol} \label{figure7}
-    \end{figure}
-
-    %\begin{itemize}
-    %    \item Approximation of the optimum result for each level, is it possible?
-    %\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{frame}{Scenario Two: Web Services and Many Communities}
-    \begin{itemize}
-        \item Based on Coalition Structure theory
-        \begin{itemize}
-            \item What coalitions to form?
-            \item Stability in coalition structure, is a partition of players, where no other partition can provide all agents with better utility.
-            \item Social welfare: $\operatorname*{arg\,max}_{CS} v(CS)$ where $v(CS) = \sum_{C \in CS}v(C)$.
-        \end{itemize}
-        \item Has to be distributed not centralized.
-        \item Merge and Split Algorithm {\footnotesize{\color{blue}{(Krzysztof R. Apt and Andreas Witzel)}}}
-        \begin{itemize}
-            \item Is iterative
-            \item Converges to a final partition
-        \end{itemize}
-    \end{itemize}
-    \begin{figure}[htbp]
-        \centering
-        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
-        \includegraphics[width=0.5 \columnwidth]{figures/scenario2.png}
-        %%\includegraphics[scale=0.5]{figure1}
-        %\caption{The NetBill payment protocol} \label{figure7}
-    \end{figure}       	
 \end{frame}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame26 Contribution and Research Activities %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Preliminary Results}
-\begin{frame}{Preliminary Results}
-
-    \begin{figure}[!t]
-    \centering
-    %\includegraphics[scale=0.6]{graph1Final+.eps}
-    \includegraphics[width=2.1in]{figures/task_done_opt.pdf}
-    \includegraphics[width=2.1in]{figures/task_qos_opt.pdf}
-    \caption{Part (a): Cumulative number of requests successfully
-    done. Part (b): Average QoS of requests performed.}
-    \label{performanceall}
-    \end{figure}
-
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Preliminary Results}
-    \begin{figure}[!t]
-        \centering
-        %\includegraphics[scale=0.6]{graph1Final+.eps}
-        \includegraphics[width=3in]{figures/least_core.pdf}
-        \caption{Analysis of \emph{$\epsilon$-core} set non-emptiness, for different values of $\epsilon$}. \label{f_leastcore}
-    \end{figure}
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Preliminary Results}
-    \begin{figure}[!t]
-        \centering
-        %\includegraphics[scale=0.6]{graph1Final+.eps}
-        \includegraphics[width=2.1in]{figures/s2_task_done.pdf}
-        \includegraphics[width=2.1in]{figures/s2_task_qos.pdf}
-        \caption{Part (a): Cumulative number of tasks succesfully done. Part
-        (b): Average QoS of tasks performed.} \label{performancemany}
-    \end{figure}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Preliminary Results}
-    \begin{figure}[!t]
-        \centering
-        %\includegraphics[scale=0.6]{graph1Final+.eps}
-        \includegraphics[width=1.45in]{figures/avg_task_ws_done.pdf}
-        \includegraphics[width=1.45in]{figures/avg_qos_ws_done.pdf}
-        \includegraphics[width=1.45in]{figures/avg_avail_ws_done.pdf}
-        \caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
-        (b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
-    \end{figure}
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame30 outline page
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Milestones}
-\begin{frame}{Milestones}
-    \begin{itemize}
-     	\itemsep=.5cm
-    	\item Introduction
-    	\item Background and Literature Review
-    	\item Proposed Research
-    	\item {\bf Timeline and Feature Work}
-    \end{itemize}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Research Activities Goal}
-\begin{frame}{Research Activities Goal}
-    \begin{enumerate}
-        \item Analyzing other cooperative solution concepts such as Kernel
-        and Nucleolus where payoff division is guaranteed to exist and may
-        have optimal results.
-
-        \item Applying other valuation function in our scenarios using for
-        instance Weighted Voting Games (WCG) in order to develop a
-        multiple weighted algorithm to find best coalition structures
-        satisfying different weights on each community.
-
-        \item Analyzing the impact of Q-learning and reinforcement
-        learning on the performance of our model.
-
-        \item Developing a community membership algorithm technique for
-        our agents in "incomplete information" settings.
-
-        %\item Developing an open source, Java based Tool, with UI for
-        %solving Core and Shapely solution concepts based on different
-        %input valuation functions.
-    \end{enumerate}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Representation and Complexity Issues}
-    \begin{itemize}
-        \item Core and Shapley value are combinatorial problems.
-        \item Input size is exponential.
-        \item Compact or succinct representation of coalition games. A representation so that the input size is a polynomial in the number of agents.
-    \end{itemize}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Induced Subgraph Games}
-    \begin{itemize}
-        \item An induced subgraph game is a coalitional game defined by an undirected weighted graph $G = (V,W)$ where $V$ is the set of vertices and $W : V \rightarrow V$ is the set of edges weights.
-For $(i,j) \in V^2$, $w_{ij}$ is the weight of the edge between $i$ and $j$.
-        \item $N = V$
-        \item for all $C \subseteq N, v(C) = \sum_{(i,j) \in C} w_{ij}$
-        \item {\color{blue}Space Complexity:} Using an adjacency matrix, we need to provide $n^2$ entries.
-        \item {\color{blue}Convexity:} If all the weights are nonnegative then the game is convex.
-        \item {\color{blue}Shapley Value:} $\phi_i(N,v) = \frac{1}{2} \sum_{(i,j) \in N^2 | i \neq j}w_{ij}$
-        \item This is {\color{blue}not complete}. Many coalition games cannot be represented by a induced subgraph game.
-
-    \end{itemize}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Different Compact Representations of Coalition Games}
-
-    \begin{table}
-        \small
-        \begin{tabular}{l|c|c|c|c}
-        Representations                  & Space    & Shapley                  & Core Existence  & Complete     \\ \hline
-        Graph (w+)                       & P        & P                        & P               & Not          \\
-        Graph                            & P        & NP-Complete              & NP-Complete     & Not          \\
-        Synergy                          & NA       & P (l input)              & P               & Not          \\
-        Multi-issue                      & NA       & P (l input)              & NP-Complete     & Complete     \\
-        MC-net                           & NA       & P (l input)              & NP-hard         & Complete     \\
-        \end{tabular}
-    \end{table}
-
-    \begin{itemize}
-        \item Our web service community valuation function representation ($v(C) = out(C)$) space requirement, grows linearly to input size.
-        \item Developing an approximation algorithm for shapely value payoff distribution vector in community setting.
-    \end{itemize}
-
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Timeline}
-    \begin{frame}{Timeline}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1 \columnwidth]{figures/timetable.png}
-%\includegraphics[width=16cm, height=21cm]{figures/figure6.eps}
-%\caption{Schedule time of research} \label{figure6}
-\end{center}
-\end{figure}
-    \end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame27 Milestones %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Publications}
-
-    \begin{enumerate}
-        \item Published a paper in 10th International Conference on Services Computing; \emph{"Efficient Coalition Formation for Web Services"} {\color{blue} (Accepted)}
-        \item Submitted a Journal Paper to the International Journal of Web and Grid Services; IEEE Transactions on Services Computing {\color{blue} (Second round of review)}
-        \item Submitted a Paper to the 10th International Conference on Service Oriented Computing (ICSOC 2012); \emph{"Analyzing Coopetition Strategies of Services within Communities"} {\color{blue} (Accepted)}
-        \item Submitted a Journal Paper to the International Journal of Expert Systems With Applications; \emph{"To Compete or to Cooperate?
-This is the Question in Communities of Autonomous Services"}
-    \end{enumerate}
-
-%\centering
-%\begin{itemize}
-%\item \textbf{Questions Please !}
-%\end{itemize}
-
-\end{frame}
-
 \end{document}

### 2014-10-10 papers/webservice-coalition-learning/figures/matlab/mlisa_stats1.m
changes

@@ -38,7 +38,7 @@ set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 axis([0 63 0 30000]);
 
 % Add legend
-hleg1 = legend('R=0.20','R=0.10','R=0.07','R=0.05');
+hleg1 = legend('R=0.05','R=0.07','R=0.10','R=0.20');
 %set(hleg1,'Location','NorthWest');
 set(hleg1, 'Position', [.24,.63,.1,.2]);
 set(hleg1,'Interpreter','none');

### 2014-10-10 papers/webservice-coalition-learning/figures/matlab/mlisa_stats2.m

@@ -36,10 +36,10 @@ set(gca,'XGrid','off','YGrid','on','ZGrid','off');
 set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 
 
-axis([0 63 0 900]);
+axis([0 63 0 890]);
 
 % Add legend
-hleg1 = legend('R=0.20','R=0.10','R=0.07','R=0.05');
+hleg1 = legend('R=0.05','R=0.07','R=0.10','R=0.20');
 %set(hleg1,'Location','NorthWest');
 set(hleg1, 'Position', [.74,.69,.1,.2]);
 set(hleg1,'Interpreter','none');

### 2014-10-10 papers/webservice-coalition-learning/figures/matlab/mlisa_stats3.m

@@ -22,7 +22,7 @@ grid on;
 %set(gca,'Ycolor',[0.5 0.5 0.5]);
 set(gca,'XTick',1:1:63);
 %set(gca,'YTick',7000:1500:18000);
-set(gca,'YTick',0:0.5:3.5);
+set(gca,'YTick',0:0.2:3.5);
 set(gca,'tickdir','in')
 set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
     '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
@@ -35,10 +35,10 @@ set(gca,'XGrid','off','YGrid','on','ZGrid','off');
 set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
 
 
-axis([0 63 0 3.5]);
+axis([0 63 1 2.2]);
 
 % Add legend
-hleg1 = legend('R=0.20','R=0.10','R=0.07','R=0.05');
+hleg1 = legend('R=0.05','R=0.07','R=0.10','R=0.20');
 %set(hleg1,'Location','NorthWest');
 set(hleg1, 'Position', [.74,.69,.1,.2]);
 set(hleg1,'Interpreter','none');
@@ -48,7 +48,8 @@ set(hleg1,'FontSize',10);
 
 % Add title and axis labels
 % title('Trigonometric Functions', 'fontsize', 10);
-xlabel({'Time';'(a)'}, 'FontSize',14);
+%xlabel({'Time';'(a)'}, 'FontSize',14);
+xlabel('Time', 'FontSize',14);
 ylabel('Utility Gain', 'FontSize',14);
 
 %Caxes = copyobj(gca,gcf);

### 2014-11-03 course-game/session1/ehsan_session1.tex
changes

@@
      	\itemsep=.5cm
-    	\item {\bf Introduction}
-    	\item S2
-    	\item S3
-    	\item S4
+    	\item {\bf Coalition Games}
+    	\item Stability and Core
+    	\item Fairness and Shapley Value
+    	\item Other Solution Conecpts
+        \item Practical Example
     \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Background}
-\begin{frame}{Presentation Outline}
-    \begin{itemize}
-     	\itemsep=.5cm
-    	\item Introduction
-    	\item {\bf Background and Literature Review}
-    	\item Proposed Research
-    	\item Timeline and Feature Work
-    \end{itemize}
-\end{frame}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame9 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame11 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Coalition Games}
 \subsection{Cooperative Game Theory}
@@
     \end{itemize}
+
+    $\forall C \subseteq S \subseteq N$
+    \begin{itemize}
+        \item {\color{blue} Monotonic:} $v(C) \leq v(S)$
+    \end{itemize}
 \end{frame}
@@
         \item {\color{blue} Group rationality:} $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
+        \begin{itemize}
+            \item if $\sum_{i \in N} x(i) < v(C)$ is not worth it for some $C$
+            \item if $\sum_{i \in N} x(i) > v(C)$ is not possible for all $C$
+        \end{itemize}
+        \item {\color{blue} Pareto Optimal:} $\sum_{i \in N} x(i) = v(N)$
+        \begin{itemize}
+            \item no agent can improve its payoff without lowering the payoff of another agent
+        \end{itemize}
+        \item {\color{blue} Anonymity:} a solution is independent of the names of the player.
     \end{itemize}
@@
 \end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Stability and Core}
+\subsection{Stability and Core}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Overview}
+    \begin{itemize}
+     	\itemsep=.5cm
+    	\item Coalition Games
+    	\item {\bf Stability and Core}
+    	\item Fairness and Shapley Value
+    	\item Other Solution Conecpts
+        \item Practical Example
+    \end{itemize}
+\end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Fairness and Shapley Value}
+\subsection{Fairness and Shapley Value}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Overview}
+    \begin{itemize}
+     	\itemsep=.5cm
+    	\item Coalition Games
+    	\item Stability and Core
+    	\item {\bf Fairness and Shapley Value}
+    	\item Other Solution Conecpts
+        \item Practical Example
+    \end{itemize}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}{Solution Concepts: Shapley Value}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Other Solution Concepts}
+\subsection{Other Solution Concepts}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Overview}
+    \begin{itemize}
+     	\itemsep=.5cm
+    	\item Coalition Games
+    	\item Stability and Core
+    	\item Fairness and Shapley Value
+    	\item {\bf Other Solution Conecpts}
+        \item Practical Example
+    \end{itemize}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}{$\epsilon$-Core}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Excess of a coalition}
+    \begin{itemize}
+        \item We consider one way to compare two imputations.
+    \end{itemize}
+
+    \begin{definition} [Excess of a coalition]\label{dfn:marginalcontribution}
+        Let (N,v) be a $TU$ game, $C \subseteq N$ be a coalition, and $x$ be a payoff distribution over $N$. The excess $e(C,x)$ of coalition $C$ at $x$ is the quantity $e(C,x) = v(C) - x(C)$.
+    \end{definition}
+
+    \begin{itemize}
+        \item Example: 
+        \begin{itemize}
+            \item let $N={1,2,3}, C={1,2}, v({1,2})=8, x=(3,2,5)$
+            \item $e(C,x)=v({1,2})-(x_1 + x_2)=8-(3+2)=3.$
+        \end{itemize}
+        \item We can interpret a positive excess $(e(C,x) > 0)$ as the amount of dissatisfaction or {\color{blue} complaint} of the members of $C$ from the allocation x.
+        \item We can use the excess to define the core:
+        \begin{itemize}
+            \item $Core(N,v)=\{x \in R^n | x is an imputation and \forall C \subseteq N, e(C,x) \leq 0\}$
+        \end{itemize}
+        \item This definition shows that no coalition has any complaint: each coalition's demand can be granted.
+    \end{itemize}
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Excess of a coalition: Example}
+
+    \centerline{$N = {1,2,3}$, $v(\{i\})=0$ $for$ $i \in \{1,2,3\}$ $v(\{1,2\}) = 5$}
+    \centerline{$v(\{1,3\}) = 6$, $v(\{2,3\}) = 6$, $v(N) = 8$}
+
+     \begin{itemize}
+        \item Let us consider two payoff vectors $x = \{3, 3,2\}$ and $y = \{2, 3,3\}$.
+        \item Let $e(x)$ denote the sequence of excesses of all coalitions at $x$.
+     \end{itemize}
+
+     \begin{table}[!htb]
+        \begin{minipage}{.5\linewidth}
+          \centering
+            \begin{tabular}{c|c}                
+                \multicolumn{2}{c}{x = \{3,3,2\}} \\
+                \hline
+                \emph{Coalition C} & $e(C,x)$\\
+                \hline
+                \{1\} & -3\\
+                \{2\} & -3\\
+                \{3\} & -3\\
+                \{1,2\} & -1\\
+                \{1,3\} & 1\\
+                \{2,3\} & 1\\
+                \{1,2,3\} & 0\\
+            \end{tabular}
+        \end{minipage}%
+        \begin{minipage}{.5\linewidth}
+          \centering            
+            \begin{tabular}{c|c}                
+                \multicolumn{2}{c}{x = \{2,3,3\}} \\            
+                \hline
+                \emph{Coalition C} & $e(C,x)$\\
+                \hline
+                \{1\} & -2\\
+                \{2\} & -3\\
+                \{3\} & -3\\
+                \{1,2\} & 0\\
+                \{1,3\} & 1\\
+                \{2,3\} & 0\\
+                \{1,2,3\} & 0\\
+            \end{tabular}
+        \end{minipage}
+    \end{table}
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Excess of a coalition}
+    \begin{itemize}
+        \item Which payoff should we prefer? $x$ or $y$? 
+        \item Let us write the excess in the decreasing order (from the greatest excess to the smallest)
+        \begin{itemize}
+            \item $Sorted$ $e(C,x):$ $\{1, 1, 0,-1,-2,-3,-3\}$
+            \item $Sorted$ $e(C,y):$ $\{1, 0, 0, 0,-2,-3,-3\}$
+        \end{itemize}
+    \end{itemize}
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Excess of a coalition: lexicographical order}
+
+    \begin{definition} [lexicographical order $\geq_{lex}$]\label{dfn:lexorder}
+        Let $\geq_{lex}$ denote the lexicographical ordering of $R^m$, 
+        $\forall(x,y) \in R^m, x \geq y$ $iff$ 
+        \begin{itemize}
+            \item $x=y$ or
+            \item $\exists t$ $1 \leq t \leq m$ and $\forall i$ $1 \leq i < t$ $x_i = y_i$ and $x_t > y_t$
+        \end{itemize}
+    \end{definition}
+
+    \begin{itemize}
+        \item Example:
+        \begin{itemize}
+            \item let $\{1, 1, 0,-1,-2,-3,-3\} \geq_{lex} \{1, 0, 0, 0,-2,-3,-3\}$            
+        \end{itemize}        
+        \item Let $l$ be a sequence of $m$ reals. We denote by {\color{blue} $l^*$} the {\color{blue} reordering} of {\color{blue} $l$} in {\color{blue} decreasing} order.
+        \item In the example, $e(x) = \{3,-3,-2,-1, 1, 1,0\}$ and then $e(x)^* = \{1, 1, 0,-1,-2,-3,-3\}$.
+        \item Hence, we can say that $y$ is better than $x$ by writing $e(x)^* \geq e(y)^*$
+    \end{itemize}
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Nucleolus}
+    \begin{itemize}
+        \item Let $(N,v)$ be a $TU$ game.
+        \item Let $Imp$ be the set of all imputations.
+        \item The {\color{blue}$nucleolus Nu(N,v)$} is the set
+        \begin{itemize}
+            \item $Nu(N,v) = \{x \in Imp|\forall y \in Imp e(y)* \geq_{lex} e(x)*\}$
+        \end{itemize}
+    \end{itemize}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Practical Example}
+\subsection{Problem Formulation and Modeling}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Overview}
+    \begin{itemize}
+     	\itemsep=.5cm
+    	\item Coalition Games
+    	\item Stability and Core
+    	\item Fairness and Shapley Value
+    	\item Other Solution Conecpts
+        \item {\bf Practical Example}
+    \end{itemize}
+\end{frame}
+
+\begin{frame}{Problem Formulation and Modeling}
+    \begin{itemize}
+        \item Communities of web services are robust service providers with well established market share and reputation.
+        \item The community is characterized by a request rate $R_C$.
+        \item Web services can perform tasks with some throughput rate ($Th_{ws}$).
+        \item Web services come with different values of $QoS_{ws}$ for different metrics.
+    \end{itemize}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Task Distribution}
+    \begin{itemize}
+        \item Our model uses a slightly modified \emph{weighted fair queuing} method for task distribution rather than Contract-Net.
+        \item All the input flow is multiplexed among different web services with weights proportional to their throughput value ($Th_{ws}$).
+        \item Queues will happen if $R_C$ is more than the summation of web services throughput.
+        \item Weighted task rate: $R_C \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ or $Th_{ws}$
+    \end{itemize}
+    \begin{figure}[htbp]
+        \centering
+        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
+        \includegraphics[width=0.8 \columnwidth]{figures/community.png}
+        %%\includegraphics[scale=0.5]{figure1}
+        %\caption{The NetBill payment protocol} \label{figure7}
+    \end{figure}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Community Revenue}
+    \begin{itemize}
+        \item Maximum potential output of a community:
+            \begin{equation*}
+                PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
+            \end{equation*}
+        \item if $\sum_{ws}{Th_{ws}} > R_C$, the community cannot perform at its maximum potential.
+        \item Actual output:
+            \begin{equation}\label{out_c}
+                Out(C) = \left\{
+                  \begin{array}{l l}
+                    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{C}$}\\
+                    PO(C) \times \frac{R_{C}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{C}$}
+                  \end{array} \right.
+            \end{equation}
+    \end{itemize}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Example 1}
+    \begin{table}[!t]
+    \renewcommand{\arraystretch}{1.3}
+    % if using array.sty, it might be a good idea to tweak the value of
+    % \extrarowheight as needed to properly center the text within the cells
+    \label{example_1}
+    \centering
+    \begin{tabular}{c c c c}
+    \hline
+    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
+    \hline
+    1 & 0.8 & 4 & 3.2\\
+    2 & 0.8 & 5 & 4.0\\
+    3 & 0.8 & 3 & 2.4\\
+    \hline
+    \end{tabular}
+    \end{table}
+
+    \begin{table}[!t]
+    \renewcommand{\arraystretch}{1.3}
+    % if using array.sty, it might be a good idea to tweak the value of
+    % \extrarowheight as needed to properly center the text within the cells
+    % \caption{Three web services}
+    \label{example_1_2}
+    \centering
+    \begin{tabular}{c c || c c}
+    \hline
+    Community & Worth & Community & Worth\\
+    \hline
+    $\left\{1\right\}$ & 3.2 & $\left\{1,2\right\}$ & 7.2\\
+    $\left\{2\right\}$ & 4.0 & $\left\{1,3\right\}$ & 5.6\\
+    $\left\{3\right\}$ & 2.4 & $\left\{2,3\right\}$ & 6.4\\
+    $\left\{1,2,3\right\}$ & 8.0\\
+    \hline
+    Community $R_C$: 10\\
+    \hline
+    \end{tabular}
+    \end{table}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{frame}{Example 2}
+%    \begin{table}[!t]
+%    \renewcommand{\arraystretch}{1.3}
+%    % if using array.sty, it might be a good idea to tweak the value of
+%    % \extrarowheight as needed to properly center the text within the cells
+%    \label{example_2}
+%    \centering
+%    \begin{tabular}{c c c c}
+%    \hline
+%    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
+%    \hline
+%    1 & 0.8 & 5 & 4.0\\
+%    2 & 0.7 & 6 & 4.2\\
+%    3 & 0.7 & 4 & 2.8\\
+%    \hline
+%    \end{tabular}
+%    \end{table}
+%
+%    \begin{table}[!t]
+%    \renewcommand{\arraystretch}{1.3}
+%    % if using array.sty, it might be a good idea to tweak the value of
+%    % \extrarowheight as needed to properly center the text within the cells
+%    % \caption{Three web services}
+%    \label{example_2_2}
+%    \centering
+%    \begin{tabular}{c c || c c}
+%    \hline
+%    Community & Worth & Community & Worth\\
+%    \hline
+%    $\left\{1\right\}$ & 4.0 & $\left\{1,2\right\}$ & 7.4\\
+%    $\left\{2\right\}$ & 4.2 & $\left\{1,3\right\}$ & 6.8\\
+%    $\left\{3\right\}$ & 2.8 & $\left\{2,3\right\}$ & 7.0\\
+%    $\left\{1,2,3\right\}$ & 7.3\\
+%    \hline
+%    Community $R_C$: 10\\
+%    \hline
+%    \end{tabular}
+%    \end{table}
+%\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Example 2}
+    \begin{table}[!t]
+    \renewcommand{\arraystretch}{0.8}
+    % if using array.sty, it might be a good idea to tweak the value of
+    % \extrarowheight as needed to properly center the text within the cells
+    \label{example_3}
+    \centering
+    \begin{tabular}{c c c c}
+    \hline
+    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
+    \hline
+    1 & 0.8 & 10 & 5\\
+    2 & 0.8 & 20 & 5\\
+    3 & 0.8 & 30 & 5\\
+    \hline
+    \end{tabular}
+    \end{table}
+
+    \begin{table}[!t]
+    \renewcommand{\arraystretch}{0.8}
+    % if using array.sty, it might be a good idea to tweak the value of
+    % \extrarowheight as needed to properly center the text within the cells
+    % \caption{Three web services}
+    \label{example_3_2}
+    \centering
+    \begin{tabular}{c c || c c}
+    \hline
+    Community & Worth & Community & Worth\\
+    \hline
+    $\left\{C_{ms_1}\right\}$ & 0 & $\left\{C_{ms_2}\right\}$ & 0\\
+    $\left\{C_{ms_1}, ws_1\right\}$ & 8 & $\left\{C_{ms_2}, ws_1\right\}$ & 8\\
+    $\left\{C_{ms_1}, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_2\right\}$ & 16\\
+    $\left\{C_{ms_1}, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_3\right\}$ & 24\\
+    $\left\{C_{ms_1}, ws_1, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2\right\}$ & 24\\
+    $\left\{C_{ms_1}, ws_1, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_3\right\}$ & 32\\
+    $\left\{C_{ms_1}, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_2, ws_3\right\}$ & 32\\
+    $\left\{C_{ms_1}, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2, ws_3\right\}$ & 32\\
+    $\left\{C_{ms_1}, C_{ms_2}, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
+    $\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
+    \hline
+    Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
+    \hline
+    \end{tabular}
+    \end{table}
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame19 Proposed Research
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Web Service Cooperative Games}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Community and Web Service Interaction Model - (Phase 1)}
+    \begin{figure}[htbp]
+        \centering
+        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
+        \includegraphics[width=0.8 \columnwidth]{figures/scenario1.png}
+        %%\includegraphics[scale=0.5]{figure1}
+        %\caption{The NetBill payment protocol} \label{figure7}
+    \end{figure}
+
+    \begin{itemize}
+        \item A typical WS community, where web services can join or leave.
+        \item $v(C) = Out(C)$.
+        \item Membership decision in made based on throughput and QoS of the web services.
+        \item Community master needs to get quality web services to keep the community stable, so other web services have no incentive to leave.
+    \end{itemize}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Community and Web Service Interaction Model - (Phase 1)}
+
+    \begin{itemize}
+        \item Upon receiving membership request, the master web service checks if the coalition will be stable having the new member.
+        \item If the game is convex, core exists.
+        \item If the game is convex, Shapley value is in core.
+        \item Convexity Condition:
+        \begin{center}
+          $v(A \cup B) \geq v(A) + v(B) - v(A \cap B)$ \\
+          $\Leftrightarrow$  \\
+          $\forall S,T | S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N,$ \\
+          {\color{blue} $v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)$ }
+        \end{center}
+        \item Depth-1 Convexity Check: $O(n)$
+        \item Depth-2 Convexity Check: $O(n^2)$
+    \end{itemize}
+
+\end{frame}
+
 \end{document}

### 2014-11-04 course-game/session1/ehsan_session1.tex
changes

@@
 \institute{Department of Computer Science and Software Engineering\\Concordia University}
-\date{Novermber 17, 2014}
+\date{Novermber 6, 2014}
 \begin{document}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame} {Example: Core}
+\begin{frame} {Example 1: Vector game}
 
@@
     The core may not be fair: the core only considers stability.
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame} {Example 2: Three-player majority game}
+    \begin{center}
+      $N = \{1,2,3\}$ \\
+      $v(\{i\}) = 0,$\\
+      $v(\{C\}) = 0, for |C| = 2$ \\
+      $v(N) = 1$ \\
+    \end{center}
+    \[ (x_1, x_2, x_3) \in Core(N,n) \iff \left\{
+      \begin{array}{l l}
+        x_i \geq 0 & \quad \forall i \in N\\
+        x_i + x_j \geq \alpha & \quad \forall(i,j) \in N^2 i \neq j\\
+        \sum_{i \in N} x_i = 1 &
+      \end{array} \right.\]
+    \[ (x_1, x_2, x_3) \in Core(N,n) \iff \left\{
+      \begin{array}{l l}
+        0 \leq x_i \leq 1 - \alpha & \quad \forall i \in N\\
+        \sum_{i \in N} x_i = 1 &
+      \end{array} \right.\]
+
+    $Core(N,v)$ is nonempty $iff \alpha \leq \frac{2}{3}$ \\
+
+    \begin{itemize}
+        \item The core may not be fair: the core only considers stability. \\
+        \item The core may not have an answer!
+    \end{itemize}
 
@@
 \end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame} {Example: Glove game}
+    The {\color{blue}glove game} is a coalitional game where the players have left and right hand gloves and the goal is to form pairs
+    \begin{center}
+      $N = \{1,2,3\}$ \\
+    \end{center}
+    where players 1 and 2 have right hand gloves and player 3 has a left hand glove.
+    \[ v(S) = \left\{
+      \begin{array}{l l}
+        1 & \quad if \quad S \in \{\{1,3\},\{2,3\},\{1,2,3\}\} \\
+        0 & \quad otherwise        
+      \end{array} \right.\]      
+    $S = \emptyset, v(\{1\}) - v(\emptyset) = 0 - 0 = 0$ \\    
+    $S = \{2\}, v(\{1,2\}) - v(\{2\}) = 0 - 0 = 0$ \\
+    $S = \{3\}, v(\{1,3\}) - v(\{3\}) = 1 - 0 = 1$ \\
+    $S = \{2,3\}, v(\{1,2,3\}) - v(\{2,3\}) = 1 - 1 = 0$ \\            
+    \begin{itemize}
+        \item ${\color{blue}x_1} = 0 + 0 + \frac{1}{6} + 0 = \frac{1}{6}$, ${\color{blue}x_2} = \frac{1}{6}$, ${\color{blue}x_3} = \frac{2}{3}$    
+        \item ${\color{blue}x} = (\frac{1}{6}, \frac{1}{6}, \frac{2}{3})$
+    \end{itemize}
+\end{frame}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
         \end{itemize}
+    \end{itemize}
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Excess of a coalition}
+
+    \begin{itemize}
         \item We can interpret a positive excess $(e(C,x) > 0)$ as the amount of dissatisfaction or {\color{blue} complaint} of the members of $C$ from the allocation x.
         \item We can use the excess to define the core:
-        \begin{itemize}
-            \item $Core(N,v)=\{x \in R^n | x is an imputation and \forall C \subseteq N, e(C,x) \leq 0\}$
-        \end{itemize}
+        \begin{center}
+            $Core(N,v)=\{x \in R^n |$ $x$ $is$ $an$ $imputation$ $and$ $\forall C \subseteq N, e(C,x) \leq 0\}$
+        \end{center}
         \item This definition shows that no coalition has any complaint: each coalition's demand can be granted.
@@
         \item Let $Imp$ be the set of all imputations.
-        \item The {\color{blue}$nucleolus Nu(N,v)$} is the set
+        \item The {\color{blue}$nucleolus$ $Nu(N,v)$} is the set:
         \begin{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Community and Web Service Interaction Model - (Phase 1)}
+\begin{frame}{Community and Web Service Interaction Model}
     \begin{figure}[htbp]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}{Community and Web Service Interaction Model - (Phase 1)}
+\begin{frame}{Community and Web Service Interaction Model}
 

### 2014-11-07 course-game/session8/ehsan_session1.tex
changes

--- 2014-11-04 course-game/session1/ehsan_session1.tex
@@
 %\newtheorem{definition}{Definition}
-\title[Lecture 8: Extensive Form Games with Perfect Information]{Lecture 8: Extensive Form Games with Perfect Information}
-\author{INSE 6441/2 DD\\ \vspace{0.2cm} Applied Game Theory and Mechanism Design \\ Fall 2014}
+\title[Lecture 8: Coalition Games]{Lecture 8: Coalition Games}
+\author{INSE 6441/2\\ \vspace{0.2cm} Applied Game Theory and Mechanism Design}
 \institute{Department of Computer Science and Software Engineering\\Concordia University}
-\date{Novermber 6, 2014}
+\date{Ehsan Khosrowshahi \\ \small{Acknowledgement: Stephane Airiau, Lloyd Shapley}}
 \begin{document}
@@
     	\item Fairness and Shapley Value
-    	\item Other Solution Conecpts
+    	\item Other Solution Concepts
         \item Practical Example
@@
   \begin{itemize}
-     \item Cooperative games are a branch of game theory that models cooperation or collaboration between agents.
-     \begin{itemize}
+     \item In game theory, a cooperative game is a game where groups of players $``coalitions''$ may enforce cooperative behaviour, hence the game is a competition between coalitions of players, rather than between individual players.
     \item Cooperation to perform a set of tasks that requires different expertise.
@@
         \item Transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
-        \end{itemize}
     \end{itemize}
@@
         \end{itemize}
+    \end{itemize}
+
+\end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Solution Properties (Cont.)}
+    Let $x \in R^n$ be a solution of the coalition game $(N,v)$
+    \begin{itemize}
         \item {\color{blue} Group rationality:} $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
@@
         \end{itemize}
-        \item {\color{blue} Pareto Optimal:} $\sum_{i \in N} x(i) = v(N)$
-        \begin{itemize}
-            \item no agent can improve its payoff without lowering the payoff of another agent
-        \end{itemize}
+%        \item {\color{blue} Pareto Optimal:} $\sum_{i \in N} x(i) = v(N)$
+%        \begin{itemize}
+%            \item no agent can improve its payoff without lowering the payoff of another agent
+%        \end{itemize}
         \item {\color{blue} Anonymity:} a solution is independent of the names of the player.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame} {Example 1: Vector game}
+\begin{frame} {Example 1: A two-player game}
 
@@
       $v(\{i\}) = 0,$\\
-      $v(\{C\}) = 0, for |C| = 2$ \\
+      $v(\{C\}) = \alpha, for |C| = 2$ \\
       $v(N) = 1$ \\
@@
     	\item {\bf Fairness and Shapley Value}
-    	\item Other Solution Conecpts
+    	\item Other Solution Concepts
         \item Practical Example
@@
     	\item Fairness and Shapley Value
-    	\item {\bf Other Solution Conecpts}
+    	\item {\bf Other Solution Concepts}
         \item Practical Example
@@
         \begin{itemize}
-            \item $Nu(N,v) = \{x \in Imp|\forall y \in Imp e(y)* \geq_{lex} e(x)*\}$
+            \item $Nu(N,v) = \{x \in Imp | \forall y \in Imp, e(y)^* \geq_{lex} e(x)^*\}$
         \end{itemize}
@@
     	\item Fairness and Shapley Value
-    	\item Other Solution Conecpts
+    	\item Other Solution Concepts
         \item {\bf Practical Example}
@@
 
+\begin{frame}{Experimental Results}
+
+    \begin{figure}[!t]
+    \centering
+    %\includegraphics[scale=0.6]{graph1Final+.eps}
+    \includegraphics[width=2.1in]{figures/task_done_opt-eps-converted-to.pdf}
+    \includegraphics[width=2.1in]{figures/task_qos_opt-eps-converted-to.pdf}
+    \caption{Part (a): Cumulative number of requests successfully
+    answered. Part (b): Average QoS of requests performed.}
+    \label{performanceall}
+    \end{figure}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Improving Community Stability}
+    \begin{itemize}
+        \item The core may not always be non-empty, core is a strong condition.
+        \item The optimal solution concepts will attract only enough services satisfying input task rate, not more.
+        \item In case of web service failure, a portion of tasks will not be handled efficiently until replacement is found.
+        \item By imposing cost on deviation or subsiding the community, its possible to attract more web services and keep the community stable.
+        \item Will be cost efficient in case of web service failure, or for replacing web services dropping in QoS metrics as they advertised.
+        \item \emph{Taxation} would need agreement between all communities (needs a centralized approach), however \emph{subsiding} can be done within communities in distributed manner.
+    \end{itemize}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Taxation and Subsiding}
+    \begin{itemize}
+        \item Least Core
+        \begin{itemize}
+            \item $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon$
+            \item $\epsilon$-core relaxes the core condition.
+        \end{itemize}
+        \item Taxation in Reliability Games \small $[Y. Bachrach, E. Elkind, 2009]$
+
+        \item Taxation and Cost of Stability \small $[R. Meir, J. S. Rosenchein, 2011]$
+
+        \item Taxation in Anonymous Games \small $[Y. Zick, M. Polukarov, 2013]$
+
+        \item Relative Core
+        \begin{itemize}
+            \item $\lambda v(C)$ is divided among players.
+            \item relative $\lambda$-Core: $\forall S \subseteq N, \sum_{x_i \in S} x_i \geq \frac{1}{\lambda}.v(S)$
+            \item Clearly any community can be stabilized by large enough $\lambda$, however the community coordinator would be interested in the minimal subsidy required to stabilize the game.
+            \item Can be solved using $LP$ if $v(S)$ is a linear function
+        \end{itemize}
+    \end{itemize}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Results: Taxation and Subsiding}
+    \begin{figure}[!t]
+        \centering
+        %\includegraphics[scale=0.6]{graph1Final+.eps}
+        \includegraphics[width=3in]{figures/taxtation-eps-converted-to.pdf}
+        \caption{Analysis of community subsiding coefficient $\lambda$ on
+        average community size (a), cost (b), number of tasks performed
+        (c), and average quality of service of tasks performed (d).}
+        \label{f_taxtation}
+    \end{figure}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}{Results: Taxation and Subsiding}
+    \begin{figure}[!t]
+        \centerline{\includegraphics[width=4.2in]{figures/tax_dyn-eps-converted-to.pdf}}
+        \caption{Analysis of community subsiding coefficient $\lambda$
+        having web service different stability levels of $\tau$ on average
+        community size, number of tasks performed, average quality of
+        service, and average cost/income of communities.}
+        \label{fig_dynamic_taxtation}
+    \end{figure}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2014-11-15 papers/webservice-coalition-learning/figures/matlab/mlisa_chart_utility.m
changes

@@ -102,7 +102,7 @@ set(gca,'XGrid','off','YGrid','on','ZGrid','off');
 hFig = figure(2);
 bar(xvalue(1:1:10), [gainR020(1:1:10), gainR010(1:1:10), gainR007(1:1:10), gainR005(1:1:10)], 1);
 xlabel('Web services','FontSize',fontsize);
-ylabel('Utility Gain','FontSize',fontsize);
+ylabel('Value of the Utility Gain','FontSize',fontsize);
 axis([0 11 0 400]);
 legend('R=0.2', 'R=0.1', 'R=0.07', 'R=0.05');
 

### 2014-11-15 papers/webservice-coalition-learning/figures/matlab/mlisa_chart_utility_ratio.m

@@ -98,7 +98,7 @@ set(gca,'XGrid','off','YGrid','on','ZGrid','off');
 hFig = figure(2);
 bar(xvalue(1:1:10), [ratioR020(1:1:10), ratioR010(1:1:10), ratioR007(1:1:10), ratioR005(1:1:10)], 1);
 xlabel('Web services','FontSize',fontsize);
-ylabel('Utility Gain','FontSize',fontsize);
+ylabel('Ratio of the Utility Gain','FontSize',fontsize);
 axis([0 11 0 22]);
 legend('R=0.2', 'R=0.1', 'R=0.07', 'R=0.05');
 

### 2015-01-14 papers/webservice-coalition-learning/figures/matlab/mlisa_chart_utility.m
changes

@@ -31,8 +31,8 @@ subplot(2, 2, 1);
 bar(xvalue(1:1:10), gainR020(1:1:10), 0.4, 'FaceColor',color1);
 hold on
 bar(xvalue(11:1:20), gainR020(11:1:20), 0.4, 'FaceColor',color2);
-xlabel('Trained WS           Rational WS','FontSize',fontsize);
-ylabel('Utility Gain','FontSize',fontsize);
+xlabel('DDM WS             Rational WS','FontSize',fontsize);
+ylabel('Utility Gain Value','FontSize',fontsize);
 title ('R=0.2 (a)','FontSize',fontsize);
 %title('TITLE');
 axis([0 21 0 400]);
@@ -57,8 +57,8 @@ subplot(2, 2, 2);
 bar(xvalue(1:1:10), gainR010(1:1:10), 0.4, 'FaceColor',color1);
 hold on
 bar(xvalue(11:1:20), gainR010(11:1:20), 0.4, 'FaceColor',color2); 
-xlabel('Trained WS           Rational WS','FontSize',fontsize);
-ylabel('Utility Gain','FontSize',fontsize);
+xlabel('DDM WS              Rational WS','FontSize',fontsize);
+ylabel('Utility Gain Value','FontSize',fontsize);
 title ('R=0.1 (b)','FontSize',fontsize);
 axis([0 21 0 400]);
 set(gca,'XTick',[1 5 10 15 20]);
@@ -72,8 +72,8 @@ subplot(2, 2, 3);
 bar(xvalue(1:1:10), gainR007(1:1:10), 0.4, 'FaceColor',color1);
 hold on
 bar(xvalue(11:1:20), gainR007(11:1:20), 0.4, 'FaceColor',color2);
-xlabel('Trained WS           Rational WS','FontSize',fontsize);
-ylabel('Utility Gain','FontSize',fontsize);
+xlabel('DDM WS              Rational WS','FontSize',fontsize);
+ylabel('Utility Gain Value','FontSize',fontsize);
 title ('R=0.07 (c)','FontSize',fontsize);
 axis([0 21 0 400]);
 set(gca,'XTick',[1 5 10 15 20]);
@@ -87,8 +87,8 @@ subplot(2, 2, 4);
 bar(xvalue(1:1:10), gainR005(1:1:10), 0.4, 'FaceColor',color1);
 hold on
 bar(xvalue(11:1:20), gainR005(11:1:20), 0.4, 'FaceColor',color2);
[…]

### 2015-01-14 papers/webservice-coalition-learning/figures/matlab/mlisa_chart_utility_ratio.m

@@ -31,8 +31,8 @@ subplot(2, 2, 1);
 bar(xvalue(1:1:10), ratioR020(1:1:10), 0.4, 'FaceColor',color1);
 hold on
 bar(xvalue(11:1:20), ratioR020(11:1:20), 0.4, 'FaceColor',color2);
-xlabel('Trained WS           Rational WS','FontSize',fontsize);
-ylabel('Utility Gain','FontSize',fontsize);
+xlabel('DDM WS              Rational WS','FontSize',fontsize);
+ylabel('Utility Gain Ratio','FontSize',fontsize);
 title ('R=0.2 (a)','FontSize',fontsize);
 %title('TITLE');
 axis([0 21 0 22]);
@@ -56,8 +56,8 @@ subplot(2, 2, 2);
 bar(xvalue(1:1:10), ratioR010(1:1:10), 0.4, 'FaceColor',color1);
 hold on
 bar(xvalue(11:1:20), ratioR010(11:1:20), 0.4, 'FaceColor',color2);
-xlabel('Trained WS           Rational WS','FontSize',fontsize);
-ylabel('Utility Gain','FontSize',fontsize);
+xlabel('DDM WS              Rational WS','FontSize',fontsize);
+ylabel('Utility Gain Ratio','FontSize',fontsize);
 title ('R=0.1 (b)','FontSize',fontsize);
 axis([0 21 0 22]);
 set(gca,'XTick',[1 5 10 15 20]);
@@ -70,8 +70,8 @@ subplot(2, 2, 3);
 bar(xvalue(1:1:10), ratioR007(1:1:10), 0.4, 'FaceColor',color1);
 hold on
 bar(xvalue(11:1:20), ratioR007(11:1:20), 0.4, 'FaceColor',color2);
-xlabel('Trained WS           Rational WS','FontSize',fontsize);
-ylabel('Utility Gain','FontSize',fontsize);
+xlabel('DDM WS              Rational WS','FontSize',fontsize);
+ylabel('Utility Gain Ratio','FontSize',fontsize);
 title ('R=0.07 (c)','FontSize',fontsize);
 axis([0 21 0 22]);
 set(gca,'XTick',[1 5 10 15 20]);
@@ -84,8 +84,8 @@ subplot(2, 2, 4);
 bar(xvalue(1:1:10), ratioR005(1:1:10), 0.4, 'FaceColor',color1);
 hold on
[…]

### 2015-01-19 papers/webservice-coalition-learning-else-template/elsarticle-template-num.tex
changes

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Decision Support Systems}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Distributed Decision Making for Dynamic Formation of Web Services Communities}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{}

\address{}

\begin{abstract}
Web services are loosely-coupled business applications willing to cooperate in distributed settings within different groups called communities. Communities aim to provide web services with better visibility, efficiency, market share and total payoff. A number of mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities. However, existing community models mostly focus on short term goals. Moreover, these models generally suffer from high computational complexity, which makes decision making about community formation in real-time extremely hard, time consuming, and even impossible in some complex cases. In this paper, we propose a strategic distributed decision making mechanism called DDM that regulates web service agents' decision making process, which is about deciding with whom to cooperate. This model first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The decision making mechanism implements a decision tree of possible viable strategies and their long-term expected utility gain.
%Utilizing the training model, the decision making mechanism implements a decision tree with an estimation of long-term utility gain for the web services. Communities can used the trained model and instantly choose best-response strategies considering their long-term gain. 
Our model helps 1) communities of web services efficiently find the appropriate web service to invite as new member; and 2) single web services find best communities to join. After being trained, web services get to compute expectations as utilities they would gain if cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated initiated by a web service. In general, DDM equips web services with efficient methods of foreseeing how their choices of actions would impact their short-term and long-term goals, therefore opting for better decisions. We performed experiments using real data from 142 users on 4,532 web services on 64 different time slots. The experimental results, show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.
\end{abstract}

\begin{keyword}
Web services\sep Community of services\sep Distributed Decision Making
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}

\IEEEPARstart{O}{ver} the past years, online services have become an important part of many scalable business applications. The increasing reliance on online service providers has significantly influenced the way web services are engineered. Therefore, given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue. One practical solution towards delivering high quality services is utilizing intelligent decision making agents. These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users\cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, journals/tsc/ZhengZYB13, Demirkan2013412}. However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided. Recent developments have attempted to shift web services from passive models, consisting of individual components, to models made up of autonomous and group-based components that share common goals. In group-based models, interaction, composition, and cooperation are the key challenges \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13} that directly impact the group's overall performance in achieving common goals. To that end, we see the emergence of web service \emph{communities}, which consist of services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}. A \emph{community} of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.

The advantages of community of web services are that the community facilitates the discovery of web services and provides better quality of service compared to passive models with individual components. Communities act as abstract web services, communicating with external entities via the same standard protocols that a normal web service employs. But, they regulate the service process via sophisticated internal communication protocols, thereby providing services based on the combined work of a number of web services. The downside to communities is the complexity of management involved in finding and inviting individual web services and managing the overall quality of the combined work of several web services.
% because although they have similar functionality, they have different attitudes. 
When interacting with communities of web services, users send their requests to the coordinators of the community, which play the role of community representative or access point. The community coordinator is responsible of receiving tasks and delivering services. Moreover, as community representative, it verifies the credentials of new web services before accepting them into the community and kicks web services that could harm the value of the community.

\textbf{Challenge and Problem Statement.} In recent work, communities of web services have been proposed in order to facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities. However, there is a twofold challenge that yet to be addressed. The first part is community development, which involves finding the right web services for the community, satisfying the objectives of all the web services and community coordinators involved within the community; and the second part is from the individual web service's side because each web service aims to join the community that would guarantee the best outcome. The advocated solutions \cite{conf/webist/MaamarLBTS07, 10.1109/ARES.2008.7, journals/soca/XuYLZB11, 10.1109/TSC.2012.12, managing-hela-jalel, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:conf/IEEEscc/LimTMB12} have attempted to address these research problems. These research problems are reflected by the two challenge parts: 
\begin{enumerate}
	\item The solutions consider the architecture of centralized management for communities where most of the decisions are made by the centralized coordinator. The problem is that in real world scenarios, decisions made by independent service providers are highly distributed.
	\item The solutions either propose complex algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to find the optimal strategy to follow, or oversimplify the problem by eliminating important parameters and using approximation techniques to make the algorithms tractable \cite{10.1109/TSC.2012.12}.
\end{enumerate}
These approximation methods sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored.

For example, instead of calculating the gain distribution using the complex shapely-value method, \cite{10.1109/TSC.2012.12} proposes a simple egalitarian way of distributing gain, which completely ignores the gain generated from collaborative work of sub-communities. Other categories of related work exist that do not focus on all the parties involved within the community \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. 
%And some other work which do not focus on rationality on web services or communities involved [refrences]. 
In \cite{journal-community-formation} we proposed a cooperative game theory based model for aggregating web services in communities. A centralized decision maker in communities based on a complete knowledge of available web service quality metrics and performance, has been used to form optimal and stable communities that maximize individual and group income. However, centrality and complete information are strong assumptions, which are not very compatible with real business scenarios.

\textbf{Contributions.} In this paper, we introduce DDM, a Distributed Decision Making model for  community formation that regulates web service agents’ decision making process in terms of cooperating and deciding which group to join and which service to invite for joining. The decision model in extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The generated decision tree improves agents' understanding of the environment and how to select actions that lead towards maximizing their utilities. The advantage of this approach is that the tree is created from the past data and reflects comprehensive vision about agents' attitude of action selection. However, the tree is subject to get continuously modified to adapt with environmental changes.
%The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems. 
The decision model provides web services with enough information which helps those services to efficiently decide and predict the outcome of their different possible collaborations. This model works in a distributed manner in which services are self-sufficient in decision making process and do not rely on a centralized decision making process. Our findings show that communities of web services can efficiently find the appropriate web service to invite for cooperation as well as allowing a single web service to find the best communities to join. In other words, the web services agents are equipped with a recommender system to suggest beneficial action. Moreover, communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their short-term and long-term goals; therefore, opting for best decision available.

To effectively train web services, we used real data set to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another. The data set has been extracted by real-world QoS evaluation results from 142 users on 4,532 Web services on 64 different time slots. Combining these data based on each web service point of view on different time slots, we acquired 5 different unique features for 4,532 web services. By engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in different time slots. We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others. All paths and the outcomes are labeled to be utilized in the training model. Using cross validation sets, web services are able to compute the optimal hypothesis function (using logistic regression) that can be used to predict outcomes of cooperative work with other individual web services or communities. Our findings show that web services equipped with DDM have by far better outcomes in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.

\textbf{Organization.} The rest of the paper is organized as follows. In Section 2 we briefly describe the preliminaries and challenging issues. Section 3 discusses the considered parameters and web service community architecture. Section 4 presents our solution model, the way data is trained and the way web services utilize the trained data in their decision making process. Section 5 describes our experiments and results. Section 6 discussed relevant related work. Finally Section 7 concludes the paper and identifies future work.

%- We want to give full distributed control to web services as autonomous agents and distribute the task of community management among all web services and let them decide how to maximize their efficiency and join and create communities.
%- Let agents train and learn long term expectations of each action and group they can join with
%- Web services cannot find the optimal solution in big space problem of many web services
%- Add rationalism and less vague decisions

%Web services provide a set of stateless software functions accessible at a network address over the web. 
%Online autonomous agent-based services are software systems providing a standard way of interoperability among different applications.

% - The recent developments are shifting web services from passive and individual components to autonomous and group-based components where interactiion, composition, and cooperation are the key challenges.

%- High demand on online services has created a massive business competition. For example, nowadays users are provided with multiple choices of web services offering local places information such as coffees, venues, and shops nearby a geographic position. It is hard for new web services to find their customers and be visible for end users amongst hundreds or thousands of other available services, even if they provide a high quality of service. Hence, the concept of communities of web services provides them with the chance of joining a platform with an established market share and reputation. However, it is crucial for a community manager to consider many factors when inviting or accepting new members. For example,  this may hurt the community stability.

%- The high competition within the services industry requires applications to use reliable and high quality online service providers. If the user were to check a web site or run an application on her mobile device upon having downtime, or having high response delay or encountering any non-satisfying quality metric, she will instantly remove the application, which is a huge business concern for application providers. For example, if a user installs a ticketing application on her mobile device and the application is not using high quality service providers, the user would instantly uninstall the application, which has an extremely negative impact on the visibility of the application.

%- Most applications cannot independently satisfy users requests and should rely on different online services. The high competition within the services industry requires applications to use reliable and high quality online service providers.

%Today web services are

%- softwares rely on third party online service providers 
%- quality of services determines the success of the business 
%- services want to maximise thier utility by cooperating with best possible communities
%- services need to get visible and join market

% Computer Society journal papers do something a tad strange with the very
% first section heading (almost always called "Introduction"). They place it
% ABOVE the main text! IEEEtran.cls currently does not do this for you.
% However, You can achieve this effect by making LaTeX jump through some
% hoops via something like:
%
%\ifCLASSOPTIONcompsoc
%  \noindent\raisebox{2\baselineskip}[0pt][0pt]%
%  {\parbox{\columnwidth}{\section{Introduction}\label{sec:introduction}%
%  \global\everypar=\everypar}}%
%  \vspace{-1\baselineskip}\vspace{-\parskip}\par
%\else
%  \section{Introduction}\label{sec:introduction}\par
%\fi
%
% Admittedly, this is a hack and may well be fragile, but seems to do the
% trick for me. Note the need to keep any \label that may be used right
% after \section in the above as the hack puts \section within a raised box.

% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps (small caps for compsoc).
%
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
%
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
%
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
%
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
%for IEEE Computer Society journal papers produced under \LaTeX\ using
%IEEEtran.cls version 1.7 and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
%I wish you the best of success.

%\hfill mds

%\hfill January 11, 2007

\section{Preliminaries and Challenging Issues}\label{s:preliminaries}
%In this section, we first present the architecture of DDM. We explore the characteristics of intelligent service agents and the features we extract for training. To do this, we first discuss some preliminaries.
In this section, we discuss the preliminary concepts of communities of web service and we introduce the challenges of community formation.

\subsection{Web Services}\label{s:ws}

In recent years, online services have become a standard part of daily life around the globe. Many modern applications rely on web services from different providers. For instance, many mobile and tablet applications that have limited storage and processing power are merely aggregating information from different online services. Examples are vast, including weather forecasting, ticket selling, shopping apps, local maps and location services.

The World Wide Web Consortium (W3C) defines web services as ``software systems designed to support interpretable machine-to-machine interaction over a network. It has an interface described in a machine-processable format (specifically WSDL). Other systems interact with the web service in a manner prescribed by its description using SOAP messages, typically conveyed using HTTP with XML serialization in conjunction with other Web-related standards.'' When developers declare a new web service, it will be
discovered based on its description, which fully discloses its functionalities. Developers also have to declare a public interface and a readable documentation to help other developers when integrating different services \cite{w3cwsdl}. Nowadays, web API, standards that do not require XML-based web service protocols like SOAP and WSDL are also emerging. They are called REST (representational state transfer) services, which are moving towards simpler communication protocols. 
%They are not restricted 
%to XML formats, recently JSON, a human readable and simpler format 
%is becoming popular among online service providers.

We are not going to delve into the engineering details of online web service implementation and its protocols in this paper. We are interested in web services from a business model perspective. Service providers usually charge end users for services they provide. For example, Google has listed pricing and plans for a wide range of services they provide on their web service console page\footnote{https://code.google.com/apis/console}.

In this paper, we abstract web services as rational agents\footnote{The term rational is used here in the sense that web services are utility maximizers} that provide services to end users. They aim to maximize their individual income  by receiving enough requests from end users. In order to increase their revenues, web services seek for more tasks if they have the capacity and throughput to do so. Web services can join communities to enhance efficiency by collaborating with others, to have access to broad market share, and for the opportunity to receive a bigger task pool from end users. Furthermore, the high reliance on web services has resulted in increased quality expectations from end users. Communities of web services can provide higher availability, performance, reliability, and recovery for end users.

\subsection{Web Service Communities}\label{s:wsc}

The community of web services is essentially a virtual group of web services having similar and complementary functionalities\cite{DBLP:journals/ijebr/MaamarSTBB09}. Communities aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols to those used by single web services. Web services join communities to increase utility by having a larger market share and task pool. Community coordinators are responsible for community development, managing membership requests from web services and distributing user tasks among the community members. Community coordinators try to attract quality web services to join and keep the community as stable and productive as possible to gain a better reputation and user satisfaction, which increases the community's market share. How web services reside within communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

\subsection{The Join Challenge}\label{s:tjc}
Sometimes, web services can increase their overall utility by collaborating with other web services as communities. This collaboration helps them with better ways of sharing resources and having higher reputation, better market share and wider visibility. Web services and communities come with different internal and external parameters, and the long-term outcome is dependent on these parameters.

The goal of all parties involved in the community is to maximize their long-term outcome while they are operating as part of the community. Web services need to be equipped with a selection strategy to choose from all of the different possible collaboration groups they can form as well as an estimation method for evaluating the long-term gain of joining different possible communities. Web services need to experiment with different possible collaborative groups and other web services in order to estimate their gain over time. However, with a high number of possible communities and many other business restrictions, it is not possible to test collaboration with random web services. Even if a linear approximate function for estimating utility based on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell_number$} growth rate of the possible number of partitions of web services into communities would make any brute-force type algorithm for the best community selection strategy intractable and impractical in real-world application settings.

\subsection{Join Consequences}\label{s:jc}
It is worth mentioning that a \emph{join} event takes place as a result of two parties that are looking to expand their collaborations. All actions are chosen in an attempt to enhance the overall outcome. However, the selected action may result in decreasing the overall utility in the long run. 
% long term.
This is the case when a single web service joins a community, but the complex process of task allocation eliminates the visibility of the web service and, thus, the web service stays idle within the community, which makes the join action a bad decision. The same event might be beneficial for the community, as it hosts a new web service that can engage in performing a new coming task. But overall, neither side benefits from collaborating with the other and the join event has negative consequences for at least one side's utility.

The more common scenario is when both parties benefit from the joining of a web service to a community. This action is rational, as both the web service and the community enhance the utility. However, the community may not be the best choice for the web service to join. In other words, the web service could have joined a better community, but, due to of lack of knowledge about the surrounding environment, joined the available community which was not the optimal choice. Since the community does enhance its utility, the web service could stay with that community, which results in a sub-optimal increase in web service's utility. In the following section the proposed model provides solutions that effectively address the aforementioned challenges.

\section{The Model Components}\label{s:themodelcomponents}

In this section, we discuss the parameters that we use in the rest of the paper. Then we present the task distribution and revenue model of our distributed web services communities.

\subsection{Internal Features}\label{s:if}

With a group of web services having identical or similar functionalities, QoS metrics provide nonfunctional characteristics for optimal candidate selection. Web service quality metrics were presented in \cite{Ardagna:2007:ASC:1263152.1263531,Menasce:2002:QIW:613357.613758,10.1109/ISSRE.2011.17}. We have adopted the most representative QoS properties of web services that highly influence the utility of web services. 
%We refer to a typical web service as ws_{i}.

Let $C = \{ws_1,ws_2,..., ws_n\}$ be a community with $|n|$ web services. We define the following features for the group of web services based on their functional parameters:

\begin{itemize}

  \item \emph{Throughput $(Th_{C})$} is the rate at which a service can process requests. QoS measures can include the maximum throughput or a function that describes how throughput varies with load intensity. Throughput is a positive real number. For communities the expected throughput value of collaborating web services can be estimated as summation of throughputs of all the services inside:

	\begin{equation}
		 Th_{C} = \left\{ 
			\begin{array}{l l}
				Th_{w} & \quad \text{if $|C| = 1$}\\
				\sum_{w \in C}{(Th_{w})} & \quad \text{if $|C| > 1$}
			\end{array} \right.
	\end{equation}

	\item \emph{Availability $(A_{C})$} is the percentage of time that a service is operating.
	The probability that the service operation is accessible. Availability is also a real number in the range $[0, 1]$. For communities the expected availability of collaborating web services considering they follow a parallel system can be estimated as:

	\begin{equation}
		A_{C} = \left\{ 
			\begin{array}{l l}
				A_{w} & \quad \text{if $|C| = 1$}\\
				1-\prod_{w \in C}{(1-A_{w})} & \quad \text{if $|C| > 1$}
			\end{array} \right.
	\end{equation}

	\item \emph{Execution Time $(Et_{C})$} is the time a service takes to respond to various types of requests. 
	%is the expected delay between the time instant when a request is sent and the time when the result is obtained. 
	Execution time is measured in milliseconds. Execution time can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests. This internal feature is a positive integer. For communities, the expected execution time of collaborating web services can be estimated as the execution time of the bottleneck service which is the service with the slowest execution time:

	\begin{equation}
		Et_{C} = \left\{ 
			\begin{array}{l l}
				Et_{w} & \quad \text{if $|C| = 1$}\\
				max_{w \in C}{(Et_{w})} & \quad \text{if $|C| > 1$}
			\end{array} \right.
	\end{equation}

	%\item \emph{Data Quality} The ability of a data collection to meet user requirements , defined as the proximity of a value v returned by web service to a value considered as correct. The measure of data quality is considered here as a real number in the range [0, 1], where 1 represents the most desirable score.
\end{itemize}

	We normalize the range of these features so that each feature contributes approximately proportionately to the final utility outcome value. We adopt the \emph{standardization} method. We subtract the \emph{mean} from each feature then we divide the values of each feature by its \emph{standard deviation}.

%$HI = \overline{HI}$

\subsection{External Features}\label{s:ef}

The quantitative values of quality metrics need some benchmark values to represent their goodness. In other words, without some benchmark values it would be difficult for web services to identify their goals, and performance quality at any specific value of these metrics. Therefore, we have introduced two external features for assessing web services' estimate with regard to their standing among other web services.

\begin{itemize}
  \item \emph{External Parameter 1} $(exp_1)$. is an estimate of how close the web service's \emph{execution time} is to other web services. It is the difference between a web service's \emph{execution time} metric and the maximum value of execution time of web services, about which the web service has recently gathered information. The less value means web service has better execution time compared to other web services.
	\begin{equation}\label{exp_1:f}
		exp_1 = Et_{i} - Et_{max}
	\end{equation}
	\item \emph{External Parameter 2} $(exp_2)$ is a comparison of the web service's rate of performing tasks to other competing web services. It is the difference between a web service's \emph{throughput} metric and the maximum value of throughput of web services, about which the web service has recently gathered information. The less value means web service has better throughput compared to other web services.
	\begin{equation}\label{exp_2Lf}
		exp_2 = Th_{max} - Th_{i}
	\end{equation}
\end{itemize}

A community of web services is abstracted as a standard web service that provides services that share the same internal and external features mentioned for web services. Inside, they adopt different protocols to manage the community; however, other web services or end users can communicate with communities of web services, using standard protocols, and inner details will be encapsulated for their clients.

\subsection{Task Distribution}

Communities of web services usually employ an implementation of Contract-Net protocol for task distribution, in which services opt for incoming tasks, and receive the tasks for which they ask. However, in our model, our community members would try to distribute tasks based on their capabilities and the QoS parameters provided by the web services. We have used a slightly modified \emph{weighted fair queuing} method to distribute tasks among community members. The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{ws}$. In the \emph{weighted fair queuing} method, the input flow is multiplexed along different paths; however, in our case, if the rate of incoming tasks is less than the community's total throughput $(Th_{C})$, which is the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with a delay. 
%Thus, the amount of tasks performed by the community is $\sum_{ws}{Th_{ws}}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$. 
However, when the incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $|input Task Rate| \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) within the community.

While distributing tasks, the community members can verify the performance, throughput and quality of service of tasks being performed by web services. The community can assess if those web services are capable of performing the number of tasks they advertised. If for any reason, there is a decline in the quality metric or throughput, the community can consider the new values as a benchmark for future performance calculations, and penalize the suspicious web services. This way, players will have incentive to truthfully disclose their actual capabilities in order to maximize profit from the community and to avoid being penalized. In addition, the system should be dynamic enough to detect and react to web services' quality metrics variation, as over time, web service metrics may degrade or improve, changes to which the community should adjust.
% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

\subsection{Community Revenue}

Communities and web services earn revenue by performing tasks. The total gain is a function of the quality of rate of tasks being performed. The utility of a collaborative group of services $U_{C}$ is the revenue of the community. Formula \ref{u_c_normal} is an estimation of the gain of the community.

\begin{equation}\label{u_c_normal}
U_{C} = \big((\alpha \times (A_{C} - Et_{C}) - \beta \times (exp1_{C} + exp2_{C})\big) \times Th_{C}
\end{equation}

The $\alpha$ and $\beta$ values are internal and external weight coefficients. Execution time and external parameters are better when they have smaller values hence the negative coefficient for them. The result is then multiplied to the throughput value $Th_{C}$, since communities are performing tasks with $Th_{C}$ rate.

The estimation can be improved, especially in cases where the input task rate is high and services are experiencing high task loads. The \emph{weighted fair queuing} method of task distribution would distribute tasks based on the individual throughput $(Th_{w})$ value of services within community. The services with higher throughput will affect the overall utility of the community more because they would take on proportionately more tasks.

\begin{equation}\label{u_c_load}
\begin{split}
U_{C} = \sum_{ws \in C}&\bigg(\big(\alpha \times (A_{ws} - Et_{ws}) \\
        & - \beta \times (exp1_{ws} + exp2_{ws})\big) \times Th_{ws}\bigg)
\end{split}
\end{equation}

\begin{table*}[ht]
\caption{An example of $gain$ matrix for 3 different communities and their combinations} % title of Table
\centering % used for centering table
\scriptsize
{\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|c c c c c c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
 & \textless348\textgreater & \textless1934\textgreater & \textless2117\textgreater & \textless348, 1934\textgreater & \textless1934, 2117\textgreater & \textless348, 1934, 2117\textgreater \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
\textless348\textgreater & - & 0.282708 & 1.027081 & 0.282708 & 18.027081 & 18.027081 \\
\textless1934\textgreater & -2.637483 & - & 6.969072 & -2.637483 & 5.509583 & 4.387725 \\
\textless2117\textgreater & 5.027081 & 2.969072 & - & 5.509583 & 2.969072 & 5.509583 \\
\textless348, 1934\textgreater & 0.0 & 0.0 & -3.851432 & - & -3.851432 & -3.851432 \\
\textless1934, 2117\textgreater & 2.969072 & 0.0 & 0.0 & 2.969072 & - & 2.969072 \\
\textless348, 1934, 2117\textgreater & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & - \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
}
\label{table:nonlin} % is used to refer this table in the text
\end{table*}

\section{The Decision Making Mechanism}\label{s:model}

In this section, we describe our data extraction process and the methodology used to equip web services with a decision making mechanism. In this methodology, we first present the data extraction and engineering process and then we evaluate the decision making mechanism for web services in community settings.

\subsection{Data Extraction and Solution Engineering}\label{ss:learningdata}

\subsubsection{Web Service data}\label{sss:webservices}

We used a data set extracted from running web services. In this data set, each web service is associated with a number of features that reflect its functionality. These web services operate in an online environment and are continuously assigned tasks to handle. Sometimes, they pass tasks around, distributing sub-tasks among themselves and handling tasks in a collaborative effort. To engage in communities, we add additional features that reflect web services' utility as a result of joining other web services to form a community. The additional features are computed based on two assumptions that we adopt for a community to be formed. Since we have 64 different time slots of extracted features for each web service, we can build a synthetic data set that contains features of a large number of web services in a sequence of time. Therefore, we train a learning model that adopts the trend of joining a community and use the model to predict/find the appropriate community for other web services. To train our model, we build a decision tree as a benchmark for our decision making mechanism. The decision tree is built by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services. As a result, we are able to classify web services as either single or joined and propose the communities that are best fitted to the web services' requirements.

\subsubsection{Filtered Data}\label{sss:filtereddata}

We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}. The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{http://www.wsdream.net/}. In this data set, each web service is associated with a number of features that reflect its functionality. By summarizing the data provided for each web service over different time slots, we have acquired three quality features for each individual web service. Their quality features are the three internal features introduced in Section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time}. 
%To engage in communities, we add two additional external features that reflect web services estimation of its quality metrics compared to other web services. 
Therefore, we have generated an array of web services with three distinct features.

\begin{figure}%[!t]
\centerline{\includegraphics[width=3.25in]{figures/cfvs.eps}}
\caption{Communities with different properties of web services actively looking for other communities to collaborate with, they send collaboration requests to communities they find the collabration  increasing the gain}
\label{fig_community}
\end{figure}

Now, we want to generate a set of feature vectors representing the communities of web services for training purposes. For communities, we add two additional external features, as discussed in Section \ref{s:ef} that reflect the community's estimation of its quality metrics compared to other web services. Therefore, we formulate a \emph{Community Feature Vector (CFV)} as $CFV_{<C>} = \{f_1,...f_5\}$ having a community of $k$ web services. $C = {ws_1,...ws_k}$. The features $f_1$ through $f_5$ represent the \emph{execution time}, \emph{throughput}, \emph{availability} and the \emph{external parameters 1 and 2} correspondingly. A set of communities, with their feature vectors and utilities evaluated, provides our algorithm with a raw training data set. We call this set of communities the \emph{template vector}, and the set of feature vectors associated with the \emph{template vector} is referred to as the \emph{community feature vector set (CFVS)}. Figure \ref{fig_community} depicts communities looking to form collaborate communities and join other communities in order to improve their utility gain.

\subsubsection{Feature Engineering}\label{sss:feng}
Let $CFVS = \{C_1, C_2,..., C_N\}$ be the community feature vector set with $N$ communities. Based on the $CFVS$ set, we create an $|N \times N|$ gain matrix for $t$ different time slots. Each entry of $gain_{n,m}^{t}$corresponds to a utility gain of web services in $C_n$, when $C_n$ joins $C_m$, based on community and web service data available for time $t$. All of these values have to be evaluated by implementing the community with members of $ws_i \in C_n$ and $ws_j \in C_m$ and evaluating its utility (see Equation \ref{u_c_load}). Therefore $gain_{n,m}^{t} = U_{C_n \cup C_m}^{t} - U_{C_{n}}^{t}$. Evaluating the utility gain for all entries of the $gain$ matrix can be a costly process with a very big number of $N$, size of the feature vector $|N|$ should be chosen carefully.

Now, we let our set of communities in the $CFVS$ set, within $|T|$ time frame iterations, choose the the best communities to join. Each community is provided with the corresponding row of data from the $gain$ matrix. Basically, $C_i$ is provided with the data in row $i$ of matrix $gain_{N,N}$, which is all of the possible utility values it can gain by joining different communities. By ordering the list, each community is utilized with an ordered set of preferences over other communities it likes to join. We define $>_{i}^t$ as the preference order of community $i$ at time $t$.

Let $P_{C_i}^t = \{C_1 >_{i}^t C_2 >_{i}^t .... >_{i}^t C_n\}$ be an ordered set of preferences for community $C_i$ at time $t$. Based on this ordered set, we define $K^t(C_i, k)$ as a set of the $k$ most preferred communities of community $i$ at time $t$.
%\subsubsection{feature vector generation}\label{sss:fvg}
\begin{equation}\label{h_t_pref_top}
\begin{split}				
K^t(C_i, k) = &\Big\{C_x | C_x >_{i}^t C_y; \forall C_y \in CFVS\ \\
				      &\wedge C_y \notin \{K^t(i, 1),K^t(i, 2),...,K^t(i, k-1)\} \Big\}				
\end{split}
\end{equation}
Based on $K^t(C_i, k)$, we define a set of communities for $C_i$ in which they are the k most preferred communities for community $i$ and also community $i$ belongs to the k most preferred communities out of all of the communities in set $K^t(C_i, k)$. This basically implies the preference is both-sided.
\begin{equation}\label{l_t_top_both}
\begin{split}	
L^t(C_i,k) = &\Big\{C_j | C_j \in K^t(C_i, k) \\
             &\wedge C_i \in \bigcup_{C_x \in K^t(C_j, k)}K^t(C_x, k)\Big\}
\end{split}
\end{equation}

Table \ref{table:nonlin} illustrates an example of a $gain$ matrix for 3 different communities and their combinations. Each row shows the gain the community can achieve by collaborating with other 5 communities. In this example for community $\textless 348 \textgreater$ we have: \\
$K(\textless 348 \textgreater, 1) = \{\textless1934, 2117\textgreater\}$ and \\
$K(\textless 348 \textgreater, 2) = \{\textless1934, 2117\textgreater, \textless1934\textgreater\}$ \\
Since $\textless 348 \textgreater$ is best preferred community of $\textless 1934, 2117 \textgreater$ therefore $L(\textless 348 \textgreater, 1)$ is not empty and contains the community $\textless1934, 2117\textgreater$.

Using the $gain$ matrix and the mentioned preference ordering relations, we are able to build a decision tree where the list of possible communities to join and their expected utilities are set.
% as well as the joined events that took place in different time slots. 
In addition to best choices, web services have access to other ordered choices and can look for the second best or third best if their first try is rejected by the target community. The consequences of each try level is analyzed in more detail in the following section, in which we launch experiments and investigate the effectiveness of the use of a decision tree with different decision layers in joining other communities and enhancing the overall utility.

\subsection{Decision Profile Generation}\label{ss:learningmodel}

Our goal is to create a decision making profile for each community in the $CFVS$ set. We are creating an environment where they can experience the outcomes of different strategies. The result will be a decision tree of the feasible and utility increasing moves over time.

We let communities pick the best communities for maximizing their utilities over different time frames. At time $t = 1$, we let each community in the $CFVS$ set choose the best community, which is a single community in set $C_j = K^t(C_i, 1)$. If community $C_j$ also has the highest preference to join $C_i$ meaning the $L^t(C_i, k=1)$ set is not empty, they would join together. Having set $k = 1$ is a very strict and hardly satisfiable condition. In order to relax the requirement, the value of $k$ is being increased by a rate $r$ proportional to time slot $t$. Basically, $k = 1 + |r \times t|$. On early steps of simulation web services and communities are more strict but as time goes on, we let them choose second and then third best options too. However, increasing $k$ quickly increases the time complexity of $K^t(C_i, k)$ by $O(k^2 \times n.log(n))$.

When communities $C_i$ and $C_j$ are in each other's top $k$ preference set, their combination is added to the list of possible communities that can join others at time $t+1$. Also, for each community $C_i$ in our initial $CFVS$ set, we maintain a tree with the community $C_i$ as its root. Its children are all of the communities that $C_i$ decided to join. As the scenario progresses over time, the merged communities may decide to join other communities. When community $C_i$ and $C_j$ decide to join each other and create community $C_k$, the new community $C_k$ will be added as a child to both $C_i$ and $C_j$ nodes. At the end of the process, each community is utilized with a tree of set of possible combination of communities it can join. Algorithm \ref{algo:dectree} illustrates the DDM tree creation procedure as pseudo-code.

Having created $|n|$ trees, for each community $C_i$, our communities are utilized with the different possible paths they can take to maximize their utilities. Using a distance function, communities and web services can utilize these results and find the $C_i$ that closely resembles their parameters. They will be utilized with a tree that has the strategies the community can use to join our communities which will be best possible path to take and communities to join while most likely being accepted by other communities since its a two sided preference. The algorithm below describes the tree creation process.

\begin{algorithm}
\DontPrintSemicolon
\KwIn{$\langle r, gain^t_{n,n}, CFVS \rangle$ learning rate $r$, $|N \times N \times T|$ gain matrix, community feature vector}
\KwOut{A set of \emph{root} nodes of the decision trees}
$k \gets 1$\;
$nodes[N] \gets$ initialize $N$ tree nodes representing each community in CFVS\;
\For{$t \gets 1$ \textbf{to} $T$} {
	$k \gets 1 + round (r \times t)$\;
  \For{all $C_i \in CFVS$} {
	  \For{all $C_j \in L^t(C_i, k)$} {
      % The "l" before the If makes it so it does not expand to a second line
      \If{$C_i \in L^t(C_j, k)$}{
        $C_k \gets C_i \cup C_j$\;
				add $C_k$ to $CFVS$ set\;
				initiate $node_k$, representing $C_k$\;
				$nodes_i.addChild (node_k)$\;
				$nodes_j.addChild (node_k)$\;
      }
%      \Else{
%        $j \gets j + 1$\;
%      }			
		}
  }
%  $i \gets i + 1$\;
}
\Return{nodes}\;
\caption{{\sc DDM Decision Tree Algorithm}}
\label{algo:dectree}
\end{algorithm}

\textbf{Complexity.} Here we analyze the computational complexity of the DDM decision tree creation algorithm on each time iteration $t$. Computing top $k$ preferred communities for $C_i$ in $L^t(C_i, k)$ requires an $O(n.log(n))$ sort time. $C_i$ has a result set of size $|k|$, and for each of those $k$ communities we need to check against their $k$ top preferred communities. Considering we already have the list sorted, line 6 in algorithm runs $O(k \times n.log(n))$ times. Doing this search for all communities in $|CFVS|$ set $n$ times (line 5), the overall order of complexity of the algorithm in regards with $n$ and $k$ is: $O(k^2 \times n^2.log(n))$.

\section{Experiments}\label{s:experiments}
We implemented DDM in Java\footnote{Source code of implementation and data is available at: \emph{https://github.com/Marooned202/DDM}}. We have extracted the set of features for 4532 web services in 64 different time slots through a data set provided by \cite{10.1109/ISSRE.2011.17}. By choosing 86 web services out of these sets and choosing a subset of all possible combinations of sizes 2, 3, and 4 of these 86 web services, we have chosen 10,000 communities and evaluated the feature vectors and utilities they can have in 64 different time slots. This provides us with the initial training feature set of size $|CFVS| = 10,000$ communities. Based on Equation \ref{u_c_load} the utility of these communities are estimated, and the gain matrix $|10000 \times~ 10000|$ of all possible ways of merging these 10,000 communities, is generated\footnote {The template vector and gain matrix generated are available at \emph{https://github.com/Marooned202/DDM/tree/master/wsds/data/run}}, and each community has the ordered preference among other communities known in the set.

We let communities and web services adopt their strategies based on our $DDM$ decision making mechanism. Based on the decisions adopted, each community will generate a decision tree profile. We let DDM run four times with different $r$ rates of 0.05, 0.07, 0.10 and 0.20. With the slow rate of $r = 0.05$, we increase $k$ in Equation \ref{u_c_normal} for every 20 time frames, which will happen only three times in our 64-step experiment. In the case of $r = 0.20$, k increases much faster, at a rate of once every 5 time frames, which increases the complexity of the $L^t(C_i,k)$ search for each community in the $CFVS$ set.

Table \ref{table:valueandgain} depicts the average utility gain value of the communities in each of the four runs. The utility gain is the increase of utility the communities gain by cooperating and joining other communities. The utility gain ratio is the ratio of their final utility over initial utility. Comparing the different search rates, we can see increasing $r$ to value of $0.10$ results in significant performance boost, however the higher rates of $r$ are not increasing the chance of finding better collaborative groups for our communities.

\begin{table}[ht]
\caption{Utility gain of web services after making collaborative groups based on DDM algorithm with different $r$ rates} % title of Table
\centering % used for centering table
{\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|c|c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
Search Rate $r$ & Utility Gain Value & Utility Gain Ratio \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
r=0.20 & 176.1499 & 6.9690 \\
r=0.10 & 174.6541 & 6.9182 \\
r=0.07 & 159.9462 & 6.2834 \\
r=0.05 & 136.0768 & 5.1032 \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
}
\label{table:valueandgain} % is used to refer this table in the text
\end{table}

%\begin{figure}%[!t]
%\centering
%\includegraphics[width=3.5in]{figures/utility_gain_r.eps}
%\caption{DDM Utility Gain Value}
%\label{utility_gain_value}
%\end{figure}
%
%\begin{figure}%[!t]
%\centering
%\includegraphics[width=3.5in]{figures/utility_ratio_r.eps}
%\caption{DDM Utility Gain Ratio}
%\label{utility_gain_ratio}
%\end{figure}

We utilize the same communities and web services with a simple rational decision making mechanism, in which communities will choose to join a community if it increases utility by any amount. We call it the $rational$ method, in the sense that it is just a rational method and is not aiming to be optimal. We chose 10 random web services and compared the results with web services which adopted our DDM model. Figure \ref{utility_gain_mlisa_and_rational} shows the comparison of the end result of utility gain values. In 18 out of 40 tries, \emph{rational} agents were not able to improve their utility at all because the communities they chose rejected their request, most likely because they would not have increased the utility of the other communities if they had joined them. The results show that a long-term strategic decision mechanism is needed to satisfy all of the services within communities. Figure \ref{utility_gain_mlisa_and_rational_ratio} shows the same results in terms of ratio of utility gain.

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_gain.eps}
\caption{Utility Gain DDM and Rational}
\label{utility_gain_mlisa_and_rational}
\end{figure}

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/utility_ratio.eps}
\caption{Ratio of Utility Gain DDM and Rational}
\label{utility_gain_mlisa_and_rational_ratio}
\end{figure}

Now, we evaluate the performance of the decision profiles generated based on our data set for other communities.% which are not included in the decision tree creation process. 
We create one thousand communities from the web services in the data set that were not involved in the decision model creation process. We define a distance function that measures the difference between basic features of communities, which measures the similarity of communities.

\begin{equation}\label{distance_c}
\begin{split}
distance (C_1, C_2) & = |Th_{C_1} - Th_{C_2}| \\
                    & + |A_{C_1} - A_{C_2}| + |Et_{C_1} - Et_{C_2}|
\end{split}
\end{equation}

Now, each community tries to find the closest community within the trained $CFVS$ set. Following its decision profile, the community can get a good estimate of the possible strategic decisions it can adopt. Basically, the trained profiles benefit the new web services in two ways. First, they provide the communities with a set of viable communities to join. Second, they provide an estimation of long-term utility gain for each available decision. In this experiment, we let communities follow the best decision within the decision tree provided to the them.

\begin{table}[ht]
\caption{Number of communities that misses the optimal decision, out of 1,000 communities} % title of Table
\centering % used for centering table
\begin{tabular}{|c|c|} % centered columns (4 columns)
\hline %inserts double horizontal lines
 Method&Miss \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
 DDM r=0.05& 375 \\ % inserting body of the table
 DDM r=0.07& 137 \\
 DDM r=0.10& 6 \\
 DDM r=0.20& 6 \\
Rational Method& 717 \\
Greedy Method& 828 \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
\label{fail_rate} % is used to refer this table in the text
\end{table}

In order to evaluate the performance of the mechanism, we used \emph{Receiver Operating Characteristic (ROC) curve}, which is a graphical plot illustrating the true negative rate against the false positive rate at various threshold settings in classifier systems. In order to classify our communities' selection strategies correctly, for each community, we evaluated the training process by replacing the community in the set with the closest one, from which it gets the strategy profile. If the actions are the same and the same utility levels are gained, we classify the decision as correct. Otherwise, it is classified as a wrong decision. \emph{AUC}, the area under the \emph{ROC curve}, is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one, and the higher number reflects better performance from the better solution.  Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of the DDM decision making mechanism. We compare our method with two other methods. The \emph{rational} method is based on the assumption that communities, as rational agents, join a community that increases their utility. The \emph{greedy} method only looks up the available list of communities and simply joins the community that maximizes its utility without considering any long-term strategy or other communities' acceptance scenarios, its an greedy algorithm and chooses a locally optimal choice. Therefore we use these two methods as our benchmark:

\begin{itemize}
  \item {\bf Rational Method:} Communities would send a join request to any available community, which will increase the utility. The other community would accept the join offer if the utility gain is positive as well.
	\item {\bf Greedy Method:} Communities do a linear search among all the available communities and send a join request to the community which results in maximum utility, The other community would accept the join offer if the utility gain is positive and the utility gain does not need to be the maximum for the community recieving the join request.
\end{itemize}

Figure \ref{roc5} compares the results for all methods. The two other methods have very high failure rates compared to our method. Table \ref{fail_rate} illustrates the number of communities that failed to find the optimal collaboration group. The results support the need for a long-term training model in a successful decision making process.

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/roc.eps}
\caption{RoC Curve}
\label{roc5}
\end{figure}
Now, we evaluate the system-specific results from users' and communities' perspectives. By distributing tasks among the communities over these time frames, we evaluate the revenue for each community. Figure \ref{stats1} shows the overall revenue gain of communities using our method. Figure \ref{stats2} shows the momentarily revenue gain for each community in each time slot compared to the previous time. These results show that the run with the higher learning rate of $r=0.20$ starts discovering better communities to join much earlier. The runs with slow rates seem to find some communities to join initially, but then they slow down until later, when they start discovering new communities to join.

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/stats1.eps}
\caption{Overall Utility of all communities}
\label{stats1}
\end{figure}

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/stats2.eps}
\caption{Utility Gain on time}
\label{stats2}
\end{figure}

Figure \ref{stats3} depicts the average community size over time, which essentially represents the number of new communities being formed. Once again, these results show that the runs with higher search rates tend to find appropriate communities to join faster.

\begin{figure}%[!t]
\centering
\includegraphics[width=3.5in]{figures/stats3.eps}
\caption{Average Community Size}
\label{stats3}
\end{figure}

\section{Related Work}\label{s:related_work}

In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
defined communities as \emph{Service Containers} that aggregate
substitutable web services providing a common functionality (same
set of operations). They abstracted \emph{Service Containers} as
web services that are created, advertised, discovered and invoked
just as elementary web services. The \emph{Container} is
considered as a manager that is responsible for web service
selection upon receiving a request on run-time. The authors have
proposed a scoring service based on non-functional requirements of
the request and web service capabilities to dynamically chose the
web service to perform the requested task. A similar concept was
proposed by Maamar et al. in
\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
web service communities as a collection of web services with a
common functionality but different QoS properties. A community
manager, upon receiving a request, delegates the request to one of
its current members. The choice is based on the performance
history and quality metrics of each web service. The authors have
proposed an efficient global web service selection algorithm in
order to approach quality constraints and preferences for
composite services which require aggregation of different types of
services to satisfy the user.

Benslimane et al. \cite{Liris-2770} have proposed a multi-layer
approach grouping similar Web services into communities and having
an interface implemented as an abstract web service for accessing
the community on top of the community layer. The interactions
between composite, management and community layers and the
bindings are performed by a generic driver called Open Software
Connectivity (OSC).

In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
service communities with centralized access across distributed web
services. They have proposed a framework for web service
management, query resolution among communities and a query caching
mechanism executed by the manager to improve the performance of
query resolution process among many distributed communities. The
key idea is to cache previous computed results for answering
future queries.

Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
proposed an architecture utilizing \emph{Contract-Net} protocol
for engineering task distribution within communities of web
services. The protocol is centrally executed by the community
manager. This architecture has been further developed in
\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
roles have been distinguished for community members: masters and
slaves. Master web services and community managers that lead
communities and are responsible for membership management. They
can invite and convince slave web services to join the community,
and attract new slave web services to their communities by
awarding them better payoff. Moreover, they can eject some slave
members from the community to improve its overall reputation if
these members are misbehaving or cannot provide the promised QoS.

In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
developed a community as a ``cluster'' that groups Web services
based on a specific area of interest. All web services in a given
community share the same functionality. These communities are
created by \emph{third party community providers} which use the
\emph{community ontology} as a template and define a set of
operations that all web services within a community should
provide. Using semantic analysis on web service operations, web
services either find and join a community with similar
functionality or create a new operation description for a new
community. The authors have described the concept of
\emph{community agents} associated to \emph{community providers}.
A community agent is responsible, among other things, of the
registration of services with the community. An example of a
community that provides health care services to senior citizens
has been used. In this example, a governmental entity is needed to
check the health care standards used by the members before
authorizing them to be part of the community. Such a central
entity is represented by the community agent. Thus, community
agents are playing the role of community managers. In a close work
\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
global planning selection algorithm and a delegation algorithm to
be run when a request to execute an operation is received by the
community. This needs a central entity to run those algorithms.
Such entity plays the same role as the community coordinator or
manager.

Most of the recent work on communities of services are either
user-centric and focus on user satisfaction
\cite{Chun02user-centricperformance} or system-centric and focus
on the whole system throughput, performance and utilization. There
are many contributions in distributed, grid, cluster and cloud
services which are system-centric. However, in real world
environments and applications, both users and service providers
are self-interested agents, aiming to maximize their own profit.
In those environments, both parties (users and services) will
collaborate as long as they are getting more benefits and payoff.

In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
mechanisms to help users and services maximize their gain. A
two-player non-cooperative game between web services and community
master was introduced in
\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this game-theoretic
model, the strategies available to a web service when facing a new
community are requesting to join the community, accepting the
master's invitation to join the community, or refusing the
invitation to join. The set of strategies for communities are
inviting the web service or refusing the web service's join
request. Based on their capacity, market share and reputation, the
two players have different sets of utilities over the strategy
profiles of the game. The main limits of this game model are: 1)
its consideration of only three quality parameters, while the
other factors are simply ignored; and 2) the non-consideration of
the web services already residing within the community. The game
is only between the community master and the new web service, and
the inputs from all the other members and their influence on the
master's decision are simply ignored. The consideration of those
inputs and this influence factor is a significant issue as
existing web services can lose utility or payoff because of the
new member, which can result in an unhealthy and unstable group.
The problem comes from the fact that the existing members should
collaborate with the new web services, so probably their
performance as a group can suffer. Existing members may even
deviate and try to join other communities if they are unsatisfied.
Those considerations of forming stable and efficient coalitions
are the main contributions of our paper.

In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
for selecting web services has been proposed. In this approach,
the authors proposed a web service selection process that the
community masters can use. The approach considers the efficiency
of all the three involved parties, namely users, web services and
communities. In this work, it is shown how the gains of these
parties are coupled together using a linear optimization process.
However, the optimization problem in this solution tends to
optimize some parameters considering all web services regardless
of their efficiency and contribution to the community's welfare.
Moreover, there are no clear thresholds for accepting or rejecting
new web services. The solution of the optimization problem could,
for instance, suggest web services already residing within the
community to increase or decrease their capacity to cover up the
weakness of other parties in the system. However, a high
performing web service could deviate anytime it finds itself
unsatisfied within the community instead of adjusting its service
parameters.

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
autonomous web services based on coalitional game theory has been
introduced. The authors have proposed an interesting algorithm to
reach individually stable coalition partition for web services in
order to maximize their efficiency. The communities choose new web
services on the promise that it would benefit the community
without decreasing any other web service's income. In the proposed
model, the worth of community is evaluated with high emphasis on
the availability metric and considering price and cost values
only. The community structure is based on a coordination chain,
where a web service is considered as a \emph{primary} web service
and the community task-distribution method initially invokes the
primary web service and only if the primary web service is
unavailable, the method invokes the next backup web services as
they are ordered in the coordination chain. We believe that this
coordination chain limits the cooperation power as it introduces a
sort of hierarchy. However, in pure and open cooperative models,
such as the one we propose in this paper, active cooperation
activities engaging simultaneously many agents so that they can
perform the tasks more efficiently are being used. Moreover, if
the availability is high, which is the case nowadays with the
recent advancements in cloud and hardware infrastructures, the
backup web services will end-up having a very low chance of
getting jobs, especially the ones further in the chain. This will
results in a considerable waste of web services capabilities.

All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process. 
So basically These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance. We address this issue by introducing DDM a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. Therefore web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.

%\subsection{Subsection Heading Here}
%Subsection text here.

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

%\subsubsection{Subsubsection Heading Here}
%Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection %text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.
%Subsubsection text here.Subsubsection text here.Subsubsection text here.

%Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection %text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex,
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE CS typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.
% However, the Computer Society has been known to put floats at the bottom.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE CS papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals use top floats exclusively.
% However, Computer Society journals sometimes do use bottom floats - bear
% this in mind when choosing appropriate optional arguments for the
% figure/table environments.
% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
% floats. This can be corrected via the \fnbelowfloat command of the
% stfloats package.

\section{Conclusion}\label{s:conclusion}

In this paper, we proposed a training model for the problem of membership management of communities of web services. Using the traning model we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves. This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available. The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices. The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms. The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.

Our plan for future work is to advance learning process on the training set that we provided in our work. SVN machine learning algorithm are suitable in classification of our training data set, to better classify correct or wrong decisions based on long-term utility gains, as data set outputs. This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
\bibliographystyle{elsarticle-num} 
\bibliography{Ehsan}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

\begin{thebibliography}{00}

%% \bibitem{label}
%% Text of bibliographic item

%\bibitem{}

\end{thebibliography}
\end{document}
\endinput
%%
%% End of file `elsarticle-template-num.tex'.

### 2015-01-19 papers/webservice-coalition-learning-omar-template/elsarticle-template-num.tex
changes

--- 2015-01-19 papers/webservice-coalition-learning-else-template/elsarticle-template-num.tex
@@
-%% 
-%% Copyright 2007, 2008, 2009 Elsevier Ltd
-%% 
-%% This file is part of the 'Elsarticle Bundle'.
-%% ---------------------------------------------
-%% 
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%% 
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%%
-
-%% Template article for Elsevier's document class `elsarticle'
-%% with numbered style bibliographic references
-%% SP 2008/03/01
-
-\documentclass[preprint,12pt]{elsarticle}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-%% please give \usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
-\usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-%% \usepackage{amsthm}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
-\journal{Decision Support Systems}
+\documentclass[11pt,onecolumn]{IEEETran}
+
+\usepackage{lineno,hyperref}
+\usepackage{graphicx}
+\usepackage{epstopdf}
+\usepackage{url}\renewcommand{\baselinestretch}{1}
+\usepackage{epsfig}
+\usepackage{amsmath,amssymb}
+\usepackage{multirow}
+\usepackage{caption}
+\usepackage{fancyvrb}
+\usepackage{mathptmx}
+\usepackage{alltt}
+\usepackage{amsmath}
+\usepackage{setspace}
+\usepackage{booktabs}
+\usepackage{tabularx}
+\usepackage{array}
+\usepackage{subcaption}
+\usepackage[english]{babel}
+\usepackage{lineno,hyperref}
+
+\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+%\usepackage[thinlines]{easytable}
+\captionsetup{font=footnotesize}
+
+\modulolinenumbers[3]
+\doublespacing
+
+%\journal{Decision Support Systems}
+
+%% `Elsevier LaTeX' style
+\bibliographystyle{elsarticle-num}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\author{
+    \IEEEauthorblockN{\normalsize Ehsan Khosrowshahi Asl\IEEEauthorrefmark{1}, Babak Khosravifar\IEEEauthorrefmark{1}, Jamal Bentahar\IEEEauthorrefmark{1}, Hadi Otrok\IEEEauthorrefmark{2}, Rabeb Mizouni\IEEEauthorrefmark{2}}\\
+    \IEEEauthorblockA{\IEEEauthorrefmark{1}Concordia Institute for Information Systems Engineering, Concordia University, Montreal, Canada}
+    \\
+    \IEEEauthorblockA{\IEEEauthorrefmark{2}Department of Electrical and Computer Engineering, KUSTAR, Abu Dhabi, UAE}
+}
+\title{Distributed Decision Making for Dynamic Formation of Web Services Communities}
 
 \begin{document}
-
-\begin{frontmatter}
-
-%% Title, authors and addresses
-
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{Distributed Decision Making for Dynamic Formation of Web Services Communities}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author{}
-
-\address{}
+\maketitle
 
@@
 \end{abstract}
-
-\begin{keyword}
-Web services\sep Community of services\sep Distributed Decision Making
-%% keywords here, in the form: keyword \sep keyword
-
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
-\end{keyword}
-
-\end{frontmatter}
-
-%% \linenumbers
-
-%% main text
+\begin{IEEEkeywords}
+Web services; Community of services; Distributed Decision Making;
+\end{IEEEkeywords}
+
+\linenumbers
+\maketitle
+
 \section{Introduction}
@@
 One practical solution towards delivering high quality services is utilizing intelligent decision making agents.
-These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users\cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, journals/tsc/ZhengZYB13, Demirkan2013412}.
+These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users\cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Demirkan2013412, journals/tsc/ZhengZYB13, Josang:2007:STR:1225318.1225716}.
 However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided.
@@
 \centering % used for centering table
-\scriptsize
 {\renewcommand{\arraystretch}{1.2}
@@
 
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
-
-%% If you have bibdatabase file and want bibtex to generate the
-%% bibitems, please use
-%%
 \bibliographystyle{elsarticle-num} 
@@
 
-%% else use the following coding to input the bibitems directly in the
-%% TeX file.
-
-\begin{thebibliography}{00}
-
-%% \bibitem{label}
-%% Text of bibliographic item
-
-%\bibitem{}
-
-\end{thebibliography}
 \end{document}
+
 \endinput
 %%
-%% End of file `elsarticle-template-num.tex'.
+%% End of file `elsarticle-template-harv.tex'.

### 2015-01-19 papers/webservice-coalition-learning-else-template/figures/matlab/babak_chart.m

@@ -1,0 +1,133 @@
+% Create the data to be plotted
+TBdata = [1:1:18];
+
+xvalue = (1:1:18);
+normal1 = [0,30,4.03749251,12.1432232,28,30,20,38.47193752,14.04091499,0,8,24.88305055,45.37468191,14,6,18,45.16825893,0.048717];
+attack1 = [24,6,18,14,2,4,16,18,53.01154208,18.9403051,53.57347789,61.68702521,47.19210552,67.55182234,51.71291161,17.52555902,0,0];
+
+normal2 = [0,30,3.239234825,12.04296696,28,30,20,29.35035582,14.0122745,0,8,20.59505431,38.24552608,14,6,18,33.60740563,    0.0146151];
+attack2= [24,6,18,14,2,4,16,16.60469875,46.1877697,9.333735534,34.72218245,51.03347268,38.34038787,42.13420307,27.43894684,0,0,0];
+
+normal3 = [0,30,2.507594309,12.02847254,28,30,20,23.50401441,14.00599075,0,8,16.31851728,32.73618704,14,6,18,28.50416389,0.00752274];
+attack3 = [24,6,18,14,2,4,16,16.161253,41.97947459,3.564454826,27.15362841,45.05967114,28.98939777,27.18244652,15.43665554,17.52555902,0,0];
+
+normal4 = [0,30,2.200978868,12.01179626,28,30,20,21.26569384,14.00301951,0,8,14.75902505,30.83083017,14,6,18,25.46815874,0.0040282];
+attack4 = [24,6,18,14,2,4,16,16.04031325,40.56574344,1.234786494,24.3739625,42.96055576,25.56965081,21.20939489,10.7047494,11.2392834,0,0];
+
+normal5 = [0,30,2.299385361,12.01324226,28,30,20,21.72293322,14.00452926,0,8,15.03706259,31.07941887,14,6,18,25.77814662,0.004822191];
+attack5 = [24,6,18,14,2,4,16,16.04,40.64,1.71,25.13,43.23,25.98,22.49,12.11,41.12,0,0];
+
+normal6 = [0,30,2.299385361,12.01324226,28,30,20,21.72293322,14.00452926,0,8,15.03706259,31.07941887,14,6,18,25.77814662,0.004822191];
[…]

### 2015-01-19 papers/webservice-coalition-learning-else-template/figures/matlab/mlisa_chart_utility.m

@@ -1,0 +1,116 @@
+% Create the data to be plotted
+
+color1 = [0.0,0.0,0.5];
+color2 = [0.7,0.7,0.95];
+fontsize = 14;
+
+[v,T,vT]=xlsread('mlisa_chart_utility.xlsx') 
+gainR020 = v((1:1:20),1);
+gainR010 = v((1:1:20),2);
+gainR007 = v((1:1:20),3);
+gainR005 = v((1:1:20),4);
+
+ratioR020 = v((25:1:44),1);
+ratioR010 = v((25:1:44),2);
+ratioR007 = v((25:1:44),3);
+ratioR005 = v((25:1:44),4);
+
+xvalue = (1:1:20)';
+wsname = vT((4:1:23),1);
+
+% Create the pie chart in position 1 of a 2x2 grid
+hFig = figure(1);
+set(hFig, 'Position', [100 100 800 800])
+%set(0,'DefaultAxesColorOrder',[1 0 0],'DefaultAxesLineStyleOrder','-|+|--|.|:')
+set(0,'DefaultAxesColorOrder',[0 0 0;0.5 0.5 0.5])
+
+
+% Create the bar chart in position 1 of a 3x2 grid
+subplot(2, 2, 1);
+%plot(xvalue, normal1, 's-', xvalue, attack1, '*-', 'linewidth', 2, 'markers',4);
+bar(xvalue(1:1:10), gainR020(1:1:10), 0.4, 'FaceColor',color1);
+hold on
+bar(xvalue(11:1:20), gainR020(11:1:20), 0.4, 'FaceColor',color2);
+xlabel('DDM WS             Rational WS','FontSize',fontsize);
+ylabel('Utility Gain Value','FontSize',fontsize);
+title ('R=0.2 (a)','FontSize',fontsize);
+%title('TITLE');
+axis([0 21 0 400]);
+set(gca,'XTick',[1 5 10 15 20]);
+hleg1 = legend('Trained', 'Rational');
+set(hleg1,'Orientation','horizontal');
+grid on
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'XTickLabel',wsname);
+%axes('xlim',[0 19],'xtick',xvalue,'xticklabel',wsname)
+
+%hleg1 = legend('Normal data', 'Attacks');
+%set(hleg1, 'Position', [.248,.842,.1,.2]);
+%set(hleg1,'Interpreter','none');
[…]

### 2015-01-19 papers/webservice-coalition-learning-else-template/figures/matlab/mlisa_chart_utility_ratio.m

@@ -1,0 +1,112 @@
+% Create the data to be plotted
+
+color1 = [0.0,0.0,0.5];
+color2 = [0.7,0.7,0.95];
+fontsize = 14;
+
+[v,T,vT]=xlsread('mlisa_chart_utility.xlsx') 
+gainR020 = v((1:1:20),1);
+gainR010 = v((1:1:20),2);
+gainR007 = v((1:1:20),3);
+gainR005 = v((1:1:20),4);
+
+ratioR020 = v((25:1:44),1);
+ratioR010 = v((25:1:44),2);
+ratioR007 = v((25:1:44),3);
+ratioR005 = v((25:1:44),4);
+
+xvalue = (1:1:20)';
+wsname = vT((4:1:23),1);
+
+% Create the pie chart in position 1 of a 2x2 grid
+hFig = figure(1);
+set(hFig, 'Position', [100 100 800 800])
+%set(0,'DefaultAxesColorOrder',[1 0 0],'DefaultAxesLineStyleOrder','-|+|--|.|:')
+set(0,'DefaultAxesColorOrder',[0 0 0;0.5 0.5 0.5])
+
+
+% Create the bar chart in position 1 of a 3x2 grid
+subplot(2, 2, 1);
+%plot(xvalue, normal1, 's-', xvalue, attack1, '*-', 'linewidth', 2, 'markers',4);
+bar(xvalue(1:1:10), ratioR020(1:1:10), 0.4, 'FaceColor',color1);
+hold on
+bar(xvalue(11:1:20), ratioR020(11:1:20), 0.4, 'FaceColor',color2);
+xlabel('DDM WS              Rational WS','FontSize',fontsize);
+ylabel('Utility Gain Ratio','FontSize',fontsize);
+title ('R=0.2 (a)','FontSize',fontsize);
+%title('TITLE');
+axis([0 21 0 22]);
+set(gca,'XTick',[1 5 10 15 20]);
+hleg1 = legend('Trained', 'Rational');
+grid on
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+%set(gca,'XTickLabel',wsname);
+%axes('xlim',[0 19],'xtick',xvalue,'xticklabel',wsname)
+
+%hleg1 = legend('Normal data', 'Attacks');
+%set(hleg1, 'Position', [.248,.842,.1,.2]);
+%set(hleg1,'Interpreter','none');
+%set(hleg1,'Orientation','horizontal');
[…]

### 2015-01-19 papers/webservice-coalition-learning-else-template/figures/matlab/mlisa_roc.m

@@ -1,0 +1,59 @@
+[v,T,vT]=xlsread('roc_all.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+%set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|:|--|-.')
+%set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-.r*|:|--|-.')
+
+i=0:49;
+it=v(:,1);iy=v(:,3);iz=v(:,5);itt=v(:,7);iyy=v(:,9);izz=v(:,11);
+t=v(:,2);y=v(:,4);z=v(:,6);tt=v(:,8);yy=v(:,10);zz=v(:,12);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(it,t,'--go',iy,y,'--ko',iz,z,':bs',itt,tt,'-.r*',iyy,yy,'-.bo',izz,zz,'--ks', 'MarkerSize',3, 'linewidth', 1);
+%set(h,'linewidth',2);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+%set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',0:200:1600);
+set(gca,'tickdir','in')
+%set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+%axis([0 50 0 1600]);
+
+% Add legend
[…]

### 2015-01-19 papers/webservice-coalition-learning-else-template/figures/matlab/mlisa_stats1.m

@@ -1,0 +1,60 @@
+[v,T,vT]=xlsread('mlisa_chart_stats.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|+-|.|:')
+
+i=0:62;
+t=v(:,1);y=v(:,2);z=v(:,3);tt=v(:,4);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+%h = plot(i,t,i,y,i,z,i,tt,'linewidth', 2);
+h = plot(i,t,'--g+',i,y,'--ko',i,z,':bs',i,tt,'-.r*', 'MarkerSize',3, 'linewidth', 1);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:63);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0:5000:30000);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '51';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    ' ';' ';'63';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 63 0 30000]);
+
+% Add legend
+hleg1 = legend('R=0.05','R=0.07','R=0.10','R=0.20');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.24,.63,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
[…]

### 2015-01-23 papers/webservice-coalition-learning-omar-template/elsarticle-template-num.tex
changes

@@
 
-To effectively train web services, we used real data set to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another.
+To effectively generate the decision model for web services, we used real data set to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another.
 The data set has been extracted by real-world QoS evaluation results from 142 users on 4,532 Web services on 64 different time slots.
@@
 Web services need to experiment with different possible collaborative groups and other web services in order to estimate their gain over time.
-However, with a high number of possible communities and many other business restrictions, it is not possible to test collaboration with random web services.
+However, with a high number of possible communities, it is not possible to test collaboration with random web services.
 Even if a linear approximate function for estimating utility based on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell_number$} growth rate of the possible number of partitions of web services into communities would make any brute-force type algorithm for the best community selection strategy intractable and impractical in real-world application settings.
@@
 is an estimate of how close the web service's \emph{execution time} is to other web services.
-It is the difference between a web service's \emph{execution time} metric and the maximum value of execution time of web services, about which the web service has recently gathered information.
+It is the difference between a web service's \emph{execution time} metric and the maximum value of execution time of all the other web services, about which the web service has information of them.
 The less value means web service has better execution time compared to other web services.
@@
 	\item \emph{External Parameter 2} $(exp_2)$ is a comparison of the web service's rate of performing tasks to other competing web services.
-It is the difference between a web service's \emph{throughput} metric and the maximum value of throughput of web services, about which the web service has recently gathered information.
+It is the difference between a web service's \emph{throughput} metric and the maximum value of throughput of all the other web services,, about which the web service has information of them.
 The less value means web service has better throughput compared to other web services.
@@
 \end{equation}
+
+\section{The Decision Making Mechanism}\label{s:model}
+
+In this section, we describe our data extraction process and the methodology used to equip web services with a decision making mechanism.
+In this methodology, we first present the data extraction and engineering process and then we evaluate the decision making mechanism for web services in community settings.
+Figure \ref{fig_steps} summarizes the steps performed in DDM from the input data to generation of decision making profiles for web services.
+
+\begin{figure}%[!t]
+\centerline{\includegraphics[width=1.75in]{figures/steps.eps}}
+\caption{A summary of DDM decision profile generation steps}
+\label{fig_steps}
+\end{figure}
+
+\subsection{Data Extraction and Solution Engineering}\label{ss:learningdata}
+
+\subsubsection{Input Web Services Data}\label{sss:webservices}
+
+%We used a data set extracted from running web services. In this data set, 
+Each web service is associated with a number of features that reflect its functionality.
+These web services operate in an online environment and are continuously assigned tasks to handle.
+Sometimes, they pass tasks around, distributing sub-tasks among themselves and handling tasks in a collaborative effort.
+To engage in communities, we add additional features that reflect web services' utility as a result of joining other web services to form a community.
+The additional features are computed based on two assumptions that we adopt for a community to be formed.
+Our raw data set provides us with 64 different time slots of extracted features for each web service.
+Using this data we can build a synthetic data set that contains features of a large number of web services in a sequence of time.
+Therefore, we train a learning model that adopts the trend of joining a community and use the model to predict/find the appropriate community for other web services.
+To train our model, we build a decision tree as a benchmark for our decision making mechanism.
+The decision tree is built by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services.
+As a result, we are able to classify web services as either single or joined and propose the communities that are best fitted to the web services' requirements.
+
+\subsubsection{Filtered Data}\label{sss:filtereddata}
+
+We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}.
+The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{http://www.wsdream.net/}.
+In this data set, each web service is associated with a number of features that reflect its functionality.
+By summarizing the data provided for each web service over different time slots, we have acquired three quality features for each individual web service.
+Their quality features are the three internal features introduced in Section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time}.
+%To engage in communities, we add two additional external features that reflect web services estimation of its quality metrics compared to other web services. 
+Therefore, we have generated an array of web services with three distinct features.
+
+\begin{figure}%[!t]
+\centerline{\includegraphics[width=3.25in]{figures/cfvs.eps}}
+\caption{Communities with different properties of web services actively looking for other communities to collaborate with, they send collaboration requests to communities they find the collabration  increasing the gain}
+\label{fig_community}
+\end{figure}
+
+Now, we want to generate a set of feature vectors representing the communities of web services for training purposes.
+For communities, we add two additional external features, as discussed in Section \ref{s:ef} that reflect the community's estimation of its quality metrics compared to other web services.
+Therefore, we formulate a \emph{Community Feature Vector (CFV)} as $CFV_{<C>} = \{f_1,...f_5\}$ having a community of $k$ web services.
+$C = {ws_1,...ws_k}$.
+The features $f_1$ through $f_5$ represent the \emph{execution time}, \emph{throughput}, \emph{availability} and the \emph{external parameters 1 and 2} correspondingly.
+A set of communities, with their feature vectors and utilities evaluated, provides our algorithm with a raw training data set.
+We call this set of communities the \emph{template vector}, and the set of feature vectors associated with the \emph{template vector} is referred to as the \emph{community feature vector set (CFVS)}.
+Figure \ref{fig_community} depicts communities looking to form collaborate communities and join other communities in order to improve their utility gain.
+
+\subsubsection{Feature Engineering}\label{sss:feng}
+Let $CFVS = \{C_1, C_2,..., C_N\}$ be the community feature vector set with $N$ communities.
+Based on the $CFVS$ set, we create an $|N \times N|$ gain matrix for $t$ different time slots.
+Each entry of $gain_{n,m}^{t}$corresponds to a utility gain of web services in $C_n$, when $C_n$ joins $C_m$, based on community and web service data available for time $t$.
+All of these values have to be evaluated by implementing the community with members of $ws_i \in C_n$ and $ws_j \in C_m$ and evaluating its utility (see Equation \ref{u_c_load}).
+Therefore $gain_{n,m}^{t} = U_{C_n \cup C_m}^{t} - U_{C_{n}}^{t}$.
+Evaluating the utility gain for all entries of the $gain$ matrix can be a costly process with a very big number of $N$, size of the feature vector $|N|$ should be chosen carefully.
 
@@
 \end{table*}
-
-\section{The Decision Making Mechanism}\label{s:model}
-
-In this section, we describe our data extraction process and the methodology used to equip web services with a decision making mechanism.
-In this methodology, we first present the data extraction and engineering process and then we evaluate the decision making mechanism for web services in community settings.
-
-\subsection{Data Extraction and Solution Engineering}\label{ss:learningdata}
-
-\subsubsection{Web Service data}\label{sss:webservices}
-
-We used a data set extracted from running web services.
-In this data set, each web service is associated with a number of features that reflect its functionality.
-These web services operate in an online environment and are continuously assigned tasks to handle.
-Sometimes, they pass tasks around, distributing sub-tasks among themselves and handling tasks in a collaborative effort.
-To engage in communities, we add additional features that reflect web services' utility as a result of joining other web services to form a community.
-The additional features are computed based on two assumptions that we adopt for a community to be formed.
-Since we have 64 different time slots of extracted features for each web service, we can build a synthetic data set that contains features of a large number of web services in a sequence of time.
-Therefore, we train a learning model that adopts the trend of joining a community and use the model to predict/find the appropriate community for other web services.
-To train our model, we build a decision tree as a benchmark for our decision making mechanism.
-The decision tree is built by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services.
-As a result, we are able to classify web services as either single or joined and propose the communities that are best fitted to the web services' requirements.
-
-\subsubsection{Filtered Data}\label{sss:filtereddata}
-
-We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}.
-The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{http://www.wsdream.net/}.
-In this data set, each web service is associated with a number of features that reflect its functionality.
-By summarizing the data provided for each web service over different time slots, we have acquired three quality features for each individual web service.
-Their quality features are the three internal features introduced in Section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time}.
-%To engage in communities, we add two additional external features that reflect web services estimation of its quality metrics compared to other web services. 
-Therefore, we have generated an array of web services with three distinct features.
-
-\begin{figure}%[!t]
-\centerline{\includegraphics[width=3.25in]{figures/cfvs.eps}}
-\caption{Communities with different properties of web services actively looking for other communities to collaborate with, they send collaboration requests to communities they find the collabration  increasing the gain}
-\label{fig_community}
-\end{figure}
-
-Now, we want to generate a set of feature vectors representing the communities of web services for training purposes.
-For communities, we add two additional external features, as discussed in Section \ref{s:ef} that reflect the community's estimation of its quality metrics compared to other web services.
-Therefore, we formulate a \emph{Community Feature Vector (CFV)} as $CFV_{<C>} = \{f_1,...f_5\}$ having a community of $k$ web services.
-$C = {ws_1,...ws_k}$.
-The features $f_1$ through $f_5$ represent the \emph{execution time}, \emph{throughput}, \emph{availability} and the \emph{external parameters 1 and 2} correspondingly.
-A set of communities, with their feature vectors and utilities evaluated, provides our algorithm with a raw training data set.
-We call this set of communities the \emph{template vector}, and the set of feature vectors associated with the \emph{template vector} is referred to as the \emph{community feature vector set (CFVS)}.
-Figure \ref{fig_community} depicts communities looking to form collaborate communities and join other communities in order to improve their utility gain.
-
-\subsubsection{Feature Engineering}\label{sss:feng}
-Let $CFVS = \{C_1, C_2,..., C_N\}$ be the community feature vector set with $N$ communities.
-Based on the $CFVS$ set, we create an $|N \times N|$ gain matrix for $t$ different time slots.
-Each entry of $gain_{n,m}^{t}$corresponds to a utility gain of web services in $C_n$, when $C_n$ joins $C_m$, based on community and web service data available for time $t$.
-All of these values have to be evaluated by implementing the community with members of $ws_i \in C_n$ and $ws_j \in C_m$ and evaluating its utility (see Equation \ref{u_c_load}).
-Therefore $gain_{n,m}^{t} = U_{C_n \cup C_m}^{t} - U_{C_{n}}^{t}$.
-Evaluating the utility gain for all entries of the $gain$ matrix can be a costly process with a very big number of $N$, size of the feature vector $|N|$ should be chosen carefully.
 

### 2015-04-05 thesis/others/khalid/chap2/chap2.tex
added thesis

\setcounter{chapter}{1}

\chapter{Background}\label{cha:background}
This chapter reviews the background needed for our thesis. We explain all concepts, techniques, and tools that are used throughout this thesis. In Section \ref{sec:social-commitment-cha2}, the concept of social commitments as a means of communication between interacting agents is discussed. Section \ref{sec:knowledge-cha2} is devoted to briefly review reasoning about knowledge in MASs. In Section \ref{sec:system-models-cha2} some modeling formalisms including Interpreted Systems, we use in this thesis, are reviewed. Temporal logics for systems specification are also presented in this section. Section \ref{sec:Model-Checking-cha2}, describes the concept of model checking. Also, a review of some prominent existing model checkers is given in this section. Finally, we conclude this chapter in Section \ref{sec:summary-chap2}.

\section{Social Commitments} \label{sec:social-commitment-cha2}
The interoperability requirement in MASs has led to the introduction of various standardized agent communication languages (ACLs). The early proposals for defining the semantics of ACLs like KQML \cite{Finin1994} and FIPA ACL\footnote{See FIPA-ACL specifications (1997,1999,2001,2002), http://www.fipa.org/repository/aclspecs.php3} are developed using agent's mental states like beliefs, desires and intentions. These are now called mentalistic approaches because their focus are on the minds of the individuals participating in the interaction. A major weakness of these approaches is that they assume that \textit{agents can read each other minds} \cite{Singh1998}. Actually, in open environments where heterogeneous agents are made by different vendors and possibility using different technologies, it seems impossible to trust other agents completely or to make strong assumptions about their internal structure. This raises a serious verification problem for such approaches \cite{Singh2008,Wooldridge2009}. To overcome this drawback, some researchers took the initiative to think about other ways for defining ACLs  \cite{Singh1998}. As a result, social commitments have come to emergence. Social commitments are basically modeled as public information conveyed by an agent to another one. More specifically, a social commitment is an agreement between an agent, namely \emph{debtor}, to another agent, \emph{creditor}, in which the debtor engages towards the creditor to bring about a certain property \cite{Castelfranchi1995,Singh2005}.
%However, despite the fact that the term of \textit{social commitments} was constructed first by Castelfranchi in \cite{Castelfranchi1995}, the notion he introduced was not purely social because it is still analyzed in terms of the mental states of the partners.
In addition to being social, commitments are also public, and objective \cite{Colombetti2000}. These properties of social commitments help heterogeneous agents attribute the same meaning to the messages being exchanged so that the meaning is expressed using concepts that do not depend on an individual agent's internal structure. Importantly, a commitment between two agents is not just a static entity, but rather a dynamic one whose state changes over time as events occurs \cite{Akin2013,Torroni2009}. This dynamicity feature supports commitments' flexibility and can be captured through the manipulation of commitments via some operations such as \emph{creation}, \emph{fulfillment},
\emph{cancellation}, \emph{release}, \emph{assignment}, and
\emph{delegation} \cite{Singh1999}. In particular, a debtor may \emph{create} a commitment, thus activating it, or \emph{fulfill} a commitment, thus discharging it. However, for different reasons, a debtor might fail to fulfill its commitment; thus, it becomes violated. Given a commitment, its creditor can freely \emph{assign} it to another creditor, and its debtor may \emph{delegate} it to a another debtor. Furthermore, a debtor may \emph{cancel} a commitment; whereas, a creditor can \emph{release} the debtor from the commitment at any time.

%

%The notion of commitments as a foundation for understanding interactions among agents has been under development for about twenty years

Commitment-based approaches to ACLs have been around for about twenty years. Defining semantics of ACLs using the notion of social commitments has its roots back to the work of Singh \cite{Singh2000} in which he was the first to formalize a commitment-based ACL in temporal logic. Since then, social commitments have gained more and more popularity as a communication approach that makes no assumptions on the agents' internal states. To develop such approaches, various commitment logics that extend CTL (Computation Tree Logic), LTL (Lineal Temporal Logic), and CTL$^{*}$ (superset of CTL and LTL) have been introduced. Examples of efforts on this line can be found in
\cite{Bentahar2004,Giordano2007,Pham2007,Singh2000,Verdicchio2003}.
These logics have been successful in specification
and verification of systems from different areas such as
commitment-based protocols
\cite{Baldoni2010,El-Menshawy2010,Fornara2004b,Yolum2004},
modeling business processes \cite{Desai2009,Telang2009} and
agent-based web services \cite{Bentahar2008}.
However, the common limitation of theses proposals is that they neglect the uncertainty aspects of MASs and tend to assume typical behavior instead. In broad terms, uncertainty is a crucial aspect in MASs and has an impact not only on the behavior of the participating agents but also on the communication process that occur among these agents. %In Chapter \ref{cha:PCTLC}, we propose a new probabilistic logic whose primary purpose is to represent and reason about commitment-based agent communication in the presence of uncertainty.

In this thesis, we consider the notion of ``social commitments'' that is meant for communication. That is, the notion of commitments as a foundation for understanding interactions among agents. Therefore, we use communicative social commitments, also called illocutionary social commitments, as defined in \cite{Bentahar2012,El-Menshawy2013a}. Those commitments are formally denoted by $C_{i \to j} \varphi$, meaning that agent $i$, the debtor, commits to agent $j$, the creditor, to bring about $\varphi$, where $\varphi$ is the content of the commitment. Different notations with the same meaning can be found in \cite{Desai2009,Fornara2004a,Singh2000}.
This notion of ``social commitments'' should not be confused with some related notions such as ``Internal Commitments'', ``Norms'', and ``Obligations''. In traditional Artificial Intelligence (AI), a commitment was understood as the commitment of a single agent to some belief or to some course of action \cite{Levesque1990}. In this direction, ``internal commitment'' \cite{Castelfranchi1995,Singh2008} which refers to a commitment of an agent to itself has been widely used in the domain of AI. Norms, which are formal specifications of deontic statements that aim at regulating the interactions among agents, have also received a considerable attention in AI and MASs domains \cite{Balke2013,Singh2013,Testerink2013}. Obligations, on the other hand, have long been used as explicit mechanisms for influencing the behavior of interacting parties and providing some stability and reliability in their interactions \cite{Dignum2002}. Some researchers consider that commitments are somewhat like direct obligations \cite{Dignum1996,Singh2008}.

In contrast, the interesting feature that differentiates social commitments from the aforementioned notions is that a social commitment is directed from one party (the debtor) to another one (the creditor) which reflects the intuition that the debtor is committed to doing something for the creditor. These commitments are illocutionary in the sense that they are used as means of conveying information among interacting agents. Moreover, communicative commitments are equipped with a grounded semantics because the social accessibility relation has an intuitive and computational interpretation that makes its model checking possible.
%However, though Castelfranchi  tried to construct the notion of ``social commitment'', but it not purely social as it is yet analyzed in terms of the mental states of the partners \cite{Castelfranchi1995}. Another type of commitments introduced in AI before

\section{Reasoning about Knowledge} \label{sec:knowledge-cha2}

knowledge logics (also known as epistemic logics) are focused on reasoning about the knowledge that agents may have about themselves, the world, or other agents \cite{Fagin1995}. These logics have been shown to be a useful framework for the analysis of distributed algorithms and security protocols. Generally, an epistemic logic captures the essence of knowledge through modal operators. In this line, the contribution of Jaakko Hintikka in \cite{Hintikka1962} is recognized as the first attempt to investigate the logic of knowledge as a modal logic. Since then, researchers in AI and MASs have carried out numerous proposals to represent the evolution of knowledge \cite{Delgado2009,Fagin1995,Halpern2003,Huang2011,Lomuscio2007,Lomuscio2012,Meyer1995,Wan2013}. Formally, agent $i$ knows something is denoted by $K_i~\varphi$. From a verification perspective, model checking the logic of knowledge was first mooted by Halpern and Vardi \cite{Halpern1991}. Since that time theoretical aspects of model checking the logic of knowledge and its combinations with temporal logic have been studied. %Most existing solutions combine the logic of knowledge with LTL and/or CTL temporal logics.

In addition to reasoning about what one agent knows, it is often useful to be able to reason about the \textit{common knowledge}: the things that everyone knows, and that everyone knows that everyone knows, etc. Everyone knows can be defined as an abbreviation:

\noindent $E_G \varphi \equiv K_1 \varphi \wedge \dots K_n \varphi$, where $G$ is a group of agents, and $n$ is the number of agents in $G$.

\noindent The common knowledge operator $C_G$ is defined in terms of $E_G$ as follows:

\noindent $C_G \equiv E_G \varphi \wedge E_G^2 \varphi \wedge \dots \wedge E_G^k \wedge \dots $, where $E_G^k$ is read: ``everyone in $G$ knows $\varphi$ to degree k''.

\section{Modeling Techniques} \label{sec:system-models-cha2}
Transition Systems (TSs) are typically used as models to describe the behavior of systems \cite{Clarke1999}. They are the underlying models for all various non-real time models. TSs are modeled as directed graphs where nodes reflect the states, and edges represent the transitions. A state describes some information about the systems at a given moment of its behavior. Whereas, a transition describes how the systems can evolve from one state to another. A TS is a tuple $\mathbb{T} =(S, Act, \rightarrow, I, AP, \mathrm{L})$, where $S$ is a set of states, $Act$ is a set of actions, $\rightarrow\subseteq S\times Act \times S$ is the transition relation, $I\subseteq S$ is a set of initial states, $AP$ is a set of atomic propositions, and $\mathrm{L}: S \to 2^{AP}$ is a labeling function \cite{Baier2008}. %In Kripke structure \cite{Clarke1999}, $\mathrm{L}$ is introduced into TS to label states. However, in this section, we review some computational models that are used for modeling probabilistic systems.
In order to model random phenomena, transition systems are enriched with probabilities. This can be done in different ways. In the rest of this section, we review some probabilistic models that are used throughout our thesis.

\subsection{Interpreted Systems} \label{interpreted-systems-cha2}

The formalism of interpreted systems introduced by Fagin el al. \cite{Fagin1995} provides a useful framework to locally
model autonomous and heterogeneous agents who interoperate within
a global system via sending and receiving messages. This thesis builds on this formalism for various reasons:

\begin{itemize}
\item It is a suitable formalism for modelling agent-based systems as it provides a good level of abstraction that allows focusing more on modeling the key characteristics of the interacting agents along the evolution of their social commitments \cite{El-Menshawy2012}.
\item It has been successfully used to reason about various aspects of MASs such as time, knowledge, commitments, and correct behavior.
\item Interpreted systems are computationally grounded \cite{Wooldridge2000b}, meaning that the semantics of interpreted systems maps directly to the paths of the system, and vice-versa.
\item Interpreted systems can be easily extended. The original version introduced by Fagin et al. \cite{Fagin1995} has been extended in various ways as we will see below. This property of being readily extensible is important for us as we always need to extend it as required.
\end{itemize}

Suppose a set $\texttt{Agt}=\{1,\ldots,n\}$ of $n$
agents. At all times, each agent in the system is assumed to be in
some \textit{local} state, which intuitively records the complete
information that the agent can access at that time. Specifically,
each agent $i\in \texttt{Agt}$ is characterized by countable sets
$L_i$ and $Act_i$ of local states and actions respectively in
which the set $Act_i$ is mainly used to account for the temporal
evolution of the system. Also, local actions for each $i\in
\texttt{Agt}$ are performed in compliance with a local protocol
$\mathcal{P}_i: L_i\rightarrow 2^{Act_i}$, which assign a set
of enabled local actions to a local state. Intuitively, this set corresponds to the actions that are enabled in a given local state. Furthermore, the environment in which agents live may be modeled by means of a special agent $e$. Associated with $e$ are a set of local states
$L_e$, a set of actions $Act_e$, and a protocol $\mathcal{P}_e$. A
tuple $g = (l_1,\ldots, l_n,l_e) \in (L_1\times \ldots \times
L_n\times L_e)$ where $l_i\in L_i$ for each $i\in \texttt{Agt}$
and $l_e\in L_e$, is called a ``global state'' and represents the
instantaneous configuration of all agents in the system at a given
time (i.e., a snapshot of the global system at a specific time).

The local evolution function $\tau_i$ that determines the
transitions for an individual agent $i$ between its local states
is defined as follows:
%
\begin{equation}
\tau_i : L_i\times L_e\times Act_i \rightarrow L_i
\end{equation}
%
Similarly, the global evolution function of the system is defined as follows:
%
\begin{equation}
\tau : G\times ACT\rightarrow G
\end{equation}
%
where $ACT=Act_1 \times \ldots \times Act_n$ and each component
$a\in ACT$ is called a ``joint action'', which is a tuple of
actions (one for each agent), and $G = L_1\times \ldots\times
L_n\times L_e$ denotes a set of global states. The notation
$l_i(g)$ is used to represent the local state of agent $i$ in the
global state $g$. In addition, $I\in G$ is an initial global state
for the system. %For simplification, we remove the environment agent from the interpreted system formalism as done in \cite{Lomuscio2007}.

Bentahar et al. \cite{Bentahar2012} and El-Menshawy et al. \cite{El-Menshawy2013a} extended Fagin et al.'s formalism of interpreted systems with shared and unshared variables in order to account for communication that occurs during the execution of MASs and to provide an intuitive semantics for social commitments that are established through communication between interacting agents. They specifically associated with each agent $i\in \texttt{Agt}$ a countable set $Var_i$ of local
variables. Then, they used those variables to represent
communication channels through which messages are sent and
received. Technically, they denoted the value of a variable $x$ in
the set $Var_i$ at local state $l_i(g)$ by $l^{x}_i(g)$. Thus,
%
\begin{equation}
\textrm{if}~ l_i(g)=l_i(g'),~\textrm{then}~ l^{x}_i(g)
=l^{x}_i(g')~ \textrm{for~all}~ x \in Var_i
\end{equation}
%
The idea is that, for two agents $i$ and $j$ to communicate, they
should share a communication channel, which is represented by
shared variables between $i$ and $j$. In this perspective, a
communication channel between $i$ and $j$ does exist iff $Var_i
\cap Var_j \neq\emptyset$. For a variable $x \in Var_i \cap
Var_j$, $l^{x}_i(g)=l^{x}_j(g')$ means the values of $x$ in
$l_i(g)$ for agent $i$ and in $l_j(g')$ for agent $j$ are the same. This
intuitively represents the existence of a communication channel
between $i$ (in $g$) and $j$ (in $g'$) through which the variable
$x$ has been sent by one of the two agents to the other, and as a
consequence of this communication, $i$ and $j$ will have the same
value for this variable. The key point is that shared variables
are only used to motivate the existence of communication channels,
not the establishment of communication. Figure \ref{fig:social accessibility-cha2} depicts the idea of using shared and unshared variables for establishing communication channels between interacting agents.
The three conditions upon which a communication channel between $i$ and $j$ exists are listed below:

For each pair $(i,j) \in \texttt{Agt}^2$, $\sim_{i\rightarrow j} \subseteq S \times S$ is a social accessibility relation. $s \sim_{i\rightarrow j} s'$ is defined by the following conditions:
      %
  \begin{enumerate}
       \item $l_i(s)=l_i(s')$.
       \item $Var_i \cap Var_j \neq \emptyset$ such that $\forall x \in Var_i \cap Var_j$ we have $l^{x}_i(s)\!=\!l^{x}_j(s')$.
       \item $\forall y \in Var_j\!-\! Var_i$ we have $l^{y}_j(s)\!=\!l^{y}_j(s')$.
  \end{enumerate}

    %\begin{figure}[t]
    \begin{figure}[!ht]
                \begin{center}
                \includegraphics[width=12cm, %height=7cm]{chap2/img/social-accessibility-cha2.eps}
                height=7cm]{chap2/img/social-accessibility1.eps}
                \end{center}
                \caption{Social accessibility relations as defined in \cite{Bentahar2012,El-Menshawy2013a}}
                \label{fig:social accessibility-cha2}
    \end{figure}

Recently, Al-Saqqar et al. \cite{Al-Saqqar2014a} have modified the definition of social accessibility relations given in \cite{Bentahar2012,El-Menshawy2013a} in such a way that the new definition does no longer depend on the unshared variables but rather depends merely on the shared variables between the interacting agents as shown in Figure \ref{fig:modified social accessibility-cha2}. The new condition upon which a communication channel is established is stated below:

 $ s \approx_{i \rightarrow j} s' $ iff $ Var_i \cap Var_j \neq \emptyset $ such that $ \forall x \in Var_i \cap Var_j $ we have $ l_i^x(s) =
l_i^x(s') = l_j^x(s')$, where $\approx_{i\rightarrow j} \subseteq S \times S$ is the new social accessibility relation \cite{Al-Saqqar2014a}.

%\begin{figure}[t]
    \begin{figure}[!ht]
                \begin{center}
                \includegraphics[width=12cm, height=7cm]{chap2/img/social-accessibility2.eps}
                \end{center}
                \caption{The modified version of social accessibility relations as in \cite{Al-Saqqar2014a}}
                \label{fig:modified social accessibility-cha2}
    \end{figure}

The original version of interpreted systems formalism was also extended by Halpern et al. \cite{Halpern2003} and further by Wan et al. \cite{Wan2013} to model the stochastic behavior of MASs. Accordingly, the local evolution function is defined as follows:
%
\begin{equation}
\tau_i: L_i \times Act_i \times L_i \rightarrow[0,1]
\end{equation}
%
such that for all $l_i \in L_i$, we have $\sum_{l'_i\in L_i}
\tau_i(l_i,a^{l_i\rightarrow l'_i},l_i')=1$ wherein
$a^{l_i\rightarrow l'_i}$ is the local action labeling a
transition between local states $l_i$ and $l'_i$ of agent $i$.

Moreover, the global evolution function is defined as follows:
%
\begin{equation}
\tau: G \times ACT \times G \rightarrow[0,1]
\end{equation}
%
%This function satisfies Markovian properties in the sense that
The sum of the probabilities over all possible transitions from a given state $g$ must be $1$: for all $g \in G$, $\sum_{\substack{g'\in G}}
\tau(g,a^{g\rightarrow g'},g')=1$ where $a^{g\rightarrow g'}$ is
the action labeling the transition between the two global states
$g$ and $g'$ of the system.

Such a modified version of the interpreted systems formalism is
called \textit{probabilistic interpreted systems}
\cite{Halpern2003}. In the formalism of probabilistic interpreted
systems, the transition probability matrix can be computed by
\cite{Wan2013}:

\begin{equation}\label{global-evo-fun}
\tau(g,a^{g\rightarrow g'},g')= {\prod_{\substack{i \in
\texttt{Agt}}} \tau_i(l_i(g), a^{l_i(g) \rightarrow
l_i(g')},l_i(g'))}
\end{equation}

\subsection{Discrete Time Markov Chains (DTMCs)} \label{sec:DTMC-cha2}

DTMCs are commonly used as models for probabilistic systems. A DTMC is a transition system that defines the probability of moving from one state to another.
\begin{definition}[DTMC]\label{def:DTMC}
Given a set of atomic propositions $AP$, a DTMC can be defined as a 4-tuple
$\mathbf{D}$ = $(S,\overline{s},\mathbf{P},L)$ where:

\begin{itemize}
  \item  $S$ is a nonempty and finite set of states;
  \item  $\overline{s}$ is the initial state;
  \item  $\mathbf{P} :  S\times S\rightarrow[0,1]$ is the transition
  probability matrix, such that for every state $s\in{S}$, we have
  $ \sum_{s' \in{S}} \mathbf{P}(s,s' )=1$;
  \item  $L : S\rightarrow 2^{AP}$  is a labelling function which assigns to each state $s \in S$ the set $L(s)$ of atomic propositions that are valid in the state.
\end{itemize}
\end{definition}

DTMCs are stochastic models of systems that change their states at discrete-times $(n=0,1,2,\dots)$ and have the following property: if the system enters state $s$ at time $n$, it stays there for exactly one unit of time and then jumps to state $s'$ at time $n+1$ with probability $\mathbf{P}(s, s')$, regardless of its history up to and including time $n-1$ \cite{Kulkarni1995}. The definition shows that states are labelled with atomic propositions which indicate the status of the system (e. g., waiting, sending). The system can change its states according to a probability distribution given by the transition probability matrix $\mathbf{P}$. Each element $\mathbf{P} (s,s')$ of the transition probability matrix gives the probability of making a transition from state $s$ to state $s'$. A transition from state $s$ to $s'$ can only take place if $\mathbf{P}(s, s') > 0$. However, if $\mathbf{P}(s, s') = 0$, no such transition is possible. Again, the probabilities from a given state must sum up to 1, i.e. $\sum_{s' \in{S}} \mathbf{P}(s,s' )=1$.

\subsection{Markov Decision Processes (MDPs)} \label{sec:MDP-cha2}
MDPs can be seen as transition systems in which in any state a nondeterministic choice between probability distributions exists.

\begin{definition}[MDP]\label{def:MDP}

Given a set of atomic propositions $AP$, an MDP model $\mathbf{M}$ can be defined as a 5-tuple, $\mathbf{M}$ = $(\mathbb{S}, AC, \textsf{P}_t ,I_i, L)$, where:

\begin{itemize}

  \item  $\mathbb{S}$ is a nonempty and finite set of states.

  \item  $\textsf{P}_t:  \mathbb{S}\times AC\times \mathbb{S}\rightarrow[0,1]$ is the transition probability function, such that for every state $s\in{\mathbb{S}}$ and action $\theta \in AC$, we have $\sum_{s' \in{\mathbb{S}}} \textsf{P}_t(s,\theta ,s') \in \{0,1\}$.

  \item  $AC $ is a set of actions. At state $s \in \mathbb{S}$, the action $\theta$ is enabled iff $\sum_{s' \in{\mathbb{S}}} \textsf{P}_t(s,\theta ,s')=1$.

  \item  $I_i$ is an initial state.

  \item  $L : \mathbb{S}\rightarrow 2^{AP}$  is a state labeling function.
\end{itemize}
\end{definition}

MDPs possess the Markov property, which requires that any information necessary to predict the effects of all events is captured in the state. In other words, the effects of an event in a state depend only on that state and not on the prior history. However, the major difference between MDPs and DTMCs is the choice of actions. While a DTMC describes the state transitions of a stochastic system, it does not capture the fact that the agent can choose an appropriate course of action in order to change the system's state. However, for an MDP, at every state one or more actions are available, and each action is associated with a probability distribution over the successor states. That is, MDPs are not augmented with a unique
probability measure. Reasoning about probabilities of sets of
paths of an MDP relies on the resolution of the nondeterminism. In
order to define the semantics of such an MDP, the notion of \textit{adversary} is used. An adversary (also referred to as scheduler, policy, or strategy \cite{Baier2008,Vardi1985}) is an entity that resolves the nondeterministic choices in MDPs. Being in a state of the system, an adversary determines the next step to be taken. %Hence, the adversary is used the notion of adversary to factor out the nondeterminism and consider the probability of some behavior of the MDP \cite{Forejt2011}.
Informally, at each step, the adversary picks an action, and then the next
state is picked according to the probability distribution
associated with the action. In our work, we focus on a special
class of adversaries called \emph{Memoryless Adversary} \cite{Forejt2011} where the choice of action depends only on the state and independent of what has happened in the history. An adversary is said to be memoryless if it always selects the same action in a given state. The induced adversaries are basically DTMC models.

A partially observable Markov decision process (POMDP) is a variant of MDPs. Actually, a POMDP is an MDP in which the agent is unable to observe the current state. Instead, the agent must maintain a probability distribution over the set of possible states, based on a set of observations and observation probabilities, and the underlying MDP. A POMDP model \cite{Kaelbling98} can be described as a tuple $(\mathrm{S},\mathbb{A},\mathrm{T},\mathbf{R},\Omega,\mathrm{O})$, where:

\begin{itemize}

  \item $\mathrm{S}$, $\mathbb{A}$, $\mathrm{T}$, and $\mathbf{R}$ describe an MDP;
  \item $\Omega$ is a finite set of observations that the agent can experience of its world; and
  \item $\mathrm{O}: \mathrm{S} \times \mathbb{A}\to \prod(\Omega)$ is the observation function, which gives, for each action and resulting state, a probability distribution over possible observations.

\end{itemize}

\section{System Specification} \label{sec:sys-spec-cha2}
In this section, we describe some logics for specifying requirements of transition-based systems. The discussed logics use atomic propositions and connective operators to describe systems properties in states.

\subsection{Temporal Logics}
Temporal logic is a modal logic with modal operators to describe the temporal order of occurrence of events. The two commonly used temporal logics are Linear Temporal Logic (LTL) \cite{Pnueli1977} and Computation Tree Logic (CTL) \cite{Emerson1990}. They differ from each other based on the way the notion of time is handled. LTL describes temporal relations on one execution path; whereas, in CTL it is possible to quantify over the paths with respect to a given state. Below, we review the two logics and then review a probabilistic extension of CTL called PCTL \cite{Hansson1994}.

\noindent \textbf{a. LTL (Linear Temporal Logic)}

In LTL, time is considered to be a linear sequence. Each moment in time has a unique possible future. Thus, temporal operators are provided for describing events along a single time line. The syntax of LTL is defined by the following BNF grammar \cite{Baier2008}:
%
\begin{align*}
    \varphi & ::= true ~|~p~|~\neg \varphi~|~\varphi \wedge \varphi~|~ \bigcirc \varphi ~ | ~ \varphi ~U~ \varphi~|
\end{align*}

\noindent where: $p\in AP$ is an atomic proposition. $\bigcirc$ and $\mathrm{U}$ stand for ``next time'' and ``until'' respectively. The formula $\bigcirc \varphi$  holds at the current state if $\varphi$ holds in the next state. The formula $\varphi U \psi$ holds at the current state, if there is some future moment for which $\psi$ holds and $\varphi$ holds at all moments until that future moment. $\lozenge \varphi$, which stands for eventually $\varphi$ holds, can be derived using the $\mathrm{U}$ operator as follows: $\lozenge \varphi \equiv \mathrm{true}~ \mathrm{U}~ \varphi$. Also, the $\square \varphi$, which stands for ``always $\varphi$, or  globally $\varphi$'', can be derived as follows: $\square \varphi \equiv \neg\lozenge~ \neg\varphi$. The Boolean connectives $\neg$ and $\vee$ are defined in the usual way.

\noindent \textbf{Semantics of LTL.} Formulae of LTL stand for properties of paths. Therefore, a path can either satisfy an LTL-formula or not. Let $\mathbb{T} =(S, Act, \rightarrow, I, AP, \mathrm{L})$ be a transition system where $S$ is a nonempty set of states, $Act$ is a set of actions, $\rightarrow\subseteq S\times Act \times S$ is the transition relation, $I\subseteq S$ is a set of initial states, $AP$ is a set of atomic propositions, and $\mathrm{L}: S \to 2^{AP}$ is a labeling function. Given $s,s' \in S$, $(s,s') \in \rightarrow$ means that $s'$ is an immediate successor of $s$. A path $\pi$ in $\mathbb{T}$ is an infinite sequence of states $\pi=(s_0,s_1,\dots)$ such that $(s_i,s_{i+1})\in \rightarrow$ for all $i\geq 0$. $\pi(i)$ is the $(i+1)$-th state in $\pi$, and $\pi_i = \pi(i), \pi(i+1), \dots$ is the suffix of $\pi$ starting at $\pi(i)$. The satisfaction of an LTL-formula $\varphi$ with respect to the path $\pi$ in the transition system $\mathbb{T}$ is denoted by $(\mathbb{T},\pi) \models \varphi$, which is inductively defined as follows:

\noindent $-~(\mathbb{T},\pi) \models p ~~~~~~~~~~~~~\emph{iff}~~~ p\in \mathrm{L}(\pi(0)),$\\
$-~(\mathbb{T},\pi) \models \neg \varphi ~~~~~~~~~~\emph{iff}~~~ (\mathbb{T},\pi)\nvDash \varphi,$\\
$-~(\mathbb{T},\pi) \models \varphi_1 \wedge \varphi_2 ~~~~\emph{iff}~~~(\mathbb{T},\pi)\models \varphi_1~\textrm{and}~(\mathbb{T},\pi) \models \varphi_2,$ \\
$-~(\mathbb{T},\pi) \models \bigcirc\varphi ~~~~~~~~~\emph{iff}~~~ (\mathbb{T},\pi(1)) \models \varphi,$\\
$-~(\mathbb{T},\pi) \models (\varphi_1~U~\varphi_2)~~\emph{iff}~~\exists~ k \geq 0~~\textrm{such that}~~ (\mathbb{T},\pi(k)) \models \varphi_2 ~\textrm{and}~\forall~ 0\leq i < k, (\mathbb{T},\pi(i)) \models \varphi_1$.

\noindent An LTL-formula $\varphi$ holds at state $s$ in the model $\mathbb{T}$, written $(\mathbb{T},s) \models \varphi$, iff all paths starting from $s$ satisfy $\varphi$. Moreover, the model $\mathbb{T}$ satisfies $\varphi$ iff $\varphi$ holds in all paths emanating from an initial state. We say that $\varphi$ is valid in $\mathbb{T}$, written $\models \varphi$ when for all $s\in S$, we have $(\mathbb{T},s)\models \varphi$.

\noindent \textbf{b. CTL (Computation Tree Logic)}

In contrast to LTL, CTL advocates a tree-like structure time, allowing some instants to have more than a single successor. Thus, it distinguishes between state formulae and path formulae. The syntax of CTL is given by the following BNF grammar \cite{Baier2008}:
%
\begin{align*}
    \varphi & ::= true ~|~p~|~\neg \varphi~|~\varphi \wedge \varphi~|~\mathrm{E}\psi~|~\mathrm{A} \psi\\
    \psi & ::=\bigcirc \varphi ~ | ~ \varphi ~U~ \varphi~|
\end{align*}

\noindent Intuitively, state formulae express a property of a state, while a path formulae express a property of a computation path where a computation path is an infinite sequence of states. $\bigcirc$ and $\mathrm{U}$ are defined as in LTL. Notice that, in CTL, a path quantifier (either $\mathrm{A}$ which stands for \textit{all paths}, or $\mathrm{E}$ which stands for \textit{some path}) is immediately followed by a single one of the usual linear
temporal operators $\Box$, $\lozenge$, $\bigcirc$, or $\mathrm{U}$ in order to construct a well formed state formula.

\noindent \textbf{Semantics of CTL.} The semantics of CTL is given via the satisfaction relation ``$\models$''. Given a transition system $\mathbb{T} =(S, Act, \rightarrow, I, AP, \mathrm{L})$, where $S$ is a nonempty set of states, $Act$ is a set of actions, $\rightarrow\subseteq S\times Act \times S$ is the transition relation, $I\subseteq S$ is a set of initial states, $AP$ is a set of atomic propositions, and $\mathrm{L}: S \to 2^{AP}$ is a labeling function. A path $\pi$ in $\mathbb{T}$ is also an infinite sequence of states $\pi=(s_0,s_1,\dots)$ such that $(s_i,s_{i+1})\in \rightarrow$ for all $i\geq 0$. $\pi(i)$ is the $(i+1)$-th state in $\pi$, and $\pi_i = \pi(i), \pi(i+1), \dots$ is the suffix of $\pi$ starting at $\pi(i)$. The set of paths starting at state $s$ is denoted by $\Pi(s)$. The satisfaction relation $(\mathbb{T},s)\models \varphi$, which means that the formula $\varphi$ holds at the state $s$ in the model $\mathbb{T}$, is defined inductively as follows:

\noindent $-~(\mathbb{T},s) \models p ~~~~~~~~~~~~~~\emph{iff}~~~ p\in \mathrm{L}(s),$\\
$-~(\mathbb{T},s) \models \neg \varphi ~~~~~~~~~~~\emph{iff}~~~ (\mathbb{T},s)\nvDash \varphi,$\\
$-~(\mathbb{T},s) \models \varphi_1 \wedge \varphi_2 ~~~~~\emph{iff}~~~(\mathbb{T},s)\models \varphi_1~\textrm{and}~(\mathbb{T},s) \models \varphi_2,$ \\
$-~(\mathbb{T},s) \models \exists \psi ~~~~~~~~~~~\emph{iff}~~~ (\mathbb{T},\pi) \models \psi ~\textrm{for~some}~ \pi \in \Pi(s),$\\
$-~(\mathbb{T},s) \models \forall \psi ~~~~~~~~~~~\emph{iff}~~~ (\mathbb{T},\pi) \models \psi ~\textrm{for~all}~ \pi \in \Pi(s).$

\noindent Like LTL, the satisfaction relation $\models$ for path formulae is defined by:

\noindent $-~(\mathbb{T},\pi) \models \bigcirc\varphi ~~~~~~~~~~\emph{iff}~~~ (\mathbb{T},\pi(1)) \models \varphi,$\\
$-~(\mathbb{T},\pi) \models (\varphi_1~U~\varphi_2)~~\emph{iff}~~\exists~ k \geq 0~~\textrm{such that}~~ (\mathbb{T},\pi(k)) \models \varphi_2 ~\textrm{and}~\forall~ 0\leq i < k, (\mathbb{T},\pi(i)) \models \varphi_1$.

\noindent State formula $\exists \psi$ is valid in state $s$ if and only if there exists some path starting in $s$ that satisfies $\psi$. In contrast, state formula $\forall \psi$ is valid in state $s$ if and only if all paths starting in $s$ satisfy $\psi$.

\noindent \textbf{c. PCTL (Probabilistic Computation Tree Logic)}

PCTL \cite{Hansson1994} is an extension of CTL with a probability operator. It is used to express properties of probabilistic systems. The syntax of PCTL is defined by the following BNF grammar \cite{Baier2008}:
%
\begin{align*}
    \varphi & ::= true ~|~p~|~\neg \varphi~|~\varphi \wedge \varphi~|~ \mathbb{P}_{\bowtie k} (\psi)~\\
    \psi & ::=\bigcirc \varphi ~ | ~ \varphi ~U~ \varphi~|~ \varphi~ U^{\leq m} ~ \varphi
\end{align*}

\noindent where: $p\in AP$ is an atomic proposition and $\mathbb{P}_{\bowtie k}$ is a probabilistic operator. $\bowtie \in\{<,\leq,>,\ge\}$. $k\in [0,1]$ is a probability bound or threshold. $m \in\mathbb{N}^+ $ is a positive integer number reflecting the maximum number of transitions needed to reach a certain state. $\varphi$ and $\psi$ are state and path formulae respectively. $\bigcirc, U$ and $U^{\leq m}$ stand for ``next time'',
``until'' and ``bounded until'' path modal connectives respectively.

\noindent \textbf{Semantics of PCTL.} Given a probabilistic model such as a Markov chain $\textbf{M} =(S,\verb"P",I,AP,L)$ where $S$ is a finite set of states, \verb"P" is the transition probability matrix, $I\subseteq S$ is a set of initial states, $AP$ is a set of atomic propositions, and $\mathrm{L}: S \to 2^{AP}$ is a labeling function. Let $\varphi$ and $\psi$ be PCTL state and path formulae respectively. The satisfaction relation $\models$ is defined for a PCTL state formula $\varphi$ inductively as follows:

\noindent $-~(\textbf{M},s) \models p ~~~~~~~~~~~~~~\emph{iff}~~~ p\in \mathrm{L}(s),$\\
$-~(\textbf{M},s) \models \neg \varphi ~~~~~~~~~~~\emph{iff}~~~ (\textbf{M},s)\nvDash \varphi,$\\
$-~(\textbf{M},s) \models \varphi_1 \wedge \varphi_2 ~~~~~\emph{iff}~~~(\textbf{M},s)\models \varphi_1~\textrm{and}~(\textbf{M},s) \models \varphi_2,$ \\
$-~(\textbf{M},s \models \mathbb{P}_{\bowtie k} (\psi)~~~~~~\emph{iff}~~Prob_s(\psi)\bowtie k, \textrm{where:}~Prob_s(\psi)=Prob_s\{\pi \in \Pi(s)~|~\pi\models
\psi\}.$

\noindent For a path $\pi \in \textbf{M}$, the satisfaction relation is defined as follows:

\noindent $-~(\textbf{M},\pi) \models \bigcirc \varphi~~~~~~~~~~~~~\emph{iff}~~(\textbf{M},\pi(1)) \models \varphi,$ \\
$-~(\textbf{M},\pi) \models \varphi_1~U^{\leq  m}~\varphi_2~~~\emph{iff}~~\exists~ k \leq m~~\textrm{s.t.}~~ \pi(k) \models \varphi_2 ~\textrm{and}~\forall i < k, (\textbf{M},\pi(i)) \models \varphi_1,$\\
$-~(\textbf{M},\pi) \models \varphi_1 ~U~\varphi_2~~~~~~~~\emph{iff}~~\exists~ m \geq 0~~\textrm{s.t.}~~(\textbf{M},\pi) \models \varphi_1~U^{\leq m}~\varphi_2.$\\

\noindent \textbf{Combining Logics}

Logic combination is emerging as a relevant research topic in many disciplines. Multi-modal logics can be constructed by combining existing logics in several ways \cite{Gabbay2003}. In this thesis, we advocate the independent join (or fusion) technique \cite{Franceschet2004}. The problem of combining logics based on the independent join technique is as follows. Given two logics $\mathbf{A}$ and $\mathbf{B}$, how do we
combine them into one logic which extends the expressive power of each one?

The combination of two logics using this technique is denoted by $\mathbf{A} \oplus \mathbf{B}$.
Given two logics $\mathbf{A}$ and $\mathbf{B}$, their languages
$\mathcal{L}_\mathbf{A}$ and $\mathcal{L}_\mathbf{B}$, and their corresponding axiomatic systems $\mathcal{H}_\mathbf{A}$ and $\mathcal{H}_\mathbf{B}$, the logic $\mathbf{A} \oplus \mathbf{B}$ is the smallest logic with the following properties:

\begin{itemize}
\item The language of the combined logic is the union of $\mathcal{L}_\mathbf{A}$ and $\mathcal{L}_\mathbf{B}$.
\item The resultant logic from the combination is axiomatised by the set of axioms $\mathcal{H}_\mathbf{A} \cup \mathcal{H}_\mathbf{B}$ which means that no ``interaction'' axiom is needed, i.e., axioms involving mixed operators are not necessarily required.

\end{itemize}

If $\mathcal{L}_\mathbf{A}$ and $\mathcal{L}_\mathbf{B}$ are interpreted in Kripke frames $\mathrm{F}_1 = (W,R_{11}, \dots ,R_{1n})$ and $\mathrm{F}_2 = (W,R_{21}, \dots ,R_{2m})$ , the semantics of the combined logic $\mathbf{A} \oplus \mathbf{B}$  can be interpreted over the Kripke frame $\mathrm{F} = (W,R_{11}, \dots ,R_{1n},R_{21}, \dots, R_{2m})$ obtained by the ``fusion'' of the two frames $\mathrm{F}_1$ and $\mathrm{F}_2$.
Using this technique ensures the preservation of important properties (such as soundness, completeness, and decidability, etc.) of the logics being combined as they are defined in the literature \cite{Konur2013}.

\section{Model Checking} \label{sec:Model-Checking-cha2}

Verification is one of the important aspects of ACLs. Generally, for ACL standards to gain acceptance, it must be possible to determine whether or not any agent-based system that claims to conform to an ACL standard actually does so. An ACL is said to be verifiable if it enjoys this property \cite{Wooldridge1998,Wooldridge2000}. In this section, we review a verification technique, namely model checking, that is utilized in this research to verify our proposed logics.

%Model checking is most widely understood as a technique for automatically verifying that finite state systems satisfy formal specifications.

Model checking is a formal, automatic technique to verify whether
or not system design models satisfy given requirements \cite{Bordini2006,Clarke1999}. In other words, it is the problem of establishing whether or not a given formula $\varphi$ is true
in a given model $M$. Its value lies in its ability to verify various aspects (such as time, knowledge, commitments, etc) of target systems \cite{Konur2013}. Typically, a model checking process involves three phases:

\begin{enumerate}
\item \textbf{Modeling:} To convert a design into a formalism so that mathematical computation and logical deduction can be performed.
\item \textbf{Specification:} To specify the properties that the model must satisfy.
\item \textbf{Verification:} To verify whether the model holds the specification.
\end{enumerate}

Despite its success in verifying hardware and software systems from different domains, model checking is generally a resource-intensive process that requires a large amount of memory and processing time. This is essentially due to the fact that the systems' state space may grow exponentially with the number of variables combined with the presence of concurrent behaviors, which may hinder the verification process. This phenomenon is known as the \textit{state explosion problem}. To alleviate  this problem, several techniques have been explored in the literature \cite{Baier2008}. Binary Decision Diagrams BDD, Partial Ordered Reduction, Compositional Reasoning, Symmetry and Induction are some well-known approaches. However, one of the most promising solutions aim at optimizing model checking algorithms by introducing symbolic data structures based on binary decision diagrams (BDDs) \cite{Clarke1999,McMillan1992}. Moreover, an ordered BDD (OBDD) is one which has an ordering for some list of variables. Model checking using BDDs is called \textit{symbolic model checking}. It emphasizes that sets of states are represented symbolically. It is more efficient than using merely individual states. The idea is to represent states and set of states as Boolean Formulae which, in turn, can be readily encoded as BDDs. To elaborate, let $Sat(\varphi)= \{s \in S ~|~ M,s\models\varphi)$ be a set of states satisfying $\varphi$. Given a CTL formula $\varphi$ and a CTL model $M = (S,R_t, V, I)$, the idea is to compute the set $Sat(\varphi)$ of states satisfying $\varphi$ in $M$, which is represented in BDDs, and then compare it against the set of initial states $I$ in $M$ that is also represented in BDD. If I $\subseteq~ Sat(\varphi)$, then the model $M$ satisfies the formula $\varphi$; otherwise, a counter-example is generated to show the path in which the model does not satisfy the formula. This type of model checking when the result is given as ``Yes'' or ``No'' (i. e. whether or not the property is satisfied) is called qualitative or non-probabilistic model checking. An overview of this type of model checking is given in Figure \ref{fig:model-checking-cha2}.

\begin{figure}[t]
                \begin{center}
                \includegraphics[width=12cm, height=7cm]{chap2/img/modelchecking1.eps}
                \end{center}
                \caption{Qualitative model checking overview}
                \label{fig:model-checking-cha2}
                \end{figure}

\subsection{Probabilistic Model Checking} \label{sec:pro-Model-Checking-cha2}

In addition to qualitative model checking, quantitative (or probabilistic) model checking techniques based on probabilistic model checkers have recently gained popularity \cite{Baier2008}. Probabilistic model checking is an automatic formal verification technique for the analysis of systems exhibiting stochastic behavior \cite{Hinton2006}. It offers the capability for interpreting the satisfiability of a given property in terms of quantitative results. In fact, the probabilistic model checking technique is similar to conventional model checking as discussed earlier. The major difference is that a probabilistic model contains additional information on the likelihood of transitions between states, or to be more specific, it can model probabilistic behavior. An overview of the probabilistic model checking procedure is given in Figure \ref{fig:prob-model-checking-cha2}. It shows that a probabilistic model checker takes as input a property and a model and delivers the result ``Yes'' or ``No'', or some probability.

\begin{figure}[t]
                \begin{center}
                \includegraphics[width=12cm, height=7cm]{chap2/img/modelchecking2.eps}
                \end{center}
                \caption{Probabilistic model checking overview}
                \label{fig:prob-model-checking-cha2}
                \end{figure}

\subsection{Model Checking Tools}
There have been various model checking tools (also known as Model Checkers) in the literature. In this section, we review some of the most widely used model checkers.
\begin{itemize}

\item \textbf{MCMAS}\\
    MCMAS (Model Checker for Multi-Agent Systems) \cite{Lomuscio2006} is an OBDD-based symbolic model checker developed for the purpose of verifying epistemic properties of multi-agent systems. It supports branching-time temporal logic CTL. It also supports interpreted systems as an underling formalism for modeling target systems. The dedicated programming language used for describing a MAS in MCMAS is called ISPL (Interpreted Systems Programming Language). MCMAS was originally designed to handle the logic of knowledge CTLK and the branching-time temporal logic CTL. Recently, it has been extended by implementing some new algorithms that allow it to accept commitment formulae and hence to verify social commitments. The new extended version is called MCMASC (MCMAS for commitments). \cite{El-Menshawy2012}.

\item \textbf{NuSMV}\\
    NuSMV \cite{Cimatti2002}, an extension version of SMV \cite{McMillan1992}, is a well-known and widely trusted model checker. It is written in ANSI C language. As an input language, NuSMV accepts files written in SMV language. While the SMV tool was originally developed to implement the OBDD-based symbolic model checking for CTL, NuSMV implements also bounded model checking techniques for LTL -- in addition to the symbolic model checking techniques for CTL. This feature distinguishes it the most from SMV. Nevertheless, both SMV and NuSMV allow for a compact description of systems under consideration using modules, which may be composed to describe the evolution of states.

\item \textbf{SPIN}\\
    The SPIN \cite{Holzmann1997} model checker is one of the most used tools for tracing software defects in concurrent system designs. It was introduced in the 1980s at Bell Labs. Later, it has been made available to the public. The original version of SPIN has been continually under development and improvement. SPIN's programming language is called PROMELA. \cite{Holzmann2003} details the theoretical foundations of SPIN and presents the user manual. The main characteristics of SPIN are:

    $\diamond$ It is designed for the temporal logic LTL.\\
    $\diamond$ It is an automata-based model checker.\\
    $\diamond$ It implements various optimization strategies, including on-the-fly model checking and partial order reduction.

\item \textbf{PRISM} \\
    PRISM \cite{Kwiatkowska2002} stands for Probabilistic Symbolic Model Checker. It is the leading tool in the area of probabilistic model checking. The tool is widely used for checking probabilistic specifications over probabilistic models. The specifications can be expressed either in PCTL or in Continuous Stochastic Logic (CSL) \cite{Baier2008,Forejt2011}. Systems models can be described using the PRISM language as Discrete-Time Markov Chains (DTMCs), Continuous-Time Markov Chains (CTMCs), or Markov Decision Processes (MDPs). PRISM has been successfully used to analyse systems with a wide range of application domains, including communication and multimedia protocols, randomised distributed algorithms, security protocols, and many others.
    PRISM is the most appropriate tool for our work thanks to its capability of verifying probabilistic properties, and accepting formulae written in PCTL. Using PRISM, it is possible to either determine if a probability satisfies a given bound or obtain the actual value.

\item \textbf{MCK} \\
    MCK (stands for Model Checking Knowledge) is a model checker for the logic of knowledge, developed at the School of Computer Science and Engineering at the University of New South Wales \cite{Gammie2004}. It is implemented using OBDD-based symbolic algorithms. In the epistemic dimension, agents may use their observations in a variety of ways to determine what they know: observation alone, observation and clock, and perfect recall of all observations. The former way (observation alone) is to evaluate an agent's knowledge based merely on its current observation. The second way (observation and clock) is to compute an agent's knowledge based both on its current observation and the current clock value. The latter way (perfect recall of all observations) is to compute an agent's knowledge based on the complete record of all its observations.

    In the temporal dimension, specification formulae may use either linear time temporal logic (LTL), or the branching-time logic (CTL).
    Recently, MCK was extended by Huang et al. \cite{Huang2011} to permit the verification of knowledge in the presence of probabilistic behavior.

\end{itemize}

\section{Summary}\label{sec:summary-chap2}
In this chapter, we introduced the background and concepts needed for the rest of my thesis. As social commitments are the main focus of this research, it is important, again, to emphasis that the notion of ``social commitments'' we consider in this thesis is the communicative social commitments that are public and observable. In the next chapter, we propose a new probabilistic approach for handling social commitments in the presence of uncertainty.

### 2015-04-05 thesis/others/khalid/chap5/chap5.tex
added thesis

\chapter{On Probabilistic Group Social Commitments}\label{cha:PCTLKC+}

In this chapter\footnote{Part of the results presented in this chapter, namely PCTL$^{\textrm{kc+}}$ logic, has been published in SoMet\_14 \cite{Sultan2014c}. The results of model checking PCTL$^{\textrm{kc+}}$ have been sumbitted to the Engineering Applications of Artificial Intelligence journal \cite{Sultan2014d}}, we improve and extend the work presented in Chapter \ref{cha:PCTLKC} by refining the probabilistic logic of knowledge and commitment (PCTL$^{kc}$) and then extending the refined logic further by operators for group knowledge and group commitment. In this respect, we define a semantics for the group social commitment operator and integrate it into the resulting logic. The developed logic is called the new probabilistic logic of knowledge and commitment (PCTL$^{\textrm{kc+}}$). Finally, we introduce a new formal verification technique that considers the new group modalities and implement it on top of the PRISM model checker.

\section{Introduction} \label{Introduction}

One of the major challenges in building complex software products
such as Multi-Agent Systems (MASs) is to advance error detection
at early stages of their life-cycles. %The social context of interacting agents in MASs has gained significance recently.
MASs community has witnessed an important shift in defining the semantics of ACLs from the so-called mental approaches that is hard to verify \cite{Singh2000} to social approaches which exploit observable and verifiable social commitments. However, the increasing demand to use social commitments as a means of communication among interacting parties \cite{Baldoni2014,Chesani2013,Akin2013} requires reasoning about and verifying the relationship between social commitments and some other systems' aspects such as agents' knowledge and uncertainty especially in the case of having group-commitment scenarios. In addition to verifying the interactions between social commitments and knowledge in the presence of uncertainty, the ultimate objective of this chapter is to verify the interactions between the two elements when the scope of interacting agents goes beyond the common agent-to-agent (i.e., one-to-one) scheme.

In order to effectively capture and express the interactions between individual and group social commitments and knowledge in probabilistic MASs, we propose a new modal logic called the new probabilistic logic of knowledge and commitments PCTL$^{\textrm{kc+}}$ which is built by combining a consistent logic of knowledge and commitment CTLKC$^+$ \cite{Al-Saqqar2014a} with a well established probabilistic temporal logic PCTL \cite{Hansson1994}. The resulting logic is extended further to accommodate operators for the group knowledge and group commitments.

At present, there is a relatively large gap in addressing the
concepts of knowledge and social commitments simultaneously in
MASs, especially with the presence of uncertainty. Existing
approaches that address the interaction between knowledge and
social commitments either limit the scope of interacting
agents to the widely used one-to-one commitment scheme and ignore the uncertainty aspect of MASs \cite{Al-Saqqar2014a}, or adopt a different kind of commitments called ``internal commitment'' rather than the ``social commitments'' that we consider in this thesis \cite{Schmidt2004}.
Furthermore, although the notion of ``group'' is important in the multi-agent community \cite{Sanchez-Anguix2013,YuW2010}, group social
commitments has not been formalized and verified yet. As knowledge
and social commitments influence each other in many real world
applications \cite{Al-Saqqar2014a}, their interactions need to be
reasoned about and verified in a systematic manner. As we said before,
uncertainty in MASs may arise due to imperfect information about
the environment in which agents interact. Besides, in some situations, it happens that even if there is some state of affairs (i.e., content of a commitment) that an agent wants to bring about, its actions might not reliably drive the state of affairs into the desired state \cite{Sultan2014a}. Consequently, commitments themselves become stochastic and the degree to which the commitment can be satisfied is not always
guaranteed.

To motivate our study of representing and verifying the
interaction between individual and group knowledge and social
commitments in probabilistic MASs when taking into account
one-to-many commitments, let us consider the following simple
example. A professor teaching an engineering course with a
capacity of $20$ students. Various scenarios could happen within
this context.

\begin{itemize}
\item \verb"Scenario 1": while the professor was explaining some
new concepts in the course, one of the students asked the
professor to provide him with more material regarding these
concepts. The professor then promised to email the student some
references the next day. This promise can be considered as a
commitment from the professor towards the student to provide him
with extra material for the new concepts. \item \verb"Scenario 2":
in the lecture before the mid-term exam, students requested the
professor to exclude some material and shorten the duration of the
exam accordingly. At the end of the lecture, the professor agreed
to exclude some parts of the covered material and to make the exam
one hour long.  This agreement can be considered as a commitment
from the professor to the group of students who are registered in
this course. Right after the class, the professor posted in the
course web site an update confirming what they agreed on.
\end{itemize}
In the first scenario, obviously both the professor and student
are aware of the commitment (sending extra materiel). However, in
the second scenario, every student registered in the course, and
not necessarily present during the lecture,  has to know about
this agreement (commitment) to avoid wasting time studying
excluded parts. In fact, because of some unexpected factors like
absence of the professor on the day of the exam, email delivery
failure, power outage, etc, there is no guarantee that these
commitments are  going to be surely fulfilled. Therefore, it is
important to have a logic system with the ability to not only
express the interaction between knowledge and social commitments,
but also to handle the concepts of knowledge and commitments
within the scope of a group when uncertainty matters. Once such a
logic is defined, it can be invested as the underlying logic for a
verification technique to verify some desirable and useful
properties expressing combinations of knowledge and social
commitments under uncertainty.

The work presented in this chapter can be seen as extension and continuation of the work presented in Chapter \ref{cha:PCTLKC} where reasoning about and verifying interactions between individual knowledge and social commitments in probabilistic MASs were first introduced. In Chapter \ref{cha:PCTLKC}, we proposed a probabilistic logic called PCTL$^{kc}$ whose expressiveness power allowed us to formulate combinations of the two concepts in the presence of uncertainty. PCTL$^{kc}$ logic was built by fusing two logics, namely PCTLC \cite{Sultan2013} and PCTLK \cite{Wan2013} using the
independent join technique \cite{Franceschet2004}. However, as pointed out in \cite{Al-Saqqar2014a}, the social accessibility relations given in \cite{Bentahar2012,El-Menshawy2013a}, have an over-specification problem, and consequently the PCTL$^{kc}$ logic suffers from some paradoxes as it adopts the aforementioned accessibility relations.

To elaborate, there exist some situations that are not desirable in real settings but with the use of PCTL$^{kc}$, they are valid. One major problem in PCTL$^{kc}$ is that agents commit everything they know to others, which brings the lack of privacy into being. Formally, this is represented by the following postulate:

\begin{itemize}
\item $K_i \varphi \Rightarrow C_{i \rightarrow j}\varphi$,  where $i \neq j$.
\end{itemize}

The validity of this postulate is based on the fact that by
establishing communication channels through which commitments are
supposed to be exchanged, the epistemic relation needed to define
the semantics of knowledge is also established. This is not
reasonable in open environments where agents are selfish. Another
problem is that agents commit everything known by others. That is,
when an agent knows that another agent knows something, the first
agent commits to bring about what the other agent knows, formally:

\begin{itemize}
\item $ K_i K_j \varphi \Rightarrow C_{i \rightarrow j} \varphi$ where $ i \neq j$.
\end{itemize}

Such a postulate should be avoided in MASs because it is not
realistic for an agent to commit for something that is out of its
capabilities. Moreover, this postulate can result in serious
circumstances if agent $j$ is malicious, so it can express
incorrect knowledge about the other agent, obliging it to
establish unwanted commitment.

On the other hand, we have some reasonable situations that should
be always valid but with the use of PCTL$^{kc}$ they can be
unsatisfied. One example in this respect is when agents should be always aware about the fulfillment of their own commitments.

\begin{itemize}
\item $Fu(C _{i\rightarrow j} \varphi) \Rightarrow K_i Fu(C
_{i\rightarrow j} \varphi)$ where $i \neq j$
\end{itemize}

It is realistic for this postulate to be valid because any agent should be aware of its fulfillment actions in order to prevent fulfilling the same commitment again and again. However, this postulate is not valid in PCTL$^{kc}$ because of the same reasons mentioned earlier. Consequently, PCTL$^{kc}$ fails to efficiently handle some practical situations in which knowledge and social commitments need to interact.

The problem is that one of the underlying logics of PCTL$^{kc}$, which
is PCTLC \cite{Sultan2013}, is built using the social accessibility relations given in \cite{Bentahar2012,El-Menshawy2013a}, which in fact over specifies and over constrains the concept of illocutionary communication. In a recent work, Al-Saqqar et al. \cite{Al-Saqqar2014a} have figured out that although the social accessibilities presented in \cite{Bentahar2012,El-Menshawy2013a} function perfectly when the concern is to model social commitments independently, they have some limitations when combined with the epistemic accessibility relations in the same model. The authors in \cite{Al-Saqqar2014a} modified the social accessibility relations proposed in \cite{Bentahar2012,El-Menshawy2013a} in order to prevent the unintended emergence of the epistemic accessibility relations from the social accessibility relations when the two accessibilities combined in the same model. Technically speaking, they relaxed the conditions upon which the social accessibility relations are established in order to decouple the social accessibility relations from the epistemic accessibility relations. The new definition of social accessibilities does no longer depend on the unshared variables but rather depends merely on the shared variables between the interacting agents as discussed in Chapter \ref{cha:background}. The new condition upon which a communication channel is established is stated below:

 $ s \approx_{i \rightarrow j} s' $ iff $ Var_i \cap Var_j \neq \emptyset $ such that $ \forall x \in Var_i \cap Var_j $ we have $ l_i^x(s) =
l_i^x(s') = l_j^x(s')$, where $\approx_{i\rightarrow j} \subseteq S \times S$ is the social accessibility relation. It has been proven that with the new social accessibilities, the resulting logic is consistent \cite{Al-Saqqar2014a}.

The work presented in this chapter differs from the one proposed in Chapter \ref{cha:PCTLKC} in the following points:

\begin{enumerate}
\item While the logic presented in Chapter \ref{cha:PCTLKC} suffers from
some paradoxes, the current work builds upon a consistent logic of
knowledge and commitment CTLKC$^+$ \cite{Al-Saqqar2014a} which
ensures having a paradox-free logic.

\item The new logic allows us to reason about commitments among
multiple agents instead of limiting the scope to merely two
agents. The concept of group knowledge is also integrated to the framework allowing us to reason about the knowledge in the case of group of agents.

\item In the current work, we generalize the model checking
technique that has been proposed in Chapter \ref{cha:PCTLKC} to fit the new group commitment operators as well.
\end{enumerate}

The contributions of this chapter are threefold. First, we present a new probabilistic logic called (PCTL$^{\textrm{kc+}}$) with expressiveness abilities to capture and represent the interactions between individual and group knowledge and social commitments.
Second, we introduce a formal verification technique for the probabilistic logic PCTL$^{\textrm{kc+}}$. The proposed technique is based on reducing
the problem of model checking PCTL$^{\textrm{kc+}}$ to the problem
of model checking PCTL. This is achieved through 1) advocating a
set of transformation rules that transform the
PCTL$^{\textrm{kc+}}$ model into a Markov Decision Process (MDP),
and then converting the obtained MDP into a DTMC using the notion
of ``adversary'' \cite{Forejt2011}; 2) reducing
PCTL$^{\textrm{kc+}}$ formulae into PCTL formulae based on a set
of formal reduction rules. Third, we implement our reduction model checking
technique on top of PRISM and apply it on a concrete case study,
namely the online shopping system \cite{Gomaa2011}. We then check
some system's properties written as PCTL$^{\textrm{kc+}}$ formulae
using the PRISM model checker by checking their corresponding PCTL
formulae. Figure \ref{fig:approach-PCTLKC+} depicts a schematic
view of our proposed framework.

\begin{figure}[t]
                \begin{center}
                \includegraphics[width=14cm, height=10cm]{chap5/img/approach-cha5-new.eps}
                \end{center}
                \caption{A schematic view of the probabilistic group social commitment approach} \label{fig:approach-PCTLKC+}
                \label{Stack}
                \end{figure}

\section{The New Probabilistic Logic of knowledge and Commitment (PCTL$^{\textrm{kc+}}$)} \label{sec:logic}

To overcome the inconsistency problem of PCTL$^{kc}$, we develop a new logic called the new probabilistic logic of knowledge and commitment (PCTL$^{\textrm{kc+}}$). To build PCTL$^{\textrm{kc+}}$, there are two obvious resources available in the literature: 1) the traditional temporal logics that have been developed for knowledge and social commitments independently or together such as CTLC \cite{Bentahar2012}, CTLK \cite{Lomuscio2007}, and CLTKC$^+$ \cite{Al-Saqqar2014a}; and 2) the existing probabilistic logics available in the literature such as PCTL \cite{Hansson1994}, PCLTK \cite{Wan2013}, and PCTLC \cite{Sultan2014a}. Unfortunately, none of these resources is perfectly suitable for the task. The former resource neglects the uncertainty aspects in MASs, while the
latter doesn't capture the interaction between knowledge and
social commitments. Therefore, we propose a solution that draws
upon both resources. In particular, we combine an existing
consistent logic of knowledge and commitment CTLKC$^+$
\cite{Al-Saqqar2014a} with a well established probabilistic
temporal logic PCTL \cite{Hansson1994}. Then, we extend the
resulting combined logic by adding new operators for the group knowledge
and group commitment.

Before going further, let us first describe a new probabilistic model over which PCTL$^{\textrm{kc+}}$ formulae can be interpreted. This model is an extension of the formalism of interpreted systems
\cite{Fagin1995} with the concepts of epistemic accessibility and
social accessibility relations. Concretely, the model of PCTL$^{\textrm{kc+}}$ is generated from combining two extended versions of the interpreted systems formalism. These extended formalisms are the extended version introduced in \cite{Halpern2003,Wan2013} and a modified version of the extended version given in \cite{Bentahar2012,El-Menshawy2013a} due to Al-Saqqar et al. \cite{Al-Saqqar2014a}.

\begin{definition} [PCTL$^{\textrm{kc+}}$ Model] ~\label{dfn:Models}

\noindent Given a set of atomic propositions $\Phi_p = (p,q,r, \ldots)$ and a set of agents $\texttt{Agt}=\{1,\ldots,n\}$,  the model $\mathfrak{M_3}=(S,\textbf{P},I,\sim_1, \ldots
,\sim_n,\{\approx_{i \rightarrow j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$ is a tuple where:
%
\begin{itemize}
\item  $S \subseteq L_1 \times \ldots \times L_n$ is a countable set of all reachable global states of the system. A state $s$ is reachable iff there exists a sequence of transitions from an initial state to $s$ in which the probability of each transition is greater than $0$.

\item  $I \in S$ is an initial global state for the system.

\item  $\textbf{P}:S\times S\rightarrow [0,1]$ is a total transition probability function defined as $\textbf{P}(s, s')=\tau(s,a^{s \rightarrow s'}, s')$ iff there exists a joint action $a=(a_1,\ldots,a_n) \in ACT$ such that\\
     $\sum_{i \in \texttt{Agt}} \tau_i(l_i(s),a^{l_i(s)\rightarrow l_i(s')},l_i(s')) > 0$ and $\sum_{s' \in S} \textbf{P}(s,s') =1$ for all $s \in S$.

\item  $\sim_i \subseteq S \times S$ is the epistemic accessibility relation for the agent $i$, such that for two global states $s$ and $s'$, we have: $s \sim_i s'$ iff $l_i(s)=l_i(s')$.

\item For each pair $(i,j) \in \texttt{Agt}^2$, $\approx_{i\rightarrow j} \subseteq S \times S$ is the social accessibility relation which is defined as follows: $ s \approx_{i\rightarrow j} s' $ iff $ Var_i \cap Var_j \neq \emptyset $ such that $ \forall x \in Var_i \cap Var_j $ we have $ l_i^x(s) = l_i^x(s') = l_j^x(s')$.

\item  $\nu : S \rightarrow 2 ^{\Phi_p} $ is a valuation function.

\end{itemize}
\end{definition}
%

The new model $\mathfrak{M_3}$ differs from the model $\mathfrak{M_2}$,  presented in Chapter \ref{cha:PCTLKC}, in one particular point which is the social accessability relation. While $\mathfrak{M_2}$ uses the social accessibility relation $\sim_{i\rightarrow j}$ that has been introduced in \cite{Bentahar2012,El-Menshawy2013a}, the new model adopts the one $\approx_{i\rightarrow j}$ proposed in \cite{Al-Saqqar2014a} in order to overcome the over-specification problem appeared in $\sim_{i\rightarrow j}$.

\subsection{Syntax of PCTL$^{\textrm{kc+}}$} \label{def:syntax-PCTLKC+}

\begin{definition}[PCTL$^{\textrm{kc+}}$ syntax]\label{def:syntax-PCTLKC+}
Let $\Phi_p=\{p,q, \dots\}$ be a set of atomic propositions, and $\texttt{Agt}=\{1, \dots, n\}$ be a set of agents. The syntax of PCTL$^{\textrm{kc+}}$, which is a combination of PCTLK \cite{Wan2013} and PCTLC \cite{Sultan2014a,Sultan2013} augmented with further operators for the group knowledge, is given by the following grammar:

\vspace{-0.5cm}
\begin{align*}
    \varphi & ::= p~|~\neg \varphi~|~\varphi \vee \varphi~|~\mathcal{K}~|~\mathcal{C}~|~ \mathbb{P}_{\bowtie k} (\psi)~|~\mathbb{P}_{\bowtie k}(\mathcal{K})|~\mathbb{P}_{\bowtie k}(\mathcal{C})\\
    \psi & ::=\bigcirc \varphi ~ | ~ \varphi ~U~ \varphi~|~ \varphi~ U^{\leq m} ~ \varphi \\
    \mathcal{K} & ::= K_i ~\varphi ~|~ E_{G} ~\varphi\\
    \mathcal{C} & ::= C_{i\rightarrow j} ~\varphi ~| ~ C_{i\rightarrow G} ~\varphi ~| ~Fu(C_{i\rightarrow j} ~\varphi) ~| ~Fu(C_{i\rightarrow G} ~\varphi)
\end{align*}
%
where;\\
\noindent -- $p\in\Phi_p$ is an atomic proposition\\
\noindent -- $i,j \in \texttt{Agt}$.\\
\noindent -- $G\subseteq \texttt{Agt}$.\\
\noindent -- $\mathbb{P}_{\bowtie k}$ is a probabilistic operator and $\bowtie \in\{<,\leq,>,\ge\}$.\\
\noindent -- $k\in [0,1]$ is a probability bound or threshold.\\
$m \in\mathbb{N}^+ $ is a positive integer number reflecting the maximum number of transitions needed to reach a certain state.\\
\noindent -- The Boolean connectives $\neg$ and $\vee$ are defined in the usual way.\\
\noindent -- $\varphi$ and $\psi$ are state and path formulae interpreted over the states and paths of $\mathfrak{M_3}$ respectively.\\
\noindent -- The modal connectives $\mathcal{K}$ and $\mathcal{C}$ stand for ``epistemic" and ``social" operators, respectively.\\

\end{definition}
\vspace{-0.5cm}

\noindent In this logic, formulae $\mathcal{K}$ are state formulae and used to express the epistemic properties through the operators; $K_i$ which stands for agent $i$ knows, $E_G$ which stands for everyone knows. Modal connectives $C_{i\rightarrow j}$ and $C_{i\rightarrow G}$ are called social formulae and stand for ``commitment'' from a debtor towards a single creditor, and ``commitment'' from a debtor to a group of creditors, respectively. Likewise, modal connectives $Fu(C_{i\rightarrow j})$ and $Fu(C_{i\rightarrow G})$ stand for ``fulfillment'' of the commitment $C_{i\rightarrow j}$ and ``fulfillment'' of the commitment $C_{i\rightarrow G}$, respectively. $\bigcirc, U$ and $U^{\leq m}$ stand for ``next time'', ``until'' and ``bounded until'' path modal connectives respectively.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Social Commitments Classification} \label{sec:commitment-classification}

Social commitments for agent communication have been always looked
at within the scope of one-to-one. However,
back to our motivating example, we realize that in addition to the
usual agent-to-agent scheme, there are certain situations where
group-agent commitments are needed. In this chapter, we are
interested to move beyond the scope of one-to-one and
investigate the case of committing to multiple agents. The idea of
investigating other schemes of social commitments rather than the
one-to-one commitment scheme seems to be both technically
interesting and intuitively appealing. In what follows, we
distinguish between two different flavors of social commitments,
namely basic (or individual) social commitment and group social
commitment.

\begin{definition} [Basic Social Commitment]~

A basic social commitment is an agreement between two agents
namely, \texttt{debtor} and \texttt{creditor} such that the
\texttt{debtor} engages towards the \texttt{creditor} to bring
about a certain property.
\end{definition}

This is the simplest form of social commitments and has long been
investigated in the literature. The commitment in this case can be
represented using the following operator: $C_{i\to j} ~\varphi$
where $i$ denotes the debtor, $j$ denotes the creditor, and
$\varphi$ denotes the content of the commitment. The fulfillment
of such a commitment is written as follows: $Fu(C_{i\to j}
~\varphi)$. However, as the common form of social commitments is
the basic social commitment, we can simply use ``social
commitments" to refer to ``basic (or individual) social
commitments".

\begin{definition} [Group Social Commitment]~

A group social commitment is an agreement between a
\texttt{debtor} and a group of \texttt{creditors} to bring about a
certain property.
\end{definition}

This kind of commitments indicates the involvement of multiple
agents in the same commitment. The creditor is a group of
independent agents that join together as a single party due to
their shared interests in the commitment at hand. A group social
commitment is represented using the following notation: $C_{i\to
G} ~\varphi$, where $i$ denotes the debtor, $G$ denotes a group of
creditors, and $\varphi$ denotes the content of the commitment.
The fulfillment of such a commitment is given by the notation
$Fu(C_{i\to G} ~\varphi)$. Technically, a group social commitment
can be seen as the conjunction of individual basic social
commitments from the debtor $i$ to each agent in the group of
creditors $G$. Formally, $C_{i\to G} ~\varphi \equiv
\bigwedge\limits_{j\in G} C_{i\rightarrow j} ~\varphi$. An
intuitive explanation of the operator $C_{i\to G} ~\varphi$ is as
follows: for a group social commitment to be held at a certain
state, the content of the commitment must be true at every
accessible state from the commitment state with respect to the
group. This implies that none of the group members could be
excluded from having all accessible states satisfy the content of
the commitment. Consequently, it is obvious that for a state to be
socially accessible from the commitment state with respect to the
group, it has to be socially accessible with respect to at least
one of the agents of the group. Therefore, we resolve the
accessibility problem resulted from having group commitments by
taking the union of the social accessibility relations of each
single agent in the group. This in turn leads us to define the
group social accessibility relation based on the social
accessibility relations presented in Definition \ref{dfn:Models}.

Let $G\subseteq \texttt{Agt}$ be a group of agents. We define the group social accessibility relation from the social accessibility relation $\approx_{i \to j}$ as follows:
\begin{definition} [Social Accessibility Relations for Group Social Commitment] \label{dfn: group social
relations}~
%
\begin{itemize}

\item $\approx_{i \rightarrow G}$ is the union of the social accessibility relations between agent $i$ and each agent in the group $G$: $\approx_{i \to G}=\bigcup\limits_{j \in G}\approx_{i\to j}$.

\end{itemize}

\end{definition}

\begin{figure}[t]
                \begin{center}
                \includegraphics[width=7cm, height=5cm]{chap5/img/group-sc.eps}
                \end{center}
                \caption{Accessibility relations for group social commitment} \label{fig:group-sc}
                \end{figure}

Notice that group social commitments have all the properties of basic social commitments with an additional constraint that they can involve more than two agents. However, a group social commitment involving only two agents is equivalent to the basic social commitment. Figure \ref{fig:group-sc} depicts the idea of group social accessibility ($G=\{j_1, j_2\}$).

\subsection{Group Knowledge}  \label{sec:Group Knowledge}
In this work, we limit the scope of group knowledge to the concept of ``Everyone Knows" introduced in \cite{Fagin1995}. ``Everyone Knows" is denoted by $E_G ~\varphi$ and means that everyone in the group $G$ knows $\varphi$. Technically, ``Everyone knows" can be seen as the conjunction of the individual knowledge of each agent in the group. Formally, $E_G ~\varphi \equiv \bigwedge\limits_{i\in G} K_i ~\varphi$.

Before we proceed to present the semantics of
PCTL$^{\textrm{kc+}}$, we need to define the epistemic
accessibility relation for $E_G ~\varphi$. Let $G\subseteq
\texttt{Agt}$ be a group of agents. We define the epistemic
accessibility relation for $E_G ~\varphi$ from the epistemic
accessibility relation $\sim_i$ as follows \cite{Wan2013}:\\

\begin{definition} [Epistemic Accessibility Relation for Everyone Knows] \label{dfn: epistemic relations}~
\begin{itemize}

\item $\sim_G^{E}$ is the union of group $G's$ accessibility
relations: $\sim_G^{E}=\bigcup\limits_{i \in G}\sim_i$.

\end{itemize}
\end{definition}

\subsection{Semantics of PCTL$^{\textrm{kc+}}$} \label{def:semantics-PCTLKC+}

Given a model $\mathfrak{M_3}=(S,\textbf{P},I,\sim_1, \ldots
,\sim_n,\{\approx_{i \to j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$, then $(\mathfrak{M_3},s) \models \varphi$ states that ``a state $s$ in the model $\mathfrak{M_3}$ satisfies a state formula $\varphi$, $(\mathfrak{M_3},\pi) \models \psi$ means that ``a path $\pi$ in the model $\mathfrak{M_3}$ satisfies a path formula $\psi$, and
$(\mathfrak{M_3},s) \models \mathbb{P}_{\bowtie k}(\psi)$ means that
``a state $s$ in $\mathfrak{M_3}$ satisfies
$\mathbb{P}_{\bowtie k}(\psi)$ if the probability of taking a path
from $s$ that satisfies $\psi$ is in the interval specified by
$\bowtie k$''. When the model $\mathfrak{M_3}$ is clear from the
context, we simply write the satisfaction relation $\models$ as
follows: $s \models \varphi$ and $\pi \models \psi$. Furthermore,
we denote the number of socially accessible states $s'$ from a given state $s$ such that $s\approx_{i\to j}s'$ by $|s\approx_{i\to j}s'|$, and $s\approx_{i\to G}s'$ by $|s\approx_{i\to G}s'|$.
We also denote the number of epistemically accessible states $s'$ from a given state $s$ such that $s\sim_i s'$ by $|s\sim_i s'|$. Similarly, we
denote the number of states $s'$ that are accessible from a given
state $s$ through $\sim_G^E$ by $|s\sim_G^E s'|$.
Finally, we define $|s\models \varphi|$ as follows:

\begin{center}
$|s\models \varphi|=
\begin{cases}
1,~~~\textrm{if}~ s\models\varphi\\
0,~~~\textrm{otherwise}.
\end{cases}$
\end{center}

%
\begin{definition}[\textbf{Satisfaction}]\label{def:semantics-pctlkc+} Satisfaction of a PCTL$^{\textrm{kc+}}$ formula in the model $\mathfrak{M_3}$ is conductively defined as follows:

\noindent $s\models p~~~~~~~~~~~~~~~~~~~\emph{iff}~~p\in \nu(s);\\
s\models \varphi_1 \vee \varphi_2 ~~~~~~~~\emph{iff}~~s\models \varphi_1~\textrm{or}~s \models \varphi_2; \\
s\models \neg \varphi~~~~~~~~~~~~~~~~\emph{iff}~~s \nvDash \varphi;\\
s\models K_i \varphi  ~~~~~~~~~~~~~~ \emph{iff}~~ \forall s'\in S ~ \textrm{s.t.} ~~ s \sim_i s',  \ \textrm{we~have}~ s'\models \varphi; \\
s\models E_G ~\varphi ~~~~~~~~~~~~ \emph{iff}~~\forall s'\in S~ \textrm{s.t.} ~~ s\sim_G^E s', \ \textrm{we~have}~ s'\models \varphi; \\
s\models C_{i\rightarrow j} \varphi  ~~~~~~~~~~ \emph{iff} ~~\forall s' \in S~\textrm{s.t.}~~s \approx_{i \rightarrow j}s', \textrm{we~have}~s'\models K_i \varphi \wedge K_j \varphi;\\
s\models C_{i\rightarrow G} \varphi  ~~~~~~~~~ \emph{iff} ~~\forall s' \in S~\textrm{s.t.}~~s \approx_{i \rightarrow G}s', \textrm{we~have}~s'\models K_i \varphi \wedge E_G ~\varphi $;\\
$s\models Fu(C_{i\rightarrow j} \varphi)$ ~\emph{iff} there exists $ s' \in S $ such that $ s' \approx_{i \rightarrow j} s $ and $~s'\models C_{i\rightarrow j} ~\varphi$ or \\
$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$there exists $ s'' \in S $ and $ s'' \sim_i s $ such that $~s''\models Fu(C_{i\rightarrow j} ~\varphi)$ or \\
$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$there exists $ s'' \in S $  and $ s'' \sim_j s $ such that $~s''\models Fu(C_{i\rightarrow j} ~\varphi)$;\\
$s\models Fu(C_{i\rightarrow G} ~\varphi)$ ~\emph{iff} there exists $ s' \in S $ such that $ s' \approx_{i \rightarrow G} s $ and $~s'\models C_{i\rightarrow G} ~\varphi$ or \\
$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$there exists $ s'' \in S $ and $ s'' \sim_i s $ such that $~s''\models Fu(C_{i\rightarrow G} ~\varphi)$ or \\
$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$there exists $ s'' \in S $  and $ s'' \sim_G^E s $ such that $~s''\models Fu(C_{i\rightarrow G} ~\varphi)$;\\
\noindent $\pi \models \bigcirc \varphi~~~~~~~~~~~~~~\emph{iff}~~\pi(1) \models \varphi; \\
\pi \models \varphi_1~U^{\leq m}~\varphi_2~~\emph{iff}~~\exists k \leq m~~\textrm{s.t.}~~ \pi(k) \models \varphi_2 ~\textrm{and}~\forall i < k, \pi(i) \models \varphi_1;\\
\pi \models \varphi_1 ~U~\varphi_2~~~~~~~\emph{iff}~~\exists m \geq 0~~\textrm{s.t.}~~\pi \models \varphi_1~U^{\leq m}~\varphi_2;$\\
\noindent $s \models \mathbb{P}_{\bowtie k} (\psi)~~~~~~~~~\emph{iff}~~Prob_s(\psi)\bowtie k$ where: $Prob_s(\psi)=Prob_s\{\pi \in \Pi(s)~|~\pi\models
\psi\};$\\

\noindent $\bullet$ For a probabilistic operator working on an epistemic formula, where the set of all accessible states from $s$ is our sample space and the set of events $\mathrm{F}$ is the set of states accessible from $s$ and satisfy the formula:

\begin{tabbing}
\noindent $s\models \mathbb{P}_{\bowtie k}(K_i~\varphi) $
    \ \ \ \ \ \= \emph{iff} \ $Prob(s \models K_i\varphi)$ $\bowtie k$ where: $Prob(s\models K_i\varphi)=\frac{\sum_{s \sim_i s'}|s'\models \varphi| }{|s \sim_i s'|};$
\end{tabbing}

\begin{tabbing}
 \noindent $s\models \mathbb{P}_{\bowtie k}(E_G~\varphi) $
    \ \ \ \ \ \= \emph{iff} \ $Prob(s \models E_G~\varphi)$ $\bowtie k$ where: $Prob(s\models E_G~\varphi)=\frac{\sum_{s \sim_G^E s'}|s'\models \varphi| }{|s \sim_G^E s'|};$

\end{tabbing}

\noindent $\bullet$  For a probabilistic operator working over a commitment formula,where the set of all accessible states from $s$ is our sample space and the set of events $\mathrm{F}$ is the set of states accessible from $s$
and satisfy the formula: \\

\noindent $s\models \mathbb{P}_{\bowtie k}(C_{i\rightarrow j}\varphi)$
   ~~\emph{iff}  $Prob(s \models C_{i\rightarrow j}\varphi) \bowtie \!k$ where: $Prob(s\models C_{i\rightarrow j}\varphi)=\frac{\sum_{s \approx_{i \rightarrow j}s'}|s'\models K_i \varphi \wedge K_j \varphi| }{|s \approx_{i \rightarrow j}s'| };$\\

\noindent $s\models \mathbb{P}_{\bowtie k}(C_{i\rightarrow G}\varphi)$
   ~\emph{iff}  $Prob(s \models C_{i\rightarrow G}\varphi) \bowtie \!k$ where: $Prob(s\models C_{i\rightarrow G}\varphi)=\frac{\sum_{s \approx_{i \rightarrow G}s'}|s'\models K_i \varphi \wedge E_G \varphi| }{|s \approx_{i \rightarrow G}s'| };$\\

\noindent $\bullet$ For a probabilistic operator working over a fulfilment formula, assuming that accessible states are also reachable:\\

\noindent $s\models \mathbb{P}_{\bowtie k}(Fu(C_{i\rightarrow j}\varphi))$
    ~~ \emph{iff}~ $Prob(s \models Fu(C_{i\rightarrow j}\varphi)) \bowtie k;$ where:

\vspace{-0.4cm}
\begin{align*}
%%
& Prob(s\models Fu(C_{i\rightarrow j}\varphi))\ = Prob_s\{\pi \in \Pi(s') ~|~s' \approx_{i \rightarrow j}s ~\textrm{and}~ \pi = s' \ldots s ~\textrm{and}~ s' \models C_{i\rightarrow j}\varphi\};
\end{align*}

\noindent $s\models \mathbb{P}_{\bowtie k}(Fu(C_{i\rightarrow G}\varphi))$
    ~~ \emph{iff}~ $Prob(s \models Fu(C_{i\rightarrow G}\varphi)) \bowtie k;$ where:

\vspace{-0.4cm}
\begin{align*}
%%
& Prob(s\models Fu(C_{i\rightarrow G}\varphi))\ = Prob_s\{\pi \in \Pi(s') ~|~
& s' \approx_{i \rightarrow G}s ~\textrm{and}~ \pi = s' \ldots s ~\textrm{and}~ s' \models C_{i\rightarrow G}\varphi\}
\end{align*}

\end{definition}

Again as in Chapter \ref{cha:PCTLKC}, in the case of the knowledge, the uncertainty is computed in such a way that it reflects the indistinguishability property of the epistemic accessibility relations. Hence, the uncertainty is computed based on the probability of epistemic accessibility relations which is calculated based on the number of accessible states satisfying the content of the knowledge over the number of equivalent states, as all the states are equally accessible. Likewise, probabilistic commitment is computed based on the number of accessible states that satisfy the content over the whole number of accessible states, which demonstrates the uncertainty of the agent over the accessible states, so that over the commitment. Probabilistic fulfillment, however, is computed using the probabilistic transitions of the path linking the commitment state to the fulfillment state.

The following proposition is straightforward from the semantics:

\begin{proposition} \label{proposition}~\\
If $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (Fu(C_{i \rightarrow
j}\varphi))$ and $(\mathfrak{M_3},s)\models Fu(C_{i \rightarrow
j}\varphi)$, then $s$ is not reachable from the commitment state.
\end{proposition}

\begin{theorem} [Epistemic Equivalences]\label{theorm:Epistemic-equivalence} \ \ \ \

    \begin{enumerate}
        \item $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1}(K_i~\varphi)$  ~~~~~~iff~~  $(\mathfrak{M_3},s) \models K_i~\varphi$
        \item $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq 0}(K_i~\varphi)$   ~~~~~~iff~~  $(\mathfrak{M_3},s)\models K_i ~\neg \varphi$
        \item $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[}(K_i~\varphi)$  ~~~~iff~~   $(\mathfrak{M_3},s)\models \neg K_i~\neg\varphi \wedge \neg K_i~\phi$
        \item $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1}(E_G~\varphi)$  ~~~~iff~~  $(\mathfrak{M_3},s) \models E_G~\varphi$
        \item $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq 0}(E_G~\varphi)$   ~~~~iff~~  $(\mathfrak{M_3},s)\models E_G ~\neg \varphi$
        \item $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[}(E_G~\varphi)$  ~~iff~~   $(\mathfrak{M_3},s)\models \neg E_G~\neg\varphi \wedge \neg E_G~\varphi$

    \end{enumerate}

\end{theorem}

\begin{proof} %\hspace{-0.9cm}
We prove the first three equivalences, the same method can be used to prove the others.
\begin{itemize}
\item First equivalence. ~\\
    $``\Rightarrow"$. Assume $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1} (K_i\varphi)$.
    By the semantics of PCTL$^{\textrm{kc+}}$, it follows that $Prob((\mathfrak{M_3},s)\models K_i~\varphi)\geq1$.
    Therefore, $\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\sim_i s'|}\geq1$. This means that $\forall s'\in S$ such that $s\sim_i s'$, we have $(\mathfrak{M_3},s')\models \varphi$ (as $\sim_i$ is reflexive, so $s'$ could be $s$ itself). Thus, $(\mathfrak{M_3},s) \models K_i ~\varphi$. \\
    $``\Leftarrow"$. Assume $(\mathfrak{M_3},s)\models K_i~\varphi$. By the PCTL$^{\textrm{kc+}}$ semantics, it follows that for all $s'\in S$ such that $s\sim_i s'$, we have $(\mathfrak{M_3},s')\models \varphi$ (i.e. all accessible states from $s$ satisfy $\varphi$).
    Consequently, $\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| = |s\sim_i s'|$.
    Therefore, $\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\sim_i s'|}\geq1$ and hence $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1} K_i\varphi)$.

\item Second equivalence. ~\\
    $``\Rightarrow"$. Assume $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (K_i\varphi)$.
    By the PCTL$^{\textrm{kc+}}$ semantics, it follows that $Prob((\mathfrak{M_3},s)\models K_i\varphi)\leq0$.
    Thus, $\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi|}{|s\sim_i s'|}\leq0$. Since $\sim_i$ is reflexive, so the set of the accessible states from $s$ is not empty. Therefore, $\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi|$ must be 0 (i.e., $\varphi$ is not true in any of the accessible states). Consequently, for all $s'\in S$ such that $s\sim_i s'$, we have $(\mathfrak{M_3},s')\nvDash \varphi$, which means $(\mathfrak{M_3},s')\models \neg \varphi$. Hence, $(\mathfrak{M_3},s)\models K_i \neg \varphi$.~\\
%
    $``\Leftarrow"$. Assume $(\mathfrak{M_3},s)\models K_i\neg \varphi$. By the PCTL$^{\textrm{kc+}}$ semantics, it follows that $\forall s'\in S$ such that $s\sim_i s'$, we have $(\mathfrak{M_3},s')\nvDash \varphi$. Since the set of the accessible states from $s$ is not empty, then $\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\sim_i s'|}\leq0$. Hence, $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (K_i\varphi)$.

\item Third equivalence. ~\\
    $``\Rightarrow"$. Assume $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[} K_i\varphi)$. By the PCTL$^{\textrm{kc+}}$ semantics, it follows that $0< Prob(s\models K_i\varphi)<1$. Thus, $0<\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| }{|s \sim_i s'|}<1$.
    This means that it would never be the case that $\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| = |s\sim_i s'|$ nor $\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| = 0$. Consequently, there exist some $s', s'' \in S$ such that $s\sim_i s'$ and $s\sim_i s''$ and $(\mathfrak{M_3},s')\models \varphi$ and $(\mathfrak{M_3},s'')\models \neg \varphi$. Hence, it is impossible to have $(\mathfrak{M_3},\overline{s})\models \neg\varphi$ or $(\mathfrak{M_3},\overline{s})\models \varphi$ for all $\overline{s}\in S$ such that $s\sim_i \overline{s}$. Consequently, $(\mathfrak{M_3},s)\nvDash K_i\neg\varphi$ and $(\mathfrak{M_3},s)\nvDash K_i\varphi$. Hence $(\mathfrak{M_3},s)\models \neg K_i\neg\varphi$ and $(\mathfrak{M_3},s)\models \neg K_i\varphi$. ~\\
    %
    $``\Leftarrow"$. Assume $(\mathfrak{M_3},s)\models \neg K_i\varphi$. By the PCTL$^{\textrm{kc+}}$ semantics, it follows that there exists $s'\in S$ such that $s\sim_i s'$ and $(\mathfrak{M_3},s')\models \neg \varphi$. Consequently, it would never be the case that for all $s'\in S$ such that $s\sim_i s'$ we have $(\mathfrak{M_3},s')\models \varphi$. Therefore, $1>\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\sim_i s'|}$. Now assume $(\mathfrak{M_3},s)\models \neg K_i\neg \varphi$. Therefore, $\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| = 0$ would never be the case as some accessible states should satisfy $\varphi$. Consequently, $\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\sim_i s'|}>0$. Thus, $0<\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| }{|s \sim_i s'|}<1$. Hence, $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[} (K_i\varphi)$.
\end{itemize}
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem} [Commitment Equivalences] \label{theorem:Commitment-Equivelances} ~

\begin{enumerate}
\item $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1} (C_{i \rightarrow
j}\varphi)$ ~~~~~iff~~ $(\mathfrak{M_3},s)\models C_{i \rightarrow
j}\varphi$

\item $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (C_{i \rightarrow
j}\varphi)$ ~~~~~iff~~ $(\mathfrak{M_3},s)\models C_{i \rightarrow
j}\neg \varphi$

\item $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[} (C_{i \rightarrow
j}\varphi)$ ~~~iff~~ $(\mathfrak{M_3},s)\models \neg C_{i
\rightarrow j}\neg\varphi \wedge \neg C_{i \rightarrow j}\varphi$

\item $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1} (C_{i \rightarrow
G}\varphi)$ ~~~~iff~~ $(\mathfrak{M_3},s)\models C_{i \rightarrow
G}\varphi$

\item $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (C_{i \rightarrow
G}\varphi)$ ~~~~iff~~ $(\mathfrak{M_3},s)\models C_{i \rightarrow
G}\neg \varphi$

\item $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[} (C_{i \rightarrow
G}\varphi)$ ~~iff~~ $(\mathfrak{M_3},s)\models \neg C_{i
\rightarrow G}\neg\varphi \wedge \neg C_{i \rightarrow G}\varphi$

\end{enumerate}

\end{theorem}

\begin{proof}
We prove the first three equivalences, the same method can be used to prove the others.

\begin{itemize}
\item First equivalence. ~\\
    $``\Rightarrow"$. Assume $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1} (C_{i \rightarrow j}\varphi)$.
    By the PCTL$^{\textrm{kc+}}$ semantics, it follows that $Prob((\mathfrak{M_3},s)\models C_{i\rightarrow j}\varphi)\geq1$.
    Thus,  $\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\approx_{i \rightarrow j}s'|}\geq1$.
    This means that for all $s'\in S$ such that $s\approx_{i \rightarrow j}s'$, we have $(\mathfrak{M_3},s')\models \varphi$, and hence $(\mathfrak{M_3},s) \models C_{i\rightarrow j}\varphi$. \\
    $``\Leftarrow"$. Assume $(\mathfrak{M_3},s)\models C_{i \rightarrow j}\varphi$. By the PCTL$^{\textrm{kc+}}$ semantics, it follows that for all $s'\in S$ such that $s\approx_{i \rightarrow j}s'$,
    we have $(\mathfrak{M_3},s')\models \varphi$ (i.e. all accessible states from $s$ satisfy $\varphi$).
    Consequently, $\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| = |s\approx_{i \rightarrow j}s'|$.
    Therefore, $\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\approx_{i \rightarrow j}s'|}\geq1$
    and hence, $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1} (C_{i \rightarrow j}\varphi)$.

\item Second equivalence. ~\\
    $``\Rightarrow"$. Assume $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (C_{i \rightarrow j}\varphi)$.
    By the PCTL$^{\textrm{kc+}}$ semantics, it follows that $Prob((\mathfrak{M_3},s)\models C_{i\rightarrow j}\varphi)\leq0$.
    Thus, $\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi|}{|s\approx_{i \rightarrow j}s'|}\leq0$.
    Since the set of the accessible states from $s$ is not empty, then $\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi|$
    must be 0 (i.e. $\varphi$ is not true in any of the accessible states). Consequently, for all $s'\in S$ such that $s\approx_{i \rightarrow j}s'$, we have $(\mathfrak{M_3},s')\nvDash \varphi$, which means $(\mathfrak{M_3},s')\vdash \neg \varphi$.
     Hence, $(\mathfrak{M_3},s)\models C_{i\rightarrow j}\neg \varphi$.~\\
%
    $``\Leftarrow"$. Assume $(\mathfrak{M_3},s)\models C_{i \rightarrow j}\neg \varphi$. By the PCTL$^{\textrm{kc+}}$ semantics,
    it follows that for all $s'\in S$ such that
    $s\approx_{i \rightarrow j}s'$, we have $(\mathfrak{M_3},s')\nvDash \varphi$. Since the set of the accessible states from $s$ is not empty, then $\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\approx_{i \rightarrow j}s'|}\leq0$. Hence, $(\mathfrak{M_3},s')\models \mathbb{P}_{\leq0} (C_{i \rightarrow j}\varphi)$.

\item Third equivalence. ~\\
    $``\Rightarrow"$. Assume $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[} (C_{i \rightarrow j}\varphi)$. By the PCTL$^{\textrm{kc+}}$ semantics, it follows that $0< Prob((\mathfrak{M_3},s)\models C_{i\rightarrow j}\varphi)<1$. Thus, $0<\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| }{|s \approx_{i \rightarrow j}s'|}<1$.
    This means that it would never be the case that $\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| = |s\approx_{i \rightarrow j}s'|$
    nor $\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| = 0$. Consequently, there exist some $s', s'' \in S$
    such that $s\approx_{i \rightarrow j}s'$ and $s\approx_{i \rightarrow j}s''$ and $(\mathfrak{M_3},s')\models \varphi$ and $(\mathfrak{M_3},s'')\models \neg \varphi$.
    Hence, it is impossible to have $(\mathfrak{M_3},\overline{s})\models \neg\varphi$ or $(\mathfrak{M_3},\overline{s})\models \varphi$ for all $\overline{s}\in S$ such that $s\approx_{i \rightarrow j}\overline{s}$. Consequently,
    $s\nvDash  C_{i \rightarrow j}\neg\varphi$ and  $(\mathfrak{M_3},s)\nvDash  C_{i \rightarrow j}\varphi$. Hence $(\mathfrak{M_3},s)\models \neg C_{i \rightarrow j}\neg\varphi$ and $(\mathfrak{M_3},s)\models \neg C_{i \rightarrow j}\varphi$. ~\\
    %
    $``\Leftarrow"$. Assume $(\mathfrak{M_3},s)\models \neg C_{i \rightarrow j}\varphi$. By the PCTL$^{\textrm{kc+}}$ semantics, it follows that there exists $s'\in S$ such that $s\approx_{i \rightarrow j}s'$ and $(\mathfrak{M_3},s')\models \neg \varphi$. Consequently, it would never be the case that $(\mathfrak{M_3},s')\models \varphi$ for all $s'\in S$
    such that $s\approx_{i \rightarrow j}s'$. Therefore,
    $1>\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\approx_{i \rightarrow j}s'|}$.
    Now assume $(\mathfrak{M_3},s)\models \neg C_{i \rightarrow j}\neg \varphi$. Therefore, $\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| = 0$ would never be he case as some accessible states should satisfy $\varphi$. Consequently,
    $\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\approx_{i \rightarrow j}s'|}>0$.
    Thus, $0<\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| }{|s \approx_{i \rightarrow j}s'|}<1$. Thus, $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[} (C_{i \rightarrow j}\varphi)$.
\end{itemize}

\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem} [Fulfillment Equivalences] \label{theorem:Fulfiilemt-Equivelances} ~

\begin{enumerate}
\item $(\mathfrak{M_3},s)\models \mathbb{P}_{>0} (Fu(C_{i \rightarrow
j}\varphi))$ iff $(\mathfrak{M_3},s)\models Fu(C_{i \rightarrow
j}\varphi)$ and $s$ is reachable from the commitment state.

\item $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (Fu(C_{i \rightarrow
j}\varphi))$ iff $(\mathfrak{M_3},s)\models \neg Fu(C_{i \rightarrow
j}\varphi)$ or $s$ is not reachable from the commitment state.

\item $(\mathfrak{M_3},s)\models \mathbb{P}_{>0} (Fu(C_{i \rightarrow
G}\varphi))$ iff $(\mathfrak{M_3},s)\models Fu(C_{i \rightarrow
G}\varphi)$ and $s$ is reachable from the commitment state.

\item $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (Fu(C_{i \rightarrow
G}\varphi))$ iff $(\mathfrak{M_3},s)\models \neg Fu(C_{i \rightarrow
G}\varphi)$ or $s$ is not reachable from the commitment state.
\end{enumerate}

\end{theorem}

\begin{proof} %\hspace{0.5cm} \\
The proofs of these equivalences are direct from Proposition
\ref{proposition} and the above semantics.

 \end{proof}

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Model Checking PCTL$^{\textrm{kc+}}$ using Reduction} \label{sec:model-checking-pctlkc+}

In this section, we generalize the model checking technique for
the logic of knowledge and social commitments proposed in
Chapter \ref{cha:PCTLKC} to cover more complex cases, such as group
knowledge and group commitment. As we have seen in the previous
section, the semantics of our new logic PCTL$^{\textrm{kc+}}$ is
defined over an extended version of interpreted systems
$\mathfrak{M_3}$. The idea of our proposed verification technique is
based mainly on reducing the problem of model checking
PCTL$^{\textrm{kc+}}$ to the problem of model checking PCTL. This
however involves two processes. First, we define transformation
rules to transform PCTL$^{\textrm{kc+}}$ model ($\mathfrak{M_3}$) to
an MDP model to be suitable for PRISM, the probabilistic model
checker of PCTL. The solution of an MDP comes in the form of an
``adversary'' \cite{Forejt2011} which is described as a mapping
of states to probability distributions over actions. Second, we
construct a set of rules to reduce PCTL$^{\textrm{kc+}}$ formulae
to PCTL formulae.

In a nutshell, our proposed model checking procedure is as follows. Given $\mathfrak{M_3}=(S,\textbf{P},I,\sim_1, \ldots
,\sim_n,\{\approx_{i \rightarrow j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$, and PCTL$^{\textrm{kc+}}$ formula $\varphi$, we have to define an MDP model $\mathfrak{M_3'}$ = $\mathscr{F}(\mathfrak{M_3})$ and PCTL formula $\mathscr{F}(\varphi)$ using the transformation function $\mathscr{F}$ such that $\mathfrak{M_3} \models \varphi$ iff $\mathscr{F}(\mathfrak{M_3})\models \mathscr{F}(\varphi)$.

\begin{figure}[h]
\centering
\includegraphics[width=15cm, height=9cm]{chap5/img/relation-translation-cha5.eps}
%height=8cm]{figures/1.eps}
\caption{Examples of translating relations in $\mathfrak{M_3}$ into labeled transitions} \label{fig:relation-translation-cha5}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Transforming the Model $\mathfrak{M_3}$} \label{sec:reducing-proposed-model-cha5}

As done in Chapter \ref{cha:PCTLKC}, given an MDP model $\mathfrak{M_3'}$ = $(\mathbb{S}, Act, \textsf{P}_t ,I_i, L)$, a major step in transforming $\mathfrak{M_3}$ into $\mathfrak{M_3'}$ is to define the set of actions $Act$. The idea is to map each relation in $\mathfrak{M_3}$ into a corresponding action in $Act$; more specifically, to translate each relation in $\mathfrak{M_3}$ into a labeled transition in $\mathfrak{M_3'}$. Then, these labels (also called actions) are used to form the set $Act$ in $\mathfrak{M_3'}$. Consequently, the different relations in $\mathfrak{M_3}$ namely, probabilistic transition relations, epistemic accessibility relations, and social accessibility relations, are translated into labeled transitions in $\mathfrak{M_3'}$. Moreover, to interpret the fulfillment of a commitment, we need to add the symmetric closure of the transition resulted from translating the social accessibility relation. Figure \ref{fig:relation-translation-cha5} (where $n$ is the number of agents, $1 \leq i \leq n$, and $1 \leq j \leq n$) explains the process of translating the probabilistic transition relation $\textbf{P}$, epistemic accessibility relations $\sim_i$, and social accessibility relations $\approx_{i \to j}$ into labeled transitions. More precisely, the action $\epsilon$ denotes a transition defined from the probabilistic transition relation $\textbf{P}$, action $\alpha^i$ denotes a transition defined from the epistemic accessibility relation $\sim_i$, action $\beta^{ij}$ denotes a transition defined from the social accessibility relation $\approx_{i \rightarrow j}$, and action $\gamma^{ij}$ denotes a transition added to capture the semantics of the fulfillment of a basic commitment. Likewise, the epistemic accessibility relation $\sim_G^E$, and the social accessibility relation $\approx_{i \rightarrow G}$ are translated in the same way where the action $\alpha_G^E$ denotes a transition defined from the epistemic accessibility relation $\sim_G^E$, action $\beta^{G}$ denotes a transition defined from the social accessibility relation $\approx_{i \rightarrow G}$, and the action $\gamma^{G}$ denotes a transition added to capture the semantics of the fulfillment of a group commitment. Consequently, the model $\mathfrak{M_3'} = (\mathbb{S}, Act, \textsf{P}_t ,I_i, L)$ can now be defined as follows:

\begin{itemize}
\item $\mathbb{S}$=$S$; $I_i$=$I$; $L$=$\nu$.

\item $Act = \{\epsilon \} \cup \{\alpha^1, \alpha^2, \dots, \alpha^n, \alpha_G^E\} \cup \{\beta^{11}, \beta^{12}, \dots, \beta^{nn}, \beta^{G}\} \cup \{\gamma^{11}, \gamma^{12}, \dots, \gamma^{nn}, \gamma^{G}\}$ where $n$ is the number of agents.

\item $\textsf{P}_t$ can be defined as the union of the transitions labeled with $\epsilon$,
 transitions labeled with $\alpha^i$, transitions labeled with $\alpha_G^E$, transitions labeled with $\beta^{ij}$, transitions labeled with $\beta^{G}$, transitions labeled with $\gamma^{ij}$, and transitions labeled with $\gamma^{G}$. The probabilities of transitions labeled with $\epsilon$ are not manipulated but rather inherited from the probabilistic transition function $\textbf{P}$. However, transitions labeled with $\alpha^i$ and emanating from the same state are given equal probabilities which reflect the indistinguishably property of epistemic relations over equivalent states. Thus, the probability of each transition annotated by $\alpha^i$ is equal to the probability of each other transition labeled with $\alpha^i$ emanating from the same state which is calculated by dividing one over the number of transitions labeled with $\alpha^i$. The probabilities of transitions labeled with $\alpha_G^E$, $\beta^{ij}$, $\beta^{G}$, $\gamma^{ij}$, and $\gamma^{G}$ are calculated in the same way. For states $s, s' \in \mathbb{S}$ and  action $\theta \in Act$, the function $\textsf{P}_t$ is defined as follows:
\begin{equation*}
    \textsf{P}_t(s, \theta , s' )=
\begin{cases}
    \textbf{P}(s, s'),          & \textrm{if}  ~~\theta = \epsilon  \\
    \frac{1}{|s\sim_i s'|},     & \textrm{if}  ~~ \theta = \alpha^i\\
    \frac{1}{|s\sim_G^E s'|},     & \textrm{if}  ~~ \theta = \alpha_G^E\\
    \frac{1}{|s\approx_{i \rightarrow j} s'|},   & \textrm{if}  ~~ \theta = \beta^{ij}\\
    \frac{1}{|s\approx_{i \rightarrow G} s'|},   & \textrm{if}  ~~ \theta = \beta^{G}\\
    \frac{1}{|s'\approx_{i \rightarrow j} s|},   & \textrm{if}  ~~ \theta = \gamma^{ij}\\
    \frac{1}{|s'\approx_{i \rightarrow G} s|},   & \textrm{if}  ~~ \theta = \gamma^{G}
    \end{cases}
    \end{equation*}

\end{itemize}

As mentioned earlier, the non-deterministic choices in MDP are
resolved using the adversary by picking one enabled transition at
each state, which induces a DTMC model. Technically speaking, the
adversary is a function from the state set $S$ to the action set
$Act$ such that it chooses in any state $s$ one of the enabled
actions. In particular, we define seven adversaries
($\sigma_\epsilon$, $\sigma_e$, $\sigma_G^E$, $\sigma_c$,
$\sigma_c^G$, $\sigma_f$, $\sigma_f^G$) that are used to define
DTMCs from the obtained MDP model as follows: $\sigma_\epsilon$
captures only the semantics of regular temporal formulae,
$\sigma_e$ captures the semantics of the knowledge formulae,
$\sigma_G^E$ captures the semantics of the operator everyone in
the group knows, $\sigma_c$ captures he semantics of the basic
commitment, $\sigma_c^G$ captures the semantics of group social
commitment, $\sigma_f$ captures the semantics of the fulfillment
of the basic commitment, and $\sigma_f^G$ captures the semantics
of the fulfillment of group commitment. Concretely, we set the
adversary $\sigma_\epsilon$ in such a way that always selects the
transitions labeled by $\epsilon$ at each state in the model. This
results in a DTMC model that captures only probabilistic temporal
transitions inherited from $\textbf{P}$ and ignores all
transitions obtained by translating the various accessibility
relations. The adversary $\sigma_e$ always picks the action
$\alpha^i$ at the state $s$ and then selects the action $\epsilon$
at all following states (i.e., first the transitions resulted from
the accessibility relations $\sim_i$ are considered, and then the
normal transitions), and so on for the other adversaries.

To this end, we introduce our reduction rules that translate each PCTL$^{\textrm{kc+}}$ formula to PCTL formula w.r.t a given adversary.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Reducing PCTL$^{\textrm{kc+}}$ Formulae into PCTL Formulae} \label{sec:reducing-pctlkc-to-pctl-cahp5}

The PCTL$^{\textrm{kc+}}$ formulae are reduced inductively into PCTL as follows:

$\mathscr{F}(p)=p$, if $p$ is an atomic proposition,

$\mathscr{F}(\neg \varphi)= \neg \mathscr{F} (\varphi)$,

$\mathscr{F}(\mathbb{P}_{\bowtie k}(\varphi \vee \psi))=\mathbb{P}_{\bowtie k}(\mathscr{F}(\varphi) \vee \mathscr{F}(\psi))$,

$\mathscr{F}(\mathbb{P}_{\bowtie k}\bigcirc \varphi)=\mathbb{P}_{\bowtie k} \bigcirc \mathscr{F}(\varphi)$,

$\mathscr{F}(\mathbb{P}_{\bowtie k}(\varphi~ U ~ \psi))=\mathbb{P}_{\bowtie k} (\mathscr{F}(\varphi) U \mathscr{F}(\psi))$,

$\mathscr{F}(\mathbb{P}_{\bowtie k}(\varphi~ U^{\leq m} ~ \psi))=\mathbb{P}_{\bowtie k} (\mathscr{F}(\varphi) U^{\leq m} \mathscr{F}(\psi))$,

$\mathscr{F}(K_i ~\varphi)= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))$,

$\mathscr{F}(\mathbb{P}_{\bowtie k} K_i ~\varphi)= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(\varphi))$,

$\mathscr{F}(E_G ~\varphi)= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))$,

$\mathscr{F}(\mathbb{P}_{\bowtie k} E_G ~\varphi)= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(\varphi))$,

$\mathscr{F}(C_{i\rightarrow j} ~\varphi)= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))$,

$\mathscr{F}(\mathbb{P}_{\bowtie k} C_{i\rightarrow j} ~\varphi)= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(\varphi))$,

$\mathscr{F}(C_{i\rightarrow G} ~\varphi)= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))$,

$\mathscr{F}(\mathbb{P}_{\bowtie k} C_{i\rightarrow G} ~\varphi)= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(\varphi))$,

$\mathscr{F}(Fu(C_{i\rightarrow j} ~\varphi))= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(C_{i\rightarrow j} ~\varphi))= \mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$,

$\mathscr{F}(\mathbb{P}_{\bowtie k} Fu(C_{i\rightarrow j} ~\varphi))= \mathbb{P}_{\bowtie k} (\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(C_{i\rightarrow j} ~\varphi))= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$,

$\mathscr{F}(Fu(C_{i\rightarrow G} ~\varphi))= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(C_{i\rightarrow G} ~\varphi))= \mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$,

$\mathscr{F}(\mathbb{P}_{\bowtie k} Fu(C_{i\rightarrow G} ~\varphi))= \mathbb{P}_{\bowtie k} (\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(C_{i\rightarrow G} ~\varphi))= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))))$.\\

To complete the reduction process, each PCTL formula has to be
interpreted over a DTMC model $\mathcal{D}$ =
$(S,\overline{s},\mathbf{P},L)$. This is achieved by indicating
which adversary is associated with which formula. In the
following, $(\mathfrak{M_3'},s)\models_{\sigma_\epsilon} \varphi$
means that the PCTL formula $\varphi$ holds in the model
$\mathcal{D}$ obtained by applying the adversary $\sigma_\epsilon$
at state $s$. The following theorem is a direct consequence of the
definition of $\mathscr{F}$ and can be easily proved by induction
on the structure of the formula.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem}[Transformation Satisfaction]\label{theorem:transf-satisf} \hspace{0.5cm}

Considering the following adversaries: $\sigma_\epsilon$, $\sigma_c$, $\sigma_c^G$, $\sigma_f$, $\sigma_f^G$, $\sigma_e$, and $\sigma_G^E$ (which are DTMCs capturing temporal, commitment, and epistemic formulae in the model $\mathfrak{M_3}$), the following equivalences hold:

$(\mathfrak{M_3},s)\models p ~~~~~~~~~~~~~~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_\epsilon} p$

$(\mathfrak{M_3},s)\models \neg \varphi ~~~~~~~~~~~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s)\models_{\sigma_\epsilon} \neg \mathscr{F}(\varphi)$

$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}(\varphi \vee \psi)
~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_\epsilon}
\mathbb{P}_{\bowtie k} \mathscr{F}(\varphi) \vee
\mathbb{P}_{\bowtie k} \mathscr{F}(\psi) $

$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}\bigcirc\varphi ~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_\epsilon} \mathbb{P}_{\bowtie k} \bigcirc \mathscr{F}(\varphi)$

$(\mathfrak{M_3},s)\models\mathbb{P}_{\bowtie k}(\varphi~ U ~ \psi) ~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_\epsilon} \mathbb{P}_{\bowtie k}(\mathscr{F}(\varphi)~ U ~\mathscr{F}(\psi))$

$(\mathfrak{M_3},s)\models\mathbb{P}_{\bowtie k}(\varphi~ U^{\leq m} ~ \psi) ~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_\epsilon} \mathbb{P}_{\bowtie k}(\mathscr{F}(\varphi)~ U^{\leq m} ~\mathscr{F}(\psi))$

$(\mathfrak{M_3},s)\models K_i \varphi ~~~~~~~~~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s)\models_{\sigma_e} \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$

$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}K_i \varphi ~~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_e} \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi)))$

$(\mathfrak{M_3},s)\models E_G \varphi ~~~~~~~~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s)\models_{\sigma_G^E} \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$

$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}E_G \varphi ~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_G^E} \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi)))$

$(\mathfrak{M_3},s)\models C_{i \rightarrow j}\varphi ~~~~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s)\models_{\sigma_c} \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$

$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}C_{i \rightarrow j}\varphi ~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_c} \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi)))$

$(\mathfrak{M_3},s)\models C_{i \rightarrow G}\varphi ~~~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s)\models_{\sigma_c^G} \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$

$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}C_{i \rightarrow j}\varphi ~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_c^G} \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi)))$

$(\mathfrak{M_3},s)\models Fu(C_{i \rightarrow j}\varphi) ~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_f} \mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$

$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}Fu(C_{i \rightarrow j}\varphi) ~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_f} \mathbb{P}_{\bowtie k} (\mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))))$

$(\mathfrak{M_3},s)\models Fu(C_{i \rightarrow G}\varphi) ~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_f^G} \mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$

$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}Fu(C_{i \rightarrow j}\varphi) ~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_f^G} \mathbb{P}_{\bowtie k} (\mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))))$

\end{theorem}

This theorem emphasizes that each translated PCTL$^{\textrm{kc+}}$
formula must be interpreted over an appropriate DTMC. That is, if
the PCTL$^{\textrm{kc+}}$ formula includes only temporal
operators, then the corresponding PCTL formula is interpreted over
the DTMC obtained by only considering the normal transitions
(i.e., $\sigma_\epsilon$). Moreover, if the formula has the form
of $K_i~\varphi$, then the corresponding PCTL formula is
interpreted over the DTMC obtained by considering first the
transitions resulted from translating epistemic accessibility
relations $\sim_i$ and then the normal transitions, which shows
why the $K$ operator is translated into the next operator
$\bigcirc$. The same intuition holds for the other epistemic and
social formulae.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem} [Soundness and Completeness of
$\mathscr{F}$] \label{soundness-CTLKC+}~\\ Let $\mathfrak{M_3}$ and
$\Phi$ be respectively PCTL$^{\textrm{kc+}}$ model and formula and
let $\mathscr{F}(\mathfrak{M_3})$  and $\mathscr{F}(\Phi)$ be the
corresponding model and formula in PCTL. We have
$\mathfrak{M_3}\models\Phi$ iff $\mathscr{F}(\mathfrak{M_3}) \models
\mathscr{F}(\Phi)$.
\end{theorem}

\begin{proof} %\hspace{0.5cm} \\
To prove the soundness (i.e., the necessary condition) and
completeness (i.e., the sufficient condition) of the proposed
reduction technique, we prove that the following three cases are
sound and complete: $\Phi = K_i \varphi$, $\Phi = C_{i \rightarrow
j} \varphi$ and $\Phi = Fu(C_{i \rightarrow j} \varphi)$. We prove
this by induction on the structure of the formula $\Phi$. The
cases when $\Phi = E_G \varphi$, $\Phi = C_{i \to G} \varphi$, and
$\Phi = Fu(C_{i \to G} \varphi)$ can be proved in a similar way.
The cases of PCTL$^{\textrm{kc+}}$ formulae that are also PCTL
formulae are straightforward.

\begin{itemize}
\item $\Phi = K_i ~\varphi$. We have $(\mathfrak{M_3},s)\models K_i
~\varphi ~\text{iff}~ (\mathfrak{M_3},s') \models \varphi$ for every
$s' \in S ~\textrm{such that}~ s\sim_i s'$. Therefore,
$(\mathfrak{M_3},s)\models K_i ~\varphi ~\text{iff}~
(\mathscr{F}(\mathfrak{M_3}),s) \models \mathscr{F}(K_i~\varphi)$.
We know that $\mathscr{F}(\mathfrak{M_3})= \mathfrak{M_3'}$. Now,
$(\mathfrak{M_3'},s) \models \mathscr{F}(K_i~\varphi)$ iff for every
$s' \in \mathbb{S} ~\textrm{such that}~ (s,\alpha^i,s') \in
\textsf{P}_t$, we have $(\mathfrak{M_3'},s') \models
\mathscr{F}(\varphi)$. However, w.r.t the semantics of $~\sigma_e$
which is a DTMC defined to interpret commitment formulae over
$\mathfrak{M_3'}$, it follows that every infinite path $\pi \in
\Pi^{\sigma_e}(s)$ satisfies that $\pi(1)=s'$ and
$(\sigma_e,\pi(1))\models \mathscr{F}(\varphi)$. Thus,
$(\sigma_e,s)\models \bigcirc\mathscr{F}(\varphi)$ for all $\pi
\in \Pi^{\sigma_e}(s)$. As the path quantifier $A$ is not defined
in PCTL, and we have $\mathbb{P}_{\geq1}$ instead, so we obtain
$(\sigma_e,s)\models
\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$.

\item $\Phi = C_{i \rightarrow j} \varphi$. We have
$(\mathfrak{M_3},s)\models C_{i\rightarrow j}\varphi ~\text{iff}~
(\mathfrak{M_3},s') \models \varphi$ for every $s' \in S
~\textrm{such that}~ s\approx_{i \rightarrow j}s'$. Consequently,
$(\mathfrak{M_3},s) \models C_{i\rightarrow j} \varphi ~\text{iff}~
(\mathfrak{M_3'},s) \models \mathscr{F}(C_{i\rightarrow j}
\varphi)$. It follows that, $(\mathfrak{M_3},s) \models
\mathscr{F}(C_{i\rightarrow j}\varphi)$ iff for every $s' \in
\mathbb{S} ~\textrm{such that}~ (s,\beta^{ij},s') \in
\textsf{P}_t$, we have $(\mathfrak{M_3'},s') \models
\mathscr{F}(\varphi)$. Now, based on the adversary $~\sigma_c$
which is a DTMC defined to interpret commitment formulae over
$\mathfrak{M_3}$, every infinite path $\pi \in \Pi^{\sigma_c}(s)$
satisfies that $\pi(1)=s'$ and $(\sigma_c,\pi(1))\models
\mathscr{F}(\varphi)$. Thus, $(\sigma_c,s)\models
\bigcirc\mathscr{F}(\varphi)$ for all $\pi \in \Pi^{\sigma_c}(s)$.
As the path quantifier $A$ is not defined in PCTL, and we have
$\mathbb{P}_{\geq1}$ instead, so we obtain $(\sigma_c,s)\models
\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$.

\item $\Phi = Fu(C_{i \rightarrow j} \varphi)$. We have
$(\mathfrak{M_3},s)\models Fu(C_{i\rightarrow j}\varphi)$ iff there
exists $s'\in S$ such that $s'\approx_{i \rightarrow j}s~
\text{and~}(\mathfrak{M_3},s')\models C_{i \rightarrow j}\varphi$.
Consequently, $(\mathfrak{M_3},s)\models
\mathscr{F}(Fu(C_{i\rightarrow j}\varphi))$ iff there exists $s'
\in \mathbb{S}$ such that $(s,\gamma^{ij},s') \in \textsf{P}_t$
and $(\mathfrak{M_3'},s') \models \mathscr{F}(C_{i \rightarrow
j}\varphi)$. Now, w.r.t the adversary $\sigma_f$ which is a DTMC
defined to interpret fulfillment formulae over $\mathfrak{M_3}$, we
obtain at least one infinite path $\pi \in \Pi^{\sigma_f}(s)$ that
satisfies $\pi(1)=s'$ and $(\sigma_f,\pi(1))\models
\mathscr{F}(C_{i \rightarrow j}\varphi)$. Since $E$ is equivalent
to $\mathbb{P}_{>0}$ and $\mathscr{F}(C_{i \rightarrow j}\varphi)$
is equivalent to
$\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$, so we obtain
$(\sigma_f,s)\models \mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq
1}(\bigcirc \mathscr{F}(\varphi)))$.
\end{itemize}
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Implementation}\label{sec:implementation-cha5}

We consider the web-based online shopping system \cite{Gomaa2011}
as a case study to evaluate the effectiveness of our proposed
verification technique.

\subsection{Online Shopping System}\label{sec:Online-s-s}

The online shopping system aims at
providing an online shopping environment for customers. Customers
can request to purchase one or more items from the supplier. By
requesting an item, the customer commits towards the supplier to
pay in order for the request to take place. Once the order is
paid, the supplier confirms the order, and commits to deliver the
requested item and enters a planned shipping date. Finally, when
the order is shipped, the customer is notified. Requested item is
either successfully delivered or refund is issued otherwise.

Because of the uncertainty associated to the underlying infrastructures of both commitments (i.e., the internet through which the payment is made and the transport system through which the delivery of purchased goods is done), there is no guarantee that these commitments are going to be fulfilled. Reasoning about and verifying the commitment to pay and the commitment to deliver have to be tackled with uncertainty in mind so that the degree of fulfilling each commitment can be measured, and so on.

We verify the online shopping system by means of
the reduction-based model check technique proposed in Section
\ref{sec:model-checking-pctlkc+}. Figure \ref{fig:Online-ss}
depicts a model for an interaction scenario between one supplier
and one customer. In every experiment, we enlarge the system by increasing the number of customers only. For simplicity, we assume that all customers perform the same commitment, which is the commitment to pay for the requested item, respectively. We also assume that the supplier commits to all customers (i.e. a group commitment) to deliver the requested
items. This allows us to verify both classes of commitment; basic
social commitments and group social commitments.

\begin{figure}%[H]
                \begin{center}
                \includegraphics[width=14cm, height=10cm]{chap5/img/online-s-s.eps}
                %height=9cm]{figures/test}
                \end{center}
                \caption{A model for the case of one supplier and one customer} \label{fig:Online-ss}
%                \label{Stack}
                \end{figure}

\subsection{System Properties}\label{sec:properties}

Properties that capture the probabilistic behavior of the online
shopping system have been verified using PRISM in various
proposals, for instance \cite{Ouchani2014}. In this section,
special emphasis is given to properties related to the concepts of
knowledge and social commitments. Concretely, we verify some
system's properties such as \textit{Safety}, \textit{Liveness}, and \textit{Reachability} that involve probabilistic
knowledge, probabilistic commitments, and combinations of both.
For the case of social commitments, our verification covers both
basic and group social commitments. All defined properties are
expressed in PCTL$^{\textrm{kc+}}$.

\begin{itemize}
\item \texttt{Safety Property:} Verifying formulae expressing this property in the system models ensures avoiding the appearance of bad situations in the real systems. One bad situation that need to be verified is when the (Cus) fulfills his commitment to pay for the requested order but the (Sup) does not commit to deliver the requested item. This situation can be expressed in PCTL$^{\textrm{kc+}}$ as follows: \\
$\varphi_2= \mathbb{P}_{\geq1}\Box\neg[\mathbb{P}_{>0} \Diamond
Fu(C_{cus\to sup} (Pay))\wedge \mathbb{P}_{\geq1}\Box\neg
(C_{sup\to cus} (Deliver))]$

\item \texttt{Liveness Property:} In all computation paths it is always the case that if the customer commits to pay for the requested item, then in the future the customer will eventually make the payment. This can be expressed in PCLT$^{\textrm{kc+}}$ as follows:\\
$\varphi_3= \mathbb{P}_{\geq1}[(C_{cus\to sup} (Pay))\supset \mathbb{P}_{\geq1}\Diamond Fu(C_{cus\to sup} (Pay))]$

\item \texttt{Reachability Property:} One possible example with regard to the online shopping system is that if the customer (Cus) commits towards the supplier (Sup) to pay for the requested item, the state at which the customer can fulfill his commitment should be reached from the initial state. That is, there should be a possibility from the initial state for the customer to reach the fulfilment state. This can be formally expressed in PCLT$^{\textrm{kc+}}$ as follows:\\
$\varphi_1= \mathbb{P}_{>0} \Diamond Fu(C_{cus\to sup} (Pay))$.

\end{itemize}

Furthermore, thanks to the probabilistic model clacking technique,
we can also get the satisfiability of given formulae in terms of
quantitative results. That is, checking whether a given formula
holds in the model with a threshold (at least 0.95\% for example)
is achievable. Let us consider the following examples:

\begin{itemize}
    \item Once the customer fulfills his commitment to pay, he will be aware about the payment with at least 0.95\%.\\
      $\varphi_4 = P_{>0.95}~ Fu (C_{cus\to sup} (Pay)) \supset K_{cus} Pay$

    \item Once the customer fulfills his commitment to pay, the supplier will be aware about the payment  with at least 0.98\%.\\
      $\varphi_5 = P_{>0.98}~ Fu (C_{cus\to sup} (Pay)) \supset K_{sup} Pay$
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Experimental Results}\label{sec:Experimental-results-cha5}

The online shopping system is encoded into the PRISM input
language as follows. Supplier agent (Sup) and Customer agent (Cus)
are mapped into \emph{modules} in the PRISM language. Each agent's
actions are used to determine the behavior of the agent (i.e., his
local states). For example, Supplier's actions (variables) are:
\textit{Accept}: Accept the request, \textit{Reject}: Reject the
request, \textit{Deliver}: Deliver the requested item,
\textit{Receipt}: Send receipt, \textit{Refund}: Refund in case of
not delivery. The global model is obtained by the synchronization
between all modules (agents).

Our implementation was performed on a TOSHIBA laptop equipped with
32-bit Windows XP with 1 GB of RAM and Genuine Intel(R) CPU at 1.6
GHz. Table \ref{Model-Construction-chap5} reports the results of 15
experiments wherein (Exp.\#) denotes the experiment number,
(\#Agent) denotes the number of agents, (\#States) denotes the
number of reachable states, (\#Transitions) denotes the number of
transitions, and (Construction Time) denotes the time needed for
building the simulated model in seconds. \\

First experiment started with only two agents; One supplier (Sup) and one Customer (Cus). In the rest of experiments, we add one more customer (Cus) each time and report the changes occurring in the size of the model and
the time needed for building the model. These results show that (\#States) and (\#Transitions) grow up exponentially as the system is augmented with more agents. However, the (Construction Time) increases polynomially till we reach a point close to the state
explosion, then it grows up dramatically. Figure
\ref{fig:model-time-cha5} shows the increase in the construction
time as more agents join the system. This dramatic change in the
time needed to build the model reflects the fact that the model
size becomes massive.

%\begin{table}[htp][H]
\begin{table}%[H]
\centering \caption{Verification results of the online shopping
system} \label{Model-Construction-chap5}
\resizebox{\textwidth}{!}{ %
\begin{tabular}{|c|c|l|l|c|}
\hline
\texttt{Exp.\#} &   \texttt{\#Agents}    & \texttt{\#States} & \texttt{\#Transitions} & \texttt{Const. Time (s)}\\
\hline\hline
\texttt{Exp.1}   &2             &30            & 74              &0.031\\
\hline
\texttt{Exp.2}   &3             &210           &700              &0.039\\
\hline
\texttt{Exp.3}   &4             &1470          &6102             &0.047\\
\hline
\texttt{Exp.4}   &5           &$1.02*10^{4}$    &$5.10*10^{4}$   &0.063\\
\hline
\texttt{Exp.5}   &6           &$7.20*10^{4}$    &$4.15*10^{5}$   &0.078\\
\hline
\texttt{Exp.6}   &7           &$5.04*10^{5}$    &$3.31*10^{6}$   &0.109\\
\hline
\texttt{Exp.7}   &8           &$3.52*10^{6}$    &$2.60*10^{7}$   &0.189\\
\hline
\texttt{Exp.8}   &9           &$2.47*10^{7}$    &$2.03*10^{8}$   &0.328\\
\hline
\texttt{Exp.9}   &10          &$1.73*10^{8}$    &$1.56*10^{9}$    &0.516\\
\hline
\texttt{Exp.10}  &11          &$1.21*10^{9}$     &$1.19*10^{10}$   &0.765\\
\hline
\texttt{Exp.11}  &12          &$8.47*10^{9}$    &$9.01*10^{10}$   &1.406\\
\hline
\texttt{Exp.12}  &13          &$5.93*10^{10}$   &$6.79*10^{11}$   &2.219\\
\hline
\texttt{Exp.13}  &14          &$4.15*10^{11}$    &$5.09*10^{12}$  &6.094\\
\hline
\texttt{Exp.14}  &15          &$2.91*10^{12}$   &$3.8*10^{13}$    &8.046\\
\hline
\texttt{Exp.15}  &16          &$2.03*10^{13}$  &$2.82*10^{14}$    &13.406\\
\hline
\end{tabular}}
\end{table}

\begin{figure}%[H]
                \begin{center}
                %\includegraphics[width=10cm, height=6cm]{chap5/img/construction-time-cha5.eps}
                \includegraphics[width=10cm, height=6cm]{chap5/img/time5.eps}
                %height=9cm]{figures/test}
                \end{center}
                \caption{Model construction time for the online shopping system} \label{fig:model-time-cha5}
%                \label{Stack}
                \end{figure}

Table \ref{formulae-prism-results-cha5} reports the model checking
results for the defined formulae ($\varphi_1$ to $\varphi_5$) for
the case of two agents (one customer and one supplier). All
formulae hold in the model as expected, which reflects the success
of our proposed model checking technique in verifying the system
properties expressed using the probabilistic logic
PCTL$^{\textrm{kc+}}$. Moreover, as shown in Table
\ref{formulae-prism-results-cha5}, although the model checking
time varies from one formula to another, it is still short
compared to the time needed for building the model.

For scalability purposes, starting from experiment \#2, we re-write the above-defined formulae in a parameterized form as follows:

$\varphi_1'= \mathbb{P}_{>0} \Diamond \bigwedge\limits_{i=1}^n Fu(C_{cus_i\to sup} (Pay_i))$.

$\varphi_2'= \mathbb{P}_{\geq1}\Box\neg[\mathbb{P}_{>0} \Diamond \bigwedge\limits_{i=1}^n
Fu(C_{cus_i\to sup} (Pay_i))\wedge \mathbb{P}_{\geq1}\Box\neg
(C_{sup\to cus_i} (Deliver_i))]$

$\varphi_3'= \mathbb{P}_{\geq1}[\bigwedge\limits_{i=1}^n (C_{cus_i\to sup} (Pay_i))\supset \mathbb{P}_{\geq1}\Diamond Fu(C_{cus_i\to sup} (Pay_i))]$

$\varphi_4' = P_{>0.95}~ \bigwedge\limits_{i=1}^n Fu (C_{cus_i\to sup} (Pay_i)) \supset K_{cus_i} Pay_i$

$\varphi_5' = P_{>0.98}~ \bigwedge\limits_{i=1}^n Fu (C_{cus_i\to sup} (Pay_i)) \supset K_{sup}
Pay_i$\\
%
where $n$ is the number of agents in the experiment.

\begin{table}%[H]
\centering \caption{Results of model checking some properties for the online shopping system} \label{formulae-prism-results-cha5}
\begin{tabular}{|c|c|c|}
\hline
\texttt{Formulae} &   \texttt{Results}    & \texttt{Time for MC (Sec.)} \\
\hline\hline
$\varphi_1$                &true           &0.06  \\
\hline
$\varphi_2$                &true           &0.13  \\
\hline
$\varphi_3$                &true           &0.11  \\
\hline
$\varphi_4$                &true           &0.06  \\
\hline
$\varphi_5$                &true           &0.07  \\
\hline
\end{tabular}
\end{table}

To be able to verify group social commitments, which is one of the
main motivations of this chapter, we need models of one supplier
agent interacting with two or more customer agents by means of
social commitments. Table \ref{formulae-prism-group-comm-cha5}
reports the results of verifying group social commitments for
experiment \#2 and experiment \#3 using the proposed
reduction technique. In experiment \#2, we have one supplier (Sup) committing to two customers (Cus$_1$) and (Cus$_2$) to deliver the goods. The commitment should be fulfilled in the future to meet the liveness property. Likewise, in experiment \#3, we have one supplier (Sup) committing to three customers (Cus$_1$), (Cus$_2$), and (Cus$_3$) to deliver the requested items.

\noindent $\varphi_6= \mathbb{P}_{\geq1}[(C_{sup \to \{cus_1,cus_2\}} (Deliver))\supset \mathbb{P}_{\geq1}\Diamond Fu(C_{sup \to \{cus_1,cus_2\}} (Deliver))]$

\noindent $\varphi_7= \mathbb{P}_{\geq1}[(C_{sup \to \{cus_1,cus_2,cus_3\}} (Deliver))\supset \mathbb{P}_{\geq1}\Diamond Fu(C_{sup \to \{cus_1,cus_2,cus_3\}} (Deliver))]$

\noindent We were also successful in verifying formulae expressing the interaction between knowledge and group social commitments for experiment \#2 and experiment \#3 as shown below.

\noindent $\varphi_8 = \mathbb{P}_{\geq1}[Fu (C_{sup \to \{cus_1,cus_2\}} (Deliver)) \supset K_{cus_1} (Deliver) \wedge  K_{cus_2} (Deliver)$]

\noindent $\varphi_9 = \mathbb{P}_{\geq1}[Fu (C_{sup \to \{cus_1,cus_2,cus_3\}} (Deliver)) \supset K_{cus_1} (Deliver) \wedge  K_{cus_2} (Deliver) \wedge  K_{cus_3} (Deliver)$]\\

Where, $\varphi_8$ states that the fulfilment of a group commitment (the commitment from $sup$ to $cus_1$ and $cus_2$ to deliver) implies that every creditor in the group will know about the content of the commitment (i.e., $cus_1$ and $cus_2$ will know about the delivery). Similarly, $\varphi_9$ states the same meaning in the case when $sup$ fulfills its commitment to three customers.

\begin{table}[htp]
\centering \caption{Model checking group commitment formulae} \label{formulae-prism-group-comm-cha5}
\begin{tabular}{|c|c|c|c|}
\hline
\texttt{Exp.\#}  &\texttt{\#Agents}  &\texttt{Formulae} &\texttt{Results} \\
\hline\hline
Exp.2            & 1 Sup, 2 Cus      &$\varphi_6$           &true  \\
\hline
Exp.3            & 1 Sup, 3 Cus      &$\varphi_7$           &true  \\
\hline
Exp.2            & 1 Sup, 2 Cus      &$\varphi_8$           &true  \\
\hline
Exp.3            & 1 Sup, 3 Cus      &$\varphi_9$           &true  \\
\hline

\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Summary}\label{sec:conclusion}

In this chapter, we introduced a formal approach for specifying and
verifying the interactions between basic (individual) and group social commitments and knowledge in probabilistic MASs. The
proposed approach encompasses three main parts. In the first
part, we presented a new probabilistic logic of knowledge and
commitments (PCLT$^{\textrm{kc+}}$). The expressive power of
PCLT$^{\textrm{kc+}}$ outperforms those of existing logics because
of its ability to express and specify not only the concepts of
knowledge and social commitments independently, but also their
interactions in the presence of uncertainty. Also, being enriched
by operators for the group knowledge and group commitments,
PCLT$^{\textrm{kc+}}$ allows handling more complicated commitment
scenarios with respect to the number of participating agents. We
categorized social commitments into two classes based on the
number of participating agents; basic social commitment (the
common one-to-one scheme) and group social commitment (one-to-many
scheme). We then presented a formal semantics for the group social
commitment. With such a classification of social commitments, we
gain an insight into different ways to utilize commitments among
communicating parties. In contrast, exiting solutions for social commitments restrict themselves to the common one-to-one commitment scheme.

In the second part, we proposed a sound and complete reduction-based model checking technique for the new logic. The proposed technique consists of reducing the problem of model checking PCLT$^{\textrm{kc+}}$ to the problem of model checking PCTL. The soundness and completeness of the reduction technique were proven. Finally, in the third part, we used the
PRISM tool to implement our reduction technique and check
PCLT$^{\textrm{kc+}}$ formulae by checking their corresponding
PCTL formulae without adding new computation cost. In terms of scalability, we showed that our reduction technique is scalable as we were
successfully able to apply it on models of size up to $10^{13}$
states and $10^{14}$ transitions. To conclude, the two main findings of this chapter are:
 \begin{enumerate}
 \item Simply combining a probabilistic logic of knowledge and a probabilistic logic of commitments to capture the interactions between the concept of knowledge and social commitments in probabilistic MASs is not quite working as excepted.
 \item Representing group social commitments and the interactions between group social commitments and knowledge in the presence of uncertainty become attainable by the use of our proposed framework.
 \end{enumerate}

### 2015-04-05 thesis/others/khalid/chap6/chap6.tex
added thesis

\chapter{Conclusion and Future Work}\label{Chap5:Conclusion}
%********************************************************************
%This chapter concludes the thesis. First, we give a summary of the main contributions of the thesis. Second, we present some hints for future directions.

%********************************************************************
\section{Conclusion}

In this thesis, we have put forward a formal framework for agent communication using a commitment-based approach in order to enable effective agent interactions in open, heterogeneous, and dynamic systems when
uncertainty matters. The main purpose of this framework is to essentially specify and reason about social commitments in probabilistic settings, so they can be formally verified. As an improvement over the existing solutions, our proposed framework targets systems exhibiting probabilistic behavior and considers commitments among a group of agents. The framework is composed of three main components. First, we presented a new probabilistic approach for tackling social commitments in the presence of uncertainty. To specify probabilistic social commitments, we defined a new logic called the probabilistic logic of commitments (PCTLC). Our new logic is interpreted over a new extended version of probabilistic interpreted systems. Furthermore, we introduced a new reduction-based model checking technique for the new logic and implemented it on top of the PRISM model checker. Then, by using the proposed reduction technique, we showed how to evaluate some systems' properties representing probabilistic social commitments -- expressed in terms of the new logic -- against system design models obtained using our extended version of probabilistic interpreted systems.

The second component of our framework focused on the interaction between knowledge and social commitments in probabilistic MASs. We introduced a new logic called the probabilistic logic of knowledge and commitment (PCTL$^{kc}$) to represent and reason about such interactions. PCTL$^{kc}$ logic is interpreted over a new version of probabilistic interpreted systems that has epistemic accessibility relations and social accessability relations at its core. To verify the new logic, we developed a verification technique based on model checking and implemented it using the PRISM tool. Our interest in the first and second contributions was focused on the common two-agent commitment scenarios (i.e. agent-to-agent scheme).

In the third part of the framework, we improved and extended our work in the second part as follows:

\begin{enumerate}

\item We refined and improved PCTL$^{kc}$ to overcome the inconsistency problem appeared when taking the recent work of Al-Saqqar et al. \cite{Al-Saqqar2014a} into consideration. Therefore, in this part, we adopted CTLKC$^+$ \cite{Al-Saqqar2014a} as a basis for our new logic and combined it with PCTL.

\item We extended the scope of interacting agents from agent-to-agent to agent-to-many. This allowed us to investigate different commitment schemes such as the case of committing to multiple agents. In this respect, we defined an adequate semantics for group social commitments for the first time in the literature.
\end{enumerate}

\noindent Based on the new semantics of group social commitments and the consistent logic of knowledge and commitment presented in \cite{Al-Saqqar2014a}, we presented a new probabilistic logic of knowledge and commitment called (PCTL$^{\textrm{kc+}}$). The new logic accommodates new operators for group social commitments and group knowledge in addition to the modalities already found in PCTL$^{kc}$. The expressiveness power of  PCTL$^{\textrm{kc+}}$ outperforms those of existing logics because of its ability not only to capture and express the combinations of knowledge and social commitments in the presence of uncertainty, but also to express formulae involving group social commitments. Formulae of PCTL$^{\textrm{kc+}}$ are interpreted over a new extended version of probabilistic interpreted systems. Our new version of interpreted systems integrates a modified version of social accessabilities that accounts for basic social commitments, group social commitments, and knowledge. To evaluate the new logic (PCTL$^{\textrm{kc+}}$), we proposed a reduction-based model checking technique and implemented it on top of PRISM.

Furthermore, we proved the soundness of all proposed verification techniques. Also, using different case studies we were successfully able to demonstrate the effectiveness and usefulness of our proposed work and evaluate the scalability of the introduced verification techniques.

Finally, as the proposed framework permits addressing probabilistic social commitments as well as their interaction with knowledge when the scope of interacting parties moves beyond the common one-to-one scheme, we believe that it will advance the literature of agent communication and help MASs designers build more effective and efficient systems.

%To conclude, we believe that the proposed framework
%********************************************************************
%* Section 7: Future Work
%********************************************************************
\section{Future Work}

There is still a long way to go in order to develop a comprehensive framework for probabilistic social commitments in MASs. In the future, we plan to extend our work by investigating several directions.

First, time complexity and space complexity of our proposed verification techniques are not analysed yet. Therefore, we intend to compute the complexity of the proposed reduction techniques of the three components.

Second, we are planning to extend our framework to support more commitment schemes such as many-to-one and many-to-many commitments. This is extremely important because in real settings there exist situations where performing such commitment scenarios contributes towards improving the efficiency of MASs.

Third, integrating more commitment actions (such as assign, delegate, ..etc) \cite{Singh2000} are of a great interest to investigate. This helps ensure that all possible commitment operations employed in probabilistic environments are adequately dealt with.

Forth, we intend to explore the interaction between social commitments and norms in probabilistic systems.

Fifth, another direction that we intend to explore is the probabilistic conditional social commitments. Conditional social commitment is still in  its infancy \cite{Kholy2014} and investigating it in systems exhibiting stochastic behavior is an open point for research.

Finally, we plan to extend the PRISM model checker to accommodate our new operators (i.e. commitment and group commitment) and then develop dedicated verification algorithms for the proposed logics and implement them directly into PRISM. So doing will allow us to compare the results obtained from the indirect method (reduction-based techniques) with the results of the direct method (dedicated algorithms).

\newpage
\textbf{Publications in refereed journals and conferences}

\textbf{Journals}

\begin{itemize}
\item K. Sultan, J. Bentahar, M. El-Menshawy, "Model Checking Probabilistic Social Commitments for Intelligent Agent Communication", Journal of Applied Soft Computing, Elsevier, 2014.

\item K. Sultan, J. Bentahar, W. Wan, F. Al-Saqqar, "Modeling and Verifying Probabilistic Multi-  Agent Systems using Knowledge and Social Commitments", Journal of Expert Systems with Applications, Elsevier, 2014.

\item F. Al-Saqqar, J. Bentahar, K. Sultan, M. El-Menshawy, "On the Interaction between Knowledge and Social Commitments in Multi-Agent Systems", Applied Intelligence Journal, Springer, 2014.

\item F. Al-Saqqar, J. Bentahar, K. Sultan, W. Wan, E. Khosrowshahi
Asl, "Model Checking Temporal Knowledge and Commitments in Multi-Agent Systems Using Reduction", Simulation Modeling Practice and Theory Journal, Elsevier, 2015.
\end{itemize}

\textbf{Conferences}

\begin{itemize}

\item K. Sultan, J. Bentahar, O. Marey, "A Probabilistic Logic to Reason about the Interaction between Knowledge and Social Commitments in MASs", In the Proc. of The 13th International Conference on Intelligent Software Methodologies, Tools, and Techniques (SOMET\_14), Langkawi, Malaysia, 2014.

\item M. Mbarki, O. Marey, J. Bentahar, K. Sultan,  "Agent Types and Adaptive Negotiation Strategies in Argumentation-Based Negotiation", In the Proc. of the IEEE International Conference on Tools with Artificial Intelligence (ICTAI), Limassol, Cyprus, 2014.

\item K. Sultan, M. El-Menshawy, J. Bentahar, "Reasoning about Social Commitments in the Presence of Uncertainty", In the Proc. of The 12th International Conference on Intelligent Software Methodologies, Tools, and Techniques (SOMET\_13), Budapest, Hungary, 2013.
\end{itemize}

\textbf{Articles in process for publication in refereed journals}

\begin{itemize}
\item K. Sultan, J. Bentahar, R. Mizouni, "Model Checking the Interaction Between Individual and Group Knowledge and Commitments in Probabilistic Multi-Agent Systems", Engineering Applications of Artificial Intelligence, Elsevier, (submitted: August 2014).
\item O. Marey, J. Bentahar, E. Khosrowshahi Asl, K. Sultan, R. Dssouli, "Decision Making under Subjective Uncertainty in Argumentation-Based Negotiation.  Ambient Intelligence and Humanized Computing, (submitted: November 2014).
\end{itemize}

%. Abstracting tokens and control paths

%This thesis can be extended in the following directions.
% \begin{itemize}
%   \item Extend our semantic to support more SysML features,
%   \item We intend to formalize SysML and UML daigrams such as state machines and sequence diagrams,  then,
%   \item Extend our framework to support them
%   \item Extend the specification framework to handle the reliability requirements and prove formally the soundness of the proposed framework.
%   \item we intend to transform a SysML activity diagram to its fractal form in order to benefit from our abstraction framework. This helps in the abstraction/refinement process of UML/SysML diagrams. Second, we extend our framework to handle other UML and SysML models such as state machine and sequence diagrams.
%  \item  Finally, we intend to investigate reducing the property within the model and applying our approach on different real systems.
%  \item Abstracting tokens and control paths.
%  \item Framework Extension: Extend our security verification framework to support other SysML behavioral diagrams: State machine, and Sequence diagrams,
%  \item Ensure the equivalence between SysML behavioral diagrams,
%  \item Extract the syntax from the metamodels.
%  \item Studying the completeness of system completeness.
%  \item Compositional verification for other operators.
%  \item we plan to extend our framework to handle more compositional verification techniques like assume-guaranty.
%  \item we explore other abstraction approaches especially data abstraction targeting more system features like time and data.
%  \item Finally, we intend to investigate reducing the property within the model.
%   \item Finally, we want to validate our approach on cyber-forensics systems.
% \end{itemize}

%In future, we would like to extend our work by investigating several directions.
%First, we intend to build our implementation within PRISM model checker. Second, we plan to extend our framework to handle more compositional verification techniques like assume-guaranty. Next, we explore other abstraction approaches especially data abstraction targeting more system features like time and data.

### 2015-04-05 thesis/thesis/Appendix.tex
added thesis

\chapter{Chapiter 3}
In this Appendix, we present proofs of the previous theorems and propositions. %For more details, the complete proofs are accessible from this link\footnote{ http://users.encs.concordia.ca/$\sim$s\_oucha}.

\begin{lemma}[Soundness]
The mapping algorithm $\Gamma$ is sound, \ie $M_\mathcal{A}\sqsubseteq_{\mathscr{R}}M_\mathcal{P}$.
\end{lemma}
\begin{proof}
To prove $M_\mathcal{A}\sqsubseteq_{\mathcal{R}}M_\mathcal{P}$, we follow a structural induction reasoning on NuAC terms and their related PRISM terms. For that, let $s,s'\in S(M_\mathcal{A})$ and $t,t'\in S(M_\mathcal{P})$. We distinguish the following cases where $L(s)$ takes different values:
\begin{enumerate}
  \item $L(s)=\labeled{l}{\marked{x}\activityedge\mathcal{N}}$ such as $x\in\{\iota,a,a!v\}\Rightarrow\exists s\stackrel{l}{\longrightarrow_{1}}s',~L(s')=\labeled{l}{x\activityedge\marked{\mathcal{N}}}$.\\
      For $L(t)=\Gamma(L(s))$, we have $L(t)=\langle L(x),\neg L(\mathcal{N})\rangle$ then $\exists t\stackrel{l}{\longrightarrow_{1}}t'$ where  $L(t')=\langle\neg L(x), L(\mathcal{N})\rangle$.
  \item $L(s)=\labeled{l}{\marked{\varodot}}$ then $\exists s\stackrel{l}{\longrightarrow_{1}}s'$ such as $L(s')=\lvert\mathcal{A}\rvert$. For $L(t)=\Gamma(L(s))$, we have  $L(t)=\langle l \rangle$ then $\exists t\stackrel{l}{\longrightarrow_{1}}t'$ where $\forall l_i\in\mathcal{L}: L(t')=\langle\cdots,\neg l_i,\cdots\rangle$. %It is clear that $\mu(s)=\mu(t)=1$ then $s\sqsubseteq_{\mathcal{R}}t$.
  \item $L(s)=\labeled{l}{\marked{\varotimes}}$ then $\exists s\stackrel{l}{\longrightarrow_{1}}s'$ such as $L(s')=\labeled{l}{\varotimes}$. For $L(t)=\Gamma(L(s))$, we have  $L(t)=\langle l\rangle$ then $\exists t\stackrel{l}{\longrightarrow_{1}}t'$ where $L(t')=\langle\neg l\rangle$. %It is clear that $\mu(s)=\mu(t)=1$ then $s\sqsubseteq_{\mathcal{R}}t$.
  \item $L(s)=\labeled{l}{}\nmarked{F(\mathcal{N}_{1},\mathcal{N}_{2})}{m}$ then $\exists s\stackrel{l}{\longrightarrow_{1}}s'$ such as $L(s')=\labeled{l}{}\nmarked{F(\marked{\mathcal{N}_{1}},\marked{\mathcal{N}_{2}})}{m-1}$. For $L(t)=\Gamma(L(s))$, we have  $L(t)=\langle l,\neg l_{\mathcal{N}_{1}},\neg l_{\mathcal{N}_{2}}\rangle$ then $\exists t\stackrel{l}{\longrightarrow_{1}}t'$ where $\forall l: L(t')=\langle\neg l, l_{\mathcal{N}_{1}}, l_{\mathcal{N}_{2}}\rangle$. %It is clear that $\mu(s)=\mu(t)=1$ then $s\sqsubseteq_{\mathcal{R}}t$.
\end{enumerate}

From the obtained results, we found that $\mu(s)=\mu(t)=1$ then $s\sqsubseteq_{\mathcal{R}}t$. In addition, the unique initial state of $\mathcal{M_{A}}$ is always corresponding to the unique initial state in $\mathcal{M_{P}}$. By following the same style of proof, we find that $\mathcal{M_{A}}\sqsubseteq_{\mathcal{R}}\mathcal{M_{P}}$, which confirms that Theorem \ref{th:ver} holds.

\end{proof}
\begin{proposition}[PCTL Preservation]\label{Th:VerPctlPreservation}
For two PAs $M_\mathcal{A}$ and $M_\mathcal{P}$ such that $\Gamma(\mathcal{A})=\mathcal{P}$ where $M_\mathcal{A}\sqsubseteq_{\mathscr{R}}M_\mathcal{P}$. For a $PCTL$ property $\phi$, then: $(M_\mathcal{A}\models\phi)\Leftrightarrow(M_\mathcal{P}\models\phi)$.
\end{proposition}
\begin{proof}
%Our abstraction is sound and the proof is provided in Appendix \ref{sub:Proofsound}.

To prove the preservation of PCTL properties, we follow an inductive reasoning on the PCTL structure. While $M_\mathcal{A}\sqsubseteq_{\mathcal{R}}M_\mathcal{P}$, for each PCTL operator $\zeta\in\{\neg,\wedge,\mathrm{X},\mathrm{U}^{\leq\,k},\mathrm{U},\mathrm{P}_{\bowtie\,p}\}$ we have:
$M_\mathcal{A}\models\zeta \Longleftrightarrow M_\mathcal{P}\models\zeta$ which means:

$(M_\mathcal{A}\models\phi_{PCTL})\Longleftrightarrow(M_\mathcal{P}\models\phi_{PCTL})$.

\end{proof}

\chapter{Chapiter 4}
\section{Motivation Proof}\label{sub:motivation}
Let $\mathcal{A}$ be a SysML activity diagram and $\widehat{\mathcal{A}}$ is its abstracted model obtained by the algorithm $\delta$ with respect to a PCTL property  $\phi$. The complexity of checking $\phi$ takes into consideration the complexity of the abstraction algorithm $\delta$, the complexity of the mapping algorithm of the obtained diagram into PRISM code and the complexity of the probabilistic model checking procedure. The both first algorithms are a DFS-based procedures with a time complexity of $\mathcal{O}(|\mathcal{A}|)$, the third one is of $\mathcal{O}(Poly(|M_{\mathcal{A}}|)\times \upsilon_{max}\times |\phi|)$ such that
$\upsilon_{max}=max\{k:\phi_1\mathrm{U}^{\leq\,k}\phi_2~occurs~in~\phi\}$ and
$M_{\mathcal{A}}\equiv\mathscr{S}(\mathcal{A})$. Hence, Equation \ref{eq:con}  and  Equation \ref{qqq} present the complexity with and without abstraction, respectively.
\begin{align}
%\begin{array}{llll}
A&=\mathcal{O}(\mathcal{A}\models p)=\mathcal{O}(|\mathcal{A}|)+O(Poly(|M_{\mathcal{A}}|)\times \upsilon_{max}\times |\phi|)\label{eq:con}\\
B&=\mathcal{O}(\mathcal{A}\models p)=\mathcal{O}(|\mathcal{A}|)+\mathcal{O}(|\widehat{\mathcal{A}}|)+\mathcal{O}(Poly(|M_{\widehat{\mathcal{A}}}~~|)\times \upsilon_{max}\times |\phi|)\label{qqq}
%\end{array}
\end{align}

By comparing the equations \ref{eq:con} and \ref{qqq}, we have:
\begin{equation*}
\begin{array}{rcll}
%B<A&\Leftrightarrow&\mathcal{O}(|\mathcal{A}|)+\mathcal{O}(|\widehat{\mathcal{A}}|)+\mathcal{O}(Poly(|M_{\widehat{\mathcal{A}}}~~|)\times \upsilon_{max}\times |\phi|)<\mathcal{O}(|\mathcal{A}|)+Poly(|M_{\mathcal{A}}|)\times \upsilon_{max}\times |\phi|)\\
B<A&\Leftrightarrow&|\mathcal{A}|+|\widehat{\mathcal{A}}|+Poly(|M_{\widehat{\mathcal{A}}}~~|)\times \upsilon_{max}\times |\phi|<|\mathcal{A}|+Poly(|M_{\mathcal{A}}|)\times \upsilon_{max}\times |\phi|\\
&\Leftrightarrow&|\widehat{\mathcal{A}}|+Poly(|M_{\widehat{\mathcal{A}}}~~|)\times \upsilon_{max}\times |\phi|<Poly(|M_{\mathcal{A}}|)\times \upsilon_{max}\times |\phi|\\
\\
&\Leftrightarrow&\frac{|\widehat{\mathcal{A}}|}{Poly(|M_{\mathcal{A}}|)\times \upsilon_{max}\times |\phi|}+\frac{Poly(|M_{\widehat{\mathcal{A}}}~~|)}{Poly(|M_{\mathcal{A}}|)} <1\\
\\&\Leftrightarrow&\frac{Poly(|M_{\widehat{\mathcal{A}}}~~|)}{Poly(|M_{\mathcal{A}}|)} \lesssim 1 (while \frac{|\widehat{\mathcal{A}}|}{Poly(|M_{\mathcal{A}}|)\times \upsilon_{max}\times |\phi|}\simeq0)\\
\end{array}
\label{eq:abs}
\end{equation*}
From this result of comparison, we conclude that applying the abstraction is useful for any model.\qed
\setcounter{proposition}{0}

\section{The Abstraction Approach Proof}\label{sub:AbstProof}

\begin{proposition}%\label{Prop:prop1}
Let $\mathcal{A}= \mathcal{A}_{0}\uparrow_{a_{1}}\ldots\uparrow_{a_{k}}\mathcal{A}_{k}$ be a SysML activity diagram with $k$ call behaviors and $\phi$ be a PCTL property. Then: \begin{center}$\forall i\leq k: \mathcal{A}_{0}\uparrow_{a_{1}}\ldots\uparrow_{a_{i}}\mathcal{A}_{i}\models\phi~\Rightarrow~\mathcal{A}\models\phi$.\end{center}
\end{proposition}

\begin{proof}
The proof of this proposition follows an induction reasoning on PCTL structure by taking into consideration the size of call behaviors composition ``$k$''.
\begin{enumerate}
  \item Case of $\phi=\phi_1\mathrm{U}\phi_2$\\
   Let $i< k$: $\mathcal{A}_{0}\uparrow_{a_{1}}\ldots\uparrow_{a_{i}}\mathcal{A}_{i}\models\phi$ $~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$(Assumption)\\
$~~~~~~~~~~~~~~~~~~~~~\Leftrightarrow \exists m,~\forall j<m:\pi(j)\models_{Adv}\phi_{1}\wedge\pi(m)\models_{Adv}\phi_{2}$. $~~~~~~~~~~~~~~~~~~~~~~~~~~$(Definition)\\
By calling a new behavior $\mathcal{A}_{i+1}$, the satisfaction path $\pi$ will not be changed while $a_{i+1}$ stays unchanged during the execution of $\mathcal{A}_{i+1}$ then we have:\\ $ \exists m',~\forall j'<m':\pi(j')\models_{Adv}\phi_{1}\wedge\pi(m')\models_{Adv}\phi_{2}$
$\Leftrightarrow ~\mathcal{A}_{0}\uparrow_{a_{1}}\ldots\uparrow_{a_{i+1}}\mathcal{A}_{i+1}\models\phi$.\\
By following the same kind of construction up to $k$ behavior, we will have:\\ $\mathcal{A}_{0}\uparrow_{a_{1}}\ldots\uparrow_{a_{k}}\mathcal{A}_{k}\models\phi$ which means: \\$~~~~~\qquad\qquad\exists m'',~\forall j''<m'':\pi(j'')\models_{Adv}\phi_{1}\wedge\pi(m'')\models_{Adv}\phi_{2}$.
 Then: $\mathcal{A}\models\phi_1\mathrm{U}\phi_2$.
\\ By following the same kind of proof, we deduce the satisfaction relation for    $\phi_1\mathrm{U}^{\leq\,k}\phi_2$ and $\mathrm{X}\phi$ cases.
  \item Case of $\phi=\phi_1\mathrm{U}^{\leq\,l}\phi_2$\\
When $j''=j$ and $m''=m$ after calling a new behavior then $\mathcal{A}\models\phi_1\mathrm{U}^{\leq\,l}\phi_2$.
Else, $\mathcal{A}\models\phi_1\mathrm{U}^{\leq\,l'}\phi_2 $ such that $l'\geq l$
 \item Case of $\mathrm{X}\phi$\\
 While $a_{i+1}$ stays true during the execution of $\mathcal{A}_{i+1}$ then the next operator is preserved.
\end{enumerate}
\end{proof}
\begin{proposition}%\label{Prop:prop2}
Let $\mathcal{A}= \mathcal{A}_{0}\uparrow_{a_{1}}\ldots\uparrow_{a_{k}}\mathcal{A}_{k}$ be a SysML activity diagram with $k$ call behaviors, $\mathcal{A}_{id}$ is the identity element for ``$\uparrow$'' operator and $\phi$ be a PCTL property. For a proposition $\alpha$, we have the following:
\begin{center}
  $\forall 1\leq i\leq k,~\alpha\notin(\sum_{\phi}\cap\sum_{\mathcal{A}_i}):[\mathcal{A}_{i}= \mathcal{A}_{id}\wedge (\mathcal{A}_{0}\uparrow_{a_{1}}\ldots\uparrow_{a_{k}}\mathcal{A}_{k})\models\phi]\Rightarrow[\mathcal{A}\models\phi]$.
\end{center}
\end{proposition}
\begin{proof}
The proof is similar to that one of Proposition \ref{Prop:prop1}, for both cases of until and next operators.  For the case of bounded until, the satisfaction of $\phi$ is not deduced while some steps are mimicked by the identity element. But, we can infer the satisfaction of two important properties are:
      \begin{enumerate}
        \item   $\forall 1\leq i\leq k,~\alpha\notin(\sum_{\phi}\cap\sum_{\mathcal{A}_i}):$\\$~~~~~~~~~~~~~~~~~[\mathcal{A}_{i}= \mathcal{A}_{id}\wedge (\mathcal{A}_{0}\uparrow_{a_{1}}\ldots\uparrow_{a_{k}}\mathcal{A}_{k})\models\phi_1\mathrm{U}^{\leq\,l}\phi_2]
            \Rightarrow\mathcal{A}\models\phi_1\mathrm{U}\phi_2$.
        \item   $\forall 1\leq i\leq k,~\alpha\notin(\sum_{\phi}\cap\sum_{\mathcal{A}_i}):$\\ $~~~~~~~~~~~~~~~~~~  [\mathcal{A}_{i}= \mathcal{A}_{id}\wedge (\mathcal{A}_{0}\uparrow_{a_{1}}\ldots\uparrow_{a_{k}}\mathcal{A}_{k})\models\phi_1\mathrm{U}^{\leq\,l}\phi_2]
            \Rightarrow\exists l'\geq l:\mathcal{A}\models\phi_1\mathrm{U}^{\leq\,l'}\phi_2$.
      \end{enumerate}
\end{proof}

\section{Complexity}\label{app:Comp}

\begin{proposition}[Application Order]
Let ``$\mathcal{A}$'' be a NuAC term and ``$\phi$'' be a PCTL property, we have:
$\Psi(\Upsilon(\Psi(\mathcal{A}),\phi))\equiv\Psi(\Upsilon(\mathcal{A},\phi))$.
\end{proposition}
\begin{proof}
Let $M_{1}=\Psi(\mathcal{A}), M_{2}=\Upsilon(M_{1},\phi)$ and $M_{3}=\Psi(M_{2})$, we have:
\begin{enumerate}
  \item $M_{1}=\Psi(\mathcal{A})\Leftrightarrow$ if $\exists \labeled{l}{\mathcal{N}_{k}\activityedge\mathcal{N}_{m}}\in\mathcal{A}$, then $\labeled{l}{\mathcal{N}_{k}\activityedge\mathcal{N}_{m}}$ is replaced by $\labeled{l}{\mathcal{N}_{km}}$ if one of the control merging rules is satisfied.
  \item $M_{2}=\Upsilon(M_{1},\phi)\Leftrightarrow$ $\forall\!a\notin\Sigma_\phi:\Upsilon(\nmarked{\labeled{l}{a}}{n}\activityedge\mathcal{N},\phi)=\nmarked{\labeled{l}{\epsilon}}{n}\activityedge\mathcal{N}$. In fact, $\Upsilon$ produces new consecutive control nodes and preserves the diagram structure.
  \item $M_{3}=\Psi(M_{2})\Leftrightarrow$ if $\exists \labeled{l}{\mathcal{N}_{i}\activityedge\mathcal{N}_{j}}\in\mathcal{A}$, then $\labeled{l}{\mathcal{N}_{i}\activityedge\mathcal{N}_{j}}$ is replaced by $\labeled{l}{\mathcal{N}_{ij}}$. The minimization rules are applied on the initial and the produced one by $\Psi$ function.
\end{enumerate}
It is clear that the first step has no effect on the second one. In addition, applying $\Psi$ two times successively is equivalent to applying it once. Thus, the proposition holds.
\end{proof}

\section{Abstraction Soundness Proof}\label{sub:Proofsound}
\setcounter{proposition}{3}
\setcounter{lemma}{0}

\begin{lemma}[$\Upsilon$-Soundness]%\label{prop:sound1}
The abstraction algorithm $\Upsilon$ is sound, \ie $M_\mathcal{{A}}\sqsubseteq_{\mathscr{R}_\Upsilon}M_\mathcal{{\widehat{A}}}$.
\end{lemma}

\begin{proof}
To prove $M_\mathcal{{A}}\sqsubseteq_{\mathscr{R}_\Upsilon}M_\mathcal{{\widehat{A}}}$, we follow a structural induction reasoning on NuAC terms such that $\mathcal{\widehat{A}}=\Upsilon(\mathcal{A})$. For that, let $s,s'\in S(M_{\mathcal{A}})$\footnote{$S(M)$ is the set of states of $M$.} and $t,t'\in S(M_{\mathcal{\widehat{A}}})$. We distinguish the following cases where $L(s)$ takes different values:
%The proof follows a structural induction on NuAC terms.
%In an inductive way, we select the $\marked{a}\activityedge\mathcal{N}$ case to prove the soundness for $\mathscr{A}bs$ procedure and $\marked{Decision(p,\langle g\rangle\mathcal{N},\langle \neg g\rangle\mathcal{N})}$ for $\mathscr{M}inim$ procedure. The remaining cases can be proved similarly.
\begin{itemize}
  \item Case $a\activityedge\mathcal{N}$:\\
Let $L(s)=\marked{a}\activityedge\mathcal{N}\Rightarrow\exists~s':
s\rightarrow~s'$ by applying ACT-2 such that:\\ $L(s^{\prime})=a\activityedge\marked{\mathcal{N}}\Rightarrow\mu_{s}(s^{\prime})=1$.\\
By considering $t$ as the abstracted state of $s$ where $L(t)=\Upsilon(L(s))$, we can distinguish two cases for ABS-1 and ABS-2 that are presented respectively as follows:
\begin{enumerate}
  \item $a\in\!\Sigma_\phi:  L(t)=\Upsilon(\marked{a}\activityedge\mathcal{N})=\marked{a}\activityedge~\Upsilon(\mathcal{N})$. By applying ACT-2, $\exists~t':
t\rightarrow t'$ such that:  $L(t^{\prime})=a\activityedge\marked{\Upsilon(\mathcal{N})}\Rightarrow\mu_{t}(t^{\prime})=1$.
Then, it exists a weight function $\triangle$ for $\mathscr{R}_\Upsilon=\{(s^{\prime},t^{\prime})\}$ such that:\\
$\triangle(s^{\prime},t^{\prime})=1\Rightarrow\mu_{s}(s^{\prime})=\triangle(s^{\prime},t^{\prime})$ and
$\triangle(t^{\prime},s^{\prime})=1\Rightarrow\mu_{t}(t^{\prime})=\triangle(t^{\prime},s^{\prime})$. \\While $\triangle(s,t)>0$ then $~s\sqsubseteq_{\mathscr{R}_\Upsilon}~t$.
  \item $a\notin\!\Sigma_\phi:L(t)=\Upsilon(s)
=\Upsilon(\marked{a}\activityedge\mathcal{N})=\marked{\epsilon}\activityedge~\Upsilon(\mathcal{N})
\Rightarrow\exists~t':~t\rightarrow~t'$.\\
 By applying ACT-2 rule such that $L(t^{\prime})=\epsilon\activityedge
\marked{\mathcal{N}}\Rightarrow\mu_{2}(t^{\prime})=1$. Then it exists a weight function $\triangle$ for $\mathscr{R}_\Upsilon=\{(s^{\prime},t^{\prime})\}$ such that:\\
$\triangle(s^{\prime},t^{\prime})=1\Rightarrow\triangle(s^{\prime},t^{\prime})=\mu_{s}(s^{\prime})$ and
$\triangle(t^{\prime},s^{\prime})=1\Rightarrow\mu_{t}(t^{\prime})=\triangle(t^{\prime},s^{\prime})$, with
$\triangle(s,t)>0$ then $~s\sqsubseteq_{\mathscr{R}_\Upsilon}~t$.
\end{enumerate}
  \item Case $\mathcal{N}_1\stackrel{g}{\mapsto}\mathcal{N}_2$ is similar to the case of $\marked{a}\activityedge\mathcal{N}$ after applying ABS-3 and ABS-4.

\end{itemize}
It is clear that, the marked NuAC term $\mathcal{A}$ is the unique initial state of $M_{\mathcal{A}}$ corresponding to the unique initial state in $M_{\widehat{\mathcal{A}}}$. By following the same style of proof, we find: \\ $~~~~~~~~~~~~~~M_\mathcal{{A}}\sqsubseteq_{\mathscr{R}_\Upsilon}M_\mathcal{{\widehat{A}}}$, which confirms that Proposition \ref{prop:sound1} holds.
\end{proof}

\begin{proposition}[$\Upsilon$-Preservation]%\label{prop:preserv1}
For two PAs $M_\mathcal{{A}}$ and $M_\mathcal{\widehat{A}}$ such that $M_\mathcal{{A}}\sqsubseteq_{\mathscr{R}_\Upsilon}M_\mathcal{{\widehat{A}}}$. If $\phi$ is a $PCTL_{\backslash X}$ property, then we have: $(M_\mathcal{\widehat{A}}\models\phi)\Rightarrow(M_\mathcal{{A}}\models\phi)$.
\end{proposition}
\begin{proof}
To prove the preservation of PCTL properties by $\mathscr{R}_\Upsilon$, we follow an inductive reasoning on PCTL structure after applying each $\Upsilon$-abstraction rule.

  Let $\pi\in~M$ with $\pi=(s_{0}\cdots~s_{i}\cdots~s_{j}\cdots~s_{n})$ and $\pi'\in~\widehat{M}$ with  $\pi'=(t_{0}\cdots~t_{k}\cdots t_{l}\cdots~t_{m})$ are two finite paths such that; $\forall s\in\pi:\exists s'\in\pi',~ s\sqsubseteq_{\mathscr{R}_\Upsilon}s'$.
For PCTL expression satisfaction, we distinguish these cases:
\begin{itemize}
  \item Case $\phi_{1}\mathrm{U}\phi_{2}$:\\
 %For $\phi_{1}=\marked{a}\activityedge\mathcal{N}$ and $\phi_{2}$.
For $\pi$ and $\pi'$ such that:
  $\pi'\models \phi_{1}\mathrm{U}\phi_{2}\Leftrightarrow \exists r'\leq m:\forall u\leq r'-1,~ L(s_{u}')=\phi_{1}$ and $L(s_{r}')=\phi_{2}$. Similarly,
  $\pi\models \phi_{1}\mathrm{U}\phi_{2}\Leftrightarrow \exists r\leq n:\forall w\leq r-1,~ L(s_{w})=\phi_{1}$ and $L(s_{r})=\phi_{2}$. By applying the ABS rules, the states that do not satisfy either $\phi_{1}$ and $\phi_{2}$ in $\pi$ are mimicked. \\Consequently, $\pi'\models \phi_{1}\mathrm{U}\phi_{2}\Rightarrow\pi\models (\phi_{1}\Rightarrow F \phi_{2}).$
  \item Case $\mathrm{P}_{\bowtie\,p}[\phi_{1}\mathrm{U}\phi_{2}]$:\\
 We have $\pi'\models \phi_{1}\mathrm{U}\phi_{2}\Rightarrow\pi\models (\phi_{1}\Rightarrow F \phi_{2})$ and the mimicked states with the ABS rules have a Dirac distribution, then: $\pi'\models P_{\bowtie\,p}[\phi_{1}\mathrm{U}\phi_{2}]\Rightarrow\pi\models P_{\bowtie\,p}[\phi_{1}\Rightarrow F \phi_{2}]$.
\end{itemize}
By following the same proof style on PCTL structure, we conclude that:
  \begin{center}
  $(M_\mathcal{\widehat{A}}\models P_{\bowtie\,p}[\phi])\Rightarrow~(M_\mathcal{{A}}\models P_{\bowtie\,p}[\phi])$.
  \end{center}
\end{proof}
%\subsection{Property Preservation Proof}\label{sub:ProofPres}

\begin{lemma}[$\Psi$-Soundness]%\label{prop:sound2}
The abstraction algorithm $\Psi$ is sound, \ie $M_\mathcal{{A}}\sqsubseteq_{\mathscr{R}_\Psi}M_\mathcal{{\widehat{A}}}$.
\end{lemma}
\begin{proof}
To prove $M_\mathcal{{A}}\sqsubseteq_{\mathscr{R}_\Psi}M_\mathcal{{\widehat{A}}}$, we follow a structural induction reasoning on NuAC terms by comparing each term before and after applying  $\Psi$ rules. Let $s_0,s_1,s_2,s_3,s_4\in S(M_\mathcal{{A}})$ and $t_0,t_1,t_2,t_3\in S(M_\mathcal{{\widehat{A}}})$. We distinguish the following cases where $L(s_0)$ takes different values:
\begin{itemize}
  \item \textbf{Case} $D(p,g,\mathcal{N},\mathcal{N'})$:
Let $L(s_0)=\marked{D(p_{1},g_{1},\mathcal{N}_{1},\mathcal{N}^{'}_{1})}$, by applying PDEC-1 rule, we will have: $s_{0}\rightarrow~\mu_{0}(s_1,s_2)$ such that:

 \begin{itemize}
   \item  $L(s_1)=D(p_{1},g_{1},\marked{\mathcal{N}_{1}},\mathcal{N}^{'}_{1})$ such as $\mu_{0}(s_1)=p_1$,
   \item $L(s_2)=D(p_{1},g_{1},\mathcal{N}_{1},\marked{\mathcal{N}^{'}_{1}})$  such as $\mu_{0}(s_2)=1-p_1$.
 \end{itemize}

By considering $\mathcal{N}_{1}=D(p_{2},g_{2},\mathcal{N}_{2},\mathcal{N}^{'}_{2})$, let $t_0$ be the merged state of $s_0$ with $s_1$ by applying the MIN-2 rule, we will have:\\
$L(t_0)=D(p_{1}\times p_{2},g_{1}\wedge g_{2},\mathcal{N}_{2},\mathcal{N}^{'}_{2},1-p_{1},\mathcal{N'}_{1})$
$\Rightarrow\exists t_1, t_2, t_3: t_0\rightarrow \mu'(t_1,t_2,t_3)$. By applying PDEC-1 rule, we have:
\begin{itemize}
  \item $L(t_1)=D(p_{1}\times p_{2},g_{1}\wedge g_{2},\marked{\mathcal{N}}_{2},\mathcal{N}^{'}_{2},1-p_{1},\neg g_{1},\mathcal{N'}_{1})\Rightarrow\mu'(t_1)=p_{1}\times\!p_{2}.$
  \item $L(t_2)=D(p_{1}\times p_{2},g_{1}\wedge g_{2},\mathcal{N}_{2},\marked{\mathcal{N}^{'}_{2}},1-p_{1},\neg g_{1},\mathcal{N'}_{1})\Rightarrow\mu'(t_2)=p_{1}\times\!(1-p_{2}).$
  \item $L(t_3)=D(p_{1}\times p_{2},g_{1}\wedge g_{2},\mathcal{N}_{2},\mathcal{N}^{'}_{2},1-p_{1},\neg g_{1},\marked{\mathcal{N}^{'}_{1}})\Rightarrow\mu'(t_3)=1-p_{1}.$
\end{itemize}
It exists a weight function $\triangle$ for $\mathscr{R}_\Psi=\{(s_0,t_0),(s_3,t_1),(s_4,t_2),(s_2,t_3)\}$ such that:
\begin{enumerate}
  \item $\triangle(s_{3},t_{1})=p_1\Rightarrow\triangle(s_{3},t_{1})=\mu'(t_1)$
  \item $\triangle(s_{4},t_{2})=p_1\times (1-p_2)\Rightarrow\triangle(s_{4},t_{2})=\mu'(t_2)$
  \item $\triangle(s_{2},t_{3})=1-p_1\Rightarrow\triangle(s_{2},t_{3})=\mu'(t_3)$
%  \item $\triangle(s_{2}'',s_{1}'')=1-p\Rightarrow\mu_{2}(s_{2}'')=\triangle(s_{2}'',s_{1}'')$
\end{enumerate}
We have: $(\triangle(s_{3},t_{1})>0\wedge\triangle(s_{2},t_{3})>0)\wedge\triangle(s_{4},t_{2})>0)\Rightarrow~\mu\sqsubseteq_{\mathscr{R}_\Psi}~\mu'$.
\end{itemize}
%\end{proof}
%%================= Join Node Case
%\begin{lem}[Join Control Node]\label{Lem:Join}
%$\forall(s,s')\in~M\times~M':
%L(s)=\marked{x.Join(N)}\wedge
%L(s')=\marked{x.Join(N')}
%\Rightarrow~s\sqsubseteq_{\mathcal{R}}~s'$
%\end{lem}
%%\textbf{\emph{Case} $Fork(\mathcal{N},\mathcal{N})$}\\
%\begin{proof}
It is clear that, the marked NuAC term $\mathcal{A}$ is the unique initial state of $M_{\mathcal{A}}$ corresponding to the unique initial state in $M_{\widehat{\mathcal{A}}}$. By following the same style of proof, we find: \\ $~~~~~~~~~~~~~~M_\mathcal{{A}}\sqsubseteq_{\mathscr{R}_\Psi}M_\mathcal{{\widehat{A}}}$, which confirms that Proposition \ref{prop:sound1} holds.
\end{proof}
\begin{proposition}[$\Psi$-Preservation]%\label{prop:preserv2}
For two PAs $M_\mathcal{{A}}$ and $M_\mathcal{{\widehat{A}}}$ such that $M_\mathcal{{A}}\sqsubseteq_{\mathscr{R}_\Psi}M_\mathcal{{\widehat{A}}}$. If $\phi$ is a $PCTL$ property, then we have: $(M_\mathcal{{\widehat{A}}}\models\phi)\Rightarrow(M_\mathcal{{A}}\models\phi)$.
\end{proposition}
\begin{proof}
To prove the preservation of PCTL properties by $\mathscr{R}_\Psi$, we follow an inductive reasoning on PCTL structure for each $\Upsilon$-abstraction rule.

  Let $\pi\in~M$ with $\pi=(s_{0}\cdots~s_{i}\cdots~s_{j}\cdots~s_{n})$ and $\pi'\in~\widehat{M}$ with  $\pi'=(t_{0}\cdots~t_{k}\cdots t_{l}\cdots~t_{m})$ are two finite paths such that; $\forall s\in\pi:\exists s'\in\pi',~ s\sqsubseteq_{\mathscr{R}_\Psi}s'$.
For PCTL expression satisfaction, we distinguish these cases:
\begin{itemize}
  \item Case $\phi_{1}\mathrm{U}\phi_{2}$:\\
 %For $\phi_{1}=\marked{a}\activityedge\mathcal{N}$ and $\phi_{2}$.
For $\pi$ and $\pi'$ such that:
  $\pi'\models \phi_{1}\mathrm{U}\phi_{2}\Leftrightarrow \exists r'\leq m:\forall u\leq r'-1,~ L(s_{u}')=\phi_{1}$ and $L(s_{r}')=\phi_{2}$. Similarly,
  $\pi\models \phi_{1}\mathrm{U}\phi_{2}\Leftrightarrow \exists r\leq n:\forall w\leq r-1,~ L(s_{w})=\phi_{1}$ and $L(s_{r})=\phi_{2}$.\\
By applying MIN rules, some states in $\pi$ are merged. \\Consequently, $\pi'\models \phi_{1}\mathrm{U}\phi_{2}\Rightarrow\pi\models \phi_{1}\Rightarrow F\phi_{2}.$
  \item Case $\mathrm{P}_{\bowtie\,p}[\phi_{1}\mathrm{U}\phi_{2}]$:\\
 We have $\pi'\models \phi_{1}\mathrm{U}\phi_{2}\Rightarrow\pi\models \phi_{1}\Rightarrow F\phi_{2}$ and the merged states with MIN rules accumulate the probabilistic distribution, then: $\pi'\models P_{\bowtie\,p}[\phi_{1}\mathrm{U}\phi_{2}]\Rightarrow\pi\models P_{\bowtie\,p}[\phi_{1}\Rightarrow F\phi_{2}]$.
\end{itemize}
By following the same proof style on PCTL structure, we conclude that:
  \begin{center}
$(M_\mathcal{{\widehat{A}}}\models\phi)\Rightarrow(M_\mathcal{{A}}\models\phi)$.
  \end{center}

%To prove the preservation of PCTL properties, we follow an inductive reasoning on the PCTL structure. As an example, we take the case of the ``Until'' operator, \ie $\mathrm{P}_{\bowtie p}[\phi_{1}\mathrm{U}\phi_{2}]$.\\
%  Let $\pi=(s_{0}\cdots~s_{i}\cdots~s_{j}\cdots~s_{n})$, and $\pi':\pi'=(s_{0}'\cdots~s_{x}'\cdots~s_{y}'\cdots~s_{z}')$ be two paths such that: $\forall s\in\pi:\exists s'\in\pi': s\sqsubseteq_{\mathcal{R}}s'$.
%
%From PCTL satisfaction relation we have:\\
%$\pi'\models P[\phi_{1}\mathrm{U}\phi_{2}]\bowtie p\Leftrightarrow $$\exists m: L(s_{i:i\leq m-1}')=\phi_{1}, L(s_{m}')=\phi_{2}$, and $P(s_{i:i\leq m-1}')\bowtie p$.\\
%To measure the probability of a sequence of states, we have:\\
% $~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~P(s_{i:i\leq m}')=P(s'_{1})\times\ldots\times\!P(s_{m}')$.
% \\ To preserve the probability value, we can distinguish between two cases:
%\begin{enumerate}
%  \item In $\mathscr{A}bs$ case: we have $\mathscr{A}bs(s_{1}\longrightarrow_{1}s_{2})=(s_{1}\longrightarrow_{1}s'_{2})\Longrightarrow P(s_{1},s_{2})=P(s'_{1},s'_{2})$ such as  $P(s'_{1},s'_{2})=1$.
%  \item In $\mathscr{M}inim$ case: we have $\mathscr{M}nim(s_{1}\longrightarrow_{p1}s_{2}\longrightarrow_{p2}s_{3})=(s'_{1}\Rightarrow_{p1\times p2}s'_{2})\Longrightarrow P(s_{1},s_{2},s_{3})=P(s'_{1},s'_{2})$ such as $P(s'_{1},s'_{2})=p1\times p2$.
%\end{enumerate}
%  From the results of 1) and 2), we conclude that the probability value is preserved. By following the same proof style on PCTL structure, we conclude that:\\
%  \begin{center}
%  $(\widehat{M}\models\phi_{PCTL_{\backslash X}})\Rightarrow(M\models\phi_{PCTL_{\backslash X}})$.
%  \end{center}
\end{proof}
 %Also, we have to prove the preservation of labels. In this case, there are two possibilities:
%\\ Either $ \exists m: L(s_{i:i\leq m-1}')=\phi_{1}$ then $(M^{'}\models\phi_{1}\mathrm{U}\phi_{2})\Rightarrow(M\models\phi_{1}\mathrm{U}\phi_{2})$, or
%$(M^{'}\models\phi_{1}\mathrm{U}\phi_{2})\Rightarrow(M\models\phi_{1}\mathrm{U}true\mathrm{U}\phi_{2})$.\\
%In general, the preservation of this type of property infers the validity of its safety property in the concrete model.

%\subsection{Numerical Results for SOS}\label{App:ExpResSOS}

%\begin{table}[h]
%\centering
%\footnotesize{\begin{tabular}{|c||c|c|c|c||c|c|c|c||c||}
%\hline
%&\multicolumn{4}{|c||}{Concrete Model}&\multicolumn{4}{|c||}{Abstract Model}&Res\\
%\hline
%$n$&$\#s$&$\#t$&Tc&Tv&$\#s$&$\#t$&Tc&Tv&\\
%\hline
%\hline
%5&4848&9682&0.404&33.31&1339&2727&0.058&5.198&0.9977\\
%\hline
%10&9308&18607&0.548&63.501&0.122&2619&5352&10.49&0.9977\\
%\hline
%15&13768&27532&0.72&94.264&3899&7977&0.147&15.914&0.9977\\
%\hline
%20&18228&36457&1.137&124.904&5179&10602&0.23&21.444&0.9977\\
%\hline
%25&22688&45382&1.156&155.256&6459&13227&0.266&25.976&0.9977\\
%\hline
%30&27148&54307&1.182&187.068&7739&15852&0.325&32.037&0.9977\\
%\hline
%35&31608&63232&1.632&217.651&9019&18477&0.457&36.725&0.9977\\
%\hline
%40&36068&72157&1.819&248.451&10299&21102&0.479&41.758&0.9977\\
%\hline
%45&40528&81082&2.11&277.156&11579&23727&0.566&47.764&0.9977\\
%\hline
%50&44988&90007&2.354&306.741&12859&26352&0.399&49.84&0.9977\\
%\hline
%\hline
%\end{tabular}}
%\caption{Verification Results for Property 1.}
%\label{tab:OnShipSys1}
%\end{table}

 %Figure \ref{fig:Absshop2} illustrates the abstracted SysML activity diagrams related to Property $\#2$.
% Table \ref{tab:OnShipSys2} shows the verification results of Property 2 for different values of the number of orders ``$n$''.
% \begin{table}[!ht]
%\centering
%\footnotesize{\begin{tabular}{|c||c|c|c|c||c|c|c|c||c||}
%\hline
%&\multicolumn{4}{|c||}{Concrete Model}&\multicolumn{4}{|c||}{Abstract Model}&Res\\
%\hline
%$n$&$\#s$&$\#t$&Tc&Tv&$\#s$&$\#t$&Tc&Tv&\\
%\hline
%\hline
%5&4848&9682&0.404&31.899&1721&3524&0.125&7.634&0.88889\\
%\hline
%10&9308&18607&0.548&58.778&3361&6884&0.212&15.733&0.88889\\
%\hline
%15&13768&27532&0.72&86.099&5001&10244&0.265&22.009&0.88889\\
%\hline
%20&18228&36457&1.137&114.154&6641&13604&0.399&30.433&0.88889\\
%\hline
%25&22688&45382&1.156&140.321&8281&16964&0.497&37.304&0.88889\\
%\hline
%30&27148&54307&1.182&168.594&9921&20324&0.468&43.051&0.88889\\
%\hline
%35&31608&63232&1.632&198.43&11561&23684&0.577&51.312&0.88889\\
%\hline
%40&36068&72157&1.819&223.198&13201&27044&0.652&59.066&0.88889\\
%\hline
%45&40528&81082&2.11&255.682&14841&30404&0.798&64.549&0.88889\\
%\hline
%50&44988&90007&2.354&281.712&16481&33764&0.989&72.041&0.88889\\
%\hline
%\hline
%\end{tabular}}
%\caption{Verification Results for Property 2.}
%\label{tab:OnShipSys2}
%\end{table}

 %Figure \ref{fig:Absshop2} presents the abstracted SysML activity diagrams related to Property 3 and .
% Table \ref{tab:OnShipSys2} shows the verification results of Property 3 in function of the number of orders ``$n$''.
% \begin{table}[!ht]
%\centering
%\footnotesize{\begin{tabular}{|c||c|c|c|c||c|c|c|c||c||}
%\hline
%&\multicolumn{4}{|c||}{Concrete Model}&\multicolumn{4}{|c||}{Abstract Model}&Res\\
%\hline
%$n$&$\#s$&$\#t$&Tc&Tv&$\#s$&$\#t$&Tc&Tv&\\
%\hline
%\hline
%5&4848&9682&0.404&38.216&1281&2596&0.118&5.203&0.145\\
%\hline
%10&9308&18607&0.548&67.652&2526&5131&0.131&10.584&0.145\\
%\hline
%15&13768&27532&0.72&100.515&3771&7666&0.155&15.743&0.145\\
%\hline
%20&18228&36457&1.137&132.783&5016&10201&0.246&21.349&0.145\\
%\hline
%25&22688&45382&1.156&165.804&6261&12736&0.271&26.432&0.145\\
%\hline
%30&27148&54307&1.182&197.927&7506&15271&0.325&32.701&0.145\\
%\hline
%35&31608&63232&1.632&232.517&8751&17806&0.417&38.776&0.145\\
%\hline
%40&36068&72157&1.819&265.686&9996&20341&0.399&44.35&0.145\\
%\hline
%45&40528&81082&2.11&295.997&11241&22876&0.465&49.914&0.145\\
%\hline
%50&44988&90007&2.354&327.812&12486&25411&0.493&54.881&0.145\\
%\hline
%\hline
%\end{tabular}}
%\caption{Verification Results for Property 3.}
%\label{tab:OnShipSys3}
%\end{table}
% The verification results for Property 4 is given in Table \ref{tab:OnShipSys4}.% for the obtained SysML activity diagrams shown in Figure \ref{tab:OnShipSys4}.
% \begin{table}[!ht]
%\centering
%\footnotesize{\begin{tabular}{|c||c|c|c|c||c|c|c|c||c||}
%\hline
%&\multicolumn{4}{|c||}{Concrete Model}&\multicolumn{4}{|c||}{Abstract Model}&Res\\
%\hline
%$n$&$\#s$&$\#t$&Tc&Tv&$\#s$&$\#t$&Tc&Tv&\\
%\hline
%\hline
%5&4848&9682&0.404&35.07&1259&2572&0.045&5.384&0.14736\\
%\hline
%10&9308&18607&0.548&71.468&2459&5042&0.183&11.316&0.14736\\
%\hline
%15&13768&27532&0.72&105.157&3659&7512&0.169&16.194&0.14736\\
%\hline
%20&18228&36457&1.137&139.413&4859&9982&0.251&22.307&0.14736\\
%\hline
%25&22688&45382&1.156&173.537&6059&12452&0.239&27.106&0.14736\\
%\hline
%30&27148&54307&1.182&204.394&7259&14922&0.257&32.307&0.14736\\
%\hline
%35&31608&63232&1.632&239.347&8459&17392&0.35&38.648&0.14736\\
%\hline
%40&36068&72157&1.819&272.494&9659&19862&0.388&43.2&0.14736\\
%\hline
%45&40528&81082&2.11&302.447&10859&22332&0.368&49.471&0.14736\\
%\hline
%50&44988&90007&2.354&337.014&12059&24802&0.485&55.057&0.14736\\
%\hline
%\hline
%\end{tabular}}
%\caption{Verification Results for Property 4.}
%\label{tab:OnShipSys4}
%\end{table}

%\subsection{Numerical Results for RTSP}\label{App:ExpResRTSP}

%\begin{table}[h]
%\centering
%\footnotesize{\begin{tabular}{|c||c|c|c|c||c|c|c|c||c||}
%\hline
%&\multicolumn{4}{|c||}{Concrete Model}&\multicolumn{4}{|c||}{Abstract Model}&Res\\
%\hline
%$n$&$\#s$&$\#t$&Tc&Tv&$\#s$&$\#t$&Tc&Tv&\\
%\hline
%\hline
%5&4848&9682&0.404&33.31&1339&2727&0.058&5.198&0.9977\\
%\hline
%10&9308&18607&0.548&63.501&0.122&2619&5352&10.49&0.9977\\
%\hline
%15&13768&27532&0.72&94.264&3899&7977&0.147&15.914&0.9977\\
%\hline
%20&18228&36457&1.137&124.904&5179&10602&0.23&21.444&0.9977\\
%\hline
%25&22688&45382&1.156&155.256&6459&13227&0.266&25.976&0.9977\\
%\hline
%30&27148&54307&1.182&187.068&7739&15852&0.325&32.037&0.9977\\
%\hline
%35&31608&63232&1.632&217.651&9019&18477&0.457&36.725&0.9977\\
%\hline
%40&36068&72157&1.819&248.451&10299&21102&0.479&41.758&0.9977\\
%\hline
%45&40528&81082&2.11&277.156&11579&23727&0.566&47.764&0.9977\\
%\hline
%50&44988&90007&2.354&306.741&12859&26352&0.399&49.84&0.9977\\
%\hline
%\hline
%\end{tabular}}
%\caption{Verification Results for Property 1.}
%\label{tab:OnShipSys1}
%\end{table}

 %Figure \ref{fig:Absshop2} illustrates the abstracted SysML activity diagrams related to Property $\#2$.
% Table \ref{tab:OnShipSys2} shows the verification results of Property 2 for different values of the number of orders ``$n$''.
%\begin{table}[!ht]
%\centering
%\footnotesize{\begin{tabular}{|c||c|c|c|c||c|c|c|c||c||}
%\hline
%&\multicolumn{4}{|c||}{Concrete Model}&\multicolumn{4}{|c||}{Abstract Model}&Res\\
%\hline
%$n$&$\#s$&$\#t$&Tc&Tv&$\#s$&$\#t$&Tc&Tv&\\
%\hline
%\hline
%5&4848&9682&0.404&31.899&1721&3524&0.125&7.634&0.88889\\
%\hline
%10&9308&18607&0.548&58.778&3361&6884&0.212&15.733&0.88889\\
%\hline
%15&13768&27532&0.72&86.099&5001&10244&0.265&22.009&0.88889\\
%\hline
%20&18228&36457&1.137&114.154&6641&13604&0.399&30.433&0.88889\\
%\hline
%25&22688&45382&1.156&140.321&8281&16964&0.497&37.304&0.88889\\
%\hline
%30&27148&54307&1.182&168.594&9921&20324&0.468&43.051&0.88889\\
%\hline
%35&31608&63232&1.632&198.43&11561&23684&0.577&51.312&0.88889\\
%\hline
%40&36068&72157&1.819&223.198&13201&27044&0.652&59.066&0.88889\\
%\hline
%45&40528&81082&2.11&255.682&14841&30404&0.798&64.549&0.88889\\
%\hline
%50&44988&90007&2.354&281.712&16481&33764&0.989&72.041&0.88889\\
%\hline
%\hline
%\end{tabular}}
%\caption{Verification Results for Property 2.}
%\label{tab:RTSP2}
%\end{table}

 %Figure \ref{fig:Absshop2} presents the abstracted SysML activity diagrams related to Property 3 and .
% Table \ref{tab:OnShipSys2} shows the verification results of Property 3 in function of the number of orders ``$n$''.
% \begin{table}[!ht]
%\centering
%\footnotesize{\begin{tabular}{|c||c|c|c|c||c|c|c|c||c||}
%\hline
%&\multicolumn{4}{|c||}{Concrete Model}&\multicolumn{4}{|c||}{Abstract Model}&Res\\
%\hline
%$n$&$\#s$&$\#t$&Tc&Tv&$\#s$&$\#t$&Tc&Tv&\\
%\hline
%\hline
%5&4848&9682&0.404&38.216&1281&2596&0.118&5.203&0.145\\
%\hline
%10&9308&18607&0.548&67.652&2526&5131&0.131&10.584&0.145\\
%\hline
%15&13768&27532&0.72&100.515&3771&7666&0.155&15.743&0.145\\
%\hline
%20&18228&36457&1.137&132.783&5016&10201&0.246&21.349&0.145\\
%\hline
%25&22688&45382&1.156&165.804&6261&12736&0.271&26.432&0.145\\
%\hline
%30&27148&54307&1.182&197.927&7506&15271&0.325&32.701&0.145\\
%\hline
%35&31608&63232&1.632&232.517&8751&17806&0.417&38.776&0.145\\
%\hline
%40&36068&72157&1.819&265.686&9996&20341&0.399&44.35&0.145\\
%\hline
%45&40528&81082&2.11&295.997&11241&22876&0.465&49.914&0.145\\
%\hline
%50&44988&90007&2.354&327.812&12486&25411&0.493&54.881&0.145\\
%\hline
%\hline
%\end{tabular}}
%\caption{Verification Results for Property 3.}
%\label{tab:RTSP3}
%\end{table}
% The verification results for Property 4 is given in Table \ref{tab:OnShipSys4}.% for the obtained SysML activity diagrams shown in Figure \ref{tab:OnShipSys4}.
% \begin{table}[!ht]
%\centering
%\footnotesize{\begin{tabular}{|c||c|c|c|c||c|c|c|c||c||}
%\hline
%&\multicolumn{4}{|c||}{Concrete Model}&\multicolumn{4}{|c||}{Abstract Model}&Res\\
%\hline
%$n$&$\#s$&$\#t$&Tc&Tv&$\#s$&$\#t$&Tc&Tv&\\
%\hline
%\hline
%5&4848&9682&0.404&35.07&1259&2572&0.045&5.384&0.14736\\
%\hline
%10&9308&18607&0.548&71.468&2459&5042&0.183&11.316&0.14736\\
%\hline
%15&13768&27532&0.72&105.157&3659&7512&0.169&16.194&0.14736\\
%\hline
%20&18228&36457&1.137&139.413&4859&9982&0.251&22.307&0.14736\\
%\hline
%25&22688&45382&1.156&173.537&6059&12452&0.239&27.106&0.14736\\
%\hline
%30&27148&54307&1.182&204.394&7259&14922&0.257&32.307&0.14736\\
%\hline
%35&31608&63232&1.632&239.347&8459&17392&0.35&38.648&0.14736\\
%\hline
%40&36068&72157&1.819&272.494&9659&19862&0.388&43.2&0.14736\\
%\hline
%45&40528&81082&2.11&302.447&10859&22332&0.368&49.471&0.14736\\
%\hline
%50&44988&90007&2.354&337.014&12059&24802&0.485&55.057&0.14736\\
%\hline
%\hline
%\end{tabular}}
%\caption{Verification Results for Property 4.}
%\label{tab:RTSP4}
%\end{table}
%\subsubsection{Result Analysis}\label{castud:Shopping}
%  Figure \ref{fig:ratesall} illustrates both abstraction rates in term of model size and computation time for the verification of PCTL properties on online shopping system. For the verification of all properties, the evolution of the abstraction rate in terms of model size and computation time is important compared to the growing of the model size. Furthermore, Table \ref{tab:OnShipSys1}, Table \ref{tab:OnShipSys2}, Table \ref{tab:OnShipSys3} and Table \ref{tab:OnShipSys4} show that our abstraction algorithm actually preserves the verification results.

### 2015-04-05 thesis/thesis/abstract.tex
added thesis

%        \thispagestyle{plain}
%        \newpage
%        \null\vskip0.50in%
%        \begin{center}
%                {\LARGE\bf{ABSTRACT}}
%        \end{center}

Interaction among autonomous agents in Multi-Agent Systems (MASs) is the key aspect for solving complex problems that an individual agent cannot handle alone. In this context, social approaches, as opposed to the mental approaches, have recently received a considerable attention in the area of agent communication. They exploit observable social commitments to develop a verifiable formal semantics by which communication protocols can be specified. However, existing approaches for defining social commitments tend to assume an absolute guarantee of correctness so that systems run in a certain manner. That is, social commitments have always been modeled with the assumption of certainty. Moreover, the widespread use of MASs increases the interest to explore the interactions between different aspects of the participating agents such as the interaction between agents' knowledge and social commitments in the presence of uncertainty. This results in having a gap, in the literature of agent communication, on modeling and verifying social commitments in probabilistic settings.

In this thesis, we aim to address the above-mentioned problems by presenting a practical formal framework that is capable of handling the problem of uncertainty in social commitments. First, we develop an approach for representing, reasoning about, and verifying probabilistic social commitments in MASs. This includes defining a new logic called the probabilistic logic of commitments (PCTLC), and a reduction-based model checking procedure for verifying the proposed logic. In the reduction technique, the problem of model checking PCTLC is transformed into the problem of model checking PCTL so that the use of the PRISM (Probabilistic Symbolic Model Checker) is made possible. Formulae of PCTLC are interpreted over an extended version of the probabilistic interpreted systems formalism. Second, we extend the work we proposed for probabilistic social commitments to be able to capture and verify the interactions between knowledge and commitments. Properties representing the interactions between the two aspects are expressed in a new developed logic called the probabilistic logic of knowledge and commitment (PCTL$^{kc}$). Third, we develop an adequate semantics for the group social commitments, for the first time in the literature, and integrate it into the framework. We then introduce an improved version of PCTL$^{kc}$ and extend it with operators for the group knowledge and group social commitments. The new refined logic is called PCTL$^{\textrm{kc+}}$. In each of the latter stages, we respectively develop a new version of the probabilistic interpreted systems over which the presented logic is interpreted, and introduce a new reduction-based verification technique to verify the proposed logic. To evaluate our proposed work, we implement the proposed verification techniques on top of the PRISM model checker and apply them on several case studies. The results demonstrate the usefulness and effectiveness of our proposed work.
%The experimental results demonstrate the efficiency and scalability of the proposed reduction techniques and show that our work is effective for addressing probabilistic social commitment in MASs.
\\
%\textbf{keywords:}
%Multi-Agent Systems, Agent Communication, Social Commitments, uncertainty, Model Checking.

%\newpage

%\endinput

### 2015-04-05 thesis/thesis/chap1/chap1.tex
added thesis

%\input{chap1/introduction.tex}

\setcounter{chapter}{0}

\chapter{Introduction}\label{cha:introduction}

In this chapter, we introduce the context of our research, which falls in the area of agent communication within Multi-Agent Systems (MASs). More precisely, it is concerned with modeling and verifying social commitments --as a means of communication among agents-- in the presence of probabilistic behavior. We also identify the motivations, problem statement, and research questions that we address in this thesis. Then, we list our objectives and discuss our methodology. Finally, we conclude this chapter by providing the thesis outline.

\section{Context of Research} \label{sec:context-chap1}

\subsection{Multi-Agent Systems (MASs)}
Nowadays, the use of distributed environments to solve complex
real world problems using entities called agents is on rise
\cite{Biswas08,Park2005}. Agents are active, social, and adaptable computer systems situated in some dynamic environment and capable of autonomous actions \cite{Wooldridge2009}. %to achieve their objectives \cite{Wooldridge2009}. %To attain their objectives, agents need abilities to cooperate, coordinate, and negotiate.
Ideally, an agent has to be \cite{Wooldridge1995}:

\begin{itemize}
\item Reactive: able to respond to changes in its environment.
\item Pro-active: capable to behave with respect to its goals (goal-directed behavior).
\item Social: able to interact and communicate with others.
\item Autonomous: able to operate without direct intervention of others.
\end{itemize}

In addition to being autonomous, agents are possibly heterogeneous; that is, agents may be independently designed by different programmers and hence it is difficult to make assumptions about their present or future behavior.
A multi-agent system (MAS) consists of a set of these autonomous
entities, which interact with each other and their
surrounding environment to achieve their (joint) objectives
\cite{Wooldridge2009}. In an open system, autonomous agents can freely enter and exit different interactions at any time \cite{Fornara2004a}. In principle, open MASs provide no guarantees about the behavior of their agents. This means that when agents are working together, such as carrying out a business protocol, an agent's misbehavior may potentially create an
exception for another agent and obstruct its proper working.
However, one can look at multi-agent systems from different
perspectives. From the computing perspective, a MAS is a
computational paradigm and an advance in computer science. From
the software engineering perspective, multi-agent technology is a
new software engineering paradigm providing new abstractions for
different phases of software development process. MASs approaches
can be seen as very efficient and modular ways of modeling and
implementing systems as they are capable of designing and
programming autonomous agents with different abilities, behaviors,
and intentions. From the artificial intelligence perspective, MASs
provide better understanding and modeling of social intelligence
and emergent behaviors.

\subsection{Agent Communication Languages (ACLs)}
Communication is a fundamental aspect for autonomous agents in MASs to coordinate with one another to solve complex problems that are difficult for an individual agent to tackle. Therefore, communication among agents is a key element to build effective MASs. In many realistic settings, agents need to interact to realize their goals. The type of interaction among the agents varies according to the goals of these interacting parties and the context of the transactions they are performing. An agent may cooperate with other agents to perform a certain task, compete with others to achieve a shared goal, or do a combination of both in order to perform individual or group tasks.

The importance of defining a standard framework for agent communication has been widely recognized. However, there have been many attempts in the literature to agree on standards for agent communication. Semantics of ACLs are defined either internally (privately) in terms of agents' beliefs and goals, or externally (publicly) in terms of agents' social commitments.
%Communication between agents are %governed by means of protocols. Roughly speaking, a protocol %determines which messages can be exchanged and in which order.
Approaches defined using the former type of semantics are called mental
approaches because they focus on the minds of interacting agents, while those defined using the latter one are called social approaches because they consider the social context of the interacting parties. In contrast to mental approaches such as those that are built using FIPA-ACL\footnote{See FIPA-ACL (Foundation for Intelligent Physical Agents - Agent Communication Language) specifications (1997,1999,2001,2002), http://www.fipa.org/repository/aclspecs.php3} and KQML (Knowledge Query and Manipulation Language) \cite{Finin1994}, social commitments proved to be a powerful representation for agent interactions \cite{Bentahar2010,Mallya2007,Yolum2004}. They provide a social semantics that abstracts away from the agents internal states and offers social and observable meaning to the messages being exchanged among agents. In the context of this thesis, we focus on the kind of communication in which the semantics of messages is defined publicly, i.e., in terms of social commitments.

\section{Motivations} \label{sec:Motivations-chap1}
Our review of the social commitments literature has revealed a gap in handling probabilistic social commitments in MASs. We have noticed that though social commitments have been the subject of a vast research activity for more than a decade, current proposals to represent and verify social commitments, for instance \cite{Bentahar2012,Bentahar2009,Bentahar2004,Colombetti2000,Colombetti2004,El-Menshawy2010,El-Menshawy2013a,Singh2000,Verdicchio2003}, assume typical settings in which agents behave in an ideal manner, and consequently commitments among interacting agents are treated under the assumption of certainty. However, in the formulation of agent-based systems, the role of uncertainty is crucial for an efficient and coherent resolution of complex problems. Simply put, agents in MASs overcome complex problems thanks to their individual capabilities to be autonomous and to adapt their behavior with the changing of the environment in which they live and
interact. Practically speaking, agents cannot always observe all the changes in the environment, but instead each agent can only have a partial view of other agents' behavior \cite{Gammie2004}. Indeed, the presence of imperfect information about the environment leads autonomous agents to make estimations about the observable world as part of their autonomous decision making processes \cite{Walley1996}. This means that agents inevitably meet uncertainty during their work, or in many cases, for the high complexity of the problem, the information they handle is (or needs to be) approximate.

This unpredictable behavior of MASs raises different important questions. The interesting issue that we are mainly focusing on is how social commitments can be tackled in such systems. In reality, due to agents' autonomy, a request to create a social commitment is not always followed by the creation of that commitment. The same principle applies to fulfilling an established commitment. That is, in some situations, even if there is some state of affairs (i.e., content of a commitment) that an agent wants to bring about, its actions might not reliably drive the state of affairs into the desired state \cite{Xuan1999}. Consequently, the problem of specifying and verifying social commitments is made more complicated by the presence of uncertainty.

The interaction between social commitments and agents' knowledge is also not receiving sufficient attention from the researchers in MASs community. For instance, the addition of epistemic reasoning to social commitments has not been widely considered yet. In fact, the ability to perform knowledge reasoning over commitments is one of the major advantages of addressing the relationship between the two concepts which ultimately helps ensure agents' awareness about their commitments and the fulfillments of these commitments. The vast majority of existing proposals have been carried out to address each of knowledge and commitments independently (see for example
\cite{Baldoni2010,Bentahar2012,Delgado2009,El-Menshawy2013a,Giordano2007,Halpern2003,Huang2011,Lomuscio2007,Pham2007,Wan2013}). However, it has been demonstrated that these two concepts (i.e., knowledge and commitments) are closely influencing each other in various practical settings such as e-commerce applications \cite{Al-Saqqar2014a}. Therefore, their interaction needs to be specified and verified in a systematic way. The only two existing approaches, to the best of our knowledge, to model such interactions between knowledge and commitments either neglect the probabilistic features of MASs by assuming an absolute degree of correctness so that systems under consideration behave in an ideal manner \cite{Al-Saqqar2014a}, or adopt a different kind of commitments called ``internal commitment'' rather than the ``social commitments'' that we consider in this thesis \cite{Schmidt2004}. The notion of ``internal commitment'' refers to a commitment of an agent to itself \cite{Singh2008}.

Another issue that has attracted our attention while reviewing the literature is the limitation of the current approaches to handle group social commitments. Although the notion of ``group'' has been, in one way or another, attached to commitments in several proposals \cite{Barbara2010,Sanchez-Anguix2013,Wright2012,YuW2010}, the semantics of ``group social commitments'' has never been materialized in the past. The need to formalize ``group social commitments'' stems from the importance of the concept of ``group'' in real settings as we will see later in Chapter \ref{cha:PCTLKC+}.

To address the above shortcomings, a major challenge in our research is to accurately represent and verify social commitments in the presence of uncertainty. Another ambitious challenge is to formally capture and verify the interaction between social commitments and agents' knowledge in probabilistic MASs. Yet another challenge is to define an appropriate semantics for social commitments under the scope of a group (i.e., one-to-many commitment schemes) and then study the relationship between individual and group social commitments and knowledge in probabilistic settings.

%In this research, we investigate a formal and systematic way to represent and verify social commitments in the presence of uncertainty. That is to realize interactions of agents where no assumptions are made on the internal states of the interacting agents as well as no assumptions are made about the presence of a reliable behavior. Therefore, the motivation for this thesis is to introduce a new logical framework by which we can represent and reason about agent interactions defined in terms of social commitments in uncertain settings.

\section{Problem and Research Questions} \label{sec:problem statement-chap1}

The main problem we are addressing in this thesis is the problem of handling \textit{probabilistic social commitments} in MASs. To ensure having effective commitment-based interactions in open and heterogeneous systems, these commitments need to be represented and verified while keeping uncertainty in mind.

Current research initiatives focus mainly on extending conventional temporal logics such as LTL \cite{Pnueli1977} and CTL \cite{Emerson1990}, and CTL$^*$ \cite{Emerson1986} to express social commitments \cite{Baldoni2010,Bentahar2012,El-Menshawy2013a,Giordano2007,Pham2007,Verdicchio2003}. The downside of the current extended logics resides in their expressiveness. In fact, existing commitment logics can neither express probabilistic social commitments nor capture the interaction between commitments and knowledge in probabilistic MASs. Besides, these logics lack the ability to deal with group-commitment scenarios and instead they are limited to the common one-to-one commitment scheme.

To circumvent this downside, we need to come up with a probabilistic logic equipped with a social operator --for commitments and their fulfilments-- that is expressive enough to represent and reason about social commitments in the presence of uncertainty.

In order to do so, some questions arise. We name these research questions: R1, R2, $\dots$ etc. The first question is: \textbf{how can we define a logic that is capable of specifying social commitments employed in uncertain settings?} [R1]. In the literature, there is no such work that considers dealing with social commitments in the presence of probabilistic behavior. Thus, our thinking was directed towards existing conventional logics to investigate the possibility of exploiting them to help define the new logic.
However, \textbf{which temporal logic to choose} is the second
question to be answered [R2]. Existing probabilistic temporal logics
such as PCTL \cite{Hansson1994} and PCTL$^*$ \cite{Baier1998}
consider neither commitments nor agent communication. We
propose to extend PCTL with modal operators for commitments and
their fulfillments. This process is achieved by combining two existing logics together. However, any logic needs to be associated with
a computational model over which formulae of the logic are interpreted. So, our third question is: \textbf{which computational model to use in order to model the target MASs?} [R3]. The underlying computational model considered throughout this thesis is the one of interpreted system formalism \cite{Fagin1995}, suitably extended whenever necessary.
Furthermore, to verify the proposed logic, we need
to answer the following question: \textbf{which formal
verification technique to use?} [R4]. In fact, there are three main
verification techniques to verify systems against given
requirements in the literature, namely testing, theorem proving,
and model checking. Model checking has some advantages over
others since it is fully automated and systematically checks all system states. On the other hand, in testing, it is hard to generate
exhaustive test cases, and theorem proving requires expertise and is only semi-automatic. So, we use model checking as a means of formal verification. However, \textbf{which model checking technique to adopt} should be answered as many techniques are already in use [R5]. Current proposals use only qualitative model checking  to ensure the correctness of commitment-based interactions in MASs. However, since our approach is built on PCTL, we propose a reduction-based probabilistic model checking technique in which the problem of model checking our logic is reduced to the one of PCTL. Finally, to check the effectiveness of our approach, we need to implement the proposed model checking technique. Hence, we need to answer the question: \textbf{which model checker to use in order to verify the proposed logic?} [R6]. In our work, we adopt the PRISM model checker\footnote{http://www.prismmodelchecker.org} as it already allows for analyzing and verifying probabilistic systems, and it also performs symbolic model checking of PCTL in which it manipulates sets of states rather than single states. Such sets are efficiently represented and transformed by means of Binary Decision Diagrams (BDDs) \cite{McMillan1992}, which help alleviate the state space problem associated with model checking.

\section{Objectives} \label{sec:objectives-chap1}
The main objectives of this research are:

\begin{enumerate}

\item Proposing a new meaningful, declarative, and verifiable logic with an expressive power that allows for representing and reasoning about commitments and their fulfillments in the presence of uncertainty.

\item Developing a new version of interpreted systems that can effectively model systems under consideration.

\item Investigating the relationship between the probabilistic social commitments and probabilistic knowledge in agent-based systems.

\item Defining a proper semantics for the group social commitments.

\item Introducing a new model checking technique for verifying social commitments expressed in terms of the proposed logic. %This objective comprises the development of a set of reduction rules to reduce the problem of model checking our logic to the problem of model checking an existing logic such as PCTL.

\end{enumerate}

\section{Methodology} \label{sec:methodology-chap1}

As an improvement over existing solutions, the research presented in this dissertation targets social commitments employed in systems exhibiting probabilistic behavior. We address the problem of specifying probabilistic social commitment in MASs by developing a novel logic called the probabilistic logic of commitments (PCTLC) that can represent and reason about social commitments in the face of uncertainty. The introduction of the new logic is motivated by the fact that the needed modal operators for reasoning about probabilistic social commitments and their fulfillments cannot be expressed using existing temporal logics. To build PCTLC, we advocate the technique of combining two existing logics in a new logic. Particulary, we adopt the independent join technique \cite{Bennett2002,Franceschet2004,Gabbay2003}. The reason why we use this technique is because it ensures the preservation of important properties of the logics being combined \cite{Konur2013}. In this perspective, we combine a logic of commitment called CTLC \cite{Bentahar2012,El-Menshawy2013a} and a probabilistic logic called PCTL \cite{Hansson1994}. This process can be seen as adding a probabilistic operator to the ingredients of the logic of commitment (CTLC), or vise versa (i.e., adding a commitment operator to the ingredients of the probabilistic logic PTLC). We model target systems using the formalism of interpreted systems. However, the original version
of interpreted systems introduced by Fagin et. al in \cite{Fagin1995} does not capture the probabilistic behavior of MASs and also does not account for the communication between interacting agents. Therefore, we combine two extended versions of the original formalism introduced respectively by Halpern \cite{Halpern2003} and Wan et al. \cite{Wan2013} to capture the stochastic behavior of the system, and Bentahar et al. \cite{Bentahar2012} and El-Menshawy et al. \cite{El-Menshawy2013a} to model the communication between interacting parties.

Furthermore, our approach evaluates social commitments at the design level as to help reduce the cost of the development process and increase robustness of target systems. This is achieved by formally verifying some given PCTLC-based properties using a model checking technique. Model checking was chosen due to the reasons stated earlier in Section \ref{sec:objectives-chap1}. However, model checking can be generally performed by one of the following methods. 1) Direct method in which new dedicated model checking algorithms are developed in order to verify social commitments, or 2) Indirect method which is also called reduction-based method or translation-based method. Indirect model checking techniques involve devising some reduction rules to reduce the problem of model checking the logic at hand to that of an existing logic in order to use current model checkers \cite{Lomuscio2007}. Certainly, each method has its own benefits with respect to the logic being verified. In this thesis we follow the latter method because it is easy to use and allows the re-use of existing model checkers \cite{El-Menshawy2013a}. Later in Chapters \ref{cha:PCTLC}, \ref{cha:PCTLKC}, and \ref{cha:PCTLKC+}, we show how the indirect method can effectively and efficiently verify probabilistic social commitments.

Our proposed model checking procedure for PCTLC includes instantiating a set of reduction rules that transform the problem of model checking PCTLC to the problem of model checking an existing probabilistic logic called PCTL. By so doing, we gain the privilege of re-using the available PRISM model checker.

The proposed logic of social commitment (PCTLC) is then extended by an epistemic operator to be able to express and reason about the interaction between knowledge and social commitments in the presence of uncertainty. The idea is that, we have various logics for each of knowledge and social commitments independently in the literature, so we combine a probabilistic logic of knowledge and a probabilistic logic of commitments in a single logic that we call the probabilistic logic of knowledge and commitment PCTL$^{kc}$. On that basis, we again construct a set of transformation rules to reduce the problem of model checking the proposed logic PCTL$^{kc}$ to that of PCTC so that formulae expressing properties written in PCTL$^{kc}$ can be model checked using PRISM by checking their corresponding formulae of PCTL.

 \begin{figure}[H]
                \begin{center}
                \includegraphics[width=16cm, height=20cm]{chap1/img/thesis-new.eps}
                \end{center}
                \caption{The Proposed Framework }
                \label{fig:proposed-framework}
    \end{figure}

To be able to handle social commitments when the scope of interacting agents is extended from the common one-to-one scheme to one-to-many scheme, we develop a semantics for the group social commitment operator and integrate it to the framework. We also add a group knowledge operator in order for the new logic to be more expressive and effective. The improved and refined logic is called the new logic of knowledge and commitments (PCTL$^{\textrm{kc+}}$). Moreover, we generalise the model checking technique proposed for PCTL$^{kc}$ to verify the new logic (PCTL$^{\textrm{kc+}}$) with the group operators.

Finally, each proposed reduction technique is implemented independently on top of the PRISM tool and applied to a concrete case study. 
Figure \ref{fig:proposed-framework} depicts the structure of the proposed work, links contributions to each other, and maps them to thesis chapters. Moreover, this figure shows where we answer each of the research questions presented in Section \ref{sec:problem statement-chap1}.

\section{Contributions}\label{sec:thesis-contributions-chap1}
We have developed a set of methods to pursue our objectives and to fill the research gap identified above. The majority of the work presented in this thesis has been published in the proceedings of various international conferences and refereed international journals. In summary, the main
contributions are:

\begin{enumerate}
\item A new logic called the probabilistic logic of commitments (PCTLC) that can represent and reason about social commitments in the presence of uncertainty \cite{Sultan2013}.

\item A new logic called the probabilistic logic of knowledge and commitment (PCTL$^{kc}$) whose expressive power helps capture the interaction between knowledge and social commitments in probabilistic MASs \cite{Sultan2014b}

\item A Semantics for group social commitment \cite{Sultan2014c}.

\item An improved version of the logic of knowledge and commitments enriched with epistemic and social group operators (PCTL$^{\textrm{kc+}}$). The distinguished feature of the new logic  lies in its ability of not only expressing the interaction between individual (basic) social commitments and knowledge, but also expressing the interaction between group social commitments and knowledge in the presence of uncertainty \cite{Sultan2014c}.

\item Three reduction-based model checking techniques for PCTLC \cite{Sultan2014a}, PCTL$^{kc}$ \cite{Sultan2014b}, and PCTL$^{\textrm{kc+}}$ \cite{Sultan2014d} respectively.

\item Implementation of the three proposed model checking techniques on top of the PRISM model checker using concrete case studies.

\end{enumerate}

\section{Thesis Organization}\label{sec:thesis-outline-chap1}
The remainder of this thesis is organized as follows. Chapter \ref{cha:background} describes the background needed for our research. Chapter \ref{cha:PCTLC}, presents a formal approach for handling probabilistic social commitments in MASs. In Chapter \ref{cha:PCTLKC}, we introduce a probabilistic approach for capturing and verifying the interaction between knowledge and social commitments. Chapter \ref{cha:PCTLKC+} presents an improved version of the approach presented in Chapter \ref{cha:PCTLKC} and then extends it to accommodate group knowledge and group commitments. %Also, in this chapter, a novel semantics for the group social commitment is given for the first time in the literature.
Chapter \ref{Chap5:Conclusion} concludes the thesis and identifies hints for future directions.

### 2015-04-05 thesis/thesis/chap3/chap3.tex
added thesis

\setcounter{chapter}{2}

\chapter{Probabilistic Social Commitments}\label{cha:PCTLC}

In this chapter\footnote{The results of this chapter have been published in the journal of Applied Soft Computing \cite{Sultan2014a}, and in SoMet\_13 \cite{Sultan2013}.}, we establish a formal approach that allows us to precisely address probabilistic social commitments in MASs. The proposed approach is based on a new logic called the Probabilistic Logic of Commitments (PCTLC). This logic is intended to be used for specifying, reasoning about, and verifying social commitments in the presence of uncertainty.
PCTLC extends PCTL \cite{Hansson1994} with a commitment modality. We model MASs using a new version of interpreted systems that merges two extended versions of the original formalism namely, the probabilistic interpreted systems \cite{Halpern2003,Wan2013}, and the communicative interpreted systems \cite{Bentahar2012,El-Menshawy2013a}. Finally, we propose a model checking technique for verifying the new logic (PCTLC). %social commitments employed in uncertain settings.

\section{Introduction} \label{sec:introduction}

In order to represent and reason about social commitments in MASs,
commitment logics that extend CTL (Computation Tree Logic), LTL
(Linear Temporal Logic), and CTL$^{*}$ (superset of CTL and LTL),
have been proposed, see for example
\cite{Bentahar2004,Giordano2007,Pham2007,Singh2000,Verdicchio2003}.

However, current logics are merely related to specifying and
verifying social commitments under the assumption of reliable behavior. That is, they assume an absolute, non-probabilistic running of systems under consideration.
Unfortunately, this is not always the case. Heterogeneous and
autonomous intelligent components in agent societies make it
challenging to precisely analyze random or unreliable agent
behaviors. This is because agents' actions are based on observing the
environment changes and in many situations agents cannot observe
all changes in the environment. Instead, each agent can only have a
partial view of other agents' behaviors \cite{LeeL09}. In such
cases, agents make estimations about the observable world as part
of their autonomous decision making processes. Moreover, when the
system being modeled is an open system, i.e., interacts with an
environment, then uncertainty in transitions may arise due to
imperfect information about the environment \cite{Walley1996}. Consequently, the problem of representing and verifying social commitments is made more complicated by the presence of transition uncertainty which makes agents uncertain about the effects of their actions on their peers and not fully
aware of the situations other agents are encountering. Moreover,
from the communication perspective, commitments themselves are
likely to be subject to probabilistic events. Xuan and Lesser
\cite{Xuan1999} have highlighted some sources of uncertainty that
make a commitment between two agents probabilistic:

\begin{enumerate}
\item The first source of uncertainty is related to the debtor's action(s). That is, debtor's action(s) might not always lead to the fulfilment of the commitment.

\item The second source comes from the agent decision processes. Debtors beliefs and desires might change such that continuing to pursue fulfilling the commitment for others becomes irrational. Debtors' beliefs about the commitment context include, for example, the degree that the agent to whom the commitment was made is still relying on its fulfillment. To the creditor, this can cause problems because its action(s) may depend on the honoring of the commitment by the debtor.

\item The third form of uncertainty comes from the incomplete knowledge of the debtor about the creditor or about the environment within which the agent interacts.
\end{enumerate}

Consequently, one cannot assume that all autonomous agents will behave as expected, and thus commitments among communicating parties cannot be treated under the assumption of certainty. Modeling uncertainty can be achieved using different tools including fuzzy logic as in \cite{Correa2013,Karray2004}, and probabilities as in \cite{Feng2011,Karthikeyan2013,Perko2011}. On the one hand, fuzzy logic is specifically designed to deal with imprecision of facts (or the membership in vaguely defined sets). Its use in MASs has been investigated by some researchers. In \cite{Garza2011a}, the authors exploited fuzzy logic in designing intelligent agents that communicate with each other using a mental approach that uses KQML \cite{Finin1994} as the underlying communication language.
However, mental approaches suffer from the semantics verification problem \cite{Wooldridge2000}. That is, they cannot verify whether an agent is acting according to a given semantics or not \cite{Wooldridge2009}. In our work, we adopt social approaches that are based on observable social commitments.

On the other hand, probability is an important component in the design and analysis of complex systems across a broad spectrum of application domains, including communication and multimedia protocols, randomised distributed algorithms, security protocols, and dynamic power management. It is commonly  used to model unreliable or unpredictable behavior. Probability deals with the chance of happening for an event or a condition (i.e., likelihood of some event or condition). Although probability has proven to be a powerful technique in handling different aspects of MASs \cite{Kulkarni2010,Wan2013}, its value in addressing social commitments for agent communication is yet to be investigated. In our research, we use probabilities to model the uncertainty because we are concerned with the likelihood of the fulfilment of the commitment. That is, when a social commitment between two agents takes place, we are interested to know about the chance of fulfilling that commitment at a certain state in the system. Additionally, using probabilities to handle the uncertainty of social commitments provides us with the privilege of exploiting existing probabilistic logics and model checkers. However, it is worth mentioning that probability assignments are not the focus of this research. Probability values can be obtained from historical data using some techniques such as the algorithm proposed in \cite{Ormandjieva2008} which allows us to compute the fixed probabilities between two states based on some other probabilities.

To motivate our study of modeling and verifying social commitments in the face of uncertainty, we use two situational examples that arise in practical settings such as web-based systems and mobile applications.

\textit{Example 1.} Let us consider the Online Shopping System
\cite{Gomaa2011} which aims at providing services for purchasing
online items. In the web-based Online Shopping System, customers
can request to purchase one or more items from the supplier.
Having selected an item, the customer commits towards the supplier
to pay in order for the request to take place. Once the order is
paid, the supplier confirms the order, and commits to deliver the
requested item and enters a planned shipping date. Finally, when
the order is shipped, the customer is notified. Because of the
uncertainty associated to the underlying infrastructures of both
commitments (i.e., the internet through which the payment is made
and the transport system used for the delivery of purchased
goods), there is no guarantee that these commitments will be
fulfilled. Therefore, reasoning about and verifying the
commitments to pay and to deliver have to be tackled with
probability in mind so that the degree of fulfilling each
commitment can be measured.

\textit{Example 2.} In the field of mobile applications which are
complex in nature, addressing social commitments should be
paired with the consideration of uncertainty of transitions and
commitments. Let us consider a simple scenario where a receiver
agent and a sender agent have an agreement, in which the receiver
agrees to pay the sender in return of the delivery of a requested
service. This can be represented as a social commitment, in which
the receiver will be committed to the sender to pay upon obtaining
the requested service. In such a scenario, because of the presence
of stochastic behavior in mobile applications, the commitment to
pay is not going to be surely satisfied.

The scenarios described above cannot be represented by existing
conventional commitment logics because of the uncertainty aspect
in both systems. Consequently, they cannot be verified. To cope
with the situation, we need a probabilistic commitment logic that
accounts for uncertainty, and a probabilistic model
checking procedure to verify properties expressed in the new logic.

The ultimate objective of this chapter is to introduce a logical approach that is capable of addressing probabilistic social commitments in MASs. This is done as follows. \underline{First}, we present a new probabilistic logic called PCTLC to express and reason about social commitments when uncertainty is a key factor. The introduction of PCTLC logic was driven by the fact that current probabilistic temporal logics such as PCTL \cite{Hansson1994} and PCTL$^*$ \cite{Baier1998} consider neither commitments nor agent communication. PCTLC extends PCTL with modalities for commitments and their fulfillments. We model probabilistic MASs by a formalism resulted from extending the  interpreted systems introduced by Fagin et al. \cite{Fagin1995}.
This extension considers agents uncertainty and their
communication abilities. Properties to be verified (i.e., social
commitments) are specified using the probabilistic logic of
commitment PCTLC. \underline{Second}, we introduce a formal and automatic, probabilistic model checking technique for probabilistic commitment-based agent interactions. Our proposed verification method is a reduction-based model checking technique and consists of transforming the problem of model
checking PCTLC into the problem of model checking PCTL \cite{Hansson1994} so that the use of PRISM is made possible. This reduction encompasses two main steps. In the first step, we devise a set of formal rules to transform the PCTLC model into an MDP model. Then, we reduce the MDP into DTMC to be as an input to the PRISM model checker. In the latter step, we transform PCTLC formulae into PCTL formulae based on some rules developed specifically for this purpose.
As argued in \cite{El-Menshawy2013a}, the main advantage of the reduction techniques compared to the direct ones is that they are easy to implement and allow the re-use of the existing model checkers. \underline{Third}, we implement the proposed model checking approach on top of the PRISM model checker and then apply it on a concrete case study, namely Oblivious Transfer Protocol \cite{Rivest1999} from cryptography domain. Figure \ref{approach-cha3} gives an overview of the proposed approach.

\begin{figure}%[h]
\begin{center}
\includegraphics [width=14cm, height=5cm]{chap3/img/approach-cha3.eps}
  \caption{A schematic view of the probabilistic social commitment approach}
\label{approach-cha3}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Probabilistic Logic of Commitments (PCTLC)}\label{sec:PCTLC}

In this section, we present a new modal logic called the probabilistic logic of commitments (PCTLC) to address probabilistic social commitments in MASs. The logic we introduce extends the probabilistic branching-time logic PCTL \cite{Hansson1994} with a commitment modality. To do so, we merge two existing logic namely PCTL \cite{Hansson1994} and CTLC \cite{Bentahar2012,El-Menshawy2013a} using the independent join technique \cite{Franceschet2004}. The independent join combines logics as they are defined in the literature. Thus, it ensures the preservation of each logic's properties in the new logic. Hereafter, we first present the syntax of our new logic, and then we define its semantics. Before going further, we define a new version of interpreted systems formalism with abilities to account for the uncertainty aspect in target MASs and to model the social interactions between communicating parties.

The PCTLC model is generated based on two extensions of the interpreted systems formalism \cite{Fagin1995} introduced in \cite{Bentahar2012,El-Menshawy2013a}, and \cite{Halpern2003,Wan2013} as discussed in Chapter \ref{cha:background}.

\begin{definition}[Models]\label{def:models}
Given a set of atomic propositions $AP = (p,q,r, \ldots)$, the
model $\mathfrak{M_1}=(S,I,\texttt{P},\{\sim_{i \rightarrow
j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$ is a tuple where:
%
\begin{itemize}
\item  $S \subseteq L_1 \times \ldots \times L_n$ is a countable
set of all reachable global states for the system. A state $s$ is
reachable iff there exists a sequence of transitions from an
initial state to $s$ in which the probability of each transition
is greater than $0$.

\item  $I \in S$ is an initial global state for the system.

\item  $\texttt{P}:S\times S\rightarrow [0,1]$ is a total
transition probability function defined as $\texttt{P}(s,
s')=\tau(s,a^{s \rightarrow s'}, s')$ iff there exists a joint
action $a=(a_1,\ldots,a_n) \in ACT$ such that \\
$\sum_{i \in \texttt{Agt}} \tau_i(l_i(s),a^{l_i(s)\rightarrow l_i(s')},l_i(s')) > 0$ and $\sum_{s' \in S} \texttt{P}(s,s') =1$
for all $s \in S$.

\item For each pair $(i,j) \in \texttt{Agt}^2$,
$\sim_{i\rightarrow j} \subseteq S \times S$ is a social accessibility relation. $s \sim_{i\rightarrow j} s'$ is defined by the following conditions:
      %
  \begin{enumerate}
       \item $l_i(s)=l_i(s')$.
       \item $Var_i \cap Var_j \neq \emptyset$ such that $\forall x \in Var_i \cap Var_j$, we have $l^{x}_i(s)\!=\!l^{x}_j(s')$.
       \item $\forall y \in Var_j\!-\! Var_i$, we have $l^{y}_j(s)\!=\!l^{y}_j(s')$.
  \end{enumerate}
       %
  \item  $\nu : S\rightarrow 2^{AP}$ is a function valuating states with atomic propositions.
\end{itemize}
\end{definition}

\noindent Our model $\mathfrak{M_1}$ can be thought of as a labeled
state-transition system in which each transition from $s$ to $s'$
is annotated with a probability value in the matrix
$\texttt{P}$ indicating the likelihood of its occurrence
wherein the transition is assumed to take a discrete time-step.
This means that there is no notion of real time, while reasoning
about discrete time is possible through state variables keeping
track of time and counting transition steps. It is also important to
mention that every state in $\mathfrak{M_1}$ has at least one
outgoing transition to avoid deadlocks. Moreover, all
terminating/final states are modeled with a self-loop.

\vspace{0.2cm} \noindent \texttt{Computation paths}. We can unfold
the model $\mathfrak{M_1}$ into a set of paths. A path through the
model $\mathfrak{M_1}$ is a non-empty (finite or infinite) sequence
$\pi=s_0~s_1~\ldots$ of global states such that
$\texttt{P}(s_r, s_{r+1})> 0$ for all $r \geq 0$. Also,
$\pi(r)$ denotes the $(r+1)^{th}$ state of $\pi$, i.e.,
$\pi(r)=s_r$ for all $r \geq 0$.

\noindent \texttt{Probability Space}. Let $\Omega$ be a sample set
(or the set of possible outcomes of an experiment). A pair
$(\Omega,\mathrm{F})$ is said to be a \textit{sample space} if
$\mathrm{F}$ is a $\sigma$-algebra of measurable subsets of
$\Omega$, which are closed under countable union and complement
and often built from basic events called \textit{cylinders} (the
elements of $\mathrm{F}$ are called \textit{events}). A triple
$(\Omega,\mathrm{F},\mu)$ is a \textit{probability space} if
$\mu$ is a probability measure over $\mathrm{F}$, i.e., $0\leq\mu
(A)\leq 1$ for all $A\in \mathrm{F}$ such that:
%
\begin{itemize}
\item $\mu(\emptyset)=0$,
\item $\mu(\Omega) = 1$, and
\item $\mu(\bigcup_{k=1}^{\infty}A_k)=\Sigma_{k=1}^\infty \mu(A_k)$ for disjoint $A_k$.
\end{itemize}

The probability matrix $\texttt{P}$ induces a probability
space on the set of infinite paths $\Pi(s)$, which start in the
state $s$, using the cylinder construction \cite{Baier2008} as
follows. An observation of a finite path determines a basic event
(cylinder). Suppose $s = s_0$; for $\pi=s_0~s_1~\ldots~s_n$, we
define the probability measure $Prob_s \{\pi\}$ %$Prob_s^{fin}$
for the $\pi$-cylinder as follows:
%
\begin{equation}
%Prob_s^{fin}=
Prob_s \{\pi\}=
\begin{cases} 1~~~\textrm{if}~\pi~\textrm{consists~of~a~single~state}\\
{\prod_{\substack{r=0}}^{n-1} \texttt{P}(s_r,s_{r+1})~~~\textrm{otherwise.}}
 \end{cases}
\end{equation}
%
\noindent This extends to a unique measure $Prob_s$ on the set of
infinite paths $\Pi(s)$ w.r.t countable union and complement
\cite{Kwiatkowska2007}.

\subsection{Syntax of PCTLC} \label{sec:syntax-PCTLKC}

\begin{definition}[PCTLC syntax]\label{def:syntax}
Given a set of atomic propositions $AP$, the PCTLC formulae are
defined by the following BNF grammar:
%
\begin{align*}
    \varphi & ::= p~|~\neg \varphi~|~\varphi \vee \varphi~|~\mathcal{C}~|~ \mathbb{P}_{\bowtie k} (\psi)~|~\mathbb{P}_{\bowtie k}(\mathcal{C})\\
    \psi & ::=\bigcirc \varphi ~ | ~ \varphi ~U~ \varphi~|~ \varphi~ U^{\leq m} ~ \varphi \\
    \mathcal{C} & ::= C_{i\rightarrow j}\varphi ~| ~ Fu(C_{i\rightarrow j}\varphi)
\end{align*}
%
where: $p\in AP$ is an atomic proposition and $\mathbb{P}_{\bowtie
k}$ is a probabilistic operator where $\bowtie \in\{<,\leq,>,\ge\}$ and $k\in [0,1]$ is a probability bound or threshold. $m \in\mathbb{N}^+ $ is a positive integer number reflecting the maximum number of transitions needed to reach a certain state. $\varphi$ and $\psi$ are state and path formulae interpreted over the states and paths of $\mathfrak{M_1}$ respectively. The
Boolean connectives $\neg$ and $\vee$ are defined in the usual
way. Formulae $\mathcal{C}$, called social formulae, are special
state formulae in PCTLC that can express social properties using
the modal connectives $C_{i\rightarrow j}$ and $Fu(C_{i\rightarrow
j})$ standing for ``commitment'' and ``fulfillment of commitment''
respectively. $\bigcirc, U$ and $U^{\leq m}$ stand for ``next time'',
``until'' and ``bounded until'' path modal connectives respectively.

\end{definition}

\noindent The intuitive meanings of the temporal and probabilistic operators are straightforward from PCTL \cite{Jonsson1991}. $C_{i\rightarrow j}\varphi$ is read as ``agent $i$ commits towards agent $j$ that $\varphi$''. $Fu(C_{i\rightarrow j}\varphi)$ is read as ``the commitment $C_{i\rightarrow j}\varphi$ is fulfilled''. The probabilistic operator $\mathbb{P}_{\bowtie k}(\mathcal{C})$ on social formulae $\mathcal{C}$ states the degree of the commitment and the
fulfillment of the commitment: how much the agent is confident
about its commitment and fulfilling its commitment respectively.

PCTLC logic allows us to express properties like $C_{i \rightarrow j} \varphi \supset (\mathbb{P}_{\ge 0.95}(\top~U^{\leq 13}Fu(C_{i\rightarrow j}\varphi)))$ which means when a commitment about $\varphi$ is
held, then the probability that the commitment is fulfilled within
13 discrete-time steps is at least 0.95, where $\supset$ stands
for the logical implication.

\subsection{Semantics of PCTLC} \label{sec: semantics of PCTLC}

The semantics of our PCTLC is interpreted over the probabilistic model  $\mathfrak{M_1}$ which was introduced above.  Given a model $\mathfrak{M_1}=(S,\texttt{P},I,\{\sim_{i \rightarrow
j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$, then
$(\mathfrak{M_1},s) \models \varphi$ states that ``a state $s$ in the
model $\mathfrak{M_1}$ satisfies the state formula $\varphi$,
$(\mathfrak{M_1},\pi) \models \psi$ means that ``a path $\pi$ in the
model $\mathfrak{M_1}$ satisfies the path formula $\psi$, and
$(\mathfrak{M_1},s) \models \mathbb{P}_{\bowtie k}(\psi)$ means that
``a state $s$ in the model $\mathfrak{M_1}$ satisfies
$\mathbb{P}_{\bowtie k}(\psi)$ if the probability of taking a path
from $s$ that satisfies $\psi$ is in the interval specified by
$\bowtie k$''. When the model $\mathfrak{M_1}$ is clear from the
context, we simply write the satisfaction relation $\models$ as
follows: $s \models \varphi$ and $\pi \models \psi$. Furthermore,
for a given pair $(i,j)\in \texttt{Agt}^2$ of agents, we denote
the number of accessible states $s'$ from a given state $s$ such
that $s\sim_{i\rightarrow j}s'$ by $|s\sim_{i\rightarrow j}s'|$.
The sample space of such pair of agents at $s$ is the set of
possible accessible states of $(i,j)$ at $s$ and is equal to
$|s\sim_{i\rightarrow j}s'|$. We also define $|s\models \varphi|$
as follows:

\begin{center}
$|s\models \varphi|=
\begin{cases}
1,~~~\textrm{if}~ s\models\varphi\\
0,~~~\textrm{otherwise.}
\end{cases}$
\end{center}

\begin{definition}[\textbf{Satisfaction}]\label{def:semantics-pctlc} Satisfaction of a PCTLC formula in the model $\mathfrak{M_1}$ is conductively defined as follows:

\begin{itemize}
\item For a non-probabilistic state formula:

$s\models p~~~~~~~~~~~~~~~~\emph{iff}~~p\in \nu(s);\\
s\models \varphi_1 \vee \varphi_2 ~~~~~~~\emph{iff}~~s\models \varphi_1~\textrm{or}~s \models \varphi_2; \\
s\models \neg \varphi~~~~~~~~~~~~~\emph{iff}~~s \nvDash \varphi;\\
s\models C_{i\rightarrow j}\varphi~~~~~~~~\emph{iff} ~~\forall s' \in S~\textrm{s.t.}~s \sim_{i \rightarrow j}s', \textrm{we~have}~s' \models \varphi;\\
%\textrm{we~have}~s' \models \varphi;\\
s\models Fu(C_{i\rightarrow j}\varphi) ~~\emph{iff} ~~\exists s' \in S~\textrm{s.t.}~s' \sim_{i \rightarrow j}s ~ \textrm{and}~s' \models C_{i\rightarrow j}\varphi;$

\item For a path formula:

%\vspace{-0.5cm}

 $\pi \models \bigcirc \varphi~~~~~~~~~~\emph{iff}~~\pi(1) \models \varphi; \\
 \pi \models \varphi_1~U^{\leq m}~\varphi_2~~\emph{iff}~~\exists~ k \leq m~~\textrm{s.t.}~~ \pi(k) \models \varphi_2 ~\textrm{and}~\forall i < k, \pi(i) \models \varphi_1;\\
 \pi \models \varphi_1 ~U~\varphi_2~~~~~\emph{iff}~~\exists~ m \geq 0~~\textrm{s.t.}~~\pi \models \varphi_1~U^{\leq m}~\varphi_2;$

\item For a probabilistic operator working over a path formula:

%\vspace{-0.5cm}
%\begin{align*}
 $s \models \mathbb{P}_{\bowtie k} (\psi)~~\emph{iff}~~Prob_s(\psi)\bowtie k~
\textrm{where:}~Prob_s(\psi)=Prob_s\{\pi \in \Pi(s)~|~\pi\models
\psi\};$
%\end{align*}

\item For a probabilistic operator working over a social formula,
where the set of events $\mathrm{F}$ is the set of states
satisfying a formula, and assuming that the probabilities of
accessible states from state $s$ are equally distributed:

%\begin{tabbing}
 $s\models \mathbb{P}_{\bowtie k}(C_{i\rightarrow j}\varphi)$
   ~\emph{iff}  $Prob(s \models C_{i\rightarrow j}\varphi) \bowtie \!k$, where:
%\end{tabbing}
%
\vspace{-0.4cm}
\begin{equation*}
Prob(s\models C_{i\rightarrow j}\varphi)=\frac{\sum_{s \sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s \sim_{i \rightarrow j}s'| };
\end{equation*}

%\begin{tabbing}
$s\models \mathbb{P}_{\bowtie k}(Fu(C_{i\rightarrow j}\varphi))$
    ~~ \emph{iff}~ $Prob(s \models Fu(C_{i\rightarrow j}\varphi)) \bowtie k$, where:
%\end{tabbing}
%
%\vspace{-0.4cm}
%\begin{equation*}
\begin{align*}
%  Prob(s\models Fu(C_{i\rightarrow j}\varphi))\ =\frac{\sum_{s' \sim_{i \rightarrow j}s}|s'\models C_{i\rightarrow j}\varphi|}{|s' \sim_{i \rightarrow j}s| }
%
& Prob(s\models Fu(C_{i\rightarrow j}\varphi))\ = Prob_s\{\pi \in \Pi(s') ~|~ s' \sim_{i \rightarrow j}s ~\textrm{and}~ \pi = s' \ldots s ~\textrm{and}~ s' \models C_{i\rightarrow j}\varphi\}
\end{align*}
%\end{equation*}

\end{itemize}

\end{definition}

Note that, the probabilistic commitment is computed based on the number of
accessible states that satisfy the content over the whole number
of accessible states, which reflects the uncertainty of the agent
over the accessible states, so that over the commitment. On the other hand, probabilistic fulfillment is computed using the probabilistic
transitions of the path linking the commitment state to the
fulfillment state.

The following proposition is straightforward from the semantics:

\begin{proposition} \label{proposition-PCTLC}~\\
If $(\mathfrak{M_1},s)\models \mathbb{P}_{\leq0} (Fu(C_{i \rightarrow
j}\varphi))$ and $(\mathfrak{M_1},s)\models Fu(C_{i \rightarrow
j}\varphi)$, then the state $s$ is not reachable from the commitment state.
\end{proposition}

\begin{theorem}[Probabilistic and Conventional Commitments Equivalences]\label{Commitments Equivelances} ~\\

\begin{enumerate}
\item $(\mathfrak{M_1},s)\models \mathbb{P}_{\geq1} (C_{i \rightarrow
j}\varphi)$ ~~~iff~~ $(\mathfrak{M_1},s)\models C_{i \rightarrow
j}\varphi$

\item $(\mathfrak{M_1},s)\models \mathbb{P}_{\leq0} (C_{i \rightarrow
j}\varphi)$ ~~~iff~~ $(\mathfrak{M_1},s)\models C_{i \rightarrow
j}\neg \varphi$

\item $(\mathfrak{M_1},s)\models \mathbb{P}_{]0,1[} (C_{i \rightarrow
j}\varphi)$ ~~iff~~ $(\mathfrak{M_1},s)\models \neg C_{i
\rightarrow j}\neg\varphi \wedge \neg C_{i \rightarrow j}\varphi$

\end{enumerate}

\end{theorem}

\begin{proof}\hspace{-0.9cm}%$~\\$
%\begin{proof} %\hspace{-0.5cm} \\
 %In what follows, we prove the above equivalences of probabilistic and conventional commitments.

\begin{itemize}
\item First equivalence. ~\\
    $``\Longrightarrow"$. Assume $s\models \mathbb{P}_{\geq1} (C_{i \rightarrow j}\varphi)$.
    By the PCTLC semantics, it follows that $Prob(s\models C_{i\rightarrow j}\varphi)\geq1$.
    Thus,  $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}\geq1$.
    This means that for all $s'\in S$ such that $s\sim_{i \rightarrow j}s'$, we have
    $s'\models \varphi$, and hence $s \models C_{i\rightarrow j}\varphi$. \\
    $``\Longleftarrow"$. Assume $s\models C_{i \rightarrow j}\varphi$. By the
    PCTLC semantics, it follows that for all $s'\in S$ such that $s\sim_{i \rightarrow j}s'$,
    we have $s'\models \varphi$ (i.e. all accessible states from $s$ satisfy $\varphi$).
    Consequently, $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = |s\sim_{i \rightarrow j}s'|$.
    Therefore, $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}\geq1$
    and hence, $s\models \mathbb{P}_{\geq1} (C_{i \rightarrow j}\varphi)$.

\item Second equivalence. ~\\
    $``\Longrightarrow"$. Assume $s\models \mathbb{P}_{\leq0} (C_{i \rightarrow j}\varphi)$.
    By the PCTLC semantics, it follows that $Prob(s\models C_{i\rightarrow j}\varphi)\leq0$.
    Thus, $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi|}{|s\sim_{i \rightarrow j}s'|}\leq0$.
    Since the set of the accessible states from $s$ is not empty, then $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi|$
    must be 0 (i.e. $\varphi$ is not true in any of the accessible states). Consequently, for all $s'\in S$
    such that $s\sim_{i \rightarrow j}s'$, we have $s'\nvDash \varphi$, which means $s'\vDash \neg \varphi$.
     Hence, $s\models C_{i\rightarrow j}\neg \varphi$.~\\
%
    $``\Longleftarrow"$. Assume $s\models C_{i \rightarrow j}\neg \varphi$. By the PCTLC semantics,
    it follows that for all $s'\in S$ such that
    $s\sim_{i \rightarrow j}s'$, we have $s'\nvDash \varphi$. Since the set of the accessible states from $s$ is not empty,
    then $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}\leq0$.
    Hence, $s\models \mathbb{P}_{\leq0} (C_{i \rightarrow j}\varphi)$.

\item Third equivalence. ~\\
    $``\Longrightarrow"$. Assume $s\models \mathbb{P}_{]0,1[} (C_{i \rightarrow j}\varphi)$. By the PCTLC semantics,
    it follows that $0< Prob(s\models C_{i\rightarrow j}\varphi)<1$. Thus,
    $0<\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s \sim_{i \rightarrow j}s'|}<1$.
    This means that it would never be the case that $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = |s\sim_{i \rightarrow j}s'|$
    nor $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = 0$. Consequently, there exist some $s', s'' \in S$
    such that $s\sim_{i \rightarrow j}s'$ and $s\sim_{i \rightarrow j}s''$ and $s'\models \varphi$ and $s''\models \neg \varphi$.
    Hence, it is impossible to have
    $\overline{s}\models \neg\varphi$ or $\overline{s}\models \varphi$ for all $\overline{s}\in S$
    such that $s\sim_{i \rightarrow j}\overline{s}$. Consequently,
    $s\nvDash  C_{i \rightarrow j}\neg\varphi$ and $s\nvDash  C_{i \rightarrow
    j}\varphi$. Hence $s\models \neg C_{i \rightarrow j}\neg\varphi$ and $s\models \neg C_{i \rightarrow j}\varphi$. ~\\
    %
    $``\Longleftarrow"$. Assume $s\models \neg C_{i \rightarrow j}\varphi$. By the PCTLC semantics,
    it follows that there exists $s'\in S$ such that $s\sim_{i \rightarrow j}s'$ and $s'\models \neg \varphi$.
    Consequently, it would never be the case that $s'\models \varphi$ for all $s'\in S$
    such that $s\sim_{i \rightarrow j}s'$. Therefore,
    $1>\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}$.
    Now assume $s\models \neg C_{i \rightarrow j}\neg \varphi$. Therefore, $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = 0$
    would never be he case as some accessible states should satisfy $\varphi$. %this means that $s\models \mathbb{P}_{\leq0} (C_{i \rightarrow j}\varphi)$
    %(see the proof of second equivalence above).
    Consequently,
    $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}>0$.
    Thus, $0<\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s \sim_{i \rightarrow j}s'|}<1$.
    Hence, $s\models \mathbb{P}_{]0,1[} (C_{i \rightarrow
    j}\varphi)$.
\end{itemize}

\end{proof}
\vspace{0.2cm}
\begin{theorem}[Probabilistic and Conventional Fulfillment Equivalences]\label{Fulfiilemt Equivelances} ~\\

\begin{enumerate}
\item $(\mathfrak{M_1},s)\models \mathbb{P}_{>0} (Fu(C_{i \rightarrow
j}\varphi))$ iff $(\mathfrak{M_1},s)\models Fu(C_{i \rightarrow
j}\varphi)$ and $s$ is reachable from the commitment state.

\item $(\mathfrak{M_1},s)\models \mathbb{P}_{\leq0} (Fu(C_{i \rightarrow
j}\varphi))$ iff $(\mathfrak{M_1},s)\models \neg Fu(C_{i \rightarrow
j}\varphi)$ or $s$ is not reachable from the commitment state.

\end{enumerate}

\end{theorem}

\begin{proof} \hspace{0.5cm} \\
The proofs of these equivalences are direct from Proposition
\ref{proposition-PCTLC} and the above semantics.

 \end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model Checking PCTLC using Reduction}\label{sec:model-checking-pctlc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
When designing communicating agent-based systems that are complex,
and stochastic in nature, formal verification is generally
recognized as one of the best design support technologies, and a
valuable tool towards having efficient systems in terms of
ensuring the compliance of system design models against the given
requirements.

Given a multi-agent system represented as a probabilistic interpreted system $\mathfrak{M_1}$ and a specification $\varphi$ in PCTLC describing a desirable property, the problem of probabilistic model checking PCTLC can be defined as: 1) establishing whether or not $(\mathfrak{M_1},
I)\models \varphi$, i.e., if $I \in Sat(\varphi)$ where
$Sat(\varphi)$=$\{s\in S ~~|~~ \mathfrak{M_1},s \models \varphi \}$
is the set of states satisfying $\varphi$, 2) comparing the
probability of satisfying $\varphi$ with a probability threshold
$\bowtie k$, where $Sat(\mathbb{P}_{\bowtie k}(\varphi))=\{s\in S
~|~ Prob_s(\varphi)\bowtie k \}$, or 3) computing the probability
of $\varphi$, $(\mathfrak{M_1}, s)\models \mathbb{P}_{=?}
~(\varphi)$. Note that answers to the second and third queries can
be: (1) truth values, when the specification simply asks for a
comparison to a probability threshold, or (2) quantitative,
returning the actual probability.

\begin{figure}[!ht]
\begin{center}
\includegraphics [width=14cm, height=4.5cm]{chap3/img/reduction-process-cha3.eps}
  \caption{The proposed reduction technique of model checking PCTLC}
\label{reduction-process}
\end{center}
\end{figure}

Figure \ref{reduction-process} depicts the workflow of our
reduction technique. As mentioned before, the idea is to reduce the problem of probabilistic model checking PCTLC to the problem of probabilistic
model checking PCTL in order to be able to use the PRISM model
checker. Concretely, the proposed reduction technique consists of
two processes (see Figure \ref{reduction-process}). In the former
process, we transform our model $\mathfrak{M_1}$ into an MDP model.
MDPs are the standard models for describing systems with
probabilistic and nondeterministic behavior \cite{Rutten2004}. At
every state of an MDP, one or more actions are available, and each
action is associated with a probability distribution over the
successor states. That is, MDPs are not augmented with a unique
probability measure. Reasoning about probabilities of sets of
paths of an MDP relies on the resolution of the nondeterminism. In
order to define the semantics of such an MDP, as in
\cite{Forejt2011}, we use the notion of adversary to factor out the nondeterminism and consider the probability of some
behavior of the MDP (i.e., allowing us to place a well-defined
probability on the set of paths for each adversary). Informally,
at each step, the adversary picks an action, and then the next
state is picked according to the probability distribution
associated with the action. In this work, we focus on a special
class of adversaries called \emph{Memoryless Adversary} where the
choice of action depends only on the state and independent of what
has happened in the history (i.e., which path led to the current
state). An adversary is said to be memoryless if it always selects
the same action in a given state. The resulting adversaries are
basically DTMC models for which we can define a probability
measure over paths. The obtained DTMC models will be the input of
the PRISM model checker. In the latter process of the reduction
technique, we transform PCTLC formulae into PCTL formulae (see
Section \ref{sec:reducing-pctlc-to-pctl}).

\subsection{Transforming the Model $\mathfrak{M_1}$} \label{sec:reducing-proposed-model}

Given $\mathfrak{M_1}=(S,\texttt{P},I,\{\sim_{i \rightarrow j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$, and a PCTLC formula $\varphi$, we define an MDP model $\mathfrak{M'_1}$ = $\mathscr{H}(\mathfrak{M_1})$ and PCTL formula $\mathscr{H}(\varphi)$ using the transformation function $\mathscr{H}$ such that $\mathfrak{M_1} \models \varphi$ iff $\mathscr{H}(\mathfrak{M_1})\models \mathscr{H}(\varphi)$.  Recall that the model $\mathfrak{M'_1}$ is an MDP model  $= (\mathbb{S}, AC, \textsf{P}_t ,I_i, L)$. Now, the model $\mathfrak{M'_1}$ can be defined using the function $\mathscr{H}$ as follows:

\begin{figure}[!htp]
\begin{center}
\includegraphics [width=12cm, height=4cm]{chap3/img/relation-translation.eps}
  \caption{Translating relations in $\mathfrak{M_1}$ model into actions in the MDP model}
\label{fig-relation-to-actions-cha3}
\end{center}
\end{figure}

\begin{itemize}
\item $\mathbb{S}$=$S$; $I_i$=$I$; $L$=$\nu$.

\item The set of atomic action propositions $AT$  is defined as
follows:\\
$AT = \{\varepsilon \} \cup \{\alpha_{1 \rightarrow 1},
\alpha_{1 \rightarrow 2}, \dots, \alpha_{n \rightarrow n}\} \cup
\{\beta_{1 \rightarrow 1}, \beta_{1 \rightarrow 2}, \dots,
\beta_{n \rightarrow n}\}$. Consequently, the set of actions $AC =
\{\gamma \} \cup \{\alpha^{11}, \alpha^{12}, \dots, \alpha^{nn}\}
\cup \{\beta^{11}, \beta^{12}, \dots, \beta^{nn}\}$ where $n$ is
the number of agents, $1 \leq i \leq n$, and $1 \leq j \leq n$.
Actions $\gamma, \alpha^{ij}$, and $\beta^{ij}$ denote transitions
defined, respectively, from the probabilistic transition relation
$\texttt{P}$, the accessibility relation $\sim_{i \rightarrow j}$,
and the transition added when there exists a transition labeled
with $\alpha^{ij}$ and needed to define the transformation of the
formula $Fu(C_{i \rightarrow j})$. Note that, $\varepsilon$ is the
atomic action forming $\gamma$, $\alpha_{i\rightarrow j}$ is the
atomic action forming $\alpha^{ij}$, and $\beta_{i\rightarrow j}$
is the atomic action forming $\beta^{ij}$.

\item $\textsf{P}_t$ combines the probabilistic transition
relations of $\texttt{P}$ and the probabilistic relations obtained
from translating accessibility relations $\sim_{i \rightarrow j}$
to transitions labeled with $\alpha^{ij}$ and probabilistic
transitions labeled with $\beta^{ij}$. The probability of each
transition labeled with $\alpha^{ij}$ is equal to the probability
of each other transition labeled with $\alpha^{ij}$ emanating from
the same state which is calculated by dividing one over the number
of transitions labeled with $\alpha^{ij}$ (i.e., equal
distribution). The probabilities of transitions labeled with
$\beta^{ij}$ are calculated in the same way. For states $s, s' \in
\mathbb{S}$ and action $\theta \in AC$, the function
$\textsf{P}_t$ is defined as follows:
\begin{equation*}
    \textsf{P}_t(s, \theta , s' )=
\begin{cases}
    \texttt{P}(s, s'),   & \textit{if } \theta = \gamma  \\
    \frac{1}{|s\sim_{i \rightarrow j} s'|},   & \textit{if } \theta = \alpha^{ij}\\
    \frac{1}{|s'\sim_{i \rightarrow j} s|},   & \textit{if } \theta = \beta^{ij}.
    \end{cases}
    \end{equation*}

\end{itemize}

Now, we define three different adversaries as follows: $\sigma_t$ to
be used for interpreting temporal formulae, $\sigma_c$ to be used
for interpreting commitment formulae, and $\sigma_{fu}$ to be used for
interpreting fulfillment formulae. It is worth to mention that
when defining $\sigma_c$ and $\sigma_{fu}$, some rules need to be
set. To define $\sigma_c$ at a state, action $\alpha^{ij}$ has to
be among the enabled actions at that state. Then, the memoryless
adversary $\sigma_c$ picks the action $\alpha^{ij}$ at this state,
and $\gamma$ at all other states. Meaning that, defining adversary
$\sigma_c$ at a state rather than a commitment state (the state
where $C_{i\rightarrow j}\varphi$ holds) would not be possible.
The same principle applies to $\sigma_fu$. However, $\sigma_t$
always picks action $\gamma$ at every state in
$\mathfrak{M'_1}$. The induced model of applying the adversary $\sigma$ over $\mathfrak{M'_1}$ is a DTMC model.

Hereafter, we introduce our reduction rules that translate PCTLC
formulae to PCTL formulae w.r.t a given adversary.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Reducing PCTLC Formulae into PCTL Formulae} \label{sec:reducing-pctlc-to-pctl}

Given the adversary $\sigma_t$, the PCTLC formulae are transformed
inductively into PCTL as follows:

$\mathscr{H}(p)=p$, if $p$ is an atomic proposition,

$\mathscr{H}(\neg \varphi)= \neg \mathscr{H} (\varphi)$,

$\mathscr{H}(\mathbb{P}_{\bowtie k}(\varphi \vee \psi))=\mathbb{P}_{\bowtie k}(\mathscr{H}(\varphi) \vee \mathscr{H}(\psi))$,

$\mathscr{H}(\mathbb{P}_{\bowtie k}\bigcirc \varphi)=\mathbb{P}_{\bowtie k} \bigcirc \mathscr{H}(\varphi)$,

$\mathscr{H}(\mathbb{P}_{\bowtie k}(\varphi~ U ~ \psi))=\mathbb{P}_{\bowtie k} (\mathscr{H}(\varphi) U \mathscr{H}(\psi))$,

$\mathscr{H}(\mathbb{P}_{\bowtie k}(\varphi~ U^{\leq m} ~ \psi))=\mathbb{P}_{\bowtie k} (\mathscr{H}(\varphi) U^{\leq m} \mathscr{H}(\psi))$,

It is important to note that, the social formulae
($C_{i\rightarrow j}, Fu$) are not transformed into PCTL by making
use of $\sigma_t$ because $\sigma_t$ does not capture the social
accessibility relation and instead it captures only the temporal
transitions at every state in the model $\mathfrak{M'_1}$.

Given the adversary $\sigma_c$, the PCTLC commitment formulae are
transformed inductively into PCTL as follows:

$\mathscr{H}(C_{i\rightarrow j}\varphi)= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{H}(\varphi))$,

$\mathscr{H}(\mathbb{P}_{\bowtie k} C_{i\rightarrow j}\varphi)= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathscr{H}(\varphi)$),

The reason behind translating a commitment formula
$C_{i\rightarrow j}\varphi$ to next operator $\bigcirc$ followed
by $\mathscr{H}(\varphi)$ is that by having transformed the social
accessibility relation $\sim_{i \rightarrow j}$ into a transition
labeled with action $\alpha^{ij}$, it is obvious that all next
states of the commitment state through the transition labeled with
$\alpha^{ij}$ satisfy $\mathscr{H}(\varphi)$ (see Figure
\ref{fig-relation-to-actions-cha3}). Hence, with respect to $\sigma_c$,
which is a DTMC model that ignores all transitions at the
commitment state except those labeled with $\alpha^{ij}$, we
clearly see that the commitment state is converted into a state
whose all successor states satisfy $\mathscr{H}(\varphi)$.

Given the adversary $\sigma_{fu}$, the PCTLC fulfillment formulae
are transformed inductively into PCTL as follows:

$\mathscr{H}(Fu(C_{i\rightarrow j}\varphi))= \mathbb{P}_{>0}(\bigcirc \mathscr{H}(C_{i\rightarrow j}\varphi))= \mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{H}(\varphi)))$,

$\mathscr{H}(\mathbb{P}_{\bowtie k} Fu(C_{i\rightarrow j}\varphi))= \mathbb{P}_{\bowtie k} (\mathbb{P}_{>0}\bigcirc\mathscr{H}(C_{i\rightarrow j}\varphi))= \mathbb{P}_{\bowtie k}(\mathbb{P}_{>0}\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{H}(\varphi)))$.

$Fu(C_{i\rightarrow j}\varphi)$ is transformed to next operator
$\bigcirc$ followed by $\mathscr{H}(C_{i\rightarrow j}\varphi)$
because w.r.t $\sigma_{fu}$, there exists a state next to the
fulfillment state in which $\mathscr{H}(C_{i\rightarrow
j}\varphi)$ holds. Notice that the added transitions, labeled with
$\beta^{ij}$, always go from the fulfillment state to a state
where  $\mathscr{H}(C_{i\rightarrow j}\varphi)$ is satisfied (they
go either to the commitment state or to the fulfilment state
itself where in both states the formula
$\mathscr{H}(C_{i\rightarrow j}\varphi$) holds). This can be
easily seen in Figure \ref{fig-relation-to-actions-cha3}. Indeed, this
intuitively complies with the fact that for a commitment to be
fulfilled, the commitment itself has to be created before and
still alive at the moment of fulfilling it (i.e., at the
fulfillment state).
%
%
%
%It is proved that the semantic of PCTL over DTMC w.r.t adversary is the same.

%
%
\begin{theorem}[Satisfaction Equivalence]\label{Satsisfaction-Equivelance}\hspace{0.5cm} \\

Let $\sigma_t$, $\sigma_c$, and $\sigma_{fu}$ be the DTMC models
corresponding to the adversaries that capture respectively temporal formulae, commitment formulae, and fulfillment formulae. The following equivalences hold:

$(\mathfrak{M_1},s)\models p ~\text{iff}~ (\sigma_t,s) \models p$

$(\mathfrak{M_1},s)\models \neg \varphi ~\text{iff}~ (\sigma_t,s)\models\neg \mathscr{H}(\varphi)$

$(\mathfrak{M_1},s)\models \mathbb{P}_{\bowtie k}(\varphi \vee \psi)
~\text{iff}~ (\sigma_t,s) \models \mathbb{P}_{\bowtie k} \mathscr{H}(\varphi) \vee \mathbb{P}_{\bowtie k} \mathscr{H}(\psi) $

$(\mathfrak{M_1},s)\models \mathbb{P}_{\bowtie k}\bigcirc\varphi ~\text{iff}~ (\sigma_t,s) \models\mathbb{P}_{\bowtie k} \bigcirc \mathscr{H}(\varphi) $

$(\mathfrak{M_1},s)\models\mathbb{P}_{\bowtie k}(\varphi~ U ~ \psi) ~\text{iff}~ (\sigma_t,s) \models \mathbb{P}_{\bowtie k}(\mathscr{H}(\varphi)~ U ~\mathscr{H}(\psi))$

$(\mathfrak{M_1},s)\models\mathbb{P}_{\bowtie k}(\varphi~ U^{\leq m} ~ \psi) ~\text{iff}~ (\sigma_t,s) \models \mathbb{P}_{\bowtie k}(\mathscr{H}(\varphi)~ U^{\leq m} ~\mathscr{H}(\psi))$

$(\mathfrak{M_1},s)\models C_{i \rightarrow j}\varphi ~\text{iff}~ (\sigma_c,s)\models \mathbb{P}_{\geq1}(\bigcirc\mathscr{H}(\varphi))$

$(\mathfrak{M_1},s)\models \mathbb{P}_{\bowtie k}C_{i \rightarrow j}\varphi ~\text{iff}~ (\sigma_c,s) \models \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq1}(\bigcirc\mathscr{H}(\varphi)))$

$(\mathfrak{M_1},s)\models Fu(C_{i \rightarrow j}\varphi) ~\text{iff}~ (\sigma_{fu},s) \models \mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{H}(\varphi)))$

$(\mathfrak{M_1},s)\models \mathbb{P}_{\bowtie k}Fu(C_{i \rightarrow j}\varphi) ~\text{iff}~ (\sigma_{fu},s) \models \mathbb{P}_{\bowtie k} (\mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{H}(\varphi))))$

\end{theorem}
This theorem emphasizes that each formula has to be associated
with an adversary (i.e., a DTMC model) over which the formula can
be interpreted. The proof of the theorem with regard to PCTL
formulae is straightforward as PCTL formulae are also PCTLC
formulae. For commitment formulae, the proof is given in Theorem
\ref{soundness-PCTL} that discusses the soundness of the transformation
rules.

%
%

\begin{theorem}[Soundness and Completeness of $\mathscr{H}$]\label{soundness-PCTL}
Let $\mathfrak{M_1}$ and $\Phi$ be respectively a PCTLC model
and formula and let $\mathscr{H}(\mathfrak{M_1})$  and
$\mathscr{H}(\Phi)$ be the corresponding model and formula in
PCTL. We have $\mathfrak{M_1}\models\Phi$ iff
$\mathscr{H}(\mathfrak{M_1}) \models \mathscr{H}(\Phi)$.
\end{theorem}

%\begin{proof}$~\\$
\begin{proof} %\hspace{0.5cm} \\
Our aim here is to prove that the proposed reduction technique is
sound (i.e., the necessary condition) and complete (i.e., the sufficient condition). We prove this by induction on the structure of the formula $\Phi$. The case of PCTLC formulae that are also PCTL formulae is
straightforward. In what follows, we analyze two cases: $\Phi =
C_{i \rightarrow j} \varphi$ and $\Phi = Fu(C_{i \rightarrow j}
\varphi)$.

\begin{itemize}
\item $\Phi = C_{i \rightarrow j} \varphi$. We have
$(\mathfrak{M_1},s)\models C_{i\rightarrow j}\varphi ~\text{iff}~
(\mathfrak{M_1},s') \models \varphi$ for every $s' \in S$
such that $s\sim_{i \rightarrow j}s'$. Consequently,
$(\mathfrak{M_1},s)\models C_{i\rightarrow j}\varphi ~\text{iff}~
(\mathfrak{M'_1},s') \models \mathscr{H}(\varphi)$ for every
$s' \in \mathbb{S}$ such that $(s,\alpha^{ij},s') \in
\textsf{P}_t$. Now, w.r.t the adversary $\sigma_c$ that is defined
to interpret commitment formulae over $\mathfrak{M'_1}$,
every infinite path $\pi \in \Pi^{\sigma_c}(s)$ satisfies that
$\pi(1)=s'$ and $(\mathfrak{M'_1}^{\sigma_c},\pi(1))\models
\mathscr{H}(\varphi)$. Then,
$(\mathfrak{M'_1}^{\sigma_c},s)\models
\bigcirc\mathscr{H}(\varphi)$ for all $\pi \in \Pi^{\sigma_c}(s)$.
As the path quantifier $A$ is not defined in PCTL, and we have
$\mathbb{P}_{\geq1}$ (weaker than $A$) instead, so we obtain
$(\mathfrak{M'_1}^{\sigma_c},s)\models
\mathbb{P}_{\geq1}(\bigcirc\mathscr{H}(\varphi))$.

\item $\Phi = Fu(C_{i \rightarrow j} \varphi)$. We have
$(\mathfrak{M_1},s)\models Fu(C_{i\rightarrow j}\varphi)$ iff there
exists $s'\in S$ such that $s'\sim_{i \rightarrow j}s~
\text{and~}(\mathfrak{M_1},s')\models C_{i \rightarrow j}\varphi$.
Consequently, $(\mathfrak{M_1},s)\models Fu(C_{i\rightarrow
j}\varphi)$ iff there exists $s' \in \mathbb{S}$ such that
$(s,\beta^{ij},s') \in \textsf{P}_t$ and
$(\mathfrak{M'_1},s') \models \mathscr{H}(C_{i \rightarrow
j}\varphi)$. Now, w.r.t the adversary $\sigma_{fu}$ which is
defined to interpret fulfillment formulae over
$\mathfrak{M'_1}$, we obtain at least one infinite path $\pi
\in \Pi^{\sigma_{fu}}(s)$ that satisfies $\pi(1)=s'$ and
$(\mathfrak{M'_1}^{\sigma_{fu}},\pi(1))\models
\mathscr{H}(C_{i \rightarrow j}\varphi)$. Since $E$ is equivalent
to $\mathbb{P}_{>0}$ and $\mathscr{H}(C_{i \rightarrow j}\varphi)$
is equivalent to
$\mathbb{P}_{\geq1}(\bigcirc\mathscr{H}(\varphi))$, so we obtain
$(\mathfrak{M'_1}^{\sigma_{fu}},s)\models
\mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc
\mathscr{H}(\varphi)))$.

\end{itemize}

\end{proof}

\vspace{-1.0cm}
\section{Implementation} \label{sec:implementaion PCTLC}

In this section, we apply our model checking approach on Oblivious Transfer Protocol \cite{Rivest1999}. For the purpose of providing experimental results demonstrating the effectiveness and efficiency of our reduction technique, we verify some properties of oblivious transfer protocol, expressed originally in PCTLC logic.

\subsection{Oblivious Transfer Protocol}
Oblivious transfer protocol was introduced in cryptography to
allow a sender to send some information to a receiver
in such a way that the sender remains oblivious to what is
received. We study the oblivious transfer protocol due to Rivest \cite{Rivest1999} in which the sender (Alice) has
two secret values $m_0$ and $m_1$. The receiver (Bob) would like
to know one of the two values without telling Alice which value he
learned. This protocol has been the subject of analysis for some
probabilistic properties \cite{Huang2011}. Rivest's solution uses
a trusted initializer (Ted) who participates only in the initial
setup to help both agents by providing them with some
random material. The random material includes two random strings ($r_0$ and $r_1$) ---with the same length as Alice's messages--- to be sent to Alice
in the setup phase. Then, Ted flips a bit ($d$) and sends it to
Bob along with a random string $rd$. Now, for Bob to request
$mc$ ($c=0$ or $1$), he sends Alice the bit $e=c\oplus d$
($\oplus$ is the exclusive OR logical gate: it takes as input two
bits and its output is $0$ if the two bits are equal, and $1$
otherwise). Then, Alice responds with the values $f_0=m_0\oplus
r_e$ and $f_1=m_1\oplus r_{1-e}$. Upon receiving $f_0$ and $f_1$,
Bob can compute $mc=f_c\oplus rd$. Having done so, Alice will
have no idea as to which message Bob chose, and Bob will have
learned nothing about $m_{1-c}$ (Alice's other message).

In order to use the PRISM model checker to verify and analyze
\emph{Oblivious Transfer Protocol}, the latter has to be encoded
into the PRISM input language. Simply, we treat the \emph{Sender}
(Alice) and \emph{Receiver} (Bob) in the protocol as agents. Then,
each agent is translated into a \emph{module} in the PRISM
language. Moreover, each agent is comprised of variables that
determine its local states. For example, Bob's variables are: bool
$S\_req$: send request, bool $R\_ack$: receive acknowledgement,
bit d: 0 or 1, bit c: 0 or 1, bit e: 0 or 1, bool $S\_e$: send bit
e, string $rd$: random variable obtained form Ted in the initial
setup, $R\_f$: receive $f_0$ and $f_1$. The global model is
obtained by the synchronization between all modules (agents).

\subsection{Oblivious Transfer Protocol Properties}

One of the main motivations of this chapter is to verify properties expressed as PCTLC formulae. Gurin and Pitt \cite{Guerin2002} expressed that verifying protocol properties can be performed at design time. This kind of verification aims to prove that some property will hold for all the interactions that correctly follow the protocol. Our proposed model checking technique mainly accommodates compliance by design-time verification of interaction properties. In fact, there have been various catalogs of properties proposed in the literature \cite{Bentahar2009,Cheng2006,Desai2007}. In our work, we
check \emph{safety}, \emph{Liveness}, and \emph{reachability}
properties in the Oblivious Transfer Protocol as they are popular
examples of protocol properties. These properties reflect some requirements of the oblivious transfer protocol that have to be met.

\begin{itemize}
\item \texttt{Property 1: Safety} ``Something bad will never occur".\\
This property can be generally expressed in CTL by the formula
$A\Box\neg p$ which is equivalent to $\mathbb{P}_{\geq1}(\Box\neg
p)$ in PCTLC where $p$ represents a bad situation. Such bad
situations include, for example, when Alice fulfills her
commitment of using the bit \emph{e} (received from Bob) along
with the random variables $r_0, r_1$ (obtained from Ted in the
initial setup) for calculating $f_0$ and $f_1$, but Bob does not
use the random variable $rd$ to compute his requested value
$mc$. This bad situation can be avoided using PCTLC as follows:

$\varphi_1= \mathbb{P}_{\geq1}\Box\neg[\mathbb{P}_{>0} \Diamond
Fu(C_{A\rightarrow B} (use-e))\wedge \mathbb{P}_{\geq1}\Box\neg
(use-rd)]$

\item \texttt{Property 2: Liveness} ``Something good will eventually
happen".\\
This property expresses that some good situation will eventually
occur. For example, in all computation paths it is always the case
that if Alice fulfills her commitment of using the bit $e$ and the
random strings $r_0, r_1$ for calculating and delivering $f_0$ and
$f_1$, then in all paths in the future Bob can use $f_0$ and $f_1$
to compute his requested value $mc$. This can be expressed as
follows:

$\varphi_2= \mathbb{P}_{\geq1}\Box[\mathbb{P}_{>0}\Diamond
Fu(C_{A\rightarrow B} (use-e))\supset \mathbb{P}_{\geq1}\Diamond
(comp-mc)]$

\item \texttt{Property 3: Reachability} ``Some particular situation
can be reached".\\
This property comes in the form $E\Diamond p$ which is equivalent
to $\mathbb{P}_{>0}\Diamond p$ in PCTLC where $p$ is the situation
that needs to be reached. For example, once Alice commits towards
Bob to use the bit $e$ in calculating $f_0$ and $f_1$, there
should be a possibility from the initial state for Alice to
eventually reach the fulfillment state where she can fulfill her
commitment towards Bob. This property can be expressed as
follows:

$\varphi_3= \mathbb{P}_{>0}\Diamond Fu(C_{A\rightarrow B} (use-e))$

\end{itemize}

\subsection{Experimental Results}\label{sec:experimental-results-cha3}

We have carried out 12 experiments. Our experiments were performed on a Dell laptop equipped with 32-bit Windows XP with 4 GB of RAM and Genuine Intel(R) CPU at 2.4 GHz. Table \ref{prism-results-cha3} reports the results of the performed experiments wherein (Exp.\#) denotes the experiment number, (\#Agent) denotes the number of agents, (\#States) denotes the number of reachable states, (\#Transitions) denotes the number of transitions, and (Construction Time) denotes the time needed for building the simulated model in seconds. We started our experiments with only two agents; Alice (sender) and Bob (Receiver). In this interaction, Bob requests a value
(information) from Alice and then Alice responses to Bob and sends
him the requested value in such a way that both agents respect the
rules of the protocol for encrypting and decrypting the
information.

\begin{table}%[htp]
\centering \caption{Verification results of the oblivious transfer
protocol} \label{prism-results-cha3}
\resizebox{\textwidth}{!}{ %
\begin{tabular}{|c|c|l|l|c|}
\hline
\texttt{Exp.\#} &   \texttt{\#Agents}    & \texttt{\#States} & \texttt{\#Transitions} & \texttt{Const. Time (s)}\\
\hline\hline
\texttt{Exp.1}   &\texttt{2}         &25        &75              & 0.016\\
\hline
\texttt{Exp.2}   &4       &625              &3125                & 0.047\\
\hline
\texttt{Exp.3}   &6       &$1.6*10^4$         &$1.1*10^5$        & 0.079\\
\hline
\texttt{Exp.4}   &8       &$3.9*10^5$         &$3.5*10^6$        & 0.188\\
\hline
\texttt{Exp.5}   &10      &$9.7*10^6$         &$1.1*10^8$        & 0.344\\
\hline
\texttt{Exp.6}   &12      &$2.4*10^8$         &$3.1*10^{9}$      & 0.547\\
\hline
\texttt{Exp.7}   &14      &$6.1*10^9$         &$9.2*10^{10}$     & 0.859\\
\hline
\texttt{Exp.8}   &16      &$1.5*10^{11}$      &$2.6*10^{12}$     & 1.11\\
\hline
\texttt{Exp.9}   &18      &$3.8*10^{12}$      &$7.2*10^{13}$     & 1.5\\
\hline
\texttt{Exp.10}  &20      &$9.5*10^{13}$      &$2*10^{15}$       & 2.531\\
\hline
\texttt{Exp.11}  &22      &$2.3*10^{15}$       &$5.5*10^{16}$    & 3.531\\
\hline
\texttt{Exp.12}  &24      &$6*10^{16}$        &$1.5*10^{18}$      & 5.609\\
\hline
\end{tabular}}
\end{table}

In the second experiment, we added two more agents
(receivers) who also request some values from Alice. For the rest
of the experiments, each time we add two more agents (receivers)
till we reach the maximum number of agents (24 agents) with which
we can successfully build the model.

In every experiment, we monitor the changes occurring in
(\#States), (\#Transitions), and (Construction Time) respectively.
From Table \ref{prism-results-cha3}, we notice that the state space
(represented in terms of reachable states) increases exponentially
as the number of agents increases (cf. Figure
\ref{fig:Obliviou-simulation}). Likewise, the number of
transitions also increases exponentially as more agents are added.
However, the time (in seconds) needed for building the model
increases polynomially, which shows the effectiveness of our model
checking approach when the system scales up (about $6*10^{16}$
states). The cause of this time increase in building the model
when more agents are added is that the number of reachable states
and the size of the model are increased. Moreover, the more we
become closer to the state explosion point as in experiments 20,
22, and 24, the higher time is need for building the model. This
reflects the fact that the model size in these experiments turns
out to be much bigger.

\begin{figure}%[!ht]
\begin{center}
\includegraphics [width=10cm, height=6cm]{chap3/img/model-time.eps}
  \caption{Model construction time for oblivious transfer protocol}
\label{fig:Obliviou-simulation}
\end{center}
\end{figure}

It is worth noticing that starting from experiment \#2 we re-write
the desirable properties $\varphi_1$, $\varphi_2$, and $\varphi_3$
in a parameterized form, as follows ($n$ is the number of agents
in the experiment):

$\varphi_1'= \mathbb{P}_{\geq1}\Box\neg[\mathbb{P}_{>0} \Diamond
\bigwedge\limits_{i=1}^n Fu(C_{A\rightarrow B_i} (use-e_i))\wedge \mathbb{P}_{\geq1}\Box\neg
(use-rd_i)]$

$\varphi_2'= \mathbb{P}_{\geq1}\Box[\mathbb{P}_{>0}\Diamond
\bigwedge\limits_{i=1}^n Fu(C_{A\rightarrow B_i} (use-e_i))\supset \mathbb{P}_{\geq1}\Diamond
(comp-mc_i)]$

$\varphi_3'= \mathbb{P}_{>0}\Diamond \bigwedge\limits_{i=1}^n Fu(C_{A\rightarrow B_i} (use-e_i))$

However, for the purpose of model checking using our reduction
technique, every defined formula needs to be transformed according
to the reduction rules presented in Section
\ref{sec:reducing-pctlc-to-pctl}. Below we show the transformed
forms of $\varphi_1$, $\varphi_2$, and $\varphi_3$ respectively in
the case of two agents (i.e., experiment \#1).

$\mathscr{H}(\varphi_1)= \mathbb{P}_{\geq1}\Box\neg[\mathbb{P}_{>0} \Diamond \mathscr{H}(Fu(C_{A\rightarrow B} (use-e)))\wedge \mathbb{P}_{\geq1}\Box\neg \mathscr{H}(use-rd)]$.

$~~~~= \mathbb{P}_{\geq1}\Box\neg[\mathbb{P}_{>0} \Diamond(\mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq1}(\bigcirc\mathscr{H}(use-e))))
\wedge\mathbb{P}_{\geq1}\Box\neg \mathscr{H}(use-rd)]$.

$~~~= \mathbb{P}_{\geq1}\Box\neg[\mathbb{P}_{>0} \Diamond(\mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq1}(\bigcirc(use-e))))
\wedge\mathbb{P}_{\geq1}\Box\neg (use-rd)]$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

$\mathscr{H}(\varphi_2)= \mathbb{P}_{\geq1}\Box[\mathbb{P}_{>0}\Diamond \mathscr{H}(Fu(C_{A\rightarrow B} (use-e)))\supset \mathbb{P}_{\geq1}\Diamond \mathscr{H}(comp-mc)]$.

$~~~= \mathbb{P}_{\geq1}\Box[\mathbb{P}_{>0}\Diamond(\mathbb{P}_{>0}
(\bigcirc\mathbb{P}_{\geq1}(\bigcirc\mathscr{H}(use-e))))\supset\mathbb{P}_{\geq1}\Diamond \mathscr{H}(comp-mc)]$.

$~~~= \mathbb{P}_{\geq1}\Box[\mathbb{P}_{>0}\Diamond(\mathbb{P}_{>0}
(\bigcirc\mathbb{P}_{\geq1}(\bigcirc(use-e))))\supset\mathbb{P}_{\geq1}\Diamond (comp-mc)]$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

$\mathscr{H}(\varphi_3)= \mathbb{P}_{>0}\Diamond \mathscr{H}(Fu(C_{A\rightarrow B} (use-e)))$.

$~~~~= \mathbb{P}_{>0}\Diamond [\mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq1}(\bigcirc\mathscr{H}(use-e)))]$.

$~~~~= \mathbb{P}_{>0}\Diamond [\mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq1}(\bigcirc(use-e)))]$.

\noindent Table \ref{formulae-prism-results-chap3} shows the results in terms of verification time (in seconds) of model checking the above defined properties when the number of agents
varies from a simple interaction scenario of two agents to more
complicated scenarios of 24 agents. The total execution time can
be easily obtained by summing up the construction time to build
the simulated model reported in Table \ref{prism-results-cha3} and the
verification time of the considered formulae. For instance, in
Exp. 12 with 24 agents, the total execution time of verifying
$\varphi_1$, $\varphi_2$, and $\varphi_3$ is $5.609 + 2.609 +
2.453 + 2.118 = 12.789$ s.

\begin{table}%[htp]
\centering \caption{Results of model checking some properties for Oblivious Transfer Protocol} \label{formulae-prism-results-chap3}
\begin{tabular}{|c|c|c|c|c|}
\hline
\texttt{Exp.\#} &   \texttt{\#Agents}    & \texttt{Time for MC $\varphi_1$} & \texttt{Time for MC $\varphi_2$} &  \texttt{Time for MC $\varphi_3$} \\
\hline\hline
1                &2           &$<$0.001      &$<$0.001      &$<$0.001       \\
\hline
2                &4           &0.015      &0.016      &0.015       \\
\hline
3                &6           &0.032      &0.031      &0.032       \\
\hline
4                &8           &0.046      &0.047      &0.062       \\
\hline
5                &10          &0.078      &0.093      &0.078       \\
\hline
6                &12          &0.11       &0.141      &0.172       \\
\hline
7                &14          &0.203      &0.188      &0.219       \\
\hline
8                &16          &0.359      &0.328      &0.343       \\
\hline
9                &18          &0.453      &0.403      &0.5       \\
\hline
10               &20          &1.062      &0.797      &0.719       \\
\hline
11               &22          &1.813      &1.125      &1.106       \\
\hline
12               &24          &2.609      &2.453      &2.118       \\
\hline

\end{tabular}
\end{table}

Notice that the three properties hold in all conducted
experiments, meaning that our approach is successful in expressing
and verifying system  properties using PCTLC. Clearly, as depicted
in Figure \ref{fig:MC-time-properties-cha3}, the time for model
checking the three properties is similar which increases
polynomially till we reach the case of 20 agents then it grows up
dramatically. However, these results demonstrate the scalability
of our reduction-based model checking technique to verify
commitments and their fulfilments in uncertain setting for agent
communication.

\begin{figure}[!ht]
\begin{center}
\includegraphics [width=13cm, height=7cm]{chap3/img/three-properties-time.eps}
  \caption{Time for model checking some properties for oblivious transfer protocol}
\label{fig:MC-time-properties-cha3}
\end{center}
\end{figure}

\section{Related Work} \label{sec:related-work-cha3}

The work of this chapter is related to a number of other proposals in the
literature. In this section, we give a brief overview of the most
relevant ones.

\subsection{Adding Commitment Operators to Existing Logics} \label{sec:related work Extending existing Logics}

Singh in \cite{Singh2000} extends CTL logic by adding operators for
social commitments, beliefs, and intentions in order to formally
model the interactions between interacting parties in a MAS. By
doing so, he was able to develop a specification language for
commitment-based protocols. The author defines three different
accessibility relations to intuitively capture the meaning of the
new modalities. With respect to the commitment, the author claims
that a commitment is satisfied at a certain state if and only if
the content of the commitment is true along all accessible paths
defined using an accessibility relation and emanating from the
commitment state (the state where the commitment holds). Though
the author claims that the proposed semantics is verifiable, no
concrete approach for verifying or model checking the semantics is
presented.

Bentahar and his colleagues in \cite{Bentahar2004,Bentahar2007}
present an approach that extends CTL$^*$ with an operator for
commitments and their actions, and two operators for argument and
dynamic logic respectively. To define a semantics for the
commitment modality, they present a new definition for the
accessibility relations. Moreover, their semantics is defined in
terms of the computations (paths) along which the commitment is
satisfied.

Cheng in \cite{Cheng2006} introduce a model checking method using
the SPIN model checker (Simple Promela Interpreter
\cite{Holzmann1997}) to verify commitment-based business
protocols and their compositions based on LTL logic. In this
method, commitments are not expressed directly in the logic as we
propose in our work. Instead, they are simply abstracted as
variables. Consequently, the intrinsic meaning of commitments is
not captured.

In \cite{Desai2007}, Desai and his group highlight some protocol
properties and classify them into general properties and
protocol-specific properties in order to verify the correctness of
commitment protocols. The presented properties are defined in
terms of Propositional Linear Temporal logic (LTL). Then, they
outline a technique for verifying commitment protocols and their
compositions against these properties. The proposed approach
involves using the SPIN model checker as a tool for the formal
verification. Among the general properties that they are
successfully able to verify are the deadlocks (which may result
from the contradictory between the axioms used in protocol
composition) and livelocks properties. As in \cite{Cheng2006},
commitments are simply abstracted using variables.

El-Menshawy and his colleagues in \cite{El-Menshawy2010} tried to
overcome the limitations raised in
\cite{Bentahar2004,Bentahar2007}. They propose a new logical
language called CTL$^{*sc}$ to develop a specification language
for commitment-based protocols. Their new logic extends CTL$^*$
with commitments and their associated actions. Furthermore, they
extend the temporal modalities of CTL$^*$ with past-directed
temporal modalities. The semantics of actions is not defined in a
recursive way as in \cite{Bentahar2004,Bentahar2007}, i.e., the
semantics of each action does not depend on other actions. Based
on their new logic, the authors develop a Social Negotiation
Protocol (SNP) that merges a set of dialogue games, commitment
actions and dialogue actions. Then, they present an automatic
verification technique to verify the SNP using symbolic model
checking in which they verified some given properties such as
Reachability, Safety, and Liveness. They implemented their
proposed verification technique using the NuSMV\cite{Cimatti2002}
and MCMAS\cite{Lomuscio2006} symbolic model checkers. Their
experimental results show the ability of the proposed approach to
handle large state spaces of $10^{16}$. However, the work does not
consider the uncertainty issue associated with the protocol.

In a later work, El-Menshawy et al. \cite{El-Menshawy2011a}
defined a new temporal logic called CTLC by extending CTL with
operators for social commitments and their fulfilments and
violations. In terms of defining CTLC, their main contribution is the definition of a new social accessibility relation. They define a new
accessibility relation in which they assume the existence of an
intermediate state between the commitment state and the
fulfillment state. The debtor, in their accessibility definition,
is uncertain about the current state so he looks for the
intermediate state (different from the current state) in which it
does not matter for him being in the commitment state, the
intermediate state, or the fulfillment state (i.e., the local
states of the debtor in the three global states are
indistinguishable). However, for the creditor it does not matter
being in the intermediate state or in the fulfillment state as
being in one of them is the same for him. Introducing the intermediate state makes the computation of the accessible states very complex.
The authors verified the proposed logic using a symbolic model checking algorithm they developed for this purpose.
They also extended the MCMAS model checker to be capable of
interpreting the new modalities. By so doing, they were able to
show that the problem of model checking CTLC is polynomial-time
reducible to the problem of model checking CTLK (Computation Tree
Logic of Knowledge \cite{Penczek2003}). However, the stochastic
aspect of the system being verified has not been addressed.

CTLC logic \cite{El-Menshawy2011a} has also been the focus of
El-Menshawy et al. \cite{El-Menshawy2011b,El-Menshawy2013a} and Bentahar et al. \cite{Bentahar2012} to verify and model check commitment-based protocols. In \cite{El-Menshawy2011b}, the authors investigate the use of
symbolic model checkers to verify the compliance of commitment
protocols against some given properties such as liveness and
safety. To do so, they reduce the problem of model checking CTLC
to the problem of model checking either CTLK or ARCTL (an
extension of CTL with action formulae \cite{Pecheur2006}) where
both are extensions of CTL. This allowed them to use MCMAS
(suitable for CTLK), and NuSMV (suitable for ARCTL). On the other
hand, Bentahar et al. \cite{Bentahar2012} refined CTLC by
introducing a set of shared and unshared variables so that their
extended version of interpreted systems can account for the
communication among the interacting agents. Technically, they
associate with each agent a countable set of local variables.
Then, they use those variables to represent communication channels
through which messages are sent and received.
Furthermore, they analyzed the time complexity of CTLC model
checking in explicit models such as Kripke-like structures, and
its space complexity for concurrent programs. Their proposed model
checking algorithms are implemented on top of the MCMAS model
checker. El-Menshawy et al. \cite{El-Menshawy2013a} also modified
CTLC into CTLC$^+$ that allows reasoning about communicating
commitments and their fulfilments. In their work, they introduce a
formal reduction technique to reduce the problem of model checking
CTLC$^+$ to the problem of model checking ARCTL and the problem of
model checking GCTL$^*$. This allows them to take a benefit of
existing model checkers such as the extended NuSMV symbolic model
checker (suitable for ARCTL) and the
CWB-NC~%\footnote{\url{http://www.cs.sunysb.edu/~cwb/DOWNLOADS/CWB/current/user.ps}}
automata-based model checker (suitable for GCTL$^*$). Moreover,
they analyzed the complexity of model checking CTLC$^+$ for
concurrent programs with respect to the size of such programs and
the length of the formulae and proved it to be PSPASE-complete.
Our work extends those proposals by considering the probabilistic
aspect of social commitments.

Focusing on business models, Telang and Singh \cite{Telang2012}
propose an expressive and declarative approach capable of
specifying business models at a high level of abstraction using
the notion of social commitments. In particular, they specify
business models using CTL logic, and model check operational
interactions (a set of business interactions) specified as UML
sequence diagrams. They map each model business to a temporal
logic specification based on the progression of the states of the
relevant commitments. Concretely, they capture the business model
as an aggregation of business patterns. Then, they map each
pattern to a CTL-based specification. To verify agent
interactions, the authors use the NuSMV model checker to compute
whether operational models correctly support a business model. In
this work, commitments are translated into NuSMV variables instead
of introducing a new commitment modality as we do in our proposal.

In \cite{El-Menshawy2013b}, the authors propose a new
logical-based language to specify commitment-based protocols. The
presented language is defined in terms of ACTL$^{*c}$ logic which
in turn extends CTL$^*$ with operators for social commitments and
their actions. Like in \cite{El-Menshawy2013a}, the authors also
present a formal reduction-based verification technique to
transfer the problem of model checking ACTL$^{*c}$ to the problem
of model checking GCTL$^*$. They implement their automatic
reduction-based model checking approach on top of the CWB-NC model
checker. Like in their proposal in \cite{El-Menshawy2013a}, agents
are assumed to be certain about their commitments.

In \cite{Gerard2013}, Gerard and Singh introduce an approach that
specify commitment protocols and their refinements using guarded
messages. The meaning of each message is defined as a set of
actions. They use CTL as the underlying logic in which the
specification is defined. The authors propose a model checking
technique to seek whether a protocol refines another protocol
correctly under certain conditions or not. The proposed tool
``Proton'' was implemented on top of the MCMAS model checker. The
commitments, which supposed to be certain, are modeled as objects
which are mapped into domain variables in ISPL (the input language
of MCMAS).

\subsection{Probabilistic Commitments} \label{sec:related work PC}

Uncertainty in commitments has to date received little attention by researches of MASs community. Herein, we review some existing proposals that treat commitments in the presence of uncertainty.

In \cite{Witwicki2007}, Witwicki and Durfee presented a
commitment-based methodology for approximating the optimal joint
policy in agent coordination. They proposed a technique to
decompose large mathematical programs that encodes the decision
problems of all agents into 1) a search for optimal commitments
regarding each agent's outgoing influences; and 2) a search for
optimal local policies that respect the commitments decided upon.
For a given set of commitments, they add constraints to the
traditional linear program formulation of MDPs to guarantee that a
feasible policy respects the commitments. Each agent can then
solve its linear program separately.

In another work, Witwicki and Durfee \cite{Witwicki2009}
investigated the use of probabilistic commitments in service
orientation. They proposed a commitment-based negotiation
mechanism based on uncertain durations by which service providers
agree to provide a service within a given time and certain
probability. The commitment between service providers and service
requesters use temporal and probabilistic parameters to summarize
expectations over future agent activities. Agents (providers and
requesters) then benefit from these commitments to build policies
about how to achieve (for providers) or utilize (for requesters)
these anticipated service outcomes. MDPs were adopted as the
underling models for modeling their agent-based systems. While the
semantics of the commitments was not formally described (i.e., in
term of logic), they have given a definition for the probabilistic
commitment as follows. ``A probabilistic temporal service
commitment $C_{ij}(s) = \langle t, \rho\rangle$ is a guarantee
that agent $i$ will perform (for agent $j$) the actions necessary
to deliver service $s$ by time $t$ with probability no less than
$\rho$" \cite{Witwicki2009}. By making use of these  probabilistic
commitments, agents can make promises to each other even if they
cannot fully guarantee service provision.

Unlike the proposals in \cite{Witwicki2007,Witwicki2009}, we
precisely use social commitments as a means of communication between
the interacting agents. In addition, these proposals
do not consider the verification aspect of commitments. However, we address the commitments between communicating parties from a formal perspective. That is, we integrate a commitment modality to probabilistic logic so that the verification of such commitments becomes achievable by means of model checking.

\subsection{Comparison}

We compare our work to the existing approaches by taking into
consideration the following criteria: Formalization, Uncertainty,
and Verification. Formalization reflects the use of formal logics
such as LTL, CTL, CTL$^*$, ARCTL or PCTL to represent and specify
the commitments. Uncertainty property indicates whether the
probabilistic behavior is considered or not. Finally, Verification
confirms the presentation of a formal verification technique to
verify the proposed approach. Table \ref{table:comparison1} shows
a summary about the comparison between our work and the existing
approaches based on the criteria described above.

\begin{table}
\centering \caption{Comparison between our approach for the probabilistic commitments and the related work} \label{table:comparison1}
\begin{tabular}{|c|c|c|c|}
\hline
\texttt{Approach}       & \texttt{Formal}   & \texttt{Uncertainty} & \texttt{Verification}\\
\hline
\hline
\cite{Bentahar2004,Bentahar2007,Singh2000}       & $\surd$         &   & \\
\hline
\cite{Bentahar2012,Cheng2006,Desai2007,El-Menshawy2010,El-Menshawy2011b,El-Menshawy2013a,El-Menshawy2013b,El-Menshawy2011a,Gerard2013,Telang2012}      & $\surd$         &   &$\surd$ \\
\hline
\cite{Witwicki2007,Witwicki2009}      &          &$\surd$   & \\
\hline
Ours                     &$\surd$   &$\surd$  &$\surd$    \\
\hline

\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\centering \caption{Comparison between PCTLC and existing logics in terms of the adopted logic} \label{table:comparison2}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\texttt{Approach}       & \texttt{LTL}   & \texttt{CTL} & \texttt{CTL$^*$} & \texttt{ARCTL}     & \texttt{PCTL} &\texttt{None}\\
\hline
\hline
\cite{Cheng2006,Desai2007}    &$\surd$          & & & & &\\
\hline
\cite{Bentahar2012,El-Menshawy2011b,El-Menshawy2013a,El-Menshawy2011a,Gerard2013,Singh2000,Telang2012}       &          &$\surd$  && && \\
\hline
\cite{Bentahar2004,Bentahar2007,El-Menshawy2010}  &          &  &$\surd$ & &&\\
\hline
\cite{El-Menshawy2013b}      &          & &  &$\surd$ &&\\
\hline
\cite{Witwicki2007,Witwicki2009}      &      &    &   && &$\surd$\\
\hline
Ours                     &   &  & & &$\surd$ & \\
\hline

\end{tabular}
\end{table}

In terms of formalization, our approach shares with most of the
surveyed proposals the idea of extending existing temporal logics
with new modalities for the commitments and their fulfilments.
However, the main feature that distinguishes it from others lies
in the logic being extended to handle social commitments. While
others adopt conventional, non-probabilistic logics such as LTL,
CTL, and CTL$^*$, ours is the only work that builds on a
probabilistic logic, namely PCTL. Table \ref{table:comparison2}
compares between our approach and other proposals with respect to
the underlying logic that has been extended to specify social
commitments.

From the verification perspective, like proposals in \cite{El-Menshawy2011b,El-Menshawy2013a,El-Menshawy2013b}, we adopt a formal reduction technique as the underlying basis for our model checking to translate the problem of model checking our logic to the problem of model checking an existing logic. However, to the best of our knowledge, non of the existing approaches has verified social commitments in the presence of uncertainty. Therefore, our approach outperforms the related approaches as it is the first attempt to  tackle the verification problem of the probabilistic social commitments. Table \ref{table:comparison3} displays a comparison between our approach and the existing ones in terms of the used model checkers.

\begin{table}
\centering \caption{Comparison between PCTLC and existing approaches in terms of the used verification tool} \label{table:comparison3}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\texttt{Approach}       & \texttt{SPIN}   & \texttt{MCMAS} & \texttt{NuSMV} & \texttt{CWB-NC}     & \texttt{PRISM} &\texttt{None}\\
\hline
\hline
\cite{Cheng2006,Desai2007}    &$\surd$          & & & & &\\
\hline
\cite{Bentahar2012,El-Menshawy2010,El-Menshawy2011b,El-Menshawy2011a,Gerard2013}       &          &$\surd$  && && \\
\hline
\cite{El-Menshawy2010,El-Menshawy2011b,El-Menshawy2013a,Telang2012}  &          &  &$\surd$ & &&\\
\hline
\cite{El-Menshawy2013b}      &          & &  &$\surd$ &&\\
\hline
\cite{Bentahar2004,Bentahar2007,Singh2000,Witwicki2007,Witwicki2009}      &      &    &   && &$\surd$\\
\hline
Ours                     &   &  & & &$\surd$ & \\
\hline

\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}\label{sec:conclusion-cha3}

In this chapter, we introduced a new model checking technique for
social commitments among agents interacting in uncertain settings.
We specified properties for such systems using Probabilistic
Computation Tree Logic of Commitments (PCTLC). The PCTLC logic
extends PCTL with a social operator for commitments and their
fulfillments. Target systems are modeled using a new version of
interpreted systems which incorporates and extends two different
versions of interpreted systems formalism to capture the
probabilistic behavior of MASs, and account for the communication
between interacting entities. The proposed model checking
technique consists of a set of reduction rules to formally reduce
the problem of model checking PCTLC to the problem of model
checking PCTL so that the use of the PRISM model checker is made
possible. The proposed verification approach was evaluated through
implementing the reduction tool on top of the PRISM model checker
and then applying it on a real case study from the cryptography
domain namely the oblivious transfer protocol. The obtained
results show the effectiveness of the proposed technique. In
particular, we were successfully able to verify some desirable
properties expressed originally in PCTLC. We also showed that the
proposed reduction technique is scalable as we were able to perform the model checking for models made of up to $1.56*10^{18}$ states
and transitions.

%We showed that the system is scalable as we were able to perform the model checking using our approach for models made of up to $1.56*10^{18}$ states and transitions.
In the next chapter, we investigate how our approach for probabilistic social commitments can be exploited to handle the interaction between social commitments and agents' knowledge in MASs.

### 2015-04-05 thesis/thesis/chap4/chap4.tex
added thesis

\setcounter{chapter}{3}

\chapter{The Interaction between Probabilistic Commitments and Knowledge}\label{cha:PCTLKC}

In this chapter\footnote{The results of this chapter have been published in the journal of Expert Systems with Applications \cite{Sultan2014b}.}, we
put forward a method for capturing and verifying the interactions between the concepts of knowledge and social commitments in probabilistic MASs. The proposed method allows us to figure out the impact of knowledge and social commitments on each other in the presence of uncertainty. To express the two concepts simultaneously in systems exhibiting probabilistic behavior, we define a new modal logic called the probabilistic logic of knowledge and commitments (PCTL$^{kc}$) which combines two existing probabilistic logics namely, the probabilistic logic of knowledge (PCTLK) \cite{Wan2012,Wan2013} and the probabilistic logic of commitments (PCTLC) that has been introduced in Chapter \ref{cha:PCTLC}. In the current chapter, MASs are modeled using a new version of interpreted systems that captures the probabilistic behavior and accounts for the communication between interacting components. Based on the proposed logic, we introduce a new model checking procedure to check the compliance of target systems against some desirable properties -- with respect to knowledge and commitments-- written in PCTL$^{kc}$. %and report some verification results.

\section{Introduction} \label{Introduction}

The rapid increase of using software agents and MASs nowadays has led to the increasing demand of finding principled techniques for modeling and verifying such systems. Generally, to build effective open MASs, several aspects which have direct influence on the efficiency and effectiveness of
the entire system must be taken into account \cite{Konur2013}.
Among other aspects, knowledge and social commitments are of a great
interest in MASs. Social commitments have been a vital approach in agent societies to capture the communication between interacting agents for more than a decade. On the other hand, knowledge has been addressed in distributed systems since 1960s \cite{Wan2013}. Recently, Al-Saqqar et al. \cite{Al-Saqqar2014a} have demonstrated that these two concepts are closely interacting with each other in various real life scenarios.

Despite the large amount of work that has been done to model and represent various aspect of probabilistic MAS, none of the existing approaches addresses the concepts of knowledge and social commitments simultaneously. In fact, the problem of reasoning about and verifying the interaction between knowledge and social commitments in the presence of uncertainty has not been investigated yet. Interpreted systems formalism \cite{Fagin1995}
and Partially Observable Markov Decision Processes POMDPs (a
variant of MDP) are the most prominent traditions in the area of
modeling and representing stochastic MASs. These models are used
to traditionally interpret some logics defined to specify and
reason about some given properties of MASs. On the one hand,
interpreted systems formalism provides a natural and yet efficient
way for modeling MASs at different levels of abstractions (i.e.,
local and global). It has been extended in \cite{Halpern2003} and
further in \cite{Wan2012,Wan2013} to capture the probabilistic
behavior of epistemic MASs. Recently, it has been extended in
\cite{Bentahar2012} and \cite{El-Menshawy2013a} to account for the
communication that occur between interacting parties in
conventional MASs. The distinct point of the extended versions of
this formalism is that knowledge and commitments can be captured
through the use of what is called accessibility relations. The
accessibility relation for knowledge denotes the existence of
equivalent states for a given agent. That is, states where the
agent cannot distinguish between being in which one of them. For
commitments, accessibility relations capture the existence of
communication channel between the communicating agents and the
transferring of information from the sender to the receiver. On
the other hand, POMDPs have been widely used to model the
uncertainty of knowledge and behavior for stochastic agents
\cite{Huang2011}. An important point of POMDPs is that there is no distinction drawn between actions taken to change the state of the world and actions taken to gain information \cite{Kaelbling1996}. This is important
because, in general, every action has both types of effect.
However, solving these models comes at a very high computational
cost \cite{Melo2011}. In this chapter, we aim to examine the use of interpreted systems formalism to capture not only knowledge and commitments
independently, but also the interactions (combinations) of the two
aspects in stochastic systems. We also intent to verify these
interactions by means of model checking.

In terms of computational logics, most current proposals address each of knowledge and commitments in MASs independently (see for example
\cite{Baldoni2010,Bentahar2012,Delgado2009,El-Menshawy2013a,Giordano2007,Halpern2003,Huang2011,Lomuscio2007,Pham2007,Wan2013}).
However, in so many real world settings, these two concepts need to
interact with each other in order to ensure rich modeling at local
(agent) and global (MAS) levels. Nevertheless, it is a challenge to guarantee the correctness of the system's behavior due to the complex nature of the autonomous and heterogenous agents, especially when they have probabilistic characteristics \cite{Song2012}.

Applying model checking techniques that were originally introduced
for standard logics, such as LTL \cite{Pnueli1977}, CTL
\cite{Emerson1990}, or PCTL \cite{Hansson1994}, to the
verification of the interaction between knowledge and social
commitments in presence of uncertainty is not straightforward as
non of these logics can capture and express the relationship
between knowledge and social commitments in probabilistic
settings. In this chapter, we introduce a model checking technique to address this open issue.

The motivation for the incorporation of knowledge and commitments
in a probabilistic logic is provided by the fact that these two
concepts not only have an impact on each other, but also their
interaction is crucial in various real scenarios. For instance, in
the field of mobile applications, which are complex in nature,
there exist situations when accounting for the interaction between
knowledge and commitments improves the output of such
applications. Let us consider a simple scenario where receiver and
sender agents share an agreement, in which the receiver agrees to
pay the sender in return of the delivery of a service he has
requested. This can be represented as a commitment, in which the
receiver will be committed to the sender to pay once the service
is made available for him. Now, if everything goes well and the
receiver successfully makes his payment, the sender has to know
that the payment is made so that he does not ask the receiver to
pay again. Moreover, the receiver (who made the payment) has to
know that he has fulfilled his commitment to avoid making multiple
payments, and so on. However, those interactions are stochastic.
For instance, the commitment to pay is not going to be surely
satisfied.

To effectively specify such properties in the face of uncertainty,
the need for a logical tool that can express probabilistic
knowledge and commitments simultaneously is indeed confirmed.
Rather than building a logic from scratch to address the
underlying aspects, we combine logics dealing with these two
individual units in a single logic. We advocate the approach of
combining existing logics because it ensures the preservation of
important properties of the logics being combined
\cite{Konur2013}. In particular, we use the independent join (or
fusion) technique \cite{Franceschet2004}. Given two logics $\mathbb{A}$ and $\mathbb{B}$, we combine them in a new logic $\mathds{A} \oplus \mathds{B}$ which extends the expressive power of each one. In our case, suppose $\mathds{A}$ addresses probabilistic epistemic properties of
agents and $\mathds{B}$ addresses the social aspects (i.e.,
probabilistic commitments and their fulfilments) between
interacting agents. Their combination should be able to not only
express epistemic and social properties, but also express the
interaction between the two concepts (i.e., express them in a
single formula). Once the new combined logic is defined, we use
the PRISM tool \cite{Kwiatkowska2002} as the formal verification tool to verify it after its reduction to PCTL, the probabilistic branching-time logic \cite{Hansson1994}.

The contributions of this chapter are threefold. First, we present a new probabilistic version of interpreted systems to model MASs using the dimensions of knowledge and social commitments. The developed version merges two extended versions of the original formalism of interpreted systems introduced by Fagin and his colleagues \cite{Fagin1995}. Those versions are introduced respectively by 1) Halpern \cite{Halpern2003} and extended later
by Wan et al. \cite{Wan2012,Wan2013} to capture the stochastic
behavior of the system; and 2) by Bentahar et al.
\cite{Bentahar2012} and El-Menshawy et al. \cite{El-Menshawy2013a}
to model the communication between interacting parties. Second, we
introduce a new logic called Probabilistic Logic of Knowledge and
Commitment (PCTL$^{kc}$) to be able to capture and reason about
the interaction between knowledge and social commitments. The
logic we define combines the Probabilistic Computation Tree Logic
of Knowledge PCTLK \cite{Wan2012,Wan2013} and the Probabilistic
Computation Tree Logic of Commitments PCTLC \cite{Sultan2013}.
PCTLK and PCTLC are, in turn, extensions of the Probabilistic
Computation Tree Logic PCTL \cite{Hansson1994} with an epistemic
modality for the knowledge and a social modality for the
commitments and their fulfilments respectively. Third, we
introduce a new model checking technique to verify the proposed
logic (PCTL$^{kc}$). The introduced technique is a reduction-based
in which the problem of model checking PCTL$^{kc}$ is transformed
into the problem of model checking an existing logic called PCTL.
To achieve this reduction, new rules have been laid down to
transform the models of PCTL$^{kc}$ to MDPs to be suitable for
the PRISM model checker. We also devise some other rules to reduce
each PCTL$^{kc}$ formula into PCTL formula. By so doing, we can
build on the existing PRISM model checker by automating our
translation to verify some given properties written originally in
our new logic PCTL$^{kc}$. Figure \ref{approach-cha4} gives an overview of the proposed approach.

\begin{figure}[h]
\begin{center}
\includegraphics [width=14cm, height=5cm]{chap4/img/approach-cha4.eps}
  \caption{An approach for the interaction between knowledge and commitments}
\label{approach-cha4}
\end{center}
\end{figure}

The work presented in this chapter represents a new trend in the direction of capturing interactions between various aspects in MASs. It can be
seen as a first attempt to combine the notions of probability,
knowledge, and commitments in a single tool giving a new
expressive power ---in terms of expressing the individual aspects
as well as their combinations in the presence of uncertainty---,
and is therefore subject to new intuitions.

\section{The Probabilistic Logic of Knowledge and Commitment (PCTL$^{kc})$} \label{sec:PCTLKC-logic}

In this section, we introduce our new probabilistic logic of knowledge and commitment (PCTL$^{kc})$. The modal logic we introduce can express knowledge and social commitments simultaneously in the presence of uncertainty. It combines two existing probabilistic logics namely, the probabilistic logic of knowledge PCTLK \cite{Wan2012,Wan2013} and the probabilistic logic of commitments PCTLC \cite{Sultan2014a,Sultan2013}. We first present the syntax of our new logic, and then we define its semantics. We also define a new version of the probabilistic interpreted systems formalism over which the semantics of PCTL$^{kc}$ can be interpreted.

As we said earlier, the new logic PCTL$^{kc}$ contains a knowledge modality that doesn't exist in the logic defined previously in Chapter \ref{cha:PCTLC}. Therefore, we need first to define the model of PCTL$^{kc}$. In fact, the PCTL$^{kc}$ model is generated from an extended version of probabilistic interpreted systems \cite{Halpern2003,Wan2013} enriched by the social accessibility relations introduced in \cite{Bentahar2012,El-Menshawy2013a} as discussed in Chapter \ref{cha:background}.

\begin{definition}[Models]\label{def:models-pctlkc}

Given a set of atomic propositions $\Phi_p = (p,q,r, \ldots)$ and a set of agents $\texttt{Agt}=\{1,\ldots,n\}$,  the model $\mathfrak{M_2}=(S,\textbf{P},I,\sim_1, \ldots
,\sim_n,\{\sim_{i \rightarrow j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$ is a tuple where:
%
\begin{itemize}
\item  $S \subseteq L_1 \times \ldots \times L_n$ is a countable
set of all reachable global states for the system. A state $s$ is
reachable iff there exists a sequence of transitions from an
initial state to $s$ in which the probability of each transition
is greater than $0$.

\item  $I \in S$ is an initial global state for the system.

\item  $\textbf{P}:S\times S\rightarrow [0,1]$ is a total
transition probability function defined as $\textbf{P}(s,
s')=\tau(s,a^{s \rightarrow s'}, s')$ iff there exists a joint
action $a=(a_1,\ldots,a_n) \in ACT$ such that\\
 $\sum_{i \in \texttt{Agt}} \tau_i(l_i(s),a^{l_i(s)\rightarrow l_i(s')},l_i(s')) > 0$ and $\sum_{s' \in S} \textbf{P}(s,s') =1$
for all $s \in S$.

\item  $\sim_i \subseteq S \times S$ is the epistemic
  accessibility relation for the agent $i$, such that for two global states $s$ and $s'$, we have: $s \sim_i s'$ iff
  $l_i(s)=l_i(s')$.

\item For each pair $(i,j) \in \texttt{Agt}^2$,
$\sim_{i\rightarrow j} \subseteq S \times S$ is a serial social
accessibility relation. $s \sim_{i\rightarrow j} s'$ is defined by
the following conditions:
      %
  \begin{enumerate}
       \item $l_i(s)=l_i(s')$.
       \item $Var_i \cap Var_j \neq \emptyset$ such that $\forall x \in Var_i \cap Var_j$ we have $l^{x}_i(s)\!=\!l^{x}_j(s')$.
       \item $\forall y \in Var_j\!-\! Var_i$ we have $l^{y}_j(s)\!=\!l^{y}_j(s')$.
  \end{enumerate}
       %
  \item  $\nu : S\rightarrow 2^{\Phi_p}$ is a function valuating states with atomic propositions.
\end{itemize}
\end{definition}
%

The difference between our new model $\mathfrak{M_2}$ and the model $\mathfrak{M_1}$ that has been proposed in Chapter \ref{cha:PCTLC} is that $\mathfrak{M_2}$ has the ability to model agents' knowledge in the system --in addition to modeling the commitment-based communication among interacting parties-- thanks to the epistemic accessibility relations that are integrated in the model. Technically, $\mathfrak{M_2}$ in an extended version of $\mathfrak{M_1}$ with epistemic accessibility relations. Computation paths of $\mathfrak{M_2}$ and probability space are defined as in Chapter \ref{cha:PCTLC}. %(Section \ref{sec: semantics of PCTLC}).

\subsection{Syntax of PCTL$^{kc}$} \label{sec:syntax-PCTLKC}
The logic we introduce in this section can be seen as an extension to the logic presented in Chapter \ref{cha:PCTLC} by adding an epistemic operator to PCTLC \cite{Sultan2014a,Sultan2013}. The resulting logic, i.e., PCTL$^{kc}$, will have the power to not only express the individual aspects of knowledge and social commitments in independent formulae, but also express combinations of the two concepts in the same formulae.

\begin{definition}[Syntax]\label{def:PCTLKC syntax}
Given a set of atomic propositions $\Phi_p$. Let $\verb"Agt"=\{1, \dots, n\}$ be a set of agents. The PCTL$^{kc}$ formulae are defined by the following BNF grammar:
%
\begin{align*}
    \varphi & ::= p~|~\neg \varphi~|~\varphi \vee \varphi~|~\mathcal{K}~|~\mathcal{C}~|~ \mathbb{P}_{\bowtie k} (\psi)~|~\mathbb{P}_{\bowtie k}(\mathcal{K})|~\mathbb{P}_{\bowtie k}(\mathcal{C})\\
    \psi & ::=\bigcirc \varphi ~ | ~ \varphi ~U~ \varphi~|~ \varphi~ U^{\leq m} ~ \varphi \\
    \mathcal{K} & ::= K_i \varphi \\
    \mathcal{C} & ::= C_{i\rightarrow j}\varphi ~| ~ Fu(C_{i\rightarrow j}\varphi)
\end{align*}
%
where $p\in\Phi_p$ is an atomic proposition and $\mathbb{P}_{\bowtie
k}$ is a probabilistic operator where $\bowtie \in\{<,\leq,>,\ge\}$ and $k\in [0,1]$ is a probability bound or threshold. $m \in\mathbb{N}^+ $ is a positive integer number reflecting the maximum number of transitions needed to reach a certain state. $\varphi$ and $\psi$ are state and path formulae interpreted over the states and paths of $\mathfrak{M_2}$ respectively. The Boolean connectives $\neg$ and $\vee$ are defined in the usual
way. Formulae $\mathcal{K}$ are state formulae called knowledge (epistemic) formulae and used to express the epistemic properties through the K$_i$ operator which stands for agent i knows. Formulae $\mathcal{C}$, called social formulae, are special state formulae in PCTL$^{kc}$ that can express social properties using the modal connectives $C_{i\rightarrow j}$ and $Fu(C_{i\rightarrow j})$ standing for ``commitment'' and ``fulfillment of commitment'' respectively. $\bigcirc, U$ and $U^{\leq m}$ stand for ``next time'', ``until'' and ``bounded until'' path modal connectives
respectively.

\end{definition}

\subsection{Semantics of PCTL$^{kc}$} \label{def:semantics-PCTLKC}

Given a model $\mathfrak{M_2}=(S,\textbf{P},I,\sim_1, \ldots
,\sim_n,\{\sim_{i \rightarrow j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$, then $(\mathfrak{M_2},s) \models \varphi$ states that ``a state $s$ in the model $\mathfrak{M_2}$ satisfies a state formula $\varphi$, $(\mathfrak{M_2},\pi) \models \psi$ means that ``a path $\pi$ in the model $\mathfrak{M_2}$ satisfies a path formula $\psi$, and
$(\mathfrak{M_2},s) \models \mathbb{P}_{\bowtie k}(\psi)$ means that
``a state $s$ in $\mathfrak{M_2}$ satisfies $\mathbb{P}_{\bowtie k}(\psi)$ if the probability of taking a path from $s$ that satisfies $\psi$ is in the interval specified by $\bowtie k$''. When the model $\mathfrak{M_2}$ is clear from the context, we simply write the satisfaction relation $\models$ as follows: $s \models \varphi$ and $\pi \models \psi$. Furthermore,
for a given pair $(i,j)\in \texttt{Agt}^2$ of agents, we denote
the number of socially accessible states $s'$ from a given state $s$ such
that $s\sim_{i\rightarrow j}s'$ by $|s\sim_{i\rightarrow j}s'|$.
We also denote the number of epistemically accessible states $s'$ from a given state $s$ such that $s\sim_i s'$ by $|s\sim_i s'|$.

Finally, we define $|s\models \varphi|$ as follows:

\begin{center}
$|s\models \varphi|=
\begin{cases}
1,~~~\textrm{if}~ s\models\varphi\\
0,~~~\textrm{otherwise.}
\end{cases}$
\end{center}

\begin{definition}[\textbf{Satisfaction}]\label{def:semantics-pctlkc} Satisfaction of a PCTL$^{kc}$ formula in the model $\mathfrak{M_2}$ is recursively defined as follows:

%\noindent In what follows, we define the semantics of PCTL$^{kc}$ formulae.

\noindent $s\models p~~~~~~~~~~~~~~\emph{iff}~~p\in \nu(s);\\
s\models \varphi_1 \vee \varphi_2 ~~~~~~\emph{iff}~~s\models \varphi_1~\textrm{or}~s \models \varphi_2; \\
s\models \neg \varphi~~~~~~~~~~~\emph{iff}~~s \nvDash \varphi;\\
s\models K_i \varphi  ~~~~~~~~~~ \emph{iff}~~ \forall s'\in S ~ \textrm{s.t.} ~~ s \sim_i s'  \ \textrm{we~have}~ s'\models \varphi; \\
s\models C_{i\rightarrow j}\varphi~~~~~~~~\emph{iff} ~~\forall s' \in S~\textrm{s.t.}~s \sim_{i \rightarrow j}s', \textrm{we~have}~s' \models \varphi;\\
s\models Fu(C_{i\rightarrow j}\varphi) ~~\emph{iff} ~~\exists s' \in S~\textrm{s.t.}~s' \sim_{i \rightarrow j}s ~ \textrm{and}~s' \models C_{i\rightarrow j}\varphi;$

\noindent $\pi \models \bigcirc \varphi~~~~~~~~~~~\emph{iff}~~\pi(1) \models \varphi; \\
\pi \models \varphi_1~U^{\leq m}~\varphi_2~~\emph{iff}~~\exists k \leq m~~\textrm{s.t.}~~ \pi(k) \models \varphi_2 ~\textrm{and}~\forall i < k, \pi(i) \models \varphi_1;\\
\pi \models \varphi_1 ~U~\varphi_2~~~~~~\emph{iff}~~\exists m \geq 0~~\textrm{s.t.}~~\pi \models \varphi_1~U^{\leq m}~\varphi_2;$

\noindent $s \models \mathbb{P}_{\bowtie k} (\psi)~~~~~~~~\emph{iff}~~Prob_s(\psi)\bowtie k$ where: $Prob_s(\psi)=Prob_s\{\pi \in \Pi(s)~|~\pi\models
\psi\};$

%\begin{itemize}
\noindent For a probabilistic operator working on an epistemic formula, where the set of all accessible states from $s$ is our sample space and the set of events $\mathrm{F}$ is the set of states accessible from $s$ and satisfy the formula:

\begin{tabbing}
$s\models \mathbb{P}_{\bowtie k}(K_i\varphi) $
    \ \ \ \ \ \= \emph{iff} \ $Prob(s \models K_i\varphi)$ $\bowtie k$ where: $Prob(s\models K_i\varphi)=\frac{\sum_{s \sim_i s'}|s'\models \varphi| }{|s \sim_i s'|};$

\end{tabbing}

\noindent For a probabilistic operator working over a commitment formula,
where the set of all accessible states from $s$ is our sample space and the set of events $\mathrm{F}$ is the set of states satisfying the formula: %and assuming that the probabilities of accessible states from state $s$ are equally distributed:

\noindent  $s\models \mathbb{P}_{\bowtie k}(C_{i\rightarrow j}\varphi)$
   ~\emph{iff}  $Prob(s \models C_{i\rightarrow j}\varphi) \bowtie \!k$ where: $Prob(s\models C_{i\rightarrow j}\varphi)=\frac{\sum_{s \sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s \sim_{i \rightarrow j}s'| };$

\noindent For a probabilistic operator working over a fulfilment formula,
 assuming that accessible states are also reachable:

\noindent $s\models \mathbb{P}_{\bowtie k}(Fu(C_{i\rightarrow j}\varphi))$
    ~~ \emph{iff}~ $Prob(s \models Fu(C_{i\rightarrow j}\varphi)) \bowtie k;$ where:
%\vspace{-0.4cm}
\begin{align*}
& Prob(s\models Fu(C_{i\rightarrow j}\varphi))\ = Prob_s\{\pi \in \Pi(s') ~|~ s' \sim_{i \rightarrow j}s ~~\textrm{and}~~ \pi = s' \ldots s ~~\textrm{and}~~ s' \models C_{i\rightarrow j}\varphi\}
\end{align*}

%\end{itemize}
\end{definition}

The probabilistic knowledge is computed in such a way to reflect the indistinguishability property of the epistemic accessibility relations. Therefore, the probability is computed based on the number of accessible states satisfying the content of the knowledge over the number of equivalent states, as all the states are equally accessible. Probabilistic commitment is also computed based on the number of accessible states that satisfy the
content over the whole number of accessible states, which demonstrates the uncertainty of the agent over the accessible states, so that over the commitment. Probabilistic fulfillment, however, is computed using the probabilistic transitions of the path linking the commitment state to the fulfillment state. The following proposition is straightforward from the semantics:

\begin{proposition} \label{proposition-PCTLKC}~\\
If $(\mathfrak{M_2},s)\models \mathbb{P}_{\leq0} (Fu(C_{i \rightarrow
j}\varphi))$ and $(\mathfrak{M_2},s)\models Fu(C_{i \rightarrow
j}\varphi)$, then $s$ is not reachable from the commitment state.
\end{proposition}

\begin{theorem} \label{thm: Ki equivalence} \ \ \ \ {Epistemic Equivalences}

    \begin{enumerate}
        \item $(\mathfrak{M_2},s)\models \mathbb{P}_{\geq1}(K_i\phi)$  ~~~~~iff~~  $(\mathfrak{M_2},s) \models K_i\phi$
        \item $(\mathfrak{M_2},s)\models \mathbb{P}_{\leq 0}(K_i\phi)$   ~~~~~iff~~  $(\mathfrak{M_2},s)\models K_i \neg \phi$
        \item $(\mathfrak{M_2},s)\models \mathbb{P}_{]0,1[}(K_i~\phi)$  ~~~iff~~   $(\mathfrak{M_2},s)\models \neg K_i\neg\phi \wedge \neg K_i\phi$

    \end{enumerate}

\end{theorem}

\begin{proof} \hspace{-0.9cm}

\begin{itemize}
\item First equivalence. ~\\
    $``\Rightarrow"$. Assume $s\models \mathbb{P}_{\geq1} (K_i\varphi)$.
    By the semantics of PCTL$^{kc}$, it follows that $Prob(s\models K_i\varphi)\geq1$.
    Therefore, $\frac{\sum_{s\sim_i s'}|s'\models \varphi| }{|s\sim_i s'|}\geq1$. This means $\forall s'\in S$ such that $s\sim_i s'$, we have
    $s'\models \varphi$ (as $\sim_i$ is reflexive, so $s'$ could be $s$ itself). Thus, $s \models K_i \varphi$. \\
    $``\Leftarrow"$. Assume $s\models K_i\varphi$. By the PCTL$^{kc}$ semantics, it follows that for all $s'\in S$ such that $s\sim_i s'$,
    we have $s'\models \varphi$ (i.e. all accessible states from $s$ satisfy $\varphi$).
    Consequently, $\sum_{s\sim_i s'}|s'\models \varphi| = |s\sim_i s'|$.
    Therefore, $\frac{\sum_{s\sim_i s'}|s'\models \varphi| }{|s\sim_i s'|}\geq1$ and hence $s\models \mathbb{P}_{\geq1} (K_i\varphi)$.

\item Second equivalence. ~\\
    $``\Rightarrow"$. Assume $s\models \mathbb{P}_{\leq0} (K_i\varphi)$.
    By the PCTL$^{kc}$ semantics, it follows that $Prob(s\models K_i\varphi)\leq0$.
    Thus, $\frac{\sum_{s\sim_i s'}|s'\models \varphi|}{|s\sim_i s'|}\leq0$. Since $\sim_i$ is reflexive, so the set of the accessible states from $s$ is not empty, therefore $\sum_{s\sim_i s'}|s'\models \varphi|$ must be 0 (i.e. $\varphi$ is not true in any of the accessible states). Consequently, for all $s'\in S$ such that $s\sim_i s'$, we have $s'\nvDash \varphi$, which means $s'\vDash \neg \varphi$. Hence, $s\models K_i \neg \varphi$.~\\
%
    $``\Leftarrow"$. Assume $s\models K_i\neg \varphi$. By the PCTL$^{kc}$ semantics, it follows that $\forall s'\in S$ such that
    $s\sim_i s'$, we have $s'\nvDash \varphi$. Since the set of the accessible states from $s$ is not empty, then $\frac{\sum_{s\sim_i s'}|s'\models \varphi| }{|s\sim_i s'|}\leq0$.
    Hence, $s\models \mathbb{P}_{\leq0} (K_i\varphi)$.

\item Third equivalence. ~\\
    $``\Rightarrow"$. Assume $s\models \mathbb{P}_{]0,1[} K_i\varphi)$. By the PCTL$^{kc}$ semantics, it follows that $0< Prob(s\models K_i\varphi)<1$. Thus, $0<\frac{\sum_{s\sim_i s'}|s'\models \varphi| }{|s \sim_i s'|}<1$.
    This means that it would never be the case that $\sum_{s\sim_i s'}|s'\models \varphi| = |s\sim_i s'|$ nor $\sum_{s\sim_i s'}|s'\models \varphi| = 0$. Consequently, there exist some $s', s'' \in S$ such that $s\sim_i s'$ and $s\sim_i s''$ and $s'\models \varphi$ and $s''\models \neg \varphi$. Hence, it is impossible to have $\overline{s}\models \neg\varphi$ or $\overline{s}\models \varphi$ for all $\overline{s}\in S$ such that $s\sim_i \overline{s}$. Consequently, $s\nvDash  K_i\neg\varphi$ and $s\nvDash K_i\varphi$. Hence $s\models \neg K_i\neg\varphi$ and $s\models \neg K_i\varphi$. ~\\
    %
    $``\Leftarrow"$. Assume $s\models \neg K_i\varphi$. By the PCTL$^{kc}$ semantics, it follows that there exists $s'\in S$ such that $s\sim_i s'$ and $s'\models \neg \varphi$. Consequently, it would never be the case that for all $s'\in S$ such that $s\sim_i s'$ we have $s'\models \varphi$. Therefore, $1>\frac{\sum_{s\sim_i s'}|s'\models \varphi| }{|s\sim_i s'|}$. Now assume $s\models \neg K_i\neg \varphi$. Therefore, $\sum_{s\sim_i s'}|s'\models \varphi| = 0$ would never be the case as some accessible states should satisfy $\varphi$. Consequently, $\frac{\sum_{s\sim_i s'}|s'\models \varphi| }{|s\sim_i s'|}>0$. Thus, $0<\frac{\sum_{s\sim_i s'}|s'\models \varphi| }{|s \sim_i s'|}<1$. Hence, $s\models \mathbb{P}_{]0,1[} (K_i\varphi)$.
\end{itemize}
\end{proof}

\vspace{0.9cm}
\begin{theorem}\label{Commitment-Equivelances}{Commitment Equivalences} ~

\begin{enumerate}
\item $(\mathfrak{M_2},s)\models \mathbb{P}_{\geq1} (C_{i \rightarrow
j}\varphi)$ ~~~iff~~ $(\mathfrak{M_2},s)\models C_{i \rightarrow
j}\varphi$

\item $(\mathfrak{M_2},s)\models \mathbb{P}_{\leq0} (C_{i \rightarrow
j}\varphi)$ ~~~iff~~ $(\mathfrak{M_2},s)\models C_{i \rightarrow
j}\neg \varphi$

\item $(\mathfrak{M_2},s)\models \mathbb{P}_{]0,1[} (C_{i \rightarrow
j}\varphi)$ ~~iff~~ $(\mathfrak{M_2},s)\models \neg C_{i
\rightarrow j}\neg\varphi \wedge \neg C_{i \rightarrow j}\varphi$

\end{enumerate}

\end{theorem}
%\vspace{1cm}
\begin{proof}\hspace{-0.9cm}

\begin{itemize}
\item First equivalence. ~\\
    $``\Rightarrow"$. Assume $s\models \mathbb{P}_{\geq1} (C_{i \rightarrow j}\varphi)$.
    By the PCTL$^{kc}$ semantics, it follows that $Prob(s\models C_{i\rightarrow j}\varphi)\geq1$.
    Thus,  $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}\geq1$.
    This means that for all $s'\in S$ such that $s\sim_{i \rightarrow j}s'$, we have
    $s'\models \varphi$, and hence $s \models C_{i\rightarrow j}\varphi$. \\
    $``\Leftarrow"$. Assume $s\models C_{i \rightarrow j}\varphi$. By the
    PCTL$^{kc}$ semantics, it follows that for all $s'\in S$ such that $s\sim_{i \rightarrow j}s'$,
    we have $s'\models \varphi$ (i.e. all accessible states from $s$ satisfy $\varphi$).
    Consequently, $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = |s\sim_{i \rightarrow j}s'|$.
    Therefore, $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}\geq1$
    and hence, $s\models \mathbb{P}_{\geq1} (C_{i \rightarrow j}\varphi)$.

\item Second equivalence. ~\\
    $``\Rightarrow"$. Assume $s\models \mathbb{P}_{\leq0} (C_{i \rightarrow j}\varphi)$.
    By the PCTL$^{kc}$ semantics, it follows that $Prob(s\models C_{i\rightarrow j}\varphi)\leq0$.
    Thus, $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi|}{|s\sim_{i \rightarrow j}s'|}\leq0$.
    Since the set of the accessible states from $s$ is not empty, then $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi|$
    must be 0 (i.e. $\varphi$ is not true in any of the accessible states). Consequently, for all $s'\in S$
    such that $s\sim_{i \rightarrow j}s'$, we have $s'\nvDash \varphi$, which means $s'\vDash \neg \varphi$.
     Hence, $s\models C_{i\rightarrow j}\neg \varphi$.~\\
%
    $``\Leftarrow"$. Assume $s\models C_{i \rightarrow j}\neg \varphi$. By the PCTL$^{kc}$ semantics,
    it follows that for all $s'\in S$ such that
    $s\sim_{i \rightarrow j}s'$, we have $s'\nvDash \varphi$. Since the set of the accessible states from $s$ is not empty,
    then $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}\leq0$.
    Hence, $s\models \mathbb{P}_{\leq0} (C_{i \rightarrow j}\varphi)$.

\item Third equivalence. ~\\
    $``\Rightarrow"$. Assume $s\models \mathbb{P}_{]0,1[} (C_{i \rightarrow j}\varphi)$. By the PCTL$^{kc}$ semantics,
    it follows that $0< Prob(s\models C_{i\rightarrow j}\varphi)<1$. Thus,
    $0<\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s \sim_{i \rightarrow j}s'|}<1$.
    This means that it would never be the case that $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = |s\sim_{i \rightarrow j}s'|$
    nor $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = 0$. Consequently, there exist some $s', s'' \in S$
    such that $s\sim_{i \rightarrow j}s'$ and $s\sim_{i \rightarrow j}s''$ and $s'\models \varphi$ and $s''\models \neg \varphi$.
    Hence, it is impossible to have
    $\overline{s}\models \neg\varphi$ or $\overline{s}\models \varphi$ for all $\overline{s}\in S$
    such that $s\sim_{i \rightarrow j}\overline{s}$. Consequently,
    $s\nvDash  C_{i \rightarrow j}\neg\varphi$ and $s\nvDash  C_{i \rightarrow
    j}\varphi$. Hence $s\models \neg C_{i \rightarrow j}\neg\varphi$ and $s\models \neg C_{i \rightarrow j}\varphi$. ~\\
    %
    $``\Leftarrow"$. Assume $s\models \neg C_{i \rightarrow j}\varphi$. By the PCTL$^{kc}$ semantics,
    it follows that there exists $s'\in S$ such that $s\sim_{i \rightarrow j}s'$ and $s'\models \neg \varphi$.
    Consequently, it would never be the case that $s'\models \varphi$ for all $s'\in S$
    such that $s\sim_{i \rightarrow j}s'$. Therefore,
    $1>\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}$.
    Now assume $s\models \neg C_{i \rightarrow j}\neg \varphi$. Therefore, $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = 0$
    would never be he case as some accessible states should satisfy $\varphi$. Consequently,
    $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}>0$.
    Thus, $0<\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s \sim_{i \rightarrow j}s'|}<1$.
    Thus, $s\models \mathbb{P}_{]0,1[} (C_{i \rightarrow
    j}\varphi)$.
\end{itemize}

\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem}\label{Fulfiilemt-Equivelances} {Fulfillment Equivalences}~

\begin{enumerate}
\item $(\mathfrak{M_2},s)\models \mathbb{P}_{>0} (Fu(C_{i \rightarrow
j}\varphi))$ iff $(\mathfrak{M_2},s)\models Fu(C_{i \rightarrow
j}\varphi)$ and $s$ is reachable from the commitment state.

\item $(\mathfrak{M_2},s)\models \mathbb{P}_{\leq0} (Fu(C_{i \rightarrow
j}\varphi))$ iff $(\mathfrak{M_2},s)\models \neg Fu(C_{i \rightarrow
j}\varphi)$ or $s$ is not reachable from the commitment state.

\end{enumerate}

\end{theorem}

\begin{proof} \hspace{0.5cm} \\
The proofs of these equivalences are direct from Proposition
\ref{proposition-PCTLKC} and the above semantics.

 \end{proof}

\section{Model Checking PCTL$^{kc}$ Using Reduction} \label{sec:model-checking-pctlkc}

In this section, we present our reduction technique to model checking PCTL$^{kc}$. Given a MAS represented as a probabilistic interpreted system $\mathfrak{M_2}$ and a desirable property $\varphi$ written in PCTL$^{kc}$, the problem of probabilistic model checking PCTL$^{kc}$ can be defined as: 1) establishing whether $(\mathfrak{M_2}, I)\models \varphi$,
i.e., if $I \in Sat(\varphi)$ where $Sat(\varphi)$=$\{s\in S ~~|~~
\mathfrak{M_2},s \models \varphi \}$ is the set of states satisfying
$\varphi$; 2) comparing the probability of satisfying $\varphi$
with a probability threshold $\bowtie k$, where
$Sat(\mathbb{P}_{\bowtie k}(\varphi))=\{s\in S ~|~
Prob_s(\varphi)\bowtie k \}$ ; or 3) computing the probability of
$\varphi$, $(\mathfrak{M_2}, s)\models \mathbb{P}_{=?} ~(\varphi)$.
Note that answers to the second and third queries can be: (1)
truth values, when the specification simply asks for a comparison
to a probability threshold; or (2) quantitative, returning the
actual probability.

Figure \ref{fig:reduction-process-PCTLKC} depicts the structure of our proposed reduction technique. The idea is to reduce the problem of probabilistic model checking PCTL$^{kc}$ to the problem of probabilistic model checking PCTL in order to use the PRISM model checker. Concretely, the proposed reduction technique consists of two processes. In the former one, we transform our model $\mathfrak{M_2}$ into an MDP model.
MDPs are the standard models for describing systems with probabilistic and nondeterministic behavior \cite{Rutten2004}. Then, we use the notion of adversary as in \cite{Kwiatkowska2003} to resolve the nondeterminism of the MDP. The resulting adversaries are basically DTMC models for which we can define a unique probability measure over paths. The obtained DTMC models will be the input of the PRISM model checker. In the latter process of the reduction technique, we transform PCTL$^{kc}$ formulae into PCTL formulae. This is basically achieved by constructing a set of rules that formally transforms the PCTL$^{kc}$ formulae into corresponding ones in PCTL.

\begin{figure}[h]
\centering
\includegraphics[width=14cm, height=7cm]{chap4/img/reduction-process-cha4.eps}
%\includegraphics[scale=0.5]{figure1}
\caption{The proposed reduction technique of model checking PCTL$^{kc}$}
\label{fig:reduction-process-PCTLKC}
\end{figure}

In a nutshell, the proposed model checking procedure is as follows. Given $\mathfrak{M_2}=(S,\textbf{P},I,\sim_1, \ldots
,\sim_n,\{\sim_{i \rightarrow j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$, and PCTL$^{kc}$ formula $\varphi$, we have to define an MDP model $\mathfrak{M'_2}$ = $\mathscr{F}(\mathfrak{M_2})$ and PCTL formula $\mathscr{F}(\varphi)$ using the transformation function $\mathscr{F}$ such that $\mathfrak{M_2} \models \varphi$ iff $\mathscr{F}(\mathfrak{M_2})\models \mathscr{F}(\varphi)$.

\begin{figure}[h]
\centering
\includegraphics[width=15cm, height=9cm]{chap4/img/relation-translation2.eps}
%\includegraphics[scale=0.5]{figure1}
\caption{Translating relations in $\mathfrak{M_2}$ into labeled transitions in the MDP model} \label{fig:relation-translation-PCTLKC}
\end{figure}

\subsection{Transforming the Model $\mathfrak{M_2}$}

In order to transform our model $\mathfrak{M_2}=(S,\textbf{P},I,\sim_1, \ldots
,\sim_n,\{\sim_{i \rightarrow j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$ into an MDP model $\mathfrak{M'_2}$ = $(\mathbb{S}, Act, \textsf{P}_t ,I_i, L)$, we need to define the set of actions $Act$. Therefore, one of the main steps that we perform in this transformation is to define the set $Act$. The idea is that, we translate different relations in $\mathfrak{M_2}$ into labeled transitions in $\mathfrak{M'_2}$. Labels (also called actions) are used to distinguish between different types of relations. Consequently, the three relations in $\mathfrak{M_2}$, namely transition relation, epistemic accessibility relation, and social accessibility relation are translated into labeled transitions in $\mathfrak{M'_2}$. Moreover, whenever we have a labeled transition representing a social accessibility relation we add the symmetric closure of it to interpret the fulfilment of the commitment. As depicted in Figure \ref{fig:relation-translation-PCTLKC} (assuming that $n$ is the number of agents, $1 \leq i \leq n$, and $1 \leq j \leq n$), actions $\delta, \alpha^i, \beta^{ij},$ and $\gamma^{ij}$ denote transitions defined, respectively, from the probabilistic transition relation $\textbf{P}$, the epistemic accessibility relation $\sim_i$ (to capture the semantics of knowledge), the social accessibility relation $\sim_{i \rightarrow j}$ (to capture the semantics of commitment), and the symmetric closure of the social accessibility relation (to capture the semantics of fulfilment).\\

The MDP model $\mathfrak{M'_2} = (\mathbb{S}, Act, \textsf{P}_t ,I_i, L)$ can now be defined as follows:

\begin{itemize}
\item $\mathbb{S}$=$S$; $I_i$=$I$; $L$=$\nu$.

\item $Act = \{\delta \} \cup \{\alpha^1, \alpha^2, \dots, \alpha^n\} \cup \{\beta^{11}, \beta^{12}, \dots, \beta^{nn}\} \cup \{\gamma^{11}, \gamma^{12}, \dots, \gamma^{nn}\}$ where $n$ is the number of agents.

\item We define $\textsf{P}_t$ as the union of the transitions labeled with $\delta$ (i.e., the probabilistic transitions of $\textbf{P}$) with the probabilistic transitions labeled with $\alpha^i$, probabilistic transitions labeled with $\beta^{ij}$, and probabilistic transitions labeled with $\gamma^{ij}$. The probabilities of transitions labeled with $\delta$ are not manipulated but rather inherited from the probabilistic transition function $\textbf{P}$. However, for transitions labeled with $\alpha^i$ and emanating from the same state are given equal probabilities (i.e., equal distribution) which reflect the uncertainty of the agent over the accessible states, so that over the content of the knowledge. Meaning that, the probability of each transition annotated by $\alpha^i$ is equal to the probability of each other transition labeled with $\alpha^i$ emanating from the same state which is calculated by dividing one over the number of transitions labeled with $\alpha^i$. The probabilities of transitions labeled with $\beta^{ij}$ and $\gamma^{ij}$ are calculated in the same way. For states $s, s' \in \mathbb{S}$ and  action $\theta \in Act$, the function $\textsf{P}_t$ is defined as follows:
\begin{equation*}
    \textsf{P}_t(s, \theta , s' )=
\begin{cases}
    \textbf{P}(s, s'),   & \textit{if } \theta = \delta  \\
    \frac{1}{|s\sim_i s'|},   & \textit{if } \theta = \alpha^i\\
    \frac{1}{|s\sim_{i \rightarrow j} s'|},   & \textit{if } \theta = \beta^{ij}\\
    \frac{1}{|s'\sim_{i \rightarrow j} s|},   & \textit{if } \theta = \gamma^{ij}.
    \end{cases}
    \end{equation*}

\end{itemize}

The induced model of applying the adversary $\sigma$ over
$\mathfrak{M'_2}$ is a DTMC model. Specifically, four adversaries are defined; $\sigma_t$ over which temporal formulae are interpreted, $\sigma_e$ to capture epistemic formulae, $\sigma_c$ to capture commitment formulae, and $\sigma_f$ to capture fulfillment formulae. These adversaries are defined based on the following rules. To define $\sigma_t$, action $\delta$ is selected at every state in $\mathfrak{M'_2}$. For $\sigma_e$, action $\alpha^i$ has to be among the enabled actions at the knowledge state. Then, the adversary picks up $\alpha^i$ at that knowledge state and $\delta$ at every other state. Adversaries $\sigma_c$, and $\sigma_f$ are defined in the same way.

\subsection{Reducing PCTL$^{kc}$ Formulae into PCTL Formulae}

In this section, we introduce our reduction rules that translate PCTL$^{kc}$ formulae to PCTL formulae w.r.t given adversary $\sigma$. Given the adversary $\sigma_t$, the PCTL$^{kc}$ formulae are transformed
inductively into PCTL as follows:

$\mathscr{F}(p)=p$, if $p$ is an atomic proposition,

$\mathscr{F}(\neg \varphi)= \neg \mathscr{F} (\varphi)$,

$\mathscr{F}(\mathbb{P}_{\bowtie k}(\varphi \vee \psi))=\mathbb{P}_{\bowtie k}(\mathscr{F}(\varphi) \vee \mathscr{F}(\psi))$,

$\mathscr{F}(\mathbb{P}_{\bowtie k}\bigcirc \varphi)=\mathbb{P}_{\bowtie k} \bigcirc \mathscr{F}(\varphi)$,

$\mathscr{F}(\mathbb{P}_{\bowtie k}(\varphi~ U ~ \psi))=\mathbb{P}_{\bowtie k} (\mathscr{F}(\varphi) U \mathscr{F}(\psi))$,

$\mathscr{F}(\mathbb{P}_{\bowtie k}(\varphi~ U^{\leq m} ~ \psi))=\mathbb{P}_{\bowtie k} (\mathscr{F}(\varphi) U^{\leq m} \mathscr{F}(\psi))$,

Note that $\sigma_t$ is a DTMC model that is used to interpret only PCTL formulas. It cannot be used to capture the transformed formulas of knowledge and commitment as it ignores all relations except those labeled by $\delta$ (i.e., transition relations of $\textbf{P}$).

Given the adversary $\sigma_e$, the PCTL$^{kc}$ epistemic formula is transformed inductively into PCTL as follows:

$\mathscr{F}(K_i \varphi)= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))$,

$\mathscr{F}(\mathbb{P}_{\bowtie k} K_i \varphi)= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(\varphi))$,

As mentioned earlier, the adversary $\sigma_e$ is a DTMC model that captures only action $\alpha^i$ at the knowledge state and $\delta$ at all other states. Intuitively, transitions labeled with $\alpha^i$ represent epistemic accessibility relations and, in fact, epistemically accessible states from the knowledge state must satisfy $\varphi$. Back to Figure \ref{fig:relation-translation-PCTLKC} (b), it is readily seen that all next states to the knowledge state through transitions labeled with $\alpha^i$ satisfy $\mathscr{F}(\varphi)$. This explains why knowledge formula $K_i~\varphi$ is transformed to next operator followed by the transformation of the content of the knowledge $(i.e., \bigcirc \mathscr{F}(\varphi))$ in all paths emanating from the knowledge state.

Given the adversary $\sigma_c$, the PCTL$^{kc}$ commitment formula is
transformed inductively into PCTL as follows:

$\mathscr{F}(C_{i\rightarrow j}\varphi)= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))$,

$\mathscr{F}(\mathbb{P}_{\bowtie k} C_{i\rightarrow j}\varphi)= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(\varphi))$,

Similar to the case of knowledge formula, Figure \ref{fig:relation-translation-PCTLKC} (c) illustrates the intuitions behind transforming the commitment formula $C_{i\rightarrow j}\varphi$ to  $\bigcirc \mathscr{F}(\varphi)$ in all baths emerging from the commitment state.

Given the adversary $\sigma_f$, the PCTL$^{kc}$ fulfillment formula
is transformed inductively into PCTL as follows:

$\mathscr{F}(Fu(C_{i\rightarrow j}\varphi))= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(C_{i\rightarrow j}\varphi))= \mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$,

$\mathscr{F}(\mathbb{P}_{\bowtie k} Fu(C_{i\rightarrow j}\varphi))= \mathbb{P}_{\bowtie k} (\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(C_{i\rightarrow j}\varphi))= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$.

Though the semantics of the fulfillment operator in PCTL$^{kc}$ requires the existence of a path containing the fulfilment state which must be socially accessible from the commitment state, in this transformation we notice that all next states to the fulfilment state through transitions labeled with $\gamma^{ij}$ should satisfy the commitment formula ($C_{i\rightarrow j}\varphi$). The reason of that is because in our transformation process, the transitions labeled with $\gamma^{ij}$ came as a result of adding the symmetric closure of transitions labeled with $\beta^{ij}$ in order to capture the semantics of the fulfilment. Therefore, all added transitions should satisfy the commitment formula ($C_{i\rightarrow j}\varphi$) (see Figure \ref{fig:relation-translation-PCTLKC} (c)).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem}[Equivalences Satisfaction]\label{Satsisfaction-Equivelance}\hspace{0.5cm}

Let $\sigma_{t}$, $\sigma_{e}$, $\sigma_{c}$, and $\sigma_f$ be the DTMC models corresponding to the adversaries that capture respectively, temporal formulae, epistemic formulae, commitment formulae, and fulfilment formulae in the model $\mathfrak{M'_2}$. The following equivalences hold:

$(\mathfrak{M_2},s)\models p ~\text{iff}~ (\sigma_t,s) \models p$

$(\mathfrak{M'_2},s)\models \neg \varphi ~\text{iff}~ (\sigma_t,s)\models\neg \mathscr{F}(\varphi)$

$(\mathfrak{M_2},s)\models \mathbb{P}_{\bowtie k}(\varphi \vee \psi)
~\text{iff}~ (\sigma_t,s) \models
\mathbb{P}_{\bowtie k} \mathscr{F}(\varphi) \vee
\mathbb{P}_{\bowtie k} \mathscr{F}(\psi) $

$(\mathfrak{M_2},s)\models \mathbb{P}_{\bowtie k}\bigcirc\varphi ~\text{iff}~ (\sigma_t,s) \models\mathbb{P}_{\bowtie k} \bigcirc \mathscr{F}(\varphi) $

$(\mathfrak{M_2},s)\models\mathbb{P}_{\bowtie k}(\varphi~ U ~ \psi) ~\text{iff}~ (\sigma_t,s) \models \mathbb{P}_{\bowtie k}(\mathscr{F}(\varphi)~ U ~\mathscr{F}(\psi))$

$(\mathfrak{M_2},s)\models\mathbb{P}_{\bowtie k}(\varphi~ U^{\leq m} ~ \psi) ~\text{iff}~ (\sigma_t,s) \models \mathbb{P}_{\bowtie k}(\mathscr{F}(\varphi)~ U^{\leq m} ~\mathscr{F}(\psi))$

$(\mathfrak{M_2},s)\models K_i \varphi ~\text{iff}~ (\sigma_e,s)\models \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$

$(\mathfrak{M_2},s)\models \mathbb{P}_{\bowtie k}K_i \varphi ~\text{iff}~ (\sigma_e,s) \models \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi)))$

$(\mathfrak{M_2},s)\models C_{i \rightarrow j}\varphi ~\text{iff}~ (\sigma_c,s)\models \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$

$(\mathfrak{M_2},s)\models \mathbb{P}_{\bowtie k}C_{i \rightarrow j}\varphi ~\text{iff}~ (\sigma_c,s) \models \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi)))$

$(\mathfrak{M_2},s)\models Fu(C_{i \rightarrow j}\varphi) ~\text{iff}~ (\sigma_f,s) \models \mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$

$(\mathfrak{M_2},s)\models \mathbb{P}_{\bowtie k}Fu(C_{i \rightarrow j}\varphi) ~\text{iff}~ (\sigma_f,s) \models \mathbb{P}_{\bowtie k} (\mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))))$

\end{theorem}

Notice that each formula has to be interpreted over a DTMC model
(adversary) that is used to solve the nondeterminism in
$\mathfrak{M'_2}$ based on the type of the formula (i.e.,
temporal, epistemic, or social). The proof of the theorem with
regard to PCTL formulae is straightforward as PCTL formulae are
also PCTL$^{kc}$ formulae. However, for epistemic and social
formulae, the proof is given in Theorem \ref{soundness-PCTLKC}.
%that discusses the soundness of the  transformation rules.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{theorem}[Soundness and Completeness of $\mathscr{F}$]\label{soundness-PCTLKC}
Let $\mathfrak{M_2}$ and $\Phi$ be respectively a PCTL$^{kc}$ model
and formula and let $\mathscr{F}(\mathfrak{M_2})$  and $\mathscr{F}(\Phi)$ be the corresponding model and formula in PCTL. We have $\mathfrak{M_2}\models\Phi$ iff $\mathscr{F}(\mathfrak{M_2}) \models \mathscr{F}(\Phi)$.
\end{theorem}

%\begin{proof}$~\\$
\begin{proof} \hspace{0.5cm} \\
To prove the soundness of the proposed reduction technique, we have to prove that the following three cases are sound: $\Phi =
K_i\varphi$, $\Phi = C_{i \rightarrow j} \varphi$ and $\Phi = Fu(C_{i \rightarrow j} \varphi)$. We prove this by induction on the structure of the formula
$\Phi$. The case of PCTL$^{kc}$ formulae that are also PCTL formulae is straightforward.

\begin{itemize}
\item $\Phi = K_i ~\varphi$. We have $(\mathfrak{M_2},s)\models K_i ~\varphi ~\text{iff}~ (\mathfrak{M_2},s') \models \varphi$ for every $s' \in S ~\textrm{such that}~ s\sim_i s'$. Therefore, $(\mathfrak{M_2},s)\models K_i ~\varphi ~\text{iff}~ (\mathscr{F}(\mathfrak{M_2}),s) \models \mathscr{F}(K_i~\varphi)$. Recall that $\mathscr{F}(\mathfrak{M_2})= \mathfrak{M'_2}$. Now, $(\mathfrak{M'_2},s) \models \mathscr{F}(K_i~\varphi)$ iff for every $s' \in \mathbb{S} ~\textrm{such that}~ (s,\alpha^i,s') \in \textsf{P}_t$, we have $(\mathfrak{M'_2},s') \models \mathscr{F}(\varphi)$. However, w.r.t the semantics of $~\sigma_e$ which is an adversary defined to interpret commitment formulae over $\mathfrak{M'_2}$, it follows that every infinite path $\pi \in \Pi^{\sigma_e}(s)$ satisfies that $\pi(1)=s'$ and $(\sigma_e,\pi(1))\models \mathscr{F}(\varphi)$. Thus, $(\sigma_e,s)\models \bigcirc\mathscr{F}(\varphi)$ for all $\pi \in \Pi^{\sigma_e}(s)$. As the path quantifier $A$ is not defined in PCTL, and we have $\mathbb{P}_{\geq1}$ instead, so we obtain $(\sigma_e,s)\models \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$.

\item $\Phi = C_{i \rightarrow j} \varphi$. We have $(\mathfrak{M_2},s)\models C_{i\rightarrow j}\varphi ~\text{iff}~ (\mathfrak{M_2},s') \models \varphi$ for every $s' \in S ~\textrm{such that}~ s\sim_{i \rightarrow j}s'$. Consequently, $(\mathfrak{M_2},s) \models C_{i\rightarrow j} \varphi ~\text{iff}~ (\mathfrak{M'_2},s) \models \mathscr{F}(C_{i\rightarrow j} \varphi)$. It follows that, $(\mathfrak{M'_2},s) \models  \mathscr{F}(C_{i\rightarrow j}\varphi)$ iff for every $s' \in \mathbb{S} ~\textrm{such that}~ (s,\beta^{ij},s') \in \textsf{P}_t$, we have $(\mathfrak{M'_2},s') \models  \mathscr{F}(\varphi)$. Now, based on the adversary $~\sigma_c$ which is defined to interpret commitment formulae over $\mathfrak{M'_2}$, every infinite path $\pi \in \Pi^{\sigma_c}(s)$ satisfies that $\pi(1)=s'$ and $(\sigma_c,\pi(1))\models \mathscr{F}(\varphi)$. Thus, $(\sigma_c,s)\models \bigcirc\mathscr{F}(\varphi)$ for all $\pi \in \Pi^{\sigma_c}(s)$. As the path quantifier $A$ is not defined in PCTL, and we have $\mathbb{P}_{\geq1}$ instead, so we obtain $(\sigma_c,s)\models  \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$.

\item $\Phi = Fu(C_{i \rightarrow j} \varphi)$. We have
$(\mathfrak{M_2},s)\models Fu(C_{i\rightarrow j}\varphi)$ iff there exists $s'\in S$ such that $s'\sim_{i \rightarrow j}s~ \text{and~}(\mathfrak{M_2},s')\models C_{i \rightarrow j}\varphi$.
Consequently, $(\mathfrak{M'_2},s)\models \mathscr{F}(Fu(C_{i\rightarrow j}\varphi))$ iff there exists $s' \in \mathbb{S}$ such that $(s,\gamma^{ij},s') \in \textsf{P}_t$ and
$(\mathfrak{M'_2},s') \models \mathscr{F}(C_{i \rightarrow j}\varphi)$. Now, w.r.t the adversary $\sigma_f$ which is defined to interpret fulfillment formulae over $\mathfrak{M'_2}$, we obtain at least one infinite path $\pi \in \Pi^{\sigma_f}(s)$ that satisfies $\pi(1)=s'$ and
$(\sigma_f,\pi(1))\models \mathscr{F}(C_{i \rightarrow j}\varphi)$. Since $E$ is equivalent to $\mathbb{P}_{>0}$ and $\mathscr{F}(C_{i \rightarrow j}\varphi)$ is equivalent to
$\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$, so we obtain $(\sigma_f,s)\models \mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$.

\end{itemize}

\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Implementation}\label{sec:Case-Study-cha4}
In this section, a case study is implemented using
PRISM \cite{Kwiatkowska2002} to verify knowledge, commitments,
and interactions between the two concepts in probabilistic MASs. We
apply the approach using the NetBill protocol
as in \cite{El-Menshawy2013a,Mallya2007,Yolum2002}. NetBill protocol
is developed for buying and selling encrypted software through the internet. We add probability to the original protocol so that the protocol will be
closer to the real world situation. There are many interactions
and communications between a buyer and a seller with NetBill protocol, and they are subject to several stochastic events, such as a buyer's request
for a quote could be successfully received by the seller in only
95\% of the cases. Another example is the buyer will satisfy his
delivery commitment with 98\% of probability. As we said before, those probabilities could be generally obtained after observing the system behavior for long time. We will introduce this modified probabilistic NetBill protocol next.

\subsection{NetBill Protocol}

The basic NetBill protocol involves one customer agent \emph{Cus} and one
merchant agent \emph{Mer} interacting to finish an online shopping
process. This protocol can also be applied to more than one
customer and one merchant. A customer \emph{Cus} requests a quote
from the merchant \emph{Mer} for an item to initialize the
protocol. We assume that 5\% of these requirements will fail to be
sent to the merchant due to internet connection issues. The
merchant replies to the successfully delivered request by
presenting a quote for the requested item. Having received the quote, we assume that 20\% of customers reject the offer and
end the protocol without any purchase. The other 80\% of customers
accept the offer. Accepting the offer means that the customer commits to send the payment to the merchant ($C_{Cus\rightarrow Mer}Pay$). We assume that only 90\% of payment commitments will be fulfilled
($Fu(C_{Cus\rightarrow Mer}Pay)$) and 10\% will be nullified. Both
customer and merchant agents will be aware if the customer
fulfills its commitments. When the merchant agent receives the
payment, then it will commit to deliver the items to the customer
($C_{Mer\rightarrow Cur}Deliver$). Suppose that 99\% of deliveries
are successful, which means that the merchant fulfills its
commitments ($Fu(C_{Mer\rightarrow Cur}Deliver)$). If the delivery fails,
the merchant violates its commitment and in this case the merchant should refund the customer. Figure \ref{NetBill} depicts the model of the modified NetBill protocol.

\begin{figure}[!h]
\begin{center}
\includegraphics[width=14cm,height=8cm]{chap4/img/Netbill.eps}
\caption{The Modified NetBill protocol} \label{NetBill}
\end{center}
\end{figure}

With the PRISM modeling language, we translate every agent into a
\emph{module} and the entire MAS is defined as a system with \emph{agent modules} which are all synchronized.

To formalize the protocol, the scenario is encoded using the
probabilistic interpreted systems $\mathfrak{M_2}$ introduced earlier in Definition \ref{def:models-pctlkc}. Two basic modules, \emph{module
Mer1} and \emph{module Cur1} are defined according to their
probabilistic transitions. They represent the customer agent
\emph{Cus1} and the merchant agent \emph{Mer1} respectively. Other
agents can just refer to these two basic agents and use
\emph{module renaming} function to duplicate a module.

\subsection{NetBill Protocol Properties}

\begin{itemize}
\item \texttt{Safety property:} When designing a system, we may set a confidence interval to allow some mistakes for properties because it seems impossible for human beings not to make any mistake in the real world. For example, ``with 99\% chance, the system will not fail" instead of ``the system will never fail". In our protocol, one bad situation is when the customer $Cus1$ sends the payment to the merchant $Mer1$ without the merchant being aware of that. The following property can avoid this bad situation:

$\varphi_1 = \mathbb{P}_{= 1}$ $[\neg (Fu(C_{Cus1\rightarrow Mer1}Pay)
\wedge  (\neg K_{Mer1}Pay))]$.

This event is critical without any uncertainty. Therefore, we
set the probability to 1.
A similar formula is when the customer fulfills its commitments,
but it turns out that it is not aware of:

$\varphi_2 = \mathbb{P}_{= 1}$ $[\neg (Fu(C_{Cus1\rightarrow Mer1}Pay) \wedge  (\neg K_{Cus1}Pay))]$.

With 1\% tolerance for missing delivery, we can define the third
\emph{safety  property}  in our logic as follows:

$\varphi_3 = \mathbb{P}_{\geq 0.99}$ $[\neg (Fu(C_{Cus1 \rightarrow Mer1} Pay) \wedge
\neg (C_{Mer1\rightarrow Cur1} Delivery))]$.

\item \texttt{Liveness property:} Contrast to \emph{safety property}, a \emph{liveness property } means ``a good thing will eventually happen". For example, when the merchant commits to deliver the goods to the customer, it will eventually deliver them. This property is expressed as follows:

$\varphi_4 = \mathbb{P}_{\geq 0.99}(C_{Mer1 \rightarrow Cus1} Deliver\Rightarrow$
$\mathbb{P}_{\ge 0} [\text{F } Fu(C_{Mer1 \rightarrow Cus1} Deliver)]) $.

\item \texttt{Reachability property:} One good example for the reachability property for the NetBill protocol is that the merchant will eventually commit towards the customer to deliver the required goods, which should be reached from the initial state. This property can be expressed as follows:

$\varphi_5 = \mathbb{P}_{\geq 0}$ [F $C_{Mer1 \rightarrow Cus1} Deliver$]

\item \texttt{Quantitative properties:} One important usage for probabilistic model checking is to compute the actual probability of some behaviors of the system. We can calculate the probability for eventually the customer $Cus1$ commits to send the payment to the merchant $Mer1$ and eventually the customer fulfills the commitment:

$\varphi_6 = \mathbb{P}_{=?}$ [F $C_{Cur1 \rightarrow Mer1} Pay$]

$\varphi_7 = \mathbb{P}_{=?}$ [F $Fu(C_{Cur1 \rightarrow Mer1} Pay)$]

\end{itemize}

\subsection{Experimental Results}\label{sec:Experimental-results-cha4}

We verified several probabilistic epistemic and commitment
properties as well as combinations made up from both properties
for the NetBill protocol. The presented experiments were
performed on a Toshiba Port\'{e}g\'{e} computer
with 2.00 GHz Intel Core2 Duo T6400 processor and 3GB memory under
64-bit Windows Vista Operating System.

\begin{table} %[!htbp]
\centering \caption{Experimental results for NetBill protocol with
PRISM} \label{tab:result-cha4}
\begin{tabular}{|c|l|l|c|c|}
    \hline
    \texttt{Number}& \multicolumn{2}{c|}{\texttt{Model}} & \multicolumn{2}{c|}{\texttt{Construction}}\\
    \cline{2-5}
    \texttt{of Agents}  & \texttt{\#States} & \ \ \ \texttt{\#Transitions} & \texttt{Iterations} & \texttt{Time (sec)} \\
    \cline{1-5}
    \hline
    \hline
    2 &  19 & \ \ \ 39 & $7$ & $0.001$\\
    \hline
    $3$ &  $108$ & \ \ \ $432$ & $10$ & $0.008$\\
    \hline
    $4$ &  $979$ & \ \ \ $3.2*10^3$ & $13$ & $0.011$\\
    \hline
    $5$ &   $6.1*10^3$ & \ \ \ $24*10^3$ & $16$ & $0.024$\\
    \hline
    6 &  $38*10^3$ & \ \ \ $171*10^3$ & 19 & 0.028\\
    \hline
    7 &   $230*10^3$ & \ \ \ $1.1*10^6$ & 22 & 0.035\\
    \hline
    8 &   $1.4*10^6$ & \ \ \ $7.8*10^6$ & 25 & 0.049\\
    \hline
    9 &   $8.4*10^6$ & \ \ \ $52*10^6$ & 28 & 0.071\\
    \hline
    10 &  $50*10^6$ & \ \ \ $343*10^6$    & 31 & 0.097\\
    \hline
    15 & $392*10^9$ & \ \ \ $3.8*10^{12}$ & 46 & 0.498\\
    \hline
\end{tabular}
\end{table}

We have conducted 10 experiments for the protocol using up to 15
agents. The results are in Table \ref{tab:result-cha4}. Model
statistics data (number of states and number of transitions) and
model construction information (iteration and construction time)
are reported. The model statistics data reflect the state space,
while the construction information indicates the time for
converting the PRISM model into a symbolic model and iterations required to find the reachable states. We have noticed that the state space increases
exponentially as the number of agents increases. However, the time
needed for constructing the model increases polynomially as more
agents are added as shown in Figure \ref{Building the model-cha4}.

\begin{figure}%[!h]
\begin{center}
\includegraphics[width=10cm,height=6cm]{chap4/img/time-for-building-model.eps}
\caption{Model construction time for the NetBill protocol} \label{Building the model-cha4}
\end{center}
\end{figure}

We verified properties expressing some requirements of the NetBill
protocol that involve probabilistic knowledge and commitments. We
checked \emph{Safety, liveness,} and \emph{Reachability}
properties as discussed above. Table \ref{formulae-PRISM-results-cha4} shows the results of model checking the above desirable properties for the
probabilistic \emph{NetBill protocol} for a system that includes
one customer and one merchant.

\begin{table}%[H]
\centering \caption{Verifying some PCTL$^{kc}$ properties for the NetBill protocol in case of two agents} \label{formulae-PRISM-results-cha4}
\begin{tabular}{|c|c|c|}
\hline
\texttt{Formulae}    & \texttt{Results} & \texttt{Time for MC (sec)} \\
\hline\hline
$\varphi_1$                &True           &  0.001     \\
\hline
$\varphi_2$               &True           &  0.001     \\
\hline
$\varphi_3$                &True           & 0.008    \\
\hline
$\varphi_4$                &True          & 0.001   \\
\hline
$\varphi_5$                &True           &  0.008  \\
\hline
$\varphi_6$                &0.80           &  0.002  \\
\hline
$\varphi_7$                &0.72           &  0.001  \\
\hline

\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Discussion} \label{sec:discussion-cha4}

As we have seen in this chapter, a probabilistic logic for addressing the interaction between knowledge and social commitments in MASs was introduced. The described approach represents the first attempt in the literature to reason about and verify the interaction between the two concepts in the presence of uncertainty. However, from a consistency point of view, the logic we proposed seems to be inconsistent and suffers from some paradoxes like those identified in \cite{Al-Saqqar2014a}. The problem is that, one of the underlying logics of PCTL$^{kc}$, which is PCTLC \cite{Sultan2013}, is built using the social accessibility relation given in \cite{Bentahar2012,El-Menshawy2013a} which, in fact, over specifies and over constrains the concept of illocutionary communication.

In the next chapter, we see how we will overcome the aforementioned problem by extending a consisting logic of knowledge and commitment called CTLKC$^+$ \cite{Al-Saqqar2014a} by a probabilistic operator so that capturing and reasoning about the interaction between the concepts of knowledge and social commitments by means of a consistence probabilistic logic becomes possible. Moreover, the logic we introduce in Chapter \ref{cha:PCTLKC+} incorporates the concepts of group social commitments and group knowledge to the framework.

\section{Related Work} \label{sec:related-work-cha4}

The work presented in this chapter can be related to three perspectives
in the literature: probabilistic knowledge, probabilistic commitments,
and the interaction between the two aspects. In this section,
we review the relevant work with respect to probabilistic knowledge
and the interaction between probabilistic knowledge and probabilistic
commitments. However, for the relevant work on probabilistic
commitments, it has been discussed in Chapter \ref{cha:PCTLC}, Section \ref{sec:related-work-cha3}.

\subsection{Probabilistic Knowledge in MASs }

Delgado and Benevides in \cite{Delgado2009} defined a
probabilistic logic called K-PCTL which extends PCTL with an
epistemic operator for the knowledge.
For modeling their target systems, the authors proposed an
approach that represents each agent in the system as a DTMC with
synchronization actions. In their DTMC model, each state either
has a synchronized action with probability 1 or regular
probabilistic transitions. Having two different actions in a
single DTMC forced them to transform it into an MDP model. From
the semantics point of view, K-PCTL formulae are interpreted over
MDP models which are augmented with accessibility relations, so
that probabilities over paths can be defined. However, the
uncertainty of the knowledge cannot be measured as the
accessibility relations are not probabilistic. Our approach
differs from this one in four main points. First, our logic
adds two modalities on top of PCTL; one for the knowledge,
and one for the commitments and their fulfilments. Therefore, dimension of system's aspects that our logic can handle is larger than that of K-PCTL making it more expressive. Second, our logic permits the
probabilistic operator to precede each of the knowledge modality
and the social modality so that we can quantitatively reason about
the two aspects which again increases its expressive power. Third,
we model the target systems using probabilistic interpreted
systems. Forth, we propose a concrete model checking technique in
which we transform the problem of model checking our logic to the
problem of model checking an existing logic allowing us to re-use
the PRISM tool instead of just suggesting to extend it.

In \cite{Huang2011}, Huang and his colleagues extended the MCK
model checker \cite{Gammie2004} with subjective probability
relative to agent knowledge using interpreted partially observed
discrete-time Markov chain (PO-DTMC). PO-DTMC is based on partial
observations with assumption on synchronous with perfect recall.
To specify properties of probabilistic interpreted systems, the
authors use a logic that combines temporal and knowledge
modalities with a probabilistic operator. In their approach, the
set of accessible states is defined as states of a special agent,
called the environment, while the remaining agents observe the
environment and perform actions based on their observations. Then,
probabilistic knowledge is expressed by a rational linear
combination of every agents' probabilities in the system: every
agent has its own probability for each accessible state, which is
supposed to be known. Unlike this work, in our approach we do not
assume that accessibility transitions are probabilistic because
this information is not always accessible to agents and sometimes
hard to quantify. Instead, we compute the probabilistic knowledge
based on the number of accessible states as they are equally
accessible. Moreover, by re-using the exiting PRISM model checker,
we do not add a computational cost that is associated to extending
the existing version of it.

Wan et al. \cite{Wan2013} has also addressed the verification of
epistemic properties in agent environments  against the background
of participating parties. They propose PCTLK, a probabilistic,
epistemic,  branching-time logic which extends CTL with
probabilistic and epistemic modalities. To verify the proposed
logic, the authors introduced a reduction-based model checking
technique to translate the problem of model checking PCTLK into
the problem of model checking PCTL. Their reduction procedure
involves two processes. First, they transform the probabilistic
interpreted systems into an MDP which is transformed further to a
DTMC. Second, they translate each PCTLK formula into a
corresponding PCTL formula. To model check a PCTLK forumla, they
check its transformed PCTL formula over the DTMC model. They
demonstrated the applicability of their proposed verification
technique by applying it on a well known case study and
implementing it using the PRISM model checker. Our work is similar
to this work, except that we have a social modality in our
proposed logic for the commitments and their fulfilments which
makes it more expressive than PCTLK.

\subsection{The Interaction between Knowledge and Social Commitments}

Little work has been done towards the problem of capturing and verifying the interactions between knowledge and social commitments in MASs.

In \cite{Schmidt2004}, Schmidt and his colleagues investigated the
problem of formalizing the interaction between knowledge and
commitments within agent dynamic logic. Apparently, the commitment
adopted in this work is not a social commitment but rather an
internal commitment as the one presented by Castelfranchi in
\cite{Castelfranchi1995}. The term ``internal commitment'' refers to a commitment of an agent to itself \cite{Singh2008}. Using their proposed Agent Dynamic Logic (ADL), the authors were able to express some combinations between knowledge and commitments such as $Comm_i~(\alpha)\to K_i~Comm_i~(\alpha)$ which expresses that agent $i$ knows ($K_i$) about his
internal commitment ($Comm_i$) to perform the action $\alpha$.
However, from a communication perspective, the internal commitment
is neither communicative nor public because it is not created as
an agreement between two agents so that an agent can commit
towards the other to bring about a certain property. In contrast,
our work focuses primary on the notion of ``social commitment"
\cite{Singh2000} which has been used as a means of communication
between interacting agents in MASs. Unlike internal commitments,
which are private and concern a particular agent, social
commitments are public and observable engagements from one agent
to another agent or a group of agents to bring about something.  Furthermore, unlike \cite{Schmidt2004}, we study such an interaction ---between the two concepts--- in systems exhibiting probabilistic behaviors.

Al-Saqqar et al. \cite{Al-Saqqar2014a} have made the first attempt
towards studying the relationship between knowledge and
communicative social commitments from a logical perspective. In
particular, they combined a logic of knowledge (called CTLK
\cite{Lomuscio2007}) and a logic of commitments (called CTLC
\cite{Bentahar2012}) in a single tool called CTLKC. Having
analyzed some postulates with different combinations between the
two concepts expressed in CTLKC, the authors identified a set of
paradoxes that makes their combined logic inconsistent. To
overcome this problem, they mitigated the over-specification
problem that arises in the social accessibility relation given in
\cite{Bentahar2012,El-Menshawy2013a}. Intuitively and broadly
speaking, a social accessibility relation for two agents $i$ and
$j$ does exist between two global states $s_1$ and $s_2$ in the
system, if there is a communication channel between the local
states of $i$ and $j$ in the global states $s_1$ and $s_2$
respectively. Based on a new social accessibility relation, they
presented a new semantics for the commitment ($C_{i\rightarrow j}
\varphi$) and fulfilment ($Fu (C _{i\rightarrow j} \varphi)$)
operators, where $C_{i\rightarrow j} \varphi$ means that agent $i$
commits towards agent $j$ to bring about $\varphi$, and $Fu (C
_{i\rightarrow j} \varphi)$ expresses the fulfillment of such a
commitment. These changes have been integrated into a new
consistent logic named CTLKC$^+$. Having defined the new logic,
the authors have been successfully able to reason about various
combinations between knowledge $K_i \varphi$, which means that
agent $i$ knows $\varphi$, and social commitments as follows:

\begin{itemize}
\item $C_{i\rightarrow j} \varphi \Rightarrow K_i (C_{i\rightarrow
j} \varphi) $ where $i \neq j$.
\item $Fu (C _{i\rightarrow j} \varphi) \Rightarrow K _i \varphi$ where $i \neq j$.
\item $Fu (C _{i\rightarrow j} \varphi) \Rightarrow K_j \varphi$ where $i \neq j$.

\end{itemize}

Then, the authors introduced a reduction model checking technique
in which they transformed the problem of model checking their new
logic (CTLKC$^+$) into the problem of model checking an existing
logic called GCTL$^*$ \cite{Bhat2001}, and computed the complexity of the reduction technique. They used the automata-based model checker CWB-NC as the verification tool.

The verification of CTLKC$^+$ was further investigated in \cite{Al-Saqqar2014b}. The authors used a symbolic model checking technique based on reducing the problem of model checking CTLKC$^+$ into that of ARCTL. Then, they used the extended NuSMV to verify some given properties written in CTLKC$^+$. Their approach was carried out automatically using a JAVA transformation tool. This allowed them to overcome the scalability problem of automata-based model modeling checking techniques, which is a highly considerable problem in model checking real applications of multi-agent systems. The complexity analysis of the proposed reduction-based technique was also provided.

Unlike this work that tends to assume ideal behavior for MASs so it limits its application to reliable environments, ours considers the unreliable behavior of MASs. Therefore, we add a probabilistic modality to the logic to be able to reason about some desirable properties in the presence of uncertainty. Our proposal subsumes the one in \cite{Al-Saqqar2014a} because probability values range from 0 to 1 (when probability is equal to 1, the system becomes certain). Therefore, our framework outperforms this proposal in the sense that not only qualitative reasoning about the interaction between knowledge and commitments is achievable but also quantitative reasoning becomes possible.

\subsection{Comparison}

We compare our framework to the existing proposals by taking into
consideration five criteria: Knowledge, Commitments, Uncertainty,
Formalization, and Verification. Knowledge property shows whether
the approach addresses epistemic properties of the systems or not.
Commitments property indicates whether it addresses the social
commitments or not. Uncertainty reflects target systems whose
behavior is probabilistic. Formalization indicates the use of
formal logics, or formal methods in general. Finally, Verification
confirms the presentation of a formal verification technique to
verify the proposed approach. Table \ref{table:comparison} shows a
summary about the comparison between our framework and the
existing approaches based on the criteria described above.
We observe that our framework outperforms the related approaches as
it satisfies all the listed criteria.

\begin{table}
\centering \caption{Comparison between PCTL$^{kc}$ and the related work } \label{table:comparison}
\begin{tabular}{cccccc}
\hline
\texttt{Approach}       &\texttt{Knowledge} & \texttt{Commitment} & \texttt{Uncertainty}   & \texttt{Formal} & \texttt{Verification}\\
\hline
\cite{Witwicki2007,Witwicki2009}    &         &$\surd$   &$\surd$    &         &    \\
\cite{Huang2011}      &          &$\surd$   &$\surd$    &$\surd$  &$\surd$    \\
\cite{Delgado2009}     &$\surd$   &          &$\surd$    &$\surd$  &    \\
\cite{Wan2013}         &$\surd$   &          &$\surd$    &$\surd$  &$\surd$    \\
\cite{Al-Saqqar2014a}   &$\surd$   &$\surd$   &           &$\surd$  &$\surd$    \\
Our approach         &$\surd$   &$\surd$   &$\surd$    &$\surd$  &$\surd$    \\
\hline

\end{tabular}
\end{table}

To summarize, the advancement of our work over existing work lies in the expressiveness power of the proposed logic which allows autonomous agents in MASs to represent and verify the interaction between knowledge and social commitments in the face of uncertainty. Moreover, the new probabilistic interpreted systems introduced in this chapter helps MASs developers to have rich modeling with respect to knowledge and social commitments. That is, not only modeling knowledge and social commitments independently in the presence of uncertainty is possible, but also modeling the interaction between them has become possible by making use of our proposed probabilistic model.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Summary}\label{sec:conclusion-cha4}

In this chapter, we presented a novel technique for specifying and evaluating the interaction between knowledge and social commitments in stochastic MASs. The proposed technique allows us, for the first time in the literature, to perform epistemic reasoning on social commitments in probabilistic MASs. This helps ensure agents' awareness about their commitments and the fulfillments of these commitments. In particular, we first developed a new version of interpreted systems that captures the probabilistic behavior of knowledge and commitments and accounts for the communication between interacting parties. Second, we defined a new logical framework that merges concepts of probabilistic knowledge and probabilistic commitments in a single logic called PCTL$^{kc}$, so that complex formulae including both modalities
can be expressed. Third, we introduced a new model checking
technique to formally verify the compliance of MASs against some
given properties expressed using the new logic. The proposed model
checking procedure is reduction-based, in which the problem of
model checking PCTL$^{kc}$ is transformed (by the use of some rules) into the problem of model checking an existing logic, namely PCTL. The key advantage of such a reduction is gaining the privilege to re-use a well
known model checker such as PRISM. The soundness of the proposed
reduction technique was provided. Moreover, we demonstrated the
effectiveness of the proposed framework by applying it to the
NetBill protocol, a concrete case study from e-business domain.
The results have initially confirmed the expressive
capabilities of PCTL$^{kc}$ in handling the
interaction between knowledge and social commitments in
probabilistic settings. Moreover, the scalability of the proposed model
checking technique was evaluated and models having up to $4
\times 10^{11}$ states can be effectively verified.

In the next chapter, we refine and extend the approach presented for the interaction between individual knowledge and commitments to accommodate  group knowledge and group commitments as well.

### 2015-04-05 thesis/thesis/cover.tex
added thesis

%\cutitle{A Logic-based Framework for Addressing Probabilistic Social Commitments in Multi-Agent Systems}

%\cutitle{Probabilistic Social Commitments in Multi-Agent Systems: Representation and Model Checking}

%\cutitle{On the Probabilistic Social Commitments in Multi-Agent Systems}
%\cutitle{Probabilistic Social Commitments: Representation and Verification}

\cutitle{Modeling and Verifying Probabilistic Social Commitments in Multi-Agent Systems}

\cudept{Computer Science and Software Engineering}   % your dept.
\cudegree{Doctor of Philosophy}           % your expected degree <-,
\cudegreeshort{Ph.~D.}
\culname{Sultan}                    % your family name
\cufname{Khalid Ibrahim}                    % your given name

\cusupervisor{Dr. Jamal Bentahar}        % your Big-Boss complete name
%\cucosupervisor{Dr. }   % your small big-boss name
\cuexaminerA{Dr. Olga Ormandjieva}
\cuexaminerB{Dr. Rachida Dssouli}
\cuexaminerC{Dr. Abdessamad Ben Hamza}
%\cuexaminerA{}
\cuextexaminer{Dr. Elhadi Shakshuki}     % Another of the previous kind

\cuchair{Dr. G\"osta Grahne}           % the boss of your boss

\cumonth{January}                % the month you expected to graduate
\cuyear{2015}                 % and the year.
%\cudedication{\ \\ \\ \\ \\ \\ \\ \\ \\
%\begin{center}{\bf{To My Parents,\\ My Wife and daughter,\\ and My Brothers and Sisters.}} \\
%\end{center}}
\cuabstract{\input{abstract}}
%%
%
%
%
\cuthanks{\input{ack}}

\cumaketitlepage       % title page, not numbered
\cumakesignaturepage   % sign. page, not numbered
\cumakeabstract
%\cumakededication      % To Mom and Dad
\cumakethanks          % Thanks Boss!
\cutocdeep{4}          % how deep you want to go in the toc: 0: reset to 1
\cumaketableofcontents % Gues\cumakelistoffigures   % id.
\cumakelistoftables    % id.
\cumakelistoffigures
\cumakelistofsymbols   % a gook work should have a list of symbols.
\custartbody    % this initialize double-spacing, page-numbering ...

%%% Local Variables:
%%% TeX-master: "thesis"
%%% End:

### 2015-04-09 thesis/thesis/cover.tex
initial changes

@@
 
-\cutitle{Modeling and Verifying Probabilistic Social Commitments in Multi-Agent Systems}
+\cutitle{Efficient Community Formation for Web Services}
 
@@
 \cudegreeshort{Ph.~D.}
-\culname{Sultan}                    % your family name
-\cufname{Khalid Ibrahim}                    % your given name
+\culname{Khosrowshahi-Asl}                    % your family name
+\cufname{Ehsan}                    % your given name
 
 \cusupervisor{Dr. Jamal Bentahar}        % your Big-Boss complete name
-%\cucosupervisor{Dr. }   % your small big-boss name
-\cuexaminerA{Dr. Olga Ormandjieva}
-\cuexaminerB{Dr. Rachida Dssouli}
-\cuexaminerC{Dr. Abdessamad Ben Hamza}
+\cucosupervisor{Dr. Hadi Otrok}   % your small big-boss name
+\cuexaminerA{Dr. O}
+\cuexaminerB{Dr. R}
+\cuexaminerC{Dr. A}
 %\cuexaminerA{}
-\cuextexaminer{Dr. Elhadi Shakshuki}     % Another of the previous kind
+\cuextexaminer{Dr. E}     % Another of the previous kind
 
@@
 
-\cumonth{January}                % the month you expected to graduate
+\cumonth{July}                % the month you expected to graduate
 \cuyear{2015}                 % and the year.

### 2015-04-09 thesis/thesis/abstract.tex
changes

@@
 
-Interaction among autonomous agents in Multi-Agent Systems (MASs) is the key aspect for solving complex problems that an individual agent cannot handle alone.
-In this context, social approaches, as opposed to the mental approaches, have recently received a considerable attention in the area of agent communication.
-They exploit observable social commitments to develop a verifiable formal semantics by which communication protocols can be specified.
-However, existing approaches for defining social commitments tend to assume an absolute guarantee of correctness so that systems run in a certain manner.
-That is, social commitments have always been modeled with the assumption of certainty.
-Moreover, the widespread use of MASs increases the interest to explore the interactions between different aspects of the participating agents such as the interaction between agents' knowledge and social commitments in the presence of uncertainty.
-This results in having a gap, in the literature of agent communication, on modeling and verifying social commitments in probabilistic settings.
+ abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract.
 
-In this thesis, we aim to address the above-mentioned problems by presenting a practical formal framework that is capable of handling the problem of uncertainty in social commitments.
-First, we develop an approach for representing, reasoning about, and verifying probabilistic social commitments in MASs.
-This includes defining a new logic called the probabilistic logic of commitments (PCTLC), and a reduction-based model checking procedure for verifying the proposed logic.
-In the reduction technique, the problem of model checking PCTLC is transformed into the problem of model checking PCTL so that the use of the PRISM (Probabilistic Symbolic Model Checker) is made possible.
-Formulae of PCTLC are interpreted over an extended version of the probabilistic interpreted systems formalism.
-Second, we extend the work we proposed for probabilistic social commitments to be able to capture and verify the interactions between knowledge and commitments.
-Properties representing the interactions between the two aspects are expressed in a new developed logic called the probabilistic logic of knowledge and commitment (PCTL$^{kc}$).
-Third, we develop an adequate semantics for the group social commitments, for the first time in the literature, and integrate it into the framework.
-We then introduce an improved version of PCTL$^{kc}$ and extend it with operators for the group knowledge and group social commitments.
-The new refined logic is called PCTL$^{\textrm{kc+}}$.
-In each of the latter stages, we respectively develop a new version of the probabilistic interpreted systems over which the presented logic is interpreted, and introduce a new reduction-based verification technique to verify the proposed logic.
-To evaluate our proposed work, we implement the proposed verification techniques on top of the PRISM model checker and apply them on several case studies.
-The results demonstrate the usefulness and effectiveness of our proposed work.
+ abstract abstract abstract abstract abstract abstract  abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract.
 %The experimental results demonstrate the efficiency and scalability of the proposed reduction techniques and show that our work is effective for addressing probabilistic social commitment in MASs.

### 2015-04-14 thesis/thesis/abstract.tex
changes

@@
 
- abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract.
+ \textbf{This is not real abstract} In the last few years, communities of services have been studied in a certain numbers of proposals as virtual pockets of similar expertise.
+The motivation is to provide these services with high chance of discovery through better visibility, and to enhance their capabilities when it comes to provide requested functionalities.
+There are a number of proposed mechanisms and models on aggregating web services and making them cooperate within their communities.
+However, forming optimal and stable communities as coalitions to maximize individual and group efficiency and income for all the involved parties has not been addressed yet.
+Also, in the proposed frameworks of these communities, a common assumption is that residing services, which are supposed to be autonomous and intelligent, are competing over received requests.
+However, those services can also exhibit cooperative behaviors, for instance in terms of substituting each other.
+Deciding to compete or cooperate inside communities is a problem yet to be investigated.
 
- abstract abstract abstract abstract abstract abstract  abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract.
+In this thesis, we identify the problem of defining efficient algorithms for coalition formation mechanisms within communities and propose some results using cooperative game-theoretic techniques.
+We propose a mechanism for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities.
+The ultimate objective is to develop a mechanism for web services to form stable groups allowing them to maximize their efficiency and generate near-optimal (welfare-maximizing) communities.
+The theoretical and extensive simulation results show that our algorithms provide web services and community owners, in real-world like environments, with applicable and near-optimal decision making mechanisms.
+We also propose a decision mechanism based on learning methods for services within communities to effectively choose the tasks to perform based on their capabilities and the competition between other community members.
 %The experimental results demonstrate the efficiency and scalability of the proposed reduction techniques and show that our work is effective for addressing probabilistic social commitment in MASs.

### 2015-04-22 thesis/thesis/chap1/chap1.tex
changes

@@
 
-\chapter{Introduction}\label{cha:introduction}
+\chapter{Introduction}\label{sec:intro}
+[Proposal] In this chapter, we introduce the context of this research, which
+is about communities of web services abstracted as autonomous
+agents. Those agent-based web services use cooperative game
+theoretic solution concepts for decision making. We discuss the
+motivations of this work and briefly review the literature to
+identify the problems we aim to solve in this thesis. Moreover, we
+discuss our objectives and preliminary contributions.
 
-In this chapter, we introduce the context of our research, which falls in the area of agent communication within Multi-Agent Systems (MASs).
-More precisely, it is concerned with modeling and verifying social commitments --as a means of communication among agents-- in the presence of probabilistic behavior.
-We also identify the motivations, problem statement, and research questions that we address in this thesis.
-Then, we list our objectives and discuss our methodology.
-Finally, we conclude this chapter by providing the thesis outline.
+\section{Context of Research}\label{sec:motivation}
 
-\section{Context of Research} \label{sec:context-chap1}
+Over the past years, online services have become part of many
+scalable business applications. The increasing reliance on
+web-based applications has significantly influenced the way web
+services are engineered. Web services provide a set of stateless
+software functions accessible at a network address over the web.
+The recent developments are shifting web services from passive and
+individual components to autonomous and group-based components
+where interaction, composition, and cooperation are the key
+challenges \cite{ICWS2011-1,SCC2011-1}. The main objective is to
+achieve a seamless integration of business processes, applications
+and web services. Delivering high quality services considering the
+dynamic and unpredictable nature of the Internet is still a very
+critical and challenging issue.
 
-\subsection{Multi-Agent Systems (MASs)}
-Nowadays, the use of distributed environments to solve complex
-real world problems using entities called agents is on rise
-\cite{Biswas08,Park2005}.
-Agents are active, social, and adaptable computer systems situated in some dynamic environment and capable of autonomous actions \cite{Wooldridge2009}.
-%to achieve their objectives \cite{Wooldridge2009}.
-%To attain their objectives, agents need abilities to cooperate, coordinate, and negotiate.
-Ideally, an agent has to be \cite{Wooldridge1995}:
+Typically, web services are business applications deployed as
+autonomous and interoperable agents \cite{Alescio}. In fact, the
+W3C consortium defines a web service as ``an abstract notion that
+must be implemented by a concrete agent''. However, the web is
+stocked with agent-based services that offer similar business
+functionalities, which leads to service consumers having
+difficulties in choosing the most appropriate agents to interact
+with.
 
+The need for highly available and responsive services has called
+for grouping and collaborative mechanisms of loosely-coupled web
+services, particularly in business settings. The idea of grouping
+web services within communities and the way those communities are
+engineered so that web services can better collaborate have been
+proposed and investigated in
+\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
+Communities are virtual groups of web services having similar
+functionalities \cite{Zeng:2003:QDW:775152.775211,
+Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7},
+but probably different non-functional quality attributes, which
+form the QoS parameters. When communities are used, users send
+their requests to the masters of those communities, which are
+responsible of managing the communities, forwarding the requests
+to the suitable member web services and checking the credentials
+of those members. Communities aim to provide higher service
+availability and performance than what individual web services can
+provide. The high availability of services and the community
+resilience to failure are guaranteed since web services can
+cooperate and replace each other within the same community and
+since there is no single point of failure in the communities
+architecture.
+
+\section{Motivating Scenario}\label{sec:motexample}
+
+In this section, we present a scenario and demonstrate why there
+is need for communities of services. We first propose an example
+of a real world scenario, focusing on user experience. There are a
+plethora of options available to people in today's society,
+including weather forecasting, ticketing services, map services,
+local places guides and so on. Most mobile or web applications
+cannot independently satisfy users requests and should rely on
+different online services. The high competition within the
+services industry requires applications to use reliable and high
+quality online service providers.
+
+If the user were to check a web site or run an application on her
+mobile device upon having downtime, or having high response delay
+or encountering any non-satisfying quality metric, she will
+instantly remove the application, which is a huge business concern
+for application providers. For example, if a user installs a
+ticketing application on her mobile device and the application is
+not using high quality service providers, the user would instantly
+uninstall the application, which has an extremely negative impact
+on the
+visibility of the application. %Let us say you search "Montreal
+%Weather" on a search engine and you click on a web site which is
+%slow because it is using a bad weather web service as source of
+%its raw data, the user will leave the web site and try another
+%link from search results, which has a bad Search Engine
+%Optimization (SEO) effect for the web site, and search engines
+%would not show that web site on search results anymore, which is a
+%business and revenue loss for the application.
+Thus, end user satisfaction is the main goal for competitive
+online providers. Communities of web service, by providing
+services with higher quality, higher uptime and reliability for
+end users, aim to reach this goal. To this end, community
+management decisions should capitalize on important QoS parameters
+while forming the community and during membership management.
+
+High demand on online services has created a massive business
+competition. For example, nowadays users are provided with
+multiple choices of web services offering local places information
+such as coffees, venues, and shops nearby a geographic position.
+It is hard for new web services to find their customers and be
+visible for end users amongst hundreds or thousands of other
+available services, even if they provide a high quality of
+service. Hence, the concept of communities of web services
+provides them with the chance of joining a platform with an
+established market share and reputation. However, it is crucial
+for a community manager to consider many factors when inviting or
+accepting new members. For example, if the market share is not big
+enough, bringing new web services can cause revenue drop for the
+already residing members. This may encourage other web services to
+collude, leave, or join other communities, hurting the community
+stability. This is an important issue which has not been addressed
+previously in the relevant literature. On the other hand, if
+communities bound the number of web services to ensure higher
+revenue, availability and response time could be negatively
+affected if some members encounter problems. This is because
+alternative web services for substitution will be limited.  This
+has also not been efficiently addressed in the related work.
+Consequently, community formation algorithms satisfying some
+desirable properties such as community stability and overall
+revenue are yet to be defined considering end users, community
+managers and service providers.
+
+\section{Motivation and Research Questions}\label{sec:researchquestions}
+
+Web service communities are dynamic by design
+\cite{DBLP:journals/ijebr/MaamarSTBB09}. In these communities, web
+services are modeled as intelligent autonomous agents, where they
+can adopt a strategy maximizing their payoff at any time. A web
+service can ask joining a community and has the right to leave it.
+Community managers can invite or ask a web service to leave in
+order to maximize the community profit. Users can simply stop
+sending requests to a web service which is not providing
+satisfactory services. Thus its important to consider all the
+parties involved in the decision making process about the
+community management. Most of the recent work on communities of
+services are either user-centric and focus on user satisfaction
+\cite{Chun02user-centricperformance} or system-centric and focus
+on the whole system throughput, performance and utilization. There
+are many contributions in distributed, grid, cluster and cloud
+services which are system-centric. However, in real world
+environments and applications, both users and service providers
+are self-interested agents, aiming to maximize their own profit.
+In those environments, both parties (users and services) will
+collaborate as long as they are getting more benefits and payoff.
+Our initial research question is: \emph{How can we model the
+community of agent-based services in order to maximize the utility
+of involved users, web services and community organizers?}
+
+In order to address this problem, recently
+\cite{DBLP:conf/IEEEscc/LimTMB12,
+DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
+mechanisms to help users and services maximize their gain. A
+two-player non-cooperative game between web services and community
+master was introduced in
+\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In
+\cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
+for selecting web services has been proposed. In this approach,
+the authors proposed a web service selection process that the
+community masters can use. The approach considers the efficiency
+of all the three involved parties, namely users, web services and
+communities. The issue with these solution concepts is that they
+consider community as a whole and model it as one entity in their
+formulations. A community master decides on behalf of all the
+members using an aggregated function of parameters. This can hurt
+the overall revenue for some individual web services, or even a
+subset of web services. Those services can collude and form their
+own community and gain more, instead of having to adjust and share
+their resources with other members. Another important issue which
+needs to be considered is the community stability. In community of
+web services, the members and community organizers collaborate to
+perform tasks. Having jointly completed a task and generated
+revenue, they need to agree on some reasonable method of dividing
+profits (or tasks) among themselves. This is a key issue for the
+group stability still to be investigated. If the revenue sharing
+mechanism is not fair enough for any subset of web services
+working in the community, these agents, as profit maximizing
+entities, would just deviate and make their own group. So an
+important research question that we would like to address is:
+\emph{How can we model fair and stable communities as coalitions
+of agent-based web services?}
+
+%The consideration of those inputs is a significant
+%issue as existing web services can lose utility or payoff because
+%of the new member, which can results in an unhealthy and unstable
+%group. The problem comes from the fact that the existing members
+%should collaborate with the new web services, so probably their
+%performance as a group can suffer. Existing members may even
+%deviate and try to join other communities if they are unsatisfied.
+%Those considerations of forming stable and efficient coalitions
+%are the main contributions of our paper.
+
+%However, a high
+%performing web service could deviate anytime it finds itself
+%unsatisfied within the community instead of adjusting its service
+%parameters.
+
+In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
+autonomous web services based on coalitional game theory has been
+introduced. The authors have proposed an algorithm to reach
+individually stable coalition partition for web services in order
+to maximize their efficiency. The communities choose new web
+services on the promise that it would benefit the community
+without decreasing any other web service's income. In their model,
+the worth of community is evaluated with high emphasis on the
+availability metric and considering price and cost values only.
+The community structure is based on a coordination chain, where a
+web service is assigned as a \emph{primary} web service and the
+community task distribution method will initially invoke the
+primary web service. Only if the primary web service is
+unavailable, the next backup web services in the ordered
+coordination chain will be invoked. However, in cooperative
+models, it is preferred to have a real and active cooperative
+activity engaging all agents to perform the tasks more
+efficiently. Thus, the final research question we would like to
+work on is: \emph{How can we model and analyze the cooperation
+among the community members in realistic, applicable and practical
+settings?}
+
+% ooooooold
+%\indent When monitoring a dialogue between two or more agents, there are many question that should be answered. In this thesis, we are interested in answering the following questions:
+%\begin{itemize}
+%\item How much are agents certain about selecting a move at each dialogue step?
+%\item How much are agents certain about their dialogues?
+%\item How good are agents in the real dialogue (i.e. the effective dialogue)?
+%\item How far are agents from the right dialogue (i.e. the best dialogue given the knowledge bases of the participants)?
+%\end{itemize}
+%Answering these questions is undoubtedly complex. Therefore, we do not expect a comprehensive answer to all these questions.
+
+\section{Research Objectives and Contributions}\label{sec:motexample}
+
+In this research work, our first objective is to propose a
+cooperative model as game for the aggregation of web services
+within communities. The solution concepts of our cooperative game
+seeks to find efficient ways of forming coalitions (teams) of web
+services so that they can maximize their gain and payoff, and
+distribute the gain in a fair way among all the member services.
+Achieving Fairness when the gain is distributed among the
+community members is the main factor to keep the coalition stable
+as no web service will expect to gain better by deviating from the
+community. In other words, the coalition is made efficient if all
+the members are satisfied. We first propose a representation
+function for communities of web services based on their QoS
+attributes. By using this function, we can evaluate the $worth$ of
+each community of web services. When facing new membership
+requests, a typical community master checks whether the new
+coalition having the old and new set of web services will keep the
+community stable or not. The community master will reject the
+membership requests if it finds out that the new coalition would
+be unstable, preventing $any$ subset of web services from gaining
+significantly more by deviating from the community and joining
+other communities or forming new ones. The computation of
+solutions for cooperative games is combinatorial in nature and
+proven to be NP-complete \cite{Algorithmic}, making this
+computation impractical in real world applications. However, using
+the concepts of coalition stability, the second objective is to
+investigate approximation algorithms running in polynomial time
+providing web services and community masters with applicable and
+near-optimal decision making mechanisms.
+
+\indent To summarize, the main problem we aim to tackle in this
+thesis is the formation of stable and efficient coalitions
+maximizing web services and community revenue. The main objectives
+are:
 \begin{itemize}
-\item Reactive: able to respond to changes in its environment.
-\item Pro-active: capable to behave with respect to its goals (goal-directed behavior).
-\item Social: able to interact and communicate with others.
-\item Autonomous: able to operate without direct intervention of others.
+\item To propose a cooperative model and analyze its solution
+concepts in order to address the problem of optimizing coalition
+formation for a stable community.
+
+\item To reduce the complexity of computing the solution concepts
+of the cooperative model tailored to the problem of communities of
+agent-based web services in order to make these solutions
+applicable in real world scenarios.
+
+\item To analyze the effect of different membership and taxation
+models that the master can apply to the members on the stability
+of the community.
+
+\item To investigate the impact of learning on individual and
+group decision making within the cooperative model of the
+community.
+
+\item To validate the proposed methods by extensive simulations
+and comparison with other similar proposals.
 \end{itemize}
 
-In addition to being autonomous, agents are possibly heterogeneous; that is, agents may be independently designed by different programmers and hence it is difficult to make assumptions about their present or future behavior.
-A multi-agent system (MAS) consists of a set of these autonomous
-entities, which interact with each other and their
-surrounding environment to achieve their (joint) objectives
-\cite{Wooldridge2009}.
-In an open system, autonomous agents can freely enter and exit different interactions at any time \cite{Fornara2004a}.
-In principle, open MASs provide no guarantees about the behavior of their agents.
-This means that when agents are working together, such as carrying out a business protocol, an agent's misbehavior may potentially create an
-exception for another agent and obstruct its proper working.
-However, one can look at multi-agent systems from different
-perspectives. From the computing perspective, a MAS is a
-computational paradigm and an advance in computer science. From
-the software engineering perspective, multi-agent technology is a
-new software engineering paradigm providing new abstractions for
-different phases of software development process. MASs approaches
-can be seen as very efficient and modular ways of modeling and
-implementing systems as they are capable of designing and
-programming autonomous agents with different abilities, behaviors,
-and intentions. From the artificial intelligence perspective, MASs
-provide better understanding and modeling of social intelligence
-and emergent behaviors.
+\section{Proposal Organization}\label{sec:outline}
+The rest of the proposal is organized as follows: We present in
+Chapter 111 the background needed for our research along
+with relevant related work. Chapter 222
+provides the problem statement and presents our solution model in
+two different scenarios with some preliminary results. Finally, in
+Chapter 333, we present our conclusion,
+future plan, and the timetable of our research.
 
-\subsection{Agent Communication Languages (ACLs)}
-Communication is a fundamental aspect for autonomous agents in MASs to coordinate with one another to solve complex problems that are difficult for an individual agent to tackle.
-Therefore, communication among agents is a key element to build effective MASs.
-In many realistic settings, agents need to interact to realize their goals.
-The type of interaction among the agents varies according to the goals of these interacting parties and the context of the transactions they are performing.
-An agent may cooperate with other agents to perform a certain task, compete with others to achieve a shared goal, or do a combination of both in order to perform individual or group tasks.
+\section{Context of Research}\label{sec:motivation_s}
 
-The importance of defining a standard framework for agent communication has been widely recognized.
-However, there have been many attempts in the literature to agree on standards for agent communication.
-Semantics of ACLs are defined either internally (privately) in terms of agents' beliefs and goals, or externally (publicly) in terms of agents' social commitments.
-%Communication between agents are %governed by means of protocols. Roughly speaking, a protocol %determines which messages can be exchanged and in which order.
-Approaches defined using the former type of semantics are called mental
-approaches because they focus on the minds of interacting agents, while those defined using the latter one are called social approaches because they consider the social context of the interacting parties.
-In contrast to mental approaches such as those that are built using FIPA-ACL\footnote{See FIPA-ACL (Foundation for Intelligent Physical Agents - Agent Communication Language) specifications (1997,1999,2001,2002), http://www.fipa.org/repository/aclspecs.php3} and KQML (Knowledge Query and Manipulation Language) \cite{Finin1994}, social commitments proved to be a powerful representation for agent interactions \cite{Bentahar2010,Mallya2007,Yolum2004}.
-They provide a social semantics that abstracts away from the agents internal states and offers social and observable meaning to the messages being exchanged among agents.
-In the context of this thesis, we focus on the kind of communication in which the semantics of messages is defined publicly, i.e., in terms of social commitments.
+[seminar] Over the past years, online services have become part of many
+scalable business applications. The increasing reliance on
+web-based applications has significantly influenced the way web
+services are engineered.
+%Web services provide a set of stateless
+%software functions accessible at a network address over the web.
+%The recent developments are shifting web services from passive and
+%individual components to autonomous and group-based components
+%where interaction, composition, and cooperation are the key
+%challenges \cite{ICWS2011-1,SCC2011-1}. The main objective is to
+%achieve a seamless integration of business processes, applications
+%and web services. Delivering high quality services considering the
+%dynamic and unpredictable nature of the Internet is still a very
+%critical and challenging issue.
+%Typically, web services are business applications deployed as
+%autonomous and interoperable agents \cite{Alescio}. In fact, the
+%W3C consortium defines a web service as ``an abstract notion that
+%must be implemented by a concrete agent''. However, the web is
+%stocked with agent-based services that offer similar business
+%functionalities, which leads to service consumers having
+%difficulties in choosing the most appropriate agents to interact
+%with.
+The need for highly available and responsive services has called
+for grouping and collaborative mechanisms of loosely-coupled web
+services, particularly in business settings. The idea of grouping
+web services within communities and the way those communities are
+engineered so that web services can better collaborate have been
+proposed and investigated in
+\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
+Communities are virtual groups of web services having similar
+functionalities \cite{Zeng:2003:QDW:775152.775211,
+Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7},
+but probably different non-functional quality attributes, which
+form the QoS parameters.
+%When communities are used, users send
+%their requests to the masters of those communities, which are
+%responsible of managing the communities, forwarding the requests
+%to the suitable member web services and checking the credentials
+%of those members.
+Communities aim to provide higher service
+availability and performance than what individual web services can
+provide.
+%The high availability of services and the community
+%resilience to failure are guaranteed since web services can
+%cooperate and replace each other within the same community and
+%since there is no single point of failure in the communities
+%architecture.
 
-\section{Motivations} \label{sec:Motivations-chap1}
-Our review of the social commitments literature has revealed a gap in handling probabilistic social commitments in MASs.
-We have noticed that though social commitments have been the subject of a vast research activity for more than a decade, current proposals to represent and verify social commitments, for instance \cite{Bentahar2012,Bentahar2009,Bentahar2004,Colombetti2000,Colombetti2004,El-Menshawy2010,El-Menshawy2013a,Singh2000,Verdicchio2003}, assume typical settings in which agents behave in an ideal manner, and consequently commitments among interacting agents are treated under the assumption of certainty.
-However, in the formulation of agent-based systems, the role of uncertainty is crucial for an efficient and coherent resolution of complex problems.
-Simply put, agents in MASs overcome complex problems thanks to their individual capabilities to be autonomous and to adapt their behavior with the changing of the environment in which they live and
-interact.
-Practically speaking, agents cannot always observe all the changes in the environment, but instead each agent can only have a partial view of other agents' behavior \cite{Gammie2004}.
-Indeed, the presence of imperfect information about the environment leads autonomous agents to make estimations about the observable world as part of their autonomous decision making processes \cite{Walley1996}.
-This means that agents inevitably meet uncertainty during their work, or in many cases, for the high complexity of the problem, the information they handle is (or needs to be) approximate.
+\section{Motivation and Research Objectives}\label{sec:motexample_s}
 
-This unpredictable behavior of MASs raises different important questions.
-The interesting issue that we are mainly focusing on is how social commitments can be tackled in such systems.
-In reality, due to agents' autonomy, a request to create a social commitment is not always followed by the creation of that commitment.
-The same principle applies to fulfilling an established commitment.
-That is, in some situations, even if there is some state of affairs (i.e., content of a commitment) that an agent wants to bring about, its actions might not reliably drive the state of affairs into the desired state \cite{Xuan1999}.
-Consequently, the problem of specifying and verifying social commitments is made more complicated by the presence of uncertainty.
+Web service communities are dynamic by design
+\cite{DBLP:journals/ijebr/MaamarSTBB09}. In these communities, web
+services are modeled as intelligent autonomous agents, where they
+can adopt a strategy maximizing their payoff at any time. A web
+service can ask joining a community and has the right to leave it.
+Community managers can invite or ask a web service to leave in
+order to maximize the community profit. Users can simply stop
+sending requests to a web service which is not providing
+satisfactory services. Thus it is important to consider all the
+parties involved in the decision making process about the
+community management.
 
-The interaction between social commitments and agents' knowledge is also not receiving sufficient attention from the researchers in MASs community.
-For instance, the addition of epistemic reasoning to social commitments has not been widely considered yet.
-In fact, the ability to perform knowledge reasoning over commitments is one of the major advantages of addressing the relationship between the two concepts which ultimately helps ensure agents' awareness about their commitments and the fulfillments of these commitments.
-The vast majority of existing proposals have been carried out to address each of knowledge and commitments independently (see for example
-\cite{Baldoni2010,Bentahar2012,Delgado2009,El-Menshawy2013a,Giordano2007,Halpern2003,Huang2011,Lomuscio2007,Pham2007,Wan2013}).
-However, it has been demonstrated that these two concepts (i.e., knowledge and commitments) are closely influencing each other in various practical settings such as e-commerce applications \cite{Al-Saqqar2014a}.
-Therefore, their interaction needs to be specified and verified in a systematic way.
-The only two existing approaches, to the best of our knowledge, to model such interactions between knowledge and commitments either neglect the probabilistic features of MASs by assuming an absolute degree of correctness so that systems under consideration behave in an ideal manner \cite{Al-Saqqar2014a}, or adopt a different kind of commitments called ``internal commitment'' rather than the ``social commitments'' that we consider in this thesis \cite{Schmidt2004}.
-The notion of ``internal commitment'' refers to a commitment of an agent to itself \cite{Singh2008}.
+In this research work, our first objective is to propose a
+cooperative model as game for the aggregation of web services
+within communities. The solution concepts of our cooperative game
+seeks to find efficient ways of forming coalitions (teams) of web
+services so that they can maximize their gain and payoff, and
+distribute the gain in a fair way among all the member services.
+Achieving Fairness when the gain is distributed among the
+community members is the main factor to keep the coalition stable
+as no web service will expect to gain better by deviating from the
+community. In other words, the coalition is made efficient if all
+the members are satisfied. We first propose a representation
+function for communities of web services based on their QoS
+attributes. By using this function, we can evaluate the $worth$ of
+each community of web services. When facing new membership
+requests, a typical community master checks whether the new
+coalition having the old and new set of web services will keep the
+community stable or not. The community master will reject the
+membership requests if it finds out that the new coalition would
+be unstable, preventing $any$ subset of web services from gaining
+significantly more by deviating from the community and joining
+other communities or forming new ones. The computation of
+solutions for cooperative games is combinatorial in nature and
+proven to be NP-complete \cite{Algorithmic}, making this
+computation impractical in real world applications. However, using
+the concepts of coalition stability, the second objective is to
+investigate approximation algorithms running in polynomial time
+providing web services and community masters with applicable and
+near-optimal decision making mechanisms.
 
-Another issue that has attracted our attention while reviewing the literature is the limitation of the current approaches to handle group social commitments.
-Although the notion of ``group'' has been, in one way or another, attached to commitments in several proposals \cite{Barbara2010,Sanchez-Anguix2013,Wright2012,YuW2010}, the semantics of ``group social commitments'' has never been materialized in the past.
-The need to formalize ``group social commitments'' stems from the importance of the concept of ``group'' in real settings as we will see later in Chapter \ref{cha:PCTLKC+}.
+Within communities, services can exhibit competitive behavior as they provide the same functionalities and the number of users requests is finite.
+However, for the same reason of being functionally similar, services can cooperate with each other, for example to substitute each other in order to perform some sub-tasks.
+So as an extension of our work, we have proposed a framework in which services can opt for performing tasks if they feel they are capable enough
+or decide to cooperate by showing the availability to perform some sub-tasks.
+We have implemented an online learning mechanism for services with different capabilities to learn over time which strategy to choose based on their own and other services status and capabilities.
+After establishing states of our model and observing convincing results from our learning method, we plan to extend the learning process using reinforcement learning (Q-learning) techniques.
 
-To address the above shortcomings, a major challenge in our research is to accurately represent and verify social commitments in the presence of uncertainty.
-Another ambitious challenge is to formally capture and verify the interaction between social commitments and agents' knowledge in probabilistic MASs.
-Yet another challenge is to define an appropriate semantics for social commitments under the scope of a group (i.e., one-to-many commitment schemes) and then study the relationship between individual and group social commitments and knowledge in probabilistic settings.
+\indent To summarize, the main problems we aim to tackle in this
+thesis are the formation of stable and efficient coalitions
+maximizing web services and community revenue and the decision over the strategy to play about competing or cooperating.
+The main objectives are:
+\begin{itemize}
+\item To propose a cooperative model and analyze its solution
+concepts in order to address the problem of optimizing coalition
+formation for a stable community.
 
-%In this research, we investigate a formal and systematic way to represent and verify social commitments in the presence of uncertainty.
-That is to realize interactions of agents where no assumptions are made on the internal states of the interacting agents as well as no assumptions are made about the presence of a reliable behavior.
-Therefore, the motivation for this thesis is to introduce a new logical framework by which we can represent and reason about agent interactions defined in terms of social commitments in uncertain settings.
+\item To reduce the complexity of computing the solution concepts
+of the cooperative model tailored to the problem of communities of
+agent-based web services in order to make these solutions
+applicable in real world scenarios.
 
-\section{Problem and Research Questions} \label{sec:problem statement-chap1}
+\item To analyze the effect of different membership and taxation
+models that the master can apply to the members on the stability
+of the community.
 
-The main problem we are addressing in this thesis is the problem of handling \textit{probabilistic social commitments} in MASs.
-To ensure having effective commitment-based interactions in open and heterogeneous systems, these commitments need to be represented and verified while keeping uncertainty in mind.
+\item To investigate the impact of learning on individual and
+group decision making within the cooperative model of the
+community.
 
-Current research initiatives focus mainly on extending conventional temporal logics such as LTL \cite{Pnueli1977} and CTL \cite{Emerson1990}, and CTL$^*$ \cite{Emerson1986} to express social commitments \cite{Baldoni2010,Bentahar2012,El-Menshawy2013a,Giordano2007,Pham2007,Verdicchio2003}.
-The downside of the current extended logics resides in their expressiveness.
-In fact, existing commitment logics can neither express probabilistic social commitments nor capture the interaction between commitments and knowledge in probabilistic MASs.
-Besides, these logics lack the ability to deal with group-commitment scenarios and instead they are limited to the common one-to-one commitment scheme.
+\item To validate the proposed methods by extensive simulations
+and comparison with other similar proposals.
+\end{itemize}
 
-To circumvent this downside, we need to come up with a probabilistic logic equipped with a social operator --for commitments and their fulfilments-- that is expressive enough to represent and reason about social commitments in the presence of uncertainty.
-
-In order to do so, some questions arise.
-We name these research questions: R1, R2, $\dots$ etc.
-The first question is: \textbf{how can we define a logic that is capable of specifying social commitments employed in uncertain settings?} [R1].
-In the literature, there is no such work that considers dealing with social commitments in the presence of probabilistic behavior.
-Thus, our thinking was directed towards existing conventional logics to investigate the possibility of exploiting them to help define the new logic.
-However, \textbf{which temporal logic to choose} is the second
-question to be answered [R2]. Existing probabilistic temporal logics
-such as PCTL \cite{Hansson1994} and PCTL$^*$ \cite{Baier1998}
-consider neither commitments nor agent communication. We
-propose to extend PCTL with modal operators for commitments and
-their fulfillments. This process is achieved by combining two existing logics together. However, any logic needs to be associated with
-a computational model over which formulae of the logic are interpreted.
-So, our third question is: \textbf{which computational model to use in order to model the target MASs?} [R3].
-The underlying computational model considered throughout this thesis is the one of interpreted system formalism \cite{Fagin1995}, suitably extended whenever necessary.
-Furthermore, to verify the proposed logic, we need
-to answer the following question: \textbf{which formal
-verification technique to use?} [R4]. In fact, there are three main
-verification techniques to verify systems against given
-requirements in the literature, namely testing, theorem proving,
-and model checking. Model checking has some advantages over
-others since it is fully automated and systematically checks all system states. On the other hand, in testing, it is hard to generate
-exhaustive test cases, and theorem proving requires expertise and is only semi-automatic.
-So, we use model checking as a means of formal verification.
-However, \textbf{which model checking technique to adopt} should be answered as many techniques are already in use [R5].
-Current proposals use only qualitative model checking  to ensure the correctness of commitment-based interactions in MASs.
-However, since our approach is built on PCTL, we propose a reduction-based probabilistic model checking technique in which the problem of model checking our logic is reduced to the one of PCTL.
-Finally, to check the effectiveness of our approach, we need to implement the proposed model checking technique.
-Hence, we need to answer the question: \textbf{which model checker to use in order to verify the proposed logic?} [R6].
-In our work, we adopt the PRISM model checker\footnote{http://www.prismmodelchecker.org} as it already allows for analyzing and verifying probabilistic systems, and it also performs symbolic model checking of PCTL in which it manipulates sets of states rather than single states.
-Such sets are efficiently represented and transformed by means of Binary Decision Diagrams (BDDs) \cite{McMillan1992}, which help alleviate the state space problem associated with model checking.
-
-\section{Objectives} \label{sec:objectives-chap1}
-The main objectives of this research are:
-
-\begin{enumerate}
-
-\item Proposing a new meaningful, declarative, and verifiable logic with an expressive power that allows for representing and reasoning about commitments and their fulfillments in the presence of uncertainty.
-
-\item Developing a new version of interpreted systems that can effectively model systems under consideration.
-
-\item Investigating the relationship between the probabilistic social commitments and probabilistic knowledge in agent-based systems.
-
-\item Defining a proper semantics for the group social commitments.
-
-\item Introducing a new model checking technique for verifying social commitments expressed in terms of the proposed logic.
-%This objective comprises the development of a set of reduction rules to reduce the problem of model checking our logic to the problem of model checking an existing logic such as PCTL.
-
-\end{enumerate}
-
-\section{Methodology} \label{sec:methodology-chap1}
-
-As an improvement over existing solutions, the research presented in this dissertation targets social commitments employed in systems exhibiting probabilistic behavior.
-We address the problem of specifying probabilistic social commitment in MASs by developing a novel logic called the probabilistic logic of commitments (PCTLC) that can represent and reason about social commitments in the face of uncertainty.
-The introduction of the new logic is motivated by the fact that the needed modal operators for reasoning about probabilistic social commitments and their fulfillments cannot be expressed using existing temporal logics.
-To build PCTLC, we advocate the technique of combining two existing logics in a new logic.
-Particulary, we adopt the independent join technique \cite{Bennett2002,Franceschet2004,Gabbay2003}.
-The reason why we use this technique is because it ensures the preservation of important properties of the logics being combined \cite{Konur2013}.
-In this perspective, we combine a logic of commitment called CTLC \cite{Bentahar2012,El-Menshawy2013a} and a probabilistic logic called PCTL \cite{Hansson1994}.
-This process can be seen as adding a probabilistic operator to the ingredients of the logic of commitment (CTLC), or vise versa (i.e., adding a commitment operator to the ingredients of the probabilistic logic PTLC).
-We model target systems using the formalism of interpreted systems.
-However, the original version
-of interpreted systems introduced by Fagin et.
-al in \cite{Fagin1995} does not capture the probabilistic behavior of MASs and also does not account for the communication between interacting agents.
-Therefore, we combine two extended versions of the original formalism introduced respectively by Halpern \cite{Halpern2003} and Wan et al.
-\cite{Wan2013} to capture the stochastic behavior of the system, and Bentahar et al.
-\cite{Bentahar2012} and El-Menshawy et al.
-\cite{El-Menshawy2013a} to model the communication between interacting parties.
-
-Furthermore, our approach evaluates social commitments at the design level as to help reduce the cost of the development process and increase robustness of target systems.
-This is achieved by formally verifying some given PCTLC-based properties using a model checking technique.
-Model checking was chosen due to the reasons stated earlier in Section \ref{sec:objectives-chap1}.
-However, model checking can be generally performed by one of the following methods.
-1) Direct method in which new dedicated model checking algorithms are developed in order to verify social commitments, or 2) Indirect method which is also called reduction-based method or translation-based method.
-Indirect model checking techniques involve devising some reduction rules to reduce the problem of model checking the logic at hand to that of an existing logic in order to use current model checkers \cite{Lomuscio2007}.
-Certainly, each method has its own benefits with respect to the logic being verified.
-In this thesis we follow the latter method because it is easy to use and allows the re-use of existing model checkers \cite{El-Menshawy2013a}.
-Later in Chapters \ref{cha:PCTLC}, \ref{cha:PCTLKC}, and \ref{cha:PCTLKC+}, we show how the indirect method can effectively and efficiently verify probabilistic social commitments.
-
-Our proposed model checking procedure for PCTLC includes instantiating a set of reduction rules that transform the problem of model checking PCTLC to the problem of model checking an existing probabilistic logic called PCTL.
-By so doing, we gain the privilege of re-using the available PRISM model checker.
-
-The proposed logic of social commitment (PCTLC) is then extended by an epistemic operator to be able to express and reason about the interaction between knowledge and social commitments in the presence of uncertainty.
-The idea is that, we have various logics for each of knowledge and social commitments independently in the literature, so we combine a probabilistic logic of knowledge and a probabilistic logic of commitments in a single logic that we call the probabilistic logic of knowledge and commitment PCTL$^{kc}$.
-On that basis, we again construct a set of transformation rules to reduce the problem of model checking the proposed logic PCTL$^{kc}$ to that of PCTC so that formulae expressing properties written in PCTL$^{kc}$ can be model checked using PRISM by checking their corresponding formulae of PCTL.
-
- \begin{figure}[H]
-                \begin{center}
-                \includegraphics[width=16cm, height=20cm]{chap1/img/thesis-new.eps}
-                \end{center}
-                \caption{The Proposed Framework }
-                \label{fig:proposed-framework}
-    \end{figure}
-
-To be able to handle social commitments when the scope of interacting agents is extended from the common one-to-one scheme to one-to-many scheme, we develop a semantics for the group social commitment operator and integrate it to the framework.
-We also add a group knowledge operator in order for the new logic to be more expressive and effective.
-The improved and refined logic is called the new logic of knowledge and commitments (PCTL$^{\textrm{kc+}}$).
-Moreover, we generalise the model checking technique proposed for PCTL$^{kc}$ to verify the new logic (PCTL$^{\textrm{kc+}}$) with the group operators.
-
-Finally, each proposed reduction technique is implemented independently on top of the PRISM tool and applied to a concrete case study. 
-Figure \ref{fig:proposed-framework} depicts the structure of the proposed work, links contributions to each other, and maps them to thesis chapters.
-Moreover, this figure shows where we answer each of the research questions presented in Section \ref{sec:problem statement-chap1}.
-
-\section{Contributions}\label{sec:thesis-contributions-chap1}
-We have developed a set of methods to pursue our objectives and to fill the research gap identified above.
-The majority of the work presented in this thesis has been published in the proceedings of various international conferences and refereed international journals.
-In summary, the main
-contributions are:
-
-\begin{enumerate}
-\item A new logic called the probabilistic logic of commitments (PCTLC) that can represent and reason about social commitments in the presence of uncertainty \cite{Sultan2013}.
-
-\item A new logic called the probabilistic logic of knowledge and commitment (PCTL$^{kc}$) whose expressive power helps capture the interaction between knowledge and social commitments in probabilistic MASs \cite{Sultan2014b}
-
-\item A Semantics for group social commitment \cite{Sultan2014c}.
-
-\item An improved version of the logic of knowledge and commitments enriched with epistemic and social group operators (PCTL$^{\textrm{kc+}}$).
-The distinguished feature of the new logic  lies in its ability of not only expressing the interaction between individual (basic) social commitments and knowledge, but also expressing the interaction between group social commitments and knowledge in the presence of uncertainty \cite{Sultan2014c}.
-
-\item Three reduction-based model checking techniques for PCTLC \cite{Sultan2014a}, PCTL$^{kc}$ \cite{Sultan2014b}, and PCTL$^{\textrm{kc+}}$ \cite{Sultan2014d} respectively.
-
-\item Implementation of the three proposed model checking techniques on top of the PRISM model checker using concrete case studies.
-
-\end{enumerate}
-
-\section{Thesis Organization}\label{sec:thesis-outline-chap1}
-The remainder of this thesis is organized as follows.
-Chapter \ref{cha:background} describes the background needed for our research.
-Chapter \ref{cha:PCTLC}, presents a formal approach for handling probabilistic social commitments in MASs.
-In Chapter \ref{cha:PCTLKC}, we introduce a probabilistic approach for capturing and verifying the interaction between knowledge and social commitments.
-Chapter \ref{cha:PCTLKC+} presents an improved version of the approach presented in Chapter \ref{cha:PCTLKC} and then extends it to accommodate group knowledge and group commitments.
-%Also, in this chapter, a novel semantics for the group social commitment is given for the first time in the literature.
-Chapter \ref{Chap5:Conclusion} concludes the thesis and identifies hints for future directions.
+\section{Report Organization}\label{sec:outline_s}
+The rest of the report is organized as follows. We present in
+Chapter 111 the background needed for our research along
+with relevant related work. Chapter 222
+provides the problem statement and presents our solution model in
+two different scenarios with some preliminary results. Finally, in
+Chapter 333, we present our conclusion,
+future plan, and the timetable of our research.

### 2015-04-22 thesis/thesis/chap2/chap2.tex
changes

--- 2013-12-02 proposal/proposal/chapter2.tex
@@
 \setcounter{chapter}{1}
-%*******************************START Background **********************************
 
-\chapter{Background and Relevant Literature}\label{sec:MAS}
-
+\chapter{Background}\label{cha:background}
 In this chapter, we briefly review web services, then we introduce
@@
 Consider a game $G = (N, v)$, with two players where $N = {1,2}$.
-Each of these players can produce 5 units of output working alone and by collaborating they can produce 20 units worth of output.
-Therefore we have: $v({1}) = 5, v({2}) = 5, v({1,2}) = 20$.
-The $core$ of the game, which is the set of all possible distribution of gain among players guaranteeing stability is: $core(N,v) = \{(x_1,x_2) \in R^2 | x_1 >= 5, x_2 >= 5, x_1 + x_2 = 20\}$, as illustrated in figure \ref{fig:coreex1}.
-Distributing the 20 units of income, among these two players, for all the points in the line will make outcome stable, since non of these players can gain more than 5 by working alone.
-However although they have same qualities, the core can suggest a stable outcode where one agent can earn three times more than the other agent: $\{5,15\}$.
-As mentioned in previous section, $core$ result may not be fair, the $core$ only considers stability.
-However, \emph{Shapley value} considers fairness.
-According to equation \ref{eq:shapley}, the two  workers should each share 10 units of income, since they have the same marginal contribution to all subsets of the coalition.
-As you can see the distribution vector of $\{10,10\}$ is also a member in $core$ set.
-Later we are going to show if $core$ of a coalition game is not empty, and game is convex, the shapely value lies within $core$ set.
+Each of these players can produce 5 units of output working alone
+and by collaborating they can produce 20 units worth of output.
+Therefore we have: $v({1}) = 5, v({2}) = 5, v({1,2}) = 20$. The
+$core$ of the game, which is the set of all possible distribution
+of gain among players guaranteeing stability is: $core(N,v) =
+\{(x_1,x_2) \in R^2 | x_1 >= 5, x_2 >= 5, x_1 + x_2 = 20\}$, as
+illustrated in Figure 2. Distributing the 20 units of income,
+among these two players, for all the points in the line will make
+outcome stable, since non of these players can gain more than 5 by
+working alone. However although they have same qualities, the core
+can suggest a stable outcode where one agent can earn three times
+more than the other agent: $\{5,15\}$. As mentioned in previous
+section, $core$ result may not be fair, the $core$ only considers
+stability. However, \emph{Shapley value} considers fairness.
+According to equation \ref{eq:shapley}, the two  workers should
+each share 10 units of income, since they have the same marginal
+contribution to all subsets of the coalition. As you can see the
+distribution vector of $\{10,10\}$ is also a member in $core$ set.
+Later we are going to show if $core$ of a coalition game is not
+empty, and game is convex, the shapely value lies within $core$
+set.
 \end{example}
@@
 
-        \subsection{Representation and Complexity issues}\label{sec:CWSArchitecture}
+        \subsection{Representation and Complexity Issues}\label{sec:CWSArchitecture}
 
-        Shapely value is the unique "fair" way to distribute the total surplus generated by the coalition, among all the players.
+        Shapely value is the unique ``fair'' way to distribute the total surplus generated by the coalition, among all the players.
         The nature of the Shapley value is combinatorial, as all possible orderings to form a
@@
         decision making mechanisms.
-
-%*******************************End Background **********************************

### 2015-04-22 thesis/thesis/chap3/chap3.tex
changes

@@
 
-\chapter{Probabilistic Social Commitments}\label{cha:PCTLC}
-
-In this chapter\footnote{The results of this chapter have been published in the journal of Applied Soft Computing \cite{Sultan2014a}, and in SoMet\_13 \cite{Sultan2013}.}, we establish a formal approach that allows us to precisely address probabilistic social commitments in MASs.
-The proposed approach is based on a new logic called the Probabilistic Logic of Commitments (PCTLC).
-This logic is intended to be used for specifying, reasoning about, and verifying social commitments in the presence of uncertainty.
-PCTLC extends PCTL \cite{Hansson1994} with a commitment modality.
-We model MASs using a new version of interpreted systems that merges two extended versions of the original formalism namely, the probabilistic interpreted systems \cite{Halpern2003,Wan2013}, and the communicative interpreted systems \cite{Bentahar2012,El-Menshawy2013a}.
-Finally, we propose a model checking technique for verifying the new logic (PCTLC).
-%social commitments employed in uncertain settings.
-
-\section{Introduction} \label{sec:introduction}
-
-In order to represent and reason about social commitments in MASs,
-commitment logics that extend CTL (Computation Tree Logic), LTL
-(Linear Temporal Logic), and CTL$^{*}$ (superset of CTL and LTL),
-have been proposed, see for example
-\cite{Bentahar2004,Giordano2007,Pham2007,Singh2000,Verdicchio2003}.
-
-However, current logics are merely related to specifying and
-verifying social commitments under the assumption of reliable behavior. That is, they assume an absolute, non-probabilistic running of systems under consideration.
-Unfortunately, this is not always the case. Heterogeneous and
-autonomous intelligent components in agent societies make it
-challenging to precisely analyze random or unreliable agent
-behaviors. This is because agents' actions are based on observing the
-environment changes and in many situations agents cannot observe
-all changes in the environment. Instead, each agent can only have a
-partial view of other agents' behaviors \cite{LeeL09}. In such
-cases, agents make estimations about the observable world as part
-of their autonomous decision making processes. Moreover, when the
-system being modeled is an open system, i.e., interacts with an
-environment, then uncertainty in transitions may arise due to
-imperfect information about the environment \cite{Walley1996}.
-Consequently, the problem of representing and verifying social commitments is made more complicated by the presence of transition uncertainty which makes agents uncertain about the effects of their actions on their peers and not fully
-aware of the situations other agents are encountering. Moreover,
-from the communication perspective, commitments themselves are
-likely to be subject to probabilistic events. Xuan and Lesser
-\cite{Xuan1999} have highlighted some sources of uncertainty that
-make a commitment between two agents probabilistic:
-
-\begin{enumerate}
-\item The first source of uncertainty is related to the debtor's action(s). That is, debtor's action(s) might not always lead to the fulfilment of the commitment.
-
-\item The second source comes from the agent decision processes.
-Debtors beliefs and desires might change such that continuing to pursue fulfilling the commitment for others becomes irrational.
-Debtors' beliefs about the commitment context include, for example, the degree that the agent to whom the commitment was made is still relying on its fulfillment.
-To the creditor, this can cause problems because its action(s) may depend on the honoring of the commitment by the debtor.
-
-\item The third form of uncertainty comes from the incomplete knowledge of the debtor about the creditor or about the environment within which the agent interacts.
-\end{enumerate}
-
-Consequently, one cannot assume that all autonomous agents will behave as expected, and thus commitments among communicating parties cannot be treated under the assumption of certainty.
-Modeling uncertainty can be achieved using different tools including fuzzy logic as in \cite{Correa2013,Karray2004}, and probabilities as in \cite{Feng2011,Karthikeyan2013,Perko2011}.
-On the one hand, fuzzy logic is specifically designed to deal with imprecision of facts (or the membership in vaguely defined sets).
-Its use in MASs has been investigated by some researchers.
-In \cite{Garza2011a}, the authors exploited fuzzy logic in designing intelligent agents that communicate with each other using a mental approach that uses KQML \cite{Finin1994} as the underlying communication language.
-However, mental approaches suffer from the semantics verification problem \cite{Wooldridge2000}.
-That is, they cannot verify whether an agent is acting according to a given semantics or not \cite{Wooldridge2009}.
-In our work, we adopt social approaches that are based on observable social commitments.
-
-On the other hand, probability is an important component in the design and analysis of complex systems across a broad spectrum of application domains, including communication and multimedia protocols, randomised distributed algorithms, security protocols, and dynamic power management.
-It is commonly  used to model unreliable or unpredictable behavior.
-Probability deals with the chance of happening for an event or a condition (i.e., likelihood of some event or condition).
-Although probability has proven to be a powerful technique in handling different aspects of MASs \cite{Kulkarni2010,Wan2013}, its value in addressing social commitments for agent communication is yet to be investigated.
-In our research, we use probabilities to model the uncertainty because we are concerned with the likelihood of the fulfilment of the commitment.
-That is, when a social commitment between two agents takes place, we are interested to know about the chance of fulfilling that commitment at a certain state in the system.
-Additionally, using probabilities to handle the uncertainty of social commitments provides us with the privilege of exploiting existing probabilistic logics and model checkers.
-However, it is worth mentioning that probability assignments are not the focus of this research.
-Probability values can be obtained from historical data using some techniques such as the algorithm proposed in \cite{Ormandjieva2008} which allows us to compute the fixed probabilities between two states based on some other probabilities.
-
-To motivate our study of modeling and verifying social commitments in the face of uncertainty, we use two situational examples that arise in practical settings such as web-based systems and mobile applications.
-
-\textit{Example 1.} Let us consider the Online Shopping System
-\cite{Gomaa2011} which aims at providing services for purchasing
-online items. In the web-based Online Shopping System, customers
-can request to purchase one or more items from the supplier.
-Having selected an item, the customer commits towards the supplier
-to pay in order for the request to take place. Once the order is
-paid, the supplier confirms the order, and commits to deliver the
-requested item and enters a planned shipping date. Finally, when
-the order is shipped, the customer is notified. Because of the
-uncertainty associated to the underlying infrastructures of both
-commitments (i.e., the internet through which the payment is made
-and the transport system used for the delivery of purchased
-goods), there is no guarantee that these commitments will be
-fulfilled. Therefore, reasoning about and verifying the
-commitments to pay and to deliver have to be tackled with
-probability in mind so that the degree of fulfilling each
-commitment can be measured.
-
-\textit{Example 2.} In the field of mobile applications which are
-complex in nature, addressing social commitments should be
-paired with the consideration of uncertainty of transitions and
-commitments. Let us consider a simple scenario where a receiver
-agent and a sender agent have an agreement, in which the receiver
-agrees to pay the sender in return of the delivery of a requested
-service. This can be represented as a social commitment, in which
-the receiver will be committed to the sender to pay upon obtaining
-the requested service. In such a scenario, because of the presence
-of stochastic behavior in mobile applications, the commitment to
-pay is not going to be surely satisfied.
-
-The scenarios described above cannot be represented by existing
-conventional commitment logics because of the uncertainty aspect
-in both systems. Consequently, they cannot be verified. To cope
-with the situation, we need a probabilistic commitment logic that
-accounts for uncertainty, and a probabilistic model
-checking procedure to verify properties expressed in the new logic.
-
-The ultimate objective of this chapter is to introduce a logical approach that is capable of addressing probabilistic social commitments in MASs.
-This is done as follows.
-\underline{First}, we present a new probabilistic logic called PCTLC to express and reason about social commitments when uncertainty is a key factor.
-The introduction of PCTLC logic was driven by the fact that current probabilistic temporal logics such as PCTL \cite{Hansson1994} and PCTL$^*$ \cite{Baier1998} consider neither commitments nor agent communication.
-PCTLC extends PCTL with modalities for commitments and their fulfillments.
-We model probabilistic MASs by a formalism resulted from extending the  interpreted systems introduced by Fagin et al.
-\cite{Fagin1995}.
-This extension considers agents uncertainty and their
-communication abilities. Properties to be verified (i.e., social
-commitments) are specified using the probabilistic logic of
-commitment PCTLC.
-\underline{Second}, we introduce a formal and automatic, probabilistic model checking technique for probabilistic commitment-based agent interactions.
-Our proposed verification method is a reduction-based model checking technique and consists of transforming the problem of model
-checking PCTLC into the problem of model checking PCTL \cite{Hansson1994} so that the use of PRISM is made possible.
-This reduction encompasses two main steps.
-In the first step, we devise a set of formal rules to transform the PCTLC model into an MDP model.
-Then, we reduce the MDP into DTMC to be as an input to the PRISM model checker.
-In the latter step, we transform PCTLC formulae into PCTL formulae based on some rules developed specifically for this purpose.
-As argued in \cite{El-Menshawy2013a}, the main advantage of the reduction techniques compared to the direct ones is that they are easy to implement and allow the re-use of the existing model checkers.
-\underline{Third}, we implement the proposed model checking approach on top of the PRISM model checker and then apply it on a concrete case study, namely Oblivious Transfer Protocol \cite{Rivest1999} from cryptography domain.
-Figure \ref{approach-cha3} gives an overview of the proposed approach.
-
-\begin{figure}%[h]
-\begin{center}
-\includegraphics [width=14cm, height=5cm]{chap3/img/approach-cha3.eps}
-  \caption{A schematic view of the probabilistic social commitment approach}
-\label{approach-cha3}
-\end{center}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Probabilistic Logic of Commitments (PCTLC)}\label{sec:PCTLC}
-
-In this section, we present a new modal logic called the probabilistic logic of commitments (PCTLC) to address probabilistic social commitments in MASs.
-The logic we introduce extends the probabilistic branching-time logic PCTL \cite{Hansson1994} with a commitment modality.
-To do so, we merge two existing logic namely PCTL \cite{Hansson1994} and CTLC \cite{Bentahar2012,El-Menshawy2013a} using the independent join technique \cite{Franceschet2004}.
-The independent join combines logics as they are defined in the literature.
-Thus, it ensures the preservation of each logic's properties in the new logic.
-Hereafter, we first present the syntax of our new logic, and then we define its semantics.
-Before going further, we define a new version of interpreted systems formalism with abilities to account for the uncertainty aspect in target MASs and to model the social interactions between communicating parties.
-
-The PCTLC model is generated based on two extensions of the interpreted systems formalism \cite{Fagin1995} introduced in \cite{Bentahar2012,El-Menshawy2013a}, and \cite{Halpern2003,Wan2013} as discussed in Chapter \ref{cha:background}.
-
-\begin{definition}[Models]\label{def:models}
-Given a set of atomic propositions $AP = (p,q,r, \ldots)$, the
-model $\mathfrak{M_1}=(S,I,\texttt{P},\{\sim_{i \rightarrow
-j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$ is a tuple where:
-%
-\begin{itemize}
-\item  $S \subseteq L_1 \times \ldots \times L_n$ is a countable
-set of all reachable global states for the system. A state $s$ is
-reachable iff there exists a sequence of transitions from an
-initial state to $s$ in which the probability of each transition
-is greater than $0$.
-
-\item  $I \in S$ is an initial global state for the system.
-
-\item  $\texttt{P}:S\times S\rightarrow [0,1]$ is a total
-transition probability function defined as $\texttt{P}(s,
-s')=\tau(s,a^{s \rightarrow s'}, s')$ iff there exists a joint
-action $a=(a_1,\ldots,a_n) \in ACT$ such that \\
-$\sum_{i \in \texttt{Agt}} \tau_i(l_i(s),a^{l_i(s)\rightarrow l_i(s')},l_i(s')) > 0$ and $\sum_{s' \in S} \texttt{P}(s,s') =1$
-for all $s \in S$.
-
-\item For each pair $(i,j) \in \texttt{Agt}^2$,
-$\sim_{i\rightarrow j} \subseteq S \times S$ is a social accessibility relation. $s \sim_{i\rightarrow j} s'$ is defined by the following conditions:
-      %
-  \begin{enumerate}
-       \item $l_i(s)=l_i(s')$.
-       \item $Var_i \cap Var_j \neq \emptyset$ such that $\forall x \in Var_i \cap Var_j$, we have $l^{x}_i(s)\!=\!l^{x}_j(s')$.
-       \item $\forall y \in Var_j\!-\! Var_i$, we have $l^{y}_j(s)\!=\!l^{y}_j(s')$.
-  \end{enumerate}
-       %
-  \item  $\nu : S\rightarrow 2^{AP}$ is a function valuating states with atomic propositions.
-\end{itemize}
-\end{definition}
-
-\noindent Our model $\mathfrak{M_1}$ can be thought of as a labeled
-state-transition system in which each transition from $s$ to $s'$
-is annotated with a probability value in the matrix
-$\texttt{P}$ indicating the likelihood of its occurrence
-wherein the transition is assumed to take a discrete time-step.
-This means that there is no notion of real time, while reasoning
-about discrete time is possible through state variables keeping
-track of time and counting transition steps. It is also important to
-mention that every state in $\mathfrak{M_1}$ has at least one
-outgoing transition to avoid deadlocks. Moreover, all
-terminating/final states are modeled with a self-loop.
-
-\vspace{0.2cm} \noindent \texttt{Computation paths}. We can unfold
-the model $\mathfrak{M_1}$ into a set of paths. A path through the
-model $\mathfrak{M_1}$ is a non-empty (finite or infinite) sequence
-$\pi=s_0~s_1~\ldots$ of global states such that
-$\texttt{P}(s_r, s_{r+1})> 0$ for all $r \geq 0$. Also,
-$\pi(r)$ denotes the $(r+1)^{th}$ state of $\pi$, i.e.,
-$\pi(r)=s_r$ for all $r \geq 0$.
-
-\noindent \texttt{Probability Space}. Let $\Omega$ be a sample set
-(or the set of possible outcomes of an experiment). A pair
-$(\Omega,\mathrm{F})$ is said to be a \textit{sample space} if
-$\mathrm{F}$ is a $\sigma$-algebra of measurable subsets of
-$\Omega$, which are closed under countable union and complement
-and often built from basic events called \textit{cylinders} (the
-elements of $\mathrm{F}$ are called \textit{events}). A triple
-$(\Omega,\mathrm{F},\mu)$ is a \textit{probability space} if
-$\mu$ is a probability measure over $\mathrm{F}$, i.e., $0\leq\mu
-(A)\leq 1$ for all $A\in \mathrm{F}$ such that:
-%
-\begin{itemize}
-\item $\mu(\emptyset)=0$,
-\item $\mu(\Omega) = 1$, and
-\item $\mu(\bigcup_{k=1}^{\infty}A_k)=\Sigma_{k=1}^\infty \mu(A_k)$ for disjoint $A_k$.
-\end{itemize}
-
-The probability matrix $\texttt{P}$ induces a probability
-space on the set of infinite paths $\Pi(s)$, which start in the
-state $s$, using the cylinder construction \cite{Baier2008} as
-follows. An observation of a finite path determines a basic event
-(cylinder). Suppose $s = s_0$; for $\pi=s_0~s_1~\ldots~s_n$, we
-define the probability measure $Prob_s \{\pi\}$ %$Prob_s^{fin}$
-for the $\pi$-cylinder as follows:
-%
+\chapter{Coalition Formation for Autonomous Web Services}\label{sec:coalitionformationws}
+
+In this chapter, we present our coalition model of agent-based web
+services within communities\cite{SCC2013efficient}. We start by describing the general
+architecture and considered parameters for web services.
+Thereafter, problem modeling and formulation will be introduced in
+terms of task distribution and community revenue. Web service
+cooperative games in different settings will follow along with
+some simulation results.
+
+\section{Preliminaries}\label{s:preliminaries}
+
+In this section, we discuss the parameters and preliminary
+concepts that we use in the rest of the proposal.
+
+\subsection{Architecture}
+
+Our system consists of three main types of entities working
+together:
+
+\emph{1) Web services} are rational entities that aim to maximize
+their utilities by providing high quality services to end users.
+They aim to maximize their individual income by receiving enough
+requests from end users. In order to increase their revenue, web
+services seek for more tasks if they have the capacity and
+throughput to do so. Web services can join communities to have
+better efficiency by collaborating with others, to have access to
+higher market share, and to have opportunity of receiving a bigger
+task pool from end users. Throughout this proposal, in our
+equations, we refer to web services as $ws$ and to the set of web
+services hosted by a given community as $C$. To simplify the
+notation, sometimes we simply write $ws$ instead of $ws \in C$ to
+go through the elements $ws$ of the set $C$.
+
+\emph{2) Master Web Services} or the community coordinators, are representatives of the
+communities of web services and responsible for their management.
+Communities receive requests from users and aim to host a healthy
+set of web services to perform the required tasks. They seek to
+maximize user satisfaction by having tasks accomplished according
+to the desired QoS. In fact, higher user satisfaction will bring
+more user requests and increase the market share and revenue of
+the community.
+
+\emph{3) Users} generate requests and try to find the best
+available services. User satisfaction is abstracted as function of
+quantity and quality of tasks accomplished by a given service.
+Higher user satisfaction leads to higher trust of the community by users hence directing more requests towards that service provider.
+
+\subsection{Web Service Parameters}\label{ws_parameters}
+
+Web services come with different quality of service parameters.
+These parameters with a short description are listed in Table
+\ref{qosws}.
+
+\begin{table}[!t]
+\centering
+\caption{List of web service QoS parameters.}
+\begin{tabular}{|c|c||c|c|}
+\hline
+\textbf{Parameter} & \textbf{Definition} \\
+\hline\hline
+$Availability$ & Probability of being available during \\
+&a time frame \\
+$Reliability$ & Probability of successfully handling \\
+&requests during a timeframe\\
+$Successability$ & Rate of successfully handled requests \\
+$Throughput$ & Average rate of handling requests \\
+$Latency$ & The average latency of services\\
+$Capacity$ & Amount of resources available\\
+$Cost$ & Mean service fee \\
+$Regulatory$ & Compliance with standards, law and rules\\
+$Security$ & Quality of confidentiality \\
+&and non-repudiation\\
+\hline
+\end{tabular}
+\label{qosws}
+\end{table}
+
+We adopted a real world dataset \cite{DBLP:conf/smc/Al-MasriM09a}
+which has aggregated and normalized each of these parameters to a
+real value between 0 and 1. Since requests are not shared among
+web services and are distributed among all of them inside a
+community, each one of them comes with a given QoS denoted by
+$(QoS_{ws})$. We assume that $(QoS_{ws})$ is obtained by a certain
+aggregation function of the parameters considered in Table
+\ref{qosws}. We use this quality output later in evaluating the
+community \emph{worth} or \emph{payoff} function.
+
+\subsection{Web Service Communities}\label{webservice-communities}
+
+Figure 3 represents our revised architecture of web service
+communities where tasks are to be distributed among the members
+that are interested in forming stable coalitions. As discussed in
+Chapter 2, communities are essentially virtual platforms
+aggregating web services having similar and complementary
+functionalities and communicate with other entities such as UDDI
+registries and users using particular protocols. Web services join
+communities to increase their utility by having larger market
+share and task pool. Community coordinators or master web services
+are responsible for community development, managing membership
+requests from web services and distributing user tasks among the
+community members. Community coordinators try to attract quality
+web services and keep the community as stable and productive as
+possible to gain better reputation and user satisfaction, which
+results in having higher revenue.
+
+\begin{figure*}[!t]
+\centerline{\includegraphics[width=15cm]{Figures/archss.eps}}
+\caption{Architecture of Web Service communities}
+\label{fig_community}
+\end{figure*}
+
+\section{Problem Formulation and Modeling}\label{s:model}
+
+In this section, we present  web services and community coordinator's interactions, the task distribution process and revenue models in web service communities.
+
+\subsection{Task Distribution}
+
+As mentioned in Section \ref{webservice-communities}, communities
+are robust service providers with well established market share
+and reputation. By maintaining their reputation and performance,
+they attract  end users which choose them as service providers to
+perform their tasks. The community master is characterized by a
+request rate $(R_C)$ from users. Each web service comes with a
+given QoS ($QoS_{ws}$) from which the throughput $Th_{ws}$ is
+excluded. Throughput is the average rate of tasks a web service
+can perform per time unit. Its exclusion from $QoS_{ws}$ allows us
+to build our analysis on the particular value of $Th_{ws}$. Thus,
+web services perform tasks with an average output quality of
+$QoS_{ws}$ and a throughput rate of $Th_{ws}$.
+
+The community master uses a slightly modified \emph{weighted fair queuing} method to distribute tasks among its members.
+The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{ws}$.
+In \emph{weighted fair queuing} method \emph{all} the input flow is multiplexed along different paths, however in our case if the input rate $(R_C)$ of the community is more than the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with delay.
+Thus, the amount of tasks performed by community is $\sum_{ws \in C}{(Th_{ws})}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$.
+However, when the input rate $(R_C)$ of the community is less than the summation of throughput values of the web services in the community,
+%the community has more web services having more total throughput value than community's request rate
+$(R_C)$ the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $R_C \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) and the total rate of tasks being performed is $R_C$, the community's receiving request rate.
+
+While distributing tasks, the community master can verify the performance, throughput and quality of service of   tasks being performed by web services.
+It can recognize if web services are capable of doing the amount of tasks they advertised.
+If for any reason there is a decline in quality metrics or throughput, the  community master will announce the new parameters and community masters and members can consider those values as benchmark for future performance calculations but also to penalize them.
+In this way, players have incentive to reveal their real capabilities to profit best from the community and to avoid being penalized.
+In addition, the system should be dynamic enough to detect and react to web services quality metrics variation as over time web service metrics may  degrade or improve, a change that the community should adjust to.
+% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities.
+Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.
+
+\subsection{Community Revenue}
+
+The communities and web services earn revenue by performing tasks.
+The total gain is function of quality ($QoS_{ws}$) and throughput
+($Th_{ws}$) of tasks being performed. As mentioned in section
+\ref{ws_parameters}, $QoS_{ws}$ is obtained by a certain
+aggregation function of the parameters considered in Table
+\ref{qosws}. We have adopted a linear equal weight average over
+all QoS parameters listed in Table \ref{qosws} excluding the
+$Throughput$ and $Cost$ parameters. A community has the option to
+weigh specific QoS parameters depending on the expectations of
+their clients.
+
+The maximum potential output of a community $(PO(C))$  is an aggregation of number of tasks, times their quality, for each web service member of the community:
+
 \begin{equation}
-%Prob_s^{fin}=
-Prob_s \{\pi\}=
-\begin{cases} 1~~~\textrm{if}~\pi~\textrm{consists~of~a~single~state}\\
-{\prod_{\substack{r=0}}^{n-1} \texttt{P}(s_r,s_{r+1})~~~\textrm{otherwise.}}
- \end{cases}
+PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
 \end{equation}
-%
-\noindent This extends to a unique measure $Prob_s$ on the set of
-infinite paths $\Pi(s)$ w.r.t countable union and complement
-\cite{Kwiatkowska2007}.
-
-\subsection{Syntax of PCTLC} \label{sec:syntax-PCTLKC}
-
-\begin{definition}[PCTLC syntax]\label{def:syntax}
-Given a set of atomic propositions $AP$, the PCTLC formulae are
-defined by the following BNF grammar:
-%
-\begin{align*}
-    \varphi & ::= p~|~\neg \varphi~|~\varphi \vee \varphi~|~\mathcal{C}~|~ \mathbb{P}_{\bowtie k} (\psi)~|~\mathbb{P}_{\bowtie k}(\mathcal{C})\\
-    \psi & ::=\bigcirc \varphi ~ | ~ \varphi ~U~ \varphi~|~ \varphi~ U^{\leq m} ~ \varphi \\
-    \mathcal{C} & ::= C_{i\rightarrow j}\varphi ~| ~ Fu(C_{i\rightarrow j}\varphi)
-\end{align*}
-%
-where: $p\in AP$ is an atomic proposition and $\mathbb{P}_{\bowtie
-k}$ is a probabilistic operator where $\bowtie \in\{<,\leq,>,\ge\}$ and $k\in [0,1]$ is a probability bound or threshold.
-$m \in\mathbb{N}^+ $ is a positive integer number reflecting the maximum number of transitions needed to reach a certain state.
-$\varphi$ and $\psi$ are state and path formulae interpreted over the states and paths of $\mathfrak{M_1}$ respectively.
-The
-Boolean connectives $\neg$ and $\vee$ are defined in the usual
-way. Formulae $\mathcal{C}$, called social formulae, are special
-state formulae in PCTLC that can express social properties using
-the modal connectives $C_{i\rightarrow j}$ and $Fu(C_{i\rightarrow
-j})$ standing for ``commitment'' and ``fulfillment of commitment''
-respectively. $\bigcirc, U$ and $U^{\leq m}$ stand for ``next time'',
-``until'' and ``bounded until'' path modal connectives respectively.
-
-\end{definition}
-
-\noindent The intuitive meanings of the temporal and probabilistic operators are straightforward from PCTL \cite{Jonsson1991}.
-$C_{i\rightarrow j}\varphi$ is read as ``agent $i$ commits towards agent $j$ that $\varphi$''.
-$Fu(C_{i\rightarrow j}\varphi)$ is read as ``the commitment $C_{i\rightarrow j}\varphi$ is fulfilled''.
-The probabilistic operator $\mathbb{P}_{\bowtie k}(\mathcal{C})$ on social formulae $\mathcal{C}$ states the degree of the commitment and the
-fulfillment of the commitment: how much the agent is confident
-about its commitment and fulfilling its commitment respectively.
-
-PCTLC logic allows us to express properties like $C_{i \rightarrow j} \varphi \supset (\mathbb{P}_{\ge 0.95}(\top~U^{\leq 13}Fu(C_{i\rightarrow j}\varphi)))$ which means when a commitment about $\varphi$ is
-held, then the probability that the commitment is fulfilled within
-13 discrete-time steps is at least 0.95, where $\supset$ stands
-for the logical implication.
-
-\subsection{Semantics of PCTLC} \label{sec: semantics of PCTLC}
-
-The semantics of our PCTLC is interpreted over the probabilistic model  $\mathfrak{M_1}$ which was introduced above.  Given a model $\mathfrak{M_1}=(S,\texttt{P},I,\{\sim_{i \rightarrow
-j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$, then
-$(\mathfrak{M_1},s) \models \varphi$ states that ``a state $s$ in the
-model $\mathfrak{M_1}$ satisfies the state formula $\varphi$,
-$(\mathfrak{M_1},\pi) \models \psi$ means that ``a path $\pi$ in the
-model $\mathfrak{M_1}$ satisfies the path formula $\psi$, and
-$(\mathfrak{M_1},s) \models \mathbb{P}_{\bowtie k}(\psi)$ means that
-``a state $s$ in the model $\mathfrak{M_1}$ satisfies
-$\mathbb{P}_{\bowtie k}(\psi)$ if the probability of taking a path
-from $s$ that satisfies $\psi$ is in the interval specified by
-$\bowtie k$''. When the model $\mathfrak{M_1}$ is clear from the
-context, we simply write the satisfaction relation $\models$ as
-follows: $s \models \varphi$ and $\pi \models \psi$. Furthermore,
-for a given pair $(i,j)\in \texttt{Agt}^2$ of agents, we denote
-the number of accessible states $s'$ from a given state $s$ such
-that $s\sim_{i\rightarrow j}s'$ by $|s\sim_{i\rightarrow j}s'|$.
-The sample space of such pair of agents at $s$ is the set of
-possible accessible states of $(i,j)$ at $s$ and is equal to
-$|s\sim_{i\rightarrow j}s'|$. We also define $|s\models \varphi|$
-as follows:
-
-\begin{center}
-$|s\models \varphi|=
-\begin{cases}
-1,~~~\textrm{if}~ s\models\varphi\\
-0,~~~\textrm{otherwise.}
-\end{cases}$
-\end{center}
-
-\begin{definition}[\textbf{Satisfaction}]\label{def:semantics-pctlc} Satisfaction of a PCTLC formula in the model $\mathfrak{M_1}$ is conductively defined as follows:
-
-\begin{itemize}
-\item For a non-probabilistic state formula:
-
-$s\models p~~~~~~~~~~~~~~~~\emph{iff}~~p\in \nu(s);\\
-s\models \varphi_1 \vee \varphi_2 ~~~~~~~\emph{iff}~~s\models \varphi_1~\textrm{or}~s \models \varphi_2; \\
-s\models \neg \varphi~~~~~~~~~~~~~\emph{iff}~~s \nvDash \varphi;\\
-s\models C_{i\rightarrow j}\varphi~~~~~~~~\emph{iff} ~~\forall s' \in S~\textrm{s.t.}~s \sim_{i \rightarrow j}s', \textrm{we~have}~s' \models \varphi;\\
-%\textrm{we~have}~s' \models \varphi;\\
-s\models Fu(C_{i\rightarrow j}\varphi) ~~\emph{iff} ~~\exists s' \in S~\textrm{s.t.}~s' \sim_{i \rightarrow j}s ~ \textrm{and}~s' \models C_{i\rightarrow j}\varphi;$
-
-\item For a path formula:
-
-%\vspace{-0.5cm}
-
- $\pi \models \bigcirc \varphi~~~~~~~~~~\emph{iff}~~\pi(1) \models \varphi; \\
- \pi \models \varphi_1~U^{\leq m}~\varphi_2~~\emph{iff}~~\exists~ k \leq m~~\textrm{s.t.}~~ \pi(k) \models \varphi_2 ~\textrm{and}~\forall i < k, \pi(i) \models \varphi_1;\\
- \pi \models \varphi_1 ~U~\varphi_2~~~~~\emph{iff}~~\exists~ m \geq 0~~\textrm{s.t.}~~\pi \models \varphi_1~U^{\leq m}~\varphi_2;$
-
-\item For a probabilistic operator working over a path formula:
-
-%\vspace{-0.5cm}
-%\begin{align*}
- $s \models \mathbb{P}_{\bowtie k} (\psi)~~\emph{iff}~~Prob_s(\psi)\bowtie k~
-\textrm{where:}~Prob_s(\psi)=Prob_s\{\pi \in \Pi(s)~|~\pi\models
-\psi\};$
-%\end{align*}
-
-\item For a probabilistic operator working over a social formula,
-where the set of events $\mathrm{F}$ is the set of states
-satisfying a formula, and assuming that the probabilities of
-accessible states from state $s$ are equally distributed:
-
-%\begin{tabbing}
- $s\models \mathbb{P}_{\bowtie k}(C_{i\rightarrow j}\varphi)$
-   ~\emph{iff}  $Prob(s \models C_{i\rightarrow j}\varphi) \bowtie \!k$, where:
-%\end{tabbing}
-%
-\vspace{-0.4cm}
-\begin{equation*}
-Prob(s\models C_{i\rightarrow j}\varphi)=\frac{\sum_{s \sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s \sim_{i \rightarrow j}s'| };
-\end{equation*}
-
-%\begin{tabbing}
-$s\models \mathbb{P}_{\bowtie k}(Fu(C_{i\rightarrow j}\varphi))$
-    ~~ \emph{iff}~ $Prob(s \models Fu(C_{i\rightarrow j}\varphi)) \bowtie k$, where:
-%\end{tabbing}
-%
-%\vspace{-0.4cm}
-%\begin{equation*}
-\begin{align*}
-%  Prob(s\models Fu(C_{i\rightarrow j}\varphi))\ =\frac{\sum_{s' \sim_{i \rightarrow j}s}|s'\models C_{i\rightarrow j}\varphi|}{|s' \sim_{i \rightarrow j}s| }
-%
-& Prob(s\models Fu(C_{i\rightarrow j}\varphi))\ = Prob_s\{\pi \in \Pi(s') ~|~ s' \sim_{i \rightarrow j}s ~\textrm{and}~ \pi = s' \ldots s ~\textrm{and}~ s' \models C_{i\rightarrow j}\varphi\}
-\end{align*}
-%\end{equation*}
-
-\end{itemize}
-
-\end{definition}
-
-Note that, the probabilistic commitment is computed based on the number of
-accessible states that satisfy the content over the whole number
-of accessible states, which reflects the uncertainty of the agent
-over the accessible states, so that over the commitment. On the other hand, probabilistic fulfillment is computed using the probabilistic
-transitions of the path linking the commitment state to the
-fulfillment state.
-
-The following proposition is straightforward from the semantics:
-
-\begin{proposition} \label{proposition-PCTLC}~\\
-If $(\mathfrak{M_1},s)\models \mathbb{P}_{\leq0} (Fu(C_{i \rightarrow
-j}\varphi))$ and $(\mathfrak{M_1},s)\models Fu(C_{i \rightarrow
-j}\varphi)$, then the state $s$ is not reachable from the commitment state.
-\end{proposition}
-
-\begin{theorem}[Probabilistic and Conventional Commitments Equivalences]\label{Commitments Equivelances} ~\\
-
-\begin{enumerate}
-\item $(\mathfrak{M_1},s)\models \mathbb{P}_{\geq1} (C_{i \rightarrow
-j}\varphi)$ ~~~iff~~ $(\mathfrak{M_1},s)\models C_{i \rightarrow
-j}\varphi$
-
-\item $(\mathfrak{M_1},s)\models \mathbb{P}_{\leq0} (C_{i \rightarrow
-j}\varphi)$ ~~~iff~~ $(\mathfrak{M_1},s)\models C_{i \rightarrow
-j}\neg \varphi$
-
-\item $(\mathfrak{M_1},s)\models \mathbb{P}_{]0,1[} (C_{i \rightarrow
-j}\varphi)$ ~~iff~~ $(\mathfrak{M_1},s)\models \neg C_{i
-\rightarrow j}\neg\varphi \wedge \neg C_{i \rightarrow j}\varphi$
-
-\end{enumerate}
-
-\end{theorem}
-
-\begin{proof}\hspace{-0.9cm}%$~\\$
-%\begin{proof} %\hspace{-0.5cm} \\
- %In what follows, we prove the above equivalences of probabilistic and conventional commitments.
-
-\begin{itemize}
-\item First equivalence. ~\\
-    $``\Longrightarrow"$. Assume $s\models \mathbb{P}_{\geq1} (C_{i \rightarrow j}\varphi)$.
-    By the PCTLC semantics, it follows that $Prob(s\models C_{i\rightarrow j}\varphi)\geq1$.
-    Thus,  $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}\geq1$.
-    This means that for all $s'\in S$ such that $s\sim_{i \rightarrow j}s'$, we have
-    $s'\models \varphi$, and hence $s \models C_{i\rightarrow j}\varphi$. \\
-    $``\Longleftarrow"$. Assume $s\models C_{i \rightarrow j}\varphi$. By the
-    PCTLC semantics, it follows that for all $s'\in S$ such that $s\sim_{i \rightarrow j}s'$,
-    we have $s'\models \varphi$ (i.e. all accessible states from $s$ satisfy $\varphi$).
-    Consequently, $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = |s\sim_{i \rightarrow j}s'|$.
-    Therefore, $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}\geq1$
-    and hence, $s\models \mathbb{P}_{\geq1} (C_{i \rightarrow j}\varphi)$.
-
-\item Second equivalence. ~\\
-    $``\Longrightarrow"$. Assume $s\models \mathbb{P}_{\leq0} (C_{i \rightarrow j}\varphi)$.
-    By the PCTLC semantics, it follows that $Prob(s\models C_{i\rightarrow j}\varphi)\leq0$.
-    Thus, $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi|}{|s\sim_{i \rightarrow j}s'|}\leq0$.
-    Since the set of the accessible states from $s$ is not empty, then $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi|$
-    must be 0 (i.e. $\varphi$ is not true in any of the accessible states). Consequently, for all $s'\in S$
-    such that $s\sim_{i \rightarrow j}s'$, we have $s'\nvDash \varphi$, which means $s'\vDash \neg \varphi$.
-     Hence, $s\models C_{i\rightarrow j}\neg \varphi$.~\\
-%
-    $``\Longleftarrow"$. Assume $s\models C_{i \rightarrow j}\neg \varphi$. By the PCTLC semantics,
-    it follows that for all $s'\in S$ such that
-    $s\sim_{i \rightarrow j}s'$, we have $s'\nvDash \varphi$. Since the set of the accessible states from $s$ is not empty,
-    then $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}\leq0$.
-    Hence, $s\models \mathbb{P}_{\leq0} (C_{i \rightarrow j}\varphi)$.
-
-\item Third equivalence. ~\\
-    $``\Longrightarrow"$. Assume $s\models \mathbb{P}_{]0,1[} (C_{i \rightarrow j}\varphi)$. By the PCTLC semantics,
-    it follows that $0< Prob(s\models C_{i\rightarrow j}\varphi)<1$. Thus,
-    $0<\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s \sim_{i \rightarrow j}s'|}<1$.
-    This means that it would never be the case that $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = |s\sim_{i \rightarrow j}s'|$
-    nor $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = 0$. Consequently, there exist some $s', s'' \in S$
-    such that $s\sim_{i \rightarrow j}s'$ and $s\sim_{i \rightarrow j}s''$ and $s'\models \varphi$ and $s''\models \neg \varphi$.
-    Hence, it is impossible to have
-    $\overline{s}\models \neg\varphi$ or $\overline{s}\models \varphi$ for all $\overline{s}\in S$
-    such that $s\sim_{i \rightarrow j}\overline{s}$. Consequently,
-    $s\nvDash  C_{i \rightarrow j}\neg\varphi$ and $s\nvDash  C_{i \rightarrow
-    j}\varphi$. Hence $s\models \neg C_{i \rightarrow j}\neg\varphi$ and $s\models \neg C_{i \rightarrow j}\varphi$. ~\\
-    %
-    $``\Longleftarrow"$. Assume $s\models \neg C_{i \rightarrow j}\varphi$. By the PCTLC semantics,
-    it follows that there exists $s'\in S$ such that $s\sim_{i \rightarrow j}s'$ and $s'\models \neg \varphi$.
-    Consequently, it would never be the case that $s'\models \varphi$ for all $s'\in S$
-    such that $s\sim_{i \rightarrow j}s'$. Therefore,
-    $1>\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}$.
-    Now assume $s\models \neg C_{i \rightarrow j}\neg \varphi$. Therefore, $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = 0$
-    would never be he case as some accessible states should satisfy $\varphi$. %this means that $s\models \mathbb{P}_{\leq0} (C_{i \rightarrow j}\varphi)$
-    %(see the proof of second equivalence above).
-    Consequently,
-    $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}>0$.
-    Thus, $0<\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s \sim_{i \rightarrow j}s'|}<1$.
-    Hence, $s\models \mathbb{P}_{]0,1[} (C_{i \rightarrow
-    j}\varphi)$.
-\end{itemize}
-
-\end{proof}
-\vspace{0.2cm}
-\begin{theorem}[Probabilistic and Conventional Fulfillment Equivalences]\label{Fulfiilemt Equivelances} ~\\
-
-\begin{enumerate}
-\item $(\mathfrak{M_1},s)\models \mathbb{P}_{>0} (Fu(C_{i \rightarrow
-j}\varphi))$ iff $(\mathfrak{M_1},s)\models Fu(C_{i \rightarrow
-j}\varphi)$ and $s$ is reachable from the commitment state.
-
-\item $(\mathfrak{M_1},s)\models \mathbb{P}_{\leq0} (Fu(C_{i \rightarrow
-j}\varphi))$ iff $(\mathfrak{M_1},s)\models \neg Fu(C_{i \rightarrow
-j}\varphi)$ or $s$ is not reachable from the commitment state.
-
-\end{enumerate}
-
-\end{theorem}
-
-\begin{proof} \hspace{0.5cm} \\
-The proofs of these equivalences are direct from Proposition
-\ref{proposition-PCTLC} and the above semantics.
-
- \end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Model Checking PCTLC using Reduction}\label{sec:model-checking-pctlc}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-When designing communicating agent-based systems that are complex,
-and stochastic in nature, formal verification is generally
-recognized as one of the best design support technologies, and a
-valuable tool towards having efficient systems in terms of
-ensuring the compliance of system design models against the given
-requirements.
-
-Given a multi-agent system represented as a probabilistic interpreted system $\mathfrak{M_1}$ and a specification $\varphi$ in PCTLC describing a desirable property, the problem of probabilistic model checking PCTLC can be defined as: 1) establishing whether or not $(\mathfrak{M_1},
-I)\models \varphi$, i.e., if $I \in Sat(\varphi)$ where
-$Sat(\varphi)$=$\{s\in S ~~|~~ \mathfrak{M_1},s \models \varphi \}$
-is the set of states satisfying $\varphi$, 2) comparing the
-probability of satisfying $\varphi$ with a probability threshold
-$\bowtie k$, where $Sat(\mathbb{P}_{\bowtie k}(\varphi))=\{s\in S
-~|~ Prob_s(\varphi)\bowtie k \}$, or 3) computing the probability
-of $\varphi$, $(\mathfrak{M_1}, s)\models \mathbb{P}_{=?}
-~(\varphi)$. Note that answers to the second and third queries can
-be: (1) truth values, when the specification simply asks for a
-comparison to a probability threshold, or (2) quantitative,
-returning the actual probability.
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics [width=14cm, height=4.5cm]{chap3/img/reduction-process-cha3.eps}
-  \caption{The proposed reduction technique of model checking PCTLC}
-\label{reduction-process}
-\end{center}
-\end{figure}
-
-Figure \ref{reduction-process} depicts the workflow of our
-reduction technique. As mentioned before, the idea is to reduce the problem of probabilistic model checking PCTLC to the problem of probabilistic
-model checking PCTL in order to be able to use the PRISM model
-checker. Concretely, the proposed reduction technique consists of
-two processes (see Figure \ref{reduction-process}). In the former
-process, we transform our model $\mathfrak{M_1}$ into an MDP model.
-MDPs are the standard models for describing systems with
-probabilistic and nondeterministic behavior \cite{Rutten2004}. At
-every state of an MDP, one or more actions are available, and each
-action is associated with a probability distribution over the
-successor states. That is, MDPs are not augmented with a unique
-probability measure. Reasoning about probabilities of sets of
-paths of an MDP relies on the resolution of the nondeterminism. In
-order to define the semantics of such an MDP, as in
-\cite{Forejt2011}, we use the notion of adversary to factor out the nondeterminism and consider the probability of some
-behavior of the MDP (i.e., allowing us to place a well-defined
-probability on the set of paths for each adversary). Informally,
-at each step, the adversary picks an action, and then the next
-state is picked according to the probability distribution
-associated with the action. In this work, we focus on a special
-class of adversaries called \emph{Memoryless Adversary} where the
-choice of action depends only on the state and independent of what
-has happened in the history (i.e., which path led to the current
-state). An adversary is said to be memoryless if it always selects
-the same action in a given state. The resulting adversaries are
-basically DTMC models for which we can define a probability
-measure over paths. The obtained DTMC models will be the input of
-the PRISM model checker. In the latter process of the reduction
-technique, we transform PCTLC formulae into PCTL formulae (see
-Section \ref{sec:reducing-pctlc-to-pctl}).
-
-\subsection{Transforming the Model $\mathfrak{M_1}$} \label{sec:reducing-proposed-model}
-
-Given $\mathfrak{M_1}=(S,\texttt{P},I,\{\sim_{i \rightarrow j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$, and a PCTLC formula $\varphi$, we define an MDP model $\mathfrak{M'_1}$ = $\mathscr{H}(\mathfrak{M_1})$ and PCTL formula $\mathscr{H}(\varphi)$ using the transformation function $\mathscr{H}$ such that $\mathfrak{M_1} \models \varphi$ iff $\mathscr{H}(\mathfrak{M_1})\models \mathscr{H}(\varphi)$.
-Recall that the model $\mathfrak{M'_1}$ is an MDP model  $= (\mathbb{S}, AC, \textsf{P}_t ,I_i, L)$.
-Now, the model $\mathfrak{M'_1}$ can be defined using the function $\mathscr{H}$ as follows:
-
-\begin{figure}[!htp]
-\begin{center}
-\includegraphics [width=12cm, height=4cm]{chap3/img/relation-translation.eps}
-  \caption{Translating relations in $\mathfrak{M_1}$ model into actions in the MDP model}
-\label{fig-relation-to-actions-cha3}
-\end{center}
-\end{figure}
-
-\begin{itemize}
-\item $\mathbb{S}$=$S$; $I_i$=$I$; $L$=$\nu$.
-
-\item The set of atomic action propositions $AT$  is defined as
-follows:\\
-$AT = \{\varepsilon \} \cup \{\alpha_{1 \rightarrow 1},
-\alpha_{1 \rightarrow 2}, \dots, \alpha_{n \rightarrow n}\} \cup
-\{\beta_{1 \rightarrow 1}, \beta_{1 \rightarrow 2}, \dots,
-\beta_{n \rightarrow n}\}$. Consequently, the set of actions $AC =
-\{\gamma \} \cup \{\alpha^{11}, \alpha^{12}, \dots, \alpha^{nn}\}
-\cup \{\beta^{11}, \beta^{12}, \dots, \beta^{nn}\}$ where $n$ is
-the number of agents, $1 \leq i \leq n$, and $1 \leq j \leq n$.
-Actions $\gamma, \alpha^{ij}$, and $\beta^{ij}$ denote transitions
-defined, respectively, from the probabilistic transition relation
-$\texttt{P}$, the accessibility relation $\sim_{i \rightarrow j}$,
-and the transition added when there exists a transition labeled
-with $\alpha^{ij}$ and needed to define the transformation of the
-formula $Fu(C_{i \rightarrow j})$. Note that, $\varepsilon$ is the
-atomic action forming $\gamma$, $\alpha_{i\rightarrow j}$ is the
-atomic action forming $\alpha^{ij}$, and $\beta_{i\rightarrow j}$
-is the atomic action forming $\beta^{ij}$.
-
-\item $\textsf{P}_t$ combines the probabilistic transition
-relations of $\texttt{P}$ and the probabilistic relations obtained
-from translating accessibility relations $\sim_{i \rightarrow j}$
-to transitions labeled with $\alpha^{ij}$ and probabilistic
-transitions labeled with $\beta^{ij}$. The probability of each
-transition labeled with $\alpha^{ij}$ is equal to the probability
-of each other transition labeled with $\alpha^{ij}$ emanating from
-the same state which is calculated by dividing one over the number
-of transitions labeled with $\alpha^{ij}$ (i.e., equal
-distribution). The probabilities of transitions labeled with
-$\beta^{ij}$ are calculated in the same way. For states $s, s' \in
-\mathbb{S}$ and action $\theta \in AC$, the function
-$\textsf{P}_t$ is defined as follows:
-\begin{equation*}
-    \textsf{P}_t(s, \theta , s' )=
-\begin{cases}
-    \texttt{P}(s, s'),   & \textit{if } \theta = \gamma  \\
-    \frac{1}{|s\sim_{i \rightarrow j} s'|},   & \textit{if } \theta = \alpha^{ij}\\
-    \frac{1}{|s'\sim_{i \rightarrow j} s|},   & \textit{if } \theta = \beta^{ij}.
-    \end{cases}
-    \end{equation*}
-
-\end{itemize}
-
-Now, we define three different adversaries as follows: $\sigma_t$ to
-be used for interpreting temporal formulae, $\sigma_c$ to be used
-for interpreting commitment formulae, and $\sigma_{fu}$ to be used for
-interpreting fulfillment formulae. It is worth to mention that
-when defining $\sigma_c$ and $\sigma_{fu}$, some rules need to be
-set. To define $\sigma_c$ at a state, action $\alpha^{ij}$ has to
-be among the enabled actions at that state. Then, the memoryless
-adversary $\sigma_c$ picks the action $\alpha^{ij}$ at this state,
-and $\gamma$ at all other states. Meaning that, defining adversary
-$\sigma_c$ at a state rather than a commitment state (the state
-where $C_{i\rightarrow j}\varphi$ holds) would not be possible.
-The same principle applies to $\sigma_fu$. However, $\sigma_t$
-always picks action $\gamma$ at every state in
-$\mathfrak{M'_1}$. The induced model of applying the adversary $\sigma$ over $\mathfrak{M'_1}$ is a DTMC model.
-
-Hereafter, we introduce our reduction rules that translate PCTLC
-formulae to PCTL formulae w.r.t a given adversary.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Reducing PCTLC Formulae into PCTL Formulae} \label{sec:reducing-pctlc-to-pctl}
-
-Given the adversary $\sigma_t$, the PCTLC formulae are transformed
-inductively into PCTL as follows:
-
-$\mathscr{H}(p)=p$, if $p$ is an atomic proposition,
-
-$\mathscr{H}(\neg \varphi)= \neg \mathscr{H} (\varphi)$,
-
-$\mathscr{H}(\mathbb{P}_{\bowtie k}(\varphi \vee \psi))=\mathbb{P}_{\bowtie k}(\mathscr{H}(\varphi) \vee \mathscr{H}(\psi))$,
-
-$\mathscr{H}(\mathbb{P}_{\bowtie k}\bigcirc \varphi)=\mathbb{P}_{\bowtie k} \bigcirc \mathscr{H}(\varphi)$,
-
-$\mathscr{H}(\mathbb{P}_{\bowtie k}(\varphi~ U ~ \psi))=\mathbb{P}_{\bowtie k} (\mathscr{H}(\varphi) U \mathscr{H}(\psi))$,
-
-$\mathscr{H}(\mathbb{P}_{\bowtie k}(\varphi~ U^{\leq m} ~ \psi))=\mathbb{P}_{\bowtie k} (\mathscr{H}(\varphi) U^{\leq m} \mathscr{H}(\psi))$,
-
-It is important to note that, the social formulae
-($C_{i\rightarrow j}, Fu$) are not transformed into PCTL by making
-use of $\sigma_t$ because $\sigma_t$ does not capture the social
-accessibility relation and instead it captures only the temporal
-transitions at every state in the model $\mathfrak{M'_1}$.
-
-Given the adversary $\sigma_c$, the PCTLC commitment formulae are
-transformed inductively into PCTL as follows:
-
-$\mathscr{H}(C_{i\rightarrow j}\varphi)= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{H}(\varphi))$,
-
-$\mathscr{H}(\mathbb{P}_{\bowtie k} C_{i\rightarrow j}\varphi)= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathscr{H}(\varphi)$),
-
-The reason behind translating a commitment formula
-$C_{i\rightarrow j}\varphi$ to next operator $\bigcirc$ followed
-by $\mathscr{H}(\varphi)$ is that by having transformed the social
-accessibility relation $\sim_{i \rightarrow j}$ into a transition
-labeled with action $\alpha^{ij}$, it is obvious that all next
-states of the commitment state through the transition labeled with
-$\alpha^{ij}$ satisfy $\mathscr{H}(\varphi)$ (see Figure
-\ref{fig-relation-to-actions-cha3}). Hence, with respect to $\sigma_c$,
-which is a DTMC model that ignores all transitions at the
-commitment state except those labeled with $\alpha^{ij}$, we
-clearly see that the commitment state is converted into a state
-whose all successor states satisfy $\mathscr{H}(\varphi)$.
-
-Given the adversary $\sigma_{fu}$, the PCTLC fulfillment formulae
-are transformed inductively into PCTL as follows:
-
-$\mathscr{H}(Fu(C_{i\rightarrow j}\varphi))= \mathbb{P}_{>0}(\bigcirc \mathscr{H}(C_{i\rightarrow j}\varphi))= \mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{H}(\varphi)))$,
-
-$\mathscr{H}(\mathbb{P}_{\bowtie k} Fu(C_{i\rightarrow j}\varphi))= \mathbb{P}_{\bowtie k} (\mathbb{P}_{>0}\bigcirc\mathscr{H}(C_{i\rightarrow j}\varphi))= \mathbb{P}_{\bowtie k}(\mathbb{P}_{>0}\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{H}(\varphi)))$.
-
-$Fu(C_{i\rightarrow j}\varphi)$ is transformed to next operator
-$\bigcirc$ followed by $\mathscr{H}(C_{i\rightarrow j}\varphi)$
-because w.r.t $\sigma_{fu}$, there exists a state next to the
-fulfillment state in which $\mathscr{H}(C_{i\rightarrow
-j}\varphi)$ holds. Notice that the added transitions, labeled with
-$\beta^{ij}$, always go from the fulfillment state to a state
-where  $\mathscr{H}(C_{i\rightarrow j}\varphi)$ is satisfied (they
-go either to the commitment state or to the fulfilment state
-itself where in both states the formula
-$\mathscr{H}(C_{i\rightarrow j}\varphi$) holds). This can be
-easily seen in Figure \ref{fig-relation-to-actions-cha3}. Indeed, this
-intuitively complies with the fact that for a commitment to be
-fulfilled, the commitment itself has to be created before and
-still alive at the moment of fulfilling it (i.e., at the
-fulfillment state).
-%
-%
-%
-%It is proved that the semantic of PCTL over DTMC w.r.t adversary is the same.
-
-%
-%
-\begin{theorem}[Satisfaction Equivalence]\label{Satsisfaction-Equivelance}\hspace{0.5cm} \\
-
-Let $\sigma_t$, $\sigma_c$, and $\sigma_{fu}$ be the DTMC models
-corresponding to the adversaries that capture respectively temporal formulae, commitment formulae, and fulfillment formulae. The following equivalences hold:
-
-$(\mathfrak{M_1},s)\models p ~\text{iff}~ (\sigma_t,s) \models p$
-
-$(\mathfrak{M_1},s)\models \neg \varphi ~\text{iff}~ (\sigma_t,s)\models\neg \mathscr{H}(\varphi)$
-
-$(\mathfrak{M_1},s)\models \mathbb{P}_{\bowtie k}(\varphi \vee \psi)
-~\text{iff}~ (\sigma_t,s) \models \mathbb{P}_{\bowtie k} \mathscr{H}(\varphi) \vee \mathbb{P}_{\bowtie k} \mathscr{H}(\psi) $
-
-$(\mathfrak{M_1},s)\models \mathbb{P}_{\bowtie k}\bigcirc\varphi ~\text{iff}~ (\sigma_t,s) \models\mathbb{P}_{\bowtie k} \bigcirc \mathscr{H}(\varphi) $
-
-$(\mathfrak{M_1},s)\models\mathbb{P}_{\bowtie k}(\varphi~ U ~ \psi) ~\text{iff}~ (\sigma_t,s) \models \mathbb{P}_{\bowtie k}(\mathscr{H}(\varphi)~ U ~\mathscr{H}(\psi))$
-
-$(\mathfrak{M_1},s)\models\mathbb{P}_{\bowtie k}(\varphi~ U^{\leq m} ~ \psi) ~\text{iff}~ (\sigma_t,s) \models \mathbb{P}_{\bowtie k}(\mathscr{H}(\varphi)~ U^{\leq m} ~\mathscr{H}(\psi))$
-
-$(\mathfrak{M_1},s)\models C_{i \rightarrow j}\varphi ~\text{iff}~ (\sigma_c,s)\models \mathbb{P}_{\geq1}(\bigcirc\mathscr{H}(\varphi))$
-
-$(\mathfrak{M_1},s)\models \mathbb{P}_{\bowtie k}C_{i \rightarrow j}\varphi ~\text{iff}~ (\sigma_c,s) \models \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq1}(\bigcirc\mathscr{H}(\varphi)))$
-
-$(\mathfrak{M_1},s)\models Fu(C_{i \rightarrow j}\varphi) ~\text{iff}~ (\sigma_{fu},s) \models \mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{H}(\varphi)))$
-
-$(\mathfrak{M_1},s)\models \mathbb{P}_{\bowtie k}Fu(C_{i \rightarrow j}\varphi) ~\text{iff}~ (\sigma_{fu},s) \models \mathbb{P}_{\bowtie k} (\mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{H}(\varphi))))$
-
-\end{theorem}
-This theorem emphasizes that each formula has to be associated
-with an adversary (i.e., a DTMC model) over which the formula can
-be interpreted. The proof of the theorem with regard to PCTL
-formulae is straightforward as PCTL formulae are also PCTLC
-formulae. For commitment formulae, the proof is given in Theorem
-\ref{soundness-PCTL} that discusses the soundness of the transformation
-rules.
-
-%
-%
-
-\begin{theorem}[Soundness and Completeness of $\mathscr{H}$]\label{soundness-PCTL}
-Let $\mathfrak{M_1}$ and $\Phi$ be respectively a PCTLC model
-and formula and let $\mathscr{H}(\mathfrak{M_1})$  and
-$\mathscr{H}(\Phi)$ be the corresponding model and formula in
-PCTL. We have $\mathfrak{M_1}\models\Phi$ iff
-$\mathscr{H}(\mathfrak{M_1}) \models \mathscr{H}(\Phi)$.
-\end{theorem}
-
-%\begin{proof}$~\\$
-\begin{proof} %\hspace{0.5cm} \\
-Our aim here is to prove that the proposed reduction technique is
-sound (i.e., the necessary condition) and complete (i.e., the sufficient condition).
-We prove this by induction on the structure of the formula $\Phi$.
-The case of PCTLC formulae that are also PCTL formulae is
-straightforward. In what follows, we analyze two cases: $\Phi =
-C_{i \rightarrow j} \varphi$ and $\Phi = Fu(C_{i \rightarrow j}
-\varphi)$.
-
-\begin{itemize}
-\item $\Phi = C_{i \rightarrow j} \varphi$. We have
-$(\mathfrak{M_1},s)\models C_{i\rightarrow j}\varphi ~\text{iff}~
-(\mathfrak{M_1},s') \models \varphi$ for every $s' \in S$
-such that $s\sim_{i \rightarrow j}s'$. Consequently,
-$(\mathfrak{M_1},s)\models C_{i\rightarrow j}\varphi ~\text{iff}~
-(\mathfrak{M'_1},s') \models \mathscr{H}(\varphi)$ for every
-$s' \in \mathbb{S}$ such that $(s,\alpha^{ij},s') \in
-\textsf{P}_t$. Now, w.r.t the adversary $\sigma_c$ that is defined
-to interpret commitment formulae over $\mathfrak{M'_1}$,
-every infinite path $\pi \in \Pi^{\sigma_c}(s)$ satisfies that
-$\pi(1)=s'$ and $(\mathfrak{M'_1}^{\sigma_c},\pi(1))\models
-\mathscr{H}(\varphi)$. Then,
-$(\mathfrak{M'_1}^{\sigma_c},s)\models
-\bigcirc\mathscr{H}(\varphi)$ for all $\pi \in \Pi^{\sigma_c}(s)$.
-As the path quantifier $A$ is not defined in PCTL, and we have
-$\mathbb{P}_{\geq1}$ (weaker than $A$) instead, so we obtain
-$(\mathfrak{M'_1}^{\sigma_c},s)\models
-\mathbb{P}_{\geq1}(\bigcirc\mathscr{H}(\varphi))$.
-
-\item $\Phi = Fu(C_{i \rightarrow j} \varphi)$. We have
-$(\mathfrak{M_1},s)\models Fu(C_{i\rightarrow j}\varphi)$ iff there
-exists $s'\in S$ such that $s'\sim_{i \rightarrow j}s~
-\text{and~}(\mathfrak{M_1},s')\models C_{i \rightarrow j}\varphi$.
-Consequently, $(\mathfrak{M_1},s)\models Fu(C_{i\rightarrow
-j}\varphi)$ iff there exists $s' \in \mathbb{S}$ such that
-$(s,\beta^{ij},s') \in \textsf{P}_t$ and
-$(\mathfrak{M'_1},s') \models \mathscr{H}(C_{i \rightarrow
-j}\varphi)$. Now, w.r.t the adversary $\sigma_{fu}$ which is
-defined to interpret fulfillment formulae over
-$\mathfrak{M'_1}$, we obtain at least one infinite path $\pi
-\in \Pi^{\sigma_{fu}}(s)$ that satisfies $\pi(1)=s'$ and
-$(\mathfrak{M'_1}^{\sigma_{fu}},\pi(1))\models
-\mathscr{H}(C_{i \rightarrow j}\varphi)$. Since $E$ is equivalent
-to $\mathbb{P}_{>0}$ and $\mathscr{H}(C_{i \rightarrow j}\varphi)$
-is equivalent to
-$\mathbb{P}_{\geq1}(\bigcirc\mathscr{H}(\varphi))$, so we obtain
-$(\mathfrak{M'_1}^{\sigma_{fu}},s)\models
-\mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc
-\mathscr{H}(\varphi)))$.
-
-\end{itemize}
-
-\end{proof}
-
-\vspace{-1.0cm}
-\section{Implementation} \label{sec:implementaion PCTLC}
-
-In this section, we apply our model checking approach on Oblivious Transfer Protocol \cite{Rivest1999}.
-For the purpose of providing experimental results demonstrating the effectiveness and efficiency of our reduction technique, we verify some properties of oblivious transfer protocol, expressed originally in PCTLC logic.
-
-\subsection{Oblivious Transfer Protocol}
-Oblivious transfer protocol was introduced in cryptography to
-allow a sender to send some information to a receiver
-in such a way that the sender remains oblivious to what is
-received. We study the oblivious transfer protocol due to Rivest \cite{Rivest1999} in which the sender (Alice) has
-two secret values $m_0$ and $m_1$. The receiver (Bob) would like
-to know one of the two values without telling Alice which value he
-learned. This protocol has been the subject of analysis for some
-probabilistic properties \cite{Huang2011}. Rivest's solution uses
-a trusted initializer (Ted) who participates only in the initial
-setup to help both agents by providing them with some
-random material. The random material includes two random strings ($r_0$ and $r_1$) ---with the same length as Alice's messages--- to be sent to Alice
-in the setup phase. Then, Ted flips a bit ($d$) and sends it to
-Bob along with a random string $rd$. Now, for Bob to request
-$mc$ ($c=0$ or $1$), he sends Alice the bit $e=c\oplus d$
-($\oplus$ is the exclusive OR logical gate: it takes as input two
-bits and its output is $0$ if the two bits are equal, and $1$
-otherwise). Then, Alice responds with the values $f_0=m_0\oplus
-r_e$ and $f_1=m_1\oplus r_{1-e}$. Upon receiving $f_0$ and $f_1$,
-Bob can compute $mc=f_c\oplus rd$. Having done so, Alice will
-have no idea as to which message Bob chose, and Bob will have
-learned nothing about $m_{1-c}$ (Alice's other message).
-
-In order to use the PRISM model checker to verify and analyze
-\emph{Oblivious Transfer Protocol}, the latter has to be encoded
-into the PRISM input language. Simply, we treat the \emph{Sender}
-(Alice) and \emph{Receiver} (Bob) in the protocol as agents. Then,
-each agent is translated into a \emph{module} in the PRISM
-language. Moreover, each agent is comprised of variables that
-determine its local states. For example, Bob's variables are: bool
-$S\_req$: send request, bool $R\_ack$: receive acknowledgement,
-bit d: 0 or 1, bit c: 0 or 1, bit e: 0 or 1, bool $S\_e$: send bit
-e, string $rd$: random variable obtained form Ted in the initial
-setup, $R\_f$: receive $f_0$ and $f_1$. The global model is
-obtained by the synchronization between all modules (agents).
-
-\subsection{Oblivious Transfer Protocol Properties}
-
-One of the main motivations of this chapter is to verify properties expressed as PCTLC formulae.
-Gurin and Pitt \cite{Guerin2002} expressed that verifying protocol properties can be performed at design time.
-This kind of verification aims to prove that some property will hold for all the interactions that correctly follow the protocol.
-Our proposed model checking technique mainly accommodates compliance by design-time verification of interaction properties.
-In fact, there have been various catalogs of properties proposed in the literature \cite{Bentahar2009,Cheng2006,Desai2007}.
-In our work, we
-check \emph{safety}, \emph{Liveness}, and \emph{reachability}
-properties in the Oblivious Transfer Protocol as they are popular
-examples of protocol properties. These properties reflect some requirements of the oblivious transfer protocol that have to be met.
-
-\begin{itemize}
-\item \texttt{Property 1: Safety} ``Something bad will never occur".\\
-This property can be generally expressed in CTL by the formula
-$A\Box\neg p$ which is equivalent to $\mathbb{P}_{\geq1}(\Box\neg
-p)$ in PCTLC where $p$ represents a bad situation. Such bad
-situations include, for example, when Alice fulfills her
-commitment of using the bit \emph{e} (received from Bob) along
-with the random variables $r_0, r_1$ (obtained from Ted in the
-initial setup) for calculating $f_0$ and $f_1$, but Bob does not
-use the random variable $rd$ to compute his requested value
-$mc$. This bad situation can be avoided using PCTLC as follows:
-
-$\varphi_1= \mathbb{P}_{\geq1}\Box\neg[\mathbb{P}_{>0} \Diamond
-Fu(C_{A\rightarrow B} (use-e))\wedge \mathbb{P}_{\geq1}\Box\neg
-(use-rd)]$
-
-\item \texttt{Property 2: Liveness} ``Something good will eventually
-happen".\\
-This property expresses that some good situation will eventually
-occur. For example, in all computation paths it is always the case
-that if Alice fulfills her commitment of using the bit $e$ and the
-random strings $r_0, r_1$ for calculating and delivering $f_0$ and
-$f_1$, then in all paths in the future Bob can use $f_0$ and $f_1$
-to compute his requested value $mc$. This can be expressed as
-follows:
-
-$\varphi_2= \mathbb{P}_{\geq1}\Box[\mathbb{P}_{>0}\Diamond
-Fu(C_{A\rightarrow B} (use-e))\supset \mathbb{P}_{\geq1}\Diamond
-(comp-mc)]$
-
-\item \texttt{Property 3: Reachability} ``Some particular situation
-can be reached".\\
-This property comes in the form $E\Diamond p$ which is equivalent
-to $\mathbb{P}_{>0}\Diamond p$ in PCTLC where $p$ is the situation
-that needs to be reached. For example, once Alice commits towards
-Bob to use the bit $e$ in calculating $f_0$ and $f_1$, there
-should be a possibility from the initial state for Alice to
-eventually reach the fulfillment state where she can fulfill her
-commitment towards Bob. This property can be expressed as
-follows:
-
-$\varphi_3= \mathbb{P}_{>0}\Diamond Fu(C_{A\rightarrow B} (use-e))$
-
-\end{itemize}
-
-\subsection{Experimental Results}\label{sec:experimental-results-cha3}
-
-We have carried out 12 experiments.
-Our experiments were performed on a Dell laptop equipped with 32-bit Windows XP with 4 GB of RAM and Genuine Intel(R) CPU at 2.4 GHz.
-Table \ref{prism-results-cha3} reports the results of the performed experiments wherein (Exp.\#) denotes the experiment number, (\#Agent) denotes the number of agents, (\#States) denotes the number of reachable states, (\#Transitions) denotes the number of transitions, and (Construction Time) denotes the time needed for building the simulated model in seconds.
-We started our experiments with only two agents; Alice (sender) and Bob (Receiver).
-In this interaction, Bob requests a value
-(information) from Alice and then Alice responses to Bob and sends
-him the requested value in such a way that both agents respect the
-rules of the protocol for encrypting and decrypting the
-information.
-
-\begin{table}%[htp]
-\centering \caption{Verification results of the oblivious transfer
-protocol} \label{prism-results-cha3}
-\resizebox{\textwidth}{!}{ %
-\begin{tabular}{|c|c|l|l|c|}
-\hline
-\texttt{Exp.\#} &   \texttt{\#Agents}    & \texttt{\#States} & \texttt{\#Transitions} & \texttt{Const. Time (s)}\\
-\hline\hline
-\texttt{Exp.1}   &\texttt{2}         &25        &75              & 0.016\\
-\hline
-\texttt{Exp.2}   &4       &625              &3125                & 0.047\\
-\hline
-\texttt{Exp.3}   &6       &$1.6*10^4$         &$1.1*10^5$        & 0.079\\
-\hline
-\texttt{Exp.4}   &8       &$3.9*10^5$         &$3.5*10^6$        & 0.188\\
-\hline
-\texttt{Exp.5}   &10      &$9.7*10^6$         &$1.1*10^8$        & 0.344\\
-\hline
-\texttt{Exp.6}   &12      &$2.4*10^8$         &$3.1*10^{9}$      & 0.547\\
-\hline
-\texttt{Exp.7}   &14      &$6.1*10^9$         &$9.2*10^{10}$     & 0.859\\
-\hline
-\texttt{Exp.8}   &16      &$1.5*10^{11}$      &$2.6*10^{12}$     & 1.11\\
-\hline
-\texttt{Exp.9}   &18      &$3.8*10^{12}$      &$7.2*10^{13}$     & 1.5\\
-\hline
-\texttt{Exp.10}  &20      &$9.5*10^{13}$      &$2*10^{15}$       & 2.531\\
-\hline
-\texttt{Exp.11}  &22      &$2.3*10^{15}$       &$5.5*10^{16}$    & 3.531\\
-\hline
-\texttt{Exp.12}  &24      &$6*10^{16}$        &$1.5*10^{18}$      & 5.609\\
-\hline
-\end{tabular}}
-\end{table}
-
-In the second experiment, we added two more agents
-(receivers) who also request some values from Alice. For the rest
-of the experiments, each time we add two more agents (receivers)
-till we reach the maximum number of agents (24 agents) with which
-we can successfully build the model.
-
-In every experiment, we monitor the changes occurring in
-(\#States), (\#Transitions), and (Construction Time) respectively.
-From Table \ref{prism-results-cha3}, we notice that the state space
-(represented in terms of reachable states) increases exponentially
-as the number of agents increases (cf. Figure
-\ref{fig:Obliviou-simulation}). Likewise, the number of
-transitions also increases exponentially as more agents are added.
-However, the time (in seconds) needed for building the model
-increases polynomially, which shows the effectiveness of our model
-checking approach when the system scales up (about $6*10^{16}$
-states). The cause of this time increase in building the model
-when more agents are added is that the number of reachable states
-and the size of the model are increased. Moreover, the more we
-become closer to the state explosion point as in experiments 20,
-22, and 24, the higher time is need for building the model. This
-reflects the fact that the model size in these experiments turns
-out to be much bigger.
-
-\begin{figure}%[!ht]
-\begin{center}
-\includegraphics [width=10cm, height=6cm]{chap3/img/model-time.eps}
-  \caption{Model construction time for oblivious transfer protocol}
-\label{fig:Obliviou-simulation}
-\end{center}
-\end{figure}
-
-It is worth noticing that starting from experiment \#2 we re-write
-the desirable properties $\varphi_1$, $\varphi_2$, and $\varphi_3$
-in a parameterized form, as follows ($n$ is the number of agents
-in the experiment):
-
-$\varphi_1'= \mathbb{P}_{\geq1}\Box\neg[\mathbb{P}_{>0} \Diamond
-\bigwedge\limits_{i=1}^n Fu(C_{A\rightarrow B_i} (use-e_i))\wedge \mathbb{P}_{\geq1}\Box\neg
-(use-rd_i)]$
-
-$\varphi_2'= \mathbb{P}_{\geq1}\Box[\mathbb{P}_{>0}\Diamond
-\bigwedge\limits_{i=1}^n Fu(C_{A\rightarrow B_i} (use-e_i))\supset \mathbb{P}_{\geq1}\Diamond
-(comp-mc_i)]$
-
-$\varphi_3'= \mathbb{P}_{>0}\Diamond \bigwedge\limits_{i=1}^n Fu(C_{A\rightarrow B_i} (use-e_i))$
-
-However, for the purpose of model checking using our reduction
-technique, every defined formula needs to be transformed according
-to the reduction rules presented in Section
-\ref{sec:reducing-pctlc-to-pctl}. Below we show the transformed
-forms of $\varphi_1$, $\varphi_2$, and $\varphi_3$ respectively in
-the case of two agents (i.e., experiment \#1).
-
-$\mathscr{H}(\varphi_1)= \mathbb{P}_{\geq1}\Box\neg[\mathbb{P}_{>0} \Diamond \mathscr{H}(Fu(C_{A\rightarrow B} (use-e)))\wedge \mathbb{P}_{\geq1}\Box\neg \mathscr{H}(use-rd)]$.
-
-$~~~~= \mathbb{P}_{\geq1}\Box\neg[\mathbb{P}_{>0} \Diamond(\mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq1}(\bigcirc\mathscr{H}(use-e))))
-\wedge\mathbb{P}_{\geq1}\Box\neg \mathscr{H}(use-rd)]$.
-
-$~~~= \mathbb{P}_{\geq1}\Box\neg[\mathbb{P}_{>0} \Diamond(\mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq1}(\bigcirc(use-e))))
-\wedge\mathbb{P}_{\geq1}\Box\neg (use-rd)]$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-$\mathscr{H}(\varphi_2)= \mathbb{P}_{\geq1}\Box[\mathbb{P}_{>0}\Diamond \mathscr{H}(Fu(C_{A\rightarrow B} (use-e)))\supset \mathbb{P}_{\geq1}\Diamond \mathscr{H}(comp-mc)]$.
-
-$~~~= \mathbb{P}_{\geq1}\Box[\mathbb{P}_{>0}\Diamond(\mathbb{P}_{>0}
-(\bigcirc\mathbb{P}_{\geq1}(\bigcirc\mathscr{H}(use-e))))\supset\mathbb{P}_{\geq1}\Diamond \mathscr{H}(comp-mc)]$.
-
-$~~~= \mathbb{P}_{\geq1}\Box[\mathbb{P}_{>0}\Diamond(\mathbb{P}_{>0}
-(\bigcirc\mathbb{P}_{\geq1}(\bigcirc(use-e))))\supset\mathbb{P}_{\geq1}\Diamond (comp-mc)]$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-$\mathscr{H}(\varphi_3)= \mathbb{P}_{>0}\Diamond \mathscr{H}(Fu(C_{A\rightarrow B} (use-e)))$.
-
-$~~~~= \mathbb{P}_{>0}\Diamond [\mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq1}(\bigcirc\mathscr{H}(use-e)))]$.
-
-$~~~~= \mathbb{P}_{>0}\Diamond [\mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq1}(\bigcirc(use-e)))]$.
-
-\noindent Table \ref{formulae-prism-results-chap3} shows the results in terms of verification time (in seconds) of model checking the above defined properties when the number of agents
-varies from a simple interaction scenario of two agents to more
-complicated scenarios of 24 agents. The total execution time can
-be easily obtained by summing up the construction time to build
-the simulated model reported in Table \ref{prism-results-cha3} and the
-verification time of the considered formulae. For instance, in
-Exp. 12 with 24 agents, the total execution time of verifying
-$\varphi_1$, $\varphi_2$, and $\varphi_3$ is $5.609 + 2.609 +
-2.453 + 2.118 = 12.789$ s.
-
-\begin{table}%[htp]
-\centering \caption{Results of model checking some properties for Oblivious Transfer Protocol} \label{formulae-prism-results-chap3}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\texttt{Exp.\#} &   \texttt{\#Agents}    & \texttt{Time for MC $\varphi_1$} & \texttt{Time for MC $\varphi_2$} &  \texttt{Time for MC $\varphi_3$} \\
-\hline\hline
-1                &2           &$<$0.001      &$<$0.001      &$<$0.001       \\
-\hline
-2                &4           &0.015      &0.016      &0.015       \\
-\hline
-3                &6           &0.032      &0.031      &0.032       \\
-\hline
-4                &8           &0.046      &0.047      &0.062       \\
-\hline
-5                &10          &0.078      &0.093      &0.078       \\
-\hline
-6                &12          &0.11       &0.141      &0.172       \\
-\hline
-7                &14          &0.203      &0.188      &0.219       \\
-\hline
-8                &16          &0.359      &0.328      &0.343       \\
-\hline
-9                &18          &0.453      &0.403      &0.5       \\
-\hline
-10               &20          &1.062      &0.797      &0.719       \\
-\hline
-11               &22          &1.813      &1.125      &1.106       \\
-\hline
-12               &24          &2.609      &2.453      &2.118       \\
-\hline
-
+
+If the summation of throughput values ($Th_{ws}$) of community members exceeds the input task rate of the community ($R_C$) the community cannot perform at its maximum potential.
+It denotes the case when the community has more web services than it needs to perform the input task load.
+The actual output has to be normalized to the amount of tasks being performed.
+
+\begin{equation}\label{out_c}
+Out(C) = \left\{
+  \begin{array}{l l}
+    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{C}$}\\
+    PO(C) \times \frac{R_{C}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{C}$}
+  \end{array} \right.
+\end{equation}
+
+The revenue function of the web service community is a linear function of $Out(C)$ with a positive constant multiplier.
+
+\subsection{Case Study}
+
+In this section, we analyze three numerical examples and discuss the motivation of web services and community interactions and the strategies they can adopt and the revenue they can earn adopting these different strategies.
+
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+\caption{Case Study: Example 1}
+\label{example_1}
+\centering
+\begin{tabular}{c c c c}
+\hline
+$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
+\hline
+1 & 0.8 & 4 & 3.2\\
+2 & 0.8 & 5 & 4.0\\
+3 & 0.8 & 3 & 2.4\\
+\hline
 \end{tabular}
@@
 
-Notice that the three properties hold in all conducted
-experiments, meaning that our approach is successful in expressing
-and verifying system  properties using PCTLC. Clearly, as depicted
-in Figure \ref{fig:MC-time-properties-cha3}, the time for model
-checking the three properties is similar which increases
-polynomially till we reach the case of 20 agents then it grows up
-dramatically. However, these results demonstrate the scalability
-of our reduction-based model checking technique to verify
-commitments and their fulfilments in uncertain setting for agent
-communication.
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics [width=13cm, height=7cm]{chap3/img/three-properties-time.eps}
-  \caption{Time for model checking some properties for oblivious transfer protocol}
-\label{fig:MC-time-properties-cha3}
-\end{center}
-\end{figure}
-
-\section{Related Work} \label{sec:related-work-cha3}
-
-The work of this chapter is related to a number of other proposals in the
-literature. In this section, we give a brief overview of the most
-relevant ones.
-
-\subsection{Adding Commitment Operators to Existing Logics} \label{sec:related work Extending existing Logics}
-
-Singh in \cite{Singh2000} extends CTL logic by adding operators for
-social commitments, beliefs, and intentions in order to formally
-model the interactions between interacting parties in a MAS. By
-doing so, he was able to develop a specification language for
-commitment-based protocols. The author defines three different
-accessibility relations to intuitively capture the meaning of the
-new modalities. With respect to the commitment, the author claims
-that a commitment is satisfied at a certain state if and only if
-the content of the commitment is true along all accessible paths
-defined using an accessibility relation and emanating from the
-commitment state (the state where the commitment holds). Though
-the author claims that the proposed semantics is verifiable, no
-concrete approach for verifying or model checking the semantics is
-presented.
-
-Bentahar and his colleagues in \cite{Bentahar2004,Bentahar2007}
-present an approach that extends CTL$^*$ with an operator for
-commitments and their actions, and two operators for argument and
-dynamic logic respectively. To define a semantics for the
-commitment modality, they present a new definition for the
-accessibility relations. Moreover, their semantics is defined in
-terms of the computations (paths) along which the commitment is
-satisfied.
-
-Cheng in \cite{Cheng2006} introduce a model checking method using
-the SPIN model checker (Simple Promela Interpreter
-\cite{Holzmann1997}) to verify commitment-based business
-protocols and their compositions based on LTL logic. In this
-method, commitments are not expressed directly in the logic as we
-propose in our work. Instead, they are simply abstracted as
-variables. Consequently, the intrinsic meaning of commitments is
-not captured.
-
-In \cite{Desai2007}, Desai and his group highlight some protocol
-properties and classify them into general properties and
-protocol-specific properties in order to verify the correctness of
-commitment protocols. The presented properties are defined in
-terms of Propositional Linear Temporal logic (LTL). Then, they
-outline a technique for verifying commitment protocols and their
-compositions against these properties. The proposed approach
-involves using the SPIN model checker as a tool for the formal
-verification. Among the general properties that they are
-successfully able to verify are the deadlocks (which may result
-from the contradictory between the axioms used in protocol
-composition) and livelocks properties. As in \cite{Cheng2006},
-commitments are simply abstracted using variables.
-
-El-Menshawy and his colleagues in \cite{El-Menshawy2010} tried to
-overcome the limitations raised in
-\cite{Bentahar2004,Bentahar2007}. They propose a new logical
-language called CTL$^{*sc}$ to develop a specification language
-for commitment-based protocols. Their new logic extends CTL$^*$
-with commitments and their associated actions. Furthermore, they
-extend the temporal modalities of CTL$^*$ with past-directed
-temporal modalities. The semantics of actions is not defined in a
-recursive way as in \cite{Bentahar2004,Bentahar2007}, i.e., the
-semantics of each action does not depend on other actions. Based
-on their new logic, the authors develop a Social Negotiation
-Protocol (SNP) that merges a set of dialogue games, commitment
-actions and dialogue actions. Then, they present an automatic
-verification technique to verify the SNP using symbolic model
-checking in which they verified some given properties such as
-Reachability, Safety, and Liveness. They implemented their
-proposed verification technique using the NuSMV\cite{Cimatti2002}
-and MCMAS\cite{Lomuscio2006} symbolic model checkers. Their
-experimental results show the ability of the proposed approach to
-handle large state spaces of $10^{16}$. However, the work does not
-consider the uncertainty issue associated with the protocol.
-
-In a later work, El-Menshawy et al. \cite{El-Menshawy2011a}
-defined a new temporal logic called CTLC by extending CTL with
-operators for social commitments and their fulfilments and
-violations. In terms of defining CTLC, their main contribution is the definition of a new social accessibility relation. They define a new
-accessibility relation in which they assume the existence of an
-intermediate state between the commitment state and the
-fulfillment state. The debtor, in their accessibility definition,
-is uncertain about the current state so he looks for the
-intermediate state (different from the current state) in which it
-does not matter for him being in the commitment state, the
-intermediate state, or the fulfillment state (i.e., the local
-states of the debtor in the three global states are
-indistinguishable). However, for the creditor it does not matter
-being in the intermediate state or in the fulfillment state as
-being in one of them is the same for him. Introducing the intermediate state makes the computation of the accessible states very complex.
-The authors verified the proposed logic using a symbolic model checking algorithm they developed for this purpose.
-They also extended the MCMAS model checker to be capable of
-interpreting the new modalities. By so doing, they were able to
-show that the problem of model checking CTLC is polynomial-time
-reducible to the problem of model checking CTLK (Computation Tree
-Logic of Knowledge \cite{Penczek2003}). However, the stochastic
-aspect of the system being verified has not been addressed.
-
-CTLC logic \cite{El-Menshawy2011a} has also been the focus of
-El-Menshawy et al.
-\cite{El-Menshawy2011b,El-Menshawy2013a} and Bentahar et al.
-\cite{Bentahar2012} to verify and model check commitment-based protocols.
-In \cite{El-Menshawy2011b}, the authors investigate the use of
-symbolic model checkers to verify the compliance of commitment
-protocols against some given properties such as liveness and
-safety. To do so, they reduce the problem of model checking CTLC
-to the problem of model checking either CTLK or ARCTL (an
-extension of CTL with action formulae \cite{Pecheur2006}) where
-both are extensions of CTL. This allowed them to use MCMAS
-(suitable for CTLK), and NuSMV (suitable for ARCTL). On the other
-hand, Bentahar et al. \cite{Bentahar2012} refined CTLC by
-introducing a set of shared and unshared variables so that their
-extended version of interpreted systems can account for the
-communication among the interacting agents. Technically, they
-associate with each agent a countable set of local variables.
-Then, they use those variables to represent communication channels
-through which messages are sent and received.
-Furthermore, they analyzed the time complexity of CTLC model
-checking in explicit models such as Kripke-like structures, and
-its space complexity for concurrent programs. Their proposed model
-checking algorithms are implemented on top of the MCMAS model
-checker. El-Menshawy et al. \cite{El-Menshawy2013a} also modified
-CTLC into CTLC$^+$ that allows reasoning about communicating
-commitments and their fulfilments. In their work, they introduce a
-formal reduction technique to reduce the problem of model checking
-CTLC$^+$ to the problem of model checking ARCTL and the problem of
-model checking GCTL$^*$. This allows them to take a benefit of
-existing model checkers such as the extended NuSMV symbolic model
-checker (suitable for ARCTL) and the
-CWB-NC~%\footnote{\url{http://www.cs.sunysb.edu/~cwb/DOWNLOADS/CWB/current/user.ps}}
-automata-based model checker (suitable for GCTL$^*$). Moreover,
-they analyzed the complexity of model checking CTLC$^+$ for
-concurrent programs with respect to the size of such programs and
-the length of the formulae and proved it to be PSPASE-complete.
-Our work extends those proposals by considering the probabilistic
-aspect of social commitments.
-
-Focusing on business models, Telang and Singh \cite{Telang2012}
-propose an expressive and declarative approach capable of
-specifying business models at a high level of abstraction using
-the notion of social commitments. In particular, they specify
-business models using CTL logic, and model check operational
-interactions (a set of business interactions) specified as UML
-sequence diagrams. They map each model business to a temporal
-logic specification based on the progression of the states of the
-relevant commitments. Concretely, they capture the business model
-as an aggregation of business patterns. Then, they map each
-pattern to a CTL-based specification. To verify agent
-interactions, the authors use the NuSMV model checker to compute
-whether operational models correctly support a business model. In
-this work, commitments are translated into NuSMV variables instead
-of introducing a new commitment modality as we do in our proposal.
-
-In \cite{El-Menshawy2013b}, the authors propose a new
-logical-based language to specify commitment-based protocols. The
-presented language is defined in terms of ACTL$^{*c}$ logic which
-in turn extends CTL$^*$ with operators for social commitments and
-their actions. Like in \cite{El-Menshawy2013a}, the authors also
-present a formal reduction-based verification technique to
-transfer the problem of model checking ACTL$^{*c}$ to the problem
-of model checking GCTL$^*$. They implement their automatic
-reduction-based model checking approach on top of the CWB-NC model
-checker. Like in their proposal in \cite{El-Menshawy2013a}, agents
-are assumed to be certain about their commitments.
-
-In \cite{Gerard2013}, Gerard and Singh introduce an approach that
-specify commitment protocols and their refinements using guarded
-messages. The meaning of each message is defined as a set of
-actions. They use CTL as the underlying logic in which the
-specification is defined. The authors propose a model checking
-technique to seek whether a protocol refines another protocol
-correctly under certain conditions or not. The proposed tool
-``Proton'' was implemented on top of the MCMAS model checker. The
-commitments, which supposed to be certain, are modeled as objects
-which are mapped into domain variables in ISPL (the input language
-of MCMAS).
-
-\subsection{Probabilistic Commitments} \label{sec:related work PC}
-
-Uncertainty in commitments has to date received little attention by researches of MASs community. Herein, we review some existing proposals that treat commitments in the presence of uncertainty.
-
-In \cite{Witwicki2007}, Witwicki and Durfee presented a
-commitment-based methodology for approximating the optimal joint
-policy in agent coordination. They proposed a technique to
-decompose large mathematical programs that encodes the decision
-problems of all agents into 1) a search for optimal commitments
-regarding each agent's outgoing influences; and 2) a search for
-optimal local policies that respect the commitments decided upon.
-For a given set of commitments, they add constraints to the
-traditional linear program formulation of MDPs to guarantee that a
-feasible policy respects the commitments. Each agent can then
-solve its linear program separately.
-
-In another work, Witwicki and Durfee \cite{Witwicki2009}
-investigated the use of probabilistic commitments in service
-orientation. They proposed a commitment-based negotiation
-mechanism based on uncertain durations by which service providers
-agree to provide a service within a given time and certain
-probability. The commitment between service providers and service
-requesters use temporal and probabilistic parameters to summarize
-expectations over future agent activities. Agents (providers and
-requesters) then benefit from these commitments to build policies
-about how to achieve (for providers) or utilize (for requesters)
-these anticipated service outcomes. MDPs were adopted as the
-underling models for modeling their agent-based systems. While the
-semantics of the commitments was not formally described (i.e., in
-term of logic), they have given a definition for the probabilistic
-commitment as follows. ``A probabilistic temporal service
-commitment $C_{ij}(s) = \langle t, \rho\rangle$ is a guarantee
-that agent $i$ will perform (for agent $j$) the actions necessary
-to deliver service $s$ by time $t$ with probability no less than
-$\rho$" \cite{Witwicki2009}. By making use of these  probabilistic
-commitments, agents can make promises to each other even if they
-cannot fully guarantee service provision.
-
-Unlike the proposals in \cite{Witwicki2007,Witwicki2009}, we
-precisely use social commitments as a means of communication between
-the interacting agents. In addition, these proposals
-do not consider the verification aspect of commitments.
-However, we address the commitments between communicating parties from a formal perspective.
-That is, we integrate a commitment modality to probabilistic logic so that the verification of such commitments becomes achievable by means of model checking.
-
-\subsection{Comparison}
-
-We compare our work to the existing approaches by taking into
-consideration the following criteria: Formalization, Uncertainty,
-and Verification. Formalization reflects the use of formal logics
-such as LTL, CTL, CTL$^*$, ARCTL or PCTL to represent and specify
-the commitments. Uncertainty property indicates whether the
-probabilistic behavior is considered or not. Finally, Verification
-confirms the presentation of a formal verification technique to
-verify the proposed approach. Table \ref{table:comparison1} shows
-a summary about the comparison between our work and the existing
-approaches based on the criteria described above.
-
-\begin{table}
-\centering \caption{Comparison between our approach for the probabilistic commitments and the related work} \label{table:comparison1}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\texttt{Approach}       & \texttt{Formal}   & \texttt{Uncertainty} & \texttt{Verification}\\
-\hline
-\hline
-\cite{Bentahar2004,Bentahar2007,Singh2000}       & $\surd$         &   & \\
-\hline
-\cite{Bentahar2012,Cheng2006,Desai2007,El-Menshawy2010,El-Menshawy2011b,El-Menshawy2013a,El-Menshawy2013b,El-Menshawy2011a,Gerard2013,Telang2012}      & $\surd$         &   &$\surd$ \\
-\hline
-\cite{Witwicki2007,Witwicki2009}      &          &$\surd$   & \\
-\hline
-Ours                     &$\surd$   &$\surd$  &$\surd$    \\
-\hline
-
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+% \caption{Three web services}
+\label{example_1_2}
+\centering
+\begin{tabular}{c c || c c}
+\hline
+Community & Worth & Community & Worth\\
+\hline
+$\left\{1\right\}$ & 3.2 & $\left\{1,2\right\}$ & 7.2\\
+$\left\{2\right\}$ & 4.0 & $\left\{1,3\right\}$ & 5.6\\
+$\left\{3\right\}$ & 2.4 & $\left\{2,3\right\}$ & 6.4\\
+$\left\{1,2,3\right\}$ & 8.0\\
+\hline
+Community $R_C$: 10\\
+\hline
 \end{tabular}
 \end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}
-\centering \caption{Comparison between PCTLC and existing logics in terms of the adopted logic} \label{table:comparison2}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-\texttt{Approach}       & \texttt{LTL}   & \texttt{CTL} & \texttt{CTL$^*$} & \texttt{ARCTL}     & \texttt{PCTL} &\texttt{None}\\
-\hline
-\hline
-\cite{Cheng2006,Desai2007}    &$\surd$          & & & & &\\
-\hline
-\cite{Bentahar2012,El-Menshawy2011b,El-Menshawy2013a,El-Menshawy2011a,Gerard2013,Singh2000,Telang2012}       &          &$\surd$  && && \\
-\hline
-\cite{Bentahar2004,Bentahar2007,El-Menshawy2010}  &          &  &$\surd$ & &&\\
-\hline
-\cite{El-Menshawy2013b}      &          & &  &$\surd$ &&\\
-\hline
-\cite{Witwicki2007,Witwicki2009}      &      &    &   && &$\surd$\\
-\hline
-Ours                     &   &  & & &$\surd$ & \\
-\hline
-
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+\caption{Case Study: Example 2}
+\label{example_2}
+\centering
+\begin{tabular}{c c c c}
+\hline
+$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
+\hline
+1 & 0.8 & 5 & 4.0\\
+2 & 0.7 & 6 & 4.2\\
+3 & 0.7 & 4 & 2.8\\
+\hline
 \end{tabular}
@@
 
-In terms of formalization, our approach shares with most of the
-surveyed proposals the idea of extending existing temporal logics
-with new modalities for the commitments and their fulfilments.
-However, the main feature that distinguishes it from others lies
-in the logic being extended to handle social commitments. While
-others adopt conventional, non-probabilistic logics such as LTL,
-CTL, and CTL$^*$, ours is the only work that builds on a
-probabilistic logic, namely PCTL. Table \ref{table:comparison2}
-compares between our approach and other proposals with respect to
-the underlying logic that has been extended to specify social
-commitments.
-
-From the verification perspective, like proposals in \cite{El-Menshawy2011b,El-Menshawy2013a,El-Menshawy2013b}, we adopt a formal reduction technique as the underlying basis for our model checking to translate the problem of model checking our logic to the problem of model checking an existing logic.
-However, to the best of our knowledge, non of the existing approaches has verified social commitments in the presence of uncertainty.
-Therefore, our approach outperforms the related approaches as it is the first attempt to  tackle the verification problem of the probabilistic social commitments.
-Table \ref{table:comparison3} displays a comparison between our approach and the existing ones in terms of the used model checkers.
-
-\begin{table}
-\centering \caption{Comparison between PCTLC and existing approaches in terms of the used verification tool} \label{table:comparison3}
-\begin{tabular}{|c|c|c|c|c|c|c|}
-\hline
-\texttt{Approach}       & \texttt{SPIN}   & \texttt{MCMAS} & \texttt{NuSMV} & \texttt{CWB-NC}     & \texttt{PRISM} &\texttt{None}\\
-\hline
-\hline
-\cite{Cheng2006,Desai2007}    &$\surd$          & & & & &\\
-\hline
-\cite{Bentahar2012,El-Menshawy2010,El-Menshawy2011b,El-Menshawy2011a,Gerard2013}       &          &$\surd$  && && \\
-\hline
-\cite{El-Menshawy2010,El-Menshawy2011b,El-Menshawy2013a,Telang2012}  &          &  &$\surd$ & &&\\
-\hline
-\cite{El-Menshawy2013b}      &          & &  &$\surd$ &&\\
-\hline
-\cite{Bentahar2004,Bentahar2007,Singh2000,Witwicki2007,Witwicki2009}      &      &    &   && &$\surd$\\
-\hline
-Ours                     &   &  & & &$\surd$ & \\
-\hline
-
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+% \caption{Three web services}
+\label{example_2_2}
+\centering
+\begin{tabular}{c c || c c}
+\hline
+Community & Worth & Community & Worth\\
+\hline
+$\left\{1\right\}$ & 4.0 & $\left\{1,2\right\}$ & 7.4\\
+$\left\{2\right\}$ & 4.2 & $\left\{1,3\right\}$ & 6.8\\
+$\left\{3\right\}$ & 2.8 & $\left\{2,3\right\}$ & 7.0\\
+$\left\{1,2,3\right\}$ & 7.3\\
+\hline
+Community $R_C$: 10\\
+\hline
 \end{tabular}
 \end{table}
-
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%, %%%%%%%%%%%%%%%%%%%%%%
+
+In the first example,  we present the case of a community with
+$R_C =10 $, and three web services, each having different
+$QoS_{ws}$ and $Th_{ws}$ values as listed in Table
+\ref{example_1}. The worth of a community is calculated based on
+$Out(C)$ equation (\ref{out_c}) which is the amount of output
+being generated by the community. The first table  lists the web
+services with their aggregated $QoS_{ws}$ parameters, their task
+input rate while working alone, and also their  throughput value
+$Th_{ws}$. The second table shows all the possible communities and
+their respective worth. The obtained values suggest that
+communities having more web services have better gain and output.
+However each community needs to  distribute the gain between web
+services. Sometimes it is impossible to share the gain between all
+web services in a way that no subset of them would individually
+gain more if they form their own group. In this example, the value
+community of ${ws_1}$ and ${ws_2}$ is 7.2, With ${ws_3}$ joining
+the community the worth increases to 8.0. However there is no way
+to distribute the value among web services to have  ${ws_1}$ and
+${ws_2}$  earning 7.2, and ${ws_3}$ earning at least 2.4, the gain
+they could earn before joining the community. This fact makes the
+group unstable. In the second  example, shown in Table
+\ref{example_2}, we even have situations where a web service
+(${ws_3}$) joining a community ($\left\{ws_1,ws_2\right\}$)
+decreases the value of community. The reason is, the community is
+already full and all tasks are almost being distributed and new
+community with bad quality can degrade the average quality of
+tasks being done by the community. In both examples, the request
+of joining of web service ${ws_3}$ should be rejected by the
+community.
+
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+\caption{Case Study: Example 3}
+\label{example_3}
+\centering
+\begin{tabular}{c c c c}
+\hline
+$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
+\hline
+1 & 0.8 & 10 & 5\\
+2 & 0.8 & 20 & 5\\
+3 & 0.8 & 30 & 5\\
+\hline
+\end{tabular}
+\end{table}
+
+\begin{table}[!t]
+\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+% \caption{Three web services}
+\label{example_3_2}
+\centering
+\begin{tabular}{c c || c c}
+\hline
+Community & Worth & Community & Worth\\
+\hline
+$\left\{C_{ms_1}\right\}$ & 0 & $\left\{C_{ms_2}\right\}$ & 0\\
+$\left\{C_{ms_1}, ws_1\right\}$ & 8 & $\left\{C_{ms_2}, ws_1\right\}$ & 8\\
+$\left\{C_{ms_1}, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_2\right\}$ & 16\\
+$\left\{C_{ms_1}, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_3\right\}$ & 24\\
+$\left\{C_{ms_1}, ws_1, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2\right\}$ & 24\\
+$\left\{C_{ms_1}, ws_1, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_3\right\}$ & 32\\
+$\left\{C_{ms_1}, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_2, ws_3\right\}$ & 32\\
+$\left\{C_{ms_1}, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2, ws_3\right\}$ & 32\\
+$\left\{C_{ms_1}, C_{ms_2}, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
+$\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
+\hline
+Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
+\hline
+\end{tabular}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In Example 3, we consider the case of having different communities with different market share, ${R_C}$ values.
+Web services also have a small share of market independently, providing them with a small task pull.
+In these kind of scenarios, the solution considers individual maximization of payoff and also the total worth of all communities which represents the \emph{social welfare}.
+In this example the most efficient partition of web services is earned by having two coalitions of $\left\{C_{master_1}, ws_2\right\}$ and $\left\{C_{master_2}, ws_1, ws_3\right\}$, which yields a total value of $32 + 16 = 48$.
+In these types of scenarios, the goal is to reach stability, adopting a distributed approach where all players have the power of choice on the decision of whether or not they join a coalition.
+The communities usually start the game having some established members, encountering new web services, the communities may exchange web services and new web services would join them having at least one player gaining utility, without hurting any other participant.
+In this example if we initially having two coalitions of $\left\{C_{master_1}, ws_2\right\}$ and $\left\{C_{master_2}, ws_1\right\}$ and a ${ws_3}$ as new web service, ${ws_3}$ joining ${C_{master_1}}$ would hurt at least itself or $ws_2$, however ${ws_3}$ joining ${C_{master_2}}$ would not hurt any participants and ${ws_3}$ would earn more within the community and the community will have enough web services performing the incoming tasks from users.
+
+The first two examples illustrate the fact that a community cannot simply increase its revenue by adding more web services.
+The web services and even community owners are autonomous agents and would deviate and be displeased about the community if new members cause a drop in their profit.
+The job of the community master is to attract as many quality web services it can and keep them satisfied; hence the group stability is guaranteed.
+The third example highlights another type of problem we would like to address, which is how to form best possible groups of communities, and allocate web services among communities in a way which would maximize payoff for of our agents and members already residing in the communities.
+In next section, we provide collaborative game theory based algorithms for our autonomous agents, to tackle these problems and find applicable and efficient strategies for communities and web services to maximize their profit.
+
+ \section{Web Service Cooperative Games}\label{s:game_solution}
+
+In this section, we present different web service community models
+and focus on the problem of how both web services and community
+masters as rational entities would adopt strategies to maximize
+their payoff.
+
+\subsection {Web Services and One Community}
+
+In this scenario, we assume the existence of a typical community
+managed by its master, and web services need to join it to be able
+to get requests from the master. The community master is
+characterized by a requests rate $(R_{C})$ from users. Each web
+service comes with a given QoS ($QoS_{ws}$). The worth of a community
+$v(C)$ is set to Out(C) based on equation \ref{out_c}.
+
+As mentioned in previous section, the worth and output of a
+community  is a function of the
+throughput and provided QoS of its web service members. If the throughput rate is more than
+the master's input request rate, it means the web services inside
+the community are capable of serving more requests than the
+demand. Considering this factor, the valuation function is
+designed to balance the output performance so that it matches the
+exact throughput rate and QoS the web service can provide within
+the particular community.
+%** In the case where the limited tasks are distributed among web services uniformly, the value of coalition would be the proportion of the average QoS times their throughput to rate of available requests.
+**
+
+In this first scenario, we only consider one grand coalition and
+analyze the system from the point of view of one single master web
+service and a collection of web services. The master web service
+decides which members can join
+%or should leave%
+the community and distributes the requests and income among its
+community members (see Figure \ref{fig_sim1}).
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{Figures/s1.eps}`
+\caption{Web Services and A Grand Community}
+\label{fig_sim1}
+\end{figure}
+
+The membership decision is made based on throughput and \emph{QoS}
+of the considered web service. The goal is to have quality web
+services in the community so it stays stable and no other web
+services would have incentives to deviate and leave the coalition
+$C$. Therefore, a basic method would be to check the core of the
+coalition $C$ considering all the current community members (all
+web services already residing within the community) and the new
+web service. This algorithm uses the \emph{Shapley value}
+distribution method as described in Equation \ref{eq:shapley} to
+distribute the gain of $v(C)$ among all the members and then
+checks if the \emph{Shapley value} payoff vector for this
+community having the characteristic function $v(C)$ is in the
+\emph{core}. In the \emph{Shapley value} payoff vector, the payoff
+for each web service $ws_i$ is calculated based on its marginal
+contribution $v(C \cup {i}) - v(C)$ over all the possible
+different permutations in which the coalition can be formed, which
+makes the payoff distribution fair. Because of going through all
+the possible permutations of subsets of $N$, the nature of the
+\emph{Shapley value} is combinatorial, which makes it impractical
+to use as the size of our coalitions grows. However, it is proven
+that in convex games, the \emph{Shapley value} lies in the core
+\cite{DBLP:conf/ijcai/GrecoMPS11, myerson1991game}. Thus, if the
+\emph{Core} is non-empty, the payoff vector is a member of the
+\emph{Core}. The following proposition is important to make our
+algorithm tractable.
+% so in our algorithm we check the core membership of this payoff vector.
+
+%\ref{eq:convex}.
+
+%\newtheorem{theorem}{Proposition}
+%\begin{theorem}[Einstein-Podolsky-Rosenberg]
+\begin{theorem}\label{proposition1}
+A game with a characteristic function $v$
+is convex if and only if for all $S$, $T$, and $i$ where $S
+\subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in
+N$,
+%For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
+\begin{equation}\label{eq:convex_snow}
+v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
+\end{equation}
+\end{theorem}
+
+%\begin{Proposition}\label{proposition} A game with a characteristic function $v$
+%is convex if and only if for all $S$, $T$, and $i$ where $S
+%\subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in
+%N$,
+%For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
+%\begin{equation}\label{eq:convex_snow}
+%v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
+%\end{equation}
+%\end{Proposition}
+
+\begin{proof}
+We first prove the ``only if'' direction:
+%\\$~~~~$\textbf{1}. ``only if'' direction:\\
+\\$~~~~$\ \textbf{1}. ``only if'' direction:\\
+%\setlength{\abovedisplayshortskip}{2pt}
+Assume:\\
+\vspace{-0.5cm}
+\begin{gather*}\label{convexsnowproof}
+v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\})
+- v(T)
+\\
+\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq v (T \cup \left\{i\right\}) + v(S)
+\end{gather*}
+
+Considering $S \subseteq T$:
+\setlength{\abovedisplayshortskip}{2pt}
+\begin{gather*}
+T \cup \left\{i\right\} = (S \cup \left\{i\right\}) \cup T
+\\
+S = (S \cup \left\{i\right\}) \cap T
+\end{gather*}
+
+By setting $A = S \cup \left\{i\right\}$ and $B = T$ we have:
+\setlength{\abovedisplayshortskip}{2pt}
+\begin{gather*}
+v(S \cup \left\{i\right\}) + v(T) \leq v (T \cup \left\{i\right\}) + v(S)
+\\
+\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq
+\\
+v((S \cup \left\{i\right\}) \cup T) + v((S \cup \left\{i\right\}) \cap T)
+\\
+\rightarrow v(A) + v(B) \leq v(A \cup B) + v(A \cap B)
+\end{gather*}
+Consequently, the game is convex.
+
+\textbf{2}. ``if'' direction:\\
+Assume the game is convex. Thus, for all $A, B \subset N$, we
+have: \setlength{\abovedisplayshortskip}{2pt}
+\begin{gather*}
+v(A) - v(A \cap B) \leq v(A \cup B) - v(B)
+\end{gather*}
+
+By setting $S \cup \left\{i\right\} = A$ and $T = B$ where $S \subseteq T$:
+\setlength{\abovedisplayshortskip}{2pt}
+\begin{gather*}
+v(S \cup \left\{i\right\}) - v((S \cup \left\{i\right\}) \cap T) \leq v(T \cup (S \cup \left\{i\right\})) - v(T)
+\\
+\rightarrow v(S \cup \left\{i\right\}) - v(S) \leq v(T \cup \left\{i\right\}) - v(T)
+\end{gather*}
+
+\end{proof}
+
+Thus, in order to keep the characteristic function convex, new web
+services should have more marginal contribution as the coalition
+size grows.
+
+Our algorithm works as follows. Given an  established community
+with a master and some member web services, a web service would send a \emph{join request} to join  the
+community. Ideally, the \emph{core}
+or \emph{$\epsilon$-core} stability of the group having this new
+member should be analyzed. As the normal core membership algorithm is computationally
+intractable, we exploit Proposition \ref{proposition1} and Equation
+\ref{eq:convex_snow} to check the convexity of our game having
+characteristic function where the new member is added. In the
+equation, let $C$  be our community members before
+having the new web service join the community. Let  ${i}$ be the new web
+service, and then verify the equation for $S$, setting $ S = T /
+W1 $ where $W1$ is the set of all possible subsets of the set $N$
+having the size $1$. We can relax the equation a bit by adding a
+constant $\epsilon$ to the left side of the equation. We call this
+method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
+satisfied for all $W1$, we let the new web service join our
+community, since the web service will contribute positively enough
+to make our new community stable. Since only subsets of size $1$
+are checked, the following Proposition holds.
+
+\begin{theorem}\label{complexity1}
+\emph{The run time complexity of Depth-1 Convex-Checker algorithm is
+$O(n)$.}
+\end{theorem}
+
+By this result, we obtain a significant reduction from $O(2^n)$,
+which is the complexity of checking all possible subsets of $N$.
+In our second method, we use the same algorithm, but this time we
+set $W2$ to be the set of all possible subsets of size two and one
+of the community $C$. We call this method \emph{Depth-2
+Convex-Checker} and its run time complexity is still
+linear:
+
+\begin{theorem}\label{complexity2}
+\emph{The run time complexity of Depth-2 Convex-Checker algorithm is
+$O(n^2)$.}
+\end{theorem}
+
+It is possible to develop an algorithm that continues the
+verification of this condition against subsets of size $3$,
+$4$, etc. until the algorithm gets interrupted.
+
+\subsection {Web Services and Many Communities}
+
+In this scenario, we consider multiple communities managed by
+multiple master web services, each of which is providing
+independent request pools (see Figure \ref{fig_sim2}). Identical
+to the first scenario, master web services form coalitions with
+web services. We use coalition structure formation methods to
+partition web services into non-empty disjoint coalition
+structures. As mentioned in Section \ref{sec:coalition}, the used
+algorithms in \cite{Sandholm:1999:CSG:317145.317152,DBLP:conf/ijcai/GrecoMPS11,DBLP:conf/ijcai/RahwanMJ11} try to
+solve key fundamental problems of what coalitions to form, and how
+to divide the payoffs among the collaborators.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=3in]{Figures/s2.eps}
+\caption{Web Services and Many Communities}
+\label{fig_sim2}
+\end{figure}
+
+In coalition-formation games, formation of the coalitions is the
+most important aspect. The solutions focus on maximizing the
+social welfare. For any coalition structure $\pi$, let
+$v_{cs}(\pi)$ denote the total worth $\sum_{C \in \pi}{v(C)}$,
+which represents the \emph{social welfare}. The solution concepts
+in this area deal with finding the maximum value for the social
+welfare over all the possible coalition structures $\pi$. There
+are $centralized$ algorithms for this end, but these approaches
+are generally NP-complete. The reason is that the number of all
+possible partitions of the set $N$ grows exponentially with the
+number of players in $N$, and the centralized algorithms need to
+iterate through all these partitions.
+%These algorithms \cite{DBLP:conf/ijcai/GrecoMPS11, DBLP:conf/ijcai/RahwanMJ11, RePEc:wpa:wuwpga:0110001} are centralized algorithms, where all the complexity.
+However these algorithms are more intractable than Core stable solutions and practical with some constraints in practice\cite{RePEc:wpa:wuwpga:0110001}.
+In our model, we propose using a distributed algorithm where each
+community master and web service can be a decision maker and
+decide for its own good. The aim is to find less complex and
+distributed algorithms for forming web services coalitions
+\cite{DBLP:journals/igtr/AptW09,Dieckmann02dynamiccoalition,ray2007game}.
+The distributed merge-and-split algorithm in
+\cite{DBLP:journals/igtr/AptW09} suits our application very well.
+It keeps splitting and merging coalitions to partitions which are
+preferred by all the players inside those coalitions.
+
+This merge-and-split algorithm is designed to be adaptable to
+different applications. One major ingredient to use such an
+algorithm is a preference relation or well-defined orders proper
+for comparing collections of different coalition partitions of the
+same set of players. Having two partition sets of players, namely
+$P = {P_1,...,P_k}$ and $Q = {Q_1,...Q_l}$, one example would be
+to use the social welfare comparison $\sum^k_{i=1}v(P_i) >
+\sum^l_{j=1}v(Q_j)$. For our scenario, we use \emph{Pareto order}
+comparison, which is an individual-value order appropriate for our
+self-interest web services. In the Pareto order, an allocation or
+partition $P$ is preferred over another $Q$ if at least one player
+improves its payoff in the new allocation and all the other
+players still maintain their payoff ($p_i \geq q_i$ with at least
+one element $p_i > q_i$).
+
+The valuation function $v(C)$ for this scenario is the same as
+\emph{``Web Services and One Community''} scenario. However, in
+order to prevent master web services joining the same community,
+we set $v(C) = 0$ when $C$ has either none, or more than one
+master web service as member.
+
+In this scenario, as new web services are discovered and get ready
+to join communities, our algorithm keeps merging and splitting
+partitions based on the preference function. The decision to merge
+or split is based on the fact that all players must benefit. The
+new web services will merge with communities if $all$ the players
+are able to improve their individual payoff, and some web services
+may split from old communities, if splitting does not decrease the
+payoff of \emph{any} web service of the community. According to
+\cite{DBLP:journals/corr/abs-cs-0605132}, this sequence of merging
+and splitting will converge to a final partition, where web
+services cannot improve their payoff. More details of this
+algorithm and analysis of generic solutions on coalition formation
+games are described in \cite{DBLP:journals/igtr/AptW09}.
+
+\subsection{Taxation, Subsiding and Community Stability}\label{s:tax}
+
+ssed $core$ as one of the prominent solution concepts in cooperative games.
+Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group.
+However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal amount of $\epsilon$ by deviating.
+Stability is an attractive property for communities.
+In addition, communities would benefit by having slightly more web services then the exact number of web services satisfying task rate cap.
+This is because  there is always a possibility that the agents may leave the community or they may under perform and degrade the quality values they were initially performing with.
+
+One way for communities to ensure  stability could be  by applying a tax, $\epsilon$ amount of cost for web services changing communities which would make deviation a costly act.
+However this would require all community coordinators to agree on a same amount of taxation, being governed by some external entities or web services would join communities with lesser amount of tax.
+Another viable solution to our scenario is to stabilize the game using external subsidies.
+The reason a gamWe discue is not stable is that the community is not making enough revenue to allocate  enough gain to the players.
+A community master can subside its community with a constant coefficient value of $\lambda$.
+
+Rewarding a community with high number of quality participants with $\lambda v(C)$, where $\lambda \leq 1$.
+
+Obviously with a big number of $\lambda$, it is always possible to stabilize the community.
+However, this can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable.
+Subsiding or taxing in order to reduce the bargaining power of sub coalitions are called $taxation$ \cite{eps346856} methods.
+
+%Thus, another way to garantee \emph{$\epsilon$-core} stability can be achieved by some surplus payments from community coordinators.
+These concepts of applying cost in coallition values in order to reduce their bargaining power are called $taxtation$ methods\cite{eps346856}.
+
+%The \emph{$\epsilon$-core} concept, in its definition, considers the willing to join or deviate from agent's point of view.
+It claims agents for any reason will be not willing to deviate to gain less than $\epsilon$ amount of profit.
+Communities can agree on However, in our case, the community master is willing to keep web services in communities too.
+There are several reasons for this, one reason is there is always possibility that agents may leave the community or they may under perform from the quality values they were initially performing with.
+To this end, our communities will reward and valuate web services in the community
+
+\section{Experimental Results and Analysis}\label{s:resutls}
+
+In this section, we discuss the experiments we performed for our
+scenarios to validate the applicability and performance of our
+proposed methods in realistic environments. We created a pool of
+web services and populated most of their \emph{QoS} parameters
+from a real world web service dataset
+\cite{DBLP:conf/smc/Al-MasriM09a}. We implemented the simulations
+using Java and executed the simulations on an Intel Xeon X3450
+machine with 6GBs of memory. For other parameters missing from the
+dataset, we used normal random distribution with parameters
+estimated using the method of maximum likelihood.
+
+One of the key criteria reflecting the performance of web service
+coalitions is the user satisfaction. User satisfaction can be
+measured in terms of quality and quantity of requests (or tasks)
+successfully answered by the communities. We initiated the
+communities with few web services, then let rejecting and
+accepting random web services go for a short number of iterations.
+After that, we started the request distribution for the communities
+and let them allocate requests among member web services.
+Thereafter, we measured the average output performance of tasks in
+communities following different methods.
+
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=3in]{Figures/task_done_opt.eps}
+\includegraphics[width=3in]{Figures/task_qos_opt.eps}
+\caption{Part (a): Cumulative number of requests successfully
+done. Part (b): Average QoS of requests performed.}
+\label{performanceall}
+\end{figure}
+
+Figure \ref{performanceall} depicts the results of optimal
+\emph{$\epsilon$-core}, \emph{Depth-1 Convex-Checker},
+\emph{Depth-2 Convex-Checker}, \emph{3-Way Satisfaction}
+\cite{DBLP:conf/IEEEscc/LimTMB12}, and \emph{2 Player
+Non-Cooperative} \cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods
+in \emph{one grand community with many web services} scenario.
+
+For the \emph{optimal core} method we have used the well known \emph{$\epsilon$-core} method as the
+taxtation method to relax the core condition to help communities, attract web services.
+We have assigned $\epsilon$ to 15\% of total community worth, $\epsilon = 0.15 \times v(C)$, which allows
+subsets of the coalition to gain maximum 15\% of $v(C)$. In the
+\emph{optimal $\epsilon$-core} method, we capped the coalition
+size to 25 web services, since the method is computationally
+intractable as number of web services increase and anything more than that would make it
+impractical to run in our simulations. In the other methods, there
+were no cap on size of the community and we had communities of
+size 60 web services at some points.
+In this scenario our community receives 30 tasks on average per iteration, from users.
+The community, after the task distribution process on each iteration, will reevaluate QoS metrics of its members and can check for new membership requests.
+Web services may join or leave the community between iterations.
+The results show that our
+\emph{depth-2 convex checker} method is performing better compared
+to the other methods and its performance is close to optimal
+\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
+and the \emph{3-Way Satisfaction} method, are also performing well.
+
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=3in]{Figures/least_core.eps}
+\caption{Analysis of \emph{$\epsilon$-core} set non-emptiness, for different values of $\epsilon$} \label{f_leastcore}
+\end{figure}
+
+As mentioned in Section \ref{s:preliminaries}, the concept of
+\emph{core}, assumes no coalition of players can gain anything by
+deviating, which is a fairly strong requirement, and that is why
+the notion of \emph{$\epsilon$-core} was introduced. Least-Core
+$e(G)$ of a game $G$, is the minimum amount of $\epsilon$ so that
+the core is not empty. We evaluated the non-emptiness of \emph{$\epsilon$-core} set using the
+valuation function and a set of web services. We picked random
+number of web services from the dataset and formed around 10,000
+random coalitions consisting of 3 to 26 web services. We choose 26
+as the maximum number of members in our coalition since it
+is computationally very complex for larger coalitions to verify whether
+\emph{$\epsilon$-core} set is empty or not.
+Also instead of considering $\epsilon$ amount of constant deviation in \emph{$\epsilon$-core} definition (Equation \ref{eq:core2}), we similarly defined \emph{relative $\epsilon$-core} concept where no coalition would benefit more than \emph{$\epsilon$ $\times$ v(C)} by deviating.
+We set $\epsilon$ between 0 and 1 and verify the \emph{relative $\epsilon$-core} set non-emptiness.
+The results in Figure
+\ref{f_leastcore} illustrates that almost 10\% of our random web
+service coalitions have non-empty \emph{core} solution and
+\emph{$\epsilon$-core} solution is \emph{always} non-empty when we
+let agents gain only 30\% more of $v(C)$ by deviating.
+
+One of the properties of coalition structure formation algorithms
+in our second scenario is that they partition web services with low
+throughput rate so that they usually join coalitions with less
+request rate. Since the characteristic function $v(C)$ and the
+fair Shapely payoff vector is proportional to web services'
+contribution, the web services with small contribution will get
+paid much less in communities having web services with high
+throughput. On the other hand, according to the valuation function
+$v(C)$, web services with high throughput will not contribute well
+to communities with low amount of user requests (low market
+share). The strong web services are likely to deviate from weak
+coalitions, joining a stronger one, which makes the initial
+coalition unstable.
+
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=3in]{Figures/s2_task_done.eps}
+\includegraphics[width=3in]{Figures/s2_task_qos.eps}
+\caption{Part (a): Cumulative number of tasks succesfully done. Part
+(b): Average QoS of tasks performed.} \label{performancemany}
+\end{figure}
+
+In Figure \ref{performancemany}, we compare our \emph{Web Services
+and many Communities} scenario with a method which ignores QoS
+parameters and forms coalitions by allowing web services to join
+only if they have enough requests for themselves. In other words,
+web services can join a community when the request rate is less
+than the throughput of all the member web services. We name this
+method \emph{Random Formation} and use it as a benchmark for our
+QoS-aware coalition formation process. In this scenario, each user individually generates randomly
+between 0 to 10 number of tasks per iteration, then the users target a community and direct their requests to the chosen community. As the results illustrate,
+our method forms better coalitions of web services improving
+performance and satisfaction for both web services and coalitions.
+
+\begin{figure}[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=2.5in]{Figures/avg_task_ws_done.eps}
+\includegraphics[width=2.5in]{Figures/avg_qos_ws_done.eps}
+\includegraphics[width=2.5in]{Figures/avg_avail_ws_done.eps}
+\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
+(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
+\end{figure}
+
+Finally, in our last experiment, we compare our work with the work
+in \cite{10.1109/TSC.2012.12} which we call it \emph{High
+Availability Coalition} method, because of nature of their
+community valuation function, which focuses on community
+availability as main consideration. Their community formation
+model is very different than ours, however we have been very
+careful to make the experiment environment as fair and similar as
+possible. We limited our maximum community size by 5 in order to
+have communities with almost the same size. In their method, they
+have used web services as backups rather than active collaborative
+players, and they only get task when the first web service in an
+ordered chain fails to perform the task. However with recent
+advancement in cloud and hardware infrastructures availability is
+less of an issue for web services, and web services are highly
+available. Part(a) of figure \ref{fig_avail_method} shows our
+method performs almost performs tasks successfully with rate of
+three times more than \emph{High Availability Coalition} method
+because of real cooperative nature and task distribution of our
+algorithm. This result shows using web services as backups, and
+not as real collabrative players is a huge waste of web service
+capability since they have very low chance of getting jobs and its
+the primary web service (the first in their coordination chain)
+which does most of the work. The average quality of service of
+tasks performed is also better since our method considers all
+quality of service metrics mentioned in Table \ref{qosws}. Part(c)
+shows the availability of community from end user point of view.
+The \emph {High Availability Coalition} method almost has 100\%
+uptime since they use web services as backups, so the chance of
+job failing reduces significantly as community members increase.
+In our method we have more chance of fail for each web service,
+however with some subsiding, and hiring a few more web service
+they can compensate the low chance of failure of web services in
+our community.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In this chapter, we introduced a new model checking technique for
-social commitments among agents interacting in uncertain settings.
-We specified properties for such systems using Probabilistic
-Computation Tree Logic of Commitments (PCTLC). The PCTLC logic
-extends PCTL with a social operator for commitments and their
-fulfillments. Target systems are modeled using a new version of
-interpreted systems which incorporates and extends two different
-versions of interpreted systems formalism to capture the
-probabilistic behavior of MASs, and account for the communication
-between interacting entities. The proposed model checking
-technique consists of a set of reduction rules to formally reduce
-the problem of model checking PCTLC to the problem of model
-checking PCTL so that the use of the PRISM model checker is made
-possible. The proposed verification approach was evaluated through
-implementing the reduction tool on top of the PRISM model checker
-and then applying it on a real case study from the cryptography
-domain namely the oblivious transfer protocol. The obtained
-results show the effectiveness of the proposed technique. In
-particular, we were successfully able to verify some desirable
-properties expressed originally in PCTLC. We also showed that the
-proposed reduction technique is scalable as we were able to perform the model checking for models made of up to $1.56*10^{18}$ states
-and transitions.
-
-%We showed that the system is scalable as we were able to perform the model checking using our approach for models made of up to $1.56*10^{18}$ states and transitions.
-In the next chapter, we investigate how our approach for probabilistic social commitments can be exploited to handle the interaction between social commitments and agents' knowledge in MASs.
+In this chapter,

### 2015-04-22 thesis/thesis/chap4/chap4.tex
changes

@@
 
-\chapter{The Interaction between Probabilistic Commitments and Knowledge}\label{cha:PCTLKC}
+\chapter{Training Chapter}\label{cha:PCTLKC}
 
-In this chapter\footnote{The results of this chapter have been published in the journal of Expert Systems with Applications \cite{Sultan2014b}.}, we
-put forward a method for capturing and verifying the interactions between the concepts of knowledge and social commitments in probabilistic MASs.
-The proposed method allows us to figure out the impact of knowledge and social commitments on each other in the presence of uncertainty.
-To express the two concepts simultaneously in systems exhibiting probabilistic behavior, we define a new modal logic called the probabilistic logic of knowledge and commitments (PCTL$^{kc}$) which combines two existing probabilistic logics namely, the probabilistic logic of knowledge (PCTLK) \cite{Wan2012,Wan2013} and the probabilistic logic of commitments (PCTLC) that has been introduced in Chapter \ref{cha:PCTLC}.
-In the current chapter, MASs are modeled using a new version of interpreted systems that captures the probabilistic behavior and accounts for the communication between interacting components.
-Based on the proposed logic, we introduce a new model checking procedure to check the compliance of target systems against some desirable properties -- with respect to knowledge and commitments-- written in PCTL$^{kc}$.
-%and report some verification results.
+\section{Introduction}
 
-\section{Introduction} \label{Introduction}
+Over the past years, online services have become an important part of many scalable business applications.
+The increasing reliance on online service providers has significantly influenced the way web services are engineered.
+Therefore, given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue.
+One practical solution towards delivering high quality services is utilizing intelligent decision making agents.
+These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users\cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Demirkan2013412, journals/tsc/ZhengZYB13, Josang:2007:STR:1225318.1225716}.
+However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided.
+Recent developments have attempted to shift web services from passive models, consisting of individual components, to models made up of autonomous and group-based components that share common goals.
+In group-based models, interaction, composition, and cooperation are the key challenges \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13} that directly impact the group's overall performance in achieving common goals.
+To that end, we see the emergence of web service \emph{communities}, which consist of services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}.
+A \emph{community} of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.
 
-The rapid increase of using software agents and MASs nowadays has led to the increasing demand of finding principled techniques for modeling and verifying such systems.
-Generally, to build effective open MASs, several aspects which have direct influence on the efficiency and effectiveness of
-the entire system must be taken into account \cite{Konur2013}.
-Among other aspects, knowledge and social commitments are of a great
-interest in MASs.
-Social commitments have been a vital approach in agent societies to capture the communication between interacting agents for more than a decade.
-On the other hand, knowledge has been addressed in distributed systems since 1960s \cite{Wan2013}.
-Recently, Al-Saqqar et al.
-\cite{Al-Saqqar2014a} have demonstrated that these two concepts are closely interacting with each other in various real life scenarios.
+The advantages of community of web services are that the community facilitates the discovery of web services and provides better quality of service compared to passive models with individual components.
+Communities act as abstract web services, communicating with external entities via the same standard protocols that a normal web service employs.
+But, they regulate the service process via sophisticated internal communication protocols, thereby providing services based on the combined work of a number of web services.
+The downside to communities is the complexity of management involved in finding and inviting individual web services and managing the overall quality of the combined work of several web services.
+% because although they have similar functionality, they have different attitudes.
+When interacting with communities of web services, users send their requests to the coordinators of the community, which play the role of community representative or access point.
+The community coordinator is responsible of receiving tasks and delivering services.
+Moreover, as community representative, it verifies the credentials of new web services before accepting them into the community and kicks web services that could harm the value of the community.
 
-Despite the large amount of work that has been done to model and represent various aspect of probabilistic MAS, none of the existing approaches addresses the concepts of knowledge and social commitments simultaneously.
-In fact, the problem of reasoning about and verifying the interaction between knowledge and social commitments in the presence of uncertainty has not been investigated yet.
-Interpreted systems formalism \cite{Fagin1995}
-and Partially Observable Markov Decision Processes POMDPs (a
-variant of MDP) are the most prominent traditions in the area of
-modeling and representing stochastic MASs. These models are used
-to traditionally interpret some logics defined to specify and
-reason about some given properties of MASs. On the one hand,
-interpreted systems formalism provides a natural and yet efficient
-way for modeling MASs at different levels of abstractions (i.e.,
-local and global). It has been extended in \cite{Halpern2003} and
-further in \cite{Wan2012,Wan2013} to capture the probabilistic
-behavior of epistemic MASs. Recently, it has been extended in
-\cite{Bentahar2012} and \cite{El-Menshawy2013a} to account for the
-communication that occur between interacting parties in
-conventional MASs. The distinct point of the extended versions of
-this formalism is that knowledge and commitments can be captured
-through the use of what is called accessibility relations. The
-accessibility relation for knowledge denotes the existence of
-equivalent states for a given agent. That is, states where the
-agent cannot distinguish between being in which one of them. For
-commitments, accessibility relations capture the existence of
-communication channel between the communicating agents and the
-transferring of information from the sender to the receiver. On
-the other hand, POMDPs have been widely used to model the
-uncertainty of knowledge and behavior for stochastic agents
-\cite{Huang2011}.
-An important point of POMDPs is that there is no distinction drawn between actions taken to change the state of the world and actions taken to gain information \cite{Kaelbling1996}.
-This is important
-because, in general, every action has both types of effect.
-However, solving these models comes at a very high computational
-cost \cite{Melo2011}. In this chapter, we aim to examine the use of interpreted systems formalism to capture not only knowledge and commitments
-independently, but also the interactions (combinations) of the two
-aspects in stochastic systems. We also intent to verify these
-interactions by means of model checking.
+\textbf{Challenge and Problem Statement.} In recent work, communities of web services have been proposed in order to facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities.
+However, there is a twofold challenge that yet to be addressed.
+The first part is community development, which involves finding the right web services for the community, satisfying the objectives of all the web services and community coordinators involved within the community; and the second part is from the individual web service's side because each web service aims to join the community that would guarantee the best outcome.
+The advocated solutions \cite{conf/webist/MaamarLBTS07, 10.1109/ARES.2008.7, journals/soca/XuYLZB11, 10.1109/TSC.2012.12, managing-hela-jalel, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:conf/IEEEscc/LimTMB12} have attempted to address these research problems.
+These research problems are reflected by the two challenge parts:
+\begin{enumerate}
+	\item The solutions consider the architecture of centralized management for communities where most of the decisions are made by the centralized coordinator.
+The problem is that in real world scenarios, decisions made by independent service providers are highly distributed.
+	\item The solutions either propose complex algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to find the optimal strategy to follow, or oversimplify the problem by eliminating important parameters and using approximation techniques to make the algorithms tractable \cite{10.1109/TSC.2012.12}.
+\end{enumerate}
+These approximation methods sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored.
 
-In terms of computational logics, most current proposals address each of knowledge and commitments in MASs independently (see for example
-\cite{Baldoni2010,Bentahar2012,Delgado2009,El-Menshawy2013a,Giordano2007,Halpern2003,Huang2011,Lomuscio2007,Pham2007,Wan2013}).
-However, in so many real world settings, these two concepts need to
-interact with each other in order to ensure rich modeling at local
-(agent) and global (MAS) levels.
-Nevertheless, it is a challenge to guarantee the correctness of the system's behavior due to the complex nature of the autonomous and heterogenous agents, especially when they have probabilistic characteristics \cite{Song2012}.
+For example, instead of calculating the gain distribution using the complex shapely-value method, \cite{10.1109/TSC.2012.12} proposes a simple egalitarian way of distributing gain, which completely ignores the gain generated from collaborative work of sub-communities.
+Other categories of related work exist that do not focus on all the parties involved within the community \cite{DBLP:conf/IEEEscc/KhosravifarABT11}.
+%And some other work which do not focus on rationality on web services or communities involved [refrences].
+In \cite{journal-community-formation} we proposed a cooperative game theory based model for aggregating web services in communities.
+A centralized decision maker in communities based on a complete knowledge of available web service quality metrics and performance, has been used to form optimal and stable communities that maximize individual and group income.
+However, centrality and complete information are strong assumptions, which are not very compatible with real business scenarios.
 
-Applying model checking techniques that were originally introduced
-for standard logics, such as LTL \cite{Pnueli1977}, CTL
-\cite{Emerson1990}, or PCTL \cite{Hansson1994}, to the
-verification of the interaction between knowledge and social
-commitments in presence of uncertainty is not straightforward as
-non of these logics can capture and express the relationship
-between knowledge and social commitments in probabilistic
-settings. In this chapter, we introduce a model checking technique to address this open issue.
+\textbf{Contributions.} In this paper, we introduce DDM, a Distributed Decision Making model for  community formation that regulates web service agents’ decision making process in terms of cooperating and deciding which group to join and which service to invite for joining.
+The decision model in extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
+The generated decision tree improves agents' understanding of the environment and how to select actions that lead towards maximizing their utilities.
+The advantage of this approach is that the tree is created from the past data and reflects comprehensive vision about agents' attitude of action selection.
+However, the tree is subject to get continuously modified to adapt with environmental changes.
+%The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems.
+The decision model provides web services with enough information which helps those services to efficiently decide and predict the outcome of their different possible collaborations.
+This model works in a distributed manner in which services are self-sufficient in decision making process and do not rely on a centralized decision making process.
+Our findings show that communities of web services can efficiently find the appropriate web service to invite for cooperation as well as allowing a single web service to find the best communities to join.
+In other words, the web services agents are equipped with a recommender system to suggest beneficial action.
+Moreover, communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
+In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their short-term and long-term goals; therefore, opting for best decision available.
 
-The motivation for the incorporation of knowledge and commitments
-in a probabilistic logic is provided by the fact that these two
-concepts not only have an impact on each other, but also their
-interaction is crucial in various real scenarios. For instance, in
-the field of mobile applications, which are complex in nature,
-there exist situations when accounting for the interaction between
-knowledge and commitments improves the output of such
-applications. Let us consider a simple scenario where receiver and
-sender agents share an agreement, in which the receiver agrees to
-pay the sender in return of the delivery of a service he has
-requested. This can be represented as a commitment, in which the
-receiver will be committed to the sender to pay once the service
-is made available for him. Now, if everything goes well and the
-receiver successfully makes his payment, the sender has to know
-that the payment is made so that he does not ask the receiver to
-pay again. Moreover, the receiver (who made the payment) has to
-know that he has fulfilled his commitment to avoid making multiple
-payments, and so on. However, those interactions are stochastic.
-For instance, the commitment to pay is not going to be surely
-satisfied.
+To effectively generate the decision model for web services, we used real data set to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another.
+The data set has been extracted by real-world QoS evaluation results from 142 users on 4,532 Web services on 64 different time slots.
+Combining these data based on each web service point of view on different time slots, we acquired 5 different unique features for 4,532 web services.
+By engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in different time slots.
+We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others.
+All paths and the outcomes are labeled to be utilized in the training model.
+Using cross validation sets, web services are able to compute the optimal hypothesis function (using logistic regression) that can be used to predict outcomes of cooperative work with other individual web services or communities.
+Our findings show that web services equipped with DDM have by far better outcomes in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.
 
-To effectively specify such properties in the face of uncertainty,
-the need for a logical tool that can express probabilistic
-knowledge and commitments simultaneously is indeed confirmed.
-Rather than building a logic from scratch to address the
-underlying aspects, we combine logics dealing with these two
-individual units in a single logic. We advocate the approach of
-combining existing logics because it ensures the preservation of
-important properties of the logics being combined
-\cite{Konur2013}. In particular, we use the independent join (or
-fusion) technique \cite{Franceschet2004}.
-Given two logics $\mathbb{A}$ and $\mathbb{B}$, we combine them in a new logic $\mathds{A} \oplus \mathds{B}$ which extends the expressive power of each one.
-In our case, suppose $\mathds{A}$ addresses probabilistic epistemic properties of
-agents and $\mathds{B}$ addresses the social aspects (i.e.,
-probabilistic commitments and their fulfilments) between
-interacting agents. Their combination should be able to not only
-express epistemic and social properties, but also express the
-interaction between the two concepts (i.e., express them in a
-single formula). Once the new combined logic is defined, we use
-the PRISM tool \cite{Kwiatkowska2002} as the formal verification tool to verify it after its reduction to PCTL, the probabilistic branching-time logic \cite{Hansson1994}.
+\section{Preliminaries and Challenging Issues}\label{s:preliminaries}
+%In this section, we first present the architecture of DDM.
+We explore the characteristics of intelligent service agents and the features we extract for training.
+To do this, we first discuss some preliminaries.
+In this section, we discuss the preliminary concepts of communities of web service and we introduce the challenges of community formation.
 
-The contributions of this chapter are threefold.
-First, we present a new probabilistic version of interpreted systems to model MASs using the dimensions of knowledge and social commitments.
-The developed version merges two extended versions of the original formalism of interpreted systems introduced by Fagin and his colleagues \cite{Fagin1995}.
-Those versions are introduced respectively by 1) Halpern \cite{Halpern2003} and extended later
-by Wan et al. \cite{Wan2012,Wan2013} to capture the stochastic
-behavior of the system; and 2) by Bentahar et al.
-\cite{Bentahar2012} and El-Menshawy et al. \cite{El-Menshawy2013a}
-to model the communication between interacting parties. Second, we
-introduce a new logic called Probabilistic Logic of Knowledge and
-Commitment (PCTL$^{kc}$) to be able to capture and reason about
-the interaction between knowledge and social commitments. The
-logic we define combines the Probabilistic Computation Tree Logic
-of Knowledge PCTLK \cite{Wan2012,Wan2013} and the Probabilistic
-Computation Tree Logic of Commitments PCTLC \cite{Sultan2013}.
-PCTLK and PCTLC are, in turn, extensions of the Probabilistic
-Computation Tree Logic PCTL \cite{Hansson1994} with an epistemic
-modality for the knowledge and a social modality for the
-commitments and their fulfilments respectively. Third, we
-introduce a new model checking technique to verify the proposed
-logic (PCTL$^{kc}$). The introduced technique is a reduction-based
-in which the problem of model checking PCTL$^{kc}$ is transformed
-into the problem of model checking an existing logic called PCTL.
-To achieve this reduction, new rules have been laid down to
-transform the models of PCTL$^{kc}$ to MDPs to be suitable for
-the PRISM model checker. We also devise some other rules to reduce
-each PCTL$^{kc}$ formula into PCTL formula. By so doing, we can
-build on the existing PRISM model checker by automating our
-translation to verify some given properties written originally in
-our new logic PCTL$^{kc}$. Figure \ref{approach-cha4} gives an overview of the proposed approach.
+\subsection{Web Services}\label{s:ws}
 
-\begin{figure}[h]
-\begin{center}
-\includegraphics [width=14cm, height=5cm]{chap4/img/approach-cha4.eps}
-  \caption{An approach for the interaction between knowledge and commitments}
-\label{approach-cha4}
-\end{center}
+In recent years, online services have become a standard part of daily life around the globe.
+Many modern applications rely on web services from different providers.
+For instance, many mobile and tablet applications that have limited storage and processing power are merely aggregating information from different online services.
+Examples are vast, including weather forecasting, ticket selling, shopping apps, local maps and location services.
+
+The World Wide Web Consortium (W3C) defines web services as ``software systems designed to support interpretable machine-to-machine interaction over a network.
+It has an interface described in a machine-processable format (specifically WSDL).
+Other systems interact with the web service in a manner prescribed by its description using SOAP messages, typically conveyed using HTTP with XML serialization in conjunction with other Web-related standards.'' When developers declare a new web service, it will be
+discovered based on its description, which fully discloses its functionalities.
+Developers also have to declare a public interface and a readable documentation to help other developers when integrating different services \cite{w3cwsdl}.
+Nowadays, web API, standards that do not require XML-based web service protocols like SOAP and WSDL are also emerging.
+They are called REST (representational state transfer) services, which are moving towards simpler communication protocols.
+%They are not restricted
+%to XML formats, recently JSON, a human readable and simpler format
+%is becoming popular among online service providers.
+
+We are not going to delve into the engineering details of online web service implementation and its protocols in this paper.
+We are interested in web services from a business model perspective.
+Service providers usually charge end users for services they provide.
+For example, Google has listed pricing and plans for a wide range of services they provide on their web service console page\footnote{https://code.google.com/apis/console}.
+
+In this paper, we abstract web services as rational agents\footnote{The term rational is used here in the sense that web services are utility maximizers} that provide services to end users.
+They aim to maximize their individual income  by receiving enough requests from end users.
+In order to increase their revenues, web services seek for more tasks if they have the capacity and throughput to do so.
+Web services can join communities to enhance efficiency by collaborating with others, to have access to broad market share, and for the opportunity to receive a bigger task pool from end users.
+Furthermore, the high reliance on web services has resulted in increased quality expectations from end users.
+Communities of web services can provide higher availability, performance, reliability, and recovery for end users.
+
+\subsection{Web Service Communities}\label{s:wsc}
+
+The community of web services is essentially a virtual group of web services having similar and complementary functionalities\cite{DBLP:journals/ijebr/MaamarSTBB09}.
+Communities aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols to those used by single web services.
+Web services join communities to increase utility by having a larger market share and task pool.
+Community coordinators are responsible for community development, managing membership requests from web services and distributing user tasks among the community members.
+Community coordinators try to attract quality web services to join and keep the community as stable and productive as possible to gain a better reputation and user satisfaction, which increases the community's market share.
+How web services reside within communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+
+\subsection{The Join Challenge}\label{s:tjc}
+Sometimes, web services can increase their overall utility by collaborating with other web services as communities.
+This collaboration helps them with better ways of sharing resources and having higher reputation, better market share and wider visibility.
+Web services and communities come with different internal and external parameters, and the long-term outcome is dependent on these parameters.
+
+The goal of all parties involved in the community is to maximize their long-term outcome while they are operating as part of the community.
+Web services need to be equipped with a selection strategy to choose from all of the different possible collaboration groups they can form as well as an estimation method for evaluating the long-term gain of joining different possible communities.
+Web services need to experiment with different possible collaborative groups and other web services in order to estimate their gain over time.
+However, with a high number of possible communities, it is not possible to test collaboration with random web services.
+Even if a linear approximate function for estimating utility based on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell_number$} growth rate of the possible number of partitions of web services into communities would make any brute-force type algorithm for the best community selection strategy intractable and impractical in real-world application settings.
+
+\subsection{Join Consequences}\label{s:jc}
+It is worth mentioning that a \emph{join} event takes place as a result of two parties that are looking to expand their collaborations.
+All actions are chosen in an attempt to enhance the overall outcome.
+However, the selected action may result in decreasing the overall utility in the long run.
+% long term.
+This is the case when a single web service joins a community, but the complex process of task allocation eliminates the visibility of the web service and, thus, the web service stays idle within the community, which makes the join action a bad decision.
+The same event might be beneficial for the community, as it hosts a new web service that can engage in performing a new coming task.
+But overall, neither side benefits from collaborating with the other and the join event has negative consequences for at least one side's utility.
+
+The more common scenario is when both parties benefit from the joining of a web service to a community.
+This action is rational, as both the web service and the community enhance the utility.
+However, the community may not be the best choice for the web service to join.
+In other words, the web service could have joined a better community, but, due to of lack of knowledge about the surrounding environment, joined the available community which was not the optimal choice.
+Since the community does enhance its utility, the web service could stay with that community, which results in a sub-optimal increase in web service's utility.
+In the following section the proposed model provides solutions that effectively address the aforementioned challenges.
+
+\section{The Model Components}\label{s:themodelcomponents}
+
+In this section, we discuss the parameters that we use in the rest of the paper. Then we present the task distribution and revenue model of our distributed web services communities.
+
+\subsection{Internal Features}\label{s:if}
+
+With a group of web services having identical or similar functionalities, QoS metrics provide nonfunctional characteristics for optimal candidate selection.
+Web service quality metrics were presented in \cite{Ardagna:2007:ASC:1263152.1263531,Menasce:2002:QIW:613357.613758,10.1109/ISSRE.2011.17}.
+We have adopted the most representative QoS properties of web services that highly influence the utility of web services.
+%We refer to a typical web service as ws_{i}.
+
+Let $C = \{ws_1,ws_2,..., ws_n\}$ be a community with $|n|$ web services. We define the following features for the group of web services based on their functional parameters:
+
+\begin{itemize}
+
+  \item \emph{Throughput $(Th_{C})$} is the rate at which a service can process requests.
+QoS measures can include the maximum throughput or a function that describes how throughput varies with load intensity.
+Throughput is a positive real number.
+For communities the expected throughput value of collaborating web services can be estimated as summation of throughputs of all the services inside:
+
+	\begin{equation}
+		 Th_{C} = \left\{
+			\begin{array}{l l}
+				Th_{w} & \quad \text{if $|C| = 1$}\\
+				\sum_{w \in C}{(Th_{w})} & \quad \text{if $|C| > 1$}
+			\end{array} \right.
+	\end{equation}
+
+	\item \emph{Availability $(A_{C})$} is the percentage of time that a service is operating.
+	The probability that the service operation is accessible.
+Availability is also a real number in the range $[0, 1]$.
+For communities the expected availability of collaborating web services considering they follow a parallel system can be estimated as:
+
+	\begin{equation}
+		A_{C} = \left\{
+			\begin{array}{l l}
+				A_{w} & \quad \text{if $|C| = 1$}\\
+				1-\prod_{w \in C}{(1-A_{w})} & \quad \text{if $|C| > 1$}
+			\end{array} \right.
+	\end{equation}
+
+	\item \emph{Execution Time $(Et_{C})$} is the time a service takes to respond to various types of requests.
+	%is the expected delay between the time instant when a request is sent and the time when the result is obtained.
+	Execution time is measured in milliseconds.
+Execution time can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests.
+This internal feature is a positive integer.
+For communities, the expected execution time of collaborating web services can be estimated as the execution time of the bottleneck service which is the service with the slowest execution time:
+
+	\begin{equation}
+		Et_{C} = \left\{
+			\begin{array}{l l}
+				Et_{w} & \quad \text{if $|C| = 1$}\\
+				max_{w \in C}{(Et_{w})} & \quad \text{if $|C| > 1$}
+			\end{array} \right.
+	\end{equation}
+
+	%\item \emph{Data Quality} The ability of a data collection to meet user requirements , defined as the proximity of a value v returned by web service to a value considered as correct.
+The measure of data quality is considered here as a real number in the range [0, 1], where 1 represents the most desirable score.
+\end{itemize}
+
+	We normalize the range of these features so that each feature contributes approximately proportionately to the final utility outcome value.
+We adopt the \emph{standardization} method.
+We subtract the \emph{mean} from each feature then we divide the values of each feature by its \emph{standard deviation}.
+
+%$HI = \overline{HI}$
+
+\subsection{External Features}\label{s:ef}
+
+The quantitative values of quality metrics need some benchmark values to represent their goodness.
+In other words, without some benchmark values it would be difficult for web services to identify their goals, and performance quality at any specific value of these metrics.
+Therefore, we have introduced two external features for assessing web services' estimate with regard to their standing among other web services.
+
+\begin{itemize}
+  \item \emph{External Parameter 1} $(exp_1)$.
+is an estimate of how close the web service's \emph{execution time} is to other web services.
+It is the difference between a web service's \emph{execution time} metric and the maximum value of execution time of all the other web services, about which the web service has information of them.
+The less value means web service has better execution time compared to other web services.
+	\begin{equation}\label{exp_1:f}
+		exp_1 = Et_{i} - Et_{max}
+	\end{equation}
+	\item \emph{External Parameter 2} $(exp_2)$ is a comparison of the web service's rate of performing tasks to other competing web services.
+It is the difference between a web service's \emph{throughput} metric and the maximum value of throughput of all the other web services,, about which the web service has information of them.
+The less value means web service has better throughput compared to other web services.
+	\begin{equation}\label{exp_2Lf}
+		exp_2 = Th_{max} - Th_{i}
+	\end{equation}
+\end{itemize}
+
+A community of web services is abstracted as a standard web service that provides services that share the same internal and external features mentioned for web services.
+Inside, they adopt different protocols to manage the community; however, other web services or end users can communicate with communities of web services, using standard protocols, and inner details will be encapsulated for their clients.
+
+\subsection{Task Distribution}
+
+Communities of web services usually employ an implementation of Contract-Net protocol for task distribution, in which services opt for incoming tasks, and receive the tasks for which they ask.
+However, in our model, our community members would try to distribute tasks based on their capabilities and the QoS parameters provided by the web services.
+We have used a slightly modified \emph{weighted fair queuing} method to distribute tasks among community members.
+The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{ws}$.
+In the \emph{weighted fair queuing} method, the input flow is multiplexed along different paths; however, in our case, if the rate of incoming tasks is less than the community's total throughput $(Th_{C})$, which is the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with a delay.
+%Thus, the amount of tasks performed by the community is $\sum_{ws}{Th_{ws}}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$.
+However, when the incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $|input Task Rate| \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) within the community.
+
+While distributing tasks, the community members can verify the performance, throughput and quality of service of tasks being performed by web services.
+The community can assess if those web services are capable of performing the number of tasks they advertised.
+If for any reason, there is a decline in the quality metric or throughput, the community can consider the new values as a benchmark for future performance calculations, and penalize the suspicious web services.
+This way, players will have incentive to truthfully disclose their actual capabilities in order to maximize profit from the community and to avoid being penalized.
+In addition, the system should be dynamic enough to detect and react to web services' quality metrics variation, as over time, web service metrics may degrade or improve, changes to which the community should adjust.
+% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities.
+Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.
+
+\subsection{Community Revenue}
+
+Communities and web services earn revenue by performing tasks.
+The total gain is a function of the quality of rate of tasks being performed.
+The utility of a collaborative group of services $U_{C}$ is the revenue of the community.
+Formula \ref{u_c_normal} is an estimation of the gain of the community.
+
+\begin{equation}\label{u_c_normal}
+U_{C} = \big((\alpha \times (A_{C} - Et_{C}) - \beta \times (exp1_{C} + exp2_{C})\big) \times Th_{C}
+\end{equation}
+
+The $\alpha$ and $\beta$ values are internal and external weight coefficients.
+Execution time and external parameters are better when they have smaller values hence the negative coefficient for them.
+The result is then multiplied to the throughput value $Th_{C}$, since communities are performing tasks with $Th_{C}$ rate.
+
+The estimation can be improved, especially in cases where the input task rate is high and services are experiencing high task loads.
+The \emph{weighted fair queuing} method of task distribution would distribute tasks based on the individual throughput $(Th_{w})$ value of services within community.
+The services with higher throughput will affect the overall utility of the community more because they would take on proportionately more tasks.
+
+\begin{equation}\label{u_c_load}
+\begin{split}
+U_{C} = \sum_{ws \in C}&\bigg(\big(\alpha \times (A_{ws} - Et_{ws}) \\
+        & - \beta \times (exp1_{ws} + exp2_{ws})\big) \times Th_{ws}\bigg)
+\end{split}
+\end{equation}
+
+\section{The Decision Making Mechanism}\label{s:model}
+
+In this section, we describe our data extraction process and the methodology used to equip web services with a decision making mechanism.
+In this methodology, we first present the data extraction and engineering process and then we evaluate the decision making mechanism for web services in community settings.
+Figure \ref{fig_steps} summarizes the steps performed in DDM from the input data to generation of decision making profiles for web services.
+
+\begin{figure}%[!t]
+\centerline{\includegraphics[width=1.75in]{figures/steps.eps}}
+\caption{A summary of DDM decision profile generation steps}
+\label{fig_steps}
 \end{figure}
 
-The work presented in this chapter represents a new trend in the direction of capturing interactions between various aspects in MASs. It can be
-seen as a first attempt to combine the notions of probability,
-knowledge, and commitments in a single tool giving a new
-expressive power ---in terms of expressing the individual aspects
-as well as their combinations in the presence of uncertainty---,
-and is therefore subject to new intuitions.
+\subsection{Data Extraction and Solution Engineering}\label{ss:learningdata}
 
-\section{The Probabilistic Logic of Knowledge and Commitment (PCTL$^{kc})$} \label{sec:PCTLKC-logic}
+\subsubsection{Input Web Services Data}\label{sss:webservices}
 
-In this section, we introduce our new probabilistic logic of knowledge and commitment (PCTL$^{kc})$.
-The modal logic we introduce can express knowledge and social commitments simultaneously in the presence of uncertainty.
-It combines two existing probabilistic logics namely, the probabilistic logic of knowledge PCTLK \cite{Wan2012,Wan2013} and the probabilistic logic of commitments PCTLC \cite{Sultan2014a,Sultan2013}.
-We first present the syntax of our new logic, and then we define its semantics.
-We also define a new version of the probabilistic interpreted systems formalism over which the semantics of PCTL$^{kc}$ can be interpreted.
+%We used a data set extracted from running web services. In this data set,
+Each web service is associated with a number of features that reflect its functionality.
+These web services operate in an online environment and are continuously assigned tasks to handle.
+Sometimes, they pass tasks around, distributing sub-tasks among themselves and handling tasks in a collaborative effort.
+To engage in communities, we add additional features that reflect web services' utility as a result of joining other web services to form a community.
+The additional features are computed based on two assumptions that we adopt for a community to be formed.
+Our raw data set provides us with 64 different time slots of extracted features for each web service.
+Using this data we can build a synthetic data set that contains features of a large number of web services in a sequence of time.
+Therefore, we train a learning model that adopts the trend of joining a community and use the model to predict/find the appropriate community for other web services.
+To train our model, we build a decision tree as a benchmark for our decision making mechanism.
+The decision tree is built by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services.
+As a result, we are able to classify web services as either single or joined and propose the communities that are best fitted to the web services' requirements.
 
-As we said earlier, the new logic PCTL$^{kc}$ contains a knowledge modality that doesn't exist in the logic defined previously in Chapter \ref{cha:PCTLC}.
-Therefore, we need first to define the model of PCTL$^{kc}$.
-In fact, the PCTL$^{kc}$ model is generated from an extended version of probabilistic interpreted systems \cite{Halpern2003,Wan2013} enriched by the social accessibility relations introduced in \cite{Bentahar2012,El-Menshawy2013a} as discussed in Chapter \ref{cha:background}.
+\subsubsection{Filtered Data}\label{sss:filtereddata}
 
-\begin{definition}[Models]\label{def:models-pctlkc}
+We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}.
+The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{http://www.wsdream.net/}.
+In this data set, each web service is associated with a number of features that reflect its functionality.
+By summarizing the data provided for each web service over different time slots, we have acquired three quality features for each individual web service.
+Their quality features are the three internal features introduced in Section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time}.
+%To engage in communities, we add two additional external features that reflect web services estimation of its quality metrics compared to other web services.
+Therefore, we have generated an array of web services with three distinct features.
 
-Given a set of atomic propositions $\Phi_p = (p,q,r, \ldots)$ and a set of agents $\texttt{Agt}=\{1,\ldots,n\}$,  the model $\mathfrak{M_2}=(S,\textbf{P},I,\sim_1, \ldots
-,\sim_n,\{\sim_{i \rightarrow j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$ is a tuple where:
+\begin{figure}%[!t]
+\centerline{\includegraphics[width=3.25in]{figures/cfvs.eps}}
+\caption{Communities with different properties of web services actively looking for other communities to collaborate with, they send collaboration requests to communities they find the collabration  increasing the gain}
+\label{fig_community}
+\end{figure}
+
+Now, we want to generate a set of feature vectors representing the communities of web services for training purposes.
+For communities, we add two additional external features, as discussed in Section \ref{s:ef} that reflect the community's estimation of its quality metrics compared to other web services.
+Therefore, we formulate a \emph{Community Feature Vector (CFV)} as $CFV_{<C>} = \{f_1,...f_5\}$ having a community of $k$ web services.
+$C = {ws_1,...ws_k}$.
+The features $f_1$ through $f_5$ represent the \emph{execution time}, \emph{throughput}, \emph{availability} and the \emph{external parameters 1 and 2} correspondingly.
+A set of communities, with their feature vectors and utilities evaluated, provides our algorithm with a raw training data set.
+We call this set of communities the \emph{template vector}, and the set of feature vectors associated with the \emph{template vector} is referred to as the \emph{community feature vector set (CFVS)}.
+Figure \ref{fig_community} depicts communities looking to form collaborate communities and join other communities in order to improve their utility gain.
+
+\subsubsection{Feature Engineering}\label{sss:feng}
+Let $CFVS = \{C_1, C_2,..., C_N\}$ be the community feature vector set with $N$ communities.
+Based on the $CFVS$ set, we create an $|N \times N|$ gain matrix for $t$ different time slots.
+Each entry of $gain_{n,m}^{t}$corresponds to a utility gain of web services in $C_n$, when $C_n$ joins $C_m$, based on community and web service data available for time $t$.
+All of these values have to be evaluated by implementing the community with members of $ws_i \in C_n$ and $ws_j \in C_m$ and evaluating its utility (see Equation \ref{u_c_load}).
+Therefore $gain_{n,m}^{t} = U_{C_n \cup C_m}^{t} - U_{C_{n}}^{t}$.
+Evaluating the utility gain for all entries of the $gain$ matrix can be a costly process with a very big number of $N$, size of the feature vector $|N|$ should be chosen carefully.
+
+\begin{table*}[ht]
+\caption{An example of $gain$ matrix for 3 different communities and their combinations} % title of Table
+\centering % used for centering table
+{\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{c|c c c c c c} % centered columns (4 columns)
+\hline\hline %inserts double horizontal lines
+ & \textless348\textgreater & \textless1934\textgreater & \textless2117\textgreater & \textless348, 1934\textgreater & \textless1934, 2117\textgreater & \textless348, 1934, 2117\textgreater \\ [0.5ex] % inserts table
+%heading
+\hline % inserts single horizontal line
+\textless348\textgreater & - & 0.282708 & 1.027081 & 0.282708 & 18.027081 & 18.027081 \\
+\textless1934\textgreater & -2.637483 & - & 6.969072 & -2.637483 & 5.509583 & 4.387725 \\
+\textless2117\textgreater & 5.027081 & 2.969072 & - & 5.509583 & 2.969072 & 5.509583 \\
+\textless348, 1934\textgreater & 0.0 & 0.0 & -3.851432 & - & -3.851432 & -3.851432 \\
+\textless1934, 2117\textgreater & 2.969072 & 0.0 & 0.0 & 2.969072 & - & 2.969072 \\
+\textless348, 1934, 2117\textgreater & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & - \\ [1ex] % [1ex] adds vertical space
+\hline %inserts single line
+\end{tabular}
+}
+\label{table:nonlin} % is used to refer this table in the text
+\end{table*}
+
+Now, we let our set of communities in the $CFVS$ set, within $|T|$ time frame iterations, choose the the best communities to join.
+Each community is provided with the corresponding row of data from the $gain$ matrix.
+Basically, $C_i$ is provided with the data in row $i$ of matrix $gain_{N,N}$, which is all of the possible utility values it can gain by joining different communities.
+By ordering the list, each community is utilized with an ordered set of preferences over other communities it likes to join.
+We define $>_{i}^t$ as the preference order of community $i$ at time $t$.
+
+Let $P_{C_i}^t = \{C_1 >_{i}^t C_2 >_{i}^t ....
+>_{i}^t C_n\}$ be an ordered set of preferences for community $C_i$ at time $t$.
+Based on this ordered set, we define $K^t(C_i, k)$ as a set of the $k$ most preferred communities of community $i$ at time $t$.
+%\subsubsection{feature vector generation}\label{sss:fvg}
+\begin{equation}\label{h_t_pref_top}
+\begin{split}				
+K^t(C_i, k) = &\Big\{C_x | C_x >_{i}^t C_y; \forall C_y \in CFVS\ \\
+				      &\wedge C_y \notin \{K^t(i, 1),K^t(i, 2),...,K^t(i, k-1)\} \Big\}				
+\end{split}
+\end{equation}
+Based on $K^t(C_i, k)$, we define a set of communities for $C_i$ in which they are the k most preferred communities for community $i$ and also community $i$ belongs to the k most preferred communities out of all of the communities in set $K^t(C_i, k)$.
+This basically implies the preference is both-sided.
+\begin{equation}\label{l_t_top_both}
+\begin{split}	
+L^t(C_i,k) = &\Big\{C_j | C_j \in K^t(C_i, k) \\
+             &\wedge C_i \in \bigcup_{C_x \in K^t(C_j, k)}K^t(C_x, k)\Big\}
+\end{split}
+\end{equation}
+
+Table \ref{table:nonlin} illustrates an example of a $gain$ matrix for 3 different communities and their combinations.
+Each row shows the gain the community can achieve by collaborating with other 5 communities.
+In this example for community $\textless 348 \textgreater$ we have: \\
+$K(\textless 348 \textgreater, 1) = \{\textless1934, 2117\textgreater\}$ and \\
+$K(\textless 348 \textgreater, 2) = \{\textless1934, 2117\textgreater, \textless1934\textgreater\}$ \\
+Since $\textless 348 \textgreater$ is best preferred community of $\textless 1934, 2117 \textgreater$ therefore $L(\textless 348 \textgreater, 1)$ is not empty and contains the community $\textless1934, 2117\textgreater$.
+
+Using the $gain$ matrix and the mentioned preference ordering relations, we are able to build a decision tree where the list of possible communities to join and their expected utilities are set.
+% as well as the joined events that took place in different time slots.
+In addition to best choices, web services have access to other ordered choices and can look for the second best or third best if their first try is rejected by the target community.
+The consequences of each try level is analyzed in more detail in the following section, in which we launch experiments and investigate the effectiveness of the use of a decision tree with different decision layers in joining other communities and enhancing the overall utility.
+
+\subsection{Decision Profile Generation}\label{ss:learningmodel}
+
+Our goal is to create a decision making profile for each community in the $CFVS$ set.
+We are creating an environment where they can experience the outcomes of different strategies.
+The result will be a decision tree of the feasible and utility increasing moves over time.
+
+We let communities pick the best communities for maximizing their utilities over different time frames.
+At time $t = 1$, we let each community in the $CFVS$ set choose the best community, which is a single community in set $C_j = K^t(C_i, 1)$.
+If community $C_j$ also has the highest preference to join $C_i$ meaning the $L^t(C_i, k=1)$ set is not empty, they would join together.
+Having set $k = 1$ is a very strict and hardly satisfiable condition.
+In order to relax the requirement, the value of $k$ is being increased by a rate $r$ proportional to time slot $t$.
+Basically, $k = 1 + |r \times t|$.
+On early steps of simulation web services and communities are more strict but as time goes on, we let them choose second and then third best options too.
+However, increasing $k$ quickly increases the time complexity of $K^t(C_i, k)$ by $O(k^2 \times n.log(n))$.
+
+When communities $C_i$ and $C_j$ are in each other's top $k$ preference set, their combination is added to the list of possible communities that can join others at time $t+1$.
+Also, for each community $C_i$ in our initial $CFVS$ set, we maintain a tree with the community $C_i$ as its root.
+Its children are all of the communities that $C_i$ decided to join.
+As the scenario progresses over time, the merged communities may decide to join other communities.
+When community $C_i$ and $C_j$ decide to join each other and create community $C_k$, the new community $C_k$ will be added as a child to both $C_i$ and $C_j$ nodes.
+At the end of the process, each community is utilized with a tree of set of possible combination of communities it can join.
+Algorithm \ref{algo:dectree} illustrates the DDM tree creation procedure as pseudo-code.
+
+Having created $|n|$ trees, for each community $C_i$, our communities are utilized with the different possible paths they can take to maximize their utilities.
+Using a distance function, communities and web services can utilize these results and find the $C_i$ that closely resembles their parameters.
+They will be utilized with a tree that has the strategies the community can use to join our communities which will be best possible path to take and communities to join while most likely being accepted by other communities since its a two sided preference.
+The algorithm below describes the tree creation process.
+
+\begin{algorithm}
+\DontPrintSemicolon
+\KwIn{$\langle r, gain^t_{n,n}, CFVS \rangle$ learning rate $r$, $|N \times N \times T|$ gain matrix, community feature vector}
+\KwOut{A set of \emph{root} nodes of the decision trees}
+$k \gets 1$\;
+$nodes[N] \gets$ initialize $N$ tree nodes representing each community in CFVS\;
+\For{$t \gets 1$ \textbf{to} $T$} {
+	$k \gets 1 + round (r \times t)$\;
+  \For{all $C_i \in CFVS$} {
+	  \For{all $C_j \in L^t(C_i, k)$} {
+      % The "l" before the If makes it so it does not expand to a second line
+      \If{$C_i \in L^t(C_j, k)$}{
+        $C_k \gets C_i \cup C_j$\;
+				add $C_k$ to $CFVS$ set\;
+				initiate $node_k$, representing $C_k$\;
+				$nodes_i.addChild (node_k)$\;
+				$nodes_j.addChild (node_k)$\;
+      }
+%      \Else{
+%        $j \gets j + 1$\;
+%      }			
+		}
+  }
+%  $i \gets i + 1$\;
+}
+\Return{nodes}\;
+\caption{{\sc DDM Decision Tree Algorithm}}
+\label{algo:dectree}
+\end{algorithm}
+
+\textbf{Complexity.} Here we analyze the computational complexity of the DDM decision tree creation algorithm on each time iteration $t$.
+Computing top $k$ preferred communities for $C_i$ in $L^t(C_i, k)$ requires an $O(n.log(n))$ sort time.
+$C_i$ has a result set of size $|k|$, and for each of those $k$ communities we need to check against their $k$ top preferred communities.
+Considering we already have the list sorted, line 6 in algorithm runs $O(k \times n.log(n))$ times.
+Doing this search for all communities in $|CFVS|$ set $n$ times (line 5), the overall order of complexity of the algorithm in regards with $n$ and $k$ is: $O(k^2 \times n^2.log(n))$.
+
+\section{Experiments}\label{s:experiments}
+We implemented DDM in Java\footnote{Source code of implementation and data is available at: \emph{https://github.com/Marooned202/DDM}}.
+We have extracted the set of features for 4532 web services in 64 different time slots through a data set provided by \cite{10.1109/ISSRE.2011.17}.
+By choosing 86 web services out of these sets and choosing a subset of all possible combinations of sizes 2, 3, and 4 of these 86 web services, we have chosen 10,000 communities and evaluated the feature vectors and utilities they can have in 64 different time slots.
+This provides us with the initial training feature set of size $|CFVS| = 10,000$ communities.
+Based on Equation \ref{u_c_load} the utility of these communities are estimated, and the gain matrix $|10000 \times~ 10000|$ of all possible ways of merging these 10,000 communities, is generated\footnote {The template vector and gain matrix generated are available at \emph{https://github.com/Marooned202/DDM/tree/master/wsds/data/run}}, and each community has the ordered preference among other communities known in the set.
+
+We let communities and web services adopt their strategies based on our $DDM$ decision making mechanism.
+Based on the decisions adopted, each community will generate a decision tree profile.
+We let DDM run four times with different $r$ rates of 0.05, 0.07, 0.10 and 0.20.
+With the slow rate of $r = 0.05$, we increase $k$ in Equation \ref{u_c_normal} for every 20 time frames, which will happen only three times in our 64-step experiment.
+In the case of $r = 0.20$, k increases much faster, at a rate of once every 5 time frames, which increases the complexity of the $L^t(C_i,k)$ search for each community in the $CFVS$ set.
+
+Table \ref{table:valueandgain} depicts the average utility gain value of the communities in each of the four runs.
+The utility gain is the increase of utility the communities gain by cooperating and joining other communities.
+The utility gain ratio is the ratio of their final utility over initial utility.
+Comparing the different search rates, we can see increasing $r$ to value of $0.10$ results in significant performance boost, however the higher rates of $r$ are not increasing the chance of finding better collaborative groups for our communities.
+
+\begin{table}[ht]
+\caption{Utility gain of web services after making collaborative groups based on DDM algorithm with different $r$ rates} % title of Table
+\centering % used for centering table
+{\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{c|c|c} % centered columns (4 columns)
+\hline\hline %inserts double horizontal lines
+Search Rate $r$ & Utility Gain Value & Utility Gain Ratio \\ [0.5ex] % inserts table
+%heading
+\hline % inserts single horizontal line
+r=0.20 & 176.1499 & 6.9690 \\
+r=0.10 & 174.6541 & 6.9182 \\
+r=0.07 & 159.9462 & 6.2834 \\
+r=0.05 & 136.0768 & 5.1032 \\ [1ex] % [1ex] adds vertical space
+\hline %inserts single line
+\end{tabular}
+}
+\label{table:valueandgain} % is used to refer this table in the text
+\end{table}
+
+%\begin{figure}%[!t]
+%\centering
+%\includegraphics[width=3.5in]{figures/utility_gain_r.eps}
+%\caption{DDM Utility Gain Value}
+%\label{utility_gain_value}
+%\end{figure}
 %
-\begin{itemize}
-\item  $S \subseteq L_1 \times \ldots \times L_n$ is a countable
-set of all reachable global states for the system. A state $s$ is
-reachable iff there exists a sequence of transitions from an
-initial state to $s$ in which the probability of each transition
-is greater than $0$.
+%\begin{figure}%[!t]
+%\centering
+%\includegraphics[width=3.5in]{figures/utility_ratio_r.eps}
+%\caption{DDM Utility Gain Ratio}
+%\label{utility_gain_ratio}
+%\end{figure}
 
-\item  $I \in S$ is an initial global state for the system.
+We utilize the same communities and web services with a simple rational decision making mechanism, in which communities will choose to join a community if it increases utility by any amount.
+We call it the $rational$ method, in the sense that it is just a rational method and is not aiming to be optimal.
+We chose 10 random web services and compared the results with web services which adopted our DDM model.
+Figure \ref{utility_gain_mlisa_and_rational} shows the comparison of the end result of utility gain values.
+In 18 out of 40 tries, \emph{rational} agents were not able to improve their utility at all because the communities they chose rejected their request, most likely because they would not have increased the utility of the other communities if they had joined them.
+The results show that a long-term strategic decision mechanism is needed to satisfy all of the services within communities.
+Figure \ref{utility_gain_mlisa_and_rational_ratio} shows the same results in terms of ratio of utility gain.
 
-\item  $\textbf{P}:S\times S\rightarrow [0,1]$ is a total
-transition probability function defined as $\textbf{P}(s,
-s')=\tau(s,a^{s \rightarrow s'}, s')$ iff there exists a joint
-action $a=(a_1,\ldots,a_n) \in ACT$ such that\\
- $\sum_{i \in \texttt{Agt}} \tau_i(l_i(s),a^{l_i(s)\rightarrow l_i(s')},l_i(s')) > 0$ and $\sum_{s' \in S} \textbf{P}(s,s') =1$
-for all $s \in S$.
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/utility_gain.eps}
+\caption{Utility Gain DDM and Rational}
+\label{utility_gain_mlisa_and_rational}
+\end{figure}
 
-\item  $\sim_i \subseteq S \times S$ is the epistemic
-  accessibility relation for the agent $i$, such that for two global states $s$ and $s'$, we have: $s \sim_i s'$ iff
-  $l_i(s)=l_i(s')$.
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/utility_ratio.eps}
+\caption{Ratio of Utility Gain DDM and Rational}
+\label{utility_gain_mlisa_and_rational_ratio}
+\end{figure}
 
-\item For each pair $(i,j) \in \texttt{Agt}^2$,
-$\sim_{i\rightarrow j} \subseteq S \times S$ is a serial social
-accessibility relation. $s \sim_{i\rightarrow j} s'$ is defined by
-the following conditions:
-      %
-  \begin{enumerate}
-       \item $l_i(s)=l_i(s')$.
-       \item $Var_i \cap Var_j \neq \emptyset$ such that $\forall x \in Var_i \cap Var_j$ we have $l^{x}_i(s)\!=\!l^{x}_j(s')$.
-       \item $\forall y \in Var_j\!-\! Var_i$ we have $l^{y}_j(s)\!=\!l^{y}_j(s')$.
-  \end{enumerate}
-       %
-  \item  $\nu : S\rightarrow 2^{\Phi_p}$ is a function valuating states with atomic propositions.
-\end{itemize}
-\end{definition}
-%
+Now, we evaluate the performance of the decision profiles generated based on our data set for other communities.% which are not included in the decision tree creation process.
+We create one thousand communities from the web services in the data set that were not involved in the decision model creation process.
+We define a distance function that measures the difference between basic features of communities, which measures the similarity of communities.
 
-The difference between our new model $\mathfrak{M_2}$ and the model $\mathfrak{M_1}$ that has been proposed in Chapter \ref{cha:PCTLC} is that $\mathfrak{M_2}$ has the ability to model agents' knowledge in the system --in addition to modeling the commitment-based communication among interacting parties-- thanks to the epistemic accessibility relations that are integrated in the model.
-Technically, $\mathfrak{M_2}$ in an extended version of $\mathfrak{M_1}$ with epistemic accessibility relations.
-Computation paths of $\mathfrak{M_2}$ and probability space are defined as in Chapter \ref{cha:PCTLC}.
-%(Section \ref{sec: semantics of PCTLC}).
+\begin{equation}\label{distance_c}
+\begin{split}
+distance (C_1, C_2) & = |Th_{C_1} - Th_{C_2}| \\
+                    & + |A_{C_1} - A_{C_2}| + |Et_{C_1} - Et_{C_2}|
+\end{split}
+\end{equation}
 
-\subsection{Syntax of PCTL$^{kc}$} \label{sec:syntax-PCTLKC}
-The logic we introduce in this section can be seen as an extension to the logic presented in Chapter \ref{cha:PCTLC} by adding an epistemic operator to PCTLC \cite{Sultan2014a,Sultan2013}.
-The resulting logic, i.e., PCTL$^{kc}$, will have the power to not only express the individual aspects of knowledge and social commitments in independent formulae, but also express combinations of the two concepts in the same formulae.
+Now, each community tries to find the closest community within the trained $CFVS$ set.
+Following its decision profile, the community can get a good estimate of the possible strategic decisions it can adopt.
+Basically, the trained profiles benefit the new web services in two ways.
+First, they provide the communities with a set of viable communities to join.
+Second, they provide an estimation of long-term utility gain for each available decision.
+In this experiment, we let communities follow the best decision within the decision tree provided to the them.
 
-\begin{definition}[Syntax]\label{def:PCTLKC syntax}
-Given a set of atomic propositions $\Phi_p$. Let $\verb"Agt"=\{1, \dots, n\}$ be a set of agents. The PCTL$^{kc}$ formulae are defined by the following BNF grammar:
-%
-\begin{align*}
-    \varphi & ::= p~|~\neg \varphi~|~\varphi \vee \varphi~|~\mathcal{K}~|~\mathcal{C}~|~ \mathbb{P}_{\bowtie k} (\psi)~|~\mathbb{P}_{\bowtie k}(\mathcal{K})|~\mathbb{P}_{\bowtie k}(\mathcal{C})\\
-    \psi & ::=\bigcirc \varphi ~ | ~ \varphi ~U~ \varphi~|~ \varphi~ U^{\leq m} ~ \varphi \\
-    \mathcal{K} & ::= K_i \varphi \\
-    \mathcal{C} & ::= C_{i\rightarrow j}\varphi ~| ~ Fu(C_{i\rightarrow j}\varphi)
-\end{align*}
-%
-where $p\in\Phi_p$ is an atomic proposition and $\mathbb{P}_{\bowtie
-k}$ is a probabilistic operator where $\bowtie \in\{<,\leq,>,\ge\}$ and $k\in [0,1]$ is a probability bound or threshold.
-$m \in\mathbb{N}^+ $ is a positive integer number reflecting the maximum number of transitions needed to reach a certain state.
-$\varphi$ and $\psi$ are state and path formulae interpreted over the states and paths of $\mathfrak{M_2}$ respectively.
-The Boolean connectives $\neg$ and $\vee$ are defined in the usual
-way.
-Formulae $\mathcal{K}$ are state formulae called knowledge (epistemic) formulae and used to express the epistemic properties through the K$_i$ operator which stands for agent i knows.
-Formulae $\mathcal{C}$, called social formulae, are special state formulae in PCTL$^{kc}$ that can express social properties using the modal connectives $C_{i\rightarrow j}$ and $Fu(C_{i\rightarrow j})$ standing for ``commitment'' and ``fulfillment of commitment'' respectively.
-$\bigcirc, U$ and $U^{\leq m}$ stand for ``next time'', ``until'' and ``bounded until'' path modal connectives
-respectively.
+\begin{table}[ht]
+\caption{Number of communities that misses the optimal decision, out of 1,000 communities} % title of Table
+\centering % used for centering table
+\begin{tabular}{|c|c|} % centered columns (4 columns)
+\hline %inserts double horizontal lines
+ Method&Miss \\ [0.5ex] % inserts table
+%heading
+\hline % inserts single horizontal line
+ DDM r=0.05& 375 \\ % inserting body of the table
+ DDM r=0.07& 137 \\
+ DDM r=0.10& 6 \\
+ DDM r=0.20& 6 \\
+Rational Method& 717 \\
+Greedy Method& 828 \\ [1ex] % [1ex] adds vertical space
+\hline %inserts single line
+\end{tabular}
+\label{fail_rate} % is used to refer this table in the text
+\end{table}
 
-\end{definition}
-
-\subsection{Semantics of PCTL$^{kc}$} \label{def:semantics-PCTLKC}
-
-Given a model $\mathfrak{M_2}=(S,\textbf{P},I,\sim_1, \ldots
-,\sim_n,\{\sim_{i \rightarrow j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$, then $(\mathfrak{M_2},s) \models \varphi$ states that ``a state $s$ in the model $\mathfrak{M_2}$ satisfies a state formula $\varphi$, $(\mathfrak{M_2},\pi) \models \psi$ means that ``a path $\pi$ in the model $\mathfrak{M_2}$ satisfies a path formula $\psi$, and
-$(\mathfrak{M_2},s) \models \mathbb{P}_{\bowtie k}(\psi)$ means that
-``a state $s$ in $\mathfrak{M_2}$ satisfies $\mathbb{P}_{\bowtie k}(\psi)$ if the probability of taking a path from $s$ that satisfies $\psi$ is in the interval specified by $\bowtie k$''.
-When the model $\mathfrak{M_2}$ is clear from the context, we simply write the satisfaction relation $\models$ as follows: $s \models \varphi$ and $\pi \models \psi$.
-Furthermore,
-for a given pair $(i,j)\in \texttt{Agt}^2$ of agents, we denote
-the number of socially accessible states $s'$ from a given state $s$ such
-that $s\sim_{i\rightarrow j}s'$ by $|s\sim_{i\rightarrow j}s'|$.
-We also denote the number of epistemically accessible states $s'$ from a given state $s$ such that $s\sim_i s'$ by $|s\sim_i s'|$.
-
-Finally, we define $|s\models \varphi|$ as follows:
-
-\begin{center}
-$|s\models \varphi|=
-\begin{cases}
-1,~~~\textrm{if}~ s\models\varphi\\
-0,~~~\textrm{otherwise.}
-\end{cases}$
-\end{center}
-
-\begin{definition}[\textbf{Satisfaction}]\label{def:semantics-pctlkc} Satisfaction of a PCTL$^{kc}$ formula in the model $\mathfrak{M_2}$ is recursively defined as follows:
-
-%\noindent In what follows, we define the semantics of PCTL$^{kc}$ formulae.
-
-\noindent $s\models p~~~~~~~~~~~~~~\emph{iff}~~p\in \nu(s);\\
-s\models \varphi_1 \vee \varphi_2 ~~~~~~\emph{iff}~~s\models \varphi_1~\textrm{or}~s \models \varphi_2; \\
-s\models \neg \varphi~~~~~~~~~~~\emph{iff}~~s \nvDash \varphi;\\
-s\models K_i \varphi  ~~~~~~~~~~ \emph{iff}~~ \forall s'\in S ~ \textrm{s.t.} ~~ s \sim_i s'  \ \textrm{we~have}~ s'\models \varphi; \\
-s\models C_{i\rightarrow j}\varphi~~~~~~~~\emph{iff} ~~\forall s' \in S~\textrm{s.t.}~s \sim_{i \rightarrow j}s', \textrm{we~have}~s' \models \varphi;\\
-s\models Fu(C_{i\rightarrow j}\varphi) ~~\emph{iff} ~~\exists s' \in S~\textrm{s.t.}~s' \sim_{i \rightarrow j}s ~ \textrm{and}~s' \models C_{i\rightarrow j}\varphi;$
-
-\noindent $\pi \models \bigcirc \varphi~~~~~~~~~~~\emph{iff}~~\pi(1) \models \varphi; \\
-\pi \models \varphi_1~U^{\leq m}~\varphi_2~~\emph{iff}~~\exists k \leq m~~\textrm{s.t.}~~ \pi(k) \models \varphi_2 ~\textrm{and}~\forall i < k, \pi(i) \models \varphi_1;\\
-\pi \models \varphi_1 ~U~\varphi_2~~~~~~\emph{iff}~~\exists m \geq 0~~\textrm{s.t.}~~\pi \models \varphi_1~U^{\leq m}~\varphi_2;$
-
-\noindent $s \models \mathbb{P}_{\bowtie k} (\psi)~~~~~~~~\emph{iff}~~Prob_s(\psi)\bowtie k$ where: $Prob_s(\psi)=Prob_s\{\pi \in \Pi(s)~|~\pi\models
-\psi\};$
-
-%\begin{itemize}
-\noindent For a probabilistic operator working on an epistemic formula, where the set of all accessible states from $s$ is our sample space and the set of events $\mathrm{F}$ is the set of states accessible from $s$ and satisfy the formula:
-
-\begin{tabbing}
-$s\models \mathbb{P}_{\bowtie k}(K_i\varphi) $
-    \ \ \ \ \ \= \emph{iff} \ $Prob(s \models K_i\varphi)$ $\bowtie k$ where: $Prob(s\models K_i\varphi)=\frac{\sum_{s \sim_i s'}|s'\models \varphi| }{|s \sim_i s'|};$
-
-\end{tabbing}
-
-\noindent For a probabilistic operator working over a commitment formula,
-where the set of all accessible states from $s$ is our sample space and the set of events $\mathrm{F}$ is the set of states satisfying the formula: %and assuming that the probabilities of accessible states from state $s$ are equally distributed:
-
-\noindent  $s\models \mathbb{P}_{\bowtie k}(C_{i\rightarrow j}\varphi)$
-   ~\emph{iff}  $Prob(s \models C_{i\rightarrow j}\varphi) \bowtie \!k$ where: $Prob(s\models C_{i\rightarrow j}\varphi)=\frac{\sum_{s \sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s \sim_{i \rightarrow j}s'| };$
-
-\noindent For a probabilistic operator working over a fulfilment formula,
- assuming that accessible states are also reachable:
-
-\noindent $s\models \mathbb{P}_{\bowtie k}(Fu(C_{i\rightarrow j}\varphi))$
-    ~~ \emph{iff}~ $Prob(s \models Fu(C_{i\rightarrow j}\varphi)) \bowtie k;$ where:
-%\vspace{-0.4cm}
-\begin{align*}
-& Prob(s\models Fu(C_{i\rightarrow j}\varphi))\ = Prob_s\{\pi \in \Pi(s') ~|~ s' \sim_{i \rightarrow j}s ~~\textrm{and}~~ \pi = s' \ldots s ~~\textrm{and}~~ s' \models C_{i\rightarrow j}\varphi\}
-\end{align*}
-
-%\end{itemize}
-\end{definition}
-
-The probabilistic knowledge is computed in such a way to reflect the indistinguishability property of the epistemic accessibility relations.
-Therefore, the probability is computed based on the number of accessible states satisfying the content of the knowledge over the number of equivalent states, as all the states are equally accessible.
-Probabilistic commitment is also computed based on the number of accessible states that satisfy the
-content over the whole number of accessible states, which demonstrates the uncertainty of the agent over the accessible states, so that over the commitment.
-Probabilistic fulfillment, however, is computed using the probabilistic transitions of the path linking the commitment state to the fulfillment state.
-The following proposition is straightforward from the semantics:
-
-\begin{proposition} \label{proposition-PCTLKC}~\\
-If $(\mathfrak{M_2},s)\models \mathbb{P}_{\leq0} (Fu(C_{i \rightarrow
-j}\varphi))$ and $(\mathfrak{M_2},s)\models Fu(C_{i \rightarrow
-j}\varphi)$, then $s$ is not reachable from the commitment state.
-\end{proposition}
-
-\begin{theorem} \label{thm: Ki equivalence} \ \ \ \ {Epistemic Equivalences}
-
-    \begin{enumerate}
-        \item $(\mathfrak{M_2},s)\models \mathbb{P}_{\geq1}(K_i\phi)$  ~~~~~iff~~  $(\mathfrak{M_2},s) \models K_i\phi$
-        \item $(\mathfrak{M_2},s)\models \mathbb{P}_{\leq 0}(K_i\phi)$   ~~~~~iff~~  $(\mathfrak{M_2},s)\models K_i \neg \phi$
-        \item $(\mathfrak{M_2},s)\models \mathbb{P}_{]0,1[}(K_i~\phi)$  ~~~iff~~   $(\mathfrak{M_2},s)\models \neg K_i\neg\phi \wedge \neg K_i\phi$
-
-    \end{enumerate}
-
-\end{theorem}
-
-\begin{proof} \hspace{-0.9cm}
+In order to evaluate the performance of the mechanism, we used \emph{Receiver Operating Characteristic (ROC) curve}, which is a graphical plot illustrating the true negative rate against the false positive rate at various threshold settings in classifier systems.
+In order to classify our communities' selection strategies correctly, for each community, we evaluated the training process by replacing the community in the set with the closest one, from which it gets the strategy profile.
+If the actions are the same and the same utility levels are gained, we classify the decision as correct.
+Otherwise, it is classified as a wrong decision.
+\emph{AUC}, the area under the \emph{ROC curve}, is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one, and the higher number reflects better performance from the better solution.
+Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of the DDM decision making mechanism.
+We compare our method with two other methods.
+The \emph{rational} method is based on the assumption that communities, as rational agents, join a community that increases their utility.
+The \emph{greedy} method only looks up the available list of communities and simply joins the community that maximizes its utility without considering any long-term strategy or other communities' acceptance scenarios, its an greedy algorithm and chooses a locally optimal choice.
+Therefore we use these two methods as our benchmark:
 
 \begin{itemize}
-\item First equivalence. ~\\
-    $``\Rightarrow"$. Assume $s\models \mathbb{P}_{\geq1} (K_i\varphi)$.
-    By the semantics of PCTL$^{kc}$, it follows that $Prob(s\models K_i\varphi)\geq1$.
-    Therefore, $\frac{\sum_{s\sim_i s'}|s'\models \varphi| }{|s\sim_i s'|}\geq1$. This means $\forall s'\in S$ such that $s\sim_i s'$, we have
-    $s'\models \varphi$ (as $\sim_i$ is reflexive, so $s'$ could be $s$ itself). Thus, $s \models K_i \varphi$. \\
-    $``\Leftarrow"$. Assume $s\models K_i\varphi$. By the PCTL$^{kc}$ semantics, it follows that for all $s'\in S$ such that $s\sim_i s'$,
-    we have $s'\models \varphi$ (i.e. all accessible states from $s$ satisfy $\varphi$).
-    Consequently, $\sum_{s\sim_i s'}|s'\models \varphi| = |s\sim_i s'|$.
-    Therefore, $\frac{\sum_{s\sim_i s'}|s'\models \varphi| }{|s\sim_i s'|}\geq1$ and hence $s\models \mathbb{P}_{\geq1} (K_i\varphi)$.
-
-\item Second equivalence. ~\\
-    $``\Rightarrow"$. Assume $s\models \mathbb{P}_{\leq0} (K_i\varphi)$.
-    By the PCTL$^{kc}$ semantics, it follows that $Prob(s\models K_i\varphi)\leq0$.
-    Thus, $\frac{\sum_{s\sim_i s'}|s'\models \varphi|}{|s\sim_i s'|}\leq0$.
-Since $\sim_i$ is reflexive, so the set of the accessible states from $s$ is not empty, therefore $\sum_{s\sim_i s'}|s'\models \varphi|$ must be 0 (i.e.
-$\varphi$ is not true in any of the accessible states).
-Consequently, for all $s'\in S$ such that $s\sim_i s'$, we have $s'\nvDash \varphi$, which means $s'\vDash \neg \varphi$.
-Hence, $s\models K_i \neg \varphi$.~\\
-%
-    $``\Leftarrow"$. Assume $s\models K_i\neg \varphi$. By the PCTL$^{kc}$ semantics, it follows that $\forall s'\in S$ such that
-    $s\sim_i s'$, we have $s'\nvDash \varphi$. Since the set of the accessible states from $s$ is not empty, then $\frac{\sum_{s\sim_i s'}|s'\models \varphi| }{|s\sim_i s'|}\leq0$.
-    Hence, $s\models \mathbb{P}_{\leq0} (K_i\varphi)$.
-
-\item Third equivalence. ~\\
-    $``\Rightarrow"$.
-Assume $s\models \mathbb{P}_{]0,1[} K_i\varphi)$.
-By the PCTL$^{kc}$ semantics, it follows that $0< Prob(s\models K_i\varphi)<1$.
-Thus, $0<\frac{\sum_{s\sim_i s'}|s'\models \varphi| }{|s \sim_i s'|}<1$.
-    This means that it would never be the case that $\sum_{s\sim_i s'}|s'\models \varphi| = |s\sim_i s'|$ nor $\sum_{s\sim_i s'}|s'\models \varphi| = 0$.
-Consequently, there exist some $s', s'' \in S$ such that $s\sim_i s'$ and $s\sim_i s''$ and $s'\models \varphi$ and $s''\models \neg \varphi$.
-Hence, it is impossible to have $\overline{s}\models \neg\varphi$ or $\overline{s}\models \varphi$ for all $\overline{s}\in S$ such that $s\sim_i \overline{s}$.
-Consequently, $s\nvDash  K_i\neg\varphi$ and $s\nvDash K_i\varphi$.
-Hence $s\models \neg K_i\neg\varphi$ and $s\models \neg K_i\varphi$.
-~\\
-    %
-    $``\Leftarrow"$.
-Assume $s\models \neg K_i\varphi$.
-By the PCTL$^{kc}$ semantics, it follows that there exists $s'\in S$ such that $s\sim_i s'$ and $s'\models \neg \varphi$.
-Consequently, it would never be the case that for all $s'\in S$ such that $s\sim_i s'$ we have $s'\models \varphi$.
-Therefore, $1>\frac{\sum_{s\sim_i s'}|s'\models \varphi| }{|s\sim_i s'|}$.
-Now assume $s\models \neg K_i\neg \varphi$.
-Therefore, $\sum_{s\sim_i s'}|s'\models \varphi| = 0$ would never be the case as some accessible states should satisfy $\varphi$.
-Consequently, $\frac{\sum_{s\sim_i s'}|s'\models \varphi| }{|s\sim_i s'|}>0$.
-Thus, $0<\frac{\sum_{s\sim_i s'}|s'\models \varphi| }{|s \sim_i s'|}<1$.
-Hence, $s\models \mathbb{P}_{]0,1[} (K_i\varphi)$.
-\end{itemize}
-\end{proof}
-
-\vspace{0.9cm}
-\begin{theorem}\label{Commitment-Equivelances}{Commitment Equivalences} ~
-
-\begin{enumerate}
-\item $(\mathfrak{M_2},s)\models \mathbb{P}_{\geq1} (C_{i \rightarrow
-j}\varphi)$ ~~~iff~~ $(\mathfrak{M_2},s)\models C_{i \rightarrow
-j}\varphi$
-
-\item $(\mathfrak{M_2},s)\models \mathbb{P}_{\leq0} (C_{i \rightarrow
-j}\varphi)$ ~~~iff~~ $(\mathfrak{M_2},s)\models C_{i \rightarrow
-j}\neg \varphi$
-
-\item $(\mathfrak{M_2},s)\models \mathbb{P}_{]0,1[} (C_{i \rightarrow
-j}\varphi)$ ~~iff~~ $(\mathfrak{M_2},s)\models \neg C_{i
-\rightarrow j}\neg\varphi \wedge \neg C_{i \rightarrow j}\varphi$
-
-\end{enumerate}
-
-\end{theorem}
-%\vspace{1cm}
-\begin{proof}\hspace{-0.9cm}
-
-\begin{itemize}
-\item First equivalence. ~\\
-    $``\Rightarrow"$. Assume $s\models \mathbb{P}_{\geq1} (C_{i \rightarrow j}\varphi)$.
-    By the PCTL$^{kc}$ semantics, it follows that $Prob(s\models C_{i\rightarrow j}\varphi)\geq1$.
-    Thus,  $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}\geq1$.
-    This means that for all $s'\in S$ such that $s\sim_{i \rightarrow j}s'$, we have
-    $s'\models \varphi$, and hence $s \models C_{i\rightarrow j}\varphi$. \\
-    $``\Leftarrow"$. Assume $s\models C_{i \rightarrow j}\varphi$. By the
-    PCTL$^{kc}$ semantics, it follows that for all $s'\in S$ such that $s\sim_{i \rightarrow j}s'$,
-    we have $s'\models \varphi$ (i.e. all accessible states from $s$ satisfy $\varphi$).
-    Consequently, $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = |s\sim_{i \rightarrow j}s'|$.
-    Therefore, $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}\geq1$
-    and hence, $s\models \mathbb{P}_{\geq1} (C_{i \rightarrow j}\varphi)$.
-
-\item Second equivalence. ~\\
-    $``\Rightarrow"$. Assume $s\models \mathbb{P}_{\leq0} (C_{i \rightarrow j}\varphi)$.
-    By the PCTL$^{kc}$ semantics, it follows that $Prob(s\models C_{i\rightarrow j}\varphi)\leq0$.
-    Thus, $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi|}{|s\sim_{i \rightarrow j}s'|}\leq0$.
-    Since the set of the accessible states from $s$ is not empty, then $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi|$
-    must be 0 (i.e. $\varphi$ is not true in any of the accessible states). Consequently, for all $s'\in S$
-    such that $s\sim_{i \rightarrow j}s'$, we have $s'\nvDash \varphi$, which means $s'\vDash \neg \varphi$.
-     Hence, $s\models C_{i\rightarrow j}\neg \varphi$.~\\
-%
-    $``\Leftarrow"$. Assume $s\models C_{i \rightarrow j}\neg \varphi$. By the PCTL$^{kc}$ semantics,
-    it follows that for all $s'\in S$ such that
-    $s\sim_{i \rightarrow j}s'$, we have $s'\nvDash \varphi$. Since the set of the accessible states from $s$ is not empty,
-    then $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}\leq0$.
-    Hence, $s\models \mathbb{P}_{\leq0} (C_{i \rightarrow j}\varphi)$.
-
-\item Third equivalence. ~\\
-    $``\Rightarrow"$. Assume $s\models \mathbb{P}_{]0,1[} (C_{i \rightarrow j}\varphi)$. By the PCTL$^{kc}$ semantics,
-    it follows that $0< Prob(s\models C_{i\rightarrow j}\varphi)<1$. Thus,
-    $0<\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s \sim_{i \rightarrow j}s'|}<1$.
-    This means that it would never be the case that $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = |s\sim_{i \rightarrow j}s'|$
-    nor $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = 0$. Consequently, there exist some $s', s'' \in S$
-    such that $s\sim_{i \rightarrow j}s'$ and $s\sim_{i \rightarrow j}s''$ and $s'\models \varphi$ and $s''\models \neg \varphi$.
-    Hence, it is impossible to have
-    $\overline{s}\models \neg\varphi$ or $\overline{s}\models \varphi$ for all $\overline{s}\in S$
-    such that $s\sim_{i \rightarrow j}\overline{s}$. Consequently,
-    $s\nvDash  C_{i \rightarrow j}\neg\varphi$ and $s\nvDash  C_{i \rightarrow
-    j}\varphi$. Hence $s\models \neg C_{i \rightarrow j}\neg\varphi$ and $s\models \neg C_{i \rightarrow j}\varphi$. ~\\
-    %
-    $``\Leftarrow"$. Assume $s\models \neg C_{i \rightarrow j}\varphi$. By the PCTL$^{kc}$ semantics,
-    it follows that there exists $s'\in S$ such that $s\sim_{i \rightarrow j}s'$ and $s'\models \neg \varphi$.
-    Consequently, it would never be the case that $s'\models \varphi$ for all $s'\in S$
-    such that $s\sim_{i \rightarrow j}s'$. Therefore,
-    $1>\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}$.
-    Now assume $s\models \neg C_{i \rightarrow j}\neg \varphi$. Therefore, $\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| = 0$
-    would never be he case as some accessible states should satisfy $\varphi$. Consequently,
-    $\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s\sim_{i \rightarrow j}s'|}>0$.
-    Thus, $0<\frac{\sum_{s\sim_{i \rightarrow j}s'}|s'\models \varphi| }{|s \sim_{i \rightarrow j}s'|}<1$.
-    Thus, $s\models \mathbb{P}_{]0,1[} (C_{i \rightarrow
-    j}\varphi)$.
+  \item {\bf Rational Method:} Communities would send a join request to any available community, which will increase the utility.
+The other community would accept the join offer if the utility gain is positive as well.
+	\item {\bf Greedy Method:} Communities do a linear search among all the available communities and send a join request to the community which results in maximum utility, The other community would accept the join offer if the utility gain is positive and the utility gain does not need to be the maximum for the community recieving the join request.
 \end{itemize}
 
-\end{proof}
+Figure \ref{roc5} compares the results for all methods.
+The two other methods have very high failure rates compared to our method.
+Table \ref{fail_rate} illustrates the number of communities that failed to find the optimal collaboration group.
+The results support the need for a long-term training model in a successful decision making process.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/roc.eps}
+\caption{RoC Curve}
+\label{roc5}
+\end{figure}
+Now, we evaluate the system-specific results from users' and communities' perspectives.
+By distributing tasks among the communities over these time frames, we evaluate the revenue for each community.
+Figure \ref{stats1} shows the overall revenue gain of communities using our method.
+Figure \ref{stats2} shows the momentarily revenue gain for each community in each time slot compared to the previous time.
+These results show that the run with the higher learning rate of $r=0.20$ starts discovering better communities to join much earlier.
+The runs with slow rates seem to find some communities to join initially, but then they slow down until later, when they start discovering new communities to join.
 
-\begin{theorem}\label{Fulfiilemt-Equivelances} {Fulfillment Equivalences}~
-
-\begin{enumerate}
-\item $(\mathfrak{M_2},s)\models \mathbb{P}_{>0} (Fu(C_{i \rightarrow
-j}\varphi))$ iff $(\mathfrak{M_2},s)\models Fu(C_{i \rightarrow
-j}\varphi)$ and $s$ is reachable from the commitment state.
-
-\item $(\mathfrak{M_2},s)\models \mathbb{P}_{\leq0} (Fu(C_{i \rightarrow
-j}\varphi))$ iff $(\mathfrak{M_2},s)\models \neg Fu(C_{i \rightarrow
-j}\varphi)$ or $s$ is not reachable from the commitment state.
-
-\end{enumerate}
-
-\end{theorem}
-
-\begin{proof} \hspace{0.5cm} \\
-The proofs of these equivalences are direct from Proposition
-\ref{proposition-PCTLKC} and the above semantics.
-
- \end{proof}
-
-\section{Model Checking PCTL$^{kc}$ Using Reduction} \label{sec:model-checking-pctlkc}
-
-In this section, we present our reduction technique to model checking PCTL$^{kc}$.
-Given a MAS represented as a probabilistic interpreted system $\mathfrak{M_2}$ and a desirable property $\varphi$ written in PCTL$^{kc}$, the problem of probabilistic model checking PCTL$^{kc}$ can be defined as: 1) establishing whether $(\mathfrak{M_2}, I)\models \varphi$,
-i.e., if $I \in Sat(\varphi)$ where $Sat(\varphi)$=$\{s\in S ~~|~~
-\mathfrak{M_2},s \models \varphi \}$ is the set of states satisfying
-$\varphi$; 2) comparing the probability of satisfying $\varphi$
-with a probability threshold $\bowtie k$, where
-$Sat(\mathbb{P}_{\bowtie k}(\varphi))=\{s\in S ~|~
-Prob_s(\varphi)\bowtie k \}$ ; or 3) computing the probability of
-$\varphi$, $(\mathfrak{M_2}, s)\models \mathbb{P}_{=?} ~(\varphi)$.
-Note that answers to the second and third queries can be: (1)
-truth values, when the specification simply asks for a comparison
-to a probability threshold; or (2) quantitative, returning the
-actual probability.
-
-Figure \ref{fig:reduction-process-PCTLKC} depicts the structure of our proposed reduction technique.
-The idea is to reduce the problem of probabilistic model checking PCTL$^{kc}$ to the problem of probabilistic model checking PCTL in order to use the PRISM model checker.
-Concretely, the proposed reduction technique consists of two processes.
-In the former one, we transform our model $\mathfrak{M_2}$ into an MDP model.
-MDPs are the standard models for describing systems with probabilistic and nondeterministic behavior \cite{Rutten2004}.
-Then, we use the notion of adversary as in \cite{Kwiatkowska2003} to resolve the nondeterminism of the MDP.
-The resulting adversaries are basically DTMC models for which we can define a unique probability measure over paths.
-The obtained DTMC models will be the input of the PRISM model checker.
-In the latter process of the reduction technique, we transform PCTL$^{kc}$ formulae into PCTL formulae.
-This is basically achieved by constructing a set of rules that formally transforms the PCTL$^{kc}$ formulae into corresponding ones in PCTL.
-
-\begin{figure}[h]
+\begin{figure}%[!t]
 \centering
-\includegraphics[width=14cm, height=7cm]{chap4/img/reduction-process-cha4.eps}
-%\includegraphics[scale=0.5]{figure1}
-\caption{The proposed reduction technique of model checking PCTL$^{kc}$}
-\label{fig:reduction-process-PCTLKC}
+\includegraphics[width=3.5in]{figures/stats1.eps}
+\caption{Overall Utility of all communities}
+\label{stats1}
 \end{figure}
 
-In a nutshell, the proposed model checking procedure is as follows. Given $\mathfrak{M_2}=(S,\textbf{P},I,\sim_1, \ldots
-,\sim_n,\{\sim_{i \rightarrow j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$, and PCTL$^{kc}$ formula $\varphi$, we have to define an MDP model $\mathfrak{M'_2}$ = $\mathscr{F}(\mathfrak{M_2})$ and PCTL formula $\mathscr{F}(\varphi)$ using the transformation function $\mathscr{F}$ such that $\mathfrak{M_2} \models \varphi$ iff $\mathscr{F}(\mathfrak{M_2})\models \mathscr{F}(\varphi)$.
-
-\begin{figure}[h]
+\begin{figure}%[!t]
 \centering
-\includegraphics[width=15cm, height=9cm]{chap4/img/relation-translation2.eps}
-%\includegraphics[scale=0.5]{figure1}
-\caption{Translating relations in $\mathfrak{M_2}$ into labeled transitions in the MDP model} \label{fig:relation-translation-PCTLKC}
+\includegraphics[width=3.5in]{figures/stats2.eps}
+\caption{Utility Gain on time}
+\label{stats2}
 \end{figure}
 
-\subsection{Transforming the Model $\mathfrak{M_2}$}
+Figure \ref{stats3} depicts the average community size over time, which essentially represents the number of new communities being formed.
+Once again, these results show that the runs with higher search rates tend to find appropriate communities to join faster.
 
-In order to transform our model $\mathfrak{M_2}=(S,\textbf{P},I,\sim_1, \ldots
-,\sim_n,\{\sim_{i \rightarrow j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$ into an MDP model $\mathfrak{M'_2}$ = $(\mathbb{S}, Act, \textsf{P}_t ,I_i, L)$, we need to define the set of actions $Act$.
-Therefore, one of the main steps that we perform in this transformation is to define the set $Act$.
-The idea is that, we translate different relations in $\mathfrak{M_2}$ into labeled transitions in $\mathfrak{M'_2}$.
-Labels (also called actions) are used to distinguish between different types of relations.
-Consequently, the three relations in $\mathfrak{M_2}$, namely transition relation, epistemic accessibility relation, and social accessibility relation are translated into labeled transitions in $\mathfrak{M'_2}$.
-Moreover, whenever we have a labeled transition representing a social accessibility relation we add the symmetric closure of it to interpret the fulfilment of the commitment.
-As depicted in Figure \ref{fig:relation-translation-PCTLKC} (assuming that $n$ is the number of agents, $1 \leq i \leq n$, and $1 \leq j \leq n$), actions $\delta, \alpha^i, \beta^{ij},$ and $\gamma^{ij}$ denote transitions defined, respectively, from the probabilistic transition relation $\textbf{P}$, the epistemic accessibility relation $\sim_i$ (to capture the semantics of knowledge), the social accessibility relation $\sim_{i \rightarrow j}$ (to capture the semantics of commitment), and the symmetric closure of the social accessibility relation (to capture the semantics of fulfilment).\\
-
-The MDP model $\mathfrak{M'_2} = (\mathbb{S}, Act, \textsf{P}_t ,I_i, L)$ can now be defined as follows:
-
-\begin{itemize}
-\item $\mathbb{S}$=$S$; $I_i$=$I$; $L$=$\nu$.
-
-\item $Act = \{\delta \} \cup \{\alpha^1, \alpha^2, \dots, \alpha^n\} \cup \{\beta^{11}, \beta^{12}, \dots, \beta^{nn}\} \cup \{\gamma^{11}, \gamma^{12}, \dots, \gamma^{nn}\}$ where $n$ is the number of agents.
-
-\item We define $\textsf{P}_t$ as the union of the transitions labeled with $\delta$ (i.e., the probabilistic transitions of $\textbf{P}$) with the probabilistic transitions labeled with $\alpha^i$, probabilistic transitions labeled with $\beta^{ij}$, and probabilistic transitions labeled with $\gamma^{ij}$.
-The probabilities of transitions labeled with $\delta$ are not manipulated but rather inherited from the probabilistic transition function $\textbf{P}$.
-However, for transitions labeled with $\alpha^i$ and emanating from the same state are given equal probabilities (i.e., equal distribution) which reflect the uncertainty of the agent over the accessible states, so that over the content of the knowledge.
-Meaning that, the probability of each transition annotated by $\alpha^i$ is equal to the probability of each other transition labeled with $\alpha^i$ emanating from the same state which is calculated by dividing one over the number of transitions labeled with $\alpha^i$.
-The probabilities of transitions labeled with $\beta^{ij}$ and $\gamma^{ij}$ are calculated in the same way.
-For states $s, s' \in \mathbb{S}$ and  action $\theta \in Act$, the function $\textsf{P}_t$ is defined as follows:
-\begin{equation*}
-    \textsf{P}_t(s, \theta , s' )=
-\begin{cases}
-    \textbf{P}(s, s'),   & \textit{if } \theta = \delta  \\
-    \frac{1}{|s\sim_i s'|},   & \textit{if } \theta = \alpha^i\\
-    \frac{1}{|s\sim_{i \rightarrow j} s'|},   & \textit{if } \theta = \beta^{ij}\\
-    \frac{1}{|s'\sim_{i \rightarrow j} s|},   & \textit{if } \theta = \gamma^{ij}.
-    \end{cases}
-    \end{equation*}
-
-\end{itemize}
-
-The induced model of applying the adversary $\sigma$ over
-$\mathfrak{M'_2}$ is a DTMC model.
-Specifically, four adversaries are defined; $\sigma_t$ over which temporal formulae are interpreted, $\sigma_e$ to capture epistemic formulae, $\sigma_c$ to capture commitment formulae, and $\sigma_f$ to capture fulfillment formulae.
-These adversaries are defined based on the following rules.
-To define $\sigma_t$, action $\delta$ is selected at every state in $\mathfrak{M'_2}$.
-For $\sigma_e$, action $\alpha^i$ has to be among the enabled actions at the knowledge state.
-Then, the adversary picks up $\alpha^i$ at that knowledge state and $\delta$ at every other state.
-Adversaries $\sigma_c$, and $\sigma_f$ are defined in the same way.
-
-\subsection{Reducing PCTL$^{kc}$ Formulae into PCTL Formulae}
-
-In this section, we introduce our reduction rules that translate PCTL$^{kc}$ formulae to PCTL formulae w.r.t given adversary $\sigma$.
-Given the adversary $\sigma_t$, the PCTL$^{kc}$ formulae are transformed
-inductively into PCTL as follows:
-
-$\mathscr{F}(p)=p$, if $p$ is an atomic proposition,
-
-$\mathscr{F}(\neg \varphi)= \neg \mathscr{F} (\varphi)$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k}(\varphi \vee \psi))=\mathbb{P}_{\bowtie k}(\mathscr{F}(\varphi) \vee \mathscr{F}(\psi))$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k}\bigcirc \varphi)=\mathbb{P}_{\bowtie k} \bigcirc \mathscr{F}(\varphi)$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k}(\varphi~ U ~ \psi))=\mathbb{P}_{\bowtie k} (\mathscr{F}(\varphi) U \mathscr{F}(\psi))$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k}(\varphi~ U^{\leq m} ~ \psi))=\mathbb{P}_{\bowtie k} (\mathscr{F}(\varphi) U^{\leq m} \mathscr{F}(\psi))$,
-
-Note that $\sigma_t$ is a DTMC model that is used to interpret only PCTL formulas.
-It cannot be used to capture the transformed formulas of knowledge and commitment as it ignores all relations except those labeled by $\delta$ (i.e., transition relations of $\textbf{P}$).
-
-Given the adversary $\sigma_e$, the PCTL$^{kc}$ epistemic formula is transformed inductively into PCTL as follows:
-
-$\mathscr{F}(K_i \varphi)= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k} K_i \varphi)= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(\varphi))$,
-
-As mentioned earlier, the adversary $\sigma_e$ is a DTMC model that captures only action $\alpha^i$ at the knowledge state and $\delta$ at all other states.
-Intuitively, transitions labeled with $\alpha^i$ represent epistemic accessibility relations and, in fact, epistemically accessible states from the knowledge state must satisfy $\varphi$.
-Back to Figure \ref{fig:relation-translation-PCTLKC} (b), it is readily seen that all next states to the knowledge state through transitions labeled with $\alpha^i$ satisfy $\mathscr{F}(\varphi)$.
-This explains why knowledge formula $K_i~\varphi$ is transformed to next operator followed by the transformation of the content of the knowledge $(i.e., \bigcirc \mathscr{F}(\varphi))$ in all paths emanating from the knowledge state.
-
-Given the adversary $\sigma_c$, the PCTL$^{kc}$ commitment formula is
-transformed inductively into PCTL as follows:
-
-$\mathscr{F}(C_{i\rightarrow j}\varphi)= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k} C_{i\rightarrow j}\varphi)= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(\varphi))$,
-
-Similar to the case of knowledge formula, Figure \ref{fig:relation-translation-PCTLKC} (c) illustrates the intuitions behind transforming the commitment formula $C_{i\rightarrow j}\varphi$ to  $\bigcirc \mathscr{F}(\varphi)$ in all baths emerging from the commitment state.
-
-Given the adversary $\sigma_f$, the PCTL$^{kc}$ fulfillment formula
-is transformed inductively into PCTL as follows:
-
-$\mathscr{F}(Fu(C_{i\rightarrow j}\varphi))= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(C_{i\rightarrow j}\varphi))= \mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k} Fu(C_{i\rightarrow j}\varphi))= \mathbb{P}_{\bowtie k} (\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(C_{i\rightarrow j}\varphi))= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$.
-
-Though the semantics of the fulfillment operator in PCTL$^{kc}$ requires the existence of a path containing the fulfilment state which must be socially accessible from the commitment state, in this transformation we notice that all next states to the fulfilment state through transitions labeled with $\gamma^{ij}$ should satisfy the commitment formula ($C_{i\rightarrow j}\varphi$).
-The reason of that is because in our transformation process, the transitions labeled with $\gamma^{ij}$ came as a result of adding the symmetric closure of transitions labeled with $\beta^{ij}$ in order to capture the semantics of the fulfilment.
-Therefore, all added transitions should satisfy the commitment formula ($C_{i\rightarrow j}\varphi$) (see Figure \ref{fig:relation-translation-PCTLKC} (c)).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{theorem}[Equivalences Satisfaction]\label{Satsisfaction-Equivelance}\hspace{0.5cm}
-
-Let $\sigma_{t}$, $\sigma_{e}$, $\sigma_{c}$, and $\sigma_f$ be the DTMC models corresponding to the adversaries that capture respectively, temporal formulae, epistemic formulae, commitment formulae, and fulfilment formulae in the model $\mathfrak{M'_2}$.
-The following equivalences hold:
-
-$(\mathfrak{M_2},s)\models p ~\text{iff}~ (\sigma_t,s) \models p$
-
-$(\mathfrak{M'_2},s)\models \neg \varphi ~\text{iff}~ (\sigma_t,s)\models\neg \mathscr{F}(\varphi)$
-
-$(\mathfrak{M_2},s)\models \mathbb{P}_{\bowtie k}(\varphi \vee \psi)
-~\text{iff}~ (\sigma_t,s) \models
-\mathbb{P}_{\bowtie k} \mathscr{F}(\varphi) \vee
-\mathbb{P}_{\bowtie k} \mathscr{F}(\psi) $
-
-$(\mathfrak{M_2},s)\models \mathbb{P}_{\bowtie k}\bigcirc\varphi ~\text{iff}~ (\sigma_t,s) \models\mathbb{P}_{\bowtie k} \bigcirc \mathscr{F}(\varphi) $
-
-$(\mathfrak{M_2},s)\models\mathbb{P}_{\bowtie k}(\varphi~ U ~ \psi) ~\text{iff}~ (\sigma_t,s) \models \mathbb{P}_{\bowtie k}(\mathscr{F}(\varphi)~ U ~\mathscr{F}(\psi))$
-
-$(\mathfrak{M_2},s)\models\mathbb{P}_{\bowtie k}(\varphi~ U^{\leq m} ~ \psi) ~\text{iff}~ (\sigma_t,s) \models \mathbb{P}_{\bowtie k}(\mathscr{F}(\varphi)~ U^{\leq m} ~\mathscr{F}(\psi))$
-
-$(\mathfrak{M_2},s)\models K_i \varphi ~\text{iff}~ (\sigma_e,s)\models \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$
-
-$(\mathfrak{M_2},s)\models \mathbb{P}_{\bowtie k}K_i \varphi ~\text{iff}~ (\sigma_e,s) \models \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi)))$
-
-$(\mathfrak{M_2},s)\models C_{i \rightarrow j}\varphi ~\text{iff}~ (\sigma_c,s)\models \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$
-
-$(\mathfrak{M_2},s)\models \mathbb{P}_{\bowtie k}C_{i \rightarrow j}\varphi ~\text{iff}~ (\sigma_c,s) \models \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi)))$
-
-$(\mathfrak{M_2},s)\models Fu(C_{i \rightarrow j}\varphi) ~\text{iff}~ (\sigma_f,s) \models \mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$
-
-$(\mathfrak{M_2},s)\models \mathbb{P}_{\bowtie k}Fu(C_{i \rightarrow j}\varphi) ~\text{iff}~ (\sigma_f,s) \models \mathbb{P}_{\bowtie k} (\mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))))$
-
-\end{theorem}
-
-Notice that each formula has to be interpreted over a DTMC model
-(adversary) that is used to solve the nondeterminism in
-$\mathfrak{M'_2}$ based on the type of the formula (i.e.,
-temporal, epistemic, or social). The proof of the theorem with
-regard to PCTL formulae is straightforward as PCTL formulae are
-also PCTL$^{kc}$ formulae. However, for epistemic and social
-formulae, the proof is given in Theorem \ref{soundness-PCTLKC}.
-%that discusses the soundness of the  transformation rules.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{theorem}[Soundness and Completeness of $\mathscr{F}$]\label{soundness-PCTLKC}
-Let $\mathfrak{M_2}$ and $\Phi$ be respectively a PCTL$^{kc}$ model
-and formula and let $\mathscr{F}(\mathfrak{M_2})$  and $\mathscr{F}(\Phi)$ be the corresponding model and formula in PCTL.
-We have $\mathfrak{M_2}\models\Phi$ iff $\mathscr{F}(\mathfrak{M_2}) \models \mathscr{F}(\Phi)$.
-\end{theorem}
-
-%\begin{proof}$~\\$
-\begin{proof} \hspace{0.5cm} \\
-To prove the soundness of the proposed reduction technique, we have to prove that the following three cases are sound: $\Phi =
-K_i\varphi$, $\Phi = C_{i \rightarrow j} \varphi$ and $\Phi = Fu(C_{i \rightarrow j} \varphi)$. We prove this by induction on the structure of the formula
-$\Phi$. The case of PCTL$^{kc}$ formulae that are also PCTL formulae is straightforward.
-
-\begin{itemize}
-\item $\Phi = K_i ~\varphi$.
-We have $(\mathfrak{M_2},s)\models K_i ~\varphi ~\text{iff}~ (\mathfrak{M_2},s') \models \varphi$ for every $s' \in S ~\textrm{such that}~ s\sim_i s'$.
-Therefore, $(\mathfrak{M_2},s)\models K_i ~\varphi ~\text{iff}~ (\mathscr{F}(\mathfrak{M_2}),s) \models \mathscr{F}(K_i~\varphi)$.
-Recall that $\mathscr{F}(\mathfrak{M_2})= \mathfrak{M'_2}$.
-Now, $(\mathfrak{M'_2},s) \models \mathscr{F}(K_i~\varphi)$ iff for every $s' \in \mathbb{S} ~\textrm{such that}~ (s,\alpha^i,s') \in \textsf{P}_t$, we have $(\mathfrak{M'_2},s') \models \mathscr{F}(\varphi)$.
-However, w.r.t the semantics of $~\sigma_e$ which is an adversary defined to interpret commitment formulae over $\mathfrak{M'_2}$, it follows that every infinite path $\pi \in \Pi^{\sigma_e}(s)$ satisfies that $\pi(1)=s'$ and $(\sigma_e,\pi(1))\models \mathscr{F}(\varphi)$.
-Thus, $(\sigma_e,s)\models \bigcirc\mathscr{F}(\varphi)$ for all $\pi \in \Pi^{\sigma_e}(s)$.
-As the path quantifier $A$ is not defined in PCTL, and we have $\mathbb{P}_{\geq1}$ instead, so we obtain $(\sigma_e,s)\models \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$.
-
-\item $\Phi = C_{i \rightarrow j} \varphi$.
-We have $(\mathfrak{M_2},s)\models C_{i\rightarrow j}\varphi ~\text{iff}~ (\mathfrak{M_2},s') \models \varphi$ for every $s' \in S ~\textrm{such that}~ s\sim_{i \rightarrow j}s'$.
-Consequently, $(\mathfrak{M_2},s) \models C_{i\rightarrow j} \varphi ~\text{iff}~ (\mathfrak{M'_2},s) \models \mathscr{F}(C_{i\rightarrow j} \varphi)$.
-It follows that, $(\mathfrak{M'_2},s) \models  \mathscr{F}(C_{i\rightarrow j}\varphi)$ iff for every $s' \in \mathbb{S} ~\textrm{such that}~ (s,\beta^{ij},s') \in \textsf{P}_t$, we have $(\mathfrak{M'_2},s') \models  \mathscr{F}(\varphi)$.
-Now, based on the adversary $~\sigma_c$ which is defined to interpret commitment formulae over $\mathfrak{M'_2}$, every infinite path $\pi \in \Pi^{\sigma_c}(s)$ satisfies that $\pi(1)=s'$ and $(\sigma_c,\pi(1))\models \mathscr{F}(\varphi)$.
-Thus, $(\sigma_c,s)\models \bigcirc\mathscr{F}(\varphi)$ for all $\pi \in \Pi^{\sigma_c}(s)$.
-As the path quantifier $A$ is not defined in PCTL, and we have $\mathbb{P}_{\geq1}$ instead, so we obtain $(\sigma_c,s)\models  \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$.
-
-\item $\Phi = Fu(C_{i \rightarrow j} \varphi)$. We have
-$(\mathfrak{M_2},s)\models Fu(C_{i\rightarrow j}\varphi)$ iff there exists $s'\in S$ such that $s'\sim_{i \rightarrow j}s~ \text{and~}(\mathfrak{M_2},s')\models C_{i \rightarrow j}\varphi$.
-Consequently, $(\mathfrak{M'_2},s)\models \mathscr{F}(Fu(C_{i\rightarrow j}\varphi))$ iff there exists $s' \in \mathbb{S}$ such that $(s,\gamma^{ij},s') \in \textsf{P}_t$ and
-$(\mathfrak{M'_2},s') \models \mathscr{F}(C_{i \rightarrow j}\varphi)$.
-Now, w.r.t the adversary $\sigma_f$ which is defined to interpret fulfillment formulae over $\mathfrak{M'_2}$, we obtain at least one infinite path $\pi \in \Pi^{\sigma_f}(s)$ that satisfies $\pi(1)=s'$ and
-$(\sigma_f,\pi(1))\models \mathscr{F}(C_{i \rightarrow j}\varphi)$. Since $E$ is equivalent to $\mathbb{P}_{>0}$ and $\mathscr{F}(C_{i \rightarrow j}\varphi)$ is equivalent to
-$\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$, so we obtain $(\sigma_f,s)\models \mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$.
-
-\end{itemize}
-
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Implementation}\label{sec:Case-Study-cha4}
-In this section, a case study is implemented using
-PRISM \cite{Kwiatkowska2002} to verify knowledge, commitments,
-and interactions between the two concepts in probabilistic MASs. We
-apply the approach using the NetBill protocol
-as in \cite{El-Menshawy2013a,Mallya2007,Yolum2002}. NetBill protocol
-is developed for buying and selling encrypted software through the internet. We add probability to the original protocol so that the protocol will be
-closer to the real world situation. There are many interactions
-and communications between a buyer and a seller with NetBill protocol, and they are subject to several stochastic events, such as a buyer's request
-for a quote could be successfully received by the seller in only
-95\% of the cases. Another example is the buyer will satisfy his
-delivery commitment with 98\% of probability.
-As we said before, those probabilities could be generally obtained after observing the system behavior for long time.
-We will introduce this modified probabilistic NetBill protocol next.
-
-\subsection{NetBill Protocol}
-
-The basic NetBill protocol involves one customer agent \emph{Cus} and one
-merchant agent \emph{Mer} interacting to finish an online shopping
-process. This protocol can also be applied to more than one
-customer and one merchant. A customer \emph{Cus} requests a quote
-from the merchant \emph{Mer} for an item to initialize the
-protocol. We assume that 5\% of these requirements will fail to be
-sent to the merchant due to internet connection issues. The
-merchant replies to the successfully delivered request by
-presenting a quote for the requested item. Having received the quote, we assume that 20\% of customers reject the offer and
-end the protocol without any purchase. The other 80\% of customers
-accept the offer.
-Accepting the offer means that the customer commits to send the payment to the merchant ($C_{Cus\rightarrow Mer}Pay$).
-We assume that only 90\% of payment commitments will be fulfilled
-($Fu(C_{Cus\rightarrow Mer}Pay)$) and 10\% will be nullified. Both
-customer and merchant agents will be aware if the customer
-fulfills its commitments. When the merchant agent receives the
-payment, then it will commit to deliver the items to the customer
-($C_{Mer\rightarrow Cur}Deliver$). Suppose that 99\% of deliveries
-are successful, which means that the merchant fulfills its
-commitments ($Fu(C_{Mer\rightarrow Cur}Deliver)$). If the delivery fails,
-the merchant violates its commitment and in this case the merchant should refund the customer. Figure \ref{NetBill} depicts the model of the modified NetBill protocol.
-
-\begin{figure}[!h]
-\begin{center}
-\includegraphics[width=14cm,height=8cm]{chap4/img/Netbill.eps}
-\caption{The Modified NetBill protocol} \label{NetBill}
-\end{center}
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/stats3.eps}
+\caption{Average Community Size}
+\label{stats3}
 \end{figure}
 
-With the PRISM modeling language, we translate every agent into a
-\emph{module} and the entire MAS is defined as a system with \emph{agent modules} which are all synchronized.
+\section{Related Work}\label{s:related_work}
 
-To formalize the protocol, the scenario is encoded using the
-probabilistic interpreted systems $\mathfrak{M_2}$ introduced earlier in Definition \ref{def:models-pctlkc}. Two basic modules, \emph{module
-Mer1} and \emph{module Cur1} are defined according to their
-probabilistic transitions. They represent the customer agent
-\emph{Cus1} and the merchant agent \emph{Mer1} respectively. Other
-agents can just refer to these two basic agents and use
-\emph{module renaming} function to duplicate a module.
+In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
+defined communities as \emph{Service Containers} that aggregate
+substitutable web services providing a common functionality (same
+set of operations). They abstracted \emph{Service Containers} as
+web services that are created, advertised, discovered and invoked
+just as elementary web services. The \emph{Container} is
+considered as a manager that is responsible for web service
+selection upon receiving a request on run-time. The authors have
+proposed a scoring service based on non-functional requirements of
+the request and web service capabilities to dynamically chose the
+web service to perform the requested task. A similar concept was
+proposed by Maamar et al. in
+\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
+web service communities as a collection of web services with a
+common functionality but different QoS properties. A community
+manager, upon receiving a request, delegates the request to one of
+its current members. The choice is based on the performance
+history and quality metrics of each web service. The authors have
+proposed an efficient global web service selection algorithm in
+order to approach quality constraints and preferences for
+composite services which require aggregation of different types of
+services to satisfy the user.
 
-\subsection{NetBill Protocol Properties}
+Benslimane et al. \cite{Liris-2770} have proposed a multi-layer
+approach grouping similar Web services into communities and having
+an interface implemented as an abstract web service for accessing
+the community on top of the community layer. The interactions
+between composite, management and community layers and the
+bindings are performed by a generic driver called Open Software
+Connectivity (OSC).
 
-\begin{itemize}
-\item \texttt{Safety property:} When designing a system, we may set a confidence interval to allow some mistakes for properties because it seems impossible for human beings not to make any mistake in the real world.
-For example, ``with 99\% chance, the system will not fail" instead of ``the system will never fail".
-In our protocol, one bad situation is when the customer $Cus1$ sends the payment to the merchant $Mer1$ without the merchant being aware of that.
-The following property can avoid this bad situation:
+In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
+service communities with centralized access across distributed web
+services. They have proposed a framework for web service
+management, query resolution among communities and a query caching
+mechanism executed by the manager to improve the performance of
+query resolution process among many distributed communities. The
+key idea is to cache previous computed results for answering
+future queries.
 
-$\varphi_1 = \mathbb{P}_{= 1}$ $[\neg (Fu(C_{Cus1\rightarrow Mer1}Pay)
-\wedge  (\neg K_{Mer1}Pay))]$.
+Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
+then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
+proposed an architecture utilizing \emph{Contract-Net} protocol
+for engineering task distribution within communities of web
+services. The protocol is centrally executed by the community
+manager. This architecture has been further developed in
+\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
+conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
+roles have been distinguished for community members: masters and
+slaves. Master web services and community managers that lead
+communities and are responsible for membership management. They
+can invite and convince slave web services to join the community,
+and attract new slave web services to their communities by
+awarding them better payoff. Moreover, they can eject some slave
+members from the community to improve its overall reputation if
+these members are misbehaving or cannot provide the promised QoS.
 
-This event is critical without any uncertainty. Therefore, we
-set the probability to 1.
-A similar formula is when the customer fulfills its commitments,
-but it turns out that it is not aware of:
+In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
+developed a community as a ``cluster'' that groups Web services
+based on a specific area of interest. All web services in a given
+community share the same functionality. These communities are
+created by \emph{third party community providers} which use the
+\emph{community ontology} as a template and define a set of
+operations that all web services within a community should
+provide. Using semantic analysis on web service operations, web
+services either find and join a community with similar
+functionality or create a new operation description for a new
+community. The authors have described the concept of
+\emph{community agents} associated to \emph{community providers}.
+A community agent is responsible, among other things, of the
+registration of services with the community. An example of a
+community that provides health care services to senior citizens
+has been used. In this example, a governmental entity is needed to
+check the health care standards used by the members before
+authorizing them to be part of the community. Such a central
+entity is represented by the community agent. Thus, community
+agents are playing the role of community managers. In a close work
+\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
+global planning selection algorithm and a delegation algorithm to
+be run when a request to execute an operation is received by the
+community. This needs a central entity to run those algorithms.
+Such entity plays the same role as the community coordinator or
+manager.
 
-$\varphi_2 = \mathbb{P}_{= 1}$ $[\neg (Fu(C_{Cus1\rightarrow Mer1}Pay) \wedge  (\neg K_{Cus1}Pay))]$.
+Most of the recent work on communities of services are either
+user-centric and focus on user satisfaction
+\cite{Chun02user-centricperformance} or system-centric and focus
+on the whole system throughput, performance and utilization. There
+are many contributions in distributed, grid, cluster and cloud
+services which are system-centric. However, in real world
+environments and applications, both users and service providers
+are self-interested agents, aiming to maximize their own profit.
+In those environments, both parties (users and services) will
+collaborate as long as they are getting more benefits and payoff.
 
-With 1\% tolerance for missing delivery, we can define the third
-\emph{safety  property}  in our logic as follows:
+In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
+DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
+mechanisms to help users and services maximize their gain. A
+two-player non-cooperative game between web services and community
+master was introduced in
+\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this game-theoretic
+model, the strategies available to a web service when facing a new
+community are requesting to join the community, accepting the
+master's invitation to join the community, or refusing the
+invitation to join. The set of strategies for communities are
+inviting the web service or refusing the web service's join
+request. Based on their capacity, market share and reputation, the
+two players have different sets of utilities over the strategy
+profiles of the game. The main limits of this game model are: 1)
+its consideration of only three quality parameters, while the
+other factors are simply ignored; and 2) the non-consideration of
+the web services already residing within the community. The game
+is only between the community master and the new web service, and
+the inputs from all the other members and their influence on the
+master's decision are simply ignored. The consideration of those
+inputs and this influence factor is a significant issue as
+existing web services can lose utility or payoff because of the
+new member, which can result in an unhealthy and unstable group.
+The problem comes from the fact that the existing members should
+collaborate with the new web services, so probably their
+performance as a group can suffer. Existing members may even
+deviate and try to join other communities if they are unsatisfied.
+Those considerations of forming stable and efficient coalitions
+are the main contributions of our paper.
 
-$\varphi_3 = \mathbb{P}_{\geq 0.99}$ $[\neg (Fu(C_{Cus1 \rightarrow Mer1} Pay) \wedge
-\neg (C_{Mer1\rightarrow Cur1} Delivery))]$.
+In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
+for selecting web services has been proposed. In this approach,
+the authors proposed a web service selection process that the
+community masters can use. The approach considers the efficiency
+of all the three involved parties, namely users, web services and
+communities. In this work, it is shown how the gains of these
+parties are coupled together using a linear optimization process.
+However, the optimization problem in this solution tends to
+optimize some parameters considering all web services regardless
+of their efficiency and contribution to the community's welfare.
+Moreover, there are no clear thresholds for accepting or rejecting
+new web services. The solution of the optimization problem could,
+for instance, suggest web services already residing within the
+community to increase or decrease their capacity to cover up the
+weakness of other parties in the system. However, a high
+performing web service could deviate anytime it finds itself
+unsatisfied within the community instead of adjusting its service
+parameters.
 
-\item \texttt{Liveness property:} Contrast to \emph{safety property}, a \emph{liveness property } means ``a good thing will eventually happen".
-For example, when the merchant commits to deliver the goods to the customer, it will eventually deliver them.
-This property is expressed as follows:
+In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
+autonomous web services based on coalitional game theory has been
+introduced. The authors have proposed an interesting algorithm to
+reach individually stable coalition partition for web services in
+order to maximize their efficiency. The communities choose new web
+services on the promise that it would benefit the community
+without decreasing any other web service's income. In the proposed
+model, the worth of community is evaluated with high emphasis on
+the availability metric and considering price and cost values
+only. The community structure is based on a coordination chain,
+where a web service is considered as a \emph{primary} web service
+and the community task-distribution method initially invokes the
+primary web service and only if the primary web service is
+unavailable, the method invokes the next backup web services as
+they are ordered in the coordination chain. We believe that this
+coordination chain limits the cooperation power as it introduces a
+sort of hierarchy. However, in pure and open cooperative models,
+such as the one we propose in this paper, active cooperation
+activities engaging simultaneously many agents so that they can
+perform the tasks more efficiently are being used. Moreover, if
+the availability is high, which is the case nowadays with the
+recent advancements in cloud and hardware infrastructures, the
+backup web services will end-up having a very low chance of
+getting jobs, especially the ones further in the chain. This will
+results in a considerable waste of web services capabilities.
 
-$\varphi_4 = \mathbb{P}_{\geq 0.99}(C_{Mer1 \rightarrow Cus1} Deliver\Rightarrow$
-$\mathbb{P}_{\ge 0} [\text{F } Fu(C_{Mer1 \rightarrow Cus1} Deliver)]) $.
-
-\item \texttt{Reachability property:} One good example for the reachability property for the NetBill protocol is that the merchant will eventually commit towards the customer to deliver the required goods, which should be reached from the initial state.
-This property can be expressed as follows:
-
-$\varphi_5 = \mathbb{P}_{\geq 0}$ [F $C_{Mer1 \rightarrow Cus1} Deliver$]
-
-\item \texttt{Quantitative properties:} One important usage for probabilistic model checking is to compute the actual probability of some behaviors of the system.
-We can calculate the probability for eventually the customer $Cus1$ commits to send the payment to the merchant $Mer1$ and eventually the customer fulfills the commitment:
-
-$\varphi_6 = \mathbb{P}_{=?}$ [F $C_{Cur1 \rightarrow Mer1} Pay$]
-
-$\varphi_7 = \mathbb{P}_{=?}$ [F $Fu(C_{Cur1 \rightarrow Mer1} Pay)$]
-
-\end{itemize}
-
-\subsection{Experimental Results}\label{sec:Experimental-results-cha4}
-
-We verified several probabilistic epistemic and commitment
-properties as well as combinations made up from both properties
-for the NetBill protocol. The presented experiments were
-performed on a Toshiba Port\'{e}g\'{e} computer
-with 2.00 GHz Intel Core2 Duo T6400 processor and 3GB memory under
-64-bit Windows Vista Operating System.
-
-\begin{table} %[!htbp]
-\centering \caption{Experimental results for NetBill protocol with
-PRISM} \label{tab:result-cha4}
-\begin{tabular}{|c|l|l|c|c|}
-    \hline
-    \texttt{Number}& \multicolumn{2}{c|}{\texttt{Model}} & \multicolumn{2}{c|}{\texttt{Construction}}\\
-    \cline{2-5}
-    \texttt{of Agents}  & \texttt{\#States} & \ \ \ \texttt{\#Transitions} & \texttt{Iterations} & \texttt{Time (sec)} \\
-    \cline{1-5}
-    \hline
-    \hline
-    2 &  19 & \ \ \ 39 & $7$ & $0.001$\\
-    \hline
-    $3$ &  $108$ & \ \ \ $432$ & $10$ & $0.008$\\
-    \hline
-    $4$ &  $979$ & \ \ \ $3.2*10^3$ & $13$ & $0.011$\\
-    \hline
-    $5$ &   $6.1*10^3$ & \ \ \ $24*10^3$ & $16$ & $0.024$\\
-    \hline
-    6 &  $38*10^3$ & \ \ \ $171*10^3$ & 19 & 0.028\\
-    \hline
-    7 &   $230*10^3$ & \ \ \ $1.1*10^6$ & 22 & 0.035\\
-    \hline
-    8 &   $1.4*10^6$ & \ \ \ $7.8*10^6$ & 25 & 0.049\\
-    \hline
-    9 &   $8.4*10^6$ & \ \ \ $52*10^6$ & 28 & 0.071\\
-    \hline
-    10 &  $50*10^6$ & \ \ \ $343*10^6$    & 31 & 0.097\\
-    \hline
-    15 & $392*10^9$ & \ \ \ $3.8*10^{12}$ & 46 & 0.498\\
-    \hline
-\end{tabular}
-\end{table}
-
-We have conducted 10 experiments for the protocol using up to 15
-agents. The results are in Table \ref{tab:result-cha4}. Model
-statistics data (number of states and number of transitions) and
-model construction information (iteration and construction time)
-are reported. The model statistics data reflect the state space,
-while the construction information indicates the time for
-converting the PRISM model into a symbolic model and iterations required to find the reachable states. We have noticed that the state space increases
-exponentially as the number of agents increases. However, the time
-needed for constructing the model increases polynomially as more
-agents are added as shown in Figure \ref{Building the model-cha4}.
-
-\begin{figure}%[!h]
-\begin{center}
-\includegraphics[width=10cm,height=6cm]{chap4/img/time-for-building-model.eps}
-\caption{Model construction time for the NetBill protocol} \label{Building the model-cha4}
-\end{center}
-\end{figure}
-
-We verified properties expressing some requirements of the NetBill
-protocol that involve probabilistic knowledge and commitments. We
-checked \emph{Safety, liveness,} and \emph{Reachability}
-properties as discussed above. Table \ref{formulae-PRISM-results-cha4} shows the results of model checking the above desirable properties for the
-probabilistic \emph{NetBill protocol} for a system that includes
-one customer and one merchant.
-
-\begin{table}%[H]
-\centering \caption{Verifying some PCTL$^{kc}$ properties for the NetBill protocol in case of two agents} \label{formulae-PRISM-results-cha4}
-\begin{tabular}{|c|c|c|}
-\hline
-\texttt{Formulae}    & \texttt{Results} & \texttt{Time for MC (sec)} \\
-\hline\hline
-$\varphi_1$                &True           &  0.001     \\
-\hline
-$\varphi_2$               &True           &  0.001     \\
-\hline
-$\varphi_3$                &True           & 0.008    \\
-\hline
-$\varphi_4$                &True          & 0.001   \\
-\hline
-$\varphi_5$                &True           &  0.008  \\
-\hline
-$\varphi_6$                &0.80           &  0.002  \\
-\hline
-$\varphi_7$                &0.72           &  0.001  \\
-\hline
-
-\end{tabular}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Discussion} \label{sec:discussion-cha4}
-
-As we have seen in this chapter, a probabilistic logic for addressing the interaction between knowledge and social commitments in MASs was introduced.
-The described approach represents the first attempt in the literature to reason about and verify the interaction between the two concepts in the presence of uncertainty.
-However, from a consistency point of view, the logic we proposed seems to be inconsistent and suffers from some paradoxes like those identified in \cite{Al-Saqqar2014a}.
-The problem is that, one of the underlying logics of PCTL$^{kc}$, which is PCTLC \cite{Sultan2013}, is built using the social accessibility relation given in \cite{Bentahar2012,El-Menshawy2013a} which, in fact, over specifies and over constrains the concept of illocutionary communication.
-
-In the next chapter, we see how we will overcome the aforementioned problem by extending a consisting logic of knowledge and commitment called CTLKC$^+$ \cite{Al-Saqqar2014a} by a probabilistic operator so that capturing and reasoning about the interaction between the concepts of knowledge and social commitments by means of a consistence probabilistic logic becomes possible.
-Moreover, the logic we introduce in Chapter \ref{cha:PCTLKC+} incorporates the concepts of group social commitments and group knowledge to the framework.
-
-\section{Related Work} \label{sec:related-work-cha4}
-
-The work presented in this chapter can be related to three perspectives
-in the literature: probabilistic knowledge, probabilistic commitments,
-and the interaction between the two aspects. In this section,
-we review the relevant work with respect to probabilistic knowledge
-and the interaction between probabilistic knowledge and probabilistic
-commitments. However, for the relevant work on probabilistic
-commitments, it has been discussed in Chapter \ref{cha:PCTLC}, Section \ref{sec:related-work-cha3}.
-
-\subsection{Probabilistic Knowledge in MASs }
-
-Delgado and Benevides in \cite{Delgado2009} defined a
-probabilistic logic called K-PCTL which extends PCTL with an
-epistemic operator for the knowledge.
-For modeling their target systems, the authors proposed an
-approach that represents each agent in the system as a DTMC with
-synchronization actions. In their DTMC model, each state either
-has a synchronized action with probability 1 or regular
-probabilistic transitions. Having two different actions in a
-single DTMC forced them to transform it into an MDP model. From
-the semantics point of view, K-PCTL formulae are interpreted over
-MDP models which are augmented with accessibility relations, so
-that probabilities over paths can be defined. However, the
-uncertainty of the knowledge cannot be measured as the
-accessibility relations are not probabilistic. Our approach
-differs from this one in four main points. First, our logic
-adds two modalities on top of PCTL; one for the knowledge,
-and one for the commitments and their fulfilments.
-Therefore, dimension of system's aspects that our logic can handle is larger than that of K-PCTL making it more expressive.
-Second, our logic permits the
-probabilistic operator to precede each of the knowledge modality
-and the social modality so that we can quantitatively reason about
-the two aspects which again increases its expressive power. Third,
-we model the target systems using probabilistic interpreted
-systems. Forth, we propose a concrete model checking technique in
-which we transform the problem of model checking our logic to the
-problem of model checking an existing logic allowing us to re-use
-the PRISM tool instead of just suggesting to extend it.
-
-In \cite{Huang2011}, Huang and his colleagues extended the MCK
-model checker \cite{Gammie2004} with subjective probability
-relative to agent knowledge using interpreted partially observed
-discrete-time Markov chain (PO-DTMC). PO-DTMC is based on partial
-observations with assumption on synchronous with perfect recall.
-To specify properties of probabilistic interpreted systems, the
-authors use a logic that combines temporal and knowledge
-modalities with a probabilistic operator. In their approach, the
-set of accessible states is defined as states of a special agent,
-called the environment, while the remaining agents observe the
-environment and perform actions based on their observations. Then,
-probabilistic knowledge is expressed by a rational linear
-combination of every agents' probabilities in the system: every
-agent has its own probability for each accessible state, which is
-supposed to be known. Unlike this work, in our approach we do not
-assume that accessibility transitions are probabilistic because
-this information is not always accessible to agents and sometimes
-hard to quantify. Instead, we compute the probabilistic knowledge
-based on the number of accessible states as they are equally
-accessible. Moreover, by re-using the exiting PRISM model checker,
-we do not add a computational cost that is associated to extending
-the existing version of it.
-
-Wan et al. \cite{Wan2013} has also addressed the verification of
-epistemic properties in agent environments  against the background
-of participating parties. They propose PCTLK, a probabilistic,
-epistemic,  branching-time logic which extends CTL with
-probabilistic and epistemic modalities. To verify the proposed
-logic, the authors introduced a reduction-based model checking
-technique to translate the problem of model checking PCTLK into
-the problem of model checking PCTL. Their reduction procedure
-involves two processes. First, they transform the probabilistic
-interpreted systems into an MDP which is transformed further to a
-DTMC. Second, they translate each PCTLK formula into a
-corresponding PCTL formula. To model check a PCTLK forumla, they
-check its transformed PCTL formula over the DTMC model. They
-demonstrated the applicability of their proposed verification
-technique by applying it on a well known case study and
-implementing it using the PRISM model checker. Our work is similar
-to this work, except that we have a social modality in our
-proposed logic for the commitments and their fulfilments which
-makes it more expressive than PCTLK.
-
-\subsection{The Interaction between Knowledge and Social Commitments}
-
-Little work has been done towards the problem of capturing and verifying the interactions between knowledge and social commitments in MASs.
-
-In \cite{Schmidt2004}, Schmidt and his colleagues investigated the
-problem of formalizing the interaction between knowledge and
-commitments within agent dynamic logic. Apparently, the commitment
-adopted in this work is not a social commitment but rather an
-internal commitment as the one presented by Castelfranchi in
-\cite{Castelfranchi1995}.
-The term ``internal commitment'' refers to a commitment of an agent to itself \cite{Singh2008}.
-Using their proposed Agent Dynamic Logic (ADL), the authors were able to express some combinations between knowledge and commitments such as $Comm_i~(\alpha)\to K_i~Comm_i~(\alpha)$ which expresses that agent $i$ knows ($K_i$) about his
-internal commitment ($Comm_i$) to perform the action $\alpha$.
-However, from a communication perspective, the internal commitment
-is neither communicative nor public because it is not created as
-an agreement between two agents so that an agent can commit
-towards the other to bring about a certain property. In contrast,
-our work focuses primary on the notion of ``social commitment"
-\cite{Singh2000} which has been used as a means of communication
-between interacting agents in MASs. Unlike internal commitments,
-which are private and concern a particular agent, social
-commitments are public and observable engagements from one agent
-to another agent or a group of agents to bring about something.
-Furthermore, unlike \cite{Schmidt2004}, we study such an interaction ---between the two concepts--- in systems exhibiting probabilistic behaviors.
-
-Al-Saqqar et al. \cite{Al-Saqqar2014a} have made the first attempt
-towards studying the relationship between knowledge and
-communicative social commitments from a logical perspective. In
-particular, they combined a logic of knowledge (called CTLK
-\cite{Lomuscio2007}) and a logic of commitments (called CTLC
-\cite{Bentahar2012}) in a single tool called CTLKC. Having
-analyzed some postulates with different combinations between the
-two concepts expressed in CTLKC, the authors identified a set of
-paradoxes that makes their combined logic inconsistent. To
-overcome this problem, they mitigated the over-specification
-problem that arises in the social accessibility relation given in
-\cite{Bentahar2012,El-Menshawy2013a}. Intuitively and broadly
-speaking, a social accessibility relation for two agents $i$ and
-$j$ does exist between two global states $s_1$ and $s_2$ in the
-system, if there is a communication channel between the local
-states of $i$ and $j$ in the global states $s_1$ and $s_2$
-respectively. Based on a new social accessibility relation, they
-presented a new semantics for the commitment ($C_{i\rightarrow j}
-\varphi$) and fulfilment ($Fu (C _{i\rightarrow j} \varphi)$)
-operators, where $C_{i\rightarrow j} \varphi$ means that agent $i$
-commits towards agent $j$ to bring about $\varphi$, and $Fu (C
-_{i\rightarrow j} \varphi)$ expresses the fulfillment of such a
-commitment. These changes have been integrated into a new
-consistent logic named CTLKC$^+$. Having defined the new logic,
-the authors have been successfully able to reason about various
-combinations between knowledge $K_i \varphi$, which means that
-agent $i$ knows $\varphi$, and social commitments as follows:
-
-\begin{itemize}
-\item $C_{i\rightarrow j} \varphi \Rightarrow K_i (C_{i\rightarrow
-j} \varphi) $ where $i \neq j$.
-\item $Fu (C _{i\rightarrow j} \varphi) \Rightarrow K _i \varphi$ where $i \neq j$.
-\item $Fu (C _{i\rightarrow j} \varphi) \Rightarrow K_j \varphi$ where $i \neq j$.
-
-\end{itemize}
-
-Then, the authors introduced a reduction model checking technique
-in which they transformed the problem of model checking their new
-logic (CTLKC$^+$) into the problem of model checking an existing
-logic called GCTL$^*$ \cite{Bhat2001}, and computed the complexity of the reduction technique. They used the automata-based model checker CWB-NC as the verification tool.
-
-The verification of CTLKC$^+$ was further investigated in \cite{Al-Saqqar2014b}.
-The authors used a symbolic model checking technique based on reducing the problem of model checking CTLKC$^+$ into that of ARCTL.
-Then, they used the extended NuSMV to verify some given properties written in CTLKC$^+$.
-Their approach was carried out automatically using a JAVA transformation tool.
-This allowed them to overcome the scalability problem of automata-based model modeling checking techniques, which is a highly considerable problem in model checking real applications of multi-agent systems.
-The complexity analysis of the proposed reduction-based technique was also provided.
-
-Unlike this work that tends to assume ideal behavior for MASs so it limits its application to reliable environments, ours considers the unreliable behavior of MASs.
-Therefore, we add a probabilistic modality to the logic to be able to reason about some desirable properties in the presence of uncertainty.
-Our proposal subsumes the one in \cite{Al-Saqqar2014a} because probability values range from 0 to 1 (when probability is equal to 1, the system becomes certain).
-Therefore, our framework outperforms this proposal in the sense that not only qualitative reasoning about the interaction between knowledge and commitments is achievable but also quantitative reasoning becomes possible.
-
-\subsection{Comparison}
-
-We compare our framework to the existing proposals by taking into
-consideration five criteria: Knowledge, Commitments, Uncertainty,
-Formalization, and Verification. Knowledge property shows whether
-the approach addresses epistemic properties of the systems or not.
-Commitments property indicates whether it addresses the social
-commitments or not. Uncertainty reflects target systems whose
-behavior is probabilistic. Formalization indicates the use of
-formal logics, or formal methods in general. Finally, Verification
-confirms the presentation of a formal verification technique to
-verify the proposed approach. Table \ref{table:comparison} shows a
-summary about the comparison between our framework and the
-existing approaches based on the criteria described above.
-We observe that our framework outperforms the related approaches as
-it satisfies all the listed criteria.
-
-\begin{table}
-\centering \caption{Comparison between PCTL$^{kc}$ and the related work } \label{table:comparison}
-\begin{tabular}{cccccc}
-\hline
-\texttt{Approach}       &\texttt{Knowledge} & \texttt{Commitment} & \texttt{Uncertainty}   & \texttt{Formal} & \texttt{Verification}\\
-\hline
-\cite{Witwicki2007,Witwicki2009}    &         &$\surd$   &$\surd$    &         &    \\
-\cite{Huang2011}      &          &$\surd$   &$\surd$    &$\surd$  &$\surd$    \\
-\cite{Delgado2009}     &$\surd$   &          &$\surd$    &$\surd$  &    \\
-\cite{Wan2013}         &$\surd$   &          &$\surd$    &$\surd$  &$\surd$    \\
-\cite{Al-Saqqar2014a}   &$\surd$   &$\surd$   &           &$\surd$  &$\surd$    \\
-Our approach         &$\surd$   &$\surd$   &$\surd$    &$\surd$  &$\surd$    \\
-\hline
-
-\end{tabular}
-\end{table}
-
-To summarize, the advancement of our work over existing work lies in the expressiveness power of the proposed logic which allows autonomous agents in MASs to represent and verify the interaction between knowledge and social commitments in the face of uncertainty.
-Moreover, the new probabilistic interpreted systems introduced in this chapter helps MASs developers to have rich modeling with respect to knowledge and social commitments.
-That is, not only modeling knowledge and social commitments independently in the presence of uncertainty is possible, but also modeling the interaction between them has become possible by making use of our proposed probabilistic model.
+All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process.
+So basically These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.
+We address this issue by introducing DDM a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another.
+After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics.
+Therefore web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
+In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Summary}\label{sec:conclusion-cha4}
 
-In this chapter, we presented a novel technique for specifying and evaluating the interaction between knowledge and social commitments in stochastic MASs.
-The proposed technique allows us, for the first time in the literature, to perform epistemic reasoning on social commitments in probabilistic MASs.
-This helps ensure agents' awareness about their commitments and the fulfillments of these commitments.
-In particular, we first developed a new version of interpreted systems that captures the probabilistic behavior of knowledge and commitments and accounts for the communication between interacting parties.
-Second, we defined a new logical framework that merges concepts of probabilistic knowledge and probabilistic commitments in a single logic called PCTL$^{kc}$, so that complex formulae including both modalities
-can be expressed. Third, we introduced a new model checking
-technique to formally verify the compliance of MASs against some
-given properties expressed using the new logic. The proposed model
-checking procedure is reduction-based, in which the problem of
-model checking PCTL$^{kc}$ is transformed (by the use of some rules) into the problem of model checking an existing logic, namely PCTL.
-The key advantage of such a reduction is gaining the privilege to re-use a well
-known model checker such as PRISM. The soundness of the proposed
-reduction technique was provided. Moreover, we demonstrated the
-effectiveness of the proposed framework by applying it to the
-NetBill protocol, a concrete case study from e-business domain.
-The results have initially confirmed the expressive
-capabilities of PCTL$^{kc}$ in handling the
-interaction between knowledge and social commitments in
-probabilistic settings. Moreover, the scalability of the proposed model
-checking technique was evaluated and models having up to $4
-\times 10^{11}$ states can be effectively verified.
+In this paper, we proposed a training model for the problem of membership management of communities of web services.
+Using the traning model we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves.
+This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available.
+The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices.
+The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.
+The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.
 
-In the next chapter, we refine and extend the approach presented for the interaction between individual knowledge and commitments to accommodate  group knowledge and group commitments as well.
+Our plan for future work is to advance learning process on the training set that we provided in our work.
+SVN machine learning algorithm are suitable in classification of our training data set, to better classify correct or wrong decisions based on long-term utility gains, as data set outputs.
+This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.

### 2015-04-22 thesis/thesis/chap5/chap5.tex
changes

--- 2015-04-05 thesis/others/khalid/chap5/chap5.tex
@@
-\chapter{On Probabilistic Group Social Commitments}\label{cha:PCTLKC+}
+\chapter{LEarning Chapter}\label{cha:PCTLKC+}
 
-In this chapter\footnote{Part of the results presented in this chapter, namely PCTL$^{\textrm{kc+}}$ logic, has been published in SoMet\_14 \cite{Sultan2014c}.
-The results of model checking PCTL$^{\textrm{kc+}}$ have been sumbitted to the Engineering Applications of Artificial Intelligence journal \cite{Sultan2014d}}, we improve and extend the work presented in Chapter \ref{cha:PCTLKC} by refining the probabilistic logic of knowledge and commitment (PCTL$^{kc}$) and then extending the refined logic further by operators for group knowledge and group commitment.
-In this respect, we define a semantics for the group social commitment operator and integrate it into the resulting logic.
-The developed logic is called the new probabilistic logic of knowledge and commitment (PCTL$^{\textrm{kc+}}$).
-Finally, we introduce a new formal verification technique that considers the new group modalities and implement it on top of the PRISM model checker.
-
-\section{Introduction} \label{Introduction}
-
-One of the major challenges in building complex software products
-such as Multi-Agent Systems (MASs) is to advance error detection
-at early stages of their life-cycles. %The social context of interacting agents in MASs has gained significance recently.
-MASs community has witnessed an important shift in defining the semantics of ACLs from the so-called mental approaches that is hard to verify \cite{Singh2000} to social approaches which exploit observable and verifiable social commitments.
-However, the increasing demand to use social commitments as a means of communication among interacting parties \cite{Baldoni2014,Chesani2013,Akin2013} requires reasoning about and verifying the relationship between social commitments and some other systems' aspects such as agents' knowledge and uncertainty especially in the case of having group-commitment scenarios.
-In addition to verifying the interactions between social commitments and knowledge in the presence of uncertainty, the ultimate objective of this chapter is to verify the interactions between the two elements when the scope of interacting agents goes beyond the common agent-to-agent (i.e., one-to-one) scheme.
-
-In order to effectively capture and express the interactions between individual and group social commitments and knowledge in probabilistic MASs, we propose a new modal logic called the new probabilistic logic of knowledge and commitments PCTL$^{\textrm{kc+}}$ which is built by combining a consistent logic of knowledge and commitment CTLKC$^+$ \cite{Al-Saqqar2014a} with a well established probabilistic temporal logic PCTL \cite{Hansson1994}.
-The resulting logic is extended further to accommodate operators for the group knowledge and group commitments.
-
-At present, there is a relatively large gap in addressing the
-concepts of knowledge and social commitments simultaneously in
-MASs, especially with the presence of uncertainty. Existing
-approaches that address the interaction between knowledge and
-social commitments either limit the scope of interacting
-agents to the widely used one-to-one commitment scheme and ignore the uncertainty aspect of MASs \cite{Al-Saqqar2014a}, or adopt a different kind of commitments called ``internal commitment'' rather than the ``social commitments'' that we consider in this thesis \cite{Schmidt2004}.
-Furthermore, although the notion of ``group'' is important in the multi-agent community \cite{Sanchez-Anguix2013,YuW2010}, group social
-commitments has not been formalized and verified yet. As knowledge
-and social commitments influence each other in many real world
-applications \cite{Al-Saqqar2014a}, their interactions need to be
-reasoned about and verified in a systematic manner. As we said before,
-uncertainty in MASs may arise due to imperfect information about
-the environment in which agents interact.
-Besides, in some situations, it happens that even if there is some state of affairs (i.e., content of a commitment) that an agent wants to bring about, its actions might not reliably drive the state of affairs into the desired state \cite{Sultan2014a}.
-Consequently, commitments themselves become stochastic and the degree to which the commitment can be satisfied is not always
-guaranteed.
-
-To motivate our study of representing and verifying the
-interaction between individual and group knowledge and social
-commitments in probabilistic MASs when taking into account
-one-to-many commitments, let us consider the following simple
-example. A professor teaching an engineering course with a
-capacity of $20$ students. Various scenarios could happen within
-this context.
-
-\begin{itemize}
-\item \verb"Scenario 1": while the professor was explaining some
-new concepts in the course, one of the students asked the
-professor to provide him with more material regarding these
-concepts. The professor then promised to email the student some
-references the next day. This promise can be considered as a
-commitment from the professor towards the student to provide him
-with extra material for the new concepts. \item \verb"Scenario 2":
-in the lecture before the mid-term exam, students requested the
-professor to exclude some material and shorten the duration of the
-exam accordingly. At the end of the lecture, the professor agreed
-to exclude some parts of the covered material and to make the exam
-one hour long.  This agreement can be considered as a commitment
-from the professor to the group of students who are registered in
-this course. Right after the class, the professor posted in the
-course web site an update confirming what they agreed on.
-\end{itemize}
-In the first scenario, obviously both the professor and student
-are aware of the commitment (sending extra materiel). However, in
-the second scenario, every student registered in the course, and
-not necessarily present during the lecture,  has to know about
-this agreement (commitment) to avoid wasting time studying
-excluded parts. In fact, because of some unexpected factors like
-absence of the professor on the day of the exam, email delivery
-failure, power outage, etc, there is no guarantee that these
-commitments are  going to be surely fulfilled. Therefore, it is
-important to have a logic system with the ability to not only
-express the interaction between knowledge and social commitments,
-but also to handle the concepts of knowledge and commitments
-within the scope of a group when uncertainty matters. Once such a
-logic is defined, it can be invested as the underlying logic for a
-verification technique to verify some desirable and useful
-properties expressing combinations of knowledge and social
-commitments under uncertainty.
-
-The work presented in this chapter can be seen as extension and continuation of the work presented in Chapter \ref{cha:PCTLKC} where reasoning about and verifying interactions between individual knowledge and social commitments in probabilistic MASs were first introduced.
-In Chapter \ref{cha:PCTLKC}, we proposed a probabilistic logic called PCTL$^{kc}$ whose expressiveness power allowed us to formulate combinations of the two concepts in the presence of uncertainty.
-PCTL$^{kc}$ logic was built by fusing two logics, namely PCTLC \cite{Sultan2013} and PCTLK \cite{Wan2013} using the
-independent join technique \cite{Franceschet2004}.
-However, as pointed out in \cite{Al-Saqqar2014a}, the social accessibility relations given in \cite{Bentahar2012,El-Menshawy2013a}, have an over-specification problem, and consequently the PCTL$^{kc}$ logic suffers from some paradoxes as it adopts the aforementioned accessibility relations.
-
-To elaborate, there exist some situations that are not desirable in real settings but with the use of PCTL$^{kc}$, they are valid.
-One major problem in PCTL$^{kc}$ is that agents commit everything they know to others, which brings the lack of privacy into being.
-Formally, this is represented by the following postulate:
-
-\begin{itemize}
-\item $K_i \varphi \Rightarrow C_{i \rightarrow j}\varphi$,  where $i \neq j$.
-\end{itemize}
-
-The validity of this postulate is based on the fact that by
-establishing communication channels through which commitments are
-supposed to be exchanged, the epistemic relation needed to define
-the semantics of knowledge is also established. This is not
-reasonable in open environments where agents are selfish. Another
-problem is that agents commit everything known by others. That is,
-when an agent knows that another agent knows something, the first
-agent commits to bring about what the other agent knows, formally:
-
-\begin{itemize}
-\item $ K_i K_j \varphi \Rightarrow C_{i \rightarrow j} \varphi$ where $ i \neq j$.
-\end{itemize}
-
-Such a postulate should be avoided in MASs because it is not
-realistic for an agent to commit for something that is out of its
-capabilities. Moreover, this postulate can result in serious
-circumstances if agent $j$ is malicious, so it can express
-incorrect knowledge about the other agent, obliging it to
-establish unwanted commitment.
-
-On the other hand, we have some reasonable situations that should
-be always valid but with the use of PCTL$^{kc}$ they can be
-unsatisfied. One example in this respect is when agents should be always aware about the fulfillment of their own commitments.
-
-\begin{itemize}
-\item $Fu(C _{i\rightarrow j} \varphi) \Rightarrow K_i Fu(C
-_{i\rightarrow j} \varphi)$ where $i \neq j$
-\end{itemize}
-
-It is realistic for this postulate to be valid because any agent should be aware of its fulfillment actions in order to prevent fulfilling the same commitment again and again.
-However, this postulate is not valid in PCTL$^{kc}$ because of the same reasons mentioned earlier.
-Consequently, PCTL$^{kc}$ fails to efficiently handle some practical situations in which knowledge and social commitments need to interact.
-
-The problem is that one of the underlying logics of PCTL$^{kc}$, which
-is PCTLC \cite{Sultan2013}, is built using the social accessibility relations given in \cite{Bentahar2012,El-Menshawy2013a}, which in fact over specifies and over constrains the concept of illocutionary communication.
-In a recent work, Al-Saqqar et al.
-\cite{Al-Saqqar2014a} have figured out that although the social accessibilities presented in \cite{Bentahar2012,El-Menshawy2013a} function perfectly when the concern is to model social commitments independently, they have some limitations when combined with the epistemic accessibility relations in the same model.
-The authors in \cite{Al-Saqqar2014a} modified the social accessibility relations proposed in \cite{Bentahar2012,El-Menshawy2013a} in order to prevent the unintended emergence of the epistemic accessibility relations from the social accessibility relations when the two accessibilities combined in the same model.
-Technically speaking, they relaxed the conditions upon which the social accessibility relations are established in order to decouple the social accessibility relations from the epistemic accessibility relations.
-The new definition of social accessibilities does no longer depend on the unshared variables but rather depends merely on the shared variables between the interacting agents as discussed in Chapter \ref{cha:background}.
-The new condition upon which a communication channel is established is stated below:
-
- $ s \approx_{i \rightarrow j} s' $ iff $ Var_i \cap Var_j \neq \emptyset $ such that $ \forall x \in Var_i \cap Var_j $ we have $ l_i^x(s) =
-l_i^x(s') = l_j^x(s')$, where $\approx_{i\rightarrow j} \subseteq S \times S$ is the social accessibility relation.
-It has been proven that with the new social accessibilities, the resulting logic is consistent \cite{Al-Saqqar2014a}.
-
-The work presented in this chapter differs from the one proposed in Chapter \ref{cha:PCTLKC} in the following points:
-
-\begin{enumerate}
-\item While the logic presented in Chapter \ref{cha:PCTLKC} suffers from
-some paradoxes, the current work builds upon a consistent logic of
-knowledge and commitment CTLKC$^+$ \cite{Al-Saqqar2014a} which
-ensures having a paradox-free logic.
-
-\item The new logic allows us to reason about commitments among
-multiple agents instead of limiting the scope to merely two
-agents. The concept of group knowledge is also integrated to the framework allowing us to reason about the knowledge in the case of group of agents.
-
-\item In the current work, we generalize the model checking
-technique that has been proposed in Chapter \ref{cha:PCTLKC} to fit the new group commitment operators as well.
-\end{enumerate}
-
-The contributions of this chapter are threefold.
-First, we present a new probabilistic logic called (PCTL$^{\textrm{kc+}}$) with expressiveness abilities to capture and represent the interactions between individual and group knowledge and social commitments.
-Second, we introduce a formal verification technique for the probabilistic logic PCTL$^{\textrm{kc+}}$. The proposed technique is based on reducing
-the problem of model checking PCTL$^{\textrm{kc+}}$ to the problem
-of model checking PCTL. This is achieved through 1) advocating a
-set of transformation rules that transform the
-PCTL$^{\textrm{kc+}}$ model into a Markov Decision Process (MDP),
-and then converting the obtained MDP into a DTMC using the notion
-of ``adversary'' \cite{Forejt2011}; 2) reducing
-PCTL$^{\textrm{kc+}}$ formulae into PCTL formulae based on a set
-of formal reduction rules. Third, we implement our reduction model checking
-technique on top of PRISM and apply it on a concrete case study,
-namely the online shopping system \cite{Gomaa2011}. We then check
-some system's properties written as PCTL$^{\textrm{kc+}}$ formulae
-using the PRISM model checker by checking their corresponding PCTL
-formulae. Figure \ref{fig:approach-PCTLKC+} depicts a schematic
-view of our proposed framework.
-
-\begin{figure}[t]
-                \begin{center}
-                \includegraphics[width=14cm, height=10cm]{chap5/img/approach-cha5-new.eps}
-                \end{center}
-                \caption{A schematic view of the probabilistic group social commitment approach} \label{fig:approach-PCTLKC+}
-                \label{Stack}
-                \end{figure}
-
-\section{The New Probabilistic Logic of knowledge and Commitment (PCTL$^{\textrm{kc+}}$)} \label{sec:logic}
-
-To overcome the inconsistency problem of PCTL$^{kc}$, we develop a new logic called the new probabilistic logic of knowledge and commitment (PCTL$^{\textrm{kc+}}$).
-To build PCTL$^{\textrm{kc+}}$, there are two obvious resources available in the literature: 1) the traditional temporal logics that have been developed for knowledge and social commitments independently or together such as CTLC \cite{Bentahar2012}, CTLK \cite{Lomuscio2007}, and CLTKC$^+$ \cite{Al-Saqqar2014a}; and 2) the existing probabilistic logics available in the literature such as PCTL \cite{Hansson1994}, PCLTK \cite{Wan2013}, and PCTLC \cite{Sultan2014a}.
-Unfortunately, none of these resources is perfectly suitable for the task.
-The former resource neglects the uncertainty aspects in MASs, while the
-latter doesn't capture the interaction between knowledge and
-social commitments. Therefore, we propose a solution that draws
-upon both resources. In particular, we combine an existing
-consistent logic of knowledge and commitment CTLKC$^+$
-\cite{Al-Saqqar2014a} with a well established probabilistic
-temporal logic PCTL \cite{Hansson1994}. Then, we extend the
-resulting combined logic by adding new operators for the group knowledge
-and group commitment.
-
-Before going further, let us first describe a new probabilistic model over which PCTL$^{\textrm{kc+}}$ formulae can be interpreted. This model is an extension of the formalism of interpreted systems
-\cite{Fagin1995} with the concepts of epistemic accessibility and
-social accessibility relations.
-Concretely, the model of PCTL$^{\textrm{kc+}}$ is generated from combining two extended versions of the interpreted systems formalism.
-These extended formalisms are the extended version introduced in \cite{Halpern2003,Wan2013} and a modified version of the extended version given in \cite{Bentahar2012,El-Menshawy2013a} due to Al-Saqqar et al.
-\cite{Al-Saqqar2014a}.
-
-\begin{definition} [PCTL$^{\textrm{kc+}}$ Model] ~\label{dfn:Models}
-
-\noindent Given a set of atomic propositions $\Phi_p = (p,q,r, \ldots)$ and a set of agents $\texttt{Agt}=\{1,\ldots,n\}$,  the model $\mathfrak{M_3}=(S,\textbf{P},I,\sim_1, \ldots
-,\sim_n,\{\approx_{i \rightarrow j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$ is a tuple where:
-%
-\begin{itemize}
-\item  $S \subseteq L_1 \times \ldots \times L_n$ is a countable set of all reachable global states of the system.
-A state $s$ is reachable iff there exists a sequence of transitions from an initial state to $s$ in which the probability of each transition is greater than $0$.
-
-\item  $I \in S$ is an initial global state for the system.
-
-\item  $\textbf{P}:S\times S\rightarrow [0,1]$ is a total transition probability function defined as $\textbf{P}(s, s')=\tau(s,a^{s \rightarrow s'}, s')$ iff there exists a joint action $a=(a_1,\ldots,a_n) \in ACT$ such that\\
-     $\sum_{i \in \texttt{Agt}} \tau_i(l_i(s),a^{l_i(s)\rightarrow l_i(s')},l_i(s')) > 0$ and $\sum_{s' \in S} \textbf{P}(s,s') =1$ for all $s \in S$.
-
-\item  $\sim_i \subseteq S \times S$ is the epistemic accessibility relation for the agent $i$, such that for two global states $s$ and $s'$, we have: $s \sim_i s'$ iff $l_i(s)=l_i(s')$.
-
-\item For each pair $(i,j) \in \texttt{Agt}^2$, $\approx_{i\rightarrow j} \subseteq S \times S$ is the social accessibility relation which is defined as follows: $ s \approx_{i\rightarrow j} s' $ iff $ Var_i \cap Var_j \neq \emptyset $ such that $ \forall x \in Var_i \cap Var_j $ we have $ l_i^x(s) = l_i^x(s') = l_j^x(s')$.
-
-\item  $\nu : S \rightarrow 2 ^{\Phi_p} $ is a valuation function.
-
-\end{itemize}
-\end{definition}
-%
-
-The new model $\mathfrak{M_3}$ differs from the model $\mathfrak{M_2}$,  presented in Chapter \ref{cha:PCTLKC}, in one particular point which is the social accessability relation.
-While $\mathfrak{M_2}$ uses the social accessibility relation $\sim_{i\rightarrow j}$ that has been introduced in \cite{Bentahar2012,El-Menshawy2013a}, the new model adopts the one $\approx_{i\rightarrow j}$ proposed in \cite{Al-Saqqar2014a} in order to overcome the over-specification problem appeared in $\sim_{i\rightarrow j}$.
-
-\subsection{Syntax of PCTL$^{\textrm{kc+}}$} \label{def:syntax-PCTLKC+}
-
-\begin{definition}[PCTL$^{\textrm{kc+}}$ syntax]\label{def:syntax-PCTLKC+}
-Let $\Phi_p=\{p,q, \dots\}$ be a set of atomic propositions, and $\texttt{Agt}=\{1, \dots, n\}$ be a set of agents.
-The syntax of PCTL$^{\textrm{kc+}}$, which is a combination of PCTLK \cite{Wan2013} and PCTLC \cite{Sultan2014a,Sultan2013} augmented with further operators for the group knowledge, is given by the following grammar:
-
-\vspace{-0.5cm}
-\begin{align*}
-    \varphi & ::= p~|~\neg \varphi~|~\varphi \vee \varphi~|~\mathcal{K}~|~\mathcal{C}~|~ \mathbb{P}_{\bowtie k} (\psi)~|~\mathbb{P}_{\bowtie k}(\mathcal{K})|~\mathbb{P}_{\bowtie k}(\mathcal{C})\\
-    \psi & ::=\bigcirc \varphi ~ | ~ \varphi ~U~ \varphi~|~ \varphi~ U^{\leq m} ~ \varphi \\
-    \mathcal{K} & ::= K_i ~\varphi ~|~ E_{G} ~\varphi\\
-    \mathcal{C} & ::= C_{i\rightarrow j} ~\varphi ~| ~ C_{i\rightarrow G} ~\varphi ~| ~Fu(C_{i\rightarrow j} ~\varphi) ~| ~Fu(C_{i\rightarrow G} ~\varphi)
-\end{align*}
-%
-where;\\
-\noindent -- $p\in\Phi_p$ is an atomic proposition\\
-\noindent -- $i,j \in \texttt{Agt}$.\\
-\noindent -- $G\subseteq \texttt{Agt}$.\\
-\noindent -- $\mathbb{P}_{\bowtie k}$ is a probabilistic operator and $\bowtie \in\{<,\leq,>,\ge\}$.\\
-\noindent -- $k\in [0,1]$ is a probability bound or threshold.\\
-$m \in\mathbb{N}^+ $ is a positive integer number reflecting the maximum number of transitions needed to reach a certain state.\\
-\noindent -- The Boolean connectives $\neg$ and $\vee$ are defined in the usual way.\\
-\noindent -- $\varphi$ and $\psi$ are state and path formulae interpreted over the states and paths of $\mathfrak{M_3}$ respectively.\\
-\noindent -- The modal connectives $\mathcal{K}$ and $\mathcal{C}$ stand for ``epistemic" and ``social" operators, respectively.\\
-
-\end{definition}
-\vspace{-0.5cm}
-
-\noindent In this logic, formulae $\mathcal{K}$ are state formulae and used to express the epistemic properties through the operators; $K_i$ which stands for agent $i$ knows, $E_G$ which stands for everyone knows.
-Modal connectives $C_{i\rightarrow j}$ and $C_{i\rightarrow G}$ are called social formulae and stand for ``commitment'' from a debtor towards a single creditor, and ``commitment'' from a debtor to a group of creditors, respectively.
-Likewise, modal connectives $Fu(C_{i\rightarrow j})$ and $Fu(C_{i\rightarrow G})$ stand for ``fulfillment'' of the commitment $C_{i\rightarrow j}$ and ``fulfillment'' of the commitment $C_{i\rightarrow G}$, respectively.
-$\bigcirc, U$ and $U^{\leq m}$ stand for ``next time'', ``until'' and ``bounded until'' path modal connectives respectively.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Social Commitments Classification} \label{sec:commitment-classification}
-
-Social commitments for agent communication have been always looked
-at within the scope of one-to-one. However,
-back to our motivating example, we realize that in addition to the
-usual agent-to-agent scheme, there are certain situations where
-group-agent commitments are needed. In this chapter, we are
-interested to move beyond the scope of one-to-one and
-investigate the case of committing to multiple agents. The idea of
-investigating other schemes of social commitments rather than the
-one-to-one commitment scheme seems to be both technically
-interesting and intuitively appealing. In what follows, we
-distinguish between two different flavors of social commitments,
-namely basic (or individual) social commitment and group social
-commitment.
-
-\begin{definition} [Basic Social Commitment]~
-
-A basic social commitment is an agreement between two agents
-namely, \texttt{debtor} and \texttt{creditor} such that the
-\texttt{debtor} engages towards the \texttt{creditor} to bring
-about a certain property.
-\end{definition}
-
-This is the simplest form of social commitments and has long been
-investigated in the literature. The commitment in this case can be
-represented using the following operator: $C_{i\to j} ~\varphi$
-where $i$ denotes the debtor, $j$ denotes the creditor, and
-$\varphi$ denotes the content of the commitment. The fulfillment
-of such a commitment is written as follows: $Fu(C_{i\to j}
-~\varphi)$. However, as the common form of social commitments is
-the basic social commitment, we can simply use ``social
-commitments" to refer to ``basic (or individual) social
-commitments".
-
-\begin{definition} [Group Social Commitment]~
-
-A group social commitment is an agreement between a
-\texttt{debtor} and a group of \texttt{creditors} to bring about a
-certain property.
-\end{definition}
-
-This kind of commitments indicates the involvement of multiple
-agents in the same commitment. The creditor is a group of
-independent agents that join together as a single party due to
-their shared interests in the commitment at hand. A group social
-commitment is represented using the following notation: $C_{i\to
-G} ~\varphi$, where $i$ denotes the debtor, $G$ denotes a group of
-creditors, and $\varphi$ denotes the content of the commitment.
-The fulfillment of such a commitment is given by the notation
-$Fu(C_{i\to G} ~\varphi)$. Technically, a group social commitment
-can be seen as the conjunction of individual basic social
-commitments from the debtor $i$ to each agent in the group of
-creditors $G$. Formally, $C_{i\to G} ~\varphi \equiv
-\bigwedge\limits_{j\in G} C_{i\rightarrow j} ~\varphi$. An
-intuitive explanation of the operator $C_{i\to G} ~\varphi$ is as
-follows: for a group social commitment to be held at a certain
-state, the content of the commitment must be true at every
-accessible state from the commitment state with respect to the
-group. This implies that none of the group members could be
-excluded from having all accessible states satisfy the content of
-the commitment. Consequently, it is obvious that for a state to be
-socially accessible from the commitment state with respect to the
-group, it has to be socially accessible with respect to at least
-one of the agents of the group. Therefore, we resolve the
-accessibility problem resulted from having group commitments by
-taking the union of the social accessibility relations of each
-single agent in the group. This in turn leads us to define the
-group social accessibility relation based on the social
-accessibility relations presented in Definition \ref{dfn:Models}.
-
-Let $G\subseteq \texttt{Agt}$ be a group of agents. We define the group social accessibility relation from the social accessibility relation $\approx_{i \to j}$ as follows:
-\begin{definition} [Social Accessibility Relations for Group Social Commitment] \label{dfn: group social
-relations}~
-%
-\begin{itemize}
-
-\item $\approx_{i \rightarrow G}$ is the union of the social accessibility relations between agent $i$ and each agent in the group $G$: $\approx_{i \to G}=\bigcup\limits_{j \in G}\approx_{i\to j}$.
-
-\end{itemize}
-
-\end{definition}
-
-\begin{figure}[t]
-                \begin{center}
-                \includegraphics[width=7cm, height=5cm]{chap5/img/group-sc.eps}
-                \end{center}
-                \caption{Accessibility relations for group social commitment} \label{fig:group-sc}
-                \end{figure}
-
-Notice that group social commitments have all the properties of basic social commitments with an additional constraint that they can involve more than two agents.
-However, a group social commitment involving only two agents is equivalent to the basic social commitment.
-Figure \ref{fig:group-sc} depicts the idea of group social accessibility ($G=\{j_1, j_2\}$).
-
-\subsection{Group Knowledge}  \label{sec:Group Knowledge}
-In this work, we limit the scope of group knowledge to the concept of ``Everyone Knows" introduced in \cite{Fagin1995}.
-``Everyone Knows" is denoted by $E_G ~\varphi$ and means that everyone in the group $G$ knows $\varphi$.
-Technically, ``Everyone knows" can be seen as the conjunction of the individual knowledge of each agent in the group.
-Formally, $E_G ~\varphi \equiv \bigwedge\limits_{i\in G} K_i ~\varphi$.
-
-Before we proceed to present the semantics of
-PCTL$^{\textrm{kc+}}$, we need to define the epistemic
-accessibility relation for $E_G ~\varphi$. Let $G\subseteq
-\texttt{Agt}$ be a group of agents. We define the epistemic
-accessibility relation for $E_G ~\varphi$ from the epistemic
-accessibility relation $\sim_i$ as follows \cite{Wan2013}:\\
-
-\begin{definition} [Epistemic Accessibility Relation for Everyone Knows] \label{dfn: epistemic relations}~
-\begin{itemize}
-
-\item $\sim_G^{E}$ is the union of group $G's$ accessibility
-relations: $\sim_G^{E}=\bigcup\limits_{i \in G}\sim_i$.
-
-\end{itemize}
-\end{definition}
-
-\subsection{Semantics of PCTL$^{\textrm{kc+}}$} \label{def:semantics-PCTLKC+}
-
-Given a model $\mathfrak{M_3}=(S,\textbf{P},I,\sim_1, \ldots
-,\sim_n,\{\approx_{i \to j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$, then $(\mathfrak{M_3},s) \models \varphi$ states that ``a state $s$ in the model $\mathfrak{M_3}$ satisfies a state formula $\varphi$, $(\mathfrak{M_3},\pi) \models \psi$ means that ``a path $\pi$ in the model $\mathfrak{M_3}$ satisfies a path formula $\psi$, and
-$(\mathfrak{M_3},s) \models \mathbb{P}_{\bowtie k}(\psi)$ means that
-``a state $s$ in $\mathfrak{M_3}$ satisfies
-$\mathbb{P}_{\bowtie k}(\psi)$ if the probability of taking a path
-from $s$ that satisfies $\psi$ is in the interval specified by
-$\bowtie k$''. When the model $\mathfrak{M_3}$ is clear from the
-context, we simply write the satisfaction relation $\models$ as
-follows: $s \models \varphi$ and $\pi \models \psi$. Furthermore,
-we denote the number of socially accessible states $s'$ from a given state $s$ such that $s\approx_{i\to j}s'$ by $|s\approx_{i\to j}s'|$, and $s\approx_{i\to G}s'$ by $|s\approx_{i\to G}s'|$.
-We also denote the number of epistemically accessible states $s'$ from a given state $s$ such that $s\sim_i s'$ by $|s\sim_i s'|$. Similarly, we
-denote the number of states $s'$ that are accessible from a given
-state $s$ through $\sim_G^E$ by $|s\sim_G^E s'|$.
-Finally, we define $|s\models \varphi|$ as follows:
-
-\begin{center}
-$|s\models \varphi|=
-\begin{cases}
-1,~~~\textrm{if}~ s\models\varphi\\
-0,~~~\textrm{otherwise}.
-\end{cases}$
-\end{center}
-
-%
-\begin{definition}[\textbf{Satisfaction}]\label{def:semantics-pctlkc+} Satisfaction of a PCTL$^{\textrm{kc+}}$ formula in the model $\mathfrak{M_3}$ is conductively defined as follows:
-
-\noindent $s\models p~~~~~~~~~~~~~~~~~~~\emph{iff}~~p\in \nu(s);\\
-s\models \varphi_1 \vee \varphi_2 ~~~~~~~~\emph{iff}~~s\models \varphi_1~\textrm{or}~s \models \varphi_2; \\
-s\models \neg \varphi~~~~~~~~~~~~~~~~\emph{iff}~~s \nvDash \varphi;\\
-s\models K_i \varphi  ~~~~~~~~~~~~~~ \emph{iff}~~ \forall s'\in S ~ \textrm{s.t.} ~~ s \sim_i s',  \ \textrm{we~have}~ s'\models \varphi; \\
-s\models E_G ~\varphi ~~~~~~~~~~~~ \emph{iff}~~\forall s'\in S~ \textrm{s.t.} ~~ s\sim_G^E s', \ \textrm{we~have}~ s'\models \varphi; \\
-s\models C_{i\rightarrow j} \varphi  ~~~~~~~~~~ \emph{iff} ~~\forall s' \in S~\textrm{s.t.}~~s \approx_{i \rightarrow j}s', \textrm{we~have}~s'\models K_i \varphi \wedge K_j \varphi;\\
-s\models C_{i\rightarrow G} \varphi  ~~~~~~~~~ \emph{iff} ~~\forall s' \in S~\textrm{s.t.}~~s \approx_{i \rightarrow G}s', \textrm{we~have}~s'\models K_i \varphi \wedge E_G ~\varphi $;\\
-$s\models Fu(C_{i\rightarrow j} \varphi)$ ~\emph{iff} there exists $ s' \in S $ such that $ s' \approx_{i \rightarrow j} s $ and $~s'\models C_{i\rightarrow j} ~\varphi$ or \\
-$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$there exists $ s'' \in S $ and $ s'' \sim_i s $ such that $~s''\models Fu(C_{i\rightarrow j} ~\varphi)$ or \\
-$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$there exists $ s'' \in S $  and $ s'' \sim_j s $ such that $~s''\models Fu(C_{i\rightarrow j} ~\varphi)$;\\
-$s\models Fu(C_{i\rightarrow G} ~\varphi)$ ~\emph{iff} there exists $ s' \in S $ such that $ s' \approx_{i \rightarrow G} s $ and $~s'\models C_{i\rightarrow G} ~\varphi$ or \\
-$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$there exists $ s'' \in S $ and $ s'' \sim_i s $ such that $~s''\models Fu(C_{i\rightarrow G} ~\varphi)$ or \\
-$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$there exists $ s'' \in S $  and $ s'' \sim_G^E s $ such that $~s''\models Fu(C_{i\rightarrow G} ~\varphi)$;\\
-\noindent $\pi \models \bigcirc \varphi~~~~~~~~~~~~~~\emph{iff}~~\pi(1) \models \varphi; \\
-\pi \models \varphi_1~U^{\leq m}~\varphi_2~~\emph{iff}~~\exists k \leq m~~\textrm{s.t.}~~ \pi(k) \models \varphi_2 ~\textrm{and}~\forall i < k, \pi(i) \models \varphi_1;\\
-\pi \models \varphi_1 ~U~\varphi_2~~~~~~~\emph{iff}~~\exists m \geq 0~~\textrm{s.t.}~~\pi \models \varphi_1~U^{\leq m}~\varphi_2;$\\
-\noindent $s \models \mathbb{P}_{\bowtie k} (\psi)~~~~~~~~~\emph{iff}~~Prob_s(\psi)\bowtie k$ where: $Prob_s(\psi)=Prob_s\{\pi \in \Pi(s)~|~\pi\models
-\psi\};$\\
-
-\noindent $\bullet$ For a probabilistic operator working on an epistemic formula, where the set of all accessible states from $s$ is our sample space and the set of events $\mathrm{F}$ is the set of states accessible from $s$ and satisfy the formula:
-
-\begin{tabbing}
-\noindent $s\models \mathbb{P}_{\bowtie k}(K_i~\varphi) $
-    \ \ \ \ \ \= \emph{iff} \ $Prob(s \models K_i\varphi)$ $\bowtie k$ where: $Prob(s\models K_i\varphi)=\frac{\sum_{s \sim_i s'}|s'\models \varphi| }{|s \sim_i s'|};$
-\end{tabbing}
-
-\begin{tabbing}
- \noindent $s\models \mathbb{P}_{\bowtie k}(E_G~\varphi) $
-    \ \ \ \ \ \= \emph{iff} \ $Prob(s \models E_G~\varphi)$ $\bowtie k$ where: $Prob(s\models E_G~\varphi)=\frac{\sum_{s \sim_G^E s'}|s'\models \varphi| }{|s \sim_G^E s'|};$
-
-\end{tabbing}
-
-\noindent $\bullet$  For a probabilistic operator working over a commitment formula,where the set of all accessible states from $s$ is our sample space and the set of events $\mathrm{F}$ is the set of states accessible from $s$
-and satisfy the formula: \\
-
-\noindent $s\models \mathbb{P}_{\bowtie k}(C_{i\rightarrow j}\varphi)$
-   ~~\emph{iff}  $Prob(s \models C_{i\rightarrow j}\varphi) \bowtie \!k$ where: $Prob(s\models C_{i\rightarrow j}\varphi)=\frac{\sum_{s \approx_{i \rightarrow j}s'}|s'\models K_i \varphi \wedge K_j \varphi| }{|s \approx_{i \rightarrow j}s'| };$\\
-
-\noindent $s\models \mathbb{P}_{\bowtie k}(C_{i\rightarrow G}\varphi)$
-   ~\emph{iff}  $Prob(s \models C_{i\rightarrow G}\varphi) \bowtie \!k$ where: $Prob(s\models C_{i\rightarrow G}\varphi)=\frac{\sum_{s \approx_{i \rightarrow G}s'}|s'\models K_i \varphi \wedge E_G \varphi| }{|s \approx_{i \rightarrow G}s'| };$\\
-
-\noindent $\bullet$ For a probabilistic operator working over a fulfilment formula, assuming that accessible states are also reachable:\\
-
-\noindent $s\models \mathbb{P}_{\bowtie k}(Fu(C_{i\rightarrow j}\varphi))$
-    ~~ \emph{iff}~ $Prob(s \models Fu(C_{i\rightarrow j}\varphi)) \bowtie k;$ where:
-
-\vspace{-0.4cm}
-\begin{align*}
-%%
-& Prob(s\models Fu(C_{i\rightarrow j}\varphi))\ = Prob_s\{\pi \in \Pi(s') ~|~s' \approx_{i \rightarrow j}s ~\textrm{and}~ \pi = s' \ldots s ~\textrm{and}~ s' \models C_{i\rightarrow j}\varphi\};
-\end{align*}
-
-\noindent $s\models \mathbb{P}_{\bowtie k}(Fu(C_{i\rightarrow G}\varphi))$
-    ~~ \emph{iff}~ $Prob(s \models Fu(C_{i\rightarrow G}\varphi)) \bowtie k;$ where:
-
-\vspace{-0.4cm}
-\begin{align*}
-%%
-& Prob(s\models Fu(C_{i\rightarrow G}\varphi))\ = Prob_s\{\pi \in \Pi(s') ~|~
-& s' \approx_{i \rightarrow G}s ~\textrm{and}~ \pi = s' \ldots s ~\textrm{and}~ s' \models C_{i\rightarrow G}\varphi\}
-\end{align*}
-
-\end{definition}
-
-Again as in Chapter \ref{cha:PCTLKC}, in the case of the knowledge, the uncertainty is computed in such a way that it reflects the indistinguishability property of the epistemic accessibility relations.
-Hence, the uncertainty is computed based on the probability of epistemic accessibility relations which is calculated based on the number of accessible states satisfying the content of the knowledge over the number of equivalent states, as all the states are equally accessible.
-Likewise, probabilistic commitment is computed based on the number of accessible states that satisfy the content over the whole number of accessible states, which demonstrates the uncertainty of the agent over the accessible states, so that over the commitment.
-Probabilistic fulfillment, however, is computed using the probabilistic transitions of the path linking the commitment state to the fulfillment state.
-
-The following proposition is straightforward from the semantics:
-
-\begin{proposition} \label{proposition}~\\
-If $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (Fu(C_{i \rightarrow
-j}\varphi))$ and $(\mathfrak{M_3},s)\models Fu(C_{i \rightarrow
-j}\varphi)$, then $s$ is not reachable from the commitment state.
-\end{proposition}
-
-\begin{theorem} [Epistemic Equivalences]\label{theorm:Epistemic-equivalence} \ \ \ \
-
-    \begin{enumerate}
-        \item $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1}(K_i~\varphi)$  ~~~~~~iff~~  $(\mathfrak{M_3},s) \models K_i~\varphi$
-        \item $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq 0}(K_i~\varphi)$   ~~~~~~iff~~  $(\mathfrak{M_3},s)\models K_i ~\neg \varphi$
-        \item $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[}(K_i~\varphi)$  ~~~~iff~~   $(\mathfrak{M_3},s)\models \neg K_i~\neg\varphi \wedge \neg K_i~\phi$
-        \item $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1}(E_G~\varphi)$  ~~~~iff~~  $(\mathfrak{M_3},s) \models E_G~\varphi$
-        \item $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq 0}(E_G~\varphi)$   ~~~~iff~~  $(\mathfrak{M_3},s)\models E_G ~\neg \varphi$
-        \item $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[}(E_G~\varphi)$  ~~iff~~   $(\mathfrak{M_3},s)\models \neg E_G~\neg\varphi \wedge \neg E_G~\varphi$
-
-    \end{enumerate}
-
-\end{theorem}
-
-\begin{proof} %\hspace{-0.9cm}
-We prove the first three equivalences, the same method can be used to prove the others.
-\begin{itemize}
-\item First equivalence. ~\\
-    $``\Rightarrow"$. Assume $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1} (K_i\varphi)$.
-    By the semantics of PCTL$^{\textrm{kc+}}$, it follows that $Prob((\mathfrak{M_3},s)\models K_i~\varphi)\geq1$.
-    Therefore, $\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\sim_i s'|}\geq1$.
-This means that $\forall s'\in S$ such that $s\sim_i s'$, we have $(\mathfrak{M_3},s')\models \varphi$ (as $\sim_i$ is reflexive, so $s'$ could be $s$ itself).
-Thus, $(\mathfrak{M_3},s) \models K_i ~\varphi$.
-\\
-    $``\Leftarrow"$.
-Assume $(\mathfrak{M_3},s)\models K_i~\varphi$.
-By the PCTL$^{\textrm{kc+}}$ semantics, it follows that for all $s'\in S$ such that $s\sim_i s'$, we have $(\mathfrak{M_3},s')\models \varphi$ (i.e.
-all accessible states from $s$ satisfy $\varphi$).
-    Consequently, $\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| = |s\sim_i s'|$.
-    Therefore, $\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\sim_i s'|}\geq1$ and hence $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1} K_i\varphi)$.
-
-\item Second equivalence. ~\\
-    $``\Rightarrow"$. Assume $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (K_i\varphi)$.
-    By the PCTL$^{\textrm{kc+}}$ semantics, it follows that $Prob((\mathfrak{M_3},s)\models K_i\varphi)\leq0$.
-    Thus, $\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi|}{|s\sim_i s'|}\leq0$.
-Since $\sim_i$ is reflexive, so the set of the accessible states from $s$ is not empty.
-Therefore, $\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi|$ must be 0 (i.e., $\varphi$ is not true in any of the accessible states).
-Consequently, for all $s'\in S$ such that $s\sim_i s'$, we have $(\mathfrak{M_3},s')\nvDash \varphi$, which means $(\mathfrak{M_3},s')\models \neg \varphi$.
-Hence, $(\mathfrak{M_3},s)\models K_i \neg \varphi$.~\\
-%
-    $``\Leftarrow"$.
-Assume $(\mathfrak{M_3},s)\models K_i\neg \varphi$.
-By the PCTL$^{\textrm{kc+}}$ semantics, it follows that $\forall s'\in S$ such that $s\sim_i s'$, we have $(\mathfrak{M_3},s')\nvDash \varphi$.
-Since the set of the accessible states from $s$ is not empty, then $\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\sim_i s'|}\leq0$.
-Hence, $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (K_i\varphi)$.
-
-\item Third equivalence. ~\\
-    $``\Rightarrow"$.
-Assume $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[} K_i\varphi)$.
-By the PCTL$^{\textrm{kc+}}$ semantics, it follows that $0< Prob(s\models K_i\varphi)<1$.
-Thus, $0<\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| }{|s \sim_i s'|}<1$.
-    This means that it would never be the case that $\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| = |s\sim_i s'|$ nor $\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| = 0$.
-Consequently, there exist some $s', s'' \in S$ such that $s\sim_i s'$ and $s\sim_i s''$ and $(\mathfrak{M_3},s')\models \varphi$ and $(\mathfrak{M_3},s'')\models \neg \varphi$.
-Hence, it is impossible to have $(\mathfrak{M_3},\overline{s})\models \neg\varphi$ or $(\mathfrak{M_3},\overline{s})\models \varphi$ for all $\overline{s}\in S$ such that $s\sim_i \overline{s}$.
-Consequently, $(\mathfrak{M_3},s)\nvDash K_i\neg\varphi$ and $(\mathfrak{M_3},s)\nvDash K_i\varphi$.
-Hence $(\mathfrak{M_3},s)\models \neg K_i\neg\varphi$ and $(\mathfrak{M_3},s)\models \neg K_i\varphi$.
-~\\
-    %
-    $``\Leftarrow"$.
-Assume $(\mathfrak{M_3},s)\models \neg K_i\varphi$.
-By the PCTL$^{\textrm{kc+}}$ semantics, it follows that there exists $s'\in S$ such that $s\sim_i s'$ and $(\mathfrak{M_3},s')\models \neg \varphi$.
-Consequently, it would never be the case that for all $s'\in S$ such that $s\sim_i s'$ we have $(\mathfrak{M_3},s')\models \varphi$.
-Therefore, $1>\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\sim_i s'|}$.
-Now assume $(\mathfrak{M_3},s)\models \neg K_i\neg \varphi$.
-Therefore, $\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| = 0$ would never be the case as some accessible states should satisfy $\varphi$.
-Consequently, $\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\sim_i s'|}>0$.
-Thus, $0<\frac{\sum_{s\sim_i s'}|(\mathfrak{M_3},s')\models \varphi| }{|s \sim_i s'|}<1$.
-Hence, $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[} (K_i\varphi)$.
-\end{itemize}
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{theorem} [Commitment Equivalences] \label{theorem:Commitment-Equivelances} ~
-
-\begin{enumerate}
-\item $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1} (C_{i \rightarrow
-j}\varphi)$ ~~~~~iff~~ $(\mathfrak{M_3},s)\models C_{i \rightarrow
-j}\varphi$
-
-\item $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (C_{i \rightarrow
-j}\varphi)$ ~~~~~iff~~ $(\mathfrak{M_3},s)\models C_{i \rightarrow
-j}\neg \varphi$
-
-\item $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[} (C_{i \rightarrow
-j}\varphi)$ ~~~iff~~ $(\mathfrak{M_3},s)\models \neg C_{i
-\rightarrow j}\neg\varphi \wedge \neg C_{i \rightarrow j}\varphi$
-
-\item $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1} (C_{i \rightarrow
-G}\varphi)$ ~~~~iff~~ $(\mathfrak{M_3},s)\models C_{i \rightarrow
-G}\varphi$
-
-\item $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (C_{i \rightarrow
-G}\varphi)$ ~~~~iff~~ $(\mathfrak{M_3},s)\models C_{i \rightarrow
-G}\neg \varphi$
-
-\item $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[} (C_{i \rightarrow
-G}\varphi)$ ~~iff~~ $(\mathfrak{M_3},s)\models \neg C_{i
-\rightarrow G}\neg\varphi \wedge \neg C_{i \rightarrow G}\varphi$
-
-\end{enumerate}
-
-\end{theorem}
-
-\begin{proof}
-We prove the first three equivalences, the same method can be used to prove the others.
-
-\begin{itemize}
-\item First equivalence. ~\\
-    $``\Rightarrow"$. Assume $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1} (C_{i \rightarrow j}\varphi)$.
-    By the PCTL$^{\textrm{kc+}}$ semantics, it follows that $Prob((\mathfrak{M_3},s)\models C_{i\rightarrow j}\varphi)\geq1$.
-    Thus,  $\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\approx_{i \rightarrow j}s'|}\geq1$.
-    This means that for all $s'\in S$ such that $s\approx_{i \rightarrow j}s'$, we have $(\mathfrak{M_3},s')\models \varphi$, and hence $(\mathfrak{M_3},s) \models C_{i\rightarrow j}\varphi$. \\
-    $``\Leftarrow"$. Assume $(\mathfrak{M_3},s)\models C_{i \rightarrow j}\varphi$. By the PCTL$^{\textrm{kc+}}$ semantics, it follows that for all $s'\in S$ such that $s\approx_{i \rightarrow j}s'$,
-    we have $(\mathfrak{M_3},s')\models \varphi$ (i.e. all accessible states from $s$ satisfy $\varphi$).
-    Consequently, $\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| = |s\approx_{i \rightarrow j}s'|$.
-    Therefore, $\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\approx_{i \rightarrow j}s'|}\geq1$
-    and hence, $(\mathfrak{M_3},s)\models \mathbb{P}_{\geq1} (C_{i \rightarrow j}\varphi)$.
-
-\item Second equivalence. ~\\
-    $``\Rightarrow"$. Assume $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (C_{i \rightarrow j}\varphi)$.
-    By the PCTL$^{\textrm{kc+}}$ semantics, it follows that $Prob((\mathfrak{M_3},s)\models C_{i\rightarrow j}\varphi)\leq0$.
-    Thus, $\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi|}{|s\approx_{i \rightarrow j}s'|}\leq0$.
-    Since the set of the accessible states from $s$ is not empty, then $\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi|$
-    must be 0 (i.e.
-$\varphi$ is not true in any of the accessible states).
-Consequently, for all $s'\in S$ such that $s\approx_{i \rightarrow j}s'$, we have $(\mathfrak{M_3},s')\nvDash \varphi$, which means $(\mathfrak{M_3},s')\vdash \neg \varphi$.
-     Hence, $(\mathfrak{M_3},s)\models C_{i\rightarrow j}\neg \varphi$.~\\
-%
-    $``\Leftarrow"$. Assume $(\mathfrak{M_3},s)\models C_{i \rightarrow j}\neg \varphi$. By the PCTL$^{\textrm{kc+}}$ semantics,
-    it follows that for all $s'\in S$ such that
-    $s\approx_{i \rightarrow j}s'$, we have $(\mathfrak{M_3},s')\nvDash \varphi$.
-Since the set of the accessible states from $s$ is not empty, then $\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\approx_{i \rightarrow j}s'|}\leq0$.
-Hence, $(\mathfrak{M_3},s')\models \mathbb{P}_{\leq0} (C_{i \rightarrow j}\varphi)$.
-
-\item Third equivalence. ~\\
-    $``\Rightarrow"$.
-Assume $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[} (C_{i \rightarrow j}\varphi)$.
-By the PCTL$^{\textrm{kc+}}$ semantics, it follows that $0< Prob((\mathfrak{M_3},s)\models C_{i\rightarrow j}\varphi)<1$.
-Thus, $0<\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| }{|s \approx_{i \rightarrow j}s'|}<1$.
-    This means that it would never be the case that $\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| = |s\approx_{i \rightarrow j}s'|$
-    nor $\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| = 0$. Consequently, there exist some $s', s'' \in S$
-    such that $s\approx_{i \rightarrow j}s'$ and $s\approx_{i \rightarrow j}s''$ and $(\mathfrak{M_3},s')\models \varphi$ and $(\mathfrak{M_3},s'')\models \neg \varphi$.
-    Hence, it is impossible to have $(\mathfrak{M_3},\overline{s})\models \neg\varphi$ or $(\mathfrak{M_3},\overline{s})\models \varphi$ for all $\overline{s}\in S$ such that $s\approx_{i \rightarrow j}\overline{s}$.
-Consequently,
-    $s\nvDash  C_{i \rightarrow j}\neg\varphi$ and  $(\mathfrak{M_3},s)\nvDash  C_{i \rightarrow j}\varphi$.
-Hence $(\mathfrak{M_3},s)\models \neg C_{i \rightarrow j}\neg\varphi$ and $(\mathfrak{M_3},s)\models \neg C_{i \rightarrow j}\varphi$.
-~\\
-    %
-    $``\Leftarrow"$.
-Assume $(\mathfrak{M_3},s)\models \neg C_{i \rightarrow j}\varphi$.
-By the PCTL$^{\textrm{kc+}}$ semantics, it follows that there exists $s'\in S$ such that $s\approx_{i \rightarrow j}s'$ and $(\mathfrak{M_3},s')\models \neg \varphi$.
-Consequently, it would never be the case that $(\mathfrak{M_3},s')\models \varphi$ for all $s'\in S$
-    such that $s\approx_{i \rightarrow j}s'$. Therefore,
-    $1>\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\approx_{i \rightarrow j}s'|}$.
-    Now assume $(\mathfrak{M_3},s)\models \neg C_{i \rightarrow j}\neg \varphi$.
-Therefore, $\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| = 0$ would never be he case as some accessible states should satisfy $\varphi$.
-Consequently,
-    $\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| }{|s\approx_{i \rightarrow j}s'|}>0$.
-    Thus, $0<\frac{\sum_{s\approx_{i \rightarrow j}s'}|(\mathfrak{M_3},s')\models \varphi| }{|s \approx_{i \rightarrow j}s'|}<1$.
-Thus, $(\mathfrak{M_3},s)\models \mathbb{P}_{]0,1[} (C_{i \rightarrow j}\varphi)$.
-\end{itemize}
-
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{theorem} [Fulfillment Equivalences] \label{theorem:Fulfiilemt-Equivelances} ~
-
-\begin{enumerate}
-\item $(\mathfrak{M_3},s)\models \mathbb{P}_{>0} (Fu(C_{i \rightarrow
-j}\varphi))$ iff $(\mathfrak{M_3},s)\models Fu(C_{i \rightarrow
-j}\varphi)$ and $s$ is reachable from the commitment state.
-
-\item $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (Fu(C_{i \rightarrow
-j}\varphi))$ iff $(\mathfrak{M_3},s)\models \neg Fu(C_{i \rightarrow
-j}\varphi)$ or $s$ is not reachable from the commitment state.
-
-\item $(\mathfrak{M_3},s)\models \mathbb{P}_{>0} (Fu(C_{i \rightarrow
-G}\varphi))$ iff $(\mathfrak{M_3},s)\models Fu(C_{i \rightarrow
-G}\varphi)$ and $s$ is reachable from the commitment state.
-
-\item $(\mathfrak{M_3},s)\models \mathbb{P}_{\leq0} (Fu(C_{i \rightarrow
-G}\varphi))$ iff $(\mathfrak{M_3},s)\models \neg Fu(C_{i \rightarrow
-G}\varphi)$ or $s$ is not reachable from the commitment state.
-\end{enumerate}
-
-\end{theorem}
-
-\begin{proof} %\hspace{0.5cm} \\
-The proofs of these equivalences are direct from Proposition
-\ref{proposition} and the above semantics.
-
- \end{proof}
-
- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Model Checking PCTL$^{\textrm{kc+}}$ using Reduction} \label{sec:model-checking-pctlkc+}
-
-In this section, we generalize the model checking technique for
-the logic of knowledge and social commitments proposed in
-Chapter \ref{cha:PCTLKC} to cover more complex cases, such as group
-knowledge and group commitment. As we have seen in the previous
-section, the semantics of our new logic PCTL$^{\textrm{kc+}}$ is
-defined over an extended version of interpreted systems
-$\mathfrak{M_3}$. The idea of our proposed verification technique is
-based mainly on reducing the problem of model checking
-PCTL$^{\textrm{kc+}}$ to the problem of model checking PCTL. This
-however involves two processes. First, we define transformation
-rules to transform PCTL$^{\textrm{kc+}}$ model ($\mathfrak{M_3}$) to
-an MDP model to be suitable for PRISM, the probabilistic model
-checker of PCTL. The solution of an MDP comes in the form of an
-``adversary'' \cite{Forejt2011} which is described as a mapping
-of states to probability distributions over actions. Second, we
-construct a set of rules to reduce PCTL$^{\textrm{kc+}}$ formulae
-to PCTL formulae.
-
-In a nutshell, our proposed model checking procedure is as follows. Given $\mathfrak{M_3}=(S,\textbf{P},I,\sim_1, \ldots
-,\sim_n,\{\approx_{i \rightarrow j}\}_{{(i,j)}\in \texttt{Agt}^2},\nu)$, and PCTL$^{\textrm{kc+}}$ formula $\varphi$, we have to define an MDP model $\mathfrak{M_3'}$ = $\mathscr{F}(\mathfrak{M_3})$ and PCTL formula $\mathscr{F}(\varphi)$ using the transformation function $\mathscr{F}$ such that $\mathfrak{M_3} \models \varphi$ iff $\mathscr{F}(\mathfrak{M_3})\models \mathscr{F}(\varphi)$.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=15cm, height=9cm]{chap5/img/relation-translation-cha5.eps}
-%height=8cm]{figures/1.eps}
-\caption{Examples of translating relations in $\mathfrak{M_3}$ into labeled transitions} \label{fig:relation-translation-cha5}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Transforming the Model $\mathfrak{M_3}$} \label{sec:reducing-proposed-model-cha5}
-
-As done in Chapter \ref{cha:PCTLKC}, given an MDP model $\mathfrak{M_3'}$ = $(\mathbb{S}, Act, \textsf{P}_t ,I_i, L)$, a major step in transforming $\mathfrak{M_3}$ into $\mathfrak{M_3'}$ is to define the set of actions $Act$.
-The idea is to map each relation in $\mathfrak{M_3}$ into a corresponding action in $Act$; more specifically, to translate each relation in $\mathfrak{M_3}$ into a labeled transition in $\mathfrak{M_3'}$.
-Then, these labels (also called actions) are used to form the set $Act$ in $\mathfrak{M_3'}$.
-Consequently, the different relations in $\mathfrak{M_3}$ namely, probabilistic transition relations, epistemic accessibility relations, and social accessibility relations, are translated into labeled transitions in $\mathfrak{M_3'}$.
-Moreover, to interpret the fulfillment of a commitment, we need to add the symmetric closure of the transition resulted from translating the social accessibility relation.
-Figure \ref{fig:relation-translation-cha5} (where $n$ is the number of agents, $1 \leq i \leq n$, and $1 \leq j \leq n$) explains the process of translating the probabilistic transition relation $\textbf{P}$, epistemic accessibility relations $\sim_i$, and social accessibility relations $\approx_{i \to j}$ into labeled transitions.
-More precisely, the action $\epsilon$ denotes a transition defined from the probabilistic transition relation $\textbf{P}$, action $\alpha^i$ denotes a transition defined from the epistemic accessibility relation $\sim_i$, action $\beta^{ij}$ denotes a transition defined from the social accessibility relation $\approx_{i \rightarrow j}$, and action $\gamma^{ij}$ denotes a transition added to capture the semantics of the fulfillment of a basic commitment.
-Likewise, the epistemic accessibility relation $\sim_G^E$, and the social accessibility relation $\approx_{i \rightarrow G}$ are translated in the same way where the action $\alpha_G^E$ denotes a transition defined from the epistemic accessibility relation $\sim_G^E$, action $\beta^{G}$ denotes a transition defined from the social accessibility relation $\approx_{i \rightarrow G}$, and the action $\gamma^{G}$ denotes a transition added to capture the semantics of the fulfillment of a group commitment.
-Consequently, the model $\mathfrak{M_3'} = (\mathbb{S}, Act, \textsf{P}_t ,I_i, L)$ can now be defined as follows:
-
-\begin{itemize}
-\item $\mathbb{S}$=$S$; $I_i$=$I$; $L$=$\nu$.
-
-\item $Act = \{\epsilon \} \cup \{\alpha^1, \alpha^2, \dots, \alpha^n, \alpha_G^E\} \cup \{\beta^{11}, \beta^{12}, \dots, \beta^{nn}, \beta^{G}\} \cup \{\gamma^{11}, \gamma^{12}, \dots, \gamma^{nn}, \gamma^{G}\}$ where $n$ is the number of agents.
-
-\item $\textsf{P}_t$ can be defined as the union of the transitions labeled with $\epsilon$,
- transitions labeled with $\alpha^i$, transitions labeled with $\alpha_G^E$, transitions labeled with $\beta^{ij}$, transitions labeled with $\beta^{G}$, transitions labeled with $\gamma^{ij}$, and transitions labeled with $\gamma^{G}$.
-The probabilities of transitions labeled with $\epsilon$ are not manipulated but rather inherited from the probabilistic transition function $\textbf{P}$.
-However, transitions labeled with $\alpha^i$ and emanating from the same state are given equal probabilities which reflect the indistinguishably property of epistemic relations over equivalent states.
-Thus, the probability of each transition annotated by $\alpha^i$ is equal to the probability of each other transition labeled with $\alpha^i$ emanating from the same state which is calculated by dividing one over the number of transitions labeled with $\alpha^i$.
-The probabilities of transitions labeled with $\alpha_G^E$, $\beta^{ij}$, $\beta^{G}$, $\gamma^{ij}$, and $\gamma^{G}$ are calculated in the same way.
-For states $s, s' \in \mathbb{S}$ and  action $\theta \in Act$, the function $\textsf{P}_t$ is defined as follows:
-\begin{equation*}
-    \textsf{P}_t(s, \theta , s' )=
-\begin{cases}
-    \textbf{P}(s, s'),          & \textrm{if}  ~~\theta = \epsilon  \\
-    \frac{1}{|s\sim_i s'|},     & \textrm{if}  ~~ \theta = \alpha^i\\
-    \frac{1}{|s\sim_G^E s'|},     & \textrm{if}  ~~ \theta = \alpha_G^E\\
-    \frac{1}{|s\approx_{i \rightarrow j} s'|},   & \textrm{if}  ~~ \theta = \beta^{ij}\\
-    \frac{1}{|s\approx_{i \rightarrow G} s'|},   & \textrm{if}  ~~ \theta = \beta^{G}\\
-    \frac{1}{|s'\approx_{i \rightarrow j} s|},   & \textrm{if}  ~~ \theta = \gamma^{ij}\\
-    \frac{1}{|s'\approx_{i \rightarrow G} s|},   & \textrm{if}  ~~ \theta = \gamma^{G}
-    \end{cases}
-    \end{equation*}
-
-\end{itemize}
-
-As mentioned earlier, the non-deterministic choices in MDP are
-resolved using the adversary by picking one enabled transition at
-each state, which induces a DTMC model. Technically speaking, the
-adversary is a function from the state set $S$ to the action set
-$Act$ such that it chooses in any state $s$ one of the enabled
-actions. In particular, we define seven adversaries
-($\sigma_\epsilon$, $\sigma_e$, $\sigma_G^E$, $\sigma_c$,
-$\sigma_c^G$, $\sigma_f$, $\sigma_f^G$) that are used to define
-DTMCs from the obtained MDP model as follows: $\sigma_\epsilon$
-captures only the semantics of regular temporal formulae,
-$\sigma_e$ captures the semantics of the knowledge formulae,
-$\sigma_G^E$ captures the semantics of the operator everyone in
-the group knows, $\sigma_c$ captures he semantics of the basic
-commitment, $\sigma_c^G$ captures the semantics of group social
-commitment, $\sigma_f$ captures the semantics of the fulfillment
-of the basic commitment, and $\sigma_f^G$ captures the semantics
-of the fulfillment of group commitment. Concretely, we set the
-adversary $\sigma_\epsilon$ in such a way that always selects the
-transitions labeled by $\epsilon$ at each state in the model. This
-results in a DTMC model that captures only probabilistic temporal
-transitions inherited from $\textbf{P}$ and ignores all
-transitions obtained by translating the various accessibility
-relations. The adversary $\sigma_e$ always picks the action
-$\alpha^i$ at the state $s$ and then selects the action $\epsilon$
-at all following states (i.e., first the transitions resulted from
-the accessibility relations $\sim_i$ are considered, and then the
-normal transitions), and so on for the other adversaries.
-
-To this end, we introduce our reduction rules that translate each PCTL$^{\textrm{kc+}}$ formula to PCTL formula w.r.t a given adversary.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Reducing PCTL$^{\textrm{kc+}}$ Formulae into PCTL Formulae} \label{sec:reducing-pctlkc-to-pctl-cahp5}
-
-The PCTL$^{\textrm{kc+}}$ formulae are reduced inductively into PCTL as follows:
-
-$\mathscr{F}(p)=p$, if $p$ is an atomic proposition,
-
-$\mathscr{F}(\neg \varphi)= \neg \mathscr{F} (\varphi)$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k}(\varphi \vee \psi))=\mathbb{P}_{\bowtie k}(\mathscr{F}(\varphi) \vee \mathscr{F}(\psi))$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k}\bigcirc \varphi)=\mathbb{P}_{\bowtie k} \bigcirc \mathscr{F}(\varphi)$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k}(\varphi~ U ~ \psi))=\mathbb{P}_{\bowtie k} (\mathscr{F}(\varphi) U \mathscr{F}(\psi))$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k}(\varphi~ U^{\leq m} ~ \psi))=\mathbb{P}_{\bowtie k} (\mathscr{F}(\varphi) U^{\leq m} \mathscr{F}(\psi))$,
-
-$\mathscr{F}(K_i ~\varphi)= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k} K_i ~\varphi)= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(\varphi))$,
-
-$\mathscr{F}(E_G ~\varphi)= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k} E_G ~\varphi)= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(\varphi))$,
-
-$\mathscr{F}(C_{i\rightarrow j} ~\varphi)= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k} C_{i\rightarrow j} ~\varphi)= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(\varphi))$,
-
-$\mathscr{F}(C_{i\rightarrow G} ~\varphi)= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k} C_{i\rightarrow G} ~\varphi)= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(\varphi))$,
-
-$\mathscr{F}(Fu(C_{i\rightarrow j} ~\varphi))= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(C_{i\rightarrow j} ~\varphi))= \mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k} Fu(C_{i\rightarrow j} ~\varphi))= \mathbb{P}_{\bowtie k} (\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(C_{i\rightarrow j} ~\varphi))= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$,
-
-$\mathscr{F}(Fu(C_{i\rightarrow G} ~\varphi))= \mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(C_{i\rightarrow G} ~\varphi))= \mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$,
-
-$\mathscr{F}(\mathbb{P}_{\bowtie k} Fu(C_{i\rightarrow G} ~\varphi))= \mathbb{P}_{\bowtie k} (\mathbb{P}_{\geq 1}\bigcirc\mathscr{F}(C_{i\rightarrow G} ~\varphi))= \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))))$.\\
-
-To complete the reduction process, each PCTL formula has to be
-interpreted over a DTMC model $\mathcal{D}$ =
-$(S,\overline{s},\mathbf{P},L)$. This is achieved by indicating
-which adversary is associated with which formula. In the
-following, $(\mathfrak{M_3'},s)\models_{\sigma_\epsilon} \varphi$
-means that the PCTL formula $\varphi$ holds in the model
-$\mathcal{D}$ obtained by applying the adversary $\sigma_\epsilon$
-at state $s$. The following theorem is a direct consequence of the
-definition of $\mathscr{F}$ and can be easily proved by induction
-on the structure of the formula.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{theorem}[Transformation Satisfaction]\label{theorem:transf-satisf} \hspace{0.5cm}
-
-Considering the following adversaries: $\sigma_\epsilon$, $\sigma_c$, $\sigma_c^G$, $\sigma_f$, $\sigma_f^G$, $\sigma_e$, and $\sigma_G^E$ (which are DTMCs capturing temporal, commitment, and epistemic formulae in the model $\mathfrak{M_3}$), the following equivalences hold:
-
-$(\mathfrak{M_3},s)\models p ~~~~~~~~~~~~~~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_\epsilon} p$
-
-$(\mathfrak{M_3},s)\models \neg \varphi ~~~~~~~~~~~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s)\models_{\sigma_\epsilon} \neg \mathscr{F}(\varphi)$
-
-$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}(\varphi \vee \psi)
-~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_\epsilon}
-\mathbb{P}_{\bowtie k} \mathscr{F}(\varphi) \vee
-\mathbb{P}_{\bowtie k} \mathscr{F}(\psi) $
-
-$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}\bigcirc\varphi ~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_\epsilon} \mathbb{P}_{\bowtie k} \bigcirc \mathscr{F}(\varphi)$
-
-$(\mathfrak{M_3},s)\models\mathbb{P}_{\bowtie k}(\varphi~ U ~ \psi) ~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_\epsilon} \mathbb{P}_{\bowtie k}(\mathscr{F}(\varphi)~ U ~\mathscr{F}(\psi))$
-
-$(\mathfrak{M_3},s)\models\mathbb{P}_{\bowtie k}(\varphi~ U^{\leq m} ~ \psi) ~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_\epsilon} \mathbb{P}_{\bowtie k}(\mathscr{F}(\varphi)~ U^{\leq m} ~\mathscr{F}(\psi))$
-
-$(\mathfrak{M_3},s)\models K_i \varphi ~~~~~~~~~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s)\models_{\sigma_e} \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$
-
-$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}K_i \varphi ~~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_e} \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi)))$
-
-$(\mathfrak{M_3},s)\models E_G \varphi ~~~~~~~~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s)\models_{\sigma_G^E} \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$
-
-$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}E_G \varphi ~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_G^E} \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi)))$
-
-$(\mathfrak{M_3},s)\models C_{i \rightarrow j}\varphi ~~~~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s)\models_{\sigma_c} \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$
-
-$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}C_{i \rightarrow j}\varphi ~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_c} \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi)))$
-
-$(\mathfrak{M_3},s)\models C_{i \rightarrow G}\varphi ~~~~~~~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s)\models_{\sigma_c^G} \mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$
-
-$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}C_{i \rightarrow j}\varphi ~~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_c^G} \mathbb{P}_{\bowtie k}(\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi)))$
-
-$(\mathfrak{M_3},s)\models Fu(C_{i \rightarrow j}\varphi) ~~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_f} \mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$
-
-$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}Fu(C_{i \rightarrow j}\varphi) ~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_f} \mathbb{P}_{\bowtie k} (\mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))))$
-
-$(\mathfrak{M_3},s)\models Fu(C_{i \rightarrow G}\varphi) ~~~~~~~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_f^G} \mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi)))$
-
-$(\mathfrak{M_3},s)\models \mathbb{P}_{\bowtie k}Fu(C_{i \rightarrow j}\varphi) ~\text{iff}~ (\mathfrak{M_3'},s) \models_{\sigma_f^G} \mathbb{P}_{\bowtie k} (\mathbb{P}_{\geq 1}(\bigcirc\mathbb{P}_{\geq 1}(\bigcirc \mathscr{F}(\varphi))))$
-
-\end{theorem}
-
-This theorem emphasizes that each translated PCTL$^{\textrm{kc+}}$
-formula must be interpreted over an appropriate DTMC. That is, if
-the PCTL$^{\textrm{kc+}}$ formula includes only temporal
-operators, then the corresponding PCTL formula is interpreted over
-the DTMC obtained by only considering the normal transitions
-(i.e., $\sigma_\epsilon$). Moreover, if the formula has the form
-of $K_i~\varphi$, then the corresponding PCTL formula is
-interpreted over the DTMC obtained by considering first the
-transitions resulted from translating epistemic accessibility
-relations $\sim_i$ and then the normal transitions, which shows
-why the $K$ operator is translated into the next operator
-$\bigcirc$. The same intuition holds for the other epistemic and
-social formulae.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\begin{theorem} [Soundness and Completeness of
-$\mathscr{F}$] \label{soundness-CTLKC+}~\\ Let $\mathfrak{M_3}$ and
-$\Phi$ be respectively PCTL$^{\textrm{kc+}}$ model and formula and
-let $\mathscr{F}(\mathfrak{M_3})$  and $\mathscr{F}(\Phi)$ be the
-corresponding model and formula in PCTL. We have
-$\mathfrak{M_3}\models\Phi$ iff $\mathscr{F}(\mathfrak{M_3}) \models
-\mathscr{F}(\Phi)$.
-\end{theorem}
-
-\begin{proof} %\hspace{0.5cm} \\
-To prove the soundness (i.e., the necessary condition) and
-completeness (i.e., the sufficient condition) of the proposed
-reduction technique, we prove that the following three cases are
-sound and complete: $\Phi = K_i \varphi$, $\Phi = C_{i \rightarrow
-j} \varphi$ and $\Phi = Fu(C_{i \rightarrow j} \varphi)$. We prove
-this by induction on the structure of the formula $\Phi$. The
-cases when $\Phi = E_G \varphi$, $\Phi = C_{i \to G} \varphi$, and
-$\Phi = Fu(C_{i \to G} \varphi)$ can be proved in a similar way.
-The cases of PCTL$^{\textrm{kc+}}$ formulae that are also PCTL
-formulae are straightforward.
-
-\begin{itemize}
-\item $\Phi = K_i ~\varphi$. We have $(\mathfrak{M_3},s)\models K_i
-~\varphi ~\text{iff}~ (\mathfrak{M_3},s') \models \varphi$ for every
-$s' \in S ~\textrm{such that}~ s\sim_i s'$. Therefore,
-$(\mathfrak{M_3},s)\models K_i ~\varphi ~\text{iff}~
-(\mathscr{F}(\mathfrak{M_3}),s) \models \mathscr{F}(K_i~\varphi)$.
-We know that $\mathscr{F}(\mathfrak{M_3})= \mathfrak{M_3'}$. Now,
-$(\mathfrak{M_3'},s) \models \mathscr{F}(K_i~\varphi)$ iff for every
-$s' \in \mathbb{S} ~\textrm{such that}~ (s,\alpha^i,s') \in
-\textsf{P}_t$, we have $(\mathfrak{M_3'},s') \models
-\mathscr{F}(\varphi)$. However, w.r.t the semantics of $~\sigma_e$
-which is a DTMC defined to interpret commitment formulae over
-$\mathfrak{M_3'}$, it follows that every infinite path $\pi \in
-\Pi^{\sigma_e}(s)$ satisfies that $\pi(1)=s'$ and
-$(\sigma_e,\pi(1))\models \mathscr{F}(\varphi)$. Thus,
-$(\sigma_e,s)\models \bigcirc\mathscr{F}(\varphi)$ for all $\pi
-\in \Pi^{\sigma_e}(s)$. As the path quantifier $A$ is not defined
-in PCTL, and we have $\mathbb{P}_{\geq1}$ instead, so we obtain
-$(\sigma_e,s)\models
-\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$.
-
-\item $\Phi = C_{i \rightarrow j} \varphi$. We have
-$(\mathfrak{M_3},s)\models C_{i\rightarrow j}\varphi ~\text{iff}~
-(\mathfrak{M_3},s') \models \varphi$ for every $s' \in S
-~\textrm{such that}~ s\approx_{i \rightarrow j}s'$. Consequently,
-$(\mathfrak{M_3},s) \models C_{i\rightarrow j} \varphi ~\text{iff}~
-(\mathfrak{M_3'},s) \models \mathscr{F}(C_{i\rightarrow j}
-\varphi)$. It follows that, $(\mathfrak{M_3},s) \models
-\mathscr{F}(C_{i\rightarrow j}\varphi)$ iff for every $s' \in
-\mathbb{S} ~\textrm{such that}~ (s,\beta^{ij},s') \in
-\textsf{P}_t$, we have $(\mathfrak{M_3'},s') \models
-\mathscr{F}(\varphi)$. Now, based on the adversary $~\sigma_c$
-which is a DTMC defined to interpret commitment formulae over
-$\mathfrak{M_3}$, every infinite path $\pi \in \Pi^{\sigma_c}(s)$
-satisfies that $\pi(1)=s'$ and $(\sigma_c,\pi(1))\models
-\mathscr{F}(\varphi)$. Thus, $(\sigma_c,s)\models
-\bigcirc\mathscr{F}(\varphi)$ for all $\pi \in \Pi^{\sigma_c}(s)$.
-As the path quantifier $A$ is not defined in PCTL, and we have
-$\mathbb{P}_{\geq1}$ instead, so we obtain $(\sigma_c,s)\models
-\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$.
-
-\item $\Phi = Fu(C_{i \rightarrow j} \varphi)$. We have
-$(\mathfrak{M_3},s)\models Fu(C_{i\rightarrow j}\varphi)$ iff there
-exists $s'\in S$ such that $s'\approx_{i \rightarrow j}s~
-\text{and~}(\mathfrak{M_3},s')\models C_{i \rightarrow j}\varphi$.
-Consequently, $(\mathfrak{M_3},s)\models
-\mathscr{F}(Fu(C_{i\rightarrow j}\varphi))$ iff there exists $s'
-\in \mathbb{S}$ such that $(s,\gamma^{ij},s') \in \textsf{P}_t$
-and $(\mathfrak{M_3'},s') \models \mathscr{F}(C_{i \rightarrow
-j}\varphi)$. Now, w.r.t the adversary $\sigma_f$ which is a DTMC
-defined to interpret fulfillment formulae over $\mathfrak{M_3}$, we
-obtain at least one infinite path $\pi \in \Pi^{\sigma_f}(s)$ that
-satisfies $\pi(1)=s'$ and $(\sigma_f,\pi(1))\models
-\mathscr{F}(C_{i \rightarrow j}\varphi)$. Since $E$ is equivalent
-to $\mathbb{P}_{>0}$ and $\mathscr{F}(C_{i \rightarrow j}\varphi)$
-is equivalent to
-$\mathbb{P}_{\geq1}(\bigcirc\mathscr{F}(\varphi))$, so we obtain
-$(\sigma_f,s)\models \mathbb{P}_{>0}(\bigcirc\mathbb{P}_{\geq
-1}(\bigcirc \mathscr{F}(\varphi)))$.
-\end{itemize}
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Implementation}\label{sec:implementation-cha5}
-
-We consider the web-based online shopping system \cite{Gomaa2011}
-as a case study to evaluate the effectiveness of our proposed
-verification technique.
-
-\subsection{Online Shopping System}\label{sec:Online-s-s}
-
-The online shopping system aims at
-providing an online shopping environment for customers. Customers
-can request to purchase one or more items from the supplier. By
-requesting an item, the customer commits towards the supplier to
-pay in order for the request to take place. Once the order is
-paid, the supplier confirms the order, and commits to deliver the
-requested item and enters a planned shipping date. Finally, when
-the order is shipped, the customer is notified. Requested item is
-either successfully delivered or refund is issued otherwise.
-
-Because of the uncertainty associated to the underlying infrastructures of both commitments (i.e., the internet through which the payment is made and the transport system through which the delivery of purchased goods is done), there is no guarantee that these commitments are going to be fulfilled.
-Reasoning about and verifying the commitment to pay and the commitment to deliver have to be tackled with uncertainty in mind so that the degree of fulfilling each commitment can be measured, and so on.
-
-We verify the online shopping system by means of
-the reduction-based model check technique proposed in Section
-\ref{sec:model-checking-pctlkc+}. Figure \ref{fig:Online-ss}
-depicts a model for an interaction scenario between one supplier
-and one customer.
-In every experiment, we enlarge the system by increasing the number of customers only.
-For simplicity, we assume that all customers perform the same commitment, which is the commitment to pay for the requested item, respectively.
-We also assume that the supplier commits to all customers (i.e.
-a group commitment) to deliver the requested
-items. This allows us to verify both classes of commitment; basic
-social commitments and group social commitments.
-
-\begin{figure}%[H]
-                \begin{center}
-                \includegraphics[width=14cm, height=10cm]{chap5/img/online-s-s.eps}
-                %height=9cm]{figures/test}
-                \end{center}
-                \caption{A model for the case of one supplier and one customer} \label{fig:Online-ss}
-%                \label{Stack}
-                \end{figure}
-
-\subsection{System Properties}\label{sec:properties}
-
-Properties that capture the probabilistic behavior of the online
-shopping system have been verified using PRISM in various
-proposals, for instance \cite{Ouchani2014}. In this section,
-special emphasis is given to properties related to the concepts of
-knowledge and social commitments. Concretely, we verify some
-system's properties such as \textit{Safety}, \textit{Liveness}, and \textit{Reachability} that involve probabilistic
-knowledge, probabilistic commitments, and combinations of both.
-For the case of social commitments, our verification covers both
-basic and group social commitments. All defined properties are
-expressed in PCTL$^{\textrm{kc+}}$.
-
-\begin{itemize}
-\item \texttt{Safety Property:} Verifying formulae expressing this property in the system models ensures avoiding the appearance of bad situations in the real systems.
-One bad situation that need to be verified is when the (Cus) fulfills his commitment to pay for the requested order but the (Sup) does not commit to deliver the requested item.
-This situation can be expressed in PCTL$^{\textrm{kc+}}$ as follows: \\
-$\varphi_2= \mathbb{P}_{\geq1}\Box\neg[\mathbb{P}_{>0} \Diamond
-Fu(C_{cus\to sup} (Pay))\wedge \mathbb{P}_{\geq1}\Box\neg
-(C_{sup\to cus} (Deliver))]$
-
-\item \texttt{Liveness Property:} In all computation paths it is always the case that if the customer commits to pay for the requested item, then in the future the customer will eventually make the payment.
-This can be expressed in PCLT$^{\textrm{kc+}}$ as follows:\\
-$\varphi_3= \mathbb{P}_{\geq1}[(C_{cus\to sup} (Pay))\supset \mathbb{P}_{\geq1}\Diamond Fu(C_{cus\to sup} (Pay))]$
-
-\item \texttt{Reachability Property:} One possible example with regard to the online shopping system is that if the customer (Cus) commits towards the supplier (Sup) to pay for the requested item, the state at which the customer can fulfill his commitment should be reached from the initial state.
-That is, there should be a possibility from the initial state for the customer to reach the fulfilment state.
-This can be formally expressed in PCLT$^{\textrm{kc+}}$ as follows:\\
-$\varphi_1= \mathbb{P}_{>0} \Diamond Fu(C_{cus\to sup} (Pay))$.
-
-\end{itemize}
-
-Furthermore, thanks to the probabilistic model clacking technique,
-we can also get the satisfiability of given formulae in terms of
-quantitative results. That is, checking whether a given formula
-holds in the model with a threshold (at least 0.95\% for example)
-is achievable. Let us consider the following examples:
-
-\begin{itemize}
-    \item Once the customer fulfills his commitment to pay, he will be aware about the payment with at least 0.95\%.\\
-      $\varphi_4 = P_{>0.95}~ Fu (C_{cus\to sup} (Pay)) \supset K_{cus} Pay$
-
-    \item Once the customer fulfills his commitment to pay, the supplier will be aware about the payment  with at least 0.98\%.\\
-      $\varphi_5 = P_{>0.98}~ Fu (C_{cus\to sup} (Pay)) \supset K_{sup} Pay$
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Experimental Results}\label{sec:Experimental-results-cha5}
-
-The online shopping system is encoded into the PRISM input
-language as follows. Supplier agent (Sup) and Customer agent (Cus)
-are mapped into \emph{modules} in the PRISM language. Each agent's
-actions are used to determine the behavior of the agent (i.e., his
-local states). For example, Supplier's actions (variables) are:
-\textit{Accept}: Accept the request, \textit{Reject}: Reject the
-request, \textit{Deliver}: Deliver the requested item,
-\textit{Receipt}: Send receipt, \textit{Refund}: Refund in case of
-not delivery. The global model is obtained by the synchronization
-between all modules (agents).
-
-Our implementation was performed on a TOSHIBA laptop equipped with
-32-bit Windows XP with 1 GB of RAM and Genuine Intel(R) CPU at 1.6
-GHz. Table \ref{Model-Construction-chap5} reports the results of 15
-experiments wherein (Exp.\#) denotes the experiment number,
-(\#Agent) denotes the number of agents, (\#States) denotes the
-number of reachable states, (\#Transitions) denotes the number of
-transitions, and (Construction Time) denotes the time needed for
-building the simulated model in seconds. \\
-
-First experiment started with only two agents; One supplier (Sup) and one Customer (Cus).
-In the rest of experiments, we add one more customer (Cus) each time and report the changes occurring in the size of the model and
-the time needed for building the model.
-These results show that (\#States) and (\#Transitions) grow up exponentially as the system is augmented with more agents.
-However, the (Construction Time) increases polynomially till we reach a point close to the state
-explosion, then it grows up dramatically. Figure
-\ref{fig:model-time-cha5} shows the increase in the construction
-time as more agents join the system. This dramatic change in the
-time needed to build the model reflects the fact that the model
-size becomes massive.
-
-%\begin{table}[htp][H]
-\begin{table}%[H]
-\centering \caption{Verification results of the online shopping
-system} \label{Model-Construction-chap5}
-\resizebox{\textwidth}{!}{ %
-\begin{tabular}{|c|c|l|l|c|}
-\hline
-\texttt{Exp.\#} &   \texttt{\#Agents}    & \texttt{\#States} & \texttt{\#Transitions} & \texttt{Const. Time (s)}\\
-\hline\hline
-\texttt{Exp.1}   &2             &30            & 74              &0.031\\
-\hline
-\texttt{Exp.2}   &3             &210           &700              &0.039\\
-\hline
-\texttt{Exp.3}   &4             &1470          &6102             &0.047\\
-\hline
-\texttt{Exp.4}   &5           &$1.02*10^{4}$    &$5.10*10^{4}$   &0.063\\
-\hline
-\texttt{Exp.5}   &6           &$7.20*10^{4}$    &$4.15*10^{5}$   &0.078\\
-\hline
-\texttt{Exp.6}   &7           &$5.04*10^{5}$    &$3.31*10^{6}$   &0.109\\
-\hline
-\texttt{Exp.7}   &8           &$3.52*10^{6}$    &$2.60*10^{7}$   &0.189\\
-\hline
-\texttt{Exp.8}   &9           &$2.47*10^{7}$    &$2.03*10^{8}$   &0.328\\
-\hline
-\texttt{Exp.9}   &10          &$1.73*10^{8}$    &$1.56*10^{9}$    &0.516\\
-\hline
-\texttt{Exp.10}  &11          &$1.21*10^{9}$     &$1.19*10^{10}$   &0.765\\
-\hline
-\texttt{Exp.11}  &12          &$8.47*10^{9}$    &$9.01*10^{10}$   &1.406\\
-\hline
-\texttt{Exp.12}  &13          &$5.93*10^{10}$   &$6.79*10^{11}$   &2.219\\
-\hline
-\texttt{Exp.13}  &14          &$4.15*10^{11}$    &$5.09*10^{12}$  &6.094\\
-\hline
-\texttt{Exp.14}  &15          &$2.91*10^{12}$   &$3.8*10^{13}$    &8.046\\
-\hline
-\texttt{Exp.15}  &16          &$2.03*10^{13}$  &$2.82*10^{14}$    &13.406\\
-\hline
-\end{tabular}}
-\end{table}
-
-\begin{figure}%[H]
-                \begin{center}
-                %\includegraphics[width=10cm, height=6cm]{chap5/img/construction-time-cha5.eps}
-                \includegraphics[width=10cm, height=6cm]{chap5/img/time5.eps}
-                %height=9cm]{figures/test}
-                \end{center}
-                \caption{Model construction time for the online shopping system} \label{fig:model-time-cha5}
-%                \label{Stack}
-                \end{figure}
-
-Table \ref{formulae-prism-results-cha5} reports the model checking
-results for the defined formulae ($\varphi_1$ to $\varphi_5$) for
-the case of two agents (one customer and one supplier). All
-formulae hold in the model as expected, which reflects the success
-of our proposed model checking technique in verifying the system
-properties expressed using the probabilistic logic
-PCTL$^{\textrm{kc+}}$. Moreover, as shown in Table
-\ref{formulae-prism-results-cha5}, although the model checking
-time varies from one formula to another, it is still short
-compared to the time needed for building the model.
-
-For scalability purposes, starting from experiment \#2, we re-write the above-defined formulae in a parameterized form as follows:
-
-$\varphi_1'= \mathbb{P}_{>0} \Diamond \bigwedge\limits_{i=1}^n Fu(C_{cus_i\to sup} (Pay_i))$.
-
-$\varphi_2'= \mathbb{P}_{\geq1}\Box\neg[\mathbb{P}_{>0} \Diamond \bigwedge\limits_{i=1}^n
-Fu(C_{cus_i\to sup} (Pay_i))\wedge \mathbb{P}_{\geq1}\Box\neg
-(C_{sup\to cus_i} (Deliver_i))]$
-
-$\varphi_3'= \mathbb{P}_{\geq1}[\bigwedge\limits_{i=1}^n (C_{cus_i\to sup} (Pay_i))\supset \mathbb{P}_{\geq1}\Diamond Fu(C_{cus_i\to sup} (Pay_i))]$
-
-$\varphi_4' = P_{>0.95}~ \bigwedge\limits_{i=1}^n Fu (C_{cus_i\to sup} (Pay_i)) \supset K_{cus_i} Pay_i$
-
-$\varphi_5' = P_{>0.98}~ \bigwedge\limits_{i=1}^n Fu (C_{cus_i\to sup} (Pay_i)) \supset K_{sup}
-Pay_i$\\
-%
-where $n$ is the number of agents in the experiment.
-
-\begin{table}%[H]
-\centering \caption{Results of model checking some properties for the online shopping system} \label{formulae-prism-results-cha5}
-\begin{tabular}{|c|c|c|}
-\hline
-\texttt{Formulae} &   \texttt{Results}    & \texttt{Time for MC (Sec.)} \\
-\hline\hline
-$\varphi_1$                &true           &0.06  \\
-\hline
-$\varphi_2$                &true           &0.13  \\
-\hline
-$\varphi_3$                &true           &0.11  \\
-\hline
-$\varphi_4$                &true           &0.06  \\
-\hline
-$\varphi_5$                &true           &0.07  \\
-\hline
-\end{tabular}
-\end{table}
-
-To be able to verify group social commitments, which is one of the
-main motivations of this chapter, we need models of one supplier
-agent interacting with two or more customer agents by means of
-social commitments. Table \ref{formulae-prism-group-comm-cha5}
-reports the results of verifying group social commitments for
-experiment \#2 and experiment \#3 using the proposed
-reduction technique.
-In experiment \#2, we have one supplier (Sup) committing to two customers (Cus$_1$) and (Cus$_2$) to deliver the goods.
-The commitment should be fulfilled in the future to meet the liveness property.
-Likewise, in experiment \#3, we have one supplier (Sup) committing to three customers (Cus$_1$), (Cus$_2$), and (Cus$_3$) to deliver the requested items.
-
-\noindent $\varphi_6= \mathbb{P}_{\geq1}[(C_{sup \to \{cus_1,cus_2\}} (Deliver))\supset \mathbb{P}_{\geq1}\Diamond Fu(C_{sup \to \{cus_1,cus_2\}} (Deliver))]$
-
-\noindent $\varphi_7= \mathbb{P}_{\geq1}[(C_{sup \to \{cus_1,cus_2,cus_3\}} (Deliver))\supset \mathbb{P}_{\geq1}\Diamond Fu(C_{sup \to \{cus_1,cus_2,cus_3\}} (Deliver))]$
-
-\noindent We were also successful in verifying formulae expressing the interaction between knowledge and group social commitments for experiment \#2 and experiment \#3 as shown below.
-
-\noindent $\varphi_8 = \mathbb{P}_{\geq1}[Fu (C_{sup \to \{cus_1,cus_2\}} (Deliver)) \supset K_{cus_1} (Deliver) \wedge  K_{cus_2} (Deliver)$]
-
-\noindent $\varphi_9 = \mathbb{P}_{\geq1}[Fu (C_{sup \to \{cus_1,cus_2,cus_3\}} (Deliver)) \supset K_{cus_1} (Deliver) \wedge  K_{cus_2} (Deliver) \wedge  K_{cus_3} (Deliver)$]\\
-
-Where, $\varphi_8$ states that the fulfilment of a group commitment (the commitment from $sup$ to $cus_1$ and $cus_2$ to deliver) implies that every creditor in the group will know about the content of the commitment (i.e., $cus_1$ and $cus_2$ will know about the delivery).
-Similarly, $\varphi_9$ states the same meaning in the case when $sup$ fulfills its commitment to three customers.
-
-\begin{table}[htp]
-\centering \caption{Model checking group commitment formulae} \label{formulae-prism-group-comm-cha5}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\texttt{Exp.\#}  &\texttt{\#Agents}  &\texttt{Formulae} &\texttt{Results} \\
-\hline\hline
-Exp.2            & 1 Sup, 2 Cus      &$\varphi_6$           &true  \\
-\hline
-Exp.3            & 1 Sup, 3 Cus      &$\varphi_7$           &true  \\
-\hline
-Exp.2            & 1 Sup, 2 Cus      &$\varphi_8$           &true  \\
-\hline
-Exp.3            & 1 Sup, 3 Cus      &$\varphi_9$           &true  \\
-\hline
-
-\end{tabular}
-\end{table}
-
+In this chapter
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In this chapter, we introduced a formal approach for specifying and
-verifying the interactions between basic (individual) and group social commitments and knowledge in probabilistic MASs. The
-proposed approach encompasses three main parts. In the first
-part, we presented a new probabilistic logic of knowledge and
-commitments (PCLT$^{\textrm{kc+}}$). The expressive power of
-PCLT$^{\textrm{kc+}}$ outperforms those of existing logics because
-of its ability to express and specify not only the concepts of
-knowledge and social commitments independently, but also their
-interactions in the presence of uncertainty. Also, being enriched
-by operators for the group knowledge and group commitments,
-PCLT$^{\textrm{kc+}}$ allows handling more complicated commitment
-scenarios with respect to the number of participating agents. We
-categorized social commitments into two classes based on the
-number of participating agents; basic social commitment (the
-common one-to-one scheme) and group social commitment (one-to-many
-scheme). We then presented a formal semantics for the group social
-commitment. With such a classification of social commitments, we
-gain an insight into different ways to utilize commitments among
-communicating parties. In contrast, exiting solutions for social commitments restrict themselves to the common one-to-one commitment scheme.
-
-In the second part, we proposed a sound and complete reduction-based model checking technique for the new logic.
-The proposed technique consists of reducing the problem of model checking PCLT$^{\textrm{kc+}}$ to the problem of model checking PCTL.
-The soundness and completeness of the reduction technique were proven.
-Finally, in the third part, we used the
-PRISM tool to implement our reduction technique and check
-PCLT$^{\textrm{kc+}}$ formulae by checking their corresponding
-PCTL formulae without adding new computation cost. In terms of scalability, we showed that our reduction technique is scalable as we were
-successfully able to apply it on models of size up to $10^{13}$
-states and $10^{14}$ transitions. To conclude, the two main findings of this chapter are:
- \begin{enumerate}
- \item Simply combining a probabilistic logic of knowledge and a probabilistic logic of commitments to capture the interactions between the concept of knowledge and social commitments in probabilistic MASs is not quite working as excepted.
- \item Representing group social commitments and the interactions between group social commitments and knowledge in the presence of uncertainty become attainable by the use of our proposed framework.
- \end{enumerate}
+In this chapter,

### 2015-04-22 thesis/thesis/chap6/chap6.tex
changes

--- 2015-04-05 thesis/others/khalid/chap6/chap6.tex
@@
 
-There is still a long way to go in order to develop a comprehensive framework for probabilistic social commitments in MASs.
-In the future, we plan to extend our work by investigating several directions.
-
-First, time complexity and space complexity of our proposed verification techniques are not analysed yet.
-Therefore, we intend to compute the complexity of the proposed reduction techniques of the three components.
-
-Second, we are planning to extend our framework to support more commitment schemes such as many-to-one and many-to-many commitments.
-This is extremely important because in real settings there exist situations where performing such commitment scenarios contributes towards improving the efficiency of MASs.
-
-Third, integrating more commitment actions (such as assign, delegate, ..etc) \cite{Singh2000} are of a great interest to investigate.
-This helps ensure that all possible commitment operations employed in probabilistic environments are adequately dealt with.
-
-Forth, we intend to explore the interaction between social commitments and norms in probabilistic systems.
-
-Fifth, another direction that we intend to explore is the probabilistic conditional social commitments.
-Conditional social commitment is still in  its infancy \cite{Kholy2014} and investigating it in systems exhibiting stochastic behavior is an open point for research.
-
-Finally, we plan to extend the PRISM model checker to accommodate our new operators (i.e.
-commitment and group commitment) and then develop dedicated verification algorithms for the proposed logics and implement them directly into PRISM.
-So doing will allow us to compare the results obtained from the indirect method (reduction-based techniques) with the results of the direct method (dedicated algorithms).
+There is
 
@@
 \end{itemize}
-
-%. Abstracting tokens and control paths
-
-%This thesis can be extended in the following directions.
-% \begin{itemize}
-%   \item Extend our semantic to support more SysML features,
-%   \item We intend to formalize SysML and UML daigrams such as state machines and sequence diagrams,  then,
-%   \item Extend our framework to support them
-%   \item Extend the specification framework to handle the reliability requirements and prove formally the soundness of the proposed framework.
-%   \item we intend to transform a SysML activity diagram to its fractal form in order to benefit from our abstraction framework.
-This helps in the abstraction/refinement process of UML/SysML diagrams.
-Second, we extend our framework to handle other UML and SysML models such as state machine and sequence diagrams.
-%  \item  Finally, we intend to investigate reducing the property within the model and applying our approach on different real systems.
-%  \item Abstracting tokens and control paths.
-%  \item Framework Extension: Extend our security verification framework to support other SysML behavioral diagrams: State machine, and Sequence diagrams,
-%  \item Ensure the equivalence between SysML behavioral diagrams,
-%  \item Extract the syntax from the metamodels.
-%  \item Studying the completeness of system completeness.
-%  \item Compositional verification for other operators.
-%  \item we plan to extend our framework to handle more compositional verification techniques like assume-guaranty.
-%  \item we explore other abstraction approaches especially data abstraction targeting more system features like time and data.
-%  \item Finally, we intend to investigate reducing the property within the model.
-%   \item Finally, we want to validate our approach on cyber-forensics systems.
-% \end{itemize}
-
-%In future, we would like to extend our work by investigating several directions.
-%First, we intend to build our implementation within PRISM model checker.
-Second, we plan to extend our framework to handle more compositional verification techniques like assume-guaranty.
-Next, we explore other abstraction approaches especially data abstraction targeting more system features like time and data.

### 2015-05-06 thesis/thesis/chap2/chap2.tex
changes

@@
 
-        When dealing with cooperative games, two issues need to be
-        addressed:\\ 1. Which coalitions among all possible coalitions to form? \\
-        2. How to reward each member when a task is completed?\\
-        %
+        \noindent When dealing with cooperative games, two issues need to be
+        addressed:    
+        \begin{enumerate}
+            \item Which coalitions among all possible coalitions to form?
+            \item How to reward each member when a task is completed?
+        \end{enumerate} 
         The following sections help address these two issues.
@@
 %          The fact that each worker's share of output is held down by interworker competition suggests that the workers might
-%          be better off if they were to agree not to join deviating coalitions \emph{except as a group}. You are  asked to check
-%          this idea in the following exercise.
+%          be better off if they were to agree not to join deviating coalitions \emph{except as a group}.
 
         %\subsection{Cooperative Games in Service Oriented Computing}\label{sec:CWSArchitecture}
+
+        \subsection{Stability of Coalitions}
+
+        Core stability is a highly desirable property however in many problems it is not achievable.
+It would be more ideal to maintain a set of somewhat stable payoffs when the core is empty.
+There are several approaches to achieve this goal.
+One may drop the stability requirement and focus on other types of solutions for which a payoff division is guaranteed to exist.
+Two well known solution concepts in this category are \emph{nucleolus}\cite{schmeidler_nucleolus_1969} and the \emph{bargaining set}\cite{Davis67existenceof}.
+They try to minimize some measure of unhappiness in the game for the agents.
+
+        Another approach to stabilize the game can be achieved via external subsides.
+When \emph{Core} is empty it means the game is not stable since the coalition is unable to generate enough revenue to satisfy the demands of each subset of agents.
+An external party that is interested in stabilizing the game provides a subsidy to the agents if they form the grand coalition, and thus a value of $\lambda v(C)$ is divided among them, where $\lambda \geq 1$.
+Clearly any game can be stabilized using a large enough $\lambda$, however the external party would be interested in the minimal subsidy required in order to stabilize the game.
+
+        A community can also be stabilized by relaxing the core constraints.
+According to \emph{Core}, an outcome is unstable if a coalition can benefit even by a small amount from deviating, which is a strong requirement.
+In fact, in some situations, deviations can be costly, or players may have loyalty to their coalitions, or even it can be computationally intractable to find those small benefits.
+It would only make sense for a coalition to deviate if the gain from a deviation exceeds the cost of performing the deviation.
+\emph{$\epsilon$-core} relaxes the notion of the core, and only requires that no coalition would benefit significantly, or within a constant amount($\epsilon$) by deviating (see Equation \ref{eq:core}).
+
+           \begin{equation}\label{eq:core2}
+               \forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
+           \end{equation}
+
+        Alternatively, $\epsilon$ can be thought of as a \emph{tax} imposed on a coalition should it choose to deviate.
+This can again be seen as an external party, trying to stabilize the coalition by imposing some \emph{tax} on deviation.
+Taxation and subsiding as methods of stabilizing cooperative games have been studied in \cite{RePEc:spr:jogath:v:38:y:2009:i:1:p:3-16, Bachrach:2009:CSC:1692490.1692502, conf/ijcai/MeirRM11}.
 

### 2015-05-09 papers/webservice-coalition-learning-omar-template/elsarticle-template-num.tex
rabeb comments

@@
 After being trained, web services get to compute expectations as utilities they would gain if cooperating with communities of different characteristics.
-In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated initiated by a web service.
+In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated by a web service.
 In general, DDM equips web services with efficient methods of foreseeing how their choices of actions would impact their short-term and long-term goals, therefore opting for better decisions.
 We performed experiments using real data from 142 users on 4,532 web services on 64 different time slots.
-The experimental results, show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.
+The experimental results, show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-optimal decision making mechanisms.
 \end{abstract}
@@
 In group-based models, interaction, composition, and cooperation are the key challenges \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13} that directly impact the group's overall performance in achieving common goals.
-To that end, we see the emergence of web service \emph{communities}, which consist of services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}.
+To that end, we see the emergence of web service \emph{communities}, which consist of grouping of services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}.
 A \emph{community} of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.
 
-The advantages of community of web services are that the community facilitates the discovery of web services and provides better quality of service compared to passive models with individual components.
+Web Service communities have the advantages of facilitating web service discovery and providing better quality of service compared to individual components.
 Communities act as abstract web services, communicating with external entities via the same standard protocols that a normal web service employs.
@@
 
-\textbf{Challenge and Problem Statement.} In recent work, communities of web services have been proposed in order to facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities.
-However, there is a twofold challenge that yet to be addressed.
-The first part is community development, which involves finding the right web services for the community, satisfying the objectives of all the web services and community coordinators involved within the community; and the second part is from the individual web service's side because each web service aims to join the community that would guarantee the best outcome.
+\textbf{Challenge and Problem Statement.} In recent work, communities of web services have been proposed in order to facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities\cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}.
+However,  two important challenges are to be addressed: 1) choice of best web services during community development from the community perspective and 2) choice of the best community to join from the web service perspective.
 The advocated solutions \cite{conf/webist/MaamarLBTS07, 10.1109/ARES.2008.7, journals/soca/XuYLZB11, 10.1109/TSC.2012.12, managing-hela-jalel, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:conf/IEEEscc/LimTMB12} have attempted to address these research problems.
-These research problems are reflected by the two challenge parts:
+However the solutions have not addressed these two challenging issues:
 \begin{enumerate}
@@
 \end{enumerate}
-These approximation methods sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored.
+These approximation methods sometimes negatively influence the outcome because simplifying the constraints may negatively cause important aspects of the problem to be ignored.
 
@@
 The generated decision tree improves agents' understanding of the environment and how to select actions that lead towards maximizing their utilities.
-The advantage of this approach is that the tree is created from the past data and reflects comprehensive vision about agents' attitude of action selection.
-However, the tree is subject to get continuously modified to adapt with environmental changes.
+The advantage of this approach is that the tree which is initially created from the past data and reflects comprehensive vision about agents' attitude of action selection based on agents' past expiriences.
+However, the tree based on recieving new feedback and outcome from actions, is subject to get continuously modified to adapt with environmental changes.
 %The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems. 
@@
 
-\section{Preliminaries and Challenging Issues}\label{s:preliminaries}
+\section{Preliminaries and Challenges in WS Communities}\label{s:preliminaries}
 %In this section, we first present the architecture of DDM.
@@
 Nowadays, web API, standards that do not require XML-based web service protocols like SOAP and WSDL are also emerging.
-They are called REST (representational state transfer) services, which are moving towards simpler communication protocols.
+They are called RESTful (representational state transfer) services, which are moving towards simpler communication protocols.
 %They are not restricted 
@@
 Web services can join communities to enhance efficiency by collaborating with others, to have access to broad market share, and for the opportunity to receive a bigger task pool from end users.
-Furthermore, the high reliance on web services has resulted in increased quality expectations from end users.
+%Furthermore, the high reliance on web services has resulted in increased quality expectations from end users.
 Communities of web services can provide higher availability, performance, reliability, and recovery for end users.
@@
 
-The community of web services is essentially a virtual group of web services having similar and complementary functionalities\cite{DBLP:journals/ijebr/MaamarSTBB09}.
+The community of web services is essentially a virtual group of web services having similar functionalities\cite{DBLP:journals/ijebr/MaamarSTBB09}.
 Communities aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols to those used by single web services.
@@
 This collaboration helps them with better ways of sharing resources and having higher reputation, better market share and wider visibility.
-Web services and communities come with different internal and external parameters, and the long-term outcome is dependent on these parameters.
+Web services and communities come with different quality metric parameters, and the long-term outcome is dependent on these parameters.
 
@@
 	\begin{equation}
-		 Th_{C} = \left\{ 
-			\begin{array}{l l}
-				Th_{w} & \quad \text{if $|C| = 1$}\\
-				\sum_{w \in C}{(Th_{w})} & \quad \text{if $|C| > 1$}
-			\end{array} \right.
+		 Th_{C} = \sum_{w \in C}{(Th_{w})}
 	\end{equation}
@@
 	\begin{equation}
-		A_{C} = \left\{ 
-			\begin{array}{l l}
-				A_{w} & \quad \text{if $|C| = 1$}\\
-				1-\prod_{w \in C}{(1-A_{w})} & \quad \text{if $|C| > 1$}
-			\end{array} \right.
+		A_{C} = 1-\prod_{w \in C}{(1-A_{w})} 
 	\end{equation}
@@
 	\begin{equation}
-		Et_{C} = \left\{ 
-			\begin{array}{l l}
-				Et_{w} & \quad \text{if $|C| = 1$}\\
-				max_{w \in C}{(Et_{w})} & \quad \text{if $|C| > 1$}
-			\end{array} \right.
+		Et_{C} = max_{w \in C}{(Et_{w})}
 	\end{equation}
@@
 
-	We normalize the range of these features so that each feature contributes approximately proportionately to the final utility outcome value.
+	We normalize the range of these features so that each feature contributes proportionally to the final utility outcome value.
 We adopt the \emph{standardization} method.
@@
 is an estimate of how close the web service's \emph{execution time} is to other web services.
-It is the difference between a web service's \emph{execution time} metric and the maximum value of execution time of all the other web services, about which the web service has information of them.
-The less value means web service has better execution time compared to other web services.
+It is the difference between a web service's \emph{execution time} metric and the maximum value of execution time of all the other web services.
+The smaller value means web service has better execution time compared to other web services.
 	\begin{equation}\label{exp_1:f}
@@
 	\item \emph{External Parameter 2} $(exp_2)$ is a comparison of the web service's rate of performing tasks to other competing web services.
-It is the difference between a web service's \emph{throughput} metric and the maximum value of throughput of all the other web services,, about which the web service has information of them.
+It is the difference between a web service's \emph{throughput} metric and the maximum value of throughput of all the other web services.
 The less value means web service has better throughput compared to other web services.
@@
 
-A community of web services is abstracted as a standard web service that provides services that share the same internal and external features mentioned for web services.
-Inside, they adopt different protocols to manage the community; however, other web services or end users can communicate with communities of web services, using standard protocols, and inner details will be encapsulated for their clients.
+A community of web services is abstracted as a standard web service that provides services that share the same internal and external features mentioned above for the web services.
+Inside, they adopt different protocols to manage the community; however, other web services or end users can communicate with communities of web services, using standard web service protocols.
 
@@
 %Thus, the amount of tasks performed by the community is $\sum_{ws}{Th_{ws}}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$. 
-However, when the incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $|input Task Rate| \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) within the community.
-
-While distributing tasks, the community members can verify the performance, throughput and quality of service of tasks being performed by web services.
+When the incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $|input Task Rate| \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) within the community.
+
+While distributing tasks, the community can verify the performance, throughput and quality of service of tasks being performed by web services.
 The community can assess if those web services are capable of performing the number of tasks they advertised.
@@
 These web services operate in an online environment and are continuously assigned tasks to handle.
-Sometimes, they pass tasks around, distributing sub-tasks among themselves and handling tasks in a collaborative effort.
 To engage in communities, we add additional features that reflect web services' utility as a result of joining other web services to form a community.
 The additional features are computed based on two assumptions that we adopt for a community to be formed.
-Our raw data set provides us with 64 different time slots of extracted features for each web service.
+We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}.
+The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{http://www.wsdream.net/}.
+In this data set, each web service is associated with a number of features that reflect its functionality.
+%Our raw data set provides us with 64 different time slots of extracted features for each web service. 
 Using this data we can build a synthetic data set that contains features of a large number of web services in a sequence of time.
@@
 
-We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}.
-The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{http://www.wsdream.net/}.
-In this data set, each web service is associated with a number of features that reflect its functionality.
 By summarizing the data provided for each web service over different time slots, we have acquired three quality features for each individual web service.
@@
 \textless2117\textgreater & 5.027081 & 2.969072 & - & 5.509583 & 2.969072 & 5.509583 \\
-\textless348, 1934\textgreater & 0.0 & 0.0 & -3.851432 & - & -3.851432 & -3.851432 \\
-\textless1934, 2117\textgreater & 2.969072 & 0.0 & 0.0 & 2.969072 & - & 2.969072 \\
-\textless348, 1934, 2117\textgreater & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & - \\ [1ex] % [1ex] adds vertical space
+\textless348, 1934\textgreater & - & - & -3.851432 & - & -3.851432 & -3.851432 \\
+\textless1934, 2117\textgreater & 2.969072 & - & - & 2.969072 & - & 2.969072 \\
+\textless348, 1934, 2117\textgreater & - & - & - & - & - & - \\ [1ex] % [1ex] adds vertical space
 \hline %inserts single line
@@
 K^t(C_i, k) = &\Big\{C_x | C_x >_{i}^t C_y; \forall C_y \in CFVS\ \\
-				      &\wedge C_y \notin \{K^t(i, 1),K^t(i, 2),...,K^t(i, k-1)\} \Big\}				
+				      &\wedge C_y \notin \{K^t(C_i, 1),K^t(C_i, 2),...,K^t(C_i, k-1)\} \Big\}				
 \end{split}
@@
 We implemented DDM in Java\footnote{Source code of implementation and data is available at: \emph{https://github.com/Marooned202/DDM}}.
-We have extracted the set of features for 4532 web services in 64 different time slots through a data set provided by \cite{10.1109/ISSRE.2011.17}.
+We recall that have extracted the set of features for 4532 web services in 64 different time slots through a data set provided by \cite{10.1109/ISSRE.2011.17}.
 By choosing 86 web services out of these sets and choosing a subset of all possible combinations of sizes 2, 3, and 4 of these 86 web services, we have chosen 10,000 communities and evaluated the feature vectors and utilities they can have in 64 different time slots.
@@
 Figure \ref{stats3} depicts the average community size over time, which essentially represents the number of new communities being formed.
-Once again, these results show that the runs with higher search rates tend to find appropriate communities to join faster.
+The results show once again the communities with higher search rates grow faster in size implying that the communities find appropriate web services to join with faster.
 

### 2015-05-09 thesis/thesis/chap1/chap1.tex
rabeb comments

@@
 
+\emph{A research question about making architecture and decision making mechanism distributed}
+
+\emph{A research question about adaptation and training needed for when agents have non-complete information}
+
 % ooooooold
@@
 
-\section{Proposal Organization}\label{sec:outline}
+\section{Thesis Organization}\label{sec:outline}
 The rest of the proposal is organized as follows: We present in
@@
 or decide to cooperate by showing the availability to perform some sub-tasks.
-We have implemented an online learning mechanism for services with different capabilities to learn over time which strategy to choose based on their own and other services status and capabilities.
+
+%We have implemented an online learning mechanism for services with different capabilities to learn over time which strategy to choose based on their own and other services status and capabilities.
 After establishing states of our model and observing convincing results from our learning method, we plan to extend the learning process using reinforcement learning (Q-learning) techniques.
@@
 
-\section{Report Organization}\label{sec:outline_s}
-The rest of the report is organized as follows. We present in
+\section{Thesis Organization}\label{sec:outline_s}
+The rest of the thesis is organized as follows. We present in
 Chapter 111 the background needed for our research along

### 2015-05-09 thesis/thesis/chap2/chap2.tex
rabeb comments

@@
 
-The idea of grouping web services within virtual structures was
-fist proposed by Zeng et al. \cite{Zeng:2003:QDW:775152.775211}.
-The authors defined web service community as collection of web
-services providing the same functionality, but with different
-quality metrics. Medjahed and Boubuettaya
-\cite{journals/dpd/MedjahedB05} have proposed a framework and a
-community builder mechanism which uses semantic analysis,
-providing an ontological organization of web services having the
-same domain of interest. The community builder would suggest web
-services having similar operations to join the same community, or
-form their own community in case the semantic analysis cannot find
-any community that matches the service types.
+In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
+defined communities as \emph{Service Containers} that aggregate
+substitutable web services providing a common functionality (same
+set of operations). They abstracted \emph{Service Containers} as
+web services that are created, advertised, discovered and invoked
+just as elementary web services. The \emph{Container} is
+considered as a manager that is responsible for web service
+selection upon receiving a request on run-time. The authors have
+proposed a scoring service based on non-functional requirements of
+the request and web service capabilities to dynamically chose the
+web service to perform the requested task. A similar concept was
+proposed by Maamar et al. in
+\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
+web service communities as a collection of web services with a
+common functionality but different QoS properties. A community
+manager, upon receiving a request, delegates the request to one of
+its current members. The choice is based on the performance
+history and quality metrics of each web service. The authors have
+proposed an efficient global web service selection algorithm in
+order to approach quality constraints and preferences for
+composite services which require aggregation of different types of
+services to satisfy the user.
+
+Benslimane et al. \cite{Liris-2770} have proposed a multi-layer
+approach grouping similar Web services into communities and having
+an interface implemented as an abstract web service for accessing
+the community on top of the community layer. The interactions
+between composite, management and community layers and the
+bindings are performed by a generic driver called Open Software
+Connectivity (OSC).
+
+In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
+service communities with centralized access across distributed web
+services. They have proposed a framework for web service
+management, query resolution among communities and a query caching
+mechanism executed by the manager to improve the performance of
+query resolution process among many distributed communities. The
+key idea is to cache previous computed results for answering
+future queries.
+
+Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
+then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
+proposed an architecture utilizing \emph{Contract-Net} protocol
+for engineering task distribution within communities of web
+services. The protocol is centrally executed by the community
+manager. This architecture has been further developed in
+\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
+conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
+roles have been distinguished for community members: masters and
+slaves. Master web services and community managers that lead
+communities and are responsible for membership management. They
+can invite and convince slave web services to join the community,
+and attract new slave web services to their communities by
+awarding them better payoff. Moreover, they can eject some slave
+members from the community to improve its overall reputation if
+these members are misbehaving or cannot provide the promised QoS.
+
+In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
+developed a community as a ``cluster'' that groups Web services
+based on a specific area of interest. All web services in a given
+community share the same functionality. These communities are
+created by \emph{third party community providers} which use the
+\emph{community ontology} as a template and define a set of
+operations that all web services within a community should
+provide. Using semantic analysis on web service operations, web
+services either find and join a community with similar
+functionality or create a new operation description for a new
+community. The authors have described the concept of
+\emph{community agents} associated to \emph{community providers}.
+A community agent is responsible, among other things, of the
+registration of services with the community. An example of a
+community that provides health care services to senior citizens
+has been used. In this example, a governmental entity is needed to
+check the health care standards used by the members before
+authorizing them to be part of the community. Such a central
+entity is represented by the community agent. Thus, community
+agents are playing the role of community managers. In a close work
+\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
+global planning selection algorithm and a delegation algorithm to
+be run when a request to execute an operation is received by the
+community. This needs a central entity to run those algorithms.
+Such entity plays the same role as the community coordinator or
+manager.
 
@@
 In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
-        DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
-        users and services maximize their gain. A two-player
-        non-cooperative game between web services and community master was
-        introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this
-        game-theoretic model, the strategies available to a web service
-        when facing a new community are requesting to join the community,
-        accepting the master's invitation to join the community, or
-        refusing the invitation to join. The set of strategies for
-        communities are inviting the web service or refusing the web
-        service's join request. Based on their capacity, market share and
-        reputation, the two players have different set of utilities over
-        the strategy profiles of the game. The main limits of this game
-        model are: 1) its consideration of only three quality parameters,
-        while the other factors are simply ignored; and 2) the
-        non-consideration of the web services already residing within the
-        community. The game is only between the community master and the
-        new web service, and the inputs from all the other members are
-        simply ignored. The consideration of those inputs is a significant
-        issue as existing web services can lose utility or payoff because
-        of the new member, which can results in an unhealthy and unstable
-        group. The problem comes from the fact that the existing members
-        should collaborate with the new web services, so probably their
+DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
+mechanisms to help users and services maximize their gain. A
+two-player non-cooperative game between web services and community
+master was introduced in
+\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this game-theoretic
+model, the strategies available to a web service when facing a new
+community are requesting to join the community, accepting the
+master's invitation to join the community, or refusing the
+invitation to join. The set of strategies for communities are
+inviting the web service or refusing the web service's join
+request. Based on their capacity, market share and reputation, the
+two players have different sets of utilities over the strategy
+profiles of the game. The main limits of this game model are: 1)
+its consideration of only three quality parameters, while the
+other factors are simply ignored; and 2) the non-consideration of
+the web services already residing within the community. The game
+is only between the community master and the new web service, and
+the inputs from all the other members and their influence on the
+master's decision are simply ignored. The consideration of those
+inputs and this influence factor is a significant issue as
+existing web services can lose utility or payoff because of the
+new member, which can result in an unhealthy and unstable group.
+The problem comes from the fact that the existing members should
+collaborate with the new web services, so probably their
 performance as a group can suffer. Existing members may even
@@
 Those considerations of forming stable and efficient coalitions
-        are the main contributions of this research work.
+are the main contributions of our paper.
 
@@
 
-        In \cite{10.1109/TSC.2012.12}, a cooperative scheme among autonomous
-        web services based on coalitional game theory has been introduced. The authors have proposed an algorithm to
-        reach individually stable coalition partition for web services in order to
-        maximize their efficiency. The communities choose new web services on the promise
-        that it would benefit the community without decreasing any other web service's
-        income. In their model, the worth of community is evaluated with high emphasis on
-        availability metric and considering price and cost values only. The community structure is based on a coordination chain,
-        where a web service is assigned as a \emph{primary} web service and the community task destribution
-        method, will initially invoke the primary web service and only if the primary web service is unavailable
-        will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to
-        have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays
-        with recent advancement in cloud and hardware infrastructures availability is becoming less of an issue. So the backup web services
-        in their model have a very low chance of getting jobs, especially the ones further in chain, which is huge waste of web services
-        capabilities.
+In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
+autonomous web services based on coalitional game theory has been
+introduced. The authors have proposed an interesting algorithm to
+reach individually stable coalition partition for web services in
+order to maximize their efficiency. The communities choose new web
+services on the promise that it would benefit the community
+without decreasing any other web service's income. In the proposed
+model, the worth of community is evaluated with high emphasis on
+the availability metric and considering price and cost values
+only. The community structure is based on a coordination chain,
+where a web service is considered as a \emph{primary} web service
+and the community task-distribution method initially invokes the
+primary web service and only if the primary web service is
+unavailable, the method invokes the next backup web services as
+they are ordered in the coordination chain. We believe that this
+coordination chain limits the cooperation power as it introduces a
+sort of hierarchy. However, in pure and open cooperative models,
+such as the one we propose in this paper, active cooperation
+activities engaging simultaneously many agents so that they can
+perform the tasks more efficiently are being used. Moreover, if
+the availability is high, which is the case nowadays with the
+recent advancements in cloud and hardware infrastructures, the
+backup web services will end-up having a very low chance of
+getting jobs, especially the ones further in the chain. This will
+results in a considerable waste of web services capabilities.
+
+%All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process.
+%So basically These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.
+We address this issue by introducing DDM a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another.
+After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics.
+Therefore web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
+In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.
 

### 2015-05-09 thesis/thesis/chap3/chap3.tex
rabeb comments

@@
 In this chapter, we present our coalition model of agent-based web
-services within communities\cite{SCC2013efficient}. We start by describing the general
+services within communities \cite{SCC2013efficient}. We start by describing the general
 architecture and considered parameters for web services.
@@
 
-ssed $core$ as one of the prominent solution concepts in cooperative games.
-Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group.
-However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal amount of $\epsilon$ by deviating.
-Stability is an attractive property for communities.
-In addition, communities would benefit by having slightly more web services then the exact number of web services satisfying task rate cap.
-This is because  there is always a possibility that the agents may leave the community or they may under perform and degrade the quality values they were initially performing with.
-
-One way for communities to ensure  stability could be  by applying a tax, $\epsilon$ amount of cost for web services changing communities which would make deviation a costly act.
-However this would require all community coordinators to agree on a same amount of taxation, being governed by some external entities or web services would join communities with lesser amount of tax.
-Another viable solution to our scenario is to stabilize the game using external subsidies.
-The reason a gamWe discue is not stable is that the community is not making enough revenue to allocate  enough gain to the players.
-A community master can subside its community with a constant coefficient value of $\lambda$.
-
-Rewarding a community with high number of quality participants with $\lambda v(C)$, where $\lambda \leq 1$.
-
-Obviously with a big number of $\lambda$, it is always possible to stabilize the community.
-However, this can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable.
-Subsiding or taxing in order to reduce the bargaining power of sub coalitions are called $taxation$ \cite{eps346856} methods.
+We discussed $core$ as one of the prominent solution concepts in
+cooperative games. Working together, completing tasks and
+generating revenue, agents need to distribute the gain in a way no
+agents would gain more by forming their own group. However, in
+most cases, the core of a game is empty, so we introduced the
+\emph{$\epsilon$-core} concept, where agents would only earn a
+minimal amount of $\epsilon$ by deviating from the coalition.
+Stability is an attractive property for communities. In addition,
+communities would benefit by having slightly more web services
+than the exact number of web services needed to satisfy the task
+rate cap. This is because there is always a possibility that the
+web services may leave the community or they may under perform and
+degrade the quality values they were initially performing with.
+
+The solution we propose for communities to ensure stability is
+applying a tax $\epsilon$, which is an amount of cost for those
+web services that decide to change communities (let us say from
+$C$ to $C'$), which would make deviation a costly act. However,
+this would require all the community coordinators to agree on a
+same amount of taxation, being governed by some external entities;
+otherwise, web services would join communities charging the lowest
+amount of tax. Before deciding to change the community, each web
+service $i$ has to be sure that the gain $g_i(C \rightarrow C')$
+calculated in Equation \ref{eq:gainsh} based on the Shapley values
+of $i$ in the previous and new communities and the tax $\epsilon$
+is positive, which means, what the web service would gain in $C'$
+is greater than what it gains in $C$ and the tax it would pay if
+moving all together:
+
+\begin{equation}\label{eq:gainsh}
+g_i(C \rightarrow C') = \phi_i(C',v) - \phi_i(C,v) - \epsilon
+\end{equation}
+
+Another viable solution we introduce to our scenario is to
+stabilize the game using external subsidies. The reason a game is
+not stable is that the community is not making enough revenue to
+allocate enough gain to the players. A community coordinator can
+subside its community with a constant coefficient value of
+$\lambda$.
+%
+%Rewarding a community with high number of quality participants
+%with $\lambda v(C)$, where $\lambda \leq 1$.
+%
+Obviously, with a big value for $\lambda$, it is always possible
+to stabilize the community. However, this can be a costly act for
+the community coordinators, so they are interested in the minimum
+subside value of $\lambda$ making the community stable. This can
+be achieved by solving the following linear program:
+%
+  \begin{alignat*}{3}
+    \min~   & \lambda  \\
+    \text{s.t. } & \lambda v(C) > v(C') & ~& \text{ for all } C' \subset C
+  \end{alignat*}
+
+%When a new web service $i$, wants to join the community, the
+%valuation function of the community members and the new web
+%service is subsided by the community coordinator in order to
+%incentivize formation of this community and is set to:
+%\begin{equation}\label{eq:taxv}
+%v'(C \cup \{i\}) = \lambda \times v(C \cup \{i\})
+%\end{equation}
+%In equation \ref{eq:taxv} the value of $v'$ is
+%replaced with the valuation function for the new forming coalition
+%$C \cup \{i\}$.
+Subsiding or taxing in order to reduce the
+bargaining power of sub coalitions are called $taxation$
+\cite{eps346856} methods. We evaluate the effectiveness of these
+two methods experimentally through extensive implementations in
+the next section.
 
@@
 
+\section{Coopetitive Behavior of Services within Communities}\label{s:coop}
+
+In previous sections, our focus was on community formation and we emphasised on cooperative behavior of the web services as agents.
+Within communities, those services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}.
+In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite.
+However, the same reason of providing similar functionalities can lead services to cooperate because they can replace each other in case of failure or unavailability, and services can do better in a coalition structure.
+Analyzing services competition and cooperation strategies within communities is still an open problem that motivates the research described in this section.
+we propose a mechanism within which service agents
+in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this report interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task.
+We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate).
+In the proposed system, We explore details behind the strategic decision making procedures and enable service agents to apply different techniques to constrain high efficiency and obtain the maximum utility.
+We investigate services' expected payoffs and the involved probabilities that are used to choose over the two interacting strategies.
+
+%\subsection{The Proposed Framework}\label{The Proposed Framework}
+Here, we first present the architecture of the proposed
+model. We explore the characteristics of intelligent service
+agents and their network. We link this architecture to the
+implemented system where we investigate the services' coopetitive
+attitudes. We compute the involved system parameters and explain
+the services' interactive strategy profiles by highlighting their
+coopetitive choices.
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=1]{Figures/architecture++.eps}
+\caption{Services are partitioned into competitive and cooperative
+sets. Competitive services may get tasks directly from the master
+agent and they can share it with other cooperative services in
+their collaborative networks within the same community.}
+\label{architectureFigure}
+\end{figure}
+
+\subsection{Architecture}
+
+Figure \ref{architectureFigure} illustrates the architecture of a
+typical community aggregating a number of services with different
+interactive strategies. Some of them compete for the task where
+they directly deal with the master. Some others cooperate in the
+associated task where they only deal with the competed service as
+the task leader and do not directly interact with the master (the
+master deals only with the service that has bid for the task,
+which is responsible of choosing its collaborative network). In
+both sets, some service agents are for certain moments out of any
+collaboration network. Upon allocation of
+the task, the service is responsible for offering the required QoS
+that is stated in the task being generated by a consumer.
+Afterwards,  the master rewards or penalizes the competing
+service by upgrading or degrading its reputation according to the
+offered QoS compared with the required one. This comparison
+influences the sorting mechanism used by the master to allocate
+the tasks in further task allocation rounds.
+
+%ok til here
+
+\subsection{System Parameters}
+In this section, we demonstrate the involved parameters and their
+corresponding formulations and explanations.
+
+\textbf{Task QoS} ($T_{QoS}^r$) is the required QoS metric for a
+specific task $r$. Users define tasks with specific QoS
+requirements such as response time, availability, and
+successability (or accuracy). We aggregate and
+normalize these metrics to a value between $0$
+and $1$. %Throughout this paper, we refer to this value as
+%$T_{QoS}$.
+
+\textbf{Service QoS} ($QoS_w^r$) is the QoS provided by the
+service $w$ after performing the task $r$. Again, the metrics that
+contribute in computing this QoS are aggregated and normalized to
+a value between $0$ and $1$. The offered quality might or might
+not meet the required task quality $T_{QoS}^r$. In the latter
+case, the service user would be disappointed and a negative
+satisfaction feedback is expected. In our proposed system, both
+cases are considered when calculating the services' reputation.
+
+%\textbf{NTD} is the number of tasks completed by a web service.
+
+\textbf{Budget} ($B_w^t$) is the amount of money the service agent
+$w$ has in its disposal during the window time $t$ (i.e.,
+$[0,t]$), which helps pay for the community membership fees
+($\epsilon$) and is one of the parameters that the service agent
+considers when deciding about getting involved in a competition or
+not.
+
+\textbf{Reputation} ($Rep_w^t$) is a significant factor in any
+online community \cite{Fouss:2010:PRM:1751668.1751727}. Without a reputation enabling
+mechanism, users cannot differentiate among services, specially
+the ones which offer the same type of service. Reputation
+mechanisms usually aggregate users' experiences and in our case it
+strongly depends on QoS that each service provides. Users define
+tasks, each one with specific quality $T_{QoS}^r$, so that after
+performing a certain number of tasks, each one with $QoS_w^r$,
+during a window time $t$, the reputation of $w$ gets evaluated by
+the master agent. $Rep_{w}^{t}$ refers to the reputation of $w$
+during that window time $t$.
+
+In Equation \ref{repr}, we compute the reward that the master
+computes considering the task $r$'s QoS $T_{QoS}^r$ compared with
+the service offered quality $QoS_w^r$. In case the offered quality
+meets user expectations, the reward value would be positive. In
+this system, we consider a small value as default rewards $\eta$
+which the master considers together with the proportional level of
+satisfaction as a weighted value (by $\upsilon$). In this case,
+the higher the offered quality, the more weighted reward. In case
+the offered quality did not meet the user expectations, the reward
+would be negative. A default penalty value $\rho$ (where
+$\rho>\eta$) together with the weighted proportional difference
+are therefore considered. The idea is to harshly penalize the
+services rather than rewarding them. To this end, rational service
+agents should carefully analyze their capabilities once the
+available tasks are announced. Equation \ref{reward} computes the
+obtained reward by $w$ during the window time $t$ considering the
+set $task_w^t$ of tasks performed by $w$ during the window time
+$t$. In our proposal, service agents have the goal of increasing
+their budget, which is directly related to their reputation. Thus,
+they have to decide strategically how to maximize this value.
+
+\begin{equation} \label{repr}
+reward_w^r = \begin{cases}
+\eta + \upsilon \frac{QoS_w^r}{T_{QoS}^r+QoS_w^r}   & \text{if $T_{QoS}^r\leq QoS_w^r$;}\\
+-(\rho +  \upsilon \frac{T_{QoS}^r}{T_{QoS}^r+QoS_w^r} ) & \text{otherwise.}\\
+\end{cases}
+\end{equation}
+
+\begin{equation} \label{reward}
+reward_w^t =
+\begin{cases}
+\frac{\sum_{r \in
+task_w^t}reward_w^r}{|task_w^t|}& \text{if $task_w^t \neq \emptyset$;}\\
+0 & \text{otherwise.}\\
+\end{cases}
+\end{equation}
+
+The assigned reputation value is updated by the computed reward
+value. The computed reputation of services is bounded by the
+minimum and maximum reputation values $0$ and $1$. % to constrain
+%the balance the cooperative community of web services. The updated
+%Let $\Gamma = Rep_{w}^{t} + reward_w^t$.
+%The updated reputation
+%value is then computed as follows:
+%
+%\begin{equation}\label{repz}
+%%Rep_{w}^{t+1} = Rep_{w}^{t} + reward
+%%\end{equation}
+%%\begin{equation*}
+%Rep_{w}^{t+1} = \begin{cases}
+%
+%\Gamma & \text{if $ 0 \leq \Gamma \leq 1$;}\\
+%0  & \text{if $\Gamma < 0$;}\\
+%1 & \text{if $\Gamma > 1$.}\\
+%\end{cases}
+%\end{equation}
+%
+%For new services with no previous reputation value, we use the
+%bootstrapping trust technique proposed in \cite{conf/icwe/YahyaouiZ11}. This
+%technique consists in giving the new services a chance and observe
+%their behaviors for a period of testing time. The observation
+%sequence is modeled as a hidden Markov model that is used to
+%detect the behavior of the service by comparing the observation
+%behavior against pre-defined trust patterns. Based on the matching
+%result, an initial value is assigned to the service. Using this
+%initial reputation value, services quickly converge to their
+%actual and stable values using the update function.
+
+%\begin{proposition}\label{Complexity-Rep}
+%$Rep_{w}^{t}$ can be computed in time $O(|t|)$, i.e., in time
+%linear in the size of the window $t$.
+%\end{proposition}
+
+%\begin{proof}\footnote{In this paper, we
+%assume that the common arithmetic and elementary functions, such
+%as multiplication, division and trigonometric functions can be
+%computed in time $O(1)$ as they operate on inputs of fixed sizes.}
+%The function $Rep_{w}^{t}$ is recursive on $t$, but the algorithm
+%works by storing the last calculated reputation value in a
+%variable, so it will not be recalculated again at each iteration.
+%However, the calculation of $reward_w^t$ is needed. Since the
+%function $reward_w^t$ can be computed in time linear in the number
+%of tasks (see Equations \ref{repr} and \ref{reward}), which in
+%turn is linear in the size of the window time, the result follows.
+%$\Box$
+%\end{proof}
+
+\textbf{Growth Factor} ($G_w^t$) is a parameter which declares
+services' performance based on their recent strategies and
+activities. Growth factor is relative to services' reputation
+$Rep_w^t$, QoS during the window time $t$ $QoS_w^t$, and budget
+$B_w^t$. This factor is the main variable a typical service uses
+to decide about which strategy to adopt. We use Equation \ref{eq:growthfactor} to compute the
+growth factor $G^t_w$ of the service $w$ during the window time
+$t$ as the average of the three aforementioned parameters, where
+$n_t$ is the total number of offered tasks to the whole community
+during the
+window time $t$, %(we consider the time window $t$ large enough so
+%that $n_t \neq 0$),
+$\mu_w$ is the mean received service fee, and $\epsilon$ is the
+cost of community membership.
+
+\begin{equation}\label{eq:growthfactor}
+G^t_w = \frac{Rep^t_w + QoS_w^t+\frac{B_w^t}{n_t  \mu_w -
+\epsilon}}{3}
+\end{equation}
+\begin{equation*}
+\mu_{w} \in\{\mu_{w, CM}, \mu_{w, CO}\},~~~QoS_w^t =
+\begin{cases} \frac{\sum_{r \in
+task_w^t}QoS_w^r}{|task_w^t|}& \text{if $task_w^t \neq \emptyset$;}\\
+0 & \text{otherwise.}\\
+\end{cases}
+\end{equation*}
+
+  % if the profit $\beta_w$ made by the web service $w$
+%considering the mean received service fee $\mu_w$ and the cost of
+%community membership $\epsilon$ is positive.
+%It is easy to show that Equation \ref{eq:growthfactor} satisfies
+%the three aforementioned properties by calculating the partial
+%derivatives $\partial G^t_w$ of this function in 1) $QoS_w^t$
+%($\frac{\partial G^t_w}{\partial QoS_w^t} = \frac{1}{3} $); 2)
+%$Rep^t_w$ ($\frac{\partial G^t_w}{\partial Rep^t_w} = \frac{1}{3}
+%$); and 3) $B_w^t$ ($\frac{\partial G^t_w}{\partial B_w^t} =
+%\frac{1}{3 (n_t \mu_w - \epsilon)} $). Thus, the sign of the two
+%first partial derivatives is positive and the sign of
+%$\frac{\partial G^t_w}{\partial B_w^t}$ depends on the sign of the
+%maximum profit $n_t \mu_w - \epsilon$, so we are done.
+The mean
+service fee depends on the strategy adopted by the service because
+a competitive service receives higher fees $\mu_{w, CM}$ compared
+to a cooperative one $\mu_{w, CO}$ ($\mu_{w, CM} > \mu_{w, CO}$).
+The motivation behind this is that a competitive service for a
+given task is the leader for that task while other cooperative
+services are performing specific subtasks as asked by the leader.
+
+%\begin{proposition}\label{Complexity-Growth_Factor}
+%$G_w^t$ can be computed in time linear in the size of the window
+%$t$.
+%\end{proposition}
+%
+%\begin{proof}
+%As shown in the second part of Equation \ref{eq:growthfactor}, the
+%function $QoS_w^t$ can be computed in time linear in the number of
+%tasks, which in turn is linear in the size of the window time.
+%Since $B_w^t$ is constant, the result follows from Proposition
+%\ref{Complexity-Rep}. $\Box$
+%\end{proof}
+
+\subsection{Service Interactive Strategies}
+
+The main goal of each individual service agent is to increase its
+income (payoff). This income can be earned from tasks (or
+requests) done by this service. In our model, services can decide
+to compete to get a task from the master agent or to cooperate
+with other services within a given collaborative network (the way
+a collaborative network is set by a leader is based on the
+cooperative services reputation and their QoS parameters that
+should coincide with the required QoS). Therefore we define two
+types of service strategies. First, when a service has higher
+level of confidence based on its growth factor, it can compete to
+get a task from the master and adopts the competitive strategy.
+Second, when the service agent has a lower level of confidence
+that it does not feel capable to compete, it waits for some other
+services to cooperate with to perform some tasks \footnote{Through
+the report, requests or tasks are supposed to be decomposable.},
+and thus it adopts the cooperative strategy. Services estimate the
+outcome of all the strategies and choose one of them accordingly.
+This decision is not static but can change over time so service
+agents can switch from one strategy to the other, and this dynamic
+attitude is referred to as coopetition.
+
 \section{Experimental Results and Analysis}\label{s:resutls}
+
+\subsection{Coalition Formation and Stability}
 
@@
 scenarios to validate the applicability and performance of our
-proposed methods in realistic environments. We created a pool of
-web services and populated most of their \emph{QoS} parameters
-from a real world web service dataset
-\cite{DBLP:conf/smc/Al-MasriM09a}. We implemented the simulations
-using Java and executed the simulations on an Intel Xeon X3450
-machine with 6GBs of memory. For other parameters missing from the
-dataset, we used normal random distribution with parameters
-estimated using the method of maximum likelihood.
+proposed methods in realistic environments.
+An XML SOAP based messaging system was implemented. We created a pool of web services and populated most of
+their \emph{QoS} parameters from a real world web service dataset
+\cite{DBLP:conf/smc/Al-MasriM09a}\footnote[1]{The implemented
+environment includes the QWS dataset by Eyhab Al-Masri and Qusay
+H. Mahmoud freely available at:
+http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/.}. To test
+our methods, we formed around 10,000 random coalitions consisting
+of 3 to 160 web services. In average, the communities were populated by 60 web
+services. We implemented the
+scenarios using Java and executed the experiments on an Intel Xeon
+X3450 machine with 6GBs of memory.
 
@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{Figures/task_done_opt.eps}
-\includegraphics[width=3in]{Figures/task_qos_opt.eps}
+\includegraphics[width=2.8in]{Figures/task_done_opt.eps}
+\includegraphics[width=2.8in]{Figures/task_qos_opt.eps}
 \caption{Part (a): Cumulative number of requests successfully
@@
 
-\begin{figure}[!t]
+\begin{figure*}%[!t]
 \centering
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=2.5in]{Figures/avg_task_ws_done.eps}
-\includegraphics[width=2.5in]{Figures/avg_qos_ws_done.eps}
-\includegraphics[width=2.5in]{Figures/avg_avail_ws_done.eps}
-\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
-(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
+\includegraphics[width=3in]{Figures/taxtation.eps}
+\caption{Analysis of community subsiding coefficient $\lambda$ on
+average community size (a), cost (b), number of tasks performed
+(c), and average quality of service of tasks performed (d).}
+\label{f_taxtation}
+\end{figure*}
+
+As mentioned in Section \ref{s:tax}, a solution to help the
+community stabilize is to subside the community by a relative
+coefficient ($\lambda$) so the value of $\lambda v(C)$ is divided
+among the community members. We have analyzed the effect of
+subsiding and the cost it incurs to our web service communities.
+Figure \ref{f_taxtation} shows the results. In this experiment, we
+have set a community with input task rate $R_C$ of 100 and having
+web services throughput rate $Th_{ws}$ values from a normal
+distribution with average 10 tasks per iteration and standard
+deviation 2. Part (a) shows the community size increases in a
+linear fashion as ($\lambda$) increases. However, the cost (Part
+(b)) is having a slight exponential growth rate since, not only
+($\lambda$) increases, but also the size of the community is
+increasing slowly. Therefore, subsiding can be costly for larger
+number of $\lambda$ values. Part (c) depicts the number of tasks
+done by the community per iteration. It is obvious that with
+$\lambda$ value of 1.3, which is 30\% of the community valuation,
+the number of tasks done almost reaches the input task rate cap of
+100 tasks per iteration. The average quality of tasks also has a
+slight increase since the community will be able to afford better
+and more web services to join the community (Part (d)). These
+results show the effectiveness of our subsiding method and its
+impact on the QoS. In fact, using more than 30\% of the community
+valuation as subsidy is not very effective and is costly to
+perform.
+
+\begin{figure*}%[!t]In the previous experiment, we considered the scenario where all
+web services are stable, will not leave the group, and will
+fulfill their promised QoS for a good period of time. However, in
+real world scenarios of web services, this is not always the case.
+This is the reason why the community coordinator would be interested in paying
+web services in order to keep the group reliable from the end
+user's point of view.
+\centerline{\includegraphics[width=6.8in]{Figures/tax_dyn.eps}}
+\caption{Analysis of community subsiding coefficient $\lambda$
+having web service different stability levels of $\tau$ on average
+community size, number of tasks performed, average quality of
+service, and average cost/income of communities.}
+\label{fig_dynamic_taxtation}
+\end{figure*}
+
+In our next scenario, we have introduced the
+new instability variable $\tau$ ranging from 0 to 1, 0 meaning web
+services having no instability issues and will perform as they
+claimed until the end of the experiment, and 1 meaning very
+unstable web services, which will stop functioning on the first
+iteration of the community distributing tasks. Figure
+\ref{fig_dynamic_taxtation} illustrates the results of our
+experiment having web services with average instability values of
+0 to 0.5 and having relative subside value $\lambda$ of 1, 1.3,
+1.6, and 2. The \emph{Cost/Income} charts on the right column show
+that having subside value of 1.3 incurs the least cost and
+increases the community income significantly. Subsiding values of
+1.6 and 2 yield high cost to the community and only slightly
+increase the community revenue. Moreover, the role of subsiding is
+much more obvious when we have unstable web services. In scenarios
+where web services are 100\% stable, the subsiding cost will
+hardly be compensated by the community revenue.
+
+\begin{figure*}%[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=2.5in]{Figures/s2_task_done.eps}
+\includegraphics[width=2.5in]{Figures/s2_task_qos.eps}
+\caption{Part (a): Cumulative number of tasks successfully done.
+Part (b): Average QoS of tasks performed.} \label{performancemany}
+\end{figure*}
+
+In Figure \ref{performancemany}, we consider \emph{Web Services
+and many Communities} scenario and we compare our dynamic
+coalition formation solution with a method which ignores QoS
+parameters and forms communities by allowing web services to join
+only if they have enough requests for themselves. In other words,
+web services can join a community when the request rate is less
+than the throughput of all the member web services. We name this
+method \emph{Random Formation} and use it as a benchmark for our
+QoS-aware community formation process. In this scenario, each user
+individually generates randomly between 0 to 10 number of tasks
+per iteration, then the users target a community and direct their
+requests to the chosen community. As the results illustrate, our
+method forms better communities of web services improving
+performance and satisfaction for both web services and
+communities.
+
+\begin{figure*}%[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=1.9in]{Figures/avg_task_ws_done.eps}
+\includegraphics[width=1.9in]{Figures/avg_qos_ws_done.eps}
+\includegraphics[width=1.9in]{Figures/avg_avail_ws_done.eps}
+\caption{A comparison between our community model and the High
+Availability Coalition model from \cite{10.1109/TSC.2012.12}. Part
+(a): Cumulative number of tasks successfully done. Part (b):
+Average QoS of tasks performed. Part (c): Average community
+service availability} \label{fig_avail_method}
+\end{figure*}
+
+Finally, in our last experiment, we compare our model with the
+solution proposed in \cite{10.1109/TSC.2012.12}, which we call
+\emph{High Availability Coalition} model. In this method, the
+community valuation function focuses on the community availability
+as main consideration. The community formation model used in this
+method is very different from ours, but we have been very careful
+to make the experiment environment as fair and similar to ours as
+possible. We limited our maximum community size to 5 in order to
+have communities with almost the same size as in
+\cite{10.1109/TSC.2012.12}. In the High Availability Coalition
+model, the authors have used web services as backups rather than
+active collaborative players, and those web services only get a
+task when the first web service in an ordered chain fails to
+perform that task. %However, with recent advancement in cloud and
+%hardware infrastructures, availability is less of an issue for web
+%services, and web services are highly available.
+Part(a) of Figure \ref{fig_avail_method} shows that with our
+method, the number of tasks successfully done is higher with a
+rate of three times more than the High Availability Coalition
+model thanks to the cooperative behavior of web services and the
+task distribution process of our algorithm. This result shows that
+using web services as backups, and not as real collaborative
+players results in a considerable waste of web services capability
+since services have very low chance of getting jobs and its the
+primary web service (the first in the coordination chain) which
+does most of the work. As shown in Part (b), the average quality
+of service of tasks performed using our solution is also higher
+since our method considers all quality of service metrics used. Part(c) shows the availability of
+communities from the end user's point of view. The High
+Availability Coalition model has almost 100\% uptime since web
+services are used as backups, so the chance of job failing is
+getting reduced significantly as community members increase. In
+our method, we have more chance of failure for each web service.
+However, with some subsidies and by hiring a few more web
+services, the chance of failure of web services in our communities
+can be lowered.
+
+\subsection{Coopetitive Behavior}\label{sb:resutlscoop}
+
+In this section, the objective is to investigate the effectiveness of the proposed strategic system in Section \ref{s:coop}.
+We start our discussions with cumulative budget comparison
+regarding different communities within which services follow
+different reasoning techniques. Figure \ref{Graph1} part (a)
+illustrates three graphs for three different communities. Each
+community hosts services that follow different reasoning
+techniques: (1) a community that follows the interactive reasoning
+techniques presented in this report (referred to as coopetitive);
+(2) a community that follows a stochastic reasoning technique so
+decisions about selecting competitive or cooperative strategies
+are totally random (referred to as random coopetitive); and (3) a
+competitive community where all services follow the competitive
+strategy (referred to as competitive).
+%The proposed model's
+%reasoning mechanism allows services to make decisions that
+%maximize their utilities, so that if the service cannot compete,
+%the procedure would suggest to collaborate, which is better than
+%competing and failing to obtain the task. In this case, the service stays idle but
+%still pays the community membership fee, which means losing
+%utility. The developed strategic decision making mechanism leads
+%some service agents to follow cooperative strategies that overall
+%maintain an optimal community budget. In the same figure, we
+%observe the cumulative budget of a community where services follow
+%random interacting strategies. The outcome is clearly lower
+%because services at each run randomly decide over their acting
+%strategies. This potentially influences the community budget
+%because a low quality service if randomly selects to follow the
+%competitive strategy, it will fail to perform a task with high QoS
+%requirements.
+
+The results illustrated in Figure \ref{Graph1} part (a)  verify
+the importance of the strategic decision making procedure to
+logically decide over the possible competitive and cooperative
+choices. Figure \ref{Graph1} part (b) illustrates communities
+average reputation of involved services. The graphs represent the
+influence of the rewards that the master agent uses to encourage
+highly capable services to compete for a task. As for the
+cumulative budget, we observe that the coopetitive community
+outperforms the random coopetitive and competitive communities in
+terms of average reputation. The proposed model's average
+reputation increases because services follow optimal strategies
+where they can perform better so obtain higher rewards. For the
+same reasons as for the cumulative budget, the average reputation
+of the random coopetitive community
+outperforms the one of the competitive community. %The idea is to balance web
+%services' strategies to maintain optimal community budget.
+
+\begin{figure}%[h]
+%\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[scale=0.47]{Figures/graphbgtmed.eps}
+\includegraphics[scale=0.47]{Figures/graphrep.eps}
+\caption{Part (a): Cumulative community budget comparison. Part
+(b): Average community reputation comparison over different
+strategic decisions.} \label{Graph1}
 \end{figure}
 
-Finally, in our last experiment, we compare our work with the work
-in \cite{10.1109/TSC.2012.12} which we call it \emph{High
-Availability Coalition} method, because of nature of their
-community valuation function, which focuses on community
-availability as main consideration. Their community formation
-model is very different than ours, however we have been very
-careful to make the experiment environment as fair and similar as
-possible. We limited our maximum community size by 5 in order to
-have communities with almost the same size. In their method, they
-have used web services as backups rather than active collaborative
-players, and they only get task when the first web service in an
-ordered chain fails to perform the task. However with recent
-advancement in cloud and hardware infrastructures availability is
-less of an issue for web services, and web services are highly
-available. Part(a) of figure \ref{fig_avail_method} shows our
-method performs almost performs tasks successfully with rate of
-three times more than \emph{High Availability Coalition} method
-because of real cooperative nature and task distribution of our
-algorithm. This result shows using web services as backups, and
-not as real collabrative players is a huge waste of web service
-capability since they have very low chance of getting jobs and its
-the primary web service (the first in their coordination chain)
-which does most of the work. The average quality of service of
-tasks performed is also better since our method considers all
-quality of service metrics mentioned in Table \ref{qosws}. Part(c)
-shows the availability of community from end user point of view.
-The \emph {High Availability Coalition} method almost has 100\%
-uptime since they use web services as backups, so the chance of
-job failing reduces significantly as community members increase.
-In our method we have more chance of fail for each web service,
-however with some subsiding, and hiring a few more web service
-they can compensate the low chance of failure of web services in
-our community.
+ %Figure \ref{Graph2} part (a) illustrates the reputation of the proposed $Coopetitive$ community where
+ %we highlight the range of reputation change in the community.
+The vertical lines denote the range of %reputation that is associated with the master web service.
+The rewards and penalties applied to %different
+% web services show that the master web service over runs extends the reputation range and takes %control of the whole community. In the developed model, web services are encouraged to choose
+ %optimal strategies. This is maintained over growth factor comparison of the $Coopetitive$ web %services.
+
+In our model, services are managed by selfish agents in the sense
+they try to maximize their own utilities. We analyze how their
+strategies affect the social welfare, and from user's and
+community's point of view how good the tasks are being performed.
+This directly impacts user's satisfaction and community's
+reputation in general. The Higher quality and quantity of tasks
+performed leads to higher user's satisfaction for the community
+which results in better reputation for the community. The results
+in Figure \ref{graph_task} show the quality and quantity of tasks
+being done successfully in three communities adopting the three
+different aforementioned strategy decision algorithms. As clearly confirmed by the simulation, the coopetitive community
+outperforms the stochastic and compete communities.
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=0.35]{Figures/graphtaskdone.eps}
+\includegraphics[scale=0.35]{Figures/graphtasksatisfaction.eps}
+\includegraphics[scale=0.35]{Figures/graphavgqostask.eps}
+\caption{Overall performance from community's point of view. Part
+(a) Total number of tasks successfully done. Part (b) Ratio of
+tasks satisfied with required QoS. Part (c) Average QoS of
+performed tasks.} \label{graph_task}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-05-09 thesis/thesis/chap6/chap6.tex
rabeb comments

@@
 
-In this thesis, we have put forward a formal framework for agent communication using a commitment-based approach in order to enable effective agent interactions in open, heterogeneous, and dynamic systems when
-uncertainty matters.
-The main purpose of this framework is to essentially specify and reason about social commitments in probabilistic settings, so they can be formally verified.
-As an improvement over the existing solutions, our proposed framework targets systems exhibiting probabilistic behavior and considers commitments among a group of agents.
-The framework is composed of three main components.
-First, we presented a new probabilistic approach for tackling social commitments in the presence of uncertainty.
-To specify probabilistic social commitments, we defined a new logic called the probabilistic logic of commitments (PCTLC).
-Our new logic is interpreted over a new extended version of probabilistic interpreted systems.
-Furthermore, we introduced a new reduction-based model checking technique for the new logic and implemented it on top of the PRISM model checker.
-Then, by using the proposed reduction technique, we showed how to evaluate some systems' properties representing probabilistic social commitments -- expressed in terms of the new logic -- against system design models obtained using our extended version of probabilistic interpreted systems.
-
-The second component of our framework focused on the interaction between knowledge and social commitments in probabilistic MASs.
-We introduced a new logic called the probabilistic logic of knowledge and commitment (PCTL$^{kc}$) to represent and reason about such interactions.
-PCTL$^{kc}$ logic is interpreted over a new version of probabilistic interpreted systems that has epistemic accessibility relations and social accessability relations at its core.
-To verify the new logic, we developed a verification technique based on model checking and implemented it using the PRISM tool.
-Our interest in the first and second contributions was focused on the common two-agent commitment scenarios (i.e.
-agent-to-agent scheme).
-
-In the third part of the framework, we improved and extended our work in the second part as follows:
-
-\begin{enumerate}
-
-\item We refined and improved PCTL$^{kc}$ to overcome the inconsistency problem appeared when taking the recent work of Al-Saqqar et al.
-\cite{Al-Saqqar2014a} into consideration.
-Therefore, in this part, we adopted CTLKC$^+$ \cite{Al-Saqqar2014a} as a basis for our new logic and combined it with PCTL.
-
-\item We extended the scope of interacting agents from agent-to-agent to agent-to-many.
-This allowed us to investigate different commitment schemes such as the case of committing to multiple agents.
-In this respect, we defined an adequate semantics for group social commitments for the first time in the literature.
-\end{enumerate}
-
-\noindent Based on the new semantics of group social commitments and the consistent logic of knowledge and commitment presented in \cite{Al-Saqqar2014a}, we presented a new probabilistic logic of knowledge and commitment called (PCTL$^{\textrm{kc+}}$).
-The new logic accommodates new operators for group social commitments and group knowledge in addition to the modalities already found in PCTL$^{kc}$.
-The expressiveness power of  PCTL$^{\textrm{kc+}}$ outperforms those of existing logics because of its ability not only to capture and express the combinations of knowledge and social commitments in the presence of uncertainty, but also to express formulae involving group social commitments.
-Formulae of PCTL$^{\textrm{kc+}}$ are interpreted over a new extended version of probabilistic interpreted systems.
-Our new version of interpreted systems integrates a modified version of social accessabilities that accounts for basic social commitments, group social commitments, and knowledge.
-To evaluate the new logic (PCTL$^{\textrm{kc+}}$), we proposed a reduction-based model checking technique and implemented it on top of PRISM.
-
-Furthermore, we proved the soundness of all proposed verification techniques.
-Also, using different case studies we were successfully able to demonstrate the effectiveness and usefulness of our proposed work and evaluate the scalability of the introduced verification techniques.
-
-Finally, as the proposed framework permits addressing probabilistic social commitments as well as their interaction with knowledge when the scope of interacting parties moves beyond the common one-to-one scheme, we believe that it will advance the literature of agent communication and help MASs designers build more effective and efficient systems.
-
+Conclusion Conclusion Conclusion
 %To conclude, we believe that the proposed framework
@@
 
-There is
+Future Work Future Work Future Work
 

### 2015-05-09 papers/webservice-coalition-learning/figures/matlab/mlisa_stats3.m

@@ -50,7 +50,7 @@ set(hleg1,'FontSize',10);
 % title('Trigonometric Functions', 'fontsize', 10);
 %xlabel({'Time';'(a)'}, 'FontSize',14);
 xlabel('Time', 'FontSize',14);
-ylabel('Utility Gain', 'FontSize',14);
+ylabel('Community Size', 'FontSize',14);
 
 %Caxes = copyobj(gca,gcf);
 %set(Caxes, 'color', 'none', 'xcolor', 'k', 'xgrid', 'off', 'ycolor','k', 'ygrid','off');

### 2015-05-09 papers/webservice-coalition-learning-elsevier-template/elsarticle-template-num.tex
rabeb comments-2

--- 2015-01-19 papers/webservice-coalition-learning-else-template/elsarticle-template-num.tex
@@
 
-\journal{Decision Support Systems}
+\journal{Nuclear Physics B}
 
@@
 %% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
+\title{Title\tnoteref{label1}}
+\tnotetext[label1]{}
+\author{Name\corref{cor1}\fnref{label2}}
+\ead{email address}
+%%\ead[url]{home page}
+%%\fntext[label2]{}
+%%\cortext[cor1]{}
+%%\address{Address\fnref{label3}}
+%%\fntext[label3]{}
 
@@
 The experimental results, show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.
+
 \end{abstract}
@@
 \begin{keyword}
-Web services\sep Community of services\sep Distributed Decision Making
 %% keywords here, in the form: keyword \sep keyword
@@
 %% or \MSC[2008] code \sep code (2000 is the default)
-
+Web services \sep Community of services \sep Distributed Decision Making
 \end{keyword}
@@
 
-\IEEEPARstart{O}{ver} the past years, online services have become an important part of many scalable business applications.
+Over the past years, online services have become an important part of many scalable business applications.
 The increasing reliance on online service providers has significantly influenced the way web services are engineered.
@@
 One practical solution towards delivering high quality services is utilizing intelligent decision making agents.
-These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users\cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, journals/tsc/ZhengZYB13, Demirkan2013412}.
+These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users\cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, journals/tsc/ZhengZYB13}.
 However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided.
@@
 Finally Section 7 concludes the paper and identifies future work.
-
-%- We want to give full distributed control to web services as autonomous agents and distribute the task of community management among all web services and let them decide how to maximize their efficiency and join and create communities.
-%- Let agents train and learn long term expectations of each action and group they can join with
-%- Web services cannot find the optimal solution in big space problem of many web services
-%- Add rationalism and less vague decisions
-
-%Web services provide a set of stateless software functions accessible at a network address over the web. 
-%Online autonomous agent-based services are software systems providing a standard way of interoperability among different applications.
-
-% - The recent developments are shifting web services from passive and individual components to autonomous and group-based components where interactiion, composition, and cooperation are the key challenges.
-
-%- High demand on online services has created a massive business competition.
-For example, nowadays users are provided with multiple choices of web services offering local places information such as coffees, venues, and shops nearby a geographic position.
-It is hard for new web services to find their customers and be visible for end users amongst hundreds or thousands of other available services, even if they provide a high quality of service.
-Hence, the concept of communities of web services provides them with the chance of joining a platform with an established market share and reputation.
-However, it is crucial for a community manager to consider many factors when inviting or accepting new members.
-For example,  this may hurt the community stability.
-
-%- The high competition within the services industry requires applications to use reliable and high quality online service providers.
-If the user were to check a web site or run an application on her mobile device upon having downtime, or having high response delay or encountering any non-satisfying quality metric, she will instantly remove the application, which is a huge business concern for application providers.
-For example, if a user installs a ticketing application on her mobile device and the application is not using high quality service providers, the user would instantly uninstall the application, which has an extremely negative impact on the visibility of the application.
-
-%- Most applications cannot independently satisfy users requests and should rely on different online services.
-The high competition within the services industry requires applications to use reliable and high quality online service providers.
-
-%Today web services are
-
-%- softwares rely on third party online service providers 
-%- quality of services determines the success of the business 
-%- services want to maximise thier utility by cooperating with best possible communities
-%- services need to get visible and join market
-
-% Computer Society journal papers do something a tad strange with the very
-% first section heading (almost always called "Introduction"). They place it
-% ABOVE the main text! IEEEtran.cls currently does not do this for you.
-% However, You can achieve this effect by making LaTeX jump through some
-% hoops via something like:
-%
-%\ifCLASSOPTIONcompsoc
-%  \noindent\raisebox{2\baselineskip}[0pt][0pt]%
-%  {\parbox{\columnwidth}{\section{Introduction}\label{sec:introduction}%
-%  \global\everypar=\everypar}}%
-%  \vspace{-1\baselineskip}\vspace{-\parskip}\par
-%\else
-%  \section{Introduction}\label{sec:introduction}\par
-%\fi
-%
-% Admittedly, this is a hack and may well be fragile, but seems to do the
-% trick for me. Note the need to keep any \label that may be used right
-% after \section in the above as the hack puts \section within a raised box.
-
-% The very first letter is a 2 line initial drop letter followed
-% by the rest of the first word in caps (small caps for compsoc).
-%
-% form to use if the first word consists of a single letter:
-% \IEEEPARstart{A}{demo} file is ....
-%
-% form to use if you need the single drop letter followed by
-% normal text (unknown if ever used by IEEE):
-% \IEEEPARstart{A}{}demo file is ....
-%
-% Some journals put the first two words in caps:
-% \IEEEPARstart{T}{his demo} file is ....
-%
-% Here we have the typical use of a "T" for an initial drop letter
-% and "HIS" in caps to complete the first word.
-%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
-%for IEEE Computer Society journal papers produced under \LaTeX\ using
-%IEEEtran.cls version 1.7 and later.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-%I wish you the best of success.
-
-%\hfill mds
-
-%\hfill January 11, 2007
 
@@
 
-\begin{table*}[ht]
+\begin{table}[ht]
 \caption{An example of $gain$ matrix for 3 different communities and their combinations} % title of Table
@@
 \label{table:nonlin} % is used to refer this table in the text
-\end{table*}
+\end{table}
 
@@
 
-%\subsection{Subsection Heading Here}
-%Subsection text here.
-
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
-
-%\subsubsection{Subsubsection Heading Here}
-%Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection %text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.
-%Subsubsection text here.Subsubsection text here.Subsubsection text here.
-
-%Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection %text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.Subsubsection text here.
-
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex,
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that IEEE CS typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-% However, the Computer Society has been known to put floats at the bottom.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command, the
-% \label for the overall figure must come after \caption.
-% \hfil must be used as a separator to get equal spacing.
-% The subfigure.sty package works much the same way, except \subfigure is
-% used instead of \subfloat.
-%
-%\begin{figure*}[!t]
-%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
-%\label{fig_second_case}}}
-%\caption{Simulation results}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE CS papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals use top floats exclusively.
-% However, Computer Society journals sometimes do use bottom floats - bear
-% this in mind when choosing appropriate optional arguments for the
-% figure/table environments.
-% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
-% floats. This can be corrected via the \fnbelowfloat command of the
-% stfloats package.
-
 \section{Conclusion}\label{s:conclusion}
@@
 
-%\bibitem{}
+\bibitem{}
 

### 2015-05-09 papers/webservice-coalition-learning-elsevier-template/figures/matlab/mlisa_stats2.m

@@ -1,0 +1,61 @@
+[v,T,vT]=xlsread('mlisa_chart_stats.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|+-|.|:')
+
+i=0:62;
+%t=v(:,21);y=v(:,22);z=v(:,23);tt=v(:,24);
+t=v(:,31);y=v(:,32);z=v(:,33);tt=v(:,34);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+%h = plot(i,t,i,y,i,z,i,tt,'linewidth', 2);
+h = plot(i,t,'--g+',i,y,'--ko',i,z,':bs',i,tt,'-.r*', 'MarkerSize',3, 'linewidth', 1);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:63);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',0:5000:30000);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '51';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    ' ';' ';'63';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 63 0 890]);
+
+% Add legend
+hleg1 = legend('R=0.05','R=0.07','R=0.10','R=0.20');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.74,.69,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
[…]

### 2015-05-09 papers/webservice-coalition-learning-elsevier-template/figures/matlab/mlisa_stats3.m

@@ -1,0 +1,61 @@
+[v,T,vT]=xlsread('mlisa_chart_stats.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|-.|--|+-|.|:')
+
+i=0:62;
+t=v(:,7);y=v(:,8);z=v(:,9);tt=v(:,10);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+%h = plot(i,t,i,y,i,z,i,tt,'linewidth', 2);
+h = plot(i,t,'--g+',i,y,'--ko',i,z,':bs',i,tt,'-.r*', 'MarkerSize',3, 'linewidth', 1);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+set(gca,'XTick',1:1:63);
+%set(gca,'YTick',7000:1500:18000);
+set(gca,'YTick',0:0.2:3.5);
+set(gca,'tickdir','in')
+set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '41';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    '51';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+    ' ';' ';'63';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+axis([0 63 1 2.2]);
+
+% Add legend
+hleg1 = legend('R=0.05','R=0.07','R=0.10','R=0.20');
+%set(hleg1,'Location','NorthWest');
+set(hleg1, 'Position', [.74,.69,.1,.2]);
+set(hleg1,'Interpreter','none');
+%set(hleg1,'color','none');
+set(hleg1,'FontSize',10);
+%legend boxoff;
+
[…]

### 2015-05-10 thesis/thesis/chap3/chap3.tex
added coop

--- 2015-04-22 thesis/thesis/chap3/chap3.tex
@@
 
-ssed $core$ as one of the prominent solution concepts in cooperative games.
-Working together, completing tasks and generating revenue, agents need to distribute the gain in a way no agents would gain more by having their own group.
-However, in most cases the core of a game is empty so we introduced the \emph{$\epsilon$-core} concept, where agents would only earn a minimal amount of $\epsilon$ by deviating.
-Stability is an attractive property for communities.
-In addition, communities would benefit by having slightly more web services then the exact number of web services satisfying task rate cap.
-This is because  there is always a possibility that the agents may leave the community or they may under perform and degrade the quality values they were initially performing with.
+We discussed $core$ as one of the prominent solution concepts in
+cooperative games. Working together, completing tasks and
+generating revenue, agents need to distribute the gain in a way no
+agents would gain more by forming their own group. However, in
+most cases, the core of a game is empty, so we introduced the
+\emph{$\epsilon$-core} concept, where agents would only earn a
+minimal amount of $\epsilon$ by deviating from the coalition.
+Stability is an attractive property for communities. In addition,
+communities would benefit by having slightly more web services
+than the exact number of web services needed to satisfy the task
+rate cap. This is because there is always a possibility that the
+web services may leave the community or they may under perform and
+degrade the quality values they were initially performing with.
 
-One way for communities to ensure  stability could be  by applying a tax, $\epsilon$ amount of cost for web services changing communities which would make deviation a costly act.
-However this would require all community coordinators to agree on a same amount of taxation, being governed by some external entities or web services would join communities with lesser amount of tax.
-Another viable solution to our scenario is to stabilize the game using external subsidies.
-The reason a gamWe discue is not stable is that the community is not making enough revenue to allocate  enough gain to the players.
-A community master can subside its community with a constant coefficient value of $\lambda$.
+The solution we propose for communities to ensure stability is
+applying a tax $\epsilon$, which is an amount of cost for those
+web services that decide to change communities (let us say from
+$C$ to $C'$), which would make deviation a costly act. However,
+this would require all the community coordinators to agree on a
+same amount of taxation, being governed by some external entities;
+otherwise, web services would join communities charging the lowest
+amount of tax. Before deciding to change the community, each web
+service $i$ has to be sure that the gain $g_i(C \rightarrow C')$
+calculated in Equation \ref{eq:gainsh} based on the Shapley values
+of $i$ in the previous and new communities and the tax $\epsilon$
+is positive, which means, what the web service would gain in $C'$
+is greater than what it gains in $C$ and the tax it would pay if
+moving all together:
 
-Rewarding a community with high number of quality participants with $\lambda v(C)$, where $\lambda \leq 1$.
+\begin{equation}\label{eq:gainsh}
+g_i(C \rightarrow C') = \phi_i(C',v) - \phi_i(C,v) - \epsilon
+\end{equation}
 
-Obviously with a big number of $\lambda$, it is always possible to stabilize the community.
-However, this can be a costly act for community masters so they are interested in the minimum subside value of $\lambda$ making the game stable.
-Subsiding or taxing in order to reduce the bargaining power of sub coalitions are called $taxation$ \cite{eps346856} methods.
+Another viable solution we introduce to our scenario is to
+stabilize the game using external subsidies. The reason a game is
+not stable is that the community is not making enough revenue to
+allocate enough gain to the players. A community coordinator can
+subside its community with a constant coefficient value of
+$\lambda$.
+%
+%Rewarding a community with high number of quality participants
+%with $\lambda v(C)$, where $\lambda \leq 1$.
+%
+Obviously, with a big value for $\lambda$, it is always possible
+to stabilize the community. However, this can be a costly act for
+the community coordinators, so they are interested in the minimum
+subside value of $\lambda$ making the community stable. This can
+be achieved by solving the following linear program:
+%
+  \begin{alignat*}{3}
+    \min~   & \lambda  \\
+    \text{s.t. } & \lambda v(C) > v(C') & ~& \text{ for all } C' \subset C
+  \end{alignat*}
+
+%When a new web service $i$, wants to join the community, the
+%valuation function of the community members and the new web
+%service is subsided by the community coordinator in order to
+%incentivize formation of this community and is set to:
+%\begin{equation}\label{eq:taxv}
+%v'(C \cup \{i\}) = \lambda \times v(C \cup \{i\})
+%\end{equation}
+%In equation \ref{eq:taxv} the value of $v'$ is
+%replaced with the valuation function for the new forming coalition
+%$C \cup \{i\}$.
+Subsiding or taxing in order to reduce the
+bargaining power of sub coalitions are called $taxation$
+\cite{eps346856} methods. We evaluate the effectiveness of these
+two methods experimentally through extensive implementations in
+the next section.
 
@@
 
-\begin{figure}[!t]
+\begin{figure*}%[!t]
 \centering
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=2.5in]{Figures/avg_task_ws_done.eps}
-\includegraphics[width=2.5in]{Figures/avg_qos_ws_done.eps}
-\includegraphics[width=2.5in]{Figures/avg_avail_ws_done.eps}
-\caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
-(b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
-\end{figure}
+\includegraphics[width=3in]{Figures/taxtation.eps}
+\caption{Analysis of community subsiding coefficient $\lambda$ on
+average community size (a), cost (b), number of tasks performed
+(c), and average quality of service of tasks performed (d).}
+\label{f_taxtation}
+\end{figure*}
 
-Finally, in our last experiment, we compare our work with the work
-in \cite{10.1109/TSC.2012.12} which we call it \emph{High
-Availability Coalition} method, because of nature of their
-community valuation function, which focuses on community
-availability as main consideration. Their community formation
-model is very different than ours, however we have been very
-careful to make the experiment environment as fair and similar as
-possible. We limited our maximum community size by 5 in order to
-have communities with almost the same size. In their method, they
-have used web services as backups rather than active collaborative
-players, and they only get task when the first web service in an
-ordered chain fails to perform the task. However with recent
-advancement in cloud and hardware infrastructures availability is
-less of an issue for web services, and web services are highly
-available. Part(a) of figure \ref{fig_avail_method} shows our
-method performs almost performs tasks successfully with rate of
-three times more than \emph{High Availability Coalition} method
-because of real cooperative nature and task distribution of our
-algorithm. This result shows using web services as backups, and
-not as real collabrative players is a huge waste of web service
-capability since they have very low chance of getting jobs and its
-the primary web service (the first in their coordination chain)
-which does most of the work. The average quality of service of
-tasks performed is also better since our method considers all
-quality of service metrics mentioned in Table \ref{qosws}. Part(c)
-shows the availability of community from end user point of view.
-The \emph {High Availability Coalition} method almost has 100\%
-uptime since they use web services as backups, so the chance of
-job failing reduces significantly as community members increase.
-In our method we have more chance of fail for each web service,
-however with some subsiding, and hiring a few more web service
-they can compensate the low chance of failure of web services in
-our community.
+As mentioned in Section \ref{s:tax}, a solution to help the
+community stabilize is to subside the community by a relative
+coefficient ($\lambda$) so the value of $\lambda v(C)$ is divided
+among the community members. We have analyzed the effect of
+subsiding and the cost it incurs to our web service communities.
+Figure \ref{f_taxtation} shows the results. In this experiment, we
+have set a community with input task rate $R_C$ of 100 and having
+web services throughput rate $Th_{ws}$ values from a normal
+distribution with average 10 tasks per iteration and standard
+deviation 2. Part (a) shows the community size increases in a
+linear fashion as ($\lambda$) increases. However, the cost (Part
+(b)) is having a slight exponential growth rate since, not only
+($\lambda$) increases, but also the size of the community is
+increasing slowly. Therefore, subsiding can be costly for larger
+number of $\lambda$ values. Part (c) depicts the number of tasks
+done by the community per iteration. It is obvious that with
+$\lambda$ value of 1.3, which is 30\% of the community valuation,
+the number of tasks done almost reaches the input task rate cap of
+100 tasks per iteration. The average quality of tasks also has a
+slight increase since the community will be able to afford better
+and more web services to join the community (Part (d)). These
+results show the effectiveness of our subsiding method and its
+impact on the QoS. In fact, using more than 30\% of the community
+valuation as subsidy is not very effective and is costly to
+perform.
+
+\begin{figure*}%[!t]In the previous experiment, we considered the scenario where all
+web services are stable, will not leave the group, and will
+fulfill their promised QoS for a good period of time. However, in
+real world scenarios of web services, this is not always the case.
+This is the reason why the community coordinator would be interested in paying
+web services in order to keep the group reliable from the end
+user's point of view.
+\centerline{\includegraphics[width=6.8in]{Figures/tax_dyn.eps}}
+\caption{Analysis of community subsiding coefficient $\lambda$
+having web service different stability levels of $\tau$ on average
+community size, number of tasks performed, average quality of
+service, and average cost/income of communities.}
+\label{fig_dynamic_taxtation}
+\end{figure*}
+
+In our next scenario, we have introduced the
+new instability variable $\tau$ ranging from 0 to 1, 0 meaning web
+services having no instability issues and will perform as they
+claimed until the end of the experiment, and 1 meaning very
+unstable web services, which will stop functioning on the first
+iteration of the community distributing tasks. Figure
+\ref{fig_dynamic_taxtation} illustrates the results of our
+experiment having web services with average instability values of
+0 to 0.5 and having relative subside value $\lambda$ of 1, 1.3,
+1.6, and 2. The \emph{Cost/Income} charts on the right column show
+that having subside value of 1.3 incurs the least cost and
+increases the community income significantly. Subsiding values of
+1.6 and 2 yield high cost to the community and only slightly
+increase the community revenue. Moreover, the role of subsiding is
+much more obvious when we have unstable web services. In scenarios
+where web services are 100\% stable, the subsiding cost will
+hardly be compensated by the community revenue.
+
+\begin{figure*}%[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=2.5in]{Figures/s2_task_done.eps}
+\includegraphics[width=2.5in]{Figures/s2_task_qos.eps}
+\caption{Part (a): Cumulative number of tasks successfully done.
+Part (b): Average QoS of tasks performed.} \label{performancemany}
+\end{figure*}
+
+In Figure \ref{performancemany}, we consider \emph{Web Services
+and many Communities} scenario and we compare our dynamic
+coalition formation solution with a method which ignores QoS
+parameters and forms communities by allowing web services to join
+only if they have enough requests for themselves. In other words,
+web services can join a community when the request rate is less
+than the throughput of all the member web services. We name this
+method \emph{Random Formation} and use it as a benchmark for our
+QoS-aware community formation process. In this scenario, each user
+individually generates randomly between 0 to 10 number of tasks
+per iteration, then the users target a community and direct their
+requests to the chosen community. As the results illustrate, our
+method forms better communities of web services improving
+performance and satisfaction for both web services and
+communities.
+
+\begin{figure*}%[!t]
+\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[width=1.9in]{Figures/avg_task_ws_done.eps}
+\includegraphics[width=1.9in]{Figures/avg_qos_ws_done.eps}
+\includegraphics[width=1.9in]{Figures/avg_avail_ws_done.eps}
+\caption{A comparison between our community model and the High
+Availability Coalition model from \cite{10.1109/TSC.2012.12}. Part
+(a): Cumulative number of tasks successfully done. Part (b):
+Average QoS of tasks performed. Part (c): Average community
+service availability} \label{fig_avail_method}
+\end{figure*}
+
+Finally, in our last experiment, we compare our model with the
+solution proposed in \cite{10.1109/TSC.2012.12}, which we call
+\emph{High Availability Coalition} model. In this method, the
+community valuation function focuses on the community availability
+as main consideration. The community formation model used in this
+method is very different from ours, but we have been very careful
+to make the experiment environment as fair and similar to ours as
+possible. We limited our maximum community size to 5 in order to
+have communities with almost the same size as in
+\cite{10.1109/TSC.2012.12}. In the High Availability Coalition
+model, the authors have used web services as backups rather than
+active collaborative players, and those web services only get a
+task when the first web service in an ordered chain fails to
+perform that task. %However, with recent advancement in cloud and
+%hardware infrastructures, availability is less of an issue for web
+%services, and web services are highly available.
+Part(a) of Figure \ref{fig_avail_method} shows that with our
+method, the number of tasks successfully done is higher with a
+rate of three times more than the High Availability Coalition
+model thanks to the cooperative behavior of web services and the
+task distribution process of our algorithm. This result shows that
+using web services as backups, and not as real collaborative
+players results in a considerable waste of web services capability
+since services have very low chance of getting jobs and its the
+primary web service (the first in the coordination chain) which
+does most of the work. As shown in Part (b), the average quality
+of service of tasks performed using our solution is also higher
+since our method considers all quality of service metrics used. Part(c) shows the availability of
+communities from the end user's point of view. The High
+Availability Coalition model has almost 100\% uptime since web
+services are used as backups, so the chance of job failing is
+getting reduced significantly as community members increase. In
+our method, we have more chance of failure for each web service.
+However, with some subsidies and by hiring a few more web
+services, the chance of failure of web services in our communities
+can be lowered.
+
+\subsection{Coopetitive Behavior}\label{sb:resutlscoop}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-05-10 thesis/thesis/chap4/chap4.tex
rabeb comments
added coop

@@
 
-\chapter{Training Chapter}\label{cha:PCTLKC}
+\chapter{Coopetitive Behavior of Services within Communities}\label{cha:PCTLKC}
 
@@
 
-Over the past years, online services have become an important part of many scalable business applications.
-The increasing reliance on online service providers has significantly influenced the way web services are engineered.
-Therefore, given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue.
-One practical solution towards delivering high quality services is utilizing intelligent decision making agents.
-These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users\cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Demirkan2013412, journals/tsc/ZhengZYB13, Josang:2007:STR:1225318.1225716}.
-However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided.
-Recent developments have attempted to shift web services from passive models, consisting of individual components, to models made up of autonomous and group-based components that share common goals.
-In group-based models, interaction, composition, and cooperation are the key challenges \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13} that directly impact the group's overall performance in achieving common goals.
-To that end, we see the emergence of web service \emph{communities}, which consist of services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}.
-A \emph{community} of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.
+In previous chapter, our focus was on community formation and we emphasised on cooperative behavior of the web services as agents.
+Within communities, those services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}.
+In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite.
+However, the same reason of providing similar functionalities can lead services to cooperate because they can replace each other in case of failure or unavailability, and services can do better in a coalition structure.
+Analyzing services competition and cooperation strategies within communities is still an open problem that motivates the research described in this section.
+we propose a mechanism within which service agents
+in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this report interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task.
+We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate).
+In the proposed system, We explore details behind the strategic decision making procedures and enable service agents to apply different techniques to constrain high efficiency and obtain the maximum utility.
+We investigate services' expected payoffs and the involved probabilities that are used to choose over the two interacting strategies.
 
-The advantages of community of web services are that the community facilitates the discovery of web services and provides better quality of service compared to passive models with individual components.
-Communities act as abstract web services, communicating with external entities via the same standard protocols that a normal web service employs.
-But, they regulate the service process via sophisticated internal communication protocols, thereby providing services based on the combined work of a number of web services.
-The downside to communities is the complexity of management involved in finding and inviting individual web services and managing the overall quality of the combined work of several web services.
-% because although they have similar functionality, they have different attitudes.
-When interacting with communities of web services, users send their requests to the coordinators of the community, which play the role of community representative or access point.
-The community coordinator is responsible of receiving tasks and delivering services.
-Moreover, as community representative, it verifies the credentials of new web services before accepting them into the community and kicks web services that could harm the value of the community.
+%\subsection{The Proposed Framework}\label{The Proposed Framework}
+Here, we first present the architecture of the proposed
+model. We explore the characteristics of intelligent service
+agents and their network. We link this architecture to the
+implemented system where we investigate the services' coopetitive
+attitudes. We compute the involved system parameters and explain
+the services' interactive strategy profiles by highlighting their
+coopetitive choices.
 
-\textbf{Challenge and Problem Statement.} In recent work, communities of web services have been proposed in order to facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities.
-However, there is a twofold challenge that yet to be addressed.
-The first part is community development, which involves finding the right web services for the community, satisfying the objectives of all the web services and community coordinators involved within the community; and the second part is from the individual web service's side because each web service aims to join the community that would guarantee the best outcome.
-The advocated solutions \cite{conf/webist/MaamarLBTS07, 10.1109/ARES.2008.7, journals/soca/XuYLZB11, 10.1109/TSC.2012.12, managing-hela-jalel, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:conf/IEEEscc/LimTMB12} have attempted to address these research problems.
-These research problems are reflected by the two challenge parts:
-\begin{enumerate}
-	\item The solutions consider the architecture of centralized management for communities where most of the decisions are made by the centralized coordinator.
-The problem is that in real world scenarios, decisions made by independent service providers are highly distributed.
-	\item The solutions either propose complex algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to find the optimal strategy to follow, or oversimplify the problem by eliminating important parameters and using approximation techniques to make the algorithms tractable \cite{10.1109/TSC.2012.12}.
-\end{enumerate}
-These approximation methods sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored.
+\begin{figure}[h]
+\centering
+\includegraphics[scale=1]{Figures/architecture++.eps}
+\caption{Services are partitioned into competitive and cooperative
+sets. Competitive services may get tasks directly from the master
+agent and they can share it with other cooperative services in
+their collaborative networks within the same community.}
+\label{architectureFigure}
+\end{figure}
 
-For example, instead of calculating the gain distribution using the complex shapely-value method, \cite{10.1109/TSC.2012.12} proposes a simple egalitarian way of distributing gain, which completely ignores the gain generated from collaborative work of sub-communities.
-Other categories of related work exist that do not focus on all the parties involved within the community \cite{DBLP:conf/IEEEscc/KhosravifarABT11}.
-%And some other work which do not focus on rationality on web services or communities involved [refrences].
-In \cite{journal-community-formation} we proposed a cooperative game theory based model for aggregating web services in communities.
-A centralized decision maker in communities based on a complete knowledge of available web service quality metrics and performance, has been used to form optimal and stable communities that maximize individual and group income.
-However, centrality and complete information are strong assumptions, which are not very compatible with real business scenarios.
+\section{Architecture}
 
-\textbf{Contributions.} In this paper, we introduce DDM, a Distributed Decision Making model for  community formation that regulates web service agents’ decision making process in terms of cooperating and deciding which group to join and which service to invite for joining.
-The decision model in extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
-The generated decision tree improves agents' understanding of the environment and how to select actions that lead towards maximizing their utilities.
-The advantage of this approach is that the tree is created from the past data and reflects comprehensive vision about agents' attitude of action selection.
-However, the tree is subject to get continuously modified to adapt with environmental changes.
-%The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems.
-The decision model provides web services with enough information which helps those services to efficiently decide and predict the outcome of their different possible collaborations.
-This model works in a distributed manner in which services are self-sufficient in decision making process and do not rely on a centralized decision making process.
-Our findings show that communities of web services can efficiently find the appropriate web service to invite for cooperation as well as allowing a single web service to find the best communities to join.
-In other words, the web services agents are equipped with a recommender system to suggest beneficial action.
-Moreover, communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
-In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their short-term and long-term goals; therefore, opting for best decision available.
+Figure \ref{architectureFigure} illustrates the architecture of a
+typical community aggregating a number of services with different
+interactive strategies. Some of them compete for the task where
+they directly deal with the master. Some others cooperate in the
+associated task where they only deal with the competed service as
+the task leader and do not directly interact with the master (the
+master deals only with the service that has bid for the task,
+which is responsible of choosing its collaborative network). In
+both sets, some service agents are for certain moments out of any
+collaboration network. Upon allocation of
+the task, the service is responsible for offering the required QoS
+that is stated in the task being generated by a consumer.
+Afterwards,  the master rewards or penalizes the competing
+service by upgrading or degrading its reputation according to the
+offered QoS compared with the required one. This comparison
+influences the sorting mechanism used by the master to allocate
+the tasks in further task allocation rounds.
 
-To effectively generate the decision model for web services, we used real data set to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another.
-The data set has been extracted by real-world QoS evaluation results from 142 users on 4,532 Web services on 64 different time slots.
-Combining these data based on each web service point of view on different time slots, we acquired 5 different unique features for 4,532 web services.
-By engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in different time slots.
-We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others.
-All paths and the outcomes are labeled to be utilized in the training model.
-Using cross validation sets, web services are able to compute the optimal hypothesis function (using logistic regression) that can be used to predict outcomes of cooperative work with other individual web services or communities.
-Our findings show that web services equipped with DDM have by far better outcomes in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.
+%ok til here
 
-\section{Preliminaries and Challenging Issues}\label{s:preliminaries}
-%In this section, we first present the architecture of DDM.
-We explore the characteristics of intelligent service agents and the features we extract for training.
-To do this, we first discuss some preliminaries.
-In this section, we discuss the preliminary concepts of communities of web service and we introduce the challenges of community formation.
+\section{System Parameters}
+In this section, we demonstrate the involved parameters and their
+corresponding formulations and explanations.
 
-\subsection{Web Services}\label{s:ws}
+\textbf{Task QoS} ($T_{QoS}^r$) is the required QoS metric for a
+specific task $r$. Users define tasks with specific QoS
+requirements such as response time, availability, and
+successability (or accuracy). We aggregate and
+normalize these metrics to a value between $0$
+and $1$. %Throughout this paper, we refer to this value as
+%$T_{QoS}$.
 
-In recent years, online services have become a standard part of daily life around the globe.
-Many modern applications rely on web services from different providers.
-For instance, many mobile and tablet applications that have limited storage and processing power are merely aggregating information from different online services.
-Examples are vast, including weather forecasting, ticket selling, shopping apps, local maps and location services.
+\textbf{Service QoS} ($QoS_w^r$) is the QoS provided by the
+service $w$ after performing the task $r$. Again, the metrics that
+contribute in computing this QoS are aggregated and normalized to
+a value between $0$ and $1$. The offered quality might or might
+not meet the required task quality $T_{QoS}^r$. In the latter
+case, the service user would be disappointed and a negative
+satisfaction feedback is expected. In our proposed system, both
+cases are considered when calculating the services' reputation.
 
-The World Wide Web Consortium (W3C) defines web services as ``software systems designed to support interpretable machine-to-machine interaction over a network.
-It has an interface described in a machine-processable format (specifically WSDL).
-Other systems interact with the web service in a manner prescribed by its description using SOAP messages, typically conveyed using HTTP with XML serialization in conjunction with other Web-related standards.'' When developers declare a new web service, it will be
-discovered based on its description, which fully discloses its functionalities.
-Developers also have to declare a public interface and a readable documentation to help other developers when integrating different services \cite{w3cwsdl}.
-Nowadays, web API, standards that do not require XML-based web service protocols like SOAP and WSDL are also emerging.
-They are called REST (representational state transfer) services, which are moving towards simpler communication protocols.
-%They are not restricted
-%to XML formats, recently JSON, a human readable and simpler format
-%is becoming popular among online service providers.
+%\textbf{NTD} is the number of tasks completed by a web service.
 
-We are not going to delve into the engineering details of online web service implementation and its protocols in this paper.
-We are interested in web services from a business model perspective.
-Service providers usually charge end users for services they provide.
-For example, Google has listed pricing and plans for a wide range of services they provide on their web service console page\footnote{https://code.google.com/apis/console}.
+\textbf{Budget} ($B_w^t$) is the amount of money the service agent
+$w$ has in its disposal during the window time $t$ (i.e.,
+$[0,t]$), which helps pay for the community membership fees
+($\epsilon$) and is one of the parameters that the service agent
+considers when deciding about getting involved in a competition or
+not.
 
-In this paper, we abstract web services as rational agents\footnote{The term rational is used here in the sense that web services are utility maximizers} that provide services to end users.
-They aim to maximize their individual income  by receiving enough requests from end users.
-In order to increase their revenues, web services seek for more tasks if they have the capacity and throughput to do so.
-Web services can join communities to enhance efficiency by collaborating with others, to have access to broad market share, and for the opportunity to receive a bigger task pool from end users.
-Furthermore, the high reliance on web services has resulted in increased quality expectations from end users.
-Communities of web services can provide higher availability, performance, reliability, and recovery for end users.
+\textbf{Reputation} ($Rep_w^t$) is a significant factor in any
+online community \cite{Fouss:2010:PRM:1751668.1751727}. Without a reputation enabling
+mechanism, users cannot differentiate among services, specially
+the ones which offer the same type of service. Reputation
+mechanisms usually aggregate users' experiences and in our case it
+strongly depends on QoS that each service provides. Users define
+tasks, each one with specific quality $T_{QoS}^r$, so that after
+performing a certain number of tasks, each one with $QoS_w^r$,
+during a window time $t$, the reputation of $w$ gets evaluated by
+the master agent. $Rep_{w}^{t}$ refers to the reputation of $w$
+during that window time $t$.
 
-\subsection{Web Service Communities}\label{s:wsc}
+In Equation \ref{repr}, we compute the reward that the master
+computes considering the task $r$'s QoS $T_{QoS}^r$ compared with
+the service offered quality $QoS_w^r$. In case the offered quality
+meets user expectations, the reward value would be positive. In
+this system, we consider a small value as default rewards $\eta$
+which the master considers together with the proportional level of
+satisfaction as a weighted value (by $\upsilon$). In this case,
+the higher the offered quality, the more weighted reward. In case
+the offered quality did not meet the user expectations, the reward
+would be negative. A default penalty value $\rho$ (where
+$\rho>\eta$) together with the weighted proportional difference
+are therefore considered. The idea is to harshly penalize the
+services rather than rewarding them. To this end, rational service
+agents should carefully analyze their capabilities once the
+available tasks are announced. Equation \ref{reward} computes the
+obtained reward by $w$ during the window time $t$ considering the
+set $task_w^t$ of tasks performed by $w$ during the window time
+$t$. In our proposal, service agents have the goal of increasing
+their budget, which is directly related to their reputation. Thus,
+they have to decide strategically how to maximize this value.
 
-The community of web services is essentially a virtual group of web services having similar and complementary functionalities\cite{DBLP:journals/ijebr/MaamarSTBB09}.
-Communities aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols to those used by single web services.
-Web services join communities to increase utility by having a larger market share and task pool.
-Community coordinators are responsible for community development, managing membership requests from web services and distributing user tasks among the community members.
-Community coordinators try to attract quality web services to join and keep the community as stable and productive as possible to gain a better reputation and user satisfaction, which increases the community's market share.
-How web services reside within communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
-
-\subsection{The Join Challenge}\label{s:tjc}
-Sometimes, web services can increase their overall utility by collaborating with other web services as communities.
-This collaboration helps them with better ways of sharing resources and having higher reputation, better market share and wider visibility.
-Web services and communities come with different internal and external parameters, and the long-term outcome is dependent on these parameters.
-
-The goal of all parties involved in the community is to maximize their long-term outcome while they are operating as part of the community.
-Web services need to be equipped with a selection strategy to choose from all of the different possible collaboration groups they can form as well as an estimation method for evaluating the long-term gain of joining different possible communities.
-Web services need to experiment with different possible collaborative groups and other web services in order to estimate their gain over time.
-However, with a high number of possible communities, it is not possible to test collaboration with random web services.
-Even if a linear approximate function for estimating utility based on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell_number$} growth rate of the possible number of partitions of web services into communities would make any brute-force type algorithm for the best community selection strategy intractable and impractical in real-world application settings.
-
-\subsection{Join Consequences}\label{s:jc}
-It is worth mentioning that a \emph{join} event takes place as a result of two parties that are looking to expand their collaborations.
-All actions are chosen in an attempt to enhance the overall outcome.
-However, the selected action may result in decreasing the overall utility in the long run.
-% long term.
-This is the case when a single web service joins a community, but the complex process of task allocation eliminates the visibility of the web service and, thus, the web service stays idle within the community, which makes the join action a bad decision.
-The same event might be beneficial for the community, as it hosts a new web service that can engage in performing a new coming task.
-But overall, neither side benefits from collaborating with the other and the join event has negative consequences for at least one side's utility.
-
-The more common scenario is when both parties benefit from the joining of a web service to a community.
-This action is rational, as both the web service and the community enhance the utility.
-However, the community may not be the best choice for the web service to join.
-In other words, the web service could have joined a better community, but, due to of lack of knowledge about the surrounding environment, joined the available community which was not the optimal choice.
-Since the community does enhance its utility, the web service could stay with that community, which results in a sub-optimal increase in web service's utility.
-In the following section the proposed model provides solutions that effectively address the aforementioned challenges.
-
-\section{The Model Components}\label{s:themodelcomponents}
-
-In this section, we discuss the parameters that we use in the rest of the paper. Then we present the task distribution and revenue model of our distributed web services communities.
-
-\subsection{Internal Features}\label{s:if}
-
-With a group of web services having identical or similar functionalities, QoS metrics provide nonfunctional characteristics for optimal candidate selection.
-Web service quality metrics were presented in \cite{Ardagna:2007:ASC:1263152.1263531,Menasce:2002:QIW:613357.613758,10.1109/ISSRE.2011.17}.
-We have adopted the most representative QoS properties of web services that highly influence the utility of web services.
-%We refer to a typical web service as ws_{i}.
-
-Let $C = \{ws_1,ws_2,..., ws_n\}$ be a community with $|n|$ web services. We define the following features for the group of web services based on their functional parameters:
-
-\begin{itemize}
-
-  \item \emph{Throughput $(Th_{C})$} is the rate at which a service can process requests.
-QoS measures can include the maximum throughput or a function that describes how throughput varies with load intensity.
-Throughput is a positive real number.
-For communities the expected throughput value of collaborating web services can be estimated as summation of throughputs of all the services inside:
-
-	\begin{equation}
-		 Th_{C} = \left\{
-			\begin{array}{l l}
-				Th_{w} & \quad \text{if $|C| = 1$}\\
-				\sum_{w \in C}{(Th_{w})} & \quad \text{if $|C| > 1$}
-			\end{array} \right.
+\begin{equation} \label{repr}
+reward_w^r = \begin{cases}
+\eta + \upsilon \frac{QoS_w^r}{T_{QoS}^r+QoS_w^r}   & \text{if $T_{QoS}^r\leq QoS_w^r$;}\\
+-(\rho +  \upsilon \frac{T_{QoS}^r}{T_{QoS}^r+QoS_w^r} ) & \text{otherwise.}\\
+\end{cases}
 \end{equation}
 
-	\item \emph{Availability $(A_{C})$} is the percentage of time that a service is operating.
-	The probability that the service operation is accessible.
-Availability is also a real number in the range $[0, 1]$.
-For communities the expected availability of collaborating web services considering they follow a parallel system can be estimated as:
-
-	\begin{equation}
-		A_{C} = \left\{
-			\begin{array}{l l}
-				A_{w} & \quad \text{if $|C| = 1$}\\
-				1-\prod_{w \in C}{(1-A_{w})} & \quad \text{if $|C| > 1$}
-			\end{array} \right.
+\begin{equation} \label{reward}
+reward_w^t =
+\begin{cases}
+\frac{\sum_{r \in
+task_w^t}reward_w^r}{|task_w^t|}& \text{if $task_w^t \neq \emptyset$;}\\
+0 & \text{otherwise.}\\
+\end{cases}
 \end{equation}
 
-	\item \emph{Execution Time $(Et_{C})$} is the time a service takes to respond to various types of requests.
-	%is the expected delay between the time instant when a request is sent and the time when the result is obtained.
-	Execution time is measured in milliseconds.
-Execution time can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests.
-This internal feature is a positive integer.
-For communities, the expected execution time of collaborating web services can be estimated as the execution time of the bottleneck service which is the service with the slowest execution time:
+The assigned reputation value is updated by the computed reward
+value. The computed reputation of services is bounded by the
+minimum and maximum reputation values $0$ and $1$. % to constrain
+%the balance the cooperative community of web services. The updated
+Let $\Gamma = Rep_{w}^{t} + reward_w^t$. The updated reputation
+value is then computed as follows:
 
-	\begin{equation}
-		Et_{C} = \left\{
-			\begin{array}{l l}
-				Et_{w} & \quad \text{if $|C| = 1$}\\
-				max_{w \in C}{(Et_{w})} & \quad \text{if $|C| > 1$}
-			\end{array} \right.
+\begin{equation}\label{repz}
+%Rep_{w}^{t+1} = Rep_{w}^{t} + reward
+%\end{equation}
+%\begin{equation*}
+Rep_{w}^{t+1} = \begin{cases}
+
+\Gamma & \text{if $ 0 \leq \Gamma \leq 1$;}\\
+0  & \text{if $\Gamma < 0$;}\\
+1 & \text{if $\Gamma > 1$.}\\
+\end{cases}
+\end{equation}
+%
+For new services with no previous reputation value, we use the
+bootstrapping trust technique proposed in \cite{Yahyaoui2}. This
+technique consists in giving the new services a chance and observe
+their behaviors for a period of testing time. The observation
+sequence is modeled as a hidden Markov model that is used to
+detect the behavior of the service by comparing the observation
+behavior against pre-defined trust patterns. Based on the matching
+result, an initial value is assigned to the service. Using this
+initial reputation value, services quickly converge to their
+actual and stable values using the update function.
+
+\begin{proposition}\label{Complexity-Rep}
+$Rep_{w}^{t}$ can be computed in time $O(|t|)$, i.e., in time
+linear in the size of the window $t$.
+\end{proposition}
+
+\begin{proof}\footnote{In this paper, we
+assume that the common arithmetic and elementary functions, such
+as multiplication, division and trigonometric functions can be
+computed in time $O(1)$ as they operate on inputs of fixed sizes.}
+The function $Rep_{w}^{t}$ is recursive on $t$, but the algorithm
+works by storing the last calculated reputation value in a
+variable, so it will not be recalculated again at each iteration.
+However, the calculation of $reward_w^t$ is needed. Since the
+function $reward_w^t$ can be computed in time linear in the number
+of tasks (see Equations \ref{repr} and \ref{reward}), which in
+turn is linear in the size of the window time, the result follows.
+$\Box$
+\end{proof}
+
+\textbf{Growth Factor} ($G_w^t$) is a parameter which declares
+services' performance based on their recent strategies and
+activities. Growth factor is relative to services' reputation
+$Rep_w^t$, QoS during the window time $t$ $QoS_w^t$, and budget
+$B_w^t$. This factor is the main variable a typical service uses
+to decide about which strategy to adopt. We use Equation \ref{eq:growthfactor} to compute the
+growth factor $G^t_w$ of the service $w$ during the window time
+$t$ as the average of the three aforementioned parameters, where
+$n_t$ is the total number of offered tasks to the whole community
+during the
+window time $t$, %(we consider the time window $t$ large enough so
+%that $n_t \neq 0$),
+$\mu_w$ is the mean received service fee, and $\epsilon$ is the
+cost of community membership.
+
+\begin{equation}\label{eq:growthfactor}
+G^t_w = \frac{Rep^t_w + QoS_w^t+\frac{B_w^t}{n_t  \mu_w -
+\epsilon}}{3}
+\end{equation}
+\begin{equation*}
+\mu_{w} \in\{\mu_{w, CM}, \mu_{w, CO}\},~~~QoS_w^t =
+\begin{cases} \frac{\sum_{r \in
+task_w^t}QoS_w^r}{|task_w^t|}& \text{if $task_w^t \neq \emptyset$;}\\
+0 & \text{otherwise.}\\
+\end{cases}
+\end{equation*}
+
+This equation is designed so that it satisfies the following
+desirable properties:
+
+\begin{enumerate}
+
+\item The growth factor function should be monotonically
+increasing in the offered quality of service $QoS_w^t$.
+
+\item The growth factor function should be monotonically
+increasing in the service's reputation $Rep^t_w$.
+
+\item The growth factor function should be monotonically
+increasing in the budget $B_w^t$ if the maximum possible profit is
+positive and monotonically decreasing in $B_w^t$ if the maximum
+possible profit is negative. This property reflects the idea that
+the budget contributes in the increase of the growth factor as far
+as there is a chance to make profit. In fact, the contribution of
+the budget $B_w^t$ in the calculation of the growth factor should
+be proportional to the maximum possible profit $n_t \mu_w -
+\epsilon$ where the service $w$ receives all the offered tasks
+during the window time $t$.
+
+\end{enumerate}
+
+  % if the profit $\beta_w$ made by the web service $w$
+%considering the mean received service fee $\mu_w$ and the cost of
+%community membership $\epsilon$ is positive.
+It is easy to show that Equation \ref{eq:growthfactor} satisfies
+the three aforementioned properties by calculating the partial
+derivatives $\partial G^t_w$ of this function in 1) $QoS_w^t$
+($\frac{\partial G^t_w}{\partial QoS_w^t} = \frac{1}{3} $); 2)
+$Rep^t_w$ ($\frac{\partial G^t_w}{\partial Rep^t_w} = \frac{1}{3}
+$); and 3) $B_w^t$ ($\frac{\partial G^t_w}{\partial B_w^t} =
+\frac{1}{3 (n_t \mu_w - \epsilon)} $). Thus, the sign of the two
+first partial derivatives is positive and the sign of
+$\frac{\partial G^t_w}{\partial B_w^t}$ depends on the sign of the
+maximum profit $n_t \mu_w - \epsilon$, so we are done. The mean
+service fee depends on the strategy adopted by the service because
+a competitive service receives higher fees $\mu_{w, CM}$ compared
+to a cooperative one $\mu_{w, CO}$ ($\mu_{w, CM} > \mu_{w, CO}$).
+The motivation behind this is that a competitive service for a
+given task is the leader for that task while other cooperative
+services are performing specific subtasks as asked by the leader.
+
+\begin{proposition}\label{Complexity-Growth_Factor}
+$G_w^t$ can be computed in time linear in the size of the window
+$t$.
+\end{proposition}
+
+\begin{proof}
+As shown in the second part of Equation \ref{eq:growthfactor}, the
+function $QoS_w^t$ can be computed in time linear in the number of
+tasks, which in turn is linear in the size of the window time.
+Since $B_w^t$ is constant, the result follows from Proposition
+\ref{Complexity-Rep}. $\Box$
+\end{proof}
+
+The above explained parameters and other additional parameters
+which will be used in the rest of this chapter are listed and self
+explained in Table \ref{t4:Preliminaries}.
+
+\begin{table}
+\centering
+\caption{List of abbreviations.}
+\begin{tabular}{|c|c||c|c|}
+\hline
+\textbf{Notation} & \textbf{Definition} & \textbf{Notation} & \textbf{Definition}\\
+\hline\hline
+$T_{QoS}^r$    & Required task QoS for the task $r$   & $T_{QoS}^t$      & Mean required task QoS during $t$\\
+$QoS_w^r$      & Service $w$ QoS for the task $r$ & $QoS_w^t$        & $w$ QoS during the window time $t$\\
+$Reward_w^r$   & Reward obtained by $w$ w.r.t. $r$    & $Reward_w^t$ & Reward to update the reputation\\
+$Rep^t_w$      & Reputation assigned for $w$          & $B_w^t$          & Budget associated to service $w$ \\
+$G^t_w$        & Growth factor of $w$ during $t$      & $\epsilon$       & Community membership fee\\
+$\pi_{w,CM}^t$ & Competition payoff of $w$            & $\pi_{w,CO}^t$   & Cooperation payoff of $w$\\
+$p_{w,CM}^t$   & Competition probability of $w$       & $p_{w,CO}^t$     & Cooperation probability of $w$\\
+$COF_w^t$      & Cooperation fee of $w$               & $\beta_{w}$      & Profit of $w$\\
+$\mu_{w, CM}$  & Mean service fee for competing $w$   & $\mu_{w, CO}$    & Mean service fee for cooperating $w$\\
+$\tau_w^t$     & Coopetitive threshold of $w$         & $P_w^t$          & Probability of competing for $w$\\
+$U_w^t$        & Utility of $w$                       & $E^t_w$          & Expected number of tasks\\
+
+\hline
+\end{tabular}
+\label{t4:Preliminaries}
+\end{table}
+
+\section{Service Interactive Strategies}
+
+The main goal of each individual service agent is to increase its
+income (payoff). This income can be earned from tasks (or
+requests) done by this service. In our model, services can decide
+to compete to get a task from the master agent or to cooperate
+with other services within a given collaborative network (the way
+a collaborative network is set by a leader is based on the
+cooperative services reputation and their QoS parameters that
+should coincide with the required QoS). Therefore we define two
+types of service strategies. First, when a service has higher
+level of confidence based on its growth factor, it can compete to
+get a task from the master and adopts the competitive strategy.
+Second, when the service agent has a lower level of confidence
+that it does not feel capable to compete, it waits for some other
+services to cooperate with to perform some tasks \footnote{Through
+the report, requests or tasks are supposed to be decomposable.},
+and thus it adopts the cooperative strategy. Services estimate the
+outcome of all the strategies and choose one of them accordingly.
+This decision is not static but can change over time so service
+agents can switch from one strategy to the other, and this dynamic
+attitude is referred to as coopetition. The underlying decision
+making process is presented in the next section.
+
+\section{Theoretical Results}\label{Theoretical Results}
+
+\subsection{Service Decision Making Procedure}
+%In the previous section, we introduced web services' interaction
+%strategies.
+In this section, we explore in details the interaction strategies
+and the outcome of each strategy in terms of services' utilities.
+The main part of services' decision making procedure falls into
+their growth factor analysis. In fact, the comparison of the
+growth factor to a particular threshold is the main reason that
+influences the service's decision to follow either competitive or
+cooperative behavior. service agents initially compute this value
+and compare it with their computed threshold. Generally the main
+challenge is the threshold computation and we cope with this issue
+in the rest of this section. We additionally use the obtained
+results in the implemented environment and analyze their
+effectiveness on services' strategic decision making procedures.
+
+Figure \ref{decisionMakingProcedure} shows the decision making
+process that is followed by a typical service. In case the service
+agent is ready to compete, there is a chance that it bids for a
+task if it has the required capabilities to accomplish that task,
+or stays silent and returns to the cooperative status. But in case
+the service agent is willing to cooperate, it has to wait for a
+cooperation opportunity that could be triggered by another service
+agent that competed and obtained the task, so both services will
+be part of the same collaborative network. In the decision making
+process presented in Figure \ref{decisionMakingProcedure}, we
+assume that the competing service might get the task (denoted as
+$Bid/obtainedTask$) or not in case of being rejected by the master
+agent, or do not even bid for the task (denoted as
+$Silent/rejectedTask$). For simplicity reasons and without loss of
+generality, we group the two cases of $Bids$ and $obtainedTask$
+together as well as $Silent$ and $rejectedTask$. The rational
+behind this aggregation is the fact that our main concentration is
+services' status (competitive or cooperative) over different
+decision making rounds, which could be caused by internal factors
+(the services) or by the external factor (the master agent).
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=0.55]{Figures/decision1++.eps}
+\caption{Decision making process over competitive and cooperative
+strategies.} \label{decisionMakingProcedure}
+\end{figure}
+
+Consider a service $w$ that is willing to compete for the period
+of time $t$ (that means the computed growth factor is more than
+the analyzed threshold). This service can estimate the expected
+payoff associated to this decision, called \emph{competition
+payoff}. Equation \ref{CMPff} computes this expected payoff for
+the competing service $w$ ($\pi_{w,CM}^t$) considering the
+$Bid/obtainedTask$ probability of $p_{w,CM}^t$ and
+$Silent/rejectedTask$ probability of $1-p_{w,CM}^t$.
+
+\begin{equation}\label{CMPff}
+\pi_{w,CM}^t=p_{w,CM}^t(\mu_{w, CM}E^t_w-COF_w^t
+E^t_w-\epsilon)+(1-p_{w,CM}^t)(-\epsilon)
 \end{equation}
 
-	%\item \emph{Data Quality} The ability of a data collection to meet user requirements , defined as the proximity of a value v returned by web service to a value considered as correct.
-The measure of data quality is considered here as a real number in the range [0, 1], where 1 represents the most desirable score.
-\end{itemize}
+In Equation \ref{CMPff}, $E^t_w$ is the number of tasks that $w$
+expects during the window time $t$, and $\mu_{w, CM}$ is the mean
+service fee that is assigned by the master agent to $w$. This
+means that a competing service directly obtains this fee from the
+master agent. Moreover, the competing service $w$ expects a
+cooperation fee ($COF_w^t$) that it gives to its collaborators in
+case $w$ needs to cooperate with other services (cooperative
+service agents in its collaboration network). In any case, the
+competing or cooperating service agent pays a fixed amount of
+membership ($\epsilon$) to the master agent, which plays the role
+of the community's coordinator. This fee would be taken into
+account when a service decides to leave to a cheaper community or
+act alone. But to concentrate on the main concerns of this paper,
+we skip these small details.\\\\
+%
+From Equation \ref{CMPff}, the following proposition is
+straightforward.
 
-	We normalize the range of these features so that each feature contributes approximately proportionately to the final utility outcome value.
-We adopt the \emph{standardization} method.
-We subtract the \emph{mean} from each feature then we divide the values of each feature by its \emph{standard deviation}.
+\begin{proposition}\label{Complexity-Competition_Payoff}
+The complexity of computing the competition payoff $\pi_{w,CM}^t$
+is linear in the competition probability $p_{w,CM}^t$, the
+expected number of tasks $E^t_w$, and the cooperation fee
+$COF_w^t$.
+\end{proposition}
 
-%$HI = \overline{HI}$
+The arrival of requests for service $w$ during the time unit $t$
+(denoted here by $m_w(t)$) can be modeled as a nonhomogeneous
+Poisson process \cite{Khosravifar-ICWS2010,Ruggeri2005}, which
+means as a Poisson process with dynamic arrival rate
+$\lambda_w(x)$ where $x$ belongs to the time unit $t$. The arrival
+rate is thus a function of time and typically varies significantly
+from moment to moment. In nonhomogeneous Poisson process, $m_w(t)$
+is expressed as follows:
 
-\subsection{External Features}\label{s:ef}
+$$ m_w(t)= \int_0^t \! \lambda_w(x) \ \mathrm{d}x$$
+%
+And the probability of having exactly $n$ requests during the
+window $t$ is computed as follows:
 
-The quantitative values of quality metrics need some benchmark values to represent their goodness.
-In other words, without some benchmark values it would be difficult for web services to identify their goals, and performance quality at any specific value of these metrics.
-Therefore, we have introduced two external features for assessing web services' estimate with regard to their standing among other web services.
+$$ p(m_w(t) = n) = \frac{(m_w(t))^n}{n! \ e^{m_w(t)}}  $$
+%
+Let $Max_w^t$ be the maximum number of requests that $w$ can
+receive during $t$. The number of expected requests $E^t_w$ is
+given by the parameter $\lambda_w(t)$ as follows:
 
-\begin{itemize}
-  \item \emph{External Parameter 1} $(exp_1)$.
-is an estimate of how close the web service's \emph{execution time} is to other web services.
-It is the difference between a web service's \emph{execution time} metric and the maximum value of execution time of all the other web services, about which the web service has information of them.
-The less value means web service has better execution time compared to other web services.
-	\begin{equation}\label{exp_1:f}
-		exp_1 = Et_{i} - Et_{max}
+\begin{equation}\label{Expectation}
+E^t_w = \lambda_w(t) = \sum_{n=1}^{Max_w^t} n \ p(m_w(t) = n)
 \end{equation}
-	\item \emph{External Parameter 2} $(exp_2)$ is a comparison of the web service's rate of performing tasks to other competing web services.
-It is the difference between a web service's \emph{throughput} metric and the maximum value of throughput of all the other web services,, about which the web service has information of them.
-The less value means web service has better throughput compared to other web services.
-	\begin{equation}\label{exp_2Lf}
-		exp_2 = Th_{max} - Th_{i}
+%
+The parameter $\lambda_w(t)$ is usually estimated from data
+samples using the least squares, iterative least squares, or
+maximum likelihood \cite{Massey1996}.
+
+\begin{proposition}\label{Complexity-Expectation}
+The complexity of computing the expected number of requests
+$E^t_w$ is linear in the size of the window time $t$.
+\end{proposition}
+
+\begin{proof}
+For a fixed function $\lambda_w(x)$, $m_w(t)$ can be computed in
+$O(1)$. Thus, from Equation \ref{Expectation}, it follows that
+$E^t_w$ can be computed in time linear in $Max_w^t$. As $Max_w^t$
+is linear in $t$, the result follows. $\Box$
+\end{proof}
+
+Similar to the competitive service case, if a service $w$ declares
+cooperative status, its expected \emph{cooperation payoff}
+($\pi_{w,CO}^t$) is computed in Equation \ref{CLPff}. In this
+equation, $p_{w,CO}^t$ is the probability of getting involved in a
+cooperative task with other services and $1-p_{w,CO}^t$ is the
+probability of failure to find such a cooperation opportunity.
+These two probabilities are set when $w$ decides to compete. We
+recall that $\mu_{w, CO}$ denotes the mean cooperation fee that is
+directly obtained from the leader (i.e., the competitive) service
+of the underlying collaborative network. Compared to $\mu_{w,
+CM}$, $\mu_{w, CO}$ is relatively smaller since the competitive
+service generally dedicates a portion of its obtained income to
+pay other cooperative services.
+
+\begin{equation}\label{CLPff}
+\pi_{w,CO}^t=p_{w,CO}^t (\mu_{w,
+CO}E^t_w-\epsilon)+(1-p_{w,CO}^t)(-\epsilon)
 \end{equation}
-\end{itemize}
+%
+From Equation \ref{CLPff}, the following proposition holds.
 
-A community of web services is abstracted as a standard web service that provides services that share the same internal and external features mentioned for web services.
-Inside, they adopt different protocols to manage the community; however, other web services or end users can communicate with communities of web services, using standard protocols, and inner details will be encapsulated for their clients.
+\begin{proposition}\label{Complexity-Cooperation_Payoff}
+The complexity of computing the cooperation payoff $\pi_{w,CO}^t$
+is linear in the cooperation probability $p_{w,CO}^t$ and the
+expected number of tasks $E^t_w$.
+\end{proposition}
 
-\subsection{Task Distribution}
+To analyze the expected payoffs obtained from different
+strategies, services need to compute the estimated probabilities
+that distinguish subcases in each behaviorial status ($p_{w,CM}^t$
+for competitive and $p_{w,CO}^t$ for cooperative). To estimate
+these probabilities, we should notice that they are functions of
+services' reputation values ($Rep_w^t$). Furthermore, $p_{w,CM}^t$
+is also function of the difference between the offered QoS
+($QoS_w^t$) and the mean requested one considering the set of all
+tasks $task^t$ ($T_{QoS}^t$ (see Equation \ref{Mean-Quality}));
+and $p_{w,CO}^t$ is function of the reputation of other services
+in the community because the leader is supposed to be selective
+when it comes to choose the collaborators. To this end, we first
+discuss the desirable properties of an estimation function of each
+of these probabilities, and show that the proposed ones satisfy
+those properties.
 
-Communities of web services usually employ an implementation of Contract-Net protocol for task distribution, in which services opt for incoming tasks, and receive the tasks for which they ask.
-However, in our model, our community members would try to distribute tasks based on their capabilities and the QoS parameters provided by the web services.
-We have used a slightly modified \emph{weighted fair queuing} method to distribute tasks among community members.
-The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{ws}$.
-In the \emph{weighted fair queuing} method, the input flow is multiplexed along different paths; however, in our case, if the rate of incoming tasks is less than the community's total throughput $(Th_{C})$, which is the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with a delay.
-%Thus, the amount of tasks performed by the community is $\sum_{ws}{Th_{ws}}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$.
-However, when the incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $|input Task Rate| \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) within the community.
+\begin{equation}\label{Mean-Quality}
+T_{QoS}^t =
+\begin{cases} \frac{\sum_{r \in
+task^t}T_{QoS}^r}{|task^t|}& \text{if $task^t \neq \emptyset$;}\\
+0 & \text{otherwise.}\\
+\end{cases}
+\end{equation}
+%
 
-While distributing tasks, the community members can verify the performance, throughput and quality of service of tasks being performed by web services.
-The community can assess if those web services are capable of performing the number of tasks they advertised.
-If for any reason, there is a decline in the quality metric or throughput, the community can consider the new values as a benchmark for future performance calculations, and penalize the suspicious web services.
-This way, players will have incentive to truthfully disclose their actual capabilities in order to maximize profit from the community and to avoid being penalized.
-In addition, the system should be dynamic enough to detect and react to web services' quality metrics variation, as over time, web service metrics may degrade or improve, changes to which the community should adjust.
-% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities.
-Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.
+\begin{proposition}\label{Complexity-Mean_Quality}
+$T_{QoS}^t$ can be computed in time linear in the size of the
+window $t$.
+\end{proposition}
 
-\subsection{Community Revenue}
+\begin{proof}
+From Equation \ref{Mean-Quality},  $T_{QoS}^t$ can be computed in
+time linear in $|task^t|$, which in turn is linear in the window
+size $|t|$. $\Box$
 
-Communities and web services earn revenue by performing tasks.
-The total gain is a function of the quality of rate of tasks being performed.
-The utility of a collaborative group of services $U_{C}$ is the revenue of the community.
-Formula \ref{u_c_normal} is an estimation of the gain of the community.
+\end{proof}
 
-\begin{equation}\label{u_c_normal}
-U_{C} = \big((\alpha \times (A_{C} - Et_{C}) - \beta \times (exp1_{C} + exp2_{C})\big) \times Th_{C}
+The desired properties of $p_{w,CM}^t$ are as follows:
+
+\begin{property}
+$p_{w,CM}^t$ is continuous with regard to $Rep^t_w$, $QoS_w^t$,
+and $T_{QoS}^t$.
+\end{property}
+%
+\begin{property}
+$p_{w,CM}^t$  is monotonically increasing in $Rep^t_w$ and
+$QoS_w^t - T_{QoS}^t$ while $QoS_w^t - T_{QoS}^t$ is positive.
+\end{property}
+%
+\begin{property}
+$p_{w,CM}^t$ is null if $QoS_w^t - T_{QoS}^t$ is negative.
+\end{property}
+%
+%\begin{property}
+%Assuming that the web service $w$ is known by the master web
+%service, $Rep^t_w$ is monotonically increasing or decreasing in
+%$QoS_w$.
+%\end{property}
+%
+\begin{property}
+The increase slope of $p_{w,CM}^t$ is higher when the reputation
+$Rep^t_w$ increases in the interval $[0, 0.5]$ than when it
+increases in the interval $]0.5, 1]$.
+\end{property}
+
+\noindent Property 1 simply says that the probability of success
+competition $p_{w,CM}^t$ can be always estimated as far as
+$Rep^t_w$, $QoS_w^t$, and $T_{QoS}^t$ are available. Property 2
+says that the reputation and QoS are two key factors that
+influence the value of $p_{w,CM}^t$ in the sense of positive
+correlation. Property 3 indicates that the probability
+$p_{w,CM}^t$ is null if the offered QoS is less than the
+expectation. Property 4 promotes the increase of the reputation
+for new comers and imposes higher increase rate at the beginning
+of the reputation curve because it is always hard to build the
+reputation, but once it is built, its maintenance is less
+challenging.
+
+\noindent The desired properties of $p_{w,CO}^t$ are as follows:
+
+\begin{property}
+$p_{w,CO}^t$ is continuous with regard to $Rep^t_w$ and the
+reputation of other services in the community.
+\end{property}
+%
+\begin{property}
+$p_{w,CO}^t$  is monotonically increasing in $Rep^t_w$ and
+ monotonically decreasing in the community average reputation.
+\end{property}
+%
+%\begin{property}
+%$p_{w,CM}$ is null if $QoS_w^t - T_{QoS}^t$ is negative.
+%\end{property}
+%
+%\begin{property}
+%Assuming that the web service $w$ is known by the master web
+%service, $Rep^t_w$ is monotonically increasing or decreasing in
+%$QoS_w$.
+%\end{property}
+%
+\begin{property}
+The increase slope of $p_{w,CO}^t$ is higher when the reputation
+$Rep^t_w$ increases in the interval $[0, 0.5]$ than when it
+increases in the interval $]0.5, 1]$.
+\end{property}
+
+\noindent Property 5 is similar to Property 1. Property 6 says
+that $w$ has more chance to get involved in a cooperation if it
+has high reputation compared to the other members. This chance
+decreases if other services have higher reputation. Property 7 is
+similar to Property 4.
+
+Equations  \ref{CMp_w} and \ref{CLp_w} respectively compute the
+estimated success probability in cases where service $w$ is
+competing and cooperating. These values are computed considering
+service's reputation value ($Rep^t_w$ computed by the master),
+service's offered QoS ($QoS^t_w$), the task required QoS
+($T_{QoS}^t$), which is the mean required QoS computed from
+previous tasks, the maximum offered QoS ($QoS_k^t$, which is
+provided by another competitive service $k$), and the cooperative
+factor $CL_w^t$ of service $w$ during the window time $t$, which
+is computed as the portion of service's current reputation on the
+average reputation of the community $\mathcal{C}$.
+
+\begin{equation} \label{CMp_w}
+p_{w,CM}^t = \begin{cases}
+\sin(Rep^t_w\frac{\pi}{2})\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k^t-T_{QoS}^t)} & \text{if $QoS_w^t\geq T_{QoS}^t$;}\\
+0 & \text{otherwise.}\\
+\end{cases}
 \end{equation}
 
-The $\alpha$ and $\beta$ values are internal and external weight coefficients.
-Execution time and external parameters are better when they have smaller values hence the negative coefficient for them.
-The result is then multiplied to the throughput value $Th_{C}$, since communities are performing tasks with $Th_{C}$ rate.
+\begin{equation}\label{CLp_w}
+p_{w,CO}^t=\sin(Rep^t_w\frac{\pi}{2})CL_w^t
+\end{equation}
+\begin{equation*}
+CL_w^t=\frac{Rep^t_w}{\sum_{k\in
+\mathcal{C}}Rep^t_k/|\mathcal{C}|}
+\end{equation*}
 
-The estimation can be improved, especially in cases where the input task rate is high and services are experiencing high task loads.
-The \emph{weighted fair queuing} method of task distribution would distribute tasks based on the individual throughput $(Th_{w})$ value of services within community.
-The services with higher throughput will affect the overall utility of the community more because they would take on proportionately more tasks.
+\begin{theorem}
+Equation  \ref{CMp_w} satisfies Properties 1 to 4.
+\end{theorem}
 
-\begin{equation}\label{u_c_load}
-\begin{split}
-U_{C} = \sum_{ws \in C}&\bigg(\big(\alpha \times (A_{ws} - Et_{ws}) \\
-        & - \beta \times (exp1_{ws} + exp2_{ws})\big) \times Th_{ws}\bigg)
-\end{split}
+\begin{proof}
+It is easy to show the continuity of Equation \ref{CMp_w}, which
+satisfies Property 1. The partial derivative $\frac{\partial
+p_{w,CM}^t}{\partial Rep^t_w} = \frac{\pi}{2}
+\cos(Rep^t_w\frac{\pi}{2})\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k^t-T_{QoS}^t)}$
+is positive as the function $\cos$ (the derivative of $\sin$) is
+positive on $[0, \frac{\pi}{2}]$, $Rep^t_w \in [0, 1]$, and
+$QoS_w^t\geq T_{QoS}^t$. The partial derivative $\partial
+p_{w,CM}^t$ with regard to $QoS_w^t - T_{QoS}^t$ ($\frac{\partial
+p_{w,CM}^t}{\partial(QoS_w^t - T_{QoS}^t)} =
+\frac{\sin(Rep^t_w\frac{\pi}{2})}{Max_k(Qos_k^t-T_{QoS}^t)}$) is
+also positive since $Qos_k^t-T_{QoS}^t > 0$ and
+$Rep^t_w\frac{\pi}{2} \in [0, \frac{\pi}{2}]$ and $\sin$ is
+positive on $[0, \frac{\pi}{2}]$, which proves the satisfaction of
+Property 2. Property 3 is straightforward. Finally, the increase
+slope of the function $\sin$ on $[0, \frac{\pi}{2}]$ proves
+Property 4. $\Box$
+\end{proof}
+
+\begin{theorem}
+Equation  \ref{CLp_w} satisfies Properties 5 to 7.
+\end{theorem}
+%
+\begin{proof}
+We can easily show the continuity  of Equation \ref{CLp_w} from
+which Property 5 follows. Property 6 can be shown by calculating
+the partial derivative $\partial p_{w,CO}^t$ first with regard to
+$Rep^t_w$ and second with regard to the community $\mathcal{C}$
+average reputation $\sum_{k\in \mathcal{C}}Rep^t_k/|\mathcal{C}|$,
+where $|\mathcal{C}|$ is the cardinality of the considered
+community $\mathcal{C}$. The first partial derivative
+($\frac{\pi}{2}\cos(Rep^t_w\frac{\pi}{2})CL_w^t$) is positive and
+the second ($\frac{-\sin(Rep^t_w\frac{\pi}{2})Rep^t_w}{(\sum_{k\in
+\mathcal{C}}Rep^t_k/|\mathcal{C}|)^2}$) is negative, which proves
+the satisfaction of Property 6. The proof of satisfaction of
+Property 7 is similar to the one of Property 4. $\Box$
+\end{proof}
+%Considering these involved parameters, we verify that properties
+%$1$ to $3$ are satisfied. For property $4$, we use $sinus$
+%function to promote the role of reputation influence in this
+%system. Using $sinus$ function, we promote reputation increase of
+%web services specially when it is less than $50\%$. Considering
+%the desired properties, the formulas represented in Equations
+%\ref{CMp_w} and \ref{CLp_w} are candidates we chose to compute the
+%probabilities regarding $Competitive$ and $Cooperative$
+%strategies. These formulas are used in implemented system and
+%verified with respect to their accuracy and effectiveness in
+%adopting different interacting strategies.
+
+%In the proposed heuristic  function, the web service $w$ is not
+%aware of current $T_{QoS}$ and $QoS_k$, but could use its previous
+%information to estimate their values. To this end, if the web
+%service is more informative about the previous data, it could
+%obtain more realistic measurement over the estimated
+%probabilities.
+%
+%
+%We compute the success probability of cooperation ($p_{w,CO}$)
+%similarly in the sense  that we still promote reputation influence
+%using $sinus$ function, but multiplied to the cooperative factor
+%$CL_w$ of the web service $w$. This value is computed as the
+%portion of web service's current reputation on the average
+%reputation of the community.
+
+\begin{proposition}\label{Complexity-Probability_Competition}
+$p_{w,CM}^t$ can be computed in time linear in the window size
+$|t|$.
+\end{proposition}
+
+\begin{proof}
+The result follows directly from 1) Equation \ref{CMp_w}; 2)
+Proposition \ref{Complexity-Rep} (Complexity of $Rep^t_w$ is
+linear in the window size $|t|$); 3) second part of Equation
+\ref{eq:growthfactor} (the function $QoS_w^t$ can be computed in
+time linear in the number of tasks, which in turn is linear in the
+size of the window time); 4) Proposition
+\ref{Complexity-Mean_Quality} (Complexity of $T_{QoS}^t$ is linear
+in the size of the window $t$); and 5) the fact that those
+functions are computed independently one from the other. $\Box$
+\end{proof}
+
+\begin{proposition}\label{Complexity-Probability_Cooperation}
+$p_{w,CO}^t$ can be computed in time $O(|t|.|\mathcal{C}|)$, which
+means linear in both the size of the window $t$ and the size of
+the community $\mathcal{C}$.
+\end{proposition}
+
+\begin{proof}
+From Proposition \ref{Complexity-Rep}, $Rep^t_w$ can be computed
+in $O(|t|)$. Consequently, the function $\sum_{k\in
+\mathcal{C}}Rep^t_k$ can be computed in $O(|t|.|\mathcal{C}|)$, so
+it does the computation of the function $CL_w^t$ as $Rep^t_w$ will
+be computed just once and stored in a variable. The same variable
+will be used to compute $\sin(Rep^t_w\frac{\pi}{2})$. Thus, from
+Equation \ref{CLp_w}, the result follows. $\Box$
+\end{proof}
+
+\subsection{Coopetition Threshold}
+
+In this part, we compute the coopetition threshold that a typical
+service agent could use to adopt reasonable interacting strategies
+and we empirically verify the effectiveness of the obtained
+results in the next section. In fact, to decide which strategy to
+adopt, we let the service agent $w$ compare its growth factor
+$G_w^t$ with the coopetition threshold $\tau_w^t$ it holds at
+current window time $t$ and choose to compete with probability
+$P_w^t$ that we compute in Equation \ref{P}. Based on this
+probability, we calculate the total utility $U_w^t$ in Equation
+\ref{U}.
+
+\begin{equation} \label{P}
+P_w^t= \begin{cases}
+\frac{G_w^t}{\tau_w^t}  & \text{if $G_w^t\leq \tau_w^t$;}\\
+1 & \text{otherwise.}\\
+\end{cases}
 \end{equation}
 
-\section{The Decision Making Mechanism}\label{s:model}
+\begin{equation}\label{U}
+U_w^t=P_w^t(\pi_{w,CM}^t)+(1-P_w^t)(\pi_{w,CO}^t)
+\end{equation}
 
-In this section, we describe our data extraction process and the methodology used to equip web services with a decision making mechanism.
-In this methodology, we first present the data extraction and engineering process and then we evaluate the decision making mechanism for web services in community settings.
-Figure \ref{fig_steps} summarizes the steps performed in DDM from the input data to generation of decision making profiles for web services.
+%Equation  \ref{U} computes the
+%expected utility (as accumulated fee) regarding web service $w$.
+%This estimated utility is result of aggregation of two different
+%interacting strategies of $Competitive$ and $Cooperative$.
+%Aggregating these strategic payoffs, web service $w$ follows
+%probability distribution of $\{P,1-P\}$. This probability
+%distribution is computed in Equation \ref{P}, which is a function
+%of the growth factor ($G_w$) and computed threshold ($Tr^t$). So
+%if the web service is aware of the reasonable threshold, the value
+%$p$ could be computed and used as the core of strategic
+%probability distribution. But there is a case where the web
+%service does not have a reasonable threshold value and cannot
+%rigorously decide for any adopting strategies.
 
-\begin{figure}%[!t]
-\centerline{\includegraphics[width=1.75in]{figures/steps.eps}}
-\caption{A summary of DDM decision profile generation steps}
-\label{fig_steps}
+The key factor in the computation of the probability $P_w^t$ and
+the associated utility is the threshold value. To compute the
+threshold, we use the game-theoretic best response technique. A
+typical service agent $w$ will follow the best response strategy
+to maximize its expected aggregated payoff. The idea is to
+equalize the expected payoffs of the two acting strategies:
+compete and cooperate.
+%
+%
+%by following the following three probability distributions: (1)
+%$\{1,0\}$ where the web service always competes; (2) $\{0,1\}$
+%where the web service always cooperates; and (3)
+%$\{\frac{1}{2},\frac{1}{2}\}$ where the web service equalize the
+%probabilities and decides with unbiased distribution. Following
+%the third case, the web service equites the expected payoffs as
+%outcomes of different interacting strategies.
+%
+The objective behind equalizing payoffs is to explore conditions
+under which service agent $w$ could react with best response to
+further decision making procedures. We use the obtained conditions
+to compute the threshold $\tau_w^t$ during the window time $t$. By
+equalizing $\pi_{w,CM}^t$ and $\pi_{w,CO}^t$, we obtain:
+
+\begin{equation*}\label{equit}
+\pi_{w,CM}^t=\pi_{w,CO}^t      \rightarrow
+\end{equation*}
+\begin{equation*}
+p_{w,CM}^t(\mu_{w,CM}-COF_w^t-\epsilon)+(1-p_{w,CM}^t)(-\epsilon)=p_{w,CO}^t(\mu_{w,
+CO}-\epsilon)+(1-p_{w,CO}^t)(-\epsilon)
+\end{equation*}
+Which means:
+\begin{equation*}
+p_{w,CM}^t(\mu_{w,CM}-COF_w^t - \epsilon) =
+p_{w,CO}^t(\mu_{w,CO}-\epsilon)+(-\epsilon)(p_{w,CM}^t -
+p_{w,CO}^t)
+\end{equation*}
+So, we obtain:
+\begin{equation*}
+\mu_{w,CM}-COF_w^t - \epsilon =
+\frac{p_{w,CO}^t~~\mu_{w,CO}}{p_{w,CM}^t}-\epsilon
+\end{equation*}
+Therefore:
+\begin{equation*}
+\mu_{w,CM}-COF_w^t = \frac{p_{w,CO}^t~~\mu_{w,CO}}{p_{w,CM}^t}
+\end{equation*}
+From which, we derive:
+\begin{equation*}
+COF_w^t = \mu_{w,CM} - \frac{p_{w,CO}^t~~\mu_{w,CO}}{p_{w,CM}^t}
+\end{equation*}
+Replacing $p_{w,CM}^t$ and $p_{w,CO}^t$ using Equations
+\ref{CMp_w} and \ref{CLp_w}, we derive the following:
+\begin{equation*}
+COF_w^t = \mu_{w,CM} -
+\frac{sin(Rep^t_w\frac{\pi}{2})CL_w^t~~\mu_{w,CO}}{sin(Rep^t_w\frac{\pi}{2})\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k-T_{QoS}^t)}}
+\end{equation*}
+%The fixed membership fee $\epsilon$ could be taken out and
+%canceled from both sides of the equation so we obtain the
+%following:
+%\begin{equation*}
+%p_{w,CM}^t(\mu_{w,CM}-COF_w^t)=p_{w,CO}^t(\mu_{w,CO})\rightarrow
+%\end{equation*}
+%
+%\begin{equation*}
+%sin(Rep^t_w\frac{\pi}{2})\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k-T_{QoS}^t)}(\mu_{w,
+%CM}-COF_w^t)=sin(Rep^t_w\frac{\pi}{2})CL_w^t(\mu_{w, CO})
+%\end{equation*}
+By simplifying the $sinus$ function from both the numerator and
+denominator sides and substituting the cooperation factor $CL_w^t$
+of service $w$ we obtain Equation \ref{CLF}:
+
+\begin{equation}\label{CLF}
+COF_w^t=\mu_{w,CM}-\frac{Rep^t_w~|\mathcal{C}|}{\sum_{k\in
+\mathcal{C}}Rep^t_k}\frac{\mu_{w,CO}Max_k(Qos_k^t-T_{QoS}^t)}{QoS_w^t-T_{QoS}^t}
+\end{equation}
+
+Equation \ref{CLF} computes the cooperation fee $COF_w^t$ that is
+assigned by service $w$. This fee represents the amount that $w$
+spends to cooperate with other service(s) to accomplish the task.
+By so doing, we obtain the maximum amount of cooperation fee that
+service $w$ can use to constrain the positive payoff out of
+competing. Otherwise, the service stays as cooperative entity.
+
+\begin{proposition}\label{Complexity-COF}
+$COF_w^t$ can be computed in time $O(|t|.|\mathcal{C}|)$, which
+means linear in both the size of the window $t$ and the size of
+the community $\mathcal{C}$.
+\end{proposition}
+
+\begin{proof}
+From Proposition \ref{Complexity-Rep}, $Rep^t_w$ can be computed
+in $O(|t|)$. Consequently, the function $\sum_{k\in
+\mathcal{C}}Rep^t_k$ can be computed in $O(|t|.|\mathcal{C}|)$.
+Since $QoS_w^t$ and $T_{QoS}^t$ can be computed in time $O(t)$
+(from the second part of Equation \ref{eq:growthfactor} and
+Proposition \ref{Complexity-Mean_Quality} respectively), we are
+done. $\Box$
+\end{proof}
+
+\begin{lemma} \label{Complexity-Competition_Payoff-Final}
+The competition payoff $\pi_{w,CM}^t$ can be computed in time
+$O(|t|.|\mathcal{C}|)$.
+\end{lemma}
+
+\begin{proof}
+The result follows directly from Propositions
+\ref{Complexity-Competition_Payoff}, \ref{Complexity-Expectation},
+\ref{Complexity-Probability_Competition}, and
+\ref{Complexity-COF}. $\Box$
+\end{proof}
+
+\begin{lemma} \label{Complexity-Cooperation_Payoff-Final}
+The cooperation payoff $\pi_{w,CO}^t$ can be computed in time
+$O(|t|.|\mathcal{C}|)$.
+\end{lemma}
+
+\begin{proof}
+The result follows directly from Propositions
+\ref{Complexity-Expectation}, \ref{Complexity-Cooperation_Payoff},
+and \ref{Complexity-Probability_Cooperation}. $\Box$
+\end{proof}
+
+%\begin{equation*}
+%\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k^t-T_{QoS}^t)}(\mu_{w,CM}-COF_w^t)=\frac{Rep^t_w}{\sum_{k\in
+%Community}Rep^t_k}(\mu_{w, CO})
+%\end{equation*}
+%
+
+We use the maximum cooperation fee that a service agent considers
+to constrain the positive expected payoff when the competitive
+strategy is adopted to update the threshold for the consequent
+time window ($t+1$). We compare the maximum cooperation fee with
+the required fee ($ReqF_w^t$) that the service indicates to
+accomplish the task. The outcome of this comparison is a factor
+that uses the current threshold $\tau_w^t$ to compute the
+consequent threshold $\tau_w^{t+1}$. As in online learning, the
+idea is to compute iteratively the threshold until the fixed point
+is achieved, which indicates the threshold's conversion, where the
+initial value is randomly chosen (in the simulation different
+initial values are used). Equation
+\ref{Trt} shows this computation. %We restrict the range of this value to $(0.15,0.85)$ to
+%avoid some unreasonable results that could occur due to different
+%reasons like system start point or heavy loaded competitive web
+%services, \textit{etc}.
+To investigate the effectiveness of this threshold on the outcomes
+of the services that follow this reasoning technique, in the next
+section, we compare the results of different agents with diverse
+strategic reasoning techniques.
+
+\begin{equation}\label{Trt}
+\tau_w^{t+1}=\begin{cases}
+\Theta & \text{if $0 \leq \Theta \leq 1$}\\
+1 & \text{if $\Theta > 1$;}\\
+0 & \text{if $\Theta < 0$.}\\
+\end{cases}
+\end{equation}
+\begin{equation*}
+\Theta =\tau_w^t \ \frac{COF_w^t}{ReqF_w^t}
+\end{equation*}
+
+\begin{proposition}\label{Complexity-Threshold}
+The threshold $\tau_w^{t}$ can be computed in time
+$O(|t|.|\mathcal{C}|)$, which means linear in both the size of the
+window $t$ and the size of the community $\mathcal{C}$.
+\end{proposition}
+
+\begin{proof}
+From Equation \ref{Trt}, the computation of $\tau_w^{t}$ is
+recursive on $t$, and the algorithm works by keeping the last
+computed value in a variable, which saves the time of
+re-calculation. Thus, the complexity of calculating $\tau_w^{t}$
+is determined by the complexity of calculating $COF_w^t$ since
+$ReqF_w^t$ is constant during the period $t$. Consequently, the
+result follows from Proposition \ref{Complexity-COF}. $\Box$
+\end{proof}
+
+\begin{theorem}\label{Complexity-Procedure}
+The time complexity of the proposed decision mechanism is
+$O(|t|.|\mathcal{C}|)$, which means linear in both the size of the
+window $t$ and the size of the community $\mathcal{C}$.
+\end{theorem}
+
+\begin{proof}
+The procedure mechanism is based on comparing the growth factor
+$G_w^t$ with the coopetition threshold $\tau_w^t$ as shown in
+Equations \ref{P} and \ref{U}. Thus, the result follows from
+Propositions \ref{Complexity-Growth_Factor} and
+\ref{Complexity-Threshold}. $\Box$
+\end{proof}
+
+\section{Experimental Results and Analysis}\label{s4:resutls}
+
+In this section, the objective is to investigate the effectiveness of the proposed strategic system.
+We start our discussions with cumulative budget comparison
+regarding different communities within which services follow
+different reasoning techniques. Figure \ref{Graph1} part (a)
+illustrates three graphs for three different communities. Each
+community hosts services that follow different reasoning
+techniques: (1) a community that follows the interactive reasoning
+techniques presented in this report (referred to as coopetitive);
+(2) a community that follows a stochastic reasoning technique so
+decisions about selecting competitive or cooperative strategies
+are totally random (referred to as random coopetitive); and (3) a
+competitive community where all services follow the competitive
+strategy (referred to as competitive).
+%The proposed model's
+%reasoning mechanism allows services to make decisions that
+%maximize their utilities, so that if the service cannot compete,
+%the procedure would suggest to collaborate, which is better than
+%competing and failing to obtain the task. In this case, the service stays idle but
+%still pays the community membership fee, which means losing
+%utility. The developed strategic decision making mechanism leads
+%some service agents to follow cooperative strategies that overall
+%maintain an optimal community budget. In the same figure, we
+%observe the cumulative budget of a community where services follow
+%random interacting strategies. The outcome is clearly lower
+%because services at each run randomly decide over their acting
+%strategies. This potentially influences the community budget
+%because a low quality service if randomly selects to follow the
+%competitive strategy, it will fail to perform a task with high QoS
+%requirements.
+
+The results illustrated in Figure \ref{Graph1} part (a)  verify
+the importance of the strategic decision making procedure to
+logically decide over the possible competitive and cooperative
+choices. Figure \ref{Graph1} part (b) illustrates communities
+average reputation of involved services. The graphs represent the
+influence of the rewards that the master agent uses to encourage
+highly capable services to compete for a task. As for the
+cumulative budget, we observe that the coopetitive community
+outperforms the random coopetitive and competitive communities in
+terms of average reputation. The proposed model's average
+reputation increases because services follow optimal strategies
+where they can perform better so obtain higher rewards. For the
+same reasons as for the cumulative budget, the average reputation
+of the random coopetitive community
+outperforms the one of the competitive community. %The idea is to balance web
+%services' strategies to maintain optimal community budget.
+
+\begin{figure}%[h]
+%\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[scale=0.47]{Figures/graphbgtmed.eps}
+\includegraphics[scale=0.47]{Figures/graphrep.eps}
+\caption{Part (a): Cumulative community budget comparison. Part
+(b): Average community reputation comparison over different
+strategic decisions.} \label{Graph1}
 \end{figure}
 
-\subsection{Data Extraction and Solution Engineering}\label{ss:learningdata}
+ %Figure \ref{Graph2} part (a) illustrates the reputation of the proposed $Coopetitive$ community where
+ %we highlight the range of reputation change in the community.
+The vertical lines denote the range of %reputation that is associated with the master web service.
+The rewards and penalties applied to %different
+% web services show that the master web service over runs extends the reputation range and takes %control of the whole community. In the developed model, web services are encouraged to choose
+ %optimal strategies. This is maintained over growth factor comparison of the $Coopetitive$ web %services.
 
-\subsubsection{Input Web Services Data}\label{sss:webservices}
+In our model, services are managed by selfish agents in the sense
+they try to maximize their own utilities. We analyze how their
+strategies affect the social welfare, and from user's and
+community's point of view how good the tasks are being performed.
+This directly impacts user's satisfaction and community's
+reputation in general. The Higher quality and quantity of tasks
+performed leads to higher user's satisfaction for the community
+which results in better reputation for the community. The results
+in Figure \ref{graph_task} show the quality and quantity of tasks
+being done successfully in three communities adopting the three
+different aforementioned strategy decision algorithms. As clearly confirmed by the simulation, the coopetitive community
+outperforms the stochastic and compete communities.
 
-%We used a data set extracted from running web services. In this data set,
-Each web service is associated with a number of features that reflect its functionality.
-These web services operate in an online environment and are continuously assigned tasks to handle.
-Sometimes, they pass tasks around, distributing sub-tasks among themselves and handling tasks in a collaborative effort.
-To engage in communities, we add additional features that reflect web services' utility as a result of joining other web services to form a community.
-The additional features are computed based on two assumptions that we adopt for a community to be formed.
-Our raw data set provides us with 64 different time slots of extracted features for each web service.
-Using this data we can build a synthetic data set that contains features of a large number of web services in a sequence of time.
-Therefore, we train a learning model that adopts the trend of joining a community and use the model to predict/find the appropriate community for other web services.
-To train our model, we build a decision tree as a benchmark for our decision making mechanism.
-The decision tree is built by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services.
-As a result, we are able to classify web services as either single or joined and propose the communities that are best fitted to the web services' requirements.
-
-\subsubsection{Filtered Data}\label{sss:filtereddata}
-
-We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}.
-The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{http://www.wsdream.net/}.
-In this data set, each web service is associated with a number of features that reflect its functionality.
-By summarizing the data provided for each web service over different time slots, we have acquired three quality features for each individual web service.
-Their quality features are the three internal features introduced in Section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time}.
-%To engage in communities, we add two additional external features that reflect web services estimation of its quality metrics compared to other web services.
-Therefore, we have generated an array of web services with three distinct features.
-
-\begin{figure}%[!t]
-\centerline{\includegraphics[width=3.25in]{figures/cfvs.eps}}
-\caption{Communities with different properties of web services actively looking for other communities to collaborate with, they send collaboration requests to communities they find the collabration  increasing the gain}
-\label{fig_community}
+\begin{figure}[h]
+\centering
+\includegraphics[scale=0.35]{Figures/graphtaskdone.eps}
+\includegraphics[scale=0.35]{Figures/graphtasksatisfaction.eps}
+\includegraphics[scale=0.35]{Figures/graphavgqostask.eps}
+\caption{Overall performance from community's point of view. Part
+(a) Total number of tasks successfully done. Part (b) Ratio of
+tasks satisfied with required QoS. Part (c) Average QoS of
+performed tasks.} \label{graph_task}
 \end{figure}
 
-Now, we want to generate a set of feature vectors representing the communities of web services for training purposes.
-For communities, we add two additional external features, as discussed in Section \ref{s:ef} that reflect the community's estimation of its quality metrics compared to other web services.
-Therefore, we formulate a \emph{Community Feature Vector (CFV)} as $CFV_{<C>} = \{f_1,...f_5\}$ having a community of $k$ web services.
-$C = {ws_1,...ws_k}$.
-The features $f_1$ through $f_5$ represent the \emph{execution time}, \emph{throughput}, \emph{availability} and the \emph{external parameters 1 and 2} correspondingly.
-A set of communities, with their feature vectors and utilities evaluated, provides our algorithm with a raw training data set.
-We call this set of communities the \emph{template vector}, and the set of feature vectors associated with the \emph{template vector} is referred to as the \emph{community feature vector set (CFVS)}.
-Figure \ref{fig_community} depicts communities looking to form collaborate communities and join other communities in order to improve their utility gain.
+We conclude our analysis by discussing how effective our
+coopetitive decision making model is by comparing the final
+utility (in terms of income) of services following our model with
+other services deviating from that coopetitive model. In Figure
+\ref{graph_dev} Part (a), we made the services deviate from the
+suggested strategy. As the simulation shows, the more services
+deviate from our coopetitive strategy the more they make less
+benefits. In Part (b), we pick one random service and simulate the
+scenario with its default coopetitive strategy and then we redo
+the simulation with exactly the same environment parameters while
+gradually alternating the decisions. By alternating we mean
+adapting the opposite of what our model does suggest. Thus, if the
+coopetitive model suggests to compete, the service agent will
+cooperate and vice versa. We run this scenario 50 times and at the
+end we check the service's budget and see if it gains more by
+deviating or not. We did this for one single deviation (i.e.,
+alternating only one decision) to 10 different deviations
+(alternating 10 different decisions) during the 50 times run. As
+the results show, deviating from the coopetitive strategy yields
+less income for the service.
 
-\subsubsection{Feature Engineering}\label{sss:feng}
-Let $CFVS = \{C_1, C_2,..., C_N\}$ be the community feature vector set with $N$ communities.
-Based on the $CFVS$ set, we create an $|N \times N|$ gain matrix for $t$ different time slots.
-Each entry of $gain_{n,m}^{t}$corresponds to a utility gain of web services in $C_n$, when $C_n$ joins $C_m$, based on community and web service data available for time $t$.
-All of these values have to be evaluated by implementing the community with members of $ws_i \in C_n$ and $ws_j \in C_m$ and evaluating its utility (see Equation \ref{u_c_load}).
-Therefore $gain_{n,m}^{t} = U_{C_n \cup C_m}^{t} - U_{C_{n}}^{t}$.
-Evaluating the utility gain for all entries of the $gain$ matrix can be a costly process with a very big number of $N$, size of the feature vector $|N|$ should be chosen carefully.
-
-\begin{table*}[ht]
-\caption{An example of $gain$ matrix for 3 different communities and their combinations} % title of Table
-\centering % used for centering table
-{\renewcommand{\arraystretch}{1.2}
-\begin{tabular}{c|c c c c c c} % centered columns (4 columns)
-\hline\hline %inserts double horizontal lines
- & \textless348\textgreater & \textless1934\textgreater & \textless2117\textgreater & \textless348, 1934\textgreater & \textless1934, 2117\textgreater & \textless348, 1934, 2117\textgreater \\ [0.5ex] % inserts table
-%heading
-\hline % inserts single horizontal line
-\textless348\textgreater & - & 0.282708 & 1.027081 & 0.282708 & 18.027081 & 18.027081 \\
-\textless1934\textgreater & -2.637483 & - & 6.969072 & -2.637483 & 5.509583 & 4.387725 \\
-\textless2117\textgreater & 5.027081 & 2.969072 & - & 5.509583 & 2.969072 & 5.509583 \\
-\textless348, 1934\textgreater & 0.0 & 0.0 & -3.851432 & - & -3.851432 & -3.851432 \\
-\textless1934, 2117\textgreater & 2.969072 & 0.0 & 0.0 & 2.969072 & - & 2.969072 \\
-\textless348, 1934, 2117\textgreater & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & - \\ [1ex] % [1ex] adds vertical space
-\hline %inserts single line
-\end{tabular}
-}
-\label{table:nonlin} % is used to refer this table in the text
-\end{table*}
-
-Now, we let our set of communities in the $CFVS$ set, within $|T|$ time frame iterations, choose the the best communities to join.
-Each community is provided with the corresponding row of data from the $gain$ matrix.
-Basically, $C_i$ is provided with the data in row $i$ of matrix $gain_{N,N}$, which is all of the possible utility values it can gain by joining different communities.
-By ordering the list, each community is utilized with an ordered set of preferences over other communities it likes to join.
-We define $>_{i}^t$ as the preference order of community $i$ at time $t$.
-
-Let $P_{C_i}^t = \{C_1 >_{i}^t C_2 >_{i}^t ....
->_{i}^t C_n\}$ be an ordered set of preferences for community $C_i$ at time $t$.
-Based on this ordered set, we define $K^t(C_i, k)$ as a set of the $k$ most preferred communities of community $i$ at time $t$.
-%\subsubsection{feature vector generation}\label{sss:fvg}
-\begin{equation}\label{h_t_pref_top}
-\begin{split}				
-K^t(C_i, k) = &\Big\{C_x | C_x >_{i}^t C_y; \forall C_y \in CFVS\ \\
-				      &\wedge C_y \notin \{K^t(i, 1),K^t(i, 2),...,K^t(i, k-1)\} \Big\}				
-\end{split}
-\end{equation}
-Based on $K^t(C_i, k)$, we define a set of communities for $C_i$ in which they are the k most preferred communities for community $i$ and also community $i$ belongs to the k most preferred communities out of all of the communities in set $K^t(C_i, k)$.
-This basically implies the preference is both-sided.
-\begin{equation}\label{l_t_top_both}
-\begin{split}	
-L^t(C_i,k) = &\Big\{C_j | C_j \in K^t(C_i, k) \\
-             &\wedge C_i \in \bigcup_{C_x \in K^t(C_j, k)}K^t(C_x, k)\Big\}
-\end{split}
-\end{equation}
-
-Table \ref{table:nonlin} illustrates an example of a $gain$ matrix for 3 different communities and their combinations.
-Each row shows the gain the community can achieve by collaborating with other 5 communities.
-In this example for community $\textless 348 \textgreater$ we have: \\
-$K(\textless 348 \textgreater, 1) = \{\textless1934, 2117\textgreater\}$ and \\
-$K(\textless 348 \textgreater, 2) = \{\textless1934, 2117\textgreater, \textless1934\textgreater\}$ \\
-Since $\textless 348 \textgreater$ is best preferred community of $\textless 1934, 2117 \textgreater$ therefore $L(\textless 348 \textgreater, 1)$ is not empty and contains the community $\textless1934, 2117\textgreater$.
-
-Using the $gain$ matrix and the mentioned preference ordering relations, we are able to build a decision tree where the list of possible communities to join and their expected utilities are set.
-% as well as the joined events that took place in different time slots.
-In addition to best choices, web services have access to other ordered choices and can look for the second best or third best if their first try is rejected by the target community.
-The consequences of each try level is analyzed in more detail in the following section, in which we launch experiments and investigate the effectiveness of the use of a decision tree with different decision layers in joining other communities and enhancing the overall utility.
-
-\subsection{Decision Profile Generation}\label{ss:learningmodel}
-
-Our goal is to create a decision making profile for each community in the $CFVS$ set.
-We are creating an environment where they can experience the outcomes of different strategies.
-The result will be a decision tree of the feasible and utility increasing moves over time.
-
-We let communities pick the best communities for maximizing their utilities over different time frames.
-At time $t = 1$, we let each community in the $CFVS$ set choose the best community, which is a single community in set $C_j = K^t(C_i, 1)$.
-If community $C_j$ also has the highest preference to join $C_i$ meaning the $L^t(C_i, k=1)$ set is not empty, they would join together.
-Having set $k = 1$ is a very strict and hardly satisfiable condition.
-In order to relax the requirement, the value of $k$ is being increased by a rate $r$ proportional to time slot $t$.
-Basically, $k = 1 + |r \times t|$.
-On early steps of simulation web services and communities are more strict but as time goes on, we let them choose second and then third best options too.
-However, increasing $k$ quickly increases the time complexity of $K^t(C_i, k)$ by $O(k^2 \times n.log(n))$.
-
-When communities $C_i$ and $C_j$ are in each other's top $k$ preference set, their combination is added to the list of possible communities that can join others at time $t+1$.
-Also, for each community $C_i$ in our initial $CFVS$ set, we maintain a tree with the community $C_i$ as its root.
-Its children are all of the communities that $C_i$ decided to join.
-As the scenario progresses over time, the merged communities may decide to join other communities.
-When community $C_i$ and $C_j$ decide to join each other and create community $C_k$, the new community $C_k$ will be added as a child to both $C_i$ and $C_j$ nodes.
-At the end of the process, each community is utilized with a tree of set of possible combination of communities it can join.
-Algorithm \ref{algo:dectree} illustrates the DDM tree creation procedure as pseudo-code.
-
-Having created $|n|$ trees, for each community $C_i$, our communities are utilized with the different possible paths they can take to maximize their utilities.
-Using a distance function, communities and web services can utilize these results and find the $C_i$ that closely resembles their parameters.
-They will be utilized with a tree that has the strategies the community can use to join our communities which will be best possible path to take and communities to join while most likely being accepted by other communities since its a two sided preference.
-The algorithm below describes the tree creation process.
-
-\begin{algorithm}
-\DontPrintSemicolon
-\KwIn{$\langle r, gain^t_{n,n}, CFVS \rangle$ learning rate $r$, $|N \times N \times T|$ gain matrix, community feature vector}
-\KwOut{A set of \emph{root} nodes of the decision trees}
-$k \gets 1$\;
-$nodes[N] \gets$ initialize $N$ tree nodes representing each community in CFVS\;
-\For{$t \gets 1$ \textbf{to} $T$} {
-	$k \gets 1 + round (r \times t)$\;
-  \For{all $C_i \in CFVS$} {
-	  \For{all $C_j \in L^t(C_i, k)$} {
-      % The "l" before the If makes it so it does not expand to a second line
-      \If{$C_i \in L^t(C_j, k)$}{
-        $C_k \gets C_i \cup C_j$\;
-				add $C_k$ to $CFVS$ set\;
-				initiate $node_k$, representing $C_k$\;
-				$nodes_i.addChild (node_k)$\;
-				$nodes_j.addChild (node_k)$\;
-      }
-%      \Else{
-%        $j \gets j + 1$\;
-%      }			
-		}
-  }
-%  $i \gets i + 1$\;
-}
-\Return{nodes}\;
-\caption{{\sc DDM Decision Tree Algorithm}}
-\label{algo:dectree}
-\end{algorithm}
-
-\textbf{Complexity.} Here we analyze the computational complexity of the DDM decision tree creation algorithm on each time iteration $t$.
-Computing top $k$ preferred communities for $C_i$ in $L^t(C_i, k)$ requires an $O(n.log(n))$ sort time.
-$C_i$ has a result set of size $|k|$, and for each of those $k$ communities we need to check against their $k$ top preferred communities.
-Considering we already have the list sorted, line 6 in algorithm runs $O(k \times n.log(n))$ times.
-Doing this search for all communities in $|CFVS|$ set $n$ times (line 5), the overall order of complexity of the algorithm in regards with $n$ and $k$ is: $O(k^2 \times n^2.log(n))$.
-
-\section{Experiments}\label{s:experiments}
-We implemented DDM in Java\footnote{Source code of implementation and data is available at: \emph{https://github.com/Marooned202/DDM}}.
-We have extracted the set of features for 4532 web services in 64 different time slots through a data set provided by \cite{10.1109/ISSRE.2011.17}.
-By choosing 86 web services out of these sets and choosing a subset of all possible combinations of sizes 2, 3, and 4 of these 86 web services, we have chosen 10,000 communities and evaluated the feature vectors and utilities they can have in 64 different time slots.
-This provides us with the initial training feature set of size $|CFVS| = 10,000$ communities.
-Based on Equation \ref{u_c_load} the utility of these communities are estimated, and the gain matrix $|10000 \times~ 10000|$ of all possible ways of merging these 10,000 communities, is generated\footnote {The template vector and gain matrix generated are available at \emph{https://github.com/Marooned202/DDM/tree/master/wsds/data/run}}, and each community has the ordered preference among other communities known in the set.
-
-We let communities and web services adopt their strategies based on our $DDM$ decision making mechanism.
-Based on the decisions adopted, each community will generate a decision tree profile.
-We let DDM run four times with different $r$ rates of 0.05, 0.07, 0.10 and 0.20.
-With the slow rate of $r = 0.05$, we increase $k$ in Equation \ref{u_c_normal} for every 20 time frames, which will happen only three times in our 64-step experiment.
-In the case of $r = 0.20$, k increases much faster, at a rate of once every 5 time frames, which increases the complexity of the $L^t(C_i,k)$ search for each community in the $CFVS$ set.
-
-Table \ref{table:valueandgain} depicts the average utility gain value of the communities in each of the four runs.
-The utility gain is the increase of utility the communities gain by cooperating and joining other communities.
-The utility gain ratio is the ratio of their final utility over initial utility.
-Comparing the different search rates, we can see increasing $r$ to value of $0.10$ results in significant performance boost, however the higher rates of $r$ are not increasing the chance of finding better collaborative groups for our communities.
-
-\begin{table}[ht]
-\caption{Utility gain of web services after making collaborative groups based on DDM algorithm with different $r$ rates} % title of Table
-\centering % used for centering table
-{\renewcommand{\arraystretch}{1.2}
-\begin{tabular}{c|c|c} % centered columns (4 columns)
-\hline\hline %inserts double horizontal lines
-Search Rate $r$ & Utility Gain Value & Utility Gain Ratio \\ [0.5ex] % inserts table
-%heading
-\hline % inserts single horizontal line
-r=0.20 & 176.1499 & 6.9690 \\
-r=0.10 & 174.6541 & 6.9182 \\
-r=0.07 & 159.9462 & 6.2834 \\
-r=0.05 & 136.0768 & 5.1032 \\ [1ex] % [1ex] adds vertical space
-\hline %inserts single line
-\end{tabular}
-}
-\label{table:valueandgain} % is used to refer this table in the text
-\end{table}
-
-%\begin{figure}%[!t]
+\begin{figure}%[h]
 %\centering
-%\includegraphics[width=3.5in]{figures/utility_gain_r.eps}
-%\caption{DDM Utility Gain Value}
-%\label{utility_gain_value}
-%\end{figure}
-%
-%\begin{figure}%[!t]
-%\centering
-%\includegraphics[width=3.5in]{figures/utility_ratio_r.eps}
-%\caption{DDM Utility Gain Ratio}
-%\label{utility_gain_ratio}
-%\end{figure}
-
-We utilize the same communities and web services with a simple rational decision making mechanism, in which communities will choose to join a community if it increases utility by any amount.
-We call it the $rational$ method, in the sense that it is just a rational method and is not aiming to be optimal.
-We chose 10 random web services and compared the results with web services which adopted our DDM model.
-Figure \ref{utility_gain_mlisa_and_rational} shows the comparison of the end result of utility gain values.
-In 18 out of 40 tries, \emph{rational} agents were not able to improve their utility at all because the communities they chose rejected their request, most likely because they would not have increased the utility of the other communities if they had joined them.
-The results show that a long-term strategic decision mechanism is needed to satisfy all of the services within communities.
-Figure \ref{utility_gain_mlisa_and_rational_ratio} shows the same results in terms of ratio of utility gain.
-
-\begin{figure}%[!t]
-\centering
-\includegraphics[width=3.5in]{figures/utility_gain.eps}
-\caption{Utility Gain DDM and Rational}
-\label{utility_gain_mlisa_and_rational}
+\includegraphics[scale=0.47]{Figures/graphdev.eps}
+\includegraphics[scale=0.47]{Figures/graphdev2.eps}
+\caption{Utility loss while deviating from our coopetitive
+decision process. Part (a) Overall budget when deviating from our
+model in 0, 10, 20, 30, 40, and 50 percent of decisions. Part (b)
+Ratio of getting earning utility (budget) when deviating from our
+coopetitive strategy in 1 to 10 decisions.} \label{graph_dev}
 \end{figure}
 
-\begin{figure}%[!t]
-\centering
-\includegraphics[width=3.5in]{figures/utility_ratio.eps}
-\caption{Ratio of Utility Gain DDM and Rational}
-\label{utility_gain_mlisa_and_rational_ratio}
-\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary}\label{sec:conclusion-cha3}
 
-Now, we evaluate the performance of the decision profiles generated based on our data set for other communities.% which are not included in the decision tree creation process.
-We create one thousand communities from the web services in the data set that were not involved in the decision model creation process.
-We define a distance function that measures the difference between basic features of communities, which measures the similarity of communities.
-
-\begin{equation}\label{distance_c}
-\begin{split}
-distance (C_1, C_2) & = |Th_{C_1} - Th_{C_2}| \\
-                    & + |A_{C_1} - A_{C_2}| + |Et_{C_1} - Et_{C_2}|
-\end{split}
-\end{equation}
-
-Now, each community tries to find the closest community within the trained $CFVS$ set.
-Following its decision profile, the community can get a good estimate of the possible strategic decisions it can adopt.
-Basically, the trained profiles benefit the new web services in two ways.
-First, they provide the communities with a set of viable communities to join.
-Second, they provide an estimation of long-term utility gain for each available decision.
-In this experiment, we let communities follow the best decision within the decision tree provided to the them.
-
-\begin{table}[ht]
-\caption{Number of communities that misses the optimal decision, out of 1,000 communities} % title of Table
-\centering % used for centering table
-\begin{tabular}{|c|c|} % centered columns (4 columns)
-\hline %inserts double horizontal lines
- Method&Miss \\ [0.5ex] % inserts table
-%heading
-\hline % inserts single horizontal line
- DDM r=0.05& 375 \\ % inserting body of the table
- DDM r=0.07& 137 \\
- DDM r=0.10& 6 \\
- DDM r=0.20& 6 \\
-Rational Method& 717 \\
-Greedy Method& 828 \\ [1ex] % [1ex] adds vertical space
-\hline %inserts single line
-\end{tabular}
-\label{fail_rate} % is used to refer this table in the text
-\end{table}
-
-In order to evaluate the performance of the mechanism, we used \emph{Receiver Operating Characteristic (ROC) curve}, which is a graphical plot illustrating the true negative rate against the false positive rate at various threshold settings in classifier systems.
-In order to classify our communities' selection strategies correctly, for each community, we evaluated the training process by replacing the community in the set with the closest one, from which it gets the strategy profile.
-If the actions are the same and the same utility levels are gained, we classify the decision as correct.
-Otherwise, it is classified as a wrong decision.
-\emph{AUC}, the area under the \emph{ROC curve}, is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one, and the higher number reflects better performance from the better solution.
-Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of the DDM decision making mechanism.
-We compare our method with two other methods.
-The \emph{rational} method is based on the assumption that communities, as rational agents, join a community that increases their utility.
-The \emph{greedy} method only looks up the available list of communities and simply joins the community that maximizes its utility without considering any long-term strategy or other communities' acceptance scenarios, its an greedy algorithm and chooses a locally optimal choice.
-Therefore we use these two methods as our benchmark:
-
-\begin{itemize}
-  \item {\bf Rational Method:} Communities would send a join request to any available community, which will increase the utility.
-The other community would accept the join offer if the utility gain is positive as well.
-	\item {\bf Greedy Method:} Communities do a linear search among all the available communities and send a join request to the community which results in maximum utility, The other community would accept the join offer if the utility gain is positive and the utility gain does not need to be the maximum for the community recieving the join request.
-\end{itemize}
-
-Figure \ref{roc5} compares the results for all methods.
-The two other methods have very high failure rates compared to our method.
-Table \ref{fail_rate} illustrates the number of communities that failed to find the optimal collaboration group.
-The results support the need for a long-term training model in a successful decision making process.
-
-\begin{figure}%[!t]
-\centering
-\includegraphics[width=3.5in]{figures/roc.eps}
-\caption{RoC Curve}
-\label{roc5}
-\end{figure}
-Now, we evaluate the system-specific results from users' and communities' perspectives.
-By distributing tasks among the communities over these time frames, we evaluate the revenue for each community.
-Figure \ref{stats1} shows the overall revenue gain of communities using our method.
-Figure \ref{stats2} shows the momentarily revenue gain for each community in each time slot compared to the previous time.
-These results show that the run with the higher learning rate of $r=0.20$ starts discovering better communities to join much earlier.
-The runs with slow rates seem to find some communities to join initially, but then they slow down until later, when they start discovering new communities to join.
-
-\begin{figure}%[!t]
-\centering
-\includegraphics[width=3.5in]{figures/stats1.eps}
-\caption{Overall Utility of all communities}
-\label{stats1}
-\end{figure}
-
-\begin{figure}%[!t]
-\centering
-\includegraphics[width=3.5in]{figures/stats2.eps}
-\caption{Utility Gain on time}
-\label{stats2}
-\end{figure}
-
-Figure \ref{stats3} depicts the average community size over time, which essentially represents the number of new communities being formed.
-Once again, these results show that the runs with higher search rates tend to find appropriate communities to join faster.
-
-\begin{figure}%[!t]
-\centering
-\includegraphics[width=3.5in]{figures/stats3.eps}
-\caption{Average Community Size}
-\label{stats3}
-\end{figure}
-
-\section{Related Work}\label{s:related_work}
-
-In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
-defined communities as \emph{Service Containers} that aggregate
-substitutable web services providing a common functionality (same
-set of operations). They abstracted \emph{Service Containers} as
-web services that are created, advertised, discovered and invoked
-just as elementary web services. The \emph{Container} is
-considered as a manager that is responsible for web service
-selection upon receiving a request on run-time. The authors have
-proposed a scoring service based on non-functional requirements of
-the request and web service capabilities to dynamically chose the
-web service to perform the requested task. A similar concept was
-proposed by Maamar et al. in
-\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
-web service communities as a collection of web services with a
-common functionality but different QoS properties. A community
-manager, upon receiving a request, delegates the request to one of
-its current members. The choice is based on the performance
-history and quality metrics of each web service. The authors have
-proposed an efficient global web service selection algorithm in
-order to approach quality constraints and preferences for
-composite services which require aggregation of different types of
-services to satisfy the user.
-
-Benslimane et al. \cite{Liris-2770} have proposed a multi-layer
-approach grouping similar Web services into communities and having
-an interface implemented as an abstract web service for accessing
-the community on top of the community layer. The interactions
-between composite, management and community layers and the
-bindings are performed by a generic driver called Open Software
-Connectivity (OSC).
-
-In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
-service communities with centralized access across distributed web
-services. They have proposed a framework for web service
-management, query resolution among communities and a query caching
-mechanism executed by the manager to improve the performance of
-query resolution process among many distributed communities. The
-key idea is to cache previous computed results for answering
-future queries.
-
-Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
-then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
-proposed an architecture utilizing \emph{Contract-Net} protocol
-for engineering task distribution within communities of web
-services. The protocol is centrally executed by the community
-manager. This architecture has been further developed in
-\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
-conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
-roles have been distinguished for community members: masters and
-slaves. Master web services and community managers that lead
-communities and are responsible for membership management. They
-can invite and convince slave web services to join the community,
-and attract new slave web services to their communities by
-awarding them better payoff. Moreover, they can eject some slave
-members from the community to improve its overall reputation if
-these members are misbehaving or cannot provide the promised QoS.
-
-In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
-developed a community as a ``cluster'' that groups Web services
-based on a specific area of interest. All web services in a given
-community share the same functionality. These communities are
-created by \emph{third party community providers} which use the
-\emph{community ontology} as a template and define a set of
-operations that all web services within a community should
-provide. Using semantic analysis on web service operations, web
-services either find and join a community with similar
-functionality or create a new operation description for a new
-community. The authors have described the concept of
-\emph{community agents} associated to \emph{community providers}.
-A community agent is responsible, among other things, of the
-registration of services with the community. An example of a
-community that provides health care services to senior citizens
-has been used. In this example, a governmental entity is needed to
-check the health care standards used by the members before
-authorizing them to be part of the community. Such a central
-entity is represented by the community agent. Thus, community
-agents are playing the role of community managers. In a close work
-\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
-global planning selection algorithm and a delegation algorithm to
-be run when a request to execute an operation is received by the
-community. This needs a central entity to run those algorithms.
-Such entity plays the same role as the community coordinator or
-manager.
-
-Most of the recent work on communities of services are either
-user-centric and focus on user satisfaction
-\cite{Chun02user-centricperformance} or system-centric and focus
-on the whole system throughput, performance and utilization. There
-are many contributions in distributed, grid, cluster and cloud
-services which are system-centric. However, in real world
-environments and applications, both users and service providers
-are self-interested agents, aiming to maximize their own profit.
-In those environments, both parties (users and services) will
-collaborate as long as they are getting more benefits and payoff.
-
-In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
-DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
-mechanisms to help users and services maximize their gain. A
-two-player non-cooperative game between web services and community
-master was introduced in
-\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this game-theoretic
-model, the strategies available to a web service when facing a new
-community are requesting to join the community, accepting the
-master's invitation to join the community, or refusing the
-invitation to join. The set of strategies for communities are
-inviting the web service or refusing the web service's join
-request. Based on their capacity, market share and reputation, the
-two players have different sets of utilities over the strategy
-profiles of the game. The main limits of this game model are: 1)
-its consideration of only three quality parameters, while the
-other factors are simply ignored; and 2) the non-consideration of
-the web services already residing within the community. The game
-is only between the community master and the new web service, and
-the inputs from all the other members and their influence on the
-master's decision are simply ignored. The consideration of those
-inputs and this influence factor is a significant issue as
-existing web services can lose utility or payoff because of the
-new member, which can result in an unhealthy and unstable group.
-The problem comes from the fact that the existing members should
-collaborate with the new web services, so probably their
-performance as a group can suffer. Existing members may even
-deviate and try to join other communities if they are unsatisfied.
-Those considerations of forming stable and efficient coalitions
-are the main contributions of our paper.
-
-In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
-for selecting web services has been proposed. In this approach,
-the authors proposed a web service selection process that the
-community masters can use. The approach considers the efficiency
-of all the three involved parties, namely users, web services and
-communities. In this work, it is shown how the gains of these
-parties are coupled together using a linear optimization process.
-However, the optimization problem in this solution tends to
-optimize some parameters considering all web services regardless
-of their efficiency and contribution to the community's welfare.
-Moreover, there are no clear thresholds for accepting or rejecting
-new web services. The solution of the optimization problem could,
-for instance, suggest web services already residing within the
-community to increase or decrease their capacity to cover up the
-weakness of other parties in the system. However, a high
-performing web service could deviate anytime it finds itself
-unsatisfied within the community instead of adjusting its service
-parameters.
-
-In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
-autonomous web services based on coalitional game theory has been
-introduced. The authors have proposed an interesting algorithm to
-reach individually stable coalition partition for web services in
-order to maximize their efficiency. The communities choose new web
-services on the promise that it would benefit the community
-without decreasing any other web service's income. In the proposed
-model, the worth of community is evaluated with high emphasis on
-the availability metric and considering price and cost values
-only. The community structure is based on a coordination chain,
-where a web service is considered as a \emph{primary} web service
-and the community task-distribution method initially invokes the
-primary web service and only if the primary web service is
-unavailable, the method invokes the next backup web services as
-they are ordered in the coordination chain. We believe that this
-coordination chain limits the cooperation power as it introduces a
-sort of hierarchy. However, in pure and open cooperative models,
-such as the one we propose in this paper, active cooperation
-activities engaging simultaneously many agents so that they can
-perform the tasks more efficiently are being used. Moreover, if
-the availability is high, which is the case nowadays with the
-recent advancements in cloud and hardware infrastructures, the
-backup web services will end-up having a very low chance of
-getting jobs, especially the ones further in the chain. This will
-results in a considerable waste of web services capabilities.
-
-All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process.
-So basically These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.
-We address this issue by introducing DDM a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another.
-After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics.
-Therefore web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
-In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Summary}\label{sec:conclusion-cha4}
-
-In this paper, we proposed a training model for the problem of membership management of communities of web services.
-Using the traning model we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves.
-This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available.
-The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices.
-The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.
-The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.
-
-Our plan for future work is to advance learning process on the training set that we provided in our work.
-SVN machine learning algorithm are suitable in classification of our training data set, to better classify correct or wrong decisions based on long-term utility gains, as data set outputs.
-This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.
+In this chapter,

### 2015-05-10 thesis/thesis/chap5/chap5.tex
added coop

@@
-\chapter{LEarning Chapter}\label{cha:PCTLKC+}
+\setcounter{chapter}{4}
 
-In this chapter
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter{Training Chapter}\label{cha:PCTLKC}
 
-\section{Summary}\label{sec:conclusion}
+\section{Introduction}
 
-In this chapter,
+Over the past years, online services have become an important part of many scalable business applications.
+The increasing reliance on online service providers has significantly influenced the way web services are engineered.
+Therefore, given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue.
+One practical solution towards delivering high quality services is utilizing intelligent decision making agents.
+These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users\cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Demirkan2013412, journals/tsc/ZhengZYB13, Josang:2007:STR:1225318.1225716}.
+However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided.
+Recent developments have attempted to shift web services from passive models, consisting of individual components, to models made up of autonomous and group-based components that share common goals.
+In group-based models, interaction, composition, and cooperation are the key challenges \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13} that directly impact the group's overall performance in achieving common goals.
+To that end, we see the emergence of web service \emph{communities}, which consist of services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}.
+A \emph{community} of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.
+
+The advantages of community of web services are that the community facilitates the discovery of web services and provides better quality of service compared to passive models with individual components.
+Communities act as abstract web services, communicating with external entities via the same standard protocols that a normal web service employs.
+But, they regulate the service process via sophisticated internal communication protocols, thereby providing services based on the combined work of a number of web services.
+The downside to communities is the complexity of management involved in finding and inviting individual web services and managing the overall quality of the combined work of several web services.
+% because although they have similar functionality, they have different attitudes.
+When interacting with communities of web services, users send their requests to the coordinators of the community, which play the role of community representative or access point.
+The community coordinator is responsible of receiving tasks and delivering services.
+Moreover, as community representative, it verifies the credentials of new web services before accepting them into the community and kicks web services that could harm the value of the community.
+
+\textbf{Challenge and Problem Statement.} In recent work, communities of web services have been proposed in order to facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities.
+However, there is a twofold challenge that yet to be addressed.
+The first part is community development, which involves finding the right web services for the community, satisfying the objectives of all the web services and community coordinators involved within the community; and the second part is from the individual web service's side because each web service aims to join the community that would guarantee the best outcome.
+The advocated solutions \cite{conf/webist/MaamarLBTS07, 10.1109/ARES.2008.7, journals/soca/XuYLZB11, 10.1109/TSC.2012.12, managing-hela-jalel, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:conf/IEEEscc/LimTMB12} have attempted to address these research problems.
+These research problems are reflected by the two challenge parts:
+\begin{enumerate}
+	\item The solutions consider the architecture of centralized management for communities where most of the decisions are made by the centralized coordinator.
+The problem is that in real world scenarios, decisions made by independent service providers are highly distributed.
+	\item The solutions either propose complex algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to find the optimal strategy to follow, or oversimplify the problem by eliminating important parameters and using approximation techniques to make the algorithms tractable \cite{10.1109/TSC.2012.12}.
+\end{enumerate}
+These approximation methods sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored.
+
+For example, instead of calculating the gain distribution using the complex shapely-value method, \cite{10.1109/TSC.2012.12} proposes a simple egalitarian way of distributing gain, which completely ignores the gain generated from collaborative work of sub-communities.
+Other categories of related work exist that do not focus on all the parties involved within the community \cite{DBLP:conf/IEEEscc/KhosravifarABT11}.
+%And some other work which do not focus on rationality on web services or communities involved [refrences].
+In \cite{journal-community-formation} we proposed a cooperative game theory based model for aggregating web services in communities.
+A centralized decision maker in communities based on a complete knowledge of available web service quality metrics and performance, has been used to form optimal and stable communities that maximize individual and group income.
+However, centrality and complete information are strong assumptions, which are not very compatible with real business scenarios.
+
+\textbf{Contributions.} In this paper, we introduce DDM, a Distributed Decision Making model for  community formation that regulates web service agents’ decision making process in terms of cooperating and deciding which group to join and which service to invite for joining.
+The decision model in extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
+The generated decision tree improves agents' understanding of the environment and how to select actions that lead towards maximizing their utilities.
+The advantage of this approach is that the tree is created from the past data and reflects comprehensive vision about agents' attitude of action selection.
+However, the tree is subject to get continuously modified to adapt with environmental changes.
+%The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems.
+The decision model provides web services with enough information which helps those services to efficiently decide and predict the outcome of their different possible collaborations.
+This model works in a distributed manner in which services are self-sufficient in decision making process and do not rely on a centralized decision making process.
+Our findings show that communities of web services can efficiently find the appropriate web service to invite for cooperation as well as allowing a single web service to find the best communities to join.
+In other words, the web services agents are equipped with a recommender system to suggest beneficial action.
+Moreover, communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
+In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their short-term and long-term goals; therefore, opting for best decision available.
+
+To effectively generate the decision model for web services, we used real data set to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another.
+The data set has been extracted by real-world QoS evaluation results from 142 users on 4,532 Web services on 64 different time slots.
+Combining these data based on each web service point of view on different time slots, we acquired 5 different unique features for 4,532 web services.
+By engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in different time slots.
+We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others.
+All paths and the outcomes are labeled to be utilized in the training model.
+Using cross validation sets, web services are able to compute the optimal hypothesis function (using logistic regression) that can be used to predict outcomes of cooperative work with other individual web services or communities.
+Our findings show that web services equipped with DDM have by far better outcomes in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.
+
+\section{Preliminaries and Challenging Issues}\label{s4:preliminaries}
+%In this section, we first present the architecture of DDM.
+We explore the characteristics of intelligent service agents and the features we extract for training.
+To do this, we first discuss some preliminaries.
+In this section, we discuss the preliminary concepts of communities of web service and we introduce the challenges of community formation.
+
+\subsection{Web Services}\label{s:ws}
+
+In recent years, online services have become a standard part of daily life around the globe.
+Many modern applications rely on web services from different providers.
+For instance, many mobile and tablet applications that have limited storage and processing power are merely aggregating information from different online services.
+Examples are vast, including weather forecasting, ticket selling, shopping apps, local maps and location services.
+
+The World Wide Web Consortium (W3C) defines web services as ``software systems designed to support interpretable machine-to-machine interaction over a network.
+It has an interface described in a machine-processable format (specifically WSDL).
+Other systems interact with the web service in a manner prescribed by its description using SOAP messages, typically conveyed using HTTP with XML serialization in conjunction with other Web-related standards.'' When developers declare a new web service, it will be
+discovered based on its description, which fully discloses its functionalities.
+Developers also have to declare a public interface and a readable documentation to help other developers when integrating different services \cite{w3cwsdl}.
+Nowadays, web API, standards that do not require XML-based web service protocols like SOAP and WSDL are also emerging.
+They are called REST (representational state transfer) services, which are moving towards simpler communication protocols.
+%They are not restricted
+%to XML formats, recently JSON, a human readable and simpler format
+%is becoming popular among online service providers.
+
+We are not going to delve into the engineering details of online web service implementation and its protocols in this paper.
+We are interested in web services from a business model perspective.
+Service providers usually charge end users for services they provide.
+For example, Google has listed pricing and plans for a wide range of services they provide on their web service console page\footnote{https://code.google.com/apis/console}.
+
+In this paper, we abstract web services as rational agents\footnote{The term rational is used here in the sense that web services are utility maximizers} that provide services to end users.
+They aim to maximize their individual income  by receiving enough requests from end users.
+In order to increase their revenues, web services seek for more tasks if they have the capacity and throughput to do so.
+Web services can join communities to enhance efficiency by collaborating with others, to have access to broad market share, and for the opportunity to receive a bigger task pool from end users.
+Furthermore, the high reliance on web services has resulted in increased quality expectations from end users.
+Communities of web services can provide higher availability, performance, reliability, and recovery for end users.
+
+\subsection{Web Service Communities}\label{s:wsc}
+
+The community of web services is essentially a virtual group of web services having similar and complementary functionalities\cite{DBLP:journals/ijebr/MaamarSTBB09}.
+Communities aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols to those used by single web services.
+Web services join communities to increase utility by having a larger market share and task pool.
+Community coordinators are responsible for community development, managing membership requests from web services and distributing user tasks among the community members.
+Community coordinators try to attract quality web services to join and keep the community as stable and productive as possible to gain a better reputation and user satisfaction, which increases the community's market share.
+How web services reside within communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+
+\subsection{The Join Challenge}\label{s:tjc}
+Sometimes, web services can increase their overall utility by collaborating with other web services as communities.
+This collaboration helps them with better ways of sharing resources and having higher reputation, better market share and wider visibility.
+Web services and communities come with different internal and external parameters, and the long-term outcome is dependent on these parameters.
+
+The goal of all parties involved in the community is to maximize their long-term outcome while they are operating as part of the community.
+Web services need to be equipped with a selection strategy to choose from all of the different possible collaboration groups they can form as well as an estimation method for evaluating the long-term gain of joining different possible communities.
+Web services need to experiment with different possible collaborative groups and other web services in order to estimate their gain over time.
+However, with a high number of possible communities, it is not possible to test collaboration with random web services.
+Even if a linear approximate function for estimating utility based on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell_number$} growth rate of the possible number of partitions of web services into communities would make any brute-force type algorithm for the best community selection strategy intractable and impractical in real-world application settings.
+
+\subsection{Join Consequences}\label{s:jc}
+It is worth mentioning that a \emph{join} event takes place as a result of two parties that are looking to expand their collaborations.
+All actions are chosen in an attempt to enhance the overall outcome.
+However, the selected action may result in decreasing the overall utility in the long run.
+% long term.
+This is the case when a single web service joins a community, but the complex process of task allocation eliminates the visibility of the web service and, thus, the web service stays idle within the community, which makes the join action a bad decision.
+The same event might be beneficial for the community, as it hosts a new web service that can engage in performing a new coming task.
+But overall, neither side benefits from collaborating with the other and the join event has negative consequences for at least one side's utility.
+
+The more common scenario is when both parties benefit from the joining of a web service to a community.
+This action is rational, as both the web service and the community enhance the utility.
+However, the community may not be the best choice for the web service to join.
+In other words, the web service could have joined a better community, but, due to of lack of knowledge about the surrounding environment, joined the available community which was not the optimal choice.
+Since the community does enhance its utility, the web service could stay with that community, which results in a sub-optimal increase in web service's utility.
+In the following section the proposed model provides solutions that effectively address the aforementioned challenges.
+
+\section{The Model Components}\label{s:themodelcomponents}
+
+In this section, we discuss the parameters that we use in the rest of the paper. Then we present the task distribution and revenue model of our distributed web services communities.
+
+\subsection{Internal Features}\label{s:if}
+
+With a group of web services having identical or similar functionalities, QoS metrics provide nonfunctional characteristics for optimal candidate selection.
+Web service quality metrics were presented in \cite{Ardagna:2007:ASC:1263152.1263531,Menasce:2002:QIW:613357.613758,10.1109/ISSRE.2011.17}.
+We have adopted the most representative QoS properties of web services that highly influence the utility of web services.
+%We refer to a typical web service as ws_{i}.
+
+Let $C = \{ws_1,ws_2,..., ws_n\}$ be a community with $|n|$ web services. We define the following features for the group of web services based on their functional parameters:
+
+\begin{itemize}
+
+  \item \emph{Throughput $(Th_{C})$} is the rate at which a service can process requests.
+QoS measures can include the maximum throughput or a function that describes how throughput varies with load intensity.
+Throughput is a positive real number.
+For communities the expected throughput value of collaborating web services can be estimated as summation of throughputs of all the services inside:
+
+	\begin{equation}
+		 Th_{C} = \left\{
+			\begin{array}{l l}
+				Th_{w} & \quad \text{if $|C| = 1$}\\
+				\sum_{w \in C}{(Th_{w})} & \quad \text{if $|C| > 1$}
+			\end{array} \right.
+	\end{equation}
+
+	\item \emph{Availability $(A_{C})$} is the percentage of time that a service is operating.
+	The probability that the service operation is accessible.
+Availability is also a real number in the range $[0, 1]$.
+For communities the expected availability of collaborating web services considering they follow a parallel system can be estimated as:
+
+	\begin{equation}
+		A_{C} = \left\{
+			\begin{array}{l l}
+				A_{w} & \quad \text{if $|C| = 1$}\\
+				1-\prod_{w \in C}{(1-A_{w})} & \quad \text{if $|C| > 1$}
+			\end{array} \right.
+	\end{equation}
+
+	\item \emph{Execution Time $(Et_{C})$} is the time a service takes to respond to various types of requests.
+	%is the expected delay between the time instant when a request is sent and the time when the result is obtained.
+	Execution time is measured in milliseconds.
+Execution time can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests.
+This internal feature is a positive integer.
+For communities, the expected execution time of collaborating web services can be estimated as the execution time of the bottleneck service which is the service with the slowest execution time:
+
+	\begin{equation}
+		Et_{C} = \left\{
+			\begin{array}{l l}
+				Et_{w} & \quad \text{if $|C| = 1$}\\
+				max_{w \in C}{(Et_{w})} & \quad \text{if $|C| > 1$}
+			\end{array} \right.
+	\end{equation}
+
+	%\item \emph{Data Quality} The ability of a data collection to meet user requirements , defined as the proximity of a value v returned by web service to a value considered as correct.
+The measure of data quality is considered here as a real number in the range [0, 1], where 1 represents the most desirable score.
+\end{itemize}
+
+	We normalize the range of these features so that each feature contributes approximately proportionately to the final utility outcome value.
+We adopt the \emph{standardization} method.
+We subtract the \emph{mean} from each feature then we divide the values of each feature by its \emph{standard deviation}.
+
+%$HI = \overline{HI}$
+
+\subsection{External Features}\label{s:ef}
+
+The quantitative values of quality metrics need some benchmark values to represent their goodness.
+In other words, without some benchmark values it would be difficult for web services to identify their goals, and performance quality at any specific value of these metrics.
+Therefore, we have introduced two external features for assessing web services' estimate with regard to their standing among other web services.
+
+\begin{itemize}
+  \item \emph{External Parameter 1} $(exp_1)$.
+is an estimate of how close the web service's \emph{execution time} is to other web services.
+It is the difference between a web service's \emph{execution time} metric and the maximum value of execution time of all the other web services, about which the web service has information of them.
+The less value means web service has better execution time compared to other web services.
+	\begin{equation}\label{exp_1:f}
+		exp_1 = Et_{i} - Et_{max}
+	\end{equation}
+	\item \emph{External Parameter 2} $(exp_2)$ is a comparison of the web service's rate of performing tasks to other competing web services.
+It is the difference between a web service's \emph{throughput} metric and the maximum value of throughput of all the other web services,, about which the web service has information of them.
+The less value means web service has better throughput compared to other web services.
+	\begin{equation}\label{exp_2Lf}
+		exp_2 = Th_{max} - Th_{i}
+	\end{equation}
+\end{itemize}
+
+A community of web services is abstracted as a standard web service that provides services that share the same internal and external features mentioned for web services.
+Inside, they adopt different protocols to manage the community; however, other web services or end users can communicate with communities of web services, using standard protocols, and inner details will be encapsulated for their clients.
+
+\subsection{Task Distribution}
+
+Communities of web services usually employ an implementation of Contract-Net protocol for task distribution, in which services opt for incoming tasks, and receive the tasks for which they ask.
+However, in our model, our community members would try to distribute tasks based on their capabilities and the QoS parameters provided by the web services.
+We have used a slightly modified \emph{weighted fair queuing} method to distribute tasks among community members.
+The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{ws}$.
+In the \emph{weighted fair queuing} method, the input flow is multiplexed along different paths; however, in our case, if the rate of incoming tasks is less than the community's total throughput $(Th_{C})$, which is the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with a delay.
+%Thus, the amount of tasks performed by the community is $\sum_{ws}{Th_{ws}}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$.
+However, when the incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $|input Task Rate| \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) within the community.
+
+While distributing tasks, the community members can verify the performance, throughput and quality of service of tasks being performed by web services.
+The community can assess if those web services are capable of performing the number of tasks they advertised.
+If for any reason, there is a decline in the quality metric or throughput, the community can consider the new values as a benchmark for future performance calculations, and penalize the suspicious web services.
+This way, players will have incentive to truthfully disclose their actual capabilities in order to maximize profit from the community and to avoid being penalized.
+In addition, the system should be dynamic enough to detect and react to web services' quality metrics variation, as over time, web service metrics may degrade or improve, changes to which the community should adjust.
+% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities.
+Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.
+
+\subsection{Community Revenue}
+
+Communities and web services earn revenue by performing tasks.
+The total gain is a function of the quality of rate of tasks being performed.
+The utility of a collaborative group of services $U_{C}$ is the revenue of the community.
+Formula \ref{u_c_normal} is an estimation of the gain of the community.
+
+\begin{equation}\label{u_c_normal}
+U_{C} = \big((\alpha \times (A_{C} - Et_{C}) - \beta \times (exp1_{C} + exp2_{C})\big) \times Th_{C}
+\end{equation}
+
+The $\alpha$ and $\beta$ values are internal and external weight coefficients.
+Execution time and external parameters are better when they have smaller values hence the negative coefficient for them.
+The result is then multiplied to the throughput value $Th_{C}$, since communities are performing tasks with $Th_{C}$ rate.
+
+The estimation can be improved, especially in cases where the input task rate is high and services are experiencing high task loads.
+The \emph{weighted fair queuing} method of task distribution would distribute tasks based on the individual throughput $(Th_{w})$ value of services within community.
+The services with higher throughput will affect the overall utility of the community more because they would take on proportionately more tasks.
+
+\begin{equation}\label{u_c_load}
+\begin{split}
+U_{C} = \sum_{ws \in C}&\bigg(\big(\alpha \times (A_{ws} - Et_{ws}) \\
+        & - \beta \times (exp1_{ws} + exp2_{ws})\big) \times Th_{ws}\bigg)
+\end{split}
+\end{equation}
+
+\section{The Decision Making Mechanism}\label{s:model}
+
+In this section, we describe our data extraction process and the methodology used to equip web services with a decision making mechanism.
+In this methodology, we first present the data extraction and engineering process and then we evaluate the decision making mechanism for web services in community settings.
+Figure \ref{fig_steps} summarizes the steps performed in DDM from the input data to generation of decision making profiles for web services.
+
+\begin{figure}%[!t]
+\centerline{\includegraphics[width=1.75in]{figures/steps.eps}}
+\caption{A summary of DDM decision profile generation steps}
+\label{fig_steps}
+\end{figure}
+
+\subsection{Data Extraction and Solution Engineering}\label{ss:learningdata}
+
+\subsubsection{Input Web Services Data}\label{sss:webservices}
+
+%We used a data set extracted from running web services. In this data set,
+Each web service is associated with a number of features that reflect its functionality.
+These web services operate in an online environment and are continuously assigned tasks to handle.
+Sometimes, they pass tasks around, distributing sub-tasks among themselves and handling tasks in a collaborative effort.
+To engage in communities, we add additional features that reflect web services' utility as a result of joining other web services to form a community.
+The additional features are computed based on two assumptions that we adopt for a community to be formed.
+Our raw data set provides us with 64 different time slots of extracted features for each web service.
+Using this data we can build a synthetic data set that contains features of a large number of web services in a sequence of time.
+Therefore, we train a learning model that adopts the trend of joining a community and use the model to predict/find the appropriate community for other web services.
+To train our model, we build a decision tree as a benchmark for our decision making mechanism.
+The decision tree is built by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services.
+As a result, we are able to classify web services as either single or joined and propose the communities that are best fitted to the web services' requirements.
+
+\subsubsection{Filtered Data}\label{sss:filtereddata}
+
+We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}.
+The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{http://www.wsdream.net/}.
+In this data set, each web service is associated with a number of features that reflect its functionality.
+By summarizing the data provided for each web service over different time slots, we have acquired three quality features for each individual web service.
+Their quality features are the three internal features introduced in Section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time}.
+%To engage in communities, we add two additional external features that reflect web services estimation of its quality metrics compared to other web services.
+Therefore, we have generated an array of web services with three distinct features.
+
+\begin{figure}%[!t]
+\centerline{\includegraphics[width=3.25in]{figures/cfvs.eps}}
+\caption{Communities with different properties of web services actively looking for other communities to collaborate with, they send collaboration requests to communities they find the collabration  increasing the gain}
+\label{fig_community}
+\end{figure}
+
+Now, we want to generate a set of feature vectors representing the communities of web services for training purposes.
+For communities, we add two additional external features, as discussed in Section \ref{s:ef} that reflect the community's estimation of its quality metrics compared to other web services.
+Therefore, we formulate a \emph{Community Feature Vector (CFV)} as $CFV_{<C>} = \{f_1,...f_5\}$ having a community of $k$ web services.
+$C = {ws_1,...ws_k}$.
+The features $f_1$ through $f_5$ represent the \emph{execution time}, \emph{throughput}, \emph{availability} and the \emph{external parameters 1 and 2} correspondingly.
+A set of communities, with their feature vectors and utilities evaluated, provides our algorithm with a raw training data set.
+We call this set of communities the \emph{template vector}, and the set of feature vectors associated with the \emph{template vector} is referred to as the \emph{community feature vector set (CFVS)}.
+Figure \ref{fig_community} depicts communities looking to form collaborate communities and join other communities in order to improve their utility gain.
+
+\subsubsection{Feature Engineering}\label{sss:feng}
+Let $CFVS = \{C_1, C_2,..., C_N\}$ be the community feature vector set with $N$ communities.
+Based on the $CFVS$ set, we create an $|N \times N|$ gain matrix for $t$ different time slots.
+Each entry of $gain_{n,m}^{t}$corresponds to a utility gain of web services in $C_n$, when $C_n$ joins $C_m$, based on community and web service data available for time $t$.
+All of these values have to be evaluated by implementing the community with members of $ws_i \in C_n$ and $ws_j \in C_m$ and evaluating its utility (see Equation \ref{u_c_load}).
+Therefore $gain_{n,m}^{t} = U_{C_n \cup C_m}^{t} - U_{C_{n}}^{t}$.
+Evaluating the utility gain for all entries of the $gain$ matrix can be a costly process with a very big number of $N$, size of the feature vector $|N|$ should be chosen carefully.
+
+\begin{table*}[ht]
+\caption{An example of $gain$ matrix for 3 different communities and their combinations} % title of Table
+\centering % used for centering table
+{\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{c|c c c c c c} % centered columns (4 columns)
+\hline\hline %inserts double horizontal lines
+ & \textless348\textgreater & \textless1934\textgreater & \textless2117\textgreater & \textless348, 1934\textgreater & \textless1934, 2117\textgreater & \textless348, 1934, 2117\textgreater \\ [0.5ex] % inserts table
+%heading
+\hline % inserts single horizontal line
+\textless348\textgreater & - & 0.282708 & 1.027081 & 0.282708 & 18.027081 & 18.027081 \\
+\textless1934\textgreater & -2.637483 & - & 6.969072 & -2.637483 & 5.509583 & 4.387725 \\
+\textless2117\textgreater & 5.027081 & 2.969072 & - & 5.509583 & 2.969072 & 5.509583 \\
+\textless348, 1934\textgreater & 0.0 & 0.0 & -3.851432 & - & -3.851432 & -3.851432 \\
+\textless1934, 2117\textgreater & 2.969072 & 0.0 & 0.0 & 2.969072 & - & 2.969072 \\
+\textless348, 1934, 2117\textgreater & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & - \\ [1ex] % [1ex] adds vertical space
+\hline %inserts single line
+\end{tabular}
+}
+\label{table:nonlin} % is used to refer this table in the text
+\end{table*}
+
+Now, we let our set of communities in the $CFVS$ set, within $|T|$ time frame iterations, choose the the best communities to join.
+Each community is provided with the corresponding row of data from the $gain$ matrix.
+Basically, $C_i$ is provided with the data in row $i$ of matrix $gain_{N,N}$, which is all of the possible utility values it can gain by joining different communities.
+By ordering the list, each community is utilized with an ordered set of preferences over other communities it likes to join.
+We define $>_{i}^t$ as the preference order of community $i$ at time $t$.
+
+Let $P_{C_i}^t = \{C_1 >_{i}^t C_2 >_{i}^t ....
+>_{i}^t C_n\}$ be an ordered set of preferences for community $C_i$ at time $t$.
+Based on this ordered set, we define $K^t(C_i, k)$ as a set of the $k$ most preferred communities of community $i$ at time $t$.
+%\subsubsection{feature vector generation}\label{sss:fvg}
+\begin{equation}\label{h_t_pref_top}
+\begin{split}				
+K^t(C_i, k) = &\Big\{C_x | C_x >_{i}^t C_y; \forall C_y \in CFVS\ \\
+				      &\wedge C_y \notin \{K^t(i, 1),K^t(i, 2),...,K^t(i, k-1)\} \Big\}				
+\end{split}
+\end{equation}
+Based on $K^t(C_i, k)$, we define a set of communities for $C_i$ in which they are the k most preferred communities for community $i$ and also community $i$ belongs to the k most preferred communities out of all of the communities in set $K^t(C_i, k)$.
+This basically implies the preference is both-sided.
+\begin{equation}\label{l_t_top_both}
+\begin{split}	
+L^t(C_i,k) = &\Big\{C_j | C_j \in K^t(C_i, k) \\
+             &\wedge C_i \in \bigcup_{C_x \in K^t(C_j, k)}K^t(C_x, k)\Big\}
+\end{split}
+\end{equation}
+
+Table \ref{table:nonlin} illustrates an example of a $gain$ matrix for 3 different communities and their combinations.
+Each row shows the gain the community can achieve by collaborating with other 5 communities.
+In this example for community $\textless 348 \textgreater$ we have: \\
+$K(\textless 348 \textgreater, 1) = \{\textless1934, 2117\textgreater\}$ and \\
+$K(\textless 348 \textgreater, 2) = \{\textless1934, 2117\textgreater, \textless1934\textgreater\}$ \\
+Since $\textless 348 \textgreater$ is best preferred community of $\textless 1934, 2117 \textgreater$ therefore $L(\textless 348 \textgreater, 1)$ is not empty and contains the community $\textless1934, 2117\textgreater$.
+
+Using the $gain$ matrix and the mentioned preference ordering relations, we are able to build a decision tree where the list of possible communities to join and their expected utilities are set.
+% as well as the joined events that took place in different time slots.
+In addition to best choices, web services have access to other ordered choices and can look for the second best or third best if their first try is rejected by the target community.
+The consequences of each try level is analyzed in more detail in the following section, in which we launch experiments and investigate the effectiveness of the use of a decision tree with different decision layers in joining other communities and enhancing the overall utility.
+
+\subsection{Decision Profile Generation}\label{ss:learningmodel}
+
+Our goal is to create a decision making profile for each community in the $CFVS$ set.
+We are creating an environment where they can experience the outcomes of different strategies.
+The result will be a decision tree of the feasible and utility increasing moves over time.
+
+We let communities pick the best communities for maximizing their utilities over different time frames.
+At time $t = 1$, we let each community in the $CFVS$ set choose the best community, which is a single community in set $C_j = K^t(C_i, 1)$.
+If community $C_j$ also has the highest preference to join $C_i$ meaning the $L^t(C_i, k=1)$ set is not empty, they would join together.
+Having set $k = 1$ is a very strict and hardly satisfiable condition.
+In order to relax the requirement, the value of $k$ is being increased by a rate $r$ proportional to time slot $t$.
+Basically, $k = 1 + |r \times t|$.
+On early steps of simulation web services and communities are more strict but as time goes on, we let them choose second and then third best options too.
+However, increasing $k$ quickly increases the time complexity of $K^t(C_i, k)$ by $O(k^2 \times n.log(n))$.
+
+When communities $C_i$ and $C_j$ are in each other's top $k$ preference set, their combination is added to the list of possible communities that can join others at time $t+1$.
+Also, for each community $C_i$ in our initial $CFVS$ set, we maintain a tree with the community $C_i$ as its root.
+Its children are all of the communities that $C_i$ decided to join.
+As the scenario progresses over time, the merged communities may decide to join other communities.
+When community $C_i$ and $C_j$ decide to join each other and create community $C_k$, the new community $C_k$ will be added as a child to both $C_i$ and $C_j$ nodes.
+At the end of the process, each community is utilized with a tree of set of possible combination of communities it can join.
+Algorithm \ref{algo:dectree} illustrates the DDM tree creation procedure as pseudo-code.
+
+Having created $|n|$ trees, for each community $C_i$, our communities are utilized with the different possible paths they can take to maximize their utilities.
+Using a distance function, communities and web services can utilize these results and find the $C_i$ that closely resembles their parameters.
+They will be utilized with a tree that has the strategies the community can use to join our communities which will be best possible path to take and communities to join while most likely being accepted by other communities since its a two sided preference.
+The algorithm below describes the tree creation process.
+
+\begin{algorithm}
+\DontPrintSemicolon
+\KwIn{$\langle r, gain^t_{n,n}, CFVS \rangle$ learning rate $r$, $|N \times N \times T|$ gain matrix, community feature vector}
+\KwOut{A set of \emph{root} nodes of the decision trees}
+$k \gets 1$\;
+$nodes[N] \gets$ initialize $N$ tree nodes representing each community in CFVS\;
+\For{$t \gets 1$ \textbf{to} $T$} {
+	$k \gets 1 + round (r \times t)$\;
+  \For{all $C_i \in CFVS$} {
+	  \For{all $C_j \in L^t(C_i, k)$} {
+      % The "l" before the If makes it so it does not expand to a second line
+      \If{$C_i \in L^t(C_j, k)$}{
+        $C_k \gets C_i \cup C_j$\;
+				add $C_k$ to $CFVS$ set\;
+				initiate $node_k$, representing $C_k$\;
+				$nodes_i.addChild (node_k)$\;
+				$nodes_j.addChild (node_k)$\;
+      }
+%      \Else{
+%        $j \gets j + 1$\;
+%      }			
+		}
+  }
+%  $i \gets i + 1$\;
+}
+\Return{nodes}\;
+\caption{{\sc DDM Decision Tree Algorithm}}
+\label{algo:dectree}
+\end{algorithm}
+
+\textbf{Complexity.} Here we analyze the computational complexity of the DDM decision tree creation algorithm on each time iteration $t$.
+Computing top $k$ preferred communities for $C_i$ in $L^t(C_i, k)$ requires an $O(n.log(n))$ sort time.
+$C_i$ has a result set of size $|k|$, and for each of those $k$ communities we need to check against their $k$ top preferred communities.
+Considering we already have the list sorted, line 6 in algorithm runs $O(k \times n.log(n))$ times.
+Doing this search for all communities in $|CFVS|$ set $n$ times (line 5), the overall order of complexity of the algorithm in regards with $n$ and $k$ is: $O(k^2 \times n^2.log(n))$.
+
+\section{Experiments}\label{s:experiments}
+We implemented DDM in Java\footnote{Source code of implementation and data is available at: \emph{https://github.com/Marooned202/DDM}}.
+We have extracted the set of features for 4532 web services in 64 different time slots through a data set provided by \cite{10.1109/ISSRE.2011.17}.
+By choosing 86 web services out of these sets and choosing a subset of all possible combinations of sizes 2, 3, and 4 of these 86 web services, we have chosen 10,000 communities and evaluated the feature vectors and utilities they can have in 64 different time slots.
+This provides us with the initial training feature set of size $|CFVS| = 10,000$ communities.
+Based on Equation \ref{u_c_load} the utility of these communities are estimated, and the gain matrix $|10000 \times~ 10000|$ of all possible ways of merging these 10,000 communities, is generated\footnote {The template vector and gain matrix generated are available at \emph{https://github.com/Marooned202/DDM/tree/master/wsds/data/run}}, and each community has the ordered preference among other communities known in the set.
+
+We let communities and web services adopt their strategies based on our $DDM$ decision making mechanism.
+Based on the decisions adopted, each community will generate a decision tree profile.
+We let DDM run four times with different $r$ rates of 0.05, 0.07, 0.10 and 0.20.
+With the slow rate of $r = 0.05$, we increase $k$ in Equation \ref{u_c_normal} for every 20 time frames, which will happen only three times in our 64-step experiment.
+In the case of $r = 0.20$, k increases much faster, at a rate of once every 5 time frames, which increases the complexity of the $L^t(C_i,k)$ search for each community in the $CFVS$ set.
+
+Table \ref{table:valueandgain} depicts the average utility gain value of the communities in each of the four runs.
+The utility gain is the increase of utility the communities gain by cooperating and joining other communities.
+The utility gain ratio is the ratio of their final utility over initial utility.
+Comparing the different search rates, we can see increasing $r$ to value of $0.10$ results in significant performance boost, however the higher rates of $r$ are not increasing the chance of finding better collaborative groups for our communities.
+
+\begin{table}[ht]
+\caption{Utility gain of web services after making collaborative groups based on DDM algorithm with different $r$ rates} % title of Table
+\centering % used for centering table
+{\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{c|c|c} % centered columns (4 columns)
+\hline\hline %inserts double horizontal lines
+Search Rate $r$ & Utility Gain Value & Utility Gain Ratio \\ [0.5ex] % inserts table
+%heading
+\hline % inserts single horizontal line
+r=0.20 & 176.1499 & 6.9690 \\
+r=0.10 & 174.6541 & 6.9182 \\
+r=0.07 & 159.9462 & 6.2834 \\
+r=0.05 & 136.0768 & 5.1032 \\ [1ex] % [1ex] adds vertical space
+\hline %inserts single line
+\end{tabular}
+}
+\label{table:valueandgain} % is used to refer this table in the text
+\end{table}
+
+%\begin{figure}%[!t]
+%\centering
+%\includegraphics[width=3.5in]{figures/utility_gain_r.eps}
+%\caption{DDM Utility Gain Value}
+%\label{utility_gain_value}
+%\end{figure}
+%
+%\begin{figure}%[!t]
+%\centering
+%\includegraphics[width=3.5in]{figures/utility_ratio_r.eps}
+%\caption{DDM Utility Gain Ratio}
+%\label{utility_gain_ratio}
+%\end{figure}
+
+We utilize the same communities and web services with a simple rational decision making mechanism, in which communities will choose to join a community if it increases utility by any amount.
+We call it the $rational$ method, in the sense that it is just a rational method and is not aiming to be optimal.
+We chose 10 random web services and compared the results with web services which adopted our DDM model.
+Figure \ref{utility_gain_mlisa_and_rational} shows the comparison of the end result of utility gain values.
+In 18 out of 40 tries, \emph{rational} agents were not able to improve their utility at all because the communities they chose rejected their request, most likely because they would not have increased the utility of the other communities if they had joined them.
+The results show that a long-term strategic decision mechanism is needed to satisfy all of the services within communities.
+Figure \ref{utility_gain_mlisa_and_rational_ratio} shows the same results in terms of ratio of utility gain.
+
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/utility_gain.eps}
+\caption{Utility Gain DDM and Rational}
+\label{utility_gain_mlisa_and_rational}
+\end{figure}
+
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/utility_ratio.eps}
+\caption{Ratio of Utility Gain DDM and Rational}
+\label{utility_gain_mlisa_and_rational_ratio}
+\end{figure}
+
+Now, we evaluate the performance of the decision profiles generated based on our data set for other communities.% which are not included in the decision tree creation process.
+We create one thousand communities from the web services in the data set that were not involved in the decision model creation process.
+We define a distance function that measures the difference between basic features of communities, which measures the similarity of communities.
+
+\begin{equation}\label{distance_c}
+\begin{split}
+distance (C_1, C_2) & = |Th_{C_1} - Th_{C_2}| \\
+                    & + |A_{C_1} - A_{C_2}| + |Et_{C_1} - Et_{C_2}|
+\end{split}
+\end{equation}
+
+Now, each community tries to find the closest community within the trained $CFVS$ set.
+Following its decision profile, the community can get a good estimate of the possible strategic decisions it can adopt.
+Basically, the trained profiles benefit the new web services in two ways.
+First, they provide the communities with a set of viable communities to join.
+Second, they provide an estimation of long-term utility gain for each available decision.
+In this experiment, we let communities follow the best decision within the decision tree provided to the them.
+
+\begin{table}[ht]
+\caption{Number of communities that misses the optimal decision, out of 1,000 communities} % title of Table
+\centering % used for centering table
+\begin{tabular}{|c|c|} % centered columns (4 columns)
+\hline %inserts double horizontal lines
+ Method&Miss \\ [0.5ex] % inserts table
+%heading
+\hline % inserts single horizontal line
+ DDM r=0.05& 375 \\ % inserting body of the table
+ DDM r=0.07& 137 \\
+ DDM r=0.10& 6 \\
+ DDM r=0.20& 6 \\
+Rational Method& 717 \\
+Greedy Method& 828 \\ [1ex] % [1ex] adds vertical space
+\hline %inserts single line
+\end{tabular}
+\label{fail_rate} % is used to refer this table in the text
+\end{table}
+
+In order to evaluate the performance of the mechanism, we used \emph{Receiver Operating Characteristic (ROC) curve}, which is a graphical plot illustrating the true negative rate against the false positive rate at various threshold settings in classifier systems.
+In order to classify our communities' selection strategies correctly, for each community, we evaluated the training process by replacing the community in the set with the closest one, from which it gets the strategy profile.
+If the actions are the same and the same utility levels are gained, we classify the decision as correct.
+Otherwise, it is classified as a wrong decision.
+\emph{AUC}, the area under the \emph{ROC curve}, is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one, and the higher number reflects better performance from the better solution.
+Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of the DDM decision making mechanism.
+We compare our method with two other methods.
+The \emph{rational} method is based on the assumption that communities, as rational agents, join a community that increases their utility.
+The \emph{greedy} method only looks up the available list of communities and simply joins the community that maximizes its utility without considering any long-term strategy or other communities' acceptance scenarios, its an greedy algorithm and chooses a locally optimal choice.
+Therefore we use these two methods as our benchmark:
+
+\begin{itemize}
+  \item {\bf Rational Method:} Communities would send a join request to any available community, which will increase the utility.
+The other community would accept the join offer if the utility gain is positive as well.
+	\item {\bf Greedy Method:} Communities do a linear search among all the available communities and send a join request to the community which results in maximum utility, The other community would accept the join offer if the utility gain is positive and the utility gain does not need to be the maximum for the community recieving the join request.
+\end{itemize}
+
+Figure \ref{roc5} compares the results for all methods.
+The two other methods have very high failure rates compared to our method.
+Table \ref{fail_rate} illustrates the number of communities that failed to find the optimal collaboration group.
+The results support the need for a long-term training model in a successful decision making process.
+
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/roc.eps}
+\caption{RoC Curve}
+\label{roc5}
+\end{figure}
+Now, we evaluate the system-specific results from users' and communities' perspectives.
+By distributing tasks among the communities over these time frames, we evaluate the revenue for each community.
+Figure \ref{stats1} shows the overall revenue gain of communities using our method.
+Figure \ref{stats2} shows the momentarily revenue gain for each community in each time slot compared to the previous time.
+These results show that the run with the higher learning rate of $r=0.20$ starts discovering better communities to join much earlier.
+The runs with slow rates seem to find some communities to join initially, but then they slow down until later, when they start discovering new communities to join.
+
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/stats1.eps}
+\caption{Overall Utility of all communities}
+\label{stats1}
+\end{figure}
+
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/stats2.eps}
+\caption{Utility Gain on time}
+\label{stats2}
+\end{figure}
+
+Figure \ref{stats3} depicts the average community size over time, which essentially represents the number of new communities being formed.
+Once again, these results show that the runs with higher search rates tend to find appropriate communities to join faster.
+
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/stats3.eps}
+\caption{Average Community Size}
+\label{stats3}
+\end{figure}
+
+\section{Related Work}\label{s:related_work}
+
+In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
+defined communities as \emph{Service Containers} that aggregate
+substitutable web services providing a common functionality (same
+set of operations). They abstracted \emph{Service Containers} as
+web services that are created, advertised, discovered and invoked
+just as elementary web services. The \emph{Container} is
+considered as a manager that is responsible for web service
+selection upon receiving a request on run-time. The authors have
+proposed a scoring service based on non-functional requirements of
+the request and web service capabilities to dynamically chose the
+web service to perform the requested task. A similar concept was
+proposed by Maamar et al. in
+\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
+web service communities as a collection of web services with a
+common functionality but different QoS properties. A community
+manager, upon receiving a request, delegates the request to one of
+its current members. The choice is based on the performance
+history and quality metrics of each web service. The authors have
+proposed an efficient global web service selection algorithm in
+order to approach quality constraints and preferences for
+composite services which require aggregation of different types of
+services to satisfy the user.
+
+Benslimane et al. \cite{Liris-2770} have proposed a multi-layer
+approach grouping similar Web services into communities and having
+an interface implemented as an abstract web service for accessing
+the community on top of the community layer. The interactions
+between composite, management and community layers and the
+bindings are performed by a generic driver called Open Software
+Connectivity (OSC).
+
+In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
+service communities with centralized access across distributed web
+services. They have proposed a framework for web service
+management, query resolution among communities and a query caching
+mechanism executed by the manager to improve the performance of
+query resolution process among many distributed communities. The
+key idea is to cache previous computed results for answering
+future queries.
+
+Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
+then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
+proposed an architecture utilizing \emph{Contract-Net} protocol
+for engineering task distribution within communities of web
+services. The protocol is centrally executed by the community
+manager. This architecture has been further developed in
+\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
+conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
+roles have been distinguished for community members: masters and
+slaves. Master web services and community managers that lead
+communities and are responsible for membership management. They
+can invite and convince slave web services to join the community,
+and attract new slave web services to their communities by
+awarding them better payoff. Moreover, they can eject some slave
+members from the community to improve its overall reputation if
+these members are misbehaving or cannot provide the promised QoS.
+
+In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
+developed a community as a ``cluster'' that groups Web services
+based on a specific area of interest. All web services in a given
+community share the same functionality. These communities are
+created by \emph{third party community providers} which use the
+\emph{community ontology} as a template and define a set of
+operations that all web services within a community should
+provide. Using semantic analysis on web service operations, web
+services either find and join a community with similar
+functionality or create a new operation description for a new
+community. The authors have described the concept of
+\emph{community agents} associated to \emph{community providers}.
+A community agent is responsible, among other things, of the
+registration of services with the community. An example of a
+community that provides health care services to senior citizens
+has been used. In this example, a governmental entity is needed to
+check the health care standards used by the members before
+authorizing them to be part of the community. Such a central
+entity is represented by the community agent. Thus, community
+agents are playing the role of community managers. In a close work
+\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
+global planning selection algorithm and a delegation algorithm to
+be run when a request to execute an operation is received by the
+community. This needs a central entity to run those algorithms.
+Such entity plays the same role as the community coordinator or
+manager.
+
+Most of the recent work on communities of services are either
+user-centric and focus on user satisfaction
+\cite{Chun02user-centricperformance} or system-centric and focus
+on the whole system throughput, performance and utilization. There
+are many contributions in distributed, grid, cluster and cloud
+services which are system-centric. However, in real world
+environments and applications, both users and service providers
+are self-interested agents, aiming to maximize their own profit.
+In those environments, both parties (users and services) will
+collaborate as long as they are getting more benefits and payoff.
+
+In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
+DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
+mechanisms to help users and services maximize their gain. A
+two-player non-cooperative game between web services and community
+master was introduced in
+\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this game-theoretic
+model, the strategies available to a web service when facing a new
+community are requesting to join the community, accepting the
+master's invitation to join the community, or refusing the
+invitation to join. The set of strategies for communities are
+inviting the web service or refusing the web service's join
+request. Based on their capacity, market share and reputation, the
+two players have different sets of utilities over the strategy
+profiles of the game. The main limits of this game model are: 1)
+its consideration of only three quality parameters, while the
+other factors are simply ignored; and 2) the non-consideration of
+the web services already residing within the community. The game
+is only between the community master and the new web service, and
+the inputs from all the other members and their influence on the
+master's decision are simply ignored. The consideration of those
+inputs and this influence factor is a significant issue as
+existing web services can lose utility or payoff because of the
+new member, which can result in an unhealthy and unstable group.
+The problem comes from the fact that the existing members should
+collaborate with the new web services, so probably their
+performance as a group can suffer. Existing members may even
+deviate and try to join other communities if they are unsatisfied.
+Those considerations of forming stable and efficient coalitions
+are the main contributions of our paper.
+
+In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
+for selecting web services has been proposed. In this approach,
+the authors proposed a web service selection process that the
+community masters can use. The approach considers the efficiency
+of all the three involved parties, namely users, web services and
+communities. In this work, it is shown how the gains of these
+parties are coupled together using a linear optimization process.
+However, the optimization problem in this solution tends to
+optimize some parameters considering all web services regardless
+of their efficiency and contribution to the community's welfare.
+Moreover, there are no clear thresholds for accepting or rejecting
+new web services. The solution of the optimization problem could,
+for instance, suggest web services already residing within the
+community to increase or decrease their capacity to cover up the
+weakness of other parties in the system. However, a high
+performing web service could deviate anytime it finds itself
+unsatisfied within the community instead of adjusting its service
+parameters.
+
+In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
+autonomous web services based on coalitional game theory has been
+introduced. The authors have proposed an interesting algorithm to
+reach individually stable coalition partition for web services in
+order to maximize their efficiency. The communities choose new web
+services on the promise that it would benefit the community
+without decreasing any other web service's income. In the proposed
+model, the worth of community is evaluated with high emphasis on
+the availability metric and considering price and cost values
+only. The community structure is based on a coordination chain,
+where a web service is considered as a \emph{primary} web service
+and the community task-distribution method initially invokes the
+primary web service and only if the primary web service is
+unavailable, the method invokes the next backup web services as
+they are ordered in the coordination chain. We believe that this
+coordination chain limits the cooperation power as it introduces a
+sort of hierarchy. However, in pure and open cooperative models,
+such as the one we propose in this paper, active cooperation
+activities engaging simultaneously many agents so that they can
+perform the tasks more efficiently are being used. Moreover, if
+the availability is high, which is the case nowadays with the
+recent advancements in cloud and hardware infrastructures, the
+backup web services will end-up having a very low chance of
+getting jobs, especially the ones further in the chain. This will
+results in a considerable waste of web services capabilities.
+
+All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process.
+So basically These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.
+We address this issue by introducing DDM a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another.
+After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics.
+Therefore web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
+In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary}\label{sec:conclusion-cha4}
+
+In this paper, we proposed a training model for the problem of membership management of communities of web services.
+Using the traning model we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves.
+This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available.
+The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices.
+The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.
+The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.
+
+Our plan for future work is to advance learning process on the training set that we provided in our work.
+SVN machine learning algorithm are suitable in classification of our training data set, to better classify correct or wrong decisions based on long-term utility gains, as data set outputs.
+This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.

### 2015-05-10 thesis/thesis/chap4/chap4.tex
changes

@@
 
-In this section, the objective is to investigate the effectiveness of the proposed strategic system.
+In this section, we provide an empirical analysis over the
+theoretical results regarding the characteristics of intelligent
+service agents hosted in different communities of services. In the
+implemented system, we simulate the behaviors of service consumers
+as request generators, service agents as service providers, and
+master agents as community representatives. 
+%These entities are developed with respect to what is explained in Section \ref{s4:Preliminaries}. 
+In this section, the objective is to
+investigate the effectiveness of the proposed strategic system on
+intelligent services' overall budget and also the average quality
+and quantity of tasks performed by the community of services,
+which directly affects user satisfaction.
+%Before conducting the simulation, the
+%expected behavior of our model is to enhance the budget of web
+%services when using our proposed strategic interacting system.
+%Although this result is promising, we would like to investigate
+%the effectiveness of the proposed strategic system on intelligent
+%web services' overall budget compared to the best case. Moreover,
+To verify these objectives, we study the overall performance of
+the community hosting the reasoning-empowered services compared to
+the ones hosting stochastic and purely competitive services. By
+stochastic services, we mean services that adopt at each moment
+competitive or cooperative strategies in an equally but random
+way. By equally, we mean the choices are fairly divided between
+the two strategies.
+
+The simulation application is written in
+\textit{C\#} using \textit{Visual Studio}.
+We performed the implementation on a single Intel Xeon X3450 machine with 6GBs of memory.
+Web services were modeled as a \emph{class} and using \emph{Await} and \emph{Async} models we initiated many web services, each running as a thread.
+We implemented XML based messaging system (like SOAP) with request parameters and a list of XML based responses.
+The request contains the flight dates, the origin and destination, type of tickets, and number of guests.
+The response contains different flights with different companies, prices, timing, etc.
+A pool of services are initialized with values taken from a real dataset that includes $2507$ real services functioning on the web.
+The dataset records the QoS values of $9$ parameters including \textit{availability},
+\textit{throughput}, and \textit{reliability} \cite{Almasri}.
+
 We start our discussions with cumulative budget comparison

### 2015-06-01 papers/webservice-coalition-learning-omar-template/elsarticle-template-num.tex
changes
added notes

@@
 \begin{figure}%[!t]
-\centerline{\includegraphics[width=1.75in]{figures/steps.eps}}
+\centerline{\includegraphics[width=6.0in]{figures/steps.eps}}
 \caption{A summary of DDM decision profile generation steps}
@@
 The result will be a decision tree of the feasible and utility increasing moves over time.
+The root of decision tree represents a community in the $CFVS$ set, and the other nodes represents the result of the parent nodes' action of joining other communities and the expected utility of the community.
+Therefore, each node represents a community with a set of feature values of the parent node's community joining some other community, and an expected utility outcome of the newly formed community.
 

### 2015-06-12 papers/webservice-coalition-learning-june-2015/elsarticle-template-num.tex
added new version of paper

--- 2015-05-09 papers/webservice-coalition-learning-omar-template/elsarticle-template-num.tex
@@
-\documentclass[11pt,onecolumn]{IEEETran}
+\documentclass[11pt,onecolumn]{IEEEtran}
+
+\newtheorem{theorem}{Theorem}
 
@@
 %% `Elsevier LaTeX' style
-\bibliographystyle{elsarticle-num}
+%\bibliographystyle{elsarticle-num}
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 services and make them cooperate within their communities.
-However, existing community models mostly focus on short term goals.
+However, existing community models mostly focus on short-term utility gain.
 Moreover, these models generally suffer from high computational complexity, which makes decision making about community formation in real-time extremely hard, time consuming, and even impossible in some complex cases.
@@
 Our model helps 1) communities of web services efficiently find the appropriate web service to invite as new member; and 2) single web services find best communities to join.
-After being trained, web services get to compute expectations as utilities they would gain if cooperating with communities of different characteristics.
-In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated by a web service.
+After being trained, web services get to compute expectations as utilities they would gain if they cooperate with communities of different characteristics.
+In contrast, communities can take the training into account and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated by a web service.
 In general, DDM equips web services with efficient methods of foreseeing how their choices of actions would impact their short-term and long-term goals, therefore opting for better decisions.
-We performed experiments using real data from 142 users on 4,532 web services on 64 different time slots.
-The experimental results, show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-optimal decision making mechanisms.
+We performed experiments using real data from 142 users on 4,532 web services during 64 different time slots.
+The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-optimal decision making mechanisms.
 \end{abstract}
 \begin{IEEEkeywords}
-Web services; Community of services; Distributed Decision Making;
+Web services; Community of services; Distributed decision making;
 \end{IEEEkeywords}
@@
 The increasing reliance on online service providers has significantly influenced the way web services are engineered.
-Therefore, given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue.
-One practical solution towards delivering high quality services is utilizing intelligent decision making agents.
-These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users\cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Demirkan2013412, journals/tsc/ZhengZYB13, Josang:2007:STR:1225318.1225716}.
+Given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue.
+One practical solution towards delivering such quality services is utilizing intelligent decision making agents.
+These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users \cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Demirkan2013412, journals/tsc/ZhengZYB13, Josang:2007:STR:1225318.1225716}.
 However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided.
-Recent developments have attempted to shift web services from passive models, consisting of individual components, to models made up of autonomous and group-based components that share common goals.
-In group-based models, interaction, composition, and cooperation are the key challenges \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13} that directly impact the group's overall performance in achieving common goals.
-To that end, we see the emergence of web service \emph{communities}, which consist of grouping of services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}.
-A \emph{community} of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.
-
-Web Service communities have the advantages of facilitating web service discovery and providing better quality of service compared to individual components.
+Recent developments have attempted to shift web services from simple models, consisting of individual components, to models made up of autonomous and group-based components that share common goals.
+In group-based models, interaction, composition, and cooperation are the key challenges that directly impact the group's overall performance in achieving common goals \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13}.
+To that end, we see the emergence of web service \emph{communities}, which consist of grouping services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic}.
+A community of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.
+
+Web Service communities have the advantages of facilitating web service discovery and providing better quality of service compared to individual services.
 Communities act as abstract web services, communicating with external entities via the same standard protocols that a normal web service employs.
-But, they regulate the service process via sophisticated internal communication protocols, thereby providing services based on the combined work of a number of web services.
-The downside to communities is the complexity of management involved in finding and inviting individual web services and managing the overall quality of the combined work of several web services.
+The difference is that communities regulate the service process via sophisticated internal communication protocols, thereby providing services based on the combined efforts of a number of web services.
+The downside to communities is the complexity of management involved in finding and inviting adequate individual services and managing the overall quality of the combined work of several services.
 % because although they have similar functionality, they have different attitudes. 
-When interacting with communities of web services, users send their requests to the coordinators of the community, which play the role of community representative or access point.
+When interacting with a community of web services, users send their requests to the coordinator of the community, which plays the role of community representative or access point.
 The community coordinator is responsible of receiving tasks and delivering services.
-Moreover, as community representative, it verifies the credentials of new web services before accepting them into the community and kicks web services that could harm the value of the community.
-
-\textbf{Challenge and Problem Statement.} In recent work, communities of web services have been proposed in order to facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities\cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}.
-However,  two important challenges are to be addressed: 1) choice of best web services during community development from the community perspective and 2) choice of the best community to join from the web service perspective.
-The advocated solutions \cite{conf/webist/MaamarLBTS07, 10.1109/ARES.2008.7, journals/soca/XuYLZB11, 10.1109/TSC.2012.12, managing-hela-jalel, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:conf/IEEEscc/LimTMB12} have attempted to address these research problems.
-However the solutions have not addressed these two challenging issues:
+Moreover, as community representative, it verifies the credentials of new web services before accepting them into the community and kicks services that could harm the value of the community.
+
+\textbf{Challenges and Problem Statement.} In recent work, communities of web services have been proposed in order to facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities \cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic}.
+However,  two important challenges are to be addressed: 1) choice of the best web services during community development from the community perspective; and 2) choice of the best community to join from the web service perspective.
+The advocated solutions  \cite{10.1109/ARES.2008.7, conf/webist/MaamarLBTS07, journals/soca/XuYLZB11, 10.1109/TSC.2012.12, managing-hela-jalel, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:conf/IEEEscc/LimTMB12} have attempted to address these challenges.
+However, those solutions have two main limits:
 \begin{enumerate}
@@
 The problem is that in real world scenarios, decisions made by independent service providers are highly distributed.
-	\item The solutions either propose complex algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to find the optimal strategy to follow, or oversimplify the problem by eliminating important parameters and using approximation techniques to make the algorithms tractable \cite{10.1109/TSC.2012.12}.
+	\item The solutions either propose complex algorithms \cite{10.1109/TSC.2012.12, DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2014.2312940} to find the optimal strategy to follow, or oversimplify the problem by eliminating important parameters and using approximation techniques to make the algorithms tractable \cite{10.1109/TSC.2012.12}.
 \end{enumerate}
-These approximation methods sometimes negatively influence the outcome because simplifying the constraints may negatively cause important aspects of the problem to be ignored.
-
-For example, instead of calculating the gain distribution using the complex shapely-value method, \cite{10.1109/TSC.2012.12} proposes a simple egalitarian way of distributing gain, which completely ignores the gain generated from collaborative work of sub-communities.
-Other categories of related work exist that do not focus on all the parties involved within the community \cite{DBLP:conf/IEEEscc/KhosravifarABT11}.
+These approximation methods sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored.
+For instance, instead of calculating the gain distribution using the adequate, but complex shapely-value method, the authors is \cite{10.1109/TSC.2012.12} propose a simple egalitarian way of distributing gain, which completely ignores the gain generated from collaborative work of sub-communities.
+Other categories of related work, for instance \cite{10.1109/TSC.2012.12, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:journals/ijebr/MaamarSTBB09}, restrict the decision process within the community coordinator, so other members of the community are not effectively involved.
 %And some other work which do not focus on rationality on web services or communities involved [refrences]. 
-In \cite{journal-community-formation} we proposed a cooperative game theory based model for aggregating web services in communities.
-A centralized decision maker in communities based on a complete knowledge of available web service quality metrics and performance, has been used to form optimal and stable communities that maximize individual and group income.
+In \cite{journal-community-formation}, we proposed a cooperative game-theory-based model for aggregating web services in communities.
+A centralized decision maker in communities, based on a complete knowledge of available web service quality metrics and performance, has been used to form optimal and stable communities that maximize individual and group income.
 However, centrality and complete information are strong assumptions, which are not very compatible with real business scenarios.
@@
 \textbf{Contributions.} In this paper, we introduce DDM, a Distributed Decision Making model for community formation that regulates web service agents’ decision making process in terms of cooperating and deciding which group to join and which service to invite for joining.
-The decision model in extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
+Unlike existing work on community formation, our decision model is extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
 The generated decision tree improves agents' understanding of the environment and how to select actions that lead towards maximizing their utilities.
-The advantage of this approach is that the tree which is initially created from the past data and reflects comprehensive vision about agents' attitude of action selection based on agents' past expiriences.
-However, the tree based on recieving new feedback and outcome from actions, is subject to get continuously modified to adapt with environmental changes.
+The advantage of this approach is that the tree, which is initially created from the past data, reflects a comprehensive vision about agents' attitudes in terms of their action selection based on their past experiences.
+Moreover, the tree is getting continuously updated based on both new received feedback and the outcome of chosen actions.
+This continuous update makes the approach adapted to any change in the environment.
 %The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems. 
-The decision model provides web services with enough information which helps those services to efficiently decide and predict the outcome of their different possible collaborations.
-This model works in a distributed manner in which services are self-sufficient in decision making process and do not rely on a centralized decision making process.
+The decision model provides web services with enough information which helps those services efficiently decide and predict the outcome of their different possible collaborations.
+This model works in a distributed manner in which services are self-sufficient in their decision making and do not rely on a centralized decision making process.
 Our findings show that communities of web services can efficiently find the appropriate web service to invite for cooperation as well as allowing a single web service to find the best communities to join.
-In other words, the web services agents are equipped with a recommender system to suggest beneficial action.
-Moreover, communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
-In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their short-term and long-term goals; therefore, opting for best decision available.
-
-To effectively generate the decision model for web services, we used real data set to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another.
-The data set has been extracted by real-world QoS evaluation results from 142 users on 4,532 Web services on 64 different time slots.
-Combining these data based on each web service point of view on different time slots, we acquired 5 different unique features for 4,532 web services.
+The proposed model can be seen as a recommneder system that suggests beneficial actions for both communities and single services.
+Communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
+In general, DDM equips web services with efficient methods for foreseeing how their choices will impact both their short-term and long-term goals; therefore, opting for the best decision available.
+
+To effectively generate the decision model for web services, we used a real dataset to extract web services' individual characteristics and used them to measure outcomes when these services cooperate with one another.
+The dataset has been extracted from real-world QoS evaluation results from 142 users on 4,532 Web services during 64 different time slots.
+Combining the available data based on each web service point of view on different time slots, we acquired 5 different unique features for those 4,532 web services.
 By engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in different time slots.
-We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others.
-All paths and the outcomes are labeled to be utilized in the training model.
+We were able to investigate the path a web service might take to achieve the best utility out of effective interactions with others.
+All the paths and outcomes are labeled to be utilized in the training model.
 Using cross validation sets, web services are able to compute the optimal hypothesis function (using logistic regression) that can be used to predict outcomes of cooperative work with other individual web services or communities.
-Our findings show that web services equipped with DDM have by far better outcomes in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.
+Our findings show that web services equipped with DDM have by far better outcomes than the ones that either do not cooperate or randomly find communities to join.
 
 \textbf{Organization.} The rest of the paper is organized as follows.
-In Section 2 we briefly describe the preliminaries and challenging issues.
-Section 3 discusses the considered parameters and web service community architecture.
-Section 4 presents our solution model, the way data is trained and the way web services utilize the trained data in their decision making process.
+In Section 2, we briefly describe the preliminaries and challenging issues.
+Section 3 discusses the considered parameters and the architecture of web services communities.
+Section 4 presents our solution model, the way the trained model is built and the way web services utilize the trained data in their decision making process.
 Section 5 describes our experiments and results.
-Section 6 discussed relevant related work.
-Finally Section 7 concludes the paper and identifies future work.
+Section 6 discusses relevant related work.
+Finally Section 7 concludes the paper and identifies potential future work.
 
@@
 
-\section{Preliminaries and Challenges in WS Communities}\label{s:preliminaries}
+\section{Preliminaries and Challenging Issues}\label{s:preliminaries}
 %In this section, we first present the architecture of DDM.
@@
 To do this, we first discuss some preliminaries.
-In this section, we discuss the preliminary concepts of communities of web service and we introduce the challenges of community formation.
+In this section, we discuss the preliminary concepts of communities of web services and introduce the challenges behind community formation.
 
@@
 
-In recent years, online services have become a standard part of daily life around the globe.
+In the recent years, online services have become a standard part of daily life around the globe.
 Many modern applications rely on web services from different providers.
@@
 
-The World Wide Web Consortium (W3C) defines web services as ``software systems designed to support interpretable machine-to-machine interaction over a network.
+The World Wide Web Consortium (W3C) defines web services as ``software systems designed to support interoperable machine-to-machine interaction over a network.
 It has an interface described in a machine-processable format (specifically WSDL).
-Other systems interact with the web service in a manner prescribed by its description using SOAP messages, typically conveyed using HTTP with XML serialization in conjunction with other Web-related standards.'' When developers declare a new web service, it will be
+Other systems interact with the web service in a manner prescribed by its description using SOAP messages, typically conveyed using HTTP with XML serialization in conjunction with other Web-related standards''.
+When developers declare a new web service, it will be
 discovered based on its description, which fully discloses its functionalities.
@@
 Service providers usually charge end users for services they provide.
-For example, Google has listed pricing and plans for a wide range of services they provide on their web service console page\footnote{https://code.google.com/apis/console}.
-
-In this paper, we abstract web services as rational agents\footnote{The term rational is used here in the sense that web services are utility maximizers} that provide services to end users.
+For example, Google has listed pricing and plans for a wide range of services they provide on their web service console page\footnote{\url{https://code.google.com/apis/console}}.
+
+As in other proposals \cite{journals/mags/BaldoniBM10,10.1109/TSC.2012.12,DBLP:conf/IEEEscc/KhosravifarABT11}, in this paper, we abstract web services as rational agents\footnote{The term rational is used here in the sense that web services are utility maximizers.} that provide services to end users.
 They aim to maximize their individual income  by receiving enough requests from end users.
@@
 
-\subsection{Web Service Communities}\label{s:wsc}
-
-The community of web services is essentially a virtual group of web services having similar functionalities\cite{DBLP:journals/ijebr/MaamarSTBB09}.
+\subsection{Web Services Communities}\label{s:wsc}
+
+The community of web services is essentially a virtual group of web services having similar functionalities \cite{DBLP:journals/ijebr/MaamarSTBB09}.
 Communities aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols to those used by single web services.
 Web services join communities to increase utility by having a larger market share and task pool.
-Community coordinators are responsible for community development, managing membership requests from web services and distributing user tasks among the community members.
-Community coordinators try to attract quality web services to join and keep the community as stable and productive as possible to gain a better reputation and user satisfaction, which increases the community's market share.
+The community coordinator is responsible for securing the community, managing membership requests from web services and distributing user tasks among the community members.
+The coordinator tries to attract quality web services to join and keep the community as stable and productive as possible to gain better reputation and user satisfaction, which increases the community's market share.
 How web services reside within communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
@@
 \subsection{The Join Challenge}\label{s:tjc} 
-Sometimes, web services can increase their overall utility by collaborating with other web services as communities.
-This collaboration helps them with better ways of sharing resources and having higher reputation, better market share and wider visibility.
-Web services and communities come with different quality metric parameters, and the long-term outcome is dependent on these parameters.
+It has been showed in \cite{10.1109/ARES.2008.7,10.1109/TSC.2012.12,10.1109/TSC.2014.2312940} that web services can increase their overall utility by collaborating with other web services within communities.
+This collaboration provides them with better ways of sharing resources and having higher reputation, greater market share and wider visibility.
+Web services and communities come with different quality metrics, and the long-term outcome depends on these metrics.
 
 The goal of all parties involved in the community is to maximize their long-term outcome while they are operating as part of the community.
-Web services need to be equipped with a selection strategy to choose from all of the different possible collaboration groups they can form as well as an estimation method for evaluating the long-term gain of joining different possible communities.
-Web services need to experiment with different possible collaborative groups and other web services in order to estimate their gain over time.
+Web services need to be equipped with a selection strategy to choose from the different possible collaboration groups they can form as well as an estimation method for evaluating the long-term gain of joining different possible communities.
+Web services need to experiment with different possible collaborative groups in order to estimate their gain over time.
 However, with a high number of possible communities, it is not possible to test collaboration with random web services.
-Even if a linear approximate function for estimating utility based on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell_number$} growth rate of the possible number of partitions of web services into communities would make any brute-force type algorithm for the best community selection strategy intractable and impractical in real-world application settings.
+Even if a linear approximate function for estimating utility based on community web services' parameters is adopted, the exponential \footnote{Bell number: \url{http://en.wikipedia.org/wiki/Bell\_number}} growth rate of the possible number of partitions of web services into communities would make any brute-force type algorithm for the best community selection strategy intractable and impractical in real-world application settings.
 
 \subsection{Join Consequences}\label{s:jc}
-It is worth mentioning that a \emph{join} event takes place as a result of two parties that are looking to expand their collaborations.
+It is worth mentioning that a \emph{join} event takes place as a result of interaction between two parties that are looking to expand their collaborations.
 All actions are chosen in an attempt to enhance the overall outcome.
@@
 % long term.
-This is the case when a single web service joins a community, but the complex process of task allocation eliminates the visibility of the web service and, thus, the web service stays idle within the community, which makes the join action a bad decision.
+This is the case when a single web service joins a community, but the complex process of task allocation eliminates the visibility of that service, which stays idle within the community.
+This makes the join action of that service a bad decision.
 The same event might be beneficial for the community, as it hosts a new web service that can engage in performing a new coming task.
-But overall, neither side benefits from collaborating with the other and the join event has negative consequences for at least one side's utility.
+But overall, in this particular case, if the new web service stays idle for a long period of time, neither side will benefit from collaborating with the other and the join event will result in negative consequences for at least one side's utility.
 
 The more common scenario is when both parties benefit from the joining of a web service to a community.
-This action is rational, as both the web service and the community enhance the utility.
-However, the community may not be the best choice for the web service to join.
-In other words, the web service could have joined a better community, but, due to of lack of knowledge about the surrounding environment, joined the available community which was not the optimal choice.
-Since the community does enhance its utility, the web service could stay with that community, which results in a sub-optimal increase in web service's utility.
-In the following section the proposed model provides solutions that effectively address the aforementioned challenges.
-
-\section{The Model Components}\label{s:themodelcomponents}
-
-In this section, we discuss the parameters that we use in the rest of the paper. Then we present the task distribution and revenue model of our distributed web services communities.
+This joining action is then rational as both the web service and community enhance their utilities.
+However, the community may not be the best choice for the web service.
+In other words, the web service could have joined a better community if it had enough and accurate knowledge about the surrounding environment.
+Since the community does enhance its utility, the web service could stay with that community, which results in a non-optimal increase in web service's utility.
+In the following section, the proposed model provides solutions that effectively address the aforementioned challenges.
+
+\section{Model Components}\label{s:themodelcomponents}
+
+In this section, we discuss the parameters that we use in the rest of the paper. Then, we present the task distribution and revenue model of our distributed web services communities.
 
@@
 With a group of web services having identical or similar functionalities, QoS metrics provide nonfunctional characteristics for optimal candidate selection.
-Web service quality metrics were presented in \cite{Ardagna:2007:ASC:1263152.1263531,Menasce:2002:QIW:613357.613758,10.1109/ISSRE.2011.17}.
-We have adopted the most representative QoS properties of web services that highly influence the utility of web services.
+Web services quality metrics have been studied and analyzed in various proposals, for instance in in \cite{Ardagna:2007:ASC:1263152.1263531,Menasce:2002:QIW:613357.613758,10.1109/ISSRE.2011.17}.
+In this paper, we adopt the most representative QoS properties of those services that highly influence their utility.
 %We refer to a typical web service as ws_{i}.
 
-Let $C = \{ws_1,ws_2,..., ws_n\}$ be a community with $|n|$ web services. We define the following features for the group of web services based on their functional parameters:
+Let $C = \{ws_1,ws_2,..., ws_n\}$ be a community with $n$ web services. We define the following features for the group of web services based on their functional parameters:
 
@@
 
-  \item \emph{Throughput $(Th_{C})$} is the rate at which a service can process requests.
+  \item \emph{Throughput} is the rate at which a service can process requests.
 QoS measures can include the maximum throughput or a function that describes how throughput varies with load intensity.
 Throughput is a positive real number.
-For communities the expected throughput value of collaborating web services can be estimated as summation of throughputs of all the services inside:
+For a given community $C$, the expected throughput value $(Th_{C})$ can be estimated as the summation of throughput of all the service members $Th_{w}~ (w \in C)$:
 
@@
 
-	\item \emph{Availability $(A_{C})$} is the percentage of time that a service is operating.
-	The probability that the service operation is accessible.
-Availability is also a real number in the range $[0, 1]$.
-For communities the expected availability of collaborating web services considering they follow a parallel system can be estimated as:
+	\item \emph{Availability} is the percentage of time that a service is operating. It is computed as
+the probability that the service operation is accessible.
+Availability of a web service $A_w$ is a real number in the range $[0, 1]$.
+For a community $C$, the expected availability $(A_{C})$ considering the members operate in parallel (independently from each other) can be estimated as:
 
@@
 
-	\item \emph{Execution Time $(Et_{C})$} is the time a service takes to respond to various types of requests. 
+	\item \emph{Execution Time} is the time a service takes to respond to various types of requests. 
 	%is the expected delay between the time instant when a request is sent and the time when the result is obtained. 
-	Execution time is measured in milliseconds.
-Execution time can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests.
+	Execution time is usually measured in milliseconds and can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests.
 This internal feature is a positive integer.
-For communities, the expected execution time of collaborating web services can be estimated as the execution time of the bottleneck service which is the service with the slowest execution time:
+For a typical community $C$, the expected execution time $Et_{C}$ can be estimated as the execution time of the bottleneck service which is the service with the slowest execution time $Et_{w}$:
 
@@
 	We normalize the range of these features so that each feature contributes proportionally to the final utility outcome value.
-We adopt the \emph{standardization} method.
-We subtract the \emph{mean} from each feature then we divide the values of each feature by its \emph{standard deviation}.
+We adopt the \emph{standardization} method consisting of subtracting the \emph{mean} from each feature, then dividing the subtraction result by the \emph{standard deviation}.
 
@@
 The quantitative values of quality metrics need some benchmark values to represent their goodness.
-In other words, without some benchmark values it would be difficult for web services to identify their goals, and performance quality at any specific value of these metrics.
-Therefore, we have introduced two external features for assessing web services' estimate with regard to their standing among other web services.
+In fact, without some benchmark values, it would be difficult for web services to identify their performance quality at any specific value of these metrics.
+Therefore, we introduce two external features for assessing web services' estimate with regard to their standing among other web services.
 
 \begin{itemize}
-  \item \emph{External Parameter 1} $(exp_1)$.
-is an estimate of how close the web service's \emph{execution time} is to other web services.
-It is the difference between a web service's \emph{execution time} metric and the maximum value of execution time of all the other web services.
-The smaller value means web service has better execution time compared to other web services.
+  \item \emph{External Parameter 1} ($Exp1_i$ where $i$ is a community or a web service) is an estimate of how close the community's or the web service's \emph{execution time} is to the best execution time in the whole system.
+It is the difference between a community's or a web service's \emph{execution time} metric and the minimum value of execution time of all the other communities or web services.
+The smaller the value the better the external feature compared to other peers.
+In other words, small value of $Exp1_i$ means $i$ is among the best communities or services in the system.
 	\begin{equation}\label{exp_1:f}
-		exp_1 = Et_{i} - Et_{max}
+		Exp1_i = Et_{i} - Et_{min}
 	\end{equation}
-	\item \emph{External Parameter 2} $(exp_2)$ is a comparison of the web service's rate of performing tasks to other competing web services.
-It is the difference between a web service's \emph{throughput} metric and the maximum value of throughput of all the other web services.
-The less value means web service has better throughput compared to other web services.
+	\item \emph{External Parameter 2} ($Exp2_i$ where $i$ is a community or a web service)  is a comparison of the community's or the web service's rate of performing tasks to the best rate in the system.
+It is the difference between a community's or a web service's \emph{throughput} metric and the maximum value of throughput in the system.
+As for $Exp1_i$, the smaller the value the better the external feature.
 	\begin{equation}\label{exp_2Lf}
-		exp_2 = Th_{max} - Th_{i}
+		Exp2_i = Th_{max} - Th_{i}
 	\end{equation}
@@
 
-A community of web services is abstracted as a standard web service that provides services that share the same internal and external features mentioned above for the web services.
-Inside, they adopt different protocols to manage the community; however, other web services or end users can communicate with communities of web services, using standard web service protocols.
+%A community of web services is abstracted as a standard web service that provides services that share the same internal and 
+%external features mentioned above for the web services. Inside, they adopt different protocols to manage the community; 
+%however, other web services or end users can communicate with communities of web services, using standard web service protocols.
 
@@
 
-Communities of web services usually employ an implementation of Contract-Net protocol for task distribution, in which services opt for incoming tasks, and receive the tasks for which they ask.
-However, in our model, our community members would try to distribute tasks based on their capabilities and the QoS parameters provided by the web services.
-We have used a slightly modified \emph{weighted fair queuing} method to distribute tasks among community members.
-The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{ws}$.
-In the \emph{weighted fair queuing} method, the input flow is multiplexed along different paths; however, in our case, if the rate of incoming tasks is less than the community's total throughput $(Th_{C})$, which is the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with a delay.
+Communities of web services usually employ an implementation of Contract-Net protocol for task distribution, in which services bid on incoming tasks, and receive some of the tasks for which they bid \cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:conf/aina/ElnaffarMYBT08}.
+In our model, our community members would try to distribute tasks based on their capabilities and the QoS parameters provided by the web services.
+We use a slightly modified \emph{weighted fair queuing} method to distribute tasks among community members.
+The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{w}$ for each web service $w$.
+In the \emph{weighted fair queuing} method, the input flow is multiplexed along different paths.
+However, in our model, if the rate of incoming tasks is less than the community's total throughput $(Th_{C})$, which is the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with a delay.
 %Thus, the amount of tasks performed by the community is $\sum_{ws}{Th_{ws}}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$. 
-When the incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $|input Task Rate| \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) within the community.
+When the incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $Itr \times \frac{Th_{w}}{\sum_{w}{Th_{w}}}$ for each web service $w$ within the community, where $Itr$ is the input task rate.
 
@@
 Communities and web services earn revenue by performing tasks.
-The total gain is a function of the quality of rate of tasks being performed.
-The utility of a collaborative group of services $U_{C}$ is the revenue of the community.
-Formula \ref{u_c_normal} is an estimation of the gain of the community.
+The total gain is a function of the quality and rate of performing tasks.
+The utility of a collaborative group of services $U_{C}$ (i.e., the revenue of the community) is a function of internal and external parameters:
+
+\begin{equation}\label{u_c_general}
+U_{C} = f(A_{C}, Et_{C}, Exp1_{C}, Exp2_{C}, Th_{C})
+\end{equation}
+%
+where $f$ is increasing in $A_{C}$ and $Th_{C}$ and decreasing in $Et_{C}, Exp1_{C}$ and $Exp2_{C}$. An example of this function is given in Equation \ref{u_c_normal}:
 
@@
 
-The $\alpha$ and $\beta$ values are internal and external weight coefficients.
-Execution time and external parameters are better when they have smaller values hence the negative coefficient for them.
-The result is then multiplied to the throughput value $Th_{C}$, since communities are performing tasks with $Th_{C}$ rate.
-
-The estimation can be improved, especially in cases where the input task rate is high and services are experiencing high task loads.
+The $\alpha$ and $\beta$ parameters are internal and external weight coefficients.
+Small values for execution time and external parameters ensure better performance, which justifies their negative coefficients.
+The result is then multiplied by the throughput value $Th_{C}$, since communities are performing tasks with $Th_{C}$ rate.
+
+\begin{theorem}
+The function given in Equation \ref{u_c_normal} satisfies the properties of $f$.
+\end{theorem}
+
+The proof of this theorem is straightforward by simply calculating the partial derivative $\partial f$ with respect to the different variables.
+
+The estimation of the utility can be improved, especially in cases where the input task rate is high and services are experiencing high task loads.
 The \emph{weighted fair queuing} method of task distribution would distribute tasks based on the individual throughput $(Th_{w})$ value of services within community.
-The services with higher throughput will affect the overall utility of the community more because they would take on proportionately more tasks.
+In fact, services having higher throughput affect strongly the overall utility of the community because they would take on proportionality more tasks.
+The improved utility is given as a function of individual internal and external parameters:
+
+\begin{equation}\label{improved_u_c_general}
+U_{C} = g_{w\in C}(A_{w}, Et_{w}, Exp1_{w}, Exp2_{w}, Th_{w})
+\end{equation}
+%
+where $g_{w\in C}$ is increasing in $A_{w}$ and $Th_{w}$ and decreasing in $Et_{w}, Exp1_{w}$ and $Exp2_{w}$. An example of this function is given in Equation \ref{u_c_load}:
 
@@
 \begin{split}
-U_{C} = \sum_{ws \in C}&\bigg(\big(\alpha \times (A_{ws} - Et_{ws}) \\
-        & - \beta \times (exp1_{ws} + exp2_{ws})\big) \times Th_{ws}\bigg)
+U_{C} = \sum_{w \in C}&\bigg(\big(\alpha \times (A_{w} - Et_{w}) \\
+        & - \beta \times (Exp1_{w} + Exp2_{w})\big) \times Th_{w}\bigg)
 \end{split}
@@
 
+The following theorem holds:
+
+\begin{theorem}
+The function given in Equation \ref{u_c_load} satisfies the properties of $g_{w\in C}$.
+\end{theorem}
+
 \section{The Decision Making Mechanism}\label{s:model}
 
-In this section, we describe our data extraction process and the methodology used to equip web services with a decision making mechanism.
+In this section, we describe our data extraction process and the methodology used to equip web services and communities with a decision making mechanism.
 In this methodology, we first present the data extraction and engineering process and then we evaluate the decision making mechanism for web services in community settings.
-Figure \ref{fig_steps} summarizes the steps performed in DDM from the input data to generation of decision making profiles for web services.
+Figure \ref{fig_steps} summarizes the steps performed in DDM from the input data to the generation of decision making profiles for web services and communities.
+The objective is to use the input data to build a decision tree for each service and community included in the data set, which will be be served as a benchmark for other services and communities in their decision making mechanism.
+The decision tree is made up by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services.
+The ultimate objective is to propose for each web service and community the best joint decision about forming a group that maximizes every one's utility.
+The DDM's steps are explained in the following sections.
 
 \begin{figure}%[!t]
-\centerline{\includegraphics[width=1.75in]{figures/steps.eps}}
+\centerline{\includegraphics[width=5.25in]{figures/steps.eps}}
 \caption{A summary of DDM decision profile generation steps}
@@
 
-\subsubsection{Input Web Services Data}\label{sss:webservices}
+\subsubsection{Input Data}\label{sss:webservices}
 
 %We used a data set extracted from running web services. In this data set, 
-Each web service is associated with a number of features that reflect its functionality.
+Each web service is associated with a number of quality metrics that reflect its non functional parameters.
 These web services operate in an online environment and are continuously assigned tasks to handle.
-To engage in communities, we add additional features that reflect web services' utility as a result of joining other web services to form a community.
-The additional features are computed based on two assumptions that we adopt for a community to be formed.
-We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}.
-The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{http://www.wsdream.net/}.
-In this data set, each web service is associated with a number of features that reflect its functionality.
+%To engage in communities, we add the external features that reflect web services' utility as a result of joining other web services to form a community (see Section \ref{s:ef}).
+%The additional features are %computed based on two assumptions that we adopt for a community to be formed.
+We used the web services data set provided in \cite{10.1109/ISSRE.2011.17}.
+The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{\url{http://www.wsdream.net/}}.
+%In this data set, each web service is associated with a number of features that reflect its functionality.
 %Our raw data set provides us with 64 different time slots of extracted features for each web service. 
-Using this data we can build a synthetic data set that contains features of a large number of web services in a sequence of time.
-Therefore, we train a learning model that adopts the trend of joining a community and use the model to predict/find the appropriate community for other web services.
-To train our model, we build a decision tree as a benchmark for our decision making mechanism.
-The decision tree is built by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services.
-As a result, we are able to classify web services as either single or joined and propose the communities that are best fitted to the web services' requirements.
-
-\subsubsection{Filtered Data}\label{sss:filtereddata}
-
-By summarizing the data provided for each web service over different time slots, we have acquired three quality features for each individual web service.
-Their quality features are the three internal features introduced in Section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time}.
+Using this data, we built a synthetic data set that contains features of a large number of web services and communities in different time intervals.
+The goal is to use the data set to train a decision-making model that adopts the trend of joining a community and use the model to predict/find the appropriate community for other web services.
+%To train our model, we build a decision tree as a benchmark for our decision making mechanism.
+The decision tree is made up by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services.
+The ultimate objective is to propose for each web service and community the best joint decision about forming a group that maximizes every one's utility.
+
+\subsubsection{Feature Extraction}\label{sss:filtereddata}
+
+By processing the data provided for each web service over different time slots, we obtain the three internal quality features introduced in Section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time} and the two external features discussed in Section \ref{s:ef}.
+In fact, web services and communities are represented using feature vectors of these five internal and external features.
+
 %To engage in communities, we add two additional external features that reflect web services estimation of its quality metrics compared to other web services. 
-Therefore, we have generated an array of web services with three distinct features.
+%Therefore, we have generated an array of web services with three distinct features.
 
 \begin{figure}%[!t]
-\centerline{\includegraphics[width=3.25in]{figures/cfvs.eps}}
-\caption{Communities with different properties of web services actively looking for other communities to collaborate with, they send collaboration requests to communities they find the collabration  increasing the gain}
+\centerline{\includegraphics[width=3.15in]{figures/cfvs.eps}}
+\caption{Communities with different properties of web services actively looking for other communities to collaborate with}
 \label{fig_community}
@@
 
-Now, we want to generate a set of feature vectors representing the communities of web services for training purposes.
-For communities, we add two additional external features, as discussed in Section \ref{s:ef} that reflect the community's estimation of its quality metrics compared to other web services.
-Therefore, we formulate a \emph{Community Feature Vector (CFV)} as $CFV_{<C>} = \{f_1,...f_5\}$ having a community of $k$ web services.
-$C = {ws_1,...ws_k}$.
-The features $f_1$ through $f_5$ represent the \emph{execution time}, \emph{throughput}, \emph{availability} and the \emph{external parameters 1 and 2} correspondingly.
+%By combining these three internal features to the two external features discussed in Section \ref{s:ef} that reflect the community's estimation of its quality metrics, we generate a set of feature vectors representing the communities of web services for training purposes.
+
+We formulate a \emph{Community Feature Vector (CFV)} as $CFV_{<C>} = [f_1,...f_5]$ having a community of $k$ web services ($C = \{ws_1,...ws_k\}$, $k \geq 1$)\footnote{A web service is considered as a community of one web service.}.
+The features $f_1$ through $f_5$ represent the \emph{execution time}, \emph{throughput}, \emph{availability} and the \emph{external parameters 1 and 2} respectively.
 A set of communities, with their feature vectors and utilities evaluated, provides our algorithm with a raw training data set.
-We call this set of communities the \emph{template vector}, and the set of feature vectors associated with the \emph{template vector} is referred to as the \emph{community feature vector set (CFVS)}.
-Figure \ref{fig_community} depicts communities looking to form collaborate communities and join other communities in order to improve their utility gain.
+We call this set of communities the \emph{template vector} $CS$, and the set of feature vectors associated with the \emph{template vector} is referred to as the \emph{community feature vector set (CFVS)}.
+Figure \ref{fig_community} depicts web services and communities looking to form new groups in order to improve their utility gain.
 
 \subsubsection{Feature Engineering}\label{sss:feng}
-Let $CFVS = \{C_1, C_2,..., C_N\}$ be the community feature vector set with $N$ communities.
-Based on the $CFVS$ set, we create an $|N \times N|$ gain matrix for $t$ different time slots.
-Each entry of $gain_{n,m}^{t}$corresponds to a utility gain of web services in $C_n$, when $C_n$ joins $C_m$, based on community and web service data available for time $t$.
-All of these values have to be evaluated by implementing the community with members of $ws_i \in C_n$ and $ws_j \in C_m$ and evaluating its utility (see Equation \ref{u_c_load}).
-Therefore $gain_{n,m}^{t} = U_{C_n \cup C_m}^{t} - U_{C_{n}}^{t}$.
-Evaluating the utility gain for all entries of the $gain$ matrix can be a costly process with a very big number of $N$, size of the feature vector $|N|$ should be chosen carefully.
+Let $CFVS = \{CFV_{<C_1>}, \dots, CFV_{<C_N>}\}$ be the community feature vector set with $N$ communities.
+Based on the $CFVS$ set, we create an $|N \times N|$ gain matrix $gain^{t}$ for each time slot $t$.
+Each entry $gain_{n,m}^{t}$ corresponds to a utility gain of community $C_n$ when it joins community $C_m$.
+This gain is computed as follows: $gain_{n,m}^{t} = U_{C_n \cup C_m}^{t} - U_{C_{n}}^{t}$ where $U_{C_n \cup C_m}^{t}$ and $U_{C_{n}}^{t}$ are the utilities at time $t$ computed using Equation \ref{u_c_load}.
+Evaluating the utility gain for all entries of the $gain^t$ matrix is a computationally heavy process when $N$, the size  of the feature vector set, is large.
+Therefore, this size should be chosen carefully.
 
@@
 
-Now, we let our set of communities in the $CFVS$ set, within $|T|$ time frame iterations, choose the the best communities to join.
-Each community is provided with the corresponding row of data from the $gain$ matrix.
-Basically, $C_i$ is provided with the data in row $i$ of matrix $gain_{N,N}$, which is all of the possible utility values it can gain by joining different communities.
-By ordering the list, each community is utilized with an ordered set of preferences over other communities it likes to join.
-We define $>_{i}^t$ as the preference order of community $i$ at time $t$.
-
-Let $P_{C_i}^t = \{C_1 >_{i}^t C_2 >_{i}^t ....
->_{i}^t C_n\}$ be an ordered set of preferences for community $C_i$ at time $t$.
-Based on this ordered set, we define $K^t(C_i, k)$ as a set of the $k$ most preferred communities of community $i$ at time $t$.
+%Now, we let our set of communities in the $CFVS$ set, within $|T|$ time frame iterations, choose the the best communities to join.    
+Each community is provided with the corresponding row of data from the $gain^t$ matrix.
+Basically, $C_i$ is provided with the data in row $i$ of this matrix, which reports all the possible utility values $C_i$ can gain by joining different communities.
+By ordering the utility gain values of the row, each community is equipped with an ordered set of preferences over other communities it can join.
+We define $\geq_{i}^t$ as the preference order of community $i$ at time $t$.
+
+Let $C_1 \geq_{i}^t C_2 \geq_{i}^t ~\dots~ C_{i-1} \geq_{i}^t C_{i+1} \geq_{i}^t ~\dots~ C_n$ be an ordered sequence of preferences for community $C_i$ at time $t$.
+Based on this sequence, we define $K^t(C_i, k)$ as a set of the $k$ most preferred communities of community $i$ at time $t$.
 %\subsubsection{feature vector generation}\label{sss:fvg}
@@
 \begin{split}				
-K^t(C_i, k) = &\Big\{C_x | C_x >_{i}^t C_y; \forall C_y \in CFVS\ \\
-				      &\wedge C_y \notin \{K^t(C_i, 1),K^t(C_i, 2),...,K^t(C_i, k-1)\} \Big\}				
+K^t(C_i, 0) = &\emptyset \\
+K^t(C_i, k) = &\Big\{C_x | C_x \geq_{i}^t C_y ~\forall C_y \in CS ~\wedge~ C_x \neq C_y ~\wedge~ C_y \notin K^t(C_i, k-1) \Big\}				
 \end{split}
 \end{equation}
-Based on $K^t(C_i, k)$, we define a set of communities for $C_i$ in which they are the k most preferred communities for community $i$ and also community $i$ belongs to the k most preferred communities out of all of the communities in set $K^t(C_i, k)$.
-This basically implies the preference is both-sided.
+Based on $K^t(C_i, k)$, we define a set of communities $C_j$ for $C_i$ which are the $k$ most preferred communities for $C_i$ and $C_i$ belongs to the $k$ most preferred communities of $C_j$.
+This basically yields the preference in both sides.
 \begin{equation}\label{l_t_top_both}
 \begin{split}	
-L^t(C_i,k) = &\Big\{C_j | C_j \in K^t(C_i, k) \\
-             &\wedge C_i \in \bigcup_{C_x \in K^t(C_j, k)}K^t(C_x, k)\Big\}
+L^t(C_i,k) = \Big\{C_j | C_j \in K^t(C_i, k)~ \wedge~ C_i \in K^t(C_j, k)\Big\}
 \end{split}
@@
 Each row shows the gain the community can achieve by collaborating with other 5 communities.
-In this example for community $\textless 348 \textgreater$ we have: \\
+In this example, for community $\textless 348 \textgreater$ we have: \\
 $K(\textless 348 \textgreater, 1) = \{\textless1934, 2117\textgreater\}$ and \\
 $K(\textless 348 \textgreater, 2) = \{\textless1934, 2117\textgreater, \textless1934\textgreater\}$ \\
-Since $\textless 348 \textgreater$ is best preferred community of $\textless 1934, 2117 \textgreater$ therefore $L(\textless 348 \textgreater, 1)$ is not empty and contains the community $\textless1934, 2117\textgreater$.
+Since $\textless 348 \textgreater$ is the best preferred community of $\textless 1934, 2117 \textgreater$ and vice versa, therefore $L(\textless 348 \textgreater, 1)$ is not empty and contains the community $\textless1934, 2117\textgreater$.
 
@@
 % as well as the joined events that took place in different time slots. 
-In addition to best choices, web services have access to other ordered choices and can look for the second best or third best if their first try is rejected by the target community.
-The consequences of each try level is analyzed in more detail in the following section, in which we launch experiments and investigate the effectiveness of the use of a decision tree with different decision layers in joining other communities and enhancing the overall utility.
+In addition to the best choice, web services have access to other ordered choices and can look for the second best or third best if their first try is rejected by the target community.
+This aspect is analyzed in more detail in the following section, in which we launch experiments and investigate the effectiveness of the use of a decision tree with different decision layers in joining other communities and enhancing the overall utility.
 
@@
 
-Our goal is to create a decision making profile for each community in the $CFVS$ set.
-We are creating an environment where they can experience the outcomes of different strategies.
-The result will be a decision tree of the feasible and utility increasing moves over time.
-
-We let communities pick the best communities for maximizing their utilities over different time frames.
-At time $t = 1$, we let each community in the $CFVS$ set choose the best community, which is a single community in set $C_j = K^t(C_i, 1)$.
-If community $C_j$ also has the highest preference to join $C_i$ meaning the $L^t(C_i, k=1)$ set is not empty, they would join together.
+Our goal is to create a decision making profile for each community in the
+$CFVS$ set. We are creating an environment where the communities can experience the
+outcomes of different strategies. The result will be a decision tree of the
+feasible and utility-increasing moves over time. The root of the decision tree
+represents a community in the $CFVS$ set, and the other nodes represent
+the communities resulting from the parent node's action of joining them along with their feature values and
+expected utility.
+
+We let communities pick the best communities maximizing their utilities over different time frames.
+At time $t = 1$, we let each community in the $CFVS$ set choose the best community, which is a single community in the set $\{C_j\} = K^t(C_i, 1)$.
+If community $C_j$ also ranks $C_i$ to be the highest preferred community to join, meaning the set $L^t(C_i, k=1)$ is not empty, they would join each other.
 Having set $k = 1$ is a very strict and hardly satisfiable condition.
-In order to relax the requirement, the value of $k$ is being increased by a rate $r$ proportional to time slot $t$.
-Basically, $k = 1 + |r \times t|$.
-On early steps of simulation web services and communities are more strict but as time goes on, we let them choose second and then third best options too.
-However, increasing $k$ quickly increases the time complexity of $K^t(C_i, k)$ by $O(k^2 \times n.log(n))$.
-
-When communities $C_i$ and $C_j$ are in each other's top $k$ preference set, their combination is added to the list of possible communities that can join others at time $t+1$.
-Also, for each community $C_i$ in our initial $CFVS$ set, we maintain a tree with the community $C_i$ as its root.
-Its children are all of the communities that $C_i$ decided to join.
+In order to relax the requirement, we increase the value of $k$ by a rate $r$ proportional to time slot $t$: $k = 1 + |r \times t|$.
+On early steps of the training process, web services and communities are more strict, but as time goes on, we let them choose second and then third best options too.
+However, increasing $k$  increases the time complexity as well.
+
+When communities $C_i$ and $C_j$ are in each other's top $k$ preference set, the new combined community, i.e., $C_i \cup C_j$ is added to the list of possible communities that can join others at time $t+1$.
+Moreover, for each community $C_i$ in our initial $CFVS$ set, we maintain a tree with the community $C_i$ as its root.
+Its children are all the communities that $C_i$ decided to join.
 As the scenario progresses over time, the merged communities may decide to join other communities.
-When community $C_i$ and $C_j$ decide to join each other and create community $C_k$, the new community $C_k$ will be added as a child to both $C_i$ and $C_j$ nodes.
-At the end of the process, each community is utilized with a tree of set of possible combination of communities it can join.
+When communities $C_i$ and $C_j$ decide to join each other and create community $C_k$, the new community $C_k$ will be added as a child to both $C_i$ and $C_j$ nodes.
+At the end of the process, each community is utilized with a tree representing all possible combinations of communities it can join.
 Algorithm \ref{algo:dectree} illustrates the DDM tree creation procedure as pseudo-code.
-
-Having created $|n|$ trees, for each community $C_i$, our communities are utilized with the different possible paths they can take to maximize their utilities.
-Using a distance function, communities and web services can utilize these results and find the $C_i$ that closely resembles their parameters.
-They will be utilized with a tree that has the strategies the community can use to join our communities which will be best possible path to take and communities to join while most likely being accepted by other communities since its a two sided preference.
-The algorithm below describes the tree creation process.
 
@@
 \DontPrintSemicolon
-\KwIn{$\langle r, gain^t_{n,n}, CFVS \rangle$ learning rate $r$, $|N \times N \times T|$ gain matrix, community feature vector}
+\KwIn{$\langle r, gain, CFVS \rangle$: rate $r$, $|N \times N \times T|$ gain matrix, $CFVS$ community feature vector}
 \KwOut{A set of \emph{root} nodes of the decision trees}
 $k \gets 1$\;
-$nodes[N] \gets$ initialize $N$ tree nodes representing each community in CFVS\;
+$nodes[N] \gets$ initialize $N$ tree nodes representing each community in $CFVS$\;
 \For{$t \gets 1$ \textbf{to} $T$} {
@@
   \For{all $C_i \in CFVS$} {
-	  \For{all $C_j \in L^t(C_i, k)$} {
+	  \For{all $C_j \in K^t(C_i, k)$} {
       % The "l" before the If makes it so it does not expand to a second line
-      \If{$C_i \in L^t(C_j, k)$}{
+      \If{$C_i \in K^t(C_j, k)$}{
         $C_k \gets C_i \cup C_j$\;
@@
 
+Having created $|n|$ trees, one per community, our communities are utilized with the different possible paths they can take to maximize their utilities.
+Using a distance function\footnote{See Section \ref{s:experiments} for an example of this function.}, communities and web services outside the training set can find the community that closely resembles their parameters within the $CFVS$ set.
+Those new communities can use the trees of the closest communities in the training set to have an estimation of the outcome of all possible joining actions they can take.
+By so doing, new communities can request to join the best communities which will maximize their gain.
+Such a request is most likely to be accepted as the decision considers the preferences and utility gain of the other side as well.
+
+As a real scenario example from the used data set, Figure \ref{fig_tree} depicts a snapshot from a decision tree created by the DDM algorithm for a particular singleton community $C_{1273}$.
+This tree shows the different communities that $C_{1273}$ has experienced with during the training process.
+Each line shows the web services list within a community, the community's feature vector and the last value on each line is the overall gained  utility of the community.
+
+\begin{figure}%[!t]
+\centerline{\includegraphics[width=6.25in]{figures/tree1.eps}}
+\caption{A partial view of a decision tree created by DDM}
+\label{fig_tree}
+\end{figure}
+
 \textbf{Complexity.} Here we analyze the computational complexity of the DDM decision tree creation algorithm on each time iteration $t$.
-Computing top $k$ preferred communities for $C_i$ in $L^t(C_i, k)$ requires an $O(n.log(n))$ sort time.
-$C_i$ has a result set of size $|k|$, and for each of those $k$ communities we need to check against their $k$ top preferred communities.
-Considering we already have the list sorted, line 6 in algorithm runs $O(k \times n.log(n))$ times.
-Doing this search for all communities in $|CFVS|$ set $n$ times (line 5), the overall order of complexity of the algorithm in regards with $n$ and $k$ is: $O(k^2 \times n^2.log(n))$.
+Computing top $k$ preferred communities for $C_i$ in $K^t(C_i, k)$ requires $O(n.log(n))$ sort time.
+The size of $K^t(C_i, k)$ is $k$, and for each of those $k$ communities, we need to check against their $k$ top preferred communities, which needs $O(k^2)$.
+Line 5 iterates through $n$ communities, Line 6 takes $O(n.log(n))$ to compute and iterates $k$ times, and considering we already have the list sorted, Line 7 can reuse the sorted preferences.
+Thus, Line 7 takes $O(k)$ time to check if $C_i$ is member of $K^t(C_i, k)$.
+Multiplying these iterations, the order of complexity of the algorithm with regard to $n$ and $k$ for each time slot is: $O(k^2 \times n^2.log(n))$.
+Since the whole algorithm runs $T$ times, the overall complexity is $O(T \times k^2 \times n^2.log(n))$.
 
 \section{Experiments}\label{s:experiments}
-We implemented DDM in Java\footnote{Source code of implementation and data is available at: \emph{https://github.com/Marooned202/DDM}}.
-We recall that have extracted the set of features for 4532 web services in 64 different time slots through a data set provided by \cite{10.1109/ISSRE.2011.17}.
-By choosing 86 web services out of these sets and choosing a subset of all possible combinations of sizes 2, 3, and 4 of these 86 web services, we have chosen 10,000 communities and evaluated the feature vectors and utilities they can have in 64 different time slots.
+We implemented DDM in Java\footnote{Source code of implementation and data is available at: \url{https://github.com/Marooned202/DDM}}.
+We recall that we have extracted the set of features for 4532 web services in 64 different time slots through a data set provided in \cite{10.1109/ISSRE.2011.17}.
+By randomly choosing 86 web services out of this data set for each run, and selecting a subset of all possible combinations of sizes 2, 3, and 4 of these 86 web services, we have been able to create 10,000 communities and evaluated the feature vectors and utilities they can have in the 64 time slots.
 This provides us with the initial training feature set of size $|CFVS| = 10,000$ communities.
-Based on Equation \ref{u_c_load} the utility of these communities are estimated, and the gain matrix $|10000 \times~ 10000|$ of all possible ways of merging these 10,000 communities, is generated\footnote {The template vector and gain matrix generated are available at \emph{https://github.com/Marooned202/DDM/tree/master/wsds/data/run}}, and each community has the ordered preference among other communities known in the set.
+Based on Equation \ref{u_c_load}, the utilities of these communities are estimated, and then the $gain$ matrix of size $|10,000 \times~ 10,000|$ of all possible ways of merging these 10,000 communities is generated\footnote {The template vector and $gain$ matrix generated are available at \url{https://github.com/Marooned202/DDM/tree/master/wsds/data/run}}.
+Based on the $gain$ matrix, each community has an ordered preference among other communities in the set.
 
@@
 With the slow rate of $r = 0.05$, we increase $k$ in Equation \ref{u_c_normal} for every 20 time frames, which will happen only three times in our 64-step experiment.
-In the case of $r = 0.20$, k increases much faster, at a rate of once every 5 time frames, which increases the complexity of the $L^t(C_i,k)$ search for each community in the $CFVS$ set.
+In the case of $r = 0.20$, $k$ increases much faster, at a rate of once every 5 time frames, which increases the complexity of the $L^t(C_i,k)$ search for each community in the $CFVS$ set.
 
@@
 The utility gain ratio is the ratio of their final utility over initial utility.
-Comparing the different search rates, we can see increasing $r$ to value of $0.10$ results in significant performance boost, however the higher rates of $r$ are not increasing the chance of finding better collaborative groups for our communities.
+Comparing the different search rates, we can see that increasing the value of $r$ from $0.05$ to $0.10$ results in a significant performance boost.
+However, higher rates of $r$ ($r > 0.10$) are not increasing the chance of finding better collaborative groups for our communities while unnecessarily increasing the search complexity.
 
@@
 
-We utilize the same communities and web services with a simple rational decision making mechanism, in which communities will choose to join a community if it increases utility by any amount.
-We call it the $rational$ method, in the sense that it is just a rational method and is not aiming to be optimal.
-We chose 10 random web services and compared the results with web services which adopted our DDM model.
+The closest related work \cite{10.1109/TSC.2012.12,
+DBLP:conf/IEEEscc/LimTMB12, DBLP:conf/IEEEscc/KhosravifarABT11} and our
+previous work \cite{journal-community-formation} regarding the community formation problem have considered a centralized approach where a community manager has complete information of all the web services and their quality
+metric and parameters. Those proposals run complex algorithms through all the space of
+solutions in order to find the optimal answer. However, in this paper, we
+have considered an unexplored and more realistic situation where information is incomplete and a decision
+profile is generated based on a smaller set of web services. Our solution helps
+communities and web services select actions that lead towards
+maximizing their utilities. Therefore, considering the different settings,
+we cannot experimentally compare our work with the mentioned related work.
+
+To compare our work against a benchmark, we utilize the same communities and web services with a simple rational decision making mechanism in which a community will choose to join another one if it increases its utility by any amount, without aiming to be optimal.
+We call this method the {\textit{rational} method.
+We have chosen 10 random web services and compared the results with web services which adopted our DDM model.
 Figure \ref{utility_gain_mlisa_and_rational} shows the comparison of the end result of utility gain values.
 In 18 out of 40 tries, \emph{rational} agents were not able to improve their utility at all because the communities they chose rejected their request, most likely because they would not have increased the utility of the other communities if they had joined them.
-The results show that a long-term strategic decision mechanism is needed to satisfy all of the services within communities.
+The results show that a long-term strategic decision mechanism is needed to satisfy all the services within communities.
 Figure \ref{utility_gain_mlisa_and_rational_ratio} shows the same results in terms of ratio of utility gain.
@@
 \includegraphics[width=3.5in]{figures/utility_gain.eps}
-\caption{Utility Gain DDM and Rational}
+\caption{DDM against Rational: utility gain }
 \label{utility_gain_mlisa_and_rational}
@@
 \includegraphics[width=3.5in]{figures/utility_ratio.eps}
-\caption{Ratio of Utility Gain DDM and Rational}
+\caption{DDM against Rational: ratio of utility gain}
 \label{utility_gain_mlisa_and_rational_ratio}
@@
 Now, we evaluate the performance of the decision profiles generated based on our data set for other communities.% which are not included in the decision tree creation process. 
-We create one thousand communities from the web services in the data set that were not involved in the decision model creation process.
-We define a distance function that measures the difference between basic features of communities, which measures the similarity of communities.
+We create 1,000 communities from the web services in the data set that were not involved in the training process of our decision model.
+We define a distance function that measures the difference between basic features of communities, which measures the similarity among communities.
 
@@
 Following its decision profile, the community can get a good estimate of the possible strategic decisions it can adopt.
-Basically, the trained profiles benefit the new web services in two ways.
+Basically, the trained profiles benefit the new communities in two ways.
 First, they provide the communities with a set of viable communities to join.
 Second, they provide an estimation of long-term utility gain for each available decision.
-In this experiment, we let communities follow the best decision within the decision tree provided to the them.
+In this experiment, we let communities follow the best decision within the decision tree provided to them.
+
+In order to evaluate the performance of the mechanism, we used \emph{Receiver Operating Characteristic (ROC) curve}, which is a graphical plot illustrating the true negative rate against the false positive rate at various threshold settings in classifier systems.
+In order to classify our communities' selection strategies correctly, for each community, we evaluated the training process by replacing the community in the set with the closest one, from which it gets the strategy profile.
+If the actions are the same and the same utility levels are gained, we classify the decision as correct.
+Otherwise, it is classified as a wrong decision.
+\emph{AUC}, the area under the \emph{ROC curve}, is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one, and the higher the number the better the solution, which reflects better performance.
+Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of the DDM decision making mechanism.
+As benchmark, we compare our method with two other methods: the \emph{rational} method and the \emph{greedy} method.
+The \emph{greedy} method only looks up the available list of communities and simply joins the community that maximizes its utility without considering any long-term strategy or other communities' acceptance scenarios.
+It is a greedy algorithm that focuses on choosing a locally optimal choice.
+
+\begin{itemize}
+  \item {\bf Rational Method:} Communities would send a join request to any available community, which will increase the utility.
+The other community would accept the join offer if its own utility gain is positive as well.
+	\item {\bf Greedy Method:} Communities do a linear search among all the available communities and send a join request to the community which results in maximum utility.
+The other community would accept the join offer if its own utility gain is positive and the utility gain does not need to be the maximum for the community receiving the join request.
+\end{itemize}
+
+Figure \ref{roc5} compares the results for all the methods.
+The \emph{rational} and \emph{greedy} methods have very high failure rates compared to our method.
+Table \ref{fail_rate} illustrates the number of communities that failed to find the optimal collaboration group.
+The results support the need for a long-term training model in a successful decision making process.
+
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/roc.eps}
+\caption{RoC Curve}
+\label{roc5}
+\end{figure}
 
@@
 
-In order to evaluate the performance of the mechanism, we used \emph{Receiver Operating Characteristic (ROC) curve}, which is a graphical plot illustrating the true negative rate against the false positive rate at various threshold settings in classifier systems.
-In order to classify our communities' selection strategies correctly, for each community, we evaluated the training process by replacing the community in the set with the closest one, from which it gets the strategy profile.
-If the actions are the same and the same utility levels are gained, we classify the decision as correct.
-Otherwise, it is classified as a wrong decision.
-\emph{AUC}, the area under the \emph{ROC curve}, is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one, and the higher number reflects better performance from the better solution.
-Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of the DDM decision making mechanism.
-We compare our method with two other methods.
-The \emph{rational} method is based on the assumption that communities, as rational agents, join a community that increases their utility.
-The \emph{greedy} method only looks up the available list of communities and simply joins the community that maximizes its utility without considering any long-term strategy or other communities' acceptance scenarios, its an greedy algorithm and chooses a locally optimal choice.
-Therefore we use these two methods as our benchmark:
-
-\begin{itemize}
-  \item {\bf Rational Method:} Communities would send a join request to any available community, which will increase the utility.
-The other community would accept the join offer if the utility gain is positive as well.
-	\item {\bf Greedy Method:} Communities do a linear search among all the available communities and send a join request to the community which results in maximum utility, The other community would accept the join offer if the utility gain is positive and the utility gain does not need to be the maximum for the community recieving the join request.
-\end{itemize}
-
-Figure \ref{roc5} compares the results for all methods.
-The two other methods have very high failure rates compared to our method.
-Table \ref{fail_rate} illustrates the number of communities that failed to find the optimal collaboration group.
-The results support the need for a long-term training model in a successful decision making process.
-
-\begin{figure}%[!t]
-\centering
-\includegraphics[width=3.5in]{figures/roc.eps}
-\caption{RoC Curve}
-\label{roc5}
-\end{figure}
 Now, we evaluate the system-specific results from users' and communities' perspectives.
-By distributing tasks among the communities over these time frames, we evaluate the revenue for each community.
+By distributing tasks among the communities over the 64 time frames, we evaluate the revenue for each community.
 Figure \ref{stats1} shows the overall revenue gain of communities using our method.
@@
 \includegraphics[width=3.5in]{figures/stats1.eps}
-\caption{Overall Utility of all communities}
+\caption{Overall utility of all the communities}
 \label{stats1}
@@
 \includegraphics[width=3.5in]{figures/stats2.eps}
-\caption{Utility Gain on time}
+\caption{Utility gain over time}
 \label{stats2}
@@
 Figure \ref{stats3} depicts the average community size over time, which essentially represents the number of new communities being formed.
-The results show once again the communities with higher search rates grow faster in size implying that the communities find appropriate web services to join with faster.
+The results show once again the communities using DDM with higher search rates grow faster in size, implying that the communities find appropriate web services to join with faster.
 
@@
 \includegraphics[width=3.5in]{figures/stats3.eps}
-\caption{Average Community Size}
+\caption{Average community size}
 \label{stats3}

### 2015-06-12 papers/webservice-coalition-learning-june-2015/figures/matlab/babak_chart_roc.m

@@ -1,0 +1,59 @@
+[v,T,vT]=xlsread('babak_data_roc.xlsx') 
+% 'xlsx' for exell 2007
+%v: Double
+%T and vT : cell
+%use v containing numbers 
+
+%set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-|:|--|-.')
+%set(0,'DefaultAxesColorOrder',[0 0 0],'DefaultAxesLineStyleOrder','-.r*|:|--|-.')
+
+i=0:49;
+it=v(:,7);iy=v(:,9);iz=v(:,15);itt=v(:,20);
+t=v(:,8);y=v(:,10);z=v(:,16);tt=v(:,21);
+%set(gcf,'Position',[100 100 800 500]);
+set(gcf,'Position',[100 100 550 375]);
+
+%subplot(1,3,1);
+
+h = plot(it,t,'--go',iy,y,'--mo',iz,z,':bs',itt,tt,'-.r*', 'MarkerSize',2);
+%set(h(1),'linewidth',3);
+grid on;
+
+%set(gca,'Xcolor',[0.5 0.5 0.5]);
+%set(gca,'Ycolor',[0.5 0.5 0.5]);
+%set(gca,'XTick',1:1:50);
+%set(gca,'YTick',7000:1500:18000);
+%set(gca,'YTick',0:200:1600);
+set(gca,'tickdir','in')
+%set(gca,'XTickLabel',{'1';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '11';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '21';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '31';' ';' ';' ';' ';' ';' ';' ';' ';' ';
+%    '41';' ';' ';' ';' ';' ';' ';' ';' ';'50';});
+set(gca,'XGrid','off','YGrid','on','ZGrid','off');
+set(gca,'YTickLabel',num2str(get(gca,'YTick').'));
+
+
+%axis([0 50 0 1600]);
+
+% Add legend
[…]

### 2015-06-25 papers/webservice-coalition-learning-june-2015/elsarticle-template-num.tex
changes

@@
 
-In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
-defined communities as \emph{Service Containers} that aggregate
-substitutable web services providing a common functionality (same
-set of operations). They abstracted \emph{Service Containers} as
-web services that are created, advertised, discovered and invoked
-just as elementary web services. The \emph{Container} is
-considered as a manager that is responsible for web service
-selection upon receiving a request on run-time. The authors have
-proposed a scoring service based on non-functional requirements of
-the request and web service capabilities to dynamically chose the
-web service to perform the requested task. A similar concept was
-proposed by Maamar et al. in
-\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
-web service communities as a collection of web services with a
-common functionality but different QoS properties. A community
-manager, upon receiving a request, delegates the request to one of
-its current members. The choice is based on the performance
-history and quality metrics of each web service. The authors have
-proposed an efficient global web service selection algorithm in
-order to approach quality constraints and preferences for
-composite services which require aggregation of different types of
-services to satisfy the user.
-
-Benslimane et al. \cite{Liris-2770} have proposed a multi-layer
-approach grouping similar Web services into communities and having
-an interface implemented as an abstract web service for accessing
-the community on top of the community layer. The interactions
-between composite, management and community layers and the
-bindings are performed by a generic driver called Open Software
-Connectivity (OSC).
-
-In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
-service communities with centralized access across distributed web
-services. They have proposed a framework for web service
-management, query resolution among communities and a query caching
-mechanism executed by the manager to improve the performance of
-query resolution process among many distributed communities. The
-key idea is to cache previous computed results for answering
-future queries.
-
-Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
-then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
-proposed an architecture utilizing \emph{Contract-Net} protocol
-for engineering task distribution within communities of web
-services. The protocol is centrally executed by the community
-manager. This architecture has been further developed in
-\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
-conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
-roles have been distinguished for community members: masters and
-slaves. Master web services and community managers that lead
-communities and are responsible for membership management. They
-can invite and convince slave web services to join the community,
-and attract new slave web services to their communities by
-awarding them better payoff. Moreover, they can eject some slave
-members from the community to improve its overall reputation if
-these members are misbehaving or cannot provide the promised QoS.
-
-In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
-developed a community as a ``cluster'' that groups Web services
-based on a specific area of interest. All web services in a given
-community share the same functionality. These communities are
-created by \emph{third party community providers} which use the
-\emph{community ontology} as a template and define a set of
-operations that all web services within a community should
-provide. Using semantic analysis on web service operations, web
-services either find and join a community with similar
-functionality or create a new operation description for a new
-community. The authors have described the concept of
-\emph{community agents} associated to \emph{community providers}.
-A community agent is responsible, among other things, of the
-registration of services with the community. An example of a
-community that provides health care services to senior citizens
-has been used. In this example, a governmental entity is needed to
-check the health care standards used by the members before
-authorizing them to be part of the community. Such a central
-entity is represented by the community agent. Thus, community
-agents are playing the role of community managers. In a close work
-\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
-global planning selection algorithm and a delegation algorithm to
-be run when a request to execute an operation is received by the
-community. This needs a central entity to run those algorithms.
-Such entity plays the same role as the community coordinator or
-manager.
-
 Most of the recent work on communities of services are either
@@
 In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.
+\\
+
+\noindent \textbf{Web Service Communities}
+
+Here we introduce the related research work regarding the engineering and formation of communities of web services.
+In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
+defined communities of web services as \emph{Service Containers} that aggregate substitutable web services providing a common functionality (same
+set of operations). They abstracted \emph{Service Containers} as web services that are created, advertised, discovered and invoked
+just as elementary web services. The \emph{Container} is
+considered as a manager that is responsible for web service
+selection upon receiving a request on run-time. The authors have
+proposed a scoring service based on non-functional requirements of
+the request and web service capabilities to dynamically chose the
+web service to perform the requested task. A similar concept was
+proposed by Maamar et al. in
+\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
+web service communities as a collection of web services with a
+common functionality but different QoS properties. A community
+manager, upon receiving a request, delegates the request to one of
+its current members. The choice is based on the performance
+history and quality metrics of each web service. The authors have
+proposed an efficient global web service selection algorithm in
+order to approach quality constraints and preferences for
+composite services which require aggregation of different types of
+services to satisfy the user.
+
+Benslimane et al. \cite{Liris-2770} have proposed a multi-layer
+approach grouping similar Web services into communities and having
+an interface implemented as an abstract web service for accessing
+the community on top of the community layer. The interactions
+between composite, management and community layers and the
+bindings are performed by a generic driver called Open Software
+Connectivity (OSC).
+
+In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
+service communities with centralized access across distributed web
+services. They have proposed a framework for web service
+management, query resolution among communities and a query caching
+mechanism executed by the manager to improve the performance of
+query resolution process among many distributed communities. The
+key idea is to cache previous computed results for answering
+future queries.
+
+Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
+then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
+proposed an architecture utilizing \emph{Contract-Net} protocol
+for engineering task distribution within communities of web
+services. The protocol is centrally executed by the community
+manager. This architecture has been further developed in
+\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
+conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
+roles have been distinguished for community members: masters and
+slaves. Master web services and community managers that lead
+communities and are responsible for membership management. They
+can invite and convince slave web services to join the community,
+and attract new slave web services to their communities by
+awarding them better payoff. Moreover, they can eject some slave
+members from the community to improve its overall reputation if
+these members are misbehaving or cannot provide the promised QoS.
+
+In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
+developed a community as a ``cluster'' that groups Web services
+based on a specific area of interest. All web services in a given
+community share the same functionality. These communities are
+created by \emph{third party community providers} which use the
+\emph{community ontology} as a template and define a set of
+operations that all web services within a community should
+provide. Using semantic analysis on web service operations, web
+services either find and join a community with similar
+functionality or create a new operation description for a new
+community. The authors have described the concept of
+\emph{community agents} associated to \emph{community providers}.
+A community agent is responsible, among other things, of the
+registration of services with the community. An example of a
+community that provides health care services to senior citizens
+has been used. In this example, a governmental entity is needed to
+check the health care standards used by the members before
+authorizing them to be part of the community. Such a central
+entity is represented by the community agent. Thus, community
+agents are playing the role of community managers. In a close work
+\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
+global planning selection algorithm and a delegation algorithm to
+be run when a request to execute an operation is received by the
+community. This needs a central entity to run those algorithms.
+Such entity plays the same role as the community coordinator or
+manager.
 

### 2015-06-28 papers/webservice-coalition-learning-submitted-r0/elsarticle-template-num.tex
changes

--- 2015-06-25 papers/webservice-coalition-learning-june-2015/elsarticle-template-num.tex
@@
 \author{
-    \IEEEauthorblockN{\normalsize Ehsan Khosrowshahi Asl\IEEEauthorrefmark{1}, Babak Khosravifar\IEEEauthorrefmark{1}, Jamal Bentahar\IEEEauthorrefmark{1}, Hadi Otrok\IEEEauthorrefmark{2}, Rabeb Mizouni\IEEEauthorrefmark{2}}\\
+    \IEEEauthorblockN{\normalsize Ehsan Khosrowshahi Asl\IEEEauthorrefmark{1}, Jamal Bentahar\IEEEauthorrefmark{1}, Hadi Otrok\IEEEauthorrefmark{2}, Babak Khosravifar\IEEEauthorrefmark{1}, Rabeb Mizouni\IEEEauthorrefmark{2}}\\
     \IEEEauthorblockA{\IEEEauthorrefmark{1}Concordia Institute for Information Systems Engineering, Concordia University, Montreal, Canada}
@@
 }
-\title{Distributed Decision Making for Dynamic Formation of Web Services Communities}
+\title{Distributed Decision Making for Dynamic Formation of Communities of Web Services}
 
@@
 This model first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
-The decision making mechanism implements a decision tree of possible viable strategies and their long-term expected utility gain.
+The decision making mechanism is implemented as a decision tree of viable strategies and their long-term expected utility gain.
 %Utilizing the training model, the decision making mechanism implements a decision tree with an estimation of long-term utility gain for the web services.
@@
 \begin{IEEEkeywords}
-Web services; Community of services; Distributed decision making;
+Web services; Community of services; Distributed decision making
 \end{IEEEkeywords}
@@
 The problem is that in real world scenarios, decisions made by independent service providers are highly distributed.
-	\item The solutions either propose complex algorithms \cite{10.1109/TSC.2012.12, DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2014.2312940} to find the optimal strategy to follow, or oversimplify the problem by eliminating important parameters and using approximation techniques to make the algorithms tractable \cite{10.1109/TSC.2012.12}.
+	\item The solutions either propose complex algorithms \cite{10.1109/TSC.2012.12, DBLP:conf/IEEEscc/LimTMB12, journal-community-formation} to find the optimal strategy to follow, or oversimplify the problem by eliminating important parameters and using approximation techniques to make the algorithms tractable \cite{10.1109/TSC.2012.12}.
 \end{enumerate}
@@
 \subsection{The Join Challenge}\label{s:tjc} 
-It has been showed in \cite{10.1109/ARES.2008.7,10.1109/TSC.2012.12,10.1109/TSC.2014.2312940} that web services can increase their overall utility by collaborating with other web services within communities.
+It has been showed in \cite{10.1109/ARES.2008.7,10.1109/TSC.2012.12,journal-community-formation} that web services can increase their overall utility by collaborating with other web services within communities.
 This collaboration provides them with better ways of sharing resources and having higher reputation, greater market share and wider visibility.
@@
 \begin{figure}%[!t]
-\centerline{\includegraphics[width=5.25in]{figures/steps.eps}}
+\centerline{\includegraphics[width=5.25in]{figures/steps-final.eps}}
 \caption{A summary of DDM decision profile generation steps}
@@
 In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
-autonomous web services based on coalitional game theory has been
+autonomous web services based on coalition game theory has been
 introduced. The authors have proposed an interesting algorithm to
@@
 the availability is high, which is the case nowadays with the
-recent advancements in cloud and hardware infrastructures, the
+recent advancements in cloud infrastructures and hardware technologies, the
 backup web services will end-up having a very low chance of
@@
 All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process.
-So basically These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.
+So basically, these solutions generally suffer from high complexity, which makes decision making very hard, even impossible in some cases in a real-time fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.
 We address this issue by introducing DDM a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another.
 After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics.
-Therefore web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
+Therefore, web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
 In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.
@@
 In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
-defined communities of web services as \emph{Service Containers} that aggregate substitutable web services providing a common functionality (same
-set of operations). They abstracted \emph{Service Containers} as web services that are created, advertised, discovered and invoked
-just as elementary web services. The \emph{Container} is
-considered as a manager that is responsible for web service
-selection upon receiving a request on run-time. The authors have
-proposed a scoring service based on non-functional requirements of
-the request and web service capabilities to dynamically chose the
-web service to perform the requested task. A similar concept was
-proposed by Maamar et al. in
-\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
-web service communities as a collection of web services with a
-common functionality but different QoS properties. A community
-manager, upon receiving a request, delegates the request to one of
-its current members. The choice is based on the performance
-history and quality metrics of each web service. The authors have
-proposed an efficient global web service selection algorithm in
-order to approach quality constraints and preferences for
-composite services which require aggregation of different types of
-services to satisfy the user.
-
-Benslimane et al. \cite{Liris-2770} have proposed a multi-layer
-approach grouping similar Web services into communities and having
-an interface implemented as an abstract web service for accessing
-the community on top of the community layer. The interactions
-between composite, management and community layers and the
-bindings are performed by a generic driver called Open Software
-Connectivity (OSC).
+defined communities of web services as \emph{Service Containers} that aggregate substitutable web services having the same set of operations and providing common functionalities.
+They abstracted \emph{Service Containers} as web services that are created, advertised, discovered and invoked just as elementary web services.
+The \emph{Container} is considered as a manager that is responsible for web service selection upon receiving a request on run-time.
+The authors have proposed a scoring technique based on non-functional requirements of the request and web service capabilities to dynamically chose the web service to perform the requested task.
+A similar concept was proposed by Maamar et al.
+in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+The authors introduced web service communities as a collection of web services with a common functionality but different QoS properties.
+A community manager, upon receiving a request, delegates the request to one of its current members.
+The choice is based on the performance history and quality metrics of each web service.
+The authors have proposed an efficient global web service selection algorithm in order to approach quality constraints and preferences for composite services which requires aggregation of different types of services to satisfy the user.
+In the same line of research, Benslimane et al.
+\cite{Liris-2770} have proposed a multi-layer approach grouping similar web services into communities and having an interface implemented as an abstract web service for accessing the community.
+The considered layers are: composite, management and community.
+The interactions among those layers and the bindings are performed by a generic driver called Open Software Connectivity (OSC).
+However, unlike our work, these proposals only tackle the problem of internal community management from the task execution perspective, but not the problem of community formation and the one of dynamically selecting which community to join and which web service to invite.
+Moreover, the web services selection process is done centrally by the community manager, while we address the problem more realistically from the distributed angle.
 
@@
 key idea is to cache previous computed results for answering
-future queries.
-
-Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
+future queries. Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
 then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
@@
 services. The protocol is centrally executed by the community
-manager. This architecture has been further developed in
+manager. This architecture has been further extended in
 \cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
@@
 roles have been distinguished for community members: masters and
-slaves. Master web services and community managers that lead
+slaves. Master web services are community managers that lead
 communities and are responsible for membership management. They
@@
 these members are misbehaving or cannot provide the promised QoS. 
-
 In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
@@
 Such entity plays the same role as the community coordinator or
-manager.
+manager. All these proposals have in common the consideration 
+of the central entity for community management, which includes the hiring and firing of the community members, while our approach is fully distributed.
+Moreover, the stability of the community has not been investigated.
+Another major difference with our work is that the decision making process is only one way and unilateral from the community manager perspective.
+In our proposal, both participants, namely communities and web services, participate in the decision making process and a joining decision is made only if it is the best option for both players.
 
@@
 
-In this paper, we proposed a training model for the problem of membership management of communities of web services.
-Using the traning model we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves.
-This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available.
-The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices.
-The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.
+In this paper, we proposed DDM, a strategic distributed decision making mechanism that regulates the community formation process and  membership management in communities of web services.
+This mechanism helps web services and communities decide with whom to be grouped and cooperate.
+DDM first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
+Communities and web services can use the trained model and instantly choose best-response strategies considering their long-term gain.
+In fact, the decision making mechanism is implemented as a decision tree of possible viable strategies along with their long-term expected utility.
+The ultimate goal of our mechanism is to choose the best decision when it comes to community formation, which goes beyond short-term utility increasing choices, usually considered in the literature.
+The experimental results show that our approach allows web services and communities, in real-world-like environments, to make near-perfect decisions.
 The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.
 
-Our plan for future work is to advance learning process on the training set that we provided in our work.
-SVN machine learning algorithm are suitable in classification of our training data set, to better classify correct or wrong decisions based on long-term utility gains, as data set outputs.
+Our plan for future work is to advance further the learning process on the training set we provided in our work by leveraging some game theoretical approaches.
+In fact, game theory provides powerful techniques for strategic decision making, particularly cooperative and coalition formation games.
+Hedonic games and fractional hedonic games are of particular interest where the utility of a player in a community depends on the identity of the other members of the community and the value this player ascribes to those members.
+We intent to investigate stability solution concepts such as Shapely value so that long-term decisions will be based on the probability that the community will stay for long period.
+
+%The SVM machine learning algorithm is suitable for classification of our training data set to better distinguish  decisions based on long-term utility, as data set outputs.
 This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.
@@
 \bibliographystyle{elsarticle-num} 
-\bibliography{Ehsan}
+\bibliography{Ehsan1}
 

### 2015-06-29 thesis/thesis/chap1/chap1.tex
changes

--- 2015-04-22 thesis/thesis/chap1/chap1.tex
@@
 \chapter{Introduction}\label{sec:intro}
-[Proposal] In this chapter, we introduce the context of this research, which
+In this chapter, we introduce the context of this research, which
 is about communities of web services abstracted as autonomous
@@
 but probably different non-functional quality attributes, which
-form the QoS parameters. When communities are used, users send
-their requests to the masters of those communities, which are
-responsible of managing the communities, forwarding the requests
-to the suitable member web services and checking the credentials
-of those members. Communities aim to provide higher service
+form the QoS parameters.
+%When communities are used, users send
+%their requests to the masters of those communities, which are
+%responsible of managing the communities, forwarding the requests
+%to the suitable member web services and checking the credentials
+%of those members.
+Communities aim to provide higher service
 availability and performance than what individual web services can
-provide. The high availability of services and the community
-resilience to failure are guaranteed since web services can
-cooperate and replace each other within the same community and
-since there is no single point of failure in the communities
-architecture.
+provide.
+%The high availability of services and the community
+%resilience to failure are guaranteed since web services can
+%cooperate and replace each other within the same community and
+%since there is no single point of failure in the communities
+%architecture.
 
@@
 
+Within communities, services can exhibit competitive behavior as they provide the same functionalities and the number of users requests is finite.
+However, for the same reason of being functionally similar, services can cooperate with each other, for example to substitute each other in order to perform some sub-tasks.
+So as an extension of our work, we have proposed a framework in which services can opt for performing tasks if they feel they are capable enough
+or decide to cooperate by showing the availability to perform some sub-tasks. \emph{How can we approach a cooperative model within a community where both competitive and cooperative behaviors exist?}
+
+In most of the recent work on communities of web service, the solutions consider the architecture of centralized management for communities where most of the decisions are made by the centralized coordinator.
+The problem is that in real world scenarios, decisions made by independent service providers are highly distributed.
+\emph{How can we model a distributed decision making process for formation of communities of services?}
+
+Also in all of the mentioned works, the community manager as a centralized entity, has complete information of all the web services and their quality.
+However, centrality and complete information are strong assumptions, which are not very compatible with real business scenarios.
+\emph{How can we train web services based on smaller set of information to operate efficiently when information is non-complete?}
+
 % ooooooold
@@
 
+In order to address the centralized decision making process limitations and adopt a distributed decision making approach, we introduce DDM, a Distributed Decision Making model for community formation.
+DDM regulates web service agents’ decision making process in terms of cooperating and deciding which group to join and which service to invite for joining.
+Unlike existing work on community formation, our decision model is extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
+The generated decision tree improves agents' understanding of the environment and how to select actions that lead towards maximizing their utilities.
+The advantage of this approach is that the tree, which is initially created from the past data, reflects a comprehensive vision about agents' attitudes in terms of their action selection based on their past experiences.
+Moreover, the tree is getting continuously updated based on both new received feedback and the outcome of chosen actions.
+This continuous update makes the approach adapted to any change in the environment.
+%The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems.
+The decision model provides web services with enough information which helps those services efficiently decide and predict the outcome of their different possible collaborations.
+This model works in a distributed manner in which services are self-sufficient in their decision making and do not rely on a centralized decision making process.
+Our findings show that communities of web services can efficiently find the appropriate web service to invite for cooperation as well as allowing a single web service to find the best communities to join.
+The proposed model can be seen as a recommneder system that suggests beneficial actions for both communities and single services.
+Communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
+In general, DDM equips web services with efficient methods for foreseeing how their choices will impact both their short-term and long-term goals; therefore, opting for the best decision available.
+
+To effectively generate the decision model for web services, we used a real dataset to extract web services' individual characteristics and used them to measure outcomes when these services cooperate with one another.
+The dataset has been extracted from real-world QoS evaluation results from 142 users on 4,532 Web services during 64 different time slots.
+Combining the available data based on each web service point of view on different time slots, we acquired 5 different unique features for those 4,532 web services.
+By engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in different time slots.
+We were able to investigate the path a web service might take to achieve the best utility out of effective interactions with others.
+All the paths and outcomes are labeled to be utilized in the training model.
+Using cross validation sets, web services are able to compute the optimal hypothesis function (using logistic regression) that can be used to predict outcomes of cooperative work with other individual web services or communities.
+Our findings show that web services equipped with DDM have by far better outcomes than the ones that either do not cooperate or randomly find communities to join.
+
 \indent To summarize, the main problem we aim to tackle in this
@@
 
-\item To reduce the complexity of computing the solution concepts
-of the cooperative model tailored to the problem of communities of
-agent-based web services in order to make these solutions
-applicable in real world scenarios.
+\item To reduce the complexity of computing the solution concepts of the cooperative model tailored to the problem of communities of agent-based web services in order to make these solutions applicable in real world scenarios.
 
-\item To analyze the effect of different membership and taxation
-models that the master can apply to the members on the stability
-of the community.
+\item To analyze the effect of different membership and taxation models that the master can apply to the members on the stability of the community.
 
-\item To investigate the impact of learning on individual and
-group decision making within the cooperative model of the
-community.
+\item To investigate the impact of learning on individual and group decision making within the cooperative model of the community.
 
-\item To validate the proposed methods by extensive simulations
-and comparison with other similar proposals.
+\item To approach the community decision making process in a distributed manner and train agents so they can operate efficiently when information is non-complete.
+
+\item To validate the proposed methods by extensive simulations and comparison with other similar proposals.
 \end{itemize}
 
-\section{Proposal Organization}\label{sec:outline}
-The rest of the proposal is organized as follows: We present in
-Chapter 111 the background needed for our research along
-with relevant related work. Chapter 222
-provides the problem statement and presents our solution model in
-two different scenarios with some preliminary results. Finally, in
-Chapter 333, we present our conclusion,
-future plan, and the timetable of our research.
+\begin{figure}[!t]
+\centering
+\includegraphics[width=6in]{Figures/structure.eps}`
+\caption{The Proposed Framework}
+\label{fig_structure}
+\end{figure}
 
-\section{Context of Research}\label{sec:motivation_s}
+Figure \ref{fig_structure} highlights our contributions and proposed model for community of web service management.
 
-[seminar] Over the past years, online services have become part of many
-scalable business applications. The increasing reliance on
-web-based applications has significantly influenced the way web
-services are engineered.
-%Web services provide a set of stateless
-%software functions accessible at a network address over the web.
-%The recent developments are shifting web services from passive and
-%individual components to autonomous and group-based components
-%where interaction, composition, and cooperation are the key
-%challenges \cite{ICWS2011-1,SCC2011-1}. The main objective is to
-%achieve a seamless integration of business processes, applications
-%and web services. Delivering high quality services considering the
-%dynamic and unpredictable nature of the Internet is still a very
-%critical and challenging issue.
-%Typically, web services are business applications deployed as
-%autonomous and interoperable agents \cite{Alescio}. In fact, the
-%W3C consortium defines a web service as ``an abstract notion that
-%must be implemented by a concrete agent''. However, the web is
-%stocked with agent-based services that offer similar business
-%functionalities, which leads to service consumers having
-%difficulties in choosing the most appropriate agents to interact
-%with.
-The need for highly available and responsive services has called
-for grouping and collaborative mechanisms of loosely-coupled web
-services, particularly in business settings. The idea of grouping
-web services within communities and the way those communities are
-engineered so that web services can better collaborate have been
-proposed and investigated in
-\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
-Communities are virtual groups of web services having similar
-functionalities \cite{Zeng:2003:QDW:775152.775211,
-Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7},
-but probably different non-functional quality attributes, which
-form the QoS parameters.
-%When communities are used, users send
-%their requests to the masters of those communities, which are
-%responsible of managing the communities, forwarding the requests
-%to the suitable member web services and checking the credentials
-%of those members.
-Communities aim to provide higher service
-availability and performance than what individual web services can
-provide.
-%The high availability of services and the community
-%resilience to failure are guaranteed since web services can
-%cooperate and replace each other within the same community and
-%since there is no single point of failure in the communities
-%architecture.
+\section{Thesis Organization}\label{sec:outline}
+The rest of the proposal is organized as follows: We present in Chapter 2 the background needed for our research along with relevant related work.
+Chapter 3 provides an efficient method of coalition formation for web services.
+In chapter 4 we discuss the cooperative behaviour within the communities of web services.
+Chapter 5 presents a distributed method of formation of web services communities.
+Finally in chapter 6, we present our conclusion and future plan.
 
-\section{Motivation and Research Objectives}\label{sec:motexample_s}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Web service communities are dynamic by design
-\cite{DBLP:journals/ijebr/MaamarSTBB09}. In these communities, web
-services are modeled as intelligent autonomous agents, where they
-can adopt a strategy maximizing their payoff at any time. A web
-service can ask joining a community and has the right to leave it.
-Community managers can invite or ask a web service to leave in
-order to maximize the community profit. Users can simply stop
-sending requests to a web service which is not providing
-satisfactory services. Thus it is important to consider all the
-parties involved in the decision making process about the
-community management.
-
-In this research work, our first objective is to propose a
-cooperative model as game for the aggregation of web services
-within communities. The solution concepts of our cooperative game
-seeks to find efficient ways of forming coalitions (teams) of web
-services so that they can maximize their gain and payoff, and
-distribute the gain in a fair way among all the member services.
-Achieving Fairness when the gain is distributed among the
-community members is the main factor to keep the coalition stable
-as no web service will expect to gain better by deviating from the
-community. In other words, the coalition is made efficient if all
-the members are satisfied. We first propose a representation
-function for communities of web services based on their QoS
-attributes. By using this function, we can evaluate the $worth$ of
-each community of web services. When facing new membership
-requests, a typical community master checks whether the new
-coalition having the old and new set of web services will keep the
-community stable or not. The community master will reject the
-membership requests if it finds out that the new coalition would
-be unstable, preventing $any$ subset of web services from gaining
-significantly more by deviating from the community and joining
-other communities or forming new ones. The computation of
-solutions for cooperative games is combinatorial in nature and
-proven to be NP-complete \cite{Algorithmic}, making this
-computation impractical in real world applications. However, using
-the concepts of coalition stability, the second objective is to
-investigate approximation algorithms running in polynomial time
-providing web services and community masters with applicable and
-near-optimal decision making mechanisms.
-
-Within communities, services can exhibit competitive behavior as they provide the same functionalities and the number of users requests is finite.
-However, for the same reason of being functionally similar, services can cooperate with each other, for example to substitute each other in order to perform some sub-tasks.
-So as an extension of our work, we have proposed a framework in which services can opt for performing tasks if they feel they are capable enough
-or decide to cooperate by showing the availability to perform some sub-tasks.
-We have implemented an online learning mechanism for services with different capabilities to learn over time which strategy to choose based on their own and other services status and capabilities.
+%
+%\section{Context of Research}\label{sec:motivation_s}
+%
+%[seminar] Over the past years, online services have become part of many
+%scalable business applications. The increasing reliance on
+%web-based applications has significantly influenced the way web
+%services are engineered.
+%%Web services provide a set of stateless
+%%software functions accessible at a network address over the web.
+%%The recent developments are shifting web services from passive and
+%%individual components to autonomous and group-based components
+%%where interaction, composition, and cooperation are the key
+%%challenges \cite{ICWS2011-1,SCC2011-1}. The main objective is to
+%%achieve a seamless integration of business processes, applications
+%%and web services. Delivering high quality services considering the
+%%dynamic and unpredictable nature of the Internet is still a very
+%%critical and challenging issue.
+%%Typically, web services are business applications deployed as
+%%autonomous and interoperable agents \cite{Alescio}. In fact, the
+%%W3C consortium defines a web service as ``an abstract notion that
+%%must be implemented by a concrete agent''. However, the web is
+%%stocked with agent-based services that offer similar business
+%%functionalities, which leads to service consumers having
+%%difficulties in choosing the most appropriate agents to interact
+%%with.
+%The need for highly available and responsive services has called
+%for grouping and collaborative mechanisms of loosely-coupled web
+%services, particularly in business settings. The idea of grouping
+%web services within communities and the way those communities are
+%engineered so that web services can better collaborate have been
+%proposed and investigated in
+%\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
+%Communities are virtual groups of web services having similar
+%functionalities \cite{Zeng:2003:QDW:775152.775211,
+%Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7},
+%but probably different non-functional quality attributes, which
+%form the QoS parameters.
+%%When communities are used, users send
+%%their requests to the masters of those communities, which are
+%%responsible of managing the communities, forwarding the requests
+%%to the suitable member web services and checking the credentials
+%%of those members.
+%Communities aim to provide higher service
+%availability and performance than what individual web services can
+%provide.
+%%The high availability of services and the community
+%%resilience to failure are guaranteed since web services can
+%%cooperate and replace each other within the same community and
+%%since there is no single point of failure in the communities
+%%architecture.
+%
+%
+%\section{Motivation and Research Objectives}\label{sec:motexample_s}
+%
+%Web service communities are dynamic by design
+%\cite{DBLP:journals/ijebr/MaamarSTBB09}. In these communities, web
+%services are modeled as intelligent autonomous agents, where they
+%can adopt a strategy maximizing their payoff at any time. A web
+%service can ask joining a community and has the right to leave it.
+%Community managers can invite or ask a web service to leave in
+%order to maximize the community profit. Users can simply stop
+%sending requests to a web service which is not providing
+%satisfactory services. Thus it is important to consider all the
+%parties involved in the decision making process about the
+%community management.
+%
+%In this research work, our first objective is to propose a
+%cooperative model as game for the aggregation of web services
+%within communities. The solution concepts of our cooperative game
+%seeks to find efficient ways of forming coalitions (teams) of web
+%services so that they can maximize their gain and payoff, and
+%distribute the gain in a fair way among all the member services.
+%Achieving Fairness when the gain is distributed among the
+%community members is the main factor to keep the coalition stable
+%as no web service will expect to gain better by deviating from the
+%community. In other words, the coalition is made efficient if all
+%the members are satisfied. We first propose a representation
+%function for communities of web services based on their QoS
+%attributes. By using this function, we can evaluate the $worth$ of
+%each community of web services. When facing new membership
+%requests, a typical community master checks whether the new
+%coalition having the old and new set of web services will keep the
+%community stable or not. The community master will reject the
+%membership requests if it finds out that the new coalition would
+%be unstable, preventing $any$ subset of web services from gaining
+%significantly more by deviating from the community and joining
+%other communities or forming new ones. The computation of
+%solutions for cooperative games is combinatorial in nature and
+%proven to be NP-complete \cite{Algorithmic}, making this
+%computation impractical in real world applications. However, using
+%the concepts of coalition stability, the second objective is to
+%investigate approximation algorithms running in polynomial time
+%providing web services and community masters with applicable and
+%near-optimal decision making mechanisms.
+%
+%Within communities, services can exhibit competitive behavior as they provide the same functionalities and the number of users requests is finite.
+%However, for the same reason of being functionally similar, services can cooperate with each other, for example to substitute each other in order to perform some sub-tasks.
+%So as an extension of our work, we have proposed a framework in which services can opt for performing tasks if they feel they are capable enough
+%or decide to cooperate by showing the availability to perform some sub-tasks.
+%
+%%We have implemented an online learning mechanism for services with different capabilities to learn over time which strategy to choose based on their own and other services status and capabilities.
 After establishing states of our model and observing convincing results from our learning method, we plan to extend the learning process using reinforcement learning (Q-learning) techniques.
-
-\indent To summarize, the main problems we aim to tackle in this
-thesis are the formation of stable and efficient coalitions
-maximizing web services and community revenue and the decision over the strategy to play about competing or cooperating.
-The main objectives are:
-\begin{itemize}
-\item To propose a cooperative model and analyze its solution
-concepts in order to address the problem of optimizing coalition
-formation for a stable community.
-
-\item To reduce the complexity of computing the solution concepts
-of the cooperative model tailored to the problem of communities of
-agent-based web services in order to make these solutions
-applicable in real world scenarios.
-
-\item To analyze the effect of different membership and taxation
-models that the master can apply to the members on the stability
-of the community.
-
-\item To investigate the impact of learning on individual and
-group decision making within the cooperative model of the
-community.
-
-\item To validate the proposed methods by extensive simulations
-and comparison with other similar proposals.
-\end{itemize}
-
-\section{Report Organization}\label{sec:outline_s}
-The rest of the report is organized as follows. We present in
-Chapter 111 the background needed for our research along
-with relevant related work. Chapter 222
-provides the problem statement and presents our solution model in
-two different scenarios with some preliminary results. Finally, in
-Chapter 333, we present our conclusion,
-future plan, and the timetable of our research.
+%
+%
+%
+%\indent To summarize, the main problems we aim to tackle in this
+%thesis are the formation of stable and efficient coalitions
+%maximizing web services and community revenue and the decision over the strategy to play about competing or cooperating.
+%The main objectives are:
+%\begin{itemize}
+%\item To propose a cooperative model and analyze its solution
+%concepts in order to address the problem of optimizing coalition
+%formation for a stable community.
+%
+%\item To reduce the complexity of computing the solution concepts
+%of the cooperative model tailored to the problem of communities of
+%agent-based web services in order to make these solutions
+%applicable in real world scenarios.
+%
+%\item To analyze the effect of different membership and taxation
+%models that the master can apply to the members on the stability
+%of the community.
+%
+%\item To investigate the impact of learning on individual and
+%group decision making within the cooperative model of the
+%community.
+%
+%\item To validate the proposed methods by extensive simulations
+%and comparison with other similar proposals.
+%\end{itemize}
+%
+%
+%
+%
+%\section{Thesis Organization}\label{sec:outline_s}
+%The rest of the thesis is organized as follows. We present in
+%Chapter 111 the background needed for our research along
+%with relevant related work. Chapter 222
+%provides the problem statement and presents our solution model in
+%two different scenarios with some preliminary results. Finally, in
+%Chapter 333, we present our conclusion,
+%future plan, and the timetable of our research.
+%
+%
+%

### 2015-06-29 thesis/thesis/chap5/chap5.tex
changes

--- 2015-04-22 thesis/thesis/chap5/chap5.tex
@@
-\chapter{LEarning Chapter}\label{cha:PCTLKC+}
+\setcounter{chapter}{4}
 
-In this chapter
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter{Distributed Decision Making for Dynamic Formation of Web Services Communities}\label{cha:PCTLKC}
 
-\section{Summary}\label{sec:conclusion}
+\section{Introduction}
 
-In this chapter,
+Over the past years, online services have become an important part of many scalable business applications.
+The increasing reliance on online service providers has significantly influenced the way web services are engineered.
+Given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue.
+One practical solution towards delivering such quality services is utilizing intelligent decision making agents.
+These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users \cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Demirkan2013412, journals/tsc/ZhengZYB13, Josang:2007:STR:1225318.1225716}.
+However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided.
+Recent developments have attempted to shift web services from simple models, consisting of individual components, to models made up of autonomous and group-based components that share common goals.
+In group-based models, interaction, composition, and cooperation are the key challenges that directly impact the group's overall performance in achieving common goals \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13}.
+To that end, we see the emergence of web service \emph{communities}, which consist of grouping services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic}.
+A community of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.
+
+Web Service communities have the advantages of facilitating web service discovery and providing better quality of service compared to individual services.
+Communities act as abstract web services, communicating with external entities via the same standard protocols that a normal web service employs.
+The difference is that communities regulate the service process via sophisticated internal communication protocols, thereby providing services based on the combined efforts of a number of web services.
+The downside to communities is the complexity of management involved in finding and inviting adequate individual services and managing the overall quality of the combined work of several services.
+% because although they have similar functionality, they have different attitudes.
+When interacting with a community of web services, users send their requests to the coordinator of the community, which plays the role of community representative or access point.
+The community coordinator is responsible of receiving tasks and delivering services.
+Moreover, as community representative, it verifies the credentials of new web services before accepting them into the community and kicks services that could harm the value of the community.
+
+\textbf{Challenges and Problem Statement.} In recent work, communities of web services have been proposed in order to facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities \cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic}.
+However,  two important challenges are to be addressed: 1) choice of the best web services during community development from the community perspective; and 2) choice of the best community to join from the web service perspective.
+The advocated solutions  \cite{10.1109/ARES.2008.7, conf/webist/MaamarLBTS07, journals/soca/XuYLZB11, 10.1109/TSC.2012.12, managing-hela-jalel, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:conf/IEEEscc/LimTMB12} have attempted to address these challenges.
+However, those solutions have two main limits:
+\begin{enumerate}
+	\item The solutions consider the architecture of centralized management for communities where most of the decisions are made by the centralized coordinator.
+The problem is that in real world scenarios, decisions made by independent service providers are highly distributed.
+	\item The solutions either propose complex algorithms \cite{10.1109/TSC.2012.12, DBLP:conf/IEEEscc/LimTMB12, journal-community-formation} to find the optimal strategy to follow, or oversimplify the problem by eliminating important parameters and using approximation techniques to make the algorithms tractable \cite{10.1109/TSC.2012.12}.
+\end{enumerate}
+These approximation methods sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored.
+For instance, instead of calculating the gain distribution using the adequate, but complex shapely-value method, the authors is \cite{10.1109/TSC.2012.12} propose a simple egalitarian way of distributing gain, which completely ignores the gain generated from collaborative work of sub-communities.
+Other categories of related work, for instance \cite{10.1109/TSC.2012.12, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:journals/ijebr/MaamarSTBB09}, restrict the decision process within the community coordinator, so other members of the community are not effectively involved.
+%And some other work which do not focus on rationality on web services or communities involved [refrences].
+In \cite{journal-community-formation}, we proposed a cooperative game-theory-based model for aggregating web services in communities.
+A centralized decision maker in communities, based on a complete knowledge of available web service quality metrics and performance, has been used to form optimal and stable communities that maximize individual and group income.
+However, centrality and complete information are strong assumptions, which are not very compatible with real business scenarios.
+
+\textbf{Contributions.} In this paper, we introduce DDM, a Distributed Decision Making model for community formation that regulates web service agents’ decision making process in terms of cooperating and deciding which group to join and which service to invite for joining.
+Unlike existing work on community formation, our decision model is extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
+The generated decision tree improves agents' understanding of the environment and how to select actions that lead towards maximizing their utilities.
+The advantage of this approach is that the tree, which is initially created from the past data, reflects a comprehensive vision about agents' attitudes in terms of their action selection based on their past experiences.
+Moreover, the tree is getting continuously updated based on both new received feedback and the outcome of chosen actions.
+This continuous update makes the approach adapted to any change in the environment.
+%The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems.
+The decision model provides web services with enough information which helps those services efficiently decide and predict the outcome of their different possible collaborations.
+This model works in a distributed manner in which services are self-sufficient in their decision making and do not rely on a centralized decision making process.
+Our findings show that communities of web services can efficiently find the appropriate web service to invite for cooperation as well as allowing a single web service to find the best communities to join.
+The proposed model can be seen as a recommneder system that suggests beneficial actions for both communities and single services.
+Communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
+In general, DDM equips web services with efficient methods for foreseeing how their choices will impact both their short-term and long-term goals; therefore, opting for the best decision available.
+
+To effectively generate the decision model for web services, we used a real dataset to extract web services' individual characteristics and used them to measure outcomes when these services cooperate with one another.
+The dataset has been extracted from real-world QoS evaluation results from 142 users on 4,532 Web services during 64 different time slots.
+Combining the available data based on each web service point of view on different time slots, we acquired 5 different unique features for those 4,532 web services.
+By engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in different time slots.
+We were able to investigate the path a web service might take to achieve the best utility out of effective interactions with others.
+All the paths and outcomes are labeled to be utilized in the training model.
+Using cross validation sets, web services are able to compute the optimal hypothesis function (using logistic regression) that can be used to predict outcomes of cooperative work with other individual web services or communities.
+Our findings show that web services equipped with DDM have by far better outcomes than the ones that either do not cooperate or randomly find communities to join.
+
+\section{Preliminaries and Challenging Issues}\label{s4:preliminaries}
+%In this section, we first present the architecture of DDM.
+We explore the characteristics of intelligent service agents and the features we extract for training.
+To do this, we first discuss some preliminaries.
+In this section, we discuss the preliminary concepts of communities of web services and introduce the challenges behind community formation.
+
+\subsection{Web Services}\label{s:ws}
+
+In the recent years, online services have become a standard part of daily life around the globe.
+Many modern applications rely on web services from different providers.
+For instance, many mobile and tablet applications that have limited storage and processing power are merely aggregating information from different online services.
+Examples are vast, including weather forecasting, ticket selling, shopping apps, local maps and location services.
+
+The World Wide Web Consortium (W3C) defines web services as ``software systems designed to support interoperable machine-to-machine interaction over a network.
+It has an interface described in a machine-processable format (specifically WSDL).
+Other systems interact with the web service in a manner prescribed by its description using SOAP messages, typically conveyed using HTTP with XML serialization in conjunction with other Web-related standards''.
+When developers declare a new web service, it will be
+discovered based on its description, which fully discloses its functionalities.
+Developers also have to declare a public interface and a readable documentation to help other developers when integrating different services \cite{w3cwsdl}.
+Nowadays, web API, standards that do not require XML-based web service protocols like SOAP and WSDL are also emerging.
+They are called RESTful (representational state transfer) services, which are moving towards simpler communication protocols.
+%They are not restricted
+%to XML formats, recently JSON, a human readable and simpler format
+%is becoming popular among online service providers.
+
+We are not going to delve into the engineering details of online web service implementation and its protocols in this paper.
+We are interested in web services from a business model perspective.
+Service providers usually charge end users for services they provide.
+For example, Google has listed pricing and plans for a wide range of services they provide on their web service console page\footnote{$https://code.google.com/apis/console$}.
+
+As in other proposals \cite{journals/mags/BaldoniBM10,10.1109/TSC.2012.12,DBLP:conf/IEEEscc/KhosravifarABT11}, in this paper, we abstract web services as rational agents\footnote{The term rational is used here in the sense that web services are utility maximizers.} that provide services to end users.
+They aim to maximize their individual income  by receiving enough requests from end users.
+In order to increase their revenues, web services seek for more tasks if they have the capacity and throughput to do so.
+Web services can join communities to enhance efficiency by collaborating with others, to have access to broad market share, and for the opportunity to receive a bigger task pool from end users.
+Furthermore, the high reliance on web services has resulted in increased quality expectations from end users.
+Communities of web services can provide higher availability, performance, reliability, and recovery for end users.
+
+\subsection{Web Service Communities}\label{s:wsc}
+
+The community of web services is essentially a virtual group of web services having similar functionalities \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+Communities aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols to those used by single web services.
+Web services join communities to increase utility by having a larger market share and task pool.
+The community coordinator is responsible for securing the community, managing membership requests from web services and distributing user tasks among the community members.
+The coordinator tries to attract quality web services to join and keep the community as stable and productive as possible to gain better reputation and user satisfaction, which increases the community's market share.
+How web services reside within communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+
+\subsection{The Join Challenge}\label{s:tjc}
+It has been showed in \cite{10.1109/ARES.2008.7,10.1109/TSC.2012.12,journal-community-formation} that web services can increase their overall utility by collaborating with other web services within communities.
+This collaboration provides them with better ways of sharing resources and having higher reputation, greater market share and wider visibility.
+Web services and communities come with different quality metrics, and the long-term outcome depends on these metrics.
+
+The goal of all parties involved in the community is to maximize their long-term outcome while they are operating as part of the community.
+Web services need to be equipped with a selection strategy to choose from the different possible collaboration groups they can form as well as an estimation method for evaluating the long-term gain of joining different possible communities.
+Web services need to experiment with different possible collaborative groups in order to estimate their gain over time.
+However, with a high number of possible communities, it is not possible to test collaboration with random web services.
+Even if a linear approximate function for estimating utility based on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell\_number$} growth rate of the possible number of partitions of web services into communities would make any brute-force type algorithm for the best community selection strategy intractable and impractical in real-world application settings.
+
+\subsection{Join Consequences}\label{s:jc}
+It is worth mentioning that a \emph{join} event takes place as a result of interaction between two parties that are looking to expand their collaborations.
+All actions are chosen in an attempt to enhance the overall outcome.
+However, the selected action may result in decreasing the overall utility in the long run.
+% long term.
+This is the case when a single web service joins a community, but the complex process of task allocation eliminates the visibility of that service, which stays idle within the community.
+This makes the join action of that service a bad decision.
+The same event might be beneficial for the community, as it hosts a new web service that can engage in performing a new coming task.
+But overall, in this particular case, if the new web service stays idle for a long period of time, neither side will benefit from collaborating with the other and the join event will result in negative consequences for at least one side's utility.
+
+The more common scenario is when both parties benefit from the joining of a web service to a community.
+This joining action is then rational as both the web service and community enhance their utilities.
+However, the community may not be the best choice for the web service.
+In other words, the web service could have joined a better community if it had enough and accurate knowledge about the surrounding environment.
+Since the community does enhance its utility, the web service could stay with that community, which results in a non-optimal increase in web service's utility.
+In the following section, the proposed model provides solutions that effectively address the aforementioned challenges.
+
+\section{The Model Components}\label{s:themodelcomponents}
+
+In this section, we discuss the parameters that we use in the rest of the paper. Then, we present the task distribution and revenue model of our distributed web services communities.
+
+\subsection{Internal Features}\label{s:if}
+
+With a group of web services having identical or similar functionalities, QoS metrics provide nonfunctional characteristics for optimal candidate selection.
+Web services quality metrics have been studied and analyzed in various proposals, for instance in in \cite{Ardagna:2007:ASC:1263152.1263531,Menasce:2002:QIW:613357.613758,10.1109/ISSRE.2011.17}.
+In this paper, we adopt the most representative QoS properties of those services that highly influence their utility.
+%We refer to a typical web service as ws_{i}.
+
+Let $C = \{ws_1,ws_2,..., ws_n\}$ be a community with $n$ web services. We define the following features for the group of web services based on their functional parameters:
+
+\begin{itemize}
+
+  \item \emph{Throughput} is the rate at which a service can process requests.
+QoS measures can include the maximum throughput or a function that describes how throughput varies with load intensity.
+Throughput is a positive real number.
+For a given community $C$, the expected throughput value $(Th_{C})$ can be estimated as the summation of throughput of all the service members $Th_{w}~ (w \in C)$:
+
+	\begin{equation}
+		 Th_{C} = \sum_{w \in C}{(Th_{w})}
+	\end{equation}
+
+	\item \emph{Availability} is the percentage of time that a service is operating. It is computed as
+the probability that the service operation is accessible.
+Availability of a web service $A_w$ is a real number in the range $[0, 1]$.
+For a community $C$, the expected availability $(A_{C})$ considering the members operate in parallel (independently from each other) can be estimated as:
+
+	\begin{equation}
+		A_{C} = 1-\prod_{w \in C}{(1-A_{w})}
+	\end{equation}
+
+	\item \emph{Execution Time} is the time a service takes to respond to various types of requests.
+	%is the expected delay between the time instant when a request is sent and the time when the result is obtained.
+	Execution time is usually measured in milliseconds and can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests.
+This internal feature is a positive integer.
+For a typical community $C$, the expected execution time $Et_{C}$ can be estimated as the execution time of the bottleneck service which is the service with the slowest execution time $Et_{w}$:
+
+	\begin{equation}
+		Et_{C} = max_{w \in C}{(Et_{w})}
+	\end{equation}
+
+	%\item \emph{Data Quality} The ability of a data collection to meet user requirements , defined as the proximity of a value v returned by web service to a value considered as correct.
+The measure of data quality is considered here as a real number in the range [0, 1], where 1 represents the most desirable score.
+\end{itemize}
+
+	We normalize the range of these features so that each feature contributes proportionally to the final utility outcome value.
+We adopt the \emph{standardization} method consisting of subtracting the \emph{mean} from each feature, then dividing the subtraction result by the \emph{standard deviation}.
+
+%$HI = \overline{HI}$
+
+\subsection{External Features}\label{s:ef}
+
+The quantitative values of quality metrics need some benchmark values to represent their goodness.
+In fact, without some benchmark values, it would be difficult for web services to identify their performance quality at any specific value of these metrics.
+Therefore, we introduce two external features for assessing web services' estimate with regard to their standing among other web services.
+
+\begin{itemize}
+  \item \emph{External Parameter 1} ($Exp1_i$ where $i$ is a community or a web service) is an estimate of how close the community's or the web service's \emph{execution time} is to the best execution time in the whole system.
+It is the difference between a community's or a web service's \emph{execution time} metric and the minimum value of execution time of all the other communities or web services.
+The smaller the value the better the external feature compared to other peers.
+In other words, small value of $Exp1_i$ means $i$ is among the best communities or services in the system.
+	\begin{equation}\label{exp_1:f}
+		Exp1_i = Et_{i} - Et_{min}
+	\end{equation}
+	\item \emph{External Parameter 2} ($Exp2_i$ where $i$ is a community or a web service)  is a comparison of the community's or the web service's rate of performing tasks to the best rate in the system.
+It is the difference between a community's or a web service's \emph{throughput} metric and the maximum value of throughput in the system.
+As for $Exp1_i$, the smaller the value the better the external feature.
+	\begin{equation}\label{exp_2Lf}
+		Exp2_i = Th_{max} - Th_{i}
+	\end{equation}
+\end{itemize}
+
+\subsection{Task Distribution}
+
+Communities of web services usually employ an implementation of Contract-Net protocol for task distribution, in which services bid on incoming tasks, and receive some of the tasks for which they bid \cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:conf/aina/ElnaffarMYBT08}.
+In our model, our community members would try to distribute tasks based on their capabilities and the QoS parameters provided by the web services.
+We use a slightly modified \emph{weighted fair queuing} method to distribute tasks among community members.
+The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{w}$ for each web service $w$.
+In the \emph{weighted fair queuing} method, the input flow is multiplexed along different paths.
+However, in our model, if the rate of incoming tasks is less than the community's total throughput $(Th_{C})$, which is the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with a delay.
+%Thus, the amount of tasks performed by the community is $\sum_{ws}{Th_{ws}}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$.
+When the incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $Itr \times \frac{Th_{w}}{\sum_{w}{Th_{w}}}$ for each web service $w$ within the community, where $Itr$ is the input task rate.
+
+While distributing tasks, the community can verify the performance, throughput and quality of service of tasks being performed by web services.
+The community can assess if those web services are capable of performing the number of tasks they advertised.
+If for any reason, there is a decline in the quality metric or throughput, the community can consider the new values as a benchmark for future performance calculations, and penalize the suspicious web services.
+This way, players will have incentive to truthfully disclose their actual capabilities in order to maximize profit from the community and to avoid being penalized.
+In addition, the system should be dynamic enough to detect and react to web services' quality metrics variation, as over time, web service metrics may degrade or improve, changes to which the community should adjust.
+% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities.
+Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.
+
+\subsection{Community Revenue}
+
+Communities and web services earn revenue by performing tasks.
+The total gain is a function of the quality and rate of performing tasks.
+The utility of a collaborative group of services $U_{C}$ (i.e., the revenue of the community) is a function of internal and external parameters:
+
+\begin{equation}\label{u_c_general}
+U_{C} = f(A_{C}, Et_{C}, Exp1_{C}, Exp2_{C}, Th_{C})
+\end{equation}
+%
+where $f$ is increasing in $A_{C}$ and $Th_{C}$ and decreasing in $Et_{C}, Exp1_{C}$ and $Exp2_{C}$. An example of this function is given in Equation \ref{u_c_normal}:
+
+\begin{equation}\label{u_c_normal}
+U_{C} = \big((\alpha \times (A_{C} - Et_{C}) - \beta \times (exp1_{C} + exp2_{C})\big) \times Th_{C}
+\end{equation}
+
+The $\alpha$ and $\beta$ parameters are internal and external weight coefficients.
+Small values for execution time and external parameters ensure better performance, which justifies their negative coefficients.
+The result is then multiplied by the throughput value $Th_{C}$, since communities are performing tasks with $Th_{C}$ rate.
+
+\begin{theorem}
+The function given in Equation \ref{u_c_normal} satisfies the properties of $f$.
+\end{theorem}
+
+The proof of this theorem is straightforward by simply calculating the partial derivative $\partial f$ with respect to the different variables.
+
+The estimation of the utility can be improved, especially in cases where the input task rate is high and services are experiencing high task loads.
+The \emph{weighted fair queuing} method of task distribution would distribute tasks based on the individual throughput $(Th_{w})$ value of services within community.
+In fact, services having higher throughput affect strongly the overall utility of the community because they would take on proportionality more tasks.
+The improved utility is given as a function of individual internal and external parameters:
+
+\begin{equation}\label{improved_u_c_general}
+U_{C} = g_{w\in C}(A_{w}, Et_{w}, Exp1_{w}, Exp2_{w}, Th_{w})
+\end{equation}
+%
+where $g_{w\in C}$ is increasing in $A_{w}$ and $Th_{w}$ and decreasing in $Et_{w}, Exp1_{w}$ and $Exp2_{w}$. An example of this function is given in Equation \ref{u_c_load}:
+
+\begin{equation}\label{u_c_load}
+\begin{split}
+U_{C} = \sum_{w \in C}&\bigg(\big(\alpha \times (A_{w} - Et_{w}) \\
+        & - \beta \times (Exp1_{w} + Exp2_{w})\big) \times Th_{w}\bigg)
+\end{split}
+\end{equation}
+
+The following theorem holds:
+
+\begin{theorem}
+The function given in Equation \ref{u_c_load} satisfies the properties of $g_{w\in C}$.
+\end{theorem}
+
+\section{The Decision Making Mechanism}\label{s:model}
+
+In this section, we describe our data extraction process and the methodology used to equip web services and communities with a decision making mechanism.
+In this methodology, we first present the data extraction and engineering process and then we evaluate the decision making mechanism for web services in community settings.
+Figure \ref{fig_steps} summarizes the steps performed in DDM from the input data to the generation of decision making profiles for web services and communities.
+The objective is to use the input data to build a decision tree for each service and community included in the data set, which will be be served as a benchmark for other services and communities in their decision making mechanism.
+The decision tree is made up by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services.
+The ultimate objective is to propose for each web service and community the best joint decision about forming a group that maximizes every one's utility.
+The DDM's steps are explained in the following sections.
+
+\begin{figure}%[!t]
+\centerline{\includegraphics[width=5.25in]{figures/steps.eps}}
+\caption{A summary of DDM decision profile generation steps}
+\label{fig_steps}
+\end{figure}
+
+\subsection{Data Extraction and Solution Engineering}\label{ss:learningdata}
+
+\subsubsection{Input Web Services Data}\label{sss:webservices}
+
+%We used a data set extracted from running web services. In this data set,
+Each web service is associated with a number of quality metrics that reflect its non functional parameters.
+These web services operate in an online environment and are continuously assigned tasks to handle.
+%To engage in communities, we add the external features that reflect web services' utility as a result of joining other web services to form a community (see Section \ref{s:ef}).
+%The additional features are %computed based on two assumptions that we adopt for a community to be formed.
+We used the web services data set provided in \cite{10.1109/ISSRE.2011.17}.
+The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{http://www.wsdream.net/}.
+%In this data set, each web service is associated with a number of features that reflect its functionality.
+%Our raw data set provides us with 64 different time slots of extracted features for each web service.
+Using this data, we built a synthetic data set that contains features of a large number of web services and communities in different time intervals.
+The goal is to use the data set to train a decision-making model that adopts the trend of joining a community and use the model to predict/find the appropriate community for other web services.
+%To train our model, we build a decision tree as a benchmark for our decision making mechanism.
+The decision tree is made up by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services.
+The ultimate objective is to propose for each web service and community the best joint decision about forming a group that maximizes every one's utility.
+
+\subsubsection{Feature Extraction}\label{sss:filtereddata}
+
+By processing the data provided for each web service over different time slots, we obtain the three internal quality features introduced in Section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time} and the two external features discussed in Section \ref{s:ef}.
+In fact, web services and communities are represented using feature vectors of these five internal and external features.
+
+%To engage in communities, we add two additional external features that reflect web services estimation of its quality metrics compared to other web services.
+%Therefore, we have generated an array of web services with three distinct features.
+
+\begin{figure}%[!t]
+\centerline{\includegraphics[width=3.15in]{figures/cfvs.eps}}
+\caption{Communities with different properties of web services actively looking for other communities to collaborate with}
+\label{fig_community}
+\end{figure}
+
+%By combining these three internal features to the two external features discussed in Section \ref{s:ef} that reflect the community's estimation of its quality metrics, we generate a set of feature vectors representing the communities of web services for training purposes.
+
+We formulate a \emph{Community Feature Vector (CFV)} as $CFV_{<C>} = [f_1,...f_5]$ having a community of $k$ web services ($C = \{ws_1,...ws_k\}$, $k \geq 1$)\footnote{A web service is considered as a community of one web service.}.
+The features $f_1$ through $f_5$ represent the \emph{execution time}, \emph{throughput}, \emph{availability} and the \emph{external parameters 1 and 2} respectively.
+A set of communities, with their feature vectors and utilities evaluated, provides our algorithm with a raw training data set.
+We call this set of communities the \emph{template vector} $CS$, and the set of feature vectors associated with the \emph{template vector} is referred to as the \emph{community feature vector set (CFVS)}.
+Figure \ref{fig_community} depicts web services and communities looking to form new groups in order to improve their utility gain.
+
+\subsubsection{Feature Engineering}\label{sss:feng}
+Let $CFVS = \{CFV_{<C_1>}, \dots, CFV_{<C_N>}\}$ be the community feature vector set with $N$ communities.
+Based on the $CFVS$ set, we create an $|N \times N|$ gain matrix $gain^{t}$ for each time slot $t$.
+Each entry $gain_{n,m}^{t}$ corresponds to a utility gain of community $C_n$ when it joins community $C_m$.
+This gain is computed as follows: $gain_{n,m}^{t} = U_{C_n \cup C_m}^{t} - U_{C_{n}}^{t}$ where $U_{C_n \cup C_m}^{t}$ and $U_{C_{n}}^{t}$ are the utilities at time $t$ computed using Equation \ref{u_c_load}.
+Evaluating the utility gain for all entries of the $gain^t$ matrix is a computationally heavy process when $N$, the size  of the feature vector set, is large.
+Therefore, this size should be chosen carefully.
+
+\begin{table*}[ht]
+\footnotesize
+\caption{An example of $gain$ matrix for 3 different communities and their combinations} % title of Table
+\centering % used for centering table
+{\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{c|c c c c c c} % centered columns (4 columns)
+\hline\hline %inserts double horizontal lines
+ & \textless348\textgreater & \textless1934\textgreater & \textless2117\textgreater & \textless348, 1934\textgreater & \textless1934, 2117\textgreater & \textless348, 1934, 2117\textgreater \\ [0.5ex] % inserts table
+%heading
+\hline % inserts single horizontal line
+\textless348\textgreater & - & 0.282708 & 1.027081 & 0.282708 & 18.027081 & 18.027081 \\
+\textless1934\textgreater & -2.637483 & - & 6.969072 & -2.637483 & 5.509583 & 4.387725 \\
+\textless2117\textgreater & 5.027081 & 2.969072 & - & 5.509583 & 2.969072 & 5.509583 \\
+\textless348, 1934\textgreater & 0.0 & 0.0 & -3.851432 & - & -3.851432 & -3.851432 \\
+\textless1934, 2117\textgreater & 2.969072 & 0.0 & 0.0 & 2.969072 & - & 2.969072 \\
+\textless348, 1934, 2117\textgreater & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & - \\ [1ex] % [1ex] adds vertical space
+\hline %inserts single line
+\end{tabular}
+}
+\label{table:nonlin} % is used to refer this table in the text
+\end{table*}
+
+%Now, we let our set of communities in the $CFVS$ set, within $|T|$ time frame iterations, choose the the best communities to join.
+Each community is provided with the corresponding row of data from the $gain^t$ matrix.
+Basically, $C_i$ is provided with the data in row $i$ of this matrix, which reports all the possible utility values $C_i$ can gain by joining different communities.
+By ordering the utility gain values of the row, each community is equipped with an ordered set of preferences over other communities it can join.
+We define $\geq_{i}^t$ as the preference order of community $i$ at time $t$.
+
+Let $C_1 \geq_{i}^t C_2 \geq_{i}^t ~\dots~ C_{i-1} \geq_{i}^t C_{i+1} \geq_{i}^t ~\dots~ C_n$ be an ordered sequence of preferences for community $C_i$ at time $t$.
+Based on this sequence, we define $K^t(C_i, k)$ as a set of the $k$ most preferred communities of community $i$ at time $t$.
+%\subsubsection{feature vector generation}\label{sss:fvg}
+\begin{equation}\label{h_t_pref_top}
+\begin{split}				
+K^t(C_i, 0) = &\emptyset \\
+K^t(C_i, k) = &\Big\{C_x | C_x \geq_{i}^t C_y ~\forall C_y \in CS ~\wedge~ C_x \neq C_y ~\wedge~ C_y \notin K^t(C_i, k-1) \Big\}				
+\end{split}
+\end{equation}
+Based on $K^t(C_i, k)$, we define a set of communities $C_j$ for $C_i$ which are the $k$ most preferred communities for $C_i$ and $C_i$ belongs to the $k$ most preferred communities of $C_j$.
+This basically yields the preference in both sides.
+\begin{equation}\label{l_t_top_both}
+\begin{split}	
+L^t(C_i,k) = \Big\{C_j | C_j \in K^t(C_i, k)~ \wedge~ C_i \in K^t(C_j, k)\Big\}
+\end{split}
+\end{equation}
+
+Table \ref{table:nonlin} illustrates an example of a $gain$ matrix for 3 different communities and their combinations.
+Each row shows the gain the community can achieve by collaborating with other 5 communities.
+In this example, for community $\textless 348 \textgreater$ we have: \\
+$K(\textless 348 \textgreater, 1) = \{\textless1934, 2117\textgreater\}$ and \\
+$K(\textless 348 \textgreater, 2) = \{\textless1934, 2117\textgreater, \textless1934\textgreater\}$ \\
+Since $\textless 348 \textgreater$ is the best preferred community of $\textless 1934, 2117 \textgreater$ and vice versa, therefore $L(\textless 348 \textgreater, 1)$ is not empty and contains the community $\textless1934, 2117\textgreater$.
+
+Using the $gain$ matrix and the mentioned preference ordering relations, we are able to build a decision tree where the list of possible communities to join and their expected utilities are set.
+% as well as the joined events that took place in different time slots.
+In addition to the best choice, web services have access to other ordered choices and can look for the second best or third best if their first try is rejected by the target community.
+This aspect is analyzed in more detail in the following section, in which we launch experiments and investigate the effectiveness of the use of a decision tree with different decision layers in joining other communities and enhancing the overall utility.
+
+\subsection{Decision Profile Generation}\label{ss:learningmodel}
+
+Our goal is to create a decision making profile for each community in the
+$CFVS$ set. We are creating an environment where the communities can experience the
+outcomes of different strategies. The result will be a decision tree of the
+feasible and utility-increasing moves over time. The root of the decision tree
+represents a community in the $CFVS$ set, and the other nodes represent
+the communities resulting from the parent node's action of joining them along with their feature values and
+expected utility.
+
+We let communities pick the best communities maximizing their utilities over different time frames.
+At time $t = 1$, we let each community in the $CFVS$ set choose the best community, which is a single community in the set $\{C_j\} = K^t(C_i, 1)$.
+If community $C_j$ also ranks $C_i$ to be the highest preferred community to join, meaning the set $L^t(C_i, k=1)$ is not empty, they would join each other.
+Having set $k = 1$ is a very strict and hardly satisfiable condition.
+In order to relax the requirement, we increase the value of $k$ by a rate $r$ proportional to time slot $t$: $k = 1 + |r \times t|$.
+On early steps of the training process, web services and communities are more strict, but as time goes on, we let them choose second and then third best options too.
+However, increasing $k$  increases the time complexity as well.
+
+When communities $C_i$ and $C_j$ are in each other's top $k$ preference set, the new combined community, i.e., $C_i \cup C_j$ is added to the list of possible communities that can join others at time $t+1$.
+Moreover, for each community $C_i$ in our initial $CFVS$ set, we maintain a tree with the community $C_i$ as its root.
+Its children are all the communities that $C_i$ decided to join.
+As the scenario progresses over time, the merged communities may decide to join other communities.
+When communities $C_i$ and $C_j$ decide to join each other and create community $C_k$, the new community $C_k$ will be added as a child to both $C_i$ and $C_j$ nodes.
+At the end of the process, each community is utilized with a tree representing all possible combinations of communities it can join.
+Algorithm \ref{algo:dectree} illustrates the DDM tree creation procedure as pseudo-code.
+
+\begin{algorithm}
+\DontPrintSemicolon
+\KwIn{$\langle r, gain^t_{n,n}, CFVS \rangle$ learning rate $r$, $|N \times N \times T|$ gain matrix, community feature vector}
+\KwOut{A set of \emph{root} nodes of the decision trees}
+$k \gets 1$\;
+$nodes[N] \gets$ initialize $N$ tree nodes representing each community in CFVS\;
+\For{$t \gets 1$ \textbf{to} $T$} {
+	$k \gets 1 + round (r \times t)$\;
+  \For{all $C_i \in CFVS$} {
+	  \For{all $C_j \in L^t(C_i, k)$} {
+      % The "l" before the If makes it so it does not expand to a second line
+      \If{$C_i \in L^t(C_j, k)$}{
+        $C_k \gets C_i \cup C_j$\;
+				add $C_k$ to $CFVS$ set\;
+				initiate $node_k$, representing $C_k$\;
+				$nodes_i.addChild (node_k)$\;
+				$nodes_j.addChild (node_k)$\;
+      }
+%      \Else{
+%        $j \gets j + 1$\;
+%      }			
+		}
+  }
+%  $i \gets i + 1$\;
+}
+\Return{nodes}\;
+\caption{{\sc DDM Decision Tree Algorithm}}
+\label{algo:dectree}
+\end{algorithm}
+
+Having created $|n|$ trees, one per community, our communities are utilized with the different possible paths they can take to maximize their utilities.
+Using a distance function\footnote{See Section \ref{s:experiments} for an example of this function.}, communities and web services outside the training set can find the community that closely resembles their parameters within the $CFVS$ set.
+Those new communities can use the trees of the closest communities in the training set to have an estimation of the outcome of all possible joining actions they can take.
+By so doing, new communities can request to join the best communities which will maximize their gain.
+Such a request is most likely to be accepted as the decision considers the preferences and utility gain of the other side as well.
+
+As a real scenario example from the used data set, Figure \ref{fig_tree} depicts a snapshot from a decision tree created by the DDM algorithm for a particular singleton community $C_{1273}$.
+This tree shows the different communities that $C_{1273}$ has experienced with during the training process.
+Each line shows the web services list within a community, the community's feature vector and the last value on each line is the overall gained  utility of the community.
+
+\begin{figure}%[!t]
+\centerline{\includegraphics[width=6.25in]{figures/tree1.eps}}
+\caption{A partial view of a decision tree created by DDM}
+\label{fig_tree}
+\end{figure}
+
+\textbf{Complexity.} Here we analyze the computational complexity of the DDM decision tree creation algorithm on each time iteration $t$.
+Computing top $k$ preferred communities for $C_i$ in $K^t(C_i, k)$ requires $O(n.log(n))$ sort time.
+The size of $K^t(C_i, k)$ is $k$, and for each of those $k$ communities, we need to check against their $k$ top preferred communities, which needs $O(k^2)$.
+Line 5 iterates through $n$ communities, Line 6 takes $O(n.log(n))$ to compute and iterates $k$ times, and considering we already have the list sorted, Line 7 can reuse the sorted preferences.
+Thus, Line 7 takes $O(k)$ time to check if $C_i$ is member of $K^t(C_i, k)$.
+Multiplying these iterations, the order of complexity of the algorithm with regard to $n$ and $k$ for each time slot is: $O(k^2 \times n^2.log(n))$.
+Since the whole algorithm runs $T$ times, the overall complexity is $O(T \times k^2 \times n^2.log(n))$.
+
+\section{Experiments}\label{s:experiments}
+We implemented DDM in Java\footnote{Source code of implementation and data is available at: $https://github.com/Marooned202/DDM$}.
+We recall that we have extracted the set of features for 4532 web services in 64 different time slots through a data set provided in \cite{10.1109/ISSRE.2011.17}.
+By randomly choosing 86 web services out of this data set for each run, and selecting a subset of all possible combinations of sizes 2, 3, and 4 of these 86 web services, we have been able to create 10,000 communities and evaluated the feature vectors and utilities they can have in the 64 time slots.
+This provides us with the initial training feature set of size $|CFVS| = 10,000$ communities.
+Based on Equation \ref{u_c_load}, the utilities of these communities are estimated, and then the $gain$ matrix of size $|10,000 \times~ 10,000|$ of all possible ways of merging these 10,000 communities is generated\footnote {The template vector and $gain$ matrix generated are available at $https://github.com/Marooned202/DDM/tree/master/wsds/data/run$}.
+Based on the $gain$ matrix, each community has an ordered preference among other communities in the set.
+
+We let communities and web services adopt their strategies based on our $DDM$ decision making mechanism.
+Based on the decisions adopted, each community will generate a decision tree profile.
+We let DDM run four times with different $r$ rates of 0.05, 0.07, 0.10 and 0.20.
+With the slow rate of $r = 0.05$, we increase $k$ in Equation \ref{u_c_normal} for every 20 time frames, which will happen only three times in our 64-step experiment.
+In the case of $r = 0.20$, $k$ increases much faster, at a rate of once every 5 time frames, which increases the complexity of the $L^t(C_i,k)$ search for each community in the $CFVS$ set.
+
+Table \ref{table:valueandgain} depicts the average utility gain value of the communities in each of the four runs.
+The utility gain is the increase of utility the communities gain by cooperating and joining other communities.
+The utility gain ratio is the ratio of their final utility over initial utility.
+Comparing the different search rates, we can see that increasing the value of $r$ from $0.05$ to $0.10$ results in a significant performance boost.
+However, higher rates of $r$ ($r > 0.10$) are not increasing the chance of finding better collaborative groups for our communities while unnecessarily increasing the search complexity.
+
+\begin{table}[ht]
+\caption{Utility gain of web services after making collaborative groups based on DDM algorithm with different $r$ rates} % title of Table
+\centering % used for centering table
+{\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{c|c|c} % centered columns (4 columns)
+\hline\hline %inserts double horizontal lines
+Search Rate $r$ & Utility Gain Value & Utility Gain Ratio \\ [0.5ex] % inserts table
+%heading
+\hline % inserts single horizontal line
+r=0.20 & 176.1499 & 6.9690 \\
+r=0.10 & 174.6541 & 6.9182 \\
+r=0.07 & 159.9462 & 6.2834 \\
+r=0.05 & 136.0768 & 5.1032 \\ [1ex] % [1ex] adds vertical space
+\hline %inserts single line
+\end{tabular}
+}
+\label{table:valueandgain} % is used to refer this table in the text
+\end{table}
+
+%\begin{figure}%[!t]
+%\centering
+%\includegraphics[width=3.5in]{figures/utility_gain_r.eps}
+%\caption{DDM Utility Gain Value}
+%\label{utility_gain_value}
+%\end{figure}
+%
+%\begin{figure}%[!t]
+%\centering
+%\includegraphics[width=3.5in]{figures/utility_ratio_r.eps}
+%\caption{DDM Utility Gain Ratio}
+%\label{utility_gain_ratio}
+%\end{figure}
+
+The closest related work \cite{10.1109/TSC.2012.12,
+DBLP:conf/IEEEscc/LimTMB12, DBLP:conf/IEEEscc/KhosravifarABT11} and our
+previous work \cite{journal-community-formation} regarding the community formation problem have considered a centralized approach where a community manager has complete information of all the web services and their quality
+metric and parameters. Those proposals run complex algorithms through all the space of
+solutions in order to find the optimal answer. However, in this paper, we
+have considered an unexplored and more realistic situation where information is incomplete and a decision
+profile is generated based on a smaller set of web services. Our solution helps
+communities and web services select actions that lead towards
+maximizing their utilities. Therefore, considering the different settings,
+we cannot experimentally compare our work with the mentioned related work.
+
+To compare our work against a benchmark, we utilize the same communities and web services with a simple rational decision making mechanism in which a community will choose to join another one if it increases its utility by any amount, without aiming to be optimal.
+We call this method the {\textit{rational} method.
+We have chosen 10 random web services and compared the results with web services which adopted our DDM model.
+Figure \ref{utility_gain_mlisa_and_rational} shows the comparison of the end result of utility gain values.
+In 18 out of 40 tries, \emph{rational} agents were not able to improve their utility at all because the communities they chose rejected their request, most likely because they would not have increased the utility of the other communities if they had joined them.
+The results show that a long-term strategic decision mechanism is needed to satisfy all the services within communities.
+Figure \ref{utility_gain_mlisa_and_rational_ratio} shows the same results in terms of ratio of utility gain.
+
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/utility_gain.eps}
+\caption{DDM against Rational: utility gain }
+\label{utility_gain_mlisa_and_rational}
+\end{figure}
+
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/utility_ratio.eps}
+\caption{DDM against Rational: ratio of utility gain}
+\label{utility_gain_mlisa_and_rational_ratio}
+\end{figure}
+
+Now, we evaluate the performance of the decision profiles generated based on our data set for other communities.% which are not included in the decision tree creation process.
+We create 1,000 communities from the web services in the data set that were not involved in the training process of our decision model.
+We define a distance function that measures the difference between basic features of communities, which measures the similarity among communities.
+
+\begin{equation}\label{distance_c}
+\begin{split}
+distance (C_1, C_2) & = |Th_{C_1} - Th_{C_2}| \\
+                    & + |A_{C_1} - A_{C_2}| + |Et_{C_1} - Et_{C_2}|
+\end{split}
+\end{equation}
+
+Now, each community tries to find the closest community within the trained $CFVS$ set.
+Following its decision profile, the community can get a good estimate of the possible strategic decisions it can adopt.
+Basically, the trained profiles benefit the new communities in two ways.
+First, they provide the communities with a set of viable communities to join.
+Second, they provide an estimation of long-term utility gain for each available decision.
+In this experiment, we let communities follow the best decision within the decision tree provided to them.
+
+In order to evaluate the performance of the mechanism, we used \emph{Receiver Operating Characteristic (ROC) curve}, which is a graphical plot illustrating the true negative rate against the false positive rate at various threshold settings in classifier systems.
+In order to classify our communities' selection strategies correctly, for each community, we evaluated the training process by replacing the community in the set with the closest one, from which it gets the strategy profile.
+If the actions are the same and the same utility levels are gained, we classify the decision as correct.
+Otherwise, it is classified as a wrong decision.
+\emph{AUC}, the area under the \emph{ROC curve}, is equal to the probability that a classifier will rank a randomly chosen positive instance higher than a randomly chosen negative one, and the higher the number the better the solution, which reflects better performance.
+Figure \ref{roc5} illustrates the \emph{ROC curve} evaluation of the DDM decision making mechanism.
+As benchmark, we compare our method with two other methods: the \emph{rational} method and the \emph{greedy} method.
+The \emph{greedy} method only looks up the available list of communities and simply joins the community that maximizes its utility without considering any long-term strategy or other communities' acceptance scenarios.
+It is a greedy algorithm that focuses on choosing a locally optimal choice.
+
+\begin{itemize}
+  \item {\bf Rational Method:} Communities would send a join request to any available community, which will increase the utility.
+The other community would accept the join offer if its own utility gain is positive as well.
+	\item {\bf Greedy Method:} Communities do a linear search among all the available communities and send a join request to the community which results in maximum utility.
+The other community would accept the join offer if its own utility gain is positive and the utility gain does not need to be the maximum for the community receiving the join request.
+\end{itemize}
+
+Figure \ref{roc5} compares the results for all the methods.
+The \emph{rational} and \emph{greedy} methods have very high failure rates compared to our method.
+Table \ref{fail_rate} illustrates the number of communities that failed to find the optimal collaboration group.
+The results support the need for a long-term training model in a successful decision making process.
+
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/roc.eps}
+\caption{RoC Curve}
+\label{roc5}
+\end{figure}
+
+\begin{table}[ht]
+\caption{Number of communities that misses the optimal decision, out of 1,000 communities} % title of Table
+\centering % used for centering table
+\begin{tabular}{|c|c|} % centered columns (4 columns)
+\hline %inserts double horizontal lines
+ Method&Miss \\ [0.5ex] % inserts table
+%heading
+\hline % inserts single horizontal line
+ DDM r=0.05& 375 \\ % inserting body of the table
+ DDM r=0.07& 137 \\
+ DDM r=0.10& 6 \\
+ DDM r=0.20& 6 \\
+Rational Method& 717 \\
+Greedy Method& 828 \\ [1ex] % [1ex] adds vertical space
+\hline %inserts single line
+\end{tabular}
+\label{fail_rate} % is used to refer this table in the text
+\end{table}
+
+Now, we evaluate the system-specific results from users' and communities' perspectives.
+By distributing tasks among the communities over the 64 time frames, we evaluate the revenue for each community.
+Figure \ref{stats1} shows the overall revenue gain of communities using our method.
+Figure \ref{stats2} shows the momentarily revenue gain for each community in each time slot compared to the previous time.
+These results show that the run with the higher learning rate of $r=0.20$ starts discovering better communities to join much earlier.
+The runs with slow rates seem to find some communities to join initially, but then they slow down until later, when they start discovering new communities to join.
+
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/stats1.eps}
+\caption{Overall utility of all the communities}
+\label{stats1}
+\end{figure}
+
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/stats2.eps}
+\caption{Utility gain over time}
+\label{stats2}
+\end{figure}
+
+Figure \ref{stats3} depicts the average community size over time, which essentially represents the number of new communities being formed.
+The results show once again the communities using DDM with higher search rates grow faster in size, implying that the communities find appropriate web services to join with faster.
+
+\begin{figure}%[!t]
+\centering
+\includegraphics[width=3.5in]{figures/stats3.eps}
+\caption{Average community size}
+\label{stats3}
+\end{figure}
+
+\section{Related Work}\label{s:related_work}
+
+Most of the recent work on communities of services are either
+user-centric and focus on user satisfaction
+\cite{Chun02user-centricperformance} or system-centric and focus
+on the whole system throughput, performance and utilization. There
+are many contributions in distributed, grid, cluster and cloud
+services which are system-centric. However, in real world
+environments and applications, both users and service providers
+are self-interested agents, aiming to maximize their own profit.
+In those environments, both parties (users and services) will
+collaborate as long as they are getting more benefits and payoff.
+
+In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
+DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
+mechanisms to help users and services maximize their gain. A
+two-player non-cooperative game between web services and community
+master was introduced in
+\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this game-theoretic
+model, the strategies available to a web service when facing a new
+community are requesting to join the community, accepting the
+master's invitation to join the community, or refusing the
+invitation to join. The set of strategies for communities are
+inviting the web service or refusing the web service's join
+request. Based on their capacity, market share and reputation, the
+two players have different sets of utilities over the strategy
+profiles of the game. The main limits of this game model are: 1)
+its consideration of only three quality parameters, while the
+other factors are simply ignored; and 2) the non-consideration of
+the web services already residing within the community. The game
+is only between the community master and the new web service, and
+the inputs from all the other members and their influence on the
+master's decision are simply ignored. The consideration of those
+inputs and this influence factor is a significant issue as
+existing web services can lose utility or payoff because of the
+new member, which can result in an unhealthy and unstable group.
+The problem comes from the fact that the existing members should
+collaborate with the new web services, so probably their
+performance as a group can suffer. Existing members may even
+deviate and try to join other communities if they are unsatisfied.
+Those considerations of forming stable and efficient coalitions
+are the main contributions of our paper.
+
+In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
+for selecting web services has been proposed. In this approach,
+the authors proposed a web service selection process that the
+community masters can use. The approach considers the efficiency
+of all the three involved parties, namely users, web services and
+communities. In this work, it is shown how the gains of these
+parties are coupled together using a linear optimization process.
+However, the optimization problem in this solution tends to
+optimize some parameters considering all web services regardless
+of their efficiency and contribution to the community's welfare.
+Moreover, there are no clear thresholds for accepting or rejecting
+new web services. The solution of the optimization problem could,
+for instance, suggest web services already residing within the
+community to increase or decrease their capacity to cover up the
+weakness of other parties in the system. However, a high
+performing web service could deviate anytime it finds itself
+unsatisfied within the community instead of adjusting its service
+parameters.
+
+In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
+autonomous web services based on coalition game theory has been
+introduced. The authors have proposed an interesting algorithm to
+reach individually stable coalition partition for web services in
+order to maximize their efficiency. The communities choose new web
+services on the promise that it would benefit the community
+without decreasing any other web service's income. In the proposed
+model, the worth of community is evaluated with high emphasis on
+the availability metric and considering price and cost values
+only. The community structure is based on a coordination chain,
+where a web service is considered as a \emph{primary} web service
+and the community task-distribution method initially invokes the
+primary web service and only if the primary web service is
+unavailable, the method invokes the next backup web services as
+they are ordered in the coordination chain. We believe that this
+coordination chain limits the cooperation power as it introduces a
+sort of hierarchy. However, in pure and open cooperative models,
+such as the one we propose in this paper, active cooperation
+activities engaging simultaneously many agents so that they can
+perform the tasks more efficiently are being used. Moreover, if
+the availability is high, which is the case nowadays with the
+recent advancements in cloud infrastructures and hardware technologies, the
+backup web services will end-up having a very low chance of
+getting jobs, especially the ones further in the chain. This will
+results in a considerable waste of web services capabilities.
+
+All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process.
+So basically, these solutions generally suffer from high complexity, which makes decision making very hard, even impossible in some cases in a real-time fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.
+We address this issue by introducing DDM a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another.
+After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics.
+Therefore, web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
+In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.
+\\
+
+\noindent \textbf{Web Service Communities}
+
+Here we introduce the related research work regarding the engineering and formation of communities of web services.
+In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
+defined communities of web services as \emph{Service Containers} that aggregate substitutable web services having the same set of operations and providing common functionalities.
+They abstracted \emph{Service Containers} as web services that are created, advertised, discovered and invoked just as elementary web services.
+The \emph{Container} is considered as a manager that is responsible for web service selection upon receiving a request on run-time.
+The authors have proposed a scoring technique based on non-functional requirements of the request and web service capabilities to dynamically chose the web service to perform the requested task.
+A similar concept was proposed by Maamar et al.
+in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+The authors introduced web service communities as a collection of web services with a common functionality but different QoS properties.
+A community manager, upon receiving a request, delegates the request to one of its current members.
+The choice is based on the performance history and quality metrics of each web service.
+The authors have proposed an efficient global web service selection algorithm in order to approach quality constraints and preferences for composite services which requires aggregation of different types of services to satisfy the user.
+In the same line of research, Benslimane et al.
+\cite{Liris-2770} have proposed a multi-layer approach grouping similar web services into communities and having an interface implemented as an abstract web service for accessing the community.
+The considered layers are: composite, management and community.
+The interactions among those layers and the bindings are performed by a generic driver called Open Software Connectivity (OSC).
+However, unlike our work, these proposals only tackle the problem of internal community management from the task execution perspective, but not the problem of community formation and the one of dynamically selecting which community to join and which web service to invite.
+Moreover, the web services selection process is done centrally by the community manager, while we address the problem more realistically from the distributed angle.
+
+In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
+service communities with centralized access across distributed web
+services. They have proposed a framework for web service
+management, query resolution among communities and a query caching
+mechanism executed by the manager to improve the performance of
+query resolution process among many distributed communities. The
+key idea is to cache previous computed results for answering
+future queries. Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
+then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
+proposed an architecture utilizing \emph{Contract-Net} protocol
+for engineering task distribution within communities of web
+services. The protocol is centrally executed by the community
+manager. This architecture has been further extended in
+\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
+conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
+roles have been distinguished for community members: masters and
+slaves. Master web services are community managers that lead
+communities and are responsible for membership management. They
+can invite and convince slave web services to join the community,
+and attract new slave web services to their communities by
+awarding them better payoff. Moreover, they can eject some slave
+members from the community to improve its overall reputation if
+these members are misbehaving or cannot provide the promised QoS.
+In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
+developed a community as a ``cluster'' that groups Web services
+based on a specific area of interest. All web services in a given
+community share the same functionality. These communities are
+created by \emph{third party community providers} which use the
+\emph{community ontology} as a template and define a set of
+operations that all web services within a community should
+provide. Using semantic analysis on web service operations, web
+services either find and join a community with similar
+functionality or create a new operation description for a new
+community. The authors have described the concept of
+\emph{community agents} associated to \emph{community providers}.
+A community agent is responsible, among other things, of the
+registration of services with the community. An example of a
+community that provides health care services to senior citizens
+has been used. In this example, a governmental entity is needed to
+check the health care standards used by the members before
+authorizing them to be part of the community. Such a central
+entity is represented by the community agent. Thus, community
+agents are playing the role of community managers. In a close work
+\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
+global planning selection algorithm and a delegation algorithm to
+be run when a request to execute an operation is received by the
+community. This needs a central entity to run those algorithms.
+Such entity plays the same role as the community coordinator or
+manager. All these proposals have in common the consideration
+of the central entity for community management, which includes the hiring and firing of the community members, while our approach is fully distributed.
+Moreover, the stability of the community has not been investigated.
+Another major difference with our work is that the decision making process is only one way and unilateral from the community manager perspective.
+In our proposal, both participants, namely communities and web services, participate in the decision making process and a joining decision is made only if it is the best option for both players.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary}\label{sec:conclusion-cha4}
+
+In this research work, we proposed a training model for the problem of membership management of communities of web services.
+Using the traning model we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves.
+This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available.
+The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices.
+The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.
+The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.
+
+Our plan for future work is to advance learning process on the training set that we provided in our work.
+SVN machine learning algorithm are suitable in classification of our training data set, to better classify correct or wrong decisions based on long-term utility gains, as data set outputs.
+This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.

### 2015-06-30 thesis/thesis/chap6/chap6.tex
changes

@@
 \begin{itemize}
-\item K. Sultan, J. Bentahar, M. El-Menshawy, "Model Checking Probabilistic Social Commitments for Intelligent Agent Communication", Journal of Applied Soft Computing, Elsevier, 2014.
+\item E. Khosrowshahi Asl, J. Bentahar, H. Otrok, R. Mizouni, "Efficient Coalition Formation for Web Services", IEEE Transactions on Services Computing, 2015.
 
-\item K.
-Sultan, J.
-Bentahar, W.
-Wan, F.
-Al-Saqqar, "Modeling and Verifying Probabilistic Multi-  Agent Systems using Knowledge and Social Commitments", Journal of Expert Systems with Applications, Elsevier, 2014.
+\item E.
+Khosrowshahi Asl, J.
+Bentahar, H.
+Otrok, B.
+Khosravifar, R.
+Mizouni, "To compete or cooperate?
+This is the question in communities of autonomous services", Journal of Expert Systems with Applications, Elsevier, 2014.
 
-\item F. Al-Saqqar, J. Bentahar, K. Sultan, M. El-Menshawy, "On the Interaction between Knowledge and Social Commitments in Multi-Agent Systems", Applied Intelligence Journal, Springer, 2014.
-
-\item F. Al-Saqqar, J. Bentahar, K. Sultan, W. Wan, E. Khosrowshahi
-Asl, "Model Checking Temporal Knowledge and Commitments in Multi-Agent Systems Using Reduction", Simulation Modeling Practice and Theory Journal, Elsevier, 2015.
 \end{itemize}
@@
 \begin{itemize}
+\item E. Khosrowshahi Asl, J. Bentahar, H. Otrok, R. Mizouni, "Efficient Community Formation for Web Services",  IEEE SCC, Santa Clara, CA, USA, 2013.
 
-\item K.
-Sultan, J.
-Bentahar, O.
-Marey, "A Probabilistic Logic to Reason about the Interaction between Knowledge and Social Commitments in MASs", In the Proc.
-of The 13th International Conference on Intelligent Software Methodologies, Tools, and Techniques (SOMET\_14), Langkawi, Malaysia, 2014.
-
-\item M.
-Mbarki, O.
-Marey, J.
-Bentahar, K.
-Sultan,  "Agent Types and Adaptive Negotiation Strategies in Argumentation-Based Negotiation", In the Proc.
-of the IEEE International Conference on Tools with Artificial Intelligence (ICTAI), Limassol, Cyprus, 2014.
-
-\item K.
-Sultan, M.
-El-Menshawy, J.
-Bentahar, "Reasoning about Social Commitments in the Presence of Uncertainty", In the Proc.
-of The 12th International Conference on Intelligent Software Methodologies, Tools, and Techniques (SOMET\_13), Budapest, Hungary, 2013.
 \end{itemize}
@@
 \begin{itemize}
-\item K.
-Sultan, J.
-Bentahar, R.
-Mizouni, "Model Checking the Interaction Between Individual and Group Knowledge and Commitments in Probabilistic Multi-Agent Systems", Engineering Applications of Artificial Intelligence, Elsevier, (submitted: August 2014).
-\item O.
-Marey, J.
-Bentahar, E.
-Khosrowshahi Asl, K.
-Sultan, R.
-Dssouli, "Decision Making under Subjective Uncertainty in Argumentation-Based Negotiation.
-Ambient Intelligence and Humanized Computing, (submitted: November 2014).
+\item E.
+Khosrowshahi Asl, J.
+Bentahar, H.
+Otrok, R.
+Mizouni, "Distributed Decision Making for Dynamic Formation of Web Services Communities", Decision Support Systems, Elsevier (Submitted: June, 2015).
 \end{itemize}

### 2015-07-02 thesis/thesis/chap6/chap6.tex
changes

@@
 
-Conclusion Conclusion Conclusion
-%To conclude, we believe that the proposed framework
-%********************************************************************
-%* Section 7: Future Work
-%********************************************************************
+In this theses we proposed three models for aggregation of web services within communities.
+The goal of our models are to maximize efficiency by collaborating and forming stable communities.
+In our first contributions focus on stability and
+
 \section{Future Work}
@@
 
+\item F.
+Al-Saqqar, J.
+Bentahar, K.
+Sultan, W.
+Wan, E.
+Khosrowshahi Asl:, "Model checking temporal knowledge and commitments in multi-agent systems using reduction", Journal of Simulation Modelling Practice and Theory, 2015.
+
 \end{itemize}
@@
 \item E. Khosrowshahi Asl, J. Bentahar, H. Otrok, R. Mizouni, "Efficient Community Formation for Web Services", IEEE SCC, Santa Clara, CA, USA, 2013.
+
+\item B. Khoravifar, M. Alishahi, E. Khosrowshahi Asl, J. Bentahar, R. Mizouni, H. Otrok, "Analyzing Coopetition Strategies of Services within Communities", ICSOC, Shanghai, China, 2012
+
+\item H.
+O.
+Marey, J.
+Bentahar, E.
+Khosrowshahi Asl, M.
+Mbarki, R.
+Dssouli, "Agents' Uncertainty in Argumentation-based Negotiation: Classification and Implementation", ANT/SEIT, Hasselt, Belgium, 2014.
+
+\item H. Fallatah, J. Bentahar, E. Khosrowshahi Asl, "Social Network-Based Framework for Web Services Discovery", IEEE  FiCloud, Barcelona, Spain, 2014.
 

### 2015-07-02 thesis/thesis/chap6/chap6.tex
changes

@@
 The goal of our models are to maximize efficiency by collaborating and forming stable communities.
-In our first contributions focus on stability and
+In our first contributions we focused on stability and fairness for all web services within the communities.
+This model offers an applicable mechanism for membership requests and selection of serb services.
+The ultimate goal is to increase revenue by improving user satisfaction, which comes from the ability to perform more tasks with high quality.
+
+In our next step of research work, the focus was on inter-community interaction between services involved within the community.
+The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behaviour of intelligent services that are active within communities.
+We considered two acting strategies where service agenets expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers.
+Our proposed model advances the state-of-the-art in cooperative systems by enabling intelligent agent-based services to effectively choose their interacting strategies that lead to optimal outcomes.
+The proposed framework provides a reasoning technique that service agents can use to increase their overall obtained utilities.
+The theoretical results presented in this paper are also backed by simulation results using a real services dataset.
+Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
+services deviate from the coopetitive strategy suggested by our decision-making mechanism the more they make less benefits.
+Thus, deviating from our coopetitive strategy yields less income for the service.
+
+In our final step of the work, we proposed DDM, a strategic distributed decision making mechanism that regulates the community formation process and  membership management in communities of web services.
+This mechanism helps web services and communities decide with whom to be grouped and cooperate.
+DDM first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
+Communities and web services can use the trained model and instantly choose best-response strategies considering their long-term gain.
+In fact, the decision making mechanism is implemented as a decision tree of possible viable strategies along with their long-term expected utility.
+The ultimate goal of our mechanism is to choose the best decision when it comes to community formation, which goes beyond short-term utility increasing choices, usually considered in the literature.
+The experimental results show that our approach allows web services and communities, in real-world-like environments, to make near-perfect decisions.
+The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.
 
@@
 
-Future Work Future Work Future Work
+As future work, for the community formation in our first model, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal
+$\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications.
+From web service perspective, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks.
+Also bargaining theory from cooperating game theory concepts can be used to help web services resolve the instability and unfairness issues by side payments.
+
+For the distributed model, our future work is to advance further the learning process on the training set we provided in our work by leveraging some game theoretical approaches.
+In fact, game theory provides powerful techniques for strategic decision making, particularly cooperative and coalition formation games.
+Hedonic games and fractional hedonic games are of particular interest where the utility of a player in a community depends on the identity of the other members of the community and the value this player ascribes to those members.
+We intent to investigate stability solution concepts such as Shapely value so that long-term decisions will be based on the probability that the community will stay for long period.
+The SVM machine learning algorithm is suitable for classification of our training data set to better distinguish  decisions based on long-term utility, as data set outputs.
+This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.
 

### 2015-07-03 thesis/thesis/chap1/chap1.tex
changes

@@
 \chapter{Introduction}\label{sec:intro}
-In this chapter, we introduce the context of this research, which
-is about communities of web services abstracted as autonomous
-agents. Those agent-based web services use cooperative game
-theoretic solution concepts for decision making. We discuss the
-motivations of this work and briefly review the literature to
-identify the problems we aim to solve in this thesis. Moreover, we
-discuss our objectives and preliminary contributions.
+In this chapter, we introduce the context of this research, which is about communities of web services abstracted as autonomous agents.
+Those agent-based web services use intelligent decision making mechanisms to improve their performance in multi-agent setting.
+We discuss the motivations of this work and briefly review the literature to identify the problems we aim to solve in this thesis.
+Moreover, we discuss our objectives and preliminary contributions.
 
@@
 community of agent-based services in order to maximize the utility
-of involved users, web services and community organizers?}
+of involved users, web services and community organizers?[R1]}
 
@@
 \emph{How can we model fair and stable communities as coalitions
-of agent-based web services?}
+of agent-based web services?[R2]}
 
@@
 among the community members in realistic, applicable and practical
-settings?}
+settings?[R3]}
 
@@
 So as an extension of our work, we have proposed a framework in which services can opt for performing tasks if they feel they are capable enough
-or decide to cooperate by showing the availability to perform some sub-tasks. \emph{How can we approach a cooperative model within a community where both competitive and cooperative behaviors exist?}
+or decide to cooperate by showing the availability to perform some sub-tasks.
+\emph{How can we approach a cooperative model within a community where both competitive and cooperative behaviors exist?[R4]}
 
@@
 The problem is that in real world scenarios, decisions made by independent service providers are highly distributed.
-\emph{How can we model a distributed decision making process for formation of communities of services?}
+\emph{How can we model a distributed decision making process for formation of communities of services?[R5]}
 
@@
 However, centrality and complete information are strong assumptions, which are not very compatible with real business scenarios.
-\emph{How can we train web services based on smaller set of information to operate efficiently when information is non-complete?}
+\emph{How can we train web services based on smaller set of information to operate efficiently when information is non-complete[R6]?}
 
@@
 
-\indent To summarize, the main problem we aim to tackle in this
-thesis is the formation of stable and efficient coalitions
-maximizing web services and community revenue. The main objectives
-are:
+\indent To summarize, the main problem we aim to tackle in this thesis is the formation of stable and efficient coalitions maximizing web services and community revenue. The main objectives are:
 \begin{itemize}
-\item To propose a cooperative model and analyze its solution
-concepts in order to address the problem of optimizing coalition
-formation for a stable community.
+\item To propose a cooperative model and analyze its solution concepts in order to address the problem of optimizing coalition formation for a stable community.
 
@@
 \centering
-\includegraphics[width=6in]{Figures/structure.eps}`
+\includegraphics[width=6in]{Figures/model.eps}`
 \caption{The Proposed Framework}
-\label{fig_structure}
+\label{fig_model}
 \end{figure}
 
-Figure \ref{fig_structure} highlights our contributions and proposed model for community of web service management.
+\begin{figure}[!t]
+\centering
+\includegraphics[width=6in]{Figures/c1.eps}`
+\caption{First contribution: Efficient Coalition Formation for Web Services}
+\label{fig_c1}
+\end{figure}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=6in]{Figures/c2.eps}`
+\caption{Second contribution: Analyzing Coopetition Strategies of Services within Communities}
+\label{fig_c2}
+\end{figure}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=6in]{Figures/c3.eps}`
+\caption{This contribution: Distributed decision making for dynamic formation of web services communities}
+\label{fig_c3}
+\end{figure}
+
+Figure \ref{fig_model} highlights our contributions and proposed model for community of web service management.
 

### 2015-07-03 thesis/thesis/chap4/chap4.tex
changes

--- 2015-04-22 thesis/thesis/chap4/chap4.tex
@@
 
-\chapter{Training Chapter}\label{cha:PCTLKC}
+\chapter{Distributed Decision Making for Dynamic Formation of Web Services Communities}\label{cha:PCTLKC}
 
@@
 The increasing reliance on online service providers has significantly influenced the way web services are engineered.
-Therefore, given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue.
-One practical solution towards delivering high quality services is utilizing intelligent decision making agents.
-These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users\cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Demirkan2013412, journals/tsc/ZhengZYB13, Josang:2007:STR:1225318.1225716}.
+Given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue.
+One practical solution towards delivering such quality services is utilizing intelligent decision making agents.
+These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users \cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Demirkan2013412, journals/tsc/ZhengZYB13, Josang:2007:STR:1225318.1225716}.
 However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided.
-Recent developments have attempted to shift web services from passive models, consisting of individual components, to models made up of autonomous and group-based components that share common goals.
-In group-based models, interaction, composition, and cooperation are the key challenges \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13} that directly impact the group's overall performance in achieving common goals.
-To that end, we see the emergence of web service \emph{communities}, which consist of services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}.
-A \emph{community} of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.
+Recent developments have attempted to shift web services from simple models, consisting of individual components, to models made up of autonomous and group-based components that share common goals.
+In group-based models, interaction, composition, and cooperation are the key challenges that directly impact the group's overall performance in achieving common goals \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13}.
+To that end, we see the emergence of web service \emph{communities}, which consist of grouping services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic}.
+A community of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.
 
-The advantages of community of web services are that the community facilitates the discovery of web services and provides better quality of service compared to passive models with individual components.
+Web Service communities have the advantages of facilitating web service discovery and providing better quality of service compared to individual services.
 Communities act as abstract web services, communicating with external entities via the same standard protocols that a normal web service employs.
-But, they regulate the service process via sophisticated internal communication protocols, thereby providing services based on the combined work of a number of web services.
-The downside to communities is the complexity of management involved in finding and inviting individual web services and managing the overall quality of the combined work of several web services.
+The difference is that communities regulate the service process via sophisticated internal communication protocols, thereby providing services based on the combined efforts of a number of web services.
+The downside to communities is the complexity of management involved in finding and inviting adequate individual services and managing the overall quality of the combined work of several services.
 % because although they have similar functionality, they have different attitudes.
-When interacting with communities of web services, users send their requests to the coordinators of the community, which play the role of community representative or access point.
+When interacting with a community of web services, users send their requests to the coordinator of the community, which plays the role of community representative or access point.
 The community coordinator is responsible of receiving tasks and delivering services.
-Moreover, as community representative, it verifies the credentials of new web services before accepting them into the community and kicks web services that could harm the value of the community.
+Moreover, as community representative, it verifies the credentials of new web services before accepting them into the community and kicks services that could harm the value of the community.
 
-\textbf{Challenge and Problem Statement.} In recent work, communities of web services have been proposed in order to facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities.
-However, there is a twofold challenge that yet to be addressed.
-The first part is community development, which involves finding the right web services for the community, satisfying the objectives of all the web services and community coordinators involved within the community; and the second part is from the individual web service's side because each web service aims to join the community that would guarantee the best outcome.
-The advocated solutions \cite{conf/webist/MaamarLBTS07, 10.1109/ARES.2008.7, journals/soca/XuYLZB11, 10.1109/TSC.2012.12, managing-hela-jalel, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:conf/IEEEscc/LimTMB12} have attempted to address these research problems.
-These research problems are reflected by the two challenge parts:
+\textbf{Challenges and Problem Statement.} In recent work, communities of web services have been proposed in order to facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities \cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic}.
+However,  two important challenges are to be addressed: 1) choice of the best web services during community development from the community perspective; and 2) choice of the best community to join from the web service perspective.
+The advocated solutions  \cite{10.1109/ARES.2008.7, conf/webist/MaamarLBTS07, journals/soca/XuYLZB11, 10.1109/TSC.2012.12, managing-hela-jalel, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:conf/IEEEscc/LimTMB12} have attempted to address these challenges.
+However, those solutions have two main limits:
 \begin{enumerate}
@@
 The problem is that in real world scenarios, decisions made by independent service providers are highly distributed.
-	\item The solutions either propose complex algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to find the optimal strategy to follow, or oversimplify the problem by eliminating important parameters and using approximation techniques to make the algorithms tractable \cite{10.1109/TSC.2012.12}.
+	\item The solutions either propose complex algorithms \cite{10.1109/TSC.2012.12, DBLP:conf/IEEEscc/LimTMB12, journal-community-formation} to find the optimal strategy to follow, or oversimplify the problem by eliminating important parameters and using approximation techniques to make the algorithms tractable \cite{10.1109/TSC.2012.12}.
 \end{enumerate}
 These approximation methods sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored.
-
-For example, instead of calculating the gain distribution using the complex shapely-value method, \cite{10.1109/TSC.2012.12} proposes a simple egalitarian way of distributing gain, which completely ignores the gain generated from collaborative work of sub-communities.
-Other categories of related work exist that do not focus on all the parties involved within the community \cite{DBLP:conf/IEEEscc/KhosravifarABT11}.
+For instance, instead of calculating the gain distribution using the adequate, but complex shapely-value method, the authors is \cite{10.1109/TSC.2012.12} propose a simple egalitarian way of distributing gain, which completely ignores the gain generated from collaborative work of sub-communities.
+Other categories of related work, for instance \cite{10.1109/TSC.2012.12, DBLP:conf/IEEEscc/KhosravifarABT11, DBLP:journals/ijebr/MaamarSTBB09}, restrict the decision process within the community coordinator, so other members of the community are not effectively involved.
 %And some other work which do not focus on rationality on web services or communities involved [refrences].
-In \cite{journal-community-formation} we proposed a cooperative game theory based model for aggregating web services in communities.
-A centralized decision maker in communities based on a complete knowledge of available web service quality metrics and performance, has been used to form optimal and stable communities that maximize individual and group income.
+In \cite{journal-community-formation}, we proposed a cooperative game-theory-based model for aggregating web services in communities.
+A centralized decision maker in communities, based on a complete knowledge of available web service quality metrics and performance, has been used to form optimal and stable communities that maximize individual and group income.
 However, centrality and complete information are strong assumptions, which are not very compatible with real business scenarios.
@@
 \textbf{Contributions.} In this paper, we introduce DDM, a Distributed Decision Making model for community formation that regulates web service agents’ decision making process in terms of cooperating and deciding which group to join and which service to invite for joining.
-The decision model in extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
+Unlike existing work on community formation, our decision model is extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
 The generated decision tree improves agents' understanding of the environment and how to select actions that lead towards maximizing their utilities.
-The advantage of this approach is that the tree is created from the past data and reflects comprehensive vision about agents' attitude of action selection.
-However, the tree is subject to get continuously modified to adapt with environmental changes.
+The advantage of this approach is that the tree, which is initially created from the past data, reflects a comprehensive vision about agents' attitudes in terms of their action selection based on their past experiences.
+Moreover, the tree is getting continuously updated based on both new received feedback and the outcome of chosen actions.
+This continuous update makes the approach adapted to any change in the environment.
 %The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems.
-The decision model provides web services with enough information which helps those services to efficiently decide and predict the outcome of their different possible collaborations.
-This model works in a distributed manner in which services are self-sufficient in decision making process and do not rely on a centralized decision making process.
+The decision model provides web services with enough information which helps those services efficiently decide and predict the outcome of their different possible collaborations.
+This model works in a distributed manner in which services are self-sufficient in their decision making and do not rely on a centralized decision making process.
 Our findings show that communities of web services can efficiently find the appropriate web service to invite for cooperation as well as allowing a single web service to find the best communities to join.
-In other words, the web services agents are equipped with a recommender system to suggest beneficial action.
-Moreover, communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
-In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their short-term and long-term goals; therefore, opting for best decision available.
+The proposed model can be seen as a recommneder system that suggests beneficial actions for both communities and single services.
+Communities can consider the decision model and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
+In general, DDM equips web services with efficient methods for foreseeing how their choices will impact both their short-term and long-term goals; therefore, opting for the best decision available.
 
-To effectively generate the decision model for web services, we used real data set to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another.
-The data set has been extracted by real-world QoS evaluation results from 142 users on 4,532 Web services on 64 different time slots.
-Combining these data based on each web service point of view on different time slots, we acquired 5 different unique features for 4,532 web services.
+To effectively generate the decision model for web services, we used a real dataset to extract web services' individual characteristics and used them to measure outcomes when these services cooperate with one another.
+The dataset has been extracted from real-world QoS evaluation results from 142 users on 4,532 Web services during 64 different time slots.
+Combining the available data based on each web service point of view on different time slots, we acquired 5 different unique features for those 4,532 web services.
 By engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in different time slots.
-We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others.
-All paths and the outcomes are labeled to be utilized in the training model.
+We were able to investigate the path a web service might take to achieve the best utility out of effective interactions with others.
+All the paths and outcomes are labeled to be utilized in the training model.
 Using cross validation sets, web services are able to compute the optimal hypothesis function (using logistic regression) that can be used to predict outcomes of cooperative work with other individual web services or communities.
-Our findings show that web services equipped with DDM have by far better outcomes in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.
+Our findings show that web services equipped with DDM have by far better outcomes than the ones that either do not cooperate or randomly find communities to join.
 
-\section{Preliminaries and Challenging Issues}\label{s:preliminaries}
+\section{Preliminaries and Challenging Issues}\label{s4:preliminaries}
 %In this section, we first present the architecture of DDM.
@@
 Nowadays, web API, standards that do not require XML-based web service protocols like SOAP and WSDL are also emerging.
-They are called REST (representational state transfer) services, which are moving towards simpler communication protocols.
+They are called RESTful (representational state transfer) services, which are moving towards simpler communication protocols.
 %They are not restricted
@@
 Service providers usually charge end users for services they provide.
-For example, Google has listed pricing and plans for a wide range of services they provide on their web service console page\footnote{https://code.google.com/apis/console}.
+For example, Google has listed pricing and plans for a wide range of services they provide on their web service console page\footnote{$https://code.google.com/apis/console$}.
 
-In this paper, we abstract web services as rational agents\footnote{The term rational is used here in the sense that web services are utility maximizers} that provide services to end users.
+As in other proposals \cite{journals/mags/BaldoniBM10,10.1109/TSC.2012.12,DBLP:conf/IEEEscc/KhosravifarABT11}, in this paper, we abstract web services as rational agents\footnote{The term rational is used here in the sense that web services are utility maximizers.} that provide services to end users.
 They aim to maximize their individual income  by receiving enough requests from end users.
@@
 
-The community of web services is essentially a virtual group of web services having similar and complementary functionalities\cite{DBLP:journals/ijebr/MaamarSTBB09}.
+The community of web services is essentially a virtual group of web services having similar functionalities \cite{DBLP:journals/ijebr/MaamarSTBB09}.
 Communities aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols to those used by single web services.
 Web services join communities to increase utility by having a larger market share and task pool.
-Community coordinators are responsible for community development, managing membership requests from web services and distributing user tasks among the community members.
-Community coordinators try to attract quality web services to join and keep the community as stable and productive as possible to gain a better reputation and user satisfaction, which increases the community's market share.
+The community coordinator is responsible for securing the community, managing membership requests from web services and distributing user tasks among the community members.
+The coordinator tries to attract quality web services to join and keep the community as stable and productive as possible to gain better reputation and user satisfaction, which increases the community's market share.
 How web services reside within communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
@@
 \subsection{The Join Challenge}\label{s:tjc}
-Sometimes, web services can increase their overall utility by collaborating with other web services as communities.
-This collaboration helps them with better ways of sharing resources and having higher reputation, better market share and wider visibility.
-Web services and communities come with different internal and external parameters, and the long-term outcome is dependent on these parameters.
+It has been showed in \cite{10.1109/ARES.2008.7,10.1109/TSC.2012.12,journal-community-formation} that web services can increase their overall utility by collaborating with other web services within communities.
+This collaboration provides them with better ways of sharing resources and having higher reputation, greater market share and wider visibility.
+Web services and communities come with different quality metrics, and the long-term outcome depends on these metrics.
 
 The goal of all parties involved in the community is to maximize their long-term outcome while they are operating as part of the community.
-Web services need to be equipped with a selection strategy to choose from all of the different possible collaboration groups they can form as well as an estimation method for evaluating the long-term gain of joining different possible communities.
-Web services need to experiment with different possible collaborative groups and other web services in order to estimate their gain over time.
+Web services need to be equipped with a selection strategy to choose from the different possible collaboration groups they can form as well as an estimation method for evaluating the long-term gain of joining different possible communities.
+Web services need to experiment with different possible collaborative groups in order to estimate their gain over time.
 However, with a high number of possible communities, it is not possible to test collaboration with random web services.
-Even if a linear approximate function for estimating utility based on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell_number$} growth rate of the possible number of partitions of web services into communities would make any brute-force type algorithm for the best community selection strategy intractable and impractical in real-world application settings.
+Even if a linear approximate function for estimating utility based on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell\_number$} growth rate of the possible number of partitions of web services into communities would make any brute-force type algorithm for the best community selection strategy intractable and impractical in real-world application settings.
 
 \subsection{Join Consequences}\label{s:jc}
-It is worth mentioning that a \emph{join} event takes place as a result of two parties that are looking to expand their collaborations.
+It is worth mentioning that a \emph{join} event takes place as a result of interaction between two parties that are looking to expand their collaborations.
 All actions are chosen in an attempt to enhance the overall outcome.
@@
 % long term.
-This is the case when a single web service joins a community, but the complex process of task allocation eliminates the visibility of the web service and, thus, the web service stays idle within the community, which makes the join action a bad decision.
+This is the case when a single web service joins a community, but the complex process of task allocation eliminates the visibility of that service, which stays idle within the community.
+This makes the join action of that service a bad decision.
 The same event might be beneficial for the community, as it hosts a new web service that can engage in performing a new coming task.
-But overall, neither side benefits from collaborating with the other and the join event has negative consequences for at least one side's utility.
+But overall, in this particular case, if the new web service stays idle for a long period of time, neither side will benefit from collaborating with the other and the join event will result in negative consequences for at least one side's utility.
 
 The more common scenario is when both parties benefit from the joining of a web service to a community.
-This action is rational, as both the web service and the community enhance the utility.
-However, the community may not be the best choice for the web service to join.
-In other words, the web service could have joined a better community, but, due to of lack of knowledge about the surrounding environment, joined the available community which was not the optimal choice.
-Since the community does enhance its utility, the web service could stay with that community, which results in a sub-optimal increase in web service's utility.
-In the following section the proposed model provides solutions that effectively address the aforementioned challenges.
+This joining action is then rational as both the web service and community enhance their utilities.
+However, the community may not be the best choice for the web service.
+In other words, the web service could have joined a better community if it had enough and accurate knowledge about the surrounding environment.
+Since the community does enhance its utility, the web service could stay with that community, which results in a non-optimal increase in web service's utility.
+In the following section, the proposed model provides solutions that effectively address the aforementioned challenges.
 
@@
 
-In this section, we discuss the parameters that we use in the rest of the paper. Then we present the task distribution and revenue model of our distributed web services communities.
+In this section, we discuss the parameters that we use in the rest of the paper. Then, we present the task distribution and revenue model of our distributed web services communities.
 
@@
 
-  \item \emph{Throughput $(Th_{C})$} is the rate at which a service can process requests.
+  \item \emph{Throughput} is the rate at which a service can process requests.
 QoS measures can include the maximum throughput or a function that describes how throughput varies with load intensity.
 Throughput is a positive real number.
-For communities the expected throughput value of collaborating web services can be estimated as summation of throughputs of all the services inside:
+For a given community $C$, the expected throughput value $(Th_{C})$ can be estimated as the summation of throughput of all the service members $Th_{w}~ (w \in C)$:
 
 	\begin{equation}
-		 Th_{C} = \left\{
-			\begin{array}{l l}
-				Th_{w} & \quad \text{if $|C| = 1$}\\
-				\sum_{w \in C}{(Th_{w})} & \quad \text{if $|C| > 1$}
-			\end{array} \right.
+		 Th_{C} = \sum_{w \in C}{(Th_{w})}
 	\end{equation}
 
-	\item \emph{Availability $(A_{C})$} is the percentage of time that a service is operating.
-	The probability that the service operation is accessible.
-Availability is also a real number in the range $[0, 1]$.
-For communities the expected availability of collaborating web services considering they follow a parallel system can be estimated as:
+	\item \emph{Availability} is the percentage of time that a service is operating. It is computed as
+the probability that the service operation is accessible.
+Availability of a web service $A_w$ is a real number in the range $[0, 1]$.
+For a community $C$, the expected availability $(A_{C})$ considering the members operate in parallel (independently from each other) can be estimated as:
 
 	\begin{equation}
-		A_{C} = \left\{
-			\begin{array}{l l}
-				A_{w} & \quad \text{if $|C| = 1$}\\
-				1-\prod_{w \in C}{(1-A_{w})} & \quad \text{if $|C| > 1$}
-			\end{array} \right.
+		A_{C} = 1-\prod_{w \in C}{(1-A_{w})}
 	\end{equation}
 
-	\item \emph{Execution Time $(Et_{C})$} is the time a service takes to respond to various types of requests.
+	\item \emph{Execution Time} is the time a service takes to respond to various types of requests.
 	%is the expected delay between the time instant when a request is sent and the time when the result is obtained.
-	Execution time is measured in milliseconds.
-Execution time can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests.
+	Execution time is usually measured in milliseconds and can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests.
 This internal feature is a positive integer.
-For communities, the expected execution time of collaborating web services can be estimated as the execution time of the bottleneck service which is the service with the slowest execution time:
+For a typical community $C$, the expected execution time $Et_{C}$ can be estimated as the execution time of the bottleneck service which is the service with the slowest execution time $Et_{w}$:
 
 	\begin{equation}
-		Et_{C} = \left\{
-			\begin{array}{l l}
-				Et_{w} & \quad \text{if $|C| = 1$}\\
-				max_{w \in C}{(Et_{w})} & \quad \text{if $|C| > 1$}
-			\end{array} \right.
+		Et_{C} = max_{w \in C}{(Et_{w})}
 	\end{equation}
@@
 
-	We normalize the range of these features so that each feature contributes approximately proportionately to the final utility outcome value.
-We adopt the \emph{standardization} method.
-We subtract the \emph{mean} from each feature then we divide the values of each feature by its \emph{standard deviation}.
+	We normalize the range of these features so that each feature contributes proportionally to the final utility outcome value.
+We adopt the \emph{standardization} method consisting of subtracting the \emph{mean} from each feature, then dividing the subtraction result by the \emph{standard deviation}.
 
@@
 The quantitative values of quality metrics need some benchmark values to represent their goodness.
-In other words, without some benchmark values it would be difficult for web services to identify their goals, and performance quality at any specific value of these metrics.
-Therefore, we have introduced two external features for assessing web services' estimate with regard to their standing among other web services.
+In fact, without some benchmark values, it would be difficult for web services to identify their performance quality at any specific value of these metrics.
+Therefore, we introduce two external features for assessing web services' estimate with regard to their standing among other web services.
 
 \begin{itemize}
-  \item \emph{External Parameter 1} $(exp_1)$.
-is an estimate of how close the web service's \emph{execution time} is to other web services.
-It is the difference between a web service's \emph{execution time} metric and the maximum value of execution time of all the other web services, about which the web service has information of them.
-The less value means web service has better execution time compared to other web services.
+  \item \emph{External Parameter 1} ($Exp1_i$ where $i$ is a community or a web service) is an estimate of how close the community's or the web service's \emph{execution time} is to the best execution time in the whole system.
+It is the difference between a community's or a web service's \emph{execution time} metric and the minimum value of execution time of all the other communities or web services.
+The smaller the value the better the external feature compared to other peers.
+In other words, small value of $Exp1_i$ means $i$ is among the best communities or services in the system.
 	\begin{equation}\label{exp_1:f}
-		exp_1 = Et_{i} - Et_{max}
+		Exp1_i = Et_{i} - Et_{min}
 	\end{equation}
-	\item \emph{External Parameter 2} $(exp_2)$ is a comparison of the web service's rate of performing tasks to other competing web services.
-It is the difference between a web service's \emph{throughput} metric and the maximum value of throughput of all the other web services,, about which the web service has information of them.
-The less value means web service has better throughput compared to other web services.
+	\item \emph{External Parameter 2} ($Exp2_i$ where $i$ is a community or a web service)  is a comparison of the community's or the web service's rate of performing tasks to the best rate in the system.
+It is the difference between a community's or a web service's \emph{throughput} metric and the maximum value of throughput in the system.
+As for $Exp1_i$, the smaller the value the better the external feature.
 	\begin{equation}\label{exp_2Lf}
-		exp_2 = Th_{max} - Th_{i}
+		Exp2_i = Th_{max} - Th_{i}
 	\end{equation}
@@
 
-A community of web services is abstracted as a standard web service that provides services that share the same internal and external features mentioned for web services.
-Inside, they adopt different protocols to manage the community; however, other web services or end users can communicate with communities of web services, using standard protocols, and inner details will be encapsulated for their clients.
-
 \subsection{Task Distribution}
 
-Communities of web services usually employ an implementation of Contract-Net protocol for task distribution, in which services opt for incoming tasks, and receive the tasks for which they ask.
-However, in our model, our community members would try to distribute tasks based on their capabilities and the QoS parameters provided by the web services.
-We have used a slightly modified \emph{weighted fair queuing} method to distribute tasks among community members.
-The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{ws}$.
-In the \emph{weighted fair queuing} method, the input flow is multiplexed along different paths; however, in our case, if the rate of incoming tasks is less than the community's total throughput $(Th_{C})$, which is the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with a delay.
+Communities of web services usually employ an implementation of Contract-Net protocol for task distribution, in which services bid on incoming tasks, and receive some of the tasks for which they bid \cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:conf/aina/ElnaffarMYBT08}.
+In our model, our community members would try to distribute tasks based on their capabilities and the QoS parameters provided by the web services.
+We use a slightly modified \emph{weighted fair queuing} method to distribute tasks among community members.
+The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{w}$ for each web service $w$.
+In the \emph{weighted fair queuing} method, the input flow is multiplexed along different paths.
+However, in our model, if the rate of incoming tasks is less than the community's total throughput $(Th_{C})$, which is the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with a delay.
 %Thus, the amount of tasks performed by the community is $\sum_{ws}{Th_{ws}}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$.
-However, when the incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $|input Task Rate| \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) within the community.
+When the incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $Itr \times \frac{Th_{w}}{\sum_{w}{Th_{w}}}$ for each web service $w$ within the community, where $Itr$ is the input task rate.
 
-While distributing tasks, the community members can verify the performance, throughput and quality of service of tasks being performed by web services.
+While distributing tasks, the community can verify the performance, throughput and quality of service of tasks being performed by web services.
 The community can assess if those web services are capable of performing the number of tasks they advertised.
@@
 
-The $\alpha$ and $\beta$ values are internal and external weight coefficients.
-Execution time and external parameters are better when they have smaller values hence the negative coefficient for them.
-The result is then multiplied to the throughput value $Th_{C}$, since communities are performing tasks with $Th_{C}$ rate.
+The $\alpha$ and $\beta$ parameters are internal and external weight coefficients.
+Small values for execution time and external parameters ensure better performance, which justifies their negative coefficients.
+The result is then multiplied by the throughput value $Th_{C}$, since communities are performing tasks with $Th_{C}$ rate.
 
-The estimation can be improved, especially in cases where the input task rate is high and services are experiencing high task loads.
+\begin{theorem}
+The function given in Equation \ref{u_c_normal} satisfies the properties of $f$.
+\end{theorem}
+
+The proof of this theorem is straightforward by simply calculating the partial derivative $\partial f$ with respect to the different variables.
+
+The estimation of the utility can be improved, especially in cases where the input task rate is high and services are experiencing high task loads.
 The \emph{weighted fair queuing} method of task distribution would distribute tasks based on the individual throughput $(Th_{w})$ value of services within community.
-The services with higher throughput will affect the overall utility of the community more because they would take on proportionately more tasks.
+In fact, services having higher throughput affect strongly the overall utility of the community because they would take on proportionality more tasks.
+The improved utility is given as a function of individual internal and external parameters:
+
+\begin{equation}\label{improved_u_c_general}
+U_{C} = g_{w\in C}(A_{w}, Et_{w}, Exp1_{w}, Exp2_{w}, Th_{w})
+\end{equation}
+%
+where $g_{w\in C}$ is increasing in $A_{w}$ and $Th_{w}$ and decreasing in $Et_{w}, Exp1_{w}$ and $Exp2_{w}$. An example of this function is given in Equation \ref{u_c_load}:
 
@@
 %We used a data set extracted from running web services. In this data set,
-Each web service is associated with a number of features that reflect its functionality.
+Each web service is associated with a number of quality metrics that reflect its non functional parameters.
 These web services operate in an online environment and are continuously assigned tasks to handle.
-Sometimes, they pass tasks around, distributing sub-tasks among themselves and handling tasks in a collaborative effort.
-To engage in communities, we add additional features that reflect web services' utility as a result of joining other web services to form a community.
-The additional features are computed based on two assumptions that we adopt for a community to be formed.
-Our raw data set provides us with 64 different time slots of extracted features for each web service.
-Using this data we can build a synthetic data set that contains features of a large number of web services in a sequence of time.
-Therefore, we train a learning model that adopts the trend of joining a community and use the model to predict/find the appropriate community for other web services.
-To train our model, we build a decision tree as a benchmark for our decision making mechanism.
-The decision tree is built by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services.
-As a result, we are able to classify web services as either single or joined and propose the communities that are best fitted to the web services' requirements.
+%To engage in communities, we add the external features that reflect web services' utility as a result of joining other web services to form a community (see Section \ref{s:ef}).
+%The additional features are %computed based on two assumptions that we adopt for a community to be formed.
+We used the web services data set provided in \cite{10.1109/ISSRE.2011.17}.
+The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{http://www.wsdream.net/}.
+%In this data set, each web service is associated with a number of features that reflect its functionality.
+%Our raw data set provides us with 64 different time slots of extracted features for each web service.
+Using this data, we built a synthetic data set that contains features of a large number of web services and communities in different time intervals.
+The goal is to use the data set to train a decision-making model that adopts the trend of joining a community and use the model to predict/find the appropriate community for other web services.
+%To train our model, we build a decision tree as a benchmark for our decision making mechanism.
+The decision tree is made up by training the real data obtained from operating web services and extracting features related to their performance, either alone or as part of a joint effort with other web services.
+The ultimate objective is to propose for each web service and community the best joint decision about forming a group that maximizes every one's utility.
 
-\subsubsection{Filtered Data}\label{sss:filtereddata}
+\subsubsection{Feature Extraction}\label{sss:filtereddata}
 
-We have adopted the web service data set provided by \cite{10.1109/ISSRE.2011.17}.
-The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{http://www.wsdream.net/}.
-In this data set, each web service is associated with a number of features that reflect its functionality.
-By summarizing the data provided for each web service over different time slots, we have acquired three quality features for each individual web service.
-Their quality features are the three internal features introduced in Section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time}.
+By processing the data provided for each web service over different time slots, we obtain the three internal quality features introduced in Section \ref{s:if}: \emph{throughput}, \emph{availability} and \emph{execution time} and the two external features discussed in Section \ref{s:ef}.
+In fact, web services and communities are represented using feature vectors of these five internal and external features.
+
 %To engage in communities, we add two additional external features that reflect web services estimation of its quality metrics compared to other web services.
-Therefore, we have generated an array of web services with three distinct features.
+%Therefore, we have generated an array of web services with three distinct features.
 
 \begin{figure}%[!t]
-\centerline{\includegraphics[width=3.25in]{figures/cfvs.eps}}
-\caption{Communities with different properties of web services actively looking for other communities to collaborate with, they send collaboration requests to communities they find the collabration  increasing the gain}
+\centerline{\includegraphics[width=3.15in]{figures/cfvs.eps}}
+\caption{Communities with different properties of web services actively looking for other communities to collaborate with}
 \label{fig_community}
@@
 
-Now, we want to generate a set of feature vectors representing the communities of web services for training purposes.
-For communities, we add two additional external features, as discussed in Section \ref{s:ef} that reflect the community's estimation of its quality metrics compared to other web services.
-Therefore, we formulate a \emph{Community Feature Vector (CFV)} as $CFV_{<C>} = \{f_1,...f_5\}$ having a community of $k$ web services.
-$C = {ws_1,...ws_k}$.
-The features $f_1$ through $f_5$ represent the \emph{execution time}, \emph{throughput}, \emph{availability} and the \emph{external parameters 1 and 2} correspondingly.
+%By combining these three internal features to the two external features discussed in Section \ref{s:ef} that reflect the community's estimation of its quality metrics, we generate a set of feature vectors representing the communities of web services for training purposes.
+
+We formulate a \emph{Community Feature Vector (CFV)} as $CFV_{<C>} = [f_1,...f_5]$ having a community of $k$ web services ($C = \{ws_1,...ws_k\}$, $k \geq 1$)\footnote{A web service is considered as a community of one web service.}.
+The features $f_1$ through $f_5$ represent the \emph{execution time}, \emph{throughput}, \emph{availability} and the \emph{external parameters 1 and 2} respectively.
 A set of communities, with their feature vectors and utilities evaluated, provides our algorithm with a raw training data set.
-We call this set of communities the \emph{template vector}, and the set of feature vectors associated with the \emph{template vector} is referred to as the \emph{community feature vector set (CFVS)}.
-Figure \ref{fig_community} depicts communities looking to form collaborate communities and join other communities in order to improve their utility gain.
+We call this set of communities the \emph{template vector} $CS$, and the set of feature vectors associated with the \emph{template vector} is referred to as the \emph{community feature vector set (CFVS)}.
+Figure \ref{fig_community} depicts web services and communities looking to form new groups in order to improve their utility gain.
 
 \subsubsection{Feature Engineering}\label{sss:feng}
-Let $CFVS = \{C_1, C_2,..., C_N\}$ be the community feature vector set with $N$ communities.
-Based on the $CFVS$ set, we create an $|N \times N|$ gain matrix for $t$ different time slots.
-Each entry of $gain_{n,m}^{t}$corresponds to a utility gain of web services in $C_n$, when $C_n$ joins $C_m$, based on community and web service data available for time $t$.
-All of these values have to be evaluated by implementing the community with members of $ws_i \in C_n$ and $ws_j \in C_m$ and evaluating its utility (see Equation \ref{u_c_load}).
-Therefore $gain_{n,m}^{t} = U_{C_n \cup C_m}^{t} - U_{C_{n}}^{t}$.
-Evaluating the utility gain for all entries of the $gain$ matrix can be a costly process with a very big number of $N$, size of the feature vector $|N|$ should be chosen carefully.
+Let $CFVS = \{CFV_{<C_1>}, \dots, CFV_{<C_N>}\}$ be the community feature vector set with $N$ communities.
+Based on the $CFVS$ set, we create an $|N \times N|$ gain matrix $gain^{t}$ for each time slot $t$.
+Each entry $gain_{n,m}^{t}$ corresponds to a utility gain of community $C_n$ when it joins community $C_m$.
+This gain is computed as follows: $gain_{n,m}^{t} = U_{C_n \cup C_m}^{t} - U_{C_{n}}^{t}$ where $U_{C_n \cup C_m}^{t}$ and $U_{C_{n}}^{t}$ are the utilities at time $t$ computed using Equation \ref{u_c_load}.
+Evaluating the utility gain for all entries of the $gain^t$ matrix is a computationally heavy process when $N$, the size  of the feature vector set, is large.
+Therefore, this size should be chosen carefully.
 
 \begin{table*}[ht]
+\footnotesize
 \caption{An example of $gain$ matrix for 3 different communities and their combinations} % title of Table
@@
 
-Now, we let our set of communities in the $CFVS$ set, within $|T|$ time frame iterations, choose the the best communities to join.
-Each community is provided with the corresponding row of data from the $gain$ matrix.
-Basically, $C_i$ is provided with the data in row $i$ of matrix $gain_{N,N}$, which is all of the possible utility values it can gain by joining different communities.
-By ordering the list, each community is utilized with an ordered set of preferences over other communities it likes to join.
-We define $>_{i}^t$ as the preference order of community $i$ at time $t$.
+%Now, we let our set of communities in the $CFVS$ set, within $|T|$ time frame iterations, choose the the best communities to join.
+Each community is provided with the corresponding row of data from the $gain^t$ matrix.
+Basically, $C_i$ is provided with the data in row $i$ of this matrix, which reports all the possible utility values $C_i$ can gain by joining different communities.
+By ordering the utility gain values of the row, each community is equipped with an ordered set of preferences over other communities it can join.
+We define $\geq_{i}^t$ as the preference order of community $i$ at time $t$.
 
-Let $P_{C_i}^t = \{C_1 >_{i}^t C_2 >_{i}^t ....
->_{i}^t C_n\}$ be an ordered set of preferences for community $C_i$ at time $t$.
-Based on this ordered set, we define $K^t(C_i, k)$ as a set of the $k$ most preferred communities of community $i$ at time $t$.
+Let $C_1 \geq_{i}^t C_2 \geq_{i}^t ~\dots~ C_{i-1} \geq_{i}^t C_{i+1} \geq_{i}^t ~\dots~ C_n$ be an ordered sequence of preferences for community $C_i$ at time $t$.
+Based on this sequence, we define $K^t(C_i, k)$ as a set of the $k$ most preferred communities of community $i$ at time $t$.
 %\subsubsection{feature vector generation}\label{sss:fvg}
@@
 \begin{split}				
-K^t(C_i, k) = &\Big\{C_x | C_x >_{i}^t C_y; \forall C_y \in CFVS\ \\
-				      &\wedge C_y \notin \{K^t(i, 1),K^t(i, 2),...,K^t(i, k-1)\} \Big\}				
+K^t(C_i, 0) = &\emptyset \\
+K^t(C_i, k) = &\Big\{C_x | C_x \geq_{i}^t C_y ~\forall C_y \in CS ~\wedge~ C_x \neq C_y ~\wedge~ C_y \notin K^t(C_i, k-1) \Big\}				
 \end{split}
 \end{equation}
-Based on $K^t(C_i, k)$, we define a set of communities for $C_i$ in which they are the k most preferred communities for community $i$ and also community $i$ belongs to the k most preferred communities out of all of the communities in set $K^t(C_i, k)$.
-This basically implies the preference is both-sided.
+Based on $K^t(C_i, k)$, we define a set of communities $C_j$ for $C_i$ which are the $k$ most preferred communities for $C_i$ and $C_i$ belongs to the $k$ most preferred communities of $C_j$.
+This basically yields the preference in both sides.
 \begin{equation}\label{l_t_top_both}
 \begin{split}	
-L^t(C_i,k) = &\Big\{C_j | C_j \in K^t(C_i, k) \\
-             &\wedge C_i \in \bigcup_{C_x \in K^t(C_j, k)}K^t(C_x, k)\Big\}
+L^t(C_i,k) = \Big\{C_j | C_j \in K^t(C_i, k)~ \wedge~ C_i \in K^t(C_j, k)\Big\}
 \end{split}
@@
 % as well as the joined events that took place in different time slots.
-In addition to best choices, web services have access to other ordered choices and can look for the second best or third best if their first try is rejected by the target community.
-The consequences of each try level is analyzed in more detail in the following section, in which we launch experiments and investigate the effectiveness of the use of a decision tree with different decision layers in joining other communities and enhancing the overall utility.
+In addition to the best choice, web services have access to other ordered choices and can look for the second best or third best if their first try is rejected by the target community.
+This aspect is analyzed in more detail in the following section, in which we launch experiments and investigate the effectiveness of the use of a decision tree with different decision layers in joining other communities and enhancing the overall utility.
 
@@
 
-Our goal is to create a decision making profile for each community in the $CFVS$ set.
-We are creating an environment where they can experience the outcomes of different strategies.
-The result will be a decision tree of the feasible and utility increasing moves over time.
+Our goal is to create a decision making profile for each community in the
+$CFVS$ set. We are creating an environment where the communities can experience the
+outcomes of different strategies. The result will be a decision tree of the
+feasible and utility-increasing moves over time. The root of the decision tree
+represents a community in the $CFVS$ set, and the other nodes represent
+the communities resulting from the parent node's action of joining them along with their feature values and
+expected utility.
 
-We let communities pick the best communities for maximizing their utilities over different time frames.
-At time $t = 1$, we let each community in the $CFVS$ set choose the best community, which is a single community in set $C_j = K^t(C_i, 1)$.
-If community $C_j$ also has the highest preference to join $C_i$ meaning the $L^t(C_i, k=1)$ set is not empty, they would join together.
+We let communities pick the best communities maximizing their utilities over different time frames.
+At time $t = 1$, we let each community in the $CFVS$ set choose the best community, which is a single community in the set $\{C_j\} = K^t(C_i, 1)$.
+If community $C_j$ also ranks $C_i$ to be the highest preferred community to join, meaning the set $L^t(C_i, k=1)$ is not empty, they would join each other.
 Having set $k = 1$ is a very strict and hardly satisfiable condition.
-In order to relax the requirement, the value of $k$ is being increased by a rate $r$ proportional to time slot $t$.
-Basically, $k = 1 + |r \times t|$.
-On early steps of simulation web services and communities are more strict but as time goes on, we let them choose second and then third best options too.
-However, increasing $k$ quickly increases the time complexity of $K^t(C_i, k)$ by $O(k^2 \times n.log(n))$.
+In order to relax the requirement, we increase the value of $k$ by a rate $r$ proportional to time slot $t$: $k = 1 + |r \times t|$.
+On early steps of the training process, web services and communities are more strict, but as time goes on, we let them choose second and then third best options too.
+However, increasing $k$  increases the time complexity as well.
 
-When communities $C_i$ and $C_j$ are in each other's top $k$ preference set, their combination is added to the list of possible communities that can join others at time $t+1$.
-Also, for each community $C_i$ in our initial $CFVS$ set, we maintain a tree with the community $C_i$ as its root.
-Its children are all of the communities that $C_i$ decided to join.
+When communities $C_i$ and $C_j$ are in each other's top $k$ preference set, the new combined community, i.e., $C_i \cup C_j$ is added to the list of possible communities that can join others at time $t+1$.
+Moreover, for each community $C_i$ in our initial $CFVS$ set, we maintain a tree with the community $C_i$ as its root.
+Its children are all the communities that $C_i$ decided to join.
 As the scenario progresses over time, the merged communities may decide to join other communities.
-When community $C_i$ and $C_j$ decide to join each other and create community $C_k$, the new community $C_k$ will be added as a child to both $C_i$ and $C_j$ nodes.
-At the end of the process, each community is utilized with a tree of set of possible combination of communities it can join.
+When communities $C_i$ and $C_j$ decide to join each other and create community $C_k$, the new community $C_k$ will be added as a child to both $C_i$ and $C_j$ nodes.
+At the end of the process, each community is utilized with a tree representing all possible combinations of communities it can join.
 Algorithm \ref{algo:dectree} illustrates the DDM tree creation procedure as pseudo-code.
-
-Having created $|n|$ trees, for each community $C_i$, our communities are utilized with the different possible paths they can take to maximize their utilities.
-Using a distance function, communities and web services can utilize these results and find the $C_i$ that closely resembles their parameters.
-They will be utilized with a tree that has the strategies the community can use to join our communities which will be best possible path to take and communities to join while most likely being accepted by other communities since its a two sided preference.
-The algorithm below describes the tree creation process.
 
@@
 
+Having created $|n|$ trees, one per community, our communities are utilized with the different possible paths they can take to maximize their utilities.
+Using a distance function\footnote{See Section \ref{s:experiments} for an example of this function.}, communities and web services outside the training set can find the community that closely resembles their parameters within the $CFVS$ set.
+Those new communities can use the trees of the closest communities in the training set to have an estimation of the outcome of all possible joining actions they can take.
+By so doing, new communities can request to join the best communities which will maximize their gain.
+Such a request is most likely to be accepted as the decision considers the preferences and utility gain of the other side as well.
+
+As a real scenario example from the used data set, Figure \ref{fig_tree} depicts a snapshot from a decision tree created by the DDM algorithm for a particular singleton community $C_{1273}$.
+This tree shows the different communities that $C_{1273}$ has experienced with during the training process.
+Each line shows the web services list within a community, the community's feature vector and the last value on each line is the overall gained  utility of the community.
+
+\begin{figure}%[!t]
+\centerline{\includegraphics[width=6.25in]{figures/tree1.eps}}
+\caption{A partial view of a decision tree created by DDM}
+\label{fig_tree}
+\end{figure}
+
 \textbf{Complexity.} Here we analyze the computational complexity of the DDM decision tree creation algorithm on each time iteration $t$.
-Computing top $k$ preferred communities for $C_i$ in $L^t(C_i, k)$ requires an $O(n.log(n))$ sort time.
-$C_i$ has a result set of size $|k|$, and for each of those $k$ communities we need to check against their $k$ top preferred communities.
-Considering we already have the list sorted, line 6 in algorithm runs $O(k \times n.log(n))$ times.
-Doing this search for all communities in $|CFVS|$ set $n$ times (line 5), the overall order of complexity of the algorithm in regards with $n$ and $k$ is: $O(k^2 \times n^2.log(n))$.
+Computing top $k$ preferred communities for $C_i$ in $K^t(C_i, k)$ requires $O(n.log(n))$ sort time.
+The size of $K^t(C_i, k)$ is $k$, and for each of those $k$ communities, we need to check against their $k$ top preferred communities, which needs $O(k^2)$.
+Line 5 iterates through $n$ communities, Line 6 takes $O(n.log(n))$ to compute and iterates $k$ times, and considering we already have the list sorted, Line 7 can reuse the sorted preferences.
+Thus, Line 7 takes $O(k)$ time to check if $C_i$ is member of $K^t(C_i, k)$.
+Multiplying these iterations, the order of complexity of the algorithm with regard to $n$ and $k$ for each time slot is: $O(k^2 \times n^2.log(n))$.
+Since the whole algorithm runs $T$ times, the overall complexity is $O(T \times k^2 \times n^2.log(n))$.
 
 \section{Experiments}\label{s:experiments}
-We implemented DDM in Java\footnote{Source code of implementation and data is available at: \emph{https://github.com/Marooned202/DDM}}.
-We have extracted the set of features for 4532 web services in 64 different time slots through a data set provided by \cite{10.1109/ISSRE.2011.17}.
-By choosing 86 web services out of these sets and choosing a subset of all possible combinations of sizes 2, 3, and 4 of these 86 web services, we have chosen 10,000 communities and evaluated the feature vectors and utilities they can have in 64 different time slots.
+We implemented DDM in Java\footnote{Source code of implementation and data is available at: $https://github.com/Marooned202/DDM$}.
+We recall that we have extracted the set of features for 4532 web services in 64 different time slots through a data set provided in \cite{10.1109/ISSRE.2011.17}.
+By randomly choosing 86 web services out of this data set for each run, and selecting a subset of all possible combinations of sizes 2, 3, and 4 of these 86 web services, we have been able to create 10,000 communities and evaluated the feature vectors and utilities they can have in the 64 time slots.
 This provides us with the initial training feature set of size $|CFVS| = 10,000$ communities.
-Based on Equation \ref{u_c_load} the utility of these communities are estimated, and the gain matrix $|10000 \times~ 10000|$ of all possible ways of merging these 10,000 communities, is generated\footnote {The template vector and gain matrix generated are available at \emph{https://github.com/Marooned202/DDM/tree/master/wsds/data/run}}, and each community has the ordered preference among other communities known in the set.
+Based on Equation \ref{u_c_load}, the utilities of these communities are estimated, and then the $gain$ matrix of size $|10,000 \times~ 10,000|$ of all possible ways of merging these 10,000 communities is generated\footnote {The template vector and $gain$ matrix generated are available at $https://github.com/Marooned202/DDM/tree/master/wsds/data/run$}.
+Based on the $gain$ matrix, each community has an ordered preference among other communities in the set.
 
@@
 Now, we evaluate the performance of the decision profiles generated based on our data set for other communities.% which are not included in the decision tree creation process.
-We create one thousand communities from the web services in the data set that were not involved in the decision model creation process.
-We define a distance function that measures the difference between basic features of communities, which measures the similarity of communities.
+We create 1,000 communities from the web services in the data set that were not involved in the training process of our decision model.
+We define a distance function that measures the difference between basic features of communities, which measures the similarity among communities.
 
@@
 Figure \ref{stats3} depicts the average community size over time, which essentially represents the number of new communities being formed.
-Once again, these results show that the runs with higher search rates tend to find appropriate communities to join faster.
+The results show once again the communities using DDM with higher search rates grow faster in size, implying that the communities find appropriate web services to join with faster.
 
@@
 \section{Related Work}\label{s:related_work}
-
-In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
-defined communities as \emph{Service Containers} that aggregate
-substitutable web services providing a common functionality (same
-set of operations). They abstracted \emph{Service Containers} as
-web services that are created, advertised, discovered and invoked
-just as elementary web services. The \emph{Container} is
-considered as a manager that is responsible for web service
-selection upon receiving a request on run-time. The authors have
-proposed a scoring service based on non-functional requirements of
-the request and web service capabilities to dynamically chose the
-web service to perform the requested task. A similar concept was
-proposed by Maamar et al. in
-\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
-web service communities as a collection of web services with a
-common functionality but different QoS properties. A community
-manager, upon receiving a request, delegates the request to one of
-its current members. The choice is based on the performance
-history and quality metrics of each web service. The authors have
-proposed an efficient global web service selection algorithm in
-order to approach quality constraints and preferences for
-composite services which require aggregation of different types of
-services to satisfy the user.
-
-Benslimane et al. \cite{Liris-2770} have proposed a multi-layer
-approach grouping similar Web services into communities and having
-an interface implemented as an abstract web service for accessing
-the community on top of the community layer. The interactions
-between composite, management and community layers and the
-bindings are performed by a generic driver called Open Software
-Connectivity (OSC).
-
-In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
-service communities with centralized access across distributed web
-services. They have proposed a framework for web service
-management, query resolution among communities and a query caching
-mechanism executed by the manager to improve the performance of
-query resolution process among many distributed communities. The
-key idea is to cache previous computed results for answering
-future queries.
-
-Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
-then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
-proposed an architecture utilizing \emph{Contract-Net} protocol
-for engineering task distribution within communities of web
-services. The protocol is centrally executed by the community
-manager. This architecture has been further developed in
-\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
-conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
-roles have been distinguished for community members: masters and
-slaves. Master web services and community managers that lead
-communities and are responsible for membership management. They
-can invite and convince slave web services to join the community,
-and attract new slave web services to their communities by
-awarding them better payoff. Moreover, they can eject some slave
-members from the community to improve its overall reputation if
-these members are misbehaving or cannot provide the promised QoS.
-
-In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
-developed a community as a ``cluster'' that groups Web services
-based on a specific area of interest. All web services in a given
-community share the same functionality. These communities are
-created by \emph{third party community providers} which use the
-\emph{community ontology} as a template and define a set of
-operations that all web services within a community should
-provide. Using semantic analysis on web service operations, web
-services either find and join a community with similar
-functionality or create a new operation description for a new
-community. The authors have described the concept of
-\emph{community agents} associated to \emph{community providers}.
-A community agent is responsible, among other things, of the
-registration of services with the community. An example of a
-community that provides health care services to senior citizens
-has been used. In this example, a governmental entity is needed to
-check the health care standards used by the members before
-authorizing them to be part of the community. Such a central
-entity is represented by the community agent. Thus, community
-agents are playing the role of community managers. In a close work
-\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
-global planning selection algorithm and a delegation algorithm to
-be run when a request to execute an operation is received by the
-community. This needs a central entity to run those algorithms.
-Such entity plays the same role as the community coordinator or
-manager.
 
@@
 All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process.
-So basically These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.
+So basically, these solutions generally suffer from high complexity, which makes decision making very hard, even impossible in some cases in a real-time fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.
 We address this issue by introducing DDM a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another.
 After being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics.
-Therefore web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
+Therefore, web services and communities can make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service.
 In general, DDM equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.
+\\
+
+\noindent \textbf{Web Service Communities}
+
+Here we introduce the related research work regarding the engineering and formation of communities of web services.
+In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
+defined communities of web services as \emph{Service Containers} that aggregate substitutable web services having the same set of operations and providing common functionalities.
+They abstracted \emph{Service Containers} as web services that are created, advertised, discovered and invoked just as elementary web services.
+The \emph{Container} is considered as a manager that is responsible for web service selection upon receiving a request on run-time.
+The authors have proposed a scoring technique based on non-functional requirements of the request and web service capabilities to dynamically chose the web service to perform the requested task.
+A similar concept was proposed by Maamar et al.
+in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+The authors introduced web service communities as a collection of web services with a common functionality but different QoS properties.
+A community manager, upon receiving a request, delegates the request to one of its current members.
+The choice is based on the performance history and quality metrics of each web service.
+The authors have proposed an efficient global web service selection algorithm in order to approach quality constraints and preferences for composite services which requires aggregation of different types of services to satisfy the user.
+In the same line of research, Benslimane et al.
+\cite{Liris-2770} have proposed a multi-layer approach grouping similar web services into communities and having an interface implemented as an abstract web service for accessing the community.
+The considered layers are: composite, management and community.
+The interactions among those layers and the bindings are performed by a generic driver called Open Software Connectivity (OSC).
+However, unlike our work, these proposals only tackle the problem of internal community management from the task execution perspective, but not the problem of community formation and the one of dynamically selecting which community to join and which web service to invite.
+Moreover, the web services selection process is done centrally by the community manager, while we address the problem more realistically from the distributed angle.
+
+In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
+service communities with centralized access across distributed web
+services. They have proposed a framework for web service
+management, query resolution among communities and a query caching
+mechanism executed by the manager to improve the performance of
+query resolution process among many distributed communities. The
+key idea is to cache previous computed results for answering
+future queries. Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
+then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
+proposed an architecture utilizing \emph{Contract-Net} protocol
+for engineering task distribution within communities of web
+services. The protocol is centrally executed by the community
+manager. This architecture has been further extended in
+\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
+conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
+roles have been distinguished for community members: masters and
+slaves. Master web services are community managers that lead
+communities and are responsible for membership management. They
+can invite and convince slave web services to join the community,
+and attract new slave web services to their communities by
+awarding them better payoff. Moreover, they can eject some slave
+members from the community to improve its overall reputation if
+these members are misbehaving or cannot provide the promised QoS.
+In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
+developed a community as a ``cluster'' that groups Web services
+based on a specific area of interest. All web services in a given
+community share the same functionality. These communities are
+created by \emph{third party community providers} which use the
+\emph{community ontology} as a template and define a set of
+operations that all web services within a community should
+provide. Using semantic analysis on web service operations, web
+services either find and join a community with similar
+functionality or create a new operation description for a new
+community. The authors have described the concept of
+\emph{community agents} associated to \emph{community providers}.
+A community agent is responsible, among other things, of the
+registration of services with the community. An example of a
+community that provides health care services to senior citizens
+has been used. In this example, a governmental entity is needed to
+check the health care standards used by the members before
+authorizing them to be part of the community. Such a central
+entity is represented by the community agent. Thus, community
+agents are playing the role of community managers. In a close work
+\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
+global planning selection algorithm and a delegation algorithm to
+be run when a request to execute an operation is received by the
+community. This needs a central entity to run those algorithms.
+Such entity plays the same role as the community coordinator or
+manager. All these proposals have in common the consideration
+of the central entity for community management, which includes the hiring and firing of the community members, while our approach is fully distributed.
+Moreover, the stability of the community has not been investigated.
+Another major difference with our work is that the decision making process is only one way and unilateral from the community manager perspective.
+In our proposal, both participants, namely communities and web services, participate in the decision making process and a joining decision is made only if it is the best option for both players.
 
@@
 
-In this paper, we proposed a training model for the problem of membership management of communities of web services.
+In this research work, we proposed a training model for the problem of membership management of communities of web services.
 Using the traning model we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves.

### 2015-07-03 thesis/thesis/chap5/chap5.tex
changes

--- 2015-04-22 thesis/thesis/chap5/chap5.tex
@@
-\chapter{LEarning Chapter}\label{cha:PCTLKC+}
+\setcounter{chapter}{4}
 
-In this chapter
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter{Coopetitive Behavior of Services within Communities}\label{cha:PCTLKC}
 
-\section{Summary}\label{sec:conclusion}
+\section{Introduction}
+
+In previous chapter, our focus was on community formation and we emphasised on cooperative behavior of the web services as agents.
+Within communities, those services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}.
+In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite.
+However, the same reason of providing similar functionalities can lead services to cooperate because they can replace each other in case of failure or unavailability, and services can do better in a coalition structure.
+Analyzing services competition and cooperation strategies within communities is still an open problem that motivates the research described in this section.
+we propose a mechanism within which service agents
+in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this report interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task.
+We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate).
+In the proposed system, We explore details behind the strategic decision making procedures and enable service agents to apply different techniques to constrain high efficiency and obtain the maximum utility.
+We investigate services' expected payoffs and the involved probabilities that are used to choose over the two interacting strategies.
+
+%\subsection{The Proposed Framework}\label{The Proposed Framework}
+Here, we first present the architecture of the proposed
+model. We explore the characteristics of intelligent service
+agents and their network. We link this architecture to the
+implemented system where we investigate the services' coopetitive
+attitudes. We compute the involved system parameters and explain
+the services' interactive strategy profiles by highlighting their
+coopetitive choices.
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=1]{Figures/architecture++.eps}
+\caption{Services are partitioned into competitive and cooperative
+sets. Competitive services may get tasks directly from the master
+agent and they can share it with other cooperative services in
+their collaborative networks within the same community.}
+\label{architectureFigure}
+\end{figure}
+
+\section{Architecture}
+
+Figure \ref{architectureFigure} illustrates the architecture of a
+typical community aggregating a number of services with different
+interactive strategies. Some of them compete for the task where
+they directly deal with the master. Some others cooperate in the
+associated task where they only deal with the competed service as
+the task leader and do not directly interact with the master (the
+master deals only with the service that has bid for the task,
+which is responsible of choosing its collaborative network). In
+both sets, some service agents are for certain moments out of any
+collaboration network. Upon allocation of
+the task, the service is responsible for offering the required QoS
+that is stated in the task being generated by a consumer.
+Afterwards,  the master rewards or penalizes the competing
+service by upgrading or degrading its reputation according to the
+offered QoS compared with the required one. This comparison
+influences the sorting mechanism used by the master to allocate
+the tasks in further task allocation rounds.
+
+%ok til here
+
+\section{System Parameters}
+In this section, we demonstrate the involved parameters and their
+corresponding formulations and explanations.
+
+\textbf{Task QoS} ($T_{QoS}^r$) is the required QoS metric for a
+specific task $r$. Users define tasks with specific QoS
+requirements such as response time, availability, and
+successability (or accuracy). We aggregate and
+normalize these metrics to a value between $0$
+and $1$. %Throughout this paper, we refer to this value as
+%$T_{QoS}$.
+
+\textbf{Service QoS} ($QoS_w^r$) is the QoS provided by the
+service $w$ after performing the task $r$. Again, the metrics that
+contribute in computing this QoS are aggregated and normalized to
+a value between $0$ and $1$. The offered quality might or might
+not meet the required task quality $T_{QoS}^r$. In the latter
+case, the service user would be disappointed and a negative
+satisfaction feedback is expected. In our proposed system, both
+cases are considered when calculating the services' reputation.
+
+%\textbf{NTD} is the number of tasks completed by a web service.
+
+\textbf{Budget} ($B_w^t$) is the amount of money the service agent
+$w$ has in its disposal during the window time $t$ (i.e.,
+$[0,t]$), which helps pay for the community membership fees
+($\epsilon$) and is one of the parameters that the service agent
+considers when deciding about getting involved in a competition or
+not.
+
+\textbf{Reputation} ($Rep_w^t$) is a significant factor in any
+online community \cite{Fouss:2010:PRM:1751668.1751727}. Without a reputation enabling
+mechanism, users cannot differentiate among services, specially
+the ones which offer the same type of service. Reputation
+mechanisms usually aggregate users' experiences and in our case it
+strongly depends on QoS that each service provides. Users define
+tasks, each one with specific quality $T_{QoS}^r$, so that after
+performing a certain number of tasks, each one with $QoS_w^r$,
+during a window time $t$, the reputation of $w$ gets evaluated by
+the master agent. $Rep_{w}^{t}$ refers to the reputation of $w$
+during that window time $t$.
+
+In Equation \ref{repr}, we compute the reward that the master
+computes considering the task $r$'s QoS $T_{QoS}^r$ compared with
+the service offered quality $QoS_w^r$. In case the offered quality
+meets user expectations, the reward value would be positive. In
+this system, we consider a small value as default rewards $\eta$
+which the master considers together with the proportional level of
+satisfaction as a weighted value (by $\upsilon$). In this case,
+the higher the offered quality, the more weighted reward. In case
+the offered quality did not meet the user expectations, the reward
+would be negative. A default penalty value $\rho$ (where
+$\rho>\eta$) together with the weighted proportional difference
+are therefore considered. The idea is to harshly penalize the
+services rather than rewarding them. To this end, rational service
+agents should carefully analyze their capabilities once the
+available tasks are announced. Equation \ref{reward} computes the
+obtained reward by $w$ during the window time $t$ considering the
+set $task_w^t$ of tasks performed by $w$ during the window time
+$t$. In our proposal, service agents have the goal of increasing
+their budget, which is directly related to their reputation. Thus,
+they have to decide strategically how to maximize this value.
+
+\begin{equation} \label{repr}
+reward_w^r = \begin{cases}
+\eta + \upsilon \frac{QoS_w^r}{T_{QoS}^r+QoS_w^r}   & \text{if $T_{QoS}^r\leq QoS_w^r$;}\\
+-(\rho +  \upsilon \frac{T_{QoS}^r}{T_{QoS}^r+QoS_w^r} ) & \text{otherwise.}\\
+\end{cases}
+\end{equation}
+
+\begin{equation} \label{reward}
+reward_w^t =
+\begin{cases}
+\frac{\sum_{r \in
+task_w^t}reward_w^r}{|task_w^t|}& \text{if $task_w^t \neq \emptyset$;}\\
+0 & \text{otherwise.}\\
+\end{cases}
+\end{equation}
+
+The assigned reputation value is updated by the computed reward
+value. The computed reputation of services is bounded by the
+minimum and maximum reputation values $0$ and $1$. % to constrain
+%the balance the cooperative community of web services. The updated
+Let $\Gamma = Rep_{w}^{t} + reward_w^t$. The updated reputation
+value is then computed as follows:
+
+\begin{equation}\label{repz}
+%Rep_{w}^{t+1} = Rep_{w}^{t} + reward
+%\end{equation}
+%\begin{equation*}
+Rep_{w}^{t+1} = \begin{cases}
+
+\Gamma & \text{if $ 0 \leq \Gamma \leq 1$;}\\
+0  & \text{if $\Gamma < 0$;}\\
+1 & \text{if $\Gamma > 1$.}\\
+\end{cases}
+\end{equation}
+%
+For new services with no previous reputation value, we use the
+bootstrapping trust technique proposed in \cite{Yahyaoui2}. This
+technique consists in giving the new services a chance and observe
+their behaviors for a period of testing time. The observation
+sequence is modeled as a hidden Markov model that is used to
+detect the behavior of the service by comparing the observation
+behavior against pre-defined trust patterns. Based on the matching
+result, an initial value is assigned to the service. Using this
+initial reputation value, services quickly converge to their
+actual and stable values using the update function.
+
+\begin{proposition}\label{Complexity-Rep}
+$Rep_{w}^{t}$ can be computed in time $O(|t|)$, i.e., in time
+linear in the size of the window $t$.
+\end{proposition}
+
+\begin{proof}\footnote{In this paper, we
+assume that the common arithmetic and elementary functions, such
+as multiplication, division and trigonometric functions can be
+computed in time $O(1)$ as they operate on inputs of fixed sizes.}
+The function $Rep_{w}^{t}$ is recursive on $t$, but the algorithm
+works by storing the last calculated reputation value in a
+variable, so it will not be recalculated again at each iteration.
+However, the calculation of $reward_w^t$ is needed. Since the
+function $reward_w^t$ can be computed in time linear in the number
+of tasks (see Equations \ref{repr} and \ref{reward}), which in
+turn is linear in the size of the window time, the result follows.
+$\Box$
+\end{proof}
+
+\textbf{Growth Factor} ($G_w^t$) is a parameter which declares
+services' performance based on their recent strategies and
+activities. Growth factor is relative to services' reputation
+$Rep_w^t$, QoS during the window time $t$ $QoS_w^t$, and budget
+$B_w^t$. This factor is the main variable a typical service uses
+to decide about which strategy to adopt. We use Equation \ref{eq:growthfactor} to compute the
+growth factor $G^t_w$ of the service $w$ during the window time
+$t$ as the average of the three aforementioned parameters, where
+$n_t$ is the total number of offered tasks to the whole community
+during the
+window time $t$, %(we consider the time window $t$ large enough so
+%that $n_t \neq 0$),
+$\mu_w$ is the mean received service fee, and $\epsilon$ is the
+cost of community membership.
+
+\begin{equation}\label{eq:growthfactor}
+G^t_w = \frac{Rep^t_w + QoS_w^t+\frac{B_w^t}{n_t  \mu_w -
+\epsilon}}{3}
+\end{equation}
+\begin{equation*}
+\mu_{w} \in\{\mu_{w, CM}, \mu_{w, CO}\},~~~QoS_w^t =
+\begin{cases} \frac{\sum_{r \in
+task_w^t}QoS_w^r}{|task_w^t|}& \text{if $task_w^t \neq \emptyset$;}\\
+0 & \text{otherwise.}\\
+\end{cases}
+\end{equation*}
+
+This equation is designed so that it satisfies the following
+desirable properties:
+
+\begin{enumerate}
+
+\item The growth factor function should be monotonically
+increasing in the offered quality of service $QoS_w^t$.
+
+\item The growth factor function should be monotonically
+increasing in the service's reputation $Rep^t_w$.
+
+\item The growth factor function should be monotonically
+increasing in the budget $B_w^t$ if the maximum possible profit is
+positive and monotonically decreasing in $B_w^t$ if the maximum
+possible profit is negative. This property reflects the idea that
+the budget contributes in the increase of the growth factor as far
+as there is a chance to make profit. In fact, the contribution of
+the budget $B_w^t$ in the calculation of the growth factor should
+be proportional to the maximum possible profit $n_t \mu_w -
+\epsilon$ where the service $w$ receives all the offered tasks
+during the window time $t$.
+
+\end{enumerate}
+
+  % if the profit $\beta_w$ made by the web service $w$
+%considering the mean received service fee $\mu_w$ and the cost of
+%community membership $\epsilon$ is positive.
+It is easy to show that Equation \ref{eq:growthfactor} satisfies
+the three aforementioned properties by calculating the partial
+derivatives $\partial G^t_w$ of this function in 1) $QoS_w^t$
+($\frac{\partial G^t_w}{\partial QoS_w^t} = \frac{1}{3} $); 2)
+$Rep^t_w$ ($\frac{\partial G^t_w}{\partial Rep^t_w} = \frac{1}{3}
+$); and 3) $B_w^t$ ($\frac{\partial G^t_w}{\partial B_w^t} =
+\frac{1}{3 (n_t \mu_w - \epsilon)} $). Thus, the sign of the two
+first partial derivatives is positive and the sign of
+$\frac{\partial G^t_w}{\partial B_w^t}$ depends on the sign of the
+maximum profit $n_t \mu_w - \epsilon$, so we are done. The mean
+service fee depends on the strategy adopted by the service because
+a competitive service receives higher fees $\mu_{w, CM}$ compared
+to a cooperative one $\mu_{w, CO}$ ($\mu_{w, CM} > \mu_{w, CO}$).
+The motivation behind this is that a competitive service for a
+given task is the leader for that task while other cooperative
+services are performing specific subtasks as asked by the leader.
+
+\begin{proposition}\label{Complexity-Growth_Factor}
+$G_w^t$ can be computed in time linear in the size of the window
+$t$.
+\end{proposition}
+
+\begin{proof}
+As shown in the second part of Equation \ref{eq:growthfactor}, the
+function $QoS_w^t$ can be computed in time linear in the number of
+tasks, which in turn is linear in the size of the window time.
+Since $B_w^t$ is constant, the result follows from Proposition
+\ref{Complexity-Rep}. $\Box$
+\end{proof}
+
+The above explained parameters and other additional parameters
+which will be used in the rest of this chapter are listed and self
+explained in Table \ref{t4:Preliminaries}.
+
+\begin{table}
+\centering
+\caption{List of abbreviations.}
+\begin{tabular}{|c|c||c|c|}
+\hline
+\textbf{Notation} & \textbf{Definition} & \textbf{Notation} & \textbf{Definition}\\
+\hline\hline
+$T_{QoS}^r$    & Required task QoS for the task $r$   & $T_{QoS}^t$      & Mean required task QoS during $t$\\
+$QoS_w^r$      & Service $w$ QoS for the task $r$ & $QoS_w^t$        & $w$ QoS during the window time $t$\\
+$Reward_w^r$   & Reward obtained by $w$ w.r.t. $r$    & $Reward_w^t$ & Reward to update the reputation\\
+$Rep^t_w$      & Reputation assigned for $w$          & $B_w^t$          & Budget associated to service $w$ \\
+$G^t_w$        & Growth factor of $w$ during $t$      & $\epsilon$       & Community membership fee\\
+$\pi_{w,CM}^t$ & Competition payoff of $w$            & $\pi_{w,CO}^t$   & Cooperation payoff of $w$\\
+$p_{w,CM}^t$   & Competition probability of $w$       & $p_{w,CO}^t$     & Cooperation probability of $w$\\
+$COF_w^t$      & Cooperation fee of $w$               & $\beta_{w}$      & Profit of $w$\\
+$\mu_{w, CM}$  & Mean service fee for competing $w$   & $\mu_{w, CO}$    & Mean service fee for cooperating $w$\\
+$\tau_w^t$     & Coopetitive threshold of $w$         & $P_w^t$          & Probability of competing for $w$\\
+$U_w^t$        & Utility of $w$                       & $E^t_w$          & Expected number of tasks\\
+
+\hline
+\end{tabular}
+\label{t4:Preliminaries}
+\end{table}
+
+\section{Service Interactive Strategies}
+
+The main goal of each individual service agent is to increase its
+income (payoff). This income can be earned from tasks (or
+requests) done by this service. In our model, services can decide
+to compete to get a task from the master agent or to cooperate
+with other services within a given collaborative network (the way
+a collaborative network is set by a leader is based on the
+cooperative services reputation and their QoS parameters that
+should coincide with the required QoS). Therefore we define two
+types of service strategies. First, when a service has higher
+level of confidence based on its growth factor, it can compete to
+get a task from the master and adopts the competitive strategy.
+Second, when the service agent has a lower level of confidence
+that it does not feel capable to compete, it waits for some other
+services to cooperate with to perform some tasks \footnote{Through
+the report, requests or tasks are supposed to be decomposable.},
+and thus it adopts the cooperative strategy. Services estimate the
+outcome of all the strategies and choose one of them accordingly.
+This decision is not static but can change over time so service
+agents can switch from one strategy to the other, and this dynamic
+attitude is referred to as coopetition. The underlying decision
+making process is presented in the next section.
+
+\section{Theoretical Results}\label{Theoretical Results}
+
+\subsection{Service Decision Making Procedure}
+%In the previous section, we introduced web services' interaction
+%strategies.
+In this section, we explore in details the interaction strategies
+and the outcome of each strategy in terms of services' utilities.
+The main part of services' decision making procedure falls into
+their growth factor analysis. In fact, the comparison of the
+growth factor to a particular threshold is the main reason that
+influences the service's decision to follow either competitive or
+cooperative behavior. service agents initially compute this value
+and compare it with their computed threshold. Generally the main
+challenge is the threshold computation and we cope with this issue
+in the rest of this section. We additionally use the obtained
+results in the implemented environment and analyze their
+effectiveness on services' strategic decision making procedures.
+
+Figure \ref{decisionMakingProcedure} shows the decision making
+process that is followed by a typical service. In case the service
+agent is ready to compete, there is a chance that it bids for a
+task if it has the required capabilities to accomplish that task,
+or stays silent and returns to the cooperative status. But in case
+the service agent is willing to cooperate, it has to wait for a
+cooperation opportunity that could be triggered by another service
+agent that competed and obtained the task, so both services will
+be part of the same collaborative network. In the decision making
+process presented in Figure \ref{decisionMakingProcedure}, we
+assume that the competing service might get the task (denoted as
+$Bid/obtainedTask$) or not in case of being rejected by the master
+agent, or do not even bid for the task (denoted as
+$Silent/rejectedTask$). For simplicity reasons and without loss of
+generality, we group the two cases of $Bids$ and $obtainedTask$
+together as well as $Silent$ and $rejectedTask$. The rational
+behind this aggregation is the fact that our main concentration is
+services' status (competitive or cooperative) over different
+decision making rounds, which could be caused by internal factors
+(the services) or by the external factor (the master agent).
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=0.55]{Figures/decision1++.eps}
+\caption{Decision making process over competitive and cooperative
+strategies.} \label{decisionMakingProcedure}
+\end{figure}
+
+Consider a service $w$ that is willing to compete for the period
+of time $t$ (that means the computed growth factor is more than
+the analyzed threshold). This service can estimate the expected
+payoff associated to this decision, called \emph{competition
+payoff}. Equation \ref{CMPff} computes this expected payoff for
+the competing service $w$ ($\pi_{w,CM}^t$) considering the
+$Bid/obtainedTask$ probability of $p_{w,CM}^t$ and
+$Silent/rejectedTask$ probability of $1-p_{w,CM}^t$.
+
+\begin{equation}\label{CMPff}
+\pi_{w,CM}^t=p_{w,CM}^t(\mu_{w, CM}E^t_w-COF_w^t
+E^t_w-\epsilon)+(1-p_{w,CM}^t)(-\epsilon)
+\end{equation}
+
+In Equation \ref{CMPff}, $E^t_w$ is the number of tasks that $w$
+expects during the window time $t$, and $\mu_{w, CM}$ is the mean
+service fee that is assigned by the master agent to $w$. This
+means that a competing service directly obtains this fee from the
+master agent. Moreover, the competing service $w$ expects a
+cooperation fee ($COF_w^t$) that it gives to its collaborators in
+case $w$ needs to cooperate with other services (cooperative
+service agents in its collaboration network). In any case, the
+competing or cooperating service agent pays a fixed amount of
+membership ($\epsilon$) to the master agent, which plays the role
+of the community's coordinator. This fee would be taken into
+account when a service decides to leave to a cheaper community or
+act alone. But to concentrate on the main concerns of this paper,
+we skip these small details.\\\\
+%
+From Equation \ref{CMPff}, the following proposition is
+straightforward.
+
+\begin{proposition}\label{Complexity-Competition_Payoff}
+The complexity of computing the competition payoff $\pi_{w,CM}^t$
+is linear in the competition probability $p_{w,CM}^t$, the
+expected number of tasks $E^t_w$, and the cooperation fee
+$COF_w^t$.
+\end{proposition}
+
+The arrival of requests for service $w$ during the time unit $t$
+(denoted here by $m_w(t)$) can be modeled as a nonhomogeneous
+Poisson process \cite{Khosravifar-ICWS2010,Ruggeri2005}, which
+means as a Poisson process with dynamic arrival rate
+$\lambda_w(x)$ where $x$ belongs to the time unit $t$. The arrival
+rate is thus a function of time and typically varies significantly
+from moment to moment. In nonhomogeneous Poisson process, $m_w(t)$
+is expressed as follows:
+
+$$ m_w(t)= \int_0^t \! \lambda_w(x) \ \mathrm{d}x$$
+%
+And the probability of having exactly $n$ requests during the
+window $t$ is computed as follows:
+
+$$ p(m_w(t) = n) = \frac{(m_w(t))^n}{n! \ e^{m_w(t)}}  $$
+%
+Let $Max_w^t$ be the maximum number of requests that $w$ can
+receive during $t$. The number of expected requests $E^t_w$ is
+given by the parameter $\lambda_w(t)$ as follows:
+
+\begin{equation}\label{Expectation}
+E^t_w = \lambda_w(t) = \sum_{n=1}^{Max_w^t} n \ p(m_w(t) = n)
+\end{equation}
+%
+The parameter $\lambda_w(t)$ is usually estimated from data
+samples using the least squares, iterative least squares, or
+maximum likelihood \cite{Massey1996}.
+
+\begin{proposition}\label{Complexity-Expectation}
+The complexity of computing the expected number of requests
+$E^t_w$ is linear in the size of the window time $t$.
+\end{proposition}
+
+\begin{proof}
+For a fixed function $\lambda_w(x)$, $m_w(t)$ can be computed in
+$O(1)$. Thus, from Equation \ref{Expectation}, it follows that
+$E^t_w$ can be computed in time linear in $Max_w^t$. As $Max_w^t$
+is linear in $t$, the result follows. $\Box$
+\end{proof}
+
+Similar to the competitive service case, if a service $w$ declares
+cooperative status, its expected \emph{cooperation payoff}
+($\pi_{w,CO}^t$) is computed in Equation \ref{CLPff}. In this
+equation, $p_{w,CO}^t$ is the probability of getting involved in a
+cooperative task with other services and $1-p_{w,CO}^t$ is the
+probability of failure to find such a cooperation opportunity.
+These two probabilities are set when $w$ decides to compete. We
+recall that $\mu_{w, CO}$ denotes the mean cooperation fee that is
+directly obtained from the leader (i.e., the competitive) service
+of the underlying collaborative network. Compared to $\mu_{w,
+CM}$, $\mu_{w, CO}$ is relatively smaller since the competitive
+service generally dedicates a portion of its obtained income to
+pay other cooperative services.
+
+\begin{equation}\label{CLPff}
+\pi_{w,CO}^t=p_{w,CO}^t (\mu_{w,
+CO}E^t_w-\epsilon)+(1-p_{w,CO}^t)(-\epsilon)
+\end{equation}
+%
+From Equation \ref{CLPff}, the following proposition holds.
+
+\begin{proposition}\label{Complexity-Cooperation_Payoff}
+The complexity of computing the cooperation payoff $\pi_{w,CO}^t$
+is linear in the cooperation probability $p_{w,CO}^t$ and the
+expected number of tasks $E^t_w$.
+\end{proposition}
+
+To analyze the expected payoffs obtained from different
+strategies, services need to compute the estimated probabilities
+that distinguish subcases in each behaviorial status ($p_{w,CM}^t$
+for competitive and $p_{w,CO}^t$ for cooperative). To estimate
+these probabilities, we should notice that they are functions of
+services' reputation values ($Rep_w^t$). Furthermore, $p_{w,CM}^t$
+is also function of the difference between the offered QoS
+($QoS_w^t$) and the mean requested one considering the set of all
+tasks $task^t$ ($T_{QoS}^t$ (see Equation \ref{Mean-Quality}));
+and $p_{w,CO}^t$ is function of the reputation of other services
+in the community because the leader is supposed to be selective
+when it comes to choose the collaborators. To this end, we first
+discuss the desirable properties of an estimation function of each
+of these probabilities, and show that the proposed ones satisfy
+those properties.
+
+\begin{equation}\label{Mean-Quality}
+T_{QoS}^t =
+\begin{cases} \frac{\sum_{r \in
+task^t}T_{QoS}^r}{|task^t|}& \text{if $task^t \neq \emptyset$;}\\
+0 & \text{otherwise.}\\
+\end{cases}
+\end{equation}
+%
+
+\begin{proposition}\label{Complexity-Mean_Quality}
+$T_{QoS}^t$ can be computed in time linear in the size of the
+window $t$.
+\end{proposition}
+
+\begin{proof}
+From Equation \ref{Mean-Quality},  $T_{QoS}^t$ can be computed in
+time linear in $|task^t|$, which in turn is linear in the window
+size $|t|$. $\Box$
+
+\end{proof}
+
+The desired properties of $p_{w,CM}^t$ are as follows:
+
+\begin{property}
+$p_{w,CM}^t$ is continuous with regard to $Rep^t_w$, $QoS_w^t$,
+and $T_{QoS}^t$.
+\end{property}
+%
+\begin{property}
+$p_{w,CM}^t$  is monotonically increasing in $Rep^t_w$ and
+$QoS_w^t - T_{QoS}^t$ while $QoS_w^t - T_{QoS}^t$ is positive.
+\end{property}
+%
+\begin{property}
+$p_{w,CM}^t$ is null if $QoS_w^t - T_{QoS}^t$ is negative.
+\end{property}
+%
+%\begin{property}
+%Assuming that the web service $w$ is known by the master web
+%service, $Rep^t_w$ is monotonically increasing or decreasing in
+%$QoS_w$.
+%\end{property}
+%
+\begin{property}
+The increase slope of $p_{w,CM}^t$ is higher when the reputation
+$Rep^t_w$ increases in the interval $[0, 0.5]$ than when it
+increases in the interval $]0.5, 1]$.
+\end{property}
+
+\noindent Property 1 simply says that the probability of success
+competition $p_{w,CM}^t$ can be always estimated as far as
+$Rep^t_w$, $QoS_w^t$, and $T_{QoS}^t$ are available. Property 2
+says that the reputation and QoS are two key factors that
+influence the value of $p_{w,CM}^t$ in the sense of positive
+correlation. Property 3 indicates that the probability
+$p_{w,CM}^t$ is null if the offered QoS is less than the
+expectation. Property 4 promotes the increase of the reputation
+for new comers and imposes higher increase rate at the beginning
+of the reputation curve because it is always hard to build the
+reputation, but once it is built, its maintenance is less
+challenging.
+
+\noindent The desired properties of $p_{w,CO}^t$ are as follows:
+
+\begin{property}
+$p_{w,CO}^t$ is continuous with regard to $Rep^t_w$ and the
+reputation of other services in the community.
+\end{property}
+%
+\begin{property}
+$p_{w,CO}^t$  is monotonically increasing in $Rep^t_w$ and
+ monotonically decreasing in the community average reputation.
+\end{property}
+%
+%\begin{property}
+%$p_{w,CM}$ is null if $QoS_w^t - T_{QoS}^t$ is negative.
+%\end{property}
+%
+%\begin{property}
+%Assuming that the web service $w$ is known by the master web
+%service, $Rep^t_w$ is monotonically increasing or decreasing in
+%$QoS_w$.
+%\end{property}
+%
+\begin{property}
+The increase slope of $p_{w,CO}^t$ is higher when the reputation
+$Rep^t_w$ increases in the interval $[0, 0.5]$ than when it
+increases in the interval $]0.5, 1]$.
+\end{property}
+
+\noindent Property 5 is similar to Property 1. Property 6 says
+that $w$ has more chance to get involved in a cooperation if it
+has high reputation compared to the other members. This chance
+decreases if other services have higher reputation. Property 7 is
+similar to Property 4.
+
+Equations  \ref{CMp_w} and \ref{CLp_w} respectively compute the
+estimated success probability in cases where service $w$ is
+competing and cooperating. These values are computed considering
+service's reputation value ($Rep^t_w$ computed by the master),
+service's offered QoS ($QoS^t_w$), the task required QoS
+($T_{QoS}^t$), which is the mean required QoS computed from
+previous tasks, the maximum offered QoS ($QoS_k^t$, which is
+provided by another competitive service $k$), and the cooperative
+factor $CL_w^t$ of service $w$ during the window time $t$, which
+is computed as the portion of service's current reputation on the
+average reputation of the community $\mathcal{C}$.
+
+\begin{equation} \label{CMp_w}
+p_{w,CM}^t = \begin{cases}
+\sin(Rep^t_w\frac{\pi}{2})\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k^t-T_{QoS}^t)} & \text{if $QoS_w^t\geq T_{QoS}^t$;}\\
+0 & \text{otherwise.}\\
+\end{cases}
+\end{equation}
+
+\begin{equation}\label{CLp_w}
+p_{w,CO}^t=\sin(Rep^t_w\frac{\pi}{2})CL_w^t
+\end{equation}
+\begin{equation*}
+CL_w^t=\frac{Rep^t_w}{\sum_{k\in
+\mathcal{C}}Rep^t_k/|\mathcal{C}|}
+\end{equation*}
+
+\begin{theorem}
+Equation  \ref{CMp_w} satisfies Properties 1 to 4.
+\end{theorem}
+
+\begin{proof}
+It is easy to show the continuity of Equation \ref{CMp_w}, which
+satisfies Property 1. The partial derivative $\frac{\partial
+p_{w,CM}^t}{\partial Rep^t_w} = \frac{\pi}{2}
+\cos(Rep^t_w\frac{\pi}{2})\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k^t-T_{QoS}^t)}$
+is positive as the function $\cos$ (the derivative of $\sin$) is
+positive on $[0, \frac{\pi}{2}]$, $Rep^t_w \in [0, 1]$, and
+$QoS_w^t\geq T_{QoS}^t$. The partial derivative $\partial
+p_{w,CM}^t$ with regard to $QoS_w^t - T_{QoS}^t$ ($\frac{\partial
+p_{w,CM}^t}{\partial(QoS_w^t - T_{QoS}^t)} =
+\frac{\sin(Rep^t_w\frac{\pi}{2})}{Max_k(Qos_k^t-T_{QoS}^t)}$) is
+also positive since $Qos_k^t-T_{QoS}^t > 0$ and
+$Rep^t_w\frac{\pi}{2} \in [0, \frac{\pi}{2}]$ and $\sin$ is
+positive on $[0, \frac{\pi}{2}]$, which proves the satisfaction of
+Property 2. Property 3 is straightforward. Finally, the increase
+slope of the function $\sin$ on $[0, \frac{\pi}{2}]$ proves
+Property 4. $\Box$
+\end{proof}
+
+\begin{theorem}
+Equation  \ref{CLp_w} satisfies Properties 5 to 7.
+\end{theorem}
+%
+\begin{proof}
+We can easily show the continuity  of Equation \ref{CLp_w} from
+which Property 5 follows. Property 6 can be shown by calculating
+the partial derivative $\partial p_{w,CO}^t$ first with regard to
+$Rep^t_w$ and second with regard to the community $\mathcal{C}$
+average reputation $\sum_{k\in \mathcal{C}}Rep^t_k/|\mathcal{C}|$,
+where $|\mathcal{C}|$ is the cardinality of the considered
+community $\mathcal{C}$. The first partial derivative
+($\frac{\pi}{2}\cos(Rep^t_w\frac{\pi}{2})CL_w^t$) is positive and
+the second ($\frac{-\sin(Rep^t_w\frac{\pi}{2})Rep^t_w}{(\sum_{k\in
+\mathcal{C}}Rep^t_k/|\mathcal{C}|)^2}$) is negative, which proves
+the satisfaction of Property 6. The proof of satisfaction of
+Property 7 is similar to the one of Property 4. $\Box$
+\end{proof}
+%Considering these involved parameters, we verify that properties
+%$1$ to $3$ are satisfied. For property $4$, we use $sinus$
+%function to promote the role of reputation influence in this
+%system. Using $sinus$ function, we promote reputation increase of
+%web services specially when it is less than $50\%$. Considering
+%the desired properties, the formulas represented in Equations
+%\ref{CMp_w} and \ref{CLp_w} are candidates we chose to compute the
+%probabilities regarding $Competitive$ and $Cooperative$
+%strategies. These formulas are used in implemented system and
+%verified with respect to their accuracy and effectiveness in
+%adopting different interacting strategies.
+
+%In the proposed heuristic  function, the web service $w$ is not
+%aware of current $T_{QoS}$ and $QoS_k$, but could use its previous
+%information to estimate their values. To this end, if the web
+%service is more informative about the previous data, it could
+%obtain more realistic measurement over the estimated
+%probabilities.
+%
+%
+%We compute the success probability of cooperation ($p_{w,CO}$)
+%similarly in the sense  that we still promote reputation influence
+%using $sinus$ function, but multiplied to the cooperative factor
+%$CL_w$ of the web service $w$. This value is computed as the
+%portion of web service's current reputation on the average
+%reputation of the community.
+
+\begin{proposition}\label{Complexity-Probability_Competition}
+$p_{w,CM}^t$ can be computed in time linear in the window size
+$|t|$.
+\end{proposition}
+
+\begin{proof}
+The result follows directly from 1) Equation \ref{CMp_w}; 2)
+Proposition \ref{Complexity-Rep} (Complexity of $Rep^t_w$ is
+linear in the window size $|t|$); 3) second part of Equation
+\ref{eq:growthfactor} (the function $QoS_w^t$ can be computed in
+time linear in the number of tasks, which in turn is linear in the
+size of the window time); 4) Proposition
+\ref{Complexity-Mean_Quality} (Complexity of $T_{QoS}^t$ is linear
+in the size of the window $t$); and 5) the fact that those
+functions are computed independently one from the other. $\Box$
+\end{proof}
+
+\begin{proposition}\label{Complexity-Probability_Cooperation}
+$p_{w,CO}^t$ can be computed in time $O(|t|.|\mathcal{C}|)$, which
+means linear in both the size of the window $t$ and the size of
+the community $\mathcal{C}$.
+\end{proposition}
+
+\begin{proof}
+From Proposition \ref{Complexity-Rep}, $Rep^t_w$ can be computed
+in $O(|t|)$. Consequently, the function $\sum_{k\in
+\mathcal{C}}Rep^t_k$ can be computed in $O(|t|.|\mathcal{C}|)$, so
+it does the computation of the function $CL_w^t$ as $Rep^t_w$ will
+be computed just once and stored in a variable. The same variable
+will be used to compute $\sin(Rep^t_w\frac{\pi}{2})$. Thus, from
+Equation \ref{CLp_w}, the result follows. $\Box$
+\end{proof}
+
+\subsection{Coopetition Threshold}
+
+In this part, we compute the coopetition threshold that a typical
+service agent could use to adopt reasonable interacting strategies
+and we empirically verify the effectiveness of the obtained
+results in the next section. In fact, to decide which strategy to
+adopt, we let the service agent $w$ compare its growth factor
+$G_w^t$ with the coopetition threshold $\tau_w^t$ it holds at
+current window time $t$ and choose to compete with probability
+$P_w^t$ that we compute in Equation \ref{P}. Based on this
+probability, we calculate the total utility $U_w^t$ in Equation
+\ref{U}.
+
+\begin{equation} \label{P}
+P_w^t= \begin{cases}
+\frac{G_w^t}{\tau_w^t}  & \text{if $G_w^t\leq \tau_w^t$;}\\
+1 & \text{otherwise.}\\
+\end{cases}
+\end{equation}
+
+\begin{equation}\label{U}
+U_w^t=P_w^t(\pi_{w,CM}^t)+(1-P_w^t)(\pi_{w,CO}^t)
+\end{equation}
+
+%Equation  \ref{U} computes the
+%expected utility (as accumulated fee) regarding web service $w$.
+%This estimated utility is result of aggregation of two different
+%interacting strategies of $Competitive$ and $Cooperative$.
+%Aggregating these strategic payoffs, web service $w$ follows
+%probability distribution of $\{P,1-P\}$. This probability
+%distribution is computed in Equation \ref{P}, which is a function
+%of the growth factor ($G_w$) and computed threshold ($Tr^t$). So
+%if the web service is aware of the reasonable threshold, the value
+%$p$ could be computed and used as the core of strategic
+%probability distribution. But there is a case where the web
+%service does not have a reasonable threshold value and cannot
+%rigorously decide for any adopting strategies.
+
+The key factor in the computation of the probability $P_w^t$ and
+the associated utility is the threshold value. To compute the
+threshold, we use the game-theoretic best response technique. A
+typical service agent $w$ will follow the best response strategy
+to maximize its expected aggregated payoff. The idea is to
+equalize the expected payoffs of the two acting strategies:
+compete and cooperate.
+%
+%
+%by following the following three probability distributions: (1)
+%$\{1,0\}$ where the web service always competes; (2) $\{0,1\}$
+%where the web service always cooperates; and (3)
+%$\{\frac{1}{2},\frac{1}{2}\}$ where the web service equalize the
+%probabilities and decides with unbiased distribution. Following
+%the third case, the web service equites the expected payoffs as
+%outcomes of different interacting strategies.
+%
+The objective behind equalizing payoffs is to explore conditions
+under which service agent $w$ could react with best response to
+further decision making procedures. We use the obtained conditions
+to compute the threshold $\tau_w^t$ during the window time $t$. By
+equalizing $\pi_{w,CM}^t$ and $\pi_{w,CO}^t$, we obtain:
+
+\begin{equation*}\label{equit}
+\pi_{w,CM}^t=\pi_{w,CO}^t      \rightarrow
+\end{equation*}
+\begin{equation*}
+p_{w,CM}^t(\mu_{w,CM}-COF_w^t-\epsilon)+(1-p_{w,CM}^t)(-\epsilon)=p_{w,CO}^t(\mu_{w,
+CO}-\epsilon)+(1-p_{w,CO}^t)(-\epsilon)
+\end{equation*}
+Which means:
+\begin{equation*}
+p_{w,CM}^t(\mu_{w,CM}-COF_w^t - \epsilon) =
+p_{w,CO}^t(\mu_{w,CO}-\epsilon)+(-\epsilon)(p_{w,CM}^t -
+p_{w,CO}^t)
+\end{equation*}
+So, we obtain:
+\begin{equation*}
+\mu_{w,CM}-COF_w^t - \epsilon =
+\frac{p_{w,CO}^t~~\mu_{w,CO}}{p_{w,CM}^t}-\epsilon
+\end{equation*}
+Therefore:
+\begin{equation*}
+\mu_{w,CM}-COF_w^t = \frac{p_{w,CO}^t~~\mu_{w,CO}}{p_{w,CM}^t}
+\end{equation*}
+From which, we derive:
+\begin{equation*}
+COF_w^t = \mu_{w,CM} - \frac{p_{w,CO}^t~~\mu_{w,CO}}{p_{w,CM}^t}
+\end{equation*}
+Replacing $p_{w,CM}^t$ and $p_{w,CO}^t$ using Equations
+\ref{CMp_w} and \ref{CLp_w}, we derive the following:
+\begin{equation*}
+COF_w^t = \mu_{w,CM} -
+\frac{sin(Rep^t_w\frac{\pi}{2})CL_w^t~~\mu_{w,CO}}{sin(Rep^t_w\frac{\pi}{2})\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k-T_{QoS}^t)}}
+\end{equation*}
+%The fixed membership fee $\epsilon$ could be taken out and
+%canceled from both sides of the equation so we obtain the
+%following:
+%\begin{equation*}
+%p_{w,CM}^t(\mu_{w,CM}-COF_w^t)=p_{w,CO}^t(\mu_{w,CO})\rightarrow
+%\end{equation*}
+%
+%\begin{equation*}
+%sin(Rep^t_w\frac{\pi}{2})\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k-T_{QoS}^t)}(\mu_{w,
+%CM}-COF_w^t)=sin(Rep^t_w\frac{\pi}{2})CL_w^t(\mu_{w, CO})
+%\end{equation*}
+By simplifying the $sinus$ function from both the numerator and
+denominator sides and substituting the cooperation factor $CL_w^t$
+of service $w$ we obtain Equation \ref{CLF}:
+
+\begin{equation}\label{CLF}
+COF_w^t=\mu_{w,CM}-\frac{Rep^t_w~|\mathcal{C}|}{\sum_{k\in
+\mathcal{C}}Rep^t_k}\frac{\mu_{w,CO}Max_k(Qos_k^t-T_{QoS}^t)}{QoS_w^t-T_{QoS}^t}
+\end{equation}
+
+Equation \ref{CLF} computes the cooperation fee $COF_w^t$ that is
+assigned by service $w$. This fee represents the amount that $w$
+spends to cooperate with other service(s) to accomplish the task.
+By so doing, we obtain the maximum amount of cooperation fee that
+service $w$ can use to constrain the positive payoff out of
+competing. Otherwise, the service stays as cooperative entity.
+
+\begin{proposition}\label{Complexity-COF}
+$COF_w^t$ can be computed in time $O(|t|.|\mathcal{C}|)$, which
+means linear in both the size of the window $t$ and the size of
+the community $\mathcal{C}$.
+\end{proposition}
+
+\begin{proof}
+From Proposition \ref{Complexity-Rep}, $Rep^t_w$ can be computed
+in $O(|t|)$. Consequently, the function $\sum_{k\in
+\mathcal{C}}Rep^t_k$ can be computed in $O(|t|.|\mathcal{C}|)$.
+Since $QoS_w^t$ and $T_{QoS}^t$ can be computed in time $O(t)$
+(from the second part of Equation \ref{eq:growthfactor} and
+Proposition \ref{Complexity-Mean_Quality} respectively), we are
+done. $\Box$
+\end{proof}
+
+\begin{lemma} \label{Complexity-Competition_Payoff-Final}
+The competition payoff $\pi_{w,CM}^t$ can be computed in time
+$O(|t|.|\mathcal{C}|)$.
+\end{lemma}
+
+\begin{proof}
+The result follows directly from Propositions
+\ref{Complexity-Competition_Payoff}, \ref{Complexity-Expectation},
+\ref{Complexity-Probability_Competition}, and
+\ref{Complexity-COF}. $\Box$
+\end{proof}
+
+\begin{lemma} \label{Complexity-Cooperation_Payoff-Final}
+The cooperation payoff $\pi_{w,CO}^t$ can be computed in time
+$O(|t|.|\mathcal{C}|)$.
+\end{lemma}
+
+\begin{proof}
+The result follows directly from Propositions
+\ref{Complexity-Expectation}, \ref{Complexity-Cooperation_Payoff},
+and \ref{Complexity-Probability_Cooperation}. $\Box$
+\end{proof}
+
+%\begin{equation*}
+%\frac{QoS_w^t-T_{QoS}^t}{Max_k(Qos_k^t-T_{QoS}^t)}(\mu_{w,CM}-COF_w^t)=\frac{Rep^t_w}{\sum_{k\in
+%Community}Rep^t_k}(\mu_{w, CO})
+%\end{equation*}
+%
+
+We use the maximum cooperation fee that a service agent considers
+to constrain the positive expected payoff when the competitive
+strategy is adopted to update the threshold for the consequent
+time window ($t+1$). We compare the maximum cooperation fee with
+the required fee ($ReqF_w^t$) that the service indicates to
+accomplish the task. The outcome of this comparison is a factor
+that uses the current threshold $\tau_w^t$ to compute the
+consequent threshold $\tau_w^{t+1}$. As in online learning, the
+idea is to compute iteratively the threshold until the fixed point
+is achieved, which indicates the threshold's conversion, where the
+initial value is randomly chosen (in the simulation different
+initial values are used). Equation
+\ref{Trt} shows this computation. %We restrict the range of this value to $(0.15,0.85)$ to
+%avoid some unreasonable results that could occur due to different
+%reasons like system start point or heavy loaded competitive web
+%services, \textit{etc}.
+To investigate the effectiveness of this threshold on the outcomes
+of the services that follow this reasoning technique, in the next
+section, we compare the results of different agents with diverse
+strategic reasoning techniques.
+
+\begin{equation}\label{Trt}
+\tau_w^{t+1}=\begin{cases}
+\Theta & \text{if $0 \leq \Theta \leq 1$}\\
+1 & \text{if $\Theta > 1$;}\\
+0 & \text{if $\Theta < 0$.}\\
+\end{cases}
+\end{equation}
+\begin{equation*}
+\Theta =\tau_w^t \ \frac{COF_w^t}{ReqF_w^t}
+\end{equation*}
+
+\begin{proposition}\label{Complexity-Threshold}
+The threshold $\tau_w^{t}$ can be computed in time
+$O(|t|.|\mathcal{C}|)$, which means linear in both the size of the
+window $t$ and the size of the community $\mathcal{C}$.
+\end{proposition}
+
+\begin{proof}
+From Equation \ref{Trt}, the computation of $\tau_w^{t}$ is
+recursive on $t$, and the algorithm works by keeping the last
+computed value in a variable, which saves the time of
+re-calculation. Thus, the complexity of calculating $\tau_w^{t}$
+is determined by the complexity of calculating $COF_w^t$ since
+$ReqF_w^t$ is constant during the period $t$. Consequently, the
+result follows from Proposition \ref{Complexity-COF}. $\Box$
+\end{proof}
+
+\begin{theorem}\label{Complexity-Procedure}
+The time complexity of the proposed decision mechanism is
+$O(|t|.|\mathcal{C}|)$, which means linear in both the size of the
+window $t$ and the size of the community $\mathcal{C}$.
+\end{theorem}
+
+\begin{proof}
+The procedure mechanism is based on comparing the growth factor
+$G_w^t$ with the coopetition threshold $\tau_w^t$ as shown in
+Equations \ref{P} and \ref{U}. Thus, the result follows from
+Propositions \ref{Complexity-Growth_Factor} and
+\ref{Complexity-Threshold}. $\Box$
+\end{proof}
+
+\section{Experimental Results and Analysis}\label{s4:resutls}
+
+In this section, we provide an empirical analysis over the
+theoretical results regarding the characteristics of intelligent
+service agents hosted in different communities of services. In the
+implemented system, we simulate the behaviors of service consumers
+as request generators, service agents as service providers, and
+master agents as community representatives.
+%These entities are developed with respect to what is explained in Section \ref{s4:Preliminaries}.
+In this section, the objective is to
+investigate the effectiveness of the proposed strategic system on
+intelligent services' overall budget and also the average quality
+and quantity of tasks performed by the community of services,
+which directly affects user satisfaction.
+%Before conducting the simulation, the
+%expected behavior of our model is to enhance the budget of web
+%services when using our proposed strategic interacting system.
+%Although this result is promising, we would like to investigate
+%the effectiveness of the proposed strategic system on intelligent
+%web services' overall budget compared to the best case. Moreover,
+To verify these objectives, we study the overall performance of
+the community hosting the reasoning-empowered services compared to
+the ones hosting stochastic and purely competitive services. By
+stochastic services, we mean services that adopt at each moment
+competitive or cooperative strategies in an equally but random
+way. By equally, we mean the choices are fairly divided between
+the two strategies.
+
+The simulation application is written in
+\textit{C\#} using \textit{Visual Studio}.
+We performed the implementation on a single Intel Xeon X3450 machine with 6GBs of memory.
+Web services were modeled as a \emph{class} and using \emph{Await} and \emph{Async} models we initiated many web services, each running as a thread.
+We implemented XML based messaging system (like SOAP) with request parameters and a list of XML based responses.
+The request contains the flight dates, the origin and destination, type of tickets, and number of guests.
+The response contains different flights with different companies, prices, timing, etc.
+A pool of services are initialized with values taken from a real dataset that includes $2507$ real services functioning on the web.
+The dataset records the QoS values of $9$ parameters including \textit{availability},
+\textit{throughput}, and \textit{reliability} \cite{Almasri}.
+
+We start our discussions with cumulative budget comparison
+regarding different communities within which services follow
+different reasoning techniques. Figure \ref{Graph1} part (a)
+illustrates three graphs for three different communities. Each
+community hosts services that follow different reasoning
+techniques: (1) a community that follows the interactive reasoning
+techniques presented in this report (referred to as coopetitive);
+(2) a community that follows a stochastic reasoning technique so
+decisions about selecting competitive or cooperative strategies
+are totally random (referred to as random coopetitive); and (3) a
+competitive community where all services follow the competitive
+strategy (referred to as competitive).
+%The proposed model's
+%reasoning mechanism allows services to make decisions that
+%maximize their utilities, so that if the service cannot compete,
+%the procedure would suggest to collaborate, which is better than
+%competing and failing to obtain the task. In this case, the service stays idle but
+%still pays the community membership fee, which means losing
+%utility. The developed strategic decision making mechanism leads
+%some service agents to follow cooperative strategies that overall
+%maintain an optimal community budget. In the same figure, we
+%observe the cumulative budget of a community where services follow
+%random interacting strategies. The outcome is clearly lower
+%because services at each run randomly decide over their acting
+%strategies. This potentially influences the community budget
+%because a low quality service if randomly selects to follow the
+%competitive strategy, it will fail to perform a task with high QoS
+%requirements.
+
+The results illustrated in Figure \ref{Graph1} part (a)  verify
+the importance of the strategic decision making procedure to
+logically decide over the possible competitive and cooperative
+choices. Figure \ref{Graph1} part (b) illustrates communities
+average reputation of involved services. The graphs represent the
+influence of the rewards that the master agent uses to encourage
+highly capable services to compete for a task. As for the
+cumulative budget, we observe that the coopetitive community
+outperforms the random coopetitive and competitive communities in
+terms of average reputation. The proposed model's average
+reputation increases because services follow optimal strategies
+where they can perform better so obtain higher rewards. For the
+same reasons as for the cumulative budget, the average reputation
+of the random coopetitive community
+outperforms the one of the competitive community. %The idea is to balance web
+%services' strategies to maintain optimal community budget.
+
+\begin{figure}%[h]
+%\centering
+%\includegraphics[scale=0.6]{graph1Final+.eps}
+\includegraphics[scale=0.47]{Figures/graphbgtmed.eps}
+\includegraphics[scale=0.47]{Figures/graphrep.eps}
+\caption{Part (a): Cumulative community budget comparison. Part
+(b): Average community reputation comparison over different
+strategic decisions.} \label{Graph1}
+\end{figure}
+
+ %Figure \ref{Graph2} part (a) illustrates the reputation of the proposed $Coopetitive$ community where
+ %we highlight the range of reputation change in the community.
+The vertical lines denote the range of %reputation that is associated with the master web service.
+The rewards and penalties applied to %different
+% web services show that the master web service over runs extends the reputation range and takes %control of the whole community. In the developed model, web services are encouraged to choose
+ %optimal strategies. This is maintained over growth factor comparison of the $Coopetitive$ web %services.
+
+In our model, services are managed by selfish agents in the sense
+they try to maximize their own utilities. We analyze how their
+strategies affect the social welfare, and from user's and
+community's point of view how good the tasks are being performed.
+This directly impacts user's satisfaction and community's
+reputation in general. The Higher quality and quantity of tasks
+performed leads to higher user's satisfaction for the community
+which results in better reputation for the community. The results
+in Figure \ref{graph_task} show the quality and quantity of tasks
+being done successfully in three communities adopting the three
+different aforementioned strategy decision algorithms. As clearly confirmed by the simulation, the coopetitive community
+outperforms the stochastic and compete communities.
+
+\begin{figure}[h]
+\centering
+\includegraphics[scale=0.35]{Figures/graphtaskdone.eps}
+\includegraphics[scale=0.35]{Figures/graphtasksatisfaction.eps}
+\includegraphics[scale=0.35]{Figures/graphavgqostask.eps}
+\caption{Overall performance from community's point of view. Part
+(a) Total number of tasks successfully done. Part (b) Ratio of
+tasks satisfied with required QoS. Part (c) Average QoS of
+performed tasks.} \label{graph_task}
+\end{figure}
+
+We conclude our analysis by discussing how effective our
+coopetitive decision making model is by comparing the final
+utility (in terms of income) of services following our model with
+other services deviating from that coopetitive model. In Figure
+\ref{graph_dev} Part (a), we made the services deviate from the
+suggested strategy. As the simulation shows, the more services
+deviate from our coopetitive strategy the more they make less
+benefits. In Part (b), we pick one random service and simulate the
+scenario with its default coopetitive strategy and then we redo
+the simulation with exactly the same environment parameters while
+gradually alternating the decisions. By alternating we mean
+adapting the opposite of what our model does suggest. Thus, if the
+coopetitive model suggests to compete, the service agent will
+cooperate and vice versa. We run this scenario 50 times and at the
+end we check the service's budget and see if it gains more by
+deviating or not. We did this for one single deviation (i.e.,
+alternating only one decision) to 10 different deviations
+(alternating 10 different decisions) during the 50 times run. As
+the results show, deviating from the coopetitive strategy yields
+less income for the service.
+
+\begin{figure}%[h]
+%\centering
+\includegraphics[scale=0.47]{Figures/graphdev.eps}
+\includegraphics[scale=0.47]{Figures/graphdev2.eps}
+\caption{Utility loss while deviating from our coopetitive
+decision process. Part (a) Overall budget when deviating from our
+model in 0, 10, 20, 30, 40, and 50 percent of decisions. Part (b)
+Ratio of getting earning utility (budget) when deviating from our
+coopetitive strategy in 1 to 10 decisions.} \label{graph_dev}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Summary}\label{sec:conclusion-cha3}
 

### 2015-07-04 thesis/thesis/chap2/chap2.tex
changes

@@
 
+\subsection{Communities of Web Services}\label{sec:communities_rel}
+
 In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
@@
 manager.
+
+\subsection{Web Service Community Formation}\label{sec:communities_for_rel}
 
@@
 
+\subsection{Coopetitive Behaviour Within Communities of Web Services}\label{sec:coopetetive}
+
+At the best of our knowledge, there is no work in the literature
+of service and agent computing addressing the issue of coopetition
+strategies and when to cooperate or to compete. However, some
+relevant proposals to the model presented in this paper are the
+ones that address service selection and task allocation
+mechanisms. In many frameworks proposed in the literature, service
+selection and task allocation are regulated based on the
+reputation parameter \cite{Bentahar,Rosario,Ruth,Yahyaoui}.
+\textbf{In \cite{Huang}, the authors propose a framework to match potential
+benefits of services while cooperating with one another. The
+interesting idea is to consider the benefits under four
+categories: innovation and learning, internal business process,
+customer, and financial benefits.
+Innovation and learning perspective} focuses on the knowledge, skills, and systems needed to improve the business continually.
+Necessary factors to build strategic capabilities and efficiency in addressed in internal business process.
+Values that customers seek are considered in \emph{customer perspective} and financial performance to maximize the shareholder value are analyzed in \emph{financial perspective}.
+Their goal is to design the framework for cooperating web services, inline with business strategy of firms in IT industry.
+In \cite{Alchieri}, the authors
+present a dependable framework for cooperative service agents that
+is based on the tuple space coordination model. The
+intrusion-tolerant perspective is emphasized in this paper where
+several security mechanisms are developed to enable a reliable
+coordination system. %In \cite{Maximilien2}, authors propose
+%ontology for quality of service. Users compute the web services'
+%reputation using ratings.
+The proposed frameworks mostly aim to facilitate the coordination
+mechanism between services. However, the opposite strategy of
+competing is not analyzed where services might be more successful
+when competing within the same group. In fact, services are not
+always willing to cooperate even if they have some common goals,
+particularly when they operate within groups such as communities.
+In such a context, service agents can follow different interacting
+strategies and have to decide when to compete and when to
+cooperate so that their ultimate goal, maximizing their incomes,
+can be better achieved. In our framework, we analyze those
+different strategies to help services in their decision making
+process when these
+agents function within communities. %We summarize most of
+%these proposals and concentrate on strategic decision making
+%system that ranks web services in the community and analyze their
+%effective interacting strategies to accomplish continuous
+%requested tasks.
+We enable service agents to reasonably evaluate and decide over
+their coopetition strategies, which means deciding when to compete
+and when to cooperate.
+
+Furthermore, there are a number of related proposals that take
+into account the correlation between (web) services and the ways
+these services coordinate their actions to accomplish the required
+tasks. In \cite{Jurca,Jurca2,Malik,Maximilien1,Yahyaoui}, the
+authors propose to rank services based on their reputation in the
+system and to use this ranking as a means to facilitate
+cooperation of services. In those models, services rely on one
+another on the basis of the reputation ranking system, using,
+among other parameters, the QoS \cite{Qian-Tao-2012}. There are
+other models that facilitate cooperation mechanisms among services
+using various techniques. Examples of those techniques include 1)
+coordination between two types of behaviors associated with
+component services: operational and control behaviors
+\cite{Yahyaoui3}; 2) Services-based workflows \cite{Wu-2011}; 3)
+transaction-based approaches \cite{Gao,Rosario}; 4) agent
+coordination mechanisms \cite{Charif,Gutierrez-Garcia-2013}; 5)
+logical techniques \cite{Okutan,Tang}; and 6) community models,
+which are virtual structures that aim at increasing the visibility
+of services and facilitating their discovery and composition by
+hosting and gathering services having similar or complementary
+functionalities but different QoS parameters
+\cite{Khosravifar2010}. %There are also some frameworks
+%\cite{Ferguson,Ferguson2} that consider game-theoretic analysis on
+%the expected payoffs obtained via different acting strategies.
+However, deciding about which strategy to choose when services are
+competing but still need to cooperate to accomplish complex tasks
+has not been addressed and kept as open issue in all these
+proposals as faithfully argued in
+\cite{Maamar2011,Khosravifar-ICSOC2012}.
+
 %All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process.

### 2015-07-07 thesis/thesis/chap2/chap2.tex
changes

@@
 
-At the best of our knowledge, there is no work in the literature
-of service and agent computing addressing the issue of coopetition
-strategies and when to cooperate or to compete. However, some
-relevant proposals to the model presented in this paper are the
-ones that address service selection and task allocation
-mechanisms. In many frameworks proposed in the literature, service
-selection and task allocation are regulated based on the
-reputation parameter \cite{Bentahar,Rosario,Ruth,Yahyaoui}.
-\textbf{In \cite{Huang}, the authors propose a framework to match potential
-benefits of services while cooperating with one another. The
-interesting idea is to consider the benefits under four
-categories: innovation and learning, internal business process,
-customer, and financial benefits.
-Innovation and learning perspective} focuses on the knowledge, skills, and systems needed to improve the business continually.
+At the best of our knowledge, there is no work in the literature of service and agent computing addressing the issue of coopetition strategies and when to cooperate or to compete.
+However, some relevant proposals to our proposed model are the ones that address service selection and task allocation mechanisms.
+In many frameworks proposed in the literature, service selection and task allocation are regulated based on the reputation parameter \cite{Bentahar:2012:ARA:2343124.2343267,DBLP:journals/jwsr/RosarioBJ10,Ruth_Tu_2007-7,journals/kbs/Yahyaoui12}.
+In \cite{HuangCommunications}, the authors propose a framework to match potential benefits of services while cooperating with one another.
+The interesting idea is to consider the benefits under four categories: innovation and learning, internal business process, customer, and financial benefits.
+Innovation and learning perspective focuses on the knowledge, skills, and systems needed to improve the business continually.
 Necessary factors to build strategic capabilities and efficiency in addressed in internal business process.
@@
 Their goal is to design the framework for cooperating web services, inline with business strategy of firms in IT industry.
-In \cite{Alchieri}, the authors
-present a dependable framework for cooperative service agents that
-is based on the tuple space coordination model. The
-intrusion-tolerant perspective is emphasized in this paper where
-several security mechanisms are developed to enable a reliable
-coordination system. %In \cite{Maximilien2}, authors propose
-%ontology for quality of service. Users compute the web services'
-%reputation using ratings.
-The proposed frameworks mostly aim to facilitate the coordination
-mechanism between services. However, the opposite strategy of
-competing is not analyzed where services might be more successful
-when competing within the same group. In fact, services are not
-always willing to cooperate even if they have some common goals,
-particularly when they operate within groups such as communities.
-In such a context, service agents can follow different interacting
-strategies and have to decide when to compete and when to
-cooperate so that their ultimate goal, maximizing their incomes,
-can be better achieved. In our framework, we analyze those
-different strategies to help services in their decision making
-process when these
-agents function within communities. %We summarize most of
-%these proposals and concentrate on strategic decision making
-%system that ranks web services in the community and analyze their
-%effective interacting strategies to accomplish continuous
-%requested tasks.
-We enable service agents to reasonably evaluate and decide over
-their coopetition strategies, which means deciding when to compete
-and when to cooperate.
+In \cite{alchieri:a}, the authors present a dependable framework for cooperative service agents that is based on the tuple space coordination model.
+The intrusion-tolerant perspective is emphasized in this paper where several security mechanisms are developed to enable a reliable coordination system.
+%In \cite{Maximilien2}, authors propose %ontology for quality of service.
+Users compute the web services' %reputation using ratings.
+The proposed frameworks mostly aim to facilitate the coordination mechanism between services.
+However, the opposite strategy of competing is not analyzed where services might be more successful when competing within the same group.
+In fact, services are not always willing to cooperate even if they have some common goals, particularly when they operate within groups such as communities.
+In such a context, service agents can follow different interacting strategies and have to decide when to compete and when to cooperate so that their ultimate goal, maximizing their incomes, can be better achieved.
+In our framework, we analyze those different strategies to help services in their decision making process when these
+agents function within communities. 
+%We summarize most of %these proposals and concentrate on strategic decision making %system that ranks web services in the community and analyze their %effective interacting strategies to accomplish continuous %requested tasks.
+We enable service agents to reasonably evaluate and decide over their coopetition strategies, which means deciding when to compete and when to cooperate.
 
@@
 these services coordinate their actions to accomplish the required
-tasks. In \cite{Jurca,Jurca2,Malik,Maximilien1,Yahyaoui}, the
+tasks. In \cite{Jurca2007b,Jurca2005d,DBLP:conf/wise/MalikB07,Maximilien1,Yahyaoui}, the
 authors propose to rank services based on their reputation in the

### 2015-07-07 thesis/thesis/chap2/chap2.tex
changes

@@
 these services coordinate their actions to accomplish the required
-tasks. In \cite{Jurca2007b,Jurca2005d,DBLP:conf/wise/MalikB07,Maximilien1,Yahyaoui}, the
+tasks. In \cite{Jurca2007b,Jurca2005d,DBLP:conf/wise/MalikB07,Maximilien:2001:REW:844331.844335,journals/kbs/Yahyaoui12}, the
 authors propose to rank services based on their reputation in the
@@
 another on the basis of the reputation ranking system, using,
-among other parameters, the QoS \cite{Qian-Tao-2012}. There are
+among other parameters, the QoS \cite{Tao:2012:NPA:2064113.2064479}. There are
 other models that facilitate cooperation mechanisms among services
@@
 component services: operational and control behaviors
-\cite{Yahyaoui3}; 2) Services-based workflows \cite{Wu-2011}; 3)
-transaction-based approaches \cite{Gao,Rosario}; 4) agent
-coordination mechanisms \cite{Charif,Gutierrez-Garcia-2013}; 5)
-logical techniques \cite{Okutan,Tang}; and 6) community models,
+\cite{DBLP:journals/ijwgs/YahyaouiMB10}; 2) Services-based workflows \cite{Wu2011}; 3)
+transaction-based approaches \cite{Gao:2011:STI:2093449.2093450,DBLP:conf/icws/RosarioBHJ07}; 4) agent
+coordination mechanisms \cite{DBLP:journals/aamas/CharifS13,DBLP:journals/apin/Gutierrez-GarciaS13}; 5)
+logical techniques \cite{Okutan:2010:MAA:1805335.1805430,tang:automatic}; and 6) community models,
 which are virtual structures that aim at increasing the visibility
@@
 functionalities but different QoS parameters
-\cite{Khosravifar2010}. %There are also some frameworks
+\cite{DBLP:journals/jwsr/KhosravifarBMT10}. %There are also some frameworks
 %\cite{Ferguson,Ferguson2} that consider game-theoretic analysis on
@@
 proposals as faithfully argued in
-\cite{Maamar2011,Khosravifar-ICSOC2012}.
+\cite{1fd085d030db49d9ad024f89d13faff3,DBLP:conf/icsoc/KhosravifarAABMO12}.
 

### 2015-07-07 thesis/thesis/chap5/chap5.tex
changes

@@
 For new services with no previous reputation value, we use the
-bootstrapping trust technique proposed in \cite{Yahyaoui2}. This
+bootstrapping trust technique proposed in \cite{DBLP:conf/icwe/YahyaouiZ11}. This
 technique consists in giving the new services a chance and observe
@@
 (denoted here by $m_w(t)$) can be modeled as a nonhomogeneous
-Poisson process \cite{Khosravifar-ICWS2010,Ruggeri2005}, which
+Poisson process \cite{DBLP:conf/icws/KhosravifarBM10,RePEc:spr:sistpr:v:8:y:2005:i:3:p:311-329}, which
 means as a Poisson process with dynamic arrival rate
@@
 samples using the least squares, iterative least squares, or
-maximum likelihood \cite{Massey1996}.
+maximum likelihood \cite{DBLP:journals/telsys/MasseyPW96}.
 
@@
 The dataset records the QoS values of $9$ parameters including \textit{availability},
-\textit{throughput}, and \textit{reliability} \cite{Almasri}.
+\textit{throughput}, and \textit{reliability} \cite{DBLP:conf/www/Al-MasriM07a}.
 

### 2015-07-08 thesis/thesis/chap1/chap1.tex
changes

@@
 In order to address the centralized decision making process limitations and adopt a distributed decision making approach, we introduce DDM, a Distributed Decision Making model for community formation.
-DDM regulates web service agents’ decision making process in terms of cooperating and deciding which group to join and which service to invite for joining.
+DDM regulates web service agents' decision making process in terms of cooperating and deciding which group to join and which service to invite for joining.
 Unlike existing work on community formation, our decision model is extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.

### 2015-07-08 thesis/thesis/chap2/chap2.tex
changes

@@
 
-        In this research work, we will use game theory to
-        propose a cooperative game model for the aggregation of web
-        services within communities. The solution concepts of our
-        cooperative game seeks to find efficient ways of forming
-        coalitions (teams) of web services so that they can maximize their
-        gain and payoff, and distribute the gain in a fair way among all
-        the web services. Achieving Fairness when the gain is distributed
-        among the community members is the main factor to keep the
-        coalition stable as no web service will expect to gain better by
-        deviating from the community. In other words, the coalition is made
-        efficient if all the members are satisfied. We first propose a
-        representation function for communities of web services based on
-        their QoS attributes. By using this function, we can evaluate the
-        $worth$ of each community of web services. When facing new
-        membership requests, a typical community master checks whether the
-        new coalition having the old and new set of web services will keep
-        the community stable or not. The community master will reject the
-        membership requests if it finds out that the new coalition would
-        be unstable, preventing $any$ subset of web services from gaining
-        significantly more by deviating from the community and joining
-        other communities or forming new ones. The computation of
-        solutions for cooperative game theory problems is combinatorial in
-        nature and proven to be NP-complete \cite{Algorithmic}, making
-        this computation impractical in real world applications. However,
-        using the concepts of coalition stability, we propose
-        approximation algorithms running in polynomial time providing web
-        services and community masters with applicable and near-optimal
-        decision making mechanisms.
+In this research work, as the first contribution we will tackle with the issue of community formation in an efficient way for all the web service and communities involved.
+We will use game theory to propose a cooperative game model for the aggregation of web services within communities.
+The solution concepts of our cooperative game seeks to find efficient ways of forming coalitions (teams) of web services so that they can maximize their gain and payoff, and distribute the gain in a fair way among all the web services.
+Achieving Fairness when the gain is distributed among the community members is the main factor to keep the coalition stable as no web service will expect to gain better by deviating from the community.
+In other words, the coalition is made efficient if all the members are satisfied.
+We first propose a representation function for communities of web services based on their QoS attributes.
+By using this function, we can evaluate the $worth$ of each community of web services.
+When facing new membership requests, a typical community master checks whether the new coalition having the old and new set of web services will keep the community stable or not.
+The community master will reject the membership requests if it finds out that the new coalition would be unstable, preventing $any$ subset of web services from gaining significantly more by deviating from the community and joining other communities or forming new ones.
+The computation of solutions for cooperative game theory problems is combinatorial in nature and proven to be NP-complete \cite{Algorithmic}, making this computation impractical in real world applications.
+However, using the concepts of coalition stability, we propose approximation algorithms running in polynomial time providing web services and community masters with applicable and near-optimal decision making mechanisms.
+
+Next we will tackle the issue of distributed model of web services and propose a decision model for scenarios where information is incomplete.
+We proposed a training model for the problem of membership management of communities of web services.
+Using the traning model we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves.
+This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available.
+The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices.
+The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.
+The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.
+
+In our last contribution, the focus is on internal community management.
+We proposed a game-theoretic based model to analyze the best efficiency characteristics for the active services in open networks.
+The proposed framework considers the chances of web services in joining a community in different cases with truthful and lying information service agents.
+The proposed game analyzes the existing Nash equilibrium and situations where the maximum payoff is obtained.

### 2015-07-08 thesis/thesis/chap3/chap3.tex
changes

@@
 
-In this chapter,
+In this section, we proposed a cooperative game theory-based model for the aggregation of web services within communities.
+The goal of our services is to maximize efficiency by collaborating and forming stable coalitions.
+Our method considers stability and fairness for all web services within a community and offers an applicable mechanism for membership requests and selection of web services.
+The ultimate goal is to increase revenue by improving user satisfaction, which comes from the ability to perform more
+tasks with high quality. Simulation results show that our, polynomial in complexity, approximation algorithms provide web services and community owners with applicable and near-optimal
+decision making mechanisms.
+
+As future work in this area, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications.
+From web service perspective, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks.
+Also bargaining theory from cooperating game theory concepts can be used to help web services resolve the instability and unfairness issues by side payments.
+
+In this chapter, we assumed our web services and communities have compelte knowledge of all the other web services and their parameters.
+In next section we propose distributed decision making model which can perform in scenarios where information is incomplete.

### 2015-07-08 thesis/thesis/chap5/chap5.tex
changes

@@
 
-In this chapter,
+In this chapter, we proposed a game-theoretic based model to analyze the best efficiency characteristics for the active services in open networks.
+The proposed framework considers the chances of web services in joining a community in different cases with truthful and lying information service agents.
+The proposed game analyzes the existing Nash equilibrium and situations where the maximum payoff is obtained.
+
+Our model has the advantage of being simple and taking into account three important factors: (1) rational services seek better status in the environment by joining the community; (2) rational information service agents obtain higher payoff by truth telling; and (3) the community is obtaining more effective web services while the information service agents challenge for providing truthful information.
+As future work, we plan to consider the user role in the game to obtain more accurate results when users act rationally.
+Moreover, we would like to achieve a collusion resistant efficiency mechanism, which is still an open problem in open environments.

### 2015-07-08 thesis/thesis/chap6/chap6.tex
changes

@@
 
-\item F.
+%\item F.
 Al-Saqqar, J.
@@
 
-\item H.
+%\item H.
 O.
@@
 
-\item H. Fallatah, J. Bentahar, E. Khosrowshahi Asl, "Social Network-Based Framework for Web Services Discovery", IEEE  FiCloud, Barcelona, Spain, 2014.
+%\item H. Fallatah, J. Bentahar, E. Khosrowshahi Asl, "Social Network-Based Framework for Web Services Discovery", IEEE  FiCloud, Barcelona, Spain, 2014.
 

### 2015-07-09 thesis/thesis/chap1/chap1.tex
changes

@@
 We discuss the motivations of this work and briefly review the literature to identify the problems we aim to solve in this thesis.
-Moreover, we discuss our objectives and preliminary contributions.
+Moreover, we discuss our objectives and contributions.
 
@@
 web-based applications has significantly influenced the way web
-services are engineered. Web services provide a set of stateless
-software functions accessible at a network address over the web.
+services are engineered. Web services provide a set of online software functions accessible at a network address over the web.
 The recent developments are shifting web services from passive and
@@
 services industry requires applications to use reliable and high
-quality online service providers.
+quality online services.
 
@@
 sending requests to a web service which is not providing
-satisfactory services. Thus its important to consider all the
+satisfactory services. Thus, it is important to consider all the
 parties involved in the decision making process about the
-community management. Most of the recent work on communities of
+community formation and management. Most of the recent work on communities of
 services are either user-centric and focus on user satisfaction
@@
 mechanisms to help users and services maximize their gain. A
-two-player non-cooperative game between web services and community
-master was introduced in
+two-player non-cooperative game between web services and community master (i.e., manager) was introduced in
 \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In
@@
 subset of web services. Those services can collude and form their
-own community and gain more, instead of having to adjust and share
+own community to increase their payoff, instead of having to adjust and share
 their resources with other members. Another important issue which
@@
 working in the community, these agents, as profit maximizing
-entities, would just deviate and make their own group. So an
+entities, would deviate and make their own group. Thus, an important an
 important research question that we would like to address is:
@@
 activity engaging all agents to perform the tasks more
-efficiently. Thus, the final research question we would like to
-work on is: \emph{How can we model and analyze the cooperation
+efficiently. Thus, the final research question we aim to investigate is: \emph{How can we model and analyze the cooperation
 among the community members in realistic, applicable and practical
@@
 However, for the same reason of being functionally similar, services can cooperate with each other, for example to substitute each other in order to perform some sub-tasks.
-So as an extension of our work, we have proposed a framework in which services can opt for performing tasks if they feel they are capable enough
+For instance, services can opt for performing tasks if they feel they are capable enough
 or decide to cooperate by showing the availability to perform some sub-tasks.
-\emph{How can we approach a cooperative model within a community where both competitive and cooperative behaviors exist?[R4]}
+The relevant question to be addressed is: \emph{How can we design a community model where both competitive and cooperative behaviors exist?[R4]}
 
 In most of the recent work on communities of web service, the solutions consider the architecture of centralized management for communities where most of the decisions are made by the centralized coordinator.
-The problem is that in real world scenarios, decisions made by independent service providers are highly distributed.
-\emph{How can we model a distributed decision making process for formation of communities of services?[R5]}
+However, in real world scenarios, decisions made by independent service providers are highly distributed.
+\emph{How can we model a distributed decision making process for the problem of forming communities of services?[R5]}
 
-Also in all of the mentioned works, the community manager as a centralized entity, has complete information of all the web services and their quality.
-However, centrality and complete information are strong assumptions, which are not very compatible with real business scenarios.
-\emph{How can we train web services based on smaller set of information to operate efficiently when information is non-complete[R6]?}
+Also in all of the mentioned proposals, the community manager as a centralized entity, has complete information of all the web services and their quality.
+However, centrality and complete information are strong assumptions, which are not fully compatible with real business scenarios.
+\emph{How can we train web services based on limited information to operate efficiently[R6]?}
 
@@
 
+\noindent \emph{\textbf{Contribution \#1:} Efficient Coalition Formation for Web Services\cite{10.1109/TSC.2014.2312940}.}
+
 In this research work, our first objective is to propose a
@@
 distribute the gain in a fair way among all the member services.
-Achieving Fairness when the gain is distributed among the
+Achieving fairness when the gain is distributed among the
 community members is the main factor to keep the coalition stable
@@
 proven to be NP-complete \cite{Algorithmic}, making this
-computation impractical in real world applications. However, using
+computation impractical in scalable real world applications. However, using
 the concepts of coalition stability, the second objective is to
@@
 
+\noindent \emph{\textbf{Contribution \#2:} Distributed decision making for dynamic formation of web services communities.}
+
 In order to address the centralized decision making process limitations and adopt a distributed decision making approach, we introduce DDM, a Distributed Decision Making model for community formation.
@@
 Unlike existing work on community formation, our decision model is extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
-The generated decision tree improves agents' understanding of the environment and how to select actions that lead towards maximizing their utilities.
+The generated decision tree improves agents' understanding of the environment and and helps them select actions that lead towards maximizing their utilities.
 The advantage of this approach is that the tree, which is initially created from the past data, reflects a comprehensive vision about agents' attitudes in terms of their action selection based on their past experiences.
 Moreover, the tree is getting continuously updated based on both new received feedback and the outcome of chosen actions.
-This continuous update makes the approach adapted to any change in the environment.
+This continuous update makes the approach adaptable to any change in the environment.
 %The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems.
@@
 
+\noindent \emph{\textbf{Contribution \#3:} Analyzing Coopetition Strategies of Services within Communities\cite{DBLP:journals/eswa/AslBMKO14}.}
+
+In previous contributions, our focus was on community formation and we emphasised on cooperative behavior of the web services as agents.
+In our next contribution our focus is on the internal management affairs of communities of web services.
+Within communities, the web services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}.
+In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite.
+However, the same reason of providing similar functionalities can lead services to cooperate because they can replace each other in case of failure or unavailability, and services can do better in a coalition structure.
+Analyzing services competition and cooperation strategies within communities is still an open problem that motivates the research described in this section.
+we propose a mechanism within which service agents
+in the community could choose either to compete for an announced task\footnote{Requests and tasks are used in this thesis interchangeably.}, or to cooperate with other competing services in the same community to accomplish some subtasks of the announced task.
+We equip intelligent web services to follow a reasoning technique to choose best interactive strategy (Coopetitive attitude, which is categorized to compete and cooperate).
+In the proposed system, We explore details behind the strategic decision making procedures and enable service agents to apply different techniques to constrain high efficiency and obtain the maximum utility.
+We investigate services' expected payoffs and the involved probabilities that are used to choose over the two interacting strategies.
+
 \indent To summarize, the main problem we aim to tackle in this thesis is the formation of stable and efficient coalitions maximizing web services and community revenue. The main objectives are:
@@
 
-\item To approach the community decision making process in a distributed manner and train agents so they can operate efficiently when information is non-complete.
+\item To design the community decision making process in a distributed manner and train agents so they can operate efficiently when information is incomplete.
 
@@
 
-\begin{figure}[!t]
-\centering
-\includegraphics[width=6in]{Figures/c1.eps}`
-\caption{First contribution: Efficient Coalition Formation for Web Services}
-\label{fig_c1}
-\end{figure}
+%\begin{figure}[!t]
+%\centering
+%\includegraphics[width=6in]{Figures/c1.eps}`
+%\caption{First contribution: Efficient Coalition Formation for Web Services}
+%\label{fig_c1}
+%\end{figure}
+%
+%\begin{figure}[!t]
+%\centering
+%\includegraphics[width=6in]{Figures/c2.eps}`
+%\caption{Second contribution: Analyzing Coopetition Strategies of Services within Communities}
+%\label{fig_c2}
+%\end{figure}
+%
+%\begin{figure}[!t]
+%\centering
+%\includegraphics[width=6in]{Figures/c3.eps}`
+%\caption{This contribution: Distributed decision making for dynamic formation of web services communities}
+%\label{fig_c3}
+%\end{figure}
 
-\begin{figure}[!t]
-\centering
-\includegraphics[width=6in]{Figures/c2.eps}`
-\caption{Second contribution: Analyzing Coopetition Strategies of Services within Communities}
-\label{fig_c2}
-\end{figure}
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=6in]{Figures/c3.eps}`
-\caption{This contribution: Distributed decision making for dynamic formation of web services communities}
-\label{fig_c3}
-\end{figure}
-
-Figure \ref{fig_model} highlights our contributions and proposed model for community of web service management.
+Figure \ref{fig_model} highlights our contributions and proposed model for communities of web services formation and management.
 
@@
 Chapter 3 provides an efficient method of coalition formation for web services.
-In chapter 4 we discuss the cooperative behaviour within the communities of web services.
+In Chapter 4 we discuss the cooperative behaviour within the communities of web services.
 Chapter 5 presents a distributed method of formation of web services communities.
-Finally in chapter 6, we present our conclusion and future plan.
+Finally in Chapter 6, we present our conclusion and future plan.
 

### 2015-07-09 thesis/thesis/chap5/chap5.tex
changes

@@
 In previous chapter, our focus was on community formation and we emphasised on cooperative behavior of the web services as agents.
-Within communities, those services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}.
+Within communities, the web services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}.
 In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite.

### 2015-07-10 thesis/thesis/abstract.tex
changes

@@
 
- \textbf{This is not real abstract} In the last few years, communities of services have been studied in a certain numbers of proposals as virtual pockets of similar expertise.
+In the last few years, communities of services have been studied in a certain numbers of proposals as virtual pockets of similar expertise.
 The motivation is to provide these services with high chance of discovery through better visibility, and to enhance their capabilities when it comes to provide requested functionalities.

### 2015-07-10 thesis/thesis/chap2/chap2.tex
changes

@@
 we discuss the cooperative game theory concepts used throughout
-the proposal. Finally, we discuss relevant related work on web
+the thesis. Finally, we discuss relevant related work on web
 service communities and games in the literature of service
@@
 We are not going to delve into engineering details of online web
-service implementation and its protocols in this proposal. We are
+service implementation and its protocols in this thesis. We are
 interested in web services from their business model perspective.
@@
 Those considerations of forming stable and efficient coalitions
-are the main contributions of our paper.
+are the main contributions of our research work.
 

### 2015-07-10 thesis/thesis/chap3/chap3.tex
changes

@@
 In this section, we discuss the parameters and preliminary
-concepts that we use in the rest of the proposal.
+concepts that we use in the rest of the chapter.
 
@@
 higher market share, and to have opportunity of receiving a bigger
-task pool from end users. Throughout this proposal, in our
+task pool from end users. Throughout this thesis, in our
 equations, we refer to web services as $ws$ and to the set of web

### 2015-07-10 thesis/thesis/chap4/chap4.tex
changes

@@
 
-\textbf{Contributions.} In this paper, we introduce DDM, a Distributed Decision Making model for community formation that regulates web service agents’ decision making process in terms of cooperating and deciding which group to join and which service to invite for joining.
+\textbf{Contributions.} In this chapter, we introduce DDM, a Distributed Decision Making model for community formation that regulates web service agents’ decision making process in terms of cooperating and deciding which group to join and which service to invite for joining.
 Unlike existing work on community formation, our decision model is extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
@@
 
-We are not going to delve into the engineering details of online web service implementation and its protocols in this paper.
+We are not going to delve into the engineering details of online web service implementation and its protocols in this thesis.
 We are interested in web services from a business model perspective.
@@
 
-In this section, we discuss the parameters that we use in the rest of the paper. Then, we present the task distribution and revenue model of our distributed web services communities.
+In this section, we discuss the parameters that we use in the rest of the chapter. Then, we present the task distribution and revenue model of our distributed web services communities.
 
@@
 Web services quality metrics have been studied and analyzed in various proposals, for instance in in \cite{Ardagna:2007:ASC:1263152.1263531,Menasce:2002:QIW:613357.613758,10.1109/ISSRE.2011.17}.
-In this paper, we adopt the most representative QoS properties of those services that highly influence their utility.
+In this chapter, we adopt the most representative QoS properties of those services that highly influence their utility.
 %We refer to a typical web service as ws_{i}.
@@
 metric and parameters. Those proposals run complex algorithms through all the space of
-solutions in order to find the optimal answer. However, in this paper, we
+solutions in order to find the optimal answer. However, in this research work, we
 have considered an unexplored and more realistic situation where information is incomplete and a decision
@@
 Those considerations of forming stable and efficient coalitions
-are the main contributions of our paper.
+are the main contributions of our thesis.
 
@@
 Another major difference with our work is that the decision making process is only one way and unilateral from the community manager perspective.
-In our proposal, both participants, namely communities and web services, participate in the decision making process and a joining decision is made only if it is the best option for both players.
+In our contribution, both participants, namely communities and web services, participate in the decision making process and a joining decision is made only if it is the best option for both players.
 
@@
 This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.
+
+In next chapter, we analyse the internal community behaviour of web services, and propose a model for competing and cooperating agents within the communities of web services.

### 2015-07-10 thesis/thesis/chap5/chap5.tex
changes

@@
 
-\begin{proof}\footnote{In this paper, we
+\begin{proof}\footnote{In this work, we
 assume that the common arithmetic and elementary functions, such
@@
 account when a service decides to leave to a cheaper community or
-act alone. But to concentrate on the main concerns of this paper,
+act alone. But to concentrate on the main concerns of this thesis,
 we skip these small details.\\\\

### 2015-07-12 thesis/thesis/abstract.tex
changes

@@
 However, those services can also exhibit cooperative behaviors, for instance in terms of substituting each other.
+When competitive and cooperative behaviors and strategies are combined, autonomous services are said to be ``coopetitive''.
 Deciding to compete or cooperate inside communities is a problem yet to be investigated.
 
-In this thesis, we identify the problem of defining efficient algorithms for coalition formation mechanisms within communities and propose some results using cooperative game-theoretic techniques.
+In this thesis, we first identify the problem of defining efficient algorithms for coalition formation mechanisms within communities and propose some results using cooperative game-theoretic techniques.
+We propose a mechanism for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities.
+Then in order to address the coopetitive relation within our web services, we propose a decision making mechanism for our web services to efficiently choose competition or cooperation strategies to maximize their payoffs.
+We prove that the proposed decision mechanism is
+efficient and can be implemented in time linear in the length of the time period considered for the analysis and the number of services in the community. Moreover, we conduct extensive
+simulations, analyze various scenarios, and confirm the obtained theoretical results using parameters from a real web services dataset.
+
+%.
+and propose some results using cooperative game-theoretic techniques.
 We propose a mechanism for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities.
@@
 %The experimental results demonstrate the efficiency and scalability of the proposed reduction techniques and show that our work is effective for addressing probabilistic social commitment in MASs.
-\\
+
 %\textbf{keywords:}

### 2015-07-12 thesis/thesis/chap1/chap1.tex
changes

@@
 community of agent-based services in order to maximize the utility
-of involved users, web services and community organizers?[R1]}
+of involved users, web services and community organizers? [R1]}
 
@@
 \emph{How can we model fair and stable communities as coalitions
-of agent-based web services?[R2]}
+of agent-based web services? [R2]}
 
@@
 among the community members in realistic, applicable and practical
-settings?[R3]}
+settings? [R3]}
 
@@
 or decide to cooperate by showing the availability to perform some sub-tasks.
-The relevant question to be addressed is: \emph{How can we design a community model where both competitive and cooperative behaviors exist?[R4]}
+The relevant question to be addressed is: \emph{How can we design a community model where both competitive and cooperative behaviors exist?
+[R4]}
 
@@
 However, in real world scenarios, decisions made by independent service providers are highly distributed.
-\emph{How can we model a distributed decision making process for the problem of forming communities of services?[R5]}
+\emph{How can we model a distributed decision making process for the problem of forming communities of services?
+[R5]}
 
@@
 However, centrality and complete information are strong assumptions, which are not fully compatible with real business scenarios.
-\emph{How can we train web services based on limited information to operate efficiently[R6]?}
+\emph{How can we train web services based on limited information to operate efficiently? [R6]}
 
@@
 
-\section{Research Objectives and Contributions}\label{sec:motexample}
+\section{Contributions}\label{sec:motexample}
 
-\noindent \emph{\textbf{Contribution \#1:} Efficient Coalition Formation for Web Services\cite{10.1109/TSC.2014.2312940}.}
+\subsection{Contribution 1: Efficient Coalition Formation for Web Services}
 
-In this research work, our first objective is to propose a
+%\cite{10.1109/TSC.2014.2312940}.}
+
+In this research work\footnote{This contribution was published in \cite{10.1109/TSC.2014.2312940}}, our first objective is to propose a
 cooperative model as game for the aggregation of web services
@@
 
-\noindent \emph{\textbf{Contribution \#2:} Distributed decision making for dynamic formation of web services communities.}
+\subsection{Contribution 2: Distributed decision making for dynamic formation of web services communities.}
 
-In order to address the centralized decision making process limitations and adopt a distributed decision making approach, we introduce DDM, a Distributed Decision Making model for community formation.
+In order to address the centralized decision making process limitations and adopt a distributed decision making approach, we introduce DDM\footnote{This contribution is submitted to International Journal of Decision Support Systems as a journal paper}, a Distributed Decision Making model for community formation.
 DDM regulates web service agents' decision making process in terms of cooperating and deciding which group to join and which service to invite for joining.
@@
 
-\noindent \emph{\textbf{Contribution \#3:} Analyzing Coopetition Strategies of Services within Communities\cite{DBLP:journals/eswa/AslBMKO14}.}
+\subsection{Contribution 3: Analyzing Coopetition Strategies of Services within Communities}
 
 In previous contributions, our focus was on community formation and we emphasised on cooperative behavior of the web services as agents.
-In our next contribution our focus is on the internal management affairs of communities of web services.
+In our next contribution\footnote{This contribution was published in \cite{DBLP:journals/eswa/AslBMKO14}} our focus is on the internal management affairs of communities of web services.
 Within communities, the web services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}.
+When competitive and cooperative behaviors and strategies are combined, autonomous services are said to be ``coopetitive''.
 In typical business settings, services are used to compete within communities as they provide the same functionalities and the number of users requests is finite.

### 2015-07-12 thesis/thesis/chap4/chap4.tex
changes

@@
 
-\section{Related Work}\label{s:related_work}
-
-Most of the recent work on communities of services are either
-user-centric and focus on user satisfaction
-\cite{Chun02user-centricperformance} or system-centric and focus
-on the whole system throughput, performance and utilization. There
-are many contributions in distributed, grid, cluster and cloud
-services which are system-centric. However, in real world
-environments and applications, both users and service providers
-are self-interested agents, aiming to maximize their own profit.
-In those environments, both parties (users and services) will
-collaborate as long as they are getting more benefits and payoff.
-
-In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
-DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
-mechanisms to help users and services maximize their gain. A
-two-player non-cooperative game between web services and community
-master was introduced in
-\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this game-theoretic
-model, the strategies available to a web service when facing a new
-community are requesting to join the community, accepting the
-master's invitation to join the community, or refusing the
-invitation to join. The set of strategies for communities are
-inviting the web service or refusing the web service's join
-request. Based on their capacity, market share and reputation, the
-two players have different sets of utilities over the strategy
-profiles of the game. The main limits of this game model are: 1)
-its consideration of only three quality parameters, while the
-other factors are simply ignored; and 2) the non-consideration of
-the web services already residing within the community. The game
-is only between the community master and the new web service, and
-the inputs from all the other members and their influence on the
-master's decision are simply ignored. The consideration of those
-inputs and this influence factor is a significant issue as
-existing web services can lose utility or payoff because of the
-new member, which can result in an unhealthy and unstable group.
-The problem comes from the fact that the existing members should
-collaborate with the new web services, so probably their
-performance as a group can suffer. Existing members may even
-deviate and try to join other communities if they are unsatisfied.
-Those considerations of forming stable and efficient coalitions
-are the main contributions of our thesis.
-
-In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
-for selecting web services has been proposed. In this approach,
-the authors proposed a web service selection process that the
-community masters can use. The approach considers the efficiency
-of all the three involved parties, namely users, web services and
-communities. In this work, it is shown how the gains of these
-parties are coupled together using a linear optimization process.
-However, the optimization problem in this solution tends to
-optimize some parameters considering all web services regardless
-of their efficiency and contribution to the community's welfare.
-Moreover, there are no clear thresholds for accepting or rejecting
-new web services. The solution of the optimization problem could,
-for instance, suggest web services already residing within the
-community to increase or decrease their capacity to cover up the
-weakness of other parties in the system. However, a high
-performing web service could deviate anytime it finds itself
-unsatisfied within the community instead of adjusting its service
-parameters.
-
-In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
-autonomous web services based on coalition game theory has been
-introduced. The authors have proposed an interesting algorithm to
-reach individually stable coalition partition for web services in
-order to maximize their efficiency. The communities choose new web
-services on the promise that it would benefit the community
-without decreasing any other web service's income. In the proposed
-model, the worth of community is evaluated with high emphasis on
-the availability metric and considering price and cost values
-only. The community structure is based on a coordination chain,
-where a web service is considered as a \emph{primary} web service
-and the community task-distribution method initially invokes the
-primary web service and only if the primary web service is
-unavailable, the method invokes the next backup web services as
-they are ordered in the coordination chain. We believe that this
-coordination chain limits the cooperation power as it introduces a
-sort of hierarchy. However, in pure and open cooperative models,
-such as the one we propose in this paper, active cooperation
-activities engaging simultaneously many agents so that they can
-perform the tasks more efficiently are being used. Moreover, if
-the availability is high, which is the case nowadays with the
-recent advancements in cloud infrastructures and hardware technologies, the
-backup web services will end-up having a very low chance of
-getting jobs, especially the ones further in the chain. This will
-results in a considerable waste of web services capabilities.
-
-All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process.
-So basically, these solutions generally suffer from high complexity, which makes decision making very hard, even impossible in some cases in a real-time fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.
+%\section{Related Work}\label{s:related_work}
+%
+%Most of the recent work on communities of services are either
+%user-centric and focus on user satisfaction
+%\cite{Chun02user-centricperformance} or system-centric and focus
+%on the whole system throughput, performance and utilization. There
+%are many contributions in distributed, grid, cluster and cloud
+%services which are system-centric. However, in real world
+%environments and applications, both users and service providers
+%are self-interested agents, aiming to maximize their own profit.
+%In those environments, both parties (users and services) will
+%collaborate as long as they are getting more benefits and payoff.
+%
+%In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
+%DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed
+%mechanisms to help users and services maximize their gain. A
+%two-player non-cooperative game between web services and community
+%master was introduced in
+%\cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this game-theoretic
+%model, the strategies available to a web service when facing a new
+%community are requesting to join the community, accepting the
+%master's invitation to join the community, or refusing the
+%invitation to join. The set of strategies for communities are
+%inviting the web service or refusing the web service's join
+%request. Based on their capacity, market share and reputation, the
+%two players have different sets of utilities over the strategy
+%profiles of the game. The main limits of this game model are: 1)
+%its consideration of only three quality parameters, while the
+%other factors are simply ignored; and 2) the non-consideration of
+%the web services already residing within the community. The game
+%is only between the community master and the new web service, and
+%the inputs from all the other members and their influence on the
+%master's decision are simply ignored. The consideration of those
+%inputs and this influence factor is a significant issue as
+%existing web services can lose utility or payoff because of the
+%new member, which can result in an unhealthy and unstable group.
+%The problem comes from the fact that the existing members should
+%collaborate with the new web services, so probably their
+%performance as a group can suffer. Existing members may even
+%deviate and try to join other communities if they are unsatisfied.
+%Those considerations of forming stable and efficient coalitions
+%are the main contributions of our thesis.
+%
+%In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
+%for selecting web services has been proposed. In this approach,
+%the authors proposed a web service selection process that the
+%community masters can use. The approach considers the efficiency
+%of all the three involved parties, namely users, web services and
+%communities. In this work, it is shown how the gains of these
+%parties are coupled together using a linear optimization process.
+%However, the optimization problem in this solution tends to
+%optimize some parameters considering all web services regardless
+%of their efficiency and contribution to the community's welfare.
+%Moreover, there are no clear thresholds for accepting or rejecting
+%new web services. The solution of the optimization problem could,
+%for instance, suggest web services already residing within the
+%community to increase or decrease their capacity to cover up the
+%weakness of other parties in the system. However, a high
+%performing web service could deviate anytime it finds itself
+%unsatisfied within the community instead of adjusting its service
+%parameters.
+%
+%In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
+%autonomous web services based on coalition game theory has been
+%introduced. The authors have proposed an interesting algorithm to
+%reach individually stable coalition partition for web services in
+%order to maximize their efficiency. The communities choose new web
+%services on the promise that it would benefit the community
+%without decreasing any other web service's income. In the proposed
+%model, the worth of community is evaluated with high emphasis on
+%the availability metric and considering price and cost values
+%only. The community structure is based on a coordination chain,
+%where a web service is considered as a \emph{primary} web service
+%and the community task-distribution method initially invokes the
+%primary web service and only if the primary web service is
+%unavailable, the method invokes the next backup web services as
+%they are ordered in the coordination chain. We believe that this
+%coordination chain limits the cooperation power as it introduces a
+%sort of hierarchy. However, in pure and open cooperative models,
+%such as the one we propose in this paper, active cooperation
+%activities engaging simultaneously many agents so that they can
+%perform the tasks more efficiently are being used. Moreover, if
+%the availability is high, which is the case nowadays with the
+%recent advancements in cloud infrastructures and hardware technologies, the
+%backup web services will end-up having a very low chance of
+%getting jobs, especially the ones further in the chain. This will
+%results in a considerable waste of web services capabilities.
+%
+%All the proposed frameworks share a common aspect, which is providing the solution based on assumption of having complete information of all services and performing evaluations based on a large number of input each time they want to adopt a strategic decision making process.
+%So basically, these solutions generally suffer from high complexity, which makes decision making very hard, even impossible in some cases in a real-time fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.
 We address this issue by introducing DDM a framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another.
@@
 \\
-
-\noindent \textbf{Web Service Communities}
-
-Here we introduce the related research work regarding the engineering and formation of communities of web services.
+%
+%\noindent \textbf{Web Service Communities}
+%
+%Here we introduce the related research work regarding the engineering and formation of communities of web services.
 In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
@@
 Moreover, the web services selection process is done centrally by the community manager, while we address the problem more realistically from the distributed angle.
-
-In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
-service communities with centralized access across distributed web
-services. They have proposed a framework for web service
-management, query resolution among communities and a query caching
-mechanism executed by the manager to improve the performance of
-query resolution process among many distributed communities. The
-key idea is to cache previous computed results for answering
-future queries. Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
-then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
-proposed an architecture utilizing \emph{Contract-Net} protocol
-for engineering task distribution within communities of web
-services. The protocol is centrally executed by the community
-manager. This architecture has been further extended in
-\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
-conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
-roles have been distinguished for community members: masters and
-slaves. Master web services are community managers that lead
-communities and are responsible for membership management. They
-can invite and convince slave web services to join the community,
-and attract new slave web services to their communities by
-awarding them better payoff. Moreover, they can eject some slave
-members from the community to improve its overall reputation if
-these members are misbehaving or cannot provide the promised QoS.
-In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
-developed a community as a ``cluster'' that groups Web services
-based on a specific area of interest. All web services in a given
-community share the same functionality. These communities are
-created by \emph{third party community providers} which use the
-\emph{community ontology} as a template and define a set of
-operations that all web services within a community should
-provide. Using semantic analysis on web service operations, web
-services either find and join a community with similar
-functionality or create a new operation description for a new
-community. The authors have described the concept of
-\emph{community agents} associated to \emph{community providers}.
-A community agent is responsible, among other things, of the
-registration of services with the community. An example of a
-community that provides health care services to senior citizens
-has been used. In this example, a governmental entity is needed to
-check the health care standards used by the members before
-authorizing them to be part of the community. Such a central
-entity is represented by the community agent. Thus, community
-agents are playing the role of community managers. In a close work
-\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
-global planning selection algorithm and a delegation algorithm to
-be run when a request to execute an operation is received by the
-community. This needs a central entity to run those algorithms.
-Such entity plays the same role as the community coordinator or
-manager. All these proposals have in common the consideration
-of the central entity for community management, which includes the hiring and firing of the community members, while our approach is fully distributed.
+%
+%In \cite{managing-hela-jalel}, Limam and Akaichi have proposed web
+%service communities with centralized access across distributed web
+%services. They have proposed a framework for web service
+%management, query resolution among communities and a query caching
+%mechanism executed by the manager to improve the performance of
+%query resolution process among many distributed communities. The
+%key idea is to cache previous computed results for answering
+%future queries. Maamar et al. initially in \cite{conf/webist/MaamarLBTS07} and
+%then comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}
+%proposed an architecture utilizing \emph{Contract-Net} protocol
+%for engineering task distribution within communities of web
+%services. The protocol is centrally executed by the community
+%manager. This architecture has been further extended in
+%\cite{CSTintercommunity, conf/IEEEscc/BenharrefSBB11,
+%conf/IEEEscc/KhosravifarBMMT10, conf/aina/LimTM11}. Two types of
+%roles have been distinguished for community members: masters and
+%slaves. Master web services are community managers that lead
+%communities and are responsible for membership management. They
+%can invite and convince slave web services to join the community,
+%and attract new slave web services to their communities by
+%awarding them better payoff. Moreover, they can eject some slave
+%members from the community to improve its overall reputation if
+%these members are misbehaving or cannot provide the promised QoS.
+%In \cite{Medjahed05adynamic}, Medjahed and Bouguettaya have
+%developed a community as a ``cluster'' that groups Web services
+%based on a specific area of interest. All web services in a given
+%community share the same functionality. These communities are
+%created by \emph{third party community providers} which use the
+%\emph{community ontology} as a template and define a set of
+%operations that all web services within a community should
+%provide. Using semantic analysis on web service operations, web
+%services either find and join a community with similar
+%functionality or create a new operation description for a new
+%community. The authors have described the concept of
+%\emph{community agents} associated to \emph{community providers}.
+%A community agent is responsible, among other things, of the
+%registration of services with the community. An example of a
+%community that provides health care services to senior citizens
+%has been used. In this example, a governmental entity is needed to
+%check the health care standards used by the members before
+%authorizing them to be part of the community. Such a central
+%entity is represented by the community agent. Thus, community
+%agents are playing the role of community managers. In a close work
+%\cite{Zeng:2003:QDW:775152.775211}, Zeng et al. have described a
+%global planning selection algorithm and a delegation algorithm to
+%be run when a request to execute an operation is received by the
+%community. This needs a central entity to run those algorithms.
+%Such entity plays the same role as the community coordinator or
+%manager. All these proposals have in common the consideration
+%of the central entity for community management, which includes the hiring and firing of the community members, while our approach is fully distributed.
 Moreover, the stability of the community has not been investigated.

### 2015-07-12 thesis/thesis/chap1/chap1.tex
changes

@@
 
+In most of the recent work on communities of web service, the solutions consider the architecture of centralized management for communities where most of the decisions are made by the centralized coordinator.
+However, in real world scenarios, decisions made by independent service providers are highly distributed.
+\emph{How can we model a distributed decision making process for the problem of forming communities of services?
+[R4]}
+
+Also in all of the mentioned proposals, the community manager as a centralized entity, has complete information of all the web services and their quality.
+However, centrality and complete information are strong assumptions, which are not fully compatible with real business scenarios.
+\emph{How can we train web services based on limited information to operate efficiently? [R5]}
+
 Within communities, services can exhibit competitive behavior as they provide the same functionalities and the number of users requests is finite.
@@
 The relevant question to be addressed is: \emph{How can we design a community model where both competitive and cooperative behaviors exist?
-[R4]}
-
-In most of the recent work on communities of web service, the solutions consider the architecture of centralized management for communities where most of the decisions are made by the centralized coordinator.
-However, in real world scenarios, decisions made by independent service providers are highly distributed.
-\emph{How can we model a distributed decision making process for the problem of forming communities of services?
-[R5]}
-
-Also in all of the mentioned proposals, the community manager as a centralized entity, has complete information of all the web services and their quality.
-However, centrality and complete information are strong assumptions, which are not fully compatible with real business scenarios.
-\emph{How can we train web services based on limited information to operate efficiently? [R6]}
+[R6]}
 
@@
 The rest of the proposal is organized as follows: We present in Chapter 2 the background needed for our research along with relevant related work.
+We introduce the web services and the concept of communities of web services and the theoretical background used throughout the these.
 Chapter 3 provides an efficient method of coalition formation for web services.
-In Chapter 4 we discuss the cooperative behaviour within the communities of web services.
-Chapter 5 presents a distributed method of formation of web services communities.
+In this chapter we have addressed $[R1]$, $[R2]$, $[R3]$ research questions on efficient ways of community formation.
+Chapter 4 presents a distributed method of formation of web services communities.
+In this chapter we address $[R4]$, $[R5]$ research questions by proposing DDM, a distributed decision making mechanism for our web services which can perform in distributed manner and when information is incomplete.
+In Chapter 5 we delve into internal management of communities of web services and we address the $[R6]$ research question by analyzing the cooperative behaviour within the communities of web services.
 Finally in Chapter 6, we present our conclusion and future plan.

### 2015-07-12 thesis/thesis/chap2/chap2.tex
changes

@@
 forecasting, ticket selling, shopping apps, local maps and places
-searching.
+searching are some of them.
 
@@
 
-Cooperative game is a branch of game theory that studies
+The theory of cooperative games is a branch of game theory that is a branch of game theory that studies
 strategies of self-interested entities or agents in a setting
@@
 
-        The second criteria is called the \emph{feasibility} condition,
+        The second criterion is called the \emph{feasibility} condition,
         according to which, the payoff for each agent cannot be more than
@@
             benefit significantly, or within a constant amount($\epsilon$) by
-            deviating (see Equation \ref{eq:core}).
+            deviating (see Equation \ref{eq:core2}).
 
@@
 One may drop the stability requirement and focus on other types of solutions for which a payoff division is guaranteed to exist.
-Two well known solution concepts in this category are \emph{nucleolus}\cite{schmeidler_nucleolus_1969} and the \emph{bargaining set}\cite{Davis67existenceof}.
+Two well known solution concepts in this category are \emph{nucleolus} \cite{schmeidler_nucleolus_1969} and the \emph{bargaining set} \cite{Davis67existenceof}.
 They try to minimize some measure of unhappiness in the game for the agents.
@@
 It would only make sense for a coalition to deviate if the gain from a deviation exceeds the cost of performing the deviation.
-\emph{$\epsilon$-core} relaxes the notion of the core, and only requires that no coalition would benefit significantly, or within a constant amount($\epsilon$) by deviating (see Equation \ref{eq:core}).
+\emph{$\epsilon$-core} relaxes the notion of the core, and only requires that no coalition would benefit significantly, or within a constant amount($\epsilon$) by deviating (see Equation \ref{eq:core3}).
 
-           \begin{equation}\label{eq:core2}
+           \begin{equation}\label{eq:core3}
                \forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
@@
 
-In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
+Here we introduce the related research work regarding the engineering and formation
+of communities of web services. In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
 defined communities as \emph{Service Containers} that aggregate
@@
 sort of hierarchy. However, in pure and open cooperative models,
-such as the one we propose in this paper, active cooperation
+such as the one we propose in this thesis, active cooperation
 activities engaging simultaneously many agents so that they can
@@
 In \cite{alchieri:a}, the authors present a dependable framework for cooperative service agents that is based on the tuple space coordination model.
-The intrusion-tolerant perspective is emphasized in this paper where several security mechanisms are developed to enable a reliable coordination system.
+The intrusion-tolerant perspective is emphasized in the paper where several security mechanisms are developed to enable a reliable coordination system.
 %In \cite{Maximilien2}, authors propose %ontology for quality of service.
@@
 
-In this research work, as the first contribution we will tackle with the issue of community formation in an efficient way for all the web service and communities involved.
+In this thesis, as the first contribution, we will tackle the issue of community formation in an efficient way for all the web services and communities involved.
 We will use game theory to propose a cooperative game model for the aggregation of web services within communities.
 The solution concepts of our cooperative game seeks to find efficient ways of forming coalitions (teams) of web services so that they can maximize their gain and payoff, and distribute the gain in a fair way among all the web services.
-Achieving Fairness when the gain is distributed among the community members is the main factor to keep the coalition stable as no web service will expect to gain better by deviating from the community.
+Achieving fairness when the gain is distributed among the community members is the main factor to keep the coalition stable as no web service will expect to gain better by deviating from the community.
 In other words, the coalition is made efficient if all the members are satisfied.

### 2015-07-12 thesis/thesis/chap3/chap3.tex
changes

@@
 
-\subsection{Coopetitive Behavior}\label{sb:resutlscoop}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In this section, we proposed a cooperative game theory-based model for the aggregation of web services within communities.
+In this chapter, we proposed a cooperative game theory-based model for the aggregation of web services within communities.
 The goal of our services is to maximize efficiency by collaborating and forming stable coalitions.
@@
 
-As future work in this area, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications.
+%As future work in this area, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications.
 From web service perspective, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks.
@@
 In this chapter, we assumed our web services and communities have compelte knowledge of all the other web services and their parameters.
-In next section we propose distributed decision making model which can perform in scenarios where information is incomplete.
+In next chapter we propose distributed decision making model which can perform in scenarios where information is incomplete.

### 2015-07-12 thesis/thesis/chap4/chap4.tex
changes

@@
 
-Over the past years, online services have become an important part of many scalable business applications.
-The increasing reliance on online service providers has significantly influenced the way web services are engineered.
-Given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue.
+Given the dynamic and unpredictable nature of the Internet, delivering high quality services is a critical and challenging issue.
 One practical solution towards delivering such quality services is utilizing intelligent decision making agents.
@@
 
-\section{Preliminaries and Challenging Issues}\label{s4:preliminaries}
+\section{Challenging Issues}\label{s4:preliminaries}
 %In this section, we first present the architecture of DDM.
@@
 To do this, we first discuss some preliminaries.
-In this section, we discuss the preliminary concepts of communities of web services and introduce the challenges behind community formation.
-
-\subsection{Web Services}\label{s:ws}
-
-In the recent years, online services have become a standard part of daily life around the globe.
-Many modern applications rely on web services from different providers.
-For instance, many mobile and tablet applications that have limited storage and processing power are merely aggregating information from different online services.
-Examples are vast, including weather forecasting, ticket selling, shopping apps, local maps and location services.
-
-The World Wide Web Consortium (W3C) defines web services as ``software systems designed to support interoperable machine-to-machine interaction over a network.
-It has an interface described in a machine-processable format (specifically WSDL).
-Other systems interact with the web service in a manner prescribed by its description using SOAP messages, typically conveyed using HTTP with XML serialization in conjunction with other Web-related standards''.
-When developers declare a new web service, it will be
-discovered based on its description, which fully discloses its functionalities.
-Developers also have to declare a public interface and a readable documentation to help other developers when integrating different services \cite{w3cwsdl}.
-Nowadays, web API, standards that do not require XML-based web service protocols like SOAP and WSDL are also emerging.
-They are called RESTful (representational state transfer) services, which are moving towards simpler communication protocols.
-%They are not restricted
-%to XML formats, recently JSON, a human readable and simpler format
-%is becoming popular among online service providers.
-
-We are not going to delve into the engineering details of online web service implementation and its protocols in this thesis.
-We are interested in web services from a business model perspective.
-Service providers usually charge end users for services they provide.
-For example, Google has listed pricing and plans for a wide range of services they provide on their web service console page\footnote{$https://code.google.com/apis/console$}.
-
-As in other proposals \cite{journals/mags/BaldoniBM10,10.1109/TSC.2012.12,DBLP:conf/IEEEscc/KhosravifarABT11}, in this paper, we abstract web services as rational agents\footnote{The term rational is used here in the sense that web services are utility maximizers.} that provide services to end users.
-They aim to maximize their individual income  by receiving enough requests from end users.
-In order to increase their revenues, web services seek for more tasks if they have the capacity and throughput to do so.
-Web services can join communities to enhance efficiency by collaborating with others, to have access to broad market share, and for the opportunity to receive a bigger task pool from end users.
-Furthermore, the high reliance on web services has resulted in increased quality expectations from end users.
-Communities of web services can provide higher availability, performance, reliability, and recovery for end users.
-
-\subsection{Web Service Communities}\label{s:wsc}
-
-The community of web services is essentially a virtual group of web services having similar functionalities \cite{DBLP:journals/ijebr/MaamarSTBB09}.
-Communities aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols to those used by single web services.
-Web services join communities to increase utility by having a larger market share and task pool.
-The community coordinator is responsible for securing the community, managing membership requests from web services and distributing user tasks among the community members.
-The coordinator tries to attract quality web services to join and keep the community as stable and productive as possible to gain better reputation and user satisfaction, which increases the community's market share.
-How web services reside within communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
+In this section, we introduce the challenges behind community formation.
 
@@
 
-Our plan for future work is to advance learning process on the training set that we provided in our work.
+%Our plan for future work is to advance learning process on the training set that we provided in our work.
 SVN machine learning algorithm are suitable in classification of our training data set, to better classify correct or wrong decisions based on long-term utility gains, as data set outputs.

### 2015-07-13 thesis/thesis/chap3/chap3.tex
changes

@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=2.8in]{Figures/task_done_opt.eps}
-\includegraphics[width=2.8in]{Figures/task_qos_opt.eps}
+\includegraphics[width=3.5in]{Figures/task_done_opt.eps}
+\includegraphics[width=3.5in]{Figures/task_qos_opt.eps}
 \caption{Part (a): Cumulative number of requests successfully
@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{Figures/least_core.eps}
+\includegraphics[width=3.5in]{Figures/least_core.eps}
 \caption{Analysis of \emph{$\epsilon$-core} set non-emptiness, for different values of $\epsilon$} \label{f_leastcore}
@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{Figures/s2_task_done.eps}
-\includegraphics[width=3in]{Figures/s2_task_qos.eps}
+\includegraphics[width=3.5in]{Figures/s2_task_done.eps}
+\includegraphics[width=3.5in]{Figures/s2_task_qos.eps}
 \caption{Part (a): Cumulative number of tasks succesfully done. Part
@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3in]{Figures/taxtation.eps}
+\includegraphics[width=4in]{Figures/taxtation.eps}
 \caption{Analysis of community subsiding coefficient $\lambda$ on
@@
 user's point of view.
-\centerline{\includegraphics[width=6.8in]{Figures/tax_dyn.eps}}
+\centerline{\includegraphics[width=7in]{Figures/tax_dyn.eps}}
 \caption{Analysis of community subsiding coefficient $\lambda$
@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=2.5in]{Figures/s2_task_done.eps}
-\includegraphics[width=2.5in]{Figures/s2_task_qos.eps}
+\includegraphics[width=3.5in]{Figures/s2_task_done.eps}
+\includegraphics[width=3.5in]{Figures/s2_task_qos.eps}
 \caption{Part (a): Cumulative number of tasks successfully done.
@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=1.9in]{Figures/avg_task_ws_done.eps}
-\includegraphics[width=1.9in]{Figures/avg_qos_ws_done.eps}
-\includegraphics[width=1.9in]{Figures/avg_avail_ws_done.eps}
+\includegraphics[width=3.5in]{Figures/avg_task_ws_done.eps}
+\includegraphics[width=3.5in]{Figures/avg_qos_ws_done.eps}
+\includegraphics[width=3.5in]{Figures/avg_avail_ws_done.eps}
 \caption{A comparison between our community model and the High

### 2015-07-13 thesis/thesis/chap6/chap6.tex
changes

@@
 In our first contributions we focused on stability and fairness for all web services within the communities.
-This model offers an applicable mechanism for membership requests and selection of serb services.
+In this work we addressed the shortcomings of community formation in recent work such as considering best strategies which benefit all services involved, making solutions practical in real-time settings and also fairness and stability of communities.
+The proposed model offers an applicable mechanism for membership requests and selection of web services.
 The ultimate goal is to increase revenue by improving user satisfaction, which comes from the ability to perform more tasks with high quality.
 
-In our next step of research work, the focus was on inter-community interaction between services involved within the community.
-The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behaviour of intelligent services that are active within communities.
-We considered two acting strategies where service agenets expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers.
-Our proposed model advances the state-of-the-art in cooperative systems by enabling intelligent agent-based services to effectively choose their interacting strategies that lead to optimal outcomes.
-The proposed framework provides a reasoning technique that service agents can use to increase their overall obtained utilities.
-The theoretical results presented in this paper are also backed by simulation results using a real services dataset.
-Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
-services deviate from the coopetitive strategy suggested by our decision-making mechanism the more they make less benefits.
-Thus, deviating from our coopetitive strategy yields less income for the service.
-
-In our final step of the work, we proposed DDM, a strategic distributed decision making mechanism that regulates the community formation process and  membership management in communities of web services.
-This mechanism helps web services and communities decide with whom to be grouped and cooperate.
+In our next step of research work, we proposed DDM, a strategic distributed decision making mechanism that regulates the community formation process and membership management in communities of web services.
+In this work we tried to tackle the issue of autonomous web services not having a centralized architecture and complete information of all the parameters of other web services.
+The proposed mechanism helps web services and communities decide with whom to be grouped and cooperate.
 DDM first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
@@
 The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.
+
+In our final step of the work, the focus was on inter-community interaction between services involved within the community.
+The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behaviour of intelligent services that are active within communities.
+We considered two acting strategies where service agenets expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers.
+Our proposed model advances the state-of-the-art in cooperative systems by enabling intelligent agent-based services to effectively choose their interacting strategies that lead to optimal outcomes.
+The proposed framework provides a reasoning technique that service agents can use to increase their overall obtained utilities.
+The theoretical results presented in this thesis are also backed by simulation results using a real services dataset.
+Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
+services deviate from the coopetitive strategy suggested by our decision-making mechanism the more they make less benefits.
+Thus, deviating from our coopetitive strategy yields less income for the service.
+
+%Our plan for future work is to advance learning process on the training set that we provided in our work.
+SVN machine learning algorithm are suitable in classification of our training data set, to better classify correct or wrong decisions based on long-term utility gains, as data set outputs.
+This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.
+
+%As future work in this area, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications.
+From web service perspective, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks.
+Also bargaining theory from cooperating game theory concepts can be used to help web services resolve the instability and unfairness issues by side payments.
+
+%As future work, we plan to consider the user role in the game to obtain more accurate results when users act rationally.
+Moreover, we would like to achieve a collusion resistant efficiency mechanism, which is still an open problem in open environments.
 

### 2015-07-14 thesis/thesis/chap6/chap6.tex
changes

@@
 The ultimate goal is to increase revenue by improving user satisfaction, which comes from the ability to perform more tasks with high quality.
+The theoretical and extensive simulation results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-optimal decision making mechanisms.
 
@@
 The ultimate goal of our mechanism is to choose the best decision when it comes to community formation, which goes beyond short-term utility increasing choices, usually considered in the literature.
+We performed excrements using real date from 142 users on 4,532 web services during 64 different time slots.
 The experimental results show that our approach allows web services and communities, in real-world-like environments, to make near-perfect decisions.
-The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.
+Moreover, the experiments using real data samples support the need for a long-term training model in a successful decision making process.
 
@@
 The theoretical results presented in this thesis are also backed by simulation results using a real services dataset.
+Moreover, we conduct extensive simulations, analyze various scenarios, and confirm the obtained theoretical results using parameters from a real services dataset on the web.
 Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
 services deviate from the coopetitive strategy suggested by our decision-making mechanism the more they make less benefits.
-Thus, deviating from our coopetitive strategy yields less income for the service.
 

### 2015-07-15 thesis/thesis/abstract.tex
changes

@@
 However, forming optimal and stable communities as coalitions to maximize individual and group efficiency and income for all the involved parties has not been addressed yet.
-Also, in the proposed frameworks of these communities, a common assumption is that residing services, which are supposed to be autonomous and intelligent, are competing over received requests.
+Moreover, in the proposed frameworks of these communities, a common assumption is that residing services, which are supposed to be autonomous and intelligent, are competing over received requests.
 However, those services can also exhibit cooperative behaviors, for instance in terms of substituting each other.
@@
 
-In this thesis, we first identify the problem of defining efficient algorithms for coalition formation mechanisms within communities and propose some results using cooperative game-theoretic techniques.
-We propose a mechanism for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities.
-Then in order to address the coopetitive relation within our web services, we propose a decision making mechanism for our web services to efficiently choose competition or cooperation strategies to maximize their payoffs.
-We prove that the proposed decision mechanism is
-efficient and can be implemented in time linear in the length of the time period considered for the analysis and the number of services in the community. Moreover, we conduct extensive
-simulations, analyze various scenarios, and confirm the obtained theoretical results using parameters from a real web services dataset.
+In this thesis, we first identify the problem of defining efficient algorithms for coalition formation mechanisms.
+We study the community formation problem in two different settings: 1) Communities with centralized manager having complete information using cooperative game-theoretic techniques 2) Communities with distributed decision making mechanisms having incomplete information using training methods.
+We propose mechanisms for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities.
+Then in order to address the coopetitive relation within communities of web services, we propose a decision making mechanism for our web services to efficiently choose competition or cooperation strategies to maximize their payoffs.
+We prove that the proposed decision mechanism is efficient and can be implemented in time linear in the length of the time period considered for the analysis and the number of services in the community.
+Moreover, we conduct extensive simulations, analyze various scenarios, and confirm the obtained theoretical results using parameters from a real web services dataset.
 

### 2015-07-15 thesis/thesis/chap1/chap1.tex
changes

@@
 
-Web service communities are dynamic by design
+Web services communities are dynamic by design
 \cite{DBLP:journals/ijebr/MaamarSTBB09}. In these communities, web
@@
 
-\subsection{Contribution 2: Distributed decision making for dynamic formation of web services communities.}
+\subsection{Contribution 2: Distributed Decision Making for Dynamic Formation of Web Services Communities}
 
@@
 %
-%Web service communities are dynamic by design
+%Web services communities are dynamic by design
 %\cite{DBLP:journals/ijebr/MaamarSTBB09}. In these communities, web

### 2015-07-15 thesis/thesis/chap2/chap2.tex
changes

@@
 
-\subsection{Web Service Communities}\label{sec:CWSDefinition}
+\subsection{Web Services Communities}\label{sec:CWSDefinition}
 Community refers to ``the condition of sharing or having certain
@@
 \cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
-web service communities as a collection of web services with a
+web services communities as a collection of web services with a
 common functionality but different QoS properties. A community
@@
 
-\subsection{Web Service Community Formation}\label{sec:communities_for_rel}
+\subsection{Web Services Community Formation}\label{sec:communities_for_rel}
 

### 2015-07-15 thesis/thesis/chap3/chap3.tex
changes

@@
 
-\subsection{Web Service Communities}\label{webservice-communities}
+\subsection{Web Services Communities}\label{webservice-communities}
 
@@
 \centerline{\includegraphics[width=15cm]{Figures/archss.eps}}
-\caption{Architecture of Web Service communities}
+\caption{Architecture of Web Services communities}
 \label{fig_community}
@@
 
-In this section, we present  web services and community coordinator's interactions, the task distribution process and revenue models in web service communities.
+In this section, we present  web services and community coordinator's interactions, the task distribution process and revenue models in web services communities.
 
@@
 
-The revenue function of the web service community is a linear function of $Out(C)$ with a positive constant multiplier.
+The revenue function of the web services community is a linear function of $Out(C)$ with a positive constant multiplier.
 
@@
 
-In this section, we present different web service community models
+In this section, we present different web services community models
 and focus on the problem of how both web services and community
@@
 among the community members. We have analyzed the effect of
-subsiding and the cost it incurs to our web service communities.
+subsiding and the cost it incurs to our web services communities.
 Figure \ref{f_taxtation} shows the results. In this experiment, we
@@
 %As future work in this area, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications.
-From web service perspective, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks.
+From web service perspective, the work can be extended to consider web services compositions where a group of web services having different set of skills cooperate to perform composite tasks.
 Also bargaining theory from cooperating game theory concepts can be used to help web services resolve the instability and unfairness issues by side payments.

### 2015-07-15 thesis/thesis/chap4/chap4.tex
changes

@@
 
-Web Service communities have the advantages of facilitating web service discovery and providing better quality of service compared to individual services.
+Web Services communities have the advantages of facilitating web service discovery and providing better quality of service compared to individual services.
 Communities act as abstract web services, communicating with external entities via the same standard protocols that a normal web service employs.
@@
 \centering
-\includegraphics[width=3.5in]{figures/utility_gain.eps}
+\includegraphics[width=5in]{figures/utility_gain.eps}
 \caption{DDM against Rational: utility gain }
@@
 \centering
-\includegraphics[width=3.5in]{figures/utility_ratio.eps}
+\includegraphics[width=5in]{figures/utility_ratio.eps}
 \caption{DDM against Rational: ratio of utility gain}
@@
 \centering
-\includegraphics[width=3.5in]{figures/roc.eps}
+\includegraphics[width=4in]{figures/roc.eps}
 \caption{RoC Curve}
@@
 \centering
-\includegraphics[width=3.5in]{figures/stats1.eps}
+\includegraphics[width=4in]{figures/stats1.eps}
 \caption{Overall utility of all the communities}
@@
 \centering
-\includegraphics[width=3.5in]{figures/stats2.eps}
+\includegraphics[width=4in]{figures/stats2.eps}
 \caption{Utility gain over time}
@@
 \centering
-\includegraphics[width=3.5in]{figures/stats3.eps}
+\includegraphics[width=4in]{figures/stats3.eps}
 \caption{Average community size}
@@
 %
-%\noindent \textbf{Web Service Communities}
+%\noindent \textbf{Web Services Communities}
 %
@@
 in \cite{DBLP:journals/ijebr/MaamarSTBB09}.
-The authors introduced web service communities as a collection of web services with a common functionality but different QoS properties.
+The authors introduced web services communities as a collection of web services with a common functionality but different QoS properties.
 A community manager, upon receiving a request, delegates the request to one of its current members.

### 2015-07-15 thesis/thesis/chap6/chap6.tex
changes

@@
 $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications.
-From web service perspective, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks.
+From web service perspective, the work can be extended to consider web services compositions where a group of web services having different set of skills cooperate to perform composite tasks.
 Also bargaining theory from cooperating game theory concepts can be used to help web services resolve the instability and unfairness issues by side payments.

### 2015-07-15 thesis/thesis/chap1/chap1.tex
behaivour

@@
 In this chapter we address $[R4]$, $[R5]$ research questions by proposing DDM, a distributed decision making mechanism for our web services which can perform in distributed manner and when information is incomplete.
-In Chapter 5 we delve into internal management of communities of web services and we address the $[R6]$ research question by analyzing the cooperative behaviour within the communities of web services.
+In Chapter 5 we delve into internal management of communities of web services and we address the $[R6]$ research question by analyzing the cooperative behavior within the communities of web services.
 Finally in Chapter 6, we present our conclusion and future plan.

### 2015-07-15 thesis/thesis/chap4/chap4.tex
behaivour

@@
 
-In next chapter, we analyse the internal community behaviour of web services, and propose a model for competing and cooperating agents within the communities of web services.
+In next chapter, we analyse the internal community behavior of web services, and propose a model for competing and cooperating agents within the communities of web services.

### 2015-07-15 thesis/thesis/chap6/chap6.tex
behaivour

@@
 In our final step of the work, the focus was on inter-community interaction between services involved within the community.
-The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behaviour of intelligent services that are active within communities.
+The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behavior of intelligent services that are active within communities.
 We considered two acting strategies where service agenets expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers.

### 2015-07-15 thesis/thesis/abstract.tex
changes

@@
 In this thesis, we first identify the problem of defining efficient algorithms for coalition formation mechanisms.
-We study the community formation problem in two different settings: 1) Communities with centralized manager having complete information using cooperative game-theoretic techniques 2) Communities with distributed decision making mechanisms having incomplete information using training methods.
+We study the community formation problem in two different settings: (1) Communities with centralized manager having complete information using cooperative game-theoretic techniques (2) Communities with distributed decision making mechanisms having incomplete information using training methods.
 We propose mechanisms for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities.

### 2015-07-15 thesis/thesis/chap5/chap5.tex
changes

@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[scale=0.47]{Figures/graphbgtmed.eps}
-\includegraphics[scale=0.47]{Figures/graphrep.eps}
+\includegraphics[scale=0.55]{Figures/graphbgtmed.eps}
+\includegraphics[scale=0.55]{Figures/graphrep.eps}
 \caption{Part (a): Cumulative community budget comparison. Part
@@
 \centering
-\includegraphics[scale=0.35]{Figures/graphtaskdone.eps}
-\includegraphics[scale=0.35]{Figures/graphtasksatisfaction.eps}
-\includegraphics[scale=0.35]{Figures/graphavgqostask.eps}
+\includegraphics[scale=0.55]{Figures/graphtaskdone.eps}
+\includegraphics[scale=0.55]{Figures/graphtasksatisfaction.eps}
+\includegraphics[scale=0.55]{Figures/graphavgqostask.eps}
 \caption{Overall performance from community's point of view. Part
@@
 %\centering
-\includegraphics[scale=0.47]{Figures/graphdev.eps}
-\includegraphics[scale=0.47]{Figures/graphdev2.eps}
+\includegraphics[scale=0.55]{Figures/graphdev.eps}
+\includegraphics[scale=0.55]{Figures/graphdev2.eps}
 \caption{Utility loss while deviating from our coopetitive
@@
 
-Our model has the advantage of being simple and taking into account three important factors: (1) rational services seek better status in the environment by joining the community; (2) rational information service agents obtain higher payoff by truth telling; and (3) the community is obtaining more effective web services while the information service agents challenge for providing truthful information.
-As future work, we plan to consider the user role in the game to obtain more accurate results when users act rationally.
+Our model has the advantage of being simple and taking into account three important factors: (1) rational web services seek better status in the environment by joining the community; (2) rational web services obtain higher payoff by truth telling; and (3) the community is obtaining more effective web services
+%As future work, we plan to consider the user role in the game to obtain more accurate results when users act rationally.
 Moreover, we would like to achieve a collusion resistant efficiency mechanism, which is still an open problem in open environments.

### 2015-07-15 thesis/thesis/chap6/chap6.tex
changes

@@
 
-In this theses we proposed three models for aggregation of web services within communities.
+In this theses, we proposed three models for aggregation of web services within communities.
 The goal of our models are to maximize efficiency by collaborating and forming stable communities.
-In our first contributions we focused on stability and fairness for all web services within the communities.
+In our first contributions, we focused on stability and fairness for all web services within the communities.
 In this work we addressed the shortcomings of community formation in recent work such as considering best strategies which benefit all services involved, making solutions practical in real-time settings and also fairness and stability of communities.
@@
 In fact, the decision making mechanism is implemented as a decision tree of possible viable strategies along with their long-term expected utility.
-The ultimate goal of our mechanism is to choose the best decision when it comes to community formation, which goes beyond short-term utility increasing choices, usually considered in the literature.
+The ultimate goal of our mechanism is to make a better decision when it comes to community formation, which goes beyond short-term utility increasing choices, usually considered in the literature.
 We performed excrements using real date from 142 users on 4,532 web services during 64 different time slots.
@@
 The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behavior of intelligent services that are active within communities.
-We considered two acting strategies where service agenets expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers.
+We considered two acting strategies where service agents expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers.
 Our proposed model advances the state-of-the-art in cooperative systems by enabling intelligent agent-based services to effectively choose their interacting strategies that lead to optimal outcomes.
@@
 Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
-services deviate from the coopetitive strategy suggested by our decision-making mechanism the more they make less benefits.
+services deviate from the coopetitive strategy suggested by our decision-making mechanism the less benefits they make.
 
@@
 From web service perspective, the work can be extended to consider web services compositions where a group of web services having different set of skills cooperate to perform composite tasks.
-Also bargaining theory from cooperating game theory concepts can be used to help web services resolve the instability and unfairness issues by side payments.
+Also bargaining theory from cooperative game theory concepts can be used to help web services resolve the instability and unfairness issues by side payments.
 
-For the distributed model, our future work is to advance further the learning process on the training set we provided in our work by leveraging some game theoretical approaches.
+For the distributed model, our future plan is to advance further the learning process on the training set we provided in our work by leveraging some game theoretical approaches.
 In fact, game theory provides powerful techniques for strategic decision making, particularly cooperative and coalition formation games.
@@
 
-%\item F.
+\item F.
 Al-Saqqar, J.
@@
 Wan, E.
-Khosrowshahi Asl:, "Model checking temporal knowledge and commitments in multi-agent systems using reduction", Journal of Simulation Modelling Practice and Theory, 2015.
+Khosrowshahi Asl, "Model checking temporal knowledge and commitments in multi-agent systems using reduction", Journal of Simulation Modelling Practice and Theory, 2015.
+
+\item O.
+Marey, J.
+Bentahar, E.
+Khosrowshahi Asl, K.
+Soltan, R.
+Dssouli, "Decision making under subjective uncertainty in argumentation-based agent negotiation", Journal of Ambient Intelligence and Humanized Computing, 2015.
 
@@
 
-%\item H.
-O.
-Marey, J.
-Bentahar, E.
-Khosrowshahi Asl, M.
-Mbarki, R.
-Dssouli, "Agents' Uncertainty in Argumentation-based Negotiation: Classification and Implementation", ANT/SEIT, Hasselt, Belgium, 2014.
+\item O. Marey, J. Bentahar, E. Khosrowshahi Asl, M. Mbarki, R. Dssouli, "Agents' Uncertainty in Argumentation-based Negotiation: Classification and Implementation", ANT/SEIT, Hasselt, Belgium, 2014.
 
-%\item H. Fallatah, J. Bentahar, E. Khosrowshahi Asl, "Social Network-Based Framework for Web Services Discovery", IEEE  FiCloud, Barcelona, Spain, 2014.
+\item H. Fallatah, J. Bentahar, E. Khosrowshahi Asl, "Social Network-Based Framework for Web Services Discovery", IEEE  FiCloud, Barcelona, Spain, 2014.
 

### 2015-07-15 thesis/thesis/chap6/chap6.tex
changes

@@
 From web service perspective, the work can be extended to consider web services compositions where a group of web services having different set of skills cooperate to perform composite tasks.
-Also bargaining theory from cooperative game theory concepts can be used to help web services resolve the instability and unfairness issues by side payments.
+Also bargaining theory from cooperative game theory concepts\cite{RePEc:roc:rocher:554} can be used to help web services resolve the instability and unfairness issues by side payments.
 
 For the distributed model, our future plan is to advance further the learning process on the training set we provided in our work by leveraging some game theoretical approaches.
-In fact, game theory provides powerful techniques for strategic decision making, particularly cooperative and coalition formation games.
-Hedonic games and fractional hedonic games are of particular interest where the utility of a player in a community depends on the identity of the other members of the community and the value this player ascribes to those members.
-We intent to investigate stability solution concepts such as Shapely value so that long-term decisions will be based on the probability that the community will stay for long period.
-The SVM machine learning algorithm is suitable for classification of our training data set to better distinguish  decisions based on long-term utility, as data set outputs.
-This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.
+Hedonic games and fractional hedonic games\cite{Brandl:2015:FHG:2772879.2773307, Aziz_GGMT_70} are of particular interest where the utility of a player in a community depends on the identity of the other members of the community and the value this player ascribes to those members.
+We intent to investigate stability solution concepts such as Shapely value so that long-term decisions will be based on the probability that the community will last for long period.
+The SVM machine learning algorithm\cite{Osuna97trainingsupport, Cortes:1995:SN:218919.218929} is suitable for classification of our training data set to better distinguish  decisions based on long-term utility, as data set outputs.
+This can further facilitate the process of finding optimal cooperators in which will result in enhancing web services' overall performance as service providers.
 

### 2015-07-15 thesis/thesis/abstract.tex
style change

--- 2015-07-15 thesis/thesis/abstract.tex
@@
 In this thesis, we first identify the problem of defining efficient algorithms for coalition formation mechanisms.
-We study the community formation problem in two different settings: 1) Communities with centralized manager having complete information using cooperative game-theoretic techniques 2) Communities with distributed decision making mechanisms having incomplete information using training methods.
+We study the community formation problem in two different settings: 1) Communities with centralized manager having complete information using cooperative game-theoretic techniques.
+2) Communities with distributed decision making mechanisms having incomplete information using training methods.
 We propose mechanisms for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities.

### 2015-07-15 thesis/thesis/abstract.tex
change

@@
 The motivation is to provide these services with high chance of discovery through better visibility, and to enhance their capabilities when it comes to provide requested functionalities.
-There are a number of proposed mechanisms and models on aggregating web services and making them cooperate within their communities.
+There are some proposed mechanisms and models on aggregating web services and making them cooperate within their communities.
 However, forming optimal and stable communities as coalitions to maximize individual and group efficiency and income for all the involved parties has not been addressed yet.
@@
 In this thesis, we first identify the problem of defining efficient algorithms for coalition formation mechanisms.
-We study the community formation problem in two different settings: 1) Communities with centralized manager having complete information using cooperative game-theoretic techniques.
-2) Communities with distributed decision making mechanisms having incomplete information using training methods.
+We study the community formation problem in two different settings: 1) communities with centralized manager having complete information using cooperative game-theoretic techniques; and 2) communities with distributed decision making mechanisms having incomplete information using training methods.
 We propose mechanisms for community membership requests and selections of web services in the scenarios where there is interaction between one community and many web services and scenarios where web services can join multiple established communities.

### 2015-07-15 thesis/thesis/ack.tex
change

I would never have been able to finish my dissertation without the guidance of my committee members, help from friends, and support from my family.

I would like to thank my supervisors, Prof. Jamal Bentahar and Prof. Hadi Otrok for giving me the opportunity to work under their supervision. I am very grateful to them for their valuable suggestions and guidance throughout the preparation of this thesis. I learned a lot of valuable lessons which will be useful for me beyond the scope of this thesis, throughout my lifetime.

I would like to thank my examiner committee Professors Peter Grogono, Ferhat Khendek, Joey Paquet and Muhammad Younas for giving me the honor by being in my PhD committee. Their time and effort are greatly appreciated.

I would like thank my colleague Babak Khosravifar who was always willing to help and give his best suggestions. Also, I would like to thank my friends and lab colleagues Omar Marey, Faisal Al-Saqqar and Khalid Sultan for their help and support.

Finally, I am very grateful to my parents for their understanding, encouragement and their endless support.

### 2015-07-15 thesis/thesis/chap1/chap1.tex
change

@@
 
-In order to address the centralized decision making process limitations and adopt a distributed decision making approach, we introduce DDM\footnote{This contribution is submitted to International Journal of Decision Support Systems as a journal paper}, a Distributed Decision Making model for community formation.
+In order to address the centralized decision making process limitations and adopt a distributed decision making approach, we introduce DDM\footnote{This contribution is submitted to International Journal of Decision Support Systems}, a Distributed Decision Making model for community formation.
 DDM regulates web service agents' decision making process in terms of cooperating and deciding which group to join and which service to invite for joining.
@@
 
-In previous contributions, our focus was on community formation and we emphasised on cooperative behavior of the web services as agents.
+In the previous contributions, our focus was on community formation and we emphasized cooperative behavior of the web services as agents.
 In our next contribution\footnote{This contribution was published in \cite{DBLP:journals/eswa/AslBMKO14}} our focus is on the internal management affairs of communities of web services.

### 2015-07-15 thesis/thesis/chap2/chap2.tex
behaivour
change

@@
 
-        Core stability is a highly desirable property however in many problems it is not achievable.
-It would be more ideal to maintain a set of somewhat stable payoffs when the core is empty.
+        Core stability is a highly desirable property.
+However, in many problems this property is not achievable.
+It would be more ideal to maintain a set of quasi-stable payoffs when the core is empty.
 There are several approaches to achieve this goal.
@@
 It would only make sense for a coalition to deviate if the gain from a deviation exceeds the cost of performing the deviation.
-\emph{$\epsilon$-core} relaxes the notion of the core, and only requires that no coalition would benefit significantly, or within a constant amount($\epsilon$) by deviating (see Equation \ref{eq:core3}).
+\emph{$\epsilon$-core} relaxes the notion of the core, and only requires that no coalition would benefit significantly, or within a constant amount ($\epsilon$) by deviating (see Equation \ref{eq:core3}).
 
@@
 
-\subsection{Coopetitive Behaviour Within Communities of Web Services}\label{sec:coopetetive}
+\subsection{Coopetitive Behavior Within Communities of Web Services}\label{sec:coopetetive}
 
@@
 The computation of solutions for cooperative game theory problems is combinatorial in nature and proven to be NP-complete \cite{Algorithmic}, making this computation impractical in real world applications.
-However, using the concepts of coalition stability, we propose approximation algorithms running in polynomial time providing web services and community masters with applicable and near-optimal decision making mechanisms.
+However, using the concepts of coalition stability, we proposed approximation algorithms running in polynomial time providing web services and community masters with applicable and near-optimal decision making mechanisms.
 
-Next we will tackle the issue of distributed model of web services and propose a decision model for scenarios where information is incomplete.
-We proposed a training model for the problem of membership management of communities of web services.
-Using the traning model we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves.
-This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available.
+Next, we will tackle the issue of distributed model of web services and propose a decision model for scenarios where information is incomplete.
+We will propose a training model for the problem of membership management of communities of web services.
+Using the traning model we aim to create a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves.
+This will equip our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available.
 The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices.
-The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.
+%The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.
 The results of experiments using real data samples support the need for a long-term training model in a successful decision making process.
@@
 In our last contribution, the focus is on internal community management.
-We proposed a game-theoretic based model to analyze the best efficiency characteristics for the active services in open networks.
-The proposed framework considers the chances of web services in joining a community in different cases with truthful and lying information service agents.
-The proposed game analyzes the existing Nash equilibrium and situations where the maximum payoff is obtained.
+We will introduce a game-theoretic based model to analyze the efficiency characteristics for the active services in open networks.
+The proposed framework will consider the chances of web services in joining a community in different cases with truthful and lying information service agents.
+The proposed game will analyze the existing Nash equilibrium and situations where the maximum payoff is obtained.

### 2015-07-15 thesis/thesis/chap3/chap3.tex
change

@@
 terms of task distribution and community revenue. Web service
-cooperative games in different settings will follow along with
-some simulation results.
+cooperative games in different settings will follow along with simulation results.
 
@@
 
-In this chapter, we assumed our web services and communities have compelte knowledge of all the other web services and their parameters.
-In next chapter we propose distributed decision making model which can perform in scenarios where information is incomplete.
+In this chapter, we assumed our web services and communities have complete knowledge of all the other web services and their parameters.
+In the next chapter, we propose distributed decision making model which can perform in scenarios where information is incomplete.

### 2015-07-15 thesis/thesis/chap4/chap4.tex
change

@@
 
-\subsubsection{Input Web Services Data}\label{sss:webservices}
+\bigskip
+\noindent \textbf{A. Input Web Services Data}\label{sss:webservices}
 
@@
 
-\subsubsection{Feature Extraction}\label{sss:filtereddata}
+\bigskip
+\noindent \textbf {B. Feature Extraction}\label{sss:filtereddata}
 
@@
 
-\subsubsection{Feature Engineering}\label{sss:feng}
+\bigskip
+\noindent \textbf {C. Feature Engineering}\label{sss:feng}
+
 Let $CFVS = \{CFV_{<C_1>}, \dots, CFV_{<C_N>}\}$ be the community feature vector set with $N$ communities.
@@
 In this research work, we proposed a training model for the problem of membership management of communities of web services.
-Using the traning model we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves.
-This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore they opted for best decision available.
+Using the training model, we created a decision making profile for each community and web service involved which provides them with a set of feasible and utility increasing moves.
+This utilized our web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, which allowed them to make better decisions.
 The ultimate goal is to choose the best decision when it comes to communities formation, among many possible short-term rational and utility increasing choices.
@@
 
-In next chapter, we analyse the internal community behavior of web services, and propose a model for competing and cooperating agents within the communities of web services.
+In the next chapter, we analyse the internal community behavior of web services, and propose a model for competing and cooperating agents within the communities of web services.

### 2015-07-15 thesis/thesis/chap5/chap5.tex
change

@@
 
-In previous chapter, our focus was on community formation and we emphasised on cooperative behavior of the web services as agents.
+In the previous chapter, our focus was on community formation and we emphasized cooperative behavior of the web services as agents.
 Within communities, the web services, selfish and utility maximizers by nature, can follow two different strategies, namely cooperation and competition in order to increase their payoffs when they provide services to consumers \cite{VuFind-10008938119}.
@@
 %These entities are developed with respect to what is explained in Section \ref{s4:Preliminaries}.
-In this section, the objective is to
-investigate the effectiveness of the proposed strategic system on
+The objective is to investigate the effectiveness of the proposed strategic system on
 intelligent services' overall budget and also the average quality
@@
 
-In this chapter, we proposed a game-theoretic based model to analyze the best efficiency characteristics for the active services in open networks.
+In this chapter, we proposed a game-theoretic based model to analyze the efficiency characteristics for the active services in open networks.
 The proposed framework considers the chances of web services in joining a community in different cases with truthful and lying information service agents.
@@
 
-Our model has the advantage of being simple and taking into account three important factors: (1) rational web services seek better status in the environment by joining the community; (2) rational web services obtain higher payoff by truth telling; and (3) the community is obtaining more effective web services
+Our model has the advantage of being simple and taking into account three important factors: (1) rational web services seek better status in the environment by joining the community; (2) rational web services obtain higher payoff by truth telling; and (3) the community is obtaining more effective web services.
+These advantages are confirmed through the conducted simulations.
 %As future work, we plan to consider the user role in the game to obtain more accurate results when users act rationally.

### 2015-07-15 thesis/thesis/chap6/chap6.tex
change

@@
 
-In this theses, we proposed three models for aggregation of web services within communities.
+In this thesis, we proposed three models for aggregation of web services within communities.
 The goal of our models are to maximize efficiency by collaborating and forming stable communities.
-In our first contributions, we focused on stability and fairness for all web services within the communities.
-In this work we addressed the shortcomings of community formation in recent work such as considering best strategies which benefit all services involved, making solutions practical in real-time settings and also fairness and stability of communities.
+In our first contribution, we focused on stability and fairness for all web services within the communities.
+In this work, we addressed the shortcomings of community formation in recent work such as considering best strategies which benefit all services involved, making solutions practical in real-time settings and taking into account the fairness and stability of communities.
 The proposed model offers an applicable mechanism for membership requests and selection of web services.
@@
 In our next step of research work, we proposed DDM, a strategic distributed decision making mechanism that regulates the community formation process and membership management in communities of web services.
-In this work we tried to tackle the issue of autonomous web services not having a centralized architecture and complete information of all the parameters of other web services.
+In this work, we tried to tackle the issue of autonomous web services not having a centralized architecture and complete information of all the parameters of other web services.
 The proposed mechanism helps web services and communities decide with whom to be grouped and cooperate.
@@
 The ultimate goal of our mechanism is to make a better decision when it comes to community formation, which goes beyond short-term utility increasing choices, usually considered in the literature.
-We performed excrements using real date from 142 users on 4,532 web services during 64 different time slots.
+We performed experiments using real date from 142 users on 4,532 web services during 64 different time slots.
 The experimental results show that our approach allows web services and communities, in real-world-like environments, to make near-perfect decisions.
@@
 The theoretical results presented in this thesis are also backed by simulation results using a real services dataset.
-Moreover, we conduct extensive simulations, analyze various scenarios, and confirm the obtained theoretical results using parameters from a real services dataset on the web.
+Moreover, we conducted extensive simulations, analyzed various scenarios, and confirmed the obtained theoretical results using parameters from a real services dataset on the web.
 Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
@@
 From web service perspective, the work can be extended to consider web services compositions where a group of web services having different set of skills cooperate to perform composite tasks.
-Also bargaining theory from cooperative game theory concepts\cite{RePEc:roc:rocher:554} can be used to help web services resolve the instability and unfairness issues by side payments.
+Also bargaining theory from cooperative game theory concepts \cite{RePEc:roc:rocher:554} can be used to help web services resolve the instability and unfairness issues by side payments.
 
 For the distributed model, our future plan is to advance further the learning process on the training set we provided in our work by leveraging some game theoretical approaches.
-Hedonic games and fractional hedonic games\cite{Brandl:2015:FHG:2772879.2773307, Aziz_GGMT_70} are of particular interest where the utility of a player in a community depends on the identity of the other members of the community and the value this player ascribes to those members.
+Hedonic games and fractional hedonic games \cite{Brandl:2015:FHG:2772879.2773307, Aziz_GGMT_70} are of particular interest where the utility of a player in a community depends on the identity of the other members of the community and the value this player ascribes to those members.
 We intent to investigate stability solution concepts such as Shapely value so that long-term decisions will be based on the probability that the community will last for long period.
-The SVM machine learning algorithm\cite{Osuna97trainingsupport, Cortes:1995:SN:218919.218929} is suitable for classification of our training data set to better distinguish  decisions based on long-term utility, as data set outputs.
-This can further facilitate the process of finding optimal cooperators in which will result in enhancing web services' overall performance as service providers.
+The SVM machine learning algorithm \cite{Osuna97trainingsupport, Cortes:1995:SN:218919.218929} is suitable for classification of our training data set to better distinguish  decisions based on long-term utility, as data set outputs.
+This can further facilitate the process of finding optimal cooperators which will result in enhancing web services' overall performance as service providers.
 
@@
 This is the question in communities of autonomous services", Journal of Expert Systems with Applications, Elsevier, 2014.
-
-\item F.
-Al-Saqqar, J.
-Bentahar, K.
-Sultan, W.
-Wan, E.
-Khosrowshahi Asl, "Model checking temporal knowledge and commitments in multi-agent systems using reduction", Journal of Simulation Modelling Practice and Theory, 2015.
 
@@
 \end{itemize}
+
+\textbf{Collaborated works}
+
+\begin{itemize}
+\item F.
+Al-Saqqar, J.
+Bentahar, K.
+Sultan, W.
+Wan, E.
+Khosrowshahi Asl, "Model checking temporal knowledge and commitments in multi-agent systems using reduction", Journal of Simulation Modelling Practice and Theory, 2015.
+\end{itemize}

### 2015-07-16 thesis/thesis/ack.tex
changes

@@
 I am very grateful to them for their valuable suggestions and guidance throughout the preparation of this thesis.
-I learned a lot of valuable lessons which will be useful for me beyond the scope of this thesis, throughout my lifetime.
+I learned a lot of valuable lessons which will be useful for me beyond the scope of this thesis throughout my lifetime.
+I also would like to thank Prof.
+Rabeb Mizouni for her significant help during my research work.
 
@@
 
-Finally, I am very grateful to my parents for their understanding, encouragement and their endless support.
+Finally, I am very grateful to my fiance and colleague Atieh Saberi and my parents for their understanding, encouragement and their endless support.

### 2015-07-16 thesis/thesis/chap3/chap3.tex
changes

@@
 H. Mahmoud freely available at:
-http://www.uoguelph.ca/\textasciitilde{}qmahmoud/qws/.}. To test
+\url{http://www.uoguelph.ca/\textasciitilde qmahmoud/qws/}.}. To test
 our methods, we formed around 10,000 random coalitions consisting
@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=3.5in]{Figures/s2_task_done.eps}
-\includegraphics[width=3.5in]{Figures/s2_task_qos.eps}
+\includegraphics[width=4in]{Figures/s2_task_done.eps}
+\includegraphics[width=4in]{Figures/s2_task_qos.eps}
 \caption{Part (a): Cumulative number of tasks succesfully done. Part
@@
 %\includegraphics[scale=0.6]{graph1Final+.eps}
-\includegraphics[width=4in]{Figures/taxtation.eps}
+\includegraphics[width=5.5in]{Figures/taxtation.eps}
 \caption{Analysis of community subsiding coefficient $\lambda$ on
@@
 user's point of view.
-\centerline{\includegraphics[width=7in]{Figures/tax_dyn.eps}}
+\centerline{\includegraphics[width=7.5in]{Figures/tax_dyn.eps}}
 \caption{Analysis of community subsiding coefficient $\lambda$

### 2015-07-16 thesis/thesis/chap4/chap4.tex
changes

@@
 We used the web services data set provided in \cite{10.1109/ISSRE.2011.17}.
-The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{http://www.wsdream.net/}.
+The raw data provides real-world QoS evaluation results from several users on 5,825 web services over 64 different time frames\footnote{\url{http://www.wsdream.net/}}.
 %In this data set, each web service is associated with a number of features that reflect its functionality.
@@
 \section{Experiments}\label{s:experiments}
-We implemented DDM in Java\footnote{Source code of implementation and data is available at: $https://github.com/Marooned202/DDM$}.
+We implemented DDM in Java\footnote{Source code of implementation and data is available at: \url{https://github.com/Marooned202/DDM}}.
 We recall that we have extracted the set of features for 4532 web services in 64 different time slots through a data set provided in \cite{10.1109/ISSRE.2011.17}.
@@
 This provides us with the initial training feature set of size $|CFVS| = 10,000$ communities.
-Based on Equation \ref{u_c_load}, the utilities of these communities are estimated, and then the $gain$ matrix of size $|10,000 \times~ 10,000|$ of all possible ways of merging these 10,000 communities is generated\footnote {The template vector and $gain$ matrix generated are available at $https://github.com/Marooned202/DDM/tree/master/wsds/data/run$}.
+Based on Equation \ref{u_c_load}, the utilities of these communities are estimated, and then the $gain$ matrix of size $|10,000 \times~ 10,000|$ of all possible ways of merging these 10,000 communities is generated\footnote {The template vector and $gain$ matrix generated are available at \url{https://github.com/Marooned202/DDM/tree/master/wsds/data/run}}.
 Based on the $gain$ matrix, each community has an ordered preference among other communities in the set.
@@
 \centering
-\includegraphics[width=5in]{figures/utility_gain.eps}
+\includegraphics[width=5.5in]{figures/utility_gain.eps}
 \caption{DDM against Rational: utility gain }
@@
 \centering
-\includegraphics[width=5in]{figures/utility_ratio.eps}
+\includegraphics[width=5.5in]{figures/utility_ratio.eps}
 \caption{DDM against Rational: ratio of utility gain}
@@
 \centering
-\includegraphics[width=4in]{figures/roc.eps}
+\includegraphics[width=5in]{figures/roc.eps}
 \caption{RoC Curve}
@@
 \centering
-\includegraphics[width=4in]{figures/stats1.eps}
+\includegraphics[width=5.5in]{figures/stats1.eps}
 \caption{Overall utility of all the communities}
@@
 \centering
-\includegraphics[width=4in]{figures/stats2.eps}
+\includegraphics[width=5.5in]{figures/stats2.eps}
 \caption{Utility gain over time}
@@
 \centering
-\includegraphics[width=4in]{figures/stats3.eps}
+\includegraphics[width=5.5in]{figures/stats3.eps}
 \caption{Average community size}

### 2015-07-16 thesis/thesis/chap4/chap4.tex
changes

@@
 
-\textbf{Contributions.} In this chapter, we introduce DDM, a Distributed Decision Making model for community formation that regulates web service agents’ decision making process in terms of cooperating and deciding which group to join and which service to invite for joining.
+\textbf{Contributions.} In this chapter, we introduce DDM, a Distributed Decision Making model for community formation that regulates web service agents' decision making process in terms of cooperating and deciding which group to join and which service to invite for joining.
 Unlike existing work on community formation, our decision model is extracted from a data model in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc.
@@
 However, with a high number of possible communities, it is not possible to test collaboration with random web services.
-Even if a linear approximate function for estimating utility based on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell\_number$} growth rate of the possible number of partitions of web services into communities would make any brute-force type algorithm for the best community selection strategy intractable and impractical in real-world application settings.
+Even if a linear approximate function for estimating utility based on community web services' parameters is adopted, the exponential \footnote{Bell number: \url{http://en.wikipedia.org/wiki/Bell_number}} growth rate of the possible number of partitions of web services into communities would make any brute-force type algorithm for the best community selection strategy intractable and impractical in real-world application settings.
 
@@
 \centering
-\includegraphics[width=5.5in]{figures/stats1.eps}
+\includegraphics[width=5in]{figures/stats1.eps}
 \caption{Overall utility of all the communities}
@@
 \centering
-\includegraphics[width=5.5in]{figures/stats2.eps}
+\includegraphics[width=5in]{figures/stats2.eps}
 \caption{Utility gain over time}
@@
 \centering
-\includegraphics[width=5.5in]{figures/stats3.eps}
+\includegraphics[width=5in]{figures/stats3.eps}
 \caption{Average community size}
